### 2018-01-11 slides/2018-01-11-group-meeting/group_meeting.tex
January 11 update. Automated decomp, svd, svs, and basic recons.

\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{graphicx} \DeclareMathOperator{\argmin}{argmin}

\newcommand{\under}[2]{\underset{\scriptscriptstyle#1}{#2}}

\usetheme{simple}
\usecolortheme{}
\usefonttheme{serif}
\useinnertheme{}
\useoutertheme{}
\author{Talon Chandler}
\date{January 10, 2017}
\title{Update On 3D Orientation Reconstruction}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.3.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\begin{frame}[label=sec-1]{Forward Model}
\begin{align*}
g_i = \int_{\mathbb{S}^2}d\hat{\textbf{r}}\ h_i(\hat{\textbf{r}})f(\hat{\textbf{r}})
\end{align*}
\begin{itemize}
\item $g_i$ $\rightarrow$ is the $i$th intensity measurement
\item $h_i(\hat{\textbf{r}})$ $\rightarrow$ is the $i$th point response function
\item $f(\hat{\textbf{r}})$ $\rightarrow$ is the orientation distribution function
\end{itemize}
\end{frame}

\begin{frame}[label=sec-2]{Fourier Transforms}
\begin{align*}
\text{Fourier Transform} \rightarrow F(\nu) &= \int_{\mathbb{R}}dx\ f(x)e^{-2\pi i x\nu}\\
\text{Real Spherical Fourier Transform} \rightarrow F_l^m &= \int_{\mathbb{S}^2}d\hat{\textbf{r}}\ f(\hat{\textbf{r}})y_l^m(\hat{\textbf{r}})\\
\end{align*}
\end{frame}

\begin{frame}{Spherical Harmonics $y_l^m(\mathbf{\hat{r}})$}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true]{figs/picture}
\end{center}
\end{frame}

\begin{frame}{Integral $\rightarrow$ Matrix}
  \begin{align*}
  g_i &= \int_{\mathbb{S}^2}d\hat{\textbf{r}}\ h_i(\hat{\textbf{r}})f(\hat{\textbf{r}})\\ \\
  g_i &= \textbf{H}_i^T\textbf{F}\\ \\
  \mathbf{g} &= \mathbf{\Psi}\textbf{F}
  \end{align*}
\end{frame}

\begin{frame}{Single-view epi-illumination microscope NA = 0.8}
  \begin{align*}
  \mathbf{g} &= \mathbf{\Psi}\textbf{F}
  \end{align*}
\begin{center}
  \includegraphics[width=1.0\textwidth, interpolate=true]{figs/epi/matrix}
\end{center}
\end{frame}

\begin{frame}{Inverting A Rectangular Matrix}
  \fontsize{10pt}{7.2}\selectfont
  \begin{align*}
    \under{N\times 1}{\mathbf{g}} &= \under{N\times M}{\mathbf{\Psi}}\under{M\times 1}{\mathbf{F}}
    \intertext{Decompose $\mathbf{\Psi}$ into three matrices}
                                    \under{N\times 1}{\mathbf{g}} &= \under{N\times N}{\mathbf{U}}\under{N\times M}{\mathbf{\Sigma}}\under{M\times M}{\mathbf{V}^T}\under{M\times 1}{\mathbf{F}}\\
    \intertext{where $\mathbf{U}$ and $\mathbf{V}$ are orthogonal matrices---that is $\mathbf{U}^T = \mathbf{U}^{-1}$ or equivalently $\mathbf{U}^T\mathbf{U} = \mathbf{I}$---and $\mathbf{\Sigma}$ is a diagonal matrix. Solving for $\mathbf{F}$ gives}
    \under{M\times 1}{\mathbf{F}} &= \under{M\times M}{\mathbf{V}}\under{M\times N}{\mathbf{\Sigma}^{-1}}\under{N\times N}{\mathbf{U}^T}\under{N\times 1}{\mathbf{g}}.\\
    \intertext{But wait! $\mathbf{\Sigma}^{-1}$ doesn't exist. Instead, replace every element of $\mathbf{\Sigma}$ with its inverse (except the zeros), takes its transpose, and call it $\mathbf{\Sigma}^+$}
    \under{M\times 1}{\mathbf{F}} &= \under{M\times M}{\mathbf{V}}\under{M\times N}{\mathbf{\Sigma}^{+}}\under{N\times N}{\mathbf{U}^T}\under{N\times 1}{\mathbf{g}}.\\
    \intertext{This gives us the closest we can get to an inverse---the pseudo-inverse}
    \under{M\times 1}{\mathbf{F}} &= \under{M\times N}{\mathbf{\Psi}^{+}}\under{N\times 1}{\mathbf{g}.}
  \end{align*}
\end{frame}

\begin{frame}{Vocabulary}
  \begin{align*}
    \mathbf{\Psi}^{+}&\rightarrow \text{\textbf{pseudo-inverse} of}\ \mathbf{\Psi}\\
    \mathbf{\Psi} = \mathbf{U\Sigma V}^T&\rightarrow \text{\textbf{singular-value decomposition} of}\ \mathbf{\Psi}\\
    \text{Diagonal elements of}\ \mathbf{\Sigma}&\rightarrow \text{\textbf{singular values} of}\ \mathbf{\Psi}\\
    \text{Columns of}\ \mathbf{V}&\rightarrow \text{\textbf{right singular vectors} of}\ \mathbf{\Psi}\\
    \text{Columns of}\ \mathbf{U}&\rightarrow \text{\textbf{left singular vectors} of}\ \mathbf{\Psi}\\        
  \end{align*}
\end{frame}

\begin{frame}{Single-view epi-illumination microscope NA = 0.8}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true]{figs/svs_epi}
\end{center}
\end{frame}

\begin{frame}{Symmetric diSPIM NA = 0.8}
\begin{center}
  \includegraphics[width=1.0\textwidth, interpolate=true]{figs/dispim/matrix}
\end{center}
\end{frame}

\begin{frame}{Symmetric diSPIM, NA = 0.8}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true]{figs/svs_dispim}
\end{center}
\end{frame}

\begin{frame}{Asymmetric diSPIM, NA = 1.1/0.7}
\begin{center}
  \includegraphics[width=1.0\textwidth, interpolate=true]{figs/dispim_asymmetric/matrix}
\end{center}
\end{frame}

\begin{frame}{Asymmetric diSPIM NA = 1.1/0.7}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true]{figs/svs_dispim_asym}
\end{center}
\end{frame}

\begin{frame}{Test phantom - single fluorophores approximated by 7 degrees of spherical harmonics}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true, trim={0 0 0 12cm}]{figs/tp_test.png}
\end{center}
\end{frame}

\begin{frame}{Measured by the asymmetric diSPIM then reconstructed. No priors! Not even positivity ;)}
\begin{center}
  \includegraphics[width=0.8\textwidth, interpolate=true, trim={0 0 0 12cm}]{figs/recon_test.png}
\end{center}
\end{frame}

\begin{frame}{Up Next}
  \begin{itemize}
  \item Incorporating priors---positivity, single fluorophore, rotational symmetry
  \item Math OSA 2-page abstract on Jan 18---I'll include the work in these
    slides. I'll possibly include priors depending on how quickly that goes.
  \end{itemize}
\end{frame}

\begin{frame}[label=sec-12]{Giant Unilamallar Vesicles (GUV)\\ FOV $\approx$ 150 $\times$ 150 $\mu$\text{m}}
\begin{center}
  \includegraphics[width=0.6\textwidth, interpolate=true]{figs/guv.jpg}
\end{center}
\end{frame}
\begin{frame}[label=sec-13]{GUV Protocol}
\begin{center}
  \includegraphics[width=0.9\textwidth, interpolate=true]{figs/schmid2015}
  \raisebox{-10pt}{\makebox[0pt][r]{\footnotesize Schmid, 2015}}
\end{center}
\end{frame}

\begin{frame}[label=sec-14]{GUV Chamber}
\begin{center}
  \includegraphics[width=0.7\textwidth, interpolate=true]{figs/chamber}
  \raisebox{-10pt}{\makebox[0pt][r]{\footnotesize Schmid, 2015}}
\end{center}
\end{frame}
% Emacs 25.3.1 (Org mode 8.2.10)
\end{document}

### 2018-01-11 polharmonic/analyze_epi.py

@@ -1,44 +1,27 @@
 import numpy as np
+import dill
 from util import *
-from dispim_coeffs import *
-import scipy
-np.set_printoptions(precision=2)
-
-# Globals
-theta = Symbol('theta', real=True)
-phi = Symbol('phi', real=True)
-phi_pol = Symbol('phi_pol', real=True)
-A = Symbol('A', real=True)
-B = Symbol('B', real=True)
+from microscopes import *
+np.set_printoptions(precision=2, suppress=True)
 
 # Main script
 print("Working...")
 
-# Test forward and inverse transforms
-# prf = (sin(theta)**2)*(cos(phi - phi_pol)**2)*2*(A + B*sin(theta)**2)
-# Hlm = prf2Hlm_real(prf, max_l=4)
-# prf2 = Hlm2prf_real(Hlm)
-# print(simplify(prf - prf2.rewrite(cos)))
-# import pdb; pdb.set_trace() 
+# Specify saving paths
+folder = 'epi'
+file_name = 'psi_epi.dat'
+data_file = folder+'/'+file_name
 
-# Calculate forward model (time consuming)
-psi, labels = epi_sys_matrix(0.8, 1.33)
-dill.dump([psi, labels], open('psi_epi.dat','wb'))
+# Calculate the system matrix
+# sys_matrix = epi_sys_matrix(NA=0.8, n=1.33, phi_pols=[0, np.pi/4, np.pi/2, 3*np.pi/4])
 
-# Load
-f = open('psi_epi.dat', 'rb')
-psi, labels = dill.load(f)
+# # Save matrix_file
+# dill.dump(sys_matrix, open(data_file,'wb'))
 
-M = psi.shape[0]
-N = psi.shape[1]
+# Load 
+f = open(data_file, 'rb')
+sys_matrix = dill.load(f)
+import pdb; pdb.set_trace() 
 
-ct = np.dot(psi.T, psi)
-pinv = np.linalg.pinv(psi)
-U, s, Vh = np.linalg.svd(psi.real)
-V = Vh.conj().T
-
-# Plot singular distributions
-# plot_spherical_real([1.0], ['3,0'], filename='test.png')
-import pdb; pdb.set_trace()
-for i in range(9):
-    plot_spherical_real(V[:,i], labels, filename='spherical'+str(i)+'.png')
+# Generate plots
+generate_plots(*sys_matrix, folder)

### 2018-01-11 polharmonic/microscopes.py

@@ -1,0 +1,241 @@
+import numpy as np
+from util import *
+from sympy import *
+from sympy.matrices.dense import *
+import sympy.functions.special.spherical_harmonics as sh
+from sft import *
+import dill
+
+# Global initialize symbols
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+Theta = Symbol('Theta', real=True)
+Phi = Symbol('Phi', real=True)
+
+# Helper functions
+def NAn2AB(NA, n):
+    alpha = np.arcsin(NA/n)
+    return alpha2A(alpha), alpha2B(alpha)
+
+def alpha2A(alpha):
+    ca = np.cos(alpha)
+    return 0.25 - 0.375*ca + 0.125*(ca**3)
+
+def alpha2B(alpha):
+    ca = np.cos(alpha)
+    return 0.1875*ca + 0.1875*(ca**3)
+
+# Analytic Hlm functions for specific acquisitions 
+# z light-sheet illumination, x widefield detection
+def illzdetx(phi_pol, NA, n):
+    A, B = NAn2AB(NA, n)    
+    prf = (sin(theta)**2)*(cos(phi - phi_pol)**2)*2*(A + B*(1 - (sin(theta)**2)*(cos(phi)**2)))
+    return sft(prf)
+
+# x light-sheet illumination, z widefield detection
+def illxdetz(phi_pol, NA, n):
+    A, B = NAn2AB(NA, n)    
+    prf = ((sin(theta)*sin(phi)*sin(phi_pol) - cos(theta)*cos(phi_pol))**2)*2*(A + B*(sin(theta)**2))
+    return sft(prf)
+
+# z light-sheet illumination (small NA), z widefield detection
+def illzdetz(phi_pol, NA, n):
+    A, B = NAn2AB(NA, n)
+    prf = (sin(theta)**2)*(cos(phi - phi_pol)**2)*2*(A + B*sin(theta)**2)
+    return sft(prf)
+
+# uniform illumination (all directions), single detector along (Theta, Phi)
+def illalldetpixel(Theta, Phi):
+    prf = 1 - (sin(Theta)*cos(Phi)*sin(theta)*cos(phi) + sin(Theta)*sin(Phi)*sin(theta)*sin(phi) + cos(Theta)*cos(theta))**2
+    return sft(prf)
+
+# Complete system matrix functions
[…]

### 2018-01-11 polharmonic/sft.py

@@ -1,0 +1,58 @@
+from util import *
+import numpy as np
+from sympy import *
+import sympy.functions.special.spherical_harmonics as sh
+
+# Globals
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+
+# Analytic forward spherical Fourier transform
+def sft(f, max_l=4):
+    coeffs = []
+    for l in range(0, max_l+2, 2):
+        for m in range(-l, l+1):
+            print("Integrating: "+ str(l) + ', ' + str(m))            
+            Znm = sh.Znm(l, m, theta, phi).expand(func=True)
+            theta_int = integrate(expand(sin(theta)*Znm*f), (theta, 0, pi)) 
+            final_int = integrate(expand_trig(theta_int), (phi, 0, 2*pi))
+            coeffs.append((simplify(final_int), l, m))
+    dtypes = [('expr', 'O'), ('l', 'i4'), ('m', 'i4')]
+    return np.array(coeffs, dtype=dtypes)
+
+# Numerical forward spherical Fourier transform from delta
+def tp_sft(tp, max_l=4, return_labels=False):
+    labels = []
+    coeffs = []
+    for l in range(0, max_l+2, 2):
+        for m in range(-l, l+1):
+            coeffs.append(spZnm(l, m, tp[0], tp[1]))
+            labels.append(str(l)+','+str(m))
+    if return_labels:
+        return np.array(coeffs), np.array(labels)
+    else:
+        return np.array(coeffs)
+
+def field_tp_sft(tp_field, max_l=4):
+    x, labels = tp_sft(tp_field[0,0,:], max_l=max_l, return_labels=True)
+    return np.apply_along_axis(tp_sft, 2, tp_field, max_l=max_l), labels
+
+# Analytic inverse spherical Fourier transform
+def isft(ylm):
+    f = 0
+    for y in ylm:
+        f += y['expr']*sh.Znm(y['l'], y['m'], theta, phi).expand(func=True)
+    return f
+
+# Tests
+def test_transforms():
+    h1 = 1 - (sin(Theta)*cos(Phi)*sin(theta)*cos(phi) + sin(Theta)*sin(Phi)*sin(theta)*sin(phi) + cos(Theta)*cos(theta))**2
[…]

### 2018-01-11 polharmonic/test-inverse.py

@@ -1,21 +1,0 @@
-import numpy as np
-from util import *
-from dispim_coeffs import *
-
-# Globals
-theta = Symbol('theta', real=True)
-phi = Symbol('phi', real=True)
-phi_pol = Symbol('phi_pol', real=True)
-A = Symbol('A', real=True)
-B = Symbol('B', real=True)
-
-# Main script
-print("Working...")
-
-# Test the inverse
-prf = (sin(theta)**2)*(cos(phi - phi_pol)**2)*2*(A + B*(1 - (sin(theta)**2)*(cos(phi)**2)))
-#prf = 1 - (sin(theta)**2)*(sin(phi)**2)
-#prf = sin(theta)**2
-Hlm = prf2Hlm(prf)
-prf2 = Hlm2prf(Hlm)
-print(simplify(expand(prf).rewrite(cos) - expand(prf2).rewrite(cos)))

### 2018-01-11 polharmonic/test-known-recon.py

@@ -1,0 +1,73 @@
+from dipsim import multiframe, util, fluorophore, reconstruction
+import numpy as np
+import matplotlib.pyplot as plt
+import os; import time; start = time.time(); print('Running...')
+import matplotlib.gridspec as gridspec
+import h5py
+import plot_tpc
+
+# Generate truth orientations
+nx, ny = 50, 50
+t = np.linspace(0, np.pi/2, nx)
+p = np.linspace(0, np.pi, ny)
+tv, pv = np.meshgrid(t, p)
+tvv = np.expand_dims(tv, 2)
+pvv = np.expand_dims(pv, 2)
+cvv = 3*np.ones((nx, ny, 1))
+data = np.concatenate([tvv, pvv, cvv], 2)
+
+# Save truth data
+h5f = h5py.File('truth.h5', 'w')
+h5f.create_dataset('result', data=data)
+h5f.close()
+
+# Plot truth orientations
+# plot_tpc.plot_tpc(filename='truth.h5', output='truth.pdf')
+# print('X')
+# import pdb; pdb.set_trace()
+
+# Create microscope
+n = 1.33
+alpha1 = 60
+na1 = 1.1
+na2 = 0.71
+theta1 = np.deg2rad(45-12)
+theta2 = -np.deg2rad(45+12)
+dose_ratio = 3
+total_photons = 10000
+dose2 = total_photons/(1 + dose_ratio)
+dose1 = total_photons - dose2
+
+exp = multiframe.MultiFrameMicroscope(ill_thetas=[theta1, theta2], det_thetas=[theta2, theta1],
+                                      ill_nas=[na1, na2], det_nas=[na2, na1],
+                                      ill_types=2*['sheet'], det_types=2*['lens'],
+                                      colors=['(1,0,0)', '(0,0,1)'], n_frames=4,
+                                      max_photons=[dose1, dose2], n_samp=1.33)
+
+# Generate the intensities
+def intensities_wrapper(data, exp=exp):
+    flu = fluorophore.Fluorophore(*data)
+    return exp.calc_intensities(fluorophore=flu)
+
+intensities = np.apply_along_axis(intensities_wrapper, axis=2, arr=data)
+import pdb; pdb.set_trace()
+
+# Perform reconstructions
+def recon_wrapper(data, multiframe=exp):
+    recon = reconstruction.Reconstruction(multiframe=multiframe, recon_type='tpc',
+                                          data=data)
+    recon.evaluate()
[…]

### 2018-01-12 notes/2017-01-17/figs/dispim/svs.tex
Clean directories. Move results to notes.

\documentclass[preview, border={0pt 0pt 2pt 2pt}]{standalone}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz, pgfplots}
\usepackage{graphicx}
\begin{document}
\begin{tikzpicture}
  \pgfplotsset{width=10cm, height=5cm}
  \begin{axis}[
    axis lines=left,
    xlabel=,
    every outer x axis line/.append style={-},
    every outer y axis line/.append style={-},    
    ylabel=Singular Value,
    ylabel near ticks,
    xmin=-0.5, xmax=5.5,
    ymin=0, ymax=1.5,
    xtick={0,...,5},
    ytick={0,0.5,...,1.5},
    xticklabels={\includegraphics[scale=0.125]{sv0},\includegraphics[scale=0.125]{sv1}, \includegraphics[scale=0.125]{sv2},\includegraphics[scale=0.125]{sv3},\includegraphics[scale=0.125]{sv4}, \includegraphics[scale=0.125]{sv5}},
    xticklabel style={yshift=5pt},
    ] 
    \addplot+[
    ycomb,
    black,
    mark options={black}
    ] plot coordinates
	{(0,1.36) (1,0.43) (2,0.43) (3,0.38) (4,0.22) (5,0.03)};
\end{axis}
\end{tikzpicture}
\end{document}

### 2018-01-12 notes/2017-01-17/figs/epi/svs.tex
Clean directories. Move results to notes.

\documentclass[preview, border={0pt 0pt 2pt 2pt}]{standalone}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz, pgfplots}
\usepackage{graphicx}
\begin{document}
\begin{tikzpicture}
  \pgfplotsset{width=10cm, height=5cm}
  \begin{axis}[
    axis lines=left,
    xlabel=,
    every outer x axis line/.append style={-},
    every outer y axis line/.append style={-},    
    ylabel=Singular Value,
    ylabel near ticks,
    xmin=-0.5, xmax=2.5,
    ymin=0, ymax=1.2,
    xtick={0,...,2},
    ytick={0,0.4,...,1.2},    
    xticklabels={\includegraphics[scale=0.25]{sv0t},\includegraphics[scale=0.25]{sv1t}, \includegraphics[scale=0.25]{sv2t}},
    xticklabel style={yshift=15pt},
    ] 
    \addplot+[
    ycomb,
    black,
    mark options={black}
    ] plot coordinates
	{(0,1.18) (1,0.59) (2,0.59)};
\end{axis}
\end{tikzpicture}
\end{document}

### 2018-01-17 notes/2018-01-18-osa-abstract/abstract.tex
Data for slides and abstract. Early recons in frequency domain.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                   File: OSAmeetings.tex             %
%                  Date: March 21, 2007  MSD          %
%                                                     %
%     For preparing LaTeX manuscripts for submission  %
%       submission to OSA meetings and conferences    %
%                                                     %
%       (c) 2007 Optical Society of America           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt]{article}
\usepackage{osameet2}

%% standard packages and arguments should be modified as needed

\usepackage{amsmath,amssymb}

%\usepackage[pdftex,colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %pdflatex
\usepackage[colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %latex w/dvips

\begin{document}

\title{Preparing a Manuscript for Submission to an Optical Society of America Meeting or Conference}

\author{Author name(s)}
\address{Author affiliation and full address}
\email{talonchandler@talonchandler.com}

\begin{abstract}
\LaTeX{} users preparing manuscripts for OSA meetings or conferences
should use the new \texttt{osameet2.sty} style file and should observe the
guidelines described here to adhere to
OSA requirements. Users of Bib\TeX{} may use the \texttt{osajnl.bst}
style file, which is included in this distribution. Comments and
questions should be directed to the OSA Technical Papers Department (tel: +1 202.416.6191,  e-mail: cstech@osa.org).
\end{abstract}

\ocis{000.0000, 999.9999.}

\section{Main Text}

\subsection{Typographical Style}
Margins and type size will be set by the OSA \LaTeX{}
commands for title, author names and addresses, abstract,
references, captions, and so on. The \texttt{osameet2.sty} package
references \texttt{mathptmx.sty} for Times text and math fonts.
Authors who require Computer Modern font may modify the style file
or, preferably, invoke the package \texttt{ae.sty} or similar for
optimum output with Computer Modern.

\subsection{Author Names and Affiliations}
Author names should be given in full with first initials spelled out to assist with indexing.
Affiliations should follow the format division, organization, and address---and complete postal information should be given.
Abbreviations should not be used. United States addresses should end
with ``, USA.''

\subsection{Abstract} The abstract
should be limited to no more than words. It should be an
explicit summary of the paper that states the problem, the methods
used, and the major results and conclusions. If another publication author is referenced in the abstract, abbreviated information
(e.g., journal, volume number, first page, year) must be
given in the abstract itself, without a reference number. (The item referenced in the abstract should be the first
cited reference  in the body.)

\subsection{OCIS Subject Classification} Two Optics Classification and
Indexing Scheme (OCIS) subject classifications should be placed at
the end of the abstract with the \verb+\ocis{}+ command. OCIS
codes can be found at
\href{http://www.osapublishing.org/submit/ocis/}{http://www.osapublishing.org/submit/ocis/}.

\subsection{Notation}
\subsubsection{General Notation}
Notation must be
legible, clear, compact, and consistent with standard usage. In
general, acronyms should be defined at first use.

\clearpage

\subsubsection{Math Notation}
Equations should use standard \LaTeX{} or AMS\LaTeX{} commands (sample from Krishnan \textit{et al.} \cite{krishnan00}).

\begin{eqnarray}
\bar\varepsilon &=& \frac{\int_0ˆ\infty\varepsilon
\exp(-\beta\varepsilon)\,{\rm d}\varepsilon}{\int_0ˆ\infty
\exp(-\beta\varepsilon)\,{\rm d}\varepsilon}\nonumber\\
&=& -\frac{{\rm d}}{{\rm d}\beta}\log\Biggl[\int_0ˆ\infty\exp
(-\beta\varepsilon)\,{\rm d}\varepsilon\Biggr]=\frac1\beta=kT.
\end{eqnarray}

\section{Tables and Figures}
Figures and illustrations should be incorporated directly into the
manuscript, and the size of a figure should be commensurate with the amount
and value of the information conveyed by the figure.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=8.3cm]{figs/epi/phantom.png}
\caption{Sample figure with preferred style for labeling parts.}
\end{figure}

\begin{table}[htb]
 \centering \caption{Sample Table}
\begin{tabular}{ccc}
    \hline
    One & Two & Three \\
    \hline
    Eins & Zwei & Drei \\
    Un & Deux & Trois \\
    Jeden & Dv\v{e} & T\v{r}i \\
    \hline
   \end{tabular}
    \end{table}

 No more than
three figures should generally be included in the paper.
Place figures as close as possible to where they
are mentioned in the text. No part of a figure should extend beyond text width, and text should not wrap around figures.

\section{References}
References should be cited with the \verb+\cite{}+ command.
Bracketed citation style, as opposed to superscript, is preferred
\cite{krishnan00,vantrigt97,masters93,shoop97,kalman76,craig96,steup96}.
The \texttt{osameet2.sty} style file references \texttt{cite.sty}. Comprehensive journal abbreviations are available on the CrossRef web site:
\href{http://www.crossref.org/titleList/}{http://www.crossref.org/titleList/}.

\begin{thebibliography}{99}

\bibitem{krishnan00} E. Krishnan, A. M. Shan, T. Rishi, L. A. Ajith, C. V.
Radhakrishnan, \textit{On-line Tutorial on \LaTeX{}},
``Mathematics'' (Indian \TeX{} Users Group, 2000), \\
\url{http://www.tug.org/tutorials/tugindia/chap11-scr.pdf}.

\bibitem{vantrigt97} C. van Trigt, ``Visual system-response functions and estimating reflectance,''
J. Opt. Soc. Am. A \textbf{14}, 741--755 (1997).

\bibitem{masters93} T. Masters, \emph{Practical Neural Network Recipes in C++} (Academic, 1993).

\bibitem{shoop97} B. L. Shoop, A. H. Sayles, and D. M. Litynski, ``New devices for optoelectronics: smart pixels,''
in \emph{Handbook of Fiber Optic Data Communications},
C. DeCusatis, D. Clement, E. Maass, and R. Lasky, eds. (Academic, 1997), pp. 705--758.

\bibitem{kalman76} R. E. Kalman,``Algebraic aspects of the generalized inverse of a rectangular matrix,'' in
\emph{Proceedings of Advanced Seminar on Generalized Inverse and Applications}, M. Z. Nashed, ed. (Academic, 1976), pp. 111--124.

\bibitem{craig96} R. Craig and B. Gignac, ``High-power 980-nm pump lasers,''
in \emph{Optical Fiber Communication Conference}, Vol. 2 of 1996 OSA Technical Digest Series (Optical Society of America, 1996), paper ThG1.

\bibitem{steup96} D. Steup and J. Weinzierl, ``Resonant THz-meshes,''
presented at the Fourth International Workshop on THz Electronics, Erlangen-Tennenlohe, Germany, 5--6 Sept. 1996.

\end{thebibliography}

\end{document}

### 2018-01-17 notes/2018-01-18-osa-abstract/figs/recon_data.py

@@ -9,10 +9,16 @@ def recon(folder, input_files, exp, shape, cal):
     file_name = folder+'.dat'
     data_file = folder+'/'+file_name
 
-    xspan = 15
-    yspan = 15
-    intf = data.IntensityField(input_files, x0=235, y0=585, z0=175, xspan=xspan, yspan=yspan, zspan=1, cal=cal)
-    intf.plot_int_field(output_file=folder+'/'+'data.pdf', shape=shape, line_start=(0, xspan-1), line_end=(yspan-1, 0))
+    # Large (two strand)
+    # xs, ys, zs = 50, 50, 12 
+    # x0, y0, z0 = 190, 560, 150 
+
+    # Small
+    xs, ys, zs = 10, 10, 10, 
+    x0, y0, z0 = 240, 585, 175
+
+    intf = data.IntensityField(file_names=input_files, x0=x0, y0=y0, z0=z0, xspan=xs, yspan=ys, zspan=zs, cal=cal)
+    intf.plot_int_field(output_file=folder+'/'+'data.pdf', shape=shape, line_start=(0, xs-1), line_end=(ys-1, 0))
     
     # Load 
     f = open(data_file, 'rb')
@@ -22,42 +28,33 @@ def recon(folder, input_files, exp, shape, cal):
     exp.calc_B_matrix()
 
     # Reconstruct phantom
-    df = exp.recon_dist_field(intf.g)
+    df = exp.recon_dist_field(intf, mask_threshold=0.8)
     df.plot_dist_field(exp.B, exp.xyz, exp.triangles, filename=folder+'/data_recon_shuffle.png',
-                        r=0.2, d=100, mag=1, show=True)
+                        r=0.1, d=100, mag=1, show=True)
 
+    import pdb; pdb.set_trace() 
     print('Total time: '+str(np.round(time.time() - start, 2)))
     os.system('say "done"')
 
-## A-view only
-# original
-name_head = '/Users/Talon/GoogleDrive/projects/dispim-data/20170725_Bob_Actin_results/Cell1_LSimaging_registerred/SPIM'
-names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif']
-cal = np.array([1.06, 1.0, 1.0, 1.03])
-idx = [2, 3, 0, 1]# Default [0, 1, 2, 3]
[…]

### 2018-01-17 polharmonic/data.py

@@ -4,23 +4,27 @@ import matplotlib.pyplot as plt
 from mayavi import mlab
 
 class IntensityField:
-    """An IntensityField represents the data collected from Distribution Field.  
+    """An IntensityField represents the data collected from a DistributionField.  
     It consists of an array of intensities g. 
     """
-    def __init__(self, file_names, x0=0, y0=0, z0=0, xspan=10, yspan=10, zspan=10, cal=None):
-        g = np.zeros((xspan, yspan, len(file_names)))
-        for i, file_name in enumerate(file_names):
-            im = util.tiff2array(file_name, x=x0, y=y0, z=z0, width=xspan, height=yspan, slices=zspan)
-            if cal is None:
-                g[:,:,i] = im
-            else:
-                g[:,:,i] = im/cal[i]
-        g = g/g.max()
-        self.g = g
-
+    def __init__(self, file_names=None, x0=0, y0=0, z0=0, xspan=10, yspan=10, zspan=10, cal=None):
+        if file_names is not None:
+            g = np.zeros((xspan, yspan, zspan, len(file_names)))
+            for i, file_name in enumerate(file_names):
+                im = util.tiff2array(file_name, x=x0, y=y0, z=z0, width=xspan, height=yspan, slices=zspan)
+                if cal is None:
+                    g[:,:,:,i] = im
+                else:
+                    g[:,:,:,i] = im/cal[i]
+            g = g/g.max()
+            self.g = g
+        else:
+            self.g = 0
+                
+        
     def plot_int_field(self, output_file='out.pdf', shape=(2, 4), row_labels=[], col_labels=[],
                        line_start=(0,0), line_end=(0,0),
-                       roi_upper_left=(0, 0), roi_wh=(0,0), plot_roi=False, zslice=0, dim=2):
+                       roi_upper_left=(0, 0), roi_wh=(0,0), plot_roi=False, zslice=0):
         # Create axes
         inches = 3
         fig, axs = plt.subplots(2*shape[0], shape[1], figsize=(3.5*inches, 3*inches), gridspec_kw={'height_ratios':[1, 0.2]*shape[0], 'hspace':0.1, 'wspace':0.1})
@@ -31,27 +35,20 @@ class IntensityField:
         for i, (main_ax, line_ax) in enumerate(zip(main_axs.flatten(), line_axs.flatten())):
 
             # Plot image
[…]

### 2018-01-17 polharmonic/dist.py

@@ -18,32 +18,42 @@ class DistributionField:
             self.sh_arr[i] = d.sh
             
     def plot_dist_field(self, B, xyz, triangles, filename=None,
-                        d=50, r=1, mag=1, show=False):
+                        d=50, r=1, mag=1, show=False, mask_threshold=0.01):
         # Calculate radii
-        radii = np.einsum('ij,klj->kli', B, self.sh_arr)
-
+        radii = r*np.einsum('ij,klmj->klmi', B, self.sh_arr)
+        mask = np.max(radii, axis=-1) > mask_threshold
+        
         # Create figure
         mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(400, 400))
         mlab.clf()
 
-        space = 2
-        shift = space*np.max(radii.shape[:2])/2
+        space = 1
 
-        N = radii.shape[0]*radii.shape[1]
+        N = np.sum(mask)
         j = 1
         
         # Plot
-        for i in np.ndindex(radii.shape[:2]):
-            sys.stdout.flush()            
-            sys.stdout.write("Plotting: "+ str(j) + '/' + str(N) + '\r')
+        for i in np.ndindex(radii.shape[:-1]):
+            if mask[i]:
+                sys.stdout.flush()            
+                sys.stdout.write("Plotting: "+ str(j) + '/' + str(N) + '\r')
 
-            # Split into positive and negatives
-            n = radii[i].clip(max=0) 
-            p = radii[i].clip(min=0)*(-1)
-            j += 1
+                # Split into positive and negatives
+                n = radii[i].clip(max=0) 
+                p = radii[i].clip(min=0)*(-1)
+                j += 1
 
-            mlab.triangular_mesh(p*xyz[:,0] + space*i[0] - shift, p*xyz[:,1] + space*i[1] - shift, p*xyz[:,2], triangles, color=(1, 0, 0))
-            mlab.triangular_mesh(n*xyz[:,0] + space*i[0] - shift, n*xyz[:,1] + space*i[1] - shift, n*xyz[:,2], triangles, color=(0, 0, 1))
+                if i == (2, 8, 0):
+                    mlab.triangular_mesh(p*xyz[:,0] + space*i[0], p*xyz[:,1] + space*i[1], p*xyz[:,2] + space*i[2], triangles, color=(0, 1, 0))
+                else:
[…]

### 2018-01-17 polharmonic/multi.py

@@ -1,4 +1,4 @@
-from polharmonic import ill, det, micro, util, dist, sft
+from polharmonic import ill, det, micro, util, dist, sft, data
 from cvxopt import matrix, solvers
 solvers.options['show_progress'] = False
 import sys
@@ -74,7 +74,10 @@ class MultiMicroscope:
         return np.matmul(self.psi, dist.sh)
 
     def calc_intensity_field(self, dist_field):
-        return np.einsum('ij,klj->kli', self.psi, dist_field.sh_arr)
+        g = np.einsum('ij,klmj->klmi', self.psi, dist_field.sh_arr)
+        intf = data.IntensityField()
+        intf.g = g
+        return intf
     
     def recon_dist(self, g):
         N = self.B.shape[1]
@@ -88,16 +91,21 @@ class MultiMicroscope:
         d = dist.Distribution(sh=sh)
         return d
 
-    def recon_dist_field(self, g):
-        sh_arr = np.zeros([*g.shape[:2], self.max_j])
-        N = g.shape[0]*g.shape[1]
+    def recon_dist_field(self, intf, mask_threshold=0):
+        g = intf.g
+        mask = np.max(intf.g, axis=-1) > mask_threshold
+        sh_arr = np.zeros([*g.shape[:-1], self.max_j])
+        N = np.sum(mask)
         j = 1
-        for i in np.ndindex(g.shape[:2]):
-            sys.stdout.flush()
-            sys.stdout.write("Reconstructing: "+ str(j) + '/' + str(N) + '\r')
-            j += 1
-            d = self.recon_dist(g[i])
-            sh_arr[i] = d.sh
+        for i in np.ndindex(g.shape[:-1]):
+            if mask[i]:
+                sys.stdout.flush()
+                sys.stdout.write("Reconstructing: "+ str(j) + '/' + str(N) + '\r')
+                j += 1
+                d = self.recon_dist(g[i])
+                sh_arr[i] = d.sh                
+            else:
+                sh_arr[i] = np.zeros(self.max_j)
         return dist.DistributionField(sh_arr=sh_arr)
 
     def plot_scene(self, filename):

### 2018-01-17 polharmonic/util.py

@@ -226,10 +226,8 @@ def tiff2array(filename, x=0, y=0, z=0, width=None, height=None, slices=None):
     else:
         z_max = z + slices
     im = im[z_min:z_max, y_min:y_max, x_min:x_max]
-    if slices == 1:
-        return im.squeeze()
-    else:
-        return im
+    im = np.swapaxes(im,0,2)
+    return im
 
 # Returns "equally" spaced points on a unit sphere in spherical coordinates.
 # http://stackoverflow.com/a/26127012/5854689

### 2018-01-19 notes/2018-01-18-osa-abstract/abstract.tex
Jan 18 email. First 3D recons.

@@
 
-\title{Preparing a Manuscript for Submission to an Optical Society of America Meeting or Conference}
+\title{Three-dimensional fluorophore orientation imaging with polarized multiview microscopy}
 
-\author{Author name(s)}
-\address{Author affiliation and full address}
-\email{talonchandler@talonchandler.com}
+\author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
+\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering,\\ National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
+\email{*talonchandler@talonchandler.com} %% email address is required
 
 \begin{abstract}
-\LaTeX{} users preparing manuscripts for OSA meetings or conferences
-should use the new \texttt{osameet2.sty} style file and should observe the
-guidelines described here to adhere to
-OSA requirements. Users of Bib\TeX{} may use the \texttt{osajnl.bst}
-style file, which is included in this distribution. Comments and
-questions should be directed to the OSA Technical Papers Department (tel: +1 202.416.6191,  e-mail: cstech@osa.org).
+  We show that polarized fluorescence microscopes collect data in the angular
+  frequency domain. We use this result to propose and demonstrate efficient
+  algorithms for reconstructing three-dimensional fluorophore orientations from
+  polarized multiview microscope data.
 \end{abstract}
 
-\ocis{000.0000, 999.9999.}
+\ocis{180.2520 Fluorescence microscopy, 260.5430 Polarization}
 
-\section{Main Text}
+\section{Introduction}
+\section{Theory}
+\section{Results}
 
@@
   \centering
-  \includegraphics[width=8.3cm]{figs/epi/phantom.png}
+  \includegraphics[width=17cm]{figs/asym_dispim/data.pdf}
 \caption{Sample figure with preferred style for labeling parts.}
@@
 
-\begin{table}[htb]
- \centering \caption{Sample Table}
-\begin{tabular}{ccc}
-    \hline
-    One & Two & Three \\
-    \hline
-    Eins & Zwei & Drei \\
-    Un & Deux & Trois \\
-    Jeden & Dv\v{e} & T\v{r}i \\
-    \hline
-   \end{tabular}
-    \end{table}
-
- No more than
-three figures should generally be included in the paper.
-Place figures as close as possible to where they
-are mentioned in the text. No part of a figure should extend beyond text width, and text should not wrap around figures.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=17cm]{figs/asym_dispim/recon.pdf}
+\caption{Sample figure with preferred style for labeling parts.}
+\end{figure}
 

### 2018-01-19 notes/2018-01-18-osa-abstract/figs/analyze_ortho.py

@@ -11,12 +11,13 @@ if not os.path.exists(folder):
 data_file = folder+'/'+folder+'.dat'
 
 # Build microscope
-exp = multi.MultiMicroscope(ill_thetas=[90], max_l=4, n_pts=5000)
+exp = multi.MultiMicroscope(ill_thetas=[90], det_nas=[1.1], max_l=4, n_pts=250)
 
 # Calculate and save (comment this on repeat runs)
-# exp.calc_sys_matrix()
-# dill.dump(exp.psi, open(data_file,'wb'))
+exp.calc_sys_matrix()
+dill.dump(exp.psi, open(data_file,'wb'))
 
+import pdb; pdb.set_trace() 
 # Load 
 f = open(data_file, 'rb')
 exp.psi = dill.load(f)

### 2018-01-19 notes/2018-01-18-osa-abstract/figs/check_det.py

@@ -1,0 +1,30 @@
+from polharmonic import det
+from sympy import Symbol, lambdify
+import matplotlib.pyplot as plt
+import numpy as np
+
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+
+dd = det.Detector(NA=1.1, theta_optical_axis=0)
+dd2 = det.Detector(NA=0.8, theta_optical_axis=0)
+
+prf = dd.det_prf()
+prff = lambdify(theta, prf)
+prf2 = dd2.det_prf()
+prff2 = lambdify(theta, prf2)
+
+x = np.linspace(0, 2*np.pi, 100)
+y = prff(x)
+y2 = prff2(x)
+
+f, ax = plt.subplots(1, 1, figsize=(5, 5))
+ax.plot(x, y, '-k')
+ax.plot(x, y2, '-b')
+ax.set_xlabel('theta')
+ax.set_ylabel('det prf')
+ax.set_xlim([0, 2*np.pi])
+ax.set_ylim([0, 1])
+print(np.min(y), np.max(y))
+f.savefig('det.png', dpi=300)
+

### 2018-01-19 notes/2018-01-18-osa-abstract/figs/recon_data.py

@@ -3,6 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import os; import time; start = time.time(); print('Running...')
 import dill
+import matplotlib.image as mpimg
 np.set_printoptions(precision=3, suppress=True)
 
 # Import data
@@ -12,50 +13,104 @@ names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif',
 input_files = np.array([name_head + name for name in names])
 
 # Calibration data
-cal = np.ones(8)
+cal = np.array([1.06, 1.0, 1.0, 1.03, 
+                1.08, 1.05, 1.0, 1.04])
+
+# HACKING
 # cal = np.array([1.06, 1.0, 1.0, 1.03, 
-#                 1.08, 1.05, 1.0, 1.04])
-#cal[4:] = ((1.1/0.71)**2)*cal[4:]
+#                 0.97, 1.05, 1.0, 1.15])
+
+cal_ratio = 1.1#((1.1/0.71)**2)
+cal[4:] = cal_ratio*cal[4:]
 
 # Redindexing
-idx = [0, 1, 2, 3, 4, 5, 6, 7] #[2, 3, 0, 1, 6, 7, 4, 5] 
+idx = [0, 3, 2, 1, 4, 5, 6, 7]
 input_files = input_files[idx]
 cal=cal[idx]
 
 # Build dispim microscope
 exp = multi.MultiMicroscope(ill_thetas=[90, 0], det_thetas=[0, 90],
                             det_nas=[1.1, 0.8], max_l=4, n_pts=250)
+exp_ortho = multi.MultiMicroscope(ill_thetas=[90], det_thetas=[0],
+                                  det_nas=[1.1], max_l=4, n_pts=250)
+exp_ortho2 = multi.MultiMicroscope(ill_thetas=[0], det_thetas=[90],
+                                  det_nas=[0.8], max_l=4, n_pts=250)
 
 # Load asymmetric dispim system matrix
 folder = 'asym_dispim'
 file_name = folder+'.dat'
 data_file = folder+'/'+file_name
 
+folder_ortho = 'ortho'
+file_name_ortho = folder_ortho+'.dat'
+data_file_ortho = folder_ortho+'/'+file_name_ortho
+
 # Large volume (two actin strands)
-xs, ys, zs = 50, 50, 12 
[…]

### 2018-01-19 polharmonic/dist.py

@@ -23,16 +23,20 @@ class DistributionField:
             self.sh_arr[i] = d.sh
             
     def plot_dist_field(self, B, xyz, triangles, filename=None,
-                        d=50, r=1, mag=1, show=False, mask_threshold=0.01):
+                        d=50, r=1, mag=1, show=False,
+                        mask_threshold=0.01, mask=None):
+        
         # Calculate radii
         if self.f_arr is None:
             radii = r*np.einsum('ij,klmj->klmi', B, self.sh_arr)
         elif self.sh_arr is None:
             radii = r*self.f_arr
-        mask = np.max(radii, axis=-1) > mask_threshold
+
+        if mask is None:
+            mask = np.max(radii, axis=-1) > mask_threshold
         
         # Create figure
-        mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(1000, 1000))
+        mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(800, 800))
         mlab.clf()
 
         space = 1
@@ -61,20 +65,23 @@ class DistributionField:
         elif self.sh_arr is None:
             # Black magic ahead
             x, y, z, tp = np.nonzero(radii)
+            scale = radii[x, y, z, tp]
             u = xyz[tp, 0]
             v = xyz[tp, 1]
             w = xyz[tp, 2]
-            mlab.quiver3d(x, y, z, u, v, w, mode='cylinder', scale_factor=r)
+            sss = np.random.random(*x.shape)
+            mlab.quiver3d(x, y, z, u, v, w, scalars=scale, mode='cylinder', scale_factor=r, scale_mode='scalar')
 
         if radii.shape[2] != 1: # If 3D dataset
-            mlab.outline(extent=[0,radii.shape[0],0,radii.shape[1],0,radii.shape[2]])
+            mlab.outline(extent=[0,radii.shape[0],0,radii.shape[1],0,radii.shape[2]], line_width=2*mag)
             mlab.points3d(0,0,0, color=(1, 1, 1))
 
         # View and save
+        mlab.gcf().scene.parallel_projection = True
         mlab.view(azimuth=45, elevation=45, distance=d, focalpoint=None,
                   roll=None, reset_roll=True, figure=None)
         mlab.savefig(filename, magnification=mag)
-        subprocess.call(['convert', filename, '-transparent', 'white', filename])
[…]

### 2018-01-19 polharmonic/multi.py

@@ -92,19 +92,23 @@ class MultiMicroscope:
             d = dist.Distribution(sh=sh)
             return d
         elif prior is 'single':
-            g_model = np.matmul(self.psi, np.linalg.pinv(self.B))
+            # Construct prior set (single directions w/ 10 amplitudes)
+            f_prior = np.hstack([(x*0.1 + 0.1)*np.identity(self.B.shape[0]) for x in range(10)])
+            H_model = np.matmul(self.psi, np.linalg.pinv(self.B))
+            g_model = np.matmul(H_model, f_prior)
             g_model = g_model/np.max(g_model)
             g_diff = g_model - g[:, np.newaxis]
             obj = np.linalg.norm(g_diff, ord=2, axis=0)**2
             argmin = np.argmin(obj)
-            f = np.zeros(self.B.shape[0])
-            f[argmin] = 1
+            f = f_prior[:, argmin]
+
             d = dist.Distribution(f=f)
             return d
 
-    def recon_dist_field(self, intf, mask_threshold=0, prior=None):
+    def recon_dist_field(self, intf, mask_threshold=0, mask=None, prior=None):
         g = intf.g
-        mask = np.max(intf.g, axis=-1) > mask_threshold
+        if mask is None:
+            mask = np.max(intf.g, axis=-1) > mask_threshold
         N = np.sum(mask)
         j = 1        
         if prior is None:

### 2018-01-19 notes/2018-01-18-osa-abstract/abstract.tex
Refactoring and cleaning up.

@@
 
-\author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
-\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering,\\ National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
+\author{Talon Chandler, Min Guo, Shalin Mehta, Abhishek Kumar,\\ Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
+
+\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging\\ and Bioengineering, National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Chan Zuckerberg Biohub, San Francisco, California 94158, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
 \email{*talonchandler@talonchandler.com} %% email address is required

### 2018-01-19 notes/2018-01-18-osa-abstract/figs/check_det.py

@@ -1,30 +1,0 @@
-from polharmonic import det
-from sympy import Symbol, lambdify
-import matplotlib.pyplot as plt
-import numpy as np
-
-theta = Symbol('theta', real=True)
-phi = Symbol('phi', real=True)
-
-dd = det.Detector(NA=1.1, theta_optical_axis=0)
-dd2 = det.Detector(NA=0.8, theta_optical_axis=0)
-
-prf = dd.det_prf()
-prff = lambdify(theta, prf)
-prf2 = dd2.det_prf()
-prff2 = lambdify(theta, prf2)
-
-x = np.linspace(0, 2*np.pi, 100)
-y = prff(x)
-y2 = prff2(x)
-
-f, ax = plt.subplots(1, 1, figsize=(5, 5))
-ax.plot(x, y, '-k')
-ax.plot(x, y2, '-b')
-ax.set_xlabel('theta')
-ax.set_ylabel('det prf')
-ax.set_xlim([0, 2*np.pi])
-ax.set_ylim([0, 1])
-print(np.min(y), np.max(y))
-f.savefig('det.png', dpi=300)
-

### 2018-01-19 polharmonic/data.py

@@ -8,60 +8,62 @@ import subprocess
 
 class IntensityField:
     """An IntensityField represents the data collected from a DistributionField.  
-    It consists of an array of intensities g. 
+    It consists of an array of intensities g. [nx x ny x nz x npol]
     """
-    def __init__(self, file_names=None, x0=0, y0=0, z0=0, xspan=10, yspan=10, zspan=10, cal=None):
-        if file_names is not None:
-            g = np.zeros((xspan, yspan, zspan, len(file_names)))
-            for i, file_name in enumerate(file_names):
-                im = util.tiff2array(file_name, x=x0, y=y0, z=z0, width=xspan, height=yspan, slices=zspan)
-                if cal is None:
-                    g[:,:,:,i] = im
-                else:
-                    g[:,:,:,i] = im/cal[i]
-            g = g/g.max()
-            self.g = g
-        else:
-            self.g = 0
+    def __init__(self, g=None):
+        self.g = g
+
+    def load_from_file(self, file_names=None, x0=0, y0=0, z0=0, xspan=10, yspan=10, zspan=10, cal=None):
+        g = np.zeros((xspan, yspan, zspan, len(file_names)))
+        for i, file_name in enumerate(file_names):
+            im = util.tiff2array(file_name, x=x0, y=y0, z=z0, width=xspan, height=yspan, slices=zspan)
+            if cal is None:
+                g[:,:,:,i] = im
+            else:
+                g[:,:,:,i] = im/cal[i]
+        self.g = g/g.max()
                 
-        
-    def plot_int_field(self, output_file='out.pdf', shape=(2, 4),
-                       row_labels=['$x$-illumination\n $z$-detection\n 1.1 NA', '$z$-illumination\n $x$-detection\n 0.71 NA'], col_labels=['$\phi = 0^{\circ}$', '$\phi = 45^{\circ}$', '$\phi = 90^{\circ}$', '$\phi = 135^{\circ}$'],
-                       line_start=(0,0), line_end=(0,0),
-                       roi_upper_left=(0, 0), roi_wh=(0,0), plot_roi=False, zslice=0, d=50, mag=1):
+    def plot(self, output_file='out.pdf', shape=(2, 4),
+             row_labels=None, col_labels=None,
+             dpi=400, d=50, mag=1, show=False):
         # Create axes
         inches = 3
[…]

### 2018-01-19 polharmonic/dist.py

@@ -9,12 +9,17 @@ class DistributionField:
     """A DistributionField represents many fluorophore distributions. It 
     consists of an array of Distributions."""
     def __init__(self, sh_arr=None, f_arr=None):
-        if f_arr is None:
+        if f_arr is not None and sh_arr is not None:
+            print("Warning: sh_arr and f_arr are redundant.")
+        elif f_arr is None:
             self.sh_arr = sh_arr
             self.f_arr = None
-        if sh_arr is None:
+        elif sh_arr is None:
             self.sh_arr = None
             self.f_arr = f_arr
+
+    def calc_f_arr(self, B):
+        self.f_arr = np.einsum('ij,klmj->klmi', B, self.sh_arr)
 
     def make_positive(self, B, max_l=None):
         for i in np.ndindex(self.sh_arr.shape[:2]):
@@ -23,67 +28,56 @@ class DistributionField:
             self.sh_arr[i] = d.sh
             
     def plot_dist_field(self, B, xyz, triangles, filename=None,
-                        d=50, r=1, mag=1, show=False,
-                        mask_threshold=0.01, mask=None):
+                        d=50, r=1, s=1, mag=1, show=False, mask=None):
         
         # Calculate radii
-        if self.f_arr is None:
-            radii = r*np.einsum('ij,klmj->klmi', B, self.sh_arr)
-        elif self.sh_arr is None:
-            radii = r*self.f_arr
-
-        if mask is None:
-            mask = np.max(radii, axis=-1) > mask_threshold
+        radii = r*self.f_arr
         
         # Create figure
         mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(800, 800))
         mlab.clf()
 
-        space = 1
-
         N = np.sum(mask)
         j = 1
-        
-        # Plot
 
-        if self.f_arr is None:
-            for i in np.ndindex(radii.shape[:-1]):
-                if mask[i]:
-                    sys.stdout.flush()            
-                    sys.stdout.write("Plotting: "+ str(j) + '/' + str(N) + '\r')
-
-                    # Split into positive and negatives
-                    n = radii[i].clip(max=0) 
-                    p = radii[i].clip(min=0)*(-1)
-                    j += 1
-
-                    if i == (2, 8, 0):
[…]

### 2018-01-19 polharmonic/multi.py

@@ -101,14 +101,11 @@ class MultiMicroscope:
             obj = np.linalg.norm(g_diff, ord=2, axis=0)**2
             argmin = np.argmin(obj)
             f = f_prior[:, argmin]
-
             d = dist.Distribution(f=f)
             return d
 
-    def recon_dist_field(self, intf, mask_threshold=0, mask=None, prior=None):
+    def recon_dist_field(self, intf, mask=None, prior=None):
         g = intf.g
-        if mask is None:
-            mask = np.max(intf.g, axis=-1) > mask_threshold
         N = np.sum(mask)
         j = 1        
         if prior is None:
@@ -122,7 +119,9 @@ class MultiMicroscope:
                     dist_arr[i] = d.sh
                 else:
                     dist_arr[i] = np.zeros(self.max_j)
-            return dist.DistributionField(sh_arr=dist_arr)
+            d = dist.DistributionField(sh_arr=dist_arr)
+            d.calc_f_arr(self.B)
+            return d
         
         elif prior is 'single':
             dist_arr = np.zeros([*g.shape[:-1], self.B.shape[0]])

### 2018-01-20 polharmonic/data.py
Working orientation color visualization.

@@ -37,18 +37,43 @@ class IntensityField:
         for i, ax in enumerate(axs.flatten()):
             
             # Calculate contours and plot
+            mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(800, 800))
             mlab.clf()
             im = self.g[:,:,:,i]
+            vol = mlab.pipeline.volume(mlab.pipeline.scalar_field(im), vmin=0, vmax=.8, color=(1, 0, 0))
+
+            # Changing the ctf:
+            from tvtk.util.ctf import ColorTransferFunction
+
+            ctf = ColorTransferFunction()
             for i in 0.1*np.arange(9):
-                color = cm.hot(i)
-                obj = mlab.contour3d(im, contours=[i],
-                                     color=color[:-1], opacity=0.8)
+                c = cm.hot(i)
+                ctf.add_rgb_point(i, c[0], c[1], c[2]) 
+            # ctf.add_hsv_point(value, h, s, v)
+            # ...
+            vol._volume_property.set_color(ctf)
+            vol._ctf = ctf
+            vol.update_ctf = True
+
+            # Changing the otf:
+            from tvtk.util.ctf import PiecewiseFunction
+            otf = PiecewiseFunction()
+            for i in 0.1*np.arange(9):
+                otf.add_point(i, i**(3))
+            vol._otf = otf
+            vol._volume_property.set_scalar_opacity(otf)
+            # for i in 0.1*np.arange(9):
+            #     color = cm.hot(i)
+            #     obj = mlab.contour3d(im, contours=[i],
+            #                          color=color[:-1], opacity=0.8)
                 
             mlab.gcf().scene.parallel_projection = True
             mlab.points3d(0,0,0, color=(1, 1, 1))
+            
             mlab.outline(extent=[0,im.shape[0],0,im.shape[1],0,im.shape[2]], line_width=2*mag)
-            mlab.view(azimuth=45, elevation=45, distance=d, focalpoint=None,
+            mlab.view(azimuth=225, elevation=45, distance=d, focalpoint=None,
                       roll=None, reset_roll=True, figure=None)
+
 
             if show:
                 mlab.show()

### 2018-01-20 polharmonic/util.py

@@ -2,9 +2,13 @@ import subprocess
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.image as mpimg
+import matplotlib
 from mayavi import mlab
 from scipy.special import sph_harm
+import scipy.misc
 from skimage import io
+import vispy
+from polharmonic import visuals
 
 # SciPy real spherical harmonics with identical interface to SymPy's Znm
 # Useful for faster numerical evaluation of Znm
@@ -231,11 +235,40 @@ def tiff2array(filename, x=0, y=0, z=0, width=None, height=None, slices=None):
 
 # Returns "equally" spaced points on a unit sphere in spherical coordinates.
 # http://stackoverflow.com/a/26127012/5854689
-def fibonacci_sphere(n):
+def fibonacci_sphere(n, xyz=False):
     z = np.linspace(1 - 1/n, -1 + 1/n, num=n) 
     theta = np.arccos(z)
     phi = np.mod((np.pi*(3.0 - np.sqrt(5.0)))*np.arange(n), 2*np.pi) - np.pi
-    return np.vstack((theta, phi)).T
+    if xyz:
+        return np.vstack((np.sin(theta)*np.cos(phi), np.sin(theta)*np.sin(phi), np.cos(theta))).T, np.vstack((theta, phi)).T
+    else:
+        return np.vstack((theta, phi)).T
+
+
+def sphere_LUT_points():
+    n = 256
+    z = np.linspace(1 - 1/n, -1 + 1/n, num=n) 
+    theta = np.arccos(z)
+    phi = np.mod((np.pi*(3.0 - np.sqrt(5.0)))*np.arange(n), 2*np.pi) - np.pi
+    xyz = np.abs(np.vstack((np.cos(phi)*np.sin(theta), np.sin(phi)*np.sin(theta), np.cos(theta))).T)
+    i = np.lexsort((xyz[:,2], xyz[:,1], xyz[:,0]))
+    return xyz[i]
+
+def sphere_LUT():
+    points = sphere_LUT_points()
+    lut = np.zeros((256, 4))
+    for i in range(256):
+        lut[i, :] = [points[i, 0], points[i, 1], points[i, 2], 1]
+    return (255*lut).astype('uint8')
+
+def uvw2color(u, v, w):
+    lut = sphere_LUT()
+    color_idx = []
+    for i in range(u.shape[0]):
[…]

### 2018-01-20 polharmonic/visuals.py

@@ -1,0 +1,63 @@
+# Custom vispy classes
+from polharmonic import util
+import numpy as np
+from vispy.geometry import create_sphere, MeshData
+from vispy.visuals.mesh import MeshVisual
+from vispy.visuals import CompoundVisual
+from vispy.scene.visuals import create_visual_node
+import matplotlib
+import matplotlib.pyplot as plt
+from vispy.visuals.transforms import (STTransform, LogTransform,
+                                      MatrixTransform, PolarTransform)
+from vispy.visuals.line import LineVisual
+from vispy.visuals.text import TextVisual
+
+class MySphereVisual(CompoundVisual):
+    
+    def __init__(self, radius=1.0, directions=None, colors=None):
+        # Convert spherical to cartesian
+        points = np.array([util.tp2xyz(*x) for x in directions])
+
+        # Create mesh
+        import scipy.spatial
+        ch = scipy.spatial.ConvexHull(points)
+        mesh = MeshData(vertices=ch.points, faces=ch.simplices)
+
+        self._mesh = MeshVisual(vertices=mesh.get_vertices(),
+                                faces=mesh.get_faces(),
+                                vertex_colors=colors)
+
+        CompoundVisual.__init__(self, [self._mesh])
+        self.mesh.set_gl_state(depth_test=True)
+
+    @property
+    def mesh(self):
+        """The vispy.visuals.MeshVisual that used to fil in.
+        """
+        return self._mesh
+
+MySphere = create_visual_node(MySphereVisual)
+
+class MyXYZAxisVisual(CompoundVisual):
+    """
+    Simple 3D axis for indicating coordinate system orientation. Axes are
+    x=red, y=green, z=blue.
+    """
+    def __init__(self, origin=[0,0,0], length=1):
+        verts = origin + np.array([[0, 0, 0],
+                                   [length, 0, 0],
+                                   [0, 0, 0],
+                                   [0, length, 0],
+                                   [0, 0, 0],
+                                   [0, 0, length]])
+
+        line = LineVisual(pos=verts, color=np.array([0, 0, 0, 1]),
+                          connect='segments', method='gl')
+
+        x = TextVisual('x', font_size=12, pos=origin + np.array([1.25*length,0,0]))
+        y = TextVisual('y', font_size=12, pos=origin + np.array([0,1.25*length,0]))
[…]

### 2018-01-21 notes/2018-01-18-osa-abstract/abstract.tex
Working orientation color visualization.
Good multi-roi reconstructions. Abstract updates.

--- 2018-01-19 notes/2018-01-18-osa-abstract/abstract.tex
@@
 
+% \bibliography{paper}
+% \bibliographystyle{osajnl}
+
 %\usepackage[pdftex,colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %pdflatex
@@
 
-\author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
-\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering,\\ National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
-\email{*talonchandler@talonchandler.com} %% email address is required
+\author{Talon Chandler,${}^{1,*}$ Min Guo,${}^2$ Shalin Mehta,${}^{1,3,4}$ Abhishek Kumar,${}^2$\\ Hari Shroff,${}^{2,5}$ Rudolf Oldenbourg,${}^{3,6}$ Patrick J. La Rivi\`ere${}^{1,5}$}
+
+\address{${}^1$Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\ ${}^2$Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging\\ and Bioengineering, National Institutes of Health, Bethesda, Maryland 20892, USA.\\ ${}^3$Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ ${}^4$(present address) Chan Zuckerberg Biohub, San Francisco, California 94158, USA.\\ ${}^5$Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ ${}^6$Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
+\email{${}^*$talonchandler@talonchandler.com} %% email address is required
 
 \begin{abstract}
-  We show that polarized fluorescence microscopes collect data in the angular
-  frequency domain. We use this result to propose and demonstrate efficient
-  algorithms for reconstructing three-dimensional fluorophore orientations from
-  polarized multiview microscope data.
+  We show that polarized fluorescence microscopes make band-limited measurements
+  in the angular frequency domain. We use this result to propose and demonstrate
+  efficient algorithms for reconstructing three-dimensional fluorophore
+  orientations from polarized multiview microscope data.
 \end{abstract}
@@
 \section{Introduction}
+
 \section{Theory}
+\cite{chandler}
+\cite{barrett} 
 \section{Results}
-
-\subsection{Typographical Style}
-Margins and type size will be set by the OSA \LaTeX{}
-commands for title, author names and addresses, abstract,
-references, captions, and so on. The \texttt{osameet2.sty} package
-references \texttt{mathptmx.sty} for Times text and math fonts.
-Authors who require Computer Modern font may modify the style file
-or, preferably, invoke the package \texttt{ae.sty} or similar for
-optimum output with Computer Modern.
-
-\subsection{Author Names and Affiliations}
-Author names should be given in full with first initials spelled out to assist with indexing.
-Affiliations should follow the format division, organization, and address---and complete postal information should be given.
-Abbreviations should not be used. United States addresses should end
-with ``, USA.''
-
-\subsection{Abstract} The abstract
-should be limited to no more than words. It should be an
-explicit summary of the paper that states the problem, the methods
-used, and the major results and conclusions. If another publication author is referenced in the abstract, abbreviated information
-(e.g., journal, volume number, first page, year) must be
-given in the abstract itself, without a reference number. (The item referenced in the abstract should be the first
-cited reference  in the body.)
-
-\subsection{OCIS Subject Classification} Two Optics Classification and
-Indexing Scheme (OCIS) subject classifications should be placed at
-the end of the abstract with the \verb+\ocis{}+ command. OCIS
-codes can be found at
-\href{http://www.osapublishing.org/submit/ocis/}{http://www.osapublishing.org/submit/ocis/}.
-
-\subsection{Notation}
-\subsubsection{General Notation}
-Notation must be
-legible, clear, compact, and consistent with standard usage. In
-general, acronyms should be defined at first use.
-
-\clearpage
-
-\subsubsection{Math Notation}
-Equations should use standard \LaTeX{} or AMS\LaTeX{} commands (sample from Krishnan \textit{et al.} \cite{krishnan00}).
-
-\begin{eqnarray}
-\bar\varepsilon &=& \frac{\int_0ˆ\infty\varepsilon
-\exp(-\beta\varepsilon)\,{\rm d}\varepsilon}{\int_0ˆ\infty
-\exp(-\beta\varepsilon)\,{\rm d}\varepsilon}\nonumber\\
-&=& -\frac{{\rm d}}{{\rm d}\beta}\log\Biggl[\int_0ˆ\infty\exp
-(-\beta\varepsilon)\,{\rm d}\varepsilon\Biggr]=\frac1\beta=kT.
-\end{eqnarray}
-
-\section{Tables and Figures}
-Figures and illustrations should be incorporated directly into the
-manuscript, and the size of a figure should be commensurate with the amount
-and value of the information conveyed by the figure.
 
@@
   \centering
-  \includegraphics[width=17cm]{figs/asym_dispim/data.pdf}
-\caption{Sample figure with preferred style for labeling parts.}
+  \includegraphics[width=17cm]{figs/roi2/data.pdf}
+\caption{Data.}
 \end{figure}
@@
   \centering
-  \includegraphics[width=17cm]{figs/asym_dispim/recon.pdf}
-\caption{Sample figure with preferred style for labeling parts.}
+  \includegraphics[width=17cm]{figs/roi2/recon.pdf}
+\caption{Reconstruction.}
 \end{figure}
 
-\section{References}
-References should be cited with the \verb+\cite{}+ command.
-Bracketed citation style, as opposed to superscript, is preferred
-\cite{krishnan00,vantrigt97,masters93,shoop97,kalman76,craig96,steup96}.
-The \texttt{osameet2.sty} style file references \texttt{cite.sty}. Comprehensive journal abbreviations are available on the CrossRef web site:
-\href{http://www.crossref.org/titleList/}{http://www.crossref.org/titleList/}.
-
-\begin{thebibliography}{99}
-
-\bibitem{krishnan00} E. Krishnan, A. M. Shan, T. Rishi, L. A. Ajith, C. V.
-Radhakrishnan, \textit{On-line Tutorial on \LaTeX{}},
-``Mathematics'' (Indian \TeX{} Users Group, 2000), \\
-\url{http://www.tug.org/tutorials/tugindia/chap11-scr.pdf}.
-
-\bibitem{vantrigt97} C. van Trigt, ``Visual system-response functions and estimating reflectance,''
-J. Opt. Soc. Am. A \textbf{14}, 741--755 (1997).
-
-\bibitem{masters93} T. Masters, \emph{Practical Neural Network Recipes in C++} (Academic, 1993).
-
-\bibitem{shoop97} B. L. Shoop, A. H. Sayles, and D. M. Litynski, ``New devices for optoelectronics: smart pixels,''
-in \emph{Handbook of Fiber Optic Data Communications},
-C. DeCusatis, D. Clement, E. Maass, and R. Lasky, eds. (Academic, 1997), pp. 705--758.
-
-\bibitem{kalman76} R. E. Kalman,``Algebraic aspects of the generalized inverse of a rectangular matrix,'' in
-\emph{Proceedings of Advanced Seminar on Generalized Inverse and Applications}, M. Z. Nashed, ed. (Academic, 1976), pp. 111--124.
-
-\bibitem{craig96} R. Craig and B. Gignac, ``High-power 980-nm pump lasers,''
-in \emph{Optical Fiber Communication Conference}, Vol. 2 of 1996 OSA Technical Digest Series (Optical Society of America, 1996), paper ThG1.
-
-\bibitem{steup96} D. Steup and J. Weinzierl, ``Resonant THz-meshes,''
-presented at the Fourth International Workshop on THz Electronics, Erlangen-Tennenlohe, Germany, 5--6 Sept. 1996.
-
-\end{thebibliography}
+\bibliography{abstract}{}
+\bibliographystyle{osajnl}
 

### 2018-01-21 notes/2018-01-18-osa-abstract/figs/recon_data.py

@@ -5,144 +5,182 @@ import os; import time; start = time.time(); print('Running...')
 import dill
 import matplotlib.image as mpimg
 np.set_printoptions(precision=3, suppress=True)
+import matplotlib as mpl
+import subprocess
+mpl.rcParams['font.serif'] = 'Times'
 
-# High level params
-folder = 'asym_dispim'
-int_field_mag = 1
-recon_mag = 1
-recon_mask_threshold = 0.6
+def recon_roi(name, xs, ys, zs, x0, y0, z0, recon_mask_threshold, d, skip, dpi=800, mag=1, note=''):
+    # High level params
+    mfolder = 'asym_dispim'
+    folder = name
+    if not os.path.exists(folder):
+        os.mkdir(folder)
+    int_field_mag = mag
+    recon_mag = mag
 
-# Import data
-name_head = '/Users/Talon/GoogleDrive/projects/dispim-data/20170725_Bob_Actin_results/Cell1_LSimaging_registerred/SPIM'
-names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif',
-         'B_reg_P3.tif', 'B_reg_P4.tif', 'B_reg_P1.tif', 'B_reg_P2.tif']
-input_files = np.array([name_head + name for name in names])
+    # Import data
+    name_head = '/Users/Talon/GoogleDrive/projects/dispim-data/20170725_Bob_Actin_results/Cell1_LSimaging_registerred/SPIM'
+    names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif',
+             'B_reg_P3.tif', 'B_reg_P4.tif', 'B_reg_P1.tif', 'B_reg_P2.tif']
+    input_files = np.array([name_head + name for name in names])
 
-# Calibration data
-cal = np.array([1.06, 1.0, 1.0, 1.03, 
-                1.08, 1.05, 1.0, 1.04])
+    # Calibration data
+    cal = np.array([1.06, 1.0, 1.0, 1.03, 
+                    1.08, 1.05, 1.0, 1.04])
 
-# Reindexing 
-idx = [0, 3, 2, 1, 4, 5, 6, 7]
-input_files = input_files[idx]
-cal = cal[idx]
+    # Reindexing 
+    idx = [0, 3, 2, 1, 4, 5, 6, 7]
[…]

### 2018-01-21 polharmonic/data.py

@@ -28,13 +28,13 @@ class IntensityField:
              dpi=400, d=50, mag=1, show=False):
         # Create axes
         inches = 3
-        fig, axs = plt.subplots(shape[0], shape[1],
+        fig, axs = plt.subplots(shape[0], shape[1]+1,
                                 figsize=(shape[1]*inches, shape[0]*inches),
-                                gridspec_kw={'hspace':-0.15, 'wspace':-0.05})
+                                gridspec_kw={'hspace':-0.175, 'wspace':-0.075, 'width_ratios':[1, 1, 1, 1, 0.05]})
         mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(800, 800))
 
         # Load data and plot
-        for i, ax in enumerate(axs.flatten()):
+        for i, ax in enumerate(axs[:,:4].flatten()):
             
             # Calculate contours and plot
             mlab.figure(1, bgcolor=(1, 1, 1), fgcolor=(0, 0, 0), size=(800, 800))
@@ -62,18 +62,13 @@ class IntensityField:
                 otf.add_point(i, i**(3))
             vol._otf = otf
             vol._volume_property.set_scalar_opacity(otf)
-            # for i in 0.1*np.arange(9):
-            #     color = cm.hot(i)
-            #     obj = mlab.contour3d(im, contours=[i],
-            #                          color=color[:-1], opacity=0.8)
-                
+
             mlab.gcf().scene.parallel_projection = True
             mlab.points3d(0,0,0, color=(1, 1, 1))
             
             mlab.outline(extent=[0,im.shape[0],0,im.shape[1],0,im.shape[2]], line_width=2*mag)
             mlab.view(azimuth=225, elevation=45, distance=d, focalpoint=None,
                       roll=None, reset_roll=True, figure=None)
-
 
             if show:
                 mlab.show()
@@ -83,12 +78,31 @@ class IntensityField:
             ax.set_axis_off()
         subprocess.call(['rm', 'temp.png'])
 
+        # Plot colorbars
+        import matplotlib as mpl
+        norm = mpl.colors.Normalize(vmin=0, vmax=1)
+        cb1 = mpl.colorbar.ColorbarBase(axs[0,-1], cmap=cm.hot, norm=norm, orientation='vertical')
+        cb1.set_label('Color Transfer Function', rotation=270, labelpad=15)
+
[…]

### 2018-01-21 polharmonic/dist.py

@@ -32,7 +32,7 @@ class DistributionField:
     def plot_dist_field(self, B, xyz, triangles, filename=None,
                         d=50, r=1, s=1, mag=1, show=False, mask=None,
                         vis_px=500, dpi=500):
-        
+
         # Calculate radii
         radii = r*self.f_arr
         
@@ -51,6 +51,7 @@ class DistributionField:
             v = xyz[tp, 1]
             w = xyz[tp, 2]
 
+            # u = np.random.random(u.shape)
             # v = np.random.random(v.shape)
             # w = np.random.random(w.shape)
             
@@ -78,10 +79,6 @@ class DistributionField:
             # y = y - ys/2
             # z = z - zs/2
             
-            # Setup viewing window
-            # xyz, tp = util.fibonacci_sphere(1000, xyz=True)
-            # util.plot_sphere(filename='scale.png', directions=tp, data=xyz,
-            #                  show=show, vis_px=500)
             
             # vispy.use('PyQt4')
             # canvas = vispy.scene.SceneCanvas(keys='interactive', bgcolor='white',

### 2018-01-22 notes/2018-01-18-osa-abstract/abstract.tex
Email to group w/ abstract draft.

@@
 \begin{abstract}
-  We show that polarized fluorescence microscopes make band-limited measurements
+  \hspace{-0.75em} We show that polarized fluorescence microscopes make band-limited measurements
   in the angular frequency domain. We use this result to propose and demonstrate
@@
 \section{Introduction}
+Polarized fluorescence microscopes can measure the orientation of fluorophores
+in live specimens\cite{weiss1999}. Unfortunately, existing techniques are
+limited to imaging two-dimensional orientations in thin samples, and attempts to
+generalize these approaches to three-dimensional orientations have faced
+computational difficulties. We propose the use of the spherical harmonics to
+simplify the analysis of polarized fluorescence microscopes. In the same way
+that the Fourier transform simplifies the analysis of spatial imaging systems,
+the spherical Fourier transform simplifies the analysis of angular imaging
+systems.
 
 \section{Theory}
-\cite{chandler}
-\cite{barrett} 
-\section{Results}
+Consider a small volume that contains many non-interacting fluorophores. We
+define the orientation distribution function $f(\hat{\mathbf{r}})$ as the number
+of fluorophores per steradian oriented in a direction $\hat{\mathbf{r}}$. The
+goal of polarized fluorescence microscopy is to estimate $f(\hat{\mathbf{r}})$
+in many volumes throughout a three-dimensional sample.
+
+The forward model for an $N$-measurement polarized fluorescence microscope is
+given by
+\begin{align}
+  g_i = \int_{\mathbb{S}^2}d\hat{\textbf{r}}\ h_i(\hat{\textbf{r}})f(\hat{\textbf{r}})\hspace{1em}\text{for}\hspace{1em} i=1,\dotsc,N
+\end{align}
+where $h_i(\hat{\textbf{r}})$ is the point response function of the $i$th
+microscope configuration, the integral is over the sphere $\mathbb{S}^2$, and
+$g_i$ is the $i$th intensity measurement. By discretizing $f(\hat{\mathbf{r}})$
+and expanding $h(\hat{\mathbf{r}})$ in terms of the spherical harmonics, we can
+rewrite Equation~1 as
+\begin{align}
+  \mathbf{g} = \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f}
+\end{align}
+where $\mathbf{f} = [f(\hat{\mathbf{r}}_1), \cdots, f(\hat{\mathbf{r}}_R)]^T$ is
+a vector of $R$ samples of $f(\hat{\mathbf{r}})$; $\mathbf{B}$ is a matrix of
+the spherical harmonics evaluated at the sample points,
+$\mathbf{B}_{ij} = Y_j(\hat{\mathbf{r}}_i)$ where $Y_j$ is the $j$th spherical
+harmonic; $\cdot^+$ is the Moore-Penrose pseudoinverse; $\Psi$ is a matrix of
+the spherical harmonic coefficients of the point response functions,
+$\Psi_{ij} = \int_{\mathbb{S}^2}d\hat{\textbf{r}}\
+h_i(\hat{\mathbf{r}})Y_j(\hat{\mathbf{r}})$; and
+$\mathbf{g} = [g_1, \cdots, g_N]^T$ is a vector of the $N$ intensity
+measurements.
+
+The point response functions for a wide class of polarized fluorescence
+microscopes have been calculated previously\cite{chandler}. For many polarized
+fluorescence microscopes the point response function can be expanded in terms of
+a small number of spherical harmonics. If the point response functions can be
+expanded in terms of $M$ spherical harmonics then $\Psi$ is an $N\times M$
+matrix and $\mathbf{B}^+$ only needs to be calculated in the first $M$
+columns. This simplification reduces Equation 1 from a set of integrals to an
+efficient series of matrix multiplications.
+
+\section{Methods and Results}
+We labeled the actin filaments of a fixed-cell sample with Alexa Fluor 488
+Phalloidin and imaged the sample with an asymmetric 1.1/0.71 NA dual-view
+inverted selective plane illumination microscope\cite{wu2017} with variable
+polarizers added to both illumination paths. The dipole moment of Alexa Fluor
+488 Phalloidin is known to align parallel to the long axis of actin filaments,
+so this sample makes a suitable test specimen for our reconstruction
+algorithm. We imaged the specimen volume eight times---two views with four
+illumination polarization orientations each.
+
+To reconstruct the orientation in each voxel we solved the following problem 
+\begin{align}
+\mathbf{f^{\thinspace *}}= \underset{\mathbf{f}\in\{\mathbf{e}_i\}\ i = 0,\dotsc,R}{\text{argmin}}
+\ \ ||\thinspace\mathbf{g} - \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f}\thinspace||_2^2
+\end{align}
+where $\mathbf{e}_i$ is a vector with a one in the $i$th entry and zeros
+elsewhere. By constraining $\mathbf{f}$ we are assuming that all of the
+fluorophores in each voxel are oriented in the same direction---a reasonable
+assumption for this sample.
 
@@
   \centering
-  \includegraphics[width=17cm]{figs/roi2/data.pdf}
-\caption{Data.}
+  \includegraphics[width=16.cm, trim={0.1cm 1.3cm 0 0.5cm}]{figs/roi2/data.pdf}
+  \caption{Intensity data from a $13.5\times 13.5\times 5.4\ \mu$m${}^3$ volume
+    from two views (rows) and four illumination polarization orientations
+    (columns).}
 \end{figure}
-
+\vspace{0.1em}
 \begin{figure}[htbp]
   \centering
-  \includegraphics[width=17cm]{figs/roi2/recon.pdf}
-\caption{Reconstruction.}
+  \includegraphics[width=16.0cm, trim={1cm 1.2cm 0 0.8cm}]{figs/roi2/recon.pdf}
+  \caption{Orientation reconstructions using (left) only data from the 1.1 NA
+    view, (center) only data from the 0.71 NA view, and (right) data from both
+    views. Data from both views is required to correctly reconstruct the
+    three-dimensional orientation of fluorophores.}
 \end{figure}
-
-\bibliography{abstract}{}
+\vspace{-2.5em}
+{\footnotesize\bibliography{abstract}{}}
 \bibliographystyle{osajnl}

### 2018-01-23 notes/2018-01-18-osa-abstract/abstract.tex
OSA abstract revisions to coauthors.

--- 2018-01-21 notes/2018-01-18-osa-abstract/abstract.tex
@@
 \usepackage{amsmath,amssymb}
+\usepackage{floatrow}
+\usepackage[export]{adjustbox}
 
@@
 
-\title{Three-dimensional fluorophore orientation imaging with polarized multiview microscopy}
+\title{Three-Dimensional Fluorophore Orientation Imaging with Multiview Polarized Microscopy}
 
@@
 \begin{abstract}
-  We show that polarized fluorescence microscopes make band-limited measurements
-  in the angular frequency domain. We use this result to propose and demonstrate
-  efficient algorithms for reconstructing three-dimensional fluorophore
-  orientations from polarized multiview microscope data.
+  \hspace{-0.75em} We show that polarized fluorescence microscopes make
+  band-limited measurements in the angular frequency domain. We use this result
+  to propose and demonstrate efficient algorithms for reconstructing
+  three-dimensional fluorophore orientations from multiview polarized microscope
+  data.
 \end{abstract}
-
+\vspace{0.03em}
 \ocis{180.2520 Fluorescence microscopy, 260.5430 Polarization}
-
+\vspace{-1em}
 \section{Introduction}
+Polarized fluorescence microscopes can measure the orientation of fluorophores
+in live specimens\cite{weiss1999}. Unfortunately, existing techniques are
+limited to imaging two-dimensional orientations, and attempts to generalize
+these approaches to three-dimensional orientations have faced computational
+difficulties. We propose the use of the spherical harmonics to simplify the
+analysis of polarized fluorescence microscopes. In the same way that the Fourier
+transform simplifies the analysis of spatial imaging systems, the spherical
+Fourier transform simplifies the analysis of angular imaging systems.
 
 \section{Theory}
-\cite{chandler}
-\cite{barrett} 
-\section{Results}
+Consider a small voxel that contains many non-interacting fluorophores. We define the
+orientation distribution function $f(\hat{\mathbf{s}})$ as the number of
+fluorophores per steradian oriented in a direction $\hat{\mathbf{s}}$. The goal
+of polarized fluorescence microscopy is to estimate $f(\hat{\mathbf{s}})$ in
+many voxels throughout a three-dimensional sample.
 
+The forward model for an $N$-measurement polarized fluorescence microscope is
+given by
+\begin{align}
+  g_i = \int_{\mathbb{S}^2}d\hat{\mathbf{s}}\ h_i(\hat{\mathbf{s}})f(\hat{\mathbf{s}})\hspace{1em}\text{for}\hspace{1em} i=1,\dotsc,N,
+\end{align}
+where $h_i(\hat{\mathbf{s}})$ is the kernel of the $i$th microscope
+configuration, the integral is over the sphere $\mathbb{S}^2$, and $g_i$ is the
+$i$th intensity measurement. Note that we are applying this forward model to
+each voxel independently---we assume that there is no spatial blurring so the
+signal from each voxel is independent. By discretizing $f(\hat{\mathbf{s}})$ and
+expanding $h(\hat{\mathbf{s}})$ in terms of the spherical harmonics, we can
+rewrite Eq. (1) as
+\begin{align}
+  \mathbf{g} = \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f},
+\end{align}
+where $\mathbf{f} = [f(\hat{\mathbf{s}}_1), \cdots, f(\hat{\mathbf{s}}_R)]^T$ is
+a vector of $R$ samples of $f(\hat{\mathbf{s}})$; $\mathbf{B}$ is a matrix of
+the spherical harmonics evaluated at the sample points,
+$\mathbf{B}_{ij} = Y_j(\hat{\mathbf{s}}_i)$ where $Y_j$ is the $j$th spherical
+harmonic; $\cdot^+$ is the Moore-Penrose pseudoinverse; $\Psi$ is a matrix of
+the spherical harmonic coefficients of the kernels,
+$\Psi_{ij} = \int_{\mathbb{S}^2}d\hat{\textbf{s}}\
+h_i(\hat{\mathbf{s}})Y_j(\hat{\mathbf{s}})$; and
+$\mathbf{g} = [g_1, \cdots, g_N]^T$ is a vector of the $N$ intensity
+measurements.
+
+The kernels for a wide class of polarized fluorescence microscopes have been
+calculated previously\cite{chandler}. For many polarized fluorescence
+microscopes the kernel can be expanded in terms of a small number of spherical
+harmonics. If the kernel can be expanded in terms of $M$ spherical harmonics
+then $\Psi$ is an $N\times M$ matrix and $\mathbf{B}^+$ only needs to be
+calculated in the first $M$ columns. This simplification reduces Eq. (1) from
+a set of integrals to an efficient series of matrix multiplications.
+
+\section{Methods and Results}
+We labeled the actin filaments of a fixed-cell sample with Alexa Fluor 488
+Phalloidin and imaged the sample with an asymmetric 1.1/0.71 NA dual-view
+inverted selective plane illumination microscope with orthogonal objectives
+\cite{wu2017} and variable polarizers added to both illumination paths. The
+dipole moment of Alexa Fluor 488 Phalloidin is known to align parallel to the
+long axis of actin filaments, so this sample makes a suitable test specimen for
+our reconstruction algorithm. We imaged the specimen volume eight times---two
+views with four illumination polarization orientations each.
+
+To reconstruct the orientation in each voxel we solved the following problem 
+\begin{align}
+\mathbf{f^{\thinspace *}}= \underset{\mathbf{f}\in\{\mathbf{e}_i\}\ i = 0,\dotsc,R}{\text{argmin}}
+\ \ ||\thinspace\mathbf{g} - \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f}\thinspace||_2^2,
+\end{align}
+where $\mathbf{e}_i$ is a vector with a one in the $i$th entry and zeros
+elsewhere. By constraining $\mathbf{f}$ we are assuming that all of the
+fluorophores in each voxel are oriented in the same direction---a reasonable
+assumption for this sample.
 \begin{figure}[htbp]
   \centering
-  \includegraphics[width=17cm]{figs/roi2/data.pdf}
-\caption{Data.}
+  \includegraphics[width=16.cm, trim={0.1cm 1.3cm 0 0.5cm}]{figs/roi2/data.pdf}
+  \caption{Fluorescence intensities of a small volume
+    ($13.5\times 13.5\times 5.4\ \mu$m${}^3$) of a cell that was fixed, stained
+    with Alexa Fluor 488 Phalloidin, and imaged in a dual-view microscope
+    (diSPIM). The staining reveals two sets of actin bundles. Because
+    fluorophores are aligned parallel to the bundles, their fluorescence
+    intensities are modulated by the propagation direction and polarization of
+    the excitation light. Bundles from bottom right to top left are highlighted
+    for $x$-illumination and $z$-detection with
+    $\phi_{\text{pol}} = 90^{\circ}$, while their intensities almost disappear
+    for $z$-illumination and $x$-detection with $\phi_{\text{pol}} = 0^{\circ}$,
+    which reveals the bundles running from bottom left to top right. The
+    transfer functions at right use the normalized intensity value in each voxel
+    to assign a color and opacity to each voxel.}
 \end{figure}
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=17cm]{figs/roi2/recon.pdf}
-\caption{Reconstruction.}
-\end{figure}
-
-\bibliography{abstract}{}
+\vspace{-1.22em}
+\begin{minipage}{.263\textwidth}
+  \includegraphics[width=3.7cm, trim={0cm 0cm 0 0cm}, right]{figs/roi2/recon_color.png}
+\end{minipage}% This must go next to `\end{minipage}`
+\begin{minipage}{.639\textwidth}
+  Fig. 2. Reconstruction of fluorophore orientations based on all intensity
+    data shown in Fig. 1. Orientations are shown as short lines only in voxels
+    whose fluorescence intensities surpassed a threshold. To highlight the two
+    sets of actin bundles discussed in the caption of Fig. 1, we split the
+    volume with a plane and colored the proximal voxels red and the distal
+    voxels green. The reconstructed orientations approximately align with the
+    long axes of the actin filaments as expected.
+\end{minipage}
+ \vspace{-1em}
+{\footnotesize\bibliography{abstract}{}}
 \bibliographystyle{osajnl}

### 2018-01-23 notes/2018-01-18-osa-abstract/tester.tex
OSA abstract revisions to coauthors.

\documentclass{article}
\usepackage[demo]{graphicx}
\usepackage{floatrow}
\usepackage[export]{adjustbox}

\begin{document}

\begin{figure}
    \includegraphics[width=1\textwidth,left]{name}
    \caption{centered image}
\end{figure}

\begin{figure}
\flushleft
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=6cm}}]{figure}[\FBwidth]
{\caption{A test figure with its caption side by side}\label{fig:test}}
{\includegraphics[width=4cm]{name}}
\end{figure}

\begin{figure}
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=4cm}}]{figure}[\FBwidth]
{\caption{A test figure with its caption side by side}\label{fig:test}}
{\includegraphics[width=5cm]{name}}
\end{figure}

\end{document}

### 2018-01-23 notes/2018-01-18-osa-abstract/figs/explore_recon.py

@@ -1,0 +1,213 @@
+from polharmonic import data, util, multi
+import numpy as np
+import matplotlib.pyplot as plt
+import os; import time; start = time.time(); print('Running...')
+import dill
+import matplotlib.image as mpimg
+np.set_printoptions(precision=3, suppress=True)
+import matplotlib as mpl
+import subprocess
+mpl.rcParams['font.serif'] = 'Times'
+
+def recon_roi(name, xs, ys, zs, x0, y0, z0, recon_mask_threshold, d, skip, dpi=800, mag=1, note='', idx =[0, 3, 2, 1, 4, 5, 6, 7], file_out=None, second_cal=1):
+    # High level params
+    mfolder = 'asym_dispim'
+    folder = name
+    if not os.path.exists(folder):
+        os.mkdir(folder)
+    int_field_mag = mag
+    recon_mag = mag
+
+    # Import data
+    name_head = '/Users/Talon/GoogleDrive/projects/dispim-data/20170725_Bob_Actin_results/Cell1_LSimaging_registerred/SPIM'
+    names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif',
+             'B_reg_P3.tif', 'B_reg_P4.tif', 'B_reg_P1.tif', 'B_reg_P2.tif']
+    input_files = np.array([name_head + name for name in names])
+
+    # Calibration data
+    cal = np.array([1.06, 1.0, 1.0, 1.03, 
+                    1.08, 1.05, 1.0, 1.04])
+
+    # Reindexing 
+    input_files = input_files[idx]
+    cal = cal[idx]
+
+    # Write to logfile
+    f = open(folder+'/log.txt', 'w')
+    f.write('name: ' + folder + '\n')
+    f.write('note: ' + note + '\n')        
+    f.write('roi coords (px) = ' + str(xs) + ', ' + str(ys) + ', ' + str(zs) + '\n' )
+    f.write('span (px) = ' + str(xs) + ', ' + str(ys) + ', ' + str(zs) + '\n' )
+    f.write('span (um) = ' + str(0.135*xs) + ', ' + str(0.135*ys) + ', ' + str(0.135*zs) + '\n' )
+    f.write('skip (px) = ' + str(skip) + '\n')
+    f.write('threshold (normalized) = ' + str(recon_mask_threshold) + '\n')
+
+    f.close()
+
+    # Load and plot intensity fields
+    intf = data.IntensityField()
[…]

### 2018-01-23 notes/2018-01-18-osa-abstract/figs/recon_data2.py

@@ -1,0 +1,187 @@
+from polharmonic import data, util, multi
+import numpy as np
+import matplotlib.pyplot as plt
+import os; import time; start = time.time(); print('Running...')
+import dill
+import matplotlib.image as mpimg
+np.set_printoptions(precision=3, suppress=True)
+import matplotlib as mpl
+import subprocess
+mpl.rcParams['font.serif'] = 'Times'
+
+def recon_roi(name, xs, ys, zs, x0, y0, z0, recon_mask_threshold, d, skip, dpi=800, mag=1, note=''):
+    # High level params
+    mfolder = 'asym_dispim'
+    folder = name
+    if not os.path.exists(folder):
+        os.mkdir(folder)
+    int_field_mag = mag
+    recon_mag = mag
+
+    # Import data
+    name_head = '/Users/Talon/GoogleDrive/projects/dispim-data/20170725_Bob_Actin_results/Cell1_LSimaging_registerred/SPIM'
+    names = ['A_reg_P3.tif', 'A_reg_P4.tif', 'A_reg_P1.tif', 'A_reg_P2.tif',
+             'B_reg_P3.tif', 'B_reg_P4.tif', 'B_reg_P1.tif', 'B_reg_P2.tif']
+    input_files = np.array([name_head + name for name in names])
+
+    # Calibration data
+    cal = np.array([1.06, 1.0, 1.0, 1.03, 
+                    1.08, 1.05, 1.0, 1.04])
+
+    # Reindexing 
+    idx = [0, 3, 2, 1, 4, 5, 6, 7]
+    input_files = input_files[idx]
+    cal = cal[idx]
+
+    # Write to logfile
+    f = open(folder+'/log.txt', 'w')
+    f.write('name: ' + folder + '\n')
+    f.write('note: ' + note + '\n')        
+    f.write('roi coords (px) = ' + str(xs) + ', ' + str(ys) + ', ' + str(zs) + '\n' )
+    f.write('span (px) = ' + str(xs) + ', ' + str(ys) + ', ' + str(zs) + '\n' )
+    f.write('span (um) = ' + str(0.135*xs) + ', ' + str(0.135*ys) + ', ' + str(0.135*zs) + '\n' )
+    f.write('skip (px) = ' + str(skip) + '\n')
+    f.write('threshold (normalized) = ' + str(recon_mask_threshold) + '\n')
+
+    f.close()
+
+    # Load and plot intensity fields
+    intf = data.IntensityField()
[…]

### 2018-01-23 notes/2018-01-18-osa-abstract/figs/recon_pipeline.py

@@ -1,0 +1,56 @@
+import numpy as np
+import dill
+from polharmonic import util, multi, dist, sft
+import os; import time; start = time.time(); print('Running...')
+np.set_printoptions(precision=3, suppress=True)
+
+# Specify saving path
+folder = 'recon-pipeline'
+if not os.path.exists(folder):
+    os.makedirs(folder)
+data_file = 'asym_dispim/asym_dispim.dat'
+
+# Build microscope
+exp = multi.MultiMicroscope(ill_thetas=[90, 0], det_thetas=[0, 90],
+                            det_nas=[1.1, 0.8], max_l=4, n_pts=5000)
+
+# Calculate and save (comment this on repeat runs)
+# exp.calc_sys_matrix()
+# dill.dump(exp.psi, open(data_file,'wb'))
+
+# Load 
+f = open(data_file, 'rb')
+exp.psi = dill.load(f)
+
+# Calculate B
+exp.calc_B_matrix()
+
+# Generate phantom of true orientations
+nx, ny = 12, 12
+t = np.linspace(0, np.pi/2, nx)
+p = np.linspace(0, 2*np.pi, ny)
+tv, pv = np.meshgrid(t, p)
+tvv = np.expand_dims(tv, 2)
+pvv = np.expand_dims(pv, 2)
+tp_field = np.concatenate([tvv, pvv], 2)
+
+# Expand onto spherical harmonics
+import pdb; pdb.set_trace()
+tp_known_field = util.fibonacci_sphere(exp.n_pts)
+sh_field = sft.field_tp_sft(tp_field, max_l=4)
+df = dist.DistributionField(sh_arr=sh_field)
+df.make_positive(exp.B)
+df.sh_arr[:,:,6:] = 0 # Low pass to simplify phantom
+df.sh_arr = np.expand_dims(df.sh_arr, 2)
+df.plot_dist_field(exp.B, exp.xyz, exp.triangles, filename=folder+'/phantom.png',
+                   r=0.7, mag=2, show=False)
+
+# Reconstruct phantom
+intf = exp.calc_intensity_field(df)
+import pdb; pdb.set_trace() 
+df2 = exp.recon_dist_field(intf)
+df2.plot_dist_field(exp.B, exp.xyz, exp.triangles, filename=folder+'/phantom_recon.png',
+                    r=0.7, mag=2, show=True)
+
+print('Total time: '+str(np.round(time.time() - start, 2)))
+os.system('say "done"')

### 2018-01-28 notes/2018-01-18-osa-abstract/abstract.tex
Finalizing osa abstract.

@@
     for $z$-illumination and $x$-detection with $\phi_{\text{pol}} = 0^{\circ}$,
-    which reveals the bundles running from bottom left to top right. The
-    transfer functions at right use the normalized intensity value in each voxel
-    to assign a color and opacity to each voxel.}
+    which reveals the bundles running from bottom left to top right.}
 \end{figure}
 
-\vspace{-1.22em}
 \begin{minipage}{.263\textwidth}
-  \includegraphics[width=3.7cm, trim={0cm 0cm 0 0cm}, right]{figs/roi2/recon_color.png}
+  \includegraphics[width=3.7cm, trim={0cm 0cm 0 0cm}, right]{figs/roi2/recon_color-min.png}
 \end{minipage}% This must go next to `\end{minipage}`

### 2018-01-28 notes/2018-01-18-osa-abstract/figs/recon_data.py

@@ -53,6 +53,7 @@ def recon_roi(name, xs, ys, zs, x0, y0, z0, recon_mask_threshold, d, skip, dpi=8
     intf.plot(output_file=folder+'/'+'data.pdf', shape=(2,4),
               row_labels=row_labels, col_labels=col_labels,
               d=d, mag=int_field_mag, dpi=400, show=False)
+    import pdb; pdb.set_trace() 
 
     # Build microscopes
     exp = multi.MultiMicroscope(ill_thetas=[90, 0], det_thetas=[0, 90],
@@ -176,7 +177,7 @@ def recon_roi(name, xs, ys, zs, x0, y0, z0, recon_mask_threshold, d, skip, dpi=8
 
 recon_roi(name='roi2', xs=100, ys=100, zs=40, x0=180, y0=545, z0=150,
           recon_mask_threshold=0.4, d=130, skip=3,
-          dpi=800, mag=3, note='zoomed out version of roi1')
+          dpi=1000, mag=5, note='zoomed out version of roi1')
 
 # recon_roi(name='roi3', xs=200, ys=250, zs=100, x0=100, y0=500, z0=100,
 #           recon_mask_threshold=0.25, d=130, skip=4,

### 2018-01-28 polharmonic/data.py

@@ -56,7 +56,7 @@ class IntensityField:
 
             ctf = ColorTransferFunction()
             for i in 0.1*np.arange(9):
-                c = cm.hot(i)
+                c = (1,1,1)#cm.binary(i)
                 ctf.add_rgb_point(i, c[0], c[1], c[2]) 
             # ctf.add_hsv_point(value, h, s, v)
             # ...
@@ -89,14 +89,15 @@ class IntensityField:
 
         # Plot colorbars
         import matplotlib as mpl
-        norm = mpl.colors.Normalize(vmin=0, vmax=1)
-        cb1 = mpl.colorbar.ColorbarBase(axs[0,-1], cmap=cm.hot, norm=norm, orientation='vertical')
-        cb1.set_label('Color Transfer Function', rotation=270, labelpad=22, fontsize=14)
-        cb1.ax.tick_params(axis='both', labelsize=14)
+        axs[0,-1].set_axis_off()
+        # norm = mpl.colors.Normalize(vmin=0, vmax=1)
+        # cb1 = mpl.colorbar.ColorbarBase(axs[0,-1], cmap=cm.hot, norm=norm, orientation='vertical')
+        # cb1.set_label('Color Transfer Function', rotation=270, labelpad=22, fontsize=14)
+        # cb1.ax.tick_params(axis='both', labelsize=14)
 
         norm = mpl.colors.PowerNorm(gamma=1./3.)
         cb2 = mpl.colorbar.ColorbarBase(axs[1,-1], cmap=cm.binary, norm=norm, orientation='vertical')
-        cb2.set_label('Opacity Transfer Function', rotation=270, labelpad=22, fontsize=14)
+        cb2.set_label('Intensity = Opacity', rotation=270, labelpad=22, fontsize=14)
         cb2.ax.tick_params(axis='both', labelsize=14)
         
         # Adjust colorbar position
@@ -107,6 +108,16 @@ class IntensityField:
         pos1 = axs[1,-1].get_position()
         pos2 = [pos1.x0 + diff/5, pos1.y0 + diff,  pos1.width, pos1.height - 2*diff] 
         axs[1, -1].set_position(pos2)
+
+        # Add xyz axes
+        from scipy.ndimage import imread
+        
+        axis1 = fig.add_axes([0.07, 0.775, 0.15, 0.15])
+        axis1.imshow(imread('frames/frames_a.png'))
+        axis1.set_axis_off()
[…]

### 2018-02-09 slides/2018-02-09-group-meeting/group_meeting.tex
Experimental slides + group meeting.

\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{graphicx} \DeclareMathOperator{\argmin}{argmin}

\newcommand{\under}[2]{\underset{\scriptscriptstyle#1}{#2}}

\usetheme{simple}
\usecolortheme{}
\usefonttheme{serif}
\useinnertheme{}
\useoutertheme{}
\author{Talon Chandler}
\date{February 9, 2017}
\title{Update On 3D Orientation Reconstruction}

\begin{document}

\maketitle
\begin{frame}[label=sec-1]{Polarized diSPIM data---Summer 2017}
Since last time:
\begin{itemize}
\item Much faster reconstructions. Reconstructed 350K voxels in 1 min on my
  laptop. Bottlenecks are file I/O (not much I can do here) and visualization
  (chokes a bit on my computer, but live renders on diSPIM computer and RCC).
\item Previously I was just reconstructing the orientation in each voxel. Now
  I'm reconstructing the orientation and the ``number'' of fluorophores in each
  voxel. In each voxel I assign an oriented glyph scaled by the number of
  fluorophores in that voxel.
\end{itemize}
\end{frame}

\begin{frame}[label=sec-1]{Polarized diSPIM data---Summer 2017}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/last_frame.png}
 \end{center}
  Fly-around video here: \url{https://www.dropbox.com/s/szvssvu9fzxsajj/orientation-anim.avi?dl=0}
\end{frame}

\begin{frame}[label=sec-1]{Polarized diSPIM data---Summer 2017}
Notes:
\begin{itemize}
\item The video shows the entire volume 68$\times$108$\times$46 $\mu$m${}^3$.
\item I reconstructed ~10$\times$ as many voxels as the ones shown in the video then
  thresholded the smallest ones away. In Paraview I can change the threshold
  with a slider and choose slice planes quickly. 
\item I'd estimate that a majority of voxel orientations align parallel with the
  actin fibers within 10 degrees. The fiber with 25-30 degree error that we saw
  before is one of the worst cases. The orientations also clearly follow the
  edges of the cells, although the individual fibers are not resolvable in these
  regions. I'm still skeptical of our data ordering, but the results are
  encouraging.
  \end{itemize}
\end{frame}

\begin{frame}{PBT Film via Fred Lanni}
  poly(1,4-phenylene-2,6-benzo-bis-thiazole)
   \begin{center}
     \includegraphics[width=0.4\textwidth]{figs/snap.png}
   \end{center}
   \begin{itemize}
   \item \textbf{Goal}: evaluate this sample as a test specimen for 3D reconstructions
   \item Broad excitation and emission spectra
   \item Stable and insoluble
   \item No published data on fluorescence anisotropy---only Fred's verbal reports
   \end{itemize}
\end{frame}

\begin{frame}{PBT Film, Single-view FluoPolscope\\20$\times$/0.5 NA, 325$\times$325 $\mu$m${}^2$ \\February 6, 2018}
   \begin{center}
     \includegraphics[width=0.6\textwidth]{figs/capture.png}
   \end{center}
\end{frame}

\begin{frame}{PBT Film, Single-view FluoPolscope\\20$\times$/0.5 NA, 325$\times$325 $\mu$m${}^2$ \\February 6, 2018}
  Notes:
  \begin{itemize}
  \item I sandwiched the PBT film between a slide and cover slip so the fibers are 
    approximately flat.
  \item I calculated the orientation lines using the existing FluoPolscope
    algorithms and overlaid the lines on the average intensity image.
  \item Good alignment along the fibers as expected (except for one pesky fiber in
    the bottom center?).
  \end{itemize}
\end{frame}

\begin{frame}{Uncontrolled polarization dual-view data\\0.8/0.8 NA, February 3, 2018}
  Notes:
  \begin{itemize}
  \item We took two datasets with the PBT film on the symmetric diSPIM without
    polarizers. The illumination light was partially polarized on one arm, and
    almost completely polarized on the other arm---I don't expect any
    quantitative results given that we didn't use polarizers.
  \item During our first collection I accidentally saturated the detector for
    most parts of sample. 
  \item During the second collection I turned down the laser power to avoid
    saturation.
  \item The two views from the first (saturated) dataset registered easily.
  \item The two views from the second (unsaturated) dataset didn't register. I
    can't visually match up any of the features in the two datasets either. This
    could be because of orientation dependence, shadowing, something else? 
  \end{itemize}
\end{frame}

\begin{frame}{Saturated data---possible registration issues?}
  \begin{center}
    \includegraphics[width=0.15\textwidth]{figs/SPIMA-regROI}
    \hspace{1em}
    \includegraphics[width=0.15\textwidth]{figs/SPIMB-regROI}    
  \end{center}
  \begin{itemize}
  \item In the saturated registered dataset I noticed that the deformed dataset
    (right) is significantly degraded compared to the undeformed dataset (left).
    I'd expect some degradation on the order of a few pixels, but this seems
    much larger. Do these results match your experience, Min?
  \end{itemize}
\end{frame}

\begin{frame}{Conclusions}
  \begin{itemize}
  \item The PBT film is a convenient sample that displays fluorescence
    anisotropy.
  \item I think it will be a useful sample for testing the diSPIM with
    polarizers. We will be able to fray the sample into all orientations, and
    we won't have to worry about labeled cells being too flat or GUVs
    being too fragile. 
  \end{itemize}
\end{frame}

\begin{frame}{Next Up}
  Next week: 
  \begin{itemize}
  \item Thesis proposal document
  \end{itemize}    
  After that: 
  \begin{itemize}
  \item Formulate joint spatio-angular restoration problem
  \item Answer lingering questions about relating these reconstructions to
    existing work. How is the ``anisotropy'' related to these reconstructions?
    Can we understand Rudolf's existing reconstructions using spherical
    harmonics?
  \end{itemize}    
\end{frame}

\end{document}

### 2018-02-20 notes/2017-01-17/figs/ortho/svs.tex
Generate ortho (ispim) svs.

\documentclass[preview, border={0pt 0pt 2pt 2pt}]{standalone}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz, pgfplots}
\usepackage{graphicx}
\begin{document}
\begin{tikzpicture}
  \pgfplotsset{width=10cm, height=5cm}
  \begin{axis}[
    axis lines=left,
    xlabel=,
    every outer x axis line/.append style={-},
    every outer y axis line/.append style={-},    
    ylabel=Singular Value,
    ylabel near ticks,
    xmin=-0.5, xmax=2.5,
    ymin=0, ymax=1.2,
    xtick={0,...,2},
    ytick={0,0.4,...,1.2},    
    xticklabels={\includegraphics[scale=0.25]{sv0},\includegraphics[scale=0.25]{sv1}, \includegraphics[scale=0.25]{sv2}},
    xticklabel style={yshift=15pt},
    ] 
    \addplot+[
    ycomb,
    black,
    mark options={black}
    ] plot coordinates
	{(0,0.96) (1,0.43) (2,0.31)};
\end{axis}
\end{tikzpicture}
\end{document}

### 2018-02-20 notes/2017-01-17/figs/analyze_ortho.py

@@ -1,7 +1,7 @@
 import numpy as np
 import dill
-from util import *
-from microscopes import *
+from polharmonic.util import *
+from polharmonic.microscopes import *
 np.set_printoptions(precision=2, suppress=True)
 
 # Main script

### 2018-02-20 polharmonic/microscopes.py

@@ -1,9 +1,9 @@
 import numpy as np
-from util import *
+from polharmonic.util import *
 from sympy import *
 from sympy.matrices.dense import *
 import sympy.functions.special.spherical_harmonics as sh
-from sft import *
+from polharmonic.sft import *
 import dill
 
 # Global initialize symbols
@@ -234,8 +234,10 @@ def generate_plots(psi, col_labels, row_labels, sch_strings, folder):
     # SVD
     U, s, Vh = np.linalg.svd(psi.real)
     V = Vh.conj().T
-    
+
+    import pdb; pdb.set_trace() 
+
     # Plot individual singular distributions
-    plot_multiple_spherical(V, col_labels, filename=folder+'/sv', r=0.8)
+    plot_multiple_spherical(V, col_labels, filename=folder+'/sv', r=0.65)
 
     # Plot singular value spectrum TODO

### 2018-02-20 polharmonic/sft.py

@@ -1,4 +1,4 @@
-from util import *
+from polharmonic.util import *
 import numpy as np
 from sympy import *
 import sympy.functions.special.spherical_harmonics as sh

### 2018-02-23 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Spatio-angular kernel notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%

\hyphenpenalty=10000
\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\ro}[1]{\mathbf{\mathfrak{r}_o}}
\providecommand{\so}[1]{\mathbf{\hat{s}_o}}
\providecommand{\rb}[1]{\mathbf{r_b}}
\providecommand{\rd}[1]{\mathbf{r_d}}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Spatio-angular Kernels and Transfer Functions for Fluorescence Microscopes \vspace{-2.5em}} \author{Talon Chandler}% and Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will consider a single-view fluorescence microscope
\textbf{with no polarizing filters} that uses TIRF excitation to excite
fluorophores in all orientations equally. This excitation scheme allows us to
focus exclusively on the detection process. We will find the spatio-angular
kernel of this microscope and analyze it in the frequency domain using the
spatio-angular Fourier transform. Along the way we will show that uniform
excitation fluorescence microscopes have spatial and angular band-limits.

We use plain roman type for scalars, e.g., $x, y, z$; bold lowercase roman type
for two-dimensional vectors, e.g., $\mb{r}$; hats for unit vectors, e.g.,
$\mb{\hat{s}}$; bold lowercase gothic type for three-dimensional vectors, e.g.,
$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g., $\mb{R}$.

\section{General Forward Model}
Consider a three-dimensional field of oriented fluorescent dipoles. We can
represent the entire object using a function $f(\ro{}, \so{})$ that
returns the number of dipoles at position $\ro{}$ per unit volume oriented in
direction $\so{}$ per unit solid angle.

The intensities measured using a general linear measurement system can by
modeled using
\begin{align}
  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})
\end{align}
where $g_i(\mb{r_d})$ is the camera frame collected under the $i$th measurement
configuration ($i$ indexes polarizer settings or views), $\mb{r_d}$ is the
two-dimensional detector coordinate, and
$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular kernel of the
$i$th measurement configuration. Our goal is to reconstruct the object
$f(\ro{}, \so{})$ from intensity measurements $g_i(\rd{})$.

\section{Spatio-angular Kernel}
In this section we will write out the kernel
$h(\rd{}; \ro{}, \so{})$ for a non-polarized single-view
fluorescence microscope with angularly uniform TIRF illumination. This section
mostly restates the results of XXXBacker and Moerner 2014XXX, so I recommend reading that paper for a more
complete understanding.

First, we find the electric field $\mb{e}$ at position
$\rb{} = r_b\cos\phi_b \mh{x} + r_b\sin\phi_b\mh{y}$ in the back focal plane
created by a single dipole at position $\ro{}=x_o\mh{x} + y_o\mh{y} + z_o\mh{z}$ and
oriented in direction $\so{}$
\begin{align}
  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(x_ox_b + y_oy_b + z_o\rho_b)}\sqrt{\frac{n_o}{n_b\rho_b}}
  \begin{bmatrix}
    \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-r_b\cos\phi_b\\
    \sin\phi_b\cos\phi_b(\rho_b - 1)&\cos^2\phi_b + \rho_b\sin^2\phi_b&-r_b\sin\phi_b\\
    0&0&0
  \end{bmatrix}\so{}\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
\end{align}
where we have defined $\rho_b \equiv \sqrt{1 - r_b^2}$ and $\Pi(x)$ is a boxcar
function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
expression term by term: the exponential term accounts for the phase objective,
the square root term conserves power before and after the objective lens, the
matrix is a position-dependent rotation matrix that models the electric field
rotation caused by the objective lens, $\so{}$ is the dipole orientation unit
vector, and $\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the
numerical aperture of the lens with
$r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$.

% Notice that the matrix in Eq. \ref{eq:bfp} contains zeros in the third
% row---this means that the electric field in the back focal plane does not
% contain a longitudinal component. Also notice that Eq. \ref{eq:bfp} does not
% depend on the transverse position of the dipole $x$ and $y$, but it does depend
% on the longitudinal position of the dipole $z$. Therefore, we can say that the
% imaging system has transverse shift invariance but not longitudinal shift
% invariance.

The next step is to find the electric field in the detector plane. We can use
the paraxial approximation here because the focal length of the tube lens is
long. In this case the electric field in the detector plane is the Fourier
transform of the electric field in the back focal plane
\begin{align}
  \mb{e_d}(\rd{};\ro{}, \so{}) = \int_{\mathbb{R}^2}d\rb{}\ \mb{e_b}(\rb{};\ro{}, \so{}) \me^{i(kn_b/f_t)\rb{}\cdot\rd{}}. \label{eq:fourier}
\end{align}

Finally, we can find the intensity measured in the detector plane (the kernel)
by taking the modulus squared of the electric field
\begin{align}
  h(\rd{}; \ro{}, \so{}) = |\mb{e_d}(\rd{};\ro{}, \so{})|^2. \label{eq:kernel}
\end{align}

Unfortunately, the Fourier transform in Eq. \ref{eq:fourier} cannot be written
in closed form, but equation \ref{eq:kernel} can be rearranged so that it can be
evaluated using six precomputed 2D Fourier transforms per $z_o$ position.

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 0.25\textwidth]{../figures/schematic.pdf}
   \caption{Simplified schematic of a single-view fluorescence microscope. The
     object is placed near the focal point of an objective lens with focal
     length $f_{o}$ in a medium with refractive index $n_o$. The object is
     parameterized by the 3D position vector $\ro{}$ ($\mb{o}$ for object) and a
     orientation unit vector $\so{}$. The light emitted by the fluorescent
     object is collected and collimated by the objective lens so that the
     electric fields are purely transverse in back focal plane. Points in the
     back focal plane are parameterized by a 2D position vector $\rb{}$
     ($\mb{b}$ for back focal plane). Finally, the tube lens with focal length
     $f_t$ refocuses the light onto a detector. Points on the detector are
     parameterized by a 2D position vector $\rd{}$ ($\mb{d}$ for detector). The
     back focal plane and detector are in a medium with refractive index
     $n_b$. Note that this schematic is not to scale---in typical microscopes
     $f_o \ll f_t$ to provide magnification.}
   \label{fig:frames_a}
\end{figure}

TODO: Show transverse shift invariance.

TODO: Program up an efficient implementation of $h(\rd{}; \ro{}, \so{})$.

TODO: Plot select kernels.

\section{Spatio-angular Transfer Function}

TODO: Show angular band limit by taking angular Fourier transform only.

TODO: Show spatial band limit by taking the spatial Fourier transform of the
first angular term.

TODO: Evaluate and plot spatio-angular transfer function numerically. This
will be expensive, but it only has to be done once for each microscope.

\section{Reconstruction}

\section{Conclusions}
\end{document}

### 2018-03-04 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Spatio-angular transfer functions w/ plots.

@@
 \hyphenpenalty=10000
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+
 \usepackage{tocloft}
@@
 \providecommand{\mf}[1]{\mathfrak{#1}}
-\providecommand{\ro}[1]{\mathbf{\mathfrak{r}_o}}
-\providecommand{\so}[1]{\mathbf{\hat{s}_o}}
-\providecommand{\rb}[1]{\mathbf{r_b}}
-\providecommand{\rd}[1]{\mathbf{r_d}}
+\providecommand{\ro}[1]{\mathbf{\mathfrak{r}}_o}
+\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
+\providecommand{\rb}[1]{\mathbf{r}_b}
+\providecommand{\rbm}[1]{r_b^{\text{m}}}
+\providecommand{\rd}[1]{\mathbf{r}_d}
 \providecommand{\mh}[1]{\mathbf{\hat{#1}}}
@@
 \begin{document}
-\title{\vspace{-2.5em} Spatio-angular Kernels and Transfer Functions for Fluorescence Microscopes \vspace{-2.5em}} \author{Talon Chandler}% and Patrick La Rivi\`ere}
+\title{\vspace{-2.5em} Spatio-angular transfer functions for fluorescence microscopes\vspace{-1em}}  \author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
 \date{\vspace{-1em}\today\vspace{-1em}}
 \maketitle
+\begin{abstract}
+  We investigate how the orientation and position of fluorescent dipole emitters
+  affects microscopic imaging using electromagnetic optics theory. Starting with
+  the thoroughly studied spatio-angular point spread function, we introduce the
+  spatio-angular coherent spread function, coherent transfer function, and
+  optical transfer function as electromagnetic counterparts to well-known
+  functions in scalar optics theory. We use these concepts to show that
+  fluorescence microscopes have a spatio-angular band limit. Finally, we study
+  polarized light microscopes and find that polarized illumination is a type of
+  structured illumination that extends the angular band limit.
+\end{abstract}
 \section{Introduction}
-In these notes we will consider a single-view fluorescence microscope
-\textbf{with no polarizing filters} that uses TIRF excitation to excite
-fluorophores in all orientations equally. This excitation scheme allows us to
-focus exclusively on the detection process. We will find the spatio-angular
-kernel of this microscope and analyze it in the frequency domain using the
-spatio-angular Fourier transform. Along the way we will show that uniform
-excitation fluorescence microscopes have spatial and angular band-limits.
+TODO
 
@@
 
-\section{General Forward Model}
+\section{General forward model}
 Consider a three-dimensional field of oriented fluorescent dipoles. We can
-represent the entire object using a function $f(\ro{}, \so{})$ that
-returns the number of dipoles at position $\ro{}$ per unit volume oriented in
-direction $\so{}$ per unit solid angle.
+represent the entire field using a function $f(\ro{}, \so{})$ that returns the
+number of dipoles at position $\ro{}$ per unit volume oriented in direction
+$\so{}$ per unit solid angle. We call $f(\ro{}, \so{})$ the fluorescence
+spatio-angular density because it has units of fluorophores per volume per solid
+angle.
 
-The intensities measured using a general linear measurement system can by
-modeled using
+If each fluorophore in the field fluoresces independently then the measured
+intensity is a weighted sum of the intensity contributions from each
+fluorophore, and we can model the imaging system with
 \begin{align}
-  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})
+  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})\label{eq:forward}
 \end{align}
-where $g_i(\mb{r_d})$ is the camera frame collected under the $i$th measurement
-configuration ($i$ indexes polarizer settings or views), $\mb{r_d}$ is the
-two-dimensional detector coordinate, and
-$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular kernel of the
-$i$th measurement configuration. Our goal is to reconstruct the object
+where $g_i(\mb{r_d})$ are the intensities measured by the detector under the
+$i$th measurement configuration ($i$ can index polarizer settings or views),
+$\mb{r_d}$ is the two-dimensional detector coordinate, and
+$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular point spread function (PSF) of
+the $i$th measurement configuration. Our goal is to reconstruct the object
 $f(\ro{}, \so{})$ from intensity measurements $g_i(\rd{})$.
 
-\section{Spatio-angular Kernel}
-In this section we will write out the kernel
-$h(\rd{}; \ro{}, \so{})$ for a non-polarized single-view
-fluorescence microscope with angularly uniform TIRF illumination. This section
-mostly restates the results of XXXBacker and Moerner 2014XXX, so I recommend reading that paper for a more
-complete understanding.
+We can also use the spatio-angular density to model translating and rotating
+fluorophores. As long as each fluorescence emission is an independent event,
+then equation \ref{eq:forward} is a valid way to model the imaging system.
 
-First, we find the electric field $\mb{e}$ at position
-$\rb{} = r_b\cos\phi_b \mh{x} + r_b\sin\phi_b\mh{y}$ in the back focal plane
-created by a single dipole at position $\ro{}=x_o\mh{x} + y_o\mh{y} + z_o\mh{z}$ and
-oriented in direction $\so{}$
+\section{Spatio-angular point spread function}
+\begin{figure}[h]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 0.4\textwidth]{../figures/schematic.pdf}
+   \caption{Simplified schematic of a single-view fluorescence microscope. The
+     object is placed near the focal point of an aplanatic objective lens with
+     focal length $f_{o}$ in a medium with refractive index $n_o$. The object is
+     parameterized by the 3D position vector $\ro{}$ ($o$ for object) and an
+     orientation unit vector $\so{}$. The light emitted by the fluorescent
+     object is collected and collimated by the objective lens so that the
+     electric fields are purely transverse in the back focal plane. Points in
+     the back focal plane are parameterized by a 2D position vector $\rb{}$ ($b$
+     for back focal plane). Finally, the tube lens with focal length $f_t$
+     refocuses the light onto a detector. Points on the detector are
+     parameterized by a 2D position vector $\rd{}$ ($d$ for detector). The back
+     focal plane and detector are in a medium with refractive index $n_t$. Note
+     that this schematic is not to scale---we consider the case where
+     $f_o \ll f_t$.}
+   \label{fig:frames_a}
+\end{figure}
+
+Figure \ref{fig:frames_a} shows a schematic of the fluorescence microscope that
+we are considering with a summary of our notation. We start by following Backer
+and Moerner \cite{backer2014} to find the electric field in the back focal plane
+due to a single dipole emitter at position $\ro{}$ oriented along $\so{}$ as 
 \begin{align}
-  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(x_ox_b + y_oy_b + z_o\rho_b)}\sqrt{\frac{n_o}{n_b\rho_b}}
+  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(z_o\rho_b)}\sqrt{\frac{1}{\rho_b}}
   \begin{bmatrix}
@@
     0&0&0
-  \end{bmatrix}\so{}\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos\varphi_o\sin\vartheta_o\\
+    \sin\varphi_o\sin\vartheta_o\\
+    \cos\vartheta_o
+  \end{bmatrix}
+\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
 \end{align}
@@
 function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
-expression term by term: the exponential term accounts for the phase objective,
+expression term by term---the exponential term accounts for the defocus phase,
 the square root term conserves power before and after the objective lens, the
-matrix is a position-dependent rotation matrix that models the electric field
-rotation caused by the objective lens, $\so{}$ is the dipole orientation unit
-vector, and $\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the
-numerical aperture of the lens with
-$r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$.
+matrix models the dipole emission process and electric field rotation caused by
+the objective lens, the vector is the dipole orientation unit vector, and
+$\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the numerical
+aperture of the lens with $r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$. Notice
+that we have omitted the dependence on the transverse position of the
+fluorophore $x_o$ and $y_o$. This is because we assume that the objective is
+aplanatic, so it displays transverse shift-invariance and the constant phase
+factor does not affect our discussion.
 
-% Notice that the matrix in Eq. \ref{eq:bfp} contains zeros in the third
-% row---this means that the electric field in the back focal plane does not
-% contain a longitudinal component. Also notice that Eq. \ref{eq:bfp} does not
-% depend on the transverse position of the dipole $x$ and $y$, but it does depend
-% on the longitudinal position of the dipole $z$. Therefore, we can say that the
-% imaging system has transverse shift invariance but not longitudinal shift
-% invariance.
+We can find the intensity in the detector plane by propagating the electric
+field to the detector plane using a scaled Fourier transform then taking the
+modulus squared
+\begin{align}
+  h_i(\rd{}; \ro{}, \so{}) = \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \label{eq:kernel}.
+\end{align}
+Following Novotny \cite{nov2006}, we write the Fourier transform in polar
+coordinates, evaluate the azimuthal integrals, and write the result concisely in
+terms of three radial integrals
+\begin{align}
+    h_i(\rd{}; \ro{}, \so{}) &= \left|\mb{e}_d(\rd{}; \ro{}, \so{})\right|^2 \label{eq:kernel2}.\\
+  \mb{e}_d(\rd{}; \ro{}, \so{}) &\propto
+  \begin{bmatrix}
+    I_0 + I_2\cos(2\phi_d) & I_2\sin(2\phi_d) & -2iI_1\cos\phi_d\\
+    I_2\sin(2\phi_d) & I_0 - I_2\cos(2\phi_d) & -2iI_1\sin\phi_d\\
+    0&0&0\\
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos\varphi_o\sin\vartheta_o\\
+    \sin\varphi_o\sin\vartheta_o\\
+    \cos\vartheta_o
+  \end{bmatrix}\label{eq:elec}
+\end{align}
+where $I_0, I_1$ and $I_2$ are
+\begin{align}
+  I_0(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  I_1(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  I_2(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
+\end{align}
+By plugging Eq. \ref{eq:elec} into equation Eq. \ref{eq:kernel2} and expanding in
+terms of the spherical harmonic functions, we can rewrite the spatio-angular
+PSF as
+\begin{equation}
+  \begin{split}
+  h(\rd{}; \ro{}, \so{}) \propto &\frac{4\sqrt{\pi}}{3}\left(I_0^2 + 2I_1^2 + I_2^2\right)Y_0^0(\so{}) -\frac{8\sqrt{15\pi}}{15}I_0I_2\sin(2\phi_d)Y_2^{-2}(\so{})\\ &+ \frac{4\sqrt{5\pi}}{15}\left(-I_0^2 + 4I_1^2 - I_2^2\right)Y_2^{0}(\so{}) +\frac{8\sqrt{15\pi}}{15}I_0I_2\cos(2\phi_d)Y_2^{-2}(\so{}).
+\label{eq:kerna}
+\end{split}
+\end{equation}
 
-The next step is to find the electric field in the detector plane. We can use
-the paraxial approximation here because the focal length of the tube lens is
-long. In this case the electric field in the detector plane is the Fourier
-transform of the electric field in the back focal plane
+We have chosen to write the spatio-angular PSF in terms of spherical harmonic
+functions for two reasons. First, it allows us to express the spatio-angular PSF
+very concisely. Instead of considering the point spread function for every
+possible dipole orientation, we only need to consider four spatio-angular
+PSFs---one for each spherical harmonic. Second, the spherical harmonic functions
+form an orthonormal basis for functions on the sphere---a convenient fact that
+we will use later.
+
+It is useful to compare equation \ref{eq:kerna} to Backer and Moerner's approach
+\cite{backer2014}. They expand the spatio-angular PSF in terms of six second
+moments of the fluorophore distribution
+$\{s_x^2, s_y^2, s_z^2, s_xs_y, s_xs_z, s_ys_z\}$. This approach is very
+useful---only six precomputed spatio-angular PSFs are required to represent an
+arbitrary spatio-angular PSF. Instead of expanding in terms of six second
+moments, we expand onto just four spherical harmonics which, unlike the second
+moments, are orthonormal functions. In the next section we will use the
+orthonormality of the spherical harmonics to derive spatio-angular transfer
+functions for fluorescence microscopes.
+
+For now, let's look closer at the spatio-angular PSF in a special case. By
+constraining the object to the focal plane ($z_o$ = 0) and applying the paraxial
+approximation ($\sin\theta\approx\theta$ and $\cos\theta\approx 1$), the
+integrals $I_{0-2}$ can be evaluated in terms of Bessel functions. We can
+evaluate $I_0$ and $I_1$ with the help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$
+and $\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $I_2 = 0$ because
+$J_2(x)$ is zero to first order. In this case, the spatio-angular PSF simplifies
+to
 \begin{align}
-  \mb{e_d}(\rd{};\ro{}, \so{}) = \int_{\mathbb{R}^2}d\rb{}\ \mb{e_b}(\rb{};\ro{}, \so{}) \me^{i(kn_b/f_t)\rb{}\cdot\rd{}}. \label{eq:fourier}
+      \lim_{\theta_{\text{max}} \ll \pi/2} h(\rd{}; \mathbf{r}_o, z_o=0, \so{}) \equiv h^*(\rd{}; \mathbf{r}_o, \so{}) \propto \frac{4\sqrt{\pi}}{3}({I_0^*}^2 + 2{I_1^*}^2)Y_0^0(\so{}) + \frac{4\sqrt{5\pi}}{15}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)Y_2^{0}(\so{})\label{eq:para}
 \end{align}
+where the integrals evaluate to
+\begin{align}
+  {I_0^*} = \left(\frac{\text{NA}}{n_o}\right)^2\left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
+  \hspace{2em}
+    {I_1^*} = \left(\frac{\text{NA}}{n_o}\right)^3\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
+  \intertext{and we have substituted}
+  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
+  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
+  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
+\end{align}
+We will continue to use an asterisk to mark the terms where we have used the paraxial
+approximation and constrained the object to the focal plane.
 
-Finally, we can find the intensity measured in the detector plane (the kernel)
-by taking the modulus squared of the electric field
+First, consider the coefficient on the $Y_0^0$ spherical harmonic in
+Eq. \ref{eq:para}. This coefficient is the point spread function for a angularly
+uniform distribution of fluorophores. The first term of the coefficient $I_0^*$
+is the familiar Airy disk that arises from the contribution of dipoles oriented
+in the transverse plane, while the second term $I_1^*$ is a smaller factor that
+arises from dipoles oriented outside of the transverse plane. This leads to an
+interesting conclusion---a uniform distribution of dipoles has a point spread
+function that is slightly wider than an Airy disk even in the paraxial
+approximation. The Airy disk is usually derived using paraxial scalar optics
+while here we have used paraxial electromagnetic optics. Therefore, we can
+consider the second term to be an electromagnetic correction to the Airy
+disk. We will quantify this difference in the next section.
+
+Next, consider the coefficient on the $Y_2^0$ spherical harmonic in
+Eq. \ref{eq:para}. This coefficient is the spatial PSF for a distribution of
+fluorophores proportional to $3\cos^2\vartheta_o - 1$. Counterintuitively, this
+fluorophore distribution cannot exist because it would require a negative number
+of fluorophores along some orientations; but if this distribution could exist,
+then this coefficient would be its spatial PSF. Considering negative
+distributions of fluorophores in our calculations should not be cause for
+concern. The spherical harmonics span the space of functions on the sphere, so
+any positive fluorophore distribution can be represented by the spherical
+harmonics and we never need to consider negative fluorophores.
+
+Finally, consider all of the spherical harmonics that have a zero
+coefficient. These spherical harmonics span the angular null space of our
+measurement system---fluorophore distributions that lie in the null space do not
+affect the measured intensities. Under the paraxial approximation all of the
+non-zero coefficients are rotationally symmetric ($m=0$) spherical harmonics
+which means that the transverse orientation of the dipoles does not affect the
+PSF. In the high NA case this is no longer true---two $m=2$ spherical harmonics
+have non-zero coefficients and the transverse orientation of dipoles does affect
+the PSF.
+
+\section{Spatio-angular transfer functions}
+We define the spatio-angular optical transfer function (OTF) as
 \begin{align}
-  h(\rd{}; \ro{}, \so{}) = |\mb{e_d}(\rd{};\ro{}, \so{})|^2. \label{eq:kernel}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{}) Y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
 \end{align}
+The spatio-angular OTF measures the ability of the microscope to pass
+spatio-angular harmonics---instead of the usual spatial harmonics
+$\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}$ we now need consider the spatio-angular
+harmonics $Y_l^m(\so{})\thinspace\me^{i 2\pi
+  \ro{}\cdot\bs{\nu}_o}$. Eq.~\ref{eq:ft} can be interpreted as the
+spatio-angular Fourier transform of the spatio-angular PSF.
 
-Unfortunately, the Fourier transform in Eq. \ref{eq:fourier} cannot be written
-in closed form, but equation \ref{eq:kernel} can be rearranged so that it can be
-evaluated using six precomputed 2D Fourier transforms per $z_o$ position.
+We can plug Eq. \ref{eq:kerna} into \ref{eq:ft} and use the orthonormality
+relation for spherical harmonics $\int_{\mathbb{S}^2}d\so{} Y_{l_0}^{m_0}(\so{})Y_{l_1}^{m_1}(\so{}) = \delta(l_0 - l_1)\delta(m_0 - m_1)$ to find that
+\begin{equation}
+  \begin{split}
+  H_l^m(\bs{\nu}_o) \propto \int_{\mathbb{R}^3}d\ro{}  &\frac{4\sqrt{\pi}}{3}\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l)\delta(m)\\ &-\frac{8\sqrt{15\pi}}{15}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2)\delta(m+2)\\ &+ \frac{4\sqrt{5\pi}}{15}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2)\delta(m)\\ &+\frac{8\sqrt{15\pi}}{15}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2)\delta(m-2).\label{eq:otf}
+\end{split}
+\end{equation}
+We can see that the microscope has an angular band limit---the microscope only
+passes intensity contributions for fluorophore distributions in the $l=0$ and
+$l=2$ bands.
+
+Once again, we constrain the object to the focal plane and apply the paraxial
+approximation to find that
+\begin{align}
+  {H_l^m}^*(\nu_o^x, \nu_o^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\frac{4\sqrt{\pi}}{3}({I_0^*}^2 + 2{I_1^*}^2)\delta(l)\delta(m) + \frac{4\sqrt{5\pi}}{15}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)\delta(l-2)\delta(m)\right]  \me^{i 2\pi(\nu_o^xx_o + \nu_o^yy_o)}\label{eq:otfh}
+\end{align}
+The integrals in Eqs. \ref{eq:otf} and \ref{eq:otfh} cannot be solved directly.
+We could proceed numerically like \cite{backer2014}, but instead we use the
+Wiener-Khinchin theorem to simplify the integral \cite{goodman1996,
+  papoulis2002}. We plug Eq. \ref{eq:kernel} into Eq. \ref{eq:ft}
+\begin{align}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2
+ Y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}, \label{eq:ft2}
+\end{align}
+change the order of the integrals
+\begin{align*}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ Y_l^m(\so{}) \int_{\mathbb{R}^3}d\ro{}\ \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \me^{i 2\pi \ro{}\cdot\bs{\nu}_o},
+\end{align*}
+and apply the Wiener-Khinchin theorem $\mathcal{F}\{|\mathcal{F}\{\mb{e}_b\}|^2\} = \mb{e}_b \star \mb{e}_b$ to find that
+\begin{align*}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ Y_l^m(\so{}) \left[\mb{e}_b \star \mb{e}_b\right](\bs{\nu}). 
+\end{align*}
+The vector auto-correlation is given by
+\begin{align*}
+[\mb{e}_b \star \mb{e}_b](\bs{\nu}) = \int_{\mathbb{R}^2}d\bs{r}_b \mb{e}_b^{T}(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu})
+\end{align*}
+where $\cdot^T$ denotes the transpose operator. To find the OTF we need to
+evaluate the vector auto-correlation of the electric field in the back focal
+plane then take the angular Fourier transform of the result.
+
+TODO: The auto-correlation calculation is in progress. I should be able to find an
+analytic formula for the OTF, but for now I am plotting it numerically in Figure 3.
+
+TODO: Plot PSFs and OTFs numerically without the paraxial approximation.
+
+TODO: Consider detection polarizers.
+
+TODO: Consider illumination polarizers.
+
+% For in focus objects under the paraxial approximation, the electric field in the back
+% focal plan is given by
+% \begin{align}
+%   \mb{e}_b^*(\rb{}) &\propto 
+%   \begin{bmatrix}
+%     1&0&-r_b\cos\phi_b\\
+%     0&1&-r_b\sin\phi_b\\    
+%     0&0&0\\
+%   \end{bmatrix}
+%   \begin{bmatrix}
+%     \cos\varphi_o\sin\vartheta_o\\
+%     \sin\varphi_o\sin\vartheta_o\\
+%     \cos\vartheta_o\\
+%   \end{bmatrix}
+%   \Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
+%   =  \begin{bmatrix}
+%     Y_1^{-1}(\so{}) + r_b\cos\phi_bY_1^0(\so{})\\
+%     Y_1^{1}(\so{}) + r_b\sin\phi_bY_1^0(\so{})\\
+%     0
+%   \end{bmatrix}
+% \Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).
+% \end{align}
+% Next we calculate the integrand of the auto-correlation
+% \begin{align*}
+%   \mb{e}_b^T(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu}) = \left[{Y_1^{-1}}^2 + 2x_bY_1^0Y_1^{-1} + x_b^2{Y_1^0}^2\right]\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).
+% \end{align*}
+
+% The autocorrelation of the electric field in the back focal plane gives the OTF
+% \begin{align*}
+%   H_l^m(\bs{\nu}) &= \frac{\int_{\mathbb{R}^2}d\bs{k}_b \mb{e_b}\left(\bs{k}_b + \frac{1}{2}\bs{\nu}\right)\mb{e_b}^{T}\left(\bs{k}_b + \frac{1}{2}\bs{\nu}\right)}{\int_{\mathbb{R}^2}d\bs{k}_b|\mb{e_b}(\bs{k_b})|^2}
+% \end{align*}
+% where $\cdot^T$ denotes the transpose operator.
+% \begin{align*}
+%   = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \mb{e_b}(\rb{} + \frac{1}{2}\bs{\nu})\mb{e_b}^{\dagger}(\rb{} - \frac{1}{2}\bs{\nu})
+% \end{align*}
+
+\tikzstyle{block} = [draw, fill=white, rectangle, 
+    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
+\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
+\tikzstyle{input} = [coordinate]
+\tikzstyle{output} = [coordinate]
+\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+\begin{figure}
+\begin{tikzpicture}[auto, node distance=3cm,>=latex]
+    \node [input, name=input] {};
+    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
+    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
+    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
+    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};
+
+    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
+    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
+    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
+    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
+      \end{tikzpicture}
+      \centering
+      \captionsetup{width=1.0\linewidth}
+      \caption{Summary of relationships between the CSF, CTF, PSF, and OTF where
+        $\mathcal{F}_D$, $|\cdot|_D$, and $\star_D$ denote the Fourier
+        transform, norm, and autocorrelation over the set $D$, respectively. See
+        \cite{goodman1996} and \cite{mertz2009} for analogous diagrams under
+        scalar optics approximations.}
+    \end{figure}
 
@@
    \centering
-   \includegraphics[width = 0.25\textwidth]{../figures/schematic.pdf}
-   \caption{Simplified schematic of a single-view fluorescence microscope. The
-     object is placed near the focal point of an objective lens with focal
-     length $f_{o}$ in a medium with refractive index $n_o$. The object is
-     parameterized by the 3D position vector $\ro{}$ ($\mb{o}$ for object) and a
-     orientation unit vector $\so{}$. The light emitted by the fluorescent
-     object is collected and collimated by the objective lens so that the
-     electric fields are purely transverse in back focal plane. Points in the
-     back focal plane are parameterized by a 2D position vector $\rb{}$
-     ($\mb{b}$ for back focal plane). Finally, the tube lens with focal length
-     $f_t$ refocuses the light onto a detector. Points on the detector are
-     parameterized by a 2D position vector $\rd{}$ ($\mb{d}$ for detector). The
-     back focal plane and detector are in a medium with refractive index
-     $n_b$. Note that this schematic is not to scale---in typical microscopes
-     $f_o \ll f_t$ to provide magnification.}
+   \includegraphics[width = 1.\textwidth]{../calculations/ft.pdf}
+   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
+     single-view fluorescence microscope with NA=0.8. The solid line is the PSF
+     for $Y_0^0$ distributions and the dashed line is the PSF for $Y_2^0$
+     distributions. $Y_2^0$ includes ``negative'' fluorophores, so it gives rise
+     to a negative PSF. \textbf{Right:} Numerical paraxial spatio-angular
+     optical transfer function for the same microscope. The $Y_0^0$ term has a
+     spatial low-pass reponse while the $Y_2^0$ term has a spatial high-pass
+     response. The relative sizes of the two terms is set by the NA---increasing
+     the NA increases the relative size of the $Y_0^2$ term. Vertical scaling is
+     correct---horizontal scaling is in progress. The cutoff frequency is
+     proportional to NA and is the same for both spherical harmonic terms.}
    \label{fig:frames_a}
@@
 
-TODO: Show transverse shift invariance.
+\section{Conclusions}
 
-TODO: Program up an efficient implementation of $h(\rd{}; \ro{}, \so{})$.
+TODO
 
-TODO: Plot select kernels.
+\bibliography{report}{}
+\bibliographystyle{unsrt}
 
-\section{Spatio-angular Transfer Function}
-
-TODO: Show angular band limit by taking angular Fourier transform only.
-
-TODO: Show spatial band limit by taking the spatial Fourier transform of the
-first angular term.
-
-TODO: Evaluate and plot spatio-angular transfer function numerically. This
-will be expensive, but it only has to be done once for each microscope.
-
-\section{Reconstruction}
-
-\section{Conclusions}
 \end{document}

### 2018-03-04 notes/2018-02-23-spatio-angular-kernel/calculations/kernel.py

@@ -1,0 +1,143 @@
+import numpy as np
+from mpmath import *
+from sympy import *
+from sympy.matrices.dense import *
+import functools
+
+# Analytical spherical fourier transform
+import sympy.functions.special.spherical_harmonics as sh
+def sft(f, max_l=4, odd_l=False):
+    coeffs = []
+    for l in range(0 + odd_l, max_l+2, 2):
+        for m in range(-l, l+1):
+            print("Integrating: "+ str(l) + ', ' + str(m))
+            Znm = sh.Znm(l, m, theta, phi).expand(func=True)
+            Znm = simplify(Znm) # Try this
+            # import pdb; pdb.set_trace() 
+            theta_int = integrate(expand_trig(sin(theta)*Znm*f), (theta, 0, pi))
+            final_int = integrate(expand_trig(theta_int.rewrite(cos)), (phi, 0, 2*pi))
+            print(simplify(final_int))
+            coeffs.append(final_int)
+    return np.array(coeffs)
+
+# Polar fourier transform
+
+print("Working...")
+
+# Symbols
+Theta = Symbol('Theta')
+Phi = Symbol('Phi')
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+n0 = Symbol('n0')
+n1 = Symbol('n1')
+phi_pol = Symbol('phi_pol')
+alpha = Symbol('alpha')
+rb = Symbol('rb')
+rd = Symbol('rd')
+rm = Symbol('rm')
+phib = Symbol('phib')
+phid = Symbol('phid', real=True)
+z = Symbol('z')
+
+# Calculate internal integrals
+
+# Make these symbols for now
+A = Symbol('A')
+B = Symbol('B')
+C = Symbol('C')
+D = Symbol('D', real=False)
+E = Symbol('E', real=False)
+X0 = Symbol('X0', real=True)
+X1 = Symbol('X1', real=True)
+X2 = Symbol('X2', real=True)
+
+# Calculate intensity
+# Full
+G = Matrix([[X0+X2*cos(2*phid), X2*sin(2*phid), -2*I*X1*cos(phid)], [X2*sin(2*phid), X0-X2*cos(2*phid), -2*I*X1*sin(phid)], [0, 0, 0]])
+# Paraxial
[…]

### 2018-03-05 slides/2018-03-05-group-meeting/group_meeting.tex
Group meeting slides

--- 2018-02-23 notes/2018-02-23-spatio-angular-kernel/report/report.tex
@@
-\documentclass[11pt]{article}
+\documentclass[presentation]{beamer}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{fixltx2e}
+\usepackage{graphicx}
+\usepackage{longtable}
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{rotating}
+\usepackage[normalem]{ulem}
+\usepackage{amsmath}
+\usepackage{textcomp}
+\usepackage{marvosym}
+\usepackage{wasysym}
+\usepackage{amssymb}
+\usepackage{hyperref}
+\tolerance=1000
+\usepackage{graphicx} \DeclareMathOperator{\argmin}{argmin}
 
-%%%%%%%%%%%%
-% Packages %
-%%%%%%%%%%%%
-
-\hyphenpenalty=10000
-\usepackage{tocloft}
-\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
-\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
-$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
-$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
-\usepackage{cleveref}
-\usepackage{xcolor}
-\usepackage[colorlinks = true,
-            linkcolor = blue,
-            urlcolor  = blue,
-            citecolor = blue,
-            anchorcolor = blue]{hyperref}
-\usepackage{epstopdf}
-\usepackage{braket}
-\usepackage{upgreek}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage{subcaption}
-\usepackage{amssymb,latexsym,amsmath,gensymb}
-\usepackage{latexsym}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{enumitem}
-\usepackage{pdflscape}
-\usepackage{url}
-\usepackage{tikz, calc}
-\usetikzlibrary{shapes.geometric, arrows, calc}
-\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
-\tikzstyle{arrow} = [thick, ->, >=stealth]
-
-\newcommand{\argmin}{\arg\!\min}
 \newcommand{\me}{\mathrm{e}}
@@
 \providecommand{\intinf}{\int_{-\infty}^{\infty}}
-\providecommand{\fig}[4]{
-  % filename, width, caption, label
-\begin{figure}[h]
- \captionsetup{width=1.0\linewidth}
- \centering
- \includegraphics[width = #2\textwidth]{#1}
- \caption{#3}
- \label{fig:#4}
-\end{figure}
-}
 
-\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
-\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
-\providecommand{\figs}[7]{
-  % filename1, filename2, caption1, caption2, label1, label2, shift
-\begin{figure}[H]
-\centering
-\begin{minipage}[b]{.45\textwidth}
-  \centering
-  \includegraphics[width=1.0\linewidth]{#1}
-  \captionsetup{justification=justified, singlelinecheck=true}
-  \caption{#3}
-  \label{fig:#5}
-\end{minipage}
+\newcommand{\under}[2]{\underset{\scriptscriptstyle#1}{#2}}
+
+\usetheme{simple}
+\usecolortheme{}
+\usefonttheme{serif}
+\useinnertheme{}
+\useoutertheme{}
+\author{Talon Chandler}
+\date{March 5, 2018}
+\title{Spatio-angular Transfer Functions}
+
+\begin{document}
+
+\maketitle
+\begin{frame}[label=sec-1]{$x$-oriented dipole point spread function}
+ \begin{center}
+   \includegraphics[width=0.8\textwidth]{figs/x.png}
+ \end{center}
+\end{frame}
+
+\begin{frame}[label=sec-1]{$z$-oriented dipole point spread function}
+ \begin{center}
+   \includegraphics[width=0.8\textwidth]{figs/z.png}
+ \end{center}
+\end{frame}
+
+\begin{frame}[label=sec-1]{Point spread functions---Novotny}
+ \begin{center}
+   \includegraphics[width=0.8\textwidth]{figs/z.png}
+ \end{center}
+\end{frame}
+
+\begin{frame}[label=sec-1]{Point spread functions---Novotny}
+ \begin{center}
+   \includegraphics[width=0.8\textwidth]{figs/nov-psf.png}
+ \end{center}
+\end{frame}
+
+\begin{frame}[label=sec-1]{Only two spherical harmonics in the paraxial spatio-angular point spread function}
+ \begin{center}
+   \includegraphics[width=0.7\textwidth]{figs/sh.png}
+ \end{center}
+\end{frame}
+
+\begin{frame}{Paraxial spatio-angular point spread function}
+\begin{align*}
+      h^*(\rd{}; \mathbf{r}_o, \so{}) \propto ({I_0^*}^2 + 2{I_1^*}^2)Y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)Y_2^{0}(\so{})\label{eq:para}
+\end{align*}
+\begin{align*}
+  {I_0^*} = \left(\frac{\text{NA}}{n_o}\right)^2\left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
   \hspace{2em}
-\begin{minipage}[b]{.45\textwidth}
-  \centering
-  \includegraphics[width=1.0\linewidth]{#2}
-  \vspace{#7em}
-  \captionsetup{justification=justified}
-  \caption{#4}
-  \label{fig:#6}
-\end{minipage}
-\end{figure}
-}
-\makeatletter
+  {I_1^*} = \left(\frac{\text{NA}}{n_o}\right)^3\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
+  \end{align*}
+  \begin{align*}
+  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
+  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
+  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
+\end{align*}
+\end{frame}
 
-\providecommand{\code}[1]{
+\begin{frame}[label=sec-1]{Paraxial spatio-angular PSF and OTF}
  \begin{center}
-\lstinputlisting{#1}
+   \includegraphics[width=1.0\textwidth]{figs/ft.pdf}
  \end{center}
-}
+\end{frame}
 
-\newcommand{\crefrangeconjunction}{--}
-%%%%%%%%%%%
-% Spacing %
-%%%%%%%%%%%
-% Margins
-\usepackage[
-top    = 1.5cm,
-bottom = 1.5cm,
-left   = 1.5cm,
-right  = 1.5cm]{geometry}
+\begin{frame}[label=sec-1]{Scalar optics transfer functions---Mertz, Goodman}
+ \begin{center}
+   \includegraphics[width=.7\textwidth]{figs/mertz.jpg}
+ \end{center}
+\end{frame}
 
-% Indents, paragraph space
-%\usepackage{parskip}
-\setlength{\parskip}{1.5ex}
+\begin{frame}[label=sec-1]{Electromagnetic optics transfer functions}
+\tikzstyle{block} = [draw, fill=white, rectangle, 
+    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
+\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
+\tikzstyle{input} = [coordinate]
+\tikzstyle{output} = [coordinate]
+\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+\begin{tikzpicture}[auto, node distance=3cm,>=latex]
+    \node [input, name=input] {};
+    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
+    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
+    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
+    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};
 
-% Section spacing
-\usepackage{titlesec}
-\titlespacing*{\title}
-{0pt}{0ex}{0ex}
-\titlespacing*{\section}
-{0pt}{0ex}{0ex}
-\titlespacing*{\subsection}
-{0pt}{0ex}{0ex}
-\titlespacing*{\subsubsection}
-{0pt}{0ex}{0ex}
+    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
+    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
+    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
+    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
+      \end{tikzpicture}
+\end{frame}
 
-% Line spacing
-\linespread{1.1}
-
-%%%%%%%%%%%%
-% Document %
-%%%%%%%%%%%%
-\begin{document}
-\title{\vspace{-2.5em} Spatio-angular Kernels and Transfer Functions for Fluorescence Microscopes \vspace{-2.5em}} \author{Talon Chandler}% and Patrick La Rivi\`ere}
-\date{\vspace{-1em}\today\vspace{-1em}}
-\maketitle
-\section{Introduction}
-In these notes we will consider a single-view fluorescence microscope
-\textbf{with no polarizing filters} that uses TIRF excitation to excite
-fluorophores in all orientations equally. This excitation scheme allows us to
-focus exclusively on the detection process. We will find the spatio-angular
-kernel of this microscope and analyze it in the frequency domain using the
-spatio-angular Fourier transform. Along the way we will show that uniform
-excitation fluorescence microscopes have spatial and angular band-limits.
-
-We use plain roman type for scalars, e.g., $x, y, z$; bold lowercase roman type
-for two-dimensional vectors, e.g., $\mb{r}$; hats for unit vectors, e.g.,
-$\mb{\hat{s}}$; bold lowercase gothic type for three-dimensional vectors, e.g.,
-$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g., $\mb{R}$.
-
-\section{General Forward Model}
-Consider a three-dimensional field of oriented fluorescent dipoles. We can
-represent the entire object using a function $f(\ro{}, \so{})$ that
-returns the number of dipoles at position $\ro{}$ per unit volume oriented in
-direction $\so{}$ per unit solid angle.
-
-The intensities measured using a general linear measurement system can by
-modeled using
-\begin{align}
-  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})
-\end{align}
-where $g_i(\mb{r_d})$ is the camera frame collected under the $i$th measurement
-configuration ($i$ indexes polarizer settings or views), $\mb{r_d}$ is the
-two-dimensional detector coordinate, and
-$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular kernel of the
-$i$th measurement configuration. Our goal is to reconstruct the object
-$f(\ro{}, \so{})$ from intensity measurements $g_i(\rd{})$.
-
-\section{Spatio-angular Kernel}
-In this section we will write out the kernel
-$h(\rd{}; \ro{}, \so{})$ for a non-polarized single-view
-fluorescence microscope with angularly uniform TIRF illumination. This section
-mostly restates the results of XXXBacker and Moerner 2014XXX, so I recommend reading that paper for a more
-complete understanding.
-
-First, we find the electric field $\mb{e}$ at position
-$\rb{} = r_b\cos\phi_b \mh{x} + r_b\sin\phi_b\mh{y}$ in the back focal plane
-created by a single dipole at position $\ro{}=x_o\mh{x} + y_o\mh{y} + z_o\mh{z}$ and
-oriented in direction $\so{}$
-\begin{align}
-  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(x_ox_b + y_oy_b + z_o\rho_b)}\sqrt{\frac{n_o}{n_b\rho_b}}
-  \begin{bmatrix}
-    \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-r_b\cos\phi_b\\
-    \sin\phi_b\cos\phi_b(\rho_b - 1)&\cos^2\phi_b + \rho_b\sin^2\phi_b&-r_b\sin\phi_b\\
-    0&0&0
-  \end{bmatrix}\so{}\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
-\end{align}
-where we have defined $\rho_b \equiv \sqrt{1 - r_b^2}$ and $\Pi(x)$ is a boxcar
-function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
-expression term by term: the exponential term accounts for the phase objective,
-the square root term conserves power before and after the objective lens, the
-matrix is a position-dependent rotation matrix that models the electric field
-rotation caused by the objective lens, $\so{}$ is the dipole orientation unit
-vector, and $\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the
-numerical aperture of the lens with
-$r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$.
-
-% Notice that the matrix in Eq. \ref{eq:bfp} contains zeros in the third
-% row---this means that the electric field in the back focal plane does not
-% contain a longitudinal component. Also notice that Eq. \ref{eq:bfp} does not
-% depend on the transverse position of the dipole $x$ and $y$, but it does depend
-% on the longitudinal position of the dipole $z$. Therefore, we can say that the
-% imaging system has transverse shift invariance but not longitudinal shift
-% invariance.
-
-The next step is to find the electric field in the detector plane. We can use
-the paraxial approximation here because the focal length of the tube lens is
-long. In this case the electric field in the detector plane is the Fourier
-transform of the electric field in the back focal plane
-\begin{align}
-  \mb{e_d}(\rd{};\ro{}, \so{}) = \int_{\mathbb{R}^2}d\rb{}\ \mb{e_b}(\rb{};\ro{}, \so{}) \me^{i(kn_b/f_t)\rb{}\cdot\rd{}}. \label{eq:fourier}
-\end{align}
-
-Finally, we can find the intensity measured in the detector plane (the kernel)
-by taking the modulus squared of the electric field
-\begin{align}
-  h(\rd{}; \ro{}, \so{}) = |\mb{e_d}(\rd{};\ro{}, \so{})|^2. \label{eq:kernel}
-\end{align}
-
-Unfortunately, the Fourier transform in Eq. \ref{eq:fourier} cannot be written
-in closed form, but equation \ref{eq:kernel} can be rearranged so that it can be
-evaluated using six precomputed 2D Fourier transforms per $z_o$ position.
-
-\begin{figure}[h]
- \captionsetup{width=1.0\linewidth}
- \centering
-   \centering
-   \includegraphics[width = 0.25\textwidth]{../figures/schematic.pdf}
-   \caption{Simplified schematic of a single-view fluorescence microscope. The
-     object is placed near the focal point of an objective lens with focal
-     length $f_{o}$ in a medium with refractive index $n_o$. The object is
-     parameterized by the 3D position vector $\ro{}$ ($\mb{o}$ for object) and a
-     orientation unit vector $\so{}$. The light emitted by the fluorescent
-     object is collected and collimated by the objective lens so that the
-     electric fields are purely transverse in back focal plane. Points in the
-     back focal plane are parameterized by a 2D position vector $\rb{}$
-     ($\mb{b}$ for back focal plane). Finally, the tube lens with focal length
-     $f_t$ refocuses the light onto a detector. Points on the detector are
-     parameterized by a 2D position vector $\rd{}$ ($\mb{d}$ for detector). The
-     back focal plane and detector are in a medium with refractive index
-     $n_b$. Note that this schematic is not to scale---in typical microscopes
-     $f_o \ll f_t$ to provide magnification.}
-   \label{fig:frames_a}
-\end{figure}
-
-TODO: Show transverse shift invariance.
-
-TODO: Program up an efficient implementation of $h(\rd{}; \ro{}, \so{})$.
-
-TODO: Plot select kernels.
-
-\section{Spatio-angular Transfer Function}
-
-TODO: Show angular band limit by taking angular Fourier transform only.
-
-TODO: Show spatial band limit by taking the spatial Fourier transform of the
-first angular term.
-
-TODO: Evaluate and plot spatio-angular transfer function numerically. This
-will be expensive, but it only has to be done once for each microscope.
-
-\section{Reconstruction}
-
-\section{Conclusions}
 \end{document}

### 2018-03-06 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Patrick's edits, refactoring, change Y to y.

@@
 \usepackage[colorlinks = true,
-            linkcolor = blue,
-            urlcolor  = blue,
-            citecolor = blue,
-            anchorcolor = blue]{hyperref}
+            linkcolor = black,
+            urlcolor  = black,
+            citecolor = black,
+            anchorcolor = black]{hyperref}
 \usepackage{epstopdf}
@@
 \usepackage{url}
+\usepackage{array}
+\newcolumntype{C}{>{$\displaystyle} c <{$}}
 \usepackage{tikz, calc}
@@
   spatio-angular coherent spread function, coherent transfer function, and
-  optical transfer function as electromagnetic counterparts to well-known
+  optical transfer function as electromagnetic extensions of well-known
   functions in scalar optics theory. We use these concepts to show that
@@
 $\mb{\hat{s}}$; bold lowercase gothic type for three-dimensional vectors, e.g.,
-$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g., $\mb{R}$.
+$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g.,
+$\mb{R}$. We use the real spherical harmonic functions
+\begin{align}
+  y_l^m(\theta, \phi) =
+  \begin{cases}
+    \sqrt{2}K_l^m\cos(m\phi)P_l^m(\cos\theta), & m > 0\\
+    K_l^0P_l^0(\cos\theta), & m = 0\\
+    \sqrt{2}K_l^m\sin(-m\phi)P_l^{-m}(\cos\theta), & m < 0\\
+  \end{cases}
+\end{align}
+where
+\begin{align}
+  K_l^m = \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-|m|)!}{(l+|m|)!}},
+\end{align}
+and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0$ and $l=1$
+spherical harmonics are given by
+\begin{equation}
+\begin{aligned}
+  y_0^0(\theta, \phi) &= \sqrt{\frac{1}{4\pi}},\\
+  y_1^{-1}(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\sin\phi\sin\theta, \hspace{2em} y_1^0(\theta, \phi) &= \sqrt{\frac{3}{4\pi}}\cos\theta, \hspace{2em} y_1^1(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\cos\phi\sin\theta.
+\end{aligned}
+\end{equation}
 
@@
 \end{align}
-where we have defined $\rho_b \equiv \sqrt{1 - r_b^2}$ and $\Pi(x)$ is a boxcar
+where $r_b$ is the distance from the center of the back focal plane in units of
+$f_o$, we define $\rho_b \equiv \sqrt{1 - r_b^2}$, and $\Pi(x)$ is a boxcar
 function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
@@
   \begin{split}
-  h(\rd{}; \ro{}, \so{}) \propto &\frac{4\sqrt{\pi}}{3}\left(I_0^2 + 2I_1^2 + I_2^2\right)Y_0^0(\so{}) -\frac{8\sqrt{15\pi}}{15}I_0I_2\sin(2\phi_d)Y_2^{-2}(\so{})\\ &+ \frac{4\sqrt{5\pi}}{15}\left(-I_0^2 + 4I_1^2 - I_2^2\right)Y_2^{0}(\so{}) +\frac{8\sqrt{15\pi}}{15}I_0I_2\cos(2\phi_d)Y_2^{-2}(\so{}).
+  h(\rd{}; \ro{}, \so{}) \propto &\left(I_0^2 + 2I_1^2 + I_2^2\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d)y_2^{2}(\so{}).
 \label{eq:kerna}
@@
 \begin{align}
-      \lim_{\theta_{\text{max}} \ll \pi/2} h(\rd{}; \mathbf{r}_o, z_o=0, \so{}) \equiv h^*(\rd{}; \mathbf{r}_o, \so{}) \propto \frac{4\sqrt{\pi}}{3}({I_0^*}^2 + 2{I_1^*}^2)Y_0^0(\so{}) + \frac{4\sqrt{5\pi}}{15}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)Y_2^{0}(\so{})\label{eq:para}
+      \lim_{\theta_{\text{max}} \ll \pi/2} h(\rd{}; \mathbf{r}_o, z_o=0, \so{}) \equiv h^{(p)}(\rd{}; \mathbf{r}_o, \so{}) \propto \left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)y_2^{0}(\so{})\label{eq:para}
 \end{align}
@@
 \begin{align}
-  {I_0^*} = \left(\frac{\text{NA}}{n_o}\right)^2\left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
+  {I_0^{(p)}} = \left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
   \hspace{2em}
-    {I_1^*} = \left(\frac{\text{NA}}{n_o}\right)^3\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
+    {I_1^{(p)}} = \frac{\text{NA}}{n_o}\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
   \intertext{and we have substituted}
@@
 \end{align}
-We will continue to use an asterisk to mark the terms where we have used the paraxial
-approximation and constrained the object to the focal plane.
+We will continue to use an superscipt $(p)$ to mark the terms where we have used
+the paraxial approximation and constrained the object to the focal plane.
 
-First, consider the coefficient on the $Y_0^0$ spherical harmonic in
+First, consider the coefficient on the $y_0^0$ spherical harmonic in
 Eq. \ref{eq:para}. This coefficient is the point spread function for a angularly
-uniform distribution of fluorophores. The first term of the coefficient $I_0^*$
+uniform distribution of fluorophores. The first term of the coefficient $I_0^{(p)}$
 is the familiar Airy disk that arises from the contribution of dipoles oriented
-in the transverse plane, while the second term $I_1^*$ is a smaller factor that
+in the transverse plane, while the second term $I_1^{(p)}$ is a smaller factor that
 arises from dipoles oriented outside of the transverse plane. This leads to an
@@
 
-Next, consider the coefficient on the $Y_2^0$ spherical harmonic in
+Next, consider the coefficient on the $y_2^0$ spherical harmonic in
 Eq. \ref{eq:para}. This coefficient is the spatial PSF for a distribution of
@@
 \begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{}) Y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{}) y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
 \end{align}
@@
 $\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}$ we now need consider the spatio-angular
-harmonics $Y_l^m(\so{})\thinspace\me^{i 2\pi
+harmonics $y_l^m(\so{})\thinspace\me^{i 2\pi
   \ro{}\cdot\bs{\nu}_o}$. Eq.~\ref{eq:ft} can be interpreted as the
@@
 We can plug Eq. \ref{eq:kerna} into \ref{eq:ft} and use the orthonormality
-relation for spherical harmonics $\int_{\mathbb{S}^2}d\so{} Y_{l_0}^{m_0}(\so{})Y_{l_1}^{m_1}(\so{}) = \delta(l_0 - l_1)\delta(m_0 - m_1)$ to find that
+relation for spherical harmonics $\int_{\mathbb{S}^2}d\so{} y_{l_0}^{m_0}(\so{})y_{l_1}^{m_1}(\so{}) = \delta(l_0 - l_1, m_0 - m_1)$ to find that
 \begin{equation}
   \begin{split}
-  H_l^m(\bs{\nu}_o) \propto \int_{\mathbb{R}^3}d\ro{}  &\frac{4\sqrt{\pi}}{3}\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l)\delta(m)\\ &-\frac{8\sqrt{15\pi}}{15}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2)\delta(m+2)\\ &+ \frac{4\sqrt{5\pi}}{15}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2)\delta(m)\\ &+\frac{8\sqrt{15\pi}}{15}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2)\delta(m-2).\label{eq:otf}
+  H_l^m(\bs{\nu}_o) \propto \int_{\mathbb{R}^3}d\ro{}  \bigg[&\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l, m) - \frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2, m+2)\\ +& \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2, m) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2, m-2)\bigg]\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}.\label{eq:otf}
 \end{split}
@@
 \begin{align}
-  {H_l^m}^*(\nu_o^x, \nu_o^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\frac{4\sqrt{\pi}}{3}({I_0^*}^2 + 2{I_1^*}^2)\delta(l)\delta(m) + \frac{4\sqrt{5\pi}}{15}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)\delta(l-2)\delta(m)\right]  \me^{i 2\pi(\nu_o^xx_o + \nu_o^yy_o)}\label{eq:otfh}
+  {H_l^m}^{(p)}(\nu_o^x, \nu_o^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)\delta(l, m) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)\delta(l-2, m)\right]  \me^{i 2\pi(\nu_o^xx_o + \nu_o^yy_o)}\label{eq:otfh}
 \end{align}
-The integrals in Eqs. \ref{eq:otf} and \ref{eq:otfh} cannot be solved directly.
-We could proceed numerically like \cite{backer2014}, but instead we use the
-Wiener-Khinchin theorem to simplify the integral \cite{goodman1996,
-  papoulis2002}. We plug Eq. \ref{eq:kernel} into Eq. \ref{eq:ft}
-\begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2
- Y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}, \label{eq:ft2}
-\end{align}
-change the order of the integrals
-\begin{align*}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ Y_l^m(\so{}) \int_{\mathbb{R}^3}d\ro{}\ \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \me^{i 2\pi \ro{}\cdot\bs{\nu}_o},
-\end{align*}
-and apply the Wiener-Khinchin theorem $\mathcal{F}\{|\mathcal{F}\{\mb{e}_b\}|^2\} = \mb{e}_b \star \mb{e}_b$ to find that
-\begin{align*}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ Y_l^m(\so{}) \left[\mb{e}_b \star \mb{e}_b\right](\bs{\nu}). 
-\end{align*}
-The vector auto-correlation is given by
-\begin{align*}
-[\mb{e}_b \star \mb{e}_b](\bs{\nu}) = \int_{\mathbb{R}^2}d\bs{r}_b \mb{e}_b^{T}(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu})
-\end{align*}
-where $\cdot^T$ denotes the transpose operator. To find the OTF we need to
-evaluate the vector auto-correlation of the electric field in the back focal
-plane then take the angular Fourier transform of the result.
+The integral in Eqs. \ref{eq:otfh} cannot be solved directly. We could proceed
+numerically like \cite{backer2014}, but instead we use the Wiener-Khinchin
+theorem to simplify the integral \cite{goodman1996, papoulis2002}. We complete
+the calculation in Appendix A and find that
+The final paraxial OTF for a single-view fluorescence microscope is
+given by
+\begin{equation}
+  H_l^m(\bs{\nu}_o)
+\end{equation}
 
@@
 TODO: Consider illumination polarizers.
-
-% For in focus objects under the paraxial approximation, the electric field in the back
-% focal plan is given by
-% \begin{align}
-%   \mb{e}_b^*(\rb{}) &\propto 
-%   \begin{bmatrix}
-%     1&0&-r_b\cos\phi_b\\
-%     0&1&-r_b\sin\phi_b\\    
-%     0&0&0\\
-%   \end{bmatrix}
-%   \begin{bmatrix}
-%     \cos\varphi_o\sin\vartheta_o\\
-%     \sin\varphi_o\sin\vartheta_o\\
-%     \cos\vartheta_o\\
-%   \end{bmatrix}
-%   \Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
-%   =  \begin{bmatrix}
-%     Y_1^{-1}(\so{}) + r_b\cos\phi_bY_1^0(\so{})\\
-%     Y_1^{1}(\so{}) + r_b\sin\phi_bY_1^0(\so{})\\
-%     0
-%   \end{bmatrix}
-% \Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).
-% \end{align}
-% Next we calculate the integrand of the auto-correlation
-% \begin{align*}
-%   \mb{e}_b^T(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu}) = \left[{Y_1^{-1}}^2 + 2x_bY_1^0Y_1^{-1} + x_b^2{Y_1^0}^2\right]\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).
-% \end{align*}
-
-% The autocorrelation of the electric field in the back focal plane gives the OTF
-% \begin{align*}
-%   H_l^m(\bs{\nu}) &= \frac{\int_{\mathbb{R}^2}d\bs{k}_b \mb{e_b}\left(\bs{k}_b + \frac{1}{2}\bs{\nu}\right)\mb{e_b}^{T}\left(\bs{k}_b + \frac{1}{2}\bs{\nu}\right)}{\int_{\mathbb{R}^2}d\bs{k}_b|\mb{e_b}(\bs{k_b})|^2}
-% \end{align*}
-% where $\cdot^T$ denotes the transpose operator.
-% \begin{align*}
-%   = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \mb{e_b}(\rb{} + \frac{1}{2}\bs{\nu})\mb{e_b}^{\dagger}(\rb{} - \frac{1}{2}\bs{\nu})
-% \end{align*}
 
@@
      single-view fluorescence microscope with NA=0.8. The solid line is the PSF
-     for $Y_0^0$ distributions and the dashed line is the PSF for $Y_2^0$
-     distributions. $Y_2^0$ includes ``negative'' fluorophores, so it gives rise
+     for $y_0^0$ distributions and the dashed line is the PSF for $y_2^0$
+     distributions. $y_2^0$ includes ``negative'' fluorophores, so it gives rise
      to a negative PSF. \textbf{Right:} Numerical paraxial spatio-angular
-     optical transfer function for the same microscope. The $Y_0^0$ term has a
-     spatial low-pass reponse while the $Y_2^0$ term has a spatial high-pass
+     optical transfer function for the same microscope. The $y_0^0$ term has a
+     spatial low-pass response while the $y_2^0$ term has a spatial high-pass
      response. The relative sizes of the two terms is set by the NA---increasing
-     the NA increases the relative size of the $Y_0^2$ term. Vertical scaling is
+     the NA increases the relative size of the $y_0^2$ term. Vertical scaling is
      correct---horizontal scaling is in progress. The cutoff frequency is
      proportional to NA and is the same for both spherical harmonic terms.}
-   \label{fig:frames_a}
+   \label{fig:para}
 \end{figure}
@@
 
+\appendix
+\section{Paraxial optical transfer function in terms of elementary functions}
+Our goal is to calculate the paraxial optical transfer function. We start by
+plugging Eq. \ref{eq:kernel} into Eq. \ref{eq:ft}, using the paraxial
+approximation, and constraining ourselves to the transverse plane
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{R}^2}d\mb{r}_o{} \int_{\mathbb{S}^2}d\so{}\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2
+ y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}\label{eq:ft2}.
+\end{align}
+We change the order of the integrals
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \int_{\mathbb{R}^2}d\mb{r}_o\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \me^{i 2\pi \ro{}\cdot\bs{\nu}_o},
+\end{align}
+then apply the Wiener-Khinchin theorem
+$\mathcal{F}\{|\mathcal{F}\{\mb{e}_b\}|^2\} = \mb{e}_b \star \mb{e}_b$ to find
+that
+\begin{align}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \left[\mb{e}_b \star \mb{e}_b\right](\bs{\nu}_o). 
+\end{align}
+The vector auto-correlation is given by
+\begin{align}
+[\mb{e}_b \star \mb{e}_b](\bs{\nu}_o) = \int_{\mathbb{R}^2}d\bs{r}_b \mb{e}_b^{T}(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu}_o),
+\end{align}
+where $\cdot^T$ denotes the transpose operator.
+
 \end{document}

### 2018-03-12 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Update notes for group meeting. Filling gaps on path to OTF.

@@
 \providecommand{\mb}[1]{\mathbf{#1}}
-\providecommand{\mf}[1]{\mathfrak{#1}}
-\providecommand{\ro}[1]{\mathbf{\mathfrak{r}}_o}
+\providecommand{\mf}[1]{\mathbf{#1}}
+\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
 \providecommand{\so}[1]{\mathbf{\hat{s}}_o}
@@
 for two-dimensional vectors, e.g., $\mb{r}$; hats for unit vectors, e.g.,
-$\mb{\hat{s}}$; bold lowercase gothic type for three-dimensional vectors, e.g.,
-$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g.,
+$\mb{\hat{s}}$; and bold capital roman type for matrices, e.g.,
 $\mb{R}$. We use the real spherical harmonic functions
 \begin{align}
-  y_l^m(\theta, \phi) =
+  y_l^m(\vartheta, \varphi) =
   \begin{cases}
-    \sqrt{2}K_l^m\cos(m\phi)P_l^m(\cos\theta), & m > 0\\
-    K_l^0P_l^0(\cos\theta), & m = 0\\
-    \sqrt{2}K_l^m\sin(-m\phi)P_l^{-m}(\cos\theta), & m < 0\\
+    \sqrt{2}K_l^m\cos(m\varphi)P_l^m(\cos\vartheta), & m > 0\\
+    K_l^0P_l^0(\cos\vartheta), & m = 0\\
+    \sqrt{2}K_l^m\sin(-m\varphi)P_l^{-m}(\cos\vartheta), & m < 0\\
   \end{cases}
@@
 \begin{aligned}
-  y_0^0(\theta, \phi) &= \sqrt{\frac{1}{4\pi}},\\
-  y_1^{-1}(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\sin\phi\sin\theta, \hspace{2em} y_1^0(\theta, \phi) &= \sqrt{\frac{3}{4\pi}}\cos\theta, \hspace{2em} y_1^1(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\cos\phi\sin\theta.
+  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}},\\
+  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta.
+\label{eq:harmonics}
 \end{aligned}
@@
 
-\section{General forward model}
-Consider a three-dimensional field of oriented fluorescent dipoles. We can
-represent the entire field using a function $f(\ro{}, \so{})$ that returns the
-number of dipoles at position $\ro{}$ per unit volume oriented in direction
-$\so{}$ per unit solid angle. We call $f(\ro{}, \so{})$ the fluorescence
-spatio-angular density because it has units of fluorophores per volume per solid
-angle.
-
-If each fluorophore in the field fluoresces independently then the measured
-intensity is a weighted sum of the intensity contributions from each
-fluorophore, and we can model the imaging system with
-\begin{align}
-  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})\label{eq:forward}
-\end{align}
-where $g_i(\mb{r_d})$ are the intensities measured by the detector under the
-$i$th measurement configuration ($i$ can index polarizer settings or views),
-$\mb{r_d}$ is the two-dimensional detector coordinate, and
-$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular point spread function (PSF) of
-the $i$th measurement configuration. Our goal is to reconstruct the object
-$f(\ro{}, \so{})$ from intensity measurements $g_i(\rd{})$.
-
-We can also use the spatio-angular density to model translating and rotating
-fluorophores. As long as each fluorescence emission is an independent event,
-then equation \ref{eq:forward} is a valid way to model the imaging system.
-
-\section{Spatio-angular point spread function}
+\section{Spatio-angular point spread functions}
 \begin{figure}[h]
@@
      focal length $f_{o}$ in a medium with refractive index $n_o$. The object is
-     parameterized by the 3D position vector $\ro{}$ ($o$ for object) and an
+     parameterized by the 2D position vector $\ro{}$ ($o$ for object) and an
      orientation unit vector $\so{}$. The light emitted by the fluorescent
@@
 we are considering with a summary of our notation. We start by following Backer
-and Moerner \cite{backer2014} to find the electric field in the back focal plane
-due to a single dipole emitter at position $\ro{}$ oriented along $\so{}$ as 
+and Moerner \cite{backer2014} to find the electric field at position $\rb{}$ in
+the back focal plane due to a single dipole emitter at position $\ro{}$ oriented
+along $\so{}$ as
 \begin{align}
-  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(z_o\rho_b)}\sqrt{\frac{1}{\rho_b}}
+  \mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) \propto \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}\sqrt{\frac{1}{\rho_b}}
   \begin{bmatrix}
-    \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-r_b\cos\phi_b\\
-    \sin\phi_b\cos\phi_b(\rho_b - 1)&\cos^2\phi_b + \rho_b\sin^2\phi_b&-r_b\sin\phi_b\\
+    \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-\frac{r_b}{f_o}\cos\phi_b\\
+    \sin\phi_b\cos\phi_b(\rho_b - 1)&\cos^2\phi_b + \rho_b\sin^2\phi_b&-\frac{r_b}{f_o}\sin\phi_b\\
     0&0&0
@@
 \end{align}
-where $r_b$ is the distance from the center of the back focal plane in units of
-$f_o$, we define $\rho_b \equiv \sqrt{1 - r_b^2}$, and $\Pi(x)$ is a boxcar
-function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
-expression term by term---the exponential term accounts for the defocus phase,
-the square root term conserves power before and after the objective lens, the
-matrix models the dipole emission process and electric field rotation caused by
-the objective lens, the vector is the dipole orientation unit vector, and
+where we define $\rho_b \equiv \sqrt{1 - \left(\frac{r_b}{f_o}\right)^2}$, and
+$\Pi(x)$ is a boxcar function that returns 1 when $|x| < 1$ and 0 otherwise. We
+can understand this expression term by term---the exponential term accounts for
+the phase as dipole emitter is moved in object space, the square root term
+conserves power before and after the objective lens, the matrix models the
+dipole emission process and electric field rotation caused by the objective
+lens, the vector is the dipole orientation unit vector, and
 $\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the numerical
-aperture of the lens with $r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$. Notice
-that we have omitted the dependence on the transverse position of the
-fluorophore $x_o$ and $y_o$. This is because we assume that the objective is
-aplanatic, so it displays transverse shift-invariance and the constant phase
-factor does not affect our discussion.
+aperture of the lens with $r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$. We use
+a tilde to mark single dipole response functions---we will consider the response
+due to a field of dipoles in the next section.
 
-We can find the intensity in the detector plane by propagating the electric
-field to the detector plane using a scaled Fourier transform then taking the
-modulus squared
+If the tube lens is weakly focusing ($f_o \ll f_t$) then we can find the
+electric field in the detector plane by taking the Fourier transform of the
+electric field in the back focal plane
 \begin{align}
-  h_i(\rd{}; \ro{}, \so{}) = \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \label{eq:kernel}.
+  \mb{\tilde{e}}_d(\rd{}; \ro{}, \so{}) \propto \int_{\mathbb{R}^2} d\rb{}\, \tilde{\mb{e}}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}. \label{eq:ed}
 \end{align}
-Following Novotny \cite{nov2006}, we write the Fourier transform in polar
-coordinates, evaluate the azimuthal integrals, and write the result concisely in
-terms of three radial integrals
+By isolating the phase term in Eq. \ref{eq:bfp} with
+$\mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) = \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
+\tilde{\underline{\mb{e}}}_b(\rb{};\ro{}, \so{})$, and plugging into Eq. \ref{eq:ed} we find
+that 
 \begin{align}
-    h_i(\rd{}; \ro{}, \so{}) &= \left|\mb{e}_d(\rd{}; \ro{}, \so{})\right|^2 \label{eq:kernel2}.\\
-  \mb{e}_d(\rd{}; \ro{}, \so{}) &\propto
+  \mb{\tilde{e}}_d(\rd{} - M\ro{}, \so{}) \propto \int_{\mathbb{R}^2} d\rb{}\, \tilde{\underline{\mb{e}}}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t)\, \rb{} \cdot [\,\rd{} - M\ro{}]}.
+\end{align}
+where $M = -\frac{n_o}{n_t}\frac{f_t}{f_o}$ is the transverse magnification.  By
+writing the electric field in the detector plane in terms of $\rd{} - M\ro{}$,
+we have established that the electric field in the detector plane is
+\textit{transverse shift-invariant}---a transverse shift of the object creates a
+magnified transverse shift of the image. We define coordinates on the detector
+centered on the image of the object
+$\rd{}' \equiv \rd{} - M\ro{} = r_d'\cos\phi_d'\mh{x} + r_d'\sin\phi_d\mh{y}$,
+then we follow Novotny \cite{nov2006} by writing the integrals in polar
+coordinates, evaluating the azimuthal integrals, and writing the result
+concisely in terms of three radial integrals
+\begin{align}
+  \tilde{\mb{e}}_d(\rd{}', \so{}) &\propto
   \begin{bmatrix}
-    I_0 + I_2\cos(2\phi_d) & I_2\sin(2\phi_d) & -2iI_1\cos\phi_d\\
-    I_2\sin(2\phi_d) & I_0 - I_2\cos(2\phi_d) & -2iI_1\sin\phi_d\\
+    A + C\cos(2\phi_d') & C\sin(2\phi_d') & -2iB\cos\phi_d'\\
+    C\sin(2\phi_d') & A - C\cos(2\phi_d') & -2iB\sin\phi_d'\\
     0&0&0\\
@@
 \end{align}
-where $I_0, I_1$ and $I_2$ are
+where $A, B$ and $C$ are
 \begin{align}
-  I_0(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  I_1(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  I_2(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
+  A(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  B(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  C(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d'\sin\theta f_o/f_t).%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
 \end{align}
-By plugging Eq. \ref{eq:elec} into equation Eq. \ref{eq:kernel2} and expanding in
-terms of the spherical harmonic functions, we can rewrite the spatio-angular
-PSF as
+We can identify Eq. \ref{eq:elec} as the vector-valued \textit{coherent spread
+  function} (CSF) of the microscope. The scalar-valued CSF---sometimes called
+the amplitude transfer function---is only applicable to cases where
+electromagnetic optics plays no role in the microscope---not true
+for oriented samples.
+
+To build our intuition about the CSF, we will rewrite the matrix multiplication
+in Eq. \ref{eq:elec} in terms of the spherical harmonics. Notice that the $l=1$
+spherical harmonics are the Cartesian components of the unit dipole axis (see
+Eq. \ref{eq:harmonics}), so the CSF becomes
+\begin{align}
+  \tilde{\mb{e}}_d(\rd{}', \so{}) &\propto
+  \begin{bmatrix}
+    [A + C\cos(2\phi_d')]y_1^{1}(\so{}) + C\sin(2\phi_d')y_1^{-1}(\so{}) - 2iB\cos\phi_d'y_1^{0}(\so{})\\
+    C\sin(2\phi_d')y_1^{1}(\so{}) + [A - C\cos(2\phi_d')]y_1^{-1}(\so{}) - 2iB\sin\phi_d'y_1^{0}(\so{})\\
+    0\\
+  \end{bmatrix}.
+\end{align}
+By applying the paraxial approximation ($\sin\theta\approx\theta$ and
+$\cos\theta\approx 1$), the integrals $A, B$ and $C$ can be evaluated in terms
+of Bessel functions. We can evaluate $A$ and $B$ with the help of
+$\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$ and $\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$,
+respectively, and $C = 0$ because $J_2(x)$ is zero to first order. In this
+case, the CSF simplifies to
+\begin{align}
+  \tilde{\mb{e}}^{(p)}_d(\rd{}', \so{}) &\propto
+  \begin{bmatrix}
+    A^{(p)}y_1^{1}(\so{}) - 2iB^{(p)}\cos\phi_d'y_1^{0}(\so{})\\
+    A^{(p)}y_1^{-1}(\so{}) - 2iB^{(p)}\sin\phi_d'y_1^{0}(\so{})\\
+    0\\
+  \end{bmatrix}\label{eq:paracsf}
+\end{align}
+where the integrals evaluate to
+\begin{align}
+  {A^{(p)}} = \frac{2J_1(\tilde{r}_d)}{\tilde{r}_d},
+  \hspace{2em}
+    {B^{(p)}} = \frac{\text{NA}}{n_o}\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
+  \intertext{and we have substituted}
+  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
+  \text{NA} = n_o\sin\theta_{\text{max}}.
+\end{align}
+We will continue to use an superscipt $(p)$ to mark the terms where we have used
+the paraxial approximation.
+
+Under the paraxial approximation the electric fields on the detector created by
+a single dipole are composed of two parts, a parallel part and a radial
+part. The coefficients of the $y_1^0$ spherical harmonic in Eq. \ref{eq:paracsf}
+create the radial part of the field---the $z$ component of the dipole generates
+a radial field on the detector with respect to the image point. The coefficients
+of the $y_1^1$ and $y_1^{-1}$ spherical harmonics create a parallel field in the
+detector plane parallel to the $x$ and $y$ components of the
+dipole. As the NA increases and the paraxial approximation no longer applies, we
+begin to see coupling between the $x(y)$ component of the dipole with the $y(x)$
+transverse field.
+
+We can find the intensity in the detector plane due to a single dipole
+by taking the modulus squared of the CSF
+\begin{align}
+  \tilde{h}(\rd{}', \so{}) = \left|\tilde{\mb{e}}_d(\rd{}', \so{})\right|^2 \label{eq:kernel}.
+\end{align}
+For convenience we keep the CSF written in terms of the spherical harmonics and
+use a table of spherical harmonic products (see Appendix \ref{realspherical}) to
+calculate the intensity in the detector plane as
 \begin{equation}
   \begin{split}
-  h(\rd{}; \ro{}, \so{}) \propto &\left(I_0^2 + 2I_1^2 + I_2^2\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d)y_2^{2}(\so{}).
+  \tilde{h}(\rd{}', \so{}) \propto &\left(A^2 + 2B^2 + C^2\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}AC\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-A^2 + 4B^2 - C^2\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}AC\cos(2\phi_d')y_2^{2}(\so{}).
 \label{eq:kerna}
@@
 \end{equation}
-
-We have chosen to write the spatio-angular PSF in terms of spherical harmonic
-functions for two reasons. First, it allows us to express the spatio-angular PSF
-very concisely. Instead of considering the point spread function for every
-possible dipole orientation, we only need to consider four spatio-angular
-PSFs---one for each spherical harmonic. Second, the spherical harmonic functions
-form an orthonormal basis for functions on the sphere---a convenient fact that
-we will use later.
+We can identify Eq. \ref{eq:kerna} as the spatio-angular \textit{point spread
+  function} (PSF) of the microscope. Writing the spatio-angular PSF in terms of
+spherical harmonic functions has two advantages. First, it allows us to express
+the spatio-angular PSF very concisely. Instead of considering the point spread
+function for every possible dipole orientation, we only need to consider four
+spatio-angular PSFs---one for each spherical harmonic. Second, the spherical
+harmonic functions form an orthonormal basis for functions on the sphere---a
+convenient fact that we will use later.
 
@@
 
-For now, let's look closer at the spatio-angular PSF in a special case. By
-constraining the object to the focal plane ($z_o$ = 0) and applying the paraxial
-approximation ($\sin\theta\approx\theta$ and $\cos\theta\approx 1$), the
-integrals $I_{0-2}$ can be evaluated in terms of Bessel functions. We can
-evaluate $I_0$ and $I_1$ with the help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$
-and $\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $I_2 = 0$ because
-$J_2(x)$ is zero to first order. In this case, the spatio-angular PSF simplifies
-to
+The spatio-angular PSF under the paraxial approximation is given by
 \begin{align}
-      \lim_{\theta_{\text{max}} \ll \pi/2} h(\rd{}; \mathbf{r}_o, z_o=0, \so{}) \equiv h^{(p)}(\rd{}; \mathbf{r}_o, \so{}) \propto \left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)y_2^{0}(\so{})\label{eq:para}
+      \tilde{h}^{(p)}(\rd{}', \so{}) \propto \left({A^{(p)}}^2 + 2{B^{(p)}}^2\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{A^{(p)}}^2 + 4{B^{(p)}}^2\right)y_2^{0}(\so{})\label{eq:para}.
 \end{align}
-where the integrals evaluate to
-\begin{align}
-  {I_0^{(p)}} = \left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \hspace{2em}
-    {I_1^{(p)}} = \frac{\text{NA}}{n_o}\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \intertext{and we have substituted}
-  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
-  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
-  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
-\end{align}
-We will continue to use an superscipt $(p)$ to mark the terms where we have used
-the paraxial approximation and constrained the object to the focal plane.
-
 First, consider the coefficient on the $y_0^0$ spherical harmonic in
 Eq. \ref{eq:para}. This coefficient is the point spread function for a angularly
-uniform distribution of fluorophores. The first term of the coefficient $I_0^{(p)}$
+uniform distribution of fluorophores. The first term of the coefficient ${A^{(p)}}^2$
 is the familiar Airy disk that arises from the contribution of dipoles oriented
-in the transverse plane, while the second term $I_1^{(p)}$ is a smaller factor that
+in the transverse plane, while the second term ${B^{(p)}}^2$ is a smaller factor that
 arises from dipoles oriented outside of the transverse plane. This leads to an
@@
 \section{Spatio-angular transfer functions}
+Consider a thin object that consists of fluorescent dipoles in arbitrary
+positions and orientations. We can represent the entire object using a function
+$\bs{\mu}(\ro{}, \so{})$ that returns a complex-valued vector for each position
+$\ro{}$ and direction $\so{}$. The magnitude of the complex-valued vector is the
+magnitude of the dipole moment and the elements of the vector give the orientation
+and phase of the radiating dipole moment. Because $\bs{\mu}(\ro{}, \so{})$
+includes the relative phases of different points and orientations in the object,
+$\bs{\mu}(\ro{}, \so{})$ can represent coupled dipoles that are emitting
+partially or completely coherently.
+
+We can find the electric field on the detector created by this object by
+multiplying $\bs{\mu}(\ro{}, \so{})$ with the CSF then integrating over all
+positions and orientations in the object
+\begin{align}
+  \mb{e}_d(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{}).\label{eq:eforward}
+\end{align}
+Note that these integrals represent a vector sum---the coherence of the electric
+fields radiated by the object can cause cancellations of the fields created on
+the detector.
+
+We can simplify this expression by expanding the CSF and the object in terms
+of spatio-angular harmonics
+\begin{align}
+  \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{E}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}_o},\label{eq:csfexp}\\
+    \bs{\mu}(\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{M}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o},\label{eq:objexp}
+\end{align}
+where $\mb{E}_l^m(\bs{\nu_o})$ and $\mb{M}_l^m(\bs{\nu_o})$ are the
+vector spatio-angular spectra of the CSF and object, respectively, given by
+\begin{align}
+  \mb{E}_l^m(\bs{\nu_o}) &= \int_{\mathbb{R}^2}d\ro{} \int_{\mathbb{S}^2}d\so{}\, \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}_o},\\
+\mb{M}_l^m(\bs{\nu_o}) &= \int_{\mathbb{R}^2}d\ro{} \int_{\mathbb{S}^2}d\so{}\, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}_o}.
+\end{align}
+In progress. By plugging Eqs. \ref{eq:csfexp} and \ref{eq:objexp} into
+Eq. \ref{eq:eforward} we find that
+\begin{align}
+  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{E}_l^m(\bs{\nu}_o)\mb{M}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}_o}.
+\label{eq:freqforward}
+\end{align}
+Eq. \ref{eq:freqforward} shows that the electric field on the detector can be
+found by resolving the object into its spatio-angular components
+$\mb{M}_l^m(\bs{\nu}_o)$, weighting each component by $\mb{E}_l^m(\bs{\nu}_o)$, then
+summing over all spatio-angular components. For this reason, we identify
+$\mb{E}_l^m(\bs{\nu}_o)$ as the spatio-angular \textit{coherent transfer function}
+(CTF).
+
 We define the spatio-angular optical transfer function (OTF) as
 \begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{}) y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
+  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h(\rd{}; \ro{}, \so{}) y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
 \end{align}
@@
 theorem to simplify the integral \cite{goodman1996, papoulis2002}. We complete
-the calculation in Appendix A and find that
+the calculation in Appendix \ref{paraxialotf} and find that
 The final paraxial OTF for a single-view fluorescence microscope is
@@
 \tikzstyle{block} = [draw, fill=white, rectangle, 
-    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
+    minimum height=2cm, minimum width=3.5cm, text width=3cm, align=center]
 \tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
@@
     \node [input, name=input] {};
-    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
-    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
-    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
-    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};
+    \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{})$};
+    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu}_o)$};
+    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu}_o)$};
+    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $\tilde{h}(\ro{}, \so{})$};
 
@@
    \includegraphics[width = 1.\textwidth]{../calculations/ft.pdf}
-   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
-     single-view fluorescence microscope with NA=0.8. The solid line is the PSF
-     for $y_0^0$ distributions and the dashed line is the PSF for $y_2^0$
-     distributions. $y_2^0$ includes ``negative'' fluorophores, so it gives rise
-     to a negative PSF. \textbf{Right:} Numerical paraxial spatio-angular
-     optical transfer function for the same microscope. The $y_0^0$ term has a
-     spatial low-pass response while the $y_2^0$ term has a spatial high-pass
-     response. The relative sizes of the two terms is set by the NA---increasing
-     the NA increases the relative size of the $y_0^2$ term. Vertical scaling is
-     correct---horizontal scaling is in progress. The cutoff frequency is
-     proportional to NA and is the same for both spherical harmonic terms.}
+   \caption{In progress. \textbf{Left:} Paraxial spatio-angular point spread
+     function for a single-view fluorescence microscope with NA=0.8. The solid
+     line is the PSF for $y_0^0$ distributions and the dashed line is the PSF
+     for $y_2^0$ distributions. $y_2^0$ includes ``negative'' fluorophores, so
+     it gives rise to a negative PSF. \textbf{Right:} Numerical paraxial
+     spatio-angular optical transfer function for the same microscope. The
+     $y_0^0$ term has a spatial low-pass response while the $y_2^0$ term has a
+     spatial high-pass response. The relative sizes of the two terms is set by
+     the NA---increasing the NA increases the relative size of the $y_0^2$ term.
+     Vertical scaling is correct---horizontal scaling is in progress. The cutoff
+     frequency is proportional to NA and is the same for both spherical harmonic
+     terms.}
    \label{fig:para}
@@
 \appendix
-\section{Paraxial optical transfer function in terms of elementary functions}
+\section{Products of real spherical harmonics}\label{realspherical}
+The six products of $l=1$ spherical harmonics are
+\begin{align}
+y_1^{-1}y_1^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^0 + - \frac{\sqrt{5}}{10 }y_2^0 + - \frac{\sqrt{15}}{10 }y_2^2,\\ 
+y_1^{-1}y_1^0\sqrt{\pi} &= \frac{\sqrt{15}}{10 }y_2^{-1} ,\\
+y_1^{-1}y_1^1\sqrt{\pi} &= - \frac{\sqrt{15}}{10 }y_2^{-2} ,\\
+y_1^0y_1^0\sqrt{\pi} &= \frac{1}{2 }y_0^0 + \frac{\sqrt{5}}{5 }y_2^0 ,\\
+y_1^0y_1^1\sqrt{\pi} &= \frac{\sqrt{15}}{10 }y_2^1 ,\\
+y_1^1y_1^1\sqrt{\pi} &= \frac{1}{2 }y_0^0 + - \frac{\sqrt{5}}{10 }y_2^0 + \frac{\sqrt{15}}{10 }y_2^2.
+\end{align}
+The fifteen products of $l=2$ spherical harmonics are
+\begin{align}
+y_2^{-2}y_2^{-2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + - \frac{\sqrt{35}}{14 }y_4^{4} \\
+y_2^{-2}y_2^{-1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{1} + \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
+y_2^{-2}y_2^{0}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{-2} + \frac{\sqrt{15}}{14 }y_4^{-2} \\
+y_2^{-2}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + - \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
+y_2^{-2}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{35}}{14 }y_4^{-4} \\
+y_2^{-1}y_2^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + - \frac{\sqrt{15}}{14 }y_2^{2} + - \frac{2}{7 }y_4^{0} + - \frac{\sqrt{5}}{7 }y_4^{2} \\
+y_2^{-1}y_2^{0}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{-1} + \frac{\sqrt{30}}{14 }y_4^{-1} \\
+y_2^{-1}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-2} + - \frac{\sqrt{5}}{7 }y_4^{-2} \\
+y_2^{-1}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
+y_2^{0}y_2^{0}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{7 }y_2^{0} + \frac{3}{7 }y_4^{0} \\
+y_2^{0}y_2^{1}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{1} + \frac{\sqrt{30}}{14 }y_4^{1} \\
+y_2^{0}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{2} + \frac{\sqrt{15}}{14 }y_4^{2} \\
+y_2^{1}y_2^{1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + \frac{\sqrt{15}}{14 }y_2^{2} + - \frac{2}{7 }y_4^{0} + \frac{\sqrt{5}}{7 }y_4^{2} \\
+y_2^{1}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{15}}{14 }y_2^{1} + - \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
+y_2^{2}y_2^{2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + \frac{\sqrt{35}}{14 }y_4^{4}
+\end{align}
+
+\section{Paraxial optical transfer function in terms of elementary functions}\label{paraxialotf}
+In progress.
+
 Our goal is to calculate the paraxial optical transfer function. We start by

### 2018-03-12 notes/2018-02-23-spatio-angular-kernel/calculations/shmult.py

@@ -1,0 +1,42 @@
+import numpy as np
+from mpmath import *
+from sympy import *
+from sympy.matrices.dense import *
+import functools
+
+# Analytical spherical fourier transform
+import sympy.functions.special.spherical_harmonics as sh
+def sh_mult(l1, m1, l2, m2):
+    tex_string = ''
+    for l in range(np.abs(l1 - l2), l1 + l2 + 2, 2):
+        for m in range(-l, l+1):
+            print("Integrating: "+ str(l) + ', ' + str(m))
+            Znm1 = sh.Znm(l1, m1, theta, phi).expand(func=True)
+            Znm2 = sh.Znm(l2, m2, theta, phi).expand(func=True)
+            Znm = sh.Znm(l, m, theta, phi).expand(func=True)            
+            theta_int = integrate(expand_trig(sin(theta)*Znm1*Znm2*Znm), (theta, 0, pi))
+            final_int = integrate(expand_trig(theta_int.rewrite(cos)), (phi, 0, 2*pi))
+            if final_int != 0:
+                tex_string += latex(simplify(final_int)) + 'y_'+str(l)+'^{'+str(m)+'} + '
+    print('y_'+str(l1)+'^{'+str(m1)+'}'+'y_'+str(l2)+'^{'+str(m2)+'} = ' + tex_string[:-2])            
+
+# Polar fourier transform
+print("Working...")
+
+# Symbols
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+
+# Calculate expansions
+# b = 1
+# for m1 in range(-b, b+1):
+#     for m2 in range(m1, b+1):
+#         sh_mult(b, m1, b, m2)
+
+print('\n\n')
+b = 2
+for m1 in range(-b, b+1):
+    for m2 in range(m1, b+1):
+        sh_mult(b, m1, b, m2)
+        
+        

### 2018-03-12 slides/2018-03-12-group-meeting/group_meeting.tex
Group meeting slides w/ group theory.

--- 2018-03-05 slides/2018-03-05-group-meeting/group_meeting.tex
@@
 \author{Talon Chandler}
-\date{March 5, 2018}
-\title{Spatio-angular Transfer Functions}
+\date{March 12, 2018}
+\title{Update on Spatio-angular Transfer Functions}
 
@@
 \maketitle
-\begin{frame}[label=sec-1]{$x$-oriented dipole point spread function}
+\begin{frame}[label=sec-1]{Steady progress on closed form OTF}
+  \begin{itemize}
+  \item Initial calculation didn't match my numerical OTF.
+  \item Found some issues that I glossed over. Calculation still in progress.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[label=sec-1]{Brute-force degeneracy finding}
  \begin{center}
-   \includegraphics[width=0.8\textwidth]{figs/x.png}
+   \includegraphics[width=0.8\textwidth]{figs/solid-angle-uncertainty.png}
  \end{center}
@@
 
-\begin{frame}[label=sec-1]{$z$-oriented dipole point spread function}
+\begin{frame}[label=sec-1]{0.8 NA Epi-illumination Microscope}
  \begin{center}
-   \includegraphics[width=0.8\textwidth]{figs/z.png}
+   \includegraphics[width=0.8\textwidth]{figs/singular-value-spectrum-epi.pdf}
  \end{center}
@@
 
-\begin{frame}[label=sec-1]{Point spread functions---Novotny}
+\begin{frame}[label=sec-1]{0.8 NA Symmetric diSPIM Microscope}
  \begin{center}
-   \includegraphics[width=0.8\textwidth]{figs/z.png}
+   \includegraphics[width=0.8\textwidth]{figs/singular-value-spectrum-dispim.pdf}
  \end{center}
@@
 
-\begin{frame}[label=sec-1]{Point spread functions---Novotny}
- \begin{center}
-   \includegraphics[width=0.8\textwidth]{figs/nov-psf.png}
- \end{center}
-\end{frame}
+\begin{frame}[label=sec-1]{Group theory for finding degeneracy}
+\begin{columns}
+  \begin{column}{0.5\textwidth}
+    \centering \textbf{Quantum mechanics}\\\vspace{2em}
+    $\mathcal{H} = \text{Hamiltonian}$\\\vspace{2em}
+    $\mathcal{H}\psi_k = W_k\psi_k$\\\vspace{2em}
+    $\mathcal{T}_j\mathcal{H} - \mathcal{H}\mathcal{T}_j = 0$\\\vspace{2em}
+    $\mathcal{T}_j$ form the symmetry group of the Hamiltonian.
+\end{column}
+\begin{column}{0.5\textwidth}  %%<--- here
+  \centering \textbf{Imaging}\\\vspace{2em}
+  $\mathcal{H} = \text{Forward operator}$\vspace{2em}
+  $\mathcal{H}^{\dagger}\mathcal{H}u_k = \mu_ku_k$\\\vspace{2em}
+  $\mathcal{T}_j\mathcal{H}^{\dagger}\mathcal{H} - \mathcal{H}^{\dagger}\mathcal{H}\mathcal{T}_j = 0$\\\vspace{2em}
+  $\mathcal{T}_j$ form the symmetry group of the imaging system.
 
-\begin{frame}[label=sec-1]{Only two spherical harmonics in the paraxial spatio-angular point spread function}
- \begin{center}
-   \includegraphics[width=0.7\textwidth]{figs/sh.png}
- \end{center}
-\end{frame}
-
-\begin{frame}{Paraxial spatio-angular point spread function}
-\begin{align*}
-      h^*(\rd{}; \mathbf{r}_o, \so{}) \propto ({I_0^*}^2 + 2{I_1^*}^2)Y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)Y_2^{0}(\so{})\label{eq:para}
-\end{align*}
-\begin{align*}
-  {I_0^*} = \left(\frac{\text{NA}}{n_o}\right)^2\left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \hspace{2em}
-  {I_1^*} = \left(\frac{\text{NA}}{n_o}\right)^3\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \end{align*}
-  \begin{align*}
-  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
-  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
-  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
-\end{align*}
-\end{frame}
-
-\begin{frame}[label=sec-1]{Paraxial spatio-angular PSF and OTF}
- \begin{center}
-   \includegraphics[width=1.0\textwidth]{figs/ft.pdf}
- \end{center}
-\end{frame}
-
-\begin{frame}[label=sec-1]{Scalar optics transfer functions---Mertz, Goodman}
- \begin{center}
-   \includegraphics[width=.7\textwidth]{figs/mertz.jpg}
- \end{center}
-\end{frame}
-
-\begin{frame}[label=sec-1]{Electromagnetic optics transfer functions}
-\tikzstyle{block} = [draw, fill=white, rectangle, 
-    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
-\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
-\tikzstyle{input} = [coordinate]
-\tikzstyle{output} = [coordinate]
-\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-\begin{tikzpicture}[auto, node distance=3cm,>=latex]
-    \node [input, name=input] {};
-    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
-    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
-    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
-    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};
-
-    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
-    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
-    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
-    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
-      \end{tikzpicture}
+\end{column}
+\end{columns}
 \end{frame}

### 2018-04-02 notes/2018-03-31-degeneracy-search/report/report.tex
Degeneracy finding.

--- 2018-03-06 notes/2018-02-23-spatio-angular-kernel/report/report.tex
@@
 \providecommand{\mb}[1]{\mathbf{#1}}
-\providecommand{\mf}[1]{\mathfrak{#1}}
-\providecommand{\ro}[1]{\mathbf{\mathfrak{r}}_o}
-\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
+\providecommand{\mf}[1]{\mathbf{#1}}
+\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
+\providecommand{\so}[1]{\mathbf{\hat{s}}_1}
+\providecommand{\s}[1]{\mathbf{\hat{s}}}
 \providecommand{\rb}[1]{\mathbf{r}_b}
@@
 \begin{document}
-\title{\vspace{-2.5em} Spatio-angular transfer functions for fluorescence microscopes\vspace{-1em}}  \author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
-\date{\vspace{-1em}\today\vspace{-1em}}
+\title{\vspace{-2.5em} Finding degeneracy in fluorescence orientation microscopes \vspace{-1em}}  \vspace{-2em} \author{}
+\date{\vspace{-3em}\today\vspace{-2em}}
 \maketitle
-\begin{abstract}
-  We investigate how the orientation and position of fluorescent dipole emitters
-  affects microscopic imaging using electromagnetic optics theory. Starting with
-  the thoroughly studied spatio-angular point spread function, we introduce the
-  spatio-angular coherent spread function, coherent transfer function, and
-  optical transfer function as electromagnetic extensions of well-known
-  functions in scalar optics theory. We use these concepts to show that
-  fluorescence microscopes have a spatio-angular band limit. Finally, we study
-  polarized light microscopes and find that polarized illumination is a type of
-  structured illumination that extends the angular band limit.
-\end{abstract}
-\section{Introduction}
-TODO
 
-We use plain roman type for scalars, e.g., $x, y, z$; bold lowercase roman type
-for two-dimensional vectors, e.g., $\mb{r}$; hats for unit vectors, e.g.,
-$\mb{\hat{s}}$; bold lowercase gothic type for three-dimensional vectors, e.g.,
-$\mb{\mathfrak{r}}$; and bold capital roman type for matrices, e.g.,
-$\mb{R}$. We use the real spherical harmonic functions
+Consider a microscope with an angular point spread function $h_i(\s{})$---we're
+assuming that the spatial and angular problems are decoupled. The forward model for
+this microscope is
 \begin{align}
-  y_l^m(\theta, \phi) =
-  \begin{cases}
-    \sqrt{2}K_l^m\cos(m\phi)P_l^m(\cos\theta), & m > 0\\
-    K_l^0P_l^0(\cos\theta), & m = 0\\
-    \sqrt{2}K_l^m\sin(-m\phi)P_l^{-m}(\cos\theta), & m < 0\\
-  \end{cases}
+  g_i = \int_{\mathbb{S}^2}d\s{}\, h_i(\s{})f(\s{}), \qquad i=1, 2, ..., N.
+\end{align}
+where $f(\s{})$ is the angular density of fluorophores and $i$ indexes $N$
+measurements.
+
+We would like to find the angular degeneracies of this microscope. In other
+words, what rotations $\mb{R}$ can we apply to samples $f(\s{})$ and measure
+the same data? Mathematically, we need to find the set of matrices $\mb{R}$ and
+functions $f(\s{})$ that satisfy
+\begin{align}
+  \int_{\mathbb{S}^2}d\s{}\, h_i(\s{})f(\s{}) - \int_{\mathbb{S}^2}d\s{}\, h_i(\s{})f(\mb{R}^{-1}\s{}) = 0, \qquad i=1, 2, ..., N. \label{eq:tosolve}
+\end{align}
+We will start by restricting the problem to objects where all of the
+fluorophores are oriented in the same direction so that
+$f(\s{}) = \delta(\s{} - \so{})$. In this case we need to find the set of
+directions $\so{}$ and matrices $\mb{R}$ that satisfy
+\begin{align}
+  h_i(\so{}) - h_i(\mb{R}^{-1}\so{}) = 0, \qquad i=1, 2, ..., N. \label{eq:tosolve2}
+\end{align}
+
+We have a set of $N$ equations that we need to solve simultaneously for
+$\so{} \in \mathbb{S}^2$ and $\mb{R} \in \mathbb{SO}(3)$. As far as I can tell
+there is no analytic way to solve this set of equations in the general case. I
+tried expanding onto spherical and rotational harmonics, but that didn't help
+because there's no easy way to relate a solution in the frequency domain to a
+solution in the normal domain. Instead, we can find as many solutions as we can
+``by hand'' then check our results numerically. I've used optimization packages
+the can optimize on $\mathbb{S}^2\times \mathbb{SO}(3)$---my rough plan is to
+seed an optimization procedure at many place on a grid in
+$\mathbb{S}^2\times \mathbb{SO}(3)$ and check (not prove!) that we have all of
+the solutions with those results. Other ideas welcome!
+
+For now let's solve a simple case ``by hand''. If we have a single point
+detector along the $z$ axis then our angular point spread function is given by
+\begin{align}
+  h^{(\mh{z})}(\so{}) = 1 - (\so{}\cdot\mh{z})^2. \label{eq:zpsf}
+\end{align}
+This is the first time I'm expressing an angular point spread function in vector
+notation, but it's easy to check that this reduces to the familiar $h^{(\mh{z})}(\so{}) = \sin^2\vartheta$ if you choose spherical coordinates so that $\so{} = \cos\varphi\sin\vartheta\mh{x} + \sin\varphi\sin\vartheta\mh{y} + \cos\vartheta\mh{z}$.
+Plugging Eq.
+\ref{eq:zpsf} into Eq.
+\ref{eq:tosolve} gives
+\begin{align}
+  -(\so{}\cdot\mh{z})^2 + (\mb{R}^{-1}\so{}\cdot\mh{z})^2 = 0.
+\end{align}
+I can find the following solutions to this equation for all $\so{} \in \mathbb{S}^2$
+\begin{align}
+  \mb{R}_0 =
+  \begin{bmatrix}
+    \cos\theta& -\sin\theta & 0\\
+    \sin\theta& \cos\theta & 0\\
+    0&0&1\\
+  \end{bmatrix} \text{for}\ 0 \leq \theta < 2\pi,
+\end{align}
+which is an arbitrary rotation about the $z$ axis;
+\begin{align}
+  \mb{R}_1 = \mb{I} + 2 \left[\mb{k}\right]_{\times}^2
 \end{align}
@@
 \begin{align}
-  K_l^m = \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-|m|)!}{(l+|m|)!}},
+  \mb{k} = \frac{\so{}\times[(\so{}\cdot\mh{z})\mh{z}]}{|\so{}\times[(\so{}\cdot\mh{z})\mh{z}]|}, \qquad  \left[\mb{k}\right]_{\times} =
+  \begin{bmatrix}
+    0& -k_z& k_y\\
+    k_z& 0 & -k_x\\
+    -k_y& k_x& 0 \\
+  \end{bmatrix},
 \end{align}
-and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0$ and $l=1$
-spherical harmonics are given by
-\begin{equation}
-\begin{aligned}
-  y_0^0(\theta, \phi) &= \sqrt{\frac{1}{4\pi}},\\
-  y_1^{-1}(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\sin\phi\sin\theta, \hspace{2em} y_1^0(\theta, \phi) &= \sqrt{\frac{3}{4\pi}}\cos\theta, \hspace{2em} y_1^1(\theta, \phi) = \sqrt{\frac{3}{4\pi}}\cos\phi\sin\theta.
-\end{aligned}
-\end{equation}
+which is a rotation that maps $\so{}$ to $-\so{}$; and
+\begin{align}
+  \mb{R}_2 = \mb{I} + 2(\so{}\cdot\mh{z})\sqrt{1 - (\so{}\cdot{z})^2}\left[\mb{k}\right]_{\times} + 2(\so{}\cdot\mh{z})^2\left[\mb{k}\right]_{\times}^2
+\end{align}
+which is a rotation that maps every $\so{}$ above the $x-y$ plane to an $\so{}$
+below the $x-y$ plane and vice versa. Notice that
+\begin{align}
+  \mb{R}_3 =
+  \begin{bmatrix}
+    -1&0&0\\
+    0&-1&0\\
+    0&0&-1\\    
+  \end{bmatrix}
+\end{align}
+is not a solution because $\mb{R}_3$ is not a member of $\mathbb{SO}(3)$---$\mb{R}_3$ is a member of the larger set $\mathbb{O}(3)$. This distinction is important
+so that we don't double count solutions.
 
-\section{General forward model}
-Consider a three-dimensional field of oriented fluorescent dipoles. We can
-represent the entire field using a function $f(\ro{}, \so{})$ that returns the
-number of dipoles at position $\ro{}$ per unit volume oriented in direction
-$\so{}$ per unit solid angle. We call $f(\ro{}, \so{})$ the fluorescence
-spatio-angular density because it has units of fluorophores per volume per solid
-angle.
-
-If each fluorophore in the field fluoresces independently then the measured
-intensity is a weighted sum of the intensity contributions from each
-fluorophore, and we can model the imaging system with
-\begin{align}
-  g_i(\rd{}) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{})\label{eq:forward}
-\end{align}
-where $g_i(\mb{r_d})$ are the intensities measured by the detector under the
-$i$th measurement configuration ($i$ can index polarizer settings or views),
-$\mb{r_d}$ is the two-dimensional detector coordinate, and
-$h_i(\rd{}; \ro{}, \so{})$ is the spatio-angular point spread function (PSF) of
-the $i$th measurement configuration. Our goal is to reconstruct the object
-$f(\ro{}, \so{})$ from intensity measurements $g_i(\rd{})$.
-
-We can also use the spatio-angular density to model translating and rotating
-fluorophores. As long as each fluorescence emission is an independent event,
-then equation \ref{eq:forward} is a valid way to model the imaging system.
-
-\section{Spatio-angular point spread function}
-\begin{figure}[h]
- \captionsetup{width=1.0\linewidth}
- \centering
-   \centering
-   \includegraphics[width = 0.4\textwidth]{../figures/schematic.pdf}
-   \caption{Simplified schematic of a single-view fluorescence microscope. The
-     object is placed near the focal point of an aplanatic objective lens with
-     focal length $f_{o}$ in a medium with refractive index $n_o$. The object is
-     parameterized by the 3D position vector $\ro{}$ ($o$ for object) and an
-     orientation unit vector $\so{}$. The light emitted by the fluorescent
-     object is collected and collimated by the objective lens so that the
-     electric fields are purely transverse in the back focal plane. Points in
-     the back focal plane are parameterized by a 2D position vector $\rb{}$ ($b$
-     for back focal plane). Finally, the tube lens with focal length $f_t$
-     refocuses the light onto a detector. Points on the detector are
-     parameterized by a 2D position vector $\rd{}$ ($d$ for detector). The back
-     focal plane and detector are in a medium with refractive index $n_t$. Note
-     that this schematic is not to scale---we consider the case where
-     $f_o \ll f_t$.}
-   \label{fig:frames_a}
-\end{figure}
-
-Figure \ref{fig:frames_a} shows a schematic of the fluorescence microscope that
-we are considering with a summary of our notation. We start by following Backer
-and Moerner \cite{backer2014} to find the electric field in the back focal plane
-due to a single dipole emitter at position $\ro{}$ oriented along $\so{}$ as 
-\begin{align}
-  \mb{e_b}(\rb{};\ro{}, \so{}) \propto \me^{in_ok(z_o\rho_b)}\sqrt{\frac{1}{\rho_b}}
-  \begin{bmatrix}
-    \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-r_b\cos\phi_b\\
-    \sin\phi_b\cos\phi_b(\rho_b - 1)&\cos^2\phi_b + \rho_b\sin^2\phi_b&-r_b\sin\phi_b\\
-    0&0&0
-  \end{bmatrix}
-  \begin{bmatrix}
-    \cos\varphi_o\sin\vartheta_o\\
-    \sin\varphi_o\sin\vartheta_o\\
-    \cos\vartheta_o
-  \end{bmatrix}
-\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
-\end{align}
-where $r_b$ is the distance from the center of the back focal plane in units of
-$f_o$, we define $\rho_b \equiv \sqrt{1 - r_b^2}$, and $\Pi(x)$ is a boxcar
-function that returns 1 when $|x| < 1$ and 0 otherwise. We can understand this
-expression term by term---the exponential term accounts for the defocus phase,
-the square root term conserves power before and after the objective lens, the
-matrix models the dipole emission process and electric field rotation caused by
-the objective lens, the vector is the dipole orientation unit vector, and
-$\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)$ accounts for the numerical
-aperture of the lens with $r_b^{\text{max}} = \frac{f_0}{n_0}\text{NA}$. Notice
-that we have omitted the dependence on the transverse position of the
-fluorophore $x_o$ and $y_o$. This is because we assume that the objective is
-aplanatic, so it displays transverse shift-invariance and the constant phase
-factor does not affect our discussion.
-
-We can find the intensity in the detector plane by propagating the electric
-field to the detector plane using a scaled Fourier transform then taking the
-modulus squared
-\begin{align}
-  h_i(\rd{}; \ro{}, \so{}) = \left|\int_{\mathbb{R}^2} d\rb{} \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \label{eq:kernel}.
-\end{align}
-Following Novotny \cite{nov2006}, we write the Fourier transform in polar
-coordinates, evaluate the azimuthal integrals, and write the result concisely in
-terms of three radial integrals
-\begin{align}
-    h_i(\rd{}; \ro{}, \so{}) &= \left|\mb{e}_d(\rd{}; \ro{}, \so{})\right|^2 \label{eq:kernel2}.\\
-  \mb{e}_d(\rd{}; \ro{}, \so{}) &\propto
-  \begin{bmatrix}
-    I_0 + I_2\cos(2\phi_d) & I_2\sin(2\phi_d) & -2iI_1\cos\phi_d\\
-    I_2\sin(2\phi_d) & I_0 - I_2\cos(2\phi_d) & -2iI_1\sin\phi_d\\
-    0&0&0\\
-  \end{bmatrix}
-  \begin{bmatrix}
-    \cos\varphi_o\sin\vartheta_o\\
-    \sin\varphi_o\sin\vartheta_o\\
-    \cos\vartheta_o
-  \end{bmatrix}\label{eq:elec}
-\end{align}
-where $I_0, I_1$ and $I_2$ are
-\begin{align}
-  I_0(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  I_1(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  I_2(r_d; z_o) &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d\sin\theta f_o/f_t)\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
-\end{align}
-By plugging Eq. \ref{eq:elec} into equation Eq. \ref{eq:kernel2} and expanding in
-terms of the spherical harmonic functions, we can rewrite the spatio-angular
-PSF as
-\begin{equation}
-  \begin{split}
-  h(\rd{}; \ro{}, \so{}) \propto &\left(I_0^2 + 2I_1^2 + I_2^2\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d)y_2^{2}(\so{}).
-\label{eq:kerna}
-\end{split}
-\end{equation}
-
-We have chosen to write the spatio-angular PSF in terms of spherical harmonic
-functions for two reasons. First, it allows us to express the spatio-angular PSF
-very concisely. Instead of considering the point spread function for every
-possible dipole orientation, we only need to consider four spatio-angular
-PSFs---one for each spherical harmonic. Second, the spherical harmonic functions
-form an orthonormal basis for functions on the sphere---a convenient fact that
-we will use later.
-
-It is useful to compare equation \ref{eq:kerna} to Backer and Moerner's approach
-\cite{backer2014}. They expand the spatio-angular PSF in terms of six second
-moments of the fluorophore distribution
-$\{s_x^2, s_y^2, s_z^2, s_xs_y, s_xs_z, s_ys_z\}$. This approach is very
-useful---only six precomputed spatio-angular PSFs are required to represent an
-arbitrary spatio-angular PSF. Instead of expanding in terms of six second
-moments, we expand onto just four spherical harmonics which, unlike the second
-moments, are orthonormal functions. In the next section we will use the
-orthonormality of the spherical harmonics to derive spatio-angular transfer
-functions for fluorescence microscopes.
-
-For now, let's look closer at the spatio-angular PSF in a special case. By
-constraining the object to the focal plane ($z_o$ = 0) and applying the paraxial
-approximation ($\sin\theta\approx\theta$ and $\cos\theta\approx 1$), the
-integrals $I_{0-2}$ can be evaluated in terms of Bessel functions. We can
-evaluate $I_0$ and $I_1$ with the help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$
-and $\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $I_2 = 0$ because
-$J_2(x)$ is zero to first order. In this case, the spatio-angular PSF simplifies
-to
-\begin{align}
-      \lim_{\theta_{\text{max}} \ll \pi/2} h(\rd{}; \mathbf{r}_o, z_o=0, \so{}) \equiv h^{(p)}(\rd{}; \mathbf{r}_o, \so{}) \propto \left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)y_2^{0}(\so{})\label{eq:para}
-\end{align}
-where the integrals evaluate to
-\begin{align}
-  {I_0^{(p)}} = \left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \hspace{2em}
-    {I_1^{(p)}} = \frac{\text{NA}}{n_o}\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
-  \intertext{and we have substituted}
-  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
-  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
-  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
-\end{align}
-We will continue to use an superscipt $(p)$ to mark the terms where we have used
-the paraxial approximation and constrained the object to the focal plane.
-
-First, consider the coefficient on the $y_0^0$ spherical harmonic in
-Eq. \ref{eq:para}. This coefficient is the point spread function for a angularly
-uniform distribution of fluorophores. The first term of the coefficient $I_0^{(p)}$
-is the familiar Airy disk that arises from the contribution of dipoles oriented
-in the transverse plane, while the second term $I_1^{(p)}$ is a smaller factor that
-arises from dipoles oriented outside of the transverse plane. This leads to an
-interesting conclusion---a uniform distribution of dipoles has a point spread
-function that is slightly wider than an Airy disk even in the paraxial
-approximation. The Airy disk is usually derived using paraxial scalar optics
-while here we have used paraxial electromagnetic optics. Therefore, we can
-consider the second term to be an electromagnetic correction to the Airy
-disk. We will quantify this difference in the next section.
-
-Next, consider the coefficient on the $y_2^0$ spherical harmonic in
-Eq. \ref{eq:para}. This coefficient is the spatial PSF for a distribution of
-fluorophores proportional to $3\cos^2\vartheta_o - 1$. Counterintuitively, this
-fluorophore distribution cannot exist because it would require a negative number
-of fluorophores along some orientations; but if this distribution could exist,
-then this coefficient would be its spatial PSF. Considering negative
-distributions of fluorophores in our calculations should not be cause for
-concern. The spherical harmonics span the space of functions on the sphere, so
-any positive fluorophore distribution can be represented by the spherical
-harmonics and we never need to consider negative fluorophores.
-
-Finally, consider all of the spherical harmonics that have a zero
-coefficient. These spherical harmonics span the angular null space of our
-measurement system---fluorophore distributions that lie in the null space do not
-affect the measured intensities. Under the paraxial approximation all of the
-non-zero coefficients are rotationally symmetric ($m=0$) spherical harmonics
-which means that the transverse orientation of the dipoles does not affect the
-PSF. In the high NA case this is no longer true---two $m=2$ spherical harmonics
-have non-zero coefficients and the transverse orientation of dipoles does affect
-the PSF.
-
-\section{Spatio-angular transfer functions}
-We define the spatio-angular optical transfer function (OTF) as
-\begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h_i(\rd{}; \ro{}, \so{}) y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
-\end{align}
-The spatio-angular OTF measures the ability of the microscope to pass
-spatio-angular harmonics---instead of the usual spatial harmonics
-$\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}$ we now need consider the spatio-angular
-harmonics $y_l^m(\so{})\thinspace\me^{i 2\pi
-  \ro{}\cdot\bs{\nu}_o}$. Eq.~\ref{eq:ft} can be interpreted as the
-spatio-angular Fourier transform of the spatio-angular PSF.
-
-We can plug Eq. \ref{eq:kerna} into \ref{eq:ft} and use the orthonormality
-relation for spherical harmonics $\int_{\mathbb{S}^2}d\so{} y_{l_0}^{m_0}(\so{})y_{l_1}^{m_1}(\so{}) = \delta(l_0 - l_1, m_0 - m_1)$ to find that
-\begin{equation}
-  \begin{split}
-  H_l^m(\bs{\nu}_o) \propto \int_{\mathbb{R}^3}d\ro{}  \bigg[&\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l, m) - \frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2, m+2)\\ +& \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2, m) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2, m-2)\bigg]\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}.\label{eq:otf}
-\end{split}
-\end{equation}
-We can see that the microscope has an angular band limit---the microscope only
-passes intensity contributions for fluorophore distributions in the $l=0$ and
-$l=2$ bands.
-
-Once again, we constrain the object to the focal plane and apply the paraxial
-approximation to find that
-\begin{align}
-  {H_l^m}^{(p)}(\nu_o^x, \nu_o^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)\delta(l, m) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)\delta(l-2, m)\right]  \me^{i 2\pi(\nu_o^xx_o + \nu_o^yy_o)}\label{eq:otfh}
-\end{align}
-The integral in Eqs. \ref{eq:otfh} cannot be solved directly. We could proceed
-numerically like \cite{backer2014}, but instead we use the Wiener-Khinchin
-theorem to simplify the integral \cite{goodman1996, papoulis2002}. We complete
-the calculation in Appendix A and find that
-The final paraxial OTF for a single-view fluorescence microscope is
-given by
-\begin{equation}
-  H_l^m(\bs{\nu}_o)
-\end{equation}
-
-TODO: The auto-correlation calculation is in progress. I should be able to find an
-analytic formula for the OTF, but for now I am plotting it numerically in Figure 3.
-
-TODO: Plot PSFs and OTFs numerically without the paraxial approximation.
-
-TODO: Consider detection polarizers.
-
-TODO: Consider illumination polarizers.
-
-\tikzstyle{block} = [draw, fill=white, rectangle, 
-    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
-\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
-\tikzstyle{input} = [coordinate]
-\tikzstyle{output} = [coordinate]
-\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-\begin{figure}
-\begin{tikzpicture}[auto, node distance=3cm,>=latex]
-    \node [input, name=input] {};
-    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
-    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
-    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
-    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};
-
-    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
-    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
-    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
-    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
-      \end{tikzpicture}
-      \centering
-      \captionsetup{width=1.0\linewidth}
-      \caption{Summary of relationships between the CSF, CTF, PSF, and OTF where
-        $\mathcal{F}_D$, $|\cdot|_D$, and $\star_D$ denote the Fourier
-        transform, norm, and autocorrelation over the set $D$, respectively. See
-        \cite{goodman1996} and \cite{mertz2009} for analogous diagrams under
-        scalar optics approximations.}
-    \end{figure}
-
-\begin{figure}[h]
- \captionsetup{width=1.0\linewidth}
- \centering
-   \centering
-   \includegraphics[width = 1.\textwidth]{../calculations/ft.pdf}
-   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
-     single-view fluorescence microscope with NA=0.8. The solid line is the PSF
-     for $y_0^0$ distributions and the dashed line is the PSF for $y_2^0$
-     distributions. $y_2^0$ includes ``negative'' fluorophores, so it gives rise
-     to a negative PSF. \textbf{Right:} Numerical paraxial spatio-angular
-     optical transfer function for the same microscope. The $y_0^0$ term has a
-     spatial low-pass response while the $y_2^0$ term has a spatial high-pass
-     response. The relative sizes of the two terms is set by the NA---increasing
-     the NA increases the relative size of the $y_0^2$ term. Vertical scaling is
-     correct---horizontal scaling is in progress. The cutoff frequency is
-     proportional to NA and is the same for both spherical harmonic terms.}
-   \label{fig:para}
-\end{figure}
-
-\section{Conclusions}
-
-TODO
-
-\bibliography{report}{}
-\bibliographystyle{unsrt}
-
-\appendix
-\section{Paraxial optical transfer function in terms of elementary functions}
-Our goal is to calculate the paraxial optical transfer function. We start by
-plugging Eq. \ref{eq:kernel} into Eq. \ref{eq:ft}, using the paraxial
-approximation, and constraining ourselves to the transverse plane
-\begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{R}^2}d\mb{r}_o{} \int_{\mathbb{S}^2}d\so{}\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2
- y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}\label{eq:ft2}.
-\end{align}
-We change the order of the integrals
-\begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \int_{\mathbb{R}^2}d\mb{r}_o\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \me^{i 2\pi \ro{}\cdot\bs{\nu}_o},
-\end{align}
-then apply the Wiener-Khinchin theorem
-$\mathcal{F}\{|\mathcal{F}\{\mb{e}_b\}|^2\} = \mb{e}_b \star \mb{e}_b$ to find
-that
-\begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \left[\mb{e}_b \star \mb{e}_b\right](\bs{\nu}_o). 
-\end{align}
-The vector auto-correlation is given by
-\begin{align}
-[\mb{e}_b \star \mb{e}_b](\bs{\nu}_o) = \int_{\mathbb{R}^2}d\bs{r}_b \mb{e}_b^{T}(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu}_o),
-\end{align}
-where $\cdot^T$ denotes the transpose operator.
+We can identify the solutions $\mb{R}_0$, $\mb{R}_1$, and $\mb{R}_2$ as matrix
+representations of a group. This group is a \textit{Frieze group} with
+\textit{dihedral symmetry}, an infinite number of possible rotations, and a
+horizontal reflection axis. Using Sch\"onflies notation we say that
+$D_{\infty h}$ is the symmetry group of the imaging system.
 

### 2018-04-02 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Updated OTF calculations.

@@
 
+Although we will not use the result immediately, we can write the electric field
+in back focal plane under the paraxial approximation. We expand Eq. \ref{eq:bfp}
+in a Taylor series about $r_b=0$ and drop all second-order and higher terms to
+find
+\begin{align}
+  \mb{\tilde{e}}^{(p)}_b(\rb{};\ro{}, \so{}) \propto \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
+  \begin{bmatrix}
+    1 & 0 &-\frac{r_b}{f_o}\cos\phi_b\\
+    0&1&-\frac{r_b}{f_o}\sin\phi_b\\
+    0&0&0
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos\varphi_o\sin\vartheta_o\\
+    \sin\varphi_o\sin\vartheta_o\\
+    \cos\vartheta_o
+  \end{bmatrix}
+\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfppara}
+\end{align}
+We will continue to use a superscript $(p)$ to mark terms that have used the
+paraxial approximation.
+
 If the tube lens is weakly focusing ($f_o \ll f_t$) then we can find the
@@
 By isolating the phase term in Eq. \ref{eq:bfp} with
-$\mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) = \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
-\tilde{\underline{\mb{e}}}_b(\rb{};\ro{}, \so{})$, and plugging into Eq. \ref{eq:ed} we find
+$\mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) \equiv \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
+\tilde{\underline{\mb{e}}}_b(\rb{};\so{})$, and plugging into Eq. \ref{eq:ed} we find
 that 
 \begin{align}
-  \mb{\tilde{e}}_d(\rd{} - M\ro{}, \so{}) \propto \int_{\mathbb{R}^2} d\rb{}\, \tilde{\underline{\mb{e}}}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t)\, \rb{} \cdot [\,\rd{} - M\ro{}]}.
+  \mb{\tilde{e}}_d(\rd{} - M\ro{}, \so{}) \propto \int_{\mathbb{R}^2} d\rb{}\, \tilde{\underline{\mb{e}}}_b(\rb{}; \so{})\me^{-i (kn_t/f_t)\, \rb{} \cdot [\,\rd{} - M\ro{}]}.
 \end{align}
@@
 centered on the image of the object
-$\rd{}' \equiv \rd{} - M\ro{} = r_d'\cos\phi_d'\mh{x} + r_d'\sin\phi_d\mh{y}$,
+$\rd{}' \equiv \rd{} - M\ro{} = r_d'\cos\phi_d'\mh{x} + r_d'\sin\phi_d'\mh{y}$,
 then we follow Novotny \cite{nov2006} by writing the integrals in polar
@@
   \begin{bmatrix}
-    A + C\cos(2\phi_d') & C\sin(2\phi_d') & -2iB\cos\phi_d'\\
-    C\sin(2\phi_d') & A - C\cos(2\phi_d') & -2iB\sin\phi_d'\\
+    A(r_d') + C(r_d')\cos(2\phi_d') & C(r_d')\sin(2\phi_d') & 2iB(r_d')\cos\phi_d'\\
+    C(r_d')\sin(2\phi_d') & A(r_d') - C(r_d')\cos(2\phi_d') & 2iB(r_d')\sin\phi_d'\\
     0&0&0\\
@@
 \end{align}
-where $A, B$ and $C$ are
+where $A(r_d'), B(r_d')$, and $C(r_d')$ are
 \begin{align}
@@
 electromagnetic optics plays no role in the microscope---not true
-for oriented samples.
+for samples that contain dipole emitters.
 
@@
   \begin{bmatrix}
-    [A + C\cos(2\phi_d')]y_1^{1}(\so{}) + C\sin(2\phi_d')y_1^{-1}(\so{}) - 2iB\cos\phi_d'y_1^{0}(\so{})\\
-    C\sin(2\phi_d')y_1^{1}(\so{}) + [A - C\cos(2\phi_d')]y_1^{-1}(\so{}) - 2iB\sin\phi_d'y_1^{0}(\so{})\\
+    [A(r_d') + C(r_d')\cos(2\phi_d')]y_1^{1}(\so{}) + C(r_d')\sin(2\phi_d')y_1^{-1}(\so{}) + 2iB(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    C(r_d')\sin(2\phi_d')y_1^{1}(\so{}) + [A(r_d') - C(r_d')\cos(2\phi_d')]y_1^{-1}(\so{}) + 2iB(r_d')\sin\phi_d'y_1^{0}(\so{})\\
     0\\
@@
 By applying the paraxial approximation ($\sin\theta\approx\theta$ and
-$\cos\theta\approx 1$), the integrals $A, B$ and $C$ can be evaluated in terms
-of Bessel functions. We can evaluate $A$ and $B$ with the help of
-$\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$ and $\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$,
-respectively, and $C = 0$ because $J_2(x)$ is zero to first order. In this
-case, the CSF simplifies to
+$\cos\theta\approx 1$), the integrals $A(r_d'), B(r_d')$ and $C(r_d')$ can be
+evaluated in terms of Bessel functions. We can evaluate $A(r_d')$ and $B(r_d')$ with the
+help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$ and
+$\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $C(r_d') = 0$ because
+$J_2(x)$ is zero to first order. In this case, the CSF simplifies to
 \begin{align}
@@
   \begin{bmatrix}
-    A^{(p)}y_1^{1}(\so{}) - 2iB^{(p)}\cos\phi_d'y_1^{0}(\so{})\\
-    A^{(p)}y_1^{-1}(\so{}) - 2iB^{(p)}\sin\phi_d'y_1^{0}(\so{})\\
+    A^{(p)}(r_d')y_1^{1}(\so{}) + 2iB^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    A^{(p)}(r_d')y_1^{-1}(\so{}) + 2iB^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
     0\\
@@
 \begin{align}
-  {A^{(p)}} = \frac{2J_1(\tilde{r}_d)}{\tilde{r}_d},
-  \hspace{2em}
-    {B^{(p)}} = \frac{\text{NA}}{n_o}\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
+  {A^{(p)}}(r_d') = \frac{J_1(2\pi ar_d')}{\pi ar_d'}, 
+  &\hspace{2em}
+    {B^{(p)}}(r_d') = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right],  \label{eq:abparadef}
   \intertext{and we have substituted}
-  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
-  \text{NA} = n_o\sin\theta_{\text{max}}.
+  a \equiv \frac{\text{NA}}{M\lambda},&\hspace{2em}
+  \text{NA} \equiv n_o\sin\theta_{\text{max}}.
 \end{align}
-We will continue to use an superscipt $(p)$ to mark the terms where we have used
-the paraxial approximation.
-
 Under the paraxial approximation the electric fields on the detector created by
@@
 \begin{align}
-  \tilde{h}(\rd{}', \so{}) = \left|\tilde{\mb{e}}_d(\rd{}', \so{})\right|^2 \label{eq:kernel}.
+  h(\rd{}', \so{}) = \left|\tilde{\mb{e}}_d(\rd{}', \so{})\right|^2 \label{eq:kernel}.
 \end{align}
@@
   \begin{split}
-  \tilde{h}(\rd{}', \so{}) \propto &\left(A^2 + 2B^2 + C^2\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}AC\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-A^2 + 4B^2 - C^2\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}AC\cos(2\phi_d')y_2^{2}(\so{}).
+  h(\rd{}', \so{}) \propto &\left(A^2(r_d') + 2B^2(r_d') + C^2(r_d')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}A(r_d')C(r_d')\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-A^2(r_d') + 4B^2(r_d') - C^2(r_d')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}A(r_d')C(r_d')\cos(2\phi_d')y_2^{2}(\so{}).
 \label{eq:kerna}
@@
 
-It is useful to compare equation \ref{eq:kerna} to Backer and Moerner's approach
+It is useful to compare Eq. \ref{eq:kerna} to Backer and Moerner's approach
 \cite{backer2014}. They expand the spatio-angular PSF in terms of six second
@@
 \begin{align}
-      \tilde{h}^{(p)}(\rd{}', \so{}) \propto \left({A^{(p)}}^2 + 2{B^{(p)}}^2\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{A^{(p)}}^2 + 4{B^{(p)}}^2\right)y_2^{0}(\so{})\label{eq:para}.
+      h^{(p)}(\rd{}', \so{}) \propto \left({A^{(p)}}^2(r_d') + 2{B^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{A^{(p)}}^2(r_d') + 4{B^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
 \end{align}
-First, consider the coefficient on the $y_0^0$ spherical harmonic in
-Eq. \ref{eq:para}. This coefficient is the point spread function for a angularly
-uniform distribution of fluorophores. The first term of the coefficient ${A^{(p)}}^2$
-is the familiar Airy disk that arises from the contribution of dipoles oriented
-in the transverse plane, while the second term ${B^{(p)}}^2$ is a smaller factor that
-arises from dipoles oriented outside of the transverse plane. This leads to an
-interesting conclusion---a uniform distribution of dipoles has a point spread
-function that is slightly wider than an Airy disk even in the paraxial
-approximation. The Airy disk is usually derived using paraxial scalar optics
-while here we have used paraxial electromagnetic optics. Therefore, we can
-consider the second term to be an electromagnetic correction to the Airy
-disk. We will quantify this difference in the next section.
+First, consider the coefficient on the $y_0^0$ spherical harmonic in Eq.
+\ref{eq:para}. This coefficient is the point spread function for an angularly
+uniform distribution of fluorophores. The first term of the coefficient
+${A^{(p)}}^2(r_d')$ is the familiar Airy disk that arises from the contribution
+of dipoles oriented in the transverse plane, while the second term
+${B^{(p)}}^2(r_d')$ is a smaller factor that arises from dipoles oriented
+outside of the transverse plane. This leads to an interesting conclusion---a
+uniform distribution of dipoles has a point spread function that is slightly
+wider than an Airy disk even in the paraxial approximation. The Airy disk is
+usually derived using paraxial scalar optics while here we have used paraxial
+electromagnetic optics. Therefore, we can consider the second term to be an
+electromagnetic correction to the Airy disk. We will quantify this difference in
+the next section.
 
@@
 
-We can simplify this expression by expanding the CSF and the object in terms
-of spatio-angular harmonics
+We can simplify this expression by expanding the CSF in terms of spatio-angular
+harmonics
 \begin{align}
-  \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{E}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}_o},\label{eq:csfexp}\\
-    \bs{\mu}(\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{M}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o},\label{eq:objexp}
+  \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}},\label{eq:csfexp}
 \end{align}
-where $\mb{E}_l^m(\bs{\nu_o})$ and $\mb{M}_l^m(\bs{\nu_o})$ are the
-vector spatio-angular spectra of the CSF and object, respectively, given by
+where $\mb{E}_l^m(\bs{\nu})$ is the spatio-angular spectrum of the CSF given
+by
 \begin{align}
-  \mb{E}_l^m(\bs{\nu_o}) &= \int_{\mathbb{R}^2}d\ro{} \int_{\mathbb{S}^2}d\so{}\, \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}_o},\\
-\mb{M}_l^m(\bs{\nu_o}) &= \int_{\mathbb{R}^2}d\ro{} \int_{\mathbb{S}^2}d\so{}\, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}_o}.
+  \mb{E}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}.\label{eq:csfdef}
 \end{align}
-In progress. By plugging Eqs. \ref{eq:csfexp} and \ref{eq:objexp} into
-Eq. \ref{eq:eforward} we find that
+We can change variables to make this expression easier to evaluate
 \begin{align}
-  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}_o{}\, \mb{E}_l^m(\bs{\nu}_o)\mb{M}_l^m(\bs{\nu}_o)y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}_o}.
+  \mb{E}_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \tilde{\mb{e}}_d(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:csfdef2}
+\end{align}
+By plugging Eq. \ref{eq:csfexp} into Eq. \ref{eq:eforward} we find that
+\begin{align}
+  \mb{e}_d(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}\right]\bs{\mu}(\ro{}, \so{}).
 \label{eq:freqforward}
+\end{align}
+We can rearrange this equation into the following form
+\begin{align}
+  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \bs{\mu}(\ro{}, \so{})y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}.
+\label{eq:freqforward}
+\end{align}
+We recognize the term in square brackets as the spatio-angular spectrum of the
+object, so we define
+\begin{align}
+\mb{M}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  
+\end{align}
+and write the electric field on the detector as
+\begin{align}
+  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \mb{M}_l^m(\mb{\nu}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforward}
 \end{align}
@@
 found by resolving the object into its spatio-angular components
-$\mb{M}_l^m(\bs{\nu}_o)$, weighting each component by $\mb{E}_l^m(\bs{\nu}_o)$, then
-summing over all spatio-angular components. For this reason, we identify
-$\mb{E}_l^m(\bs{\nu}_o)$ as the spatio-angular \textit{coherent transfer function}
-(CTF).
+$\mb{M}_l^m(\bs{\nu})$, weighting each component by $\mb{E}_l^m(\bs{\nu})$,
+then summing over all spatio-angular components. Therefore, we identify
+$\mb{E}_l^m(\bs{\nu})$ as the spatio-angular \textit{coherent transfer
+  function} (CTF).
 
-We define the spatio-angular optical transfer function (OTF) as
+In Appendix \ref{paraxialctf} we calculate the paraxial CTF for a single-view fluorescence microscope as 
 \begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{R}^3}d\ro{} \int_{\mathbb{S}^2}d\so{}\ h(\rd{}; \ro{}, \so{}) y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}. \label{eq:ft}
+  {\mb{E}_l^m}^{(p)}(\bs{\nu}) =
+\begin{bmatrix}
+  \delta(l-1, m-1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
+  \delta(l-1, m+1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
+  0\\
+  \end{bmatrix}\Pi\left(\frac{\nu}{a}\right).\label{eq:ctfinal}
 \end{align}
+The CTF shows that single-view coherent microscopes have a spatial band limit at
+$\nu = a$ and an $l=1$ angular pass band. It is useful to compare the paraxial
+CTF in Eq. \ref{eq:ctfinal} to the paraxial electric field in the back focal
+plane in Eq. \ref{eq:bfppara}. The CTF is just a rescaled version of the
+electric field in the back focal plane, and this leads to an extremely valuable
+interpretation. The CTF of a single-view fluorescence microscope is constrained
+to the three members of the $l=1$ band the value of the CTF for each $m$ is a
+rescaled version of the electric field due to a single dipole oriented along one
+of the Cartesian axes.
+
+At the risk of being too explicit, the $m=1$ CTF is a rescaled version of the
+electric field due to a dipole oriented along the $x$ axis, the $m=-1$ CTF is a
+rescaled version of the electric field due to a dipole oriented along the $y$
+axis, and the $m=0$ CTF is a rescaled version of the electric field due to a
+dipole oriented along the $z$ axis. Therefore, we can reason about the CTF by
+thinking about the electric field that single $x$-, $y$-, and $z$-oriented dipoles
+create in the back focal plane.
+
+With this interpretation in mind, the form of the CTF is not surprising. Under
+the paraxial approximation $x$- and $y$-oriented dipoles uniformly fill the back
+focal plane with an electric field parallel to the dipole axis. A $z$-oriented
+dipole creates a radial electric field with linearly increasing amplitude towards
+the edges of the back focal plane.
+
+The spatial band limit can be increased by increasing the NA of the microscope,
+so what parameter sets the angular band limit? The angular band limit in the
+current microscope is set by the dipole emission process---only $l=1$ terms show
+up in the CTF for dipole emitters. Adding polarizing filters to the microscope
+will not extend the band limit of the microscope because filters only block
+electric fields. However, polarized illumination can be used to extend the band
+limit. The excitation process is completely incoherent with the emission
+process, so the spatio-angular transfer functions of the two processes will
+multiply. We can use the multiplication rules in Appendix \ref{realspherical} to
+find the band limit of the new microscope that uses selective excitation.
+
+Next we find the intensity on the detector plane $g(\rd{})$ by taking the
+modulus squared of the electric field. Using Eq. \ref{eq:eforward} we find that
+\begin{align}
+  g(\rd{}) = |\mb{e}_d(\rd{})|^2 = \left|\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{})\right|^2. 
+\end{align}
+If the dipoles emit incoherently---a fair assumption for fluorescent emitters
+that are not within homo-FRET distance---then we can take the modulus squared of the
+object and CSF independently which gives
+\begin{align}
+  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \left|\tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\right|^2\left|\bs{\mu}(\ro{}, \so{})\right|^2. 
+\end{align}
+We recognize that $\left|\tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\right|^2$ is
+the PSF of the microscope $h(\rd{} - M\mb{r}_o, \so{})$, and
+we introduce a new function
+$f(\ro{}, \so{}) \equiv \left|\bs{\mu}(\ro{}, \so{})\right|^2$ to represent the object
+\begin{align}
+  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ h(\rd{} - M\mb{r}_o, \so{})f(\ro{}, \so{}).\label{eq:forwardint}
+\end{align}
+We can interpret $f(\ro{}, \so{})$ as the spatio-angular density of dipoles---it
+is a function that is proportional to the number of fluorophores at position
+$\ro{}$ oriented in direction $\so{}$ per unit volume per unit solid angle. Notice
+that $h$ and $f$ are scalar functions---we removed all phase information when we took
+the modulus squared.
+
+We can follow our previous work with the electric field and simplify Eq.
+\ref{eq:forwardint} by expanding the PSF in terms of spatio-angular harmonics
+\begin{align}
+  h(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}},\label{eq:ctfexp}
+\end{align}
+where $H_l^m(\bs{\nu})$ is the spatio-angular spectrum of the PSF given
+by
+\begin{align}
+  H_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, h(\rd{} - M\ro{}, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}.\label{eq:ctfdef}
+\end{align}
+We can change variables to make this expression easier to evaluate
+\begin{align}
+  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:otfdef2}
+\end{align}
+By plugging Eq. \ref{eq:ctfexp} into Eq. \ref{eq:forwardint} we find that
+\begin{align}
+  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}\right]f(\ro{}, \so{}).
+\label{eq:freqforwardint}
+\end{align}
+We can rearrange this equation into the following form
+\begin{align}
+  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, f(\ro{}, \so{})y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}.
+\label{eq:freqforward}
+\end{align}
+We recognize the term in square brackets as the spatio-angular spectrum of the
+object, so we define
+\begin{align}
+F_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, f(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  
+\end{align}
+and write the intensity on the detector as
+\begin{align}
+  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) F_l^m(\mb{\nu}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
+\end{align}
+Eq. \ref{eq:freqforwardint} shows that the intensity on the detector can be
+found by resolving the object into its spatio-angular component
+$F_l^m(\mb{\nu}_o)$, weighting each component by $H_l^m(\mb{\nu}_o)$, then
+summing over all spatio-angular components. Therefore, we identify
+$H_l^m(\mb{\nu}_o)$ as the spatio-angular \textit{optical transfer function}
+(OTF). Notice that the CSF and CTF are vector-valued functions, while the PSF
+and OTF are scalar-valued functions.
+
+In Appendix \ref{paraxialotf} we calculate the paraxial OTF for a single-view
+fluorescence microscope as
+
 The spatio-angular OTF measures the ability of the microscope to pass
 spatio-angular harmonics---instead of the usual spatial harmonics
-$\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}$ we now need consider the spatio-angular
+$\me^{i 2\pi \ro{}\cdot\bs{\nu}}$ we now need consider the spatio-angular
 harmonics $y_l^m(\so{})\thinspace\me^{i 2\pi
-  \ro{}\cdot\bs{\nu}_o}$. Eq.~\ref{eq:ft} can be interpreted as the
+  \ro{}\cdot\bs{\nu}}$. Eq.~\ref{eq:ft} can be interpreted as the
 spatio-angular Fourier transform of the spatio-angular PSF.
@@
   \begin{split}
-  H_l^m(\bs{\nu}_o) \propto \int_{\mathbb{R}^3}d\ro{}  \bigg[&\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l, m) - \frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2, m+2)\\ +& \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2, m) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2, m-2)\bigg]\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}.\label{eq:otf}
+  H_l^m(\bs{\nu}) \propto \int_{\mathbb{R}^3}d\ro{}  \bigg[&\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l, m) - \frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2, m+2)\\ +& \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2, m) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2, m-2)\bigg]\me^{i 2\pi \ro{}\cdot\bs{\nu}}.\label{eq:otf}
 \end{split}
@@
 \begin{align}
-  {H_l^m}^{(p)}(\nu_o^x, \nu_o^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)\delta(l, m) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)\delta(l-2, m)\right]  \me^{i 2\pi(\nu_o^xx_o + \nu_o^yy_o)}\label{eq:otfh}
+  {H_l^m}^{(p)}(\nu^x, \nu^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)\delta(l, m) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)\delta(l-2, m)\right]  \me^{i 2\pi(\nu^xx_o + \nu^yy_o)}\label{eq:otfh}
 \end{align}
@@
 \begin{equation}
-  H_l^m(\bs{\nu}_o)
+  H_l^m(\bs{\nu})
 \end{equation}
@@
     \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{})$};
-    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu}_o)$};
-    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu}_o)$};
+    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu})$};
+    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
     \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $\tilde{h}(\ro{}, \so{})$};
@@
 \begin{align}
-y_1^{-1}y_1^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^0 + - \frac{\sqrt{5}}{10 }y_2^0 + - \frac{\sqrt{15}}{10 }y_2^2,\\ 
+y_1^{-1}y_1^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^0 - \frac{\sqrt{5}}{10 }y_2^0 - \frac{\sqrt{15}}{10 }y_2^2,\\ 
 y_1^{-1}y_1^0\sqrt{\pi} &= \frac{\sqrt{15}}{10 }y_2^{-1} ,\\
@@
 y_1^0y_1^1\sqrt{\pi} &= \frac{\sqrt{15}}{10 }y_2^1 ,\\
-y_1^1y_1^1\sqrt{\pi} &= \frac{1}{2 }y_0^0 + - \frac{\sqrt{5}}{10 }y_2^0 + \frac{\sqrt{15}}{10 }y_2^2.
+y_1^1y_1^1\sqrt{\pi} &= \frac{1}{2 }y_0^0 - \frac{\sqrt{5}}{10 }y_2^0 + \frac{\sqrt{15}}{10 }y_2^2.
 \end{align}
@@
 \begin{align}
-y_2^{-2}y_2^{-2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + - \frac{\sqrt{35}}{14 }y_4^{4} \\
+y_2^{-2}y_2^{-2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} - \frac{\sqrt{35}}{14 }y_4^{4} \\
 y_2^{-2}y_2^{-1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{1} + \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
 y_2^{-2}y_2^{0}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{-2} + \frac{\sqrt{15}}{14 }y_4^{-2} \\
-y_2^{-2}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + - \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
+y_2^{-2}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} - \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
 y_2^{-2}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{35}}{14 }y_4^{-4} \\
-y_2^{-1}y_2^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + - \frac{\sqrt{15}}{14 }y_2^{2} + - \frac{2}{7 }y_4^{0} + - \frac{\sqrt{5}}{7 }y_4^{2} \\
+y_2^{-1}y_2^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} - \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} - \frac{\sqrt{5}}{7 }y_4^{2} \\
 y_2^{-1}y_2^{0}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{-1} + \frac{\sqrt{30}}{14 }y_4^{-1} \\
-y_2^{-1}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-2} + - \frac{\sqrt{5}}{7 }y_4^{-2} \\
+y_2^{-1}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-2} - \frac{\sqrt{5}}{7 }y_4^{-2} \\
 y_2^{-1}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
@@
 y_2^{0}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{2} + \frac{\sqrt{15}}{14 }y_4^{2} \\
-y_2^{1}y_2^{1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + \frac{\sqrt{15}}{14 }y_2^{2} + - \frac{2}{7 }y_4^{0} + \frac{\sqrt{5}}{7 }y_4^{2} \\
-y_2^{1}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{15}}{14 }y_2^{1} + - \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
-y_2^{2}y_2^{2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + \frac{\sqrt{35}}{14 }y_4^{4}
+y_2^{1}y_2^{1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} + \frac{\sqrt{5}}{7 }y_4^{2} \\
+y_2^{1}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{15}}{14 }y_2^{1} - \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
+y_2^{2}y_2^{2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + \frac{\sqrt{35}}{14 }y_4^{4}
 \end{align}
 
-\section{Paraxial optical transfer function in terms of elementary functions}\label{paraxialotf}
-In progress.
+\section{Paraxial coherent transfer function}\label{paraxialctf}
+In this appendix we calculate the paraxial CTF for a single-view fluorescence
+microscope. We start by plugging Eq. \ref{eq:paracsf} (the paraxial CSF) into Eq.
+\ref{eq:csfdef2}
+\begin{align}
+  {\mb{E}_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\,
+\begin{bmatrix}
+    A^{(p)}(r_d')y_1^{1}(\so{}) + 2iB^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    A^{(p)}(r_d')y_1^{-1}(\so{}) + 2iB^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    0\\
+  \end{bmatrix}
+  y_l^m(\so{})\thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}. 
+\end{align}
+We split the integral into two parts by writing
+\begin{align}
+  {\mb{E}_l^m}^{(p)}(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, \mb{E}^{(p)}(\bs{\nu};\so{}) y_l^m(\so{}),\\ \label{eq:splitup}
+  \mb{E}^{(p)}(\bs{\nu};\so{}) &\equiv  \int_{\mathbb{R}^2}d\rd{}'\
+\begin{bmatrix}
+    A^{(p)}(r_d')y_1^{1}(\so{}) + 2iB^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    A^{(p)}(r_d')y_1^{-1}(\so{}) + 2iB^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    0\\
+  \end{bmatrix}
+  \thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}. 
+\end{align}
+Substituting $A^{(p)}(r_d')$ and $B^{(p)}(r_d')$ using Eq. \ref{eq:abparadef} gives
+\begin{align}
+  \mb{E}^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\rd{}'\,
+\begin{bmatrix}
+    \frac{J_1(2\pi ar_d')}{\pi ar_d'}y_1^m(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right]\cos\phi_d'y_1^0(\so{})\\
+    \frac{J_1(2\pi ar_d')}{\pi ar_d'}y_1^{-1}(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right]\sin\phi_d'y_1^0(\so{})\\
+    0\\
+  \end{bmatrix}
+  \thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
+\end{align}
+We can rewrite this in terms of three two-dimensional Fourier transforms
+\begin{align}
+  \mb{E}^{(p)}(\bs{\nu}; \so{}) \propto 
+\begin{bmatrix}
+    t_1(\bs{\nu})y_1^1(\so{}) + t_2(\bs{\nu})y_1^0(\so{})\\
+    t_1(\bs{\nu})y_1^{-1}(\so{}) + t_3(\bs{\nu})y_1^0(\so{})\\
+    0\\
+  \end{bmatrix}\label{eq:tint}
+\end{align}
+where
+\begin{align}
+  t_1(\bs{\nu}) &\equiv \frac{1}{\pi a}\int_{\mathbb{R}^2}d\rd{}'\,  \frac{J_1(2\pi ar_d')}{r_d'}\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
+  t_2(\bs{\nu}) &\equiv \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi ar_d')}{r_d'}\cos\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
+  t_3(\bs{\nu}) &\equiv \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi ar_d')}{r_d'}\sin\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
+\end{align}
+All three of the functions to be transformed are separable in polar coordinates,
+so we can rewrite the Fourier transform as a sum of weighted Hankel transforms
+\cite{goodman1996}. In general, if a function $g(r, \theta)$ is separable in
+polar coordinates then we can rewrite it as
+$g(r, \theta) = g_{R}(r)g_{\Theta}(\theta)$ and its two-dimensional Fourier transform
+is given by
+\begin{align}
+  \mathcal{F}\{g(r, \theta)\} = \sum_{k=-\infty}^{\infty}c_k(-i)^k\me^{ik\phi}\mathcal{H}_k\{g_R(r)\}
+\end{align}
+where
+\begin{align}
+  c_k = \frac{1}{2\pi}\int_0^{2\pi}d\theta\, g_{\Theta}(\theta)\me^{-ik\theta}
+\end{align}
+and $\mathcal{H}_k\{\}$ is the Hankel transform of order $k$ given by
+\begin{align}
+  \mathcal{H}_k\{g_R(r)\} = 2\pi\int_0^{\infty}dr\, r g_R(r)J_k(2\pi r \nu).
+\end{align}
+First, we evaluate $t_1(\bs{\nu})$. The Fourier transform will be in polar
+coordinates, so we define polar coordinates in frequency space as
+$\bs{\nu} \equiv \nu\cos\phi_\nu\mh{x} + \nu\sin\phi_\nu\mh{y} \equiv \nu_x\mh{x} + \nu_y\mh{y}$. The
+angular part of $J_z(ar_d')/r_d'$ is a constant, so $c_k = \delta(k)$ which
+means we only need to evaluate the zero-order Hankel transform
+\begin{align}
+  t_1(\bs{\nu}) = \frac{1}{\pi a}\mathcal{H}_0\left\{\frac{J_1(2\pi ar_d')}{r_d'}\right\}.
+\end{align}
+From tabulated Hankel transforms we find that
+\begin{align}
+  \mathcal{H}_{\mu}\left\{\frac{J_{\mu+1}(2\pi ar_d')}{r_d'}\right\} =
+  \frac{1}{2\pi}a^{-\mu-1}\nu^\mu\, \Pi\left(\frac{\nu}{a}\right)\label{eq:hankstar}
+\end{align}
+when $a > 0$ and $\text{Re}(\mu) > -\frac{3}{2}$ \cite{poul1998}. Applying this result
+we find that
+\begin{align}
+  t_1(\bs{\nu}) =
+    \frac{1}{2\pi^2 a^{2}}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t1final}.
+\end{align}
+To evaluate $t_2(\bs{\nu})$ and $t_3(\bs{\nu})$ we need to be careful with the angular part. For $t_2(\bs{\nu})$
+the angular part of the function is $\cos\phi_d' = \frac{1}{2}\left(e^{i\phi_d'} + e^{-i\phi_d'}\right)$.
+Therefore, $c_k = \frac{1}{2}\delta(k-1) + \frac{1}{2}\delta(k+1)$ and we have to evaluate two Hankel transforms given by
+\begin{align}
+  t_2(\bs{\nu}) = \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\left[ie^{-i\phi_{\nu}}\mathcal{H}_{-1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\}\right].
+\end{align}
+To put the Hankel transforms in the form of Eq. \ref{eq:hankstar} we apply
+$\mathcal{H}_\mu = (-1)^\mu\mathcal{H}_{-\mu}$ to get
+\begin{align}
+  t_2(\bs{\nu}) = \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\left[-ie^{-i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\}\right].
+\end{align}
+Applying Eq. \ref{eq:hankstar} and simplifying gives
+\begin{align}
+  t_2(\bs{\nu}) =
+    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu(e^{-i\phi_\nu} + e^{i\phi_\nu})\, \Pi\left(\frac{\nu}{a}\right)
+\end{align}
+Finally, 
+\begin{align}
+  t_2(\bs{\nu}) =
+    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu\cos\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t2final}
+\end{align}
+Similarly, 
+\begin{align}
+  t_3(\bs{\nu}) =
+    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu\sin\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t3final}
+\end{align}
+Plugging Eqs. \ref{eq:t1final}, \ref{eq:t2final}, and \ref{eq:t3final} into Eq.
+\ref{eq:tint} and normalizing gives
+\begin{align}
+  {\mb{E}}^{(p)}(\bs{\nu}; \so{}) =
+\begin{bmatrix}
+  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right). \label{eq:paractfsp}
+\end{align}
+Finally, we find the paraxial CTF by evaluating the angular integral in Eq.
+\ref{eq:splitup} 
+\begin{align}
+  {\mb{E}_l^m}^{(p)}(\bs{\nu}) =
+\begin{bmatrix}
+  \delta(l-1, m-1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
+  \delta(l-1, m+1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right).
+\end{align}
 
-Our goal is to calculate the paraxial optical transfer function. We start by
-plugging Eq. \ref{eq:kernel} into Eq. \ref{eq:ft}, using the paraxial
-approximation, and constraining ourselves to the transverse plane
+\section{Paraxial optical transfer function}\label{paraxialotf}
+In this appendix we calculate the paraxial OTF for a single-view fluorescence
+microscope. We start with Eq. \ref{eq:otfdef2}
 \begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{R}^2}d\mb{r}_o{} \int_{\mathbb{S}^2}d\so{}\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2
- y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}_o}\label{eq:ft2}.
+  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:otfdef2}
 \end{align}
-We change the order of the integrals
+We could plug in the paraxial PSF and evaluate the integrals, but this will lead
+us to Fourier transforms that cannot be found in tables. Instead we use a trick
+from scalar Fourier optics and write the OTF in terms of the detected electric
+field \cite{goodman1996}
 \begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \int_{\mathbb{R}^2}d\mb{r}_o\ \left|\int_{\mathbb{R}^2} d\rb{}\, \mb{e}_b(\rb{}; \ro{}, \so{})\me^{-i (kn_t/f_t) \rb{} \cdot \rd{}}\right|^2 \me^{i 2\pi \ro{}\cdot\bs{\nu}_o},
+  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \left|\mb{e}_d(\rd{}', \so{})\right|^2 y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
 \end{align}
-then apply the Wiener-Khinchin theorem
-$\mathcal{F}\{|\mathcal{F}\{\mb{e}_b\}|^2\} = \mb{e}_b \star \mb{e}_b$ to find
-that
+Next, we manipulate this equation to
 \begin{align}
-  H_l^m(\bs{\nu}_o) = \int_{\mathbb{S}^2}d\so{}\ y_l^m(\so{}) \left[\mb{e}_b \star \mb{e}_b\right](\bs{\nu}_o). 
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}', \so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}},\\
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\delta(\rd{}'' - \rd{}')\, \me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\nu}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
 \end{align}
-The vector auto-correlation is given by
+We have followed the proof for the Wiener-Kinchin theorem \cite{papoulis2002, wiener} to explicitly show how the angular integral affects the usual scalar
+calculation. Eq. \ref{eq:hlmauto} shows that we can calculate the OTF by taking
+the vector autocorrelation of the spatial CTF then projecting the result onto
+the spherical harmonics.
+
+We will rewrite Eq. \ref{eq:hlmauto} in two parts
 \begin{align}
-[\mb{e}_b \star \mb{e}_b](\bs{\nu}_o) = \int_{\mathbb{R}^2}d\bs{r}_b \mb{e}_b^{T}(\bs{r}_b)\mb{e}_b(\bs{r}_b + \bs{\nu}_o),
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{}) H(\bs{\nu}; \so{})  \label{eq:hlmauto2}\\
+  H(\bs{\nu}; \so{}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}- \bs{\nu}/2; \so{})\mb{E}(\bs{\tau} + \bs{\nu}/2; \so{}). \label{eq:hlmspatial}
 \end{align}
-where $\cdot^T$ denotes the transpose operator.
+Notice the change of variable to simplify the autocorrelation. In the previous
+section we calculated the CTF in the paraxial case as 
+\begin{align}
+  {\mb{E}}^{(p)}(\bs{\nu}; \so{}) =
+\begin{bmatrix}
+  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right). \label{eq:ctfparax}
+\end{align}
+By introducing $\bs{\tau} \equiv \tau_x\mh{x} + \tau_y\mh{y} \equiv \tau\cos\phi_\tau\mh{x} + \tau\sin\phi_\tau\mh{y}$
+we can plug Eq. \ref{eq:ctfparax} into Eq. \ref{eq:hlmspatial} and find that
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
+  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
+  0\\
+\end{bmatrix}^{\dagger}
+  \begin{bmatrix}
+  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
+  0\\
+\end{bmatrix}\nonumber \\
+  &\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right).
+\end{align}
+Expanding the inner product gives
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &
+      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+                                                                 &\left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
+  &\left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\
+&\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right). 
+\end{align}
+All of the terms with a single $\tau_x$ or $\tau_y$ are odd, so they integrate
+to zero. Therefore
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &
+      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+&\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right). 
+\end{align}
+After expanding the spherical harmonics we can rewrite this equation in terms of
+three autocorrelations
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) &= [s_1(\bs{\nu}) + s_2(\bs{\nu}) + s_3(\bs{\nu})]y_0^0(\so{}) + \frac{2\text{NA}}{\sqrt{5}a n_o}[-s_1(\bs{\nu}) + s_2(\bs{\nu}) + s_3(\bs{\nu})]y_2^0(\so{})\label{eq:hinter}
+\end{align}
+where
+\begin{align}
+  s_1(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right),\\
+  s_2(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, (\tau_x - \nu_x/2)(\tau_x + \nu_x/2) \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right),\\
+  s_3(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, (\tau_y - \nu_y/2)(\tau_y + \nu_y/2) \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right).
+\end{align}
+We can evaluate these integrals with the help of the geometric construction
+shown in Figure \ref{fig:geometry} \cite{goodman1996}.
+
+\begin{figure}[h]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 0.8\textwidth]{../figures/geometry/geometry.pdf}
+   \caption{Geometric construction for evaluating $s_1(\bs{\nu})$,
+     $s_2(\bs{\nu})$, and $s_3(\bs{\nu})$. We need to find the boundaries of
+     integration for the overlapping region of two circles with radius $a$ and
+     distance $\nu$ between their centers. The region is given by four times the
+     difference in area between a sector of angle
+     $\arccos\left(\frac{\nu}{2a}\right)$ and a triangle with base $\nu/2$ and
+     hypotenuse $a$.}
+   \label{fig:geometry}
+\end{figure}
+
+Starting with $s_1(\bs{\nu})$ we find that
+\begin{align}
+  s_1(\bs{\nu}) &= 4\left[\left(\int\limits_0^a d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2a}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2a}{\nu}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}}d\tau_y\right)\right]\\
+  s_1(\bs{\nu}) &= 4\left[\left(\int\limits_0^a d\tau\,\tau\arccos\left(\frac{\nu}{2a}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2a}{\nu}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right)\right]\\
+  s_1(\bs{\nu}) &= 4\left[\frac{a^2}{2}\arccos\left(\frac{\nu}{2a}\right) - \frac{\nu a}{4}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]\\
+  s_1(\bs{\nu}) &= 2a^2\arccos\left(\frac{\nu}{2a}\right) - \nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}.
+\end{align}
+Note that $s_1(\bs{\nu})$ is the unnormalized OTF for a single-view
+fluorescence microscope under the scalar approximation. Next we evaluate
+$s_2(\bs{\nu})$ using the same geometric construction. This integral is not
+rotationally symmetric, so we start by restricting $\bs{\nu}$ to the $x$-axis
+\begin{align}
+  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu_x}{2a}\right)}d\phi_{\tau}(\tau\cos\phi_{\tau} - \nu_x/2)(\tau\cos\phi_{\tau} + \nu_x/2)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \int\limits_0^{\tau_x \frac{2a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}}d\tau_y(\tau_x - \nu_x/2)(\tau_x + \nu_x/2)\Bigg],\\
+  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu_x}{2a}\right)}d\phi_{\tau}(\tau^2\cos^2\phi_{\tau} - \nu_x^2/4)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \int\limits_0^{\tau_x\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}}d\tau_y(\tau_x^2 - \nu_x^2/4)\Bigg].
+\end{align}
+For the first inner integral we will make use of the following
+\begin{align}
+  \int\limits_0^{\arccos(z)} d\phi \cos^2\phi = \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\arccos(z).
+\end{align}
+This results in
+\begin{align}
+  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\left(\frac{\tau^3}{2}\left(\frac{\nu_x}{2a}\right)\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{\tau^3}{2}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{\tau\nu_x^2}{4}\arccos\left(\frac{\nu_x}{2a}\right)\right)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \left(\tau_x^3 - \frac{\tau_x\nu_x^2}{4}\right)\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
+  s_2(\nu_x) = 4\Bigg[&\left(\frac{a^4}{8}\left(\frac{\nu_x}{2a}\right)\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{8}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{8}\arccos\left(\frac{\nu_x}{2a}\right)\right) - \left(\frac{\nu_x^4}{64} - \frac{\nu_x^4}{32}\right)\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
+  s_2(\nu_x) = 4\Bigg[&\frac{\nu_xa^3}{16}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{8}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{8}\arccos\left(\frac{\nu_x}{2a}\right) + \frac{\nu_x^3a}{32}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
+  s_2(\nu_x) = &\frac{\nu_xa^3}{4}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{2}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{2}\arccos\left(\frac{\nu_x}{2a}\right) + \frac{\nu_x^3a}{8}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2},\\
+  s_2(\nu_x) = &\left(\frac{a^2}{4} - \frac{\nu_x^2}{4}\right)2a^2\arccos\left(\frac{\nu_x}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu_x^2}{8}\right)\nu_x a \sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}.
+\end{align}
+This result is only true for $\bs{\nu}$ restricted to the $x$ axis, but we can
+extend this result to the general case by noticing that the value of the
+function in the area of overlap has the same functional form for any direction
+of $\bs{\nu}$ but the total value is reduced by a factor of $\cos^2\phi_\nu$.
+This make sense because the function in the area of overlap for the circles
+displaced along the $y$-axis is zero. Therefore, the complete integral is given
+by 
+\begin{align}
+    s_2(\bs{\nu}) = &\cos^2\phi_\nu\left[\left(\frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right].
+\end{align}
+Similarly, $s_3(\bs{\nu})$ is given by
+\begin{align}
+      s_3(\bs{\nu}) = &\sin^2\phi_\nu\left[\left(\frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right].
+\end{align}
+Plugging these results into Eq. \ref{eq:hinter} gives
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) = &\left[\left(1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]y_0^0(\so{})\nonumber\\ + &\left[\left(-1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(-1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]y_2^0(\so{}).
+\end{align}
+After plugging this into Eq. \ref{eq:hlmauto2}, performing the angular integral,
+refactoring, and normalizing, we get the complete spatio-angular transfer function
+\begin{align}
+  H_l^m(\nu) &= H_0^0(\nu)\delta(l, m) + \frac{2\text{NA}}{\sqrt{5}an_o}H_2^0(\nu)\delta(l-2, m)\\
+  H_0^0(\nu) &= \left(1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\\
+  H_2^0(\nu) &= \left(-1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(-1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}
+\end{align}
 

### 2018-04-02 notes/2018-02-23-spatio-angular-kernel/calculations/kernel.py

@@ -54,15 +54,16 @@ X2 = Symbol('X2', real=True)
 
 # Calculate intensity
 # Full
-G = Matrix([[X0+X2*cos(2*phid), X2*sin(2*phid), -2*I*X1*cos(phid)], [X2*sin(2*phid), X0-X2*cos(2*phid), -2*I*X1*sin(phid)], [0, 0, 0]])
+G = Matrix([[X0+X2*cos(2*phid), X2*sin(2*phid), 2*I*X1*cos(phid)], [X2*sin(2*phid), X0-X2*cos(2*phid), 2*I*X1*sin(phid)], [0, 0, 0]])
 # Paraxial
 # G = Matrix([[X0, 0, -2*I*X1*cos(phid)], [0, X0, -2*I*X1*sin(phid)], [0, 0, 0]])
-mu = Matrix([sin(theta)*cos(phi), sin(theta)*sin(phi), cos(theta)])
+mu = Matrix([sh.Znm(1, 1, theta, phi).expand(func=True), sh.Znm(1, -1, theta, phi).expand(func=True), sh.Znm(1, 0, theta, phi).expand(func=True)])
+# mu = Matrix([sin(theta)*cos(phi), sin(theta)*sin(phi), cos(theta)])
 ed = G*mu
 I = (ed.H*ed)[0,0]
-
+import pdb; pdb.set_trace() 
 # Expand onto spherical harmonics
-# x = sft(I, max_l=2, odd_l=False)
+x = sft(I, max_l=2, odd_l=False)
 
 # Expand eb
 Gb = Matrix([[1, 0, rb], [0, 1, rb], [0,0,0]])

### 2018-04-02 notes/2018-02-23-spatio-angular-kernel/calculations/shmult.py

@@ -28,10 +28,10 @@ theta = Symbol('theta', real=True)
 phi = Symbol('phi', real=True)
 
 # Calculate expansions
-# b = 1
-# for m1 in range(-b, b+1):
-#     for m2 in range(m1, b+1):
-#         sh_mult(b, m1, b, m2)
+b = 1
+for m1 in range(-b, b+1):
+    for m2 in range(m1, b+1):
+        sh_mult(b, m1, b, m2)
 
 print('\n\n')
 b = 2

### 2018-04-02 notes/2018-03-31-degeneracy-search/report/report.tex
SO3 -> O3

@@
 We have a set of $N$ equations that we need to solve simultaneously for
-$\so{} \in \mathbb{S}^2$ and $\mb{R} \in \mathbb{SO}(3)$. As far as I can tell
-there is no analytic way to solve this set of equations in the general case. I
-tried expanding onto spherical and rotational harmonics, but that didn't help
-because there's no easy way to relate a solution in the frequency domain to a
-solution in the normal domain. Instead, we can find as many solutions as we can
-``by hand'' then check our results numerically. I've used optimization packages
-the can optimize on $\mathbb{S}^2\times \mathbb{SO}(3)$---my rough plan is to
-seed an optimization procedure at many place on a grid in
-$\mathbb{S}^2\times \mathbb{SO}(3)$ and check (not prove!) that we have all of
-the solutions with those results. Other ideas welcome!
+$\so{} \in \mathbb{S}^2$ and $\mb{R} \in \mathbb{O}(3)$. Notice that we allow
+for improper rotations ($\text{det}\mb{R} = -1$) by allowing $\mb{R} \in \mathbb{O}(3)$
+instead of restricting to $\mb{R} \in \mathbb{SO}(3)$.
+
+As far as I can tell there is no analytic way to solve this set of equations in
+the general case. I tried expanding onto spherical and rotational harmonics, but
+that didn't help because there's no easy way to relate a solution in the
+frequency domain to a solution in the normal domain. Instead, we can find as
+many solutions as we can ``by hand'' then check our results numerically. I've
+used optimization packages the can optimize on
+$\mathbb{S}^2\times \mathbb{O}(3)$---my rough plan is to seed an optimization
+procedure at many place on a grid in $\mathbb{S}^2\times \mathbb{O}(3)$ and
+check (not prove!) that we have all of the solutions with those results. Other
+ideas welcome!
 
@@
 \begin{align}
-  \mb{R}_1 = \mb{I} + 2 \left[\mb{k}\right]_{\times}^2
-\end{align}
-where
-\begin{align}
-  \mb{k} = \frac{\so{}\times[(\so{}\cdot\mh{z})\mh{z}]}{|\so{}\times[(\so{}\cdot\mh{z})\mh{z}]|}, \qquad  \left[\mb{k}\right]_{\times} =
+  \mb{R}_1 =
   \begin{bmatrix}
-    0& -k_z& k_y\\
-    k_z& 0 & -k_x\\
-    -k_y& k_x& 0 \\
+    1&0&0\\
+    0&1&0\\
+    0&0&-1\\    
   \end{bmatrix},
 \end{align}
-which is a rotation that maps $\so{}$ to $-\so{}$; and
+which is a mirroring operation about the transverse plane; and
 \begin{align}
-  \mb{R}_2 = \mb{I} + 2(\so{}\cdot\mh{z})\sqrt{1 - (\so{}\cdot{z})^2}\left[\mb{k}\right]_{\times} + 2(\so{}\cdot\mh{z})^2\left[\mb{k}\right]_{\times}^2
-\end{align}
-which is a rotation that maps every $\so{}$ above the $x-y$ plane to an $\so{}$
-below the $x-y$ plane and vice versa. Notice that
-\begin{align}
-  \mb{R}_3 =
+  \mb{R}_2 =
   \begin{bmatrix}
@@
     0&0&-1\\    
-  \end{bmatrix}
+  \end{bmatrix},
 \end{align}
-is not a solution because $\mb{R}_3$ is not a member of $\mathbb{SO}(3)$---$\mb{R}_3$ is a member of the larger set $\mathbb{O}(3)$. This distinction is important
-so that we don't double count solutions.
+which is an inversion operation.
 
@@
 
+There are more solutions to the problem---for example a proper rotation that
+maps $\so{}$ to $-\so{}$ instead of an improper rotation---but these solutions
+give the same mappings as the solutions above, so it's okay to ignore them.
+Alternatively, we could restrict ourselves to finding solutions in
+$\mathbb{SO}(3)$ to find unique solutions, but this makes the solutions much
+more difficult to identify.
+
 \end{document}

### 2018-04-11 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Converging on final OTF w/o polarizers. Patrick's ISBI edits.

@@
   functions in scalar optics theory. We use these concepts to show that
-  fluorescence microscopes have a spatio-angular band limit. Finally, we study
-  polarized light microscopes and find that polarized illumination is a type of
-  structured illumination that extends the angular band limit.
+  fluorescence microscopes have a spatio-angular band limit. 
 \end{abstract}
 \section{Introduction}
-TODO
 
@@
   \end{bmatrix}
-\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp}
+\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfp},
 \end{align}
@@
 Although we will not use the result immediately, we can write the electric field
-in back focal plane under the paraxial approximation. We expand Eq. \ref{eq:bfp}
+in the back focal plane under the paraxial approximation. We expand Eq. \ref{eq:bfp}
 in a Taylor series about $r_b=0$ and drop all second-order and higher terms to
@@
   \end{bmatrix}
-\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right)\label{eq:bfppara}
+\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).\label{eq:bfppara}
 \end{align}
@@
   \begin{bmatrix}
-    A(r_d') + C(r_d')\cos(2\phi_d') & C(r_d')\sin(2\phi_d') & 2iB(r_d')\cos\phi_d'\\
-    C(r_d')\sin(2\phi_d') & A(r_d') - C(r_d')\cos(2\phi_d') & 2iB(r_d')\sin\phi_d'\\
+    a(r_d') + c(r_d')\cos(2\phi_d') & c(r_d')\sin(2\phi_d') & 2ib(r_d')\cos\phi_d'\\
+    c(r_d')\sin(2\phi_d') & a(r_d') - c(r_d')\cos(2\phi_d') & 2ib(r_d')\sin\phi_d'\\
     0&0&0\\
@@
     \cos\vartheta_o
-  \end{bmatrix}\label{eq:elec}
-\end{align}
-where $A(r_d'), B(r_d')$, and $C(r_d')$ are
-\begin{align}
-  A(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  B(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  C(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d'\sin\theta f_o/f_t).%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
+  \end{bmatrix},\label{eq:elec}
+\end{align}
+where $a(r_d'), b(r_d')$, and $c(r_d')$ are
+\begin{align}
+  a(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  b(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  c(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d'\sin\theta f_o/f_t).%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
 \end{align}
 We can identify Eq. \ref{eq:elec} as the vector-valued \textit{coherent spread
-  function} (CSF) of the microscope. The scalar-valued CSF---sometimes called
-the amplitude transfer function---is only applicable to cases where
-electromagnetic optics plays no role in the microscope---not true
+  function} (CSF) of the microscope. The more familiar scalar-valued
+CSF---sometimes called the amplitude transfer function---is only applicable to
+cases where electromagnetic optics plays no role in the microscope---not true
 for samples that contain dipole emitters.
@@
   \begin{bmatrix}
-    [A(r_d') + C(r_d')\cos(2\phi_d')]y_1^{1}(\so{}) + C(r_d')\sin(2\phi_d')y_1^{-1}(\so{}) + 2iB(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    C(r_d')\sin(2\phi_d')y_1^{1}(\so{}) + [A(r_d') - C(r_d')\cos(2\phi_d')]y_1^{-1}(\so{}) + 2iB(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    [a(r_d') + c(r_d')\cos(2\phi_d')]y_1^{1}(\so{}) + c(r_d')\sin(2\phi_d')y_1^{-1}(\so{}) + 2ib(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    c(r_d')\sin(2\phi_d')y_1^{1}(\so{}) + [a(r_d') - c(r_d')\cos(2\phi_d')]y_1^{-1}(\so{}) + 2ib(r_d')\sin\phi_d'y_1^{0}(\so{})\\
     0\\
@@
 By applying the paraxial approximation ($\sin\theta\approx\theta$ and
-$\cos\theta\approx 1$), the integrals $A(r_d'), B(r_d')$ and $C(r_d')$ can be
-evaluated in terms of Bessel functions. We can evaluate $A(r_d')$ and $B(r_d')$ with the
+$\cos\theta\approx 1$), the integrals $a(r_d'), b(r_d')$ and $c(r_d')$ can be
+evaluated in terms of Bessel functions. We can evaluate $a(r_d')$ and $b(r_d')$ with the
 help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$ and
-$\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $C(r_d') = 0$ because
+$\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $c(r_d') = 0$ because
 $J_2(x)$ is zero to first order. In this case, the CSF simplifies to
@@
   \begin{bmatrix}
-    A^{(p)}(r_d')y_1^{1}(\so{}) + 2iB^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    A^{(p)}(r_d')y_1^{-1}(\so{}) + 2iB^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
-    0\\
-  \end{bmatrix}\label{eq:paracsf}
+    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    0\\
+  \end{bmatrix}\label{eq:paracsf},
 \end{align}
@@
 \begin{align}
-  {A^{(p)}}(r_d') = \frac{J_1(2\pi ar_d')}{\pi ar_d'}, 
+  {a^{(p)}}(r_d') = \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}, 
   &\hspace{2em}
-    {B^{(p)}}(r_d') = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right],  \label{eq:abparadef}
+    {b^{(p)}}(r_d') = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right],  \label{eq:abparadef}
   \intertext{and we have substituted}
-  a \equiv \frac{\text{NA}}{M\lambda},&\hspace{2em}
+  \nu_o \equiv \frac{\text{NA}}{M\lambda},&\hspace{2em}
   \text{NA} \equiv n_o\sin\theta_{\text{max}}.
@@
 dipole. As the NA increases and the paraxial approximation no longer applies, we
-begin to see coupling between the $x(y)$ component of the dipole with the $y(x)$
-transverse field.
+begin to see coupling between the $x$ and $y$ components of the dipole with the $y$ and $x$ transverse fields, respectively.
 
 We can find the intensity in the detector plane due to a single dipole
-by taking the modulus squared of the CSF
+by taking the squared modulus of the CSF
 \begin{align}
@@
   \begin{split}
-  h(\rd{}', \so{}) \propto &\left(A^2(r_d') + 2B^2(r_d') + C^2(r_d')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}A(r_d')C(r_d')\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-A^2(r_d') + 4B^2(r_d') - C^2(r_d')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}A(r_d')C(r_d')\cos(2\phi_d')y_2^{2}(\so{}).
+  h(\rd{}', \so{}) \propto &\left(a^2(r_d') + 2b^2(r_d') + c^2(r_d')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-a^2(r_d') + 4b^2(r_d') - c^2(r_d')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\cos(2\phi_d')y_2^{2}(\so{}).
 \label{eq:kerna}
@@
 \begin{align}
-      h^{(p)}(\rd{}', \so{}) \propto \left({A^{(p)}}^2(r_d') + 2{B^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{A^{(p)}}^2(r_d') + 4{B^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
-\end{align}
+      h^{(p)}(\rd{}', \so{}) \propto \left({a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{a^{(p)}}^2(r_d') + {4b^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
+\end{align}
+We rewrite the PSF in the following form to make plotting and interpretation easier
+\begin{align}
+  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_0^2}^{(p)}(\rd{}')y_0^2(\so{}),\\
+  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
+  {h_0^2}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right].
+\end{align}
+
 First, consider the coefficient on the $y_0^0$ spherical harmonic in Eq.
@@
 affect the measured intensities. Under the paraxial approximation all of the
-non-zero coefficients are rotationally symmetric ($m=0$) spherical harmonics
+non-zero coefficients are rotationally symmetric ($m=0$) spherical harmonics,
 which means that the transverse orientation of the dipoles does not affect the
@@
 \begin{bmatrix}
-  \delta(l-1, m-1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
-  \delta(l-1, m+1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
-  0\\
-  \end{bmatrix}\Pi\left(\frac{\nu}{a}\right).\label{eq:ctfinal}
+  \delta(l-1, m-1) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
+  \delta(l-1, m+1) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
+  0\\
+  \end{bmatrix}\Pi\left(\frac{\nu}{\nu_o}\right).\label{eq:ctfinal}
 \end{align}
 The CTF shows that single-view coherent microscopes have a spatial band limit at
-$\nu = a$ and an $l=1$ angular pass band. It is useful to compare the paraxial
+$\nu = \nu_o$ and an $l=1$ angular pass band. It is useful to compare the paraxial
 CTF in Eq. \ref{eq:ctfinal} to the paraxial electric field in the back focal
@@
 interpretation. The CTF of a single-view fluorescence microscope is constrained
-to the three members of the $l=1$ band the value of the CTF for each $m$ is a
+to the three members of the $l=1$ band. The value of the CTF for each $m$ is a
 rescaled version of the electric field due to a single dipole oriented along one
@@
 multiply. We can use the multiplication rules in Appendix \ref{realspherical} to
-find the band limit of the new microscope that uses selective excitation.
+find the band limit of a new microscope that uses selective excitation.
 
@@
 If the dipoles emit incoherently---a fair assumption for fluorescent emitters
-that are not within homo-FRET distance---then we can take the modulus squared of the
-object and CSF independently which gives
+that are not within homo-FRET distance---then we can take the squared modulus of the
+object and CSF independently, which gives
 \begin{align}
@@
 \begin{align}
-F_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, f(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  
+F_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, f(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  \label{eq:saspect}
 \end{align}
@@
 fluorescence microscope as
-
-The spatio-angular OTF measures the ability of the microscope to pass
-spatio-angular harmonics---instead of the usual spatial harmonics
-$\me^{i 2\pi \ro{}\cdot\bs{\nu}}$ we now need consider the spatio-angular
-harmonics $y_l^m(\so{})\thinspace\me^{i 2\pi
-  \ro{}\cdot\bs{\nu}}$. Eq.~\ref{eq:ft} can be interpreted as the
-spatio-angular Fourier transform of the spatio-angular PSF.
-
-We can plug Eq. \ref{eq:kerna} into \ref{eq:ft} and use the orthonormality
-relation for spherical harmonics $\int_{\mathbb{S}^2}d\so{} y_{l_0}^{m_0}(\so{})y_{l_1}^{m_1}(\so{}) = \delta(l_0 - l_1, m_0 - m_1)$ to find that
-\begin{equation}
-  \begin{split}
-  H_l^m(\bs{\nu}) \propto \int_{\mathbb{R}^3}d\ro{}  \bigg[&\left(I_0^2 + 2I_1^2 + I_2^2\right) \delta(l, m) - \frac{2\sqrt{15}}{5}I_0I_2\sin(2\phi_d)\thinspace \delta(l-2, m+2)\\ +& \frac{1}{\sqrt{5}}\left(-I_0^2 + 4I_1^2 - I_2^2\right) \delta(l-2, m) +\frac{2\sqrt{15}}{5}I_0I_2\cos(2\phi_d) \thinspace \delta(l-2, m-2)\bigg]\me^{i 2\pi \ro{}\cdot\bs{\nu}}.\label{eq:otf}
-\end{split}
-\end{equation}
-We can see that the microscope has an angular band limit---the microscope only
-passes intensity contributions for fluorophore distributions in the $l=0$ and
-$l=2$ bands.
-
-Once again, we constrain the object to the focal plane and apply the paraxial
-approximation to find that
-\begin{align}
-  {H_l^m}^{(p)}(\nu^x, \nu^y) \propto \int_{\mathbb{R}^2}d\mb{r}_o\left[\left({I_0^{(p)}}^2 + 2{I_1^{(p)}}^2\right)\delta(l, m) + \frac{1}{\sqrt{5}}\left(-{I_0^{(p)}}^2 + 4{I_1^{(p)}}^2\right)\delta(l-2, m)\right]  \me^{i 2\pi(\nu^xx_o + \nu^yy_o)}\label{eq:otfh}
-\end{align}
-The integral in Eqs. \ref{eq:otfh} cannot be solved directly. We could proceed
-numerically like \cite{backer2014}, but instead we use the Wiener-Khinchin
-theorem to simplify the integral \cite{goodman1996, papoulis2002}. We complete
-the calculation in Appendix \ref{paraxialotf} and find that
-The final paraxial OTF for a single-view fluorescence microscope is
-given by
-\begin{equation}
-  H_l^m(\bs{\nu})
-\end{equation}
-
-TODO: The auto-correlation calculation is in progress. I should be able to find an
-analytic formula for the OTF, but for now I am plotting it numerically in Figure 3.
-
-TODO: Plot PSFs and OTFs numerically without the paraxial approximation.
-
-TODO: Consider detection polarizers.
-
-TODO: Consider illumination polarizers.
-
-\tikzstyle{block} = [draw, fill=white, rectangle, 
-    minimum height=2cm, minimum width=3.5cm, text width=3cm, align=center]
-\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
-\tikzstyle{input} = [coordinate]
-\tikzstyle{output} = [coordinate]
-\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-\begin{figure}
-\begin{tikzpicture}[auto, node distance=3cm,>=latex]
-    \node [input, name=input] {};
-    \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{})$};
-    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu})$};
-    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
-    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $\tilde{h}(\ro{}, \so{})$};
-
-    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
-    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
-    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
-    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
-      \end{tikzpicture}
-      \centering
-      \captionsetup{width=1.0\linewidth}
-      \caption{Summary of relationships between the CSF, CTF, PSF, and OTF where
-        $\mathcal{F}_D$, $|\cdot|_D$, and $\star_D$ denote the Fourier
-        transform, norm, and autocorrelation over the set $D$, respectively. See
-        \cite{goodman1996} and \cite{mertz2009} for analogous diagrams under
-        scalar optics approximations.}
-    \end{figure}
+\begin{align}
+  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\label{eq:fullotf}\\
+  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + \text{NA}^2/(2n_o^2)},\\
+  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + \text{NA}^2/(2n_o^2)]}.
+\end{align}
+where
+\begin{align}
+  {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  {B}^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+Notice that the paraxial OTF is rotationally symmetric, so we can write in terms
+of $\nu$ instead of the complete spatial frequency vector $\bs{\nu}$. This will
+no longer be true when we leave the paraxial approximation or add polarizing
+filters to the system. Also, notice that ${A}^{(p)}(\nu)$ is the spatial OTF for
+an incoherent imaging system under the paraxial and scalar approximations
+\cite{goodman1996}.
+
+If our sample consists of isotropic distributions of fluorophores only, then we
+can ignore the ${H_2^0}^{(p)}(\nu)$ term in the OTF. As the NA approaches zero,
+${B}^{(p)}(\nu)$ disappears and we recover the spatial OTF from the
+spatio-angular OTF as expected. For non-zero NA the difference between the OTF
+with and without the scalar approximation is $2{B}^{(p)}(\nu)$. We can interpret
+this difference as an electromagnetic correction to the scalar OTF. The
+correction is proportional to $\frac{\text{NA}^2}{n_o^2}$, so it is a small term
+for all but high NA objectives.
+
+Next, consider the ${H_2^0}^{(p)}(\nu)$ term for NA approaching zero. In this
+limit ${H_2^0}^{(p)}(\nu)$ approaches the isotropic scalar paraxial OTF
+multiplied by a factor of $-1/\sqrt{5} \approx -0.45$. We can interpret the
+${H_2^0}^{(p)}(\nu)$ term as the spatial transfer function if our object was
+made entirely of fluorophores distributed like the $y_2^0$ spherical harmonic
+given by $y_2^0 = \sqrt{5/16\pi}(3\cos^2\vartheta -1)$. The $y_2^0$ spherical
+harmonic consists of positive fluorophores near the $z$ axis and negative
+fluorophores near the transverse plane. All of these fluorophores contribute to
+the transfer function, but the negative fluorophores in the transverse plane
+contribute the most (fluorophores in the transverse plane emit the most
+radiation along the optical axis) so the total transfer function is negative.
+
+We can use the spatio-angular OTF to derive the spatial OTF for any distribution
+of fluorophores. As an example, let's derive the spatial OTF for a $z$-oriented
+fluorophore. The object is $f(\ro{}, \so{}) = \delta(\ro{})\delta(\so{} - \mh{z})$. We can calculate
+the angular spectrum of the object as
+$F_l^m(\bs{\nu}) = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \delta(\so{} - \mh{z})y_l^m(\so{})\me{}^{-i2\pi M\ro{}\cdot\bs{\nu}} =
+y_l^m(\mh{z})$. Finally, we can plug in the angular spectrum
+into equation \ref{eq:freqforwardint}
+\begin{align}
+  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) y_l^m(\mh{z}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}, \label{eq:freqforwardint}
+\end{align}
+then plug in the spatio-angular OTF from Eq. \ref{eq:fullotf} and evaluate the
+sum to find
+\begin{align}
+  g(\rd{}) \propto \int_{\mathbb{R}^2}d\nu{}\, \left[H_0^0(\nu)y_0^0(\mh{z}) + H_2^0(\bs{\nu})y_2^0(\mh{z})\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
+\end{align}
+So the spatial OTF for a $z$ oriented dipole is given by
+\begin{align}
+  H_{\mh{z}}(\nu) \propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu).
+\end{align}
+The main result is that the spatial OTF for any dipole distribution is a linear
+combination of the OTFs for the spherical harmonics. I am partially hesitant to
+refer to $H_{\mh{z}}(\nu)$ as an OTF because it is object dependent, but the
+vocabulary is fine if it is understood that the sample only contains
+$z$-oriented dipoles. For general distributions, the complete spatio-angular OTF
+should be used instead of deriving the transfer function for every individual
+fluorophore.
+
+Fig. \ref{fig:para} shows the spatio-angular OTF for a microscope with
+$\text{NA}=0.8$ and $n=1.33$. The most important feature of this figure is that
+${H_0^0}^{(p)}(\nu)$ is a low-pass filter compared to ${H_0^2}^{(p)}(\nu)$ with
+a maximum difference of $\sim 7\%$ (with larger difference for higher NA). If the difference between
+${H_0^0}^{(p)}(\nu)$ and ${H_0^2}^{(p)}(\nu)$ is not completely obscured by
+noise, we will be able to exploit the difference to estimate the out-of-plane
+angle of dipoles with a single image (putting aside the ill-posedness of the
+problem).
 
@@
    \centering
-   \includegraphics[width = 1.\textwidth]{../calculations/ft.pdf}
-   \caption{In progress. \textbf{Left:} Paraxial spatio-angular point spread
-     function for a single-view fluorescence microscope with NA=0.8. The solid
+   \includegraphics[width = 1.\textwidth]{../calculations/psfs.pdf}
+   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
+     single-view fluorescence microscope with NA=0.8 and $n_o$=1.33. The solid
      line is the PSF for $y_0^0$ distributions and the dashed line is the PSF
-     for $y_2^0$ distributions. $y_2^0$ includes ``negative'' fluorophores, so
-     it gives rise to a negative PSF. \textbf{Right:} Numerical paraxial
-     spatio-angular optical transfer function for the same microscope. The
-     $y_0^0$ term has a spatial low-pass response while the $y_2^0$ term has a
-     spatial high-pass response. The relative sizes of the two terms is set by
-     the NA---increasing the NA increases the relative size of the $y_0^2$ term.
-     Vertical scaling is correct---horizontal scaling is in progress. The cutoff
-     frequency is proportional to NA and is the same for both spherical harmonic
-     terms.}
+     for $y_2^0$ distributions. The dotted line is the $y_2^0$ PSF normalized
+     for comparison with the $y_0^0$ PSF. The $y_2^0$ distributions includes
+     ``negative'' fluorophores, so it gives rise to a negative PSF.
+     \textbf{Right:} Numerical paraxial spatio-angular optical transfer function
+     for the same microscope. The $y_0^0$ term has a comparatively low-pass
+     response while the $y_2^0$ term has a comparatively high-pass response.}
    \label{fig:para}
 \end{figure}
-
-\section{Conclusions}
-
-TODO
 
@@
 \begin{bmatrix}
-    A^{(p)}(r_d')y_1^{1}(\so{}) + 2iB^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    A^{(p)}(r_d')y_1^{-1}(\so{}) + 2iB^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
+    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
     0\\
@@
 \end{align}
-Substituting $A^{(p)}(r_d')$ and $B^{(p)}(r_d')$ using Eq. \ref{eq:abparadef} gives
+Substituting $a^{(p)}(r_d')$ and $b^{(p)}(r_d')$ using Eq. \ref{eq:abparadef} gives
 \begin{align}
@@
 \begin{bmatrix}
-    \frac{J_1(2\pi ar_d')}{\pi ar_d'}y_1^m(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right]\cos\phi_d'y_1^0(\so{})\\
-    \frac{J_1(2\pi ar_d')}{\pi ar_d'}y_1^{-1}(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right]\sin\phi_d'y_1^0(\so{})\\
+    \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}y_1^m(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right]\cos\phi_d'y_1^0(\so{})\\
+    \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}y_1^{-1}(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi \nu_or_d'}\right]\sin\phi_d'y_1^0(\so{})\\
     0\\
@@
 \begin{align}
-  t_1(\bs{\nu}) &\equiv \frac{1}{\pi a}\int_{\mathbb{R}^2}d\rd{}'\,  \frac{J_1(2\pi ar_d')}{r_d'}\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
-  t_2(\bs{\nu}) &\equiv \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi ar_d')}{r_d'}\cos\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
-  t_3(\bs{\nu}) &\equiv \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi ar_d')}{r_d'}\sin\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
+  t_1(\bs{\nu}) &\equiv \frac{1}{\pi \nu_o}\int_{\mathbb{R}^2}d\rd{}'\,  \frac{J_1(2\pi \nu_or_d')}{r_d'}\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
+  t_2(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi \nu_or_d')}{r_d'}\cos\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
+  t_3(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi \nu_or_d')}{r_d'}\sin\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
 \end{align}
@@
 $\bs{\nu} \equiv \nu\cos\phi_\nu\mh{x} + \nu\sin\phi_\nu\mh{y} \equiv \nu_x\mh{x} + \nu_y\mh{y}$. The
-angular part of $J_z(ar_d')/r_d'$ is a constant, so $c_k = \delta(k)$ which
+angular part of $J_z(\nu_or_d')/r_d'$ is a constant, so $c_k = \delta(k)$ which
 means we only need to evaluate the zero-order Hankel transform
 \begin{align}
-  t_1(\bs{\nu}) = \frac{1}{\pi a}\mathcal{H}_0\left\{\frac{J_1(2\pi ar_d')}{r_d'}\right\}.
+  t_1(\bs{\nu}) = \frac{1}{\pi \nu_o}\mathcal{H}_0\left\{\frac{J_1(2\pi \nu_or_d')}{r_d'}\right\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{H}_{\mu}\left\{\frac{J_{\mu+1}(2\pi ar_d')}{r_d'}\right\} =
-  \frac{1}{2\pi}a^{-\mu-1}\nu^\mu\, \Pi\left(\frac{\nu}{a}\right)\label{eq:hankstar}
-\end{align}
-when $a > 0$ and $\text{Re}(\mu) > -\frac{3}{2}$ \cite{poul1998}. Applying this result
+  \mathcal{H}_{\mu}\left\{\frac{J_{\mu+1}(2\pi \nu_or_d')}{r_d'}\right\} =
+  \frac{1}{2\pi}\nu_o^{-\mu-1}\nu^\mu\, \Pi\left(\frac{\nu}{a}\right)\label{eq:hankstar}
+\end{align}
+when $\nu_o > 0$ and $\text{Re}(\mu) > -\frac{3}{2}$ \cite{poul1998}. Applying this result
 we find that
@@
   t_1(\bs{\nu}) =
-    \frac{1}{2\pi^2 a^{2}}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t1final}.
+    \frac{1}{2\pi^2 \nu_o^{2}}\, \Pi\left(\frac{\nu}{\nu_o}\right)\label{eq:t1final}.
 \end{align}
@@
 \begin{align}
-  t_2(\bs{\nu}) = \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\left[ie^{-i\phi_{\nu}}\mathcal{H}_{-1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\}\right].
+  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[ie^{-i\phi_{\nu}}\mathcal{H}_{-1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi ar_d'}\right\}\right].
 \end{align}
@@
 \begin{align}
-  t_2(\bs{\nu}) = \frac{2i}{\pi a}\frac{\text{NA}}{n_o}\left[-ie^{-i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi ar_d')}{\pi ar_d'}\right\}\right].
+  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[-ie^{-i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\}\right].
 \end{align}
@@
   t_2(\bs{\nu}) =
-    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu(e^{-i\phi_\nu} + e^{i\phi_\nu})\, \Pi\left(\frac{\nu}{a}\right)
+    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu(e^{-i\phi_\nu} + e^{i\phi_\nu})\, \Pi\left(\frac{\nu}{\nu_o}\right)
 \end{align}
@@
   t_2(\bs{\nu}) =
-    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu\cos\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t2final}
+    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\cos\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t2final}
 \end{align}
@@
   t_3(\bs{\nu}) =
-    \frac{1}{\pi^2 a^3}\frac{\text{NA}}{n_o}\nu\sin\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t3final}
+    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\sin\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t3final}
 \end{align}
@@
 \begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
-  0\\
-  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right). \label{eq:paractfsp}
+  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right). \label{eq:paractfsp}
 \end{align}
@@
 \begin{bmatrix}
-  \delta(l-1, m-1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
-  \delta(l-1, m+1) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
-  0\\
-  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right).
+  \delta(l-1, m-1) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu\delta(l-1, m)\\
+  \delta(l-1, m+1) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu\delta(l-1, m)\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right).
 \end{align}
@@
   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\nu}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
+  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\tau}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
@@
 \begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
-  0\\
-  \end{bmatrix}\, \Pi\left(\frac{\nu}{a}\right). \label{eq:ctfparax}
+  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
+  0\\
+  \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right). \label{eq:ctfparax}
 \end{align}
@@
 \begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
+    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
+  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
   0\\
@@
   \begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{a}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
+  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
+  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
   0\\
 \end{bmatrix}\nonumber \\
-  &\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right).
+  &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
 \end{align}
@@
 \begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &
-      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
-                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
-                                                                 &\left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
-  &\left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\
-&\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right). 
-\end{align}
-All of the terms with a single $\tau_x$ or $\tau_y$ are odd, so they integrate
-to zero. Therefore
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\bs{\tau}\, &
-      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
-                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{a}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
-&\Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right). 
+    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
+      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+                                                                 &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
+  &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\
+&\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
+\end{align}
+All of the terms with a single $(\tau_\cdot \pm \frac{1}{2}\nu_\cdot)$ term are
+correlations of an odd function with an even function, so they are zero.
+Therefore
+\begin{align}
+    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
+      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+&\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
 \end{align}
 After expanding the spherical harmonics we can rewrite this equation in terms of
-three autocorrelations
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) &= [s_1(\bs{\nu}) + s_2(\bs{\nu}) + s_3(\bs{\nu})]y_0^0(\so{}) + \frac{2\text{NA}}{\sqrt{5}a n_o}[-s_1(\bs{\nu}) + s_2(\bs{\nu}) + s_3(\bs{\nu})]y_2^0(\so{})\label{eq:hinter}
+two autocorrelations
+\begin{align}
+    H^{(p)}(\nu; \so{}) &\propto \Big[A^{(p)}(\nu) + 2B^{(p)}(\nu)\Big]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\Big[-A^{(p)}(\nu) + 4B^{(p)}(\nu)\Big]y_2^0(\so{})\label{eq:hinter}
 \end{align}
@@
 \begin{align}
-  s_1(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right),\\
-  s_2(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, (\tau_x - \nu_x/2)(\tau_x + \nu_x/2) \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right),\\
-  s_3(\bs{\nu}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\, (\tau_y - \nu_y/2)(\tau_y + \nu_y/2) \Pi\left(\frac{\tau - \nu/2}{a}\right)\Pi\left(\frac{\tau + \nu/2}{a}\right).
-\end{align}
-We can evaluate these integrals with the help of the geometric construction
-shown in Figure \ref{fig:geometry} \cite{goodman1996}.
+  A^{(p)}(\nu) &\equiv \frac{1}{\pi\nu_o^2}\int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right),\\
+  B^{(p)}(\nu) &\equiv \frac{\text{NA}^2}{\pi\nu_o^4n_o^2} \int_{\mathbb{R}^2}d\bs{\tau}\, \left[(\tau_x - \nu_x/2)(\tau_x + \nu_x/2) + (\tau_y - \nu_y/2)(\tau_y + \nu_y/2)\right]\nonumber \\ &\hspace{17em}\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
+\end{align}
+I've used the constant $\frac{1}{\pi\nu_o^2}$ in front of both autocorrelations
+so that the results are normalized, but these constants are not essential. Also,
+notice that both autocorrelations are rotationally symmetric, so we can write
+them as a function of $\nu$ instead of $\bs{\nu}$. We can evaluate these
+integrals with the help of the geometric construction shown in Figure
+\ref{fig:geometry} \cite{goodman1996}.
 
@@
    \includegraphics[width = 0.8\textwidth]{../figures/geometry/geometry.pdf}
-   \caption{Geometric construction for evaluating $s_1(\bs{\nu})$,
-     $s_2(\bs{\nu})$, and $s_3(\bs{\nu})$. We need to find the boundaries of
-     integration for the overlapping region of two circles with radius $a$ and
-     distance $\nu$ between their centers. The region is given by four times the
-     difference in area between a sector of angle
-     $\arccos\left(\frac{\nu}{2a}\right)$ and a triangle with base $\nu/2$ and
-     hypotenuse $a$.}
+   \caption{Geometric construction for evaluating $A^{(p)}(\bs{\nu})$ and
+     $B^{(p)}(\bs{\nu})$. We need to find the boundaries of integration for the
+     overlapping region of two circles with radius $\nu_o$ and distance $\nu$
+     between their centers. The region is given by four times the difference in
+     area between a sector of angle $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and
+     a triangle with base $\nu/2$ and hypotenuse $\nu_o$.}
    \label{fig:geometry}
@@
 
-Starting with $s_1(\bs{\nu})$ we find that
-\begin{align}
-  s_1(\bs{\nu}) &= 4\left[\left(\int\limits_0^a d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2a}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2a}{\nu}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}}d\tau_y\right)\right]\\
-  s_1(\bs{\nu}) &= 4\left[\left(\int\limits_0^a d\tau\,\tau\arccos\left(\frac{\nu}{2a}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2a}{\nu}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right)\right]\\
-  s_1(\bs{\nu}) &= 4\left[\frac{a^2}{2}\arccos\left(\frac{\nu}{2a}\right) - \frac{\nu a}{4}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]\\
-  s_1(\bs{\nu}) &= 2a^2\arccos\left(\frac{\nu}{2a}\right) - \nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}.
-\end{align}
-Note that $s_1(\bs{\nu})$ is the unnormalized OTF for a single-view
-fluorescence microscope under the scalar approximation. Next we evaluate
-$s_2(\bs{\nu})$ using the same geometric construction. This integral is not
-rotationally symmetric, so we start by restricting $\bs{\nu}$ to the $x$-axis
-\begin{align}
-  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu_x}{2a}\right)}d\phi_{\tau}(\tau\cos\phi_{\tau} - \nu_x/2)(\tau\cos\phi_{\tau} + \nu_x/2)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \int\limits_0^{\tau_x \frac{2a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}}d\tau_y(\tau_x - \nu_x/2)(\tau_x + \nu_x/2)\Bigg],\\
-  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu_x}{2a}\right)}d\phi_{\tau}(\tau^2\cos^2\phi_{\tau} - \nu_x^2/4)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \int\limits_0^{\tau_x\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}}d\tau_y(\tau_x^2 - \nu_x^2/4)\Bigg].
-\end{align}
-For the first inner integral we will make use of the following
+Starting with $A^{(p)}(\nu)$ we find that
+\begin{align}
+  A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
+  A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
+  A^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+Notice that $A^{(p)}(\nu)$ is the normalized OTF for fluorescence
+microscope with isotropic samples under the paraxial and scalar approximations.
+Next we evaluate $B^{(p)}(\nu)$ using the same geometric construction. This
+integral is rotationally symmetric, so we start by rewriting it as 
+\begin{align}
+  B^{(p)}(\nu) =  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[&\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau\cos\phi_{\tau} - \nu/2)(\tau\cos\phi_{\tau} + \nu/2)\nonumber \\ &- \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x - \nu/2)(\tau_x + \nu/2)\Bigg],\\
+  B^{(p)}(\nu) =  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[&\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2\cos^2\phi_{\tau} - \nu^2/4)\nonumber \\ &- \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x^2 - \nu^2/4)\Bigg].
+\end{align}
+For the first inner integral we make use of
 \begin{align}
@@
 \begin{align}
-  s_2(\nu_x) = 4\Bigg[&\int\limits_0^a d\tau\left(\frac{\tau^3}{2}\left(\frac{\nu_x}{2a}\right)\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{\tau^3}{2}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{\tau\nu_x^2}{4}\arccos\left(\frac{\nu_x}{2a}\right)\right)\nonumber \\ &- \int\limits_0^{\nu_x/2}d\tau_x \left(\tau_x^3 - \frac{\tau_x\nu_x^2}{4}\right)\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
-  s_2(\nu_x) = 4\Bigg[&\left(\frac{a^4}{8}\left(\frac{\nu_x}{2a}\right)\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{8}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{8}\arccos\left(\frac{\nu_x}{2a}\right)\right) - \left(\frac{\nu_x^4}{64} - \frac{\nu_x^4}{32}\right)\frac{2 a}{\nu_x}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
-  s_2(\nu_x) = 4\Bigg[&\frac{\nu_xa^3}{16}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{8}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{8}\arccos\left(\frac{\nu_x}{2a}\right) + \frac{\nu_x^3a}{32}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}\Bigg],\\
-  s_2(\nu_x) = &\frac{\nu_xa^3}{4}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2} + \frac{a^4}{2}\arccos\left(\frac{\nu_x}{2a}\right) - \frac{a^2\nu_x^2}{2}\arccos\left(\frac{\nu_x}{2a}\right) + \frac{\nu_x^3a}{8}\sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2},\\
-  s_2(\nu_x) = &\left(\frac{a^2}{4} - \frac{\nu_x^2}{4}\right)2a^2\arccos\left(\frac{\nu_x}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu_x^2}{8}\right)\nu_x a \sqrt{1 - \left(\frac{\nu_x}{2a}\right)^2}.
-\end{align}
-This result is only true for $\bs{\nu}$ restricted to the $x$ axis, but we can
-extend this result to the general case by noticing that the value of the
-function in the area of overlap has the same functional form for any direction
-of $\bs{\nu}$ but the total value is reduced by a factor of $\cos^2\phi_\nu$.
-This make sense because the function in the area of overlap for the circles
-displaced along the $y$-axis is zero. Therefore, the complete integral is given
-by 
-\begin{align}
-    s_2(\bs{\nu}) = &\cos^2\phi_\nu\left[\left(\frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right].
-\end{align}
-Similarly, $s_3(\bs{\nu})$ is given by
-\begin{align}
-      s_3(\bs{\nu}) = &\sin^2\phi_\nu\left[\left(\frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) + \left(\frac{a^2}{4} + \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right].
-\end{align}
-Plugging these results into Eq. \ref{eq:hinter} gives
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) = &\left[\left(1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]y_0^0(\so{})\nonumber\\ + &\left[\left(-1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(-1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\right]y_2^0(\so{}).
-\end{align}
-After plugging this into Eq. \ref{eq:hlmauto2}, performing the angular integral,
-refactoring, and normalizing, we get the complete spatio-angular transfer function
-\begin{align}
-  H_l^m(\nu) &= H_0^0(\nu)\delta(l, m) + \frac{2\text{NA}}{\sqrt{5}an_o}H_2^0(\nu)\delta(l-2, m)\\
-  H_0^0(\nu) &= \left(1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}\\
-  H_2^0(\nu) &= \left(-1 + \frac{a^2}{4} - \frac{\nu^2}{4}\right)2a^2\arccos\left(\frac{\nu}{2a}\right) - \left(-1 - \frac{a^2}{4} - \frac{\nu^2}{8}\right)\nu a\sqrt{1 - \left(\frac{\nu}{2a}\right)^2}
-\end{align}
-
+  B^{(p)}(\nu)&=\frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\int\limits_0^a d\tau\left(\frac{\tau^3}{2}\left(\frac{\nu}{2\nu_o}\right)\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\tau^3}{2}\arccos\left(\frac{\nu}{2a}\right) - \frac{\tau\nu^2}{4}\arccos\left(\frac{\nu}{2\nu_o}\right)\right)\nonumber \\ &\hspace{7em}- \int\limits_0^{\nu/2}d\tau_x \left(\tau_x^3 - \frac{\tau_x\nu^2}{4}\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),
+\end{align}
+\begin{align}
+  B^{(p)}(\nu) &=  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\left(\frac{\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\right)\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\nu_o^4}{8}\arccos\left(\frac{\nu}{2\nu_o}\right)- \frac{\nu_o^2\nu^2}{8}\arccos\left(\frac{\nu}{2\nu_o}\right)\right)\nonumber \\ &\hspace{7em} - \left(\frac{\nu^4}{64} - \frac{\nu^4}{32}\right)\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  B^{(p)}(\nu) &=  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\frac{\nu\nu_o^3}{16}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\nu_o^4}{8}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu_o^2\nu^2}{8}\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{\nu^3\nu_o}{32}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  B^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu^2}{\nu_o^2}\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{\nu^3}{4\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  B^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2a}\right).
+\end{align}
+
+Now that we've evaluated the autocorrelations we can complete the OTF
+calculation. By plugging Eq. \ref{eq:hinter} into Eq. \ref{eq:hlmauto2},
+performing the angular integral, and normalizing, we get the complete
+spatio-angular transfer function
+\begin{align}
+  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\\
+  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + \text{NA}^2/(2n_o^2)},\\
+  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + \text{NA}^2/(2n_o^2)]}.
+\end{align}
+where
+\begin{align}
+  {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  {B}^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+\tikzstyle{block} = [draw, fill=white, rectangle, 
+    minimum height=2cm, minimum width=3.5cm, text width=3cm, align=center]
+\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
+\tikzstyle{input} = [coordinate]
+\tikzstyle{output} = [coordinate]
+\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+\begin{figure}
+\begin{tikzpicture}[auto, node distance=3cm,>=latex]
+    \node [input, name=input] {};
+    \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{})$};
+    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu})$};
+    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
+    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\rd{} - M\ro{}, \so{})$};
+
+    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
+    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{E}_l^m(\bs{\nu})\star_{\mathbb{R}^2} \mb{E}_l^m(\bs{\nu})]$} (otf);
+    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
+    \draw [->] (csf) -- node[name=v, text width=4cm, align=center, left] {Detector\\ $|\mb{\tilde{e}}_d(\rd{} - M\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
+      \end{tikzpicture}
+      \centering
+      \captionsetup{width=1.0\linewidth}
+      \caption{Summary of relationships between the CSF, CTF, PSF, and OTF where
+        $\mathcal{F}_D$, $|\cdot|_D$, and $\star_D$ denote the Fourier
+        transform, norm, and autocorrelation over the set $D$, respectively. See
+        \cite{goodman1996} and \cite{mertz2009} for analogous diagrams under
+        scalar optics approximations.}
+    \end{figure}
 \end{document}

### 2018-04-11 notes/2018-02-23-spatio-angular-kernel/calculations/analytic.py

@@ -1,0 +1,75 @@
+import matplotlib.pyplot as plt
+import numpy as np
+# from scipy import special
+# from scipy.fftpack import fft
+
+import matplotlib
+matplotlib.rcParams.update({'font.size': 12})
+
+# def I0(x):
+#     return (2*special.jn(1,x)/x)**2
+
+# def I1(x, NA=0.8, n=1.33):
+#     return (NA/n)**2*(2*special.jn(2,x)/x)**2
+
+# def psf(x, NA=0.8, n=1.33):
+#    return I0(x) + 2*I1(x, NA, n)
+
+# def psf2(x, NA=1.1, n=1.33):
+#    return (-I0(x) + 4*I1(x, NA, n))/np.sqrt(5)
+
+def ac(NA=0.8, M=40, lamb=500):
+    return NA/(M*lamb)
+
+def w1(nu, NA=0.8, n=1.33, M=40, lamb=500):
+    return ((NA**2)/(2*(n**2)))*(1 - ((nu/ac(NA=NA, M=M, lamb=lamb))**2))
+
+def w2(nu, NA=0.8, n=1.33, M=40, lamb=500):
+    return ((NA**2)/(2*(n**2)))*(1 + 0.5*((nu/ac(NA=NA, M=M, lamb=lamb))**2))
+
+def H00(nu, NA=0.8, n=1.33, M=40, lamb=500):
+    return norm(nu, NA=NA, n=n, M=M, lamb=lamb)*((w1(nu, NA=NA, n=n, M=M, lamb=lamb) + 1)*np.arccos(nu/(2*ac(NA=NA, M=M, lamb=lamb))) + (w2(nu) - 1)*(nu/(2*ac()))*np.sqrt(1 - (nu/(2*ac(NA=NA, M=M, lamb=lamb)))**2))
+
+def H20(nu, NA=0.8, n=1.33, M=40, lamb=500):
+    return norm(nu)*(1.0/np.sqrt(5))*((2*w1(nu, NA=NA, n=n, M=M, lamb=lamb) - 1)*np.arccos(nu/(2*ac())) + (2*w2(nu) + 1)*(nu/(2*ac(NA=NA, M=M, lamb=lamb)))*np.sqrt(1 - (nu/(2*ac(NA=NA, M=M, lamb=lamb)))**2))
+
+def norm(nu, NA=0.8, n=1.33, M=40, lamb=500):
[…]

### 2018-04-17 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Numerics and analytics match. Paraxial spatio-angular otf done.

@@
 %%%%%%%%%%%%
-
+\usepackage[dvipsnames]{xcolor}
 \hyphenpenalty=10000
@@
 \begin{align}
-  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_0^2}^{(p)}(\rd{}')y_0^2(\so{}),\\
+  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}),\\
   {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
-  {h_0^2}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right].
+  {h_2^0}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right]. \label{eq:concisepsf}
 \end{align}
@@
 
-In Appendix \ref{paraxialotf} we calculate the paraxial OTF for a single-view
+In Appendix \ref{paraxialotf2} we calculate the paraxial OTF for a single-view
 fluorescence microscope as
 \begin{align}
-  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\label{eq:fullotf}\\
-  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + \text{NA}^2/(2n_o^2)},\\
-  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + \text{NA}^2/(2n_o^2)]}.
+  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m), \label{eq:fullotf} \\
+  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + (\text{NA}/n_o)^2},\\
+  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + (\text{NA}/n_o)^2]},
 \end{align}
@@
   {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  {B}^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+  B^{(p)}(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
@@
 of $\nu$ instead of the complete spatial frequency vector $\bs{\nu}$. This will
-no longer be true when we leave the paraxial approximation or add polarizing
-filters to the system. Also, notice that ${A}^{(p)}(\nu)$ is the spatial OTF for
-an incoherent imaging system under the paraxial and scalar approximations
-\cite{goodman1996}.
+not be true when we leave the paraxial approximation or add polarizing filters
+to the system. Also, notice that ${A}^{(p)}(\nu)$ is the spatial OTF for an
+incoherent imaging system (the Fourier transform of an Airy pattern) under the
+paraxial and scalar approximations \cite{goodman1996}.
 
@@
 can ignore the ${H_2^0}^{(p)}(\nu)$ term in the OTF. As the NA approaches zero,
-${B}^{(p)}(\nu)$ disappears and we recover the spatial OTF from the
+${B}^{(p)}(\nu)$ disappears and we recover the scalar OTF from the vector
 spatio-angular OTF as expected. For non-zero NA the difference between the OTF
@@
 this difference as an electromagnetic correction to the scalar OTF. The
-correction is proportional to $\frac{\text{NA}^2}{n_o^2}$, so it is a small term
+correction is proportional to $\left(\text{NA}/{n_o}\right)^2$, so it is a small term
 for all but high NA objectives.
@@
 \begin{align}
-  H_{\mh{z}}(\nu) \propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu).
-\end{align}
-The main result is that the spatial OTF for any dipole distribution is a linear
-combination of the OTFs for the spherical harmonics. I am partially hesitant to
-refer to $H_{\mh{z}}(\nu)$ as an OTF because it is object dependent, but the
-vocabulary is fine if it is understood that the sample only contains
-$z$-oriented dipoles. For general distributions, the complete spatio-angular OTF
-should be used instead of deriving the transfer function for every individual
-fluorophore.
-
-Fig. \ref{fig:para} shows the spatio-angular OTF for a microscope with
-$\text{NA}=0.8$ and $n=1.33$. The most important feature of this figure is that
-${H_0^0}^{(p)}(\nu)$ is a low-pass filter compared to ${H_0^2}^{(p)}(\nu)$ with
-a maximum difference of $\sim 7\%$ (with larger difference for higher NA). If the difference between
-${H_0^0}^{(p)}(\nu)$ and ${H_0^2}^{(p)}(\nu)$ is not completely obscured by
-noise, we will be able to exploit the difference to estimate the out-of-plane
-angle of dipoles with a single image (putting aside the ill-posedness of the
-problem).
+  H_z^{(p)}(\nu) &\propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu), \\
+    H_z^{(p)}(\nu) &= \frac{1}{2}\left(\frac{n_o}{\text{NA}}\right) B^{(p)}(\nu).
+\end{align}
+The most important result is that the spatial OTF for \textbf{any} dipole
+distribution is a linear combination of just two OTFs---one for each spherical
+harmonic. The same is true for the PSFs---the PSF for any dipole
+distribution is a linear combination of just two PSFs.
+
+Fig. \ref{fig:para} shows four important paraxial PSFs and OTFs for a microscope
+with $\text{NA}=0.8$ and $n=1.33$. Notice that the OTF for $z$-oriented
+dipoles is negative at high frequencies. An OTF that crosses zero will give a
+contrast inversion in a Siemens star test target. The negative OTF is a direct
+consequence of the donut-shaped point spread function. If we arranged a pattern
+of $z$-oriented dipoles with a sinusoid spatial frequency near the cutoff
+frequency, the regions of low intensity would report the positions of the
+fluorophores.
 
@@
    \centering
-   \includegraphics[width = 1.\textwidth]{../calculations/psfs.pdf}
-   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
-     single-view fluorescence microscope with NA=0.8 and $n_o$=1.33. The solid
-     line is the PSF for $y_0^0$ distributions and the dashed line is the PSF
-     for $y_2^0$ distributions. The dotted line is the $y_2^0$ PSF normalized
-     for comparison with the $y_0^0$ PSF. The $y_2^0$ distributions includes
-     ``negative'' fluorophores, so it gives rise to a negative PSF.
-     \textbf{Right:} Numerical paraxial spatio-angular optical transfer function
-     for the same microscope. The $y_0^0$ term has a comparatively low-pass
-     response while the $y_2^0$ term has a comparatively high-pass response.}
+   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
+   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
+     transfer functions for a single-view fluorescence microscope with
+     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
+     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
+     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
+     harmonic---negative fluorophores near the transverse plane, positive
+     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
+     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $y$-oriented
+     dipole.}
    \label{fig:para}
@@
 
-\section{Paraxial optical transfer function}\label{paraxialotf}
+% \section{Paraxial optical transfer function}\label{paraxialotf}
+% In this appendix we calculate the paraxial OTF for a single-view fluorescence
+% microscope. We start with Eq. \ref{eq:otfdef2}
+% \begin{align}
+%   H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+% \end{align}
+% We could plug in the paraxial PSF and evaluate the integrals, but this will lead
+% us to Fourier transforms that cannot be found in tables. Instead we use a trick
+% from scalar Fourier optics and write the OTF in terms of the detected electric
+% field \cite{goodman1996}
+% \begin{align}
+%   H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \left|\mb{e}_d(\rd{}', \so{})\right|^2 y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+% \end{align}
+% Next, we manipulate this equation to
+% \begin{align}
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}', \so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}},\\
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\delta(\rd{}'' - \rd{}')\, \me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\tau}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
+% \end{align}
+% We have followed the proof for the Wiener-Kinchin theorem \cite{papoulis2002, wiener} to explicitly show how the angular integral affects the usual scalar
+% calculation. Eq. \ref{eq:hlmauto} shows that we can calculate the OTF by taking
+% the vector autocorrelation of the spatial CTF then projecting the result onto
+% the spherical harmonics.
+
+% We will rewrite Eq. \ref{eq:hlmauto} in two parts
+% \begin{align}
+%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{}) H(\bs{\nu}; \so{})  \label{eq:hlmauto2}\\
+%   H(\bs{\nu}; \so{}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}- \bs{\nu}/2; \so{})\mb{E}(\bs{\tau} + \bs{\nu}/2; \so{}). \label{eq:hlmspatial}
+% \end{align}
+% Notice the change of variable to simplify the autocorrelation. In the previous
+% section we calculated the CTF in the paraxial case as 
+% \begin{align}
+%   {\mb{E}}^{(p)}(\bs{\nu}; \so{}) =
+% \begin{bmatrix}
+%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
+%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
+%   0\\
+%   \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right). \label{eq:ctfparax}
+% \end{align}
+% By introducing $\bs{\tau} \equiv \tau_x\mh{x} + \tau_y\mh{y} \equiv \tau\cos\phi_\tau\mh{x} + \tau\sin\phi_\tau\mh{y}$
+% we can plug Eq. \ref{eq:ctfparax} into Eq. \ref{eq:hlmspatial} and find that
+% \begin{align}
+%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
+%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
+%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
+%   0\\
+% \end{bmatrix}^{\dagger}
+%   \begin{bmatrix}
+%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
+%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
+%   0\\
+% \end{bmatrix}\nonumber \\
+%   &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
+% \end{align}
+% Expanding the inner product gives
+% \begin{align}
+%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
+%       \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+%                                                                  &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+%                                                                  &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
+%   &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\
+% &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
+% \end{align}
+% All of the terms with a single $(\tau_\cdot \pm \frac{1}{2}\nu_\cdot)$ term are
+% correlations of an odd function with an even function, so they are zero.
+% Therefore
+% \begin{align}
+%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
+%       \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
+%                                                                  &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
+% &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
+% \end{align}
+% After expanding the spherical harmonics we can rewrite this equation in terms of
+% two autocorrelations
+% \begin{align}
+%     H^{(p)}(\nu; \so{}) &\propto \Big[A^{(p)}(\nu) + 2B^{(p)}(\nu)\Big]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\Big[-A^{(p)}(\nu) + 4B^{(p)}(\nu)\Big]y_2^0(\so{})\label{eq:hinter}
+% \end{align}
+% where
+% \begin{align}
+%   A^{(p)}(\nu) &\equiv \frac{1}{\pi\nu_o^2}\int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right),\\
+%   B^{(p)}(\nu) &\equiv \frac{\text{NA}^2}{\pi\nu_o^4n_o^2} \int_{\mathbb{R}^2}d\bs{\tau}\, \left[(\tau_x - \nu_x/2)(\tau_x + \nu_x/2) + (\tau_y - \nu_y/2)(\tau_y + \nu_y/2)\right]\nonumber \\ &\hspace{17em}\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
+% \end{align}
+% I've used the constant $\frac{1}{\pi\nu_o^2}$ in front of both autocorrelations
+% so that the results are normalized, but these constants are not essential. Also,
+% notice that both autocorrelations are rotationally symmetric, so we can write
+% them as a function of $\nu$ instead of $\bs{\nu}$. We can evaluate these
+% integrals with the help of the geometric construction shown in Figure
+% \ref{fig:geometry} \cite{goodman1996}.
+
+% \begin{figure}[h]
+%  \captionsetup{width=1.0\linewidth}
+%  \centering
+%    \centering
+%    \includegraphics[width = 0.8\textwidth]{../figures/geometry/geometry.pdf}
+%    \caption{Geometric construction for evaluating $A^{(p)}(\bs{\nu})$ and
+%      $B^{(p)}(\bs{\nu})$. We need to find the boundaries of integration for the
+%      overlapping region of two circles with radius $\nu_o$ and distance $\nu$
+%      between their centers. The region is given by four times the difference in
+%      area between a sector of angle $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and
+%      a triangle with base $\nu/2$ and hypotenuse $\nu_o$.}
+%    \label{fig:geometry}
+% \end{figure}
+
+% Starting with $A^{(p)}(\nu)$ we find that
+% \begin{align}
+%   A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
+%   A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
+%   A^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+% \end{align}
+% Notice that $A^{(p)}(\nu)$ is the normalized OTF for fluorescence
+% microscope with isotropic samples under the paraxial and scalar approximations.
+% Next we evaluate $B^{(p)}(\nu)$ using the same geometric construction. This
+% integral is rotationally symmetric, so we start by rewriting it as 
+% \begin{align}
+%   B^{(p)}(\nu) =  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).\\
+% \end{align}
+% For the first inner integral we make use of
+% \begin{align}
+%   \int\limits_0^{\arccos(z)} d\phi \cos^2\phi &= \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\arccos(z), \\
+%   \int\limits_0^{\arccos(z)} d\phi \cos\phi &= \sqrt{1 - z^2}.
+% \end{align}
+% This results in
+% \begin{align}
+%   B^{(p)}(\nu)&=\frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B^{(p)}(\nu) &=  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B^{(p)}(\nu) &=  \frac{\text{NA}^2}{2\pi n_o^2}\Bigg[\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[-\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B^{(p)}(\nu) &= \frac{2}{\pi}\left(\frac{2\text{NA}}{n_o}\right)^2\left[-\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{1}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+% \end{align}
+
+% Now that we've evaluated the autocorrelations we can complete the OTF
+% calculation. By plugging Eq. \ref{eq:hinter} into Eq. \ref{eq:hlmauto2},
+% performing the angular integral, and normalizing, we get the complete
+% spatio-angular transfer function
+% \begin{align}
+%   {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\\
+%   {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + 8(\text{NA}/n_o)^2},\\
+%   {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + 8(\text{NA}/n_o)^2]}.
+% \end{align}
+% where
+% \begin{align}
+%   {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B^{(p)}(\nu) &= \frac{2}{\pi}\left(\frac{2\text{NA}}{n_o}\right)^2\left[-\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{1}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+% \end{align}
+
+\section{Paraxial optical transfer function}\label{paraxialotf2}    
 In this appendix we calculate the paraxial OTF for a single-view fluorescence
@@
 \begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:otfdef2}
-\end{align}
-We could plug in the paraxial PSF and evaluate the integrals, but this will lead
-us to Fourier transforms that cannot be found in tables. Instead we use a trick
-from scalar Fourier optics and write the OTF in terms of the detected electric
-field \cite{goodman1996}
-\begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \left|\mb{e}_d(\rd{}', \so{})\right|^2 y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
-\end{align}
-Next, we manipulate this equation to
-\begin{align}
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}', \so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}},\\
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\delta(\rd{}'' - \rd{}')\, \me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\tau}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
-\end{align}
-We have followed the proof for the Wiener-Kinchin theorem \cite{papoulis2002, wiener} to explicitly show how the angular integral affects the usual scalar
-calculation. Eq. \ref{eq:hlmauto} shows that we can calculate the OTF by taking
-the vector autocorrelation of the spatial CTF then projecting the result onto
-the spherical harmonics.
-
-We will rewrite Eq. \ref{eq:hlmauto} in two parts
-\begin{align}
-  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{}) H(\bs{\nu}; \so{})  \label{eq:hlmauto2}\\
-  H(\bs{\nu}; \so{}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}- \bs{\nu}/2; \so{})\mb{E}(\bs{\tau} + \bs{\nu}/2; \so{}). \label{eq:hlmspatial}
-\end{align}
-Notice the change of variable to simplify the autocorrelation. In the previous
-section we calculated the CTF in the paraxial case as 
-\begin{align}
-  {\mb{E}}^{(p)}(\bs{\nu}; \so{}) =
-\begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
-  0\\
-  \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right). \label{eq:ctfparax}
-\end{align}
-By introducing $\bs{\tau} \equiv \tau_x\mh{x} + \tau_y\mh{y} \equiv \tau\cos\phi_\tau\mh{x} + \tau\sin\phi_\tau\mh{y}$
-we can plug Eq. \ref{eq:ctfparax} into Eq. \ref{eq:hlmspatial} and find that
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
-  0\\
-\end{bmatrix}^{\dagger}
-  \begin{bmatrix}
-  y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
-  y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
-  0\\
-\end{bmatrix}\nonumber \\
-  &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
-\end{align}
-Expanding the inner product gives
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
-      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
-                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
-                                                                 &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
-  &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\
-&\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
-\end{align}
-All of the terms with a single $(\tau_\cdot \pm \frac{1}{2}\nu_\cdot)$ term are
-correlations of an odd function with an even function, so they are zero.
-Therefore
-\begin{align}
-    H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
-      \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
-                                                                 &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
-&\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
-\end{align}
-After expanding the spherical harmonics we can rewrite this equation in terms of
-two autocorrelations
-\begin{align}
-    H^{(p)}(\nu; \so{}) &\propto \Big[A^{(p)}(\nu) + 2B^{(p)}(\nu)\Big]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\Big[-A^{(p)}(\nu) + 4B^{(p)}(\nu)\Big]y_2^0(\so{})\label{eq:hinter}
-\end{align}
-where
-\begin{align}
-  A^{(p)}(\nu) &\equiv \frac{1}{\pi\nu_o^2}\int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right),\\
-  B^{(p)}(\nu) &\equiv \frac{\text{NA}^2}{\pi\nu_o^4n_o^2} \int_{\mathbb{R}^2}d\bs{\tau}\, \left[(\tau_x - \nu_x/2)(\tau_x + \nu_x/2) + (\tau_y - \nu_y/2)(\tau_y + \nu_y/2)\right]\nonumber \\ &\hspace{17em}\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
-\end{align}
-I've used the constant $\frac{1}{\pi\nu_o^2}$ in front of both autocorrelations
-so that the results are normalized, but these constants are not essential. Also,
-notice that both autocorrelations are rotationally symmetric, so we can write
-them as a function of $\nu$ instead of $\bs{\nu}$. We can evaluate these
-integrals with the help of the geometric construction shown in Figure
-\ref{fig:geometry} \cite{goodman1996}.
-
+  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h^{(p)}(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+  \label{eq:appotf}
+\end{align}
+where the paraxial PSF is given by Eq. \ref{eq:concisepsf}
+\begin{align}
+  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}),\\ \label{eq:parapsf}
+  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
+  {h_2^0}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right]. 
+\end{align}
+Plugging Eq. \ref{eq:parapsf} into Eq. \ref{eq:appotf} and evaluating the
+angular integral gives
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{R}^2}d\rd{}'\, \left[{h_0^0}^{(p)}(\rd{}')\delta(l, m) + {h_2^0}^{(p)}(\rd{}')\delta(l-2, m)\right] \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+\label{eq:appotf2}
+\end{align}
+Using the operator notation $\mathcal{F}_2\{f(\mb{r})\} = \int_{\mathbb{R}^2}d\mb{r}\{f(\mb{r})\}\me^{-i 2\pi \mb{r}\cdot\bs{\nu}}$, we can rewrite Eq. \ref{eq:appotf2} as 
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \mathcal{F}_2\{{h_0^0}^{(p)}(\rd{}')\delta(l, m) + {h_2^0}^{(p)}(\rd{}')\delta(l-2, m) \},\\
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l-2, m).
+\end{align}
+To calculate $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ we can use the
+autocorrelation theorem \cite{goodman1996}
+p\begin{align}
+  \mathcal{F}_2\left\{f^2(r)\right\} = \mathcal{F}_2\left\{f(r)\right\} \star_2 \mathcal{F}\left\{f(r)\right\},
+\end{align}
+where $\star_2$ denotes a two-dimensional autocorrelation. We can rewrite
+$\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ as
+\begin{align}
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\}.
+\end{align}
+Next, we notice that the two-dimensional Fourier transform is radially
+symmetric, so it can be written as a zero-order Hankel transform
+\begin{align}
+\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\} \star_2 \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\}, 
+\end{align}
+where the $k$-order Hankel transform is defined as
+\begin{align}
+  \mathcal{H}_k\left\{f(r)\right\} = 2\pi \int_0^\infty dr\, r f(r)J_k(2\pi r\nu).
+\end{align}
+Finally, we can apply the following Hankel transform identity
+\begin{align}
+  \mathcal{H}_{k}\left\{\frac{J_{k+1}(2\pi \nu_or_d')}{\pi\nu_o r_d'}\right\} =
+  \frac{2\nu^k}{\nu_o^{k+1}}\, \Pi\left(\frac{\nu}{\nu_o}\right)\label{eq:hankstar2},
+\end{align}
+when $\nu_o > 0$ and $\text{Re}(k) > -\frac{3}{2}$ \cite{poul1998} which gives
+\begin{align}
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right],\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \frac{4}{\nu_o^2}\left[\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\Pi\left(\frac{\nu}{\nu_o}\right)\right].
+\end{align}
+The autocorrelation is a geometry problem of finding the area of overlap of two
+displaced circles. Using the geometric construction in Fig. \ref{fig:geometry} we find that
 \begin{figure}[h]
@@
 \end{figure}
-
-Starting with $A^{(p)}(\nu)$ we find that
-\begin{align}
-  A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
-  A^{(p)}(\nu) &= \frac{4}{\pi\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right)\\
-  A^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-Notice that $A^{(p)}(\nu)$ is the normalized OTF for fluorescence
-microscope with isotropic samples under the paraxial and scalar approximations.
-Next we evaluate $B^{(p)}(\nu)$ using the same geometric construction. This
-integral is rotationally symmetric, so we start by rewriting it as 
-\begin{align}
-  B^{(p)}(\nu) =  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[&\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau\cos\phi_{\tau} - \nu/2)(\tau\cos\phi_{\tau} + \nu/2)\nonumber \\ &- \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x - \nu/2)(\tau_x + \nu/2)\Bigg],\\
-  B^{(p)}(\nu) =  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[&\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2\cos^2\phi_{\tau} - \nu^2/4)\nonumber \\ &- \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x^2 - \nu^2/4)\Bigg].
+\begin{align}
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}&= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= 8\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+Next, we calculate $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$. If we follow
+the same steps as we did for $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$, we
+will reach a dead end because there is no Hankel transform identity that we can
+use. Instead, we rewrite $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$ in the
+following way so that we can use the Hankel transform identity in Eq. \ref{eq:hankstar2}
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} = \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\cos^2(\phi_d')\right\} + \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\cos^2(\phi_d')\right\}.
+\end{align}
+Now we apply the autocorrelation theorem
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} = \left[\mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\}\right] + \left[\mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\}\right].
+\label{eq:int3}
+\end{align}
+The two autocorrelated Fourier transforms are separable in polar coordinates, so
+they can be expanded in terms of Hankel transforms \cite{goodman1996}. In
+general, if a function $f(r, \theta)$ is separable in polar coordinates then we
+can rewrite it as $f(r, \theta) = f_{R}(r)f_{\Theta}(\theta)$ and its
+two-dimensional Fourier transform can be expanded in terms of Hankel transforms
+using
+\begin{align}
+  \mathcal{F}\{f(r, \theta)\} = \sum_{k=-\infty}^{\infty}c_k(-i)^k\me^{ik\phi}\mathcal{H}_k\{f_R(r)\},
+\end{align}
+where
+\begin{align}
+  c_k = \frac{1}{2\pi}\int_0^{2\pi}d\theta\, f_{\Theta}(\theta)\me^{-ik\theta}. 
+\end{align}
+Applying the Hankel transform expansion to $\mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\}$ gives
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
+\end{align}
+Next, we apply the identity $\mathcal{H}_\mu = (-1)^\mu\mathcal{H}_{-\mu}$ and simplify
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{i\cos\phi_\nu}{2}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
+\end{align}
+Next, we evaluate the Hankel transform using Eq. \ref{eq:hankstar2}
+\begin{align}
+  \mathcal{H}_{1}\{{b^{(p)}}(r_d')\} = \mathcal{H}_{1}\left\{\frac{J_{2}(2\pi \nu_or_d')}{\pi\nu_o r_d'}\right\} =
+  \left(\frac{\text{NA}}{n_o}\right)\frac{2\nu}{\nu_o^{2}}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+\end{align}
+Therefore, 
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+\end{align}
+Similarly,
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+\end{align}
+Now we can plug these back in to the autocorrelation in Eq. \ref{eq:int3}
+\begin{align}
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}
+\end{align}
+These autocorrelations can be evaluated by finding the weighted area of overlap
+of two circles. Neither of the autocorrelations is radially symmetric, but we
+know that their sum must be radially symmetric because ${b^{(p)}}^2(r_d')$ is
+radially symmetric. We recognize that the first autocorrelation is largest for
+shifts along the $x$ axis and smallest for shifts along the $y$ axis with a
+smooth $\cos^2\phi_\nu$ weighting between the two extremes. The same is true for
+the second autocorrelation except with the $x$ and $y$ axes exchanged and a
+$\sin^2\phi_\nu$ weighting between the two extremes. Therefore, the sum of the two
+autocorrelations can be rewritten as the sum of either autocorrelation shifted along
+the $x$ axis and the $y$ axis
+\begin{align}
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
+\end{align}
+where $\star_2^x$ denotes a two-dimensional autocorrelation for shifts along the
+$x$ axis.
+
+We can use the same limits of integration as we did previously, but we need to
+include a weighted integrand. First, we evaluate the autocorrelation for shifts
+along the $x$-axis
+\begin{align}
+  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
+  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
@@
 \begin{align}
-  \int\limits_0^{\arccos(z)} d\phi \cos^2\phi = \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\arccos(z).
+  \int\limits_0^{\arccos(z)} d\phi \cos^2\phi &= \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\arccos(z), \\
+  \int\limits_0^{\arccos(z)} d\phi \cos\phi &= \sqrt{1 - z^2}.
 \end{align}
@@
 \begin{align}
-  B^{(p)}(\nu)&=\frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\int\limits_0^a d\tau\left(\frac{\tau^3}{2}\left(\frac{\nu}{2\nu_o}\right)\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\tau^3}{2}\arccos\left(\frac{\nu}{2a}\right) - \frac{\tau\nu^2}{4}\arccos\left(\frac{\nu}{2\nu_o}\right)\right)\nonumber \\ &\hspace{7em}- \int\limits_0^{\nu/2}d\tau_x \left(\tau_x^3 - \frac{\tau_x\nu^2}{4}\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),
-\end{align}
-\begin{align}
-  B^{(p)}(\nu) &=  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\left(\frac{\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\right)\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\nu_o^4}{8}\arccos\left(\frac{\nu}{2\nu_o}\right)- \frac{\nu_o^2\nu^2}{8}\arccos\left(\frac{\nu}{2\nu_o}\right)\right)\nonumber \\ &\hspace{7em} - \left(\frac{\nu^4}{64} - \frac{\nu^4}{32}\right)\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  B^{(p)}(\nu) &=  \frac{4\text{NA}^2}{\pi\nu_o^4n_o^2}\Bigg[\frac{\nu\nu_o^3}{16}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \frac{\nu_o^4}{8}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu_o^2\nu^2}{8}\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{\nu^3\nu_o}{32}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  B^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2a}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu^2}{\nu_o^2}\arccos\left(\frac{\nu}{2\nu_o}\right) + \frac{\nu^3}{4\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  B^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2a}\right).
-\end{align}
-
-Now that we've evaluated the autocorrelations we can complete the OTF
-calculation. By plugging Eq. \ref{eq:hinter} into Eq. \ref{eq:hlmauto2},
-performing the angular integral, and normalizing, we get the complete
-spatio-angular transfer function
+  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \frac{1}{2}\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &= \frac{1}{2}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &= \left[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{6}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}
+\end{align}
+Next, we evaluate the autocorrelation for shifts along the $y$-axis
+\begin{align}
+  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
+  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+For the first inner integral we make use of
+\begin{align}
+  \int\limits_0^{\arccos(z)} d\phi \sin^2\phi &= -\frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\arccos(z).
+\end{align}
+This results in
+\begin{align}
+  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \Bigg[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\label{eq:auto2}
+\end{align}
+Combining the results in Eqs. \ref{eq:auto1} and \ref{eq:auto2} gives us the final Fourier transform
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+Now that we've evaluated $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ and $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$, we can plug the results into the following equation and we have the complete spatio-angular transfer function
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l-2, m).
+\end{align}
+After refactoring and normalizing, we have the final spatio-angular transfer function
 \begin{align}
   {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\\
-  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + \text{NA}^2/(2n_o^2)},\\
-  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + \text{NA}^2/(2n_o^2)]}.
+  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + (\text{NA}/n_o)^2},\\
+  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + (\text{NA}/n_o)^2]},
 \end{align}
@@
     \end{figure}
+
 \end{document}

### 2018-04-17 notes/2018-02-23-spatio-angular-kernel/calculations/compare-ft/util.py

@@ -28,19 +28,21 @@ def myacos(x):
     return np.nan_to_num(np.arccos(np.abs(x/2)))
     
 def mysqrt(x):
-    return np.nan_to_num((np.abs(x)/2)*np.sqrt(1 - (np.abs(x)/2)**2))
+    return np.nan_to_num((np.abs(x/2))*np.sqrt(1 - (np.abs(x/2))**2))
     
 def A(x):
     return (2/np.pi)*(myacos(x) - mysqrt(x))
 
 def B(x, NA=0.8, n=1.33):
-    return ((NA**2)/(2*np.pi*(n**2)))*((1 - x**2)*myacos(x) + (1 + ((x**2)/2))*mysqrt(x))
+    N = (1/(np.pi))*((NA/n)**2)
+    poly = (3.0 - 2.0*(np.abs(x/2)**2))
+    return N*(myacos(x) - poly*mysqrt(x))
 
 def H00(x, NA=0.8, n=1.33):
-    return (A(x) + 2*B(x, NA=NA, n=n))/(1 + 0.5*(NA/n)**2)
+    return (A(x) + 2*B(x, NA=NA, n=n))/(1 + (NA/n)**2)
 
 def H20(x, NA=0.8, n=1.33):
-    return (-A(x) + 4*B(x, NA=NA, n=n))/(np.sqrt(5)*(1 + 0.5*(NA/n)**2))
+    return (-A(x) + 4*B(x, NA=NA, n=n))/(np.sqrt(5)*(1 + (NA/n)**2))
 
 # File I/O
 def save_tiff(image, filename):

### 2018-04-18 notes/2018-02-23-spatio-angular-kernel/report/report.tex
y-oriented -> z-oriented typo
Fixed small normalization issues.

@@
      fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
-     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $y$-oriented
+     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $z$-oriented
      dipole.}
@@
    \includegraphics[width = 0.8\textwidth]{../figures/geometry/geometry.pdf}
-   \caption{Geometric construction for evaluating $A^{(p)}(\bs{\nu})$ and
-     $B^{(p)}(\bs{\nu})$. We need to find the boundaries of integration for the
-     overlapping region of two circles with radius $\nu_o$ and distance $\nu$
-     between their centers. The region is given by four times the difference in
-     area between a sector of angle $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and
-     a triangle with base $\nu/2$ and hypotenuse $\nu_o$.}
+   \caption{Geometric construction for evaluating the autocorrelations. We need
+     to integrate over the overlapping region of two circles with radius $\nu_o$
+     and distance $\nu$ between their centers. The region is given by four times
+     the difference in area between a sector of angle
+     $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and a triangle with base $\nu/2$
+     and hypotenuse $\nu_o$.}
    \label{fig:geometry}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{1}{2}\left[i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}\right].
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{i\cos\phi_\nu}{2}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -i\cos\phi_\nu \mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
 \end{align}
@@
 \begin{align}
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}
 \end{align}
@@
 \begin{align}
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
 \end{align}
@@
 \begin{align}
-  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
-  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+  &\frac{-4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
+  &=  \frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
@@
 \begin{align}
-  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{1}{2}\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &= \frac{1}{2}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &= \left[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{6}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}
+  &=\frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \frac{-16}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  2\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &= 2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &= \left[2\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{2}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}
 \end{align}
@@
 \begin{align}
-  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
-  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+  &\frac{-4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
+  &=  \frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
@@
 \begin{align}
-  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \Bigg[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+  &=\frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \frac{-16}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  &=  \Bigg[2\arccos\left(\frac{\nu}{2\nu_o}\right) - 2\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{4}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \label{eq:auto2}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}

### 2018-04-20 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Missing factor of two on Ebfp.
Early draft of polarized OTF notes.

@@
   \begin{bmatrix}
-    1 & 0 &-\frac{r_b}{f_o}\cos\phi_b\\
-    0&1&-\frac{r_b}{f_o}\sin\phi_b\\
+    1 & 0 &-\frac{2r_b}{f_o}\cos\phi_b\\
+    0&1&-\frac{2r_b}{f_o}\sin\phi_b\\
     0&0&0
@@
      $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
-     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
-     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
-     harmonic---negative fluorophores near the transverse plane, positive
-     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
+     \textbf{Black:} $l=0, m=0$ spherical harmonic term---an isotropic
+     distribution of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$
+     spherical harmonic term---negative fluorophores near the transverse plane,
+     positive fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
      $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $z$-oriented

### 2018-04-20 notes/2018-04-19-polarizer-otf/report/report.tex
Early draft of polarized OTF notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathbf{#1}}
\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Spatio-angular transfer functions for polarized fluorescence microscopes\vspace{-1em}}  \author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
These notes are a continuation of the
\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-02-23-spatio-angular-kernel/report/report.pdf}{2018-02-23
  notes} on the spatio-angular transfer functions for unpolarized fluorescence
microscopes. We will use the same notation and extend those results to microscopes
with polarized illumination and detection.

\section{Polarized illumination}
We can model polarized excitation using a spatio-angular excitation point
response function $h_{\text{exc}}(\ro{}, \so{})$. In these notes we will only
consider spatially uniform excitation patterns $h_{\text{exc}}(\so{})$, but we
would need the full function to model structured illumination patterns.

We calculated several spatio-angular excitation point response functions in our
Optics Express paper \cite{chandler17} (in the paper we called this function the
excitation efficiency for a single dipole, but this is equivalent to the
excitation point spread function). If we place a spatially incoherent and
spatially uniform light source (or its image) in the aperture plane with the
optical axis along the $\mh{z}$ axis, then the excitation point response function
is given by
\begin{align}
  h^{\mh{z}}_{\text{exc}}(\Theta, \Phi; \phi_{\text{exc}}) &= \bar{D}\{\bar{A} + \bar{B}\sin^{2}{\Theta} + \bar{C}\sin^{2}{\Theta} \cos{[2 (\Phi - \phi_{\text{exc}}})]\}\label{eq:scalarabs},
\end{align}
where
$\so{} = \cos\Phi\sin\Theta\mh{x} + \sin\Phi\sin\Theta\mh{y} + \cos\Theta\mh{z}$,
the illumination polarizer orientation is given by $\mh{p} = \cos\phi_{\text{exc}}\mh{x} + \sin\phi_{\text{exc}}\mh{y}$, and 
\begin{subequations}
\begin{align}
  \bar{A} &= \frac{1}{4} - \frac{3}{8} \cos{\alpha } + \frac{1}{8} \cos^{3}{\alpha },\\
  \bar{B} &= \frac{3}{16} \cos{\alpha } - \frac{3}{16} \cos^{3}{\alpha },\\
  \bar{C} &= \frac{7}{32} - \frac{3}{32} \cos{\alpha } - \frac{3}{32} \cos^{2}{\alpha } - \frac{1}{32} \cos^{3}{\alpha},\\
  \bar{D} &= \frac{4}{3(1 - \cos\alpha)},
\end{align}\label{eq:coefficients}%
\end{subequations}
where $\alpha = \arcsin(\text{NA}/n_o)$. I'm using bars on the constants to
avoid notation overlap with the previous note set. We can rewrite this
expression in terms of spherical harmonics as
\begin{align}
  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) \propto\, &[2A + (4/3)B]y_0^0(\so{}) - \frac{4\sqrt{5}}{15}By_2^0(\so{}) + \nonumber\\ &\frac{4C}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}. \label{eq:genpsf}
\end{align}

% We can rewrite this expression in vector 
% notation as
% \begin{align}
% h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= E + F[(\so{}\cdot\mh{x})^2 + (\so{}\cdot\mh{y})] + G\left[\mh{p} \cdot \frac{(\so{}\cdot\mh{x})\mh{x} + (\so{}\cdot\mh{y})\mh{y}}{\sqrt{(\so{}\cdot\mh{x})^2 + (\so{}\cdot\mh{y})^2}}\right]^2,
% \end{align}
% where
% \begin{subequations}
%   \begin{align}
%     E &\equiv DA = \frac{1}{3} - \frac{1}{6}\cos\alpha - \frac{1}{6}\cos^2\alpha,\\
%     F &\equiv D(B-C) = -\frac{7}{24} + \frac{1}{12}\cos\alpha + \frac{5}{24}\cos^2\alpha,\\
%     G &\equiv 2DC = \frac{7}{12} + \frac{1}{3}\cos\alpha + \frac{1}{12}\cos^2\alpha.
%   \end{align}
% \end{subequations}
% Finally, we can rewrite this expression in Cartesian coordinates as 
% \begin{align}
%     h^{\mh{z}}_{\text{exc}}(s_x, s_y; p_x, p_y) &= E + F[s_x^2 + s_y^2] + G\frac{(p_xs_x + p_ys_y)^2}{s_x^2 + s_y^2},
% \end{align}
% where $s_x^2 + s_y^2 + s_z^2 = 1$ and $p_x^2 + p_y^2 + p_z^2= 1$.

The light-sheet excitation point response function is given by Eq.
\ref{eq:genpsf} in the limit of small NA which gives
\begin{align}
  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
\end{align}
To find the excitation point response function for illumination along the
$\mh{x}$ axis we need to change every $\mh{x}$ and $\mh{y}$ to $\mh{z}$ and
$-\mh{y}$, respectively. Rotating the spherical harmonics is not trivial,
but we show the relevant transformation matrix in Appendix \ref{sec:sh}. The
excitation point response function for illumination along the $\mh{x}$ axis is
given by
\begin{align}
  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
\end{align}

To find the excitation transfer functions we need to calculate
\begin{align}
  H_{l, \text{exc}}^m = \int_{\mathbb{S}^2} d\so{}\, h_{\text{exc}}(\so{}) y_l^m(\so{}).
\end{align}
This calculation is straightforward now that we've expressed the excitation
point response functions in terms of spherical harmonics. The excitation
transfer functions are
\begin{align}
  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2A + (4/3)B]\delta(l, m) - \frac{4\sqrt{5}}{15}B\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4C}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right] + (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\right\}.                                                              
\end{align}

\section{Polarized detection}
In the previous note set we found the spatio-angular detection point spread
function for unpolarized fluorescence microscopes. In this section we will find
the spatio-angular detection point spread function when there is a linear
polarizer in the detection path.

The electric field in the back-focal plane of a fluorescence microscope under
the paraxial approximation is given by
\begin{align}
   \mb{\tilde{e}}^{(p)}_b(\rb{};\ro{}, \so{}) \propto
  \begin{bmatrix}
    y_1^1(\so{}) -\frac{2r_b}{f_o}\cos\phi_by_1^0(\so{})\\
    y_1^{-1}(\so{}) -\frac{2r_b}{f_o}\sin\phi_by_1^0(\so{})\\
    0
  \end{bmatrix}.
\end{align}
If we place a polarizer oriented along $\mh{p}_d$ in the back focal plane then
the electric field becomes
\begin{align}
   \mb{\tilde{e}}^{(p)}_b(\rb{};\ro{}, \so{}) \propto \mh{p}_d \cdot
  \begin{bmatrix}
    y_1^1(\so{}) -\frac{2r_b}{f_o}\cos\phi_by_1^0(\so{})\\
    y_1^{-1}(\so{}) -\frac{2r_b}{f_o}\sin\phi_by_1^0(\so{})\\
    0
  \end{bmatrix}.
\end{align}
To find the electric field in the detector plane we need to take the
two-dimensional Fourier transform of each component. The dot product with the
polarizer is linear, so we can pull the Fourier transform inside and use the same
result from the previous notes
\begin{align}
  \tilde{\mb{e}}^{(p)}_d(\rd{}', \so{}; \mh{p}_d) &\propto \mh{p}_d \cdot
  \begin{bmatrix}
    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
    0\\
  \end{bmatrix}\label{eq:paracsf}. 
\end{align}
Finally, we can find the spatio-angular point spread function by taking the
squared modulus of the electric field on the detector.

In progress. Calculate the spatio-angular PSF then the spatio-angular OTF. 
% \begin{equation}
%   \begin{split}
%   h(\rd{}', \so{}; \mh{p}_d) \propto &\left(a^2(r_d') + 2b^2(r_d') + c^2(r_d')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-a^2(r_d') + 4b^2(r_d') - c^2(r_d')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\cos(2\phi_d')y_2^{2}(\so{}). \label{eq:kerna}
% \end{split}
% \end{equation}

\appendix
\section{Rotation of spherical harmonics} \label{sec:sh}
Given a spherical function and its spherical harmonic coefficients $c_j$ (we're
using a single index over the spherical harmonics), the spherical harmonic
coefficients of the rotated function $c'_i$ can be computed with the linear
transformation
\begin{align}
  c_i' = \sum_j M_{ij}c_j, 
\end{align}
where the elements of the linear transformation can be computed with
\begin{align}
  M_{ij} = \int_{\mathbb{S}^2} d\so{}\, y_j(\mathbf{R}\so{})y_i(\so{}), 
\end{align}
where $\mathbf{R}$ is the rotation matrix that maps the original function to the
rotated function \cite{kautz2002}. If we assemble the elements of the linear transformation into
a matrix $\mathbf{M}$, then the matrix is block sparse
\begin{align}
  \mathbf{M} =
  \begin{bmatrix}[c|ccc|cccccc]    
    1&0&0&0&0&0&0&0&0&\cdots\\ \hline
    0&\mathbf{X}&\mathbf{X}&\mathbf{X}&0&0&0&0&0&\cdots\\
    0&\mathbf{X}&\mathbf{X}&\mathbf{X}&0&0&0&0&0&\cdots\\
    0&\mathbf{X}&\mathbf{X}&\mathbf{X}&0&0&0&0&0&\cdots\\ \hline
    0&0&0&0&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\cdots\\
    0&0&0&0&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\cdots\\
    0&0&0&0&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\cdots\\
    0&0&0&0&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\cdots\\
    0&0&0&0&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\mathbf{X}&\cdots\\    
    \vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\ddots\\        
  \end{bmatrix}.
\end{align}
This means the spherical harmonic coefficients from each band transform
independently from the other bands.

To efficiently find the point spread functions and transfer functions for the
diSPIM we will compute the spherical harmonic coefficient transformation matrix
for a rotation that maps the $\mh{z}$ axis to the $\mh{x}$. The rotation matrix is
given by
\begin{align}
  \mb{R}_{\mh{z}\rightarrow\mh{x}} =
  \begin{bmatrix}
    0&0&1\\
    0&1&0\\
    -1&0&0    
  \end{bmatrix}, 
\end{align}
and the spherical harmonic coefficient transformation matrix is given by
\begin{align}
  \mathbf{M}_{\mh{z}\rightarrow\mh{x}} =
  \begin{bmatrix}[c|ccc|cccccc]
    1&0&0&0&0&0&0&0&0&\cdots\\ \hline 
    0&0&0&1&0&0&0&0&0&\cdots\\
    0&0&1&0&0&0&0&0&0&\cdots\\
    0&-1&0&0&0&0&0&0&0&\cdots\\ \hline 
    0&0&0&0&-1/2&0&0&\sqrt{3}/2&0&\cdots\\
    0&0&0&0&0&-1&0&0&0&\cdots\\
    0&0&0&0&0&0&0&0&-1&\cdots\\
    0&0&0&0&\sqrt{3}/{2}&0&0&1/2&0&\cdots\\
    0&0&0&0&0&0&1&0&0&\cdots\\    
    \vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\vdots&\ddots\\        
  \end{bmatrix},
\end{align}
when the matrix elements are ordered as
$[y_0^0 | y_1^1, y_1^{-1}, y_1^0 | y_2^0, y_2^1, y_2^{-1}, y_2^2, y_2^{-2}]$.
For more complicated transformations (higher order coefficients or arbitrary
rotations) we can use recurrence relations to find the spherical harmonic
coefficient transformation matrix \cite{ivanic1996}.

\bibliography{report}{}
\bibliographystyle{unsrt}

\end{document}

### 2018-04-20 notes/2018-04-19-polarizer-otf/calculations/compare-ft.py

@@ -1,0 +1,99 @@
+import numpy as np
+from util import *
+import matplotlib.pyplot as plt
+
+# Setup
+out = 'output/'
+NA = 0.8
+n = 1.33
+n_pixels = 257
+[X, Y] = np.meshgrid(np.linspace(-2, 2, n_pixels),
+                     np.linspace(-2, 2, n_pixels))
+R = np.sqrt(X**2 + Y**2)
+
+# Analytic OTF
+Hxan = (A(R)).astype('float32')
+Hzan = (B(R, NA=NA, n=n)).astype('float32')
+H00an = (H00(R, NA=NA, n=n)).astype('float32')
+H20an = (H20(R, NA=NA, n=n)).astype('float32')
+save_tiff(Hxan, out+'Hxan.tiff')
+save_tiff(Hzan, out+'Hzan.tiff')
+save_tiff(H00an, out+'H00an.tiff')
+save_tiff(H20an, out+'H20an.tiff')
+
+# Analytic PSF
+hhxan = (a(R)).astype('float32')
+hhzan = (b(R, NA=NA, n=n)).astype('float32')
+hh00an = (h00(R, NA=NA, n=n)).astype('float32')
+hh20an = (h20(R, NA=NA, n=n)).astype('float32')
+save_tiff(hhxan, out+'hhxan.tiff')
+save_tiff(hhzan, out+'hhzan.tiff')
+save_tiff(hh00an, out+'hh00an.tiff')
+save_tiff(hh20an, out+'hh20an.tiff')
+
+# Computed PSF
+xF, hhxftraw = myfft(Hxan)
+xF, hhzftraw = myfft(Hzan)
+xF, hh00ftraw = myfft(H00an)
+xF, hh20ftraw = myfft(H20an)
+
+hhxft = hhxftraw/np.max(hhxftraw)
+hhzft = hhzftraw/np.max(hhxftraw)
+hh00ft = hh00ftraw/np.max(hh00ftraw)
+hh20ft = hh20ftraw/np.max(hh00ftraw)
+
+save_tiff(hhxft, out+'hhxft.tiff')
+save_tiff(hhzft, out+'hhzft.tiff')
+save_tiff(hh00ft, out+'hh00ft.tiff')
+save_tiff(hh20ft, out+'hh20ft.tiff')
+
[…]

### 2018-04-20 notes/2018-04-19-polarizer-otf/calculations/rotation.py

@@ -1,0 +1,47 @@
+import numpy as np
+from mpmath import *
+from sympy import *
+from sympy.matrices.dense import *
+import functools
+
+# Analytical spherical fourier transform
+import sympy.functions.special.spherical_harmonics as sh
+def sft(f, max_l=4, odd_l=False):
+    coeffs = []
+    for l in range(0 + odd_l, max_l+2, 2):
+        for m in range(-l, l+1):
+            print("Integrating: "+ str(l) + ', ' + str(m))
+            Znm = sh.Znm(l, m, theta, phi).expand(func=True)
+            Znm = simplify(Znm) # Try this
+            import pdb; pdb.set_trace() 
+            theta_int = integrate(expand_trig(sin(theta)*Znm*f), (theta, 0, pi))
+            final_int = integrate(expand_trig(theta_int.rewrite(cos)), (phi, 0, 2*pi))
+            print(simplify(final_int))
+            coeffs.append(final_int)
+    return np.array(coeffs)
+
+# Polar fourier transform
+
+print("Working...")
+
+# Symbols
+# Theta = Symbol('Theta')
+# Phi = Symbol('Phi')
+theta = Symbol('theta')
+phi = Symbol('phi', real=True)
+x = Symbol('x', real=True)
+y = Symbol('y', real=True)
+z = Symbol('z', real=True)
+
+
+s = Matrix([cos(phi)*sin(theta), sin(phi)*sin(theta), cos(theta)])
+R = Matrix([[0, 0, 1], [0, 1, 0], [-1, 0, 0]])
+sp = R*s
+thetap = acos(sp[2])
+phip = atan(sp[1]/sp[0])
+import pdb; pdb.set_trace() 
+
+# Calculate intensity
+I0  = simplify(sh.Znm(1, 1, thetap, phip).expand(func=True))
+# Expand onto spherical harmonics
+x = sft(I0, max_l=2, odd_l=False)

### 2018-04-20 notes/2018-04-19-polarizer-otf/calculations/util.py

@@ -1,0 +1,68 @@
+import numpy as np
+from PIL import Image
+from scipy import special
+
+# PSF functions
+def scalar_a(x):
+    if x == 0:
+        return 1.0
+    else:
+        return (special.jn(1,2*np.pi*x)/(np.pi*x))**2
+a = np.vectorize(scalar_a)
+
+def s_b(x, NA=0.8, n=1.33):
+    if x == 0:
+        return 0
+    else:
+        return (NA/n)**2*(special.jn(2,2*np.pi*x)/(np.pi*x))**2
+b = np.vectorize(s_b)
+
+def h00(x, NA=0.8, n=1.33):
+   return a(x) + 2*b(x, NA, n)
+
+def h20(x, NA=0.8, n=1.33):
+   return (-a(x) + 4*b(x, NA, n))/np.sqrt(5)
+
+# OTF functions
+def myacos(x):
+    return np.nan_to_num(np.arccos(np.abs(x/2)))
+    
+def mysqrt(x):
+    return np.nan_to_num((np.abs(x/2))*np.sqrt(1 - (np.abs(x/2))**2))
+    
+def A(x):
+    return (2/np.pi)*(myacos(x) - mysqrt(x))
+
+def B(x, NA=0.8, n=1.33):
+    N = (1/(np.pi))*((NA/n)**2)
+    poly = (3.0 - 2.0*(np.abs(x/2)**2))
+    return N*(myacos(x) - poly*mysqrt(x))
+
+def H00(x, NA=0.8, n=1.33):
+    return (A(x) + 2*B(x, NA=NA, n=n))/(1 + (NA/n)**2)
+
+def H20(x, NA=0.8, n=1.33):
+    return (-A(x) + 4*B(x, NA=NA, n=n))/(np.sqrt(5)*(1 + (NA/n)**2))
+
+# File I/O
+def save_tiff(image, filename):
+    im = Image.fromarray(image) # float32
+    im.save(filename, "TIFF")
+
+def load_tiff(filename):
+    image = Image.open(filename, mode='r')
+    return np.array(image, dtype='float32')
+
+def cs(arr):
+    return arr[:, np.int(arr.shape[0]/2)]
+
+# Fourier transform
+def myfft(image, pad=1000):
+    N = image.shape[0]
+    padded_image = np.pad(image, pad_width=pad, mode='constant')
+    F = np.fft.fftshift(
+        np.fft.fftn(
[…]

### 2018-04-23 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Change to object scale coordinates; Patrick's Apr 20 edits.

@@
 \end{align}
-and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0$ and $l=1$
+and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0, 1, 2$
 spherical harmonics are given by
-\begin{equation}
-\begin{aligned}
-  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}},\\
-  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta.
-\label{eq:harmonics}
-\end{aligned}
-\end{equation}
+\begin{align}
+  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}}, \nonumber \\ 
+  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta, \nonumber \\
+  y_2^{-2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\cos\varphi\sin^2\vartheta, &\hspace{2em} y_2^{-1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\sin\vartheta\cos\vartheta,\nonumber \\
+  y_2^0(\vartheta, \varphi) &= \sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1), \nonumber \\ 
+  y_2^{1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\cos\varphi\sin\vartheta\cos\vartheta, &\hspace{2em} y_2^{2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}(\cos^2\varphi - \sin^2\varphi)\sin^2\vartheta.\label{eq:harmonics}
+\end{align}
 
@@
 \begin{align}
-  \mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) \propto \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}\sqrt{\frac{1}{\rho_b}}
-  \begin{bmatrix}
+  \mb{\tilde{e}}_b(\rb{};\ro{}, \so{}) \propto\, &\me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}\sqrt{\frac{1}{\rho_b}} \times \nonumber \\
+  &\begin{bmatrix}
     \sin^2\phi_b + \rho_b\cos^2\phi_b&\sin\phi_b\cos\phi_b(\rho_b - 1)&-\frac{r_b}{f_o}\cos\phi_b\\
@@
 can understand this expression term by term---the exponential term accounts for
-the phase as dipole emitter is moved in object space, the square root term
+the phase as the dipole emitter is moved in object space, the square root term
 conserves power before and after the objective lens, the matrix models the
@@
 \end{align}
-where $M = -\frac{n_o}{n_t}\frac{f_t}{f_o}$ is the transverse magnification.  By
-writing the electric field in the detector plane in terms of $\rd{} - M\ro{}$,
-we have established that the electric field in the detector plane is
-\textit{transverse shift-invariant}---a transverse shift of the object creates a
-magnified transverse shift of the image. We define coordinates on the detector
-centered on the image of the object
-$\rd{}' \equiv \rd{} - M\ro{} = r_d'\cos\phi_d'\mh{x} + r_d'\sin\phi_d'\mh{y}$,
-then we follow Novotny \cite{nov2006} by writing the integrals in polar
+where $M = -\frac{n_o}{n_t}\frac{f_t}{f_o}$ is the transverse magnification.
+
+By writing the electric field in the detector plane in terms of
+$\rd{} - M\ro{}$, we have established that the imaging system magnifies and
+applies a shift-invariant blur to the electric field. We can rewrite this system
+as a linear shift invariant system by following Barrett section 7.2.7
+\cite{barrett2004}. We scale the image
+$\tilde{\mb{e}}_d'(\rd{}, \so{}) \equiv \tilde{\mb{e}}_d(M\rd{}, \so{})$ and its
+coordinates $\rd{}' \equiv \rd{}/M$ so that all length scales are measured in
+object space. With these definitions we can write the electric field on the
+detector as $\tilde{\mb{e}}_d'(\rd{}' - \ro{})$ which is a linear shift
+invariant point response function. We will continue to use a prime to denote
+quantities that have been demagnified into object space.
+
+We define a convenient set of coordinates centered on the object and scaled to
+object space
+$\ro{}' \equiv \rd{}' - \ro{} = r_o'\cos\phi_o'\mh{x} + r_o'\sin\phi_o'\mh{y}$.
+Next, we follow Novotny \cite{nov2006} by writing the integrals in polar
 coordinates, evaluating the azimuthal integrals, and writing the result
@@
 \begin{align}
-  \tilde{\mb{e}}_d(\rd{}', \so{}) &\propto
-  \begin{bmatrix}
-    a(r_d') + c(r_d')\cos(2\phi_d') & c(r_d')\sin(2\phi_d') & 2ib(r_d')\cos\phi_d'\\
-    c(r_d')\sin(2\phi_d') & a(r_d') - c(r_d')\cos(2\phi_d') & 2ib(r_d')\sin\phi_d'\\
+  \tilde{\mb{e}}'_d(\ro{}', \so{}) &\propto
+  \begin{bmatrix}
+    a(r_o') + c(r_o')\cos(2\phi_o') & c(r_o')\sin(2\phi_o') & 2ib(r_o')\cos\phi_o'\\
+    c(r_o')\sin(2\phi_o') & a(r_o') - c(r_o')\cos(2\phi_o') & 2ib(r_o')\sin\phi_o'\\
     0&0&0\\
@@
 \end{align}
-where $a(r_d'), b(r_d')$, and $c(r_d')$ are
-\begin{align}
-  a(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  b(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_d'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
-  c(r_d') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_d'\sin\theta f_o/f_t).%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
+where $a(r_o'), b(r_o')$, and $c(r_o')$ are
+\begin{align}
+  a(r_o') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1+\cos\theta)J_0(k_b r_o'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  b(r_o') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin^2\theta J_1(k_b r_o'\sin\theta f_o/f_t),\\%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\},\\
+  c(r_o') &= \int_0^{\theta_{\text{max}}}d\theta\ \sqrt{\cos\theta}\sin\theta(1-\cos\theta)J_2(k_b r_o'\sin\theta f_o/f_t).%\ \text{exp}\left\{ik_bz_o[1-(1/2)(f_o/f_t)^2\sin^2\theta]\right\}.
 \end{align}
@@
 \begin{align}
-  \tilde{\mb{e}}_d(\rd{}', \so{}) &\propto
-  \begin{bmatrix}
-    [a(r_d') + c(r_d')\cos(2\phi_d')]y_1^{1}(\so{}) + c(r_d')\sin(2\phi_d')y_1^{-1}(\so{}) + 2ib(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    c(r_d')\sin(2\phi_d')y_1^{1}(\so{}) + [a(r_d') - c(r_d')\cos(2\phi_d')]y_1^{-1}(\so{}) + 2ib(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+  \tilde{\mb{e}}'_d(\ro{}', \so{}) &\propto
+  \begin{bmatrix}
+    [a(r_o') + c(r_o')\cos(2\phi_o')]y_1^{1}(\so{}) + c(r_o')\sin(2\phi_o')y_1^{-1}(\so{}) + 2ib(r_o')\cos\phi_o'y_1^{0}(\so{})\\
+    c(r_o')\sin(2\phi_o')y_1^{1}(\so{}) + [a(r_o') - c(r_o')\cos(2\phi_o')]y_1^{-1}(\so{}) + 2ib(r_o')\sin\phi_o'y_1^{0}(\so{})\\
     0\\
@@
 By applying the paraxial approximation ($\sin\theta\approx\theta$ and
-$\cos\theta\approx 1$), the integrals $a(r_d'), b(r_d')$ and $c(r_d')$ can be
-evaluated in terms of Bessel functions. We can evaluate $a(r_d')$ and $b(r_d')$ with the
+$\cos\theta\approx 1$), the integrals $a(r_o'), b(r_o')$ and $c(r_o')$ can be
+evaluated in terms of Bessel functions. We can evaluate $a(r_o')$ and $b(r_o')$ with the
 help of $\int_0^zdx\ xJ_0(ax) = zJ_1(az)/a$ and
-$\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $c(r_d') = 0$ because
+$\int_0^zdx\ x^2J_1(ax) = z^2J_2(az)/a$, respectively, and $c(r_o') = 0$ because
 $J_2(x)$ is zero to first order. In this case, the CSF simplifies to
 \begin{align}
-  \tilde{\mb{e}}^{(p)}_d(\rd{}', \so{}) &\propto
-  \begin{bmatrix}
-    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+  \tilde{\mb{e}}'^{(p)}_d(\ro{}', \so{}) &\propto
+  \begin{bmatrix}
+    a^{(p)}(r_o')y_1^{1}(\so{}) + 2ib^{(p)}(r_o')\cos\phi_o'y_1^{0}(\so{})\\
+    a^{(p)}(r_o')y_1^{-1}(\so{}) + 2ib^{(p)}(r_o')\sin\phi_o'y_1^{0}(\so{})\\
     0\\
@@
 \begin{align}
-  {a^{(p)}}(r_d') = \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}, 
+  {a^{(p)}}(r_o') = \frac{J_1(2\pi \nu_or_o')}{\pi \nu_or_o'}, 
   &\hspace{2em}
-    {b^{(p)}}(r_d') = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right],  \label{eq:abparadef}
+    {b^{(p)}}(r_o') = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o')}{\pi \nu_or_o'}\right],  \label{eq:abparadef}
   \intertext{and we have substituted}
-  \nu_o \equiv \frac{\text{NA}}{M\lambda},&\hspace{2em}
+  \nu_o \equiv \frac{\text{NA}}{\lambda},&\hspace{2em}
   \text{NA} \equiv n_o\sin\theta_{\text{max}}.
@@
 Under the paraxial approximation the electric fields on the detector created by
-a single dipole are composed of two parts, a parallel part and a radial
-part. The coefficients of the $y_1^0$ spherical harmonic in Eq. \ref{eq:paracsf}
+a single dipole are composed of two parts, a parallel part and a radial part.
+The coefficients of the $y_1^0$ spherical harmonic in Eq. \ref{eq:paracsf}
 create the radial part of the field---the $z$ component of the dipole generates
@@
 of the $y_1^1$ and $y_1^{-1}$ spherical harmonics create a parallel field in the
-detector plane parallel to the $x$ and $y$ components of the
-dipole. As the NA increases and the paraxial approximation no longer applies, we
-begin to see coupling between the $x$ and $y$ components of the dipole with the $y$ and $x$ transverse fields, respectively.
+detector plane parallel to the $x$ and $y$ components of the dipole. As the NA
+increases and the paraxial approximation no longer applies, we begin to see the
+$x$ and $y$ components of the dipole contribute to the $y$ and $x$ transverse
+fields, respectively.
 
@@
 \begin{align}
-  h(\rd{}', \so{}) = \left|\tilde{\mb{e}}_d(\rd{}', \so{})\right|^2 \label{eq:kernel}.
+  h'(\ro{}', \so{}) = \left|\tilde{\mb{e}}'_d(\ro{}', \so{})\right|^2 \label{eq:kernel}.
 \end{align}
@@
   \begin{split}
-  h(\rd{}', \so{}) \propto &\left(a^2(r_d') + 2b^2(r_d') + c^2(r_d')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\sin(2\phi_d')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-a^2(r_d') + 4b^2(r_d') - c^2(r_d')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}a(r_d')c(r_d')\cos(2\phi_d')y_2^{2}(\so{}).
+  h'(\ro{}', \so{}) \propto &\left(a^2(r_o') + 2b^2(r_o') + c^2(r_o')\right)y_0^0(\so{}) -\frac{2\sqrt{15}}{5}a(r_o')c(r_o')\sin(2\phi_o')y_2^{-2}(\so{})\\ &+ \frac{1}{\sqrt{5}}\left(-a^2(r_o') + 4b^2(r_o') - c^2(r_o')\right)y_2^{0}(\so{}) +\frac{2\sqrt{15}}{5}a(r_o')c(r_o')\cos(2\phi_o')y_2^{2}(\so{}).
 \label{eq:kerna}
@@
 \begin{align}
-      h^{(p)}(\rd{}', \so{}) \propto \left({a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{a^{(p)}}^2(r_d') + {4b^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
+      h'^{(p)}(\ro{}', \so{}) \propto \left({a^{(p)}}^2(r_o') + 2{b^{(p)}}^2(r_o')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{a^{(p)}}^2(r_o') + {4b^{(p)}}^2(r_o')\right)y_2^{0}(\so{})\label{eq:para}.
 \end{align}
@@
 \begin{align}
-  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}),\\
-  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
-  {h_2^0}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right]. \label{eq:concisepsf}
+  h'^{(p)}(\ro{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}), \label{eq:concisepsf}\\
+  {{h'}_0^0}^{(p)}(\ro{}') &\equiv {a^{(p)}}^2(r_o') + 2{b^{(p)}}^2(r_o'),\\
+  {{h'}_2^0}^{(p)}(\ro{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_o') + 4{b^{(p)}}^2(r_o')\right]. 
 \end{align}
@@
 uniform distribution of fluorophores. The first term of the coefficient
-${A^{(p)}}^2(r_d')$ is the familiar Airy disk that arises from the contribution
+${a^{(p)}}^2(r_o')$ is the familiar Airy disk that arises from the contribution
 of dipoles oriented in the transverse plane, while the second term
-${B^{(p)}}^2(r_d')$ is a smaller factor that arises from dipoles oriented
+${b^{(p)}}^2(r_o')$ is a smaller factor that arises from dipoles oriented
 outside of the transverse plane. This leads to an interesting conclusion---a
@@
 any positive fluorophore distribution can be represented by the spherical
-harmonics and we never need to consider negative fluorophores.
+harmonics, and we never need to consider negative fluorophores.
 
@@
 \begin{align}
-  \mb{e}_d(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{}).\label{eq:eforward}
+  \mb{e}'_d(\rd{}')  \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}_d'(\rd{}' - \mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{}).\label{eq:eforward}
 \end{align}
@@
 
-We can simplify this expression by expanding the CSF in terms of spatio-angular
+We can simplify this expression by expanding the object in terms of spatio-angular
 harmonics
 \begin{align}
-  \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}},\label{eq:csfexp}
-\end{align}
-where $\mb{E}_l^m(\bs{\nu})$ is the spatio-angular spectrum of the CSF given
-by
-\begin{align}
-  \mb{E}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}.\label{eq:csfdef}
-\end{align}
-We can change variables to make this expression easier to evaluate
-\begin{align}
-  \mb{E}_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \tilde{\mb{e}}_d(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:csfdef2}
-\end{align}
-By plugging Eq. \ref{eq:csfexp} into Eq. \ref{eq:eforward} we find that
-\begin{align}
-  \mb{e}_d(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}\right]\bs{\mu}(\ro{}, \so{}).
+  \bs{\mu}(\ro{}, \so{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{M}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}},
+\end{align}
+where
+\begin{align}
+\mb{M}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}}. \label{eq:objspectrum}
+\end{align}
+By plugging Eq. \ref{eq:objspectrum} into Eq. \ref{eq:eforward} we find that 
+\begin{align}
+  \mb{e}'_d(\rd{}')  \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\,  \tilde{\mb{e}}'_d(\rd{}' - \mb{r}_o, \so{})\left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{M}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}}\right].
+\end{align}
+We can rearrange this equation into the following form
+\begin{align}
+    \mb{e}'_d(\rd{}') \propto \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{M}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\,  \tilde{\mb{e}}'_d(\rd{}' - \mb{r}_o, \so{})\, \me^{i 2\pi \ro{}\cdot\bs{\nu}}\right].\label{eq:ctfpre}
+\end{align}
+We can simplify the term in square brackets by introducing 
+\begin{align}
+  \mb{E}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}'\, \tilde{\mb{e}}'_d(\ro{}', \mh{s}) y_l^m(\mh{s})\thinspace\me^{-i 2\pi \ro{}'\cdot\bs{\nu}}. \label{eq:ctf}
+\end{align}
+By applying a change of variable $\mb{r}'_o \rightarrow \rd{}' - \ro{}$ then plugging Eq.
+\ref{eq:ctf} into Eq. \ref{eq:ctfpre} we find that 
+\begin{align}
+    \mb{e}'_d(\rd{}') \propto \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})\mb{M}_l^m(\bs{\nu})y_l^m(\so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:forwardelec}
+\end{align}
+
+% \begin{align}
+%   \tilde{\mb{e}}_d(\rd{}', \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi \rd{}'\cdot\bs{\nu}},\label{eq:csfexp}
+% \end{align}
+% where $\mb{E}_l^m(\bs{\nu})$ is the spatio-angular spectrum of the CSF given
+% by
+% \begin{align}
+%   \mb{E}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \tilde{\mb{e}}_d(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:csfdef2}
+% \end{align}
+% By plugging Eq. \ref{eq:csfexp} into Eq. \ref{eq:eforward} we find that
+% \begin{align}
+%   \mb{e}_d(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}\right]\bs{\mu}(\ro{}, \so{}).
 \label{eq:freqforward}
-\end{align}
-We can rearrange this equation into the following form
-\begin{align}
-  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \bs{\mu}(\ro{}, \so{})y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}.
+% \end{align}
+% We can rearrange this equation into the following form
+% \begin{align}
+%   \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \bs{\mu}(\ro{}, \so{})y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}.
 \label{eq:freqforward}
-\end{align}
-We recognize the term in square brackets as the spatio-angular spectrum of the
-object, so we define
-\begin{align}
-\mb{M}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  
-\end{align}
-and write the electric field on the detector as
-\begin{align}
-  \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \mb{M}_l^m(\mb{\nu}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforward}
-\end{align}
-Eq. \ref{eq:freqforward} shows that the electric field on the detector can be
+% \end{align}
+% We recognize the term in square brackets as the spatio-angular spectrum of the
+% object, so we define
+% \begin{align}
+% \mb{M}_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, \bs{\mu}(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  
+% \end{align}
+% and write the electric field on the detector as
+% \begin{align}
+%   \mb{e}_d(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, \mb{E}_l^m(\bs{\nu}) \mb{M}_l^m(\mb{\nu}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforward}
+% \end{align}
+Eq. \ref{eq:forwardelec} shows that the electric field on the detector can be
 found by resolving the object into its spatio-angular components
-$\mb{M}_l^m(\bs{\nu})$, weighting each component by $\mb{E}_l^m(\bs{\nu})$,
-then summing over all spatio-angular components. Therefore, we identify
-$\mb{E}_l^m(\bs{\nu})$ as the spatio-angular \textit{coherent transfer
+$\mb{M}_l^m(\bs{\nu})$, weighting each component by $\mb{E}_l^m(\bs{\nu})$, then
+summing over the spatio-angular components. Therefore, we
+identify $\mb{E}_l^m(\bs{\nu})$ as the spatio-angular \textit{coherent transfer
   function} (CTF).
 
-In Appendix \ref{paraxialctf} we calculate the paraxial CTF for a single-view fluorescence microscope as 
+In Appendix \ref{paraxialctf} we calculate the paraxial CTF for a single-view
+fluorescence microscope as
 \begin{align}
@@
 The spatial band limit can be increased by increasing the NA of the microscope,
-so what parameter sets the angular band limit? The angular band limit in the
-current microscope is set by the dipole emission process---only $l=1$ terms show
-up in the CTF for dipole emitters. Adding polarizing filters to the microscope
-will not extend the band limit of the microscope because filters only block
-electric fields. However, polarized illumination can be used to extend the band
-limit. The excitation process is completely incoherent with the emission
-process, so the spatio-angular transfer functions of the two processes will
-multiply. We can use the multiplication rules in Appendix \ref{realspherical} to
-find the band limit of a new microscope that uses selective excitation.
-
-Next we find the intensity on the detector plane $g(\rd{})$ by taking the
-modulus squared of the electric field. Using Eq. \ref{eq:eforward} we find that
-\begin{align}
-  g(\rd{}) = |\mb{e}_d(\rd{})|^2 = \left|\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{})\right|^2. 
+so what parameter sets the coherent angular band limit? The coherent angular
+band limit in the current microscope is set by the dipole emission
+process---only $l=1$ terms show up in the CTF for dipole emitters. Adding
+polarizing filters to the microscope will not extend the coherent band limit of
+the microscope because filters only block electric fields. However, polarized
+illumination can be used to extend the band limit. The excitation process is
+completely incoherent with the emission process, so the spatio-angular transfer
+functions of the two processes will multiply. We can use the multiplication
+rules in Appendix \ref{realspherical} to find the band limit of a new microscope
+that uses selective excitation.
+
+Next we find the intensity on the detector plane in object coordinates
+$g'(\rd{}')$ by taking the modulus squared of the electric field. Using Eq.
+\ref{eq:eforward} we find that
+\begin{align}
+  g'(\rd{}') = |\mb{e}'_d(\rd{})|^2 \propto \left|\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \tilde{\mb{e}}'_d(\rd{}' - \mb{r}_o, \so{})\bs{\mu}(\ro{}, \so{})\right|^2. 
 \end{align}
@@
 \begin{align}
-  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \left|\tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\right|^2\left|\bs{\mu}(\ro{}, \so{})\right|^2. 
-\end{align}
-We recognize that $\left|\tilde{\mb{e}}_d(\rd{} - M\mb{r}_o, \so{})\right|^2$ is
-the PSF of the microscope $h(\rd{} - M\mb{r}_o, \so{})$, and
+  g'(\rd{}') \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ \left|\tilde{\mb{e}}'_d(\rd{}' - \mb{r}_o, \so{})\right|^2\left|\bs{\mu}(\ro{}, \so{})\right|^2. 
+\end{align}
+We recognize that $\left|\tilde{\mb{e}}'_d(\rd{}' - \mb{r}_o, \so{})\right|^2$ is
+the PSF of the microscope which we denote $h'(\rd{}' - \mb{r}_o, \so{})$, and
 we introduce a new function
@@
 \begin{align}
-  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ h(\rd{} - M\mb{r}_o, \so{})f(\ro{}, \so{}).\label{eq:forwardint}
+  g'(\rd{}') \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \ h'(\rd{}' - \mb{r}_o, \so{})f(\ro{}, \so{}).\label{eq:forwardint}
 \end{align}
@@
 $\ro{}$ oriented in direction $\so{}$ per unit volume per unit solid angle. Notice
-that $h$ and $f$ are scalar functions---we removed all phase information when we took
+that $h'$ and $f$ are scalar functions---we removed all phase information when we took
 the modulus squared.
@@
 We can follow our previous work with the electric field and simplify Eq.
-\ref{eq:forwardint} by expanding the PSF in terms of spatio-angular harmonics
-\begin{align}
-  h(\rd{} - M\mb{r}_o, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}},\label{eq:ctfexp}
-\end{align}
-where $H_l^m(\bs{\nu})$ is the spatio-angular spectrum of the PSF given
-by
-\begin{align}
-  H_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, h(\rd{} - M\ro{}, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}.\label{eq:ctfdef}
-\end{align}
-We can change variables to make this expression easier to evaluate
-\begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:otfdef2}
+\ref{eq:forwardint} by expanding the object in terms of spatio-angular harmonics
+\begin{align}
+  f(\ro{}, \so{}) &= \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, F_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}},\label{eq:ctfexp}
+\end{align}
+where 
+\begin{align}
+  F_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, f(\ro{}, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}\cdot\bs{\nu}}.\label{eq:ctfdef}
 \end{align}
@@
 \begin{align}
-  g(\rd{}) = \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, \left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi (\rd{} - M\ro{})\cdot\bs{\nu}}\right]f(\ro{}, \so{}).
+  g'(\rd{}') \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, h'(\rd{}' - \ro{}, \so{})\left[\sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, F_l^m(\bs{\nu})y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}}\right].
 \label{eq:freqforwardint}
@@
 \begin{align}
-  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, f(\ro{}, \so{})y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}.
-\label{eq:freqforward}
-\end{align}
-We recognize the term in square brackets as the spatio-angular spectrum of the
-object, so we define
-\begin{align}
-F_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{} \, f(\mb{r}_o, \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi M\ro{}\cdot\bs{\nu}}.  \label{eq:saspect}
-\end{align}
-and write the intensity on the detector as
-\begin{align}
-  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) F_l^m(\mb{\nu}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
-\end{align}
-Eq. \ref{eq:freqforwardint} shows that the intensity on the detector can be
-found by resolving the object into its spatio-angular component
-$F_l^m(\mb{\nu}_o)$, weighting each component by $H_l^m(\mb{\nu}_o)$, then
+  g'(\rd{}') = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, F_l^m(\bs{\nu}) \left[\int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}\, h'(\rd{}' - \ro{}, \so{})y_l^m(\so{})\thinspace\me^{i 2\pi \ro{}\cdot\bs{\nu}}\right].
+\label{eq:otfpre}
+\end{align}
+We can simplify the term in square brackets by introducing 
+\begin{align}
+  H_l^m(\bs{\nu}) \equiv \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}'\, h'(\ro{}', \mh{s}) y_l^m(\mh{s})\thinspace\me^{-i 2\pi \ro{}'\cdot\bs{\nu}}. \label{eq:otf}
+\end{align}
+By applying a change of variable $\mb{r}_o' \rightarrow \rd{}' - \ro{}$ then plugging Eq.
+\ref{eq:otf} into Eq. \ref{eq:otfpre} we find that 
+\begin{align}
+    g'(\rd{}') \propto \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu})F_l^m(\bs{\nu})y_l^m(\so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:forwardintensity}
+\end{align}
+Eq. \ref{eq:forwardintensity} shows that the intensity on the detector can be
+found by resolving the object into its spatio-angular components
+$F_l^m(\bs{\nu})$, weighting each component by $H_l^m(\bs{\nu})$, then
 summing over all spatio-angular components. Therefore, we identify
-$H_l^m(\mb{\nu}_o)$ as the spatio-angular \textit{optical transfer function}
+$H_l^m(\bs{\nu})$ as the spatio-angular \textit{optical transfer function}
 (OTF). Notice that the CSF and CTF are vector-valued functions, while the PSF
@@
 \end{align}
-
 Notice that the paraxial OTF is rotationally symmetric, so we can write in terms
@@
 this difference as an electromagnetic correction to the scalar OTF. The
-correction is proportional to $\left(\text{NA}/{n_o}\right)^2$, so it is a small term
-for all but high NA objectives.
+correction is proportional to $\left(\text{NA}/{n_o}\right)^2$, so it is largest
+for high NA objectives.
 
@@
 of fluorophores. As an example, let's derive the spatial OTF for a $z$-oriented
-fluorophore. The object is $f(\ro{}, \so{}) = \delta(\ro{})\delta(\so{} - \mh{z})$. We can calculate
-the angular spectrum of the object as
-$F_l^m(\bs{\nu}) = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \delta(\so{} - \mh{z})y_l^m(\so{})\me{}^{-i2\pi M\ro{}\cdot\bs{\nu}} =
-y_l^m(\mh{z})$. Finally, we can plug in the angular spectrum
-into equation \ref{eq:freqforwardint}
-\begin{align}
-  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) y_l^m(\mh{z}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}, \label{eq:freqforwardint}
+fluorophore at the origin. The object is
+$f(\ro{}, \so{}) = \delta(\ro{})\delta(\so{} - \mh{z})$. We can calculate the
+spatio-angular spectrum of the object as
+$F_l^m(\bs{\nu}) = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{}
+\delta(\so{} - \mh{z})y_l^m(\so{})\me{}^{-i2\pi \ro{}\cdot\bs{\nu}} =
+y_l^m(\mh{z})$. Finally, we can plug the spatio-angular spectrum into equation
+\ref{eq:forwardintensity}
+\begin{align}
+  g'(\rd{}') \propto \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) y_l^m(\mh{z}) \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}, 
 \end{align}
@@
 \begin{align}
-  g(\rd{}) \propto \int_{\mathbb{R}^2}d\nu{}\, \left[H_0^0(\nu)y_0^0(\mh{z}) + H_2^0(\bs{\nu})y_2^0(\mh{z})\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
-\end{align}
-So the spatial OTF for a $z$ oriented dipole is given by
-\begin{align}
-  H_z^{(p)}(\nu) &\propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu), \\
+  g'(\rd{}') \propto \int_{\mathbb{R}^2}d\nu{}\, \left[H_0^0(\nu)y_0^0(\mh{z}) + H_2^0(\bs{\nu})y_2^0(\mh{z})\right] \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}. 
+\end{align}
+So the paraxial spatio-angular OTF for a $z$ oriented dipole is given by
+\begin{align}
+  H_z^{(p)}(\nu) &\propto \sqrt{\frac{1}{4\pi}}{H_0^0}^{(p)}(\nu) + \sqrt{\frac{5}{4\pi}}{H_2^0}^{(p)}(\nu), \\ \label{eq:otfz}
     H_z^{(p)}(\nu) &= \frac{1}{2}\left(\frac{n_o}{\text{NA}}\right) B^{(p)}(\nu).
@@
 The most important result is that the spatial OTF for \textbf{any} dipole
-distribution is a linear combination of just two OTFs---one for each spherical
-harmonic. The same is true for the PSFs---the PSF for any dipole
-distribution is a linear combination of just two PSFs.
-
-Fig. \ref{fig:para} shows four important paraxial PSFs and OTFs for a microscope
-with $\text{NA}=0.8$ and $n=1.33$. Notice that the OTF for $z$-oriented
-dipoles is negative at high frequencies. An OTF that crosses zero will give a
-contrast inversion in a Siemens star test target. The negative OTF is a direct
-consequence of the donut-shaped point spread function. If we arranged a pattern
-of $z$-oriented dipoles with a sinusoid spatial frequency near the cutoff
-frequency, the regions of low intensity would report the positions of the
-fluorophores.
+distribution is a linear combination of the two terms in the spatio-angular OTF.
+
+We can perform an similar calculation to find the PSF for a $z$-oriented dipole.
+As we would expect from Eq. \ref{eq:otfz}, the PSF for a $z$-oriented dipole
+is given by
+\begin{align}
+  h_z^{(p)}(r_o') &\propto \sqrt{\frac{1}{4\pi}}{h_0^0}^{(p)}(r_o') + \sqrt{\frac{5}{4\pi}}{h_2^0}^{(p)}(r_o'), \\ \label{eq:psfz}
+  h_z^{(p)}(r_o') &= \frac{1}{2}\left(\frac{n_o}{\text{NA}}\right) b^{(p)}(r_o').
+\end{align}
+The PSF for \textbf{any} dipole distribution is a linear combination of the two terms in
+the spatio-angular PSF.
+
+In Fig. \ref{fig:para} we plot four important terms of the paraxial PSF and OTF
+for a microscope with $\text{NA}=0.8$ and $n=1.33$. Notice that the OTF for
+$z$-oriented dipoles is negative at high frequencies. An OTF that crosses zero
+will give a contrast inversion in a Siemens star test target. The negative OTF
+is a direct consequence of the donut-shaped point spread function. If we
+arranged a pattern of $z$-oriented dipoles with a sinusoid spatial frequency
+near the cutoff frequency, the regions of low intensity would report the
+positions of the fluorophores.
 
@@
 \begin{align}
-y_2^{-2}y_2^{-2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} - \frac{\sqrt{35}}{14 }y_4^{4} \\
-y_2^{-2}y_2^{-1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{1} + \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
-y_2^{-2}y_2^{0}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{-2} + \frac{\sqrt{15}}{14 }y_4^{-2} \\
-y_2^{-2}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} - \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
-y_2^{-2}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{35}}{14 }y_4^{-4} \\
-y_2^{-1}y_2^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} - \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} - \frac{\sqrt{5}}{7 }y_4^{2} \\
-y_2^{-1}y_2^{0}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{-1} + \frac{\sqrt{30}}{14 }y_4^{-1} \\
-y_2^{-1}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-2} - \frac{\sqrt{5}}{7 }y_4^{-2} \\
-y_2^{-1}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} \\
-y_2^{0}y_2^{0}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{7 }y_2^{0} + \frac{3}{7 }y_4^{0} \\
-y_2^{0}y_2^{1}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{1} + \frac{\sqrt{30}}{14 }y_4^{1} \\
-y_2^{0}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{2} + \frac{\sqrt{15}}{14 }y_4^{2} \\
-y_2^{1}y_2^{1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} + \frac{\sqrt{5}}{7 }y_4^{2} \\
-y_2^{1}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{15}}{14 }y_2^{1} - \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} \\
-y_2^{2}y_2^{2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + \frac{\sqrt{35}}{14 }y_4^{4}
+y_2^{-2}y_2^{-2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} - \frac{\sqrt{35}}{14 }y_4^{4} ,\\
+y_2^{-2}y_2^{-1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{1} + \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} ,\\
+y_2^{-2}y_2^{0}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{-2} + \frac{\sqrt{15}}{14 }y_4^{-2} ,\\
+y_2^{-2}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} - \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} ,\\
+y_2^{-2}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{35}}{14 }y_4^{-4} ,\\
+y_2^{-1}y_2^{-1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} - \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} - \frac{\sqrt{5}}{7 }y_4^{2} ,\\
+y_2^{-1}y_2^{0}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{-1} + \frac{\sqrt{30}}{14 }y_4^{-1} ,\\
+y_2^{-1}y_2^{1}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-2} - \frac{\sqrt{5}}{7 }y_4^{-2} ,\\
+y_2^{-1}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{15}}{14 }y_2^{-1} + \frac{\sqrt{70}}{28 }y_4^{-3} + \frac{\sqrt{10}}{28 }y_4^{-1} ,\\
+y_2^{0}y_2^{0}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{7 }y_2^{0} + \frac{3}{7 }y_4^{0} ,\\
+y_2^{0}y_2^{1}\sqrt{\pi} &= \frac{\sqrt{5}}{14 }y_2^{1} + \frac{\sqrt{30}}{14 }y_4^{1} ,\\
+y_2^{0}y_2^{2}\sqrt{\pi} &= - \frac{\sqrt{5}}{7 }y_2^{2} + \frac{\sqrt{15}}{14 }y_4^{2} ,\\
+y_2^{1}y_2^{1}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} + \frac{\sqrt{5}}{14 }y_2^{0} + \frac{\sqrt{15}}{14 }y_2^{2} - \frac{2}{7 }y_4^{0} + \frac{\sqrt{5}}{7 }y_4^{2} ,\\
+y_2^{1}y_2^{2}\sqrt{\pi} &= \frac{\sqrt{15}}{14 }y_2^{1} - \frac{\sqrt{10}}{28 }y_4^{1} + \frac{\sqrt{70}}{28 }y_4^{3} ,\\
+y_2^{2}y_2^{2}\sqrt{\pi} &= \frac{1}{2 }y_0^{0} - \frac{\sqrt{5}}{7 }y_2^{0} + \frac{1}{14 }y_4^{0} + \frac{\sqrt{35}}{14 }y_4^{4}.
 \end{align}
@@
 microscope. We start by plugging Eq. \ref{eq:paracsf} (the paraxial CSF) into Eq.
-\ref{eq:csfdef2}
-\begin{align}
-  {\mb{E}_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\,
-\begin{bmatrix}
-    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+\ref{eq:ctf}
+\begin{align}
+  {\mb{E}_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}'\,
+\begin{bmatrix}
+    a^{(p)}(r_o)y_1^{1}(\so{}) + 2ib^{(p)}(r_o)\cos\phi_o y_1^{0}(\so{})\\
+    a^{(p)}(r_o)y_1^{-1}(\so{}) + 2ib^{(p)}(r_o)\sin\phi_o y_1^{0}(\so{})\\
     0\\
   \end{bmatrix}
-  y_l^m(\so{})\thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}. 
+  y_l^m(\so{})\thinspace\me^{-i 2\pi\ro{}'\cdot\bs{\nu}}. 
 \end{align}
@@
   {\mb{E}_l^m}^{(p)}(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, \mb{E}^{(p)}(\bs{\nu};\so{}) y_l^m(\so{}),\\ \label{eq:splitup}
-  \mb{E}^{(p)}(\bs{\nu};\so{}) &\equiv  \int_{\mathbb{R}^2}d\rd{}'\
-\begin{bmatrix}
-    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+  \mb{E}^{(p)}(\bs{\nu};\so{}) &\equiv  \int_{\mathbb{R}^2}d\ro{}'\
+\begin{bmatrix}
+    a^{(p)}(r_o')y_1^{1}(\so{}) + 2ib^{(p)}(r_o')\cos\phi_o'y_1^{0}(\so{})\\
+    a^{(p)}(r_o')y_1^{-1}(\so{}) + 2ib^{(p)}(r_o')\sin\phi_o'y_1^{0}(\so{})\\
     0\\
   \end{bmatrix}
-  \thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}. 
-\end{align}
-Substituting $a^{(p)}(r_d')$ and $b^{(p)}(r_d')$ using Eq. \ref{eq:abparadef} gives
-\begin{align}
-  \mb{E}^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\rd{}'\,
-\begin{bmatrix}
-    \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}y_1^m(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right]\cos\phi_d'y_1^0(\so{})\\
-    \frac{J_1(2\pi \nu_or_d')}{\pi \nu_or_d'}y_1^{-1}(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_d')}{\pi \nu_or_d'}\right]\sin\phi_d'y_1^0(\so{})\\
+  \thinspace\me^{-i 2\pi\ro{}'\cdot\bs{\nu}}. 
+\end{align}
+Substituting $a^{(p)}(r_o')$ and $b^{(p)}(r_o')$ using Eq. \ref{eq:abparadef} gives
+\begin{align}
+  \mb{E}^{(p)}(\bs{\nu}; \so{}) = \int_{\mathbb{R}^2}d\ro{}'\,
+\begin{bmatrix}
+    \frac{J_1(2\pi \nu_or_o')}{\pi \nu_or_o'}y_1^m(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o')}{\pi \nu_or_o'}\right]\cos\phi_o'y_1^0(\so{})\\
+    \frac{J_1(2\pi \nu_or_o')}{\pi \nu_or_o'}y_1^{-1}(\so{}) + 2i\frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi ar_o')}{\pi \nu_or_o'}\right]\sin\phi_o'y_1^0(\so{})\\
     0\\
   \end{bmatrix}
-  \thinspace\me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
+  \thinspace\me^{-i 2\pi\ro{}'\cdot\bs{\nu}}.
 \end{align}
@@
     0\\
-  \end{bmatrix}\label{eq:tint}
+  \end{bmatrix}\label{eq:tint},
 \end{align}
@@
 \begin{align}
-  t_1(\bs{\nu}) &\equiv \frac{1}{\pi \nu_o}\int_{\mathbb{R}^2}d\rd{}'\,  \frac{J_1(2\pi \nu_or_d')}{r_d'}\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
-  t_2(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi \nu_or_d')}{r_d'}\cos\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}},\\
-  t_3(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\rd{}'\, \frac{J_2(2\pi \nu_or_d')}{r_d'}\sin\phi_d'\, \me^{-i 2\pi\rd{}'\cdot\bs{\nu}}.
+  t_1(\bs{\nu}) &\equiv \frac{1}{\pi \nu_o}\int_{\mathbb{R}^2}d\ro{}'\,  \frac{J_1(2\pi \nu_or_o')}{r_o'}\, \me^{-i 2\pi\ro{}'\cdot\bs{\nu}},\\
+  t_2(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\ro{}'\, \frac{J_2(2\pi \nu_or_o')}{r_o'}\cos\phi_o'\, \me^{-i 2\pi\ro{}'\cdot\bs{\nu}},\\
+  t_3(\bs{\nu}) &\equiv \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\int_{\mathbb{R}^2}d\ro{}'\, \frac{J_2(2\pi \nu_or_o')}{r_o'}\sin\phi_o'\, \me^{-i 2\pi\ro{}'\cdot\bs{\nu}}.
 \end{align}
@@
 \begin{align}
-  \mathcal{F}\{g(r, \theta)\} = \sum_{k=-\infty}^{\infty}c_k(-i)^k\me^{ik\phi}\mathcal{H}_k\{g_R(r)\}
+  \mathcal{F}\{g(r, \theta)\} = \sum_{k=-\infty}^{\infty}c_k(-i)^k\me^{ik\phi}\mathcal{H}_k\{g_R(r)\},
 \end{align}
@@
 \begin{align}
-  c_k = \frac{1}{2\pi}\int_0^{2\pi}d\theta\, g_{\Theta}(\theta)\me^{-ik\theta}
+  c_k = \frac{1}{2\pi}\int_0^{2\pi}d\theta\, g_{\Theta}(\theta)\me^{-ik\theta},
 \end{align}
@@
 \begin{align}
-  t_1(\bs{\nu}) = \frac{1}{\pi \nu_o}\mathcal{H}_0\left\{\frac{J_1(2\pi \nu_or_d')}{r_d'}\right\}.
+  t_1(\bs{\nu}) = \frac{1}{\pi \nu_o}\mathcal{H}_0\left\{\frac{J_1(2\pi \nu_or_o')}{r_o'}\right\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{H}_{\mu}\left\{\frac{J_{\mu+1}(2\pi \nu_or_d')}{r_d'}\right\} =
-  \frac{1}{2\pi}\nu_o^{-\mu-1}\nu^\mu\, \Pi\left(\frac{\nu}{a}\right)\label{eq:hankstar}
+  \mathcal{H}_{\mu}\left\{\frac{J_{\mu+1}(2\pi \nu_or_o')}{r_o'}\right\} =
+  \frac{1}{2\pi}\nu_o^{-\mu-1}\nu^\mu\, \Pi\left(\frac{\nu}{a}\right)\label{eq:hankstar},
 \end{align}
@@
 To evaluate $t_2(\bs{\nu})$ and $t_3(\bs{\nu})$ we need to be careful with the angular part. For $t_2(\bs{\nu})$
-the angular part of the function is $\cos\phi_d' = \frac{1}{2}\left(e^{i\phi_d'} + e^{-i\phi_d'}\right)$.
+the angular part of the function is $\cos\phi_o' = \frac{1}{2}\left(e^{i\phi_o'} + e^{-i\phi_o'}\right)$.
 Therefore, $c_k = \frac{1}{2}\delta(k-1) + \frac{1}{2}\delta(k+1)$ and we have to evaluate two Hankel transforms given by
 \begin{align}
-  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[ie^{-i\phi_{\nu}}\mathcal{H}_{-1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi ar_d'}\right\}\right].
+  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[ie^{-i\phi_{\nu}}\mathcal{H}_{-1}\left\{\frac{J_2(2\pi \nu_or_o')}{\pi \nu_or_o'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_o')}{\pi ar_o'}\right\}\right].
 \end{align}
@@
 \begin{align}
-  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[-ie^{-i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_d')}{\pi \nu_or_d'}\right\}\right].
+  t_2(\bs{\nu}) = \frac{2i}{\pi \nu_o}\frac{\text{NA}}{n_o}\left[-ie^{-i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_o')}{\pi \nu_or_o'}\right\} - ie^{i\phi_{\nu}}\mathcal{H}_{1}\left\{\frac{J_2(2\pi \nu_or_o')}{\pi \nu_or_o'}\right\}\right].
 \end{align}
@@
   t_2(\bs{\nu}) =
-    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\cos\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t2final}
+    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\cos\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t2final}.
 \end{align}
@@
   t_3(\bs{\nu}) =
-    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\sin\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t3final}
+    \frac{1}{\pi^2 \nu_o^3}\frac{\text{NA}}{n_o}\nu\sin\phi_{\nu}\, \Pi\left(\frac{\nu}{a}\right)\label{eq:t3final}.
 \end{align}
@@
 In this appendix we calculate the paraxial OTF for a single-view fluorescence
-microscope. We start with Eq. \ref{eq:otfdef2}
-\begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h^{(p)}(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+microscope. We start with Eq. \ref{eq:otf}
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\ro{}'\, h'^{(p)}(\ro{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \ro{}'\cdot\bs{\nu}}.
   \label{eq:appotf}
@@
 \begin{align}
-  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}),\\ \label{eq:parapsf}
-  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
-  {h_2^0}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right]. 
+  h'^{(p)}(\ro{}', \so{}) &= {h_0^0}^{(p)}(\ro{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\ro{}')y_2^0(\so{}), \label{eq:parapsf} \\ 
+  {{h'}_0^0}^{(p)}(\ro{}') &\equiv {a^{(p)}}^2(r'_o) + 2{b^{(p)}}^2(r'_o),\\
+  {{h'}_2^0}^{(p)}(\ro{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r'_o) + 4{b^{(p)}}^2(r'_o)\right]. 
 \end{align}
@@
 \begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{R}^2}d\rd{}'\, \left[{h_0^0}^{(p)}(\rd{}')\delta(l, m) + {h_2^0}^{(p)}(\rd{}')\delta(l-2, m)\right] \me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
+  {H_l^m}^{(p)}(\bs{\nu}) \propto \int_{\mathbb{R}^2}d\ro{}'\, \left[{{h'}_0^0}^{(p)}(\ro{}')\delta(l, m) + {{h'}_2^0}^{(p)}(\ro{}')\delta(l-2, m)\right] \me^{-i 2\pi \ro{}'\cdot\bs{\nu}}.
 \label{eq:appotf2}
@@
 \begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}) &\propto \mathcal{F}_2\{{h_0^0}^{(p)}(\rd{}')\delta(l, m) + {h_2^0}^{(p)}(\rd{}')\delta(l-2, m) \},\\
-  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l-2, m).
-\end{align}
-To calculate $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ we can use the
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \mathcal{F}_2\{{{h'}_0^0}^{(p)}(\ro{}')\delta(l, m) + {{h'}_2^0}^{(p)}(\ro{}')\delta(l-2, m) \},\\
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}\right]\delta(l-2, m).
+\end{align}
+To calculate $\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\}$ we can use the
 autocorrelation theorem \cite{goodman1996}
@@
 where $\star_2$ denotes a two-dimensional autocorrelation. We can rewrite
-$\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ as
-\begin{align}
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\}.
+$\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\}$ as
+\begin{align}
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o')}{\pi\nu_o r_o'}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o')}{\pi\nu_o r_o'}\right\}.
 \end{align}
@@
 \begin{align}
-\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\} \star_2 \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_d')}{\pi\nu_o r_d'}\right\}, 
+\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o')}{\pi\nu_o r_o'}\right\} \star_2 \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o')}{\pi\nu_o r_o'}\right\}, 
 \end{align}
@@
 \begin{align}
-  \mathcal{H}_{k}\left\{\frac{J_{k+1}(2\pi \nu_or_d')}{\pi\nu_o r_d'}\right\} =
+  \mathcal{H}_{k}\left\{\frac{J_{k+1}(2\pi \nu_or_o')}{\pi\nu_o r_o'}\right\} =
   \frac{2\nu^k}{\nu_o^{k+1}}\, \Pi\left(\frac{\nu}{\nu_o}\right)\label{eq:hankstar2},
@@
 \begin{align}
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right],\\
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \frac{4}{\nu_o^2}\left[\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\Pi\left(\frac{\nu}{\nu_o}\right)\right].
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\frac{2}{\nu_o}\Pi\left(\frac{\nu}{\nu_o}\right)\right],\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= \frac{4}{\nu_o^2}\left[\Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\Pi\left(\frac{\nu}{\nu_o}\right)\right].
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}&= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  \mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} &= 8\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-
-Next, we calculate $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$. If we follow
-the same steps as we did for $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$, we
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\}&= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\, \tau\int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}\right) - \left(\int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= \frac{16}{\nu_o^2}\left[\left(\int\limits_0^{\nu_o} d\tau\,\tau\arccos\left(\frac{\nu}{2\nu_o}\right)\right) - \left(\int\limits_0^{\nu/2}d\tau_x \tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  \mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= 8\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+Next, we calculate $\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}$. If we follow
+the same steps as we did for $\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\}$, we
 will reach a dead end because there is no Hankel transform identity that we can
-use. Instead, we rewrite $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$ in the
+use. Instead, we rewrite $\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}$ in the
 following way so that we can use the Hankel transform identity in Eq. \ref{eq:hankstar2}
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} = \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\cos^2(\phi_d')\right\} + \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\cos^2(\phi_d')\right\}.
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} = \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\cos^2(\phi_o')\right\} + \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\cos^2(\phi_o')\right\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} = \left[\mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\}\right] + \left[\mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\}\right].
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} = \left[\mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\}\right] + \left[\mathcal{F}_2\left\{{b^{(p)}}(r_o')\sin(\phi_o')\right\} \star_2 \mathcal{F}_2\left\{{b^{(p)}}(r_o')\sin(\phi_o')\right\}\right].
 \label{eq:int3}
@@
 \end{align}
-Applying the Hankel transform expansion to $\mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\}$ gives
-\begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{1}{2}\left[i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}\right].
+Applying the Hankel transform expansion to $\mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\}$ gives
+\begin{align}
+  \mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\} = \frac{1}{2}\left[i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_o')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_o')\}\right].
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -i\cos\phi_\nu \mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.
+  \mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\} = -i\cos\phi_\nu \mathcal{H}_{1}\{{b^{(p)}}(r_o')\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{H}_{1}\{{b^{(p)}}(r_d')\} = \mathcal{H}_{1}\left\{\frac{J_{2}(2\pi \nu_or_d')}{\pi\nu_o r_d'}\right\} =
+  \mathcal{H}_{1}\{{b^{(p)}}(r_o')\} = \mathcal{H}_{1}\left\{\frac{J_{2}(2\pi \nu_or_o')}{\pi\nu_o r_o'}\right\} =
   \left(\frac{\text{NA}}{n_o}\right)\frac{2\nu}{\nu_o^{2}}\, \Pi\left(\frac{\nu}{\nu_o}\right).
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+  \mathcal{F}_2\left\{{b^{(p)}}(r_o')\cos(\phi_o')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
+  \mathcal{F}_2\left\{{b^{(p)}}(r_o')\sin(\phi_o')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).
 \end{align}
@@
 \begin{align}
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}
 \end{align}
@@
 \begin{align}
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
 \end{align}
@@
 \begin{align}
-  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-Now that we've evaluated $\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\}$ and $\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}$, we can plug the results into the following equation and we have the complete spatio-angular transfer function
-\begin{align}
-  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_d')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\}\right]\delta(l-2, m).
+  \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+    \mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+Now that we've evaluated $\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\}$ and $\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}$, we can plug the results into the following equation and we have the complete spatio-angular transfer function
+\begin{align}
+  {H_l^m}^{(p)}(\bs{\nu}) &\propto \left[\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} + 2\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}\right]\delta(l, m) + \\&\hspace{1em}\left[-\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} + 4\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\right\}\right]\delta(l-2, m).
 \end{align}
@@
     \node [input, name=input] {};
-    \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}_d(\rd{} - M\ro{}, \so{})$};
+    \node [block, align=center] (csf) {CSF\\ $\tilde{\mb{e}}'_d(\ro{}', \so{})$};
     \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{E}_l^m(\bs{\nu})$};
     \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
-    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\rd{} - M\ro{}, \so{})$};
+    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h'(\ro{}', \so{})$};
 
@@
     \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{E}_l^m(\bs{\nu})\star_{\mathbb{R}^2} \mb{E}_l^m(\bs{\nu})]$} (otf);
-    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
-    \draw [->] (csf) -- node[name=v, text width=4cm, align=center, left] {Detector\\ $|\mb{\tilde{e}}_d(\rd{} - M\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
+    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^2\times\mathbb{S}^2}$} (otf);
+    \draw [->] (csf) -- node[name=v, text width=4cm, align=center, left] {Detector\\ $|\mb{\tilde{e}}'_d(\ro{}', \so{})|^2_{\mathbb{R}^2}$} (psf);
       \end{tikzpicture}

### 2018-04-23 notes/2018-02-23-spatio-angular-kernel/calculations/compare-ft/compare-ft.py

@@ -53,22 +53,22 @@ save_tiff(hh20ft, out+'hh20ft.tiff')
 x = np.linspace(-2, 2, n_pixels)
 f, axs = plt.subplots(1, 2, figsize=(10,5))
 
-axs[0].plot(x, cs(hh00an), '-', c='k', lw=1, label=r"${h_0^0}^{(p)}(r_d')$")
+axs[0].plot(x, cs(hh00an), '-', c='k', lw=1, label=r"${h_0^0}^{(p)}(r_o')$")
 #axs[0].plot(xF, cs(hh00ft), ':', c='k',lw=1, label=r"$h_0^0(r_d')$ FT")
 
-axs[0].plot(x, cs(hh20an), '-', c='b',lw=1, label=r"${h_0^2}^{(p)}(r_d')$")
+axs[0].plot(x, cs(hh20an), '-', c='b',lw=1, label=r"${h_2^0}^{(p)}(r_o')$")
 #axs[0].plot(xF, cs(hh20ft), ':', c='b',lw=1, label=r"$h_0^2(r_d')$ FT")
 
-axs[0].plot(x, cs(hhxan), '-', c='r',lw=1, label=r"$h_x^{(p)}(r_d')$")
+axs[0].plot(x, cs(hhxan), '-', c='r',lw=1, label=r"$h_x^{(p)}(r_o')$")
 #axs[0].plot(xF, cs(hhxft), ':', c='r',lw=1, label=r"$h_x(r_d')$ FT")
 
-axs[0].plot(x, cs(hhzan), '-', c='g',lw=1, label=r"$h_z^{(p)}(r_d')$")
+axs[0].plot(x, cs(hhzan), '-', c='g',lw=1, label=r"$h_z^{(p)}(r_o')$")
 #axs[0].plot(xF, cs(hhzft), ':', c='g',lw=1, label=r"$h_z(r_d')$ FT")
 
 # Ax 0 setup
 axs[0].set_xlim([-2, 2])
 axs[0].set_ylim([-1, 1])
-axs[0].set_xlabel(r"$r_d'\, \textrm{NA}/(M\lambda)$")
+axs[0].set_xlabel(r"$r_o'\, \textrm{NA}/\lambda$")
 axs[0].set_title(r'')
 axs[0].get_xaxis().set_ticks([-2, -1, 0, 1, 2])
[…]

### 2018-04-30 notes/2018-04-19-polarizer-otf/report/report.tex
Polarizer psfs and otfs. Notes and calculations.

@@
 \begin{align}
-  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) \propto\, &[2A + (4/3)B]y_0^0(\so{}) - \frac{4\sqrt{5}}{15}By_2^0(\so{}) + \nonumber\\ &\frac{4C}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
+  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]y_0^0(\so{}) - \frac{4\sqrt{5}}{15}\bar{B}y_2^0(\so{}) + \nonumber\\ &\frac{4\bar{C}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
 \label{eq:genpsf}
 \end{align}
-
-% We can rewrite this expression in vector 
-% notation as
-% \begin{align}
-% h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= E + F[(\so{}\cdot\mh{x})^2 + (\so{}\cdot\mh{y})] + G\left[\mh{p} \cdot \frac{(\so{}\cdot\mh{x})\mh{x} + (\so{}\cdot\mh{y})\mh{y}}{\sqrt{(\so{}\cdot\mh{x})^2 + (\so{}\cdot\mh{y})^2}}\right]^2,
-% \end{align}
-% where
-% \begin{subequations}
-%   \begin{align}
-%     E &\equiv DA = \frac{1}{3} - \frac{1}{6}\cos\alpha - \frac{1}{6}\cos^2\alpha,\\
-%     F &\equiv D(B-C) = -\frac{7}{24} + \frac{1}{12}\cos\alpha + \frac{5}{24}\cos^2\alpha,\\
-%     G &\equiv 2DC = \frac{7}{12} + \frac{1}{3}\cos\alpha + \frac{1}{12}\cos^2\alpha.
-%   \end{align}
-% \end{subequations}
-% Finally, we can rewrite this expression in Cartesian coordinates as 
-% \begin{align}
-%     h^{\mh{z}}_{\text{exc}}(s_x, s_y; p_x, p_y) &= E + F[s_x^2 + s_y^2] + G\frac{(p_xs_x + p_ys_y)^2}{s_x^2 + s_y^2},
-% \end{align}
-% where $s_x^2 + s_y^2 + s_z^2 = 1$ and $p_x^2 + p_y^2 + p_z^2= 1$.
 
@@
 \begin{align}
-  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
+  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
+  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2A + (4/3)B]\delta(l, m) - \frac{4\sqrt{5}}{15}B\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4C}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right] + (\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\right\}.
+  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]\delta(l, m) - \frac{4\sqrt{5}}{15}\bar{B}\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4\bar{C}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\Bigg\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right]\nonumber\\ &\hspace{20em}+ 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\Bigg\}.
 \end{align}
@@
     0
-  \end{bmatrix}.
+  \end{bmatrix}.\label{eq:bfp}
 \end{align}
+In these notes we will ignore the phase term in the back focal plane---see the
+previous notes for more details on shift invariance. Alternatively, we can say
+that Eq. \ref{eq:bfp} is the electric field in the back focal plane created by a
+single dipole at the focal point of the objective.
+
 If we place a polarizer oriented along $\mh{p}_d$ in the back focal plane then
@@
 \begin{align}
-  \tilde{\mb{e}}^{(p)}_d(\rd{}', \so{}; \mh{p}_d) &\propto \mh{p}_d \cdot
+  \tilde{\mb{e}}'^{(p)}_d(\ro{}', \so{}; \mh{p}_d) &\propto \mh{p}_d \cdot
   \begin{bmatrix}
-    a^{(p)}(r_d')y_1^{1}(\so{}) + 2ib^{(p)}(r_d')\cos\phi_d'y_1^{0}(\so{})\\
-    a^{(p)}(r_d')y_1^{-1}(\so{}) + 2ib^{(p)}(r_d')\sin\phi_d'y_1^{0}(\so{})\\
+    a^{(p)}(r_o')y_1^{1}(\so{}) + 2ib^{(p)}(r_o')\cos\phi_o'y_1^{0}(\so{})\\
+    a^{(p)}(r_o')y_1^{-1}(\so{}) + 2ib^{(p)}(r_o')\sin\phi_o'y_1^{0}(\so{})\\
     0\\
@@
 Finally, we can find the spatio-angular point spread function by taking the
-squared modulus of the electric field on the detector.
+squared modulus of the electric field on the detector
+\begin{align}
+  h'^{(p)}(\ro{}', \so{}; \mh{p}_d) &\equiv |\tilde{\mb{e}}'^{(p)}_d(\ro{}', \so{}; \mh{p}_d)|^2.
+\end{align}
+Expanding, factoring, and normalizing the result gives   
+\begin{align}
+    h'^{(p)}(\ro{}', \so{}; \mh{p}_d) &= {h'}_0^{0(p)}(\ro{}')y_0^0(\so{}) + {h'}_2^{0(p)}(\ro{}')y_2^0(\so{}) + {h'}_2^{2(p)}(\ro{}')y_2^2(\so{}) + {h'}_2^{-2(p)}(\ro{}')y_2^{-2}(\so{}),
+\end{align}
+where
+\begin{align}
+  {h'}_0^{0(p)}(\ro{}'; \mh{p}_d) &\equiv {a^{(p)}}^2(r_o') + 4{b^{(p)}}^2(r_o')(\mh{r}'_o\cdot\mh{p}_d)^2,\\
+{h'}_2^{0(p)}(\ro{}'; \mh{p}_d) &\equiv \frac{1}{\sqrt{5}}\left[-{a^{(p)}}^2(r_o') + 8{b^{(p)}}^2(r_o')(\mh{r}'_o\cdot\mh{p}_d)^2\right],\\
+  {h'}_2^{2(p)}(\ro{}'; \mh{p}_d) &\equiv \sqrt{\frac{3}{5}}{a^{(p)}}^2(r_o')\left[(\mh{p}_d\cdot\mh{x})^2 - (\mh{p}_d\cdot\mh{y})^2\right],\\
+  {h'}_2^{-2(p)}(\ro{}'; \mh{p}_d) &\equiv -2\sqrt{\frac{3}{5}}{a^{(p)}}^2(r_o')(\mh{p}_d\cdot\mh{x})(\mh{p}_d\cdot\mh{y}).  
+\end{align}
 
-In progress. Calculate the spatio-angular PSF then the spatio-angular OTF. 
+\begin{figure}[ht]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 1.\textwidth]{../calculations/psfs0.pdf}
+   \caption{Spatio-angular point spread function for a single-view fluorescence
+     microscope with $\text{NA}=0.8$, $n_o=1.33$ and an $\mh{x}$-oriented
+     polarizer under the paraxial approximation. \textbf{Columns:} Each term of
+     the spatio-angular point spread function. \textbf{Row 1:} Images of each
+     term with contours at $\pm 0.1$ and \textbf{Row 2:} horizontal (solid) and
+     vertical (dashed) profiles through each term. The ${h'}_0^0$ and ${h'}_2^0$
+     terms have a $\cos^2\phi_o$ dependence, so two profiles are sufficient to
+     characterize their images. The ${h'}_2^2$ and ${h'}_2^{-2}$ terms are
+     radially symmetric, so one profile is sufficient.}
+   \label{fig:psf}
+\end{figure}
+
+The spatio-angular point spread function for a fluorescence microscope with a
+polarized detection path has four terms---see Figures \ref{fig:psf} and \ref{fig:psf2} for plots.
+The ${h'}_0^0$ and ${h'}_0^2$ terms are familiar from the unpolarized case, but
+now they have an extra factor of $(\ro{}'\cdot\mh{p}_d)^2$ that accounts for the
+polarizer and breaks radial symmetry. Notice that if we average over all
+polarizer orientations then $(\ro{}'\cdot\mh{p}_d)^2 \rightarrow 1/2$, and we
+recover the spatio-angular point spread function for a microscope without a
+detection polarizer.
+
+One of the interesting predictions of the polarized spatio-angular point spread
+function is the elongated point spread function in the ${h'}_0^0$ term (which
+corresponds to a physically realizable uniform distribution of dipoles). The
+long axis of the point spread function is parallel with the transmission axis of
+the polarizing filter---this is not an intuitive result. If we applied the usual
+reasoning for the width of point spread functions---broader distributions of
+intensity in the back focal plane cause narrower point spread functions---we
+would predict that the point spread function for the ${h'}_0^0$ term would be
+elongated perpendicular to the transmission axis of the polarizer. This
+reasoning fails because we need to add the intensities at the detector, not at
+the back focal plane.
+
+The ${h'}_2^2$ and ${h'}_2^{-2}$ terms are only non-zero when a polarizing
+filter is in the detection path. These terms correspond to distributions of
+fluorophores with positive and negative fluorophores near the transverse plane
+only. Without a polarizer, the ``intensity contributions'' from the positive and
+negative fluorophores cancel, and we have no contribution from these
+distributions. With a polarizer, the intensity contribution from the positive or
+negative fluorophores dominate, and we end up with a rotationally symmetric
+contribution to the point spread function.
+
+It's interesting to compare polarizing filters with phase and amplitude filters.
+Adding a phase filter can extend the band limit of a microscope to measure new
+information about the object without blocking any photons. For example, cubic
+phase masks and microlens arrays can increase the axial band limit of a
+microscope. All lenses can be considered as phase filters, so it's almost
+obvious that phase filters can increase the band limit of an imaging system.
+Amplitude filters, on the other hand, cannot extend the band limit of a
+microscope. Amplitude filters can change the contrast for different spatial
+frequencies by blocking photons, but they do not allow new information to be
+measured. Polarizing filters share properties with phase and amplitude
+filters---they block photons \textbf{and} extend the angular band limit of the
+microscope.
+
+\begin{figure}[ht]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 1.\textwidth]{../calculations/psfsp3.pdf}
+   \caption{Spatio-angular point spread function for a single-view fluorescence
+     microscope with $\text{NA}=0.8$, $n_o=1.33$ and an
+     ($\mh{x}/2 + \sqrt{3}\mh{y}/2$)-oriented polarizer under the paraxial
+     approximation. \textbf{Columns:} Each term of the spatio-angular point
+     spread function. \textbf{Row 1:} Images of each term with contours at
+     $\pm 0.1$ and \textbf{Row 2:} horizontal (solid) and vertical (dashed)
+     profiles through each term. The ${h'}_0^0$ and ${h'}_2^0$ terms have a
+     $\cos^2\phi_o$ dependence, so two profiles are sufficient to characterize
+     their images. The ${h'}_2^2$ and ${h'}_2^{-2}$ terms are radially
+     symmetric, so one profile is sufficient.}
+   \label{fig:psf2}
+\end{figure}
+
+To find the transfer function we need to calculate the Fourier transform of the
+point spread function. We can use the following Fourier transforms that we
+evaluated in the previous notes
+\begin{align}
+\mathcal{F}_2\left\{{a^{(p)}}^2(r_o')\right\} &= 8\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+\mathcal{F}_2\left\{{b^{(p)}}^2(r_o')\cos^2\phi'_o\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\Bigg[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[5 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\nonumber\\ &\hspace{17em} - \frac{8}{3}\cos^2\phi_\nu\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+Applying these results and normalizing gives the spatio-angular transfer function for
+a fluorescence microscope with a polarizer along the detection path
+\begin{align}
+    H_m^{l(p)}(\bs{\nu}; \mh{p}_d) &= {H}_0^{0(p)}(\bs{\nu})\delta(l, m) + {H}_2^{0(p)}(\bs{\nu})\delta(l-2, m) + {H}_2^{2(p)}(\nu)\delta(l-2, m-2) + {H}_2^{-2(p)}(\nu)\delta(l-2, m+2),
+\end{align}
+where
+\begin{align}
+  {H}_0^{0(p)}(\bs{\nu}; \mh{p}_d) &\equiv \frac{1}{1 + (\text{NA}/n_o)^2}\left[{A^{(p)}}(\nu) + 2{B^{(p)}}(\nu) + 2{C^{(p)}}(\nu)\left\{2(\mh{\bs{\nu}}\cdot\mh{p}_d)^2 - 1\right\}\right],\\
+  {H}_2^{0(p)}(\bs{\nu}; \mh{p}_d) &\equiv \frac{1}{\sqrt{5}[1 + (\text{NA}/n_o)^2]}\left[-{A^{(p)}}(\nu) + 4{B^{(p)}}(\nu) + 4{C^{(p)}}(\nu)\left\{2(\mh{\bs{\nu}}\cdot\mh{p}_d)^2 - 1\right\}\right],\\
+  {H}_2^{2(p)}(\nu; \mh{p}_d) &\equiv \sqrt{\frac{3}{5}}\frac{1}{[1 + (\text{NA}/n_o)^2]}{A^{(p)}}(\nu)\left[(\mh{\bs{\nu}}\cdot\mh{x})^2 - (\mh{\bs{\nu}}\cdot\mh{y})^2\right],\\
+  {H}_2^{-2(p)}(\nu; \mh{p}_d) &\equiv -2\sqrt{\frac{3}{5}}\frac{1}{[1 + (\text{NA}/n_o)^2]}{A^{(p)}}(\nu)(\mh{\bs{\nu}}\cdot\mh{x})(\mh{\bs{\nu}}\cdot\mh{y}),
+\end{align}
+and
+\begin{align}
+  {A}^{(p)}(\nu) &\equiv \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  B^{(p)}(\nu) &\equiv \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  C^{(p)}(\nu) &\equiv \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[-\frac{4}{3}\frac{\nu}{2\nu_o} \sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+
+Figures \ref{fig:otf} and \ref{fig:otf2} show plots of the spatio-angular OTF
+for two different polarizer orientations. Notice that the polarizer does not
+change the spatial band limit of the microscope, but it does change the contrast
+at high frequencies. If we use the cutoff frequency as a resolution criterion,
+we would conclude that polarizers do not change the spatial resolution of our
+microscope. However, if we use a spatial-domain resolution criteria like the
+Rayleigh or Sparrow criteria, then we would conclude that adding a polarizer
+improves the spatial resolution in the direction perpendicular to the polarizer.
+
+Notice that the $H_0^0$ term in Figure \ref{fig:otf} is negative for spatial
+frequencies near the cutoff frequency parallel to the polarizer transmission
+axis. This means that we expect to see a contrast inversion for angularly
+uniform distributions of dipoles when the spatial frequency pattern is parallel
+to the polarizer transmission axis. In the spatial domain, this contrast
+inversion is caused by the elongation of the point spread function. The point
+spread function is wide enough that three fluorescent points spaced near the
+cutoff frequency give an intensity minimum that reports the position of the
+central fluorescent point---see Figure \ref{fig:psfmin}.
+
+\begin{figure}[H]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 1.\textwidth]{../calculations/otfs0.pdf}
+   \caption{Spatio-angular orientation transfer function for a single-view
+     fluorescence microscope with $\text{NA}=0.8$, $n_o=1.33$ and an
+     $\mh{x}$-oriented polarizer under the paraxial approximation.
+     \textbf{Columns:} Each term of the spatio-angular optical transfer
+     function. \textbf{Row 1:} Images of each term and \textbf{Row 2:}
+     horizontal (solid) and vertical (dashed) profiles through each term.}
+   \label{fig:otf}
+\end{figure}
+
+\begin{figure}[H]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 1.\textwidth]{../calculations/otfs3.pdf}
+   \caption{Spatio-angular orientation transfer function for a single-view
+     fluorescence microscope with $\text{NA}=0.8$, $n_o=1.33$ and an
+     ($\mh{x}/2 + \sqrt{3}\mh{y}/2$)-oriented polarizer under the paraxial
+     approximation. \textbf{Columns:} Each term of the spatio-angular optical
+     transfer function. \textbf{Row 1:} Images of each term and \textbf{Row 2:}
+     horizontal (solid), and vertical (dashed) profiles through each term.}
+   \label{fig:otf2}
+\end{figure}
+
+\begin{figure}[H]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[width = 0.8\textwidth]{../calculations/psf-min.pdf}
+   \caption{A polarizer creates a contrast inversion for uniformly distributed
+     dipoles at high spatial frequencies along the direction parallel to the
+     polarizer transmission axis. \textbf{Column 1:} Without a polarizer, three
+     point sources with an angularly uniform distribution create an intensity
+     pattern with three distinct peaks---the peaks report the position of the
+     point sources. \textbf{Column 2:} With a polarizer, the point sources
+     create an intensity pattern with two central peaks---the valley reports the
+     position of the central point source. All of the sources in the figures are
+     ``resolvable'' in the sense that they are spaced at a distance greater than
+     the inverse of the cutoff frequency. This figure demonstrates contrast
+     inversion at high spatial frequencies parallel to the polarizer
+     transmission axis. }
+   \label{fig:psfmin}
+\end{figure}
+
 % \begin{equation}
@@
 \appendix
-\section{Rotation of spherical harmonics} \label{sec:sh}
-Given a spherical function and its spherical harmonic coefficients $c_j$ (we're
-using a single index over the spherical harmonics), the spherical harmonic
-coefficients of the rotated function $c'_i$ can be computed with the linear
-transformation
+\section{Rotation of spherical harmonics} \label{sec:sh} Given a spherical
+function and its spherical harmonic coefficients $c_j$ (where $j$ is a single
+index over the spherical harmonics), the spherical harmonic coefficients of the
+rotated function $c'_i$ can be computed with the linear transformation
 \begin{align}

### 2018-04-30 notes/2018-04-19-polarizer-otf/calculations/compare-ft.py

@@ -1,99 +1,0 @@
-import numpy as np
-from util import *
-import matplotlib.pyplot as plt
-
-# Setup
-out = 'output/'
-NA = 0.8
-n = 1.33
-n_pixels = 257
-[X, Y] = np.meshgrid(np.linspace(-2, 2, n_pixels),
-                     np.linspace(-2, 2, n_pixels))
-R = np.sqrt(X**2 + Y**2)
-
-# Analytic OTF
-Hxan = (A(R)).astype('float32')
-Hzan = (B(R, NA=NA, n=n)).astype('float32')
-H00an = (H00(R, NA=NA, n=n)).astype('float32')
-H20an = (H20(R, NA=NA, n=n)).astype('float32')
-save_tiff(Hxan, out+'Hxan.tiff')
-save_tiff(Hzan, out+'Hzan.tiff')
-save_tiff(H00an, out+'H00an.tiff')
-save_tiff(H20an, out+'H20an.tiff')
-
-# Analytic PSF
-hhxan = (a(R)).astype('float32')
-hhzan = (b(R, NA=NA, n=n)).astype('float32')
-hh00an = (h00(R, NA=NA, n=n)).astype('float32')
-hh20an = (h20(R, NA=NA, n=n)).astype('float32')
-save_tiff(hhxan, out+'hhxan.tiff')
-save_tiff(hhzan, out+'hhzan.tiff')
-save_tiff(hh00an, out+'hh00an.tiff')
-save_tiff(hh20an, out+'hh20an.tiff')
-
-# Computed PSF
-xF, hhxftraw = myfft(Hxan)
-xF, hhzftraw = myfft(Hzan)
-xF, hh00ftraw = myfft(H00an)
-xF, hh20ftraw = myfft(H20an)
-
-hhxft = hhxftraw/np.max(hhxftraw)
-hhzft = hhzftraw/np.max(hhxftraw)
-hh00ft = hh00ftraw/np.max(hh00ftraw)
-hh20ft = hh20ftraw/np.max(hh00ftraw)
-
-save_tiff(hhxft, out+'hhxft.tiff')
-save_tiff(hhzft, out+'hhzft.tiff')
-save_tiff(hh00ft, out+'hh00ft.tiff')
-save_tiff(hh20ft, out+'hh20ft.tiff')
-
[…]

### 2018-04-30 notes/2018-04-19-polarizer-otf/calculations/compare-otfs.py

@@ -1,0 +1,107 @@
+import numpy as np
+from util import *
+import matplotlib.pyplot as plt
+import matplotlib
+matplotlib.rc('text', usetex=True)
+matplotlib.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+matplotlib.rcParams['contour.negative_linestyle'] = 'solid'
+
+f, axs = plt.subplots(4, 4, figsize=(10,14),
+                      gridspec_kw={'width_ratios':[1,1,1,0.05], 'hspace':0.1, 'wspace':0.25})
+
+polar = 0
+w = 2.0
+out_path = 'compare-otf/'
+n_px = 2**9 + 1
+pad = 2**10
+[X, Y] = np.meshgrid(np.linspace(-w, w, n_px),
+                     np.linspace(-w, w, n_px))
+R = np.sqrt(X**2 + Y**2)
+Phi = np.nan_to_num(np.arctan(Y/X))
+
+otf_funcs = [H00, H20, H22] # XXX
+otf_files = ['H00an', 'H20an', 'H22an']
+psf_funcs = [h00, h20, h22] # XXX
+psf_files = ['hh00an', 'hh20an', 'hh22an']
+ylabels = ['Image', 'OTF Profile', 'PSF Profile', 'PSF Diff']
+titles = [r"${H}_0^{0(p)}(\boldsymbol{\nu})$", r"${H}_2^{0(p)}(\boldsymbol{\nu})$", r"${H}_2^{2(p)}(\boldsymbol{\nu})$"]
+
+clabels = [[(n_px/2,0), (n_px/2,100), (n_px/2,150)],
+           [(n_px/2,0), (3*n_px/4, n_px/3), (n_px/4, n_px/3), (3*n_px/4, n_px/4), (n_px/4, n_px/4)],
+           [(n_px/2,0), (n_px/2,100), (n_px/2,450)]]
+for i, (otf_func, otf_file) in enumerate(zip(otf_funcs, otf_files)):
+    # Calculations
+    otf_arr = (otf_func(R, phi=Phi, phi_p=polar)).astype('float32')
+    psf_arr = (psf_funcs[i](R, phi=Phi, phi_p=polar)).astype('float32')
+    xF, psf_arr_ft = myfft(otf_arr, pad=pad)
+
+    if i==0:
[…]

### 2018-04-30 notes/2018-04-19-polarizer-otf/calculations/image-gen.py

@@ -1,0 +1,34 @@
+import numpy as np
+from util import *
+import matplotlib.pyplot as plt
+import os
+
+def psf_gen(n=1.5, NA=1.1, M=20, lamb=0.588, pol=None,
+            px_width=7.4, x_px=257, y_px=257, 
+            out_path='img-output/'):
+
+    if not os.path.exists(out_path):
+        os.makedirs(out_path)
+
+    x_FOV = px_width*x_px/M
+    y_FOV = px_width*y_px/M
+    [X, Y] = np.meshgrid(np.linspace(-x_FOV/2, x_FOV/2, x_px),
+                         np.linspace(-y_FOV/2, y_FOV/2, y_px))
+    R = np.sqrt(X**2 + Y**2)
+    Phi = np.nan_to_num(np.arctan(Y/X))
+
+    funcs = [h00, h20, h22, H00, H20, H22]
+    file_names = ['hh00an', 'hh20an', 'hh22an', 'H00an', 'H20an', 'H22an']
+    for func, file_name in zip(funcs, file_names):
+        file_path = out_path+file_name+'.tiff'
+        print('Generating '+file_path)
+        psf_arr = (func(R*NA/lamb, phi=Phi, n=n, NA=NA, phi_p=pol)).astype('float32')
+        save_tiff(psf_arr, file_path)
+
+psf_gen(n=1.5, NA=1.3, M=80, pol=None, out_path='img-output/NA13/')
+psf_gen(n=1.5, NA=1.1, M=80, pol=None, out_path='img-output/NA11/')
+psf_gen(n=1.5, NA=0.8, M=80, pol=None, out_path='img-output/NA08/')
+psf_gen(n=1.5, NA=1.3, M=80, pol=0, out_path='img-output/NA13pol/')
+psf_gen(n=1.5, NA=1.1, M=80, pol=0, out_path='img-output/NA11pol/')
+psf_gen(n=1.5, NA=0.8, M=80, pol=0, out_path='img-output/NA08pol/')
+        

### 2018-04-30 notes/2018-04-19-polarizer-otf/calculations/plot-psfs.py

@@ -1,0 +1,52 @@
+import numpy as np
+from util import *
+import matplotlib.pyplot as plt
+import matplotlib
+matplotlib.rcParams['contour.negative_linestyle'] = 'solid'
+
+s = 0.75
+f, axs = plt.subplots(2, 5, figsize=(s*14,s*6),
+                      gridspec_kw={'width_ratios':[1,1,1,1,0.05], 'hspace':0.03, 'wspace':0.30})
+
+polar = -np.pi/2
+w = 1.25
+out_path = 'psfs/'
+n_px = 1024
+[X, Y] = np.meshgrid(np.linspace(-w, w, n_px),
+                     np.linspace(-w, w, n_px))
+R = np.sqrt(X**2 + Y**2)
+Phi = np.nan_to_num(np.arctan(Y/X))
+
+psf_funcs = [h00, h20, h22, h2_2]
+psf_files = ['hh00an', 'hh20an', 'h22an', 'h2_2an']
+clabels = [[(n_px/2, n_px/3)], [(n_px/2,n_px/3), (n_px/4,n_px/2), (3*n_px/4,n_px/2)], [(n_px/2, n_px/3)]]
+for i, (psf_func, psf_file) in enumerate(zip(psf_funcs, psf_files)):
+    psf_arr = (psf_func(R, phi=Phi, phi_p=polar)).astype('float32')
+    #save_tiff(psf_arr, out_path+psf_file+'.tiff')
+    levels = [-0.1, 0.1]
+    im = axs[0,i].imshow(psf_arr, cmap="bwr", vmin=-1, vmax=1)
+    ct = axs[0,i].contour(psf_arr, levels, colors='k',linewidths=0.5)
+    # plt.clabel(ct, levels, inline=1, inline_spacing=15, fmt='%1.1f', fontsize=8, manual=clabels[i])
+    axs[0,i].set_axis_off()
+    x = np.linspace(-w, w, n_px)
+    axs[1,i].plot(x, cs(psf_arr), '--', c='k', lw=1)
+    axs[1,i].plot(x, cs(psf_arr, row=True), '-', c='k', lw=1)
+    axs[1,i].set_xlim([-w,w])
+    axs[1,i].set_ylim([-1,1])
+    axs[1,i].set_xlabel(r"$r_o'\, \textrm{NA}/\lambda$")
[…]

### 2018-04-30 notes/2018-04-19-polarizer-otf/calculations/psf-min.py

@@ -1,0 +1,45 @@
+import numpy as np
+from util import *
+import matplotlib.pyplot as plt
+import matplotlib
+
+f, axs = plt.subplots(1, 2, figsize=(6,4),
+                      gridspec_kw={'width_ratios':[1,1], 'hspace':0.1, 'wspace':0.1})
+w = 1.5
+h = 4.5
+NA = 1.0
+
+x = np.linspace(-w, w, 2**10)
+
+pols = [None, 0]
+s = 0.65*NA
+
+for i, pol in enumerate(pols):
+    print(pol)
+    center = h00(x, phi=0, NA=NA, n=1.33, phi_p=pol)
+    shiftr = h00(x-s, phi=0, NA=NA, n=1.33, phi_p=pol)
+    shiftl = h00(x+s, phi=0, NA=NA, n=1.33, phi_p=pol)
+
+    axs[i].plot(x, shiftl + 3.3, '-k', lw=0.5)
+    axs[i].plot(x, center + 2.3, '-k', lw=0.5)
+    axs[i].plot(x, shiftr + 1.3, '-k', lw=0.5)
+    axs[i].plot(x, center + shiftl + shiftr, '-k', lw=0.5)
+    axs[i].plot([s,s], [-100, 100], ':k', lw=0.5)
+    axs[i].plot([-s,-s], [-100, 100], ':k', lw=0.5)    
+    axs[i].plot([0,0], [-100, 100], ':k', lw=0.5)
+
+    axs[i].set_xlim([-w,w])
+    axs[i].set_ylim([0,h])
+
+axs[0].annotate(r"${h'}_0^{0(p)}(x + x')$", xy=(0,0), xytext=(-1.6, 3.3), textcoords='data', ha='right', va='center')
+axs[0].annotate(r"${h'}_0^{0(p)}(x)$", xy=(0,0), xytext=(-1.6, 2.3), textcoords='data', ha='right', va='center')
+axs[0].annotate(r"${h'}_0^{0(p)}(x - x')$", xy=(0,0), xytext=(-1.6, 1.3), textcoords='data', ha='right', va='center')
+axs[0].annotate(r"Sum", xy=(0,0), xytext=(-1.6, 0), textcoords='data', ha='right', va='center')
+axs[0].set_title(r"Without polarizer")
+axs[1].set_title(r"With polarizer")
+
+axs[0].set_axis_off()
+axs[1].set_axis_off()
+
+# Plot PSFs
+plt.savefig('psf-min.pdf', bbox_inches='tight')

### 2018-05-02 notes/2018-04-19-polarizer-otf/report/report.tex
Fix error with \bar{D} and disappearing y_2^0.

@@
 \begin{align}
-  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]y_0^0(\so{}) - \frac{4\sqrt{5}}{15}\bar{B}y_2^0(\so{}) + \nonumber\\ &\frac{4\bar{C}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
+  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]\bar{D}y_0^0(\so{}) - \frac{4\sqrt{5}}{15}\bar{B}\bar{D}y_2^0(\so{}) + \nonumber\\ &\frac{4\bar{C}\bar{D}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
 \label{eq:genpsf}
@@
 \begin{align}
-  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
+  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
+  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]\delta(l, m) - \frac{4\sqrt{5}}{15}\bar{B}\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4\bar{C}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{7}{4\sqrt{15}}\Bigg\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right]\nonumber\\ &\hspace{20em}+ 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\Bigg\}.
+  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]\bar{D}\delta(l, m) - \frac{4\sqrt{5}}{15}\bar{B}\bar{D}\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4\bar{C}\bar{D}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\Bigg\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right]\nonumber\\ &\hspace{20em}+ 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\Bigg\}.
 \end{align}

### 2018-05-02 notes/2018-02-23-spatio-angular-kernel/calculations/shmult.py

@@ -27,6 +27,7 @@ print("Working...")
 theta = Symbol('theta', real=True)
 phi = Symbol('phi', real=True)
 
+import pdb; pdb.set_trace() 
 # Calculate expansions
 b = 1
 for m1 in range(-b, b+1):

### 2018-05-03 notes/2018-04-19-polarizer-otf/report/report.tex
Redefine illumination constants to simplify. Fix signs on ill y_0^2.

@@
 \end{align}
+We can simplify this result further by redefining the constants and normalizing
+\begin{align}
+  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}, \label{eq:genpsf}
+\end{align}
+where
+\begin{subequations}
+\begin{align}
+  \tilde{A} &\equiv \cos^2(\alpha/2)\cos(\alpha),\\
+  \tilde{B} &\equiv \frac{1}{12}(\cos^2\alpha + 4\cos\alpha + 7).
+\end{align}\label{eq:coefficients}%
+\end{subequations}
 
 The light-sheet excitation point response function is given by Eq.
-\ref{eq:genpsf} in the limit of small NA which gives
+\ref{eq:genpsf} in the limit of small NA ($\tilde{A} \rightarrow 1$ and $\tilde{B} \rightarrow 1$) which gives
 \begin{align}
-  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) \propto y_0^0(\so{}) + \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
+  h^{\mh{z}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \equiv \lim_{\alpha \rightarrow 0} h^{\mh{z}}_{\text{exc}}(\so{}) = y_0^0(\so{}) - \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) \propto y_0^0(\so{}) + \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
+  h^{\mh{x}, \text{ls}}_{\text{exc}}(\so{}; \mh{p}) = y_0^0(\so{}) - \frac{1}{\sqrt{5}}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}y_2^0(\so{}) + \frac{1}{2}y_2^2(\so{})\right] + 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})y_2^{-1}(\so{})\right\}.
 \end{align}
@@
 \begin{align}
-  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) \propto\, &[2\bar{A} + (4/3)\bar{B}]\bar{D}\delta(l, m) - \frac{4\sqrt{5}}{15}\bar{B}\bar{D}\delta(l-2, m)(\so{}) + \nonumber\\ &\frac{4\bar{C}\bar{D}}{\sqrt{15}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
-  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) \propto\, &\delta(l,m) + \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\Bigg\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right]\nonumber\\ &\hspace{20em}+ 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\Bigg\}.
+  H^{m,\mh{z}}_{l,\text{exc}}(\mh{p}) &= \delta(l, m) - \frac{1}{\sqrt{5}}\tilde{A}\delta(l-2, m)(\so{}) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2, m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{z}, \text{ls}}_{l,\text{exc}}(\mh{p}) &= \delta(l,m) - \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]\delta(l-2,m-2) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})\delta(l-2, m+2)\right\},\\
+  H^{m,\mh{x}, \text{ls}}_{l, \text{exc}}(\mh{p}) &= \delta(l,m) - \frac{1}{\sqrt{5}}\delta(l-2, m) + \sqrt{\frac{3}{5}}\Bigg\{[(\mh{p}\cdot\mh{z})^2 - (\mh{p}\cdot\mh{y})^2]\left[\frac{\sqrt{3}}{2}\delta(l-2,m) + \frac{1}{2}\delta(l-2, m-2)\right]\nonumber\\ &\hspace{20em}+ 2(\mh{p}\cdot\mh{z})(\mh{p}\cdot\mh{y})\delta(l-2, m+1)\Bigg\}.
 \end{align}

### 2018-05-04 notes/2018-05-02-multiframe-svd/report/report.tex
Early draft of svd notes with PSF and OTF for fluopolscope.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathbf{#1}}
\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Singular value decomposition of multiframe\\ polarized
  fluorescence microscopes\vspace{-1em}} \author{Talon Chandler, Min Guo, Hari
  Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will develop the continuous models for several multiframe
polarized fluorescence microscopes. For each design we will calculate the
spatio-angular point spread function, optical transfer function, and singular
system consisting of the singular values, object-space singular functions, and
data-space singular functions.

All of the microscopes we will consider are imaging fields of oriented
fluorophores. To a good approximation any field of oriented fluorophores can be
represented by a member of the set
$\mbb{U} = \mbb{L}_2(\mbb{R}^3 \times \mbb{S}^2)$---square-integrable functions
that assign a scalar value to each position and orientation.

We will be considering multiframe microscopes that capture multiple images of
the same object (we assume that the object is static over the imaging time). The
data for the $i$th frame can be represented by a member of
$\mbb{V}_i = \mbb{L}_2(\mbb{R}^{N})$---square-integrable functions that assign a
scalar value to each point in a $2$-dimensional Euclidean space. If the
microscope collects $N$ frames, then all of the data can be represented by a
member of the larger set $\mbb{V} = \mbb{L}_2(\mbb{R}^{2N})$---square-integrable
functions that assign a scalar value to each point in a $2N$-dimensional
Euclidean space. We can say that the complete data space $\mbb{V}$ is built by
taking the \textit{orthogonal direct sum} of the data space for each frame
$\mbb{V}_i$
\begin{align}
  \mbb{V} = \bigoplus_{i=1}^N \mbb{V}_i.
\end{align}
Notice that we are assuming that data space is continuous---we
are ignoring the effects of finite pixels and a finite field-of-view.

We can model any linear relationship between object space and data space using
an integral transform
\begin{align}
  g(\mathfrak{r}_d) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\mathfrak{r}_d; \ro{}, \so{})f(\ro{}, \so{}), \label{eq:full}
\end{align}
where $g(\mathfrak{r}_d) \in \mbb{U}$ is the data, $f(\ro{}, \so{}) \in \mbb{V}$
is the object, and $h(\mathfrak{r}_d; \ro{}, \so{}) \in \mbb{U} \times \mbb{V}$ is
the point response function of the imaging system. Notice that $\mathfrak{r}_d$
is a 2$N$-dimensional coordinate where the first two dimensions are the
coordinates of the first image, the next two dimensions are the coordinates of
the second image, and so on. Usually it will be more convenient for us to
rewrite Eq.~\ref{eq:full} as the sum of $N$ terms
\begin{align}
    g(\mathfrak{r}_d) = \sum_{i=1}^N \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{}), \label{eq:sys2}
\end{align}
where $\rd{}$ is a 2-dimensional coordinate for each frame. We can also rewrite
the forward model as $N$ separate equations
\begin{align}
    g_i(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{}),\qquad i=1, 2,\ldots,N, \label{eq:system}
\end{align}
but this is potentially less convenient than Eqs. \ref{eq:full} and
\ref{eq:sys2} because it hides the fact there is a single integral transform
that relates object space to data space.

In these notes we'll only be considering shift-invariant microscopes, so we can
simplify the model to
\begin{align}
    g(\mathfrak{r}_d) = \sum_{i=1}^N \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{} - \ro{}, \so{})f(\ro{}, \so{}). \label{eq:sys3}
\end{align}
We can rewrite the complete forward model in Eq. \ref{eq:sys3}) more compactly
using operator notation
\begin{align}
  g(\mathfrak{r}_d) = [\mathcal{H}\mathbf{f}](\mathfrak{r}_d).
\end{align}
In these notes we will ignore magnification---in the previous notes we showed
that we can make a change of variables that puts a system with magnification in
the form of a system without magnification. In other words, we can drop the
primes that indicated magnified quantities in previous note sets. We will also
restrict ourselves to the paraxial approximation and drop the $(p)$
superscripts.

\section{Polarized epi-illumination with unpolarized epi-detection}
We will start by restricting our analysis of epi-illumination microscopes to
in-focus objects. This means that our object space is
$\mbb{L}_2(\mbb{R}^2 \times \mbb{S}^2)$.

\subsection{Point response function}
In the previous notes we showed that the excitation point response function for
polarized epi-illumination is given by
\begin{align}
  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}, \label{eq:genpsf}
\end{align}
where
\begin{subequations}
\begin{align}
  \tilde{A} &\equiv \cos^2(\alpha/2)\cos(\alpha),\\
  \tilde{B} &\equiv \frac{1}{12}(\cos^2\alpha + 4\cos\alpha + 7),
\end{align}\label{eq:coefficients}%
\end{subequations}
and $\alpha \equiv \arcsin(\text{NA}/n_o)$.

We also showed that the point response function for unpolarized epi-detection is
given by
\begin{align}
  h_{\text{det}}(\ro{}, \so{}) &= [{a}^2(r_o) + 2b^2(r_o)]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a^2(r_o) + 4b^2(r_o)\right]y_2^0(\so{}),
\end{align}
where
\begin{align}
  a(r_o) = \frac{J_1(2\pi \nu_or_o)}{\pi \nu_or_o}, 
  &\hspace{2em}
    b(r_o) = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o)}{\pi \nu_or_o}\right],  \label{eq:abparadef}
  \intertext{and}
  \nu_o \equiv \frac{\text{NA}}{\lambda},&\hspace{2em}
  \text{NA} = n_o\sin\alpha.
\end{align}
The excitation and detection processes are incoherent, so to find the complete
point response function we can multiply the excitation and detection point response
functions which gives
\begin{align}
  h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \frac{1}{\tilde{N}}\sum_{l=0}^{\infty}\sum_{m=-l}^l h_l^m(\ro{}; \mh{p})y_l^m(\so{}), 
\end{align}
where $\tilde{N} = \frac{\tilde{A}}{10} + \frac{1}{2}$ is a normalization constant
and the terms in the series are given by
\begin{align}
  h_0^0(r_o) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]a^2(r_o) + \left[-\frac{2\tilde{A}}{5} + 1\right]b^2(r_o),\\
  h_2^{-2}(r_o; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
  h_2^0(r_o) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]a^2(r_o) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]b^2(r_o),\\
  h_2^2(r_o; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
  h_4^{-2}(r_o; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
  h_4^0(r_o) &= \frac{3\tilde{A}}{35}[a^2(r_o) - 4b^2(r_o)],\\
  h_4^2(r_o; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
\end{align}
and all other $h_l^m$ terms in the series are zero. Finally, the complete
forward model for this class of microscope is given by
\begin{align}
    g(\mathfrak{r}_d) = \sum_{i=1}^N\int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} - \ro{}, \so{}; \mh{p}_i)f(\ro{}, \so{}),\qquad i=1, 2,\ldots,N. \label{eq:fwdpolillum}
\end{align}
Notice that we have used a single function $h(\rd{} - \ro{}, \so{}; \mh{p}_i)$
to describe the complete imaging system, and we have shifted the index $i$ to
the illumination polarization. A typical choice of frames is given by $N=4$ and
\begin{align}
  \mh{p}_1 = \mh{x},\hspace{2em}
  \mh{p}_2 = \frac{1}{\sqrt{2}}(\mh{x} + \mh{y}),\hspace{2em}
  \mh{p}_3 = \mh{y},\hspace{2em}
  \mh{p}_4 = \frac{1}{\sqrt{2}}(\mh{x} - \mh{y}). 
\end{align}
\indent The point response function of the microscope now contains seven terms
in the $l=0$, 2, and 4 bands. Each term is radially symmetric which means that
we expect a radially symmetric point spread function for any angular
distribution of fluorophores. Notice that the $h_l^0$ terms do not depend on the
polarizer orientation, while the $h_l^{-2}$ and $h_l^{2}$ do depend on the
polarizer orientation. This is because the fluorophore distributions
corresponding to the $h_l^0$ terms are rotationally symmetric about the optic
axis, while the other terms are not rotationally symmetric.

\subsection{Optical transfer function}
The optical transfer function for this microscope is given by
\begin{align}
  H_l^m(\nu; \mh{p}) = \frac{1}{\tilde{M}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'} H_{l'}^{m'}(\nu; \mh{p})\delta(l - l', m - m'),  
\end{align}
where
$\tilde{M} = \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right] + \left(\frac{\text{NA}}{n_o}\right)\left[-\frac{2\tilde{A}}{10} + \frac{1}{2}\right]$ is a
normalization constant, and
\begin{align}
  H_0^0(\nu) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]A(\nu) + \left[-\frac{2\tilde{A}}{5} + 1\right]B(\nu),\\
  H_2^{-2}(\nu; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
  H_2^0(\nu) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]A(\nu) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]B(\nu),\\
  H_2^2(\nu; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
  H_4^{-2}(\nu; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
  H_4^0(\nu) &= \frac{3\tilde{A}}{35}[A(\nu) - 4B(\nu)],\\
  H_4^2(\nu; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
\end{align}
all other $H_l^m$ terms in the series are zero, and  
\begin{align}
  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).                 
\end{align}

\subsection{Singular system}
% To find the singular system of the microscope we will carry out four steps.
% First, we will calculate the kernel of the microscope given by
% \begin{align}
%   k(\ro{} - \ro{}', \so{}, \so{}') = \sum_{i=0}^N\int_{\mathbb{R}^2}d\rd{}\, h(\rd{} - \ro{}, \so{})h(\rd{} - \ro{}', \so{}').
% \end{align}
% Second, we will use the kernel to set up the eigenvalue problem
% \begin{align}
%   [\mathcal{H}^{\dagger}\mathcal{H}]\mb{f}](\ro{}, \so{}) = \int_{\mbb{S}^2}d\so{}'\int_{\mbb{R}^2}d\ro{}'\, k(\ro{} - \ro{}', \so{}, \so{}')f(\ro{}', \so{}). \label{eq:eigeq}
% \end{align}
% Third, we will postulate the form of the eigenfunctions as a single spatial harmonic multiplied by a linear combination of spherical harmonics
% \begin{align}
%   u_{\bs{\rho},n}(\ro{}, \so{}) = \sum_{l=0}^\infty\sum_{m=-l}^l c_n^{lm}(\bs{\rho})y_l^m(\so{})\, \me{}^{-i 2\pi \ro{}\cdot\bs{\rho}}. \label{eq:eigfunc}
% \end{align}
% We will plug Eq. \ref{eq:eigfunc} into Eq. \ref{eq:eigeq} and solve for the
% singular values and object space singular vectors of the imaging system. Finally,
% we will find the data space singular vectors by calculating
% \begin{align}
%     v_{\bs{\rho},n,i}(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})u_{\bs{\rho},n}(\ro{}, \so{}),\qquad i=1, 2,\ldots,N, \label{eq:system}
% \end{align}

\bibliography{report}{}
\bibliographystyle{unsrt}

\end{document}

### 2018-05-04 notes/2018-05-02-multiframe-svd/calculations/gaunt-real.py

@@ -1,0 +1,88 @@
+# Tools for multiplying real spherical harmonics
+
+# Based on:
+# Herbert H.H. Homeier, E.Otto Steinborn,
+# Some properties of the coupling coefficients of real spherical harmonics
+# and their relation to Gaunt coefficients,
+# Journal of Molecular Structure
+# Volume 368, 1996, Pages 31-37, ISSN 0166-1280,
+# https://doi.org/10.1016/S0166-1280(96)90531-X.
+
+from util import *
+import numpy as np
+from sympy import *
+from sympy.physics.wigner import gaunt, wigner_3j, clebsch_gordan
+kd = KroneckerDelta
+
+# Heaviside function
+def hv(x):
+    if x > 0:
+        return 1
+    else:
+        return 0
+
+# Unitary matrix that transforms complex sh to real sh
+# See Eq. 12.
+def U(l, m, mu):
+    t1 = kd(m, 0)*kd(mu, 0)
+    t2 = hv(mu)*kd(m, mu)
+    t3 = hv(-mu)*I*((-1)**np.abs(m))*kd(m, mu)
+    t4 = hv(-mu)*(-I)*kd(m, -mu)
+    t5 = hv(mu)*((-1)**np.abs(m))*kd(m, -mu)
+    return  t1 + ((t2 + t3 + t4 + t5)/sqrt(2))
+
+# Real gaunt coefficients
+# See Eqs. 26. The sympy gaunt function does not use a complex conjugate.
+# This sum could be truncated using selection rules, but this is fairly quick.
+def Rgaunt(l1, l2, l3, m1, m2, m3):
+    result = 0
+    for m1p in range(-l1, l1+1):
+        U1 = U(l1, m1p, m1)
+        for m2p in range(-l2, l2+1):
+            U2 = U(l2, m2p, m2)
+            for m3p in range(-l3, l3+1):
+                U3 = U(l3, m3p, m3)
+                result += U1*U2*U3*gaunt(l1, l2, l3, m1p, m2p, m3p)
+    return sqrt(pi)*result
+
+# Multiply two vectors of real spherical harmonic coefficients. Vectors must
+# have the same length and be ordered like
+#
+# y_0^0, y_1^-1, y_1^0, y_1^1, y_2^-2, y_2^-1, ...
+#
+# Example:
+#
+# multiply_sh_coefficients([2, 1, 0, 0], [0, 1, 0, 0])
+#
[…]

### 2018-05-04 notes/2018-05-02-multiframe-svd/calculations/kernel.py

@@ -1,0 +1,45 @@
+import numpy as np
+from mpmath import *
+from sympy import *
+from sympy.matrices.dense import *
+import functools
+
+# Analytical spherical fourier transform
+import sympy.functions.special.spherical_harmonics as sh
+def sft(f, max_l=4, odd_l=False):
+    coeffs = []
+    for l in range(0 + odd_l, max_l+2, 2):
+        for m in range(-l, l+1):
+            print("Integrating: "+ str(l) + ', ' + str(m))
+            Znm = sh.Znm(l, m, theta, phi).expand(func=True)
+            Znm = simplify(Znm) # Try this
+            # import pdb; pdb.set_trace() 
+            theta_int = integrate(expand_trig(sin(theta)*Znm*f), (theta, 0, pi))
+            final_int = integrate(expand_trig(theta_int.rewrite(cos)), (phi, 0, 2*pi))
+            print(simplify(final_int))
+            coeffs.append(final_int)
+    return np.array(coeffs)
+
+# Polar fourier transform
+
+print("Working...")
+
+# Symbols
+Theta = Symbol('Theta')
+Phi = Symbol('Phi')
+theta = Symbol('theta', real=True)
+phi = Symbol('phi', real=True)
+
+# Calculate internal integrals
+
+# Make these symbols for now
+A = Symbol('A', real=True)
+B = Symbol('B', real=True)
+C = Symbol('C', real=True)
+D = Symbol('D', real=True)
+
+# Calculate intensity
+I = A + B*(sin(theta)**2) + C*(sin(theta)**2)*cos(2*(phi - Phi))
+
+# Expand onto spherical harmonics
+x = sft(I, max_l=4, odd_l=False)

### 2018-05-04 notes/2018-05-02-multiframe-svd/calculations/util.py

@@ -1,0 +1,142 @@
+import numpy as np
+from PIL import Image
+from scipy import special
+
+# PSF functions
+def scalar_a(x):
+    if x == 0:
+        return 1.0
+    else:
+        return (special.jn(1,2*np.pi*x)/(np.pi*x))**2
+a = np.vectorize(scalar_a)
+
+def s_b(x, NA=0.8, n=1.33):
+    if x == 0:
+        return 0
+    else:
+        return (NA/n)**2*(special.jn(2,2*np.pi*x)/(np.pi*x))**2
+b = np.vectorize(s_b)
+
+def h00(r_o, phi=0, NA=0.8, n=1.33, phi_p=None):
+    if phi_p==None:
+        return a(r_o) + 2*b(r_o, NA, n)
+    else:
+        return a(r_o) + 4*b(r_o, NA, n)*(np.cos(phi - phi_p)**2)
+        
+def h20(r_o, phi=0, NA=0.8, n=1.33, phi_p=None):
+    if phi_p==None:
+        return (1/np.sqrt(5))*(-a(r_o) + 4*b(r_o, NA, n))
+    else:
+        return (1/np.sqrt(5))*(-a(r_o) + 8*b(r_o, NA, n)*(np.cos(phi - phi_p)**2))
+
+def h22(r_o, phi=0, NA=0.8, n=1.33, phi_p=None):
+    if phi_p==None:
+        return np.zeros(r_o.shape)
+    else:
+        return np.sqrt(3.0/5.0)*a(r_o)*(np.cos(phi_p)**2 - np.sin(phi_p)**2)
+
+def h2_2(r_o, phi=0, NA=0.8, n=1.33, phi_p=None):
+    if phi_p==None:
+        return np.zeros(r_o.shape)
+    else:
+        return -2*np.sqrt(3.0/5.0)*a(r_o)*np.cos(phi_p)*np.sin(phi_p)
+    
+# OTF functions
+def myacos(x):
+    return np.nan_to_num(np.arccos(np.abs(x/2)))
+    
+def mysqrt(x):
+    return np.nan_to_num((np.abs(x/2))*np.sqrt(1 - (np.abs(x/2))**2))
+
+def mycubert(x):
+    return np.nan_to_num((np.abs(x/2))*((1 - (np.abs(x/2))**2)**(1.5)))
+
+def A(x):
+    return (2/np.pi)*(myacos(x) - mysqrt(x))
+
[…]

### 2018-05-08 notes/2018-05-02-multiframe-svd/report/report.tex
More details in notes on SVD calculation.

@@
 the same object (we assume that the object is static over the imaging time). The
-data for the $i$th frame can be represented by a member of
-$\mbb{V}_i = \mbb{L}_2(\mbb{R}^{N})$---square-integrable functions that assign a
+data for the $n$th frame can be represented by a member of
+$\mbb{V}_n = \mbb{L}_2(\mbb{R}^{2})$---square-integrable functions that assign a
 scalar value to each point in a $2$-dimensional Euclidean space. If the
@@
 taking the \textit{orthogonal direct sum} of the data space for each frame
-$\mbb{V}_i$
+$\mbb{V}_n$
 \begin{align}
-  \mbb{V} = \bigoplus_{i=1}^N \mbb{V}_i.
+  \mbb{V} = \bigoplus_{n=1}^N \mbb{V}_n.
 \end{align}
-Notice that we are assuming that data space is continuous---we
-are ignoring the effects of finite pixels and a finite field-of-view.
+Notice that we are assuming that data space is continuous---we are ignoring the
+effects of finite pixels and a finite field-of-view.
 
@@
 \begin{align}
-  g(\mathfrak{r}_d) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\mathfrak{r}_d; \ro{}, \so{})f(\ro{}, \so{}), \label{eq:full}
+  g_n(\rd{}) = [\mathcal{H}f]_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_n(\rd{}; \ro{}, \so{})f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N, \label{eq:full}
 \end{align}
-where $g(\mathfrak{r}_d) \in \mbb{U}$ is the data, $f(\ro{}, \so{}) \in \mbb{V}$
-is the object, and $h(\mathfrak{r}_d; \ro{}, \so{}) \in \mbb{U} \times \mbb{V}$ is
-the point response function of the imaging system. Notice that $\mathfrak{r}_d$
-is a 2$N$-dimensional coordinate where the first two dimensions are the
-coordinates of the first image, the next two dimensions are the coordinates of
-the second image, and so on. Usually it will be more convenient for us to
-rewrite Eq.~\ref{eq:full} as the sum of $N$ terms
-\begin{align}
-    g(\mathfrak{r}_d) = \sum_{i=1}^N \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{}), \label{eq:sys2}
-\end{align}
-where $\rd{}$ is a 2-dimensional coordinate for each frame. We can also rewrite
-the forward model as $N$ separate equations
-\begin{align}
-    g_i(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})f(\ro{}, \so{}),\qquad i=1, 2,\ldots,N, \label{eq:system}
-\end{align}
-but this is potentially less convenient than Eqs. \ref{eq:full} and
-\ref{eq:sys2} because it hides the fact there is a single integral transform
-that relates object space to data space.
+where $g_n(\rd{}) \in \mbb{V}_n$ is the data for the $n$th frame,
+$f(\ro{}, \so{}) \in \mbb{U}$ is the object, and
+$h_n(\rd{}; \ro{}, \so{}) \in \mbb{U} \times \mbb{V}_n$ is the point response
+function of the imaging system for the $n$th frame.
 
@@
 \begin{align}
-    g(\mathfrak{r}_d) = \sum_{i=1}^N \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{} - \ro{}, \so{})f(\ro{}, \so{}). \label{eq:sys3}
-\end{align}
-We can rewrite the complete forward model in Eq. \ref{eq:sys3}) more compactly
-using operator notation
-\begin{align}
-  g(\mathfrak{r}_d) = [\mathcal{H}\mathbf{f}](\mathfrak{r}_d).
+  g_n(\rd{}) = [\mathcal{H}f]_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_n(\rd{} - \ro{}, \so{})f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N. \label{eq:full}
 \end{align}
@@
 superscripts.
+
+\section{Calculating the singular value decomposition}
+In this section we will lay out the steps to calculate the singular value
+decomposition of a multiframe polarized fluorescence microscope. We will follow
+Section 2A of \cite{burvall06} closely and find the data-space singular
+functions first. In Patrick's notes we found the object-space singular functions
+first, but both approaches will give identical results and the eigenvalue
+problem is smaller for the data-space singular functions.
+
+The forward operator for the system is given by
+\begin{align}
+    [\mathcal{H}f]_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_n(\rd{} - \ro{}, \so{})f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N, \label{eq:fwd}
+\end{align}
+and the adjoint operator for the system is given by
+\begin{align}
+    [\mathcal{H}^{\dagger}\mb{g}](\ro{}, \so{}) = \sum_{j=1}^N\int_{\mbb{R}^2}d\mb{r}_{d}\, h_n(\rd{} - \ro{}, \so{})g(\rd{}).\label{eq:adj}
+\end{align}
+We will also need the data-space to data-space operator
+\begin{align}
+  [\mathcal{H}\mathcal{H}^{\dagger}\mb{g}]_n(\rd{}) = \sum_{n'=1}^N\int_{\mbb{R}^2}d\rd{}'\, k_{nn'}(\rd{} - \rd{}')g_{n'}(\rd{}'), \label{eq:backfwd}
+\end{align}
+where 
+\begin{align}
+  k_{nn'}(\rd{} - \rd{}') &= \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h_n(\rd{} - \ro{}, \so{})h_{n'}(\rd{} - \ro{}, \so{}). \label{eq:kern}
+\end{align}
+To find the data-space singular functions and singular values, we need to
+solve the following eigenequation
+\begin{align}
+  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho}, j}]_n(\rd{}) = \mu_{\bs{\rho}, n} \mb{v}_{\bs{\rho}, j}(\rd{}). \label{eq:eigval}
+\end{align}
+where $\mb{v}_{\bs{\rho}, j}(\rd{})$ are the data-space eigenfunctions and
+$\mu_{\bs{\rho}, j}$ are the eigenvalues. Each $\mb{v}_{\bs{\rho}, j}(\rd{})$ is
+an $N\times 1$ vector where each element is a function of $\rd{}$. The eigenfunctions $\mb{v}_{\bs{\rho}, j}(\rd{})$ are indexed by a
+continuous two-dimensional vector index $\bs{\rho}$ associated with the
+transverse directions and a discrete index $j$ associated with the angular
+directions. Since the imaging system is linear shift invariant, the lateral part
+of the data-space eigenfunctions will be complex exponentials. We still need to
+solve for the angular part, so the data-space eigenfunctions will be in the form
+\begin{align}
+  \mb{v}_{\bs{\rho},j}(\rd{}) = \mb{V}_j(\bs{\rho})\me{}^{i 2\pi \bs{\rho}\cdot\rd{}}. \label{eq:eigfunc}
+\end{align}
+Inserting Eqs. \ref{eq:eigfunc} and \ref{eq:kern} into \ref{eq:backfwd} yields
+\begin{align}
+  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho},j}]_n(\rd{}) = \me{}^{i 2\pi \ro{}\cdot\bs{\rho}} \sum_{n'=1}^N K_{nn'}(\bs{\rho})[\mb{V}_j(\bs{\rho})]_{n'}, \label{eq:exp}
+\end{align}
+where
+\begin{align}
+  K_{nn'}(\bs{\rho}) = \int_{\mbb{R}^2}d\rd{}'\, k_{nn'}(\rd{}')\me{}^{-i 2\pi \bs{\rho}\cdot\rd{}'}. \label{eq:kft}
+\end{align}
+Comparing Eqs. \ref{eq:eigfunc} and \ref{eq:exp} yield the eigenvalue problem
+\begin{align}
+  \mathsf{K}(\bs{\rho})\mb{V}_j(\bs{\rho}) = \mu_{\bs{\rho}, j}\mb{V}_j(\bs{\rho}), \label{eq:evp}
+\end{align}
+where $\mathsf{K}(\bs{\rho})$ is an $N\times N$ matrix containing the elements
+$K_{nn'}(\bs{\rho})$. To simplify the calculation of the elements
+$K_{nn'}(\bs{\rho})$ we notice that we need to take the Fourier transform (Eq.
+\ref{eq:kft}) of the autocorrelation of the spatio-angular point spread function
+(Eq. \ref{eq:kern}). We can use the autocorrelation theorem to relate the
+elements of $\mathsf{K}(\bs{\rho})$ to the spatio-angular optical transfer
+function as
+\begin{align}
+  K_{nn'}(\bs{\rho}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l H_{l,n}^m(\bs{\rho}) H_{l,n'}^m(\bs{\rho}). \label{eq:ksimp}
+\end{align}
+Once we have solved the $N\times N$ eigenvalue problem in Eq. \ref{eq:evp} for
+each value of $\bs{\rho}$, we can build the complete data-space eigenfunctions using
+Eq. \ref{eq:eigfunc}. Finally, we can calculate the object-space eigenfunctions from
+the data-space eigenfunctions using
+\begin{align}
+  [\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho},j}](\ro{}, \so{}) = \sqrt{\mu_{\bs{\rho}, j}}u_{\bs{\rho},j}(\ro{}, \so{}).
+\end{align}
+Plugging in Eq. \ref{eq:adj} and solving for $u_{\bs{\rho},j}(\ro{}, \so{})$ yields
+\begin{align}
+  u_{\bs{\rho},j}(\ro{}, \so{}) = \frac{1}{\sqrt{\mu_{\bs{\rho},j}}}\me{}^{i2\pi\bs{\rho}\cdot\ro{}}\sum_{n=1}^N[\mb{V}_j(\bs{\rho})]_n \sum_{l=0}^{\infty}\sum_{m=-l}^l H_{l,n}^m(\bs{\rho})y_l^m(\so{}).
+\end{align}
+As we'd expect from Patrick's notes, we can rewrite the object-space singular
+functions as a complex exponential multiplied by a linear combination of
+spherical harmonics
+\begin{align}
+u_{\bs{\rho},j}(\ro{}, \so{}) = U_j(\bs{\rho}, \so{}) \me{}^{i2\pi\bs{\rho}\cdot\ro{}},
+\end{align}
+where
+\begin{align}
+  U_{\bs{\rho},j}(\ro{}, \so{}) = \frac{1}{\sqrt{\mu_{\bs{\rho},j}}}\sum_{n=1}^N[\mb{V}_j(\bs{\rho})]_n \sum_{l=0}^{\infty}\sum_{m=-l}^l H_{l,n}^m(\bs{\rho})y_l^m(\so{}).
+\end{align}
+In summary, these are the steps to calculate the singular system for a
+polarized multiframe microscope.
+\begin{enumerate}
+\item Calculate the spatio-angular point spread function
+  $h_n(\rd{} - \ro{}, \so{})$ for $n = 1, 2, \ldots, N$.
+\item Calculate the spatio-angular optical transfer function
+  $H_{l,n}^{m}(\bs{\nu})$ for $n = 1, 2, \ldots, N$.
+\item Calculate the elements of the matrix $\mathsf{K}(\bs{\rho})$ using
+  $K_{nn'}(\bs{\rho}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l H_{l,n}^m(\bs{\rho}) H_{l,n'}^m(\bs{\rho})$.
+\item Solve the eigenvalue problem
+  $\mathsf{K}(\bs{\rho})\mb{V}_j(\bs{\rho}) = \mu_{\bs{\rho}, j}\mb{V}_j(\bs{\rho})$ at each value of $\bs{\rho}$. Store the eigenvalues $\mu_{\bs{\rho}, j}$ and eigenvectors $\mb{V}_j(\bs{\rho})$. 
+\item Calculate the data-space singular functions using $\mb{v}_{\bs{\rho},j}(\rd{}) = \mb{V}_j(\bs{\rho})\me{}^{i 2\pi \bs{\rho}\cdot\rd{}}$.
+\item Calculate the object-space singular functions using
+  \begin{align}
+   u_{\bs{\rho},j}(\ro{}, \so{}) = \frac{1}{\sqrt{\mu_{\bs{\rho},j}}}\me{}^{i2\pi\bs{\rho}\cdot\ro{}}\sum_{n=1}^N[\mb{V}_j(\bs{\rho})]_n \sum_{l=0}^{\infty}\sum_{m=-l}^l H_{l,n}^m(\bs{\rho})y_l^m(\so{}).
+  \end{align}
+\end{enumerate}
+
+Under the paraxial approximation we will be able to perform steps 1 and 2
+analytically. We could perform step 3 analytically, but I don't think this step
+will yield much insight so I will do it numerically. Step 4 can be performed
+analytically for $N \leq 4$ ($N > 4$ yields a quintic equation which has no
+solution in terms of radicals), but I will solve it numerically in all of the
+cases we'll consider. Steps 5 and 6 can be carried out numerically.
+
+Outside of the paraxial approximation we will only be able to write the
+spatio-angular point spread function in terms of an integral, so we will
+perform all steps numerically. In these notes we'll only consider the paraxial
+case, though.
 
@@
 \begin{align}
-    g(\mathfrak{r}_d) = \sum_{i=1}^N\int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} - \ro{}, \so{}; \mh{p}_i)f(\ro{}, \so{}),\qquad i=1, 2,\ldots,N. \label{eq:fwdpolillum}
+    g_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} - \ro{}, \so{}; \mh{p}_n)f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N. \label{eq:fwdpolillum}
 \end{align}
-Notice that we have used a single function $h(\rd{} - \ro{}, \so{}; \mh{p}_i)$
-to describe the complete imaging system, and we have shifted the index $i$ to
+Notice that we have used a single function $h(\rd{} - \ro{}, \so{}; \mh{p}_n)$
+to describe the complete imaging system, and we have shifted the index $n$ to
 the illumination polarization. A typical choice of frames is given by $N=4$ and
@@
 
-\subsection{Singular system}
-% To find the singular system of the microscope we will carry out four steps.
-% First, we will calculate the kernel of the microscope given by
-% \begin{align}
-%   k(\ro{} - \ro{}', \so{}, \so{}') = \sum_{i=0}^N\int_{\mathbb{R}^2}d\rd{}\, h(\rd{} - \ro{}, \so{})h(\rd{} - \ro{}', \so{}').
-% \end{align}
-% Second, we will use the kernel to set up the eigenvalue problem
-% \begin{align}
-%   [\mathcal{H}^{\dagger}\mathcal{H}]\mb{f}](\ro{}, \so{}) = \int_{\mbb{S}^2}d\so{}'\int_{\mbb{R}^2}d\ro{}'\, k(\ro{} - \ro{}', \so{}, \so{}')f(\ro{}', \so{}). \label{eq:eigeq}
-% \end{align}
-% Third, we will postulate the form of the eigenfunctions as a single spatial harmonic multiplied by a linear combination of spherical harmonics
-% \begin{align}
-%   u_{\bs{\rho},n}(\ro{}, \so{}) = \sum_{l=0}^\infty\sum_{m=-l}^l c_n^{lm}(\bs{\rho})y_l^m(\so{})\, \me{}^{-i 2\pi \ro{}\cdot\bs{\rho}}. \label{eq:eigfunc}
-% \end{align}
-% We will plug Eq. \ref{eq:eigfunc} into Eq. \ref{eq:eigeq} and solve for the
-% singular values and object space singular vectors of the imaging system. Finally,
-% we will find the data space singular vectors by calculating
-% \begin{align}
-%     v_{\bs{\rho},n,i}(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_i(\rd{}; \ro{}, \so{})u_{\bs{\rho},n}(\ro{}, \so{}),\qquad i=1, 2,\ldots,N, \label{eq:system}
-% \end{align}
-
 \bibliography{report}{}

### 2018-05-11 notes/2018-05-02-multiframe-svd/calculations/products.py
SVD notes upate and slides. Single view SVS.

@@ -1,0 +1,9 @@
+from polharmonic import det, shcoeffs
+import numpy as np
+
+x = shcoeffs.SHCoeffs([1,0,0,1,0,0])
+y = shcoeffs.SHCoeffs([1,1,0,1,0,1])
+xy = x*y
+x.plot(folder='mult/x')
+y.plot(folder='mult/y')
+xy.plot(folder='mult/xy')

### 2018-05-11 polharmonic/det.py

@@ -1,4 +1,5 @@
 import numpy as np
+import polharmonic.shcoeffs as sh
 import polharmonic.util as util
 from scipy import special
 
@@ -9,39 +10,50 @@ class Detector:
     By default we use the paraxial approximation.
     """
     def __init__(self, optical_axis=[0,0,1], na=0.8, n=1.33,
-                 polarizer=None, paraxial=True):
+                 polarizer=None, paraxial=True, detect_all=False):
         self.optical_axis = optical_axis        
         self.na = na
         self.n = n
         self.polarizer = polarizer
         self.paraxial = paraxial
+        self.detect_all = detect_all
 
     def h(self, r, phi=0):
-        # TOOD: Arbitrary optical axes; relax paraxial approximation
-        if self.polarizer is None:
-            return [a(r) + 2*b(r), 0, 0, (-a(r) + 4*b(r))/np.sqrt(5)]
+        if self.detect_all:
+            return sh.SHCoeffs([1.0, 0, 0, 0, 0, 0])
+        
+        a = self.a
+        b = self.b
+        p = self.polarizer
+        if p is None:
+            return sh.SHCoeffs([a(r) + 2*b(r), 0, 0, (-a(r) + 4*b(r))/np.sqrt(5)])
         else:
-            r_vec = [r*cos(phi), r*sin(phi), 0]
-            return [a(r) + 4*b(r)*np.dot(r_vec, self.polarizer)**2,
-                    np.sqrt(0.6)*a(r)*(self.polarizer[0]**2 - self.polarizer[1]**2),
-                    0,
-                    (-a(r) + 8*b(r)*np.dot(r_vec, self.polarizer)**2)/np.sqrt(5),
-                    0,
-                    -2*np.sqrt(0.6)*a(r)*(self.polarizer[0]**2 - self.polarizer[1]**2)]
+            r_vec = [np.cos(phi), np.sin(phi), 0]
+            return sh.SHCoeffs([a(r) + 4*b(r)*np.dot(r_vec, p)**2,
+                                -2*np.sqrt(0.6)*a(r)*p[0]*p[1],
+                                0,
[…]

### 2018-05-11 polharmonic/gaunt.py

@@ -45,6 +45,20 @@ def Rgaunt(l1, l2, l3, m1, m2, m3):
                 result += U1*U2*U3*gaunt(l1, l2, l3, m1p, m2p, m3p)
     return result.evalf()
 
+# Compute and save an array with all of the gaunt coefficients up to specified
+# band
+def calc_gaunt_tensor(filename, lmax=4):
+    jmax = myutil.maxl2maxj(lmax)
+    G = np.zeros((jmax, jmax, jmax))
+    for index, g in np.ndenumerate(G):
+        print(index)
+        l1, m1 = myutil.j2lm(index[0])
+        l2, m2 = myutil.j2lm(index[1])
+        l3, m3 = myutil.j2lm(index[2])
+        G[index] = Rgaunt(l1, l2, l3, m1, m2, m3)
+    np.save(filename, G)
+    return 1
+
 # Multiply two vectors of even band real spherical harmonic coefficients.
 # Vectors must have the same length and be ordered like
 #
@@ -55,6 +69,8 @@ def Rgaunt(l1, l2, l3, m1, m2, m3):
 # multiply_sh_coefficients([2, 1, 0, 0, 0, 0], [0, 1, 0, 0, 0, 0])
 #
 # gives the coefficients of (2y_0^0 + y_2^-2) x y_2^-2.
+#
+# Slow compared to precomputing the "gaunt tensor"---see shcoeffs.py
 def multiply_sh_coefficients(a, b):
     maxl, m = myutil.j2lm(len(a) - 1)
     c = [0]*(myutil.maxl2maxj(maxl + 2))

### 2018-05-11 polharmonic/ill.py

@@ -1,21 +1,43 @@
 import numpy as np
+import polharmonic.shcoeffs as sh
 import polharmonic.util as util
-from sympy import *
+from scipy import special
 
 class Illuminator:
-    """An Illuminator is specified by its optical axis and polarization orientation.
-    """
-    def __init__(self, theta_optical_axis=0, phi_pol=0):
-        self.theta_optical_axis = theta_optical_axis
-        self.phi_pol = phi_pol
+    """An Illuminator is specified by its optical axis, numerical aperture, 
+    the index of refraction of the sample, and polarizer orientation.
 
-    def exc_prf(self):
-        theta = Symbol('theta', real=True)
-        phi = Symbol('phi', real=True)
-        if self.theta_optical_axis == 0:
-            return (sin(theta)**2)*(cos(phi - np.deg2rad(self.phi_pol))**2)
-        elif self.theta_optical_axis == 90:
-            return ((sin(theta)*sin(phi)*sin(np.deg2rad(self.phi_pol)) - cos(theta)*cos(np.deg2rad(self.phi_pol)))**2)
+    By default we use the paraxial approximation.
+    """
+    def __init__(self, optical_axis=[0,0,1], na=0.8, n=1.33,
+                 polarizer=None, paraxial=True, illuminate_all=False):
+        self.optical_axis = optical_axis
+        self.na = na
+        self.n = n
+        
+        self.polarizer = polarizer
+        self.paraxial = paraxial
+        self.illuminate_all = illuminate_all
+
+        self.alpha = np.arcsin(self.na/self.n)
+        self.Atilde = (np.cos(self.alpha/2.0)**2)*np.cos(self.alpha)
+        self.Btilde = (1.0/12.0)*(np.cos(self.alpha/2)**2 + 4*np.cos(self.alpha) + 7)
+
+    def h(self):
+        if self.illuminate_all:
+            return sh.SHCoeffs([1.0, 0, 0, 0, 0, 0])
+        
+        p = self.polarizer
+        if p is None:
+            return sh.SHCoeffs([1, 0, 0, -self.Atilde/np.sqrt(5)])
         else:
-            print('Warning: theta_optical_axis must be 0 or 90')
-            return 0
+            return sh.SHCoeffs([1,
+                                -2*np.sqrt(0.6)*self.Btilde*p[0]*p[1],
+                                0,
+                                -self.Atilde/np.sqrt(5),
+                                0,
[…]

### 2018-05-11 polharmonic/micro.py

@@ -1,5 +1,8 @@
 import numpy as np
-from polharmonic import util, ill, det, sft
+from polharmonic import util, ill, det
+import matplotlib.pyplot as plt
+import matplotlib
+matplotlib.rcParams['contour.negative_linestyle'] = 'solid'
 
 class Microscope:
     """
@@ -10,39 +13,99 @@ class Microscope:
     and its detection path (a Detector object).
     """
     def __init__(self, ill=ill.Illuminator(), det=det.Detector(),
-                 color=(1,0,0)):
+                 color=(0,1,0.3)):
         self.ill = ill
         self.det = det
-        self.prf = self.ill.exc_prf()*self.det.det_prf()
+        self.h0 = self.ill.h()*self.det.h(0)
+        self.hnorm = (self.ill.h()*self.det.h(0)).coeffs[0]
+        self.Hnorm = (self.ill.H()*self.det.H(0)).coeffs[0]
         self.color = color
 
-    def Hlm(self, max_l=4):
-        self.Hlm = sft.sft(self.prf, max_l=max_l)
-        return self.Hlm
+    def h(self, r, phi=0):
+        return self.ill.h()*self.det.h(r, phi=phi)/self.hnorm
 
-    def plot_micro(filename=None):
-        # TODO 
-        return 0
+    def H(self, nu, phi_nu=0):
+        return self.ill.H()*self.det.H(nu, phi_nu=phi_nu)/self.Hnorm
+
+    def plot(self, func, filename='micro.pdf', n_px=2**7, plot_m=[-2, 0, 2]):
+        print('Plotting: ' + filename)
+        
+        # Calculate data for plotting
+        w = 2.05
+        [X, Y] = np.meshgrid(np.linspace(-w, w, n_px),
+                             np.linspace(-w, w, n_px))
+        R = np.sqrt(X**2 + Y**2)
+        Phi = np.nan_to_num(np.arctan(Y/X))
+
+        data = np.random.random((R.shape[0], R.shape[1], self.h0.coeffs.shape[0]))
+        for index, r in np.ndenumerate(R):
+            data[index[0], index[1], :] = (func(r, Phi[index])).coeffs
+        
+        # Layout windows
+        if plot_m is None:
+            cols = self.h0.rmax
+        else:
+            cols = len(plot_m)
+        
+        inches = 1
+        f, axs = plt.subplots(self.h0.rmax, cols,
+                              figsize=(inches*cols, inches*self.h0.rmax),
[…]

### 2018-05-11 polharmonic/shcoeffs.py

@@ -1,21 +1,34 @@
 import numpy as np
+import subprocess
 from polharmonic import util, gaunt
 import matplotlib.pyplot as plt
+from PIL import Image
+import os
+
+# Compute gaunt coefficients
+# gaunt.calc_gaunt_tensor('gaunt_l4.npy', lmax=4) # Expensive precomputation
+G = np.load(os.path.join(os.path.dirname(__file__), 'gaunt_l4.npy')) 
 
 class SHCoeffs:
     """An SHCoeffs object stores real spherical harmonic coefficients for even
-    bands. It provides methods for adding and multiplying these coefficients.
+    bands. It provides methods for adding, multiplying, and plotting these
+    coefficients.
 
     Inspired by a similar class in SHTOOLS https://shtools.github.io/SHTOOLS/
 
+    Uses the following "lexicographic ordering" of the even spherical harmonics:
+
+    y_0^0, y_2^-2, y_2^0, y_2^2, y_4^-4, ...
     """
 
     def __init__(self, coeffs):
         self.lmax, mm = util.j2lm(len(coeffs) - 1)
-        self.jmax = int(0.5*(self.lmax + 1)*(self.lmax + 2)) - 1
+        self.jmax = int(0.5*(self.lmax + 1)*(self.lmax + 2))
+        self.mmax = 2*self.lmax + 1
+        self.rmax = int(self.lmax/2) + 1
 
         # Fill the rest of the last band with zeros
-        temp = np.zeros(self.jmax + 1)
+        temp = np.zeros(self.jmax)
         temp[:len(coeffs)] = coeffs
         self.coeffs = temp
 
@@ -23,17 +36,33 @@ class SHCoeffs:
         return self.coeffs + other.coeffs
         
     def __mul__(self, other):
-        result = gaunt.multiply_sh_coefficients(self.coeffs, other.coeffs)
+        # result = gaunt.multiply_sh_coefficients(self.coeffs, other.coeffs)
+
+        # Pad inputs
+        x1 = np.pad(np.array(self.coeffs), (0, 2*(self.lmax + 2) + 1), 'constant')
+        x2 = np.pad(np.array(other.coeffs), (0, 2*(self.lmax + 2) + 1), 'constant')        
+
+        # Multiply
+        result = np.dot(np.dot(G, x1), x2)
+        
         return SHCoeffs(result)
 
-    def plot(self, ax='shcoeffs.pdf'):
-        print('test')
-        if isinstance(ax, str):
-            filename = ax
[…]

### 2018-05-11 polharmonic/util.py

@@ -1,163 +1,26 @@
-# import subprocess
-# import numpy as np
-# import matplotlib.pyplot as plt
-# import matplotlib.image as mpimg
+import subprocess
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
 # import matplotlib
 # from mayavi import mlab
-# from scipy.special import sph_harm
+from scipy.special import sph_harm
 # import scipy.misc
 # from skimage import io
 # import vispy
 # from polharmonic import visuals
 
-# # SciPy real spherical harmonics with identical interface to SymPy's Znm
-# # Useful for faster numerical evaluation of Znm
-# def spZnm(l, m, theta, phi):
-#     if m > 0:
-#         return np.real((sph_harm(m, l, phi, theta) +
-#                 np.conj(sph_harm(m, l, phi, theta)))/(np.sqrt(2)))
-#     elif m == 0:
-#         return np.real(sph_harm(m, l, phi, theta))
-#     elif m < 0:
-#         return  np.real((sph_harm(m, l, phi, theta) -
-#                  np.conj(sph_harm(m, l, phi, theta)))/(np.sqrt(2)*1j))
-
-# # Draw microscope schematic (move to Microscope class?)
-# def draw_scene(scene_string, filename='out.png', my_ax=None, dpi=300,
-#                save_file=False, chop=True):
-#     asy_string = """
-#     import three;
-#     import graph3;
-#     settings.outformat = "pdf";
-#     settings.prc = true;
-#     settings.embed= true;
-#     settings.render=16;
-
-#     size(6cm,6cm);
-#     currentprojection = orthographic(1, 1, 1);
-
-#     void circle(real Theta, real Alpha, bool dash, triple color) {
-#       triple normal = expi(Theta, 0);
-#       real h = 1 - sqrt(2 - 2*cos(Alpha) - sin(Alpha)^2);
-#       real radius = sin(Alpha);
-#       path3 mycircle = circle(c=h*normal, r=radius, normal=normal);
-#       if (dash) {
-#         draw(mycircle, p=linetype(new real[] {8,8}, offset=xpart(color))+rgb(xpart(color), ypart(color), zpart(color)));
-#       } else {
[…]

### 2018-05-12 notes/2018-05-12-geometry/report/report.tex
Geometry notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\mf}[1]{\mathbf{#1}}
\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Geometry of anisotropic media and polarized light
  microscopy data \vspace{-1em}} \author{Talon Chandler, Min Guo, Hari Shroff,
  Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
We describe the geometry of object space and data space for a large class of
polarized light microscopes. We briefly examine the mappings between object
and data spaces. Finally, we consider the transfer functions that can simplify
the mappings.

We denote the set of points on the $n$-dimensional real line $\mbb{R}^n$, the
set of points on the $n$-dimensional sphere $\mbb{S}^n$, and the set of
$n\times n$ Hermitian matrices $\mbb{H}^n$.

\section{Object spaces}
In fluorescence microscopy, the object is a three-dimensional field of oriented
fluorophores which can be described by a member of the set
$\mbb{L}_2(\mbb{R}^3\times\mbb{S}^2)$---the set of square integrable functions that
assign a scalar value to each direction at each point in 3D space.

In anisotropic microscopy, the object is a three-dimensional field of
anisotropic objects. Each point in the field can be described by its
generalized Jones matrix \cite{ortega13}---a $3\times3$ Hermitian matrix.
Although tempting, the object space is \textbf{not}
$\mbb{L}_2(\mbb{R}^3 \times \mbb{H}^3)$---the set of square integrable functions
that assigns a scalar value to each Hermitian matrix at each point in 3D
space---because the object only has a single Hermitian matrix at each point.
Instead, we will denote the object space as
$\mbb{L}_2(\mbb{R}^3; \mbb{H}^3)$---the set of square integrable functions that
assign a Hermitian matrix to each point in 3D space. Using this notation, the
objects in fluorescence microscopy would be members of the set
$\mbb{L}_2(\mbb{R}^3\times\mbb{S}^2; \mbb{H}^1)$ because $\mbb{H}^1$ are
scalars. Note that Barrett \cite{barrett2004} assumes scalar-valued functions so
the second argument of $\mbb{L}_2$ is assumed to be $\mbb{H}^1$. Meanwhile,
Sharafutdinov \cite{shara1994} makes no assumptions, so he only uses the second
argument and drops the first.

If we don't constrain the symmetric matrices, then
$\mbb{L}_2(\mbb{R}^3; \mbb{H}^3)$ can describe fields that display linear and
circular birefringence and dichroism. We often assume or know that our object
displays only birefringence or dichroism, and this prior can be formulated as a
constraint on the Hermitian matrix. Therefore, birefringence microscopy is a
subset of anisotropy microscopy. We will revisit these constraints later.

Also, we often assume or know that a birefringent object is uniaxial. To make
a Hermitian matrix describe a uniaxial object we constrain it to be rank 2.

\section{Data space}
The data space for a multiview microscope with variable polarizers on the
detection or illumination arm is a member of
$\mbb{V} = \mbb{L}_2(\mbb{S}^1\times\mbb{S}^2\times\mbb{R}^3)$ where the
$\mbb{S}^1$ dimension specifies the orientation of the detection or illumination
polarizer, the $\mbb{S}^2$ dimensions specify the optical axis of the view, and
the $\mbb{R}^3$ dimensions specifies the position on the 2D detector with 1D
defocusing. All of the polarized light microscopes we have considered so far
take discrete samples of $\mbb{V}$. Notice that $\mbb{V}$ is independent of the
object---we can use the same data space for fluorescence and anisotropy imaging.

Rudolf's existing PolScope designs take a single sample of the optical axis
dimensions (they are single view microscopes), four or five samples of the
polarizer dimension (one for each polarizer setting), and many samples of the
detector dimension (one for each pixel at each defocus position).

Our current diSPIM design takes two samples of the optical axis dimensions, four
samples of the polarizer dimension (eight would be double counting), and many
samples of the detector dimension.

Light-field designs take a dense sampling of the optical axis dimension over a
small range of angles at a single detector plane. Locally, $\mbb{S}^2$ is
approximated by $\mbb{R}^2$, and one slice of $\mbb{R}^3$ is $\mbb{R}^2$, so a
polarized light-field microscope's data space is approximately
$\mbb{L}_2(\mbb{S}^1\times\mbb{R}^4)$. This identification points towards a link
between our multiview analysis and Ng's 4-dimensional light-field analysis
\cite{ng2005}.

If we would like to consider microscopes with polarizers on the illumination and
detection arms, we can add an extra $\mbb{S}^1$ dimension and the data space
becomes $\mbb{L}_2(\mbb{S}^1\times\mbb{S}^1\times\mbb{S}^2\times\mbb{R}^3)$.

\section{Mapping object space to data space}
In fluorescence microscopy we can describe the relationship between the object
and data spaces using an integral transform
\begin{align}
    [\mathcal{H}f](\hat{\mb{s}}_v, \hat{\mb{p}}, \rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} -\ro{}, \so{}; \hat{\mb{s}}_v, \hat{\mb{p}})f(\ro{}, \so{}).\label{eq:beginning}
\end{align}
where $h(\rd{} -\ro{}, \so{}; \hat{\mb{s}}_v, \hat{\mb{p}})$ is the kernel of
the integral transform (when data space is larger than $\mbb{L}_2(\mbb{R}^2)$ I
think that ``kernel'' is more accurate than ``point spread function''). More
work is required to write the complete kernel for arbitrary viewing directions $\hat{\mb{s}}_v$.
The full kernel will be necessary for analyzing fluorescence light-field
microscopes.

I think we can make progress in anisotropic microscopy if we describe the
data as a spatially filtered tensor ray transform of the object. If we
illuminate the object incoherently (using a wide condenser back aperture under
K\"ohler illumination) and the sample is weakly anisotropic, then the electric
field at the output of the object will be the (input polarization dependent)
tensor ray transform of the object. Finally, we can propagate the output
electric field to the detector using the formalism we've developed for
fluorescence microscopy---this operation is essentially a low-pass spatial
filter.

Sharafutdinov 2.1.10 \cite{shara1994} gives an expressions for the tensor ray
transform that is a generalization of the Radon transform
\begin{align}
  [\mathcal{I}f](x, \xi) = \int \langle f(x + t\xi), \xi\rangle dt. 
\end{align}
I'm still digesting the details of how to evaluate this integral in practice,
but the analogy with the Radon transform and the physical meaning are clear.

The mapping between the object space and data space will look something like
\begin{align}
    [\mathcal{H}f](\hat{\mb{s}}_v, \hat{\mb{p}}, \rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{}; \hat{\mb{s}}_v, \hat{\mb{p}})[\mathcal{I}f](\ro{}, \so{}).\label{eq:final}
\end{align}
One difference between Eq. \ref{eq:beginning} and Eq. \ref{eq:final} is the
interpretation of the variable $\so{}$. In the fluorescence case, $\so{}$ refers
to the orientation of the dipole axis of a fluorophore. In the anisotropy case,
$\so{}$ refers to the propagation direction of a light ray.

The incoherence of the light incident on the sample is an important simplifying
assumption. If the incident light is partially coherent, then the relationship
between the object and data is a bilinear integral transform (see Barrett 5.2
\cite{barrett2004}, Goodman 7.4 \cite{goodman1985}). This type of relationship
does not allow for a simple transfer function analysis, but a transmission
cross-coefficient analysis is still possible.

\section{Transfer functions}
All of the mappings we considered in the previous section are linear, so we can
rewrite them in terms of the transfer function.

The first task is to find the geometry and dimension of the transfer function.
The transfer function must account for each dimension of the object and data
spaces while not double counting invariant dimensions between the spaces. For
example, a fluorescence microscope maps objects in
$\mbb{L}(\mbb{S}^2\times\mbb{R}^2)$ to data in
$\mbb{L}_2(\mbb{S}^1\times\mbb{S}^2\times\mbb{R}^2)$. The two spatial dimensions
are shift invariant, so we assign a single continuous spatial frequency index
$\bs{\nu}$ to those dimensions. I expect (calculation in progress) that the two
orientation dimensions are rotation invariant, so we can assign the indices $l$
and $m$ to those dimensions. Finally, we can assign the index $k$ to the data
space $\mbb{S}^1$ polarizer dimension. Therefore, the transfer function will be
of the form
\begin{align}
  H_{l,k}^{m}(\bs{\nu}) = \int_{\mbb{S}^1}d\hat{\mb{p}}\, z_k(\hat{\mb{p}}) \int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\rd{}\, \me^{-i2\pi\bs{\nu}\cdot\rd{}} h(\rd{} -\ro{}, \so{}; \hat{\mb{s}}_v, \hat{\mb{p}}),
\end{align}
where $y_l^m(\so{})$ are the real spherical harmonics and $z_k(\hat{\mb{p}})$
are the real circular harmonics.

I expect to find similar transfer functions for the anisotropy imaging case,
but I can't make much more progress until I spend more time understanding the
tensor ray transform. Sharafutdinov 2.1.15 \cite{shara1994} gives the
relationship between the an object's tensor ray transform and its Fourier
transform (a generalization of the Fourier-Slice theorem), but I don't
understand all of the notation yet.

I suspect that the nine Gell-Mann matrices will play a role in the Fourier
analysis of anisotropy microscopes \cite{ortega13}. The Gell-Mann matrices are
an orthonormal basis for $3\times 3$ Hermitian matrices $\mbb{H}^3$, so they
take the role of the spherical harmonics in fluorescence imaging. The Gell-Mann
matrices have direct physical interpretations in terms of birefringence and
dichroism of the object, so we can formulate physical priors about the object as
constraining specific Gell-Mann matrices to zero.

\bibliography{report}{}
\bibliographystyle{unsrt}

\end{document}

### 2018-05-15 notes/2018-05-02-multiframe-svd/report/report.tex
Patrick's comments.

@@
 \section{Introduction}
+% \textbf{Note:} While writing these notes I realized that multiframe microscopes
+% can be analyzed more generally by considering them as sampled versions of
+% continuous microscope designs. The results in these notes are correct, but I've
+% abandoned these notes to work on the continuous designs.
+
 In these notes we will develop the continuous models for several multiframe
@@
 \begin{align}
-    [\mathcal{H}f]_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_n(\rd{} - \ro{}, \so{})f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N, \label{eq:fwd}
+    g_n(\rd{}) = [\mathcal{H}f]_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h_n(\rd{} - \ro{}, \so{})f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N, \label{eq:fwd}
 \end{align}
@@
 \begin{align}
-    [\mathcal{H}^{\dagger}\mb{g}](\ro{}, \so{}) = \sum_{j=1}^N\int_{\mbb{R}^2}d\mb{r}_{d}\, h_n(\rd{} - \ro{}, \so{})g(\rd{}).\label{eq:adj}
+    [\mathcal{H}^{\dagger}\mb{g}](\ro{}, \so{}) = \sum_{j=1}^N\int_{\mbb{R}^2}d\mb{r}_{d}\, h_n(\rd{} - \ro{}, \so{})g_n(\rd{}).\label{eq:adj}
 \end{align}
@@
 \begin{align}
-  k_{nn'}(\rd{} - \rd{}') &= \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h_n(\rd{} - \ro{}, \so{})h_{n'}(\rd{} - \ro{}, \so{}). \label{eq:kern}
+  k_{nn'}(\rd{} - \rd{}') &= \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h_n(\rd{} - \ro{}, \so{})h_{n'}(\rd{}' - \ro{}, \so{}). \label{eq:kern}
 \end{align}
@@
 \begin{align}
-  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho}, j}]_n(\rd{}) = \mu_{\bs{\rho}, n} \mb{v}_{\bs{\rho}, j}(\rd{}). \label{eq:eigval}
+  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho}, j}]_n(\rd{}) = \mu_{\bs{\rho}, j} [\mb{v}_{\bs{\rho}, j}(\rd{})]_n. \label{eq:eigval}
 \end{align}
@@
 \begin{align}
-  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho},j}]_n(\rd{}) = \me{}^{i 2\pi \ro{}\cdot\bs{\rho}} \sum_{n'=1}^N K_{nn'}(\bs{\rho})[\mb{V}_j(\bs{\rho})]_{n'}, \label{eq:exp}
+  [\mathcal{H}\mathcal{H}^{\dagger}\mb{v}_{\bs{\rho},j}]_n(\rd{}) = \me{}^{i 2\pi \rd{}\cdot\bs{\rho}} \sum_{n'=1}^N K_{nn'}(\bs{\rho})[\mb{V}_j(\bs{\rho})]_{n'}, \label{eq:exp}
 \end{align}
@@
 \end{align}
-Comparing Eqs. \ref{eq:eigfunc} and \ref{eq:exp} yield the eigenvalue problem
+Comparing Eqs. \ref{eq:eigfunc} and \ref{eq:exp} yields the eigenvalue problem
 \begin{align}
@@
 
-\section{Polarized epi-illumination with unpolarized epi-detection}
-We will start by restricting our analysis of epi-illumination microscopes to
-in-focus objects. This means that our object space is
-$\mbb{L}_2(\mbb{R}^2 \times \mbb{S}^2)$.
+% \section{Polarized epi-illumination with unpolarized epi-detection}
+% We will start by restricting our analysis of epi-illumination microscopes to
+% in-focus objects. This means that our object space is
+% $\mbb{L}_2(\mbb{R}^2 \times \mbb{S}^2)$.
 
-\subsection{Point response function}
-In the previous notes we showed that the excitation point response function for
-polarized epi-illumination is given by
-\begin{align}
-  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}, \label{eq:genpsf}
-\end{align}
-where
-\begin{subequations}
-\begin{align}
-  \tilde{A} &\equiv \cos^2(\alpha/2)\cos(\alpha),\\
-  \tilde{B} &\equiv \frac{1}{12}(\cos^2\alpha + 4\cos\alpha + 7),
-\end{align}\label{eq:coefficients}%
-\end{subequations}
-and $\alpha \equiv \arcsin(\text{NA}/n_o)$.
+% \subsection{Point response function}
+% In the previous notes we showed that the excitation point response function for
+% polarized epi-illumination is given by
+% \begin{align}
+%   h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}, \label{eq:genpsf}
+% \end{align}
+% where
+% \begin{subequations}
+% \begin{align}
+%   \tilde{A} &\equiv \cos^2(\alpha/2)\cos(\alpha),\\
+%   \tilde{B} &\equiv \frac{1}{12}(\cos^2\alpha + 4\cos\alpha + 7),
+% \end{align}\label{eq:coefficients}%
+% \end{subequations}
+% and $\alpha \equiv \arcsin(\text{NA}/n_o)$.
 
-We also showed that the point response function for unpolarized epi-detection is
-given by
-\begin{align}
-  h_{\text{det}}(\ro{}, \so{}) &= [{a}^2(r_o) + 2b^2(r_o)]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a^2(r_o) + 4b^2(r_o)\right]y_2^0(\so{}),
-\end{align}
-where
-\begin{align}
-  a(r_o) = \frac{J_1(2\pi \nu_or_o)}{\pi \nu_or_o}, 
-  &\hspace{2em}
-    b(r_o) = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o)}{\pi \nu_or_o}\right],  \label{eq:abparadef}
-  \intertext{and}
-  \nu_o \equiv \frac{\text{NA}}{\lambda},&\hspace{2em}
-  \text{NA} = n_o\sin\alpha.
-\end{align}
-The excitation and detection processes are incoherent, so to find the complete
-point response function we can multiply the excitation and detection point response
-functions which gives
-\begin{align}
-  h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \frac{1}{\tilde{N}}\sum_{l=0}^{\infty}\sum_{m=-l}^l h_l^m(\ro{}; \mh{p})y_l^m(\so{}), 
-\end{align}
-where $\tilde{N} = \frac{\tilde{A}}{10} + \frac{1}{2}$ is a normalization constant
-and the terms in the series are given by
-\begin{align}
-  h_0^0(r_o) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]a^2(r_o) + \left[-\frac{2\tilde{A}}{5} + 1\right]b^2(r_o),\\
-  h_2^{-2}(r_o; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
-  h_2^0(r_o) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]a^2(r_o) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]b^2(r_o),\\
-  h_2^2(r_o; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
-  h_4^{-2}(r_o; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
-  h_4^0(r_o) &= \frac{3\tilde{A}}{35}[a^2(r_o) - 4b^2(r_o)],\\
-  h_4^2(r_o; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
-\end{align}
-and all other $h_l^m$ terms in the series are zero. Finally, the complete
-forward model for this class of microscope is given by
-\begin{align}
-    g_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} - \ro{}, \so{}; \mh{p}_n)f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N. \label{eq:fwdpolillum}
-\end{align}
-Notice that we have used a single function $h(\rd{} - \ro{}, \so{}; \mh{p}_n)$
-to describe the complete imaging system, and we have shifted the index $n$ to
-the illumination polarization. A typical choice of frames is given by $N=4$ and
-\begin{align}
-  \mh{p}_1 = \mh{x},\hspace{2em}
-  \mh{p}_2 = \frac{1}{\sqrt{2}}(\mh{x} + \mh{y}),\hspace{2em}
-  \mh{p}_3 = \mh{y},\hspace{2em}
-  \mh{p}_4 = \frac{1}{\sqrt{2}}(\mh{x} - \mh{y}). 
-\end{align}
-\indent The point response function of the microscope now contains seven terms
-in the $l=0$, 2, and 4 bands. Each term is radially symmetric which means that
-we expect a radially symmetric point spread function for any angular
-distribution of fluorophores. Notice that the $h_l^0$ terms do not depend on the
-polarizer orientation, while the $h_l^{-2}$ and $h_l^{2}$ do depend on the
-polarizer orientation. This is because the fluorophore distributions
-corresponding to the $h_l^0$ terms are rotationally symmetric about the optic
-axis, while the other terms are not rotationally symmetric.
+% We also showed that the point response function for unpolarized epi-detection is
+% given by
+% \begin{align}
+%   h_{\text{det}}(\ro{}, \so{}) &= [{a}^2(r_o) + 2b^2(r_o)]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a^2(r_o) + 4b^2(r_o)\right]y_2^0(\so{}),
+% \end{align}
+% where
+% \begin{align}
+%   a(r_o) = \frac{J_1(2\pi \nu_or_o)}{\pi \nu_or_o}, 
+%   &\hspace{2em}
+%     b(r_o) = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o)}{\pi \nu_or_o}\right],  \label{eq:abparadef}
+%   \intertext{and}
+%   \nu_o \equiv \frac{\text{NA}}{\lambda},&\hspace{2em}
+%   \text{NA} = n_o\sin\alpha.
+% \end{align}
+% The excitation and detection processes are incoherent, so to find the complete
+% point response function we can multiply the excitation and detection point response
+% functions which gives
+% \begin{align}
+%   h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \frac{1}{\tilde{N}}\sum_{l=0}^{\infty}\sum_{m=-l}^l h_l^m(\ro{}; \mh{p})y_l^m(\so{}), 
+% \end{align}
+% where $\tilde{N} = \frac{\tilde{A}}{10} + \frac{1}{2}$ is a normalization constant
+% and the terms in the series are given by
+% \begin{align}
+%   h_0^0(r_o) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]a^2(r_o) + \left[-\frac{2\tilde{A}}{5} + 1\right]b^2(r_o),\\
+%   h_2^{-2}(r_o; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
+%   h_2^0(r_o) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]a^2(r_o) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]b^2(r_o),\\
+%   h_2^2(r_o; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}a^2(r_o) + \frac{3\sqrt{15}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
+%   h_4^{-2}(r_o; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
+%   h_4^0(r_o) &= \frac{3\tilde{A}}{35}[a^2(r_o) - 4b^2(r_o)],\\
+%   h_4^2(r_o; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}a^2(r_o) + \frac{6\sqrt{5}}{35}b^2(r_o)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
+% \end{align}
+% and all other $h_l^m$ terms in the series are zero. Finally, the complete
+% forward model for this class of microscope is given by
+% \begin{align}
+%     g_n(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^3}d\ro{}\, h(\rd{} - \ro{}, \so{}; \mh{p}_n)f(\ro{}, \so{}),\qquad  n=1, 2,\ldots,N. \label{eq:fwdpolillum}
+% \end{align}
+% Notice that we have used a single function $h(\rd{} - \ro{}, \so{}; \mh{p}_n)$
+% to describe the complete imaging system, and we have shifted the index $n$ to
+% the illumination polarization. A typical choice of frames is given by $N=4$ and
+% \begin{align}
+%   \mh{p}_1 = \mh{x},\hspace{2em}
+%   \mh{p}_2 = \frac{1}{\sqrt{2}}(\mh{x} + \mh{y}),\hspace{2em}
+%   \mh{p}_3 = \mh{y},\hspace{2em}
+%   \mh{p}_4 = \frac{1}{\sqrt{2}}(\mh{x} - \mh{y}). 
+% \end{align}
+% \indent The point response function of the microscope now contains seven terms
+% in the $l=0$, 2, and 4 bands. Each term is radially symmetric which means that
+% we expect a radially symmetric point spread function for any angular
+% distribution of fluorophores. Notice that the $h_l^0$ terms do not depend on the
+% polarizer orientation, while the $h_l^{-2}$ and $h_l^{2}$ do depend on the
+% polarizer orientation. This is because the fluorophore distributions
+% corresponding to the $h_l^0$ terms are rotationally symmetric about the optic
+% axis, while the other terms are not rotationally symmetric.
 
-\subsection{Optical transfer function}
-The optical transfer function for this microscope is given by
-\begin{align}
-  H_l^m(\nu; \mh{p}) = \frac{1}{\tilde{M}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'} H_{l'}^{m'}(\nu; \mh{p})\delta(l - l', m - m'),  
-\end{align}
-where
-$\tilde{M} = \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right] + \left(\frac{\text{NA}}{n_o}\right)\left[-\frac{2\tilde{A}}{10} + \frac{1}{2}\right]$ is a
-normalization constant, and
-\begin{align}
-  H_0^0(\nu) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]A(\nu) + \left[-\frac{2\tilde{A}}{5} + 1\right]B(\nu),\\
-  H_2^{-2}(\nu; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
-  H_2^0(\nu) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]A(\nu) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]B(\nu),\\
-  H_2^2(\nu; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
-  H_4^{-2}(\nu; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
-  H_4^0(\nu) &= \frac{3\tilde{A}}{35}[A(\nu) - 4B(\nu)],\\
-  H_4^2(\nu; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
-\end{align}
-all other $H_l^m$ terms in the series are zero, and  
-\begin{align}
-  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
+% \subsection{Optical transfer function}
+% The optical transfer function for this microscope is given by
+% \begin{align}
+%   H_l^m(\nu; \mh{p}) = \frac{1}{\tilde{M}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'} H_{l'}^{m'}(\nu; \mh{p})\delta(l - l', m - m'),  
+% \end{align}
+% where
+% $\tilde{M} = \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right] + \left(\frac{\text{NA}}{n_o}\right)\left[-\frac{2\tilde{A}}{10} + \frac{1}{2}\right]$ is a
+% normalization constant, and
+% \begin{align}
+%   H_0^0(\nu) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]A(\nu) + \left[-\frac{2\tilde{A}}{5} + 1\right]B(\nu),\\
+%   H_2^{-2}(\nu; \mh{p}) &= \left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
+%   H_2^0(\nu) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]A(\nu) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]B(\nu),\\
+%   H_2^2(\nu; \mh{p}) &= -2\left[\frac{9\sqrt{15}}{70}A(\nu) + \frac{3\sqrt{15}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),\\
+%   H_4^{-2}(\nu; \mh{p}) &= \left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2],\\
+%   H_4^0(\nu) &= \frac{3\tilde{A}}{35}[A(\nu) - 4B(\nu)],\\
+%   H_4^2(\nu; \mh{p}) &= -2\left[-\frac{3\sqrt{5}}{70}A(\nu) + \frac{6\sqrt{5}}{35}B(\nu)\right]\tilde{B}(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y}),
+% \end{align}
+% all other $H_l^m$ terms in the series are zero, and  
+% \begin{align}
+%   A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+%   B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
+% \end{align}
 

### 2018-05-15 notes/2018-05-14-single-view-continuous-svd/report/report.tex
First draft of continuous SVD for single view microscopes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Singular value decomposition of single view\\ polarized
  fluorescence microscopes\vspace{-1em}} \author{Talon Chandler, Min Guo, Hari
  Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will develop the continuous models for single view polarized
fluorescence microscopes with either polarized illumination or polarized
detection. We will start by writing an integral transform that maps object space
to data space. Then we will calculate the kernels of the integral transform and
their corresponding transfer functions. Finally we will calculate the singular
value decomposition of the forward operator to find the limits of these designs.

\noindent We will make use of the real circular harmonic functions
\begin{align}
  z_n(\theta) =
  \begin{cases}
    \frac{1}{\sqrt{\pi}}\cos(n\theta), & n > 0,\\
    \frac{1}{\sqrt{\pi}}, & n = 0,\\
    \frac{1}{\sqrt{\pi}}\sin(n\theta), & n < 0.\\
  \end{cases}
\end{align}
The real circular harmonic functions form an orthonormal basis for functions on
the circle because
\begin{align}
  \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})z_{n'}(\mh{p}) = \delta_{nn'}.
\end{align}
Notice that we allow $z_n(\cdot)$ to take a vector argument similar to the
spherical harmonics $y_l^m(\so{})$. This allows us to use these functions
without specifying a coordinate system. Also notice that we are using $n$ to
index the circular harmonic functions---in a previous note set we used $n$ to
index frames or views.

\section{General forward model}
We will consider the problem of imaging a two-dimensional field of oriented
fluorophores. To a good approximation these objects can be represented by a
member of the set
$\mbb{U} = \mbb{L}_2(\mbb{R}^2 \times \mbb{S}^2)$---square-integrable functions
that assign a scalar value to each position and orientation.

These microscopes can collect a two-dimensional frame of intensity measurements
for each position of a single polarizer on the illumination or detection arm.
Therefore, the collected data is a member of the set
$\mbb{V} = \mbb{L}_2(\mbb{R}^2 \times \mbb{S}^1)$---square-integrable functions
that assign a scalar value to each two-dimensional position on a circle. Notice
that we are considering the largest possible data space for these
microscopes---a continuous sampling of the spatial and polarizer dimensions.
This approach allows us to answer questions about the limits of these
microscopes without considering specific choices of spatial sampling (pixels) or
polarization sampling (polarizer settings). It will be helpful to think of the
space $\mbb{L}_2(\mbb{R}^2 \times \mbb{S}^1)$ geometrically as a continuous list
of images arranged face to face in a donut---if we slice the donut along the
smaller dimension (not like a pre-cut bagel!) we can see a single
image taken with a single polarizer setting.

If the imaging system is spatially shift-invariant, then the forward and adjoint operators are given by the following integral transforms
\begin{align}
  g(\rd{}, \mh{p}) = [\mathcal{H}f](\rd{}, \hat{\mb{p}}) &= \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{}; \hat{\mb{p}})f(\ro{}, \so{}),\\
  f(\ro{}, \so{}) =  [\mathcal{H}^{\dagger}g](\ro{}, \so{}) &= \int_{\mbb{S}^1}d\hat{\mb{p}}\, \int_{\mbb{R}^2}d\mb{r}_{d}\, h(\rd{} - \ro{}, \so{}; \hat{\mb{p}})g(\rd{}, \hat{\mb{p}}).
\end{align}
where $f(\ro{}, \so{})$ is the object, $g(\rd{}, \hat{\mb{p}})$ is the data, and
$h(\rd{} -\ro{}, \so{}; \hat{\mb{p}})$ is the kernel of the integral transform.
The kernel can be interpreted as a ``point spread function'' if we visualize the
complete data space as a ``donut'' of images. A delta function at a point in object
space will give rise to the kernel evaluated at that point in data space.

We can write the forward and adjoint operators in the frequency domain as
% \begin{align}
%   g(\rd{}, \hat{\mb{p}}) = \sum_{n=-\infty}^{\infty} z_n(\mh{p}) \sum_{l=0}^{\infty}\sum_{m=-l}^{l} \int_{\mbb{R}^2}d\bs{\nu}\, H_{l,n}^m(\bs{\nu})F_l^m(\bs{\nu}), 
    %   \end{align}
\begin{align}
  G_n(\bs{\nu}) &= \sum_{l=0}^{\infty}\sum_{m=-l}^{l}H_{l,n}^m(\bs{\nu})F_l^m(\bs{\nu}),\label{eq:fwd}\\
  F_l^m(\bs{\nu}) &= \sum_{n=-\infty}^{\infty}H_{l,n}^m(\bs{\nu})G_n(\bs{\nu}),
\end{align}
where
\begin{align}
  G_{n}(\bs{\nu}) &= \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})\int_{\mbb{R}^2}d\rd{}\, \me{}^{i2\pi\rd{}\cdot\bs{\nu}}g(\rd{}, \mh{p}),\\
  H_{l,n}^m(\bs{\nu}) &= \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})\int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}h(\ro{}, \so{}; \mh{p}),\\
  F_{l}^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}f(\ro{}, \so{}).
\end{align}
To find the singular value decomposition of the forward operator, we need to solve
\begin{align}
  \mc{H}\mc{H}^{\dagger} v_{\bs{\rho},j}(\rd{}, \hat{\mb{p}}) = \mu_{\bs{\rho},j}v_{\bs{\rho},j}(\rd{}, \hat{\mb{p}}). 
\end{align}
It is much easier to solve the equivalent problem in the frequency domain
\begin{align}
  \mathsf{K}(\bs{\rho})\mathsf{V}_j(\bs{\rho}) = \mu_{\bs{\rho},j}\mathsf{V}_j(\bs{\rho}). \label{eq:freqsvd}
\end{align}
where the entries of $\mathsf{K}(\bs{\rho})$ are given by
\begin{align}
  K_{nn'}(\bs{\rho}) = \sum_{l=0}^\infty\sum_{m=-l}^{l}H_{l,n}^m(\bs{\rho})H_{l,n'}^m(\bs{\rho}),
\end{align}
and the entries of $\mathsf{V}_j(\bs{\rho})$ are related to the complete data space singular functions by
\begin{align}
  v_{\bs{\rho},j}(\rd{}, \mh{p}) = \me{}^{i 2\pi \bs{\rho}\cdot\rd{}}\sum_{n=-\infty}^{\infty}[V_n(\bs{\rho})]_j z_n(\mh{p}). \label{eq:eigfunc}
\end{align}
Once we've found the data space singular functions, we can find the object space singular functions using
\begin{align}
  [U_l^m(\bs{\rho})]_j &= \sum_{n=-\infty}^{\infty} H_{l,n}^m(\bs{\rho})[V_n(\bs{\rho})]_j, \label{eq:eigenfuncobj}\\
  u_{\bs{\rho}, j}(\ro{}, \so{}) &= \me{}^{i2\pi\bs{\rho}\cdot\ro{}}\sum_{l=0}^{\infty}\sum_{m=-l}^l [U_l^m(\bs{\rho})]_j y_l^m(\so{}).
\end{align}

\section{Polarized illumination}
\subsection{Kernel}
In previous notes we showed that the excitation point response function for
polarized epi-illumination is given by
\begin{align}
  h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{[(\mh{p}\cdot\mh{x})^2 - (\mh{p}\cdot\mh{y})^2]y_2^2(\so{}) - 2(\mh{p}\cdot\mh{x})(\mh{p}\cdot\mh{y})y_2^{-2}(\so{})\right\}, \label{eq:genpsf}
\end{align}
where
\begin{subequations}
\begin{align}
  \tilde{A} &\equiv \cos^2(\alpha/2)\cos(\alpha),\\
  \tilde{B} &\equiv \frac{1}{12}(\cos^2\alpha + 4\cos\alpha + 7),
\end{align}\label{eq:coefficients}%
\end{subequations}
and $\alpha \equiv \arcsin(\text{NA}/n_o)$. It is more convenient to write the point response function in terms of the circular harmonics
\begin{align}
    h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\tilde{A}y_2^0(\so{}) + \sqrt{\frac{3}{5}}\tilde{B}\left\{y_2^2(\so{})z_2(\mh{p}) - y_2^{-2}(\so{})z_{-2}(\mh{p})\right\}.
\end{align}

We also showed that the point response function for unpolarized epi-detection is
given by
\begin{align}
  h_{\text{det}}(\ro{}, \so{}) &= [{a}^2(r_o) + 2b^2(r_o)]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a^2(r_o) + 4b^2(r_o)\right]y_2^0(\so{}),
\end{align}
where
\begin{align}
  a(r_o) = \frac{J_1(2\pi \nu_or_o)}{\pi \nu_or_o}, 
  &\hspace{2em}
    b(r_o) = \frac{\text{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or_o)}{\pi \nu_or_o}\right],  \label{eq:abparadef}
  \intertext{and}
  \nu_o \equiv \frac{\text{NA}}{\lambda},&\hspace{2em}
  \text{NA} = n_o\sin\alpha.
\end{align}
The excitation and detection processes are incoherent, so to find the complete
point response function we can multiply the excitation and detection point response
functions which gives
\begin{align}
  h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \frac{1}{\tilde{N}}\sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}), 
\end{align}
where $\tilde{N} = \frac{\tilde{A}}{10} + \frac{1}{2}$ is a normalization constant
and the terms in the series are given by
\begin{align}
  h_{0,0}^0(r_o) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]a^2(r_o) + \left[-\frac{2\tilde{A}}{5} + 1\right]b^2(r_o),\\
  h_{2,2}^{2}(r_o) &= -h_{2,-2}^{-2}(r_o) = \frac{3\sqrt{15}\tilde{B}}{35}\left[\frac{3}{2}a^2(r_o) + b^2(r_o)\right],\\
  h_{2,0}^0(r_o) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]a^2(r_o) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]b^2(r_o),\\
  h_{4,2}^{2}(r_o) &= -h_{4,-2}^{-2}(r_o) = \frac{6\sqrt{5}\tilde{B}}{35}\left[-\frac{1}{4}a^2(r_o) + b^2(r_o)\right],\\
  h_{4,0}^0(r_o) &= \frac{3\tilde{A}}{35}[a^2(r_o) - 4b^2(r_o)],\\
\end{align}
and all other $h_{l,n}^m(r_o)$ terms in the series are zero.

\subsection{Transfer function}
The optical transfer function for this microscope is given by
\begin{align}
  H_{l,n}^m(\nu) = \frac{1}{\tilde{M}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}\sum_{n'=-\infty}^{\infty} H_{l',n'}^{m'}(\nu)\delta_{l,l'}\delta_{m,m'}\delta_{n,n'},  
\end{align}
where
$\tilde{M} = \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right] + \left(\frac{\text{NA}}{n_o}\right)\left[-\frac{2\tilde{A}}{10} + \frac{1}{2}\right]$ is a
normalization constant, and
\begin{align}
  H_{0,0}^0(\nu) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]A(\nu) + \left[-\frac{2\tilde{A}}{5} + 1\right]B(\nu),\\
  H_{2,2}^{2}(\nu) &= -H_{2,-2}^{-2}(\nu) = \frac{3\sqrt{15}\tilde{B}}{35}\left[\frac{3}{2}A(\nu) + B(\nu)\right],\\
  H_{2,0}^0(\nu) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]A(\nu) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]B(\nu),\\
  H_{4,2}^{2}(\nu) &= -H_{4,-2}^{-2}(\nu) = \frac{6\sqrt{5}\tilde{B}}{35}\left[-\frac{1}{4}A(\nu) + B(\nu)\right],\\
  H_{4,0}^0(\nu) &= \frac{3\tilde{A}}{35}[A(\nu) - 4B(\nu)],
\end{align}
and all other $H_{l,n}^m(\nu)$ terms in the series are zero, and  
\begin{align}
  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).                 
\end{align}

\subsection{Singular value decomposition}
Plugging the transfer function into the frequency-domain eigenvalue problem (Eq.
\ref{eq:freqsvd}) yields a $3\times 3$ eigenvalue problem (we suppress the index
$\bs{\rho}$ and understand that we need to solve this eigenvalue problem at each
value of $\bs{\rho}$)
\begin{align}
  \mathsf{K}\mathsf{V}_j &= \mu_{j}\mathsf{V}_j,\\
  \begin{bmatrix}
    \sum_{l,m}H_{l,-2}^{m}H_{l,-2}^{m}&\sum_{l,m}H_{l,-2}^{m}H_{l,0}^{m}&\sum_{l,m}H_{l,-2}^{m}H_{l,2}^{m}\\
    \sum_{l,m}H_{l,0}^{m}H_{l,-2}^{m}&\sum_{l,m}H_{l,0}^{m}H_{l,0}^{m}&\sum_{l,m}H_{l,0}^{m}H_{l,2}^{m}\\
    \sum_{l,m}H_{l,2}^{m}H_{l,-2}^{m}&\sum_{l,m}H_{l,2}^{m}H_{l,0}^{m}&\sum_{l,m}H_{l,2}^{m}H_{l,2}^{m}\\    
  \end{bmatrix}\mathsf{V}_j
&= \mu_{j}\mathsf{V}_j,\\
  \begin{bmatrix}
    \{H_{2,-2}^{-2}\}^2 + \{H_{4,-2}^{-2}\}^2&0&0\\
    0&\{H_{0,0}^{0}\}^2 + \{H_{2,0}^{0}\}^2 + \{H_{4,0}^{0}\}^2&0\\
    0&0&\{H_{2,2}^{2}\}^2 + \{H_{4,2}^{2}\}^2\\    
  \end{bmatrix}\mathsf{V}_j
&= \mu_{j}\mathsf{V}_j.
\end{align}
A diagonal matrix has its eigenvalues along the diagonal and its eigenvectors as
unit vectors so
\begin{align}
  \mu_{\bs{\rho},0} &= \{H_{0,0}^{0}(\rho)\}^2 + \{H_{2,0}^{0}(\rho)\}^2 + \{H_{4,0}^{0}(\rho)\}^2,\\
  \mu_{\bs{\rho},1} = \mu_{\bs{\rho},2} &= \{H_{2,2}^{2}(\rho)\}^2 + \{H_{4,2}^{2}(\rho)\}^2,
\end{align}
and
\begin{align}
  \mathsf{V}_0 =
  \begin{bmatrix}
    0\\1\\0\\
  \end{bmatrix},\qquad
  \mathsf{V}_1 =
  \begin{bmatrix}
    1\\0\\0\\
  \end{bmatrix},\qquad
  \mathsf{V}_2 =
  \begin{bmatrix}
    0\\0\\1\\
  \end{bmatrix}.
\end{align}
Notice that we have two degenerate eigenvalues, but we have found trivial
orthonormal eigenvectors---in general we will need to apply the Gram-Schmidt
procedure.

% We can substitute the $H_{l,n}^m$ functions to recover the complete eigenvalue
% spectrum as
% \begin{align}
%   \mu_{\bs{\rho},0} = &\frac{1}{70}[3\tilde{A}^2A^2(\rho) +2\tilde{A}A^2(\rho) + 21A^2(\rho) + 6\tilde{A}^2A(\rho)B(\rho) - 56\tilde{A}A(\rho)B(\rho) + \\ & \qquad 98A(\rho)B(\rho) + 54\tilde{A}^2B(\rho)^2 - 144\tilde{A}B^2(\rho) + 126B^2(\rho)],\\
%   \mu_{\bs{\rho},1} = &\mu_{\bs{\rho}, 2} = \frac{9\tilde{B}}{35}[A^2(\rho) + A(\rho)B(\rho) + B^2(\rho)].
% \end{align}
We can use Eq. \ref{eq:eigfunc} to recover the complete singular functions in
data space as
\begin{align}
  v_{\bs{\rho},0}(\rd{}, \mh{p}) &= \me{}^{i2\pi\bs{\rho}\cdot\rd{}}z_0(\mh{p}),\\
  v_{\bs{\rho},1}(\rd{}, \mh{p}) &= \me{}^{i2\pi\bs{\rho}\cdot\rd{}}z_{-2}(\mh{p}),\\
  v_{\bs{\rho},2}(\rd{}, \mh{p}) &= \me{}^{i2\pi\bs{\rho}\cdot\rd{}}z_2(\mh{p}).
\end{align}
For the final step we use Eq. \ref{eq:eigenfuncobj} to find the spectra of the
singular functions in object space
\begin{align}
  [U_l^m(\rho)]_0 &= H_{l,0}^m(\rho) = H_{0,0}^0(\rho)\delta_{l0}\delta_{m0} + H_{2,0}^0(\rho)\delta_{l2}\delta_{m0} + H_{4,0}^0(\rho)\delta_{l4}\delta_{m0},\\
  [U_l^m(\rho)]_1 &= H_{l,-2}^m(\rho) = H_{2,-2}^{-2}(\rho)\delta_{l2}\delta_{m-2} + H_{4,-2}^{-2}(\rho)\delta_{l4}\delta_{m-2},\\
  [U_l^m(\rho)]_2 &= H_{l,2}^m(\rho) = H_{l,2}^m(\rho) = H_{2,2}^{2}(\rho)\delta_{l2}\delta{m2} + H_{4,2}^{2}(\rho)\delta_{l4}\delta_{m2}.
\end{align}
Therefore, the complete singular functions in object space are
\begin{align}
  u_{\bs{\rho},0}(\ro{}, \so{}) &= \me{}^{i2\pi\bs{\rho}\cdot\ro{}}[H_{0,0}^0(\rho)y_0^0(\so{}) + H_{2,0}^0(\rho)y_2^0(\so{}) + H_{4,0}^0(\rho)y_4^0(\so{})],\\
  u_{\bs{\rho},1}(\ro{}, \so{}) &= \me{}^{i2\pi\bs{\rho}\cdot\ro{} }[H_{2,-2}^{-2}(\rho)y_2^{-2}(\so{}) + H_{4,-2}^{-2}(\rho)y_4^{-2}(\so{})],\\
  u_{\bs{\rho},2}(\ro{}, \so{}) &= \me{}^{i2\pi\bs{\rho}\cdot\ro{} }[H_{2,2}^2(\rho)y_2^2(\so{}) + H_{4,2}^2(\rho)y_4^2(\so{})].
\end{align}

We have found the complete singular system for a single view microscope with
polarized illumination. We can look closer at the singular value spectrum to
find the degeneracies of the microscope. The first major set of degeneracies is
related to the fact that $\mu_{\bs{\rho},1} = \mu_{\bs{\rho},2}$. The
corresponding singular functions in object space are related by changing the
spherical harmonic index $m$ to $-m$. This transformation is a rotation about
the optical axis, so this degeneracy corresponds to the rotational symmetry of
the microscope. The second set of degeneracies is related to the fact that the
singular values depend only on $\rho$, not the vector $\bs{\rho}$. The
corresponding singular functions in object space are spatial harmonics at the
same spatial frequency in different directions. Once again, this degeneracy
corresponds to the rotational symmetry of the microscope.

Recall the mental image of data space being arranged on a donut. If we rotate
the object that we are imaging then the data space will undergo two simultaneous
rotations---one rotation about an axis through the donut hole (imagine sticking
your finger through the donut) and another about the curved axis that runs
through the center of the dough (imagine twisting the donut in on itself so that
glaze on top would end up on the bottom). These two simultaneous rotations
correspond with the two sets of degeneracies we see in the singular value
spectrum.

Plots forthcoming!

\section{Polarized detection}
We'll use the same notation as the previous section, so there will be notation
overlap.

\subsection{Kernel}
In previous notes we showed that the excitation point response function for
unpolarized epi-illumination is given by
\begin{align}
  h_{\text{exc}}^{\mh{z}}(\so{}) = h_{\text{exc},0,0}^0y_0^0(\so{}) + h_{\text{exc},0,0}^2y_2^0(\so{}).
\end{align}
where
\begin{align}
  h_{\text{exc},0,0}^0 &= 1,\\
  h_{\text{exc},0,0}^2 &= -\frac{1}{\sqrt{5}}\tilde{A}.
\end{align}

We also showed that the point response function for polarized detection is given
by (rewritten in terms of the circular harmonics)
\begin{align}
  h_{\text{det}}(\ro{}, \so{}; \mh{p}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{\text{det},l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{\text{det},0,0}^0(\ro{}) &= a^2(r_o) + 2b^2(r_0),\\
  h_{\text{det},0,-2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{-2}(\ro{}),\\
  h_{\text{det},0,2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{2}(\ro{}),\\
  h_{\text{det},2,0}^0(\ro{}) &= \frac{1}{\sqrt{5}}\left[-a^2(r_o) + 4b^2(r_0)\right],\\
  h_{\text{det},2,-2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{-2}(\ro{}),\\
  h_{\text{det},2,2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{2}(\ro{}),\\
  h_{\text{det},2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = \sqrt{\frac{3}{5}}a^2(r_o).
\end{align}
The complete kernel for unpolarized illumination and polarized detection is given by
\begin{align}
  h(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{})\\
  h_{0,-2}^0(\ro{}) &= h_{\text{exc},0,-2}^0h_{\text{det},0,-2}^0(\ro{}) + h_{\text{exc},2,-2}^0h_{\text{det},2,-2}^0(\ro{})\\
  h_{0,2}^0(\ro{}) &= h_{\text{exc},0,2}^0h_{\text{det},0,2}^0(\ro{}) + h_{\text{exc},2,2}^0h_{\text{det},2,2}^0(\ro{})\\
  h_{2,0}^0(\ro{}) &= \\
  h_{2,-2}^0(\ro{}) &= \\
  h_{2,2}^0(\ro{}) &= \\
  h_{2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = .
\end{align}

% [h00d*h00e + h20d*h20e, h2_2d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, h00d*h20e + h00e*h20d + 2*sqrt(5)*h20d*h20e/7, 0, h22d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, 0, sqrt(15)*h20e*h2_2d/7, 0, 6*h20d*h20e/7, 0, sqrt(15)*h20e*h22d/7, 0, 0]
\begin{align}
  h_{0,0}^0(\ro{}; \mh{p}_d) = a^2(r_o) + 2b^2(r_o)[1 + z_{-2}(\ro{})z_{-2}(\mh{p}_d) + z_{2}(\ro{})z_{2}(\mh{p}_d)]
\end{align}

\subsection{Transfer function}
\subsection{Singular value decomposition}

\bibliography{report}{}
\bibliographystyle{unsrt}

\end{document}

### 2018-05-15 notes/2018-05-14-single-view-continuous-svd/calculations/svd2.py

@@ -1,0 +1,17 @@
+from sympy import *
+
+# l,m,n
+At = Symbol('At')
+A = Symbol('A')
+Bt = Symbol('Bt')
+B = Symbol('B')
+H000 = (At/10 + 1/2)*A + (-2*At/5 + 1)*B
+H222 = (3*sqrt(15)*Bt/35)*(3*A/2 + B)
+H200 = (-sqrt(5)*At/14 + sqrt(5)/10)*A + (-11*sqrt(5)*At/35 + 2/sqrt(5))*B
+H422 = 6*sqrt(5)*Bt/35*(-A/4 + B)
+H400 = 3*At/35*(A - 4*B)
+
+m0 = H000**2 + H200**2 + H400**2
+m1 = H222**2 + H422**2
+
+import pdb; pdb.set_trace() 

### 2018-05-17 notes/2018-05-14-single-view-continuous-svd/report/report.tex
Update continuous single view notes.

@@
   h_{\text{exc},0,0}^0 &= 1,\\
-  h_{\text{exc},0,0}^2 &= -\frac{1}{\sqrt{5}}\tilde{A}.
+  h_{\text{exc},2,0}^0 &= -\frac{1}{\sqrt{5}}\tilde{A}.
 \end{align}
@@
   h_{\text{det},0,0}^0(\ro{}) &= a^2(r_o) + 2b^2(r_0),\\
-  h_{\text{det},0,-2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{-2}(\ro{}),\\
-  h_{\text{det},0,2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{2}(\ro{}),\\
+  h_{\text{det},0,\pm 2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{\pm 2}(\ro{}),\\
   h_{\text{det},2,0}^0(\ro{}) &= \frac{1}{\sqrt{5}}\left[-a^2(r_o) + 4b^2(r_0)\right],\\
-  h_{\text{det},2,-2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{-2}(\ro{}),\\
-  h_{\text{det},2,2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{2}(\ro{}),\\
-  h_{\text{det},2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = \sqrt{\frac{3}{5}}a^2(r_o).
+  h_{\text{det},2,\pm 2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{\pm 2}(\ro{}),\\
+  h_{\text{det},2,2}^2(\ro{}) &= -h_{\text{det},2,-2}^{-2}(\ro{}) = \sqrt{\frac{3}{5}}a^2(r_o).
 \end{align}
@@
 \begin{align}
-  h(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
+  h(\ro{}, \so{}; \mh{p}_d) = h_{\text{exc}}(\so{})h_{\text{det}}(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
 \end{align}
@@
 \begin{align}
-  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{})\\
-  h_{0,-2}^0(\ro{}) &= h_{\text{exc},0,-2}^0h_{\text{det},0,-2}^0(\ro{}) + h_{\text{exc},2,-2}^0h_{\text{det},2,-2}^0(\ro{})\\
-  h_{0,2}^0(\ro{}) &= h_{\text{exc},0,2}^0h_{\text{det},0,2}^0(\ro{}) + h_{\text{exc},2,2}^0h_{\text{det},2,2}^0(\ro{})\\
-  h_{2,0}^0(\ro{}) &= \\
-  h_{2,-2}^0(\ro{}) &= \\
-  h_{2,2}^0(\ro{}) &= \\
-  h_{2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = .
+  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}),\\
+  h_{0,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}),\\
+  h_{2,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
+  h_{2,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
+  h_{2,\pm 2}^{\pm 2}(\ro{}) &= h_{\text{det},2,\pm 2}^{\pm 2}(\ro{})\left[h_{\text{exc},0,0}^0 - \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0\right],\\
+  h_{4,0}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
+  h_{4,\pm 2}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
+  h_{4,\pm 2}^{\pm 2}(\ro{}) &= \frac{\sqrt{15}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^{\pm 2}(\ro{}),
+\end{align}
+% hh0
+% [h000d*h000e + h200d*h200e, 0, 0, h000d*h200e + h000e*h200d + 2*sqrt(5)*h200d*h200e/7, 0, 0, 0, 0, 0, 0, 6*h200d*h200e/7, 0, 0, 0, 0]
+
+% hh2
+% [h000e*h002d + h200e*h202d, 0, 0, h000e*h202d + h002d*h200e + 2*sqrt(5)*h200e*h202d/7, 0, h222d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, 0, 0, 0, 6*h200e*h202d/7, 0, sqrt(15)*h200e*h222d/7, 0, 0]
+
+% hh_2
+% [h000e*h00_2d + h200e*h20_2d, h2_2_2d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, h000e*h20_2d + h00_2d*h200e + 2*sqrt(5)*h200e*h20_2d/7, 0, 0, 0, 0, sqrt(15)*h200e*h2_2_2d/7, 0, 6*h200e*h20_2d/7, 0, 0, 0, 0]
+and the remaining terms in the series are zero. Plugging in the excitation and
+detection point response functions gives the following
+\begin{align}
+  h_{0,0}^0(\ro{}) &= \left[\frac{\tilde{A}}{5} + 1\right]a^2(r_o) + \left[-\frac{4\tilde{A}}{5} + 2\right]b^2(r_o),\\ 
+  h_{0,\pm 2}^0(\ro{}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]b^2(r_o)z_{\pm 2}(\ro{}),\\ 
+  h_{2,0}^0(\ro{}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]a^2(r_o) + \left[-22\tilde{A} + 28\right]b^2(r_0)\right\},\\ 
+  h_{2,\pm 2}^0(\ro{}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]b^2(r_o)z_{\pm 2}(\ro{})\\ 
+  h_{2,2}^{2}(\ro{}) &= h_{2,-2}^{-2}(\ro{}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]a^2(r_o),\\ 
+  h_{4,0}^0(\ro{}) &= \frac{6\tilde{A}}{35}\left[a^2(r_o) - 4b^2(r_o)\right],\\ 
+  h_{4,\pm 2}^0(\ro{}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}b^2(r_o)z_{\pm 2}(\ro{}),\\ 
+  h_{4,2}^{2}(\ro{}) &= h_{4,-2}^{-2}(\ro{}) = -\frac{3\sqrt{5}}{35}\tilde{A}a^2(r_o). 
+\end{align}
+% hh0
+% [At*(a - 4*b)/5 + a + 2*b, 0, 0, sqrt(5)*(-5*At*a - 22*At*b - 7*a + 28*b)/35, 0, 0, 0, 0, 0, 0, 6*At*(a - 4*b)/35, 0, 0, 0, 0]
+
+% hh2
+% [2*sqrt(pi)*b*z2*(-2*At + 5)/5, 0, 0, 2*sqrt(5)*sqrt(pi)*b*z2*(-11*At + 14)/35, 0, a*(2*sqrt(15)*At/35 + sqrt(15)/5), 0, 0, 0, 0, -24*sqrt(pi)*At*b*z2/35, 0, -sqrt(15)*sqrt(3)*At*a/35, 0, 0]
+
+% hh_2
+% [2*sqrt(pi)*b*z_2*(-2*At + 5)/5, a*(0.221313334068995*At + 0.774596669241483), 0, 2*sqrt(5)*sqrt(pi)*b*z_2*(-11*At + 14)/35, 0, 0, 0, 0, -0.110656667034498*sqrt(3)*At*a, 0, -24*sqrt(pi)*At*b*z_2/35, 0, 0, 0, 0]
+
+\subsection{Transfer function}
+The transfer function for unpolarized illumination and polarized detection is
+given by
+\begin{align}
+  H_{l,n}^m(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} H_{l,n}^m(\bs{\nu})\delta_{ll'}\delta_{mm'}\delta_{nn'},
+\end{align}
+where
+\begin{align}
+  H_{0,0}^0(\bs{\nu}) &= \left[\frac{\tilde{A}}{5} + 1\right]A(\nu) + \left[-\frac{4\tilde{A}}{5} + 2\right]B(\nu),\\ 
+  H_{0,\pm 2}^0(\bs{\nu}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
+  H_{2,0}^0(\bs{\nu}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]A(\nu) + \left[-22\tilde{A} + 28\right]B(r_0)\right\},\\ 
+  H_{2,\pm 2}^0(\bs{\nu}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]C(\nu)z_{\pm 2}(\bs{\nu})\\ 
+  H_{2,2}^{2}(\bs{\nu}) &= H_{2,-2}^{-2}(\bs{\nu}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]A(\nu),\\ 
+  H_{4,0}^0(\bs{\nu}) &= \frac{6\tilde{A}}{35}\left[A(\nu) - 4B(\nu)\right],\\ 
+  H_{4,\pm 2}^0(\bs{\nu}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
+  H_{4,2}^{2}(\bs{\nu}) &= H_{4,-2}^{-2}(\bs{\nu}) = -\frac{3\sqrt{5}}{35}\tilde{A}A(\nu). 
+\end{align}
+where 
+\begin{align}
+  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  C(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[-\frac{4}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
 
-% [h00d*h00e + h20d*h20e, h2_2d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, h00d*h20e + h00e*h20d + 2*sqrt(5)*h20d*h20e/7, 0, h22d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, 0, sqrt(15)*h20e*h2_2d/7, 0, 6*h20d*h20e/7, 0, sqrt(15)*h20e*h22d/7, 0, 0]
+\subsection{Singular value decomposition}
+We follow the same procedure and plug the transfer function into the
+frequency-domain eigenvalue problem (Eq. \ref{eq:freqsvd}) which gives a
+$3\times 3$ eigenvalue problem
 \begin{align}
-  h_{0,0}^0(\ro{}; \mh{p}_d) = a^2(r_o) + 2b^2(r_o)[1 + z_{-2}(\ro{})z_{-2}(\mh{p}_d) + z_{2}(\ro{})z_{2}(\mh{p}_d)]
+  \mathsf{K}\mathsf{V}_j &= \mu_{j}\mathsf{V}_j,
 \end{align}
-
-\subsection{Transfer function}
-\subsection{Singular value decomposition}
+where the entries of $\mathsf{K}$ are given by
+\begin{align}
+  \mathsf{K}_{00} &= \sum_{l,m}H_{l,-2}^{m}H_{l,-2}^{m} = \{H_{0,-2}^{0}\}^2 + \{H_{2,-2}^{-2}\}^2 + \{H_{2,-2}^{0}\}^2 + \{H_{4,-2}^{-2}\}^2 + \{H_{4,-2}^{0}\}^2,\\
+  \mathsf{K}_{11} &= \sum_{l,m}H_{l,0}^{m}H_{l,0}^{m} = \{H_{0,0}^{0}\}^2 + \{H_{2,0}^{0}\}^2 + \{H_{4,0}^{0}\}^2,\\
+  \mathsf{K}_{22} &= \sum_{l,m}H_{l,2}^{m}H_{l,2}^{m} = \{H_{0,2}^{0}\}^2 + \{H_{2,2}^{2}\}^2 + \{H_{2,2}^{0}\}^2 + \{H_{4,2}^{2}\}^2 + \{H_{4,2}^{0}\}^2,\\
+  \mathsf{K}_{01} &= \mathsf{K}_{10} = \sum_{l,m}H_{l,-2}^{m}H_{l,0}^{m} = H_{0,-2}^{0}H_{0,0}^{0} + H_{2,-2}^{0}H_{2,0}^{0} + H_{4,-2}^{0}H_{4,0}^{0},\\
+  \mathsf{K}_{02} &= \mathsf{K}_{20} = \sum_{l,m}H_{l,-2}^{m}H_{l,2}^{m} = H_{0,-2}^{0}H_{0,2}^{0} + H_{2,-2}^{0}H_{2,2}^{0} + H_{4,-2}^{0}H_{4,2}^{0},\\
+  \mathsf{K}_{12} &= \mathsf{K}_{21} = \sum_{l,m}H_{l,0}^{m}H_{l,2}^{m} = H_{0,0}^{0}H_{0,2}^{0} + H_{2,0}^{0}H_{2,2}^{0} + H_{4,0}^{0}H_{4,2}^{0}.
+\end{align}
+The eigenvalues and eigenvectors can be computed in a closed form (and I've done
+this using a symbolic package), but writing the result would fill several pages
+with notation and provide little insight. Instead we proceed straight to plots
+of the eigenvalues and eigenvectors shown in Fig. XXX.
 

### 2018-05-17 notes/2018-05-14-single-view-continuous-svd/calculations/multiframe-otf.py

@@ -1,0 +1,14 @@
+from polharmonic import det, ill, micro, gaunt, multi
+import numpy as np
+
+m = multi.MultiMicroscope(ill_optical_axes=[[0,0,1]], det_optical_axes=[[0,0,1]],
+                          ill_nas=[0.8], det_nas=[0.8], n_samp=1.33,
+                          ill_pols=[[1,0,0], [1/np.sqrt(2), 1/np.sqrt(2), 0], [0,1,0], [-1/np.sqrt(2), 1/np.sqrt(2), 0]],
+                          det_pols=4*[None])
+m.plot_frames(folder='pol_illum')
+
+m = multi.MultiMicroscope(ill_optical_axes=[[0,0,1]], det_optical_axes=[[0,0,1]],
+                          ill_nas=[0.8], det_nas=[0.8], n_samp=1.33,
+                          ill_pols=4*[None],
+                          det_pols=[[1,0,0], [1/np.sqrt(2), 1/np.sqrt(2), 0], [0,1,0], [-1/np.sqrt(2), 1/np.sqrt(2), 0]])
+m.plot_frames(folder='pol_detect')

### 2018-05-17 notes/2018-05-14-single-view-continuous-svd/calculations/svd2.py

@@ -1,17 +1,43 @@
 from sympy import *
 
-# l,m,n
-At = Symbol('At')
-A = Symbol('A')
-Bt = Symbol('Bt')
-B = Symbol('B')
-H000 = (At/10 + 1/2)*A + (-2*At/5 + 1)*B
-H222 = (3*sqrt(15)*Bt/35)*(3*A/2 + B)
-H200 = (-sqrt(5)*At/14 + sqrt(5)/10)*A + (-11*sqrt(5)*At/35 + 2/sqrt(5))*B
-H422 = 6*sqrt(5)*Bt/35*(-A/4 + B)
-H400 = 3*At/35*(A - 4*B)
+# hlmn convention
+# Symbolic
+# H000 = Symbol('H000')
+# H002 = Symbol('H002')
+# H00_2 = Symbol('H00_2')
+# H200 = Symbol('H200')
+# H202 = Symbol('H202')
+# H20_2 = Symbol('H20_2')
+# H222 = Symbol('H222')
+# H400 = Symbol('H400')
+# H402 = Symbol('H402')
+# H40_2 = Symbol('H40_2')
+# H422 = Symbol('H422')
 
-m0 = H000**2 + H200**2 + H400**2
-m1 = H222**2 + H422**2
+A = Symbol('A')
+B = Symbol('B')
+C = Symbol('C')
+H000 = A + B
+H002 = C
+H00_2 = C
+H200 = A + B
+H202 = C
+H20_2 = C
+H222 = A
+H400 = A - B
+H402 = C
+H40_2 = C
+H422 = A
+
+K00 = H00_2**2 + H222**2 + H20_2**2 + H422**2 + H40_2**2
+K11 = H000**2 + H200**2 + H400**2
+K22 = H002**2 + H222**2 + H202**2 + H422**2 + H402**2
+K10 = H00_2*H000 + H20_2*H200 + H40_2*H400
+K02 = H00_2*H002 + H20_2*H202 + H40_2*H402
+K12 = H000*H002 + H200*H202 + H400*H402
+
+K = Matrix([[K00, K10, K02],
+           [K10, K11, K12],
+           [K02, K12, K22]])
 
 import pdb; pdb.set_trace() 

### 2018-05-22 notes/2018-05-14-single-view-continuous-svd/report/report.tex
Circular harmonic coefficients.

@@
     \frac{1}{\sqrt{\pi}}\cos(n\theta), & n > 0,\\
-    \frac{1}{\sqrt{\pi}}, & n = 0,\\
+    \frac{1}{\sqrt{2\pi}}, & n = 0,\\
     \frac{1}{\sqrt{\pi}}\sin(n\theta), & n < 0.\\
@@
 \end{align}
-The complete kernel for unpolarized illumination and polarized detection is given by
+The complete kernel for unpolarized illumination and polarized detection is
+given by the product of the excitation and detection kernels. In the previous
+case we were able to calculate this product in terms of the circular and
+spherical harmonics by hand, but this task is difficult in the general case. To
+simplify this task we precompute the triple integrals of the circular and spherical
+harmonics---see Appendix A for details. 
 \begin{align}
@@
 
+\appendix
+\section{Calculating products of circular and spherical harmonics}
+To calculate the kernels of arbitrary microscope designs we need an efficient
+way to calculate the products of functions that are linear combinations of
+circular and spherical harmonics. We start by considering the simplest case of
+multiplying two linear combinations of circular harmonics given by
+\begin{align}
+  f(\mh{p}) = \sum_{n=0}^\infty c_nz_n(\mh{p}), \qquad f'(\mh{p}) = \sum_{n'=0}^\infty c_{n'}'z_{n'}(\mh{p}). 
+\end{align}
+The product of these two functions is given by 
+\begin{align}
+  f''(\mh{p}) &= f(\mh{p})f'(\mh{p})=\sum_{n=0}^\infty \sum_{n'=0}^\infty c_n c_{n'}' z_n(\mh{p}) z_{n'}(\mh{p}) = \sum_{n''=0}^{\infty} c_{n''}''z_{n''}(\mh{p}), \label{eq:two}
+  \end{align}
+  and we would like to find a relationship between the input coefficients ($c_n$
+  $c_{n'}'$) and the output coefficients $c_{n''}''$. To find this relationship
+  we can rewrite the product the circular harmonics as a linear combination of
+  circular harmonics
+  \begin{align}
+    z_n(\mh{p})z_{n'}(\mh{p}) = \sum_{j''=0}^{\infty}P_{n,n',n''}z_{j''}(\mh{p})\label{eq:product}
+  \end{align}
+  where $P^{n''}_{n,n'}$ are the triple integrals of the circular harmonics
+  \begin{align}
+    P_{n,n',n''} = \int_{\mbb{S}^1}d\mh{p}\, z_{n}(\mh{p})z_{n'}(\mh{p})z_{n''}(\mh{p}).\label{eq:triple}
+  \end{align}
+  Plugging Eq. \ref{eq:product} into Eq. \ref{eq:two} gives
+  \begin{align}
+    \sum_{n=0}^\infty \sum_{n'=0}^\infty c_n c_{n'}' \left[\sum_{j''=0}^{\infty}P^{n''}_{n,n'}z_{j''}(\mh{p})\right] = \sum_{n''=0}^{\infty} c_{n''}''z_{n''}(\mh{p}).    
+  \end{align}
+  Therefore, the coefficients are related by
+  \begin{align}
+    c_{n''}'' = \sum_{n=0}^\infty \sum_{n'=0}^\infty P_{n,n',n''} c_n c_{n'}'.
+  \end{align}
+  Rewriting this equation in Einstein notation (summation over matching indices
+  is implied, upper indices are ``column'' indices, lower indices are ``row''
+  indices) gives
+  \begin{align}
+    {c''}^{n''} = P^{n''}_{n,n'} c_n c_{n'}'.
+  \end{align}
+  We can precompute the triple integrals $P_{n,n',n''}$ using a symbolic package
+  like Sympy.
+
+  The discussion above applies to spherical harmonics as well---we only need to replace
+  the triple integral of the circular harmonics $P_{n,n',n''}$ with the triple integral
+  of the spherical harmonics
+  \begin{align}
+    G_{j,j',j''} = \int_{\mbb{S}^2}d\mh{s}\, y_{j}(\mh{s})y_{j'}(\mh{s})y_{j''}(\mh{s}).
+  \end{align}
+  where each of the $j$ indices are a single index over the spherical harmonics.
+  We could compute the triple integrals symbolically, but these integrals can
+  take several minutes. Instead, we can write the integral in terms of the Gaunt
+  coefficients \cite{homeier1996} which are products of the Clebsch-Gordan
+  coefficients or Wigner 3-j symbols. The Gaunt coefficients have a closed form
+  expression in terms of $j,j'$, and $j''$ (usually expressed in terms of
+  $l,l',l'',m,m',m''$) that is implemented in the Sympy library \cite{sympy}.
+
+  To calculate the kernel for general polarized light microscopes we will need to multiply functions in the following form
+  \begin{align}
+  f(\mh{p}, \mh{s}) = \sum_{n=0}^\infty\sum_{j=0}^\infty c_{n,j} z_n(\mh{p})y_j(\mh{s}), \qquad f'(\mh{p}, \mh{s}) = \sum_{n'=0}^\infty\sum_{j'=0}^\infty c_{n',j'}' z_n(\mh{p})y_j(\mh{s}).
+\end{align}
+The product will be in the form
+\begin{align}
+  f(\mh{p}, \mh{s})f'(\mh{p}, \mh{s}) = \sum_{n=0}^\infty\sum_{j=0}^\infty c_{n'',j''}'' z_{n''}(\mh{p})y_{j''}(\mh{s}),
+\end{align}
+where
+\begin{align}
+  {c''}^{n'', j''} = P_{n,n'}^{n''} G_{j,j'}^{j''} c_{n,j} c_{n', j'}'.\label{eq:final}
+\end{align}
+Equation \ref{eq:final} is the main result of this section. It shows that we can
+precalculate the triple integrals of the circular and spherical harmonics and
+use the results to efficiently find the coefficients of the product of two
+arbitrary kernels. We can think of Eq. \ref{eq:final} as a bilinear map that
+acts within the vector space of harmonic function coefficients. The bilinear map
+takes two elements of the vector space and maps them to another element of the
+vector space by a rank-6 tensor product. A lower dimensional example of a
+bilinear map is the cross product which takes two vectors in three-dimensional
+Euclidean space and maps them to another vector by a rank-3 tensor product.
 \end{document}

### 2018-05-22 notes/2018-05-14-single-view-continuous-svd/calculations/test-tfcoeffs.py

@@ -1,0 +1,9 @@
+from polharmonic import tfcoeffs, shcoeffs
+import numpy as np
+
+
+x = shcoeffs.SHCoeffs([0,1,0,0])
+y = shcoeffs.SHCoeffs([0,1,0,1])
+z = tfcoeffs.TFCoeffs([x,y,y])
+z2 = z+z
+import pdb; pdb.set_trace() 

### 2018-05-23 notes/2018-05-14-single-view-continuous-svd/report/report.tex
Patrick and Corey's corrections from group meeting.

@@
 Plugging the transfer function into the frequency-domain eigenvalue problem (Eq.
-\ref{eq:freqsvd}) yields a $3\times 3$ eigenvalue problem (we suppress the index
-$\bs{\rho}$ and understand that we need to solve this eigenvalue problem at each
-value of $\bs{\rho}$)
+\ref{eq:freqsvd}) yields a denumerably infinite eigenvalue problem with only
+$3\times 3$ non-zero entries in the matrix (we suppress the index $\bs{\rho}$
+and understand that we need to solve this eigenvalue problem at each value of
+$\bs{\rho}$)
 \begin{align}
@@
   \begin{align}
-    {c''}^{n''} = P^{n''}_{n,n'} c_n c_{n'}'.
+    {c''}^{n''} = P^{n''}_{n,n'} c^n {c'}^{n'}.
   \end{align}
@@
 \begin{align}
-  {c''}^{n'', j''} = P_{n,n'}^{n''} G_{j,j'}^{j''} c_{n,j} c_{n', j'}'.\label{eq:final}
+  {c''}^{n'', j''} = P_{n,n'}^{n''} G_{j,j'}^{j''} c^{n,j} {c'}^{n', j'}.\label{eq:final}
 \end{align}

### 2018-05-28 notes/2018-05-14-single-view-continuous-svd/report/report.tex
Continous SVD notes for single-view microscopes.

@@
   g(\rd{}, \mh{p}) = [\mathcal{H}f](\rd{}, \hat{\mb{p}}) &= \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{}; \hat{\mb{p}})f(\ro{}, \so{}),\\
-  f(\ro{}, \so{}) =  [\mathcal{H}^{\dagger}g](\ro{}, \so{}) &= \int_{\mbb{S}^1}d\hat{\mb{p}}\, \int_{\mbb{R}^2}d\mb{r}_{d}\, h(\rd{} - \ro{}, \so{}; \hat{\mb{p}})g(\rd{}, \hat{\mb{p}}).
+  f(\ro{}, \so{}) =  [\mathcal{H}^{\dagger}g](\ro{}, \so{}) &= \int_{\mbb{S}^1}d\hat{\mb{p}}\, \int_{\mbb{R}^2}d\mb{r}_{d}\, h(\rd{} - \ro{}, \so{}; \hat{\mb{p}})g(\rd{}, \hat{\mb{p}}),
 \end{align}
@@
 We can write the forward and adjoint operators in the frequency domain as
-% \begin{align}
-%   g(\rd{}, \hat{\mb{p}}) = \sum_{n=-\infty}^{\infty} z_n(\mh{p}) \sum_{l=0}^{\infty}\sum_{m=-l}^{l} \int_{\mbb{R}^2}d\bs{\nu}\, H_{l,n}^m(\bs{\nu})F_l^m(\bs{\nu}), 
-    %   \end{align}
 \begin{align}
@@
   G_{n}(\bs{\nu}) &= \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})\int_{\mbb{R}^2}d\rd{}\, \me{}^{i2\pi\rd{}\cdot\bs{\nu}}g(\rd{}, \mh{p}),\\
-  H_{l,n}^m(\bs{\nu}) &= \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})\int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}h(\ro{}, \so{}; \mh{p}),\\
+  H_{l,n}^m(\bs{\nu}) &= \int_{\mbb{S}^1}d\mh{p}\, z_n(\mh{p})\int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}h(\ro{}, \so{}; \mh{p}),\label{eq:genft}\\ 
   F_{l}^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}f(\ro{}, \so{}).
@@
 \end{align}
+We derived this excitation kernel using the model from Chandler et al.
+\cite{chandler17}---a model modified from Fourkas \cite{fourkas2001}. Both
+papers claim that their equations model aplanatic (shift-invariant) objectives,
+but this is not strictly true. Fourkas and Chandler ignore the
+$1/\sqrt{\cos\theta}$ apodization factor for aplanatic objectives and
+unknowingly model a non-aplanatic objective that satisfies the Herschel
+condition instead of Abbe's sine condition. The difference between these
+models is small but non-zero under the paraxial approximation.
 
-We also showed that the point response function for unpolarized epi-detection is
+In the most recent string of note sets I have been modeling a true aplanatic
+objective under the paraxial approximation. The correct paraxial excitation model
+for an aplanatic objective is 
+\begin{align}
+  h^{\text{(ap)},\mh{z}}_{\text{exc}}(\so{}; \mh{p}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\left[1 - 2\left(\frac{\text{NA}}{n_o}\right)^2\right]y_2^0(\so{}) + \sqrt{\frac{3}{5}}\left\{y_2^2(\so{})z_2(\mh{p}) - y_2^{-2}(\so{})z_{-2}(\mh{p})\right\}.
+\label{eq:aplan}
+\end{align}
+We will drop the (ap) superscript unless there is possibility for confusion. Eq.
+\ref{eq:aplan} shows that for an aplanatic objective under the paraxial
+approximation, the $y_2^0$ term is excited less relative to the $y_0^0$ term as
+the NA increases (recall that the kernel is normalized). We also see that the
+$y_2^2$ and $y_2^{-2}$ terms do not depend on the NA, but they do depend on the
+polarizer orientation.
+
+Relevant discussion of Abbe's sine condition, the Herschel condition,
+apodization functions, and the paraxial approximation can be found in Barrett
+9.6.7 \cite{barrett2004}, Mansuripur 1.0 \cite{mansuripur2002}, and especially
+Gu 6.3 \cite{gu2000}. Although we (and Fourkas) incorrectly stated that we were
+modeling an aplanatic objective in \cite{chandler17}, we brought attention to
+our lack of apodization in the discussion section. All of our major conclusions
+would still hold if we used the correct apodization (and our numerical results
+hold for Herschel objectives although these are rarely used in microscopy).
+
+We also showed that the kernel for unpolarized epi-detection is
 given by
@@
 The excitation and detection processes are incoherent, so to find the complete
-point response function we can multiply the excitation and detection point response
-functions which gives
+kernel we multiply the excitation and detection kernels
 \begin{align}
-  h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \frac{1}{\tilde{N}}\sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}),
+  h(\ro{}, \so{}; \mh{p}) = h^{\mh{z}}_{\text{exc}}(\so{}; \mh{p})h_{\text{det}}(\ro{}, \so{}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}).
 \end{align}
-where $\tilde{N} = \frac{\tilde{A}}{10} + \frac{1}{2}$ is a normalization constant
-and the terms in the series are given by
-\begin{align}
-  h_{0,0}^0(r_o) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]a^2(r_o) + \left[-\frac{2\tilde{A}}{5} + 1\right]b^2(r_o),\\
-  h_{2,2}^{2}(r_o) &= -h_{2,-2}^{-2}(r_o) = \frac{3\sqrt{15}\tilde{B}}{35}\left[\frac{3}{2}a^2(r_o) + b^2(r_o)\right],\\
-  h_{2,0}^0(r_o) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]a^2(r_o) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]b^2(r_o),\\
-  h_{4,2}^{2}(r_o) &= -h_{4,-2}^{-2}(r_o) = \frac{6\sqrt{5}\tilde{B}}{35}\left[-\frac{1}{4}a^2(r_o) + b^2(r_o)\right],\\
-  h_{4,0}^0(r_o) &= \frac{3\tilde{A}}{35}[a^2(r_o) - 4b^2(r_o)],\\
-\end{align}
-and all other $h_{l,n}^m(r_o)$ terms in the series are zero.
+In previous notes we were able to calculate these products in terms of the
+circular and spherical harmonics by hand, but this is time consuming and error
+prone. To simplify the multiplication we precompute the triple integrals of the
+circular and spherical harmonics and compute the product using a tensor
+product---see Appendix A for details.
+
+We can write a closed form expression for the kernel, but the expression is long
+and not particularly useful. Instead, we plot each term of the kernel in Fig.
+\ref{fig:illkern}.
+
+\fig{../calculations/out/hhill.pdf}{1.0}{Five-dimensional kernel
+  $h_{l,n}^m(\ro{})$ for a single-view polarized illumination microscope with
+  0.8 NA epi-illumination and epi-detection. \textbf{Rows:} $l$ indexes the
+  object-space spherical harmonic band. \textbf{Columns:} $m$ indexes the
+  object-space spherical harmonic degree, and $n$ indexes the data-space
+  circular harmonic band. \textbf{Entries:} Each column and row contains a
+  continuous two-dimensional plot indexed by the vector $\ro{}$ ranging from
+  $-2\lambda/\text{NA}$ to $+2\lambda/\text{NA}$ (although $\ro{}$ is
+  rotationally symmetric so one dimension would suffice). All values are
+  normalized between $-1$ \textcolor{blue}{(blue)} and $+1$
+  \textcolor{red}{(red)} with $0$ colored white.}{illkern}
+  % filename, width, caption, label
+
+Each of the ($l,m,n$) terms of the kernel shown in Fig. \ref{fig:illkern} can be
+interpreted as the shape of the $z_n(\mh{p})$ component of the intensity pattern
+detected when the object consists of $y_l^m(\so{})$ distributed dipoles. For
+example, the $l=0$, $m=0$, $n=0$ term shows the intensity pattern for the
+$z_0(\mh{p})$ (constant) component detected when the object consists of
+$y_0^0(\so{})$ (uniformly distributed) dipoles. Notice that the $l=0$, $m=0$,
+$n=\pm 2$ terms are zero which means that the intensity pattern from a uniform
+distribution of fluorophores is independent of the polarizer orientation.
+
+Interestingly, every ($l$, $m$) term in the kernel has a single $n$ term that is
+non-zero. This means that each spherical harmonic component in object space
+gives rise to a single circular harmonic component in data space. This property
+is specific to polarized illumination microscopes.
+
+Finally, notice that the polarizer dimension is limited to $n= \{-2, 0, 2\}$.
+The three terms mean that three polarizer orientations are sufficient to
+completely sample that dimension. We have suspected that three measurements are
+sufficient because the polarization dependence of an intensity signal can be
+specified with three numbers---an offset, an amplitude, and a phase. The three
+circular harmonic components of the signal capture the same information as the
+offset, amplitude, and phase; and they are orthogonal functions so they allow us
+to use frequency domain techniques.
 
 \subsection{Transfer function}
-The optical transfer function for this microscope is given by
+We can calculate the transfer function using Eq. \ref{eq:genft} and the kernel,
+but this will lead to a very long expression. Instead, we calculate the
+illumination transfer function and the detection transfer function then use the
+multiplication rules in Appendix A to find the complete transfer function.
+
+The illumination transfer function is
 \begin{align}
-  H_{l,n}^m(\nu) = \frac{1}{\tilde{M}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}\sum_{n'=-\infty}^{\infty} H_{l',n'}^{m'}(\nu)\delta_{l,l'}\delta_{m,m'}\delta_{n,n'},  
+  H^m_{\text{exc},l,n} &= \delta_{l,0}\delta_{m,0}\delta_{n,0} - \frac{1}{\sqrt{5}}\left[1 - 2\left(\frac{\text{NA}}{n_o}\right)^2\right]\delta_{l,2}\delta_{m,0}\delta_{n,0} + \sqrt{\frac{3}{5}}\left\{\delta_{l,2}\delta_{m,2}\delta_{n,2} - \delta_{l,-2}\delta_{m,-2}\delta_{n,-2}\right\},
+\end{align}
+and the detection transfer function is 
+\begin{align}
+  H^m_{\text{det},l,n}(\nu) &= [A(\nu) + 2B(\nu)]\delta_{l,0}\delta_{m,0}\delta_{n,0} + \frac{1}{\sqrt{5}}\left[- A(\nu) + 4B(\nu)\right]\delta_{l,2}\delta_{m,0}\delta_{n,0},
 \end{align}
 where
-$\tilde{M} = \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right] + \left(\frac{\text{NA}}{n_o}\right)\left[-\frac{2\tilde{A}}{10} + \frac{1}{2}\right]$ is a
-normalization constant, and
-\begin{align}
-  H_{0,0}^0(\nu) &= \left[\frac{\tilde{A}}{10} + \frac{1}{2}\right]A(\nu) + \left[-\frac{2\tilde{A}}{5} + 1\right]B(\nu),\\
-  H_{2,2}^{2}(\nu) &= -H_{2,-2}^{-2}(\nu) = \frac{3\sqrt{15}\tilde{B}}{35}\left[\frac{3}{2}A(\nu) + B(\nu)\right],\\
-  H_{2,0}^0(\nu) &= \left[-\frac{\sqrt{5}\tilde{A}}{14} + \frac{\sqrt{5}}{10}\right]A(\nu) + \left[-\frac{11\sqrt{5}\tilde{A}}{35} + \frac{2}{\sqrt{5}}\right]B(\nu),\\
-  H_{4,2}^{2}(\nu) &= -H_{4,-2}^{-2}(\nu) = \frac{6\sqrt{5}\tilde{B}}{35}\left[-\frac{1}{4}A(\nu) + B(\nu)\right],\\
-  H_{4,0}^0(\nu) &= \frac{3\tilde{A}}{35}[A(\nu) - 4B(\nu)],
-\end{align}
-and all other $H_{l,n}^m(\nu)$ terms in the series are zero, and  
 \begin{align}
@@
 \end{align}
+The complete transfer function is given by
+\begin{align}
+  H_{l,n}^m(\nu) = H^m_{\text{exc},l,n} * H^m_{\text{det},l,n}(\nu),
+\end{align}
+where $*$ denotes a generalized convolution over all five indices. In Appendix A
+we show how to evaluate the convolution over the discrete indices. The
+excitation pattern is spatially uniform, so the spatial convolution is trivial.
+We plot the complete transfer function in Fig. \ref{fig:illtran}.
+\fig{../calculations/out/Hill.pdf}{1.0}{Five-dimensional transfer function
+  $H_{l,n}^m(\bs{\nu})$ for a single-view polarized illumination microscope with
+  0.8 NA epi-illumination and epi-detection. \textbf{Rows:} $l$ indexes the
+  object-space spherical harmonic band. \textbf{Columns:} $m$ indexes the
+  object-space spherical harmonic degree, and $n$ indexes the data-space
+  circular harmonic band. \textbf{Entries:} Each column and row contains a
+  continuous two-dimension plot indexed by the vector $\bs{\nu}$ ranging from
+  $-2\text{NA}/\lambda$ to $+2\text{NA}/\lambda$. All values are normalized
+  between $-1$ \textcolor{blue}{(blue)} and $+1$ \textcolor{red}{(red)} with $0$
+  colored white. Black lines are contours at 0 and $\pm 0.1$.}{illtran}
+% filename, width, caption, label
 
@@
 \end{align}
+Finally, the singular values are the square root of the eigenvalues
+\begin{align}
+  \sigma_{\bs{\rho},j} = \sqrt{\mu_{\bs{\rho},j}}. 
+\end{align}
 
 We have found the complete singular system for a single view microscope with
-polarized illumination. We can look closer at the singular value spectrum to
-find the degeneracies of the microscope. The first major set of degeneracies is
-related to the fact that $\mu_{\bs{\rho},1} = \mu_{\bs{\rho},2}$. The
-corresponding singular functions in object space are related by changing the
-spherical harmonic index $m$ to $-m$. This transformation is a rotation about
-the optical axis, so this degeneracy corresponds to the rotational symmetry of
-the microscope. The second set of degeneracies is related to the fact that the
-singular values depend only on $\rho$, not the vector $\bs{\rho}$. The
-corresponding singular functions in object space are spatial harmonics at the
-same spatial frequency in different directions. Once again, this degeneracy
-corresponds to the rotational symmetry of the microscope.
+polarized illumination. In Fig. \ref{fig:illsvs} we show all three branches of
+the singular spectrum along with the angular part of the object space singular
+functions $u_{\bs{\rho},j}(0, \so{})$.
+
+\fig{../calculations/out/SVSill.pdf}{1.0}{Singular system for a single-view
+  polarized illumination microscope with 0.8 NA epi-illumination and
+  epi-detection. \textbf{Rows:} Discrete branches of the singular value system
+  indexed by $j$. \textbf{Column 1:} Continuous singular value spectra for each
+  branch $j$ indexed by spatial frequency $\bs{\rho}$. The singular value
+  spectra are normalized with contour lines at 0 and 0.1. \textbf{Columns 2-5:}
+  Angular part of the object-space singular vector at spatial frequencies marked
+  with `x's in the first column. The camera is facing the origin along the
+  [1,1,1] axis with the optical axis of the microscope pointing up along the
+  page. A \textcolor{red}{red} surface indicates positive values, a
+  \textcolor{blue}{blue} surface indicates negative values, and the distance
+  from the origin indicates the magnitude.}{illsvs}
+
+All three branches of the singular system have object-space singular functions
+that depend on the spatial frequency (the plots in each column and row of Fig.
+\ref{fig:illsvs} are different). This dependence is largest in the $j=0$ branch
+where at low spatial frequencies the singular functions are nearly spherical,
+while at high spatial frequencies the singular functions are negative along the
+optical axis. The fact that the singular functions of the $j=0$ branch are
+non-spherical and have a spatial-frequency dependence is the most important
+result of this section---it means that a single view microscope can distinguish
+distributions of fluorophores that have different out-of-transverse-plane
+components. The $j=1$ and $j=2$ object-space singular functions still depend on
+the spatial frequency---the high-frequency singular functions are ``flatter'' in
+the transverse plane than the low-frequency singular functions---but this
+dependence is relatively small.
+
+We can use the singular value spectrum to find the degeneracies and symmetries
+of the microscope. The first major set of degeneracies is related to the fact
+that $\sigma_{\bs{\rho},1} = \sigma_{\bs{\rho},2}$. The corresponding singular
+functions in object space are related by changing the spherical harmonic index
+$m$ to $-m$. This transformation is a rotation about the optical axis, so this
+degeneracy corresponds to the rotational symmetry of the microscope. The second
+set of degeneracies is related to the fact that the singular values depend only
+on $\rho$, not the vector $\bs{\rho}$. The corresponding singular functions in
+object space are spatial harmonics at the same spatial frequency in different
+directions. Once again, this degeneracy corresponds to the rotational symmetry
+of the microscope.
 
@@
 
-Plots forthcoming!
+We have only plotted the object space singular functions for spatial frequencies
+along the $x$-axis, but these are sufficient to characterize the singular
+functions for any spatial frequency direction. To see this, notice that the
+$j=0$ singular functions are rotationally symmetric about the optical axis and
+the $j=1$ and $j=2$ singular functions are degenerate and they span a
+rotationally symmetric space of singular functions.
 
@@
 \subsection{Kernel}
-In previous notes we showed that the excitation point response function for
+Earlier we showed that the excitation point response function for
 unpolarized epi-illumination is given by
 \begin{align}
-  h_{\text{exc}}^{\mh{z}}(\so{}) = h_{\text{exc},0,0}^0y_0^0(\so{}) + h_{\text{exc},0,0}^2y_2^0(\so{}).
+  h^{\mh{z}}_{\text{exc}}(\so{}) &= y_0^0(\so{}) - \frac{1}{\sqrt{5}}\left[1 - 2\left(\frac{\text{NA}}{n_o}\right)^2\right]y_2^0(\so{}).
 \end{align}
-where
-\begin{align}
-  h_{\text{exc},0,0}^0 &= 1,\\
-  h_{\text{exc},2,0}^0 &= -\frac{1}{\sqrt{5}}\tilde{A}.
-\end{align}
-
 We also showed that the point response function for polarized detection is given
@@
 The complete kernel for unpolarized illumination and polarized detection is
-given by the product of the excitation and detection kernels. In the previous
-case we were able to calculate this product in terms of the circular and
-spherical harmonics by hand, but this task is difficult in the general case. To
-simplify this task we precompute the triple integrals of the circular and spherical
-harmonics---see Appendix A for details. 
+given by the product of the excitation and detection kernels. We plot the
+result in Fig. \ref{fig:detkern}.
+
+\fig{../calculations/out/hhdet.pdf}{1.0}{Five-dimensional kernel
+  $h_{l,n}^m(\ro{})$ for a single-view polarized detection microscope with
+  0.8 NA epi-illumination and epi-detection. \textbf{Rows:} $l$ indexes the
+  object-space spherical harmonic band. \textbf{Columns:} $m$ indexes the
+  object-space spherical harmonic degree, and $n$ indexes the data-space
+  circular harmonic band. \textbf{Entries:} Each column and row contains a
+  continuous two-dimensional plot indexed by the vector $\ro{}$ ranging from
+  $-2\lambda/\text{NA}$ to $+2\lambda/\text{NA}$ (although $\ro{}$ is
+  rotationally symmetric so one dimension would suffice). All values are
+  normalized between $-1$ \textcolor{blue}{(blue)} and $+1$
+  \textcolor{red}{(red)} with $0$ colored white.}{detkern}
+  % filename, width, caption, label
+
+In the polarized illumination case every ($l$, $m$) term in the kernel had a
+single $n$ term that is non-zero. For polarized detection this is no longer
+true---for example there are non-zero components for $l=0$, $m=0$ in the
+$n=0, \pm 2$ terms. This means that each spherical harmonic component in object
+space gives rise to multiple circular harmonic components in data space.
+
+\subsection{Transfer function}
+The transfer function for unpolarized illumination is
 \begin{align}
-  h(\ro{}, \so{}; \mh{p}_d) = h_{\text{exc}}(\so{})h_{\text{det}}(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
+  H^m_{\text{exc}, l,n} &= \delta_{l,0}\delta_{m,0}\delta_{n,0} - \frac{1}{\sqrt{5}}\left[1 - 2\left(\frac{\text{NA}}{n_o}\right)^2\right]\delta_{l,2}\delta_{m,0}\delta_{n,0},
+\end{align}
+and the transfer function for polarized detection is
+\begin{align}
+  H_{\text{det},l,n}^m(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} H_{\text{det},l,n}^m(\bs{\nu})\delta_{l,l'}\delta_{m,m'}\delta_{n,n'}, 
 \end{align}
@@
 \begin{align}
-  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}),\\
-  h_{0,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}),\\
-  h_{2,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
-  h_{2,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
-  h_{2,\pm 2}^{\pm 2}(\ro{}) &= h_{\text{det},2,\pm 2}^{\pm 2}(\ro{})\left[h_{\text{exc},0,0}^0 - \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0\right],\\
-  h_{4,0}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
-  h_{4,\pm 2}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
-  h_{4,\pm 2}^{\pm 2}(\ro{}) &= \frac{\sqrt{15}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^{\pm 2}(\ro{}),
+  H_{\text{det},0,0}^0(\bs{\nu}) &= A(\nu) + 2B(\nu),\\
+  H_{\text{det},0,\pm 2}^0(\bs{\nu}) &= 2\sqrt{\pi} C(\nu)z_{\pm 2}(\bs{\nu}),\\
+  H_{\text{det},2,0}^0(\bs{\nu}) &= \frac{1}{\sqrt{5}}\left[-A(\nu) + 4B(\nu)\right],\\
+  H_{\text{det},2,\pm 2}^0(\bs{\nu}) &= 4\sqrt{\frac{\pi}{5}}C(\nu)z_{\pm 2}(\bs{\nu}),\\
+  H_{\text{det},2,2}^2(\bs{\nu}) &= -H_{\text{det},2,-2}^{-2}(\bs{\nu}) = \sqrt{\frac{3}{5}}A(\nu).
 \end{align}
-% hh0
-% [h000d*h000e + h200d*h200e, 0, 0, h000d*h200e + h000e*h200d + 2*sqrt(5)*h200d*h200e/7, 0, 0, 0, 0, 0, 0, 6*h200d*h200e/7, 0, 0, 0, 0]
-
-% hh2
-% [h000e*h002d + h200e*h202d, 0, 0, h000e*h202d + h002d*h200e + 2*sqrt(5)*h200e*h202d/7, 0, h222d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, 0, 0, 0, 6*h200e*h202d/7, 0, sqrt(15)*h200e*h222d/7, 0, 0]
-
-% hh_2
-% [h000e*h00_2d + h200e*h20_2d, h2_2_2d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, h000e*h20_2d + h00_2d*h200e + 2*sqrt(5)*h200e*h20_2d/7, 0, 0, 0, 0, sqrt(15)*h200e*h2_2_2d/7, 0, 6*h200e*h20_2d/7, 0, 0, 0, 0]
-and the remaining terms in the series are zero. Plugging in the excitation and
-detection point response functions gives the following
+and
 \begin{align}
-  h_{0,0}^0(\ro{}) &= \left[\frac{\tilde{A}}{5} + 1\right]a^2(r_o) + \left[-\frac{4\tilde{A}}{5} + 2\right]b^2(r_o),\\ 
-  h_{0,\pm 2}^0(\ro{}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]b^2(r_o)z_{\pm 2}(\ro{}),\\ 
-  h_{2,0}^0(\ro{}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]a^2(r_o) + \left[-22\tilde{A} + 28\right]b^2(r_0)\right\},\\ 
-  h_{2,\pm 2}^0(\ro{}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]b^2(r_o)z_{\pm 2}(\ro{})\\ 
-  h_{2,2}^{2}(\ro{}) &= h_{2,-2}^{-2}(\ro{}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]a^2(r_o),\\ 
-  h_{4,0}^0(\ro{}) &= \frac{6\tilde{A}}{35}\left[a^2(r_o) - 4b^2(r_o)\right],\\ 
-  h_{4,\pm 2}^0(\ro{}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}b^2(r_o)z_{\pm 2}(\ro{}),\\ 
-  h_{4,2}^{2}(\ro{}) &= h_{4,-2}^{-2}(\ro{}) = -\frac{3\sqrt{5}}{35}\tilde{A}a^2(r_o). 
-\end{align}
-% hh0
-% [At*(a - 4*b)/5 + a + 2*b, 0, 0, sqrt(5)*(-5*At*a - 22*At*b - 7*a + 28*b)/35, 0, 0, 0, 0, 0, 0, 6*At*(a - 4*b)/35, 0, 0, 0, 0]
-
-% hh2
-% [2*sqrt(pi)*b*z2*(-2*At + 5)/5, 0, 0, 2*sqrt(5)*sqrt(pi)*b*z2*(-11*At + 14)/35, 0, a*(2*sqrt(15)*At/35 + sqrt(15)/5), 0, 0, 0, 0, -24*sqrt(pi)*At*b*z2/35, 0, -sqrt(15)*sqrt(3)*At*a/35, 0, 0]
-
-% hh_2
-% [2*sqrt(pi)*b*z_2*(-2*At + 5)/5, a*(0.221313334068995*At + 0.774596669241483), 0, 2*sqrt(5)*sqrt(pi)*b*z_2*(-11*At + 14)/35, 0, 0, 0, 0, -0.110656667034498*sqrt(3)*At*a, 0, -24*sqrt(pi)*At*b*z_2/35, 0, 0, 0, 0]
-
-\subsection{Transfer function}
-The transfer function for unpolarized illumination and polarized detection is
-given by
-\begin{align}
-  H_{l,n}^m(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} H_{l,n}^m(\bs{\nu})\delta_{ll'}\delta_{mm'}\delta_{nn'},
-\end{align}
-where
-\begin{align}
-  H_{0,0}^0(\bs{\nu}) &= \left[\frac{\tilde{A}}{5} + 1\right]A(\nu) + \left[-\frac{4\tilde{A}}{5} + 2\right]B(\nu),\\ 
-  H_{0,\pm 2}^0(\bs{\nu}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
-  H_{2,0}^0(\bs{\nu}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]A(\nu) + \left[-22\tilde{A} + 28\right]B(r_0)\right\},\\ 
-  H_{2,\pm 2}^0(\bs{\nu}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]C(\nu)z_{\pm 2}(\bs{\nu})\\ 
-  H_{2,2}^{2}(\bs{\nu}) &= H_{2,-2}^{-2}(\bs{\nu}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]A(\nu),\\ 
-  H_{4,0}^0(\bs{\nu}) &= \frac{6\tilde{A}}{35}\left[A(\nu) - 4B(\nu)\right],\\ 
-  H_{4,\pm 2}^0(\bs{\nu}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
-  H_{4,2}^{2}(\bs{\nu}) &= H_{4,-2}^{-2}(\bs{\nu}) = -\frac{3\sqrt{5}}{35}\tilde{A}A(\nu). 
-\end{align}
-where 
-\begin{align}
-  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
   C(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[-\frac{4}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
+Fig. \ref{fig:dettran} shows the complete transfer function for a polarized
+detection microscope.
+
+\fig{../calculations/out/Hdet.pdf}{1.0}{Five-dimensional transfer function
+  $H_{l,n}^m(\bs{\nu})$ for a single-view polarized detection microscope with
+  0.8 NA epi-illumination and epi-detection. \textbf{Rows:} $l$ indexes the
+  object-space spherical harmonic band. \textbf{Columns:} $m$ indexes the
+  object-space spherical harmonic degree, and $n$ indexes the data-space
+  circular harmonic band. \textbf{Entries:} Each column and row contains a
+  continuous two-dimension plot indexed by the vector $\bs{\nu}$ ranging from
+  $-2\text{NA}/\lambda$ to $+2\text{NA}/\lambda$. All values are normalized
+  between $-1$ \textcolor{blue}{(blue)} and $+1$ \textcolor{red}{(red)} with $0$
+  colored white. Black lines are contours at 0 and $\pm 0.1$.}{dettran}
+% filename, width, caption, label
 
@@
 with notation and provide little insight. Instead we proceed straight to plots
-of the eigenvalues and eigenvectors shown in Fig. XXX.
+of the singular system shown in Fig. \ref{fig:detsvs}.
+
+\fig{../calculations/out/SVSdet.pdf}{1.0}{Singular system for a single-view
+  polarized detection microscope with 0.8 NA epi-illumination and
+  epi-detection. \textbf{Rows:} Discrete branches of the singular value system
+  indexed by $j$. \textbf{Column 1:} Continuous singular value spectra for each
+  branch $j$ indexed by spatial frequency $\bs{\rho}$. The singular value
+  spectra are normalized with contour lines at 0 and 0.1. \textbf{Columns 2-5:}
+  Angular part of the object-space singular vector at spatial frequencies marked
+  with `x's in the first column. The camera is facing the origin along the
+  [1,1,1] axis with the optical axis of the microscope pointing up along the
+  page. A \textcolor{red}{red} surface indicates positive values, a
+  \textcolor{blue}{blue} surface indicates negative values, and the distance
+  from the origin indicates the magnitude.}{detsvs}
+
+First, notice that the DC term ($\bs{\rho} = 0$, $j=0$) of the polarized
+detection singular system in Fig. \ref{fig:detsvs} is identical to the DC term
+of the polarized illumination singular system in FIg. \ref{fig:illsvs}. This is
+a result we've seen before---if we ignore spatio-angular coupling then polarized
+illumination and polarized detection microscopes measure identical components of
+the object.
+
+Second, notice that there are no longer any degeneracies between the three
+branches of the singular spectrum (except at $\bs{\rho} = 0$). This means that
+moving the polarizer to the detection arm breaks a symmetry. Rotating each
+individual point in object space no longer has a corresponding transformation in
+data space because the polarizer introduces spatio-angular coupling. Each of the
+branches of the singular spectrum is still rotationally symmetric, though, so we
+preserve one of the symmetries---rotating the object about the optical axis will
+still rotate the data space about the curved axis that runs through the center
+of donut (the ``glaze inversion''!).
+
+Third, notice that the singular values of the polarized detection microscope are
+larger than the singular values of the polarized illumination microscope at all
+spatial frequencies except $\bs{\rho} = 0$ where they are equal. This means that
+a polarized detection microscope passes orthogonal components of the object more
+efficiently (the signal is less corruptible by noise) than a polarized
+illumination microscope. Although the difference is not extremely large---3-4\%
+at most---this is the most convincing reason that we should prefer polarized
+detection over polarized illumination.
+
+Finally, consider the singular functions. The singular functions are no longer
+rotationally symmetric at non-zero spatial frequencies which means that we would
+see rotated singular functions if we showed the singular functions for spatial
+frequencies off of the $x$-axis. We also see that the singular functions contain
+out-of-plane components at high spatial frequencies (espsecially in the $j=1$
+branch) just like the the polarized illumination case.
 
@@
   $c_{n'}'$) and the output coefficients $c_{n''}''$. To find this relationship
-  we can rewrite the product the circular harmonics as a linear combination of
+  we can write the product the circular harmonics as a linear combination of
   circular harmonics

### 2018-05-28 notes/2018-05-14-single-view-continuous-svd/calculations/convertAB.py

@@ -1,0 +1,15 @@
+from sympy import *
+
+# A = Symbol('A', real=True)
+# B = Symbol('B', real=True)
+alpha = Symbol('alpha', real=True)
+n = Symbol('n', real=True)
+
+A = (cos(alpha/2)**2)*(cos(alpha))
+At = A.subs([(alpha, asin(n))])
+As = simplify(expand(At))
+
+B =  (cos(alpha)**2 + 4*cos(alpha) + 7)/12
+Bt = B.subs([(alpha, asin(n))])
+Bs = simplify(expand(Bt))
+import pdb; pdb.set_trace() 

### 2018-05-28 notes/2018-05-14-single-view-continuous-svd/calculations/svd-tools.py

@@ -1,0 +1,150 @@
+from polharmonic import util as myutil
+from sympy import *
+from sympy.physics.wigner import gaunt, wigner_3j, clebsch_gordan
+kd = KroneckerDelta
+import numpy as np
+
+# Illumination 
+def hill(polarizer=True):
+    At = Symbol('At')
+    Bt = Symbol('Bt')
+    
+    n0 = [1, 0, 0, -At/sqrt(5), 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+    if polarizer:
+        n_2 = [0, -sqrt(3*pi/5)*Bt, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        n2 = [0, 0, 0, 0, 0, sqrt(3*pi/5)*Bt, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        return Array([n0, n_2, n2])
+    else:
+        return Array([n0, 15*[0], 15*[0]])
+
+# No detection spatioangular coupling -> h == H
+def Hill(polarizer=True): 
+    return hill(polarizer)
+
+# Detection
+def hdet(polarizer=False):
+    a = Symbol('a')
+    b = Symbol('b')
+    phi = Symbol('phi')
+    n0 = [a + 2*b, 0, 0, (-a + 4*b)/sqrt(5), 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+    if polarizer:
+        n_2 = [2*b*sin(2*phi), -sqrt(3/5)*a, 0, (4/sqrt(5))*b*sin(2*phi), 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        n2 = [2*b*cos(2*phi), 0, 0, (4.0/sqrt(5))*b*cos(2*phi), 0, sqrt(3/4)*a, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        return Array([n0, n_2, n2])
+    else:
+        return Array([n0, 15*[0], 15*[0]])
+
+def Hdet(polarizer=False):
+    A = Symbol('A')
+    B = Symbol('B')
+    C = Symbol('C')
+    phi_nu = Symbol('phi_nu')
+    n0 = [A + 2*B, 0, 0, (-A + 4*B)/sqrt(5), 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
[…]

### 2018-05-28 polharmonic/det.py

@@ -42,11 +42,12 @@ class Detector:
         C = self.C
         n0 = [A(nu) + 2*B(nu), 0, 0, (-A(nu) + 4*B(nu))/np.sqrt(5), 0, 0]
         if self.polarizer:
-            n_2 = [2*C(nu)*np.cos(2*phi_nu), -np.sqrt(0.6)*A(nu), 0, (4.0/np.sqrt(5))*C(nu)*np.cos(2*phi_nu), 0, 0]
-            n2 = [2*C(nu)*np.sin(2*phi_nu), 0, 0, (4.0/np.sqrt(5))*C(nu)*np.sin(2*phi_nu), 0, np.sqrt(0.6)*A(nu)]
-            return tf.TFCoeffs([n0, n_2, n2])
+            n_2 = [2*C(nu)*np.sin(2*phi_nu), -np.sqrt(0.6)*A(nu), 0, (4.0/np.sqrt(5))*C(nu)*np.sin(2*phi_nu), 0, 0]
+            n2 = [2*C(nu)*np.cos(2*phi_nu), 0, 0, (4.0/np.sqrt(5))*C(nu)*np.cos(2*phi_nu), 0, np.sqrt(0.6)*A(nu)]
+            return tf.TFCoeffs([n0, n_2, n2])#/n0[0]
         else:
-            return tf.TFCoeffs([n0, 6*[0], 6*[0]])
+            return tf.TFCoeffs([n0, 6*[0], 6*[0]])#/n0[0]
+
         
     # PSF helper functions
     def a(self, r):

### 2018-05-28 polharmonic/ill.py

@@ -21,21 +21,23 @@ class Illuminator:
         self.illuminate_all = illuminate_all
 
         self.alpha = np.arcsin(self.na/self.n)
-        self.At = (np.cos(self.alpha/2.0)**2)*np.cos(self.alpha)
-        self.Bt = (1.0/12.0)*(np.cos(self.alpha/2)**2 + 4*np.cos(self.alpha) + 7)
+        # self.At = (np.cos(self.alpha/2.0)**2)*np.cos(self.alpha)
+        # self.Bt = (1.0/12.0)*(np.cos(self.alpha/2)**2 + 4*np.cos(self.alpha) + 7)
 
     def h(self):
         if self.illuminate_all:
             return tf.TFCoeffs([[1.0, 0, 0, 0, 0, 0], 6*[0], 6*[0]])
 
-        n0 = [1, 0, 0, -self.At/np.sqrt(5), 0, 0]
+        n0 = [1 + (self.na/self.n)**2, 0, 0, -(1 - 2*((self.na/self.n)**2))/np.sqrt(5), 0, 0]
         if self.polarizer:
-            n_2 = [0, -np.sqrt(0.6*np.pi)*self.Bt, 0, 0, 0, 0]
-            n2 = [0, 0, 0, 0, 0, np.sqrt(0.6*np.pi)*self.Bt]
-            return tf.TFCoeffs([n0, n_2, n2])
+            n_2 = [0, -np.sqrt(3/5), 0, 0, 0, 0]
+            n2 = [0, 0, 0, 0, 0, np.sqrt(3/5)]
+            return tf.TFCoeffs([n0, n_2, n2])#/n0[0]
         else:
-            return tf.TFCoeffs([n0, 6*[0], 6*[0]])
+            return tf.TFCoeffs([n0, 6*[0], 6*[0]])#/n0[0]
 
     # No detection spatioangular coupling -> h == H
     def H(self): 
         return self.h()
+
+    

### 2018-05-28 polharmonic/micro.py

@@ -1,5 +1,6 @@
+import os
 import numpy as np
-from polharmonic import util, ill, det
+from polharmonic import util, ill, det, gaunt, shcoeffs
 import matplotlib.pyplot as plt
 import matplotlib
 matplotlib.rcParams['contour.negative_linestyle'] = 'solid'
@@ -29,7 +30,8 @@ class Microscope:
     def H(self, nu, phi_nu=0):
         return self.ill.H()*self.det.H(nu, phi_nu=phi_nu)/self.Hnorm
 
-    def plot(self, func=h, filename='micro.pdf', n_px=2**6, plot_m=[-2, 0, 2]):
+    def plot(self, func=h, filename='micro.pdf', n_px=2**6, plot_m=[-2, 0, 2],
+             contours=True):
         print('Plotting: ' + filename)
         
         # Calculate data for plotting
@@ -42,7 +44,7 @@ class Microscope:
         data = np.zeros((n_px, n_px, self.n_len, self.j_len))
         for index, r in np.ndenumerate(R):
             data[index[0], index[1], :, :] = (func(r, Phi[index])).coeffs
-                
+
         # Layout windows
         if plot_m is None:
             mcols = self.h0.rmax
@@ -73,7 +75,12 @@ class Microscope:
                 if index[1] % 3 == 1:
                     ax.annotate('$n='+str(n)+'$', xy=(1, 1), xytext=(0.5, 1.4),
                                 textcoords='axes fraction', ha='center', va='center')
-                    
+            if index[1] % 3 == 2 and index[1] != axs.shape[1] - 1:
+                ax.annotate("",
+                            xy=(1, -0.05), xycoords='axes fraction',
+                            xytext=(1, 1.3), textcoords='axes fraction',
+                            arrowprops=dict(arrowstyle="-", 
+                                            linewidth=0.5))
                 
             if index[1] == 0:
                 ax.annotate('$l='+str(l)+'$', xy=(1, 1), xytext=(-0.15, 0.5),
@@ -83,50 +90,115 @@ class Microscope:
             if j is not None:
                 ax.imshow(data[:,:,n,j], cmap="bwr", vmin=-1, vmax=1, interpolation='none')
                 levels = [-0.1, -1e-5, 1e-5, 0.1]
[…]

### 2018-05-28 polharmonic/shcoeffs.py

@@ -109,10 +109,20 @@ class SHCoeffs:
 
         f.savefig(filename, bbox_inches='tight')
 
-    def plot_dist(self, filename='dist.png', n_pts=2500, r=1, mag=1, show=False):
+    def plot_dist(self, filename='dist.png', n_pts=2500, r=1, mag=1, show=False,
+                  force_positive=True):
         from mayavi import mlab
         print('Plotting: ' + filename)
-        
+
+        # Flip sign if [1,1,0] direction is negative
+        if force_positive:
+            test_radii = 0
+            for i, c in enumerate(self.coeffs):
+                l, m = util.j2lm(i)
+                test_radii += c*util.spZnm(l, m, np.pi/2, np.pi/4)
+            if test_radii < 0:
+                self.coeffs = -self.coeffs 
+            
         # Calculate radii
         tp = util.fibonacci_sphere(n_pts)
         xyz = util.fibonacci_sphere(n_pts, xyz=True)
@@ -120,11 +130,11 @@ class SHCoeffs:
         for i, c in enumerate(self.coeffs):
             l, m = util.j2lm(i)
             radii += c*util.spZnm(l, m, tp[:,0], tp[:,1])
-        radii = radii/np.max(radii)
+        radii = radii/np.max(np.abs(radii))
         
         # Split into positive and negatives
-        n = radii.clip(max=0) 
-        p = radii.clip(min=0)*(-1)
+        n = r*radii.clip(max=0) 
+        p = r*radii.clip(min=0)*(-1)
 
         # Triangulation
         from scipy.spatial import ConvexHull

### 2018-05-31 notes/2018-05-31-dispim-svd/report/report.tex
Unpolarized dispim SVD notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}[1]{\mathbf{\mathfrak{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{\mathfrak{r}}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Singular value decomposition of a dual\\ orthogonal-view
  fluorescence microscope\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
  % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-3em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will find the kernel, transfer function, and singular value
decomposition of a dual orthogonal view fluorescence microscope (diSPIM). We
will model the relationship between the spatial density of fluorophores in a
three-dimensional sample---a member of $\mbb{L}_2(\mbb{R}^3)$---and the two
three-dimensional volumes---two members of $\mbb{L}_2(\mbb{R}^3)$. We could
consider the diSPIM as a microscope that makes two samples of a larger space
$\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^2)$, but I don't think this will give us any
extra insight at this point.

\section{Kernel}
The diSPIM illuminates the sample with a uniform-width Gaussian beam (we ignore
light-sheet broadening). In path A the light sheet is in the $xy$ plane for
viewing by an objective with an optical axis along the $z$ axis. In path B the
roles are reversed and the light sheet is in the $yz$ plane for viewing by an
objective with an optical axis along the $x$ axis.

We can model the relationship between the object and the data using an integral
transform
\begin{align}
  g_{\text{v}}(\rd{}) = \left[\mc{H}f\right]_{\text{v}}(\rd{}) = \int_{\mbb{R}^3}d\ro{}\, h_{\text{v}}(\rd{} - \ro{})f(\ro{}), \qquad \text{v} = \{\text{A}, \text{B}\}, 
\end{align}
where $g_{\text{v}}(\rd{})$ is the three-dimensional data collected from the
$\text{v}$th view, $f(\ro{})$ is the three-dimensional density of fluorophores,
and $h_{\text{v}}(\rd{} - \ro{})$ is the kernel (or point-spread function) for
the ${\text{v}}$th view. A typical model for the kernels of the diSPIM is
\begin{align}
  h_{\text{A}}(\ro{}) &= \mf{g}(r_x, \sigma_{\text{tr}})\mf{g}(r_y, \sigma_{\text{tr}})\mf{g}(r_z, \sigma_{\text{ax}}), \label{eq:ha}\\
  h_{\text{B}}(\ro{}) &= \mf{g}(r_x, \sigma_{\text{ax}})\mf{g}(r_y, \sigma_{\text{tr}})\mf{g}(r_z, \sigma_{\text{tr}}), \label{eq:hb}
\end{align}
where $\mf{g}(x, \sigma) \equiv \text{exp}(x^2/2\sigma^2)/\sqrt{2\pi\sigma^2}$,
$\ro{} = r_x\mh{x} + r_y\mh{y} + r_z\mh{z}$ is the three-dimensional position
vector in the object, $\sigma_{\text{tr}}$ is the spatial standard deviation of
the transverse point spread function (set by the detection NA), and
$\sigma_{\text{ax}}$ is the spatial standard deviation of the axial point spread
function (width/thickness of the light sheet).

The adjoint of forward operator is given by
\begin{align}
  f(\ro{}) = [\mc{H}^{\dagger}g](\ro{}) = \sum_{{\text{v}} = \{\text{A}, \text{B}\}}\int_{\mbb{R}^3}d\rd{}\, h_{\text{v}}(\rd{} - \ro{})g_v(\rd{}). 
\end{align}
\section{Transfer function}
We can rewrite the forward and adjoint operators in the frequency domain as
\begin{align}
  G_{\text{v}}(\bs{\nu}) &= H_{\text{v}}(\bs{\nu})F(\bs{\nu}), \label{eq:fwd} \\
  F(\bs{\nu}) &= \sum_{{\text{v}} = \{\text{A}, \text{B}\}}H_{\text{v}}(\bs{\nu})G_{\text{v}}(\bs{\nu}),\label{eq:adj}
\end{align}
where
\begin{align}
  G_{\text{v}}(\bs{\nu}) &= \int_{\mbb{R}^3}d\rd{}\, g_{\text{v}}(\rd{})e^{i2\pi\rd{}\cdot\bs{\nu}},\\
  H_{\text{v}}(\bs{\nu}) &= \int_{\mbb{R}^3}d\ro{}\, h_{\text{v}}(\ro{})e^{i2\pi\ro{}\cdot\bs{\nu}},\\
  F(\bs{\nu}) &= \int_{\mbb{R}^3}d\ro{}\, f(\ro{})e^{i2\pi\ro{}\cdot\bs{\nu}}.
\end{align}
If we use the kernels in Eqs. \ref{eq:ha} and \ref{eq:hb} then the transfer
functions are
\begin{align}
  H_{\text{A}}(\bs{\nu}) &= \mf{g}(\nu_x, 1/\sigma_{\text{tr}})\mf{g}(\nu_y, 1/\sigma_{\text{tr}})\mf{g}(\nu_z, 1/\sigma_{\text{ax}}),\\
  H_{\text{B}}(\bs{\nu}) &= \mf{g}(\nu_x, 1/\sigma_{\text{ax}})\mf{g}(\nu_y, 1/\sigma_{\text{tr}})\mf{g}(\nu_z, 1/\sigma_{\text{tr}}), 
\end{align}
where $\bs{\nu} = \nu_x\mh{x} + \nu_y\mh{y} + \nu_z\mh{z}$ is a
three-dimensional spatial frequency vector.

\section{Singular value decomposition}
To find the singular value decomposition of the imaging operator we need to
solve the eigenvalue problem
\begin{align}
  [\mc{H}^{\dagger}\mc{H}]u_{\bs{\rho}}(\ro{}) = \mu_{\bs{\rho}}u_{\bs{\rho}}(\ro{}), \label{eq:eig}
\end{align}
where $u_{\bs{\rho}}(\ro{})$ are the object space singular functions of the
system. This eigenvalue problem is easily solved in the frequency domain, so we
write the object-space singular functions as
\begin{align}
  u_{\bs{\rho}}(\ro{}) = U(\bs{\rho})e^{i2\pi\ro{}\cdot\bs{\rho}}. \label{eq:ftu}
\end{align}
Plugging Eqs. \ref{eq:fwd}, \ref{eq:adj}, and \ref{eq:ftu} into Eq. \ref{eq:eig}
gives a new eigenvalue equation
\begin{align}
  \sum_{{\text{v}} = \{\text{A}, \text{B}\}}H_{\text{v}}(\bs{\rho})H_{\text{v}}(\bs{\rho})U(\bs{\rho}) = \mu_{\bs{\rho}}U(\bs{\rho}).
\end{align}
Therefore, the eigenvalues are given by
\begin{align}
  \mu_{\bs{\rho}} = \sum_{{\text{v}} = \{\text{A}, \text{B}\}}H^2_{\text{v}}(\bs{\rho}),
\end{align}
and the eigenvectors are constants
\begin{align}
  U(\bs{\rho}) = 1. 
\end{align}
The singular values are given by the square root of the eigenvalues
\begin{align}
  \sigma_{\bs{\rho}} = \sqrt{\sum_{\text{v} = \{\text{A}, \text{B}\}}H^2_\text{v}(\bs{\rho})} = \sqrt{H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})},
\end{align}
and the object-space singular functions are the usual Fourier components of the
object
\begin{align}
  u_{\bs{\rho}}(\ro{}) = e^{i2\pi\ro{}\cdot\bs{\rho}}. 
\end{align}
Finally, the data space singular functions are given by
\begin{align}
  [v_{\bs{\rho}}]_{\text{v}}(\rd{}) = \frac{1}{\sigma_{\bs{\rho}}}\mc{H}_{\text{v}}u_{\bs{\rho}}(\ro{}) = \frac{H_{\text{v}}(\bs{\rho})}{\sqrt{H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})}}e^{i2\pi\rd{}\cdot\bs{\rho}}.
\end{align}

\section{Operator decompositions}
We can use the singular vectors and singular values to decompose the forward and
adjoint operators of the microscope. Table 1.2 of Barrett is particularly
helpful.

The forward operator decomposes into
\begin{align}
  \mc{H}_{\text{v}}f(\ro{}) = \sigma_{\bs{\rho}}\mb{v}\mb{u}^{\dagger}f(\ro{}) = \mc{F}^{-1}\left\{H_{\text{v}}(\bs{\rho})\mc{F}\left\{f(\ro{})\right\}\right\}. 
\end{align}
This result is essentially the Fourier-convolution theorem---it means that we
can apply the forward operator by taking the Fourier transform of the object,
multiplying the result by the Fourier transform of the kernel, then taking the
inverse Fourier transform.

The adjoint operator decomposes into 
\begin{align}
  \mc{H}^{\dagger}g_\text{v}(\rd{}) = \sigma_{\bs{\rho}}\mb{u}\mb{v}^{\dagger}g_\text{v}(\rd{}) = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}H_{\text{v}}(\bs{\rho})\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}. 
\end{align}
Once again this result is not too surprising, and I suspect that this is how the
existing MLEM/RL reconstructions have implemented the adjoint operator.

A potentially useful result is to decompose the Moore-Penrose pseudoinverse
operator
\begin{align}
  \mc{H}^+g_{\text{v}}(\rd{}) = \frac{1}{\sigma_{\bs{\rho}}}\mb{u}\mb{v}^{\dagger}g_{\text{v}}(\rd{}) = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}\frac{H_{\text{v}}(\bs{\rho})}{H_{\text{A}}^2(\bs{\rho}) + H_{\text{B}}^2(\bs{\rho})}\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}. \label{eq:mp}
\end{align}
This gives us a (new?) one-step reconstruction algorithm. In words:
\begin{enumerate}
\item Calculate or measure the kernel and transfer function of the microscope
  for both views and precalculate two filters:
  $H_{\text{A}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$ and $H_{\text{B}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$.
\item Take the 3D Fourier transform of the data from each view, multiply the
  result by the corresponding precalculated filter from step 1, then add the
  results.
\item Take the inverse Fourier transform. 
\end{enumerate}
This reconstruction is fast---it only requires three 3D Fourier transforms and a
single product---so it might be useful for live reconstructions during imaging.

The reconstruction has two limitations compared to MLEM/RL. First, the
Moore-Penrose pseudoinverse solution is a minimum-norm least-squares solution so
it assumes Gaussian noise and does not account for Poisson noise at low counts.
Second, the reconstruction is not constrained to positive values so noisy data
may cause a (usually slightly) negative value in the reconstructed object. These
limitations might not be a problem if an online reconstruction can help guide
the experiment while its happening and a complete MLEM/RL reconstruction can be
performed offline.

\section{Discussion}
The singular values of the dual view microscope confirm a result that matches
our intuition---the singular spectrum for a dual view microscope is the root sum
of squares of the transfer functions for each view. If we can describe the
imaging system as linear-shift invariant, I expect that this result will hold
for other multiview designs---the three-view diSPIM, possibly the mirror
diSPIM(?), and possibly unpolarized light-field designs. An analogous
calculation for the light-field microscope might yield a reconstruction
algorithm that is much faster than Broxton's spatial-domain reconstruction. TBD.

We've considered the diSPIM as a CC-CD imaging system and shown that the CD part
of the microscope is described by a rank-1 operator. Compare this with polarized
light microscopes where the angular part of the microscope is described by a
rank-3 (single-view) or rank-6 (dual-view) operator.

Finally, notice that the Moore-Penrose pseudoinverse operator in Eq.
\ref{eq:mp} reduces to a simple inverse filter if we only use the data from one
view.

\end{document}

### 2018-06-01 notes/2018-06-01-sim-svd/report/report.tex
SIM SVD notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}[1]{\mathbf{r}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Singular value decomposition of single view\\
  structured illumination
  microscopes\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
  % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-3em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will find the kernel, transfer function, and singular value
decomposition of epi-illumination and epi-detection single view structured
illumination microscopes. We will model the relationship between the spatial
density of fluorophores in a two-dimensional sample---a member of
$\mbb{L}_2(\mbb{R}^2)$---and the complete data space---a member of
$\mbb{L}_2(\mbb{R}^2 \times \mbb{R}^2 \times \mbb{S}^1)$. We will show that
structured illumination microscopes sample this five-dimensional space---pixels
sample a pair of spatial dimensions $\mbb{R}^2$, illumination pattern
orientations and spatial frequencies sample another pair of dimensions
$\mbb{R}^2$, and the phase of the illumination pattern samples a circular
dimension $\mbb{S}^1$.

\section{Kernel}
Structured illumination microscopes interfere two coherent illumination beams to
create a sinusoid squared excitation pattern in the sample. The excitation
kernel takes the form
\begin{align}
  h_{\text{exc}}(\ro{}, \mb{k}, \phi) = \cos^2(\mb{k}\cdot\ro{} - \phi) = \frac{1}{4}\me{}^{i2(\mb{k} \cdot\ro{} - \phi)} + \frac{1}{2} + \frac{1}{4}\me{}^{-i2(\mb{k}\cdot\ro{} - \phi)},\label{eq:exc}
\end{align}
where $\ro{}$ is the two-dimensional position in the sample, $\mb{k}$ is the
wave vector of the illumination pattern, and $\phi$ is the phase of the
illumination pattern. The detection process of the microscope is shift
invariant, so we can model the detection process with a detection kernel
$h_{\text{det}}(\ro{})$. In these notes we will use the paraxial detection
model
\begin{align}
  h_{\text{det}}(\ro{}) = \left[\frac{J_1(2\pi\nu_o |\ro{}|)}{\pi\nu_o |\ro{}|}\right]^2,\label{eq:det}
\end{align}
where $J_1(\cdot)$ is a first-order Bessel function of the first kind, and
$\nu_o = \text{NA}/\lambda$ is the coherent cutoff frequency. We can easily plug
in a more sophisticated detection model if we need to.

We can model the relationship between the object and the data using an integral
transform
\begin{align}
  g(\rd{}, \mb{k}, \phi) = \left[\mc{H}f\right](\rd{}, \mb{k}, \phi) = \int_{\mbb{R}^2}d\ro{}\, h_{\text{exc}}(\ro{}, \mb{k}, \phi)h_{\text{det}}(\rd{} - \ro{})f(\ro{}), 
\end{align}
where $g(\rd{}, \mb{k}, \phi)$ is the five-dimensional data set and $f(\ro{})$ is
the two-dimensional density of fluorophores.

The adjoint of the forward operator is given by
\begin{align}
  f(\ro{}) = [\mc{H}^{\dagger}g](\ro{}) = \int_{\mbb{S}^1}d\phi\int_{\mbb{R}^2}d\mb{k}\int_{\mbb{R}^2}d\rd{}\, h_{\text{exc}}(\ro{}, \mb{k}, \phi)h_{\text{det}}(\rd{} - \ro{})g_v(\rd{}, \mb{k}, \phi). 
\end{align}
\section{Transfer function}
We can rewrite the forward and adjoint operators in the frequency domain as
\begin{align}
  G_n(\bs{\nu}, \mb{k}) &= H_{n}(\bs{\nu}, \mb{k})F(\bs{\nu}), \label{eq:fwd} \\
  F(\bs{\nu}) &= \int_{\mbb{R}^2} d\mb{k}\sum_{n=0}^{\infty} H_{n}(\bs{\nu}, \mb{k})G_{n}(\bs{\nu}, \mb{k}),\label{eq:adj}
\end{align}
where
\begin{align}
  G_n(\bs{\nu}, \mb{k}) &= \int_{\mbb{S}^1}d\phi\, \me{}^{i2\pi\phi n}\int_{\mbb{R}^2}d\rd{}\, \me{}^{i2\pi\rd{}\cdot\bs{\nu}} g(\rd{}, \mb{k}, \phi),\\
  H_n(\bs{\nu}, \mb{k}) &= \int_{\mbb{S}^1}d\phi\, \me{}^{i2\pi\phi n}\int_{\mbb{R}^2}d\rd{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}} h_{\text{exc}}(\ro{}, \mb{k}, \phi)h_{\text{det}}(\ro{}), \label{eq:trans}\\  
  F(\bs{\nu}) &= \int_{\mbb{R}^3}d\ro{}\, \me{}^{i2\pi\ro{}\cdot\bs{\nu}}f(\ro{}).
\end{align}
Notice that we have taken the Fourier transform of object space variable $\ro{}$
and taken the Fourier series of the data space variable $\phi$, but we have left
the data space variable $\mb{k}$ alone because it is ``natively'' in the
frequency domain.

If we plug the kernels in Eqs. \ref{eq:exc} and \ref{eq:det} into Eq.
\ref{eq:trans} and evaluate the integrals we find the transfer function is
\begin{align}
  H_n(\bs{\nu}, \mb{k}) &= \frac{1}{4}H_{\text{det}}(\bs{\nu} - 2\mb{k})\delta_{n,2} + \frac{1}{2}H_{\text{det}}(\bs{\nu})\delta_{n,0} + \frac{1}{4}H_{\text{det}}(\bs{\nu} + 2\mb{k})\delta_{n,-2},
\end{align}
where $\delta_{n,m}$ is a Kronecker delta,
\begin{align}
  H_{\text{det}}(\bs{\nu}) = \frac{2}{\pi}\left[\arccos\left(\frac{|\bs{\nu}|}{2\nu_o}\right) - \frac{|\bs{\nu}|}{2\nu_o}\sqrt{1 - \left(\frac{|\bs{\nu}|}{2\nu_o}\right)^2}\right]\Pi\left(\frac{|\bs{\nu}|}{2\nu_o}\right),
\end{align}
is the detection transfer function for a fluorescence microscope without
structured illumination, and $\Pi\left(\cdot\right)$ is a rect function.

\section{Singular value decomposition}
To find the singular value decomposition of the imaging operator we need to
solve the eigenvalue problem
\begin{align}
  [\mc{H}^{\dagger}\mc{H}]u_{\bs{\rho}}(\ro{}) = \mu_{\bs{\rho}}u_{\bs{\rho}}(\ro{}), \label{eq:eig}
\end{align}
where $u_{\bs{\rho}}(\ro{})$ are the object space singular functions of the
system. This eigenvalue problem is easily solved in the frequency domain, so we
write the object-space singular functions as
\begin{align}
  u_{\bs{\rho}}(\ro{}) = U(\bs{\rho})e^{i2\pi\ro{}\cdot\bs{\rho}}. \label{eq:ftu}
\end{align}
Plugging Eqs. \ref{eq:fwd}, \ref{eq:adj}, and \ref{eq:ftu} into Eq. \ref{eq:eig}
gives a new eigenvalue equation
\begin{align}
  \int_{\mbb{R}^2}d\mb{k}\sum_{n = 0}^{\infty}H_{n}(\bs{\rho}, \mb{k})H_{n}(\bs{\rho}, \mb{k})U(\bs{\rho}) = \mu_{\bs{\rho}}U(\bs{\rho}).
\end{align}
Therefore, the eigenvalues are given by
\begin{align}
  \mu_{\bs{\rho}} = \int_{\mbb{R}^2}d\mb{k}\sum_{n = 0}^{\infty}H^2_{n}(\bs{\rho}, \mb{k}),
\end{align}
and the eigenvectors are constants
\begin{align}
  U(\bs{\rho}) = 1. 
\end{align}
The singular values are given by the square root of the eigenvalues
\begin{align}
  \sigma_{\bs{\rho}} = \sqrt{\int_{\mbb{R}^2}d\mb{k}\sum_{n = 0}^{\infty}H^2_{n}(\bs{\rho}, \mb{k})},
\end{align}
and the object-space singular functions are the usual Fourier components of the
object
\begin{align}
  u_{\bs{\rho}}(\ro{}) = e^{i2\pi\ro{}\cdot\bs{\rho}}. 
\end{align}
Finally, the data space singular functions are given by
\begin{align}
  v_{\bs{\rho}}(\rd{}, \mb{k}, \phi) =\frac{1}{\sigma_{\bs{\rho}}}\mc{H}_{\text{v}}u_{\bs{\rho}}(\ro{}) = \frac{\sum_{n=-\infty}^{\infty}e^{i2\pi n\phi} H_{n}(\bs{\rho}, \mb{k})}{\sqrt{\int_{\mbb{R}^2}d\mb{k}\sum_{n = 0}^{\infty}H^2_{n}(\bs{\rho}, \mb{k})}}e^{i2\pi\rd{}\cdot\bs{\rho}}.
\end{align}
Looking closer at the singular value spectrum lets us see the limits of
structured illumination microscopy. If we can illuminate the sample with all
possible $\mb{k}$ vectors, then the singular spectrum would be a constant for
all $\bs{\rho}$. This is not practically possible because real microscopes are
limited by the illumination NA of the microscope. In this case, the integral is
over the illumination NA of the microscope, and we can clearly see that the
singular value spectrum will have twice the bandwidth of a widefield microscope.

Note that we can find a closed form for the singular value spectrum, but I
haven't done this. I think that the main insight from these notes is that the
singular value spectrum is the square root of the sum of the squared transfer
functions for each individual illumination pattern. This result applies to a
(more realistic) discrete sampling of $\mb{k}$ and $\phi$ space as well.

Also note that the Fourier series expansion of the phase dimension plays a role
in the transfer function and singular value decomposition. I suspect that the
Fourier series expansion should play a role in an efficient reconstruction as
well (does it already?).

% Let's look closer at the singular value spectrum. If we could illuminate the
% sample with all possible $\mb{k}$ vectors, then the singular spectrum would be a
% constant for all $\bs{\rho}$. This is not practically possible because we are
% limited by the illumination NA of the microscope. In this case, we can 
% integrate over a much smaller region
% \begin{align}
%   \sigma_{\bs{\rho}} &= \sqrt{\int_0^{\nu_o/2}k dk\int_0^{2\pi}d\phi_k \sum_{n={-\infty}}^{\infty} H_n^2(\bs{\rho}, \mb{k})},\\
%   \sigma_{\bs{\rho}} &= \sqrt{\int_0^{\nu_o/2}k dk\int_0^{2\pi}d\phi_k \left[\frac{1}{16}H^2_{\text{det}}(\bs{\nu} - 2\mb{k}) + \frac{1}{4}H^2_{\text{det}}(\bs{\nu}) + \frac{1}{16}H^2_{\text{det}}(\bs{\nu} + 2\mb{k})\right]},\\
%   \sigma_{\bs{\rho}} &= \sqrt{\int_0^{\nu_o/2}k dk\int_0^{2\pi}d\phi_k \left[\frac{1}{8}H^2_{\text{det}}(\bs{\nu} - 2\mb{k}) + \frac{1}{4}H^2_{\text{det}}(\bs{\nu})\right]},\\ \end{align}

\end{document}

### 2018-06-08 notes/2018-05-31-dispim-svd/report/report.tex
Tikhonov regularization for plain diSPIM.

@@
 \end{enumerate}
-This reconstruction is fast---it only requires three 3D Fourier transforms and a
-single product---so it might be useful for live reconstructions during imaging.
+This reconstruction is fast---it only requires three 3D Fourier transforms, two
+scalings, and a sum---so it might be useful for live reconstructions during
+imaging.
 
@@
 
+\section{Tikhonov regularization}
+The pseudoinverse solution amplifies high-frequency noise, so we prefer a
+one-step algorithm with Tikhonov regularization. Barrett 15.114 (and discussion
+around 15.155 and 1.5156) gives the Tikhonov regularized reconstruction operator
+as
+\begin{align}
+  \mc{H}^{+\text{Tik}}_{\eta}[g_{\text{v}}(\rd{})] = \frac{\sigma_{\bs{\rho}}}{\sigma^2_{\bs{\rho}} + \eta}\mb{u}\mb{v}^{\dagger}[g_{\text{v}}(\rd{})] = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}\frac{H_{\text{v}}(\bs{\rho})}{H_{\text{A}}^2(\bs{\rho}) + H_{\text{B}}^2(\bs{\rho}) + \eta}\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}.
+\end{align}
+The Tikhonov regularized solution is identical to the pseudoinverse solution when $\eta = 0$ as expected.
+
 \end{document}

### 2018-06-15 notes/2018-05-30-polarized-dispim-svd/report/report.tex
Polarized diSPIM notes 3/4 complete.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
% \providecommand{\e}{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathfrak{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rb}{\mathbf{r}_b}
\providecommand{\rbm}{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{\mathfrak{r}}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\ms}[1]{\mathsf{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\tv}{\text{v}}
\providecommand{\tx}[1]{\text{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bp}{\bs{\rho}}
\providecommand{\p}{\mh{p}}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Singular value decomposition of a dual orthogonal-view\\
  polarized fluorescence microscope\vspace{-1em}} \author{Talon Chandler, Min
  Guo, Hari Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes we will find the kernel, transfer function, and singular value
decomposition of a dual orthogonal view polarized fluorescence microscope
(diSPIM). We will model the relationship between the spatio-angular density of
fluorophores in a three-dimensional sample---a member of
$\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^2)$---and the two three-dimensional volumes
for each illumination polarization setting---two members of
$\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^1)$. We could consider the diSPIM as a
microscope that makes two samples of a larger space
$\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^1 \times \mbb{S}^2)$, but I don't think this
will give us any extra insight at this point.

We can write the forward model for the polarized diSPIM as
\begin{align}
  g_{\tv}(\rd, \p) = \left[\mc{H}f\right]_\tv(\rd, \p) = \intr{3}d\ro \ints{2}d\so\, h_{\tv}(\rd - \ro, \p, \so)f(\ro, \so), \label{eq:fwd}
\end{align}
where $\tv \in \{\text{A}, \text{B}\}$ is the light path index, $\rd$ is the
three-dimensional detection coordinate, and all other coordinates have been
introduced in previous note sets. The adjoint operator is given by
\begin{align}
  f(\ro, \so) = [\mc{H}^\dagger \mb{g}](\ro, \so) = \sum_{\tv \in \{\text{A}, \text{B}\}} \intr{3}d\rd\ints{1}d\p\, h_{\tv}(\rd - \ro, \p, \so)g_{\tv}(\rd, \p). \label{eq:adj}
\end{align}
\section{Kernel}
The polarized diSPIM illuminates the sample with a uniform-width Gaussian beam
(we ignore light-sheet broadening) with variable polarization. In path A the
light sheet is in the $xy$ plane for viewing by an objective with an optical
axis along the $z$ axis. In path B the roles are reversed and the light sheet is
in the $yz$ plane for viewing by an objective with an optical axis along the $x$
axis.

In the
\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-05-14-single-view-continuous-svd/report/report.pdf}{May
  14 notes} we derived the excitation kernel for a polarized collimated beam (NA
= 0) traveling along the $z$ axis. The excitation kernel for path B of the
diSPIM is identical to the previously derived excitation kernel weighted by
Gaussian profile of the light sheet
\begin{align}
  h_{\tx{B}, \tx{exc}}(\ro, \so; \mh{p}) = \left[z_{0}^{\tx{B}}(\mh{p})y_0^0(\so) + \sqrt{\frac{3}{5}}z_{-2}^{\tx{B}}(\mh{p})y_2^{-2}(\so) - \frac{1}{\sqrt{5}}z_{0}^{\tx{B}}(\mh{p})y_2^0(\so) + \sqrt{\frac{3}{5}}z_{2}^{\tx{B}}(\mh{p})y_2^{2}(\so)\right]\mf{g}(r_x, \sigma_{\tx{ls}}),\label{eq:pathbexc}
\end{align}
where $\mf{g}(x, \sigma) \equiv \tx{exp}(x^2/2\sigma^2)/\sqrt{2\pi\sigma^2}$,
$\ro = r_x\mh{x} + r_y\mh{y} + r_z\mh{z}$ is the three-dimensional position
vector in the object, and $\sigma_{\tx{ls}}$ is the spatial standard deviation
(width) of the light sheet.

We can find the excitation kernel for path A by swapping the $x$ and $z$
coordinates in Eq. \ref{eq:pathbexc}. This is a simple modification for the
spatial part of the excitation kernel (change $\mf{g}(r_x, \sigma_{\tx{ls}})$
to $\mf{g}(r_z, \sigma_{\tx{ls}})$), and the coefficients of the spherical
harmonics are transformed by a matrix multiplication
\begin{align}
  \begin{bmatrix}
    {c'}_0^{0}\\ {c'}_2^{-2}\\ {c'}_2^{-1}\\ {c'}_2^0\\ {c'}_2^1\\ {c'}_2^2\\
  \end{bmatrix} =
  \begin{bmatrix}
      1&0&0&0&0&0\\
      0&0&-1&0&0&0\\
      0&-1&0&0&0&0\\
      0&0&0&-1/2&0&\sqrt{3}/2\\
      0&0&0&0&1&0\\
      0&0&0&\sqrt{3}/{2}&0&1/2\\
  \end{bmatrix}
  \begin{bmatrix}
    {c}_0^{0}\\ {c}_2^{-2}\\ {c}_2^{-1}\\ {c}_2^0\\ {c}_2^1\\ {c}_2^2
  \end{bmatrix}, \label{eq:transform}
\end{align}
where $c_l^m$ is coefficient of the $y_l^m$ spherical harmonic in the original
frame and ${c'}_l^m$ is the coefficient of the same spherical harmonic in the
rotated frame. Applying this transformation gives
\begin{align}
  h_{\tx{A}, \tx{exc}}(\ro, \so; \mh{p}) = \Bigg[z_{0}^{\tx{A}}(\mh{p})y_0^0(\so) + \sqrt{\frac{3}{5}}z^{\tx{A}}_{-2}(\mh{p})y_2^{-1}(\so) &+ \frac{1}{2\sqrt{5}}\left\{3z_2^{\tx{A}}(\mh{p}) - z_{0}^{\tx{A}}(\mh{p}) \right\} y_2^0(\so)\nonumber \\ &+ \frac{1}{2}\sqrt{\frac{3}{5}}\left\{z^{\tx{A}}_{2}(\mh{p}) - z_{0}^{\tx{A}}(\mh{p})\right\}y_2^{2}(\so)\Bigg]\mf{g}(r_z, \sigma_{\tx{ls}}).\label{eq:pathaexc}
\end{align}
Notice that we have used a different set of circular harmonics for each view.
The $z_n^{\tx{B}}(\mh{p})$ circular harmonics are defined by the angle to the $x$-axis
from the $+y$-axis direction, and the $z_n^{\tx{A}}(\mh{p})$ circular harmonics are
defined by the angle to the $z$-axis from the $+y$-axis direction. This change
of definition follows directly from swapping the $x$ and $z$ coordinates to go
from path B to path A.

In the
\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-05-14-single-view-continuous-svd/report/report.pdf}{May
  14 notes} we derived the two-dimensional detection kernel. The kernel is
two-dimensional because it only considers thin in-focus objects. For a complete
non-paraxial three-dimensional model I would eventually like to follow Backer
and Moerner \cite{backer2014}, but there is still a few weeks of work required
to find the associated transfer functions. Instead I'll follow the early diSPIM
deconvolution models \cite{wu2013} and use an axial Gaussian function to model
the detection kernel.

The detection kernel for an objective along the $z$ axis (path A) as
\begin{align}
  h_{\tx{A}, \tx{det}}(\ro, \so) &= \left[[{a}^2(r_{xy}) + 2b^2(r_{xy})]y_0^0(\so) + \frac{1}{\sqrt{5}}\left[- a^2(r_{xy}) + 4b^2(r_{xy})\right]y_2^0(\so)\right]\mathfrak{g}(r_z, \sigma_{\tx{det}}), \label{eq:det1}
\end{align}
where
\begin{align}
  a(r) = \frac{J_1(2\pi \nu_or)}{\pi \nu_or}, 
  &\hspace{2em}
    b(r) = \frac{\tx{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or)}{\pi \nu_or}\right],  \label{eq:abparadef}
    \intertext{and}
  r_{xy} \equiv \sqrt{r_x^2 + r_y^2},\hspace{2em}
  \nu_o \equiv &\frac{\tx{NA}}{\lambda},\hspace{2em}
  \tx{NA} = n_o\sin\alpha.
\end{align}

To find the two-dimensional detection kernel for path B we transform the
spherical harmonic coefficients using Eq. \ref{eq:transform}
\begin{align}
  h_{\tx{B}, \tx{det}}(\ro, \so) = \Bigg[[{a}^2(r_{yz}) + 2b^2(r_{yz})]y_0^0(\so) &+ \frac{1}{2\sqrt{5}}\left[- a^2(r_{yz}) + 4b^2(r_{yz})\right]y_2^0(\so) \nonumber \\ &+ \frac{1}{2}\sqrt{\frac{3}{5}}\left[- a^2(r_{yz}) + 4b^2(r_{yz})\right]y_2^2(\so)\Bigg]\mathfrak{g}(r_x, \sigma_{\tx{det}}), \label{eq:det2}
\end{align}
where $r_{yz} \equiv \sqrt{r_y^2 + r_z^2}$.

The complete kernel is the product of the excitation and detection kernels
\begin{align}
  h_{\tv}(\ro, \so; \mh{p}) &= h_{\tv, \tx{exc}}(\ro, \so; \mh{p})h_{\tv, \tx{det}}(\ro, \so).
\end{align}

Notice that the both the excitation and detection kernels are Gaussian along the
axial detection axis, so the complete kernel is also Gaussian along that
dimension with standard deviation
$\sigma_{\tx{ax}} = \sqrt{\sigma_{\tx{ls}}^2 + \sigma_{\tx{det}}^2}$. Therefore,
we can rewrite the kernel in the form
\begin{align}
  h_{\tx{A}}(\ro, \so; \mh{p}) &= \left[\sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n,\tx{A}}^{m}(r_{xy})y_l^m(\so)z_n(\mh{p})\right]\mathfrak{g}(r_z, \sigma_{\tx{ax}}),\\
  h_{\tx{B}}(\ro, \so; \mh{p}) &= \left[\sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n, \tx{B}}^{m}(r_{yz})y_l^m(\so)z_n(\mh{p})\right]\mathfrak{g}(r_x, \sigma_{\tx{ax}}).
\end{align}
% Figures \ref{fig:kernA} and \ref{fig:kernB} show the kernels for both viewing
% directions.

% \fig{../calculations/out/hhillx.pdf}{1.0}{Kernel $h_{l,n,\tx{A}}^m(\mb{r}_{xy})$
%   for view A of a polarized diSPIM microscope with a 0.8 NA detection objective.
%   \textbf{Rows:} $l$ indexes the object-space spherical harmonic band.
%   \textbf{Columns:} $m$ indexes the object-space spherical harmonic degree, and
%   $n$ indexes the data-space circular harmonic band. \textbf{Entries:} Each
%   column and row contains a continuous two-dimensional plot indexed by the
%   vector $\mb{r}_{xy}$ ranging from $-\lambda/2\text{NA}$ to
%   $+\lambda/2\text{NA}$ (although $\mb{r}_{xy}$ is rotationally symmetric so one
%   dimension would suffice). All values are normalized between $-1$
%   \textcolor{blue}{(blue)} and $+1$ \textcolor{red}{(red)} with $0$ colored
%   white.}{kernA}
%   % filename, width, caption, label

% \fig{../calculations/out/hhillz.pdf}{1.0}{Kernel $h_{l,n,\tx{B}}^m(\mb{r}_{yz})$
%   for view B of a polarized diSPIM microscope with a 0.8 NA detection objective.
%   See caption of Fig. \ref{fig:kernA} for details.}{kernB}
%   % filename, width, caption, label

\section{Transfer function}
We can rewrite Eqs. \ref{eq:fwd} and \ref{eq:adj} in the frequency domain as
\begin{align}
  G_{\tv, n}(\bv) &= \lmsum H_{l,n,\tv}^{m}(\bv)F_l^m(\bv), \label{eq:ffwd}\\
  F_l^m(\bv) &= \sum_{\tv \in \{\tx{A}, \tx{B}\}}\sum_{n=-\infty}^\infty H_{l,n,\tv}^{m}(\bv)G_{\tv, n}(\bv) \label{eq:fadj},
\end{align}
where
\begin{align}
  G_{\tv, n}(\bv) &= \intr{3}d\rd\, \me^{i2\pi\rd\cdot\bv}\ints{1}d\p\, z_n(\p) g_{\tv}(\rd, \p),\\
  H_{l,n,\tv}^m(\bv) &= \intr{3}d\ro\, \me^{i2\pi\ro\cdot\bv}\ints{1}d\p\, z_n(\p)\ints{2}d\so\, y_l^m(\so) h_{\tv}(\ro, \p, \so),\\
  F_l^m(\bv) &= \intr{3}d\ro\, \me^{i2\pi\ro\cdot\bv}\ints{2}d\so\, y_l^m(\so) f(\ro, \so).
\end{align}
In Figs. \ref{fig:tfA} and \ref{fig:tfB} we plot the transverse part of the
diSPIM transfer function. Extending these plots to three-dimensions is simple
given our assumption that the axial part is Gaussian. Notice that view B has a
non-zero element in the $m=-1$ column---this is a first for the microscopes
we've considered so far. Also notice that each view contributes new
information---we'll see this result in a clearer form when we find the complete
SVD.

\fig{../calculations/out/Hillx.pdf}{1.0}{Transverse transfer function
  $H_{l,n,\tx{A}}^m(\bv_{xy})$ for view A of a polarized diSPIM microscope with
  a 0.8 NA detection objective. \textbf{Rows:} $l$ indexes the object-space
  spherical harmonic band. \textbf{Columns:} $m$ indexes the object-space
  spherical harmonic degree, and $n$ indexes the data-space circular harmonic
  band. \textbf{Entries:} Each column and row contains a continuous
  two-dimensional plot indexed by the vector $\mb{r}_{xy}$ ranging from
  $-2\text{NA}/\lambda$ to $+2\text{NA}/\lambda$ (although $\mb{r}_{xy}$ is
  rotationally symmetric so one dimension would suffice). All values are
  normalized between $-1$ \textcolor{blue}{(blue)} and $+1$
  \textcolor{red}{(red)} with $0$ colored white.}{tfA}
  % filename, width, caption, label

\fig{../calculations/out/Hillz.pdf}{1.0}{Transverse transfer function
  $H_{l,n,\tx{B}}^m(\bv_{yz})$ for view B of a polarized diSPIM microscope with
  a 0.8 NA detection objective. See caption of Fig. \ref{fig:tfA} for
  details.}{tfB}
  % filename, width, caption, label

\section{Single-view singular value decomposition}
We'll start by looking at the singular value decomposition of each view by
itself. We have already developed all of the tools we need for this computation
in the
\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-05-14-single-view-continuous-svd/report/report.pdf}{May
  14 notes}, so we will jump straight to the results.

Figures \ref{fig:sysA} and \ref{fig:sysB} show the singular systems for the two
individual views of the diSPIM. As we'd expect, the object space singular
functions for the two views are identical except for a swap of the $x$ and $z$
axes. From the object space singular functions in the second and third branches
of both views, we can see each view is most sensitive to orientations
perpendicular to the illumination optical axis---this is what we'd expect for a
polarized illumination microscope.

Also notice that uniform distributions (or anything resembling a uniform
distribution) are not in the measurement space of either view. We saw the same
thing for single-view epi-illumination microscopes, although in that case there
were distributions that were mostly uniform with slight depressions along the
optical axis.

\fig{../calculations/out/SVSx.pdf}{1.0}{Singular system for view A
  ($x$-illumination, $z$-detection) of a polarized diSPIM microscope with a 0.8
  NA detection objective. \textbf{Rows:} Discrete branches of the singular value
  system indexed by $j$. \textbf{Column 1:} Continuous singular value spectra
  for each branch $j$ indexed by spatial frequency $\bs{\rho}$. The singular
  value spectra are normalized with contour lines at 0 and 0.1. \textbf{Columns
    2-5:} Angular part of the object-space singular vector at spatial
  frequencies marked with `x's in the first column. The camera is facing the
  origin along the [1,1,1] axis with the $z$ axis pointing up along the page. A
  \textcolor{red}{red} surface indicates positive values, a
  \textcolor{blue}{blue} surface indicates negative values, and the distance
  from the origin indicates the magnitude.}{sysA}
  % filename, width, caption, label

\fig{../calculations/out/SVSz.pdf}{1.0}{Singular system for view B
  ($z$-illumination, $x$-detection) of a polarized diSPIM microscope with a 0.8
  NA detection objective. See Fig. \ref{fig:sysA} caption for details. }{sysB}
  % filename, width, caption, label

\section{Dual-view singular value decomposition}
We will follow Burvall et al. \cite{burvall06} and the single-view case and
calculate the singular value decomposition in data space. We want to find the
eigenvalues $\mu_{\bp, j}$ and eigenfunctions $v_{\bp, j, \tv}(\rd, \p)$ that
satisfy
\begin{align}
  [\mc{H}\mc{H}^\dagger \mb{v}_{\bp, j}]_{\tv}(\rd, \p) = \mu_{\bp, j}v_{\bp, j, \tv}(\rd, \p). \label{eq:eig}
\end{align}
In the frequency domain the data-space singular functions will be in the form
\begin{align}
  v_{\bp, j, \tv}(\rd, \p) = \me^{i2\pi\bp\cdot\rd} \sum_{n=-\infty}^{\infty} \left[V_{n, \tv}(\bp)\right]_j z_n(\p). \label{eq:fdata}
\end{align}
Plugging Eqs. \ref{eq:ffwd}, \ref{eq:fadj}, and \ref{eq:fdata} in \ref{eq:eig} gives
\begin{align}
  \sum_{n=-\infty}^{n=\infty} \sum_{\tv \in \{\tx{A}, \tx{B}\}} \lmsum H_{l,\tv',n'}^m(\bp)H_{l,\tv,n}^m(\bp)\left[V_{n, \tv}(\bp)\right]_j = \mu_{\bp, j}\left[V_{n, \tv}(\bp)\right]_j. \label{eq:eig2}
\end{align}
If we combine the indices $n$ and $\tv$ into a multi-index $\mb{i} = (n, \tv)$ then we
can rewrite \ref{eq:eig2} as
\begin{align}
  \sum_{\mb{i}} \left[\lmsum H_{l,\mb{i}'}^m(\bp)H_{l,\mb{i}}^m(\bp)\right]\left[V_{\mb{i}}(\bp)\right]_j = \mu_{\bp, j}\left[V_{\mb{i}}(\bp)\right]_j. \label{eq:eig3}
\end{align}
Finally, we can rewrite Eq. \ref{eq:eig3} in matrix form as
\begin{align}
  \ms{K}(\bp)\ms{V}_j(\bp) = \mu_{\bp, j}\ms{V}_j(\bp),
\end{align}
where the entries of $\ms{K}(\bp)$ are given by
\begin{align}
  K_{\mb{i}, \mb{i}'} (\bp) = \lmsum H_{l,\mb{i}'}^m(\bp)H_{l,\mb{i}}^m(\bp). 
\end{align}
nFor the diSPIM, the matrix $\mathsf{K}$ has $6\times 6$ non-zero entries---two
views with three circular harmonics for each view---so solving this eigenvalue
problem at each point in frequency space is computationally feasible.

\bibliography{report}{}
\bibliographystyle{unsrt}

\end{document}

### 2018-06-15 notes/2018-05-30-polarized-dispim-svd/calculations/test-mic.py

@@ -1,0 +1,22 @@
+from polharmonic import det, ill, micro
+import numpy as np
+
+#n_px=2**4 + 1
+n_px=2**6 + 1
+folder='out/'
+
+iz = ill.Illuminator(optical_axis=[0,0,1], na=0, polarizer=True, illuminate_all=False)
+dx = det.Detector(optical_axis=[1,0,0], polarizer=False)
+mx = micro.Microscope(ill=iz, det=dx)
+# mx.plot(mx.h, filename=folder+'hhillx.pdf', n_px=n_px, contours=False,  plot_m=[-2, 1, 0, 1, 2])
+mx.plot(mx.H, filename=folder+'Hillz.pdf', n_px=n_px, plot_m=[-2, -1, 0, 1, 2])
+mx.calc_SVD(n_px=n_px)
+mx.plot_SVS(filename=folder+'SVSz.pdf')
+
+ix = ill.Illuminator(optical_axis=[1,0,0], na=0, polarizer=True, illuminate_all=False)
+dz = det.Detector(optical_axis=[0,0,1], polarizer=False)
+mz = micro.Microscope(ill=ix, det=dz)
+# mz.plot(mz.h, filename=folder+'hhillx.pdf', n_px=n_px, contours=False,  plot_m=[-2, -1, 0, 1, 2])
+mz.plot(mz.H, filename=folder+'Hillx.pdf', n_px=n_px, plot_m=[-2, -1, 0, 1, 2])
+mz.calc_SVD(n_px=n_px)
+mz.plot_SVS(filename=folder+'SVSx.pdf')

### 2018-06-15 notes/2018-05-30-polarized-dispim-svd/calculations/test-rotation.py

@@ -1,0 +1,9 @@
+from polharmonic import det, ill, micro, shcoeffs
+
+a = shcoeffs.SHCoeffs([0,0,1,0,0,0])
+a.plot_dist('normal.png', force_positive=False)
+print(a)
+
+b = a.rotate()
+b.plot_dist('rotated.png', force_positive=False)
+print(b)

### 2018-06-15 polharmonic/micro.py

@@ -17,33 +17,37 @@ class Microscope:
                  color=(0,1,0.3)):
         self.ill = ill
         self.det = det
-        self.h0 = self.ill.h()*self.det.h(0)
+        self.h0 = self.ill.h()*self.det.h(0, 0, 0)
         self.n_len = self.h0.coeffs.shape[0]
         self.j_len = self.h0.coeffs.shape[1]
-        self.hnorm = (self.ill.h()*self.det.h(0)).coeffs[0, 0]
-        self.Hnorm = (self.ill.H()*self.det.H(0)).coeffs[0, 0]
+        self.hnorm = (self.ill.h()*self.det.h(0, 0, 0)).coeffs[0, 0]
+        self.Hnorm = (self.ill.H()*self.det.H(0, 0, 0)).coeffs[0, 0]
         self.color = color
 
-    def h(self, r, phi=0):
-        return self.ill.h()*self.det.h(r, phi=phi)/self.hnorm
+    def h(self, x, y, z):
+        return self.ill.h()*self.det.h(x, y, z)/self.hnorm
 
-    def H(self, nu, phi_nu=0):
-        return self.ill.H()*self.det.H(nu, phi_nu=phi_nu)/self.Hnorm
+    def H(self, x, y, z):
+        return self.ill.H()*self.det.H(x, y, z)/self.Hnorm
 
     def plot(self, func=h, filename='micro.pdf', n_px=2**6, plot_m=[-2, 0, 2],
              contours=True):
         print('Plotting: ' + filename)
+
+        mlen = len(plot_m)
+        nlen = 3
         
-        # Calculate data for plotting
+        # Calculate data for transvsere plotting
         w = 2.05
         [X, Y] = np.meshgrid(np.linspace(-w, w, n_px),
                              np.linspace(-w, w, n_px))
-        R = np.sqrt(X**2 + Y**2)
-        Phi = np.nan_to_num(np.arctan(Y/X))
-
+        
         data = np.zeros((n_px, n_px, self.n_len, self.j_len))
-        for index, r in np.ndenumerate(R):
-            data[index[0], index[1], :, :] = (func(r, Phi[index])).coeffs
+        for index, x in np.ndenumerate(X):
+            if self.det.optical_axis == [0,0,1]: # z-detection
+                data[index[0], index[1], :, :] = (func(x, Y[index], 0)).coeffs
+            elif self.det.optical_axis == [1,0,0]: # x-detection
[…]

### 2018-06-15 polharmonic/multi.py

@@ -4,6 +4,7 @@ import matplotlib.pyplot as plt
 import matplotlib
 matplotlib.rcParams['contour.negative_linestyle'] = 'solid'
 import os
+import subprocess
 
 class MultiMicroscope:
     """A MultiMicroscope represents an experiment that collects intensity data 
@@ -12,50 +13,109 @@ class MultiMicroscope:
 
     A MultiMicroscope mainly consists of a list of Microscopes.
     """
-    def __init__(self, ill_optical_axes=[[0,0,1]], det_optical_axes=[[0,0,1]],
-                 ill_nas=[0.8], det_nas=[0.8], n_samp=1.33,
-                 ill_pols=[[1,0,0], [1/np.sqrt(2), 1/np.sqrt(2), 0], [0,1,0], [-1/np.sqrt(2), 1/np.sqrt(2), 0]],
-                 det_pols=4*[None]):
+    def __init__(self, ill_optical_axes=[[0,0,1], [1,0,0]],
+                 det_optical_axes=[[1,0,0], [0,0,1]],
+                 ill_nas=2*[0], det_nas=2*[0.8], n_samp=1.33):
 
         m = [] # List of microscopes
 
         # Cycle through paths
         for i, det_optical_axis in enumerate(det_optical_axes):
-            # Cycle through polarizations
-            for j, pol in enumerate(ill_pols):
-                ill_ = ill.Illuminator(optical_axis=ill_optical_axes[i],
-                                       na=ill_nas[i], n=n_samp,
-                                       polarizer=ill_pols[j])
-                det_ = det.Detector(optical_axis=det_optical_axes[i],
-                                    na=det_nas[i], n=n_samp,
-                                    polarizer=det_pols[j])
-                m.append(micro.Microscope(ill=ill_, det=det_)) # Add microscope
+            ill_ = ill.Illuminator(optical_axis=ill_optical_axes[i],
+                                   na=ill_nas[i], n=n_samp)
+            det_ = det.Detector(optical_axis=det_optical_axes[i],
+                                na=det_nas[i], n=n_samp)
+            m.append(micro.Microscope(ill=ill_, det=det_)) # Add microscope
 
         self.micros = m
         self.N = len(m)
-        self.jmax = m[0].h(0).jmax
+        self.jmax = m[0].h(0, 0, 0).jmax
+        self.nbranch = self.N*self.micros[0].n_len
 
[…]

### 2018-06-15 polharmonic/shcoeffs.py

@@ -62,6 +62,17 @@ class SHCoeffs:
         string = 'SHCoeffs: \n'
         string += str(self.coeffs) + '\n'
         return string
+
+    def rotate(self):
+        # Only rotate by 90 degrees about the y axis for diSPIM.
+        # Generalize later.
+        m = np.array([[1,0,0,0,0,0],
+                      [0,0,-1,0,0,0],
+                      [0,-1,0,0,0,0],
+                      [0,0,0,-1/2,0,np.sqrt(3)/2],
+                      [0,0,0,0,1,0],
+                      [0,0,0,np.sqrt(3)/2,0,1/2]])
+        return SHCoeffs(np.dot(m, self.coeffs))
     
     def plot(self, folder=''):
         if not os.path.exists(folder):
@@ -114,20 +125,21 @@ class SHCoeffs:
         from mayavi import mlab
         print('Plotting: ' + filename)
 
-        # Flip sign if [1,1,0] direction is negative
+        # Flip sign if [1,1,1] direction is negative
+        coeffs = self.coeffs
         if force_positive:
             test_radii = 0
-            for i, c in enumerate(self.coeffs):
+            for i, c in enumerate(coeffs):
                 l, m = util.j2lm(i)
-                test_radii += c*util.spZnm(l, m, np.pi/2, np.pi/4)
+                test_radii += c*util.spZnm(l, m, np.pi/4, np.pi/4)
             if test_radii < 0:
-                self.coeffs = -self.coeffs 
+                coeffs = -coeffs
             
         # Calculate radii
         tp = util.fibonacci_sphere(n_pts)
         xyz = util.fibonacci_sphere(n_pts, xyz=True)
         radii = np.zeros(tp.shape[0])
-        for i, c in enumerate(self.coeffs):
+        for i, c in enumerate(coeffs):
             l, m = util.j2lm(i)
             radii += c*util.spZnm(l, m, tp[:,0], tp[:,1])
         radii = radii/np.max(np.abs(radii))

### 2018-07-09 papers/basic-theory/paper/paper.tex
Very early draft of basic theory paper.

\documentclass{osa-article}

%% Select the journal you're submitting to
%% oe, boe, ome, osac, osajournal
\journal{osajournal}
% Key:
% Express journals must have the correct journal selected:
% {oe} Optics Express
% {boe} Biomedical Optics Express
% {ome} Optical Material Express
% {osac} OSAC Continuum
% Other OSA journals may use:
% {osajournal} Applied Optics, Advances in Optics and Photonics, Journal of the Optical Society of America A/B, Optics Letters, Optica, Photonics Research

% Uncomment if submitting to Photonics Research.
% ONLY APPLICABLE FOR \journal{osajournal}
% \setprjcopyright

% Set the article type
\articletype{Research Article}
% Note that article type is not required for Express journals (OE, BOE, OME and OSAC)

% Talon's custom commands
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
\providecommand{\rb}[1]{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}[1]{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\begin{document}

\title{Spatio-angular transfer functions for fluorescence microscopes I. Basic theory}

\author{Talon Chandler,\authormark{1,*} Author order TBD,\authormark{2,*} and Patrick La Rivi\`ere \authormark{1}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
\authormark{2}Publications Department, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{3}Currently with the Department of Electronic Journals, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}

\email{\authormark{*}talonchandler@talonchandler.com} %% email address is required

%\homepage{talonchandler@talonchandler.com} %% author's URL, if desired

%%%%%%%%%%%%%%%%%%% abstract %%%%%%%%%%%%%%%%
%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]

\begin{abstract*}
  We introduce the basic elements of a complete spatio-angular theory of
  fluorescence microscopes. We start by analyzing a single-view fluorescence
  microscope imaging an ensemble of in-focus dipole absorber/emitters using
  electromagnetic optics and the paraxial approximation. Next, we define the
  spatio-angular transfer function and show that fluorescence microscopes have
  an angular band limit. Finally, we discuss the implications of our analysis on
  quantitative fluorescence microscopy studies.
\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Fluorescence microscopes are ubiquitous tools in biology [XXX], materials
science [XXX], and metrology [XXX] for measuring the concentration of
fluorophores throughout a sample. While an unprocessed fluorescence micrograph
reports the approximate concentration of fluorophores throughout a sample,
diffraction-limited microscopes image a spatially blurred version of the true
fluorophore distribution. Therefore, microscopists who are interested in
accurate measurements will perform a computational restoration to recover some
of the information lost during the imaging process.

Restoration techniques attempt to recover the true distribution of fluorophores
using the measured data and a model of the imaging process. The model of the
imaging process can be obtained theoretically (by mathematically modeling the
instrument under idealized conditions), experimentally (by measuring the
microscope's response to a known input), or by a combination of theory and
experiment (by measuring parameters of an instrument model). In all cases, the
accuracy of the restored image is limited by the accuracy of the imaging model.

Most theoretical fluorescence microscopy imaging models make simplifying
approximations. A common (often unstated) pair of approximations is to (1) treat
fluorophores as monopole absorber/emitters and (2) treat light propagation under
the scalar approximation. In this work we will analyze fluorescence microscopes
without these approximations and find the conditions under which these
approximations are valid.

Using an experimentally determined model is an effective way to find an accurate
model without understanding all of the physical details of the imaging system,
but these approaches require a known input that can completely characterize the
imaging system. Sub-diffraction beads are commonly used as a known input for
measuring the response of a microscope, but we argue that sub-diffraction beads
are not enough to completely characterize the response of a microscope to all
fluorescent samples. Beads can only characterize the response of the microscope
to an angularly uniform distribution of fluorophores, and we will show that all
microscopes have an orientation-dependent response. A complete characterization
requires a test sample with at least three known orientation distributions.

The single-molecule localization microscopy (SMLM) community has pioneered the
use of rigorous electromagnetic models of single fluorescence microscopes
\cite{backer2014, lieb2004}. When only one fluorophore is emitting at a time,
the measured intensity pattern is strongly dependent on the orientation of the
emitting molecule. Backlund and Lew \cite{backlund2014} have shown that ignoring
the orientation of fluorophores can lead to biased estimates of their position,
so the most accurate SMLM experiments must jointly estimate the position and
orientation of the molecule. These joint estimates usually use a set of
precomputed intensity patterns and a maximum-likelihood algorithm to estimate
the orientation and position of each molecule. These methods have led to some of
the most accurate position estimates of single molecules.

Meanwhile, most fluorescence microscopists image ensembles of fluorophores.
Although many groups have used polarizers to probe the orientation of ensembles
of fluorophores \cite{mehta2016} [Forkey], to our knowledge no
work has been done on the response of fluorescence microscopes to ensembles of
oriented fluorophores. Furthermore, current restoration techniques in polarized
light microscopy are lacking because they rely on simple pixel-wise arithmetic
and do not model the propagation of light through the microscope.

In this work we model ensembles of in-focus dipole absorber/emitters using
electromagnetic optics and the paraxial approximation. This marks a first step
towards a complete three-dimensional non-paraxial theory of fluorescence
microscopes. In section 2 we model the excitation and detection processes of
dipoles. We define the most important quantity in this work, the spatio-angular
transfer function, and we use it to show that fluorescence microscopes have an
angular band limit. In section 3 we perform simulations and compare our model to
traditional scalar models. In section 4 we discuss the implications of our work
for fluorescence microscopy and lay out a path towards a complete spatio-angular
theory of fluorescence microscopy.

\section{Theory}
\subsection{Spherical harmonics}\label{sec:sph}
\begin{align}
  y_l^m(\vartheta, \varphi) =
  \begin{cases}
    \sqrt{2}K_l^m\cos(m\varphi)P_l^m(\cos\vartheta), & m > 0\\
    K_l^0P_l^0(\cos\vartheta), & m = 0\\
    \sqrt{2}K_l^m\sin(-m\varphi)P_l^{-m}(\cos\vartheta), & m < 0\\
  \end{cases}
\end{align}
where
\begin{align}
  K_l^m = \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-|m|)!}{(l+|m|)!}},
\end{align}
and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0, 1, 2$
spherical harmonics are given by
\begin{align}
  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}}, \nonumber \\ 
  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta, \nonumber \\
  y_2^{-2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\cos\varphi\sin^2\vartheta, &\hspace{2em} y_2^{-1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\sin\vartheta\cos\vartheta,\nonumber \\
  y_2^0(\vartheta, \varphi) &= \sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1), \nonumber \\ 
  y_2^{1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\cos\varphi\sin\vartheta\cos\vartheta, &\hspace{2em} y_2^{2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}(\cos^2\varphi - \sin^2\varphi)\sin^2\vartheta.\label{eq:harmonics}
\end{align}

\subsection{Excitation model}
% [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
In this section we will calculate the excitation kernel for epi-illumination
microscopes---the relative probability of exciting a molecule with a known
orientation. Our approach is similar to previous work \cite{fourkas2001,  chandler2017},
but here we consider unpolarized illumination and restrict
ourselves to the paraxial approximation.

We consider a single molecule with a fixed absorption dipole moment $\so{}$ that
we express in spherical coordinates [see Fig. 1(a)] as 
\begin{align}
  \so{} &= \cos\varphi\sin\vartheta\mh{x} + \sin\varphi\sin\vartheta\mh{y} + \cos\vartheta\mh{z}. \label{eq:spherical}
\end{align}
We can rewrite Eq. \ref{eq:spherical} in terms of spherical harmonic functions
(see Section \ref{sec:sph}) as
\begin{align}
  \so{} &=\sqrt{\frac{3}{4\pi}}\left[y_1^1(\vartheta, \varphi)\,\mh{x} + y_1^{-1}(\vartheta, \varphi)\,\mh{y} + y_1^0(\vartheta, \varphi)\, \mh{z}\right]. \label{eq:sphharm}
\end{align}
We place the molecule in the focal plane of an aplanatic and
polarization-preserving objective lens with its optical axis aligned with the
$\mh{z}$ axis. Next, we place a spatially incoherent, spatially uniform,
unpolarized thermal light source (or its image) in the back aperture of the
objective lens to illuminate the focal plane. In this geometry each point in the
back focal plane generates a plane wave that illuminates the sample.

To model the unpolarized light source we will use polarized ray tracing [cite
Torok] to find the response for a single polarized ray, then integrate over the
rays and polarizations to find the complete response. First, we model the
electric field at every point on the back focal plane as
\begin{align}
   \mb{E}_{\text{bfp}}(\phi_{\text{pol}}) &\propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y}, \label{eq:bfp0}
\end{align}
where $\phi_{\text{pol}}$ is the polarization orientation and \{$\mh{x}$,
$\mh{y}$\} are transverse Cartesian basis vectors. Notice that Eq. \ref{eq:bfp0}
describes the incoherent electric fields at every point in the back focal plane,
it does not describe a coherent plane wave. Immediately after the lens the
electric field is
\begin{align}
  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \propto \left\{[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\phi}]\,\bsh{\phi} + [\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\rho}]\,\bsh{\theta}\right\}\sqrt{\cos\theta}, \label{eq:bfp2ff}
\end{align}
where \{$\theta$, $\phi$\} are spherical coordinates, \{$\bsh{\rho}$,
$\bsh{\phi}$\} are cylindrical basis vectors, and \{$\bsh{\theta}$,
$\bsh{\phi}$\} are spherical basis vectors defined in Figure 1(a) and related by
\begin{align}
  \bsh{\rho} &= \cos\phi\mh{x} + \sin\phi\mh{y},\label{eq:rho}\\
  \bsh{\phi} &= -\sin\phi\mh{x} + \cos\phi\mh{y},\label{eq:phi}\\
  \bsh{\theta} &= \cos\phi\cos\theta\mh{x} + \sin\phi\cos\theta\mh{y} - \sin\theta\mh{z}.\label{eq:theta}               
\end{align}
In Eq. \ref{eq:bfp2ff} the
$[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\phi}]\,\bsh{\phi}$ term models
s-polarized fields, the
$[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\rho}]\,\bsh{\theta}$ term
models the rotation of p-polarized fields, and the $\sqrt{\cos\theta}$ term
models the apodization of an aplanatic lens. After plugging Eq. \ref{eq:bfp0}
and Eqs. \ref{eq:rho}--\ref{eq:theta} into Eq. \ref{eq:bfp2ff} and applying the
paraxial approximation, the electric field immediately after the lens is given
by
\begin{align}
  \mb{E}_{\text{ff}}^{(p)}(\theta, \phi, \phi_{\text{pol}}) \propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y} - \theta\cos(\phi - \phi_{\text{pol}})\mh{z}.\label{eq:eff}
\end{align}
To calculate the probability that a dipole oriented along $\so{}$ is excited by
a ray with electric field $\mb{E}$ we need to evaluate $|\mb{E}\cdot\so{}|^2$.
Evaluating this expression for each ray would be cumbersome if we used Eqs.
\ref{eq:spherical} and \ref{eq:eff} because we would need to simplify a large
number of trigonometric functions. Instead, we use Eqs. \ref{eq:sphharm} and
\ref{eq:eff} and the real Gaunt coefficients [XXXciteXXX] to find the products
of spherical harmonics. We find that
% [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
\begin{align}
  |\mb{E}_{\text{ff}}^{(p)}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2 \propto\, &\left[1 + \theta^2\cos^2(\phi - \phi_{\text{pol}})\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[ - 1 + 2\theta^2\cos^2(\phi - \phi_{\text{pol}})\right]y_2^{0}(\so{}) +\nonumber \\
                                   &\frac{\sqrt{15}}{10}\theta\sin\phi_{\text{pol}}\cos(\phi - \phi_{\text{pol}})y_2^{-1}(\so{}) + \frac{\sqrt{15}}{10}\theta\cos\phi_{\text{pol}}\cos(\phi - \phi_{\text{pol}})y_2^{1}(\so{}) -\nonumber \\  
                                   &\frac{\sqrt{15}}{20}\sin(2\phi_{\text{pol}})y_2^{-2}(\so{}) - \frac{\sqrt{15}}{20}\cos(2\phi_{\text{pol}})y_2^{2}(\so{}).\label{eq:integrand}
\end{align}
To calculate the complete excitation model we need to integrate Eq.
\ref{eq:integrand} over all polarization orientations and rays
\begin{align}
  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}^{(p)} \cdot \so{}|^2. \label{eq:integral}
\end{align}
After plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral} and evaluating
the integrals, all but two terms disappear and the orientation-dependent
excitation model is given by
\begin{align}
  h_{\text{exc}}(\so{}) &\propto \left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{}). \label{eq:excitation}
\end{align}
We note that the excitation model depends on the orientation of the molecule,
but it does not depend on the position of the molecule in the focal plane. This
is a direct consequence of our illumination geometry---we have placed incoherent
light sources in the back focal plane of the objective so each point in the
focal plane within the field of view is illuminated equally.

\subsection{Detection model}
In this section we will calculate the detection kernel of an epi-detection
microscope---the irradiance on the detector due to single molecule at a known
position with known orientation. Our approach is similar to \cite{backer2014,
  nov2006, agrawal2012}, but here we restrict ourselves to the paraxial
approximation.

We consider a single dipole emitter at the origin with a fixed dipole emission
moment oriented along $\so{}$---parallel to the excitation moment. The electric
field at a position $\mb{r}$ far from the dipole is given by
\begin{align}
  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
\end{align}
If we place the molecule in the focal plane of an aplanatic and
polarization-preserving objective lens with its optical axis aligned with the
$\mh{z}$ axis (or reuse the illumination objective), then the electric field in
the back focal plane of the lens is given by
\begin{align}
  \mb{E}_{\text{bfp}}(\rb{}, \so{}) \propto \left\{[\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\phi}]\,\bsh{\phi} + [\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\theta}]\,\bsh{\rho}\right\}\sqrt{1/\cos\theta}\,\Pi\left(\frac{r_b}{\sin\alpha}\right). \label{eq:bfp}
\end{align}
where the first term accounts for s-polarized fields, the second term accounts
for p-polarized fields, $\sqrt{1/\cos\theta}$ is the apodization factor for an
aplanatic lens, and
\begin{align}
  \Pi\left(\frac{r_b}{\sin\alpha}\right) =
  \begin{cases}
    1\quad \text{if}\quad r_b < \sin^{-1}\alpha,\\
    0\quad \text{else},
  \end{cases}
\end{align}
is the aperture stop. After expanding the dot products, applying the paraxial
approximation, and writing the dipole orientation $\so{}$ in terms of spherical
harmonic functions, we find that the electric field in the back focal plane is
given by
\begin{align}
  \mb{E}_{\text{bfp}}^{(p)}(\rb{}, \so{}) \propto \left\{\left[y_1^1(\so{}) - r_b\cos\phi_b y_1^0(\so{})\right]\mh{x} + \left[y_1^{-1}(\so{}) - r_b\sin\phi_b y_1^0(\so{})\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp2}
\end{align}
We note that Eq. \ref{eq:bfp2} is identical to previously derived models
[Piestun, Backer] except here we have used the paraxial approximation and used
spherical harmonic functions.

Next we place a tube lens one focal length from the back focal plane and a
detector (see Figure XX)). Under the paraxial approximation we can find the
electric field in the detector plane by taking the Fourier transform of the
field in the back focal plane [Goodman]
\begin{align}
  \mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}^{(p)}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
\end{align}
To evaluate the integral we rewrite it in polar coordinates
\begin{align}
\mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) &= \int_{0}^{\alpha}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}^{(p)}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
\end{align}
substitute Eq. \ref{eq:bfp2}, and apply the following identities
\begin{align}
  \int_0^{2\pi}d\phi_b
  \left\{\substack{
    \sin(n\phi_b)\\
    \cos(n\phi_b)
  }\right\}
  \text{exp}\left[ikr_br_d\cos(\phi_b - \phi_d)\right] &= 2\pi i^n
  \left\{\substack{
    \sin(n\phi'_o)\\
    \cos(n\phi'_o)
  }\right\}J_n(k r_br_d),
  \end{align}
  \begin{align}
  \int_0^{\alpha} dr_b (r_b)^{n+1}J_{n}(kr_br_d) &= \alpha^{n+1}\left[\frac{J_{n+1}(k\alpha r_d)}{k r_d}\right],
  \end{align}
to find that 
\begin{align}
  \mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) \propto &\left[\frac{J_1(k\alpha r_d)}{k\alpha r_d}y_1^1(\so{}) - i\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\cos\phi_d y_1^0(\so{})\right]\mh{x}\, + \nonumber \\& \left[\frac{J_1(k\alpha r_d)}{k\alpha r_d}y_1^{-1}(\so{}) - i\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\sin\phi_d y_1^0(\so{})\right]\mh{y}.
\end{align}
We can find the irradiance on the detector by taking the modulus squared of the
electric field
\begin{align}
  h_{\text{det}}(\rd{}, \so{}) &\propto |\mb{E}_{\text{det}}^{(p)}(\rd{}, \so{})|^2.
\end{align}
We use the real Gaunt coefficients to find that
\begin{align}
h_{\text{det}}(\rd{}, \so{}) &\propto \left[a_1( r_d) + \frac{\alpha^2}{4} a_2( r_d)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a_1( r_d) + \frac{\alpha^2}{2} a_2( r_d)\right]y_2^0(\so{}), \label{eq:detection}
\end{align}
where we have defined
\begin{align}
  a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
\end{align}

In our analysis we have only considered a dipole radiator at the origin, but we
can use the shift-invariance of 4$f$ imaging systems to model dipole radiators
at arbitrary positions in the focal plane. If we shift the dipole radiator to an
in-focus position $\ro{}$, then the irradiance pattern on the detector will be
given by $h_{\text{det}}(\rd{} - \ro{})$. We have also restricted our analysis
to an imaging system with unit magnification, but an imaging system with an
arbitrary magnification can be modeled as a system with unit magnification using
a change of variables (see \cite{barrett2004} section 7.2.7).

Finally, we note the similarities between Eqs. \ref{eq:excitation} and
\ref{eq:detection}. If we integrate the detection kernel over the detector and
use the identity $\int_{\mbb{R}^2}d\mb{r}\, a_n(r) = 1$ for $n \in \mbb{N}$,
then we find that the excitation and detection kernels are related by
\begin{align}
  h_{\text{exc}}(\so{}) = \int_{\mbb{R}^2}d\mb{r} h_{\text{det}}(\mb{r}, \so{}).
\end{align}

\subsection{Complete forward model}
In the last two section we have found closed-form expressions for the excitation
kernel $h_{\text{exc}}(\so{})$ and the detection kernel
$h_{\text{det}}(\rd{} - \ro{}, \so{})$. The complete kernel of the microscope is
the product of the excitation and detection kernels
\begin{align}
  h(\rd{} - \ro{}, \so{}) = h_{\text{exc}}(\so{})h_{\text{det}}(\rd{} - \ro{}, \so{}). \label{eq:kernel}
\end{align}
Eq. \ref{eq:kernel} gives the irradiance at position $\rd{}$ on the detector
created by a single dipole at position $\ro{}$ with dipole oriented along
$\so{}$.

Up to this point we have only modeled the imaging system's response to single
fluorescent molecules. We would like to model samples that contain ensembles of
fluorescent molecules with many fluorescent molecules, so we introduce the
\textit{spatio-angular density} to describe arbitrary distributions of
fluorescent dipoles. We define the spatio-angular density $f(\ro{}, \so{})$ as
the number of fluorescent molecules at position $\ro{}$ per unit volume oriented
along $\so{}$ per unit solid angle. Figure TODO illustrates several simple
spatio-angular densities to clarify our definition.

The detector irradiance $g(\rd{})$ created by an arbitrary spatio-angular
density $f(\ro{}, \so{})$ can be found by multiplying the spatio-angular density
by the kernel and integrating over all positions $\ro{}$ and orientations
$\so{}$
\begin{align}
g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro{}, \so{}). \label{eq:fwd}
\end{align}

\subsection{Spatio-angular transfer function}
As written Eq. \ref{eq:fwd} is an extremely expensive integral to compute---to
find the irradiance at a single point on the detector we need to evaluate the
spatio-angular density and the kernel at every point in
$\mbb{S}^2\times \mbb{R}^2$. To simplify the integral, we expand the object and
the kernel onto complex exponentials and spherical harmonics using
\begin{align}
  F_l^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]f(\ro{}, \so{}),\\
  H_l^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h(\ro{}, \so{}).
\end{align}
We also expand the detector irradiance onto spatial harmonics using the Fourier
transform
\begin{align}
  G(\bs{\nu}) \equiv \int_{\mbb{R}^2}d\rd{}\,\text{exp}\left[i2\pi \rd{}\cdot\bs{\nu}\right]g(\rd{}).
\end{align}
Given these definitions, we can rewrite Eq. \ref{eq:fwd} in the frequency domain as 
\begin{align}
G(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^{l}H_l^m(\bs{\nu})F_l^m(\bs{\nu}). 
\end{align}

In Appendix A we calculate the spatio-angular transfer function as
\begin{align}
  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\}, 
\end{align}
where
\begin{align}
  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right), \\
  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right), 
\end{align}
and $C = 1 + \frac{\alpha^2}{4} + \frac{3\alpha^4}{32}$ is a normalization
constant.

\section{Results}

\section{Discussion and conclusion}

\bibliography{paper}
\appendix
\section{Evaluating the spatio-angular transfer function}
In this appendix we will evaluate 
\begin{align}
    H_l^m(\bs{\nu}) &\propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h(\ro{}, \so{}),\label{eq:whole}
\end{align}
where
\begin{align}
  h(\rd{} - \ro{}, \so{}) &\propto h_{\text{exc}}(\so{})h_{\text{det}}(\rd{} - \ro{}, \so{}),\label{eq:split}\\ 
  h_{\text{exc}}(\so{}) &\propto \left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{}),\\  
  h_{\text{det}}(\rd{}, \so{}) &\propto \left[a_1( r_d) + \frac{\alpha^2}{4} a_2( r_d)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a_1( r_d) + \frac{\alpha^2}{2} a_2( r_d)\right]y_2^0(\so{}),
\end{align}
and
\begin{align}
    a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
\end{align}
First we plug Eq. \ref{eq:split} into Eq. \ref{eq:whole} and move the excitation
kernel out of the spatial integral
\begin{align}
    H_l^m(\bs{\nu}) &\propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})h_{\text{exc}}(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h_{\text{det}}(\rd{}, \so{}). \label{eq:satf}
\end{align}
The spatial integral requires us to evaluate the two-dimensional Fourier
transform of $a_1(r_o)$ and $a_2(r_o)$. We will define
\begin{align}
  A_n(\nu) \equiv \mathcal{F}_2\{a_n(r_o)\} =  \int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right] a_n(r_d), \label{eq:ftA}
\end{align}
and evaluate $A_1(\nu)$ and $A_2(\nu)$ later. After substituting \ref{eq:ftA}
into Eq. \ref{eq:satf} we find 
\begin{align}
  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\left\{\left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{})\right\} + \nonumber\\&\left\{\left[A_1(\nu) + \frac{\alpha^2}{4} A_2(\nu)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- A_1(\nu) + \frac{\alpha^2}{2} A_2(\nu)\right]y_2^0(\so{})\right\}. 
\end{align}
After expanding the products of spherical harmonics
\begin{align}
  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\frac{3}{5}A_1(\nu) + \frac{3\alpha^2}{40}[A_1(\nu) + A_2(\nu)] + \frac{9\alpha^4}{160}A_2(\nu)\right]y_0^0(\so{})+\nonumber\\&\frac{3\sqrt{5}}{280}\left[-16A_1(\nu) + \alpha^2[A_1(\nu) + A_2(\nu)] + 3\alpha^4 A_2(\nu)\right]y_4^0(\so{})\Bigg\},\\                             H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]y_0^0(\so{}) + \nonumber\\&\frac{\sqrt{5}}{56}\left[(-16 + \alpha^2)A_1(\nu) + (\alpha^2 + 3\alpha^4)A_2(\nu)\right]y_4^0(\so{})\Bigg\}.
\end{align}
Next, we use the orthogonality of spherical harmonics to evaluate the angular integral
\begin{align}
  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\}, 
\end{align}
where $C = 1 + \frac{\alpha^2}{4} + \frac{3\alpha^4}{32}$ is a normalization
constant.

Our final task is to calculate $A_1(\nu)$ and $A_2(\nu)$. $A_1(\nu)$ is a
well-known result \cite{goodman1996, mertz2009}, but we review the calculation
to establish the tools we'll need to evaluate $A_2(\nu)$. We start by using the
autocorrelation (Wiener-Khinchin) theorem to rewrite the Fourier transform as
\begin{align}
  A_1(\nu) = \frac{1}{\pi}\mathcal{F}_2\left\{\left[\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right]^2\right\} = \frac{1}{\pi}\left[\mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}\right] \label{eq:auto}
\end{align}
where $\star_2$ denotes a two-dimensional autocorrelation. Next, we recognize
that the Fourier transforms on the right hand side of Eq. \ref{eq:auto} are
rotationally symmetric so they can be rewritten as zero-order Hankel transforms
\begin{align}
  A_1(\nu) = \frac{1}{\pi}\left[\mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} \star_2 \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}\right] \label{eq:autoz}
\end{align}
We can apply the Hankel transform identity \cite{poul1998}
\begin{align}
  \mathcal{H}_{n-1}\left\{\frac{J_n(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} = \frac{\nu^{n-1}}{\nu_o^{n}}\Pi\left(\frac{\nu}{\nu_o}\right),\label{eq:identity}
\end{align}
to find that 
\begin{align}
  A_1(\nu) = \frac{1}{\pi\nu_o^{2}}\left[\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \Pi\left(\frac{\nu}{\nu_o}\right)\right] \label{eq:auto3}. 
\end{align}
We can use the geometric construction in Figure \ref{fig:geometry} to express the
autocorrelation in terms of an integral over a region of overlap between
two circles given by
\begin{align}
  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \int_{0}^{\nu/2}d\tau_x\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right).
\end{align}
\begin{figure}[h]
 % \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 0.8\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
   \caption{Geometric construction for evaluating the autocorrelations. We need
     to integrate over the overlapping region of two circles with radius $\nu_o$
     and distance $\nu$ between their centers. The region is given by four times
     the difference in area between a sector of angle
     $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and a triangle with base $\nu/2$
     and hypotenuse $\nu_o$.}
   \label{fig:geometry}
 \end{figure}

 To evaluate $A_2(\nu)$ we could follow the same steps, but we will reach a dead
 end because there is no Hankel transform identity for
 $\mathcal{H}_{n-1}\left\{\frac{J_{n+1}(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}$.
 Instead, we rewrite $A_2(\nu)$ as
\begin{align}
  A_2(\nu) = \frac{2}{\pi}\mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right]^2\right\} = \frac{2}{\pi}\left[\mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right]^2\right\} + \mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right]^2\right\}\right].
\end{align}
Applying the autocorrelation theorem gives
\begin{align}
  A_2(\nu) = \frac{2}{\pi}\Bigg[&\mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right\} + \nonumber\\ &\mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right\}\Bigg].
\end{align}
After converting the Fourier transforms to Hankel transforms with the identities
\begin{align}
  \mathcal{F}_2\left\{f(r)\cos(\phi)\right\} &= -i\cos\phi_{\nu}\mathcal{H}_1\left\{f(r)\right\},\\
  \mathcal{F}_2\left\{f(r)\sin(\phi)\right\} &= -i\sin\phi_{\nu}\mathcal{H}_1\left\{f(r)\right\},
\end{align}
and evaluating the Hankel transforms with Eq. \ref{eq:identity}, we find that
\begin{align}
  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\left\{\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right] + \left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}. \label{eq:long}
\end{align}
Eq. \ref{eq:long} contains two autocorrelations that require us to find the
weighted overlap of two circles. Neither of these autocorrelations are
rotationally symmetric, but their sum must be rotationally symmetric. With this
symmetry in mind, we recognize that the first autocorrelation is largest for
shifts along the $x$ direction and smallest for shifts along the $y$ direction
with a smooth $\cos^2\phi_{\nu}$ weighting between the two extremes. The same is
true for the second autocorrelations except the $x$ and $y$ axes are exchanged
and there is a $\sin^2\phi_{\nu}$ weighting between the two extremes. Therefore,
we can rewrite Eq. \ref{eq:long} as
\begin{align}
  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\Bigg\{&\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\cos^2\phi_\nu + \left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\sin^2\phi_\nu + \nonumber\\ &\left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\cos^2\phi_\nu + \left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\sin^2\phi_\nu\Bigg\}. \label{eq:long3}
\end{align}
where $\star_2^x$ denotes a two-dimensional autocorrelation for shifts along
the $x$ direction. We can use the following pair of identities
\begin{align}
  \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) = \nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_y\Pi\left(\frac{\nu}{\nu_o}\right),\\
  \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) = \nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_y\Pi\left(\frac{\nu}{\nu_o}\right),
\end{align}
to simplify Eq. \ref{eq:long3} to
\begin{align}
  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\Bigg\{&\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right] + \left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\Bigg\}. \label{eq:long4}
\end{align}
First we evaluate the autocorrelation for shifts along the $x$ axis
\begin{align}
  &= -\frac{2}{\pi\nu_o^4}\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\\
  &= -\frac{8}{\pi\nu_o^4}\Bigg[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau})\\ &\hspace{5em}- \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
\end{align}
For the first inner integral we make use of the following identities
\begin{align}
  \int_0^{\cos^{-1}z}d\phi\cos^2\phi &= \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\cos^{-1}z,\\
  \int_0^{\cos^{-1}z}d\phi\cos\phi &= \sqrt{1 - z^2},
\end{align}
which results in
\begin{align}
  &= -\frac{8}{\pi\nu_o^{4}}\Bigg[\int_0^{\nu_o}d\tau\frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2\nu_o}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\nonumber\\ &\hspace{5em}\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  -\frac{8}{\pi\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{1}{\pi}\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= \frac{1}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= \frac{1}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}
\end{align}
Next we evaluate the autocorrelation for shifts along the $y$ axis
\begin{align}
  &\frac{-2}{\pi\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
  &=  \frac{-8}{\pi\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
\end{align}
For the first inner integral we make use of
\begin{align}
  \int\limits_0^{\cos^{-1}z} d\phi \sin^2\phi &= -\frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\cos^{-1}(z).
\end{align}
This results in
\begin{align}
  &=\frac{-8}{\pi\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{-8}{\pi\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{1}{\pi}\Bigg[\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[5 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right). \label{eq:auto2}
\end{align}
Taking the sum of Eqs. \ref{eq:auto1} and \ref{eq:auto2} gives the final result
\begin{align}
  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right). 
\end{align}

\end{document}

### 2018-07-12 notes/2018-05-30-polarized-dispim-svd/report/report.tex
Finish diSPIM 3D SVD notes.

@@
 In the
+\href{https://github.com/talonchandler/polharmonic/blob/master/papers/basic-theory/paper/paper.pdf}{paper
+  draft} we derive the two-dimensional detection kernel. Note that this model
+differs from the
 \href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-05-14-single-view-continuous-svd/report/report.pdf}{May
-  14 notes} we derived the two-dimensional detection kernel. The kernel is
-two-dimensional because it only considers thin in-focus objects. For a complete
-non-paraxial three-dimensional model I would eventually like to follow Backer
-and Moerner \cite{backer2014}, but there is still a few weeks of work required
-to find the associated transfer functions. Instead I'll follow the early diSPIM
+  14 model}---the old model contains an error that over predicts the
+spatio-angular coupling by a factor of 4. The kernel is two-dimensional because
+it only considers thin in-focus objects. For a complete non-paraxial
+three-dimensional model I would eventually like to follow Backer and Moerner
+\cite{backer2014}, but there is still a few weeks of work required to find the
+associated transfer functions. Instead I'll follow the early diSPIM
 deconvolution models \cite{wu2013} and use an axial Gaussian function to model
@@
 \begin{align}
-  h_{\tx{A}, \tx{det}}(\ro, \so) &= \left[[{a}^2(r_{xy}) + 2b^2(r_{xy})]y_0^0(\so) + \frac{1}{\sqrt{5}}\left[- a^2(r_{xy}) + 4b^2(r_{xy})\right]y_2^0(\so)\right]\mathfrak{g}(r_z, \sigma_{\tx{det}}), \label{eq:det1}
+  h_{\tx{A}, \tx{det}}(\ro, \so) = \left\{\left[a_1(r_{xy}) + \frac{\alpha^2}{4}a_2(r_{xy})\right]y_0^0(\so) + \frac{1}{\sqrt{5}}\left[-a_1(r_{xy}) + \frac{\alpha^2}{2}a_2(r_{xy})\right]y_2^0(\so)\right\}\mathfrak{g}(r_z, \sigma_{\tx{det}}), \label{eq:det1}
 \end{align}
@@
 \begin{align}
-  a(r) = \frac{J_1(2\pi \nu_or)}{\pi \nu_or}, 
-  &\hspace{2em}
-    b(r) = \frac{\tx{NA}}{n_o}\left[\frac{J_2(2\pi \nu_or)}{\pi \nu_or}\right],  \label{eq:abparadef}
+  a_n(r) &\equiv \frac{n}{\pi}\left[\frac{J_n(2\pi\nu_o r)}{2\pi\nu_o r}\right],
            \intertext{and}
   r_{xy} \equiv \sqrt{r_x^2 + r_y^2},\hspace{2em}
-  \nu_o \equiv &\frac{\tx{NA}}{\lambda},\hspace{2em}
-  \tx{NA} = n_o\sin\alpha.
+  \nu_o &\equiv \frac{\tx{NA}}{\lambda},\hspace{2em}
+  \alpha \equiv \frac{\tx{NA}}{n_0}.
 \end{align}
@@
 \begin{align}
-  h_{\tx{B}, \tx{det}}(\ro, \so) = \Bigg[[{a}^2(r_{yz}) + 2b^2(r_{yz})]y_0^0(\so) &+ \frac{1}{2\sqrt{5}}\left[- a^2(r_{yz}) + 4b^2(r_{yz})\right]y_2^0(\so) \nonumber \\ &+ \frac{1}{2}\sqrt{\frac{3}{5}}\left[- a^2(r_{yz}) + 4b^2(r_{yz})\right]y_2^2(\so)\Bigg]\mathfrak{g}(r_x, \sigma_{\tx{det}}), \label{eq:det2}
+  h_{\tx{B}, \tx{det}}(\ro, \so) = \Bigg\{\left[{a}_1(r_{yz}) + \frac{\alpha^2}{4}a_2(r_{yz})\right]y_0^0(\so) &+ \frac{1}{2\sqrt{5}}\left[- a_1(r_{yz}) + \frac{\alpha^2}{2}a_2(r_{yz})\right]y_2^0(\so) \nonumber \\ &+ \frac{1}{2}\sqrt{\frac{3}{5}}\left[- a_1(r_{yz}) + \frac{\alpha^2}{2}a_2(r_{yz})\right]y_2^2(\so)\Bigg\}\mathfrak{g}(r_x, \sigma_{\tx{det}}), \label{eq:det2}
 \end{align}
@@
 In Figs. \ref{fig:tfA} and \ref{fig:tfB} we plot the transverse part of the
-diSPIM transfer function. Extending these plots to three-dimensions is simple
+diSPIM transfer function. Extending these plots to three dimensions is simple
 given our assumption that the axial part is Gaussian. Notice that view B has a
@@
 
-\fig{../calculations/out/Hillx.pdf}{1.0}{Transverse transfer function
+\fig{../calculations/out2/Hillx.pdf}{1.0}{Transverse transfer function
   $H_{l,n,\tx{A}}^m(\bv_{xy})$ for view A of a polarized diSPIM microscope with
@@
   band. \textbf{Entries:} Each column and row contains a continuous
-  two-dimensional plot indexed by the vector $\mb{r}_{xy}$ ranging from
-  $-2\text{NA}/\lambda$ to $+2\text{NA}/\lambda$ (although $\mb{r}_{xy}$ is
+  two-dimensional plot indexed by the vector $\bs{\nu}_{xy}$ ranging from
+  $-2\text{NA}/\lambda$ to $+2\text{NA}/\lambda$ (although $\bs{\nu}_{xy}$ is
   rotationally symmetric so one dimension would suffice). All values are
@@
 
-\fig{../calculations/out/Hillz.pdf}{1.0}{Transverse transfer function
+\fig{../calculations/out2/Hillz.pdf}{1.0}{Transverse transfer function
   $H_{l,n,\tx{B}}^m(\bv_{yz})$ for view B of a polarized diSPIM microscope with
@@
 Also notice that uniform distributions (or anything resembling a uniform
-distribution) are not in the measurement space of either view. We saw the same
-thing for single-view epi-illumination microscopes, although in that case there
-were distributions that were mostly uniform with slight depressions along the
-optical axis.
+distribution) are not object-space singular functions of either view. We saw the
+same thing for single-view epi-illumination microscopes, although in that case
+there were object-space singular functions that were mostly uniform with slight
+depressions along the optical axis. Note that we can still measure uniform
+distributions with either view, but these distributions have a component in the
+null space.
 
-\fig{../calculations/out/SVSx.pdf}{1.0}{Singular system for view A
+\fig{../calculations/out2/SVSx.pdf}{1.0}{Singular system for view A
   ($x$-illumination, $z$-detection) of a polarized diSPIM microscope with a 0.8
   NA detection objective. \textbf{Rows:} Discrete branches of the singular value
-  system indexed by $j$. \textbf{Column 1:} Continuous singular value spectra
+  system indexed by $j$. \textbf{Column 1:} Continuous singular value spectrum
   for each branch $j$ indexed by spatial frequency $\bs{\rho}$. The singular
@@
 
-\fig{../calculations/out/SVSz.pdf}{1.0}{Singular system for view B
+\fig{../calculations/out2/SVSz.pdf}{1.0}{Singular system for view B
   ($z$-illumination, $x$-detection) of a polarized diSPIM microscope with a 0.8
@@
 \end{align}
-nFor the diSPIM, the matrix $\mathsf{K}$ has $6\times 6$ non-zero entries---two
+For the diSPIM, the matrix $\mathsf{K}$ has $6\times 6$ non-zero entries---two
 views with three circular harmonics for each view---so solving this eigenvalue
 problem at each point in frequency space is computationally feasible.
+
+Figures \ref{fig:sysx}--\ref{fig:sysz} show the singular systems for a symmetric
+0.8 NA polarized illumination diSPIM microscope where the axial resolution
+($\propto 1/\sigma_{\text{ax}}$) is 1/3 of the lateral resolution for each view.
+I expect to modify this parameter based on bead measurements taken with the
+final system.
+
+\fig{../calculations/multi-out/SVS3Dx.pdf}{0.95}{Singular system for a symmetric
+  0.8 NA polarized illumination diSPIM microscope. \textbf{Rows:} Discrete
+  branches of the singular value system. \textbf{Column 1:} Maximum intensity
+  projections of the normalized singular value spectrum for each branch indexed
+  by 3D spatial frequency $\bs{\rho}$. \textbf{Columns 2-5:} Angular part of the
+  object-space singular vector at spatial frequencies marked with `x's in the
+  first column. The camera is facing the origin along the [1,1,1] axis with the
+  $z$ axis pointing up along the page. A \textcolor{red}{red} surface indicates
+  positive values, a \textcolor{blue}{blue} surface indicates negative values,
+  and the distance from the origin indicates the magnitude.}{sysx}
+  % filename, width, caption, label
+
+\fig{../calculations/multi-out/SVS3Dy.pdf}{1.0}{Identical to Figure
+  \ref{fig:sysx} with object space singular values along the $y$ axis.}{sysy}
+  % filename, width, caption, label
+
+\fig{../calculations/multi-out/SVS3Dz.pdf}{1.0}{Identical to Figure
+  \ref{fig:sysx} with object space singular values along the $z$ axis.}{sysz}
+  % filename, width, caption, label
 

### 2018-07-12 notes/2018-05-30-polarized-dispim-svd/calculations/test-mic.py

@@ -2,8 +2,8 @@ from polharmonic import det, ill, micro
 import numpy as np
 
 #n_px=2**4 + 1
-n_px=2**6 + 1
-folder='out/'
+n_px=2**7 + 1
+folder='out2/'
 
 iz = ill.Illuminator(optical_axis=[0,0,1], na=0, polarizer=True, illuminate_all=False)
 dx = det.Detector(optical_axis=[1,0,0], polarizer=False)

### 2018-07-12 notes/2018-05-30-polarized-dispim-svd/calculations/test-multi.py

@@ -2,16 +2,14 @@ from polharmonic import det, ill, micro, multi
 import numpy as np
 
 #n_px=2**4 + 1
-n_px=2**3 + 1
+n_px=2**4 + 1
 folder='multi-out/'
 
-mm = multi.MultiMicroscope()
+mm = multi.MultiMicroscope(sigma_ax=0.33)
 # mm.micros[0].plot(mm.micros[0].H, filename=folder+'H0.pdf', n_px=n_px, plot_m=[-2, -1, 0, 1, 2])
 mm.calc_SVD(n_px=n_px)
-mm.plot_SVS_3D(filename=folder+'SVS3D.pdf', show=False)
+mm.plot_SVS_3D(filename=folder+'SVS3Dx.pdf')
+mm.plot_SVS_3D(filename=folder+'SVS3Dy.pdf', marks=np.array([[0,0,0], [0, 0.5 ,0], [0,1,0], [0,1.5,0]]))
+mm.plot_SVS_3D(filename=folder+'SVS3Dz.pdf', marks=np.array([[0,0,0], [0, 0, 0.5], [0,0,1], [0,0,1.5]]))
 
-# mm.micros[0].calc_SVD(n_px=n_px)
-# mm.micros[0].plot_SVS(filename=folder+'SVS0.pdf')
-# mm.micros[1].calc_SVD(n_px=n_px)
-# mm.micros[1].plot_SVS(filename=folder+'SVS1.pdf')
 

### 2018-08-31 notes/2018-08-31-spang-recon/report/report.tex
Spatio-angular reconstruction notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\usepackage[linesnumbered,ruled]{algorithm2e}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{bold-extra}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\argmax}{\arg\!\max}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathfrak{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rb}{\mathbf{r}_b}
\providecommand{\rbm}{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{\mathfrak{r}}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\ms}[1]{\mathsf{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\tv}{\texttt{v}}
\providecommand{\tx}[1]{\text{#1}}
\providecommand{\tb}[1]{\textbf{#1}}
\providecommand{\ttt}[1]{\texttt{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bp}{\bs{\rho}}
\providecommand{\p}{\mh{p}}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\intinf}{\int_{-\infty}^{\infty}}

\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[H]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Spatio-angular restoration of polarized diSPIM data:\\
  analytical, numerical, and experimental results
  \vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
  % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-3em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
These notes detail the spatio-angular restoration pipeline for data collected
with the polarized diSPIM. In Section \ref{sec:fwd} we explain our forward
model---the relationship between an arbitrary spatio-angular density and the
data we collect with the polarized diSPIM. We will focus on our discrete
implementation and the computational issues that we faced. In Section
\ref{sec:inv} we will explain our inversion scheme---the set of computations
that allow us to recover a spatio-angular density from noise-corrupted data. In
Sections \ref{sec:num} and \ref{sec:exp} we will show numerical and experimental
results.

\section{Forward model} \label{sec:fwd}
\subsection{Continuous-to-continuous model} \label{sec:cc}
The objects we are attempting to simulate and reconstruct are spatio-angular
densities of fluorophores $f(\ro, \so)$---the number of fluorophores at each 3D
position $\ro$ oriented along a direction $\so$. Therefore, the complete object
space $\mbb{U}$ is the function space $\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^2)$.
The data that we sample from each arm of the polarized diSPIM is
$g(\rd, \p)$---the irradiance measured at each 3D detector position $\rd$ with
the illumination polarizer oriented along $\p$. The data space for each view is
a member of the function space $\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^1)$. We have
two views, so the complete data space $\mbb{V}$ is the function space
$[\mbb{L}_2(\mbb{R}^3 \times \mbb{S}^1)]^2$. Although this section is named
continuous-to-continuous (CC in Barrett's notation), strictly speaking this is
already a CC-CD model because we have a discrete number of views.

In previous note sets we have shown that we can write the CC model for the
polarized diSPIM as
\begin{align}
  g_{\tv}(\rd, \p) = \intr{3}d\ro \ints{2}d\so\, h_{\tv}(\rd - \ro, \p, \so)f(\ro, \so), \label{eq:fwd}
\end{align}
where $\tv \in \{\text{A}, \text{B}\}$ is the light path index, and
$h_{\tv}(\rd - \ro, \p, \so)$ is the kernel of the integral transform that maps
objects space to data space. The imaging process consists of incoherent
excitation and detection steps, so we can write the kernel as a product of an
excitation and detection kernel
\begin{align}
  h_{\tv}(\ro, \so; \mh{p}) &= h_{\tv, \tx{exc}}(\ro, \so; \mh{p})h_{\tv, \tx{det}}(\ro, \so).\label{eq:split}
\end{align}
Notice that we are considering polarized illumination, so the polarizer
coordinate $\p$ is a variable in the excitation kernel only.

The excitation kernels for each view are given by
\begin{align}
  h_{\tx{B}, \tx{exc}}(\ro, \so; \mh{p}) &= \left[z_{0}(\mh{p})y_0^0(\so) + \sqrt{\frac{3}{5}}z_{-2}(\mh{p})y_2^{-2}(\so) - \frac{1}{\sqrt{5}}z_{0}(\mh{p})y_2^0(\so) + \sqrt{\frac{3}{5}}z_{2}(\mh{p})y_2^{2}(\so)\right]\mf{g}(r_x, \sigma_{\tx{ls}}),\\
  h_{\tx{A}, \tx{exc}}(\ro, \so; \mh{p}) &= \mc{R}_{xz}\left\{h_{\tx{B}, \tx{exc}}(\ro, \so; \mh{p})\right\},
\end{align}
where $z_n(\p)$ are circular harmonic functions; $y_l^m(\so)$ are spherical
harmonic functions; $\mf{g}(\mu, \sigma)$ is a Gaussian function with mean $\mu$
and standard deviation $\sigma$; and $\mc{R}_{xz}$ is a rotation operator that
swaps the $x$ and $z$ coordinates within the function. Note that the operator
$\mc{R}_{xz}$ applies a rotation transformation to the circular and spherical
harmonics as well.

The detection kernels are given by
\begin{align}
  h_{\tx{A}, \tx{det}}(\ro, \so) &= \left\{\left[a_{1,\tx{A}}(r_{xy}) + \frac{\alpha_{\tx{A}}^2}{4}a_{2,\tx{A}}(r_{xy})\right]y_0^0(\so) + \frac{1}{\sqrt{5}}\left[-a_{1,\tx{A}}(r_{xy}) + \frac{\alpha_{\tx{A}}^2}{2}a_{2,\tx{A}}(r_{xy})\right]y_2^0(\so)\right\}\mathfrak{g}(r_z, \sigma_{\tx{det}}),\\
  h_{\tx{B}, \tx{det}}(\ro, \so) &= \mc{R}_{xz}\left\{h_{\tx{A}, \tx{det}}(\ro, \so)\right\}.
\end{align}
where
\begin{align}
  a_{n,\tv}(r) &\equiv \frac{n}{\pi}\left[\frac{J_n(2\pi\nu_{o,\tv} r)}{2\pi\nu_{o,\tv} r}\right],
           \intertext{and}
  r_{xy} \equiv \sqrt{r_x^2 + r_y^2},\hspace{2em}
  \nu_{o,\tv} &\equiv \frac{\tx{NA}_{\tv}}{\lambda},\hspace{2em}
  \alpha_{\tv} \equiv \frac{\tx{NA}_{\tv}}{n_0}. \label{eq:alpha}
\end{align}
Notice that we have added a subscript $\tv$ to NA, $\alpha$, and $\nu_o$ to allow for the possibility of an asymmetric diSPIM.

Eqs. \ref{eq:fwd}--\ref{eq:alpha} are sufficient to simulate the forward model
of a polarized diSPIM, but the integrals in Eq. \ref{eq:fwd} are extremely
expensive to calculate. If we naively discretize $f(\ro, \so)$ into
$N = 1000 \times 1000 \times 1000 \times 1000 = 10^{12}$ spatio-angular points
and discretize the data into
$M = 1000 \times 1000 \times 1000 \times 4\ \text{polarizers} \times 2\
\text{views} = 8\e{9}$ data points (a realistic data set), then simulating the
forward model (assuming the kernel is inexpensive to evaluate) would require
$\mc{O}(NM) \approx 8\e{21}$ floating-point operations (FLOPs)---not realistic
on a typical $10^{11}$ floating-point operations per second (FLOPS) machine (a
very good laptop). Aside: there's a cute mnemonic for converting large numbers
of seconds---$\pi$ seconds is approximately one nanocentury or
$\pi\e{7}\ \text{s} \approx 1\ \text{y}$. Luckily we can evaluate the forward
model much more quickly by exploiting the symmetries and rank of the integral
operator.

The first symmetry we'll exploit is shift invariance. We notice that the
spatial integral is in the form of a convolution, so we apply the
convolution theorem and rewrite Eq. \ref{eq:fwd} as
\begin{align}
  g_{\tv}(\rd, \p) = \mc{F}^{-1}_{\mbb{R}^3}\left\{\ints{2}d\so\, \mc{F}_{\mbb{R}^3}\left\{h_{\tv}(\ro, \mh{p}, \so)\right\} \mc{F}_{\mbb{R}^3}\left\{f(\ro, \so)\right\}\right\}, \label{eq:filter1}
\end{align}
where $\mc{F}_{\mbb{R}^3}$ denotes a three-dimensional Fourier transform given by
\begin{align}
  \mc{F}_{\mbb{R}^3}\left\{f_{\tv}(\ro, \so)\right\} &\equiv \intr{3}d\ro\, \me^{i2\pi\ro\cdot\bv} f_{\tv}(\ro, \so).
\end{align}
Eq. \ref{eq:filter1} is already much easier to compute than Eq. \ref{eq:fwd},
but it still requires us to evaluate a spherical integral with two 3D Fourier
transforms in the integrand. We can simplify this integral by exploiting the
angular rank of the kernel. First, we apply the following identity
\begin{align}
  \ints{2}d\mh{s}{}\, f(\mh{s})g(\mh{s}) = \lmsum \mc{F}_{\mbb{S}^2}\left\{f(\mh{s})\right\}\mc{F}_{\mbb{S}^2}\left\{g(\mh{s})\right\}, \label{eq:plan}
\end{align}
where
\begin{align}
  \mc{F}_{\mbb{S}^2}\left\{f(\mh{s})\right\} \equiv \int_{\mbb{S}^2}f(\mh{s})y_l^m(\mh{s}).
\end{align}
Eq. \ref{eq:plan} is the generalized Plancharel theorem for spherical functions.
It is a special case of the fact that scalar products are invariant under
unitary transformations (see Barrett 3.78). Next, we plug Eq. \ref{eq:plan}
into Eq. \ref{eq:filter1} to get
\begin{align}
  g_{\tv}(\rd, \p) = \mc{F}^{-1}_{\mbb{R}^3}\left\{\lmsum H_{l,\tv}^m(\bv, \mh{p}) \mc{F}_{\mbb{R}^3\times\mbb{S}^2}\left\{f(\ro, \so)\right\}\right\} \label{eq:filter}
\end{align}
where
\begin{align}
  H_{l,\tv}^m(\bv, \mh{p}) \equiv \mc{F}_{\mbb{R}^3\times\mbb{S}^2}\left\{h_{\tv}(\ro, \p, \so)\right\} &\equiv \intr{3}d\ro\, \me^{i2\pi\ro\cdot\bv}\ints{2}d\so\, y_l^m(\so) h_{\tv}(\ro, \p, \so).\label{eq:transfer}
\end{align}
Eq. \ref{eq:filter} is the main result of this section. Right now it is not
obvious that Eq. \ref{eq:filter} is any more efficient than Eq.
\ref{eq:filter1}, but when we calculate the transfer function we will see that
the sum over spherical harmonics contains a small number of terms.

We compute the transfer function $H_{l,\tv}^m(\bv, \mh{p})$ by plugging Eq.
\ref{eq:split} into Eq. \ref{eq:transfer}
\begin{align}
  H_{l,\tv}^m(\bv, \mh{p}) = \mc{F}_{\mbb{R}^3\times\mbb{S}^2}\left\{h_{\tv, \tx{exc}}(\ro, \so; \mh{p})h_{\tv, \tx{det}}(\ro, \so)\right\}.
\end{align}
We can factor the kernel for both views into a transverse and axial part (a Gaussian) so
\begin{align}
  H_{l,\tv}^m(\bv, \mh{p}) &= \mc{F}_{\mbb{R}^3\times\mbb{S}^2}\left\{h^{\text{tr}}_{\tv, \tx{exc}}(\so; \mh{p})h^{\text{tr}}_{\tv, \tx{det}}(\ro, \so)\mf{g}(0, \sigma_{\text{ax}})\right\}.
\end{align}
Rearranging the Fourier transforms gives
\begin{align}
  H_{l,\tv}^m(\bv, \mh{p}) &= \mc{F}_{\mbb{S}^2}\left\{h^{\text{tr}}_{\tv, \tx{exc}}(\so; \mh{p})\mc{F}_{\mbb{R}^2}\left\{h^{\text{tr}}_{\tv, \tx{det}}(\ro, \so)\right\}\mc{F}_{\mbb{R}^1}\left\{\mf{g}(0, \sigma_{\text{ax}})\right\}\right\}.\label{eq:rearr}
\end{align}
The Fourier transform of a Gaussian is a Gaussian with inverse standard
deviation, and in previous notes we evaluated the Fourier transform of the
transverse detection kernel as
\begin{align}
  \mc{F}_{\mbb{R}^2}\left\{h^{\text{tr}}_{\tx{A}, \tx{det}}(\ro, \so)\right\} &= \left[A_{1,\tx{A}}(\nu_{xy}) + \frac{\alpha_{\tx{A}}^2}{4}A_{2,\tx{A}}(\nu_{xy})\right]y_0^0(\so) + \frac{1}{\sqrt{5}}\left[-A_{1,\tx{A}}(\nu_{xy}) + \frac{\alpha_{\tx{A}}^2}{2}A_{2,\tx{A}}(\nu_{xy})\right]y_2^0(\so),
\end{align}
where
\begin{align}
  A_{1,\tx{A}}(\nu_{xy}) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right) - \frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\sqrt{1 - \left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right)^2}\right\}\Pi\left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right),\\
  A_{2,\tx{A}}(\nu_{xy}) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right) - \left[3 - 2\left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right)^2\right]\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\sqrt{1 - \left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right)^2}\Bigg\}\Pi\left(\frac{\nu_{xy}}{2\nu_{o,\tx{A}}}\right).
\end{align}
We have closed form solutions for the inner Fourier transforms of Eq.
\ref{eq:rearr}, but we still need to evaluate the outer spherical Fourier
transform. The function is the product of spherical Fourier transforms, so we
need to take a spherical convolution of the coefficients of the spherical
Fourier transforms of the individual functions. We could do this by hand and
write out the result, but the equations would be long and wouldn't give much
insight. Instead, we've implemented a spherical convolution that uses the Gaunt
coefficients to efficiently compute the transfer function. The most important
result is that we can compute $H_{l,\tv}^m(\bv, \mh{p})$ directly without
evaluating expensive Bessel functions then taking the Fourier transform.

We notice that both the excitation and detection kernels contain just a few
spherical harmonic functions (four for the excitation kernel, two for the
detection kernel), and these terms are all in the $l=0$ and $l=2$ bands. When we
multiply out the spherical harmonics we get a total of 9 terms in the $l=0$,
$l=2$, and $l=4$ bands. This means that the sum over spherical harmonics in Eq.
\ref{eq:filter} contains only 9 terms which is an enormous computational savings
over the complete spherical integral.

\subsection{Continuous-to-discrete model}
To convert the CC model to a CD model we weight Eq. \ref{eq:fwd} by a sampling
aperture $w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p)$ and integrate over the
continuous detector coordinates $\rd$ and $\p$ to obtain
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \intr{3}d\rd\ints{1}d\p\, w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p)\left[\intr{3}d\ro \ints{2}d\so\, h_{\tv}(\rd - \ro, \p, \so)f(\ro, \so)\right]. \label{eq:cd}
\end{align}
Notice that we use monospace type for discrete (integer) indices---$\ttt{p}$ is the
polarizer setting index, $\ttt{v}$ is the view index, and
$\tb{\ttt{r}}_{\ttt{d}}$ is the voxel multi-index.

We will rearrange the integrals and group terms in Eq. \ref{eq:cd} to find 
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \intr{3}d\ro \ints{2}d\so\, h_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}, \ttt{v}}(\ro, \so) f(\ro, \so), \label{eq:cd2}
\end{align}
where the new CD kernel is related to the CC kernel by
\begin{align}
   h_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}, \ttt{v}}(\ro,\so) = \intr{3}d\rd\ints{1}d\p\, w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p) h_{\tv}(\rd - \ro, \p, \so).
\end{align}

We can interpret the sampling aperture
$w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p)$ as the sensitivity of the
$(\tb{\ttt{r}}_{\ttt{d}}, \ttt{p})\text{th}$ measurement to the irradiance at
position $(\rd, \p)$. The simplest choice for the sampling aperture is 
\begin{align}
  w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p) = \delta(\rd - \mb{\epsilon}\tb{\ttt{r}}_{\ttt{d}})\delta(\mh{p} - \mb{\epsilon}_{\phi}\ttt{p}), \label{eq:sampling}
\end{align}
where $\mb{\epsilon}$ is the distance between voxels and $\mb{\epsilon}_{\phi}$
is the angle between polarizer settings. With this choice of sampling aperture the
CD forward model in Eq. \ref{eq:cd2} reduces to 
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \intr{3}d\ro \ints{2}d\so\, h_{\tv}(\mb{\epsilon}\tb{\ttt{r}}_{\ttt{d}} - \ro, \mb{\epsilon}_{\phi}\ttt{p}, \so)f(\ro, \so). 
\end{align}
Notice that the CD kernel is a sampled version of the CC kernel, but this is
only true when the sampling aperture is given by Eq. \ref{eq:sampling}.

A more realistic model of the sampling aperture is given by
\begin{align}
  w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p) = \frac{1}{\epsilon^3}\text{rect}\left(\frac{\rd - \mb{\epsilon}\tb{\ttt{r}}_{\ttt{d}}}{\mb{\epsilon}}\right)\delta(\mh{p} - \mb{\epsilon}_{\phi}\ttt{p}),
\end{align}
where the rect function models the aperture of each pixel. Finally, we mention
the possibility of modeling a rotating polarizer by using the following sampling
aperture
\begin{align}
  w_{\tb{\ttt{r}}_{\ttt{d}}, \ttt{p}}(\rd, \p) = \frac{1}{\epsilon^3\epsilon_{\phi}}\text{rect}\left(\frac{\rd - \mb{\epsilon}\tb{\ttt{r}}_{\ttt{d}}}{\mb{\epsilon}}\right)\text{rect}\left(\frac{\mh{p} - \mb{\epsilon}_{\phi}\ttt{p}}{\mb{\epsilon}_\phi}\right).
\end{align}
We might consider these sampling aperture in the future, but for now we will use
the sampling aperture in Eq. \ref{eq:sampling} and move forward with the CD model in Eq. \ref{eq:cd}.

\subsection{Discrete-to-discrete model}
To convert the CD model to a DD model we need to expand our object-space
functions $f(\ro, \so)$ onto a discrete set of expansion functions with
\begin{align}
  f(\ro, \so) = \sum_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} \phi_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}(\ro, \so).  \label{eq:exp}
\end{align}
We will choose our expansion functions as
\begin{align}
  \phi_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}(\ro, \so) = \delta\left(\ro - \epsilon\ttt{\tb{r}}_{\ttt{o}}\right)y_{\ttt{j}}(\so), \label{eq:expansion}
\end{align}
where $\ttt{j}$ is a single index over the spherical harmonics. This choice of
basis function may seem odd---we are representing the spatial part of our object
in a sampled voxel basis and the angular part in a spherical harmonic basis. The
main reason for this choice is that the diSPIM has a small angular rank, so we
can't reconstruct more than a few angular coefficients anyway. By expanding our
object in a spherical harmonic basis, we significantly reduce the storage and
computation requirements for our simulations and reconstructions without any
loss of accuracy.

The expansion functions in Eq. \ref{eq:expansion} are orthonormal, but they do
not form a complete basis for $\mbb{L}_2(\mbb{R}^3\times \mbb{S}^2)$. A good
choice for a complete orthonormal basis is
\begin{align}
  \phi_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}(\ro, \so) = \frac{1}{\epsilon^3}\text{rect}\left(\frac{\ro - \epsilon\ttt{\tb{r}}_{\ttt{o}}}{\epsilon}\right)y_{\ttt{j}}(\so), 
\end{align}
but we will use the basis in Eq. \ref{eq:expansion} for now to simplify our
model.

For a given object $f(\ro, \so)$, we can find the expansion coefficients using
\begin{align}
  \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} = \intr{3}d\ro\ints{2}d\so\, \phi_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}(\ro, \so)f(\ro, \so). \label{eq:theta}
\end{align}
Plugging Eq. \ref{eq:expansion} into Eq. \ref{eq:theta} gives 
\begin{align}
  \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} = \ints{2}d\so\, f(\ro - \epsilon\ttt{\tb{r}}_{\ttt{o}},\so)y_{\ttt{j}}(\so) = \mc{F}_{\mbb{S}^2}\left\{f(\ro - \epsilon\ttt{\tb{r}}_{\ttt{o}},\so)\right\} \label{eq:f2sh}
\end{align}
which shows us the procedure to find the expansion coefficients of an
object---sample the object on a spatial grid then take the spherical Fourier
transform.

If we plug Eq. \ref{eq:exp} into Eq. \ref{eq:cd} we find
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \intr{3}d\ro \ints{2}d\so\, h_{\tv}(\mb{\epsilon}\tb{\ttt{r}}_{\ttt{d}} - \ro, \mb{\epsilon}_{\phi}\ttt{p}, \so)\left[\sum_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} \phi_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}(\ro, \so)\right].
\end{align}
After plugging in the expansion functions in Eq. \ref{eq:expansion}, evaluating
the spatial integral, and rearranging terms we find
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \sum_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}\ints{2}d\so\, h_{\tv}(\mb{\epsilon}[\tb{\ttt{r}}_{\ttt{d}} - \tb{\ttt{r}}_{\ttt{o}}], \mb{\epsilon}_{\phi}\ttt{p}, \so)y_{\ttt{j}}(\so)\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}.
\end{align}
We can rewrite this equation as a DD model
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \sum_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}h_{\ttt{\tb{r}}_{\ttt{d}} - \ttt{\tb{r}}_{\ttt{o}},\ttt{p},\ttt{v},\ttt{j}}\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}},\label{eq:dd}
\end{align}
where
\begin{align}
h_{\ttt{\tb{r}},\ttt{p},\ttt{v},\ttt{j}} = \ints{2}d\so\, h_{\tv}(\mb{\epsilon}\tb{\ttt{r}}, \mb{\epsilon}_{\phi}\ttt{p}, \so)y_{\ttt{j}}(\so).\label{eq:dd2}
\end{align}
Eqs. \ref{eq:dd} and \ref{eq:dd2} specify a discrete forward model, but they are
expensive to compute because of the sum over $\ttt{\tb{r}}$ and the integral
over $\mbb{S}^2$. Following the simplifications we made in Section \ref{sec:cc}, we
apply the discrete convolution multiplication theorem to rewrite the forward
model as
\begin{align}
  g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}} = \text{DFT}^{-1}\Big\{\sum_{\ttt{j}}H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}\text{DFT}\left\{\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}\right\}\Big\}, \label{eq:fastfwd}
\end{align}
where
\begin{align}
  H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}} = \ints{2}d\so\, \text{DFT}\left\{h_{\tv}(\mb{\epsilon}\tb{\ttt{r}}, \mb{\epsilon}_{\phi}\ttt{p}, \so)\right\}y_{\ttt{j}}(\so) = H_{\ttt{v}, \ttt{j}}(\bar{\bs{\nu}}/\epsilon, \epsilon_{\phi}\ttt{p}), 
\end{align}
where the far LHS is the discrete spatio-angular transfer function and the far
RHS is the sampled continuous spatio-angular transfer function from Section 2.1.

The forward model in Eq. \ref{eq:fastfwd} is extremely fast compared to the
naive discretization we considered previously. The 3D DFTs require approximately
$3N\log N$ FLOPs (about $10^4$ FLOPs for $N = 10^3$). We know that the sum over
$\ttt{j}$ has 15 terms, and we need to calculate these 15 DFTs for each of 4
polarizer settings and 2 views. Therefore, our approximate FLOP count is
$10^4 \times 15 \times 4 \times 2 = 1.2\e{6}$---about 15 orders of magnitude
faster than our naive approach.

\subsection{Implementation details}
For small input sizes we can precompute the entire array
$H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}$ and apply Eq. \ref{eq:fastfwd}
directly. This array quickly becomes too large to store in memory
though---$10^9$ spatial points $\times$ 4 polarizers $\times$ 2 views $\times$
15 spherical harmonics $\times$ 32 bits = 480 GB. To avoid memory issues, we
separate $H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}$ into transverse and axial
parts, precompute and store these small arrays, then assemble the complete array
in pieces during the application of the forward model. We also exploit the
8-fold spatial symmetry of the array
$H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}$ and only store the positive octant.
Finally, the sum over $\ttt{j}$ needs to be computed at each point in
$\bar{\bs{\nu}}$, so we parallelize this loop over multiple CPUs.

\section{Inverse problem} \label{sec:inv} It will be convenient to rewrite the
forward model in Eq. \ref{eq:fastfwd} completely in the spatial frequency domain
as
\begin{align}
  G_{\bar{\bs{\nu}},\ttt{p},\ttt{v}} = \sum_{\ttt{j}}H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}\Theta_{\bar{\bs{\nu}},\ttt{j}}, 
\end{align}
where
\begin{align}
  G_{\bar{\bs{\nu}},\ttt{p},\ttt{v}} = \text{DFT}\left\{g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}}\right\},\\
    \Theta_{\bar{\bs{\nu}},\ttt{j}} = \text{DFT}\left\{\theta_{\tb{\ttt{r}}_{\ttt{o}},\ttt{j}}\right\}.
\end{align}
If we combine the indices $\ttt{p}$ and $\ttt{v}$ into a single multi-index $\ttt{\tb{q}} = (\ttt{p}, \ttt{v})$ then the forward model becomes
\begin{align}
  G_{\bar{\bs{\nu}},\ttt{\tb{q}}} = \sum_{\ttt{j}}H_{\bar{\bs{\nu}},\ttt{\tb{q}},\ttt{j}}\Theta_{\bar{\bs{\nu}},\ttt{j}} \label{eq:matrix}
\end{align}
which has the form of a matrix multiplication at each discrete spatial frequency
$\bar{\bs{\nu}}$. We can rewrite Eq. \ref{eq:matrix} in matrix notation as
\begin{align}
  \mb{G}_{\bar{\bs{\nu}}} = \mb{H}_{\bar{\bs{\nu}}}\bs{\Theta}_{\bar{\bs{\nu}}}.  \label{eq:matrix2}
\end{align}
Taking the SVD of $\mb{H}_{\bar{\bs{\nu}}}$ gives
\begin{align}
  \mb{G}_{\bar{\bs{\nu}}} = \sum_{k=0}^R \sqrt{\mu_{\bar{\bs{\nu}}, k}}\textbf{v}_{\bar{\bs{\nu}}, k}\textbf{u}_{\bar{\bs{\nu}}, k}^{\dagger}\bs{\Theta}_{\bar{\bs{\nu}}}, \label{eq:svd}
\end{align}
where $\mu_{\bar{\bs{\nu}}, k}$, $\textbf{v}_{\bar{\bs{\nu}}, k}$,
$\textbf{u}_{\bar{\bs{\nu}}, k}$, and $R$ are the singular values, data space
singular vectors, object space singular vectors, and rank of
$\mb{H}_{\bar{\bs{\nu}}}$, respectively. Notice that Eq. \ref{eq:svd} gives us
an even more efficient way to compute the forward model---we only need to
compute the sum up to the rank instead of summing over the spherical harmonic
coefficients. Unfortunately, this trick is only feasible if we can store the
singular value decomposition of $\mb{H}_{\bar{\bs{\nu}}}$ in memory. In our case
we have to create $\mb{H}_{\bar{\bs{\nu}}}$ on the fly, and it would be too
expensive to calculate the SVD at each point on the fly.

We would like to estimate $\bs{\Theta}_{\bar{\bs{\nu}}}$ from noise-corrupted
measurements $\mb{G}_{\bar{\bs{\nu}}}$. We can rearrange Eq. \ref{eq:svd}
to find 
\begin{align}
  \bs{\hat{\Theta}}_{\bar{\bs{\nu}}} = \sum_{k=0}^R \frac{1}{\sqrt{\mu_{\bar{\bs{\nu}}, k}}}\textbf{u}_{\bar{\bs{\nu}}, k}\textbf{v}_{\bar{\bs{\nu}}, k}^{\dagger}\mb{G}_{\bar{\bs{\nu}}}. \label{eq:pinv}
\end{align}
where\, $\hat{\vspace{0.1em}}$\, denotes an estimate. This solution is called
the Moore-Penrose pseudoinverse and it gives a least-squares solution to any set
of linear equations. Notice that the sum in Eq. \ref{eq:pinv} is only up to the
rank $R$, so this solution avoids division by zero.

In practice, the pseudoinverse solution is susceptible to corruption by noise
because of division by small singular values. To avoid this problem, we use
a Tikhonov regularization parameter that suppresses the terms in Eq. \ref{eq:pinv}
with small singular values. The Tikhonov-regularized solution is given by
\begin{align}
  \bs{\hat{\Theta}}_{\bar{\bs{\nu}}} = \sum_{k=0}^R \frac{\sqrt{\mu_{\bar{\bs{\nu}}, k}}}{\mu_{\bar{\bs{\nu}}, k} + \eta}\textbf{u}_{\bar{\bs{\nu}}, k}\textbf{v}_{\bar{\bs{\nu}}, k}^{\dagger}\mb{G}_{\bar{\bs{\nu}}},  \label{eq:tik}
\end{align}
where $\eta$ is the regularization parameter.

Although we have derived the Tikhonov-regularized solution in a heuristic way in
this section, it is possible to show that Eq. \ref{eq:tik} is the solution to the
following optimization problem
\begin{align}
  \bs{\hat{\Theta}}_{\bar{\bs{\nu}}} = \argmin_{\bs{\Theta}_{\bar{\bs{\nu}}}}\left\{|| \mb{G}_{\bar{\bs{\nu}}} - \mb{H}_{\bar{\bs{\nu}}}\bs{\Theta}_{\bar{\bs{\nu}}}||^2 + \eta ||\bs{\Theta}_{\bar{\bs{\nu}}}||^2\right\}. 
\end{align}
In this form it is clear that increasing the regularization parameter $\eta$
favors solutions with a smaller norm.

After calculating $\bs{\hat{\Theta}}_{\bar{\bs{\nu}}}$ we can find the
object-space coefficients $\hat{\theta}_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}$ with
an inverse DFT, and we have completed the inversion. In pseudocode the complete
reconstruction algorithm is given by\\
\begin{figure}[H]
\centering
\begin{minipage}{.65\linewidth}
\begin{algorithm}[H]
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{ForEach}{for each}
  \Input{Data array $g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}}$, regularization parameter $\eta$}
  \Output{Estimate of spatio-angular density coefficients $\hat{\theta}_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}$}
  $\hat{\Theta}_{\bar{\bs{\nu}},\ttt{j}} \leftarrow \text{Zeros}()$\\
  $G_{\bar{\bs{\nu}},\ttt{p},\ttt{v}} \leftarrow \text{DFT}(g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}})$\\
  \textbf{for each} $\bar{\nu}$ in $\bar{\bs{\nu}}$:\\
  \qquad $H_{\ttt{p}, \ttt{v}, \ttt{j}} \leftarrow \text{CalculateH}(\bar{\nu}, \ttt{p}, \ttt{v}, \ttt{j})$\\
  \qquad $G_{\bar{\nu}, \ttt{q}} \leftarrow \text{Flatten}(G_{\bar{\nu}, \ttt{p},\ttt{v}}, [\ttt{p},\ttt{v}])$\\
  \qquad $H_{\ttt{q}, \ttt{j}} \leftarrow \text{Flatten}(H_{\ttt{p},\ttt{v}, \ttt{j}}, [\ttt{p},\ttt{v}])$\\
  \qquad $U_{\ttt{k}, \ttt{j}}, \mu_{\ttt{k}}, V_{\ttt{k},\ttt{q}} \leftarrow \text{SVD}(H_{\ttt{q}, \ttt{j}})$\\
  \qquad $\hat{\Theta}_{\bar{\nu},\ttt{j}} \leftarrow \sum_{\ttt{k}}^R\sum_{\ttt{q}}\frac{\sqrt{\mu_{\ttt{k}}}}{\mu_{\ttt{k}} + \eta}U_{\ttt{k},\ttt{j}}V_{\ttt{k},\ttt{q}}G_{\bar{\nu}, \ttt{q}} $\\
  $\hat{\theta}_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} \leftarrow \text{DFT}^{-1}(\hat{\Theta}_{\bar{\bs{\nu}},\ttt{j}}).$
  \caption{diSPIM spatio-angular reconstruction}
\end{algorithm}
\end{minipage}
\end{figure}
Similar to the forward model calculation, we assemble
$H_{\ttt{p}, \ttt{v}, \ttt{j}}$ from precalculated matrices to avoid memory
limitations, we exploit the 8-fold symmetry of the kernel to reduce the number
of SVDs calculated in the loop, and we parallelize the loop over multiple CPUs.

\subsection{Summary parameters}
Algorithm 1 shows the complete spatio-angular reconstruction, but our choice to
reconstruct onto a spherical harmonic basis makes the result difficult to
interpret. Therefore, we need another set of computations that can convert the
spherical harmonic coefficients at each spatial point to interpretable values.
Recall that we cannot reconstruct directly to a spatio-angular density because
the result will not fit in memory---we need to reconstruct the spherical
harmonic coefficients then calculate summary parameters only as necessary.

The most informative (and expensive) set of summary parameters is to calculate
the complete orientation distribution function (ODF) from the set of spherical
harmonic coefficients. This computation is essentially an inverse spherical Fourier
transform given by
\begin{align}
  f_{\ttt{\tb{r}}_{\ttt{o}}}(\so) =  \sum_{\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} y_{\ttt{j}}(\mathbf{\hat{s}}_{o}). \label{eq:odf}
\end{align}
To calculate a visually informative ODF we need to evaluate
$f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)$ at approximately 500 points, so calculating
the ODF amounts to a $15 \times 500$ matrix multiplication at each voxel. This
matrix multiplication is the most expensive computation in the entire pipeline,
and it is not feasible to compute it in every voxel for large data sets.
Typically we only calculate and visualize a subset of the ODFs---we either
restrict ourselves to an ROI or calculate and visualize ODFs in every $N$th
voxel.

Another useful summary parameter is the spatial density of fluorophores. For
angularly continuous functions the spatial density
$\rho_{\ttt{\tb{r}}_{\ttt{o}}}$ is related to the spatio-angular density
$f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)$ by
\begin{align}
  \rho_{\ttt{\tb{r}}_{\ttt{o}}} = \int_{\mbb{S}^2}f_{\ttt{\tb{r}}_{\ttt{o}}}(\so). \label{eq:density}
\end{align}
The naive approach to computing $\rho_{\ttt{\tb{r}}_{\ttt{o}}}$ is to calculate
$f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)$ using Eq. \ref{eq:odf} then apply Eq.
\ref{eq:density}. Instead we can calculate the density directly from the spherical
harmonic coefficients using
\begin{align}
  \rho_{\ttt{\tb{r}}_{\ttt{o}}} = \int_{\mbb{S}^2}\sum_{\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}y_{\ttt{j}}(\so), 
\end{align}
then rearranging the sum and integral
\begin{align}
  \rho_{\ttt{\tb{r}}_{\ttt{o}}} = \sum_{\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}\int_{\mbb{S}^2}y_{\ttt{j}}(\so), 
\end{align}
and finally noting that only the $l=0$ spherical harmonics have a non-zero
integral over the sphere
\begin{align}
  \rho_{\ttt{\tb{r}}_{\ttt{o}}} = \sum_{l}\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}\int_{\mbb{S}^2}y^0_{l}(\so). \label{eq:fd}
\end{align}
We can precompute the integrals then apply Eq. \ref{eq:fd} as a weighted sum
over just three spherical harmonic coefficients.

Another useful summary parameter is the generalized fractional anisotropy (GFA)
that was defined in (Tuch 2004) to extend the fractional anisotropy used in
diffusion tensor MRI to high-angular resolution MRI. Tuch defines the GFA as
\begin{align}
  \vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = \frac{\text{StandardDeviation}\left\{f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)\right\}}{\text{RootMeanSquare}\left\{f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)\right\}}.\label{eq:gfa}
\end{align}
Similar to the density, the naive approach to computing
$\vartheta_{\ttt{\tb{r}}_{\ttt{o}}}$ would be to sample using Eq. \ref{eq:odf}
then apply Eq. \ref{eq:gfa}. We can improve on this by writing Eq. \ref{eq:gfa}
in terms of integrals then simplifying the integrals. We start with
\begin{align}
  \vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = \sqrt{\frac{\ints{2}d\so\left[f(\so) - (\rho_{\ttt{\tb{r}}_{\ttt{o}}}/4\pi)\right]^2}{\ints{2}d\so\left[f(\so)\right]^2}},\\
\end{align}
then plug in the spherical harmonic coefficients
\begin{align}
  \vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = \sqrt{\frac{\ints{2}d\so\left[\sum_{\ttt{j}}\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}y_{\ttt{j}}(\so) - (\rho_{\ttt{\tb{r}}_{\ttt{o}}}/4\pi)\right]^2}{\ints{2}d\so\left[\sum_{\ttt{j}} \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}y_{\ttt{j}}(\so)\right]^2}}.
\end{align}
After expanding the square brackets and exploiting the orthogonality of the
spherical harmonics we end up with
\begin{align}
  \vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = \sqrt{\frac{\sum_{\ttt{j}} \theta^2_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} + \rho^2_{\ttt{\tb{r}}_{\ttt{o}}}/2\pi + (\rho_{\ttt{\tb{r}}_{\ttt{o}}}/4\pi)^2}{\sum_{\ttt{j}} \theta^2_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}}}.
\end{align}

The final summary parameter we would like to calculate is the direction along
which the most fluorophores are oriented
\begin{align}
  \mathbf{\hat{s}}_{\ttt{\tb{r}}_{\ttt{o}}, \text{max}} =  \argmax_{\so} f_{\ttt{\tb{r}}_{\ttt{o}}}(\so). 
\end{align}
Our problem is to find the maximum point of a function on a sphere given its
spherical harmonic coefficients. If we can tolerate an angular error of
$\Delta \mathbf{\hat{s}}$ steradians, then the brute-force approach is to sample
the sphere at $4\pi/\Delta \mathbf{\hat{s}}$ approximately equally spaced points
then choose the maximum.

A faster approach is to use a simple optimization scheme that first samples
coarsely over the sphere then performs a gradient descent on the best of the
coarse samples. In general this type of scheme is not guaranteed to find the
global maximum, but I expect that a wise choice of initial sample points will
guarantee the global maximum for our bandlimited signals.

Currently I am calculating all of the summary statistics using the naive
approaches, and these calculations are the bottle neck in the reconstruction
pipeline. I will implement the improved routines soon.

\begin{table}[h]
\centering
\begin{tabular}{lll}\toprule
  Parameter name & Symbol & Interpretation\\
  \midrule
  Orientation distribution function (ODF) & $f_{\ttt{\tb{r}}_{\ttt{o}}}(\so)$ & Number of fluorophores at $\ttt{\tb{r}}_{\ttt{o}}$ oriented along $\so$.\\
  Density & $\rho_{\ttt{\tb{r}}_{\ttt{o}}}$ & Number of fluorophores at $\ttt{\tb{r}}_{\ttt{o}}$. \\
  Generalized fractional anisotropy (GFA) & $\vartheta_{\ttt{\tb{r}}_{\ttt{o}}}$ & A scale-invariant statistic of the angular spread of\\
                 & & fluorophores at $\ttt{\tb{r}}_{\ttt{o}}$. $\vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = 1$ for very anisotropic distributions\\
                 & & and $\vartheta_{\ttt{\tb{r}}_{\ttt{o}}} = 0$ for isotropic fluorophores.  \\
  Peak direction (mode) & $\mathbf{\hat{s}}_{\ttt{\tb{r}}_{\ttt{o}}, \text{max}}$ & Direction along which most fluorophores are oriented at $\ttt{\tb{r}}_{\ttt{o}}$. \\

  \bottomrule
\end{tabular}
\caption{Summary of angular summary statistics.}
\end{table}

\section{Numerical results} \label{sec:num}
\subsection{Bead studies}
Figures \ref{fig:beadx}--\ref{fig:beadiso} show the results of numerical bead
studies that we used to debug and verify our forward model. We placed a single
bead in the center of a small field-of-view then applied our forward model to
generate data that would be collected under the four polarizer settings and two
viewing directions.

First, we generated four numerical phantoms---$\mh{x}$, $\mh{y}$, and $\mh{z}$
oriented beads and an isotropic bead. The continuous spatio-angular densities of
these phantoms are given by
\begin{align}
  f_1(\ro, \so) &= \delta(\ro)\, \delta(\so - \mh{x}), \\
  f_2(\ro, \so) &= \delta(\ro)\, \delta(\so - \mh{y}), \\
  f_3(\ro, \so) &= \delta(\ro)\, \delta(\so - \mh{z}), \\
  f_4(\ro, \so) &= \delta(\ro).
\end{align}
Next, we set the FOV by choosing the number of voxels (32 per side) and the
voxel dimensions (130 nm per side). Finally, we calculated the object-space
coefficients $\theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}}$ from the spatio-angular
density using
\begin{align}
  \theta_{\ttt{\tb{r}}_{\ttt{o}},\ttt{j}} = \ints{2}d\so\, f(\ro - \epsilon\ttt{\tb{r}}_{\ttt{o}},\so)y_{\ttt{j}}(\so). \label{eq:spang2co}
\end{align}

Now that we have a numerical phantom, the next step is to specify a microscope.
We used the following parameters for our numerical simulations
\begin{align}
  \text{NA}_{\text{A}} &= 1.1,\\
  \text{NA}_{\text{B}} &= 0.71,\\
  \lambda_{\text{em}} &= 525\, \text{nm} \leftarrow \text{Alexa 488 emission},\\
  n &= 1.33 \leftarrow \text{water}.
\end{align}
We use these parameters when we calculate the elements of
$H_{\bar{\bs{\nu}},\ttt{p},\ttt{v},\ttt{j}}$. Finally, we apply Eq.
\ref{eq:fastfwd} to calculate the data
$g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}}$. Figures
\ref{fig:beadx}--\ref{fig:beadiso} show summary views of the five-dimensional
datasets $g_{\tb{\ttt{r}}_{\ttt{d}},\ttt{p},\ttt{v}}$. For each polarizer
setting and view we plot the maximum intensity projection along each of the
three axes.

Although the entire kernel is specified exactly in section 1, it is useful to
have a few rules of thumb in mind when you look at the bead results:
\begin{enumerate}
\item The probability of exciting a dipole is proportional to
  $|\mh{p}\cdot\bs{\mu}|^2 = \cos^2\theta$ where $\mh{p}$ is the polarizer
  orientation and $\bs{\mu}$ is the excitation dipole moment---lots of
  excitation when the polarization is parallel to the dipole moment.
\item A dipole emitter radiates along a direction $\mh{s}$ with a power
  proportional to $1 - |\mh{s}\cdot\bs{\mu}|^2 = \sin^2\theta$---lots of
  radiation in the plane perpendicular to the dipole moment.
\item An objective with NA $>$ 0 will collect the radiation from a cone of
  $\mh{s}$ directions.
\item When a dipole moment is parallel to the detection optical axis, then the
  light in the back focal plane will be radially polarized and the resulting
  image will look like a doughnut.
\end{enumerate}

\fig{../figures/beads/data0.pdf}{1.0}{Simulated data from a bead with $\mh{x}$-oriented
  dipole moments.}{beadx}
\fig{../figures/beads/data1.pdf}{1.0}{Simulated data from a bead with
  $\mh{y}$-oriented dipole moments.}{}
\fig{../figures/beads/data2.pdf}{1.0}{Simulated
  data from a bead with $\mh{z}$-oriented dipole moments.}{bead4}
\fig{../figures/beads/data3.pdf}{1.0}{Simulated data from an isotropic bead.}{beadiso}

We have made several assumptions about the axial part of the kernel. First, we
assume that the axial part can be described by a Gaussian. The axial part would
be more accurately described by a widefield fluorescence kernel convolved with
the Gaussian width of the light sheet, but we expect that the width of the light
sheet dominates the kernel so a pure Gaussian is appropriate. Second, we have
assumed that the width of the light sheet is constant which allows us to
describe the system as shift-invariant. This assumption has been used in
previous diSPIM deconvolutions, and it allows us to keep the computations
tractable. Finally, we have chosen the width of the axial Gaussian to be
$\sim 3\times$ broader than the transverse width of the transverse kernel of an
isotropic bead. This width was chosen to match the axial FWHM of the kernels
supplied by Min in $\ttt{PSFA\_1p1NA.tif}$ and $\ttt{PSFB\_0p71NA.tif}$.
\textcolor{blue}{\textbf{Do you think these assumptions are appropriate? Do the
    bead PSFs look reasonable?}}

\subsection{Helix studies}
We created a more complex spatio-angular phantom to test our forward model and
inversion scheme. The helix phantom is shown in Figure \ref{fig:phant}---it
consists of three helices with different coil directions and dipoles that are
aligned along the tangent of the helix at each point. On one end of the helix
the dipoles are almost completely aligned along the tangent, and at the other
end of the helix the dipoles are isotropic.

We would like to express the helix phantom as a continuous spatio-angular
density. First, we specify a single helix with a parameterized line
\begin{align}
  c(t) = (r_{\text{h}}\cos t, r_{\text{h}}\sin t, p_{\text{h}} t)\quad \text{for}\, t \in [-2\pi, 2\pi].
\end{align}
Next, for each point in space $\ro$ we find the closest point on the helix then
find the corresponding parameter $t$ and name it $t_{\ro}^*$
\begin{align}
t_{\ro}^* = \text{min}_t||c(t) - \ro||^2. 
\end{align}
Next, we build the complete helix using
\begin{align}
  f_{\text{helix}}(\ro, \so) =
  \begin{cases}
    w(\ro, \so, c'(t_{\ro}^*), \kappa(t_{\ro}^*)), & t_{\ro}^* < r_{\text{cyl}} \\
    0 & t_{\ro}^* < r_{\text{cyl}}
  \end{cases}\label{eq:helix}
\end{align}
where
\begin{align}
  w(\ro, \so, \mh{n}, \kappa) &= \frac{1}{4\pi{}_1F_1(1/2,3/2,\kappa)}e^{\kappa(\mh{n}\cdot\so)},\label{eq:watson}\\
  \kappa(t) &= kt + k_o, \label{eq:kappa}
\end{align}
and ${}_1F_1(1/2,3/2,\kappa)$ is the Kummer confluent hypergeometric function.
Eq. \ref{eq:helix} restricts the phantom to within $r_{\text{cyl}}$ of the
helix, Eq. \ref{eq:watson} is a normalized Watson distribution with spread
parameter $\kappa$, and Eq. \ref{eq:kappa} linearly increases the spread parameter as we move along the helix.

Finally, we assemble three helices
\begin{align}
  f_{\text{phantom}}(\ro, \so) = f_{\text{helix}}(\ro - \mathbf{\mathfrak{r}}_0, \so) + \mc{R}_x\left\{f_{\text{helix}}(\ro - \mathbf{\mathfrak{r}}_1, \so)\right\} + \mc{R}_y\left\{f_{\text{helix}}(\ro - \mathbf{\mathfrak{r}}_2, \so)\right\}, 
\end{align}
where $\mathcal{R}_x$ is a rotation operator that rotates the helix direction to
along the $\mh{x}$ direction. For our simulations we chose the following set of parameters
\begin{align}
  r_{\text{h}} &= 700\ \text{nm},\\
  p_{\text{h}} &= 1000\ \text{nm},\\
  \mathbf{\mathfrak{r}}_0 &= (-2080,-2080,2080)\ \text{nm},\\
  \mathbf{\mathfrak{r}}_1 &= (0,0,0)\ \text{nm},\\
  \mathbf{\mathfrak{r}}_2 &= (2080,2080,2080)\ \text{nm},\\
  r_{\text{cyl}} &= 250\ \text{nm},\\
  k &= \frac{5}{4\pi},\\
  k_0 &= 2\pi.
\end{align}
We calculated the coefficients of the object using Eq. \ref{eq:spang2co}, then
simulated the noise-free data with the same imaging parameters as the previous
section. The data we generated is shown in Figure \ref{fig:data}.

We applied our spatio-angular restoration algorithm to the noise-free data and
recovered the object in Figure \ref{fig:recon}. Alternatively, we can interpret
Figure \ref{fig:recon} as the measurement-space component of the helix
phantom---we applied the forward model then reconstructed with the pseudoinverse
solution which is identical to projection onto the measurement space (Barrett
Table 1.2).

Finally, we simulated data using the helix phantom with Poisson noise at SNR =
10 (the maximum number of photons is 100), then attempted to reconstruct the
object with several different Tikhonov regularization parameters. Figure
\ref{fig:recontik} shows that the mean square error (MSE) between the phantom
and the reconstructed object has a minimum at a specific regularization
parameter as we would expect. The optimal regularization parameter will change
as we vary the SNR, but we can use Figure \ref{fig:recontik} as evidence that
the inversion algorithm is working well.

\fig{../figures/helix/phantom.pdf}{1.0}{Helix phantom summary.}{phant}
\fig{../figures/helix/data.pdf}{1.0}{Data generated by the helix phantom.}{data}
\fig{../figures/helix/phantom-recon.pdf}{1.0}{Helix phantom reconstruction.}{recon}
\fig{../figures/helix-noise/mse.pdf}{0.5}{Mean square error of helix phantom reconstruction with SNR = 10.}{recontik}
  % filename, width, caption, label

\section{Experimental results} \label{sec:exp}

We collected several data sets with the polarized light asymmetric diSPIM (1.1
and 0.71 NA). In this section we will review the preprocessing, calibration, and
reconstructed results.

\subsection{Min's preprocessing}
Min applies the following preprocessing steps to the raw data
\begin{enumerate}
\item ``Deshearing'' the data to correct for stage scanning.
\item ROI selection to reduce the size of the data.
\item ``Isometrization'' to convert all of the data to isometric voxels.
\item Registration of the two views so that they are in the same coordinate
  system.
\end{enumerate}

\subsection{Talon's preprocessing}
I applied the following preprocessing steps to prepare Min's preprocessed data for
spatio-angular restoration.
\begin{enumerate}
\item Background correction.
\item Correcting the views for power differences.
\item Correcting the views for voxel size differences.
\item Correcting the volumes (each view and polarization) with polarization
  calibration data.
\item TODO: I will apply a bleaching correction based on the first and last
  polarizer setting. The data in these notes had negligible bleaching, so I
  haven't needed this correction yet.
\end{enumerate}

For the background correction I subtracted the mean of a background ROI from all
of the data. I applied the same background correction to the volumes from each
polarizer setting, but I applied different background corrections to the data
from each view.

To correct the views for power differences I multiplied the data from the
high-NA view by a factor of $(1.1/0.71)^2 = 2.4$. This correction models the fact the we
balanced the input power of the two views so that the pixels from each view
would collect approximately the same number of photons.

Next, I applied a correction to account for the different voxel sizes of the raw
data. Min's preprocessing outputs isometric voxels, but it does not preserve the
total number of counts before and after the correction. For example, if we put a
single (100, 100, 200) nm voxel with a value of 50 into Min's preprocessing
algorithm, the output would be two (100, 100, 100) nm voxels each with a value
of 50. I am applying a correction factor so that the output would be two (100,
100, 100) nm voxels each with a value of 25.

In the GUV dataset the raw voxel size in view A is (130, 130, 549)
nm, and the raw voxel size in view B is (227, 227, 835.8) nm. To correct for
this difference I multiply the data in view A by a factor of
$(227/130)^2(835.8/549)$ = 4.64. \textcolor{blue}{\textbf{Min, Hari---does this make sense?}}

Finally, I applied a correction factor to each volume to account for
imperfections in the polarized illumination due to misalignment or polarization
errors introduced during reflection by the dichroics. To collect calibration
data Min imaged the center of a fluorescent lake of uniformly oriented
fluorophores under each polarizer setting. He also collected data from the epi
path and the imaging path for a total of 16 volumes (epi/imaging, 4 polarizer
settings, 2 views). I manually selected an ROI in each of these 16 volumes and
stored the mean value of these ROIs. Next, I applied correction factors to
correct for errors on the illumination path. We would expect that the intensity
measured from the epi path should be constant as the polarization changes, so I
applied correction factors to account for any deviation from a constant---the
largest correction factor was approximately 5\%. Finally, I applied correction
factors to correct for errors on the detection path. We have a model that
predicts the data we would expect to collect from a uniform lake of uniformly
oriented fluorophore---namely, the transfer function evaluated at zero
spatio-angular frequency $H_{0,\tv}^0(0,\mh{p})$. I compared the calibration
data to our model and applied correction factor to account for any
differences---the largest correction factor was approximately 10\%.
\textcolor{blue}{\textbf{Min, Hari---does this make sense?}}

I applied each of the correction factors to the data, but I could have applied
the correction factors to the model. I have chosen to correct the data to make
the comparison with the simulated data in the previous section easier.

\subsection{GUV study}
Mai prepared a sample of giant unilamellar vesicles (GUVs) labelled with Alexa
Fluor 488. From two-dimensional fluorescence orientation studies we expect to
observe the dipole moments oriented normal to the surface of the vesicles.

Figure \ref{fig:guv-data} shows the corrected data and Figure
\ref{fig:guv-recon} shows the reconstructed spatio-angular density. The
reconstructed peak orientations are approximately normal to the sphere's
surface, although some orientations are not reconstructed well---the
``degeneracy'' between $\mh{x} + \mh{z}$ and $\mh{x} - \mh{z}$ oriented dipoles
is evident in the $xz$ projection of the peaks. In particular, it's
clear that the density is not recovered well for dipoles oriented along
$\mh{x} - \mh{z}$ at the points farthest from the cover slip. I suspect that
these portions of the object are in the null space of the microscope, but I am
still investigating. A GUV phantom will help us understand this issue.

\fig{../figures/guv-recon/data-corrected.pdf}{1.0}{GUV data after corrections.}{guv-data}
\vspace{-1em}
\fig{{../figures/guv-recon/guv-recon-1.0e+00}.pdf}{1.0}{GUV reconstruction with $\eta = 1$.}{guv-recon}
\vspace{-2em}
\subsection{Xylem study}
Tobias prepared a sample of xylem labeled with mScarlet. From two-dimensional
fluorescence orientation studies we expect to observe the dipole moments
oriented parallel to the helices.

Figure \ref{fig:xylem-data} shows the corrected data and Figure
\ref{fig:xylem-recon} shows the reconstructed spatio-angular density. The
reconstructed peak orientations are approximately parallel to the helix surface,
although once again the ``degeneracy'' between $\mh{x} + \mh{z}$ and
$\mh{x} - \mh{z}$ oriented dipoles is evident in the $xz$ projection of the
peaks. The $yz$ projection of the peak and ODFs is particularly promising---the
reconstructed orientations are clearly parallel to the helix around the whole
circle of orientations.

One part of the helix near the center of the $xy$ projection is nearly absent in
the data and the reconstruction. It is not clear to me why this region did not
give a larger signal in the $-\mh{x} + \mh{y}$ polarizer data since the helix is
parallel to the $-\mh{x} + \mh{y}$ direction in this region. In the numerical
phantom we successfully recovered all of the orientations in the phantom, so
it's not clear to me what is causing this problem. Reconstructing larger volumes
may point us in the right direction.

\fig{../figures/xylem-recon/data-corrected.pdf}{1.0}{Xylem data after corrections.}{xylem-data}
\fig{{../figures/xylem-recon/guv-recon-1.0e+00}.pdf}{1.0}{Xylem reconstruction with $\eta = 1$.}{xylem-recon}
\vspace{-2em}
\section{Next priorities}
Here are some of my next tasks in approximate order of priority. Feedback is
always welcome!
\begin{itemize}
\item Optimize the summary statistics calculations. These optimizations will make
  the full 1000 $\times$ 1000 $\times$ 1000 voxel reconstructions feasible.
\item Directly compare the spatial resolution of the (1) raw data (2) density
  after spatio-angular reconstruction (3) spatial deconvolution of data
  averaged over polarizations.
\item Continue reconstructing our existing data---the two color data in Gantt's
  cells, Bob's cells from last year, and the remainder of the helix data.
\item Draft a theory article for JOSA A or Optics Express. Working title:
  ``Spatio-angular transfer functions for fluorescence microscopes I. Basic
  theory''.
\end{itemize}

\end{document}

### 2018-08-31 notes/2018-08-31-spang-recon/figures/guv.py

@@ -1,0 +1,82 @@
+# This script demonstrates a spatio-angular reconstruction using polaris. It
+# reads files in guv-data/ and outputs summaries of the data with correction
+# factors applied (data-corrected.pdf), and the reconstructed object (recon.pdf,
+# recon.avi) to guv-recon/.
+
+from polaris import spang, phantom, data
+from polaris.micro import multi
+import numpy as np
+
+# Specify input and output
+in_folder = '/Users/Talon/local-data/2018-dispim-min/20180726_Mai_GUV/Cell1_processed/Registered/'
+out_folder = './guv-recon/'
+import os
+if not os.path.exists(out_folder):
+    os.makedirs(out_folder)
+
+# Read data and save mips
+vox_dim = (130,130,130) # nm
+data1 = data.Data(vox_dim=vox_dim, det_nas=[1.1, 0.71])
+order = np.array([[2, 1, 0, 3], [2, 3, 0, 1]])
+data1.read_tiff(in_folder, order=order)
+
+# Model for uniform distributions
+# Build microscope model
+spang1 = spang.Spang(f=np.zeros(data1.g.shape[0:3] + (15,)), vox_dim=vox_dim)
+m = multi.MultiMicroscope(spang1, data1, n_samp=1.33, lamb=525,
+                          spang_coupling=True)
+
+# Calculate expected values from fluorescent lake
+e0 = m.calc_point_H(0,0,0,0,data1.pols_norm)[0,:]
+e1 = m.calc_point_H(0,0,0,1,data1.pols_norm)[0,:]
+expected = np.vstack([e0, e1])
+
+# Measured values from fluorescent lake 
+# 561 calibration data. Values measured by hand from unifrom ROIs in
+# /Volumes/lacie-win/2018-07-30-pol-dipsim in P0-P4 order (no swaps)
+epi_cal = np.array([[8150,8550,8650,8350], [16250,16750,17000,16500]])
+ls_cal = np.array([[6050,5200,4900,5800], [9570,7350,6700,8800]])
+epi_normed = epi_cal/np.mean(epi_cal, axis=-1)[:,None]
+ls_corrected = ls_cal/epi_normed
+cal_data = ls_corrected/np.mean(ls_corrected, axis=-1)[:,None]
+cal_data[0,:] = cal_data[0,order[0,:]] # reorder
+cal_data[1,:] = cal_data[1,order[1,:]] # reorder
+
+# Apply corrections
+data1.remove_background()
[…]

### 2018-08-31 notes/2018-08-31-spang-recon/figures/helix.py

@@ -1,0 +1,59 @@
+from polaris import data, spang, phantom
+from polaris.micro import multi
+import numpy as np
+
+# Make output folder
+folder = './helix/'
+import os
+if not os.path.exists(folder):
+    os.makedirs(folder)
+
+# Generate phantom
+vox_dim = (130,130,130) # nm
+# helix phantom
+px = (64,64,64)
+phant = phantom.three_helix(vox_dim=vox_dim, px=px) 
+# bead phantom - try varying orientation and kappa
+# px = (32,32,32)
+# phant = phantom.bead(orientation=[1,0,0], kappa=30, vox_dim=vox_dim, px=px)
+
+# Calculate phantom statistics and save
+phant.calc_stats()
+# masking is necessary for fast rendering
+mask = phant.density > 0.1 
+# try "interact=True" to interact with the phantom
+# phant.visualize(folder+'phantom/', mask=mask, interact=False, video=True,
+#                 n_frames=15) 
+phant.save_stats(folder+'phantom/')
+phant.save_summary(folder+'phantom.pdf', mask=mask)
+
+# Specify microscope
+# try "det_nas = [0.8, 0.8]" for symmetric diSPIM
+data1 = data.Data(g=np.zeros(phant.f.shape[0:3]+(4,2)), vox_dim=vox_dim,
+                  det_nas=[1.1, 0.71])
+m = multi.MultiMicroscope(phant, data1, n_samp=1.33, lamb=525,
+                          spang_coupling=True)
+
+# Calculate system matrix
+m.calc_H()
+
+# Generate data using forward model
+# set "snr" to a positive number to simulate Poisson noise
+data1.g = m.fwd(phant.f, snr=None) 
+
+# Save data
+data1.save_mips(folder+'data.pdf')
+# try "diSPIM_format=False" for a 5D ImageJ hyperstack (pol = c, view = t)
+data1.save_tiff(folder+'data/', diSPIM_format=True) 
+
+# Calculate pseudoinverse solution
+# set "eta" to a positive number for Tikhonov regularization
+phant.f = m.pinv(data1.g, eta=0)
+
+# Calculate reconstruction statistics and save
+phant.calc_stats()
+mask = phant.density > 0.1
+# phant.visualize(folder+'phantom-recon/', mask=mask, interact=False, video=True,
+#                 n_frames=15)
+phant.save_stats(folder+'phantom-recon/')
+phant.save_summary(folder+'phantom-recon.pdf', mask=mask)

### 2018-08-31 notes/2018-08-31-spang-recon/figures/xylem.py

@@ -1,0 +1,82 @@
+# This script demonstrates a spatio-angular reconstruction using polaris. It
+# reads files in guv-data/ and outputs summaries of the data with correction
+# factors applied (data-corrected.pdf), and the reconstructed object (recon.pdf,
+# recon.avi) to guv-recon/.
+
+from polaris import spang, phantom, data
+from polaris.micro import multi
+import numpy as np
+
+# Specify input and output
+in_folder = '/Users/Talon/local-data/2018-dispim-min/20180725_plantCells/Cell1_processed/RegisteredSmall/'
+out_folder = './xylem-recon/'
+import os
+if not os.path.exists(out_folder):
+    os.makedirs(out_folder)
+
+# Read data and save mips
+vox_dim = (130,130,130) # nm
+data1 = data.Data(vox_dim=vox_dim, det_nas=[1.1, 0.71])
+order = np.array([[2, 1, 0, 3], [2, 3, 0, 1]])
+data1.read_tiff(in_folder, order=order)
+
+# Model for uniform distributions
+# Build microscope model
+spang1 = spang.Spang(f=np.zeros(data1.g.shape[0:3] + (15,)), vox_dim=vox_dim)
+m = multi.MultiMicroscope(spang1, data1, n_samp=1.33, lamb=525,
+                          spang_coupling=True)
+
+# Calculate expected values from fluorescent lake
+e0 = m.calc_point_H(0,0,0,0,data1.pols_norm)[0,:]
+e1 = m.calc_point_H(0,0,0,1,data1.pols_norm)[0,:]
+expected = np.vstack([e0, e1])
+
+# Measured values from fluorescent lake 
+# 561 calibration data. Values measured by hand from unifrom ROIs in
+# /Volumes/lacie-win/2018-07-30-pol-dipsim in P0-P4 order (no swaps)
+epi_cal = np.array([[8150,8550,8650,8350], [16250,16750,17000,16500]])
+ls_cal = np.array([[6050,5200,4900,5800], [9570,7350,6700,8800]])
+epi_normed = epi_cal/np.mean(epi_cal, axis=-1)[:,None]
+ls_corrected = ls_cal/epi_normed
+cal_data = ls_corrected/np.mean(ls_corrected, axis=-1)[:,None]
+cal_data[0,:] = cal_data[0,order[0,:]] # reorder
+cal_data[1,:] = cal_data[1,order[1,:]] # reorder
+
+# Apply corrections
+data1.remove_background()
[…]

### 2018-09-05 papers/basic-theory/calculations/shmult.py
Misc. updates.

@@ -72,8 +72,20 @@ def multiply_sh_coefficients(a, b):
 alpha = Symbol('alpha')
 a1 = Symbol('a1')
 a2 = Symbol('a2')
-x1 = [1 + alpha**2/4, 0, 0, 0, 0, 0, (-1 + alpha**2/2)/sqrt(5)]
-x2 = [a1 + a2*alpha**2/4, 0, 0, 0, 0, 0, (-a1 + a2*alpha**2/2)/sqrt(5)]
+x1 = [1 + alpha**2/4,
+      0, 0, 0,
+      0, 0, (-1 + alpha**2/2)/sqrt(5), 0, 0,
+      0, 0, 0, 0, 0, 0, 0,
+      0, 0, 0, 0, 0, 0, 0, 0, 0]
+x2 = [a1 + a2*alpha**2/4,
+      0, 0, 0,
+      0, 0, (-a1 + a2*alpha**2/2)/sqrt(5), 0, 0,
+      0, 0, 0, 0, 0, 0, 0,
+      0, 0, 0, 0, 0, 0, 0, 0, 0]
 xx = multiply_sh_coefficients(x1, x2)
 yy = multiply_sh_coefficients(x1, x1)
+
+y00 = simplify(expand(xx[0])) 
+y20 = simplify(expand(xx[6])) 
+y40 = simplify(expand(xx[20]))
 import pdb; pdb.set_trace() 

### 2018-09-05 polharmonic/det.py

@@ -79,6 +79,7 @@ class Detector:
             n2 = sh.SHCoeffs(n2).rotate().coeffs
 
         ax_weight = np.exp(-(z_ax**2)/(2*(self.sigma_ax**2)))
+        print(ax_weight)
         return tf.TFCoeffs([n0, n_2, n2])*ax_weight
 
     # PSF helper functions

### 2018-09-22 papers/basic-theory/paper/paper.tex
A2 typo
Misc. updates.
Paper figures and more writing.

@@
 \providecommand{\mc}[1]{\mathcal{#1}}
-\providecommand{\ro}[1]{\mathbf{\mathbf{r}}_o}
-\providecommand{\so}[1]{\mathbf{\hat{s}}_o}
-\providecommand{\rb}[1]{\mathbf{r}_b}
+\providecommand{\ro}{\mathbf{\mathbf{r}}_o}
+\providecommand{\so}{\mathbf{\hat{s}}_o}
+\providecommand{\rb}{\mathbf{r}_b}
 \providecommand{\rbm}[1]{r_b^{\text{m}}}
-\providecommand{\rd}[1]{\mathbf{r}_d}
+\providecommand{\rd}{\mathbf{r}_d}
 \providecommand{\rdf}{\mathpzc{r}_d}
@@
 \providecommand{\bs}[1]{\boldsymbol{#1}}
+\providecommand{\bv}{\bs{\nu}}
 \providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
 \providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
+\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
+\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
+\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
 \DeclareFontFamily{OT1}{pzc}{}
@@
 \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
+\usepackage{empheq}
+\newcommand{\eqname}[1]{\tag*{#1}}
+\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}
 
@@
 
-\title{Spatio-angular transfer functions for fluorescence microscopes I. Basic theory}
+\title{Spatio-angular fluorescence microscopy I. Basic theory}
 
@@
 \begin{abstract*}
-  We introduce the basic elements of a complete spatio-angular theory of
-  fluorescence microscopes. We start by analyzing a single-view fluorescence
-  microscope imaging an ensemble of in-focus dipole absorber/emitters using
-  electromagnetic optics and the paraxial approximation. Next, we define the
-  spatio-angular transfer function and show that fluorescence microscopes have
-  an angular band limit. Finally, we discuss the implications of our analysis on
-  quantitative fluorescence microscopy studies.
+  We introduce the basic elements of a spatio-angular theory of fluorescence
+  microscopy. We start by analyzing a paraxial single-view fluorescence
+  microscope imaging an ensemble of in-focus fluorophores without using the
+  monopole or scalar approximations. We define and calculate the spatio-angular
+  transfer function (SATF) and show that fluorescence microscopes have an
+  angular band limit. We demonstrate the value of the transfer function approach
+  by efficiently simulating the imaging process with numerical phantoms.
+  Notably, we show that information about the out-of-plane orientation of
+  in-focus fluorophores is imaged in paraxial widefield fluorescence
+  microscopes. We discuss the implications of our analysis for all quantitative
+  fluorescence microscopy studies.
 \end{abstract*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Fluorescence microscopes are ubiquitous tools in biology [XXX], materials
-science [XXX], and metrology [XXX] for measuring the concentration of
-fluorophores throughout a sample. While an unprocessed fluorescence micrograph
-reports the approximate concentration of fluorophores throughout a sample,
-diffraction-limited microscopes image a spatially blurred version of the true
-fluorophore distribution. Therefore, microscopists who are interested in
-accurate measurements will perform a computational restoration to recover some
-of the information lost during the imaging process.
+Fluorescence microscopes are widely used in biology [XXX], materials science
+[XXX], and metrology [XXX] for measuring the distribution of fluorophores
+throughout a sample. While an unprocessed fluorescence micrograph reports the
+approximate distribution of fluorophores throughout a sample, all microscopes
+are diffraction limited, so the image is a blurred version of the true
+fluorophore distribution. Therefore, microscopists who are interested in optimal
+measurements will perform a computational restoration to recover some of the
+information lost during the imaging process.
 
 Restoration techniques attempt to recover the true distribution of fluorophores
-using the measured data and a model of the imaging process. The model of the
+using the measured data and a model of the imaging process. A model of the
 imaging process can be obtained theoretically (by mathematically modeling the
 instrument under idealized conditions), experimentally (by measuring the
-microscope's response to a known input), or by a combination of theory and
-experiment (by measuring parameters of an instrument model). In all cases, the
-accuracy of the restored image is limited by the accuracy of the imaging model.
+instrument's response to a known input), or by a combination of theory and
+experiment (by measuring parameters of an instrument model). In all cases the
+accuracy of the restored fluorophore distribution is limited by the accuracy of
+the imaging model.
 
-Most theoretical fluorescence microscopy imaging models make simplifying
-approximations. A common (often unstated) pair of approximations is to (1) treat
-fluorophores as monopole absorber/emitters and (2) treat light propagation under
-the scalar approximation. In this work we will analyze fluorescence microscopes
-without these approximations and find the conditions under which these
-approximations are valid.
+All theoretical imaging models of make simplifying approximations that limit the
+accuracy of restorations, so it is important to verify that the approximations
+introduce an acceptable level of error. This work investigates the errors
+introduced by two common approximations in models of fluorescence
+microscopes---the \textit{monopole approximation} and the \textit{scalar
+  approximation}.
 
-Using an experimentally determined model is an effective way to find an accurate
-model without understanding all of the physical details of the imaging system,
-but these approaches require a known input that can completely characterize the
-imaging system. Sub-diffraction beads are commonly used as a known input for
-measuring the response of a microscope, but we argue that sub-diffraction beads
-are not enough to completely characterize the response of a microscope to all
-fluorescent samples. Beads can only characterize the response of the microscope
-to an angularly uniform distribution of fluorophores, and we will show that all
-microscopes have an orientation-dependent response. A complete characterization
-requires a test sample with at least three known orientation distributions.
+by ignoring the
+dipole excitation and emission processes and to (2) treat light propagation
+under the \textit{scalar approximation} by ignoring the polarization of light.
+These approximations can limit the accuracy of restoration in all types of
+fluorescence microscopes. The goal of this work is to analyze fluorescence
+microscopes without these approximations and find the conditions under which
+these approximations are justified.
 
-The single-molecule localization microscopy (SMLM) community has pioneered the
-use of rigorous electromagnetic models of single fluorescence microscopes
-\cite{backer2014, lieb2004}. When only one fluorophore is emitting at a time,
-the measured intensity pattern is strongly dependent on the orientation of the
-emitting molecule. Backlund and Lew \cite{backlund2014} have shown that ignoring
-the orientation of fluorophores can lead to biased estimates of their position,
-so the most accurate SMLM experiments must jointly estimate the position and
-orientation of the molecule. These joint estimates usually use a set of
-precomputed intensity patterns and a maximum-likelihood algorithm to estimate
-the orientation and position of each molecule. These methods have led to some of
-the most accurate position estimates of single molecules.
+This work lies at the intersection of three classes of fluorescence microscopy:
+(1) single-molecule localization microscopy (SMLM), (2) spatial ensemble
+fluorescence microscopy including widefield, confocal, and light-sheet
+techniques, and (3) polarized fluorescence microscopy. We briefly review these
+three classes and focus on their use of the monopole and scalar approximations.
 
-Meanwhile, most fluorescence microscopists image ensembles of fluorophores.
-Although many groups have used polarizers to probe the orientation of ensembles
-of fluorophores \cite{mehta2016} [Forkey], to our knowledge no
-work has been done on the response of fluorescence microscopes to ensembles of
-oriented fluorophores. Furthermore, current restoration techniques in polarized
-light microscopy are lacking because they rely on simple pixel-wise arithmetic
-and do not model the propagation of light through the microscope.
+The SMLM community has pioneered the use of rigorous electromagnetic models of
+fluorescence microscopes \cite{backer2014, lieb2004} [Novotny]. When a single
+molecule is fluorescing in the sample, the measured intensity pattern is
+strongly dependent on the orientation of the emitting molecule. Backlund and Lew
+\cite{backlund2014} have shown that ignoring the orientation of fluorophores can
+bias position estimates. Therefore, the most accurate SMLM experiments must
+jointly estimate the position and orientation of each molecule.
+
+A major limitation of SMLM experiments is speed
+
+Meanwhile, most fluorescence microscopists image ensembles of fluorophores and
+restore their images without considering the role that the monopole and scalar
+approximations play in the restoration process. A typical fluorescence
+microscopist is only interested in the spatial distribution of fluorophores, so
+they reason (possibly erroneously) that they can ignore the orientation of the
+emitters.
+
+A smaller community of microscopists is interested in measuring the orientation
+of ensembles of fluorophores \cite{mehta2016} [Forkey, Goldman, Moerner].
+These techniques typically use a combination of 
+Current restoration techniques use a model of the dipole excitation and emission
+process to restore the orientation of fluorophores using pixel-wise arithmetic,
+but these techniques do not perform any spatial restoration so they are
+sub-optimal. To our knowledge no work has been done to model the complete
+spatio-angular response of fluorescence microscopes to ensembles of oriented
+fluorophores.
 
 In this work we model ensembles of in-focus dipole absorber/emitters using
-electromagnetic optics and the paraxial approximation. This marks a first step
-towards a complete three-dimensional non-paraxial theory of fluorescence
-microscopes. In section 2 we model the excitation and detection processes of
-dipoles. We define the most important quantity in this work, the spatio-angular
-transfer function, and we use it to show that fluorescence microscopes have an
-angular band limit. In section 3 we perform simulations and compare our model to
-traditional scalar models. In section 4 we discuss the implications of our work
-for fluorescence microscopy and lay out a path towards a complete spatio-angular
+electromagnetic optics and the paraxial approximation. In section 2 we model the
+excitation and detection processes of dipoles, and we define the most important
+quantity in this work---the spatio-angular transfer function (SATF). We
+calculate the SATF and show that fluorescence microscopes have an angular band
+limit. In section 3 we perform simulations and compare our model to traditional
+scalar models. In section 4 we discuss the implications of our work for
+fluorescence microscopy and lay out a path towards a complete spatio-angular
 theory of fluorescence microscopy.
@@
 \section{Theory}
-\subsection{Spherical harmonics}\label{sec:sph}
+Consider a single dipole radiator at the origin with its dipole moment oriented
+along a direction $\so$. The dipole emitter creates a time-harmonic electric
+field at a position $\mb{r}$ far from the dipole proportional to
 \begin{align}
-  y_l^m(\vartheta, \varphi) =
+  \mb{E}_{\text{ff}}(\mb{r}, \so) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}\, \mh{r}\times\so\times\mh{r}.\label{eq:dip}
+\end{align}
+A typical approach to deriving Equation \ref{eq:dip} is to (1) use Maxwell's
+equations to derive the inhomogeneous electromagnetic wave equations then (2)
+use potentials to solve the wave equations with a dipole source term, then (3)
+drop the terms that decay faster than $1/|\mb{r}|$---see Jackson, Novotny, Teich
+for clear expositions. Equation~\ref{eq:dip} succinctly shows that dipole
+radiators emit spherical wavefronts of polarized light with amplitude
+proportional to $\cos\theta$ where $\theta$ is the angle between the field point
+$\mb{r}$ and the dipole axis $\so$.
+
+Many models of fluorophores approximate the vector field on the left hand side
+of Equation \ref{eq:dip} with a scalar field---the \textit{scalar
+  approximation}---and drop the orientation dependence on the right hand
+side---the \textit{monopole approximation}. The approximated field is given by
+\begin{align}
+  U_{\text{ff}}(\mb{r}) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}. \label{eq:mono}
+\end{align}
+Models that use Equation \ref{eq:mono} as a starting point do not account for
+polarization or dipole orientation effects. In Section \ref{sec:monopole} we
+will review the derivation of the monopole imaging model starting with Equation
+\ref{eq:mono}. These results are widely known, but they serve as a review of the
+concepts we will need for the dipole imaging case. In Section \ref{sec:dipole}
+will derive a dipole imaging model starting with Equation \ref{eq:dip}. Finally,
+in Section \ref{sec:trans} we will calculate the SATF for the dipole imaging
+model.
+
+\subsection{Monopole imaging model}\label{sec:monopole}
+We briefly analyze a paraxial 4$f$ fluorescence imaging system using the
+monopole and scalar approximations---a similar treatment can be found in
+\cite{goodman1996}. We start by considering a field of in-focus monopoles that
+have been excited by a spatially uniform beam. As the fluorophores relax, they
+emit scalar waves in the form of Equation \ref{eq:mono}. The waves propagate
+through the microscope and we measure the irradiance on a two dimensional
+detector.
+
+We can represent the object as a two-dimensional function $f(\ro)$ that we call
+the \textit{monopole density}---the number of monopoles at position $\ro$ per
+unit area. In the language of image science, we say that $f(\ro)$ is a member of
+the set of square integrable functions on the plane $\mbb{L}_2(\mbb{R}^2)$. The
+data we collect is the irradiance on a plane $g(\rd)$, so the data is a member
+of the same set $\mbb{L}_2(\mbb{R}^2)$.
+
+A reasonable starting point is to assume that the relationship between the
+object and the data is \textit{linear}---this seems plausibly since a scaled sum
+of monopoles will result in a scaled sum of the irradiance patterns created by
+the individual monopoles. Therefore, we can write the irradiance as the integral
+over a field of monopoles weighted by the detector response due to single
+monopoles
+\begin{empheq}[box=\widefbox]{gather}
+g(\rd{}) = \int_{\mbb{R}^2}d\ro{}\, h(\rd{}, \ro{})f(\ro{}). \label{eq:fwdmono} \\ \text{Monopole imaging model} \nonumber 
+\end{empheq}
+where $h(\rd{}, \ro{})$ is the kernel of the integral transform.
+
+The first step is to calculate the field in the back focal plane of the
+objective lens. We can model a paraxial thin lens as a quadratic phase element,
+so it converts a spherical wave to a plane wave in the back focal plane with a
+sharp cutoff at the exit pupil of the lens
+\begin{align}
+  U_{\text{bfp}}(\mb{r}_b) \propto \Pi\left(\frac{|\mb{r}_b|}{\alpha}\right) \equiv
   \begin{cases}
-    \sqrt{2}K_l^m\cos(m\varphi)P_l^m(\cos\vartheta), & m > 0\\
-    K_l^0P_l^0(\cos\vartheta), & m = 0\\
-    \sqrt{2}K_l^m\sin(-m\varphi)P_l^{-m}(\cos\vartheta), & m < 0\\
+    1\quad \text{if}\quad |\mb{r}_b| < \alpha,\\
+    0\quad \text{else}.
   \end{cases}
 \end{align}
-where
+A central result of Fourier optics is that the fields one focal distance from
+either side of a paraxial lens are related by a scaled two-dimensional Fourier
+transform. If we place a detector in the focal plane of the tube lens then the
+field on the detector is given by
 \begin{align}
-  K_l^m = \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-|m|)!}{(l+|m|)!}},
+  U_{\text{det}}(\mb{r}_d) \propto \mc{F}_{\mbb{R}^2}\left\{U_{\text{bfp}}(\mb{r}_b)\right\} = \frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}.
 \end{align}
-and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0, 1, 2$
-spherical harmonics are given by
+Finally, the detector measures the irradiance instead of the field, so we take
+the modulus squared of the field to find that the measurable image of a single
+monopole radiator at the origin is the familiar Airy disk
 \begin{align}
-  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}}, \nonumber \\ 
-  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta, \nonumber \\
-  y_2^{-2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\cos\varphi\sin^2\vartheta, &\hspace{2em} y_2^{-1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\sin\vartheta\cos\vartheta,\nonumber \\
-  y_2^0(\vartheta, \varphi) &= \sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1), \nonumber \\ 
-  y_2^{1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\cos\varphi\sin\vartheta\cos\vartheta, &\hspace{2em} y_2^{2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}(\cos^2\varphi - \sin^2\varphi)\sin^2\vartheta.\label{eq:harmonics}
+  h(\mb{r}_d, \ro = 0) \propto |U_{\text{det}}(\mb{r}_d)|^2 = \left[\frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}\right]^2.
+\end{align}
+Shifting the monopole in the transverse plane will introduce a linear phase
+factor in the back focal plane which will manifest as a shift on the detector.
+Therefore, our imaging system is shift invariant and we can rewrite the
+irradiance on the detector due to a monopole at $\ro$ as
+\begin{align}
+  h(\rd, \ro) = h(\rd - \ro). \label{eq:shift}
+\end{align}
+For convenience we have used the same letter for both functions in Equation
+\ref{eq:shift} even though they have a different number of variables. We will
+continue to rewrite functions with fewer variables in the same way throughout
+this paper. Also, Equation \ref{eq:shift} only applies directly to microscopes
+with unit magnification, but a similar relationship can be found for magnifying
+microscopes by making a change of variables---see Barrett section 7.2.7.
+
+Rotating a monopole will leave its image unchanged. Therefore, our imaging
+system is rotation invariant and we can simplify the kernel further with
+\begin{align}
+  h(\rd - \ro) = h(|\rd - \ro|). \label{eq:rotational}
 \end{align}
 
-\subsection{Excitation model}
-% [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
-In this section we will calculate the excitation kernel for epi-illumination
-microscopes---the relative probability of exciting a molecule with a known
-orientation. Our approach is similar to previous work \cite{fourkas2001,  chandler2017},
-but here we consider unpolarized illumination and restrict
-ourselves to the paraxial approximation.
+In the language of image science, Equation \ref{eq:fwdmono} specifies an
+integral transform relationship between objects that are members of the space of
+square-integrable functions on the plane $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$ and
+data that lives in the same space $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$. We can
+rewrite Equation \ref{eq:fwdmono} more abstractly as
+\begin{align}
+  \mb{g} = \mc{H}\mb{f} \label{eq:abstract}
+\end{align}
+where $\mc{H}: \mbb{L}_2(\mbb{R}^2) \rightarrow \mbb{L}_2(\mbb{R}^2)$ is the
+forward operator of the imaging system. We say that the shift invariance and
+rotational invariance introduced in Equations \ref{eq:shift} and
+\ref{eq:rotational} are \textit{symmetries of the forward operator}. Specifying
+a linear operator that maps $\mbb{L}_2(\mbb{R}^2)$ to $\mbb{L}_2(\mbb{R}^2)$
+always requires us to specify a kernel in the set $\mbb{L}_2(\mbb{R}^4)$, but we
+can exploit the symmetries of the forward operator to specify the complete
+kernel with a ``smaller'' function in the set $\mbb{L}_2(\mbb{R})$.
 
-We consider a single molecule with a fixed absorption dipole moment $\so{}$ that
-we express in spherical coordinates [see Fig. 1(a)] as 
+Just as a finite-dimensional linear operator can be represented by a matrix in a
+specific basis, the infinite-dimensional linear operator in Equation
+\ref{eq:abstract} can be represented by an integral transform in a specific
+basis. Equation \ref{eq:fwdmono} is an integral transform representation of the
+monopole imaging process in a \textit{spatial basis} with basis functions of the
+form $\delta(\mb{r} - \ro)$, but this is not always the best choice. We can
+exploit the shift-invariance of the forward operator by choosing basis functions
+of the form $\text{exp}[i2\pi \mb{r}\cdot\bs{\nu}]$ and use the Fourier
+transform to reexpress the monopole imaging model in a \textit{spatial-frequency
+  basis} as
+\begin{align}
+  G(\bs{\nu}) = H(\bs{\nu})F(\bs{\nu})\label{eq:freq}
+\end{align}
+where $\bs{\nu}$ is a two-dimensional spatial frequency, $G(\bs{\nu})$ is the
+spectrum of the irradiance, $F(\bs{\nu})$ is the spectrum of the monopole
+density, and $H(\bs{\nu})$ is the two-dimensional optical transfer function.
+Because the fast Fourier transform provides an efficient method to change
+between the spatial and spatial-frequency bases, Equation \ref{eq:freq} provides
+a computational advantage over Equation \ref{eq:fwdmono} because we only need to
+multiply two functions in $\mbb{L}_2(\mbb{R}^2)$.
+
+The optical transfer function above exploits shift invariance but does not
+exploit rotational invariance. We can define a similar transfer function that
+exploits both shift and rotational invariance by choosing the same Fourier basis
+(see Barrett 7.2.9 for related discussion) and express the transfer function
+as a member of the set $\mbb{L}_2(\mbb{R})$
+\begin{align}
+  G(\bs{\nu}) = H(|\bs{\nu}|)F(\bs{\nu}).\label{eq:freq2}
+\end{align}
+% Again, we have used the same letter symbol $H$ in Equations \ref{eq:freq} and
+% \ref{eq:freq2} to denote a function with two real variables and one real
+% variable, respectively.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=.9]{../figures/detection-coords/detection-coords.pdf}
+   \caption{Detection geometry and coordinates.}
+   \label{fig:mono}
+ \end{figure}
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=.9]{../figures/excitation-coords/excitation-coords.pdf}
+   \caption{Illumination geometry and coordinates.}
+   \label{fig:microscope}
+ \end{figure}
+
+\subsection{Dipole imaging model}\label{sec:dipole}
+We seek to extend the monopole imaging model to dipoles. Comparing Equations
+\ref{eq:dip} and \ref{eq:mono} shows that we will need to consider the
+orientation of the dipole radiators. We also notice that both monopoles and
+dipoles emit spherical wavefronts, so our argument for shift invariance in the
+monopole imaging model holds for the dipole imaging model as well. Finally, it
+is reasonable to assume that rotational invariance will be maintained under the
+paraxial approximation. Therefore, we can plausibly extend the monopole imaging
+model in Equation \ref{eq:fwdmono} to dipoles with
+\begin{empheq}[box=\widefbox]{gather}
+g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{}, \ro{}, \so{})f(\ro, \so). \label{eq:fwddip}\\ \text{Dipole imaging model}\nonumber 
+\end{empheq}
+where $f(\ro, \so)$ is the \textit{spatio-angular density}---the number of
+dipoles at position $\ro{}$ per unit area oriented along $\so{}$ per unit solid
+angle---and $\mbb{S}^2$ is the unit sphere. Notice that the functional form of
+our data is left unchanged $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$ while we have
+extended the set of possible objects to
+$\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$. Similar to the monopole case,
+the most general linear operator mapping between these two spaces would require
+a kernel in $\mbb{L}_2(\mbb{R}^4\times\mbb{S}^2)$, but we can exploit symmetries
+and specify the complete kernel with a function in
+$\mbb{L}_2(\mbb{R}\times\mbb{S}^2)$.
+
+At this point we have only asserted the plausibility of Equation
+\ref{eq:fwddip}---we still need to calculate the form of the kernel
+$h(r, \so{})$. Our first step is to notice that the kernel can be separated into
+the product of an excitation part and a detection part
+\begin{align}
+  h(r, \so) = h_{\text{exc}}(\so)\,h_{\text{det}}(r, \so). \label{eq:kernelsep}
+\end{align}
+In the next two subsections we will calculate the excitation and detection
+kernels explicitly.
+
+\subsubsection{Dipole excitation model}
+When we developed the monopole imaging model we ignored the excitation process
+because we excited the fluorophores with a spatially uniform excitation beam and
+monopoles have no orientation dependence. For the dipole imaging model we must
+account for the excitation process because the excitation process is not
+angularly uniform (except for carefully calibrated TIRF systems).
+
+In this section we will calculate the excitation kernel $h_{\text{exc}}(\so)$
+for epi-illuminationn microscopes. We can interpret $h_{\text{exc}}(\so)$ as the
+relative probability of exciting a molecule with dipole orientation $\so$. Our
+approach is similar to previous work \cite{fourkas2001, chandler2017}, but here
+we consider unpolarized and incoherent illumination and restrict ourselves to
+the paraxial approximation.
+
+We start by expressing the dipole moment $\so{}$ in spherical coordinates [see
+Fig. 1(a)] as
 \begin{align}
@@
 We can rewrite Eq. \ref{eq:spherical} in terms of spherical harmonic functions
-(see Section \ref{sec:sph}) as
+(see Appendix \ref{sec:sph}) as
 \begin{align}
@@
 \end{align}
-We place the molecule in the focal plane of an aplanatic and
+We place the dipole in the focal plane of an aplanatic and
 polarization-preserving objective lens with its optical axis aligned with the
@@
 where $\phi_{\text{pol}}$ is the polarization orientation and \{$\mh{x}$,
-$\mh{y}$\} are transverse Cartesian basis vectors. Notice that Eq. \ref{eq:bfp0}
-describes the incoherent electric fields at every point in the back focal plane,
-it does not describe a coherent plane wave. Immediately after the lens the
-electric field is
+$\mh{y}$\} are transverse Cartesian basis vectors. Note that Eq. \ref{eq:bfp0}
+describes the incoherent electric fields at every point in the back focal
+plane--- it does not describe a coherent plane wave. Immediately after the lens
+the electric field is
 \begin{align}
@@
 models the rotation of p-polarized fields, and the $\sqrt{\cos\theta}$ term
-models the apodization of an aplanatic lens. After plugging Eq. \ref{eq:bfp0}
-and Eqs. \ref{eq:rho}--\ref{eq:theta} into Eq. \ref{eq:bfp2ff} and applying the
+models the apodization of an aplanatic lens. After plugging Eqs. \ref{eq:bfp0}, \ref{eq:rho}, \ref{eq:phi}, and \ref{eq:theta} into Eq. \ref{eq:bfp2ff} and applying the
 paraxial approximation, the electric field immediately after the lens is given
@@
 \end{align}
-To calculate the probability that a dipole oriented along $\so{}$ is excited by
-a ray with electric field $\mb{E}$ we need to evaluate $|\mb{E}\cdot\so{}|^2$.
-Evaluating this expression for each ray would be cumbersome if we used Eqs.
-\ref{eq:spherical} and \ref{eq:eff} because we would need to simplify a large
-number of trigonometric functions. Instead, we use Eqs. \ref{eq:sphharm} and
-\ref{eq:eff} and the real Gaunt coefficients [XXXciteXXX] to find the products
-of spherical harmonics. We find that
+The probability that a dipole oriented along $\so{}$ is excited by a ray with
+electric field $\mb{E}$ is given by $|\mb{E}\cdot\so{}|^2$. Evaluating this
+expression for each ray would be cumbersome if we used Eqs. \ref{eq:spherical}
+and \ref{eq:eff} because we would need to simplify a large number of
+trigonometric functions. Instead, we use Eqs. \ref{eq:sphharm} and \ref{eq:eff}
+and use the real Gaunt coefficients (see Appendix A) to evaluate the products of
+spherical harmonics. We find that
 % [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
@@
 \end{align}
-To calculate the complete excitation model we need to integrate Eq.
+To find the complete excitation kernel we need to integrate Eq.
 \ref{eq:integrand} over all polarization orientations and rays
 \begin{align}
-  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}^{(p)} \cdot \so{}|^2. \label{eq:integral}
+  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}^{(p)} \cdot \so{}|^2, \label{eq:integral}
 \end{align}
+where $\alpha$ is the maximum angle the illumination rays make with the optical
+axis ($\alpha$ is equivalent to the numerical aperture in the paraxial
+approximation).
+
 After plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral} and evaluating
-the integrals, all but two terms disappear and the orientation-dependent
-excitation model is given by
+the integrals, all but two terms disappear and the 
+excitation kernel is given by
 \begin{align}
@@
 \end{align}
-We note that the excitation model depends on the orientation of the molecule,
+We note that the excitation kernel depends on the orientation of the molecule,
 but it does not depend on the position of the molecule in the focal plane. This
@@
 
-\subsection{Detection model}
+Equation \ref{eq:excitation} only contains $m = 0$ spherical harmonics, so it
+can be written as a function of $\vartheta$ only. After plugging in the
+spherical harmonic functions and simplifying we see that 
+\begin{align}
+  h_{\text{exc}}(\vartheta) &\propto \sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta \label{eq:hexctheta}
+\end{align}
+
+Equation \ref{eq:excitation} shows the probability of excitation as a function
+of dipole orientation and numerical aperture.
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.95]{../figures/excitation/excitation.pdf}
+   \caption{Caption.}
+   \label{fig:microscope}
+ \end{figure}
+
+\subsubsection{Dipole detection model}
 In this section we will calculate the detection kernel of an epi-detection
 microscope---the irradiance on the detector due to single molecule at a known
-position with known orientation. Our approach is similar to \cite{backer2014,
-  nov2006, agrawal2012}, but here we restrict ourselves to the paraxial
-approximation.
+position with known orientation. Our approach mimics existing work
+\cite{backer2014, nov2006, agrawal2012}, but we restrict ourselves to the
+paraxial approximation.
 
 We consider a single dipole emitter at the origin with a fixed dipole emission
-moment oriented along $\so{}$---parallel to the excitation moment. The electric
-field at a position $\mb{r}$ far from the dipole is given by
+moment oriented along $\so{}$. The electric field at a position $\mb{r}$ far
+from the dipole is given by
 \begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \frac{\text{exp}[ik|\mh{r}|]}{|\mh{r}|}\mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
 \end{align}
+We place the dipole in the focal plane of the same 4$f$ imaging system we
+considered in the monopole case---see Figure \ref{fig:monopole}. The dipole
+emits spherical wavefronts so we can reuse our argument for shift invariance in
+the monopole section and drop the phase dependence while keeping in mind that
+$h_{\text{det}}(\rd, \ro, \so) = h_{\text{det}}(\rd - \ro, \so)$.
+\begin{align}
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) &\propto [\mb{I} - \mh{r}\mh{r}^{\dagger}]\so \\
+\end{align}
+\begin{align}
+  \mh{r}(\theta,\phi) \approx \theta\cos\phi\mh{x} + \theta\sin\phi\mh{y} + \mh{z}
+\end{align}
+\begin{align}
+  \mb{E}_{\text{ff}}(\theta, \phi, \so{}) &\propto 
+  \begin{bmatrix}
+    1 & 0 &-\theta \cos\phi\\
+    0 & 1 &-\theta \sin\phi\\
+    -\theta\cos\phi&-\theta \sin(\phi)&0    
+  \end{bmatrix}\so
+\end{align}
+\begin{align}
+  \mb{R}_{\text{obj}}(\theta, \phi) &=
+  \begin{bmatrix}
+    1 & 0 &-\theta \cos\phi\\
+    0 & 1 &-\theta \sin\phi\\
+    -\theta\cos\phi&-\theta \sin(\phi)&1    
+  \end{bmatrix}
+\end{align}
+
 If we place the molecule in the focal plane of an aplanatic and
@@
 \begin{align}
-  \mb{E}_{\text{bfp}}(\rb{}, \so{}) \propto \left\{[\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\phi}]\,\bsh{\phi} + [\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\theta}]\,\bsh{\rho}\right\}\sqrt{1/\cos\theta}\,\Pi\left(\frac{r_b}{\sin\alpha}\right).
-\label{eq:bfp}
+  \mb{E}_{\text{bfp}}(\theta, \phi, \so) &\propto \mb{R}_{\text{obj}}(\theta,\phi)\mb{E}_{\text{ff}}(\theta, \phi, \so)
 \end{align}
-where the first term accounts for s-polarized fields, the second term accounts
-for p-polarized fields, $\sqrt{1/\cos\theta}$ is the apodization factor for an
-aplanatic lens, and
+Finally, we change from spherical coordinates to cylindrical coordinates by
+substituting $(r_b, \phi_b)$ for $(\theta, \phi)$ and we get
 \begin{align}
-  \Pi\left(\frac{r_b}{\sin\alpha}\right) =
-  \begin{cases}
-    1\quad \text{if}\quad r_b < \sin^{-1}\alpha,\\
-    0\quad \text{else},
-  \end{cases}
-\end{align}
-is the aperture stop. After expanding the dot products, applying the paraxial
-approximation, and writing the dipole orientation $\so{}$ in terms of spherical
-harmonic functions, we find that the electric field in the back focal plane is
-given by
-\begin{align}
-  \mb{E}_{\text{bfp}}^{(p)}(\rb{}, \so{}) \propto \left\{\left[y_1^1(\so{}) - r_b\cos\phi_b y_1^0(\so{})\right]\mh{x} + \left[y_1^{-1}(\so{}) - r_b\sin\phi_b y_1^0(\so{})\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right).
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{\left[s_x - s_zr_b\cos\phi_b\right]\mh{x} + \left[s_y - s_z r_b\sin\phi_b\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right).
 \label{eq:bfp2}
 \end{align}
+\begin{align}
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} + s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp3}
+\end{align}
+
 We note that Eq. \ref{eq:bfp2} is identical to previously derived models
@@
 \end{align}
+Similar to the excitation kernel, we can write the excitation kernel purely in terms of
+the inclination angle
+\begin{align}
+  h_{\text{det}}(r_d, \vartheta) &\propto a_1(r_d)\sin^2\vartheta + \frac{1}{2}\alpha^2a_2(r_d)\cos^2(\vartheta). 
+\end{align}
 
@@
 
-\subsection{Complete forward model}
-In the last two section we have found closed-form expressions for the excitation
-kernel $h_{\text{exc}}(\so{})$ and the detection kernel
-$h_{\text{det}}(\rd{} - \ro{}, \so{})$. The complete kernel of the microscope is
-the product of the excitation and detection kernels
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
+   \caption{Comparison of paraxial detection models for monopole radiators a)
+     and dipole radiators b)--d). Monopole radiators fill the back focal plane
+     with a uniform scalar field which gives rise to the familiar Airy disk on
+     the detector. A transverse dipole radiator also creates an Airy disk---the
+     back focal plane is filled with a uniform vector field. An axial dipole
+     radiator creates a radial electric field pattern in the back focal plane
+     which gives rise to a higher-order Airy disk. Back focal plane electric
+     fields from transverse dipoles are purely even while fields from axial
+     dipoles are purely odd which causes a relative $\pi/2$ phase shift for the
+     fields on the detector. The back focal plane fields from an
+     arbitrarily-oriented dipole can be decomposed into even and odd fields, so
+     the final intensity pattern is always radially symmetric.}
+   \label{fig:microscope}
+ \end{figure}
+
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/detection/detection.pdf}
+   \caption{Normalized detection kernel as a function of the scaled radial
+     detection coordinate $k\alpha r_d$, the dipole inclination angle
+     $\vartheta$, and the collection angle $\alpha$. For small collection angles
+     (left) the detection kernel of axial dipoles
+     (\textcolor{red}{\textbf{red}}) is small compared to transverse dipoles
+     (\textbf{black}), but the relative contribution of axial dipoles increases
+     with the collection angle (see \textcolor{red}{\textbf{red}} lines from left to right).}
+   \label{fig:microscope}
+ \end{figure}
+
+ \subsection{Spatio-angular transfer function}\label{sec:trans}
  \begin{align}
-  h(\rd{} - \ro{}, \so{}) = h_{\text{exc}}(\so{})h_{\text{det}}(\rd{} - \ro{}, \so{}). \label{eq:kernel}
-\end{align}
-Eq. \ref{eq:kernel} gives the irradiance at position $\rd{}$ on the detector
-created by a single dipole at position $\ro{}$ with dipole oriented along
-$\so{}$.
-
-Up to this point we have only modeled the imaging system's response to single
-fluorescent molecules. We would like to model samples that contain ensembles of
-fluorescent molecules with many fluorescent molecules, so we introduce the
-\textit{spatio-angular density} to describe arbitrary distributions of
-fluorescent dipoles. We define the spatio-angular density $f(\ro{}, \so{})$ as
-the number of fluorescent molecules at position $\ro{}$ per unit volume oriented
-along $\so{}$ per unit solid angle. Figure TODO illustrates several simple
-spatio-angular densities to clarify our definition.
-
-The detector irradiance $g(\rd{})$ created by an arbitrary spatio-angular
-density $f(\ro{}, \so{})$ can be found by multiplying the spatio-angular density
-by the kernel and integrating over all positions $\ro{}$ and orientations
-$\so{}$
-\begin{align}
-g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro{}, \so{}). \label{eq:fwd}
+g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(|\rd{} -\ro{}|, \so{})f(\ro, \so).
  \end{align}
 
-\subsection{Spatio-angular transfer function}
+ \begin{align}
+   g(\rd{}) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\int_{\mbb{S}^2}d\so{}\, \mc{F}_{\mbb{R}^2}\left\{h(|\rd{} -\ro{}|, \so{})\right\}\mc{F}_{\mbb{R}^2}\left\{f(\ro, \so)\right\}\right\}.
+ \end{align}
+\begin{align}
+  \ints{2}d\mh{s}{}\, f(\mh{s})g(\mh{s}) = \lmsum \mc{F}_{\mbb{S}^2}\left\{f(\mh{s})\right\}\mc{F}_{\mbb{S}^2}\left\{g(\mh{s})\right\}, \label{eq:plan}
+\end{align}
+where
+\begin{align}
+  \mc{F}_{\mbb{S}^2}\left\{f(\mh{s})\right\} \equiv \int_{\mbb{S}^2}f(\mh{s})y_l^m(\mh{s}).
+\end{align}
+Eq. \ref{eq:plan} is the generalized Plancharel theorem for spherical functions.
+It is a special case of the fact that scalar products are invariant under
+unitary transformations (see Barrett 3.78). Next, we plug Eq. \ref{eq:plan}
+into Eq. \ref{eq:filter1} to get
+\begin{align}
+  g(\rd) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\lmsum H_{l}^m(\bv, \mh{p}) \mc{F}_{\mbb{R}^2\times\mbb{S}^2}\left\{f(\ro, \so)\right\}\right\} \label{eq:filter}
+\end{align}
+where
+\begin{align}
+  H_{l}^m(\bv) \equiv \mc{F}_{\mbb{R}^2\times\mbb{S}^2}\left\{h(|\rd - \ro|, \so)\right\} &\equiv \intr{3}d\ro\, \me^{i2\pi\ro\cdot\bv}\ints{2}d\so\, y_l^m(\so) h(\ro, \so).\label{eq:transfer}
+\end{align}
+Eq. \ref{eq:filter} is the main result of this section. Right now it is not
+obvious that Eq. \ref{eq:filter} is any more efficient than Eq.
+\ref{eq:filter1}, but when we calculate the transfer function we will see that
+the sum over spherical harmonics contains a small number of terms.
+
 As written Eq. \ref{eq:fwd} is an extremely expensive integral to compute---to
@@
 \begin{align}
-  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\},
+  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l2}\delta_{m0}\nonumber\\&\frac{1}{7}\left[\left(1 - \frac{\alpha^2}{2}\right)A_1(\nu) + \left(-\frac{\alpha^2}{2} + \frac{\alpha^4}{4}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\},
 \end{align}
@@
   A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right), \\
-  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right),
+  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right),
 \end{align}
@@
 \section{Discussion and conclusion}
+Do microscopes transmit more information than Abbe thought?
+
+Using an experimentally determined model is an effective way to find an accurate
+model without understanding all of the physical details of the imaging system,
+but these approaches require a known input that can completely characterize the
+imaging system. Sub-diffraction beads are commonly used as a known input for
+measuring the response of a microscope, but we argue that sub-diffraction beads
+are not enough to completely characterize the response of a microscope to all
+fluorescent samples. Beads can only characterize the response of the microscope
+to an angularly uniform distribution of fluorophores, and we will show that all
+microscopes have an orientation-dependent response. A complete characterization
+requires a test sample with at least three known orientation distributions.
+
+Can experimentally measured psfs account for this?
 
@@
 \appendix
+\section{Spherical harmonics}\label{sec:sph}
+The spherical harmonics are a basis for representing functions on the sphere. In
+this appendix we will define the basis and review several important properties
+of this set of functions.
+
+The complex-valued spherical harmonics are given by
+\begin{align}
+Y_l^m(\vartheta, \varphi) = \sqrt{\frac{(2l+1)(l-m)!}{4\pi(l+m)!}}\exp(i m \varphi)P_l^m\left(\cos\theta\right)
+\end{align}
+where $P_l^m(\cos\theta)$ are the associated Legendre polynomials that include
+the Condon-Shortley phase. In this work we only use the spherical harmonics to
+represent real-valued functions so we use the real spherical harmonics given by
+\begin{align}
+  y_l^m(\vartheta, \varphi)
+  \begin{cases}
+    \frac{Y_l^m(\vartheta, \varphi) + (-1)^m Y_l^{-m}(\vartheta, \varphi)}{\sqrt{2}} &\quad m > 0, \\
+    Y_l^m(\vartheta, \varphi) &\quad m = 0, \\
+    \frac{Y_l^m(\vartheta, \varphi) - (-1)^m Y_l^{-m}(\vartheta, \varphi)}{i \sqrt{2}} &\quad m < 0.\\
+        \end{cases}
+\end{align}
+
+The $l=0, 1, 2$ spherical harmonics are given by
+\begin{align}
+  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}}, \nonumber \\ 
+  y_1^{-1}(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \nonumber\\
+  y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \nonumber \\
+  y_1^1(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta, \nonumber \\
+  y_2^{-2}(\vartheta, \varphi) &= \sqrt{\frac{15}{4\pi}}\sin\varphi\cos\varphi\sin^2\vartheta, \nonumber\\
+  y_2^{-1}(\vartheta, \varphi) &= \sqrt{\frac{15}{4\pi}}\sin\varphi\sin\vartheta\cos\vartheta,\nonumber \\
+  y_2^0(\vartheta, \varphi) &= \sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1), \nonumber \\ 
+  y_2^{1}(\vartheta, \varphi) &= \sqrt{\frac{15}{4\pi}}\cos\varphi\sin\vartheta\cos\vartheta, \nonumber \\
+  y_2^{2}(\vartheta, \varphi) &= \sqrt{\frac{15}{16\pi}}(\cos^2\varphi - \sin^2\varphi)\sin^2\vartheta. \label{eq:harmonics}
+\end{align}
+
+Real Gaunt coefficients
+
 \section{Evaluating the spatio-angular transfer function}
@@
 \begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\frac{3}{5}A_1(\nu) + \frac{3\alpha^2}{40}[A_1(\nu) + A_2(\nu)] + \frac{9\alpha^4}{160}A_2(\nu)\right]y_0^0(\so{})+\nonumber\\&\frac{3\sqrt{5}}{280}\left[-16A_1(\nu) + \alpha^2[A_1(\nu) + A_2(\nu)] + 3\alpha^4 A_2(\nu)\right]y_4^0(\so{})\Bigg\},\\                             H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]y_0^0(\so{}) + \nonumber\\&\frac{\sqrt{5}}{56}\left[(-16 + \alpha^2)A_1(\nu) + (\alpha^2 + 3\alpha^4)A_2(\nu)\right]y_4^0(\so{})\Bigg\}.
+  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\frac{3}{5}A_1(\nu) + \frac{3\alpha^2}{40}[A_1(\nu) + A_2(\nu)] + \frac{9\alpha^4}{160}A_2(\nu)\right]y_0^0(\so{})+\nonumber\\&\frac{3\sqrt{5}}{280}\left[-16A_1(\nu) + \alpha^2[A_1(\nu) + A_2(\nu)] + 3\alpha^4 A_2(\nu)\right]y_2^0(\so{})\nonumber\\&\frac{3}{35}\left[\left(1 - \frac{\alpha^2}{2}\right)A_1(\nu) + \left(-\frac{\alpha^2}{2} + \frac{\alpha^4}{4}\right)A_2(\nu)\right]y_4^0(\so{})\Bigg\},\\
+  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]y_0^0(\so{}) + \nonumber\\&\frac{\sqrt{5}}{56}\left[(-16 + \alpha^2)A_1(\nu) + (\alpha^2 + 3\alpha^4)A_2(\nu)\right]y_2^0(\so{})\nonumber\\&\frac{1}{7}\left[\left(1 - \frac{\alpha^2}{2}\right)A_1(\nu) + \left(-\frac{\alpha^2}{2} + \frac{\alpha^4}{4}\right)A_2(\nu)\right]y_4^0(\so{})\Bigg\}.
 \end{align}
@@
 \begin{align}
-  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
+  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}

### 2018-09-22 papers/basic-theory/figures/excitation-coords/excitation-coords.py

@@ -1,0 +1,209 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.text as text
+import matplotlib.gridspec as gridspec
+from scipy import special
+outer_gridspec = gridspec.GridSpec
+inner_gridspec = gridspec.GridSpecFromSubplotSpec
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+import matplotlib
+matplotlib.rc('text', usetex=True)
+matplotlib.rcParams['text.latex.preamble']=[r"\usepackage{bm}"]
+
+# Physical parameters
+lamb = 0.3
+k = 2*np.pi/lamb
+alpha = 0.5
+
+inches = 2
+outer_rows = 1
+outer_cols = 1
+inner_rows = 2
+inner_cols = 3
+widths = [3/2]*outer_cols
+heights = [1]*outer_rows
+wspace = 0
+wspace_inner = 0
+hspace = 0
+hspace_inner = 0.2
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(outer_cols - 1) + 0.5*widths[0]*wspace_inner*outer_cols),
+                        inches*(np.sum(heights) + heights[0]*(hspace)*(outer_rows - 1) + 0.5*heights[0]*hspace_inner*outer_rows)))
+
+                                
+outer_grid = outer_gridspec(ncols=outer_cols, nrows=outer_rows,
+                            width_ratios=widths, height_ratios=heights,
+                            hspace=hspace, wspace=wspace)
+for outer_row in range(outer_rows):
+    for outer_col in range(outer_cols):
+        inner_grid = inner_gridspec(inner_rows, inner_cols,
+                                    subplot_spec=outer_grid[outer_row, outer_col],
+                                    width_ratios=[1]*inner_cols, height_ratios=[1]*inner_rows,
+                                    hspace=hspace_inner, wspace=wspace_inner)
+        for inner_row in range(inner_rows):
+            for inner_col in range(inner_cols):
+                ax = f.add_subplot(inner_grid[inner_row, inner_col])
+                ax.get_xaxis().set_visible(False)
+                ax.get_yaxis().set_visible(False)
+                ax.axis('off')
+
+                # Draw lenses
+                if inner_row == 0 and (inner_col == 1 or inner_col == 3):
+                    # Kludge to smooth sharp edges
[…]

### 2018-09-22 papers/basic-theory/figures/excitation/excitation.py

@@ -1,0 +1,52 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import scipy.misc
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+
+
+inches = 2
+rows = 1
+cols = 1
+widths = [1]
+heights = [1]
+hspace = 0
+wspace = 0
+
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
+                        inches*(np.sum(heights))))
+
+outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
+                               width_ratios=widths, height_ratios=heights,
+                               hspace=hspace, wspace=wspace)
+
+def hexc(theta, alpha):
+    return np.sin(theta)**2 + 0.5*(alpha**2)*(np.cos(theta)**2)
+        
+for col in range(cols):
+    ax = f.add_subplot(outer_grid[0, col])
+    ax.set_xlim([0,np.pi/2])
+    ax.set_ylim([0,1])
+
+    for alpha in [0, np.pi/8, np.pi/4, 3*np.pi/8]:
+        theta = np.linspace(0, np.pi/2, 100)
+        ax.plot(theta, hexc(theta, alpha), '-', lw=0.5, color=[alpha/(3*np.pi/8),0,0])
+
+    ax.text(0.03, 0.85,'$\\alpha = 3\\pi/8$', ha='left', va='center', transform=ax.transData)
+    ax.text(0.03, 0.4,'$\\pi/4$', ha='left', va='center', transform=ax.transData)
+    ax.text(0.03, 0.18,'$\\pi/8$', ha='left', va='center', transform=ax.transData)
+    ax.text(0.03, 0.035,'$0$', ha='left', va='center', transform=ax.transData)
+    
+    ax.tick_params(direction='out', left=True, right=False, width=0.75)
+    ax.yaxis.set_ticks([0, 0.25, 0.5, 0.75, 1.0])
+    ax.set_yticklabels(['0','0.25','0.5','0.75','1'])
+    ax.xaxis.set_ticks([0, np.pi/8, np.pi/4, 3*np.pi/8, np.pi/2])
+    ax.set_xticklabels(['0','$\pi/8$','$\pi/4$','$3\pi/8$','$\pi/2$'])
+
[…]

### 2018-10-20 papers/basic-theory/figures/dipole-block/dipole-block.tex
Broad updates to paper.

\documentclass[crop,tikz]{standalone}% 'crop' is the default for v1.0, before it was 'preview'
% \usetikzlibrary{...}% tikz package already loaded by 'tikz' option
\usepackage{tikz}
\usepackage{amsmath, amsthm, amssymb, amsfonts, bm}
\usetikzlibrary{shapes,arrows.meta}
\usepackage{mathptmx}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}

% Talon's custom commands
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathbf{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rb}{\mathbf{r}_b}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\eqname}[1]{\tag*{#1}}
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=7em, align=center]

\begin{document}
  \begin{tikzpicture}[auto, node distance=2cm,>={Latex[length=2mm]}]
    \tikzset{font={\fontsize{9pt}{12}\selectfont}}
    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Spatio-angular\\ density};
    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular density\\ spectrum};
    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Irradiance};
    \node [block, below of=ads, node distance=2.5cm] (sas) {$F_\ell^m(\bs{\nu})$\\ Spatio-angular\\ spectrum};
    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial density\\ spectrum};
    \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
    \draw [->] (ads) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
    \draw [->] (sds) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
    \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);

    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\rd - \ro)F_\ell^m(\ro)$} (irr);
    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Orientation-dependent\\ point spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, h(\rd - \ro, \so)f(\ro, \so)$} ++(13cm,0) --  (irr.north);
    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Orientation-dependent\\ optical transfer function\\ $\int_{\mbb{S}^2}d\so\, H(\bs{\nu}, \so)F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu})$} (is);

    % Dashed box
    \draw [dashed] (sad.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$} ++(7.5cm,0) -- ++(0,-9cm) -- ++(-7.5cm,0) -- ++(0, 9cm);
    \draw [dashed] (irr.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-9cm) -- ++(-3.4cm,0) -- ++(0, 9cm);
      \end{tikzpicture}
\end{document}

### 2018-10-20 papers/basic-theory/figures/monopole-block/monopole-block.tex
Broad updates to paper.

--- 2018-10-20 papers/basic-theory/figures/dipole-block/dipole-block.tex
@@
 \DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
+% \DeclareMathAlphabet{\boldsymbol}{OMS}{cmsy}{m}{n}
 
@@
     \tikzset{font={\fontsize{9pt}{12}\selectfont}}
-    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Spatio-angular\\ density};
-    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular density\\ spectrum};
-    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Irradiance};
-    \node [block, below of=ads, node distance=2.5cm] (sas) {$F_\ell^m(\bs{\nu})$\\ Spatio-angular\\ spectrum};
-    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
-    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial density\\ spectrum};
-    \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
-    \draw [->] (ads) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
-    \draw [->] (sds) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
-    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
+    \node [block, align=center] (den) {$f(\ro{})$\\ Monopole\\ density};
+    \node [block, below of=den, node distance=2.5cm] (ds) {$F(\bs{\nu})$\\ Monopole\\ spectrum};
+    \node [block,  right of=den, node distance=7cm] (irr) {$g(\rd)$\\ Irradiance};
+    \node [block,  right of=ds, node distance=7cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
+    \draw [->] (den) -- node[] {$\mathcal{F}_{\mathbb{R}^2}$} (ds);
     \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);
 
-    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\rd - \ro)F_\ell^m(\ro)$} (irr);
-    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Orientation-dependent\\ point spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, h(\rd - \ro, \so)f(\ro, \so)$} ++(13cm,0) --  (irr.north);
-    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Orientation-dependent\\ optical transfer function\\ $\int_{\mbb{S}^2}d\so\, H(\bs{\nu}, \so)F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
-    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu})$} (is);
+    \draw [->] (den) -- node[text width=4cm, align=center] (cap1) {Point spread\\ function\\ $\int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro)$} (irr);
+    \draw [->] (ds) -- node[text width=4cm, align=center] (cap1) {Optical transfer\\ function\\ $H(\bs{\nu})F(\bs{\nu})$} (is);
 
     % Dashed box
-    \draw [dashed] (sad.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$} ++(7.5cm,0) -- ++(0,-9cm) -- ++(-7.5cm,0) -- ++(0, 9cm);
-    \draw [dashed] (irr.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-9cm) -- ++(-3.4cm,0) -- ++(0, 9cm);
+    \draw [dashed] (den.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6cm) -- ++(-3.4cm,0) -- ++(0, 6cm);
+    \draw [dashed] (irr.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6cm) -- ++(-3.4cm,0) -- ++(0, 6cm);
       \end{tikzpicture}

### 2018-10-20 papers/basic-theory/paper/paper.tex
Broad updates to paper.

--- 2018-07-09 papers/basic-theory/paper/paper.tex
@@
 
+% Talon's custom libraries
+\usepackage{empheq}
+% \usepackage{bm}
+
 % Talon's custom commands
@@
 \providecommand{\bs}[1]{\boldsymbol{#1}}
+\providecommand{\bv}{\bs{\nu}}
 \providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
 \providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
+\providecommand{\lmsum}{\sum_{\ell=0}^\infty\sum_{m=-\ell}^{\ell}}
+\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
+\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
+\providecommand{\tb}[1]{\textcolor{blue}{#1}}
 \DeclareFontFamily{OT1}{pzc}{}
@@
 \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
+\newcommand{\eqname}[1]{\tag*{#1}}
+\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}
 
@@
 \begin{abstract*}
-  We introduce the basic elements of a complete spatio-angular theory of
-  fluorescence microscopes. We start by analyzing a single-view fluorescence
-  microscope imaging an ensemble of in-focus dipole absorber/emitters using
-  electromagnetic optics and the paraxial approximation. Next, we define the
-  spatio-angular transfer function and show that fluorescence microscopes have
-  an angular band limit. Finally, we discuss the implications of our analysis on
-  quantitative fluorescence microscopy studies.
+  We introduce the basic elements of a spatio-angular theory of fluorescence
+  microscopy. We start by modeling a microscope imaging an ensemble of in-focus
+  fluorescent dipoles as a linear Hilbert-space operator with domain
+  $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$, and we
+  express the operator in terms of four different sets of object-space basis
+  functions. We show that the operator takes a particularly convenient form when
+  expressed in a basis of spatial and spherical harmonics---a form we call the
+  spatio-angular transfer function (SATF). We demonstrate our formalism by
+  analyzing a paraxial single-view fluorescence microscope without using the
+  monopole or scalar approximations. We show that this microscope has an angular
+  band limit, and we demonstrate the value of the transfer function approach by
+  efficiently simulating the imaging process with numerical phantoms. Notably,
+  we show that information about the out-of-plane orientation of ensembles of
+  in-focus fluorophores is imaged in paraxial widefield fluorescence
+  microscopes. We discuss the implications of our analysis for all quantitative
+  fluorescence microscopy studies and lay out a path towards a complete theory.
 \end{abstract*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Fluorescence microscopes are ubiquitous tools in biology [XXX], materials
-science [XXX], and metrology [XXX] for measuring the concentration of
-fluorophores throughout a sample. While an unprocessed fluorescence micrograph
-reports the approximate concentration of fluorophores throughout a sample,
-diffraction-limited microscopes image a spatially blurred version of the true
-fluorophore distribution. Therefore, microscopists who are interested in
-accurate measurements will perform a computational restoration to recover some
-of the information lost during the imaging process.
+\section{Introduction \tb{needs work}}
+
+Fluorescence microscopes are widely used in the biological sciences for
+measuring the distribution of fluorophores throughout a sample [cite]. While an
+unprocessed fluorescence micrograph reports the approximate distribution of
+fluorophores throughout a sample, all microscopes are diffraction limited
+[cite], so the image is a blurred version of the true fluorophore distribution.
+Therefore, microscopists who are interested in optimal measurements will perform
+a computational restoration to recover some of the information lost during the
+imaging process.
 
 Restoration techniques attempt to recover the true distribution of fluorophores
-using the measured data and a model of the imaging process. The model of the
+using the measured data and a model of the imaging process. A model of the
 imaging process can be obtained theoretically (by mathematically modeling the
 instrument under idealized conditions), experimentally (by measuring the
-microscope's response to a known input), or by a combination of theory and
-experiment (by measuring parameters of an instrument model). In all cases, the
-accuracy of the restored image is limited by the accuracy of the imaging model.
+instrument's response to a known input), or by a combination of theory and
+experiment (by measuring parameters of an instrument model). In all cases the
+accuracy of the restored fluorophore distribution is limited by the accuracy of
+the imaging model. All theoretical imaging models make simplifying
+approximations that limit the accuracy of restorations, so it is important to
+verify that the approximations introduce an acceptable level of error. This work
+investigates the errors introduced by two common approximations in models of
+fluorescence microscopes---the \textit{monopole approximation} and the
+\textit{scalar approximation}.
 
-Most theoretical fluorescence microscopy imaging models make simplifying
-approximations. A common (often unstated) pair of approximations is to (1) treat
-fluorophores as monopole absorber/emitters and (2) treat light propagation under
-the scalar approximation. In this work we will analyze fluorescence microscopes
-without these approximations and find the conditions under which these
-approximations are valid.
+This work lies at the intersection of three classes of fluorescence microscopy:
+(1) single-molecule localization microscopy (SMLM), (2) spatial ensemble
+fluorescence microscopy including widefield, confocal, and light-sheet
+techniques, and (3) polarized fluorescence microscopy. We briefly review these
+three classes and focus on their restoration techniques and use of the monopole
+and scalar approximations.
 
-Using an experimentally determined model is an effective way to find an accurate
-model without understanding all of the physical details of the imaging system,
-but these approaches require a known input that can completely characterize the
-imaging system. Sub-diffraction beads are commonly used as a known input for
-measuring the response of a microscope, but we argue that sub-diffraction beads
-are not enough to completely characterize the response of a microscope to all
-fluorescent samples. Beads can only characterize the response of the microscope
-to an angularly uniform distribution of fluorophores, and we will show that all
-microscopes have an orientation-dependent response. A complete characterization
-requires a test sample with at least three known orientation distributions.
+The SMLM community has pioneered the use of rigorous electromagnetic models of
+fluorescence microscopes \cite{backer2014, lieb2004} [cite Novotny]. When a
+single molecule is fluorescing in the sample, the measured intensity pattern is
+strongly dependent on the orientation of the emitting molecule. Backlund and Lew
+\cite{backlund2014} have shown that ignoring the orientation of fluorophores can
+bias position estimates, so the most accurate SMLM experiments must jointly
+estimate the position and orientation of each molecule.
 
-The single-molecule localization microscopy (SMLM) community has pioneered the
-use of rigorous electromagnetic models of single fluorescence microscopes
-\cite{backer2014, lieb2004}. When only one fluorophore is emitting at a time,
-the measured intensity pattern is strongly dependent on the orientation of the
-emitting molecule. Backlund and Lew \cite{backlund2014} have shown that ignoring
-the orientation of fluorophores can lead to biased estimates of their position,
-so the most accurate SMLM experiments must jointly estimate the position and
-orientation of the molecule. These joint estimates usually use a set of
-precomputed intensity patterns and a maximum-likelihood algorithm to estimate
-the orientation and position of each molecule. These methods have led to some of
-the most accurate position estimates of single molecules.
+Meanwhile, most fluorescence microscopists image ensembles of fluorophores and
+restore their images without considering the role that the monopole and scalar
+approximations play in the restoration process. A typical fluorescence
+microscopist is only interested in the spatial distribution of fluorophores, so
+they reason that they can ignore the orientation of the emitters.
 
-Meanwhile, most fluorescence microscopists image ensembles of fluorophores.
-Although many groups have used polarizers to probe the orientation of ensembles
-of fluorophores \cite{mehta2016} [Forkey], to our knowledge no
-work has been done on the response of fluorescence microscopes to ensembles of
-oriented fluorophores. Furthermore, current restoration techniques in polarized
-light microscopy are lacking because they rely on simple pixel-wise arithmetic
-and do not model the propagation of light through the microscope.
+A smaller community of microscopists is interested in measuring the orientation
+of ensembles of fluorophores \cite{mehta2016} [Forkey, Goldman, Moerner,
+Oldenbourg]. These techniques typically use polarized illumination or polarized
+detection to make multiple measurements of the same object. Current angular
+restoration techniques use a model of the dipole excitation and emission
+processes [Fourkas] to recover the orientation of fluorophores using pixel-wise
+arithmetic, but these techniques do not perform any spatial restoration so they
+do not use all of the information available to the microscopist. To our
+knowledge no work has been done to model the complete spatio-angular response of
+fluorescence microscopes to ensembles of oriented fluorophores.
 
+\tb{Out of date}
 In this work we model ensembles of in-focus dipole absorber/emitters using
-electromagnetic optics and the paraxial approximation. This marks a first step
-towards a complete three-dimensional non-paraxial theory of fluorescence
-microscopes. In section 2 we model the excitation and detection processes of
-dipoles. We define the most important quantity in this work, the spatio-angular
-transfer function, and we use it to show that fluorescence microscopes have an
-angular band limit. In section 3 we perform simulations and compare our model to
-traditional scalar models. In section 4 we discuss the implications of our work
-for fluorescence microscopy and lay out a path towards a complete spatio-angular
+electromagnetic optics and the paraxial approximation. In section 2 we model the
+excitation and detection processes of dipoles, and we define the most important
+quantity in this work---the spatio-angular transfer function (SATF). We
+calculate the SATF and show that fluorescence microscopes have an angular band
+limit. In section 3 we perform simulations and compare our model to traditional
+scalar models. In section 4 we discuss the implications of our work for
+fluorescence microscopy and lay out a path towards a complete spatio-angular
 theory of fluorescence microscopy.
 
-\section{Theory}
-\subsection{Spherical harmonics}\label{sec:sph}
+\subsection{Monopole emission vs. dipole emission \tb{not sure where this section should live}}
+Consider a single dipole radiator at the origin with its dipole moment oriented
+along a direction $\so$. The dipole emitter creates a time-harmonic electric
+field at a position $\mb{r}$ far from the dipole proportional to
 \begin{align}
-  y_l^m(\vartheta, \varphi) =
-  \begin{cases}
-    \sqrt{2}K_l^m\cos(m\varphi)P_l^m(\cos\vartheta), & m > 0\\
-    K_l^0P_l^0(\cos\vartheta), & m = 0\\
-    \sqrt{2}K_l^m\sin(-m\varphi)P_l^{-m}(\cos\vartheta), & m < 0\\
-  \end{cases}
+  \mb{E}_{\text{ff}}(\mb{r}, \so) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}\, \mh{r}\times\so\times\mh{r}.\label{eq:dip}
+\end{align}
+A typical approach to deriving Equation \ref{eq:dip} is to (1) use Maxwell's
+equations to derive the inhomogeneous electromagnetic wave equations then (2)
+use potentials to solve the wave equations with a dipole source term, then (3)
+drop the terms that decay faster than $1/|\mb{r}|$ [cite Jackson, Novotny,
+Teich]. Equation~\ref{eq:dip} shows that dipole radiators emit spherical
+wavefronts of polarized light with amplitude proportional to $\cos\theta$ where
+$\theta$ is the angle between the field point $\mb{r}$ and the dipole axis
+$\so$.
+
+Many models of fluorophores approximate the vector field on the left hand side
+of Equation \ref{eq:dip} with a scalar field---the \textit{scalar
+  approximation}---and drop the orientation dependence on the right hand
+side---the \textit{monopole approximation}. The approximated field is given by
+\begin{align}
+  U_{\text{ff}}(\mb{r}) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}. \label{eq:mono}
+\end{align}
+Models that use Equation \ref{eq:mono} as a starting point do not account for
+polarization or dipole orientation effects.
+
+\section{Theory \tb{outline is okay, subsections vary, recently moved changes of basis to the front}}
+We begin our analysis with the abstract Hilbert space formalism of Barrett and
+Myers \cite{barrett2004}. Our first task is to formulate the imaging process as
+a mapping between two Hilbert spaces $\mc{H}: \mbb{U} \rightarrow \mbb{V}$ where
+$\mbb{U}$ is a set than contains all possible objects, $\mbb{V}$ is a set that
+contains all possible datasets, and $\mc{H}$ is a model of the instrument that
+maps between these two spaces. We denote (possibly infinite-dimensional)
+Hilbert-space vectors in $\mbb{U}$ with $\mb{f}$, Hilbert-space vectors in
+$\mbb{V}$ with $\mb{g}$, and the mapping between the spaces with
+
+\begin{align}
+  \mb{g} = \mc{H}\mb{f}.
+\end{align}
+
+Once we have identified the spaces $\mbb{U}$ and $\mbb{V}$, we can start
+expressing the mapping between the spaces in a specific object-space and
+data-space basis. In most cases the easiest mapping to find uses a
+delta-function basis---we expand object and data space into delta functions then
+express the mapping as an integral transform. After finding this mapping we can
+start to investigate the same mapping in different bases.
+
+The above discussion is quite abstract, but it is a powerful point of view that
+will enable us to draw new conclusions about all fluorescence microscopes. In
+Section \ref{sec:monopole} we will demonstrate the formalism by examining a
+familiar monopole imaging model, and we will show that the point spread
+function and the optical transfer function are mappings between object and data
+space expressed in two different bases. In Section \ref{sec:dipole} we will
+extend the monopole imaging model to dipoles and examine the mapping in four
+different bases. In Section \ref{sec:para} we will examine the mappings for a
+more specific case---a paraxial epi-illumination single-view fluorescence
+microscope.
+
+\subsection{Monopole imaging in different bases \tb{50\%}}\label{sec:monopole}
+We start by considering a microscope that images a field of in-focus monopoles
+by recording the irradiance on a two-dimensional detector. We can represent
+the object as a function that assigns a real number to each point on a plane,
+so we identify object space as $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$. Similarly, we
+have a two-dimensional detector that measures a real number at every point on 
+a plane, so data space is the same set $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$. Our
+first task is complete---we have identified the geometry of object and data
+space.
+
+Next, we find and name the representations of our object and data in a
+specific basis. In a delta function basis the object can be represented by a
+function $f(\ro)$ called the \textit{monopole density}---the number of
+monopoles at the two-dimensional position $\ro$ per unit area. Similarly, in a
+delta function basis the data can be represented by a function $g(\rd)$ called
+the \textit{irradiance}---the power received by a surface at position $\rd$
+per unit area. It may seem pedantic to emphasize that these representations
+are in a delta function basis, but we highlight this point to make it clear
+that the delta function basis is not special---we can choose a different basis
+at will.
+
+% We start by considering a field of in-focus monopoles that have been excited by test
+% a spatially uniform beam. As the fluorophores relax, they emit scalar waves in
+% the form of Equation \ref{eq:mono}. The waves propagate through the microscope
+% and we measure the irradiance on a two dimensional detector.
+
+A reasonable starting point is to assume that the relationship between the
+object and the data is \textit{linear}---this is usually true in fluorescence
+microscopes since fluorophores emit incoherently so a scaled sum of fluorophores
+will result in a scaled sum of the irradiance patterns created by the individual
+fluorophores. If the mapping is linear we can write the irradiance as the
+integral over a field of monopoles weighted by the detector response due to
+single monopoles
+\begin{align}
+g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd,\ro)f(\ro), \label{eq:fwdmono}
+\end{align}
+where $h(\rd{}, \ro{})$ is the kernel of the integral transform.
+
+Most fluorescence microscopes are (at least approximately) shift-invariant,
+which means that shifting the object will result in a corresponding shift of the
+data. The mapping between an object and the data in a linear shift-invariant
+fluorescence microscope can be written as
+\begin{align}
+  g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro).  \label{eq:lsi}
+\end{align}
+When the imaging system is shift invariant the kernel $h(\rd - \ro)$ is usually
+called the \textit{point spread function}.
+
+The mapping between the object and the data in linear shift-invariant
+microscopes takes a particularly simple form in a spatial harmonic basis. If we
+apply the Fourier convolution theorem to Eq. \ref{eq:lsi} we find that
+\begin{align}
+  G(\bs{\nu}) = H(\bs{\nu})F(\bs{\nu}),\label{eq:freq}
+\end{align}
+where the \textit{irradiance spectrum} is given by
+\begin{align}
+  G(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+\end{align}
+the \textit{optical transfer function} is given by
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+\end{align}
+and the \textit{monopole spectrum} is given by
+\begin{align}
+    F(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}).
+\end{align}
+Notice that Eqs. \ref{eq:lsi} and \ref{eq:freq} are expressions of the same
+mapping between object and data space in different bases. Figure
+\ref{fig:monopole-block} summarizes the relationship between object and data
+space in both bases.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=1.0]{../figures/monopole-block/monopole-block.pdf}
+  \caption{We can compute the mapping between object space and data space using
+    two different bases.}
+     \label{fig:monopole-block}      
+\end{figure}
+
+\subsection{Dipole imaging in different bases \tb{50\%}}\label{sec:dipole}
+Now we consider a microscope imaging a field of in-focus \textit{dipoles} by
+recording the irradiance on a two-dimensional detector. A function that assigns
+a real number to each point on a plane is not sufficient to specify a field of
+dipoles because the dipoles can have different orientations. To represent the
+object we need to extend object space to
+$\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ where $\mbb{S}^2$ is the
+two-dimensional sphere (the usual sphere embedded in $\mbb{R}^3$).
+
+In a delta function basis the object can be represented by a function
+$f(\ro, \so)$ called the \textit{spatio-angular density}---the number of dipoles
+at position $\ro{}$ per unit area oriented along $\so{}$ per unit solid angle.
+If the imaging system is linear and shift invariant then the mapping between
+object and data space can be expressed in a delta function basis as
+  \begin{align}
+g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro, \so), \label{eq:odpsf}
+  \end{align}
+  where $h(\rd - \ro, \so)$ is the \textit{orientation-dependent point spread
+    function}.
+
+  We can make our first change of basis by applying the Fourier-convolution
+  theorem to Eq. \ref{eq:odpsf} which yields
+\begin{align}
+G(\bs{\nu}) = \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})F(\bs{\nu}, \mh{s}) \label{eq:odotf},
+\end{align}
+where we define the \textit{irradiance spectrum} as
+\begin{align}
+  G(\bs{\nu}) &= \int_{\mbb{R}^2}d\mb{r}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+  \end{align}
+  the \textit{orientation-dependent optical transfer function} as
+  \begin{align}
+  H(\bs{\nu}, \mh{s}) &= \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \mh{s})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+  \end{align}
+  and the \textit{spatial density spectrum} as
+  \begin{align}
+  F(\bs{\nu}, \mh{s}) &= \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r}, \mh{s})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}). 
+  \end{align}
+  This basis is well suited for simulating objects that are angularly sparse and
+  spatially dense.
+
+  The spherical harmonics provide another set of convenient basis functions. We
+  can change basis from spherical delta functions to spherical harmonics by
+  making use of the generalized Plancharel theorem for spherical functions
+\begin{align}
+  \ints{2}d\mh{s}{}\, h(\mh{s})f(\mh{s}) = \lmsum H_\ell^m F_\ell^m, \label{eq:plan}
 \end{align}
@@
 \begin{align}
-  K_l^m = \sqrt{\frac{(2l+1)}{4\pi}\frac{(l-|m|)!}{(l+|m|)!}},
+  F_\ell^m \equiv \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_\ell^m(\mh{s}), 
 \end{align}
-and $P_l^m(x)$ are the associated Legendre polynomials. The $l=0, 1, 2$
-spherical harmonics are given by
+is the spherical Fourier transform of $f(\mh{s})$, $\bar{z}$ denotes the complex
+conjugate of $z$, and $Y_{\ell}^m(\mh{s})$ are the spherical harmonic functions
+defined in Appendix \ref{sec:sph}. Eq. \ref{eq:plan} expresses the fact that
+scalar products are invariant under a change of basis (see Eq. 3.78 of
+\cite{barrett2004}). The left-hand side of Eq. \ref{eq:plan} is the scalar
+product of $\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the
+right hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
+spherical harmonic function basis. Applying Eq. \ref{eq:plan} to Eq.
+\ref{eq:odpsf} yields
 \begin{align}
-  y_0^0(\vartheta, \varphi) &= \sqrt{\frac{1}{4\pi}}, \nonumber \\ 
-  y_1^{-1}(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\sin\varphi\sin\vartheta, \hspace{2em} y_1^0(\vartheta, \varphi) &= \sqrt{\frac{3}{4\pi}}\cos\vartheta, \hspace{2em} y_1^1(\vartheta, \varphi) = \sqrt{\frac{3}{4\pi}}\cos\varphi\sin\vartheta, \nonumber \\
-  y_2^{-2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\cos\varphi\sin^2\vartheta, &\hspace{2em} y_2^{-1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\sin\varphi\sin\vartheta\cos\vartheta,\nonumber \\
-  y_2^0(\vartheta, \varphi) &= \sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1), \nonumber \\ 
-  y_2^{1}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}\cos\varphi\sin\vartheta\cos\vartheta, &\hspace{2em} y_2^{2}(\vartheta, \varphi) = \sqrt{\frac{15}{4\pi}}(\cos^2\varphi - \sin^2\varphi)\sin^2\vartheta.\label{eq:harmonics}
+  g(\rd) = \lmsum H_\ell^m(\rd - \ro)F_\ell^m(\ro) \label{eq:atf-form}
+\end{align}
+where we have defined the \textit{angular transfer function} as
+\begin{align}
+  H_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, h(\mb{r}, \mh{s})\bar{Y}_{\ell}^m(\mh{s}),\label{eq:atf-prep} 
+\end{align}
+and the \textit{angular density spectrum} as
+\begin{align}
+  F_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, f(\mb{r}, \mh{s})\bar{Y}_{\ell}^m(\mh{s}).
+\end{align}
+This basis is well suited for simulating objects that are spatially sparse and
+angularly dense.
+
+We can arrive at our final basis in two ways: by applying the generalized
+Plancharel theorem for spherical functions to Eq. \ref{eq:odotf} or by applying
+the Fourier convolution theorem to Eq. \ref{eq:atf-form}. We follow the
+second path and find that
+\begin{align}
+G(\bs{\nu}) = \lmsum H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu}) \label{eq:saft},
+\end{align}
+where we have defined the \textit{spatio-angular transfer function} (SATF) as
+  \begin{align}
+  H_\ell^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})\bar{Y}_\ell^m(\mh{s}),
+  \end{align}
+  and the \textit{spatio-angular density spectrum} as
+  \begin{align}
+  F_\ell^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\mh{s}\, F(\bs{\nu}, \mh{s})\bar{Y}_\ell^m(\mh{s}).
+  \end{align}
+  This basis is well suited for simulating arbitrary samples because it exploits
+  the sparsity of the imaging system---we will see this explicitly when we
+  calculate a specific case of the spatio-angular transfer function.
+
+  Figure \ref{fig:dipole-block} summarizes the relationship between the four
+  bases that we can use to compute the image of a field of dipoles.
+
+\begin{figure}
+  \hspace{-5em}
+  \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
+  \caption{We can compute the mapping between object space and data space using
+    four different bases.}
+   \label{fig:dipole-block}      
+    \end{figure}
+
+\subsection{Paraxial epi-fluorescence microscope}\label{sec:para}
+\tb{This section is probably the most mature, but it still has some mismatch with
+  newer sections. I've quit using ``kernel'' and haven't fixed it.}
+In this section we apply the tools we developed in the previous two sections to
+analyze a paraxial epi-fluorescence microscope. We start by reviewing the
+derivation of the monopole point spread function in preparation for the
+derivation of the orientation-dependent point spread function. We conclude the
+section by analyzing the dipole imaging map in the four bases we described
+earlier.
+
+\subsubsection{Monopole point spread function}
+In this section we derive the form of the monopole point spread function $h(\mb{r})$.
+First, we place a monopole emitter at the focal point of an objective lens and
+calculate the field created in the back focal plane. We can model a paraxial
+thin lens as a quadratic phase element, so it converts a spherical wave to a
+plane wave in the back focal plane with a sharp cutoff at the exit pupil of the
+lens
+\begin{align}
+  U_{\text{bfp}}(\mb{r}_b) \propto \Pi\left(\frac{|\mb{r}_b|}{\alpha}\right) \equiv
+  \begin{cases}
+    1\quad \text{if}\quad |\mb{r}_b| < \alpha,\\
+    0\quad \text{else}.
+  \end{cases}
+\end{align}
+A central result of Fourier optics is that the fields one focal distance from
+either side of a paraxial lens are related by a scaled two-dimensional Fourier
+transform. If we place a detector in the focal plane of the tube lens then the
+field on the detector is given by
+\begin{align}
+  U_{\text{det}}(\mb{r}_d) \propto \mc{F}_{\mbb{R}^2}\left\{U_{\text{bfp}}(\mb{r}_b)\right\} = \frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}.
+\end{align}
+Finally, the detector measures the irradiance instead of the field, so we take
+the modulus squared of the field to find that the measurable irradiance created
+by a single monopole radiator at the origin is the familiar Airy disk
+\begin{align}
+  h(\mb{r}_d, \ro = 0) \propto |U_{\text{det}}(\mb{r}_d)|^2 = \left[\frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}\right]^2.
+\end{align}
+Shifting the monopole in the transverse plane will introduce a linear phase
+factor in the back focal plane which will manifest as a shift on the detector
+due to the Fourier shift theorem. Therefore, the monopole imaging system is
+shift invariant and we can rewrite the irradiance on the detector due to a
+monopole at $\ro$ as
+\begin{align}
+  h(\rd, \ro) = h(\rd - \ro). \label{eq:shift}
+\end{align}
+We have modeled a microscope with unit magnification, but a similar point spread
+function can be found for magnifying microscopes by making a change of
+variables---see Barrett section 7.2.7.
+
+Rotating a monopole will leave its image unchanged. Therefore, our imaging
+system is rotation invariant and we can simplify the orientation-dependent point spread function further with
+\begin{align}
+  h(\rd - \ro) = h(|\rd - \ro|). \label{eq:rotational}
 \end{align}
 
-\subsection{Excitation model}
-% [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
-In this section we will calculate the excitation kernel for epi-illumination
-microscopes---the relative probability of exciting a molecule with a known
-orientation. Our approach is similar to previous work \cite{fourkas2001,  chandler2017},
-but here we consider unpolarized illumination and restrict
-ourselves to the paraxial approximation.
+\subsubsection{Orientation-dependent point spread function}
+In the next two subsections we will calculate the orientation dependent point
+spread function $h(\mb{r}, \mh{s})$ of a paraxial epi-fluroescence microscope.
+We can make our first simplifying step by realizing the excitation and detection
+processes are incoherent which means that the orientation-dependent PSF is
+separable
+\begin{align}
+  h(\rd, \ro, \so) = h_{\text{exc}}(\ro, \so)\,h_{\text{det}}(\rd, \ro, \so). \label{eq:kernelsep}
+\end{align}
+We can calculate the excitation and detection PSFs separately then take their product to find the complete orientation-dependent PSF.
 
-We consider a single molecule with a fixed absorption dipole moment $\so{}$ that
-we express in spherical coordinates [see Fig. 1(a)] as 
+\subsubsection{Dipole excitation model}
+When we developed the monopole imaging model we ignored the excitation process
+because we excited the fluorophores with a spatially uniform excitation beam and
+monopoles have no orientation dependence. For the dipole imaging model we must
+model the excitation process because the excitation process is rarely angularly
+uniform (carefully calibrated TIRF systems are an exception).
+
+In this section we will calculate the excitation kernel
+$h_{\text{exc}}(\ro, \so)$ for the paraxial epi-illumination microscope under
+unpolarized K\"{o}ehler illumination shown in Figure \ref{fig:microscope}. We
+will only consider spatially uniform excitation, so the excitation kernel will
+no depend on $\ro$
 \begin{align}
-  \so{} &= \cos\varphi\sin\vartheta\mh{x} + \sin\varphi\sin\vartheta\mh{y} + \cos\vartheta\mh{z}. \label{eq:spherical}
+  h_{\text{exc}}(\ro, \so) = h_{\text{exc}}(\so).
 \end{align}
-We can rewrite Eq. \ref{eq:spherical} in terms of spherical harmonic functions
-(see Section \ref{sec:sph}) as
+We can interpret $h_{\text{exc}}(\so)$ as the relative probability of exciting a
+molecule with dipole orientation $\so$. Our approach is similar to previous work
+\cite{fourkas2001, chandler2017}, but here we consider paraxial, incoherent, and
+unpolarized illumination.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=.9]{../figures/excitation-coords/excitation-coords.pdf}
+   \caption{Illumination geometry and coordinates. We calculate the excitation
+     kernel $h_{\text{exc}}(\so)$ for a paraxial, unpolarized, incoherent
+     light source (or its image) in the back focal plane of the condenser lens. }
+   \label{fig:microscope}
+ \end{figure}
+
+We start by expressing the dipole moment $\so{}$ in Cartesian coordinates
 \begin{align}
-  \so{} &=\sqrt{\frac{3}{4\pi}}\left[y_1^1(\vartheta, \varphi)\,\mh{x} + y_1^{-1}(\vartheta, \varphi)\,\mh{y} + y_1^0(\vartheta, \varphi)\, \mh{z}\right]. \label{eq:sphharm}
+  \so{} &= s_x\mh{x} + s_y\mh{y} + s_z\mh{z}. \label{eq:spherical}
 \end{align}
-We place the molecule in the focal plane of an aplanatic and
+We place the dipole in the focal plane of an aplanatic and
 polarization-preserving objective lens with its optical axis aligned with the
 $\mh{z}$ axis. Next, we place a spatially incoherent, spatially uniform,
-unpolarized thermal light source (or its image) in the back aperture of the
-objective lens to illuminate the focal plane. In this geometry each point in the
-back focal plane generates a plane wave that illuminates the sample.
+unpolarized light source (or its image) in the back aperture of the objective
+lens to illuminate the focal plane. In this geometry each point in the back
+focal plane generates a plane wave that illuminates the sample.
 
-To model the unpolarized light source we will use polarized ray tracing [cite
-Torok] to find the response for a single polarized ray, then integrate over the
-rays and polarizations to find the complete response. First, we model the
-electric field at every point on the back focal plane as
+To model the unpolarized light source we will use polarized ray tracing
+\cite{foreman2011} to find the response for a single polarized ray, then
+integrate over the rays and polarizations to find the complete response. First,
+we model the electric field at every point on the back focal plane as
 \begin{align}
@@
 where $\phi_{\text{pol}}$ is the polarization orientation and \{$\mh{x}$,
-$\mh{y}$\} are transverse Cartesian basis vectors. Notice that Eq. \ref{eq:bfp0}
-describes the incoherent electric fields at every point in the back focal plane,
-it does not describe a coherent plane wave. Immediately after the lens the
-electric field is
+$\mh{y}$\} are transverse Cartesian basis vectors. Note that Eq. \ref{eq:bfp0}
+describes the incoherent electric fields at every point in the back focal
+plane--- it does not describe a coherent plane wave. To find the electric field
+immediately after the paraxial lens we apply a position-dependent rotation
+matrix (see the rotation matrices in \cite{foreman2011, backer2014} under the
+paraxial approximation)
+
 \begin{align}
-  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \propto \left\{[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\phi}]\,\bsh{\phi} + [\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\rho}]\,\bsh{\theta}\right\}\sqrt{\cos\theta}, \label{eq:bfp2ff}
+  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) & \propto 
+  \begin{bmatrix}
+    1 & 0 &\theta \cos\phi\\
+    0 & 1 &\theta \sin\phi\\
+    -\theta\cos\phi&-\theta \sin(\phi)&1
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos\phi_{\text{pol}}\\
+    \sin\phi_{\text{pol}}\\
+    0
+  \end{bmatrix}\\
+  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) &\propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y} - \theta\cos(\phi - \phi_{\text{pol}})\mh{z}.\label{eq:eff}
 \end{align}
-where \{$\theta$, $\phi$\} are spherical coordinates, \{$\bsh{\rho}$,
-$\bsh{\phi}$\} are cylindrical basis vectors, and \{$\bsh{\theta}$,
-$\bsh{\phi}$\} are spherical basis vectors defined in Figure 1(a) and related by
+The probability that a dipole oriented along $\so{}$ is excited by a ray with
+electric field $\mb{E}$ is given by 
 \begin{align}
-  \bsh{\rho} &= \cos\phi\mh{x} + \sin\phi\mh{y},\label{eq:rho}\\
-  \bsh{\phi} &= -\sin\phi\mh{x} + \cos\phi\mh{y},\label{eq:phi}\\
-  \bsh{\theta} &= \cos\phi\cos\theta\mh{x} + \sin\phi\cos\theta\mh{y} - \sin\theta\mh{z}.\label{eq:theta}               
+  |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2 \propto s_x^2\cos^2\phi_{\text{pol}} + s_y^2\sin^2\phi_{\text{pol}} + s_z^2\theta^2\cos^2(\phi - \phi_{\text{pol}}).
+\label{eq:integrand}
 \end{align}
-In Eq. \ref{eq:bfp2ff} the
-$[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\phi}]\,\bsh{\phi}$ term models
-s-polarized fields, the
-$[\mb{E}_\text{bfp}(\phi_{\text{pol}})\cdot\bsh{\rho}]\,\bsh{\theta}$ term
-models the rotation of p-polarized fields, and the $\sqrt{\cos\theta}$ term
-models the apodization of an aplanatic lens. After plugging Eq. \ref{eq:bfp0}
-and Eqs. \ref{eq:rho}--\ref{eq:theta} into Eq. \ref{eq:bfp2ff} and applying the
-paraxial approximation, the electric field immediately after the lens is given
-by
-\begin{align}
-  \mb{E}_{\text{ff}}^{(p)}(\theta, \phi, \phi_{\text{pol}}) \propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y} - \theta\cos(\phi - \phi_{\text{pol}})\mh{z}.\label{eq:eff}
-\end{align}
-To calculate the probability that a dipole oriented along $\so{}$ is excited by
-a ray with electric field $\mb{E}$ we need to evaluate $|\mb{E}\cdot\so{}|^2$.
-Evaluating this expression for each ray would be cumbersome if we used Eqs.
-\ref{eq:spherical} and \ref{eq:eff} because we would need to simplify a large
-number of trigonometric functions. Instead, we use Eqs. \ref{eq:sphharm} and
-\ref{eq:eff} and the real Gaunt coefficients [XXXciteXXX] to find the products
-of spherical harmonics. We find that
-% [theta**2*cos(phi - phip)**2/2 + 0.5*sin(phip)**2 + 0.5*cos(phip)**2, 0, 0, 0, sqrt(15)*sin(2*phip)/10, -sqrt(15)*theta*sin(phip)*cos(phi - phip)/5, sqrt(5)*theta**2*cos(phi - phip)**2/5 - sqrt(5)*sin(phip)**2/10 - sqrt(5)*cos(phip)**2/10, -sqrt(15)*theta*cos(phip)*cos(phi - phip)/5, -sqrt(15)*sin(phip)**2/10 + sqrt(15)*cos(phip)**2/10]
-\begin{align}
-  |\mb{E}_{\text{ff}}^{(p)}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2 \propto\, &\left[1 + \theta^2\cos^2(\phi - \phi_{\text{pol}})\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[ - 1 + 2\theta^2\cos^2(\phi - \phi_{\text{pol}})\right]y_2^{0}(\so{}) +\nonumber \\
-                                   &\frac{\sqrt{15}}{10}\theta\sin\phi_{\text{pol}}\cos(\phi - \phi_{\text{pol}})y_2^{-1}(\so{}) + \frac{\sqrt{15}}{10}\theta\cos\phi_{\text{pol}}\cos(\phi - \phi_{\text{pol}})y_2^{1}(\so{}) -\nonumber \\
-                                   &\frac{\sqrt{15}}{20}\sin(2\phi_{\text{pol}})y_2^{-2}(\so{}) - \frac{\sqrt{15}}{20}\cos(2\phi_{\text{pol}})y_2^{2}(\so{}).\label{eq:integrand}
-\end{align}
-To calculate the complete excitation model we need to integrate Eq.
+To find the complete excitation kernel we need to integrate Eq.
 \ref{eq:integrand} over all polarization orientations and rays
 \begin{align}
-  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}^{(p)} \cdot \so{}|^2. \label{eq:integral}
+  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2, \label{eq:integral}
 \end{align}
-After plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral} and evaluating
-the integrals, all but two terms disappear and the orientation-dependent
-excitation model is given by
+where $\alpha$ is the maximum angle the illumination rays make with the optical
+axis. Plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral}, evaluating the
+integrals, and dropping constants gives
 \begin{align}
-  h_{\text{exc}}(\so{}) &\propto \left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{}). \label{eq:excitation}
+  h_{\text{exc}}(\vartheta) &\propto s_x^2 + s_y^2 + \frac{1}{2}\alpha^2s_z^2.
 \end{align}
-We note that the excitation model depends on the orientation of the molecule,
-but it does not depend on the position of the molecule in the focal plane. This
-is a direct consequence of our illumination geometry---we have placed incoherent
-light sources in the back focal plane of the objective so each point in the
-focal plane within the field of view is illuminated equally.
+We can rewrite the excitation kernel in terms of a single variable with the
+substitutions $s_x^2 + s_y^2 = \sin^2\vartheta$ and $s_z^2 = \cos^2\vartheta$
+\begin{align}
+  h_{\text{exc}}(\vartheta) &\propto \sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta \label{eq:hexctheta}.
+\end{align}
 
-\subsection{Detection model}
+Figure \ref{fig:excitation} shows the excitation kernel as a function of
+inclination angle $\vartheta$ and maximum excitation angle $\alpha$. The largest
+variation of the excitation kernel occurs when the maximum excitation angle is
+zero---plane-wave illumination. As $\alpha$ grows dipoles parallel to the optic
+axis are more likely to be excited and the variation of the excitation kernel
+decreases. Note that we have derived this simple model under the paraxial
+approximation, so it does not make quantitative predictions for high-NA
+illumination geometries.
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.95]{../figures/excitation/excitation.pdf}
+   \caption{Dipole excitation kernel $h_{\text{exc}}(\vartheta)$ as a function of
+     inclination angle $\vartheta$ and maximum excitation angle $\alpha$.}
+   \label{fig:excitation}
+ \end{figure}
+
+ \subsubsection{Dipole detection model}
  In this section we will calculate the detection kernel of an epi-detection
-microscope---the irradiance on the detector due to single molecule at a known
-position with known orientation. Our approach is similar to \cite{backer2014,
-  nov2006, agrawal2012}, but here we restrict ourselves to the paraxial
+ microscope---the irradiance on the detector due to a single dipole with fixed
+ position and orientation. Our approach mimics existing work \cite{backer2014,
+   nov2006, agrawal2012}, but we restrict ourselves to the paraxial
  approximation.
 
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=.9]{../figures/detection-coords/detection-coords.pdf}
+   \caption{Detection geometry and coordinates. We calculate the detection
+     kernel $h_{\text{det}}(\rd, \ro, \so)$ for a paraxial 4$f$ imaging
+     system.}
+   \label{fig:detection}
+ \end{figure}
+
 We consider a single dipole emitter at the origin with a fixed dipole emission
-moment oriented along $\so{}$---parallel to the excitation moment. The electric
-field at a position $\mb{r}$ far from the dipole is given by
+moment oriented along $\so{}$. The electric field at a position $\mb{r}$ far
+from the dipole is given by
 \begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \frac{\text{exp}[ik|\mh{r}|]}{|\mh{r}|}\mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
 \end{align}
-If we place the molecule in the focal plane of an aplanatic and
-polarization-preserving objective lens with its optical axis aligned with the
-$\mh{z}$ axis (or reuse the illumination objective), then the electric field in
-the back focal plane of the lens is given by
+We place the dipole in the focal plane of the same 4$f$ imaging system we
+considered in the monopole case---see Figure \ref{fig:detection}. The dipole emits
+spherical wavefronts so we can reuse our argument for shift invariance and drop
+the phase dependence of the electric field
 \begin{align}
-  \mb{E}_{\text{bfp}}(\rb{}, \so{}) \propto \left\{[\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\phi}]\,\bsh{\phi} + [\mb{E}_\text{ff}(\mb{r}, \so{})\cdot\bsh{\theta}]\,\bsh{\rho}\right\}\sqrt{1/\cos\theta}\,\Pi\left(\frac{r_b}{\sin\alpha}\right).
-\label{eq:bfp}
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \mh{r} \times \so{} \times \mh{r} \label{eq:ff2}
 \end{align}
-where the first term accounts for s-polarized fields, the second term accounts
-for p-polarized fields, $\sqrt{1/\cos\theta}$ is the apodization factor for an
-aplanatic lens, and
+We also note that we can rewrite a shift-invariant kernel as
 \begin{align}
-  \Pi\left(\frac{r_b}{\sin\alpha}\right) =
-  \begin{cases}
-    1\quad \text{if}\quad r_b < \sin^{-1}\alpha,\\
-    0\quad \text{else},
-  \end{cases}
+h_{\text{det}}(\rd, \ro, \so) = h_{\text{det}}(\rd - \ro, \so), 
 \end{align}
-is the aperture stop. After expanding the dot products, applying the paraxial
-approximation, and writing the dipole orientation $\so{}$ in terms of spherical
-harmonic functions, we find that the electric field in the back focal plane is
-given by
+which will simplify our derivation---we only need to calculate the response for
+a dipole positioned along the optic axis. We can rewrite the cross products in terms
+of a matrix multiplication
 \begin{align}
-  \mb{E}_{\text{bfp}}^{(p)}(\rb{}, \so{}) \propto \left\{\left[y_1^1(\so{}) - r_b\cos\phi_b y_1^0(\so{})\right]\mh{x} + \left[y_1^{-1}(\so{}) - r_b\sin\phi_b y_1^0(\so{})\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right).
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto [\mb{I} - \mh{r}\mh{r}^{\dagger}]\so,
+\end{align}
+where $\mb{I}$ is a $3\times 3$ identity matrix. If we place the molecule in the
+focal plane of an aplanatic and polarization-preserving objective lens with its
+optical axis aligned with the $\mh{z}$ axis (or reuse the illumination
+objective), then we can find the electric field in the back focal plane by
+multiplying the electric field with a position-dependent rotation matrix and
+truncating waves outside the detection collection angle $\alpha$
+\begin{align}
+  \mb{E}_{\text{bfp}}(\mb{r}, \so{}) \propto \mb{R}_{\text{obj}}(\mh{r})[\mb{I} - \mh{r}\mh{r}^{\dagger}]\so\Pi\left(\frac{\theta}{\alpha}\right).
+\end{align}
+After plugging in paraxial positions
+\begin{align}
+  \mh{r}(\theta,\phi) \approx \theta\cos\phi\mh{x} + \theta\sin\phi\mh{y} + \mh{z},
+\end{align}
+and the paraxial rotation matrix
+\begin{align}
+  \mb{R}_{\text{obj}}(\theta, \phi) &=
+  \begin{bmatrix}
+    1 & 0 &-\theta \cos\phi\\
+    0 & 1 &-\theta \sin\phi\\
+    -\theta\cos\phi&-\theta \sin(\phi)&1
+  \end{bmatrix},
+\end{align}
+then dropping the $\theta^2$ $\mh{z}$ components and changing from spherical
+coordinates to cylindrical coordinates by substituting $(r_b, \phi_b)$ for
+$(\theta, \phi)$ we find that
+\begin{align}
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{\left[s_x - s_zr_b\cos\phi_b\right]\mh{x} + \left[s_y - s_z r_b\sin\phi_b\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right).
 \label{eq:bfp2}
 \end{align}
-We note that Eq. \ref{eq:bfp2} is identical to previously derived models
-[Piestun, Backer] except here we have used the paraxial approximation and used
-spherical harmonic functions.
+Equation \ref{eq:bfp2} is easier to work with if we introduce the radial vector
+field $\mh{\bs{\rho}} = \cos\phi_b\mh{x} + \sin\phi_b\mh{y}$ and rewrite as
+\begin{align}
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp3}
+\end{align}
+Equation \ref{eq:bfp3} shows that the transverse components of the dipole
+($s_x, s_y$) create linear vector fields in the back focal plane
+($\mh{x}, \mh{y}$) while the axial component of the dipole $s_z$ creates a radial
+vector field in the back focal plane $\mh{z}$.
 
-Next we place a tube lens one focal length from the back focal plane and a
-detector (see Figure XX)). Under the paraxial approximation we can find the
-electric field in the detector plane by taking the Fourier transform of the
-field in the back focal plane [Goodman]
+We complete the 4$f$ system by placing a tube lens one focal length from the
+back focal plane and a planar detector---see Figure \ref{fig:detection}. Under
+the paraxial approximation we can find the electric field in the detector plane
+by taking the Fourier transform of the field in the back focal plane
+\cite{goodman1996}
 \begin{align}
-  \mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}^{(p)}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
+  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
+\end{align}
+We evaluate the integral in Appendix \ref{sec:ftvec} and show that 
+\begin{align}
+  \mb{E}_{\text{det}}(r_d, \so{}) \propto \frac{J_1(k\alpha r_d)}{k\alpha r_d}s_x\mh{x} + \frac{J_1(k\alpha r_d)}{k\alpha r_d}s_y\mh{y} - i\alpha\frac{J_2(k\alpha r_d)}{k\alpha r_d}s_z\mh{\bs{\rho}}.
+\end{align}
+Once again we find that the transverse component of the dipole creates a linear
+field and the axial component of the dipole creates a radial field, but on the
+detector the linear and radial fields are out of phase by $\pi/2$. This crucial
+phase factor is a direct consequence of the fact that the linear fields are real
+and even---the Fourier transform of a real and even function is real and
+even---and the radial fields are real and odd---the Fourier transform of a real
+and odd function is imaginary and odd.
+
+Our final step is to calculate the irradiance on the detector
+\begin{align}
+  h_{\text{det}}(r_d, \so{}) &\propto |\mb{E}_{\text{det}}(r_d, \so{})|^2.
+\end{align}
+The irradiance is the sum of the contributions from the linear and radial fields
+since their fields are out of phase, so
+\begin{align}
+  h_{\text{det}}(r_d, \vartheta) &\propto a_1(r_d)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r_d)\cos^2\vartheta, 
+\end{align}
+where we have defined
+\begin{align}
+  a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
+\end{align}
+Notice that we retain the $\alpha^2$ irradiance term even though we dropped
+$\theta^2$ electric field terms since these terms would become $\theta^2$
+irradiance terms.
+
+Figures \ref{fig:hdet} and \ref{fig:microscope} summarize the most important
+features of the dipole detection model. When $\alpha$ is very small the
+detection kernel is the usual Airy pattern weighted by $\sin^2\vartheta$. Note
+that the monopole detection model ignores the $\sin^2\vartheta$ dependence---see
+Figure \ref{fig:microscope} a) and b). As $\alpha$ grows the relative
+contribution of the higher-order Airy pattern increases. The most important
+result is that the dipole detection model is not separable into the product of
+a spatial and angular kernel---even under the paraxial approximation. The detection
+model is only separable when $\alpha$ approaches zero which is almost never the
+case in real microscopes. We refer to the non-separability of the detection
+kernel as \textit{spatio-angular coupling} because the orientation of the dipole
+is coupled to the spatial pattern of irradiance on the detector.
+
+The paraxial detection kernel is rotationally symmetric---it depends on $r_d$ instead of
+$\rd$. This symmetry is a result of the $\pi/2$ phase shift between the linear
+and radial fields on the detector. If the phase shift between the linear and
+radial fields was not exactly $\pi/2$ then the fields would interfere on the
+detector, and we would lose rotational symmetry. Tracing back further, the
+rotational symmetry is due to the fact that the field in the back focal plane
+could be written as a sum of a linear and radial field which is only true under
+the paraxial approximation---the rotational symmetry of the detection kernel is
+only true to first order. Despite the approximation, we still feel that the
+rotational symmetry of the detection kernel is a valuable result since it helps
+build an intuition about the dominant effects outside the paraxial
+approximation. Later in this work we will exploit this approximate symmetry to
+improve the efficiency of simulating and inverting the imaging model.
+
+Note that we have restricted our analysis to an imaging system with unit
+magnification. We will continue with this simplification and mention that an
+imaging system with an arbitrary magnification can be modeled using the model
+for a system with unit magnification and a change of variable (see
+\cite{barrett2004} section 7.2.7).
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/detection/detection.pdf}
+   \caption{Normalized detection kernel as a function of the scaled radial
+     detection coordinate $k\alpha r_d$, the dipole inclination angle
+     $\vartheta$, and the collection angle $\alpha$. For small
+     collection angles (left) the detection kernel of axial dipoles
+     (\textcolor{red}{\textbf{red}}) is small compared to transverse dipoles
+     (\textbf{black}), but the relative contribution of axial dipoles increases
+     with the collection angle (see \textcolor{red}{\textbf{red}} lines from
+     left to right).}
+   \label{fig:hdet}
+ \end{figure}
+
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
+   \caption{Comparison of paraxial detection models for monopole radiators a)
+     and dipole radiators b)--d). a) Monopole radiators fill the back focal
+     plane with a uniform scalar field which gives rise to the familiar Airy
+     disk on the detector. b) A transverse dipole radiator also creates an Airy
+     disk, but the back focal plane is filled with a uniform vector field. c) An
+     axial dipole radiator creates a radial electric field pattern in the back
+     focal plane which creates a higher-order Airy disk on the detector. d)
+     Dipoles that are not transverse or axial still create radially symmetric
+     irradiance patterns under the paraxial approximation. Fields from
+     transverse dipoles are real and even while fields from axial dipoles are
+     real and odd which causes a relative $\pi/2$ phase shift for the fields on
+     the detector. This phase shift means that the fields from transverse and
+     axial components of the dipole do not interfere which causes radially
+     symmetric irradiance patterns.}
+   \label{fig:microscope}
+ \end{figure}
+
+ \subsubsection{Simplified dipole imaging model}
+ Combining the results of the previous two sections yields a simplified dipole
+ imaging model 
+ \begin{align}
+g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(|\rd - \ro|, |\so\cdot \mh{z}|)f(\ro, \so).\label{eq:simplified}
+ \end{align}
+ where we have written the kernel in terms of $|\so\cdot\mh{z}| = \cos\vartheta$
+ to explicitly show the dependence on $\so$. In previous sections we showed that the
+ kernel is given by 
+ \begin{align}
+   h(r, \vartheta) &\propto h_{\text{exc}}(\vartheta)h_{\text{det}}(r,\vartheta).
+ \end{align}
+ Plugging in our results
+ \begin{align}
+   h(r, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[a_1(r)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r)\cos^2\vartheta\right]. \label{eq:sa-psf}
+ \end{align}
+
+ \subsubsection{Orientation-dependent optical transfer function}\label{sec:trans}
+  In Appendix \ref{sec:airy} we evaluate the 2D spatial Fourier transforms of
+  $a_1(r)$ and $a_2(r)$ to find that
+  \begin{align}
+    H(\nu, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[A_1(\nu)\sin^2\vartheta + \frac{1}{2}\alpha^2 A_2(\nu)\cos^2\vartheta\right].
+  \end{align}
+  where 
+\begin{align}
+  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right), \\
+  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+The STF is shown in Figure \ref{fig:odotf}. The STF has the usual
+spatial-frequency cutoff at $\nu = 2\nu_o$ for all dipole orientations.
+
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/stf/stf.pdf}
+   \caption{STF as a function of the scaled spatial frequency, the dipole
+     inclination angle $\vartheta$, and the collection angle $\alpha$. For small
+     collection angles (left) the STF for axial dipoles
+     (\textcolor{red}{\textbf{red}}) is small compared to transverse dipoles
+     (\textbf{black}), but the relative contribution of axial dipoles increases
+     with the collection angle (see \textcolor{red}{\textbf{red}} lines from
+     left to right). The STF of axial dipoles is negative at high spatial
+     frequencies because the central minimum of the axial kernel corresponds to
+     the position of the dipole. Equivalently, a high-spatial-frequency pattern
+     of axial dipoles will generate an irradiance pattern where the minimum
+     irradiance corresponds to the peak of the axial dipole density.}
+   \label{fig:odotf}
+ \end{figure}
+
+\subsubsection{Angular transfer function (ATF)}
+
+To calculate the angular transfer function we plug the spatio-angular point
+spread function Eq. \ref{eq:sa-psf} into Eq. \ref{eq:atf-prep} and evaluate the
+integrals using a computer algebra package \cite{meurer2017} to find
+\begin{alignat}{6}
+  H_l^m(r) \propto \quad 7&\{\hphantom{-}32&&a_1(r)&& + 4\alpha^2[a_1(r) + a_2(r)]&&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
+  4\sqrt{5}&\{-16&&a_1(r)&& + \hphantom{1}\alpha^2[a_1(r) + a_2(r)] &&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
+  8&\{\hphantom{-1}4&&a_1(r)&& - 2\alpha^2[a_1(r) + a_2(r)] &&+ \hphantom{1}\alpha^4a_2(r)\}&&\delta_{\ell 4}\delta_{m0}.
+\end{alignat}
+The degree $\ell$ and order $m$ of the non-zero terms in the ATF follow directly
+from specific features of the kernel. First, our kernel is symmetric under
+inversion of the dipole moment which appears in the kernel as even-degreed
+trigonometric functions. This symmetry is maintained in the ATF since all of the
+non-zero terms have an even degree $\ell=0, 2$, and $4$. Second, we showed that
+under the paraxial approximation our kernel is rotationally symmetric which
+allows us to write the kernel as a function of $r$ instead of $\mb{r}$. This
+symmetry is maintained in the ATF since all of the non-zero terms have order
+$m=0$. Finally, both the excitation and detection kernels are a weighted sum of
+degree-2 trigonometric functions which implies that the maximum degree of the
+kernel is 4. This feature of the kernel appears in the ATF since only
+$\ell=0, 2$, and $4$ terms are non-zero.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/atf/atf.pdf}
+   \caption{ATF as a function of the scaled radial detection coordinate
+     $k\alpha r$, the spherical harmonic degree $\ell$, and the collection angle
+     $\alpha$. 
+   }
+   \label{fig:atf}
+ \end{figure}
+
+ \subsubsection{Spatio-angular transfer function (SATF)}
+  \begin{alignat}{6}
+  H_l^m(\nu) \propto \quad 7&\{\hphantom{-}32&&A_1(\nu)&& + 4\alpha^2[A_1(\nu) + A_2(\nu)]&&+ 3\alpha^4A_2(\nu)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
+  4\sqrt{5}&\{-16&&A_1(\nu)&& + \hphantom{1}\alpha^2[A_1(\nu) + A_2(\nu)] &&+ 3\alpha^4A_2(\nu)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
+  8&\{\hphantom{-1}4&&A_1(\nu)&& - 2\alpha^2[A_1(\nu) + A_2(\nu)] &&+ \hphantom{1}\alpha^4A_2(\nu)\}&&\delta_{\ell 4}\delta_{m0}.
+\end{alignat}
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/satf/satf.pdf}
+   \caption{SATF as a function of the scaled spatial frequency, the spherical
+     harmonic degree $\ell$, and the collection angle $\alpha$. }
+   \label{fig:atf}
+ \end{figure}
+
+\section{Results}
+\subsection{Phantom with spatio-angular sparsity (single molecules)}
+\subsection{Phantom with spatial sparsity (rotating single molecules)}
+\subsection{Phantom with angular sparsity (actin fibers)}
+\subsection{Phantom without sparsity (most general)}
+
+\section{Discussion \tb{Very rough but open for discussion}}
+\subsection{Reconstructions}
+Since the ATF effectively contains three OTFs it is tempting to conclude that
+fluorescence microscopes pass three times as much information about the dipoles
+as monopoles. This is not true. The microscope still only measures a single
+member of $\mbb{L}_2(\mbb{R}^2)$ so at best we can recover the same amount of
+information about the object. In other words, we know immediately that the
+microscope is a rank-1 operator since it only measures one continuous function.
+
+We postpone a full discussion of SVD to find the object space singular functions
+that span the measurement space of the instrument.
+
+\subsection{Alternative transfer functions}
+Throughout this work we have used the spherical harmonic functions as a basis
+for functions on the sphere, but there are other basis functions that can be
+advantageous in some cases. Backer and others [CITE TODO] have used the second
+moments as basis functions for the sphere because they arise naturally when
+computing the spatio-angular point spread function. Mathematically, Backer and
+Lew use an alternative to the angular transfer function that uses the second
+moments as basis functions so their forward model is given by
+\begin{align}
+  g(\rd) = \sum_{j=1}^6 H_j(\rd - \ro)F_j(\ro)
+\end{align}
+where
+\begin{align}
+  H_j(\rd - \ro) &= \int_{\mbb{S}^2}d\so\, h(\rd - \ro, \so)Z_j(\so),\\
+  F_j(\ro) &= \int_{\mbb{S}^2}d\so\, f(\ro, \so)Z_j(\so),
+\end{align}
+and $Z_j(\mh{s}) = \{s_x^2, s_y^2, s_z^2, s_xs_y, s_ys_z, s_xs_z\}$ are the
+second moments. This formulation provides the main advantage of the ATF
+approach---efficient computation for spatially sparse and angularly dense
+samples---without requiring a cumbersome expansion of the spatio-angular point
+spread function onto spherical harmonics.
+
+The spherical harmonics provide several advantages over the second moments as
+well. First, the spherical harmonics form an orthonormal basis which often
+simplifies computation. For example, if we calculated the angular detection
+transfer function we would find that it contained two angular terms under the
+paraxial approximation. If we expanded onto second moments we would need all six
+angular basis functions and computing the forward model would be three times as
+expensive. Second, the spherical harmonics are complete which means they can
+represent arbitrary functions on the sphere while the second moments can only
+represent a small subset of all functions on the sphere. Extending the accuracy
+of the second moments using the fourth (or higher) moments is possible, but it
+requires a completely new basis. Indeed, the simple microscope we consider in
+this work requires an expansion onto fourth-order spherical harmonics, so an
+expansion onto second-order moments would not suffice. Finally, using the
+spherical harmonics provides access to a set of fast algorithms. The naive
+expansion of an arbitrary discretized $N$ point spherical function onto
+spherical harmonics (or second moments) requires a $\mc{O}(N^2)$ matrix
+multiplication while pioneering work by Driscoll and Healy [cite] showed that the
+forward discrete fast spherical harmonic transform can be computed with a
+$\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed with a
+$\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast algorithms exist
+for expansion onto the higher-order moments.
+
+The diffusion magnetic resonance imaging uses both sets of bases [cite Basser]
+[cite Tournier] for particular cases.
+
+\subsection{What determines the angular frequency cutoff?}
+The spatial-frequency cutoff of a fluorescence microscope is well known to vary
+as NA$/\lambda$---we can increase spatial resolution by increasing the NA of the
+instrument or by choosing a fluorophore with a shorter emission wavelength.
+Analogously, the angular-frequency spectrum of a fluorescence microscope depends
+on both the instrument and the sample.
+
+The simple paraxial microscope considered in this work always has three terms in
+its angular-frequency spectrum, but we can increase the number of terms by
+modifying the instrument. We will postpone the proper treatment of these effects
+until future work, but we briefly mention that the number of terms in the
+angular-frequency spectrum increases for non-paraxial microscopes, microscopes
+with polarizers on the illumination or detection paths, and multiview
+microscopes. We also mention that there are two ways to extend the
+angular-frequency spectrum of a microscope---by increasing the degree $\ell$ and
+by increasing the order $m$. Extending the angular degree cutoff $\ell_0$ gives
+the microscope the ability to measure finer angular features, while extending
+the angular order cutoff $m_0$ give the microscope the ability to measure
+features of the object that are increasingly invariant to rotation. If the
+angular order cutoff matches the angular degree cutoff $\ell_0 = m_0$ then the
+microscope can be said to have $\textit{isotropic angular resolution}$. This
+condition is not met by a single-view paraxial microscope since $\ell_0 = 4$ and
+$m_0 = 0$, but we will model microscopes with this property in future work.
+
+The number of terms in the angular frequency spectrum is also sample dependent.
+Monopoles emit light isotropically so they have a single term, dipoles have a
+three-term ATF, and higher-order excitation and detection moments will have even
+more terms---these objects have different angular band limits. We emphasize the
+similarity between the spatial and angular frequency cutoffs---both the sample
+and the instrument affect the maximum achievable resolution of the imaging
+system.
+
+Possibly implies that the spatio-angular transfer function can be factored. Cite
+3D vector transfer functions Arnison and Sheppard.
+
+\subsection{Characterizing real spatio-angular microscopes}
+The theoretical model we present in this work is an extreme simplification of a
+real microscope. We have ignored the effects of thick samples, optical
+aberration, scattering, high-NA objectives, finite fluorescence lifetimes, and
+interactions between fluorophores, and we are sure that this list of limitations
+could be extended. Because of this long list of unknown effects, real
+experiments should make an attempt to characterize the specific imaging system.
+
+Typical fluorescence microscopy experiments start with the monopole
+approximation and attempt to characterize the microscope by imaging
+sub-diffraction beads. These images are assumed to be good approximations of the
+monopole point spread function and this data can be used to restore (deconvolve)
+the data taken in arbitrary experiments.
+
+Imaging sub-diffraction beads is not enough to completely characterize the
+response of a microscope to a an oriented sample. We need at least three samples
+with a known orientations to characterize the SATF, so isotropic beads are not
+enough. Small beads may not be isotropic [cite Lew].
+
+\section{Conclusion}
+Most models of fluorescence microscopes use a monopole model to describe the
+object and the imaging system. A more complete description of any fluorescence
+microscope requires a dipole model of the object and a model of the
+spatio-angular point spread function. We developed several transfer functions
+that simplify the mapping between the spatio-angular density and the irradiance
+pattern on the detector, and we demonstrated these transfer functions by
+efficiently simulating a paraxial widefield fluorescence microscope.
+
+\bibliography{paper}
+\appendix
+\section{Fourier transform of linear and radial vector fields}\label{sec:ftvec}
+  \begin{align}
+  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
 \end{align}
@@
 \begin{align}
-\mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) &= \int_{0}^{\alpha}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}^{(p)}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
+\mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{0}^{\alpha}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
 \end{align}
-substitute Eq. \ref{eq:bfp2}, and apply the following identities
+plug in Eq. \ref{eq:bfp2}, and apply the following identities
 \begin{align}
@@
 \begin{align}
-  \mb{E}_{\text{det}}^{(p)}(\rd{}, \so{}) \propto &\left[\frac{J_1(k\alpha r_d)}{k\alpha r_d}y_1^1(\so{}) - i\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\cos\phi_d y_1^0(\so{})\right]\mh{x}\, + \nonumber \\& \left[\frac{J_1(k\alpha r_d)}{k\alpha r_d}y_1^{-1}(\so{}) - i\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\sin\phi_d y_1^0(\so{})\right]\mh{y}.
+  \mb{E}_{\text{det}}(\rd{}, \so{}) \propto &\left[s_x\frac{J_1(k\alpha r_d)}{k\alpha r_d} - is_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\cos\phi_d\right]\mh{x}\, + \nonumber \\& \left[s_y\frac{J_1(k\alpha r_d)}{k\alpha r_d} - i s_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\sin\phi_d\right]\mh{y}.
 \end{align}
-We can find the irradiance on the detector by taking the modulus squared of the
-electric field
+Similar to the back focal plane, we rewrite in terms of linear and radial vector
+fields
 \begin{align}
-  h_{\text{det}}(\rd{}, \so{}) &\propto |\mb{E}_{\text{det}}^{(p)}(\rd{}, \so{})|^2.
+  \mb{E}_{\text{det}}(\rd{}, \so{}) \propto \frac{J_1(k\alpha r_d)}{k\alpha r_d}[s_x\mh{x} + s_y\mh{y}] - i\alpha\frac{J_2(k\alpha r_d)}{k\alpha r_d}s_z\mh{\bs{\rho}}.
 \end{align}
-We use the real Gaunt coefficients to find that
+
+\section{Spherical harmonics}\label{sec:sph}
+% The spherical harmonics are an orthonormal set of basis functions on the sphere.
+% In this appendix we will define the basis and review several important
+% properties of this set of functions.
+The spherical harmonic function of degree $\ell$ and order $-\ell \leq m \leq m$
+is defined as \cite{schaeffer2013}
 \begin{align}
-h_{\text{det}}(\rd{}, \so{}) &\propto \left[a_1( r_d) + \frac{\alpha^2}{4} a_2( r_d)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a_1( r_d) + \frac{\alpha^2}{2} a_2( r_d)\right]y_2^0(\so{}), \label{eq:detection}
+Y_\ell^m(\vartheta, \varphi) = P_\ell^m\left(\cos\vartheta\right)\exp(i m \varphi)
 \end{align}
-where we have defined
+where $P_\ell^m(\cos\theta)$ are the associated Legendre polynomials normalized for the
+spherical harmonics 
+\begin{align}
+  P_\ell^m(x) = (-1)^m\sqrt{\frac{2\ell+1}{4\pi}}\sqrt{\frac{(\ell-|m|)!}{(\ell+|m|)!}}(1-x^2)^{|m|/2}\frac{d^{|m|}}{dx^{|m|}}P_\ell(x)
+\end{align}
+where $P_\ell(x)$ are the Legendre polynomials defined by the following recurrence
+\begin{align}
+  P_0(x) &= 1,\\
+  P_1(x) &= x,\\
+  \ell P_\ell(x) &= (2\ell-1)xP_{\ell-1}(x) - (\ell-1)P_{\ell-2}(x). 
+\end{align}
+
+The spherical harmonics are orthonormal which means that
+\begin{align}
+  \int_{\mbb{S}^2}d\mh{s}\, Y_\ell^m(\mh{s})\bar{Y}_{\ell'}^{m'}(\mh{s}) = \delta_{\ell\ell'}\delta_{mm'},
+\end{align}
+where $\delta_{\ell\ell'}$ denotes the Kronecker delta. The spherical harmonics form a
+complete basis so an arbitrary function on the sphere $f(\mh{s})$ can be
+expanded into a sum of weighted spherical harmonic functions
+\begin{align}
+  f(\mh{s}) = \sum_{\ell=0}^{\infty}\sum_{m=-\ell}^{l}F_\ell^mY_\ell^m(\mh{s}).
+\end{align}
+We can find the spherical harmonic coefficients $F_\ell^m$ for a given function by
+using Fourier's trick---multiply both sides by $\bar{Y}_\ell^m(\mh{s})$, integrate
+over the sphere, and exploit orthogonality to find that
+\begin{align}
+  F_\ell^m = \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_\ell^m(\mh{s}).
+\end{align}
+The coefficients $F_\ell^m$ are usually called the \textit{spherical Fourier
+  transform} of a spherical function.
+
+We briefly show how two properties of spherical functions propagate to the
+spherical Fourier transform. First, the spherical harmonic coefficients of
+spherical functions that can be written entirely as a function of the
+inclination angle $\vartheta$ are zero when $m\neq0$ because
+\begin{align}
+  \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)\bar{Y}_\ell^m(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
+\end{align}
+Second, the spherical harmonic coefficients of spherical functions that are
+symmetric under inversion $f(\mh{s}) = f(-\mh{s})$ are zero when $\ell$ is odd
+because $Y_\ell^m(-\so) = (-1)^\ell Y_\ell^m(\mh{s})$, so if $\ell$ is odd then
+\begin{align}
+  \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})\bar{Y}_{2n+1}^m(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})\bar{Y}_{2n+1}^m(-\mh{s}),\\
+&=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(\mh{s}) = 0.                                                                
+\end{align}
+\section{Fourier transform of first and second order Airy patterns} \label{sec:airy}
 \begin{align}
@@
 \end{align}
-
-In our analysis we have only considered a dipole radiator at the origin, but we
-can use the shift-invariance of 4$f$ imaging systems to model dipole radiators
-at arbitrary positions in the focal plane. If we shift the dipole radiator to an
-in-focus position $\ro{}$, then the irradiance pattern on the detector will be
-given by $h_{\text{det}}(\rd{} - \ro{})$. We have also restricted our analysis
-to an imaging system with unit magnification, but an imaging system with an
-arbitrary magnification can be modeled as a system with unit magnification using
-a change of variables (see \cite{barrett2004} section 7.2.7).
-
-Finally, we note the similarities between Eqs. \ref{eq:excitation} and
-\ref{eq:detection}. If we integrate the detection kernel over the detector and
-use the identity $\int_{\mbb{R}^2}d\mb{r}\, a_n(r) = 1$ for $n \in \mbb{N}$,
-then we find that the excitation and detection kernels are related by
-\begin{align}
-  h_{\text{exc}}(\so{}) = \int_{\mbb{R}^2}d\mb{r} h_{\text{det}}(\mb{r}, \so{}).
-\end{align}
-
-\subsection{Complete forward model}
-In the last two section we have found closed-form expressions for the excitation
-kernel $h_{\text{exc}}(\so{})$ and the detection kernel
-$h_{\text{det}}(\rd{} - \ro{}, \so{})$. The complete kernel of the microscope is
-the product of the excitation and detection kernels
-\begin{align}
-  h(\rd{} - \ro{}, \so{}) = h_{\text{exc}}(\so{})h_{\text{det}}(\rd{} - \ro{}, \so{}). \label{eq:kernel}
-\end{align}
-Eq. \ref{eq:kernel} gives the irradiance at position $\rd{}$ on the detector
-created by a single dipole at position $\ro{}$ with dipole oriented along
-$\so{}$.
-
-Up to this point we have only modeled the imaging system's response to single
-fluorescent molecules. We would like to model samples that contain ensembles of
-fluorescent molecules with many fluorescent molecules, so we introduce the
-\textit{spatio-angular density} to describe arbitrary distributions of
-fluorescent dipoles. We define the spatio-angular density $f(\ro{}, \so{})$ as
-the number of fluorescent molecules at position $\ro{}$ per unit volume oriented
-along $\so{}$ per unit solid angle. Figure TODO illustrates several simple
-spatio-angular densities to clarify our definition.
-
-The detector irradiance $g(\rd{})$ created by an arbitrary spatio-angular
-density $f(\ro{}, \so{})$ can be found by multiplying the spatio-angular density
-by the kernel and integrating over all positions $\ro{}$ and orientations
-$\so{}$
-\begin{align}
-g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro{}, \so{}). \label{eq:fwd}
-\end{align}
-
-\subsection{Spatio-angular transfer function}
-As written Eq. \ref{eq:fwd} is an extremely expensive integral to compute---to
-find the irradiance at a single point on the detector we need to evaluate the
-spatio-angular density and the kernel at every point in
-$\mbb{S}^2\times \mbb{R}^2$. To simplify the integral, we expand the object and
-the kernel onto complex exponentials and spherical harmonics using
-\begin{align}
-  F_l^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]f(\ro{}, \so{}),\\
-  H_l^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h(\ro{}, \so{}).
-\end{align}
-We also expand the detector irradiance onto spatial harmonics using the Fourier
-transform
-\begin{align}
-  G(\bs{\nu}) \equiv \int_{\mbb{R}^2}d\rd{}\,\text{exp}\left[i2\pi \rd{}\cdot\bs{\nu}\right]g(\rd{}).
-\end{align}
-Given these definitions, we can rewrite Eq. \ref{eq:fwd} in the frequency domain as 
-\begin{align}
-G(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^{l}H_l^m(\bs{\nu})F_l^m(\bs{\nu}). 
-\end{align}
-
-In Appendix A we calculate the spatio-angular transfer function as
-\begin{align}
-  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\},
-\end{align}
-where
-\begin{align}
-  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right), \\
-  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right),
-\end{align}
-and $C = 1 + \frac{\alpha^2}{4} + \frac{3\alpha^4}{32}$ is a normalization
-constant.
-
-\section{Results}
-
-\section{Discussion and conclusion}
-
-\bibliography{paper}
-\appendix
-\section{Evaluating the spatio-angular transfer function}
-In this appendix we will evaluate 
-\begin{align}
-    H_l^m(\bs{\nu}) &\propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h(\ro{}, \so{}),\label{eq:whole}
-\end{align}
-where
-\begin{align}
-  h(\rd{} - \ro{}, \so{}) &\propto h_{\text{exc}}(\so{})h_{\text{det}}(\rd{} - \ro{}, \so{}),\label{eq:split}\\ 
-  h_{\text{exc}}(\so{}) &\propto \left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{}),\\  
-  h_{\text{det}}(\rd{}, \so{}) &\propto \left[a_1( r_d) + \frac{\alpha^2}{4} a_2( r_d)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- a_1( r_d) + \frac{\alpha^2}{2} a_2( r_d)\right]y_2^0(\so{}),
-\end{align}
-and
-\begin{align}
-    a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
-\end{align}
-First we plug Eq. \ref{eq:split} into Eq. \ref{eq:whole} and move the excitation
-kernel out of the spatial integral
-\begin{align}
-    H_l^m(\bs{\nu}) &\propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})h_{\text{exc}}(\so{})\int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right]h_{\text{det}}(\rd{}, \so{}). \label{eq:satf}
-\end{align}
-The spatial integral requires us to evaluate the two-dimensional Fourier
-transform of $a_1(r_o)$ and $a_2(r_o)$. We will define
 \begin{align}
@@
 \end{align}
-and evaluate $A_1(\nu)$ and $A_2(\nu)$ later. After substituting \ref{eq:ftA}
-into Eq. \ref{eq:satf} we find 
-\begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\left\{\left[1 + \frac{\alpha^2}{4}\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]y_2^0(\so{})\right\} + \nonumber\\&\left\{\left[A_1(\nu) + \frac{\alpha^2}{4} A_2(\nu)\right]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left[- A_1(\nu) + \frac{\alpha^2}{2} A_2(\nu)\right]y_2^0(\so{})\right\}.
-\end{align}
-After expanding the products of spherical harmonics
-\begin{align}
-  H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\frac{3}{5}A_1(\nu) + \frac{3\alpha^2}{40}[A_1(\nu) + A_2(\nu)] + \frac{9\alpha^4}{160}A_2(\nu)\right]y_0^0(\so{})+\nonumber\\&\frac{3\sqrt{5}}{280}\left[-16A_1(\nu) + \alpha^2[A_1(\nu) + A_2(\nu)] + 3\alpha^4 A_2(\nu)\right]y_4^0(\so{})\Bigg\},\\                             H_l^m(\bs{\nu}) \propto \int_{\mbb{S}^2}d\so{}y_l^m(\so{})&\Bigg\{\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]y_0^0(\so{}) + \nonumber\\&\frac{\sqrt{5}}{56}\left[(-16 + \alpha^2)A_1(\nu) + (\alpha^2 + 3\alpha^4)A_2(\nu)\right]y_4^0(\so{})\Bigg\}.
-\end{align}
-Next, we use the orthogonality of spherical harmonics to evaluate the angular integral
-\begin{align}
-  H_l^m(\bs{\nu}) = \frac{1}{C}\Bigg\{&\left[\left(1 + \frac{\alpha^2}{8}\right)A_1(\nu) + \left(\frac{\alpha^2}{8} + \frac{3\alpha^4}{32}\right)A_2(\nu)\right]\delta_{l0}\delta_{m0}+\nonumber\\&\frac{2\sqrt{5}}{7}\left[\left(-1 + \frac{\alpha^2}{16}\right)A_1(\nu) + \left(\frac{\alpha^2}{16} + \frac{3\alpha^4}{16}\right)A_2(\nu)\right]\delta_{l4}\delta_{m0}\Bigg\},
-\end{align}
-where $C = 1 + \frac{\alpha^2}{4} + \frac{3\alpha^4}{32}$ is a normalization
-constant.
 
@@
 \begin{align}
-  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - 2\left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
+  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
 \end{align}
+% \section{Evaluating the angular transfer function}
+% Our goal in this Appendix is to calculate the angular transfer function by
+% taking the spherical Fourier transform of
+% \begin{align}
+%   h(r, \vartheta) = h_{\text{exc}}(\vartheta)h_{\text{det}}(r, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[a_1(r)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r)\cos^2\vartheta.\right] \label{eq:kernel}
+% \end{align}
+% We need to evaluate the integrals
+% \begin{align}
+%   F_l^m(r) \propto \int_{\mbb{S}^2} d\so h_{\text{exc}}(\vartheta)h_{\text{det}}(r, \vartheta)Y_\ell^m(\vartheta, \varphi). \label{eq:atf}
+% \end{align}
+% We could evaluate the integrals in Eq.
+% \ref{eq:kernel} using a computer algebra system, but here we evaluate by hand to
+% demonstrate a useful trick for taking the spherical harmonic transform of the
+% product of two spherical functions. First, we expand both the excitation and
+% detection kernels in a sum of spherical harmonic functions
+% \begin{align}
+%   F_l^m(r) \propto \int_{\mbb{S}^2} d\so \left[\sum_{{\ell'} m'}H_{{\ell'},\text{exc}}^{m'} Y_{\ell'}^{m'}(\vartheta, \varphi)\right]\left[\sum_{{\ell''} m''}H_{{\ell''},\text{det}}^{m''}(r) Y_{\ell''}^{m''}(\vartheta, \varphi)\right]Y_\ell^m(\vartheta, \varphi).
+% \end{align}
+% Next, we exchange the order of the sums and integrals
+% \begin{align}
+%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) \int_{\mbb{S}^2} d\so Y_\ell^m(\vartheta, \varphi) Y_{\ell'}^{m'}(\vartheta, \varphi) Y_{\ell''}^{m''}(\vartheta, \varphi).
+% \end{align}
+% Finally, if we make the definition
+% \begin{align}
+%   G_{\ell\ell'\ell''}^{mm'm''} = \int_{\mbb{S}^2}d\so\, Y_\ell^m(\vartheta, \varphi) Y_{\ell'}^{m'}(\vartheta, \varphi) Y_{\ell''}^{m''}(\vartheta, \varphi)
+% \end{align}
+% and write the angular transfer function as
+% \begin{align}
+%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) G_{\ell\ell'\ell''}^{mm'm''}. 
+% \end{align}
+% This is a valuable result because it allows us to compute the spherical harmonic
+% transform of the detection and excitation kernels individually then combine the
+% results into the final angular transfer function. The constants
+% $G_{\ell\ell'\ell''}^{mm'm''}$ are called the \textit{Gaunt coefficients} and
+% can be precomputed or found in tables.
+
+% Next, we compute the spherical Fourier transform of the excitation kernel. 
+% \begin{align}
+%   H_{\ell',\text{exc}}^{m'} \propto \int_{\mbb{S}^2}d\so\, h_{\text{exc}}(\vartheta)Y_{\ell}^m(\vartheta, \varphi). 
+% \end{align}
+% From Appendix \ref{sec:sph} we know that the integral will be zero except when
+% $m=0$ and when $\ell$ is even. Starting with $\ell = 0$ and $m=0$
+% \begin{align}
+%   H_{0,\text{exc}}^{0} \propto \int_{\mbb{S}^2}d\so\, \left[\sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta\right]\left[\frac{1}{\sqrt{4\pi}}\right] = \frac{4\sqrt{\pi}}{3}\left[1 + \frac{\alpha^2}{4}\right].
+% \end{align}
+% Next we evaluate $\ell = 2$ and $m=0$
+% \begin{align}
+%   H_{2,\text{exc}}^{0} \propto \int_{\mbb{S}^2}d\so\, \left[\sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta\right]\left[\sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1)\right] = \frac{4\sqrt{\pi}}{3}\frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right].
+% \end{align}
+% Finally, we notice can verify that the excitation kernel can be written as just
+% two spherical harmonics using the equality
+% \begin{align}
+%  h_{\text{exc}}(r, \vartheta) &= H_{0,\text{exc}}^0Y_0^0(\vartheta, \varphi) + H_{2,\text{exc}}^0Y_2^0(\vartheta, \varphi),\\
+%   \sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta &= \frac{4\sqrt{\pi}}{3}\left[1 + \frac{\alpha^2}{4}\right]\left[\frac{1}{\sqrt{4\pi}}\right] + \frac{4\sqrt{\pi}}{3}\frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]\left[\sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1)\right].
+% \end{align}
+
+% \begin{align}
+%   H_{\ell',\text{exc}}^{m'} \propto \left[1 + \frac{\alpha^2}{4}\right]\delta_{\ell'0}\delta_{m0} + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{4}\right]\delta_{\ell'0}\delta_{m0}.
+% \end{align}
+% Similarly, the spherical Fourier transform of the detection kernel is given by
+% \begin{align}
+%   H_{\ell'',\text{det}}^{m''} \propto \left[a_1(r) + \frac{\alpha^2}{4}a_2(r)\right]\delta_{\ell''0}\delta_{m0} + \frac{1}{\sqrt{5}}\left[-a_1(r) + \frac{\alpha^2}{4}a_2(r)\right]\delta_{\ell''0}\delta_{m0}.
+% \end{align}
+% Finally, we use the Gaunt coefficients to calculate the angular transfer function
+% \begin{align}
+%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) G_{\ell\ell'\ell''}^{mm'm''}.   
+% \end{align}
+% \begin{alignat}{6}
+%   F_l^m(r) \propto \quad 7&\{\hphantom{-}32&&a_1(r)&& + 4\alpha^2[a_1(r) + a_2(r)]&&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
+%   4\sqrt{5}&\{-16&&a_1(r)&& + \hphantom{1}\alpha^2[a_1(r) + a_2(r)] &&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
+%   8&\{\hphantom{-1}4&&a_1(r)&& - 2\alpha^2[a_1(r) + a_2(r)] &&+ \hphantom{1}\alpha^4a_2(r)\}&&\delta_{\ell 4}\delta_{m0}.
+% \end{alignat}
+% H0
+% 28*A1*a**2 + 224*A1 + 21*A2*a**4 + 28*A2*a**2
+% (Pdb) H2
+% 4*sqrt(5)*(A1*a**2 - 16*A1 + 3*A2*a**4 + A2*a**2)
+% (Pdb) H4
+% -16*A1*a**2 + 32*A1 + 8*A2*a**4 - 16*A2*a**2
 

### 2018-10-20 papers/basic-theory/calculations/stf-integral.py

@@ -1,0 +1,20 @@
+from sympy import *
+
+a = Symbol('a')
+A1 = Symbol('A1')
+A2 = Symbol('A2')
+theta = Symbol('theta')
+phi = Symbol('phi')
+
+Y00 = Ynm(0, 0, theta, phi).expand(func=True)
+Y20 = Ynm(2, 0, theta, phi).expand(func=True)
+Y40 = Ynm(4, 0, theta, phi).expand(func=True)
+
+# Calc expansions
+# hh = sin(theta)**2 + ((a**2)/2)*cos(theta)**2
+hh = (sin(theta)**2 + ((a**2)/2)*cos(theta)**2)*(A1*sin(theta)**2 + A2*((a**2)/2)*cos(theta)**2)
+c = 4*15*7/(2*sqrt(pi))
+H0 = c*simplify(integrate(expand(2*pi*sin(theta)*hh*Y00), (theta, 0, pi)))
+H2 = c*simplify(integrate(expand(2*pi*sin(theta)*hh*Y20), (theta, 0, pi)))
+H4 = c*simplify(integrate(expand(2*pi*sin(theta)*hh*Y40), (theta, 0, pi)))
+import pdb; pdb.set_trace() 

### 2018-10-20 papers/basic-theory/figures/atf/atf.py

@@ -1,0 +1,80 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.gridspec as gridspec
+import scipy.misc
+from scipy import special
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+
+
+inches = 2
+rows = 1
+cols = 3
+widths = [1,1,1]
+heights = [1]
+hspace = 0.05
+wspace = 0.15
+
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
+                        inches*(np.sum(heights))))
+
+outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
+                               width_ratios=widths, height_ratios=heights,
+                               hspace=hspace, wspace=wspace)
+
+def an(krda, n):
+    return (n/np.pi)*((special.jn(n, krda)/(krda))**2)
+
+def hdet(krd, theta, alpha):
+    return an(krd*alpha, 1)*np.sin(theta)**2 + 0.5*an(krd*alpha, 2)*(alpha**2)*(np.cos(theta)**2)
+
+def ATF(l, krd, alpha):
+    if l == 0:
+        return 7*(32*an(krd*alpha, 1) + 4*(alpha**2)*(an(krd*alpha, 1) + an(krd*alpha, 2)) + 3*(alpha**4)*an(krd*alpha, 2))
+    if l == 2:
+        return 4*np.sqrt(5)*(-16*an(krd*alpha, 1) + (alpha**2)*(an(krd*alpha, 1) + an(krd*alpha, 2)) + 3*(alpha**4)*an(krd*alpha, 2))
+    if l == 4:
+        return 8*(4*an(krd*alpha, 1) - 2*(alpha**2)*(an(krd*alpha, 1) + an(krd*alpha, 2)) + (alpha**4)*an(krd*alpha, 2))
+
+alphas = [np.pi/8, np.pi/4, 3*np.pi/8]
+alpha_strs = ['\\pi/8', '\\pi/4', '3\\pi/8']
+for col in range(cols):
+    alpha = alphas[col]
+    ax = f.add_subplot(outer_grid[0, col])
+    ax.set_xlim([0,7])
+    ax.set_ylim([-0.75,1])
+
[…]

### 2018-10-20 papers/basic-theory/figures/detection-coords/detection-coords.py

@@ -107,24 +107,24 @@ for outer_row in range(outer_rows):
                     if inner_row == 0:
                         ax.text(-2.75,0,'Axial view', ha='center', va='center', transform=ax.transData, rotation=90)
                         my_axes(-2,0,0,['\mathbf{\hat{z}}','\mathbf{\hat{y}}','\mathbf{\hat{x}}'], ax, dot=True)
-                        rr = 1.7
-                        theta = np.arctan(0.5)
-                        x0 = rr*np.cos(theta)
-                        y0 = rr*np.sin(theta)                        
-                        ax.arrow(x0, y0, 0.4*np.cos(theta + np.pi/2), 0.4*np.sin(theta + np.pi/2), head_width=0.05, fc='k', transform=ax.transData, clip_on=False)
-                        ax.scatter([x0], [y0], edgecolors='k', facecolors='w', marker='o', lw=0.5, clip_on=False, s=[10], zorder=9, transform=ax.transData)
-                        ax.scatter([x0], [y0], c='k', marker='.', lw=0.5, clip_on=False, s=[6.5], zorder=10, transform=ax.transData)
-                        ax.text(x0-0.4, y0+0.1, '$\hat{\\boldsymbol{\phi}}$', ha='center', va='center', transform=ax.transData)
-                        ax.text(x0-0.4, y0+0.6, '$\hat{ \\boldsymbol{\\theta}}$', ha='center', va='center', transform=ax.transData)
+                    #     rr = 1.7
+                    #     theta = np.arctan(0.5)
+                    #     x0 = rr*np.cos(theta)
+                    #     y0 = rr*np.sin(theta)                        
+                    #     ax.arrow(x0, y0, 0.4*np.cos(theta + np.pi/2), 0.4*np.sin(theta + np.pi/2), head_width=0.05, fc='k', transform=ax.transData, clip_on=False)
+                    #     ax.scatter([x0], [y0], edgecolors='k', facecolors='w', marker='o', lw=0.5, clip_on=False, s=[10], zorder=9, transform=ax.transData)
+                    #     ax.scatter([x0], [y0], c='k', marker='.', lw=0.5, clip_on=False, s=[6.5], zorder=10, transform=ax.transData)
+                    #     ax.text(x0-0.4, y0+0.1, '$\hat{\\boldsymbol{\phi}}$', ha='center', va='center', transform=ax.transData)
[…]

### 2018-10-20 papers/basic-theory/figures/excitation-coords/excitation-coords.py

@@ -89,27 +89,26 @@ for outer_row in range(outer_rows):
                     l4 = lines.Line2D([1+wsi/2,1+wsi/2], [-0.2,-0.3], c='k', lw=1, transform=ax.transAxes)
                     f.lines.extend([l1, l2, l3, l4])
 
-                    
-                if inner_col == 2:
-                    if inner_row == 0:
-                        rr = 1.7
-                        theta = np.arctan(0.5)
-                        x0 = -rr*np.cos(theta)
-                        y0 = rr*np.sin(theta)                        
-                        ax.arrow(x0, y0, -0.4*np.cos(theta + np.pi/2), 0.4*np.sin(theta + np.pi/2), head_width=0.05, fc='k', transform=ax.transData, clip_on=False)
-                        ax.scatter([x0], [y0], edgecolors='k', facecolors='w', marker='o', lw=0.5, clip_on=False, s=[10], zorder=9, transform=ax.transData)
-                        ax.scatter([x0], [y0], c='k', marker='.', lw=0.5, clip_on=False, s=[6.5], zorder=10, transform=ax.transData)
-                        ax.text(x0+0.4, y0+0.1, '$\hat{\\boldsymbol{\phi}}$', ha='center', va='center', transform=ax.transData)
-                        ax.text(x0+0.4, y0+0.6, '$\hat{ \\boldsymbol{\\theta}}$', ha='center', va='center', transform=ax.transData)
+                # if inner_col == 2:
+                    # if inner_row == 0:
+                    #     rr = 1.7
+                    #     theta = np.arctan(0.5)
+                    #     x0 = -rr*np.cos(theta)
+                    #     y0 = rr*np.sin(theta)                        
+                    #     ax.arrow(x0, y0, -0.4*np.cos(theta + np.pi/2), 0.4*np.sin(theta + np.pi/2), head_width=0.05, fc='k', transform=ax.transData, clip_on=False)
+                    #     ax.scatter([x0], [y0], edgecolors='k', facecolors='w', marker='o', lw=0.5, clip_on=False, s=[10], zorder=9, transform=ax.transData)
+                    #     ax.scatter([x0], [y0], c='k', marker='.', lw=0.5, clip_on=False, s=[6.5], zorder=10, transform=ax.transData)
[…]

### 2018-10-20 papers/basic-theory/figures/microscope/microscope.py

@@ -68,7 +68,7 @@ for outer_row in range(outer_rows):
                     f.lines.extend([l1, l2, l3, l4])
                 
                 if outer_col == 0 and inner_col == 0:
-                    row_labels = ['Detector\n intensity',
+                    row_labels = ['Detector\n irradiance',
                                   'Tube\n lens',
                                   'Back focal\n plane\n electric field',
                                   'Objective\n lens',
@@ -93,12 +93,12 @@ for outer_row in range(outer_rows):
                     if outer_col == 1 and inner_col == 0:
                         brace_lines(ax)
                         ax.text(1.0+wspace_inner/2,-0.4,'b) $\\vartheta = \pi/2$\n dipole radiator', ha='center', va='top', transform=ax.transAxes)
-                    if outer_col == 2 and inner_col == 0:
-                        brace_lines(ax)                        
-                        ax.text(1.0+wspace_inner/2,-0.4,'c) $\\vartheta = \pi/10$\n dipole radiator', ha='center', va='top', transform=ax.transAxes)
                     if outer_col == 3 and inner_col == 0:
                         brace_lines(ax)                        
-                        ax.text(1.0+wspace_inner/2,-0.4,'d) $\\vartheta = 0$\n dipole radiator', ha='center', va='top', transform=ax.transAxes)
+                        ax.text(1.0+wspace_inner/2,-0.4,'d) $\\vartheta = \pi/10$\n dipole radiator', ha='center', va='top', transform=ax.transAxes)
+                    if outer_col == 2 and inner_col == 0:
+                        brace_lines(ax)                        
+                        ax.text(1.0+wspace_inner/2,-0.4,'c) $\\vartheta = 0$\n dipole radiator', ha='center', va='top', transform=ax.transAxes)
 
                 if inner_row == 0:
                     if inner_col == 0:
@@ -118,10 +118,10 @@ for outer_row in range(outer_rows):
                     a = k*alpha
                     if outer_col == 0 or outer_col == 1:
                         z = (special.jn(1,a*r)/(a*r))**2
-                    if outer_col == 2:
+                    if outer_col == 3:
                         theta = np.pi/10
                         z = (1 - np.cos(theta)**2)*(special.jn(1,a*r)/(a*r))**2 + 0.5*np.cos(theta)**2*(special.jn(2,a*r)/(a*r))**2
[…]

### 2018-10-20 papers/basic-theory/figures/od-otf/stf.py

@@ -1,0 +1,81 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.gridspec as gridspec
+import scipy.misc
+from scipy import special
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+
+
+inches = 2
+rows = 1
+cols = 3
+widths = [1,1,1]
+heights = [1]
+hspace = 0.05
+wspace = 0.15
+
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
+                        inches*(np.sum(heights))))
+
+outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
+                               width_ratios=widths, height_ratios=heights,
+                               hspace=hspace, wspace=wspace)
+
+def A1(nu):
+    return (2/np.pi)*(np.arccos(nu/2) - (nu/2)*np.sqrt(1 - (nu/2)**2))
+
+def A2(nu):
+    return (2/np.pi)*(np.arccos(nu/2) - (3 - 2*((nu/2)**2))*(nu/2)*np.sqrt(1 - (nu/2)**2))
+
+def Hdet(nu, theta, alpha):
+    return A1(nu)*np.sin(theta)**2 + 0.5*A2(nu)*(alpha**2)*(np.cos(theta)**2)
+
+def hexc(theta, alpha):
+    return np.sin(theta)**2 + 0.5*(alpha**2)*(np.cos(theta)**2)
+
+def OTF(nu, theta, alpha):
+    return hexc(theta, alpha)*Hdet(nu, theta, alpha)
+
+alphas = [np.pi/8, np.pi/4, 3*np.pi/8]
+alpha_strs = ['\\pi/8', '\\pi/4', '3\\pi/8']
+for col in range(cols):
+    alpha = alphas[col]
+    ax = f.add_subplot(outer_grid[0, col])
+    ax.set_xlim([0,2])
+    ax.set_ylim([-0.25,1])
+
+    thetas = [0, np.pi/8, np.pi/4, 3*np.pi/8, np.pi/2]
+    theta_strs = ['0', '$\pi/8$', '$\pi/4$', '$3\pi/8$', '$\pi/2$']
+    for theta in thetas:
+        nu = np.linspace(1e-3, 2, 100)
[…]

### 2018-11-02 papers/basic-theory/paper/paper.tex
Latest draft.

@@
-\documentclass{osa-article}
+\documentclass[]{osa-article}
 
@@
 % Talon's custom commands
+\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
+\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
 \newcommand{\argmin}{\arg\!\min}
@@
 \providecommand{\mb}[1]{\mathbf{#1}}
+\providecommand{\msf}[1]{\mathsf{#1}}
 \providecommand{\mf}[1]{\mathfrak{#1}}
@@
   spatio-angular transfer function (SATF). We demonstrate our formalism by
-  analyzing a paraxial single-view fluorescence microscope without using the
+  analyzing a single-view paraxial epi-fluorescence microscope without using the
   monopole or scalar approximations. We show that this microscope has an angular
   band limit, and we demonstrate the value of the transfer function approach by
-  efficiently simulating the imaging process with numerical phantoms. Notably,
-  we show that information about the out-of-plane orientation of ensembles of
-  in-focus fluorophores is imaged in paraxial widefield fluorescence
-  microscopes. We discuss the implications of our analysis for all quantitative
-  fluorescence microscopy studies and lay out a path towards a complete theory.
+  efficiently simulating the imaging process with simple phantoms. Notably, we
+  show that information about the out-of-plane orientation of ensembles of
+  in-focus fluorophores is recorded by paraxial epi-fluorescence microscopes. We
+  discuss the implications of our analysis for all quantitative fluorescence
+  microscopy studies and lay out a path towards a complete theory.
 \end{abstract*}
 
-\section{Introduction \tb{needs work}}
+\section{Introduction}
 
 Fluorescence microscopes are widely used in the biological sciences for
-measuring the distribution of fluorophores throughout a sample [cite]. While an
-unprocessed fluorescence micrograph reports the approximate distribution of
-fluorophores throughout a sample, all microscopes are diffraction limited
-[cite], so the image is a blurred version of the true fluorophore distribution.
-Therefore, microscopists who are interested in optimal measurements will perform
-a computational restoration to recover some of the information lost during the
-imaging process.
+measuring the spatial distribution of fluorophores throughout a sample [cite].
+While an unprocessed fluorescence micrograph reports the approximate
+distribution of fluorophores throughout a sample, all microscopes are
+diffraction limited [cite], so the image is a blurred version of the true
+fluorophore distribution.
 
@@
 
+The widely-used monopole model treats fluorophores as molecules that absorb and
+emit light isotropically. Despite their use in models, monopole
+absorber/emitters do not exist in nature. All real fluorophores absorb and emit
+light anisotropically, and in this work we investigate the more realistic dipole
+model of fluorophores. Since the absorption and emission patterns of many widely
+used fluorophores including green fluroescent protein (GFP) are known to be well
+described by the dipole model [cite Inoue], we start by considering the dipole
+model before higher-order multipole models.
+
+The scalar approximation is another widely-used approximation in fluorescence
+microscopy. The scalar approximation models the propagation of light using a
+scalar-valued field $U$ instead of the more realistic vector-valued electric
+field $\mb{E}$. Although the scalar model yields realistic results in many
+cases, the scalar field ignores polarization-dependent effects. The absorption
+and emission response of dipoles strongly depends on the polarization of the
+fields, so we need to use an electromagnetic model of light propagation to
+accurately model a microscope imaging dipoles.
+
 This work lies at the intersection of three classes of fluorescence microscopy:
-(1) single-molecule localization microscopy (SMLM), (2) spatial ensemble
+(1) single molecule localization microscopy (SMLM), (2) spatial ensemble
 fluorescence microscopy including widefield, confocal, and light-sheet
 techniques, and (3) polarized fluorescence microscopy. We briefly review these
-three classes and focus on their restoration techniques and use of the monopole
-and scalar approximations.
+three classes and focus on their use of the monopole and scalar approximations.
 
@@
 single molecule is fluorescing in the sample, the measured intensity pattern is
-strongly dependent on the orientation of the emitting molecule. Backlund and Lew
-\cite{backlund2014} have shown that ignoring the orientation of fluorophores can
-bias position estimates, so the most accurate SMLM experiments must jointly
-estimate the position and orientation of each molecule.
+strongly dependent on the orientation of the emitting molecule. Backlund [cite]
+and Lew [cite] \cite{backlund2014} have shown that ignoring the orientation of
+fluorophores can bias position estimates, so the most accurate SMLM experiments
+must jointly estimate the position and orientation of each molecule.
 
@@
 arithmetic, but these techniques do not perform any spatial restoration so they
-do not use all of the information available to the microscopist. To our
-knowledge no work has been done to model the complete spatio-angular response of
-fluorescence microscopes to ensembles of oriented fluorophores.
-
-\tb{Out of date}
-In this work we model ensembles of in-focus dipole absorber/emitters using
-electromagnetic optics and the paraxial approximation. In section 2 we model the
-excitation and detection processes of dipoles, and we define the most important
-quantity in this work---the spatio-angular transfer function (SATF). We
-calculate the SATF and show that fluorescence microscopes have an angular band
-limit. In section 3 we perform simulations and compare our model to traditional
-scalar models. In section 4 we discuss the implications of our work for
-fluorescence microscopy and lay out a path towards a complete spatio-angular
-theory of fluorescence microscopy.
-
-\subsection{Monopole emission vs. dipole emission \tb{not sure where this section should live}}
-Consider a single dipole radiator at the origin with its dipole moment oriented
-along a direction $\so$. The dipole emitter creates a time-harmonic electric
-field at a position $\mb{r}$ far from the dipole proportional to
-\begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}\, \mh{r}\times\so\times\mh{r}.\label{eq:dip}
-\end{align}
-A typical approach to deriving Equation \ref{eq:dip} is to (1) use Maxwell's
-equations to derive the inhomogeneous electromagnetic wave equations then (2)
-use potentials to solve the wave equations with a dipole source term, then (3)
-drop the terms that decay faster than $1/|\mb{r}|$ [cite Jackson, Novotny,
-Teich]. Equation~\ref{eq:dip} shows that dipole radiators emit spherical
-wavefronts of polarized light with amplitude proportional to $\cos\theta$ where
-$\theta$ is the angle between the field point $\mb{r}$ and the dipole axis
-$\so$.
-
-Many models of fluorophores approximate the vector field on the left hand side
-of Equation \ref{eq:dip} with a scalar field---the \textit{scalar
-  approximation}---and drop the orientation dependence on the right hand
-side---the \textit{monopole approximation}. The approximated field is given by
-\begin{align}
-  U_{\text{ff}}(\mb{r}) \propto \frac{\text{exp}[ik|\mb{r}|]}{|\mb{r}|}. \label{eq:mono}
-\end{align}
-Models that use Equation \ref{eq:mono} as a starting point do not account for
-polarization or dipole orientation effects.
-
-\section{Theory \tb{outline is okay, subsections vary, recently moved changes of basis to the front}}
+do not use all of the available information. To our knowledge no work has been
+done to model the complete spatio-angular response of fluorescence microscopes
+to ensembles of oriented fluorophores.
+
+We begin in Section \ref{sec:theory} by formulating the imaging problem
+mathematically. We start with an abstract description of fluorescence imaging
+systems and extend the usual monopole imaging model to dipoles. Along the way we
+introduce transfer functions that will allow us to efficiently simplify our
+analysis of spatio-angular microscopes. In Section \ref{sec:results} we use the
+mathematical tools we developed in Section \ref{sec:theory} to analyze and
+simulate a single-view paraxial epi-fluorescence microscope, and we demonstrate
+our model with four simple phantoms. Finally, in Section \ref{sec:discussion} we
+discuss the results and their broader implications.
+
+\section{Theory}\label{sec:theory}
 We begin our analysis with the abstract Hilbert space formalism of Barrett and
 Myers \cite{barrett2004}. Our first task is to formulate the imaging process as
-a mapping between two Hilbert spaces $\mc{H}: \mbb{U} \rightarrow \mbb{V}$ where
+a mapping between two Hilbert spaces $\mc{H}: \mbb{U} \rightarrow \mbb{V}$, where
 $\mbb{U}$ is a set than contains all possible objects, $\mbb{V}$ is a set that
@@
 $\mbb{V}$ with $\mb{g}$, and the mapping between the spaces with
-
 \begin{align}
@@
 data-space basis. In most cases the easiest mapping to find uses a
-delta-function basis---we expand object and data space into delta functions then
-express the mapping as an integral transform. After finding this mapping we can
-start to investigate the same mapping in different bases.
+delta-function basis---we expand object and data space into delta functions,
+then express the mapping as an integral transform. After finding this mapping we
+can start to investigate the same mapping in different bases.
 
@@
 extend the monopole imaging model to dipoles and examine the mapping in four
-different bases. In Section \ref{sec:para} we will examine the mappings for a
-more specific case---a paraxial epi-illumination single-view fluorescence
-microscope.
-
-\subsection{Monopole imaging in different bases \tb{50\%}}\label{sec:monopole}
+different bases.
+
+\subsection{Monopole imaging in different bases}\label{sec:monopole}
 We start by considering a microscope that images a field of in-focus monopoles
-by recording the irradiance on a two-dimensional detector. We can represent
-the object as a function that assigns a real number to each point on a plane,
-so we identify object space as $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$. Similarly, we
-have a two-dimensional detector that measures a real number at every point on 
-a plane, so data space is the same set $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$. Our
-first task is complete---we have identified the geometry of object and data
-space.
-
-Next, we find and name the representations of our object and data in a
-specific basis. In a delta function basis the object can be represented by a
-function $f(\ro)$ called the \textit{monopole density}---the number of
-monopoles at the two-dimensional position $\ro$ per unit area. Similarly, in a
-delta function basis the data can be represented by a function $g(\rd)$ called
-the \textit{irradiance}---the power received by a surface at position $\rd$
-per unit area. It may seem pedantic to emphasize that these representations
-are in a delta function basis, but we highlight this point to make it clear
-that the delta function basis is not special---we can choose a different basis
-at will.
-
-% We start by considering a field of in-focus monopoles that have been excited by test
-% a spatially uniform beam. As the fluorophores relax, they emit scalar waves in
-% the form of Equation \ref{eq:mono}. The waves propagate through the microscope
-% and we measure the irradiance on a two dimensional detector.
+by recording the irradiance on a two-dimensional detector. This section treads
+familiar ground, but it serves to establish the concepts and notation that will
+be necessary when we extend to the dipole case.
+
+We can represent the object as a function that assigns a real number to each
+point on a plane, so we identify object space as
+$\mbb{U} = \mbb{L}_2(\mbb{R}^2)$. Similarly, we have a two-dimensional detector
+that measures a real number at every point on a plane, so data space is the same
+set $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$.
+
+Next, we name the representations of our object and data in a specific basis. In
+a delta function basis the object can be represented by a function $f(\ro)$
+called the \textit{spatial monopole density}---the number of monopoles per unit
+area at the two-dimensional position $\ro$. Similarly, in a delta function basis
+the data can be represented by a function $g'(\rd')$ called the
+\textit{irradiance}---the power received by a surface per unit area at position
+$\rd'$. It may seem pedantic to emphasize that these representations are in a
+delta function basis, but we highlight this point to make it clear that the
+delta function basis is not special---we can choose a different basis at will.
 
@@
 object and the data is \textit{linear}---this is usually true in fluorescence
-microscopes since fluorophores emit incoherently so a scaled sum of fluorophores
-will result in a scaled sum of the irradiance patterns created by the individual
-fluorophores. If the mapping is linear we can write the irradiance as the
-integral over a field of monopoles weighted by the detector response due to
-single monopoles
-\begin{align}
-g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd,\ro)f(\ro), \label{eq:fwdmono}
-\end{align}
-where $h(\rd{}, \ro{})$ is the kernel of the integral transform.
-
-Most fluorescence microscopes are (at least approximately) shift-invariant,
-which means that shifting the object will result in a corresponding shift of the
-data. The mapping between an object and the data in a linear shift-invariant
-fluorescence microscope can be written as
-\begin{align}
-  g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro).  \label{eq:lsi}
-\end{align}
-When the imaging system is shift invariant the kernel $h(\rd - \ro)$ is usually
-called the \textit{point spread function}.
+microscopes since fluorophores emit incoherently, so a scaled sum of
+fluorophores will result in a scaled sum of the irradiance patterns created by
+the individual fluorophores. If the mapping is linear, we can write the
+irradiance as a weighted integral over a field of monopoles
+\begin{align}
+g'(\rd') = \int_{\mbb{R}^2}d\ro\, h'(\rd',\ro)f(\ro), \label{eq:fwdmono}
+\end{align}
+where $h'(\rd{}', \ro{})$ is the irradiance at position $\rd'$ created by a
+point source at $\ro$.
+
+The irradiance pattern measured by many fluorescence microscopes can be modeled
+(at least approximately) as a magnifier with shift-invariant blur
+\begin{align}
+  g'(\rd') = \int_{\mbb{R}^2}d\ro\, h'(\rd' - m\ro)f(\ro), 
+\end{align}
+where $m$ is a magnification factor. To simplify our analysis we define a
+demagnified detector coordinate $\rd = \rd'/m$ and a normalization factor that
+corresponds to the total power incident on the detector plane due to a point
+source $P_{\text{mono}} = \int_{\mbb{R}^2}d\mb{r}\,h'(m\mb{r})$. We use these scaling
+factors to define the \textit{point spread function} as
+\begin{align}
+  h(\rd - \ro) = \frac{h'(m[\rd - \ro])}{P_{\text{mono}}},
+\end{align}
+and the \textit{scaled irradiance} as
+\begin{align}
+  g(\rd) = \frac{g'(m\rd)}{P_{\text{mono}}}.
+\end{align}
+With these definitions we can express the mapping between the object and the
+data as a familiar convolution
+\begin{align}
+  g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro),  \label{eq:lsi}
+\end{align}
+which will allow us to analyze this class of microscopes without carrying
+magnification or normalization factors. We will mostly be using scaled
+coordinates, so we have adopted a slightly unusual convention of using primes to
+denote unscaled coordinates.
+
+We have chosen to normalize the point spread function so that
+\begin{align}
+  \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}) = 1. \label{eq:norm}
+\end{align}
+The point spread function corresponds to a measurable irradiance, so it is
+always real-valued and positive.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=1.0]{../figures/monopole-block/monopole-block.pdf}
+  \caption{The mapping between the object and data space of a monopole
+    fluorescence microscope can be computed in two different bases---a delta
+    function basis and a spatial harmonic basis. The change of basis is given by
+    the two-dimensional Fourier transform denoted $\mathcal{F}_{\mbb{R}^2}$.}
+     \label{fig:monopole-block}      
+\end{figure}
 
@@
 \end{align}
-where the \textit{irradiance spectrum} is given by
+where we define the \textit{scaled irradiance spectrum} as
 \begin{align}
@@
 \end{align}
-the \textit{optical transfer function} is given by
-\begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
-\end{align}
-and the \textit{monopole spectrum} is given by
+the \textit{optical transfer function} as
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),\label{eq:otf}
+\end{align}
+and the \textit{monopole spectrum} as
 \begin{align}
@@
 \end{align}
+The point spread function is normalized and real-valued, so we know that the
+optical transfer function is normalized $H(0) = 1$ and conjugate-symmetric
+$H(-\bs{\nu}) = H^*(\bs{\nu})$.
+
 Notice that Eqs. \ref{eq:lsi} and \ref{eq:freq} are expressions of the same
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[scale=1.0]{../figures/monopole-block/monopole-block.pdf}
-  \caption{We can compute the mapping between object space and data space using
-    two different bases.}
-     \label{fig:monopole-block}      
-\end{figure}
-
-\subsection{Dipole imaging in different bases \tb{50\%}}\label{sec:dipole}
-Now we consider a microscope imaging a field of in-focus \textit{dipoles} by
-recording the irradiance on a two-dimensional detector. A function that assigns
-a real number to each point on a plane is not sufficient to specify a field of
-dipoles because the dipoles can have different orientations. To represent the
-object we need to extend object space to
-$\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ where $\mbb{S}^2$ is the
-two-dimensional sphere (the usual sphere embedded in $\mbb{R}^3$).
+\subsubsection{Monopole coherent transfer functions}
+
+\subsection{Dipole imaging in different bases}\label{sec:dipole}
+Now we consider a microscope imaging a field of in-focus dipoles by recording
+the irradiance on a two-dimensional detector. A function that assigns a real
+number to each point on a plane is not sufficient to specify a field of dipoles
+because the dipoles can have different orientations. To represent the object we
+need to extend object space to $\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$
+where $\mbb{S}^2$ is the two-dimensional sphere (the usual sphere embedded in
+$\mbb{R}^3$).
 
 In a delta function basis the object can be represented by a function
-$f(\ro, \so)$ called the \textit{spatio-angular density}---the number of dipoles
-at position $\ro{}$ per unit area oriented along $\so{}$ per unit solid angle.
-If the imaging system is linear and shift invariant then the mapping between
-object and data space can be expressed in a delta function basis as
-  \begin{align}
-g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro, \so), \label{eq:odpsf}
-  \end{align}
-  where $h(\rd - \ro, \so)$ is the \textit{orientation-dependent point spread
-    function}.
-
+$f(\ro, \so)$ called the \textit{spatio-angular dipole density}---the number of
+dipoles at position $\ro{}$ per unit area oriented along $\so{}$ per unit solid
+angle. Similar to the monopole case, we model the mapping between the object and
+the irradiance in a delta function basis as an integral transform
+\begin{align}
+  g'(\rd') = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\, h'(\rd', \ro, \so)f(\ro, \so). 
+\end{align}
+where $h'(\rd', \ro, \so)$ is the irradiance at position $\rd'$ created by a
+point source at $\ro$ with orientation $\so$. Once again, many fluorescence
+microscopes can be modeled as magnifiers with shift-invariant blur
+\begin{align}
+  g'(\rd') = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\, h'(\rd' - m\ro, \so)f(\ro, \so). 
+\end{align}
+
+We define the same demagnified detector coordinate $\rd = \rd'/m$ and a new
+normalization factor that corresponds to the total power incident on the
+detector due to a spatial point source with an angularly uniform distribution of
+dipoles
+$P_\text{dip} = \int_{\mbb{S}^2}d\mb{s}\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
+\mb{s})$. We use these scaling factors to define the
+\textit{orientation-dependent point spread function} as
+\begin{align}
+  h(\rd - \ro, \mb{s}) = \frac{h'(m[\rd - \ro], \mb{s})}{P_\text{dip}}, 
+\end{align}
+and the \textit{scaled irradiance} as 
+\begin{align}
+  g(\rd) = \frac{g'(m\rd)}{P_\text{dip}}. 
+\end{align}
+With these definitions we can express the mapping between the object and the
+data as an integral over the sphere with a spatial convolution at each point
+\begin{align}
+g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(\rd{} -\ro{}, \so{})f(\ro, \so). \label{eq:odpsf}
+\end{align}
+Similar to the monopole case, we have chosen to normalize the orientation-dependent point spread function so that
+\begin{align}
+  \int_{\mbb{S}^2}d\mh{s}\int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \mh{s}) = 1. 
+\end{align}
+The orientation-dependent point spread function is a measurable quantity, so it
+is real-valued and positive.
+
+\subsubsection{Orientation-dependent optical transfer function}
 We can make our first change of basis by applying the Fourier-convolution
@@
 \end{align}
-where we define the \textit{irradiance spectrum} as
-\begin{align}
-  G(\bs{\nu}) &= \int_{\mbb{R}^2}d\mb{r}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
-  \end{align}
-  the \textit{orientation-dependent optical transfer function} as
+where we define the \textit{orientation-dependent optical transfer function} as
   \begin{align}
@@
   \end{align}
-  and the \textit{spatial density spectrum} as
+and the \textit{spatial dipole spectrum} as
   \begin{align}
@@
   \end{align}
-  This basis is well suited for simulating objects that are angularly sparse and
-  spatially dense.
-
-  The spherical harmonics provide another set of convenient basis functions. We
-  can change basis from spherical delta functions to spherical harmonics by
-  making use of the generalized Plancharel theorem for spherical functions
-\begin{align}
-  \ints{2}d\mh{s}{}\, h(\mh{s})f(\mh{s}) = \lmsum H_\ell^m F_\ell^m, \label{eq:plan}
-\end{align}
-where
-\begin{align}
-  F_\ell^m \equiv \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_\ell^m(\mh{s}), 
-\end{align}
-is the spherical Fourier transform of $f(\mh{s})$, $\bar{z}$ denotes the complex
-conjugate of $z$, and $Y_{\ell}^m(\mh{s})$ are the spherical harmonic functions
-defined in Appendix \ref{sec:sph}. Eq. \ref{eq:plan} expresses the fact that
-scalar products are invariant under a change of basis (see Eq. 3.78 of
-\cite{barrett2004}). The left-hand side of Eq. \ref{eq:plan} is the scalar
-product of $\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the
-right hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
-spherical harmonic function basis. Applying Eq. \ref{eq:plan} to Eq.
-\ref{eq:odpsf} yields
+  Since the orientation-dependent point spread function is normalized and real,
+  we know that the orientation-dependent optical transfer function is normalized
+  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \mh{s}) = 1$ and conjugate-symmetric
+  $H(-\bs{\nu}, \mh{s}) = H^*(\bs{\nu}, \mh{s})$.
+
+  This choice of basis is well suited for simulating and analyzing objects that
+  are angularly sparse and spatially dense.
+
+  \begin{figure}
+  \hspace{-5em}
+  \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
+  \caption{The mapping between the object and data space of a dipole
+    fluorescence microscope can be computed in four different bases---a delta
+    function basis, a spatial-harmonic/angular-delta basis, a
+    spatial-delta/spherical-harmonic basis, and a spatio-angular harmonic basis.
+    The changes of basis are given by the two-dimensional Fourier transform
+    denoted $\mathcal{F}_{\mbb{R}^2}$ and the spherical Fourier transform
+    denoted $\mathcal{F}_{\mbb{S}^2}$.}
+   \label{fig:dipole-block}      
+    \end{figure}
+
+\subsubsection{Angular transfer function}
+The spherical harmonics are another set of convenient basis functions. We can
+change basis from spherical delta functions to spherical harmonics by applying
+the generalized Plancharel theorem for spherical functions
+\begin{align}
+  \ints{2}d\mh{s}{}\, p(\mh{s})q(\mh{s}) = \lmsum P_\ell^m Q_\ell^m, \label{eq:plan}
+\end{align}
+where $p(\mh{s})$ and $q(\mh{s})$ are arbitrary functions on the sphere and
+\begin{align}
+  P_\ell^m = \int_{\mbb{S}^2}d\mh{s}\, p(\mh{s})Y_\ell^{m*}(\mh{s}), 
+\end{align}
+is the spherical Fourier transform of $p(\mh{s})$ and $Y_{\ell}^m(\mh{s})$ are
+the spherical harmonic functions defined in Appendix \ref{sec:sph}. Eq.
+\ref{eq:plan} expresses the fact that scalar products are invariant under a
+change of basis (see Eq. 3.78 of \cite{barrett2004}). The left-hand side of Eq.
+\ref{eq:plan} is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
+delta function basis and the right hand side is the scalar product of
+$\mbb{L}_2(\mbb{S}^2)$ functions in a spherical harmonic function basis.
+Applying Eq. \ref{eq:plan} to Eq. \ref{eq:odpsf} yields
 \begin{align}
@@
 \begin{align}
-  H_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, h(\mb{r}, \mh{s})\bar{Y}_{\ell}^m(\mh{s}),\label{eq:atf-prep} 
-\end{align}
-and the \textit{angular density spectrum} as
-\begin{align}
-  F_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, f(\mb{r}, \mh{s})\bar{Y}_{\ell}^m(\mh{s}).
-\end{align}
-This basis is well suited for simulating objects that are spatially sparse and
-angularly dense.
-
+  H_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, h(\mb{r}, \mh{s})Y_{\ell}^{m*}(\mh{s}),\label{eq:atf-prep} 
+\end{align}
+and the \textit{angular dipole spectrum} as
+\begin{align}
+  F_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, f(\mb{r}, \mh{s})Y_{\ell}^{m*}(\mh{s}).
+\end{align}
+Since the orientation-dependent point spread function is normalized and
+real-valued, we know that the angular transfer function is normalized
+$\int_{\mbb{R}^2}d\mb{r}\, H_0^0(\mb{r}) = 1$ and conjugate symmetric
+$H_\ell^{-m}(\mb{r}) = (-1)^mH_\ell^{m*}(\mb{r})$.
+
+This basis is well suited for simulating and analyzing objects that are
+spatially sparse and angularly dense.
+
+\subsubsection{Spatio-angular transfer function}
 We can arrive at our final basis in two ways: by applying the generalized
@@
 \begin{align}
-G(\bs{\nu}) = \lmsum H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu}) \label{eq:saft},
-\end{align}
-where we have defined the \textit{spatio-angular transfer function} (SATF) as
-  \begin{align}
-  H_\ell^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})\bar{Y}_\ell^m(\mh{s}),
-  \end{align}
-  and the \textit{spatio-angular density spectrum} as
-  \begin{align}
-  F_\ell^m(\bs{\nu}) &\equiv \int_{\mbb{S}^2}d\mh{s}\, F(\bs{\nu}, \mh{s})\bar{Y}_\ell^m(\mh{s}).
-  \end{align}
-  This basis is well suited for simulating arbitrary samples because it exploits
-  the sparsity of the imaging system---we will see this explicitly when we
-  calculate a specific case of the spatio-angular transfer function.
+G(\bs{\nu}) = \lmsum \msf{H}_\ell^m(\bs{\nu})\msf{F}_\ell^m(\bs{\nu}) \label{eq:saft},
+\end{align}
+where we have defined the \textit{spatio-angular transfer function} as
+  \begin{align}
+  \msf{H}_\ell^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})Y_\ell^{m*}(\mh{s}),
+  \end{align}
+  and the \textit{spatio-angular dipole spectrum} as
+  \begin{align}
+  \msf{F}_\ell^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\mh{s}\, F(\bs{\nu}, \mh{s})Y_\ell^{m*}(\mh{s}).
+  \end{align}
+  Since the orientation-dependent point spread function is normalized and
+  real-valued, we know that the spatio-angular transfer function is normalized
+  $\msf{H}_0^0(0) = 1$ and conjugate symmetric
+  $\msf{H}_\ell^{-m}(-\bs{\nu}) = (-1)^m\msf{H}_\ell^{m*}(\bs{\nu})$.
+
+  This basis is well suited for simulating and analyzing arbitrary samples
+  because it exploits the sparsity of the imaging system. We will see this
+  advantage explicitly in Section XXX when we calculate a specific
+  spatio-angular transfer function and see that it has an angular band limit.
 
   Figure \ref{fig:dipole-block} summarizes the relationship between the four
-  bases that we can use to compute the image of a field of dipoles.
+  bases that we can use to compute the image of a field of dipoles. We reiterate
+  that all four bases may be useful depending on the sparsity of the sample.
+
+\subsubsection{Dipole coherent transfer functions}
+Two-dimensional Fourier transforms and spherical Fourier transforms are the only
+operations required to change between the transfer functions. However, there is
+a well-known alternative for calculating optical transfer functions in terms of
+coherent transfer functions. The key idea is that the orientation-dependent
+point spread function can always be written as the absolute square of a
+vector-valued function called the \textit{orientation-dependent coherent spread
+  function}
+\begin{align}
+  h(\mb{r}, \mh{s}) = |\mb{c}(\mb{r}, \mh{s})|^2. \label{eq:absquare}
+\end{align}
+Physically, this decomposition corresponds to the fact that the irradiance is
+always the absolute square of a vector-valued electric field.
+
+Since the orientation-dependent transfer function is given by the
+two-dimensional Fourier transform of the orientation-dependent point spread
+function
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r}, \mh{s})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\nu}],
+\end{align}
+we can plug in Eq. \ref{eq:absquare} and use the autocorrelation theorem to
+rewrite as
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\bs{\tau}\,\mb{C}(\bs{\tau}, \mh{s})\mb{C}^\dagger(\bs{\tau} - \bs{\nu}, \mh{s}), 
+\end{align}
+where the \textit{orientation-dependent coherent transfer function}
+$\mb{C}(\bs{\tau}, \mh{s})$ is the two-dimensional Fourier transform of the
+orientation-dependent coherent spread function
+\begin{align}
+  \mb{C}(\bs{\tau}, \mh{s}) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \mh{s})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\tau}].
+\end{align}
+The relationships between all six transfer function are shown in Figure
+\ref{fig:transfer-functions}. Note that we could define coherent equivalents for
+all four incoherent transfer functions, but we restrict ourselves to these two
+since they are the useful for our calculations.
 
 \begin{figure}
-  \hspace{-5em}
-  \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
-  \caption{We can compute the mapping between object space and data space using
-    four different bases.}
-   \label{fig:dipole-block}      
+  \hspace{-2em}
+  \includegraphics[scale=1.0]{../figures/transfer-functions/transfer-functions.pdf}
+  \caption{There is one incoherent transfer function for each set of
+    object-space basis functions, and these transfer functions are related by
+    two-dimensional and spherical Fourier transforms---see center and right
+    columns. There are an additional pair of coherent transfer functions that
+    are useful for calculating the point spread function and optical transfer
+    function---see left column.}
+   \label{fig:transfer-functions}
  \end{figure}
 
-\subsection{Paraxial epi-fluorescence microscope}\label{sec:para}
-\tb{This section is probably the most mature, but it still has some mismatch with
-  newer sections. I've quit using ``kernel'' and haven't fixed it.}
-In this section we apply the tools we developed in the previous two sections to
+\section{Results}\label{sec:results}
+In this section we apply the tools we developed in the previous sections to
 analyze a paraxial epi-fluorescence microscope. We start by reviewing the
@@
 
-\subsubsection{Monopole point spread function}
-In this section we derive the form of the monopole point spread function $h(\mb{r})$.
-First, we place a monopole emitter at the focal point of an objective lens and
-calculate the field created in the back focal plane. We can model a paraxial
-thin lens as a quadratic phase element, so it converts a spherical wave to a
-plane wave in the back focal plane with a sharp cutoff at the exit pupil of the
-lens
-\begin{align}
-  U_{\text{bfp}}(\mb{r}_b) \propto \Pi\left(\frac{|\mb{r}_b|}{\alpha}\right) \equiv
+TODO: Define and discuss paraxial. 4f, illumination uniformity and ignoring in
+monopole Where are excitation and detection dipoles parallel.
+
+\subsection{Monopole point spread function of a paraxial epi-fluorescence microscope}
+In this section we derive the form of the monopole point spread function
+$h(\rd - \ro)$. First, we place a monopole emitter at the focal point of an
+objective lens and calculate the field $U_{\text{bfp}}(\rb)$ created in the back
+focal plane. We can model a paraxial thin lens as a quadratic phase element, so
+it converts an incident spherical wave to a plane wave in the back focal plane
+with a sharp cutoff at the exit pupil of the lens
+\begin{align}
+  U_{\text{bfp}}(\mb{r}_b) \propto \Pi\left(\frac{|\mb{r}_b|}{2\alpha}\right) \equiv
   \begin{cases}
     1\quad \text{if}\quad |\mb{r}_b| < \alpha,\\
-    0\quad \text{else}.
+    0\quad \text{else},
   \end{cases}
 \end{align}
+where $\rb$ is the two-dimensional coordinate in the back focal plane and
+$\alpha$ is the collection half angle---see Figure XXX.
+
 A central result of Fourier optics is that the fields one focal distance from
 either side of a paraxial lens are related by a scaled two-dimensional Fourier
-transform. If we place a detector in the focal plane of the tube lens then the
-field on the detector is given by
-\begin{align}
-  U_{\text{det}}(\mb{r}_d) \propto \mc{F}_{\mbb{R}^2}\left\{U_{\text{bfp}}(\mb{r}_b)\right\} = \frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}.
-\end{align}
+transform. If we place a detector in the focal plane of the tube lens, then the
+field on the detector $U_{\text{det}}(\mb{r}_d)$ is given by
+\begin{align}
+  U_{\text{det}}(\mb{r}_d) \propto \frac{J_1(k\alpha|\mb{r}_d|)}{|\mb{r}_d|}.
+\end{align}
+where $J_n(x)$ denotes the Bessel function of the first kind of order $n$, and
+$k = 2\pi/\lambda$ is the wave number.
+
 Finally, the detector measures the irradiance instead of the field, so we take
@@
 \begin{align}
-  h(\mb{r}_d, \ro = 0) \propto |U_{\text{det}}(\mb{r}_d)|^2 = \left[\frac{J_1(k\alpha|\mb{r}_d|)}{k\alpha|\mb{r}_d|}\right]^2.
+  h(\mb{r}_d, \ro = 0) \propto |U_{\text{det}}(\mb{r}_d)|^2 = \left[\frac{J_1(k\alpha|\mb{r}_d|)}{|\mb{r}_d|}\right]^2.
 \end{align}
@@
 function can be found for magnifying microscopes by making a change of
-variables---see Barrett section 7.2.7.
+variables (see \cite{barrett2004}, section 7.2.7).
 
@@
 
-\subsubsection{Orientation-dependent point spread function}
-In the next two subsections we will calculate the orientation dependent point
-spread function $h(\mb{r}, \mh{s})$ of a paraxial epi-fluroescence microscope.
-We can make our first simplifying step by realizing the excitation and detection
-processes are incoherent which means that the orientation-dependent PSF is
-separable
+\subsection{Orientation-dependent point spread function of a paraxial epi-fluorescence microscope}
+In this section we will calculate the orientation-dependent point spread
+function $h(\rd - \ro, \mh{s})$ of a paraxial epi-fluorescence microscope. We can
+make our first simplifying step by realizing the excitation and detection
+processes are incoherent, which means that the orientation-dependent PSF is
+separable:
 \begin{align}
@@
 \end{align}
-We can calculate the excitation and detection PSFs separately then take their product to find the complete orientation-dependent PSF.
-
-\subsubsection{Dipole excitation model}
+We can calculate the excitation and detection terms separately then take their
+product to find the complete orientation-dependent point spread function.
+
+\subsubsection{Orientation-dependent excitation model}
 When we developed the monopole imaging model we ignored the excitation process
@@
 $h_{\text{exc}}(\ro, \so)$ for the paraxial epi-illumination microscope under
-unpolarized K\"{o}ehler illumination shown in Figure \ref{fig:microscope}. We
-will only consider spatially uniform excitation, so the excitation kernel will
-no depend on $\ro$
+unpolarized (TODO: Define/cite) K\"{o}ehler illumination shown in Figure
+\ref{fig:exccoords}. We will only consider spatially uniform excitation, so the
+excitation kernel will not depend on $\ro$
 \begin{align}
@@
 \cite{fourkas2001, chandler2017}, but here we consider paraxial, incoherent, and
-unpolarized illumination.
+unpolarized illumination (TODO improve).
 
@@
    \includegraphics[scale=.9]{../figures/excitation-coords/excitation-coords.pdf}
-   \caption{Illumination geometry and coordinates. We calculate the excitation
-     kernel $h_{\text{exc}}(\so)$ for a paraxial, unpolarized, incoherent
-     light source (or its image) in the back focal plane of the condenser lens. }
-   \label{fig:microscope}
+   \caption{Illumination geometry and coordinates for a paraxial epifluorescence
+     microscope. An unpolarized and incoherent light source (or its image) is in
+     the back focal plane of the condenser lens.}
+   \label{fig:exccoords}
  \end{figure}
@@
 \cite{foreman2011} to find the response for a single polarized ray, then
-integrate over the rays and polarizations to find the complete response. First,
-we model the electric field at every point on the back focal plane as
+integrate over the rays and all polarizations to find the complete response.
+First, we model the electric field at every point on the back focal plane as
 \begin{align}
@@
 matrix (see the rotation matrices in \cite{foreman2011, backer2014} under the
-paraxial approximation)
+paraxial approximation):
 
@@
     0
-  \end{bmatrix}\\
+  \end{bmatrix},\\
+  \intertext{so that}
   \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) &\propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y} - \theta\cos(\phi - \phi_{\text{pol}})\mh{z}.\label{eq:eff}
@@
 To find the complete excitation kernel we need to integrate Eq.
-\ref{eq:integrand} over all polarization orientations and rays
-\begin{align}
-  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2, \label{eq:integral}
-\end{align}
-where $\alpha$ is the maximum angle the illumination rays make with the optical
-axis. Plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral}, evaluating the
+\ref{eq:integrand} over all polarization orientations and rays:
+\begin{align}
+  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2.
+\label{eq:integral}
+\end{align}
+Plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral}, evaluating the
 integrals, and dropping constants gives
@@
 We can rewrite the excitation kernel in terms of a single variable with the
-substitutions $s_x^2 + s_y^2 = \sin^2\vartheta$ and $s_z^2 = \cos^2\vartheta$
+substitutions $s_x^2 + s_y^2 = \sin^2\vartheta$ and $s_z^2 = \cos^2\vartheta$:
 \begin{align}
@@
 
-Figure \ref{fig:excitation} shows the excitation kernel as a function of
-inclination angle $\vartheta$ and maximum excitation angle $\alpha$. The largest
+Figure \ref{fig:excitation} shows the excitation response as a function of
+inclination angle $\vartheta$ and excitation half angle $\alpha$. The largest
 variation of the excitation kernel occurs when the maximum excitation angle is
-zero---plane-wave illumination. As $\alpha$ grows dipoles parallel to the optic
+zero---plane-wave illumination. As $\alpha$ grows, dipoles parallel to the optic
 axis are more likely to be excited and the variation of the excitation kernel
-decreases. Note that we have derived this simple model under the paraxial
-approximation, so it does not make quantitative predictions for high-NA
-illumination geometries.
+decreases.
 \begin{figure}[h]
@@
    \caption{Dipole excitation kernel $h_{\text{exc}}(\vartheta)$ as a function of
-     inclination angle $\vartheta$ and maximum excitation angle $\alpha$.}
+     inclination angle $\vartheta$ and excitation half angle $\alpha$.}
    \label{fig:excitation}
@@
 
- \subsubsection{Dipole detection model}
+ \subsubsection{Orientation-dependent dipole detection model}
  In this section we will calculate the detection kernel of an epi-detection
  microscope---the irradiance on the detector due to a single dipole with fixed
- position and orientation. Our approach mimics existing work \cite{backer2014,
-   nov2006, agrawal2012}, but we restrict ourselves to the paraxial
- approximation.
+ position and orientation. [TODO Improve] Our approach mimics existing work
+ \cite{backer2014, nov2006, agrawal2012}, but we restrict ourselves to the
+ paraxial approximation.
 
@@
 \begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto [\mb{I} - \mh{r}\mh{r}^{\dagger}]\so,
-\end{align}
-where $\mb{I}$ is a $3\times 3$ identity matrix. If we place the molecule in the
-focal plane of an aplanatic and polarization-preserving objective lens with its
-optical axis aligned with the $\mh{z}$ axis (or reuse the illumination
-objective), then we can find the electric field in the back focal plane by
-multiplying the electric field with a position-dependent rotation matrix and
-truncating waves outside the detection collection angle $\alpha$
-\begin{align}
-  \mb{E}_{\text{bfp}}(\mb{r}, \so{}) \propto \mb{R}_{\text{obj}}(\mh{r})[\mb{I} - \mh{r}\mh{r}^{\dagger}]\so\Pi\left(\frac{\theta}{\alpha}\right).
+  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto [\tensor{I} - \mh{r}\mh{r}^{\dagger}]\so,
+\end{align}
+where $\tensor{I}$ is a $3\times 3$ identity matrix. If we place the molecule in
+the focal plane of an aplanatic and polarization-preserving objective lens with
+the lens' optical axis aligned with the $\mh{z}$ axis, then we can find the
+electric field in the back focal plane by multiplying the electric field with a
+position-dependent rotation matrix and truncating waves outside the detection
+collection half angle $\alpha$
+\begin{align}
+  \mb{E}_{\text{bfp}}(\mb{r}, \so{}) \propto \mb{R}_{\text{obj}}(\mh{r})[\tensor{I} - \mh{r}\mh{r}^{\dagger}]\so\Pi\left(\frac{\theta}{2\alpha}\right).
 \end{align}
@@
 \begin{align}
-  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{\left[s_x - s_zr_b\cos\phi_b\right]\mh{x} + \left[s_y - s_z r_b\sin\phi_b\right]\mh{y}\right\}\Pi\left(\frac{r_b}{\alpha}\right).
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{\left[s_x - s_zr_b\cos\phi_b\right]\mh{x} + \left[s_y - s_z r_b\sin\phi_b\right]\mh{y}\right\}\Pi\left(\frac{r_b}{2\alpha}\right).
 \label{eq:bfp2}
@@
 \begin{align}
-  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp3}
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{2\alpha}\right). \label{eq:bfp3}
 \end{align}
@@
 \begin{align}
-  \mb{E}_{\text{det}}(r_d, \so{}) \propto \frac{J_1(k\alpha r_d)}{k\alpha r_d}s_x\mh{x} + \frac{J_1(k\alpha r_d)}{k\alpha r_d}s_y\mh{y} - i\alpha\frac{J_2(k\alpha r_d)}{k\alpha r_d}s_z\mh{\bs{\rho}}.
+  \mb{E}_{\text{det}}(r_d, \so{}) \propto \frac{J_1(k\alpha r_d)}{r_d}s_x\mh{x} + \frac{J_1(k\alpha r_d)}{r_d}s_y\mh{y} - i\alpha\frac{J_2(k\alpha r_d)}{r_d}s_z\mh{\bs{\rho}}.
 \end{align}
@@
 \begin{align}
-  a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
+  a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{r_d}\right]^2. 
 \end{align}
 Notice that we retain the $\alpha^2$ irradiance term even though we dropped
-$\theta^2$ electric field terms since these terms would become $\theta^2$
+$\theta^2$ electric field terms since these terms would become $\theta^4$
 irradiance terms.
@@
 that the monopole detection model ignores the $\sin^2\vartheta$ dependence---see
-Figure \ref{fig:microscope} a) and b). As $\alpha$ grows the relative
+Figure \ref{fig:microscope} a) and b). As $\alpha$ grows, the relative
 contribution of the higher-order Airy pattern increases. The most important
-result is that the dipole detection model is not separable into the product of
-a spatial and angular kernel---even under the paraxial approximation. The detection
-model is only separable when $\alpha$ approaches zero which is almost never the
-case in real microscopes. We refer to the non-separability of the detection
-kernel as \textit{spatio-angular coupling} because the orientation of the dipole
-is coupled to the spatial pattern of irradiance on the detector.
+result is that the dipole detection model is not separable into the product of a
+spatial and angular kernel---even under the paraxial approximation. The
+detection model is only separable when $\alpha$ approaches zero, which is almost
+never the case in real microscopes. We refer to the non-separability of the
+detection kernel as \textit{spatio-angular coupling} because the orientation of
+the dipole is coupled to the spatial pattern of irradiance on the detector.
 
@@
 build an intuition about the dominant effects outside the paraxial
-approximation. Later in this work we will exploit this approximate symmetry to
-improve the efficiency of simulating and inverting the imaging model.
+approximation.
 
@@
      the detector. This phase shift means that the fields from transverse and
-     axial components of the dipole do not interfere which causes radially
+     axial components of the dipole do not interfere, which causes radially
      symmetric irradiance patterns.}
@@
 
- \subsubsection{Simplified dipole imaging model}
+\subsubsection{Complete orientation-dependent point spread function}
  Combining the results of the previous two sections yields a simplified dipole
@@
  \end{align}
- Plugging in our results
+ Plugging in our results we find:
  \begin{align}
@@
 
- \subsubsection{Orientation-dependent optical transfer function}\label{sec:trans}
+ Comment on inversion/antipodal symmetry.
+
+ To demonstrate the orientation-dependent point spread function, we calculate
+ the irradiance pattern created by a set of equally spaced dipoles with varying
+ orientation given by
+ \begin{align}
+   f_{\text{(ph1)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \delta\left(x_o - \frac{i}{3}\right)\, \delta\left(y_o - \frac{j}{3}\right)\, \delta\left(\cos\vartheta - \cos\left(\frac{\pi i}{6}\right)\right)\, \delta\left(\varphi - \frac{2\pi j}{3}\right),\label{eq:phantom1}
+ \end{align}
+ where the subscript (ph1) indicates that this is the first phantom. To find the
+ irradiance pattern we plug Eq. \ref{eq:phantom1} into Eq. \ref{eq:simplified}
+ and use the sifting property
+ \begin{align}
+   g_{\text{(ph1)}}(x_d, y_d) = \sum_{i=0}^3 \sum_{j=0}^3 h\left(\sqrt{\left(x_d - \frac{i}{3}\right)^2 + \left(y_d - \frac{j}{3}\right)^2}, \frac{\pi i}{6}\right).\label{eq:phantom1irr}
+ \end{align}
+
+\subsection{Orientation-dependent optical transfer function of a paraxial epi-fluorescence microscope}\label{sec:trans}
   In Appendix \ref{sec:airy} we evaluate the 2D spatial Fourier transforms of
@@
 \begin{align}
-  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right), \\
-  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-The STF is shown in Figure \ref{fig:odotf}. The STF has the usual
-spatial-frequency cutoff at $\nu = 2\nu_o$ for all dipole orientations.
+  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{4\nu_o}\right), \\
+  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{4\nu_o}\right).
+\end{align}
+The orientation-dependent optical transfer function is shown in Figure
+\ref{fig:odotf}. The orientation-dependent transfer function has the usual
+spatial-frequency cutoff at $\nu_c = 2\nu_o$ for all dipole orientations.
 
@@
    \includegraphics[scale=0.8]{../figures/stf/stf.pdf}
-   \caption{STF as a function of the scaled spatial frequency, the dipole
-     inclination angle $\vartheta$, and the collection angle $\alpha$. For small
-     collection angles (left) the STF for axial dipoles
-     (\textcolor{red}{\textbf{red}}) is small compared to transverse dipoles
-     (\textbf{black}), but the relative contribution of axial dipoles increases
-     with the collection angle (see \textcolor{red}{\textbf{red}} lines from
-     left to right). The STF of axial dipoles is negative at high spatial
-     frequencies because the central minimum of the axial kernel corresponds to
-     the position of the dipole. Equivalently, a high-spatial-frequency pattern
-     of axial dipoles will generate an irradiance pattern where the minimum
-     irradiance corresponds to the peak of the axial dipole density.}
+   \caption{Orientation-dependent transfer function as a function of the scaled
+     spatial frequency, the dipole inclination angle $\vartheta$, and the
+     collection angle $\alpha$. For small collection angles (left) the STF for
+     axial dipoles (\textcolor{red}{\textbf{red}}) is small compared to
+     transverse dipoles (\textbf{black}), but the relative contribution of axial
+     dipoles increases with the collection angle (see
+     \textcolor{red}{\textbf{red}} lines from left to right). The STF of axial
+     dipoles is negative at high spatial frequencies because the central minimum
+     of the axial kernel corresponds to the position of the dipole.
+     Equivalently, a high-spatial-frequency pattern of axial dipoles will
+     generate an irradiance pattern where the minimum irradiance corresponds to
+     the peak of the axial dipole density.}
    \label{fig:odotf}
@@
 
-\subsubsection{Angular transfer function (ATF)}
-
+ To demonstrate the spatial transfer spread function, we calculate the
+ irradiance pattern created by a set of equally spaced disks with varying radius
+ containing fluorophores with varying orientation given by
+ \begin{align}
+   f_{\text{(ph2)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \Pi\left(\frac{10}{j}\sqrt{\left(x_o - \frac{i}{3}\right)^2 + \left(y_o - \frac{j}{3}\right)^2}\right) \delta\left(\cos\vartheta - \cos\left(\frac{\pi i}{6}\right)\right)\, \delta\left(\varphi - \frac{2\pi j}{3}\right).\label{eq:phantom2}
+ \end{align}
+ \begin{align}
+   G_{\text{(ph2)}}(\nu_x, \nu_y) = \sum_{i=0}^3 \sum_{j=0}^3 H\left(\nu_x, \nu_y, \frac{\pi i}{6}, \frac{2\pi j}{3}\right)\left[\frac{j}{10\nu}J_1\left(\frac{2\pi j\nu}{10}\right)\right]\text{exp}\left(-2\pi i\left[\frac{i}{3}\nu_x + \frac{j}{3}\nu_y\right]\right).\label{eq:phantom2g}
+ \end{align}
+ Finally, we calculate the inverse Fourier transform of the irradiance spectrum
+ to find the irradiance.
+
+ \subsection{Angular transfer function (ATF) of a paraxial epi-fluorescence microscope}
 To calculate the angular transfer function we plug the spatio-angular point
@@
 The degree $\ell$ and order $m$ of the non-zero terms in the ATF follow directly
-from specific features of the kernel. First, our kernel is symmetric under
-inversion of the dipole moment which appears in the kernel as even-degreed
-trigonometric functions. This symmetry is maintained in the ATF since all of the
-non-zero terms have an even degree $\ell=0, 2$, and $4$. Second, we showed that
-under the paraxial approximation our kernel is rotationally symmetric which
-allows us to write the kernel as a function of $r$ instead of $\mb{r}$. This
-symmetry is maintained in the ATF since all of the non-zero terms have order
-$m=0$. Finally, both the excitation and detection kernels are a weighted sum of
-degree-2 trigonometric functions which implies that the maximum degree of the
-kernel is 4. This feature of the kernel appears in the ATF since only
-$\ell=0, 2$, and $4$ terms are non-zero.
+from specific features of the kernel. First, the spatio-angular point spread
+function is symmetric under inversion of the dipole moment. This symmetry is
+maintained in the angular transfer function since all of the non-zero terms have
+an even degree $\ell=0, 2, 4$, and the corresponding spherical harmonics
+$Y_0^0(\so)$, $Y_2^0(\so)$, $Y_4^0(\so)$ are symmetric under inversion. Second,
+we showed that under the paraxial approximation our kernel is rotationally
+symmetric which allows us to write the kernel as a function of $r$ instead of
+$\mb{r}$. This symmetry is maintained in the ATF since all of the non-zero terms
+have order $m=0$. Finally, both the excitation and detection kernels are
+degree-2 trigonometric polynomials, which implies that the maximum degree of the
+spatio-angular point spread function is 4. This feature of the kernel appears in
+the angular transfer function since only $\ell=0, 2$, and $4$ terms are
+non-zero.
 
@@
 
- \subsubsection{Spatio-angular transfer function (SATF)}
+ To demonstrate the angular transfer function, we calculate the irradiance
+ pattern created by a set of equally spaced fluorophore distributions with
+ varying orientation and angular distribution given by
+ \begin{align}
+   f_{\text{(ph3)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \delta\left(x_o - \frac{i}{3}\right)\, \delta\left(y_o - \frac{j}{3}\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right),\label{eq:phantom3}
+ \end{align}
+ where
+ \begin{align}
+   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right).
+ \end{align}
+ To calculate the irradiance pattern we calculate the angular density spectrum
+ of the phantom (we calculate the spherical Fourier transform of the cone in
+ Appendix \ref{sec:cone}), plug the result into Eq. XXX, then use the sifting
+ property to find that
+ \begin{align}
+   g_{\text{(ph3)}}(x_d, y_d) = \sum_{\ell m}\sum_{i=0}^3 \sum_{j=0}^3 H_\ell^m\left(\sqrt{\left(x_d - \frac{i}{3}\right)^2 + \left(y_d - \frac{j}{3}\right)^2}\right) F_{\ell\text{(cone)}}^m\left(\frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right),\label{eq:phantom3}
+ \end{align}
+
+\subsection{Spatio-angular transfer function (SATF)  of a paraxial epi-fluorescence microscope}
   \begin{alignat}{6}
@@
 
-\section{Results}
-\subsection{Phantom with spatio-angular sparsity (single molecules)}
-\subsection{Phantom with spatial sparsity (rotating single molecules)}
-\subsection{Phantom with angular sparsity (actin fibers)}
-\subsection{Phantom without sparsity (most general)}
-
-\section{Discussion \tb{Very rough but open for discussion}}
+ To demonstrate the spatio-angular transfer function, we calculate the
+ irradiance pattern created by a set of equally spaced disks of fluorophores
+ with varying radius and angular distribution given by
+ \begin{align}
+   f_{\text{(ph4)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \Pi\left(\frac{10}{j}\sqrt{\left(x_o - \frac{i}{3}\right)^2 + \left(y_o - \frac{j}{3}\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \frac{\pi i}{6}\right),\label{eq:phantom4}
+ \end{align}
+ To calculate the irradiance pattern created by the phantom we calculate the
+ spatio-angular spectrum, plug the result into Eq. XXX, then take the inverse
+ Fourier transform to find the irradiance.
+  \begin{align}
+    G_{\text{(ph2)}}(\nu_x, \nu_y) = \sum_{\ell m}\sum_{i=0}^3 \sum_{j=0}^3 H_\ell^m(\nu_x, \nu_y)\left[\frac{j}{10\nu}J_1\left(\frac{2\pi j\nu}{10}\right)\right]\text{exp}\left(-2\pi i\left[\frac{i}{3}\nu_x + \frac{j}{3}\nu_y\right]\right)F_{\ell\text{(cone)}}^m\left(\frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right).\label{eq:phantom4g}
+ \end{align}
+
+\section{Discussion}\label{sec:discussion}
 \subsection{Reconstructions}
@@
 as monopoles. This is not true. The microscope still only measures a single
-member of $\mbb{L}_2(\mbb{R}^2)$ so at best we can recover the same amount of
+member of $\mbb{L}_2(\mbb{R}^2)$, so at best we can recover the same amount of
 information about the object. In other words, we know immediately that the
@@
 
-We postpone a full discussion of SVD to find the object space singular functions
+TODO Expand. Make clear that later paper. We postpone a full discussion of SVD to find the object space singular functions
 that span the measurement space of the instrument.
@@
 computing the spatio-angular point spread function. Mathematically, Backer and
-Lew use an alternative to the angular transfer function that uses the second
+[XXX] use an alternative to the angular transfer function that uses the second
 moments as basis functions so their forward model is given by
 \begin{align}
-  g(\rd) = \sum_{j=1}^6 H_j(\rd - \ro)F_j(\ro)
+  g(\rd) = \sum_{j=1}^6 H_j(\rd - \ro)F_j(\ro),
 \end{align}
@@
 and $Z_j(\mh{s}) = \{s_x^2, s_y^2, s_z^2, s_xs_y, s_ys_z, s_xs_z\}$ are the
-second moments. This formulation provides the main advantage of the ATF
-approach---efficient computation for spatially sparse and angularly dense
-samples---without requiring a cumbersome expansion of the spatio-angular point
-spread function onto spherical harmonics.
-
-The spherical harmonics provide several advantages over the second moments as
-well. First, the spherical harmonics form an orthonormal basis which often
-simplifies computation. For example, if we calculated the angular detection
-transfer function we would find that it contained two angular terms under the
-paraxial approximation. If we expanded onto second moments we would need all six
-angular basis functions and computing the forward model would be three times as
-expensive. Second, the spherical harmonics are complete which means they can
-represent arbitrary functions on the sphere while the second moments can only
-represent a small subset of all functions on the sphere. Extending the accuracy
-of the second moments using the fourth (or higher) moments is possible, but it
-requires a completely new basis. Indeed, the simple microscope we consider in
-this work requires an expansion onto fourth-order spherical harmonics, so an
-expansion onto second-order moments would not suffice. Finally, using the
-spherical harmonics provides access to a set of fast algorithms. The naive
-expansion of an arbitrary discretized $N$ point spherical function onto
-spherical harmonics (or second moments) requires a $\mc{O}(N^2)$ matrix
-multiplication while pioneering work by Driscoll and Healy [cite] showed that the
-forward discrete fast spherical harmonic transform can be computed with a
-$\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed with a
-$\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast algorithms exist
-for expansion onto the higher-order moments.
-
-The diffusion magnetic resonance imaging uses both sets of bases [cite Basser]
-[cite Tournier] for particular cases.
+second moments. This formulation is similar to the angular transfer function
+approach because it exploits the spatial sparsity of sample, but it does not
+require a cumbersome expansion of the spatio-angular point spread function onto
+spherical harmonics.
+
+However, the spherical harmonics provide several advantages over the second
+moments. First, the spherical harmonics form a complete basis for functions on
+the sphere, while the second moments span a much smaller function space. The
+usual approach to extending the span of the second moments is to use the fourth
+(or higher) moments, but these are completely new basis functions. Indeed, the
+microscope we considered in this work cannot be represented using the second
+moments since it contains fourth-order terms. Second, the spherical harmonics
+are orthonormal which allows us to easily deploy tools from linear algebra. For
+example, the spatio-angular transfer function for the microscope we considered
+in this work required three angular terms so we can think of the angular
+response as a vector in a three-dimensional vector space. If we had used the
+second moments we would have required six terms, and we would not have been able
+to say anything about the dimension of the space since the second moments are
+not orthonormal. Finally, using the spherical harmonics provides access to a set
+of fast algorithms. The naive expansion of an arbitrary discretized $N$ point
+spherical function onto spherical harmonics (or second moments) requires a
+$\mc{O}(N^2)$ matrix multiplication, while pioneering work by Driscoll and Healy
+[cite] showed that the forward discrete fast spherical harmonic transform can be
+computed with a $\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed
+with a $\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast
+algorithms exist for expansion onto the higher-order moments.
 
@@
 its angular-frequency spectrum, but we can increase the number of terms by
-modifying the instrument. We will postpone the proper treatment of these effects
-until future work, but we briefly mention that the number of terms in the
-angular-frequency spectrum increases for non-paraxial microscopes, microscopes
-with polarizers on the illumination or detection paths, and multiview
-microscopes. We also mention that there are two ways to extend the
+modifying the instrument. We will postpone the complete treatment of these
+effects until future work, but we briefly mention that the number of terms in
+the angular-frequency spectrum increases for non-paraxial microscopes,
+microscopes with polarizers on the illumination or detection paths, and
+multiview microscopes. We also mention that there are two ways to extend the
 angular-frequency spectrum of a microscope---by increasing the degree $\ell$ and
-by increasing the order $m$. Extending the angular degree cutoff $\ell_0$ gives
+by increasing the order $m$. Extending the angular degree cutoff $\ell_c$ gives
 the microscope the ability to measure finer angular features, while extending
-the angular order cutoff $m_0$ give the microscope the ability to measure
+the angular order cutoff $m_c$ give the microscope the ability to measure
 features of the object that are increasingly invariant to rotation. If the
-angular order cutoff matches the angular degree cutoff $\ell_0 = m_0$ then the
+angular order cutoff matches the angular degree cutoff $\ell_c = m_c$ then the
 microscope can be said to have $\textit{isotropic angular resolution}$. This
@@
 
-Possibly implies that the spatio-angular transfer function can be factored. Cite
-3D vector transfer functions Arnison and Sheppard.
-
 \subsection{Characterizing real spatio-angular microscopes}
@@
 aberration, scattering, high-NA objectives, finite fluorescence lifetimes, and
-interactions between fluorophores, and we are sure that this list of limitations
-could be extended. Because of this long list of unknown effects, real
-experiments should make an attempt to characterize the specific imaging system.
+interactions between fluorophores, among other. Because of this long list of
+unknown effects, real experiments should make an attempt to characterize the
+specific imaging system.
 
@@
 Imaging sub-diffraction beads is not enough to completely characterize the
-response of a microscope to a an oriented sample. We need at least three samples
+response of a microscope to an oriented sample. We need at least three samples
 with a known orientations to characterize the SATF, so isotropic beads are not
@@
 \section{Fourier transform of linear and radial vector fields}\label{sec:ftvec}
-  \begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
-\end{align}
-To evaluate the integral we rewrite it in polar coordinates
-\begin{align}
-\mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{0}^{\alpha}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
-\end{align}
-plug in Eq. \ref{eq:bfp2}, and apply the following identities
+In this appendix we evaluate the two-dimensional Fourier transform of the
+electric field in the back focal plane of paraxial epi-fluorescence microscope
+given by
+  \begin{align}
+  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right],\label{eq:det2}
+  \end{align}
+where
+\begin{align}
+  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp4}
+\end{align}
+To evaluate the Fourier transform we rewrite it in polar coordinates
+\begin{align}
+\mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{0}^{\infty}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
+\end{align}
+plug in Eq. \ref{eq:bfp4}, and apply the following pair of identities
 \begin{align}
@@
   \left\{\substack{
-    \sin(n\phi'_o)\\
-    \cos(n\phi'_o)
+    \sin(n\phi_d)\\
+    \cos(n\phi_d)
   }\right\}J_n(k r_br_d),
 \end{align}
+and 
   \begin{align}
@@
   \mb{E}_{\text{det}}(\rd{}, \so{}) \propto &\left[s_x\frac{J_1(k\alpha r_d)}{k\alpha r_d} - is_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\cos\phi_d\right]\mh{x}\, + \nonumber \\& \left[s_y\frac{J_1(k\alpha r_d)}{k\alpha r_d} - i s_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\sin\phi_d\right]\mh{y}.
-\end{align}
-Similar to the back focal plane, we rewrite in terms of linear and radial vector
-fields
+\label{eq:det6}
+\end{align}
+Similar to the expression for the electric field in the back focal plane, we
+rewrite Eq. \ref{eq:det6} in terms of linear and radial vector fields
 \begin{align}
@@
 \section{Spherical harmonics}\label{sec:sph}
-% The spherical harmonics are an orthonormal set of basis functions on the sphere.
-% In this appendix we will define the basis and review several important
-% properties of this set of functions.
-The spherical harmonic function of degree $\ell$ and order $-\ell \leq m \leq m$
+The spherical harmonic function of degree $\ell$ and order $-\ell \leq m \leq \ell$
 is defined as \cite{schaeffer2013}
 \begin{align}
-Y_\ell^m(\vartheta, \varphi) = P_\ell^m\left(\cos\vartheta\right)\exp(i m \varphi)
-\end{align}
-where $P_\ell^m(\cos\theta)$ are the associated Legendre polynomials normalized for the
-spherical harmonics 
-\begin{align}
-  P_\ell^m(x) = (-1)^m\sqrt{\frac{2\ell+1}{4\pi}}\sqrt{\frac{(\ell-|m|)!}{(\ell+|m|)!}}(1-x^2)^{|m|/2}\frac{d^{|m|}}{dx^{|m|}}P_\ell(x)
-\end{align}
-where $P_\ell(x)$ are the Legendre polynomials defined by the following recurrence
+Y_\ell^m(\vartheta, \varphi) = \sqrt{\frac{2\ell+1}{4\pi}}\sqrt{\frac{(\ell-|m|)!}{(\ell+|m|)!}}P_\ell^m\left(\cos\vartheta\right)\exp(i m \varphi),
+\end{align}
+where $P_\ell^m(\cos\theta)$ are the associated Legendre polynomials with the
+Condon-Shortley phase
+\begin{align}
+  P_\ell^m(x) = (-1)^m(1-x^2)^{|m|/2}\frac{d^{|m|}}{dx^{|m|}}P_\ell(x),
+\end{align}
+and $P_\ell(x)$ are the Legendre polynomials defined by the recurrence
 \begin{align}
@@
 \end{align}
-
-The spherical harmonics are orthonormal which means that
-\begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\, Y_\ell^m(\mh{s})\bar{Y}_{\ell'}^{m'}(\mh{s}) = \delta_{\ell\ell'}\delta_{mm'},
+The spherical harmonics are orthonormal, which means that
+\begin{align}
+  \int_{\mbb{S}^2}d\mh{s}\, Y_\ell^m(\mh{s}){Y}_{\ell'}^{m'*}(\mh{s}) = \delta_{\ell\ell'}\delta_{mm'},
 \end{align}
@@
 \end{align}
-We can find the spherical harmonic coefficients $F_\ell^m$ for a given function by
-using Fourier's trick---multiply both sides by $\bar{Y}_\ell^m(\mh{s})$, integrate
-over the sphere, and exploit orthogonality to find that
+We can find the spherical harmonic coefficients $F_\ell^m$ for a given function
+using Fourier's trick---multiply both sides by $\bar{Y}_\ell^m(\mh{s})$,
+integrate over the sphere, and exploit orthogonality to find that
 \begin{align}
@@
 \end{align}
-The coefficients $F_\ell^m$ are usually called the \textit{spherical Fourier
-  transform} of a spherical function.
+The coefficients $F_\ell^m$ are called the \textit{spherical Fourier transform}
+of a spherical function.
 
@@
 \end{align}
-\section{Fourier transform of first and second order Airy patterns} \label{sec:airy}
-\begin{align}
-    a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{k\alpha r_d}\right]^2. 
-\end{align}
-\begin{align}
-  A_n(\nu) \equiv \mathcal{F}_2\{a_n(r_o)\} =  \int_{\mbb{R}^2}d\ro{}\,\text{exp}\left[i2\pi \ro{}\cdot\bs{\nu}\right] a_n(r_d), \label{eq:ftA}
-\end{align}
-
-Our final task is to calculate $A_1(\nu)$ and $A_2(\nu)$. $A_1(\nu)$ is a
-well-known result \cite{goodman1996, mertz2009}, but we review the calculation
-to establish the tools we'll need to evaluate $A_2(\nu)$. We start by using the
-autocorrelation (Wiener-Khinchin) theorem to rewrite the Fourier transform as
-\begin{align}
-  A_1(\nu) = \frac{1}{\pi}\mathcal{F}_2\left\{\left[\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right]^2\right\} = \frac{1}{\pi}\left[\mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}\right] \label{eq:auto}
-\end{align}
-where $\star_2$ denotes a two-dimensional autocorrelation. Next, we recognize
-that the Fourier transforms on the right hand side of Eq. \ref{eq:auto} are
-rotationally symmetric so they can be rewritten as zero-order Hankel transforms
-\begin{align}
-  A_1(\nu) = \frac{1}{\pi}\left[\mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} \star_2 \mathcal{H}_0\left\{\frac{J_1(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}\right] \label{eq:autoz}
-\end{align}
-We can apply the Hankel transform identity \cite{poul1998}
-\begin{align}
-  \mathcal{H}_{n-1}\left\{\frac{J_n(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\} = \frac{\nu^{n-1}}{\nu_o^{n}}\Pi\left(\frac{\nu}{\nu_o}\right),\label{eq:identity}
-\end{align}
-to find that 
-\begin{align}
-  A_1(\nu) = \frac{1}{\pi\nu_o^{2}}\left[\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \Pi\left(\frac{\nu}{\nu_o}\right)\right] \label{eq:auto3}. 
-\end{align}
-We can use the geometric construction in Figure \ref{fig:geometry} to express the
-autocorrelation in terms of an integral over a region of overlap between
-two circles given by
-\begin{align}
-  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \int_{0}^{\nu/2}d\tau_x\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right).
+\section{Fourier transform of higher-order Airy patterns} \label{sec:airy}
+In this appendix we will evaluate the two-dimensional Fourier transform of the
+higher-order Airy patterns given by
+\begin{align}
+  A_n(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, a_n(\mb{r})\, \text{exp}\left[-2\pi i\mb{r}\cdot\bs{\nu}\right],  \label{eq:ftA}
+\end{align}
+where 
+\begin{align}
+    a_n(\mb{r}) =  \frac{n}{\pi}\left[\frac{J_n(k\alpha r)}{r}\right]^2.
+\end{align}
+
+The crucial step is to rewrite the function $a_n(\mb{r})$ in terms of the absolute
+square of a simpler function with a known Fourier transform. In this case we
+rewrite as
+\begin{align}
+  A_n(\bs{\nu}) = \frac{n}{\pi}\int_{\mbb{R}^2}d\mb{r}\, |t(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\cdot\bs{\nu}\right],  \label{eq:ftA}
+\end{align}
+where 
+\begin{align}
+t_n(\mb{r}) = \frac{J_n(2\pi\nu_o r)}{r}\text{exp}[i(n-1)\phi].
+\end{align}
+where $2\pi\nu_o = k\alpha$. Note that we have made a non-obvious choice for
+$t_n(\mb{r})$ because we know that we can find its Fourier transform.
+
+% $A_1(\nu)$ is a well-known result \cite{goodman1996, mertz2009}, but we will
+% review the calculation to establish the tools we'll need to evaluate $A_2(\nu)$.
+Now we can apply the autocorrelation theorem to rewrite the Fourier transform as
+\begin{align}
+  A_n(\bs{\nu}) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \bs{\nu}), \label{eq:autocorr}
+\end{align}
+where
+\begin{align}
+  T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right]. \label{eq:tau}
+\end{align}
+We can evaluate $T_n(\bs{\tau})$ by rewriting in polar coordinates
+\begin{align}
+  T_n(\bs{\tau}) &= \int_0^{2\pi} d\phi \int_{0}^{\infty}dr\, J_n(2\pi\nu_o r)\text{exp}[i(n-1)\phi]\, \text{exp}\left[2\pi ir\tau\cos(\phi - \phi_{\tau})\right].
+\end{align}
+then evaluating the integrals with the identities (Barrett 4.111)
+\begin{align}
+  \int_0^{2\pi} d\phi\, \text{exp}[i(n-1)\phi]\text{exp}[2\pi i \tau r\cos(\phi - \phi_\tau)] = 2\pi i^{n-1}\text{exp}[i(n-1)\phi_\tau]J_{n-1}(2\pi \tau r).
+\end{align}
+and (GR 6.162)
+\begin{align}
+  \int_0^\infty dr J_n(2\pi\nu_o r)J_{n-1}(2\pi\tau r) = \frac{1}{2\pi}\frac{\tau^{n-1}}{\nu_o^n}\Pi\left(\frac{\tau}{2\nu_o}\right),
+\end{align}
+which results in 
+\begin{align}
+  T_n(\bs{\tau}) &= \frac{(i\tau\text{exp}[i\phi_\tau])^{n-1}}{\nu_o^n}\Pi\left(\frac{\tau}{2\nu_o}\right).
+\end{align}
+It will be more convenient to set up the autocorrelation in Cartesian coordinates 
+\begin{align}
+  T_n(\bs{\tau}) &= \frac{(i\tau_x - \tau_y)^{n-1}}{\nu_o^n}\Pi\left(\frac{\sqrt{\tau_x^2 + \tau_y^2}}{2\nu_o}\right). \label{eq:tn}
+\end{align}
+Now we can use Eq. \ref{eq:tn} to evaluate Eq. \ref{eq:autocorr}. Since the
+autocorrelation is rotationally symmetric we can restrict ourselves to shifts
+along the $\mh{x}$ axis so
+\begin{align}
+  A_n(\nu) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \nu\mh{x}).
+\end{align}
+Plugging in Eq. \ref{eq:tn} gives
+\begin{align}
+  A_n(\nu) = \frac{n}{\pi \nu_0^{2n}}\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n-1}\Pi\left(\frac{\sqrt{\tau_x^2 + \tau_y^2}}{\nu_o}\right)\Pi\left(\frac{\sqrt{(\tau_x - \nu)^2 + \tau_y^2}}{2\nu_o}\right).
+\end{align}
+We can interpret the autocorrelation as an integral over a region of overlap
+between a circle centered at the origin and a circle shifted to the right by
+$\nu$ (a geometric lens). Using the construction in Figure \ref{fig:geometry} we
+can express this region as
+\begin{align}
+  A_n(\nu) = \frac{4n}{\pi\nu_o^{2n}}\Bigg[&\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n-1} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n-1}\Bigg]\Pi\left(\frac{\nu}{4\nu_o}\right).
 \end{align}
@@
    \centering
-   \includegraphics[width = 0.8\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
-   \caption{Geometric construction for evaluating the autocorrelations. We need
+   \includegraphics[width = 1.0\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
+   \caption{Geometric construction for evaluating the autocorrelation. We need
      to integrate over the overlapping region of two circles with radius $\nu_o$
@@
 
- To evaluate $A_2(\nu)$ we could follow the same steps, but we will reach a dead
- end because there is no Hankel transform identity for
- $\mathcal{H}_{n-1}\left\{\frac{J_{n+1}(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right\}$.
- Instead, we rewrite $A_2(\nu)$ as
-\begin{align}
-  A_2(\nu) = \frac{2}{\pi}\mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\right]^2\right\} = \frac{2}{\pi}\left[\mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right]^2\right\} + \mathcal{F}_2\left\{\left[\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right]^2\right\}\right].
-\end{align}
-Applying the autocorrelation theorem gives
-\begin{align}
-  A_2(\nu) = \frac{2}{\pi}\Bigg[&\mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\cos\phi_{\nu}\right\} + \nonumber\\ &\mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right\} \star_2 \mathcal{F}_2\left\{\frac{J_2(2\pi\nu_o r_o)}{2\pi\nu_o r_o}\sin\phi_{\nu}\right\}\Bigg].
-\end{align}
-After converting the Fourier transforms to Hankel transforms with the identities
-\begin{align}
-  \mathcal{F}_2\left\{f(r)\cos(\phi)\right\} &= -i\cos\phi_{\nu}\mathcal{H}_1\left\{f(r)\right\},\\
-  \mathcal{F}_2\left\{f(r)\sin(\phi)\right\} &= -i\sin\phi_{\nu}\mathcal{H}_1\left\{f(r)\right\},
-\end{align}
-and evaluating the Hankel transforms with Eq. \ref{eq:identity}, we find that
-\begin{align}
-  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\left\{\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right] + \left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2 \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.
-\label{eq:long}
-\end{align}
-Eq. \ref{eq:long} contains two autocorrelations that require us to find the
-weighted overlap of two circles. Neither of these autocorrelations are
-rotationally symmetric, but their sum must be rotationally symmetric. With this
-symmetry in mind, we recognize that the first autocorrelation is largest for
-shifts along the $x$ direction and smallest for shifts along the $y$ direction
-with a smooth $\cos^2\phi_{\nu}$ weighting between the two extremes. The same is
-true for the second autocorrelations except the $x$ and $y$ axes are exchanged
-and there is a $\sin^2\phi_{\nu}$ weighting between the two extremes. Therefore,
-we can rewrite Eq. \ref{eq:long} as
-\begin{align}
-  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\Bigg\{&\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\cos^2\phi_\nu + \left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\sin^2\phi_\nu + \nonumber\\ &\left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\cos^2\phi_\nu + \left[\nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_y\Pi\left(\frac{\nu}{\nu_o}\right)\right]\sin^2\phi_\nu\Bigg\}.
-\label{eq:long3}
-\end{align}
-where $\star_2^x$ denotes a two-dimensional autocorrelation for shifts along
-the $x$ direction. We can use the following pair of identities
-\begin{align}
-  \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) = \nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_y\Pi\left(\frac{\nu}{\nu_o}\right),\\
-  \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right) = \nu_y\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_y\Pi\left(\frac{\nu}{\nu_o}\right),
-\end{align}
-to simplify Eq. \ref{eq:long3} to
-\begin{align}
-  A_2(\nu) = -\frac{2}{\pi\nu_o^4}\Bigg\{&\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right] + \left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^y \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\Bigg\}.
-\label{eq:long4}
-\end{align}
-First we evaluate the autocorrelation for shifts along the $x$ axis
-\begin{align}
-  &= -\frac{2}{\pi\nu_o^4}\left[\nu_x\Pi\left(\frac{\nu}{\nu_o}\right) \star_2^x \nu_x\Pi\left(\frac{\nu}{\nu_o}\right)\right]\\
-  &= -\frac{8}{\pi\nu_o^4}\Bigg[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau})\\ &\hspace{5em}- \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-For the first inner integral we make use of the following identities
-\begin{align}
-  \int_0^{\cos^{-1}z}d\phi\cos^2\phi &= \frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\cos^{-1}z,\\
-  \int_0^{\cos^{-1}z}d\phi\cos\phi &= \sqrt{1 - z^2},
-\end{align}
-which results in
-\begin{align}
-  &= -\frac{8}{\pi\nu_o^{4}}\Bigg[\int_0^{\nu_o}d\tau\frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2\nu_o}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\nonumber\\ &\hspace{5em}\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  -\frac{8}{\pi\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{1}{\pi}\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &= \frac{1}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &= \frac{1}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}
-\end{align}
-Next we evaluate the autocorrelation for shifts along the $y$ axis
-\begin{align}
-  &\frac{-2}{\pi\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
-  &=  \frac{-8}{\pi\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-For the first inner integral we make use of
-\begin{align}
-  \int\limits_0^{\cos^{-1}z} d\phi \sin^2\phi &= -\frac{1}{2}z\sqrt{1 - z^2} + \frac{1}{2}\cos^{-1}(z).
-\end{align}
-This results in
-\begin{align}
-  &=\frac{-8}{\pi\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{-8}{\pi\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \cos^{-1}\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  &=  \frac{1}{\pi}\Bigg[\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[5 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).
-\label{eq:auto2}
-\end{align}
-Taking the sum of Eqs. \ref{eq:auto1} and \ref{eq:auto2} gives the final result
-\begin{align}
-  A_2(\nu) = \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-% \section{Evaluating the angular transfer function}
-% Our goal in this Appendix is to calculate the angular transfer function by
-% taking the spherical Fourier transform of
-% \begin{align}
-%   h(r, \vartheta) = h_{\text{exc}}(\vartheta)h_{\text{det}}(r, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[a_1(r)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r)\cos^2\vartheta.\right] \label{eq:kernel}
-% \end{align}
-% We need to evaluate the integrals
-% \begin{align}
-%   F_l^m(r) \propto \int_{\mbb{S}^2} d\so h_{\text{exc}}(\vartheta)h_{\text{det}}(r, \vartheta)Y_\ell^m(\vartheta, \varphi). \label{eq:atf}
-% \end{align}
-% We could evaluate the integrals in Eq.
-% \ref{eq:kernel} using a computer algebra system, but here we evaluate by hand to
-% demonstrate a useful trick for taking the spherical harmonic transform of the
-% product of two spherical functions. First, we expand both the excitation and
-% detection kernels in a sum of spherical harmonic functions
-% \begin{align}
-%   F_l^m(r) \propto \int_{\mbb{S}^2} d\so \left[\sum_{{\ell'} m'}H_{{\ell'},\text{exc}}^{m'} Y_{\ell'}^{m'}(\vartheta, \varphi)\right]\left[\sum_{{\ell''} m''}H_{{\ell''},\text{det}}^{m''}(r) Y_{\ell''}^{m''}(\vartheta, \varphi)\right]Y_\ell^m(\vartheta, \varphi).
-% \end{align}
-% Next, we exchange the order of the sums and integrals
-% \begin{align}
-%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) \int_{\mbb{S}^2} d\so Y_\ell^m(\vartheta, \varphi) Y_{\ell'}^{m'}(\vartheta, \varphi) Y_{\ell''}^{m''}(\vartheta, \varphi).
-% \end{align}
-% Finally, if we make the definition
-% \begin{align}
-%   G_{\ell\ell'\ell''}^{mm'm''} = \int_{\mbb{S}^2}d\so\, Y_\ell^m(\vartheta, \varphi) Y_{\ell'}^{m'}(\vartheta, \varphi) Y_{\ell''}^{m''}(\vartheta, \varphi)
-% \end{align}
-% and write the angular transfer function as
-% \begin{align}
-%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) G_{\ell\ell'\ell''}^{mm'm''}. 
-% \end{align}
-% This is a valuable result because it allows us to compute the spherical harmonic
-% transform of the detection and excitation kernels individually then combine the
-% results into the final angular transfer function. The constants
-% $G_{\ell\ell'\ell''}^{mm'm''}$ are called the \textit{Gaunt coefficients} and
-% can be precomputed or found in tables.
-
-% Next, we compute the spherical Fourier transform of the excitation kernel. 
-% \begin{align}
-%   H_{\ell',\text{exc}}^{m'} \propto \int_{\mbb{S}^2}d\so\, h_{\text{exc}}(\vartheta)Y_{\ell}^m(\vartheta, \varphi). 
-% \end{align}
-% From Appendix \ref{sec:sph} we know that the integral will be zero except when
-% $m=0$ and when $\ell$ is even. Starting with $\ell = 0$ and $m=0$
-% \begin{align}
-%   H_{0,\text{exc}}^{0} \propto \int_{\mbb{S}^2}d\so\, \left[\sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta\right]\left[\frac{1}{\sqrt{4\pi}}\right] = \frac{4\sqrt{\pi}}{3}\left[1 + \frac{\alpha^2}{4}\right].
-% \end{align}
-% Next we evaluate $\ell = 2$ and $m=0$
-% \begin{align}
-%   H_{2,\text{exc}}^{0} \propto \int_{\mbb{S}^2}d\so\, \left[\sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta\right]\left[\sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1)\right] = \frac{4\sqrt{\pi}}{3}\frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right].
-% \end{align}
-% Finally, we notice can verify that the excitation kernel can be written as just
-% two spherical harmonics using the equality
-% \begin{align}
-%  h_{\text{exc}}(r, \vartheta) &= H_{0,\text{exc}}^0Y_0^0(\vartheta, \varphi) + H_{2,\text{exc}}^0Y_2^0(\vartheta, \varphi),\\
-%   \sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta &= \frac{4\sqrt{\pi}}{3}\left[1 + \frac{\alpha^2}{4}\right]\left[\frac{1}{\sqrt{4\pi}}\right] + \frac{4\sqrt{\pi}}{3}\frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{2}\right]\left[\sqrt{\frac{5}{16\pi}}(3\cos^2\vartheta - 1)\right].
-% \end{align}
-
-% \begin{align}
-%   H_{\ell',\text{exc}}^{m'} \propto \left[1 + \frac{\alpha^2}{4}\right]\delta_{\ell'0}\delta_{m0} + \frac{1}{\sqrt{5}}\left[-1 + \frac{\alpha^2}{4}\right]\delta_{\ell'0}\delta_{m0}.
-% \end{align}
-% Similarly, the spherical Fourier transform of the detection kernel is given by
-% \begin{align}
-%   H_{\ell'',\text{det}}^{m''} \propto \left[a_1(r) + \frac{\alpha^2}{4}a_2(r)\right]\delta_{\ell''0}\delta_{m0} + \frac{1}{\sqrt{5}}\left[-a_1(r) + \frac{\alpha^2}{4}a_2(r)\right]\delta_{\ell''0}\delta_{m0}.
-% \end{align}
-% Finally, we use the Gaunt coefficients to calculate the angular transfer function
-% \begin{align}
-%   F_l^m(r) \propto \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell',\text{exc}}^{m'}H_{\ell'',\text{det}}^{m''}(r) G_{\ell\ell'\ell''}^{mm'm''}.   
-% \end{align}
-% \begin{alignat}{6}
-%   F_l^m(r) \propto \quad 7&\{\hphantom{-}32&&a_1(r)&& + 4\alpha^2[a_1(r) + a_2(r)]&&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
-%   4\sqrt{5}&\{-16&&a_1(r)&& + \hphantom{1}\alpha^2[a_1(r) + a_2(r)] &&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
-%   8&\{\hphantom{-1}4&&a_1(r)&& - 2\alpha^2[a_1(r) + a_2(r)] &&+ \hphantom{1}\alpha^4a_2(r)\}&&\delta_{\ell 4}\delta_{m0}.
-% \end{alignat}
-% H0
-% 28*A1*a**2 + 224*A1 + 21*A2*a**4 + 28*A2*a**2
-% (Pdb) H2
-% 4*sqrt(5)*(A1*a**2 - 16*A1 + 3*A2*a**4 + A2*a**2)
-% (Pdb) H4
-% -16*A1*a**2 + 32*A1 + 8*A2*a**4 - 16*A2*a**2
+ We will only evaluate these integrals for $n=1$ and $n=2$, but the result for
+ arbitrary $n$ is likely possible as a recurrence relation. For $n=1$:
+
+\begin{align}
+  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right]\Pi\left(\frac{\nu}{4\nu_o}\right),\\
+%  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \int_{0}^{\nu/2}d\tau_x\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right).
+\end{align}
+which is a well-known result \cite{goodman1996, mertz2009}. For $n=2$:
+\begin{align}
+  A_2(\nu) = \frac{8}{\pi\nu_o^{4}}\Bigg[&\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
+  A_2(\nu) = \frac{2}{\pi}\Bigg\{&\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{4\nu_o}\right).
+\end{align}
+
+\section{Spherical Fourier transform of a double cone}\label{sec:cone}
+In this appendix we will evaluate the spherical Fourier transform of a
+normalized double-cone angular distribution with central direction $\mh{s}'$ and
+cone half-angle $\Delta$
+\begin{align}
+  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{2\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right). 
+\end{align}
+The spherical Fourier transform is given by
+\begin{align}
+  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)\bar{Y}_\ell^m(\mh{s}).
+\end{align}
+The limits of integration will be difficult to find unless we change coordinates
+to exploit the axis of symmetry $\mh{s}'$. Since the spherical function is
+rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
+symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')$ to account for the rotation
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
+\end{align}
+In this coordinate system the double cone is independent of the azimuthal angle,
+so we can evaluate the azimuthal integral and express the function in terms of an
+integral over
+$\vartheta$
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^m(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
+\end{align}
+The function $f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)$ is only non-zero on
+the intervals $\vartheta \in [0, \Delta]$ and
+$\vartheta \in [\pi - \Delta, \pi]$ so
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right].
+\end{align}
+Applying a change of coordinates with $u = \cos\vartheta$ yields
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right]. 
+\end{align}
+The Legendre polynomials $P_\ell(u)$ are even (odd) on the interval [-1, 1] when
+$\ell$ is even (odd), so the pair of integrals will be identical when $\ell$ is
+even and cancel when $\ell$ is odd. For even $\ell$
+\begin{align}
+  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
+\end{align}
+The integral evaluates to \cite{gradshteyn2007} 7.111 
+\begin{align}
+  \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
+\begin{cases}
+  1 - \cos\Delta\,, &\ell = 0\,,\\
+  \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
+\end{cases}
+\end{align}
+where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
+$m=-1$, not an inverse Legendre polynomial. Bringing everything together
+
+\begin{align}
+  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) =
+  \begin{cases}
+    1, & \ell = 0,\\
+    0, & \ell\, \text{odd},\\
+    Y_\ell^m(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
+  \end{cases}
+\end{align}
 

### 2018-11-03 papers/basic-theory/paper/paper.tex
Updates to section 2.

@@
 \usepackage{empheq}
-% \usepackage{bm}
+\usepackage{bm}
 
@@
 \providecommand{\tb}[1]{\textcolor{blue}{#1}}
-\DeclareFontFamily{OT1}{pzc}{}
-\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
+% \DeclareFontFamily{OT1}{pzc}{}
+% \DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
+% \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
 \newcommand{\eqname}[1]{\tag*{#1}}
@@
   expressed in a basis of spatial and spherical harmonics---a form we call the
-  spatio-angular transfer function (SATF). We demonstrate our formalism by
+  spatio-angular dipole transfer function. We demonstrate our formalism by
   analyzing a single-view paraxial epi-fluorescence microscope without using the
@@
 systems and extend the usual monopole imaging model to dipoles. Along the way we
-introduce transfer functions that will allow us to efficiently simplify our
-analysis of spatio-angular microscopes. In Section \ref{sec:results} we use the
-mathematical tools we developed in Section \ref{sec:theory} to analyze and
-simulate a single-view paraxial epi-fluorescence microscope, and we demonstrate
-our model with four simple phantoms. Finally, in Section \ref{sec:discussion} we
-discuss the results and their broader implications.
+introduce transfer functions that will allow us to efficiently analyze
+spatio-angular microscopes. In Section \ref{sec:results} we use the mathematical
+tools we developed in Section \ref{sec:theory} to analyze and simulate a
+single-view paraxial epi-fluorescence microscope, and we demonstrate our model
+with four simple phantoms. Finally, in Section \ref{sec:discussion} we discuss
+the results and their broader implications.
 
@@
 Section \ref{sec:monopole} we will demonstrate the formalism by examining a
-familiar monopole imaging model, and we will show that the point spread
-function and the optical transfer function are mappings between object and data
-space expressed in two different bases. In Section \ref{sec:dipole} we will
+familiar monopole imaging model, and we will demonstrate the mapping in between
+object and data in two different bases. In Section \ref{sec:dipole} we will
 extend the monopole imaging model to dipoles and examine the mapping in four
@@
 a delta function basis the object can be represented by a function $f(\ro)$
-called the \textit{spatial monopole density}---the number of monopoles per unit
-area at the two-dimensional position $\ro$. Similarly, in a delta function basis
-the data can be represented by a function $g'(\rd')$ called the
+called the \textit{monopole density}---the number of monopoles per unit area at
+the two-dimensional position $\ro$. Similarly, in a delta function basis the
+data can be represented by a function $g'(\rd')$ called the
 \textit{irradiance}---the power received by a surface per unit area at position
@@
 \end{align}
-The point spread function corresponds to a measurable irradiance, so it is
-always real-valued and positive.
+The monopole point spread function corresponds to a measurable irradiance, so it
+is always real-valued and positive.
 
@@
 \end{align}
-the \textit{optical transfer function} as
+the \textit{monopole transfer function} as
 \begin{align}
@@
 \end{align}
-The point spread function is normalized and real-valued, so we know that the
-optical transfer function is normalized $H(0) = 1$ and conjugate-symmetric
-$H(-\bs{\nu}) = H^*(\bs{\nu})$.
+The monopole point spread function is normalized and real-valued, so we know
+that the monopole transfer function is normalized $H(0) = 1$ and
+conjugate-symmetric $H(-\bs{\nu}) = H^*(\bs{\nu})$.
 
@@
 
+We have used the term \textit{monopole transfer function} instead of the more
+common \textit{optical transfer function}. We define the optical transfer
+function as the mapping between an input irradiance spectrum and an output
+irradiance spectrum in an optical system. With this definition the optical
+transfer function is not necessarily the same as the monopole transfer function.
+For example, consider a light sheet illumination scheme where a sheet of the
+sample is illuminated and an orthogonal detection arm collects the emitted
+fluorescence. Both the excitation path and the detection path can be described
+by optical transfer functions, and the monopole transfer function is given by
+the convolution of the two optical transfer functions. We will see that this is
+a valuable distinction when we consider dipole transfer functions.
+
 \subsubsection{Monopole coherent transfer functions}
+Although the Fourier transform can be used to calculate the monopole transfer
+function directly from the monopole point spread function, there is a well-known
+alternative that exploits coherent transfer functions. The key idea is that the
+monopole point spread function can always be written as the absolute square of a
+scalar-valued \textit{monopole coherent spread function} defined as
+\begin{align}
+  h(\mb{r}) = |c(\mb{r})|^2. \label{eq:absquarescalar}
+\end{align}
+Physically, the monopole coherent spread function is the scalar-valued field on
+the detector with appropriate scaling.
+
+Since the monopole transfer function is given by the two-dimensional Fourier
+transform of the monopole point spread function
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\nu}],
+\end{align}
+we can plug in Eq. \ref{eq:absquarescalar} and use the autocorrelation theorem to
+rewrite the monopole transfer function as
+\begin{align}
+  H(\bs{\nu}) = \int_{\mbb{R}^2}d\bs{\tau}\, C(\bs{\tau})C^*(\bs{\tau} - \bs{\nu}), 
+\end{align}
+where $z^*$ denotes the complex conjugate of $z$, and we have introduced the
+\textit{monopole coherent transfer function} as the two-dimensional Fourier
+transform of the orientation-dependent coherent spread function
+\begin{align}
+  C(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, c(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\tau}].
+\end{align}
+Physically, the monopole coherent transfer function is the scalar-valued field
+in a Fourier plane of the detector (often called the pupil or aperture plane)
+with appropriate scaling. This provides a valuable shortcut for analyzing
+arbitrary microscopes since it is usually straightforward to calculate the field
+in the pupil. A typical approach for calculating the transfer functions is to
+(1) calculate the field in the pupil, (2) scale the field to find the coherent
+monopole transfer function, then (3) use the relationships in Figure
+\ref{fig:monopole-transfer-functions} to calculate the other transfer functions.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=1.0]{../figures/monopole-transfer-functions/monopole-transfer-functions.pdf}
+  \caption{The incoherent monopole transfer functions are related by a
+    two-dimensional Fourier transform (right column). The coherent monopole
+    transfer functions (left column) can be used to simplify the calculation of
+    the remaining transfer functions.}
+   \label{fig:monopole-transfer-functions}
+ \end{figure}
 
@@
 In a delta function basis the object can be represented by a function
-$f(\ro, \so)$ called the \textit{spatio-angular dipole density}---the number of
-dipoles at position $\ro{}$ per unit area oriented along $\so{}$ per unit solid
-angle. Similar to the monopole case, we model the mapping between the object and
-the irradiance in a delta function basis as an integral transform
+$f(\ro, \so)$ called the \textit{dipole density}---the number of dipoles at
+position $\ro{}$ per unit area oriented along $\so{}$ per unit solid angle.
+Similar to the monopole case, we model the mapping between the object and the
+irradiance in a delta function basis as an integral transform
 \begin{align}
@@
 dipoles
-$P_\text{dip} = \int_{\mbb{S}^2}d\mb{s}\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
-\mb{s})$. We use these scaling factors to define the
-\textit{orientation-dependent point spread function} as
-\begin{align}
-  h(\rd - \ro, \mb{s}) = \frac{h'(m[\rd - \ro], \mb{s})}{P_\text{dip}}, 
+$P_\text{dip} = \int_{\mbb{S}^2}d\mh{s}\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
+\mh{s})$. We use these scaling factors to define the
+\textit{dipole point spread function} as
+\begin{align}
+  h(\rd - \ro, \so) = \frac{h'(m[\rd - \ro], \so)}{P_\text{dip}}, 
 \end{align}
@@
 With these definitions we can express the mapping between the object and the
-data as an integral over the sphere with a spatial convolution at each point
+data as
 \begin{align}
@@
 \end{align}
-Similar to the monopole case, we have chosen to normalize the orientation-dependent point spread function so that
+
+Similar to the monopole case, we have chosen to normalize the dipole point
+spread function so that
 \begin{align}
@@
 \end{align}
-The orientation-dependent point spread function is a measurable quantity, so it
-is real-valued and positive.
-
-\subsubsection{Orientation-dependent optical transfer function}
+The dipole point spread function is a measurable quantity, so it is real-valued
+and positive.
+
+\subsubsection{Spatial dipole transfer function}
 We can make our first change of basis by applying the Fourier-convolution
@@
 \end{align}
-where we define the \textit{orientation-dependent optical transfer function} as
+where we define the \textit{spatial dipole transfer function} as
   \begin{align}
@@
   \end{align}
-  Since the orientation-dependent point spread function is normalized and real,
-  we know that the orientation-dependent optical transfer function is normalized
+  Since the dipole point spread function is normalized and real, we know that
+  the spatial dipole transfer function is normalized
   $\int_{\mbb{S}^2}d\mh{s}\, H(0, \mh{s}) = 1$ and conjugate-symmetric
@@
 
-\subsubsection{Angular transfer function}
+\subsubsection{Angular dipole transfer function}
 The spherical harmonics are another set of convenient basis functions. We can
@@
 \end{align}
-where $p(\mh{s})$ and $q(\mh{s})$ are arbitrary functions on the sphere and
+where $p(\mh{s})$ and $q(\mh{s})$ are arbitrary functions on the sphere, $P_\ell^m$ and $Q_\ell^m$ are their spherical Fourier transforms defined by
 \begin{align}
@@
 \end{align}
-is the spherical Fourier transform of $p(\mh{s})$ and $Y_{\ell}^m(\mh{s})$ are
-the spherical harmonic functions defined in Appendix \ref{sec:sph}. Eq.
-\ref{eq:plan} expresses the fact that scalar products are invariant under a
-change of basis (see Eq. 3.78 of \cite{barrett2004}). The left-hand side of Eq.
-\ref{eq:plan} is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
-delta function basis and the right hand side is the scalar product of
-$\mbb{L}_2(\mbb{S}^2)$ functions in a spherical harmonic function basis.
-Applying Eq. \ref{eq:plan} to Eq. \ref{eq:odpsf} yields
+and $Y_{\ell}^m(\mh{s})$ are the spherical harmonic functions defined in
+Appendix \ref{sec:sph}. Eq. \ref{eq:plan} expresses the fact that scalar
+products are invariant under a change of basis (see Eq. 3.78 of
+\cite{barrett2004}). The left-hand side of Eq. \ref{eq:plan} is the scalar
+product of $\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the
+right hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
+spherical harmonic function basis. Applying Eq. \ref{eq:plan} to Eq.
+\ref{eq:odpsf} yields
 \begin{align}
@@
 \end{align}
-where we have defined the \textit{angular transfer function} as
+where we have defined the \textit{angular dipole transfer function} as
 \begin{align}
@@
 \end{align}
-Since the orientation-dependent point spread function is normalized and
-real-valued, we know that the angular transfer function is normalized
+Since the dipole point spread function is normalized and real-valued, we know
+that the angular dipole transfer function is normalized
 $\int_{\mbb{R}^2}d\mb{r}\, H_0^0(\mb{r}) = 1$ and conjugate symmetric
@@
 
-\subsubsection{Spatio-angular transfer function}
+\subsubsection{Spatio-angular dipole transfer function}
 We can arrive at our final basis in two ways: by applying the generalized
@@
 \end{align}
-where we have defined the \textit{spatio-angular transfer function} as
+where we have defined the \textit{spatio-angular dipole transfer function} as
   \begin{align}
@@
   \end{align}
-  Since the orientation-dependent point spread function is normalized and
-  real-valued, we know that the spatio-angular transfer function is normalized
+  Since the dipole point spread function is normalized and real-valued, we know
+  that the spatio-angular dipole transfer function is normalized
   $\msf{H}_0^0(0) = 1$ and conjugate symmetric
@@
   advantage explicitly in Section XXX when we calculate a specific
-  spatio-angular transfer function and see that it has an angular band limit.
+  spatio-angular dipole transfer function and see that it has an angular band
+  limit.
 
@@
 \subsubsection{Dipole coherent transfer functions}
-Two-dimensional Fourier transforms and spherical Fourier transforms are the only
-operations required to change between the transfer functions. However, there is
-a well-known alternative for calculating optical transfer functions in terms of
-coherent transfer functions. The key idea is that the orientation-dependent
-point spread function can always be written as the absolute square of a
-vector-valued function called the \textit{orientation-dependent coherent spread
-  function}
-\begin{align}
-  h(\mb{r}, \mh{s}) = |\mb{c}(\mb{r}, \mh{s})|^2. \label{eq:absquare}
-\end{align}
-Physically, this decomposition corresponds to the fact that the irradiance is
-always the absolute square of a vector-valued electric field.
-
-Since the orientation-dependent transfer function is given by the
-two-dimensional Fourier transform of the orientation-dependent point spread
-function
+Similar to the monopole case, there is efficient way to calculate the transfer
+functions using coherent transfer functions. The dipole point spread function
+can always be written as the absolute square of a vector-valued function called
+the \textit{dipole coherent spread function}
+\begin{align}
+  h(\mb{r}, \mh{s}) = |\mb{c}(\mb{r}, \mh{s})|^2. \label{eq:absquare2}
+\end{align}
+Physically, the dipole coherent spread function is an appropriately scaled
+vector-valued electric field on the detector. We need a vector-valued coherent
+transfer function since the polarization of the field plays a significant role
+in dipole imaging.
+
+Since the spatial dipole transfer function is given by the two-dimensional
+Fourier transform of the dipole point spread function
 \begin{align}
@@
 \end{align}
-we can plug in Eq. \ref{eq:absquare} and use the autocorrelation theorem to
-rewrite as
+we can plug in Eq. \ref{eq:absquare2} and use the autocorrelation theorem to
+rewrite the spatial dipole transfer function as 
 \begin{align}
@@
 \end{align}
-where the \textit{orientation-dependent coherent transfer function}
-$\mb{C}(\bs{\tau}, \mh{s})$ is the two-dimensional Fourier transform of the
-orientation-dependent coherent spread function
+where we have introduced the \textit{dipole coherent transfer function}
+$\mb{C}(\bs{\tau}, \mh{s})$ as the two-dimensional Fourier transform of the
+dipole coherent spread function
 \begin{align}
@@
 \end{align}
-The relationships between all six transfer function are shown in Figure
-\ref{fig:transfer-functions}. Note that we could define coherent equivalents for
-all four incoherent transfer functions, but we restrict ourselves to these two
-since they are the useful for our calculations.
+Physically, the dipole coherent transfer function corresponds to the
+vector-valued electric field created by a dipole with oriented along $\mh{s}$ in
+a Fourier plane of the detector with appropriate scaling. As with the monopole
+case we can calculate the dipole-orientation-dependent fields in the pupil
+plane, scale them appropriately to find the dipole coherent transfer function,
+the use the relationships in Figure \ref{fig:transfer-functions} to calculate
+the other transfer functions. Note that we could define coherent equivalents
+for all four incoherent transfer functions, but we restrict ourselves to these
+two since they are the most useful for our calculations.
 
@@
     columns. There are an additional pair of coherent transfer functions that
-    are useful for calculating the point spread function and optical transfer
-    function---see left column.}
+    are useful for calculating the incoherent transfer functions---see left column.}
    \label{fig:transfer-functions}

### 2018-11-05 papers/basic-theory/paper/paper.tex
Improved notation and aplanatic assumption.

@@
 \providecommand{\so}{\mathbf{\hat{s}}_o}
-\providecommand{\rb}{\mathbf{r}_b}
+\providecommand{\rp}{\mathbf{r}_p}
 \providecommand{\rbm}[1]{r_b^{\text{m}}}
@@
 \providecommand{\bv}{\bs{\nu}}
+\providecommand{\bvp}{\bs{\nu}_p}
 \providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
@@
 
-The irradiance pattern measured by many fluorescence microscopes can be modeled
+Next, we assume that the optical system is \textit{aplanatic}---Abbe's sine
+condition is satisfied and on-axis points are imaged without aberration. Abbe's
+sine condition guarantees that off-axis points are imaged without spherical
+aberration or coma \cite{mansuripur2009}, so the imaging system can be modeled
 (at least approximately) as a magnifier with shift-invariant blur
 \begin{align}
-  g'(\rd') = \int_{\mbb{R}^2}d\ro\, h'(\rd' - m\ro)f(\ro), 
-\end{align}
-where $m$ is a magnification factor. To simplify our analysis we define a
-demagnified detector coordinate $\rd = \rd'/m$ and a normalization factor that
-corresponds to the total power incident on the detector plane due to a point
-source $P_{\text{mono}} = \int_{\mbb{R}^2}d\mb{r}\,h'(m\mb{r})$. We use these scaling
-factors to define the \textit{point spread function} as
+  g'(\rd') = \int_{\mbb{R}^2}d\ro\, h'(\rd' - m\ro)f(\ro), \label{eq:nonconv}
+\end{align}
+where $m$ is a magnification factor.
+
+We can simplify our analysis by changing coordinates and writing Eq.
+\ref{eq:nonconv} as a convolution \cite{barrett2004}. We define a demagnified
+detector coordinate $\rd = \rd'/m$ and a normalization factor that corresponds
+to the total power incident on the detector plane due to a point source
+$P_{\text{mono}} = \int_{\mbb{R}^2}d\mb{r}\,h'(m\mb{r})$ where
+$\mb{r} = \rd - \ro$. We use these scaling factors to define the
+\textit{monopole point spread function} as
 \begin{align}
@@
 \begin{align}
-  g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro),  \label{eq:lsi}
-\end{align}
-which will allow us to analyze this class of microscopes without carrying
-magnification or normalization factors. We will mostly be using scaled
-coordinates, so we have adopted a slightly unusual convention of using primes to
-denote unscaled coordinates.
-
-We have chosen to normalize the point spread function so that
+  g(\rd) = \int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro).  \label{eq:lsi}
+\end{align}
+We will mostly be using scaled coordinates, so we have adopted a slightly
+unusual convention of using primes to denote unscaled coordinates.
+
+We have chosen to normalize the monopole point spread function so that
 \begin{align}
@@
 \end{align}
-The monopole point spread function corresponds to a measurable irradiance, so it
-is always real-valued and positive.
+The monopole point spread function corresponds to a
+measurable irradiance, so it is always real-valued and positive.
 
@@
 \begin{align}
-  G(\bs{\nu}) = H(\bs{\nu})F(\bs{\nu}),\label{eq:freq}
+  G(\bv) = H(\bv)F(\bv),\label{eq:freq}
 \end{align}
@@
 \begin{align}
-  G(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+  G(\bv) = \int_{\mbb{R}^2}d\mb{r}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bv),
 \end{align}
@@
 \begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),\label{eq:otf}
+  H(\bv) = \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bv),\label{eq:otf}
 \end{align}
@@
 \begin{align}
-    F(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}).
+    F(\bv) = \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bv).
 \end{align}
@@
 that the monopole transfer function is normalized $H(0) = 1$ and
-conjugate-symmetric $H(-\bs{\nu}) = H^*(\bs{\nu})$.
+conjugate-symmetric $H(-\bv) = H^*(\bv)$.
 
@@
 \begin{align}
-  h(\mb{r}) = |c(\mb{r})|^2. \label{eq:absquarescalar}
-\end{align}
-Physically, the monopole coherent spread function is the scalar-valued field on
-the detector with appropriate scaling.
+  |c(\rd - \ro)|^2 = h(\rd - \ro). \label{eq:absquarescalar}
+\end{align}
+Physically, the monopole coherent spread function corresponds to the
+scalar-valued field on the detector with appropriate scaling.
 
@@
 \begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\nu}],
+  H(\bv) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bv],
 \end{align}
@@
 \begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\bs{\tau}\, C(\bs{\tau})C^*(\bs{\tau} - \bs{\nu}), 
+  H(\bv) = \int_{\mbb{R}^2}d\bvp\, C(\bvp)C^*(\bvp - \bv), 
 \end{align}
@@
 \textit{monopole coherent transfer function} as the two-dimensional Fourier
-transform of the orientation-dependent coherent spread function
-\begin{align}
-  C(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, c(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\tau}].
-\end{align}
-Physically, the monopole coherent transfer function is the scalar-valued field
-in a Fourier plane of the detector (often called the pupil or aperture plane)
-with appropriate scaling. This provides a valuable shortcut for analyzing
-arbitrary microscopes since it is usually straightforward to calculate the field
-in the pupil. A typical approach for calculating the transfer functions is to
-(1) calculate the field in the pupil, (2) scale the field to find the coherent
-monopole transfer function, then (3) use the relationships in Figure
+transform of the monopole coherent spread function
+\begin{align}
+  C(\bvp) = \int_{\mbb{R}^2}d\mb{r}\, c(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bvp].
+\end{align}
+Physically, the monopole coherent transfer function corresponds to the
+scalar-valued field in a Fourier plane of the detector with appropriate scaling.
+We have chosen the symbol $\bvp$ as the coordinate for the coherent
+transfer function because the Fourier plane of the detector is often called the
+\textit{pupil plane}.
+
+The coherent transfer function provides a valuable shortcut for analyzing
+microscopes since it is usually straightforward to calculate the field in the
+aperture plane. A typical approach for calculating the transfer functions is to
+(1) calculate the field in the aperture plane, (2) scale the field to find the
+coherent monopole transfer function, then (3) use the relationships in Figure
 \ref{fig:monopole-transfer-functions} to calculate the other transfer functions.
@@
 where $h'(\rd', \ro, \so)$ is the irradiance at position $\rd'$ created by a
-point source at $\ro$ with orientation $\so$. Once again, many fluorescence
-microscopes can be modeled as magnifiers with shift-invariant blur
+point source at $\ro$ with orientation $\so$. If the imaging system is
+linear and aplanatic we can write the integral transform as
 \begin{align}
@@
 $P_\text{dip} = \int_{\mbb{S}^2}d\mh{s}\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
-\mh{s})$. We use these scaling factors to define the
+\so)$. We use these scaling factors to define the
 \textit{dipole point spread function} as
@@
 \begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \mh{s}) = 1. 
+  \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \so) = 1. 
 \end{align}
@@
 \begin{align}
-G(\bs{\nu}) = \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})F(\bs{\nu}, \mh{s}) \label{eq:odotf},
+G(\bv) = \int_{\mbb{S}^2}d\so\, H(\bv, \so)F(\bv, \so) \label{eq:odotf},
 \end{align}
@@
   \begin{align}
-  H(\bs{\nu}, \mh{s}) &= \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \mh{s})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}),
+  H(\bv, \so) &= \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \so)\, \text{exp}(-2\pi i\mb{r}\cdot\bv),
   \end{align}
@@
   \begin{align}
-  F(\bs{\nu}, \mh{s}) &= \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r}, \mh{s})\, \text{exp}(-2\pi i\mb{r}\cdot\bs{\nu}). 
+  F(\bv, \so) &= \int_{\mbb{R}^2}d\mb{r}\, f(\mb{r}, \so)\, \text{exp}(-2\pi i\mb{r}\cdot\bv). 
   \end{align}
@@
   the spatial dipole transfer function is normalized
-  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \mh{s}) = 1$ and conjugate-symmetric
-  $H(-\bs{\nu}, \mh{s}) = H^*(\bs{\nu}, \mh{s})$.
+  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \so) = 1$ and conjugate-symmetric
+  $H(-\bv, \so) = H^*(\bv, \so)$.
 
@@
 \begin{align}
-  \ints{2}d\mh{s}{}\, p(\mh{s})q(\mh{s}) = \lmsum P_\ell^m Q_\ell^m, \label{eq:plan}
+  \ints{2}d\mh{s}\, p(\mh{s})q(\mh{s}) = \lmsum P_\ell^m Q_\ell^m, \label{eq:plan}
 \end{align}
@@
 product of $\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the
-right hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
+right-hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
 spherical harmonic function basis. Applying Eq. \ref{eq:plan} to Eq.
@@
 \begin{align}
-  H_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, h(\mb{r}, \mh{s})Y_{\ell}^{m*}(\mh{s}),\label{eq:atf-prep} 
+  H_\ell^m(\rd - \ro) = \int_{\mbb{S}^2}d\so\, h(\rd - \ro, \so)Y_{\ell}^{m*}(\so),\label{eq:atf-prep} 
 \end{align}
@@
 \begin{align}
-  F_\ell^m(\mb{r}) = \int_{\mbb{S}^2}d\mh{s}\, f(\mb{r}, \mh{s})Y_{\ell}^{m*}(\mh{s}).
+  F_\ell^m(\ro) = \int_{\mbb{S}^2}d\so\, f(\ro, \so)Y_{\ell}^{m*}(\so).
 \end{align}
@@
 \begin{align}
-G(\bs{\nu}) = \lmsum \msf{H}_\ell^m(\bs{\nu})\msf{F}_\ell^m(\bs{\nu}) \label{eq:saft},
+G(\bv) = \lmsum \msf{H}_\ell^m(\bv)\msf{F}_\ell^m(\bv) \label{eq:saft},
 \end{align}
@@
   \begin{align}
-  \msf{H}_\ell^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\mh{s}\, H(\bs{\nu}, \mh{s})Y_\ell^{m*}(\mh{s}),
+  \msf{H}_\ell^m(\bv) &= \int_{\mbb{S}^2}d\so\, H(\bv, \so)Y_\ell^{m*}(\so),
   \end{align}
@@
   \begin{align}
-  \msf{F}_\ell^m(\bs{\nu}) &= \int_{\mbb{S}^2}d\mh{s}\, F(\bs{\nu}, \mh{s})Y_\ell^{m*}(\mh{s}).
+  \msf{F}_\ell^m(\bv) &= \int_{\mbb{S}^2}d\so\, F(\bv, \so)Y_\ell^{m*}(\so).
   \end{align}
@@
   $\msf{H}_0^0(0) = 1$ and conjugate symmetric
-  $\msf{H}_\ell^{-m}(-\bs{\nu}) = (-1)^m\msf{H}_\ell^{m*}(\bs{\nu})$.
+  $\msf{H}_\ell^{-m}(-\bv) = (-1)^m\msf{H}_\ell^{m*}(\bv)$.
 
@@
 \begin{align}
-  h(\mb{r}, \mh{s}) = |\mb{c}(\mb{r}, \mh{s})|^2. \label{eq:absquare2}
-\end{align}
-Physically, the dipole coherent spread function is an appropriately scaled
-vector-valued electric field on the detector. We need a vector-valued coherent
-transfer function since the polarization of the field plays a significant role
-in dipole imaging.
+  |\mb{c}(\rd - \ro, \so)|^2 = h(\rd - \ro, \so). \label{eq:absquare2}
+\end{align}
+Physically, the dipole coherent spread function corresponds to the vector-valued
+electric field on the detector with appropriate scaling. We need a vector-valued
+coherent transfer function since the polarization of the field plays a
+significant role in dipole imaging, so the point spread function cannot be
+written as an absolute square of a scalar-valued function.
 
@@
 \begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r}, \mh{s})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\nu}],
+  H(\bv) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\bv],
 \end{align}
@@
 \begin{align}
-  H(\bs{\nu}) = \int_{\mbb{R}^2}d\bs{\tau}\,\mb{C}(\bs{\tau}, \mh{s})\mb{C}^\dagger(\bs{\tau} - \bs{\nu}, \mh{s}), 
+  H(\bv) = \int_{\mbb{R}^2}d\bvp\,\mb{C}(\bvp, \so)\mb{C}^\dagger(\bvp - \bv, \so), 
 \end{align}
 where we have introduced the \textit{dipole coherent transfer function}
-$\mb{C}(\bs{\tau}, \mh{s})$ as the two-dimensional Fourier transform of the
-dipole coherent spread function
-\begin{align}
-  \mb{C}(\bs{\tau}, \mh{s}) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \mh{s})\,\text{exp}[-2\pi i\mb{r}\cdot\bs{\tau}].
+$\mb{C}(\bvp, \so)$ as the two-dimensional Fourier transform of the dipole
+coherent spread function
+\begin{align}
+  \mb{C}(\bvp, \so) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\bvp].
 \end{align}
 Physically, the dipole coherent transfer function corresponds to the
-vector-valued electric field created by a dipole with oriented along $\mh{s}$ in
-a Fourier plane of the detector with appropriate scaling. As with the monopole
-case we can calculate the dipole-orientation-dependent fields in the pupil
-plane, scale them appropriately to find the dipole coherent transfer function,
-the use the relationships in Figure \ref{fig:transfer-functions} to calculate
-the other transfer functions. Note that we could define coherent equivalents
-for all four incoherent transfer functions, but we restrict ourselves to these
-two since they are the most useful for our calculations.
+vector-valued electric field created by a dipole oriented along $\so$ in a
+Fourier plane of the detector with appropriate scaling. Similar to the monopole
+case, we can calculate the orientation-dependent fields in the aperture plane,
+scale appropriately to find the dipole coherent transfer function, then use the
+relationships in Figure \ref{fig:transfer-functions} to calculate the other
+transfer functions. Note that we could define coherent equivalents for all four
+incoherent transfer functions, but we restrict ourselves to these two since they
+are the most useful for our calculations.
 
@@
 $h(\rd - \ro)$. First, we place a monopole emitter at the focal point of an
-objective lens and calculate the field $U_{\text{bfp}}(\rb)$ created in the back
+objective lens and calculate the field $U_{\text{bfp}}(\rp)$ created in the back
 focal plane. We can model a paraxial thin lens as a quadratic phase element, so
@@
 \end{align}
-where $\rb$ is the two-dimensional coordinate in the back focal plane and
+where $\rp$ is the two-dimensional coordinate in the back focal plane and
 $\alpha$ is the collection half angle---see Figure XXX.
@@
 \begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right].\label{eq:det1}
+  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rp{} \mb{E}_{\text{bfp}}(\rp{})\, \text{exp}\left[ik\,\rp{}\cdot\rd{}\right].\label{eq:det1}
 \end{align}
@@
   \begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rb{} \mb{E}_{\text{bfp}}(\rb{})\, \text{exp}\left[ik\,\rb{}\cdot\rd{}\right],\label{eq:det2}
+  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rp{} \mb{E}_{\text{bfp}}(\rp{})\, \text{exp}\left[ik\,\rp{}\cdot\rd{}\right],\label{eq:det2}
   \end{align}
@@
 \begin{align}
-  A_n(\bs{\nu}) = \int_{\mbb{R}^2}d\mb{r}\, a_n(\mb{r})\, \text{exp}\left[-2\pi i\mb{r}\cdot\bs{\nu}\right],  \label{eq:ftA}
+  A_n(\bv) = \int_{\mbb{R}^2}d\mb{r}\, a_n(\mb{r})\, \text{exp}\left[-2\pi i\mb{r}\cdot\bv\right],  \label{eq:ftA}
 \end{align}
@@
 \begin{align}
-  A_n(\bs{\nu}) = \frac{n}{\pi}\int_{\mbb{R}^2}d\mb{r}\, |t(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\cdot\bs{\nu}\right],  \label{eq:ftA}
+  A_n(\bv) = \frac{n}{\pi}\int_{\mbb{R}^2}d\mb{r}\, |t(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\cdot\bv\right],  \label{eq:ftA}
 \end{align}
@@
 \begin{align}
-  A_n(\bs{\nu}) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \bs{\nu}), \label{eq:autocorr}
+  A_n(\bv) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \bv), \label{eq:autocorr}
 \end{align}

### 2018-11-07 papers/basic-theory/paper/paper.tex
Improved discussion of aplanatic imaging. Added pupil function sections.

@@
 
-\title{Spatio-angular fluorescence microscopy I. Basic theory}
-
-\author{Talon Chandler,\authormark{1,*} Author order TBD,\authormark{2,*} and Patrick La Rivi\`ere \authormark{1}}
+\title{Spatio-angular fluorescence microscopy I. Basic theory (Draft: \today)}
+
+\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
 
@@
   We introduce the basic elements of a spatio-angular theory of fluorescence
-  microscopy. We start by modeling a microscope imaging an ensemble of in-focus
-  fluorescent dipoles as a linear Hilbert-space operator with domain
+  microscopy. We start by modeling an aplanatic microscope imaging an ensemble
+  of in-focus fluorescent dipoles as a linear Hilbert-space operator with domain
   $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$, and we
@@
   spatio-angular dipole transfer function. We demonstrate our formalism by
-  analyzing a single-view paraxial epi-fluorescence microscope without using the
-  monopole or scalar approximations. We show that this microscope has an angular
-  band limit, and we demonstrate the value of the transfer function approach by
-  efficiently simulating the imaging process with simple phantoms. Notably, we
-  show that information about the out-of-plane orientation of ensembles of
-  in-focus fluorophores is recorded by paraxial epi-fluorescence microscopes. We
-  discuss the implications of our analysis for all quantitative fluorescence
-  microscopy studies and lay out a path towards a complete theory.
+  analyzing a single-view fluorescence microscope without using the monopole or
+  scalar approximations. We show that this microscope has an angular band limit,
+  and we demonstrate the value of the transfer function approach by efficiently
+  simulating the imaging process with simple phantoms. Notably, we show that
+  information about the out-of-plane orientation of ensembles of in-focus
+  fluorophores is recorded by fluorescence microscopes, and we show that these
+  effects persist in the paraxial limit. We discuss the implications of our
+  analysis for all quantitative fluorescence microscopy studies and lay out a
+  path towards a complete theory.
 \end{abstract*}
@@
 This work lies at the intersection of three classes of fluorescence microscopy:
-(1) single molecule localization microscopy (SMLM), (2) spatial ensemble
-fluorescence microscopy including widefield, confocal, and light-sheet
-techniques, and (3) polarized fluorescence microscopy. We briefly review these
-three classes and focus on their use of the monopole and scalar approximations.
-
-The SMLM community has pioneered the use of rigorous electromagnetic models of
-fluorescence microscopes \cite{backer2014, lieb2004} [cite Novotny]. When a
-single molecule is fluorescing in the sample, the measured intensity pattern is
-strongly dependent on the orientation of the emitting molecule. Backlund [cite]
-and Lew [cite] \cite{backlund2014} have shown that ignoring the orientation of
-fluorophores can bias position estimates, so the most accurate SMLM experiments
-must jointly estimate the position and orientation of each molecule.
-
-Meanwhile, most fluorescence microscopists image ensembles of fluorophores and
-restore their images without considering the role that the monopole and scalar
-approximations play in the restoration process. A typical fluorescence
-microscopist is only interested in the spatial distribution of fluorophores, so
-they reason that they can ignore the orientation of the emitters.
+(1) ensemble imaging techniques where many fluorophores are imaged in parallel
+and the goal is to find their concentration throughout the sample, (2) single
+molecule localization microscopy (SMLM) techniques where fluorophores are sparse
+in the sample and the goal is to find the position of each fluorophore, and (3)
+polarized fluorescence techniques where many fluorophores are imaged in parallel
+and the goal is to find their concentration and orientation. We briefly review
+these three classes and focus on their use of the monopole and scalar
+approximations.
+
+The large majority of fluorescence microscopes are used to image ensembles of
+fluorophores, and many widely used restoration techniques make either or both of
+the monopole and scalar approximations. The Gibson-Lanni model \cite{gibson89}
+and the Born and Wolf model \cite{born1980} are two examples of scalar models
+that are widely used to restore data collected by fluorescence microscopes, and
+the Richards and Wolf model \cite{richards} is another widely-used model that
+accounts for vectorial diffraction. All three of these models describe how
+optical fields propagate through an optical system, but they are agnostic to the
+object that is being imaged. In other words, these models are \textit{optical}
+models, and when they are used to model fluorescent objects they implicitly make
+the monopole approximation.
+
+The SMLM community has pioneered the use of rigorous electromagnetic models for
+dipole imaging systems that do not adopt the scalar or monopole approximations
+\cite{backer2014, lieb2004, nov2006}. When a single molecule fluoresces, its
+irradiance pattern on the detector is strongly dependent on the orientation of
+the emitting molecule. Backlund et al. \cite{backlund2014} have shown have shown
+that ignoring the orientation of fluorophores can bias position estimates, so
+the most accurate SMLM experiments must jointly estimate the position and
+orientation of each molecule. Some SMLM experiments use polarizers to estimate
+the orientation of single molecules more accurately [Backer DNA paper, other
+Moerner papers], and these works do not adopt the scalar or monopole
+approximations.
 
 A smaller community of microscopists is interested in measuring the orientation
-of ensembles of fluorophores \cite{mehta2016} [Forkey, Goldman, Moerner,
-Oldenbourg]. These techniques typically use polarized illumination or polarized
-detection to make multiple measurements of the same object. Current angular
-restoration techniques use a model of the dipole excitation and emission
+and position of ensembles of fluorophores \cite{mehta2016} [Forkey, Goldman,
+Moerner, Oldenbourg]. These techniques typically use polarized illumination or
+polarized detection to make multiple measurements of the same object. Current
+angular restoration techniques use a model of the dipole excitation and emission
 processes [Fourkas] to recover the orientation of fluorophores using pixel-wise
 arithmetic, but these techniques do not perform any spatial restoration so they
-do not use all of the available information. To our knowledge no work has been
-done to model the complete spatio-angular response of fluorescence microscopes
-to ensembles of oriented fluorophores.
-
+do not use all of the available information.
+
+In this work we place these three communities on a common theoretical footing.
 We begin in Section \ref{sec:theory} by formulating the imaging problem
@@
 tools we developed in Section \ref{sec:theory} to analyze and simulate a
-single-view paraxial epi-fluorescence microscope, and we demonstrate our model
-with four simple phantoms. Finally, in Section \ref{sec:discussion} we discuss
-the results and their broader implications.
+single-view epi-fluorescence microscope, and we demonstrate our model with four
+simple phantoms. Finally, in Section \ref{sec:discussion} we discuss the results
+and their broader implications.
 
@@
 Section \ref{sec:monopole} we will demonstrate the formalism by examining a
-familiar monopole imaging model, and we will demonstrate the mapping in between
-object and data in two different bases. In Section \ref{sec:dipole} we will
-extend the monopole imaging model to dipoles and examine the mapping in four
-different bases.
+familiar monopole imaging model, and we will demonstrate the mapping between
+object and data space in two different bases. In Section \ref{sec:dipole} we
+will extend the monopole imaging model to dipoles and examine the mapping in
+four different bases.
 
@@
 point on a plane, so we identify object space as
-$\mbb{U} = \mbb{L}_2(\mbb{R}^2)$. Similarly, we have a two-dimensional detector
-that measures a real number at every point on a plane, so data space is the same
-set $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$.
+$\mbb{U} = \mbb{L}_2(\mbb{R}^2)$---the set of square-integrable functions on the
+two-dimensional plane. Similarly, we have a two-dimensional detector that
+measures a real number at every point on a plane, so data space is the same set
+$\mbb{V} = \mbb{L}_2(\mbb{R}^2)$.
 
@@
 aberration or coma \cite{mansuripur2009}, so the imaging system can be modeled
-(at least approximately) as a magnifier with shift-invariant blur
+within the field-of-view of the optical system as a magnifier with
+shift-invariant blur
 \begin{align}
@@
 \end{align}
-where $m$ is a magnification factor.
+where $m$ is a magnification factor. Note that we have modeled the object and
+data as continuous two-dimensional functions that extend to infinity. All real
+objects must be restricted to a finite field-of-view and the data must be
+discretely sampled, but we continue with continuous function with infinite
+extent for convenience.
 
@@
 that the monopole transfer function is normalized $H(0) = 1$ and
-conjugate-symmetric $H(-\bv) = H^*(\bv)$.
+conjugate-symmetric $H(-\bv) = H^*(\bv)$ where $z^*$ denotes the complex
+conjugate of $z$.
 
@@
 
-We have used the term \textit{monopole transfer function} instead of the more
-common \textit{optical transfer function}. We define the optical transfer
-function as the mapping between an input irradiance spectrum and an output
-irradiance spectrum in an optical system. With this definition the optical
-transfer function is not necessarily the same as the monopole transfer function.
-For example, consider a light sheet illumination scheme where a sheet of the
-sample is illuminated and an orthogonal detection arm collects the emitted
-fluorescence. Both the excitation path and the detection path can be described
-by optical transfer functions, and the monopole transfer function is given by
-the convolution of the two optical transfer functions. We will see that this is
-a valuable distinction when we consider dipole transfer functions.
+Note that we have used the term \textit{monopole transfer function} instead of
+the commonly-used term \textit{optical transfer function}. We reserve the term
+\textit{optical transfer function} for optical systems---the optical transfer
+function maps between an input irradiance spectrum and an output irradiance
+spectrum in an optical system. We can use optical transfer functions to model
+the optical fields in a microscope, but ultimately we are always interested in
+measuring an object. Although the monopole transfer function can be identical to
+the optical transfer function, we will find the distinction to be valuable when
+we consider dipole transfer functions.
 
@@
 \end{align}
-where $z^*$ denotes the complex conjugate of $z$, and we have introduced the
+where we have introduced the
 \textit{monopole coherent transfer function} as the two-dimensional Fourier
@@
 microscopes since it is usually straightforward to calculate the field in the
-aperture plane. A typical approach for calculating the transfer functions is to
-(1) calculate the field in the aperture plane, (2) scale the field to find the
+pupil plane. A typical approach for calculating the transfer functions is to (1)
+calculate the field in the pupil plane, (2) scale the field to find the
 coherent monopole transfer function, then (3) use the relationships in Figure
@@
 where $h'(\rd', \ro, \so)$ is the irradiance at position $\rd'$ created by a
-point source at $\ro$ with orientation $\so$. If the imaging system is
-linear and aplanatic we can write the integral transform as
+point source at $\ro$ with orientation $\so$. If the optical system is aplanatic
+we can write the integral transform as
 \begin{align}
@@
 \begin{align}
-  g(\rd) = \lmsum H_\ell^m(\rd - \ro)F_\ell^m(\ro) \label{eq:atf-form}
+  g(\rd) = \lmsum H_\ell^m(\rd - \ro)F_\ell^m(\ro), \label{eq:atf-form}
 \end{align}
@@
 \section{Results}\label{sec:results}
-In this section we apply the tools we developed in the previous sections to
-analyze a paraxial epi-fluorescence microscope. We start by reviewing the
-derivation of the monopole point spread function in preparation for the
-derivation of the orientation-dependent point spread function. We conclude the
-section by analyzing the dipole imaging map in the four bases we described
-earlier.
-
-TODO: Define and discuss paraxial. 4f, illumination uniformity and ignoring in
-monopole Where are excitation and detection dipoles parallel.
-
-\subsection{Monopole point spread function of a paraxial epi-fluorescence microscope}
-In this section we derive the form of the monopole point spread function
-$h(\rd - \ro)$. First, we place a monopole emitter at the focal point of an
-objective lens and calculate the field $U_{\text{bfp}}(\rp)$ created in the back
-focal plane. We can model a paraxial thin lens as a quadratic phase element, so
-it converts an incident spherical wave to a plane wave in the back focal plane
-with a sharp cutoff at the exit pupil of the lens
+In this section we begin to apply the tools we developed in the previous section
+to analyze more specific fluorescence microscopes. During our initial discussion
+we only required the optical system to be aplanatic so that we could model it as
+a shift-invariant magnifier. Now we will be more specific and consider an
+aplanatic optical system in a \textit{$4f$ configuration} with an arbitrary
+first lens (the objective) and a \textit{paraxial second lens} (the tube lens).
+A lens can be considered paraxial if the angle $\alpha$ between the optical axis
+of the lens and the marginal ray is small enough that
+$\sin\alpha \approx \alpha$. As a rule of thumb, paraxial effects become
+significant when the numerical aperture of a lens exceeds 0.7 \cite{gu2000}, but
+this is only a rough guideline.
+
+We start by defining \textit{pupil functions} for both monopole and dipole
+imaging systems, and we explicitly relate the pupil function to the previously
+defined coherent transfer function. Next, we calculate the transfer functions
+for monopole and dipole imaging systems with high-NA objectives. We resort to
+numerics as necessary, but we can calculate several transfer function in closed
+form. We compare these results with paraxial results which are completely in
+closed form.
+
+\subsection{Monpole pupil functions}
+We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
+the field immediately following the aperture plane created by an on-axis
+monopole where $\rp$ is an unscaled two-dimensional coordinate in the pupil
+plane. In this section we will relate the monopole pupil function to the
+transfer function we defined in Section \ref{sec:theory} by following a near
+variant of the path in Barrett and Myers Section 9.7 \cite{barrett2004}.
+
+Since monopoles emit scalar fields, the monpole pupil function is a
+scalar-valued function. The optical system is aplanatic, so we can write the
+field created at a point in the aperture $\rp$ by a monopole at position $\ro$
+as
+\begin{align}
+   U_p(\rp, \ro) \propto p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil}
+\end{align}
+Eq. \ref{eq:pupil} is a restatement of the aplanatic condition for a $4f$
+optical system---the field in the aperture plane can be written as the pupil
+function multiplied by a linear phase factor that encodes the position of the
+object.
+
+Since the second lens is paraxial, we can model with relationship between the
+field in the aperture plane and the field on the detector with a scaled Fourier
+transform \cite{goodman1996}
+\begin{align}
+   U_d(\rd', \ro) \propto \int_{\mbb{R}^2}d\rp\, p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
+\label{eq:detectorfourier}
+\end{align}
+If we define $P(\bvp)$ as the two-dimensional Fourier transform of the pupil function
+then we can rewrite Eq. \ref{eq:detectorfourier} as
+\begin{align}
+  U_d(\rd', \ro) \propto P\left(\frac{n_0}{\lambda f_0}\ro + \frac{n_1}{\lambda f_1}\rd'\right),
+\end{align}
+which we can simplify further in terms of $m = -\frac{f_1n_0}{f_0n_1}$
+\begin{align}
+  U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right),
+\end{align}
+The irradiance on the detector is given by the absolute square of the field so
+\begin{align}
+  h'(\rd' - m\ro) \propto \left|P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right)\right|^2.
+\end{align}
+If we demagnify the coordinates $\rd = \rd'/m$ and the irradiance
+$h(\rd - \ro) \propto h'(m[\rd - \ro])$ we find that the monopole point spread function
+is related to the Fourier transform of the monopole pupil function by
+\begin{align}
+  h(\rd - \ro) \propto \left|P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right)\right|^2.
+\end{align}
+The monopole coherent spread function is the absolute square of the monopole point spread function so
+\begin{align}
+  c(\rd - \ro) \propto P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right).
+\end{align}
+The monopole coherent transfer function is the Fourier transform of the monopole coherent spread function so
+\begin{align}
+  C(\bvp) \propto p\left(\frac{\lambda f_o}{n_o}\bvp\right). \label{eq:monopupil}
+\end{align}
+Equation \ref{eq:monopupil} is the key result of this section---the monopole
+coherent transfer function is a scaled monopole pupil function.
+
+\subsection{Dipole pupil function} 
+We define the \textit{dipole pupil function} $\mb{p}(\rp, \so)$ of the imaging
+system as the electric field immediately following the aperture plane created by
+a dipole oriented along $\so$. Since dipoles emit vector-valued electric fields,
+the dipole pupil function is a vector-valued function. Almost all of the
+arguments in the previous section carry over to the dipole case. Briefly, we can
+write the electric field created at a point in the aperture $\rp$ by a dipole at
+$\ro$ oriented along $\so$ as
+ \begin{align}
+   \mb{E}(\rp, \ro, \so) = \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
+ \end{align}
+ The second lens is paraxial, so we can find the field on the detector with a
+ Fourier transform
+ \begin{align}
+   \mb{E}_d(\rd', \ro, \so) \propto \int_{\mbb{R}^2}d\rp\, \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
+\label{eq:detectorfourier2}
+\end{align}
+Note that the Fourier transform of a vector field is the Fourier transform of
+its scalar-valued orthogonal components, so Eq. \ref{eq:detectorfourier2}
+specifies two two-dimensional Fourier transforms. We follow the same
+manipulations as the previous section and find that the dipole coherent transfer
+function is a scaled dipole pupil function
+\begin{align}
+  \mb{C}(\bvp, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\bvp, \so\right). \label{eq:monopupil}
+\end{align}
+
+\subsection{Monopole transfer functions}
+Several works \cite{petrov2017, backlund2018} have modeled an aplanatic
+fluorescence microscope imaging isotropic emitters with the scalar pupil
+function
+\begin{align}
+  p(\rp) \propto (1 - r_p^2)^{-1/4}\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
+\end{align}
+where $\Pi(\cdot)$ is a rectangle function defined by
+\begin{align}
+  \Pi(x) = 
+  \begin{cases}
+    1\quad \text{if}\quad |x| < \frac{1}{2},\\
+    0\quad \text{else},
+  \end{cases}
+\end{align}
+which models the aperture stop of the objective, and $(1 - r_p^2)^{-1/4}$
+conserves power before and after the objective. Applying Eq. XXX we see that the
+coherent transfer function for this system is given by
+\begin{align}
+  C(\bvp)
+\end{align}
+
+In this section we calculate the form of the monopole point spread function
+$h(\rd - \ro)$ when both lenses of the optical system are paraxial. First, we
+place a monopole emitter at the focal point of the objective lens. We can model
+a paraxial thin lens as a quadratic phase element, so it converts an incident
+spherical wave to a plane wave in the back focal plane with a sharp cutoff at
+the exit pupil of the lens
 \begin{align}
@@
 
-TODO Expand. Make clear that later paper. We postpone a full discussion of SVD to find the object space singular functions
-that span the measurement space of the instrument.
+TODO Expand. Make clear that a later paper will include a full discussion of SVD
+to find the object space singular functions that span the measurement space of
+the instrument.
 
@@
 
+TODO: Cite Tournier/Descoteux change of basis from SH to SM basis.
+
 \subsection{What determines the angular frequency cutoff?}
-The spatial-frequency cutoff of a fluorescence microscope is well known to vary
-as NA$/\lambda$---we can increase spatial resolution by increasing the NA of the
+The spatial-frequency cutoff of a fluorescence microscope is well known to be
+2NA$/\lambda$---we can increase spatial resolution by increasing the NA of the
 instrument or by choosing a fluorophore with a shorter emission wavelength.
@@
 
-\subsection{Characterizing real spatio-angular microscopes}
+\subsection{Towards more realistic models}
 The theoretical model we present in this work is an extreme simplification of a
-real microscope. We have ignored the effects of thick samples, optical
-aberration, scattering, high-NA objectives, finite fluorescence lifetimes, and
-interactions between fluorophores, among other. Because of this long list of
-unknown effects, real experiments should make an attempt to characterize the
-specific imaging system.
-
-Typical fluorescence microscopy experiments start with the monopole
-approximation and attempt to characterize the microscope by imaging
-sub-diffraction beads. These images are assumed to be good approximations of the
-monopole point spread function and this data can be used to restore (deconvolve)
-the data taken in arbitrary experiments.
-
-Imaging sub-diffraction beads is not enough to completely characterize the
-response of a microscope to an oriented sample. We need at least three samples
-with a known orientations to characterize the SATF, so isotropic beads are not
-enough. Small beads may not be isotropic [cite Lew].
+real microscope. We have ignored the effects of thick samples, refractive-index
+mismatch, aberration, scattering, rotation of fluorophores, finite fluorescence
+lifetimes, and interactions between fluorophores among others. Because of this
+long list of unknown effects, real experiments will likely require extensions of
+the models developed here.
+
+TODO: Discuss/plan future papers. SVD?
+Defocus/3D imaging:
+$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3)$.
+Polarized illumination/detection imaging:
+$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)$.
+Multiview polarized illumination imaging:
+$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)^V$.
+
+TODO: Mention and cite rotating dipoles like Lew (model start point, rotation, end point):
+$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2\times\mbb{SO}^3\times\mbb{S}^2) \rightarrow \mbb{V}$.
+
+TODO: Cite connection between dipole pupil and Jones pupil. We can use the
+Jones/dipole pupil as a way to extend our model in a straightforward way. Add
+phase aberration (like the Gibson-Lanni model), polarization aberrations,
+amplitude masks, phase masks, etc. Also cite Piestun Green's tensor engineering.
+
+% Typical fluorescence microscopy experiments start with the monopole
+% approximation and attempt to characterize the microscope by imaging
+% sub-diffraction beads. These images are assumed to be good approximations of the
+% monopole point spread function and this data can be used to restore (deconvolve)
+% the data taken in arbitrary experiments.
+
+% Imaging sub-diffraction beads is not enough to completely characterize the
+% response of a microscope to an oriented sample. We need at least three samples
+% with a known orientations to characterize the SATF, so isotropic beads are not
+% enough. Small beads may not be isotropic [cite Lew].
 

### 2018-11-07 papers/basic-theory/figures/dipole-block/dipole-block.tex
Add latest figs and bib.

@@
 \usepackage{tikz}
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm}
+\usepackage{amsmath, amsthm, amssymb, amsfonts}
 \usetikzlibrary{shapes,arrows.meta}
-\usepackage{mathptmx}
+\usepackage{newtxtext,newtxmath,courier}
 \DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
@@
 % Talon's custom commands
+\usepackage{xcolor}
+\newcommand{\gray}[1]{\colorbox{black!10!white}{$\displaystyle #1\hspace{-0.2em}$}\,}
 \newcommand{\argmin}{\arg\!\min}
@@
 
-\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=7em, align=center]
+\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=5em, minimum width=7em, align=center]
 
@@
     \tikzset{font={\fontsize{9pt}{12}\selectfont}}
-    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Spatio-angular\\ density};
-    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular density\\ spectrum};
-    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Irradiance};
-    \node [block, below of=ads, node distance=2.5cm] (sas) {$F_\ell^m(\bs{\nu})$\\ Spatio-angular\\ spectrum};
-    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
-    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial density\\ spectrum};
+    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Dipole\\ density};
+    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular\\ dipole\\ spectrum};
+    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Scaled\\ irradiance};
+    \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{F}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole\\ spectrum};
+    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Scaled\\ irradiance\\ spectrum};
+    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial\\ dipole\\ spectrum};
     \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
@@
 
-    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\rd - \ro)F_\ell^m(\ro)$} (irr);
-    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Orientation-dependent\\ point spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, h(\rd - \ro, \so)f(\ro, \so)$} ++(13cm,0) --  (irr.north);
-    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Orientation-dependent\\ optical transfer function\\ $\int_{\mbb{S}^2}d\so\, H(\bs{\nu}, \so)F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
-    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu})$} (is);
+    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{H_\ell^m(\rd - \ro)}F_\ell^m(\ro)$} (irr);
+    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Dipole point\\ spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, \gray{h(\rd - \ro, \so)}f(\ro, \so)$} ++(13cm,0) --  (irr.north);
+    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Spatial dipole\\ transfer function\\ $\int_{\mbb{S}^2}d\so\, \gray{H(\bs{\nu}, \so)}F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
+    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{\mathsf{H}_\ell^m(\bs{\nu})}\mathsf{F}_\ell^m(\bs{\nu})$} (is);
 

### 2018-11-07 papers/basic-theory/figures/monopole-block/monopole-block.tex
Add latest figs and bib.

@@
-\documentclass[crop,tikz]{standalone}% 'crop' is the default for v1.0, before it was 'preview'
+\documentclass[osa-article,crop,tikz]{standalone}% 'crop' is the default for v1.0, before it was 'preview'
 % \usetikzlibrary{...}% tikz package already loaded by 'tikz' option
 \usepackage{tikz}
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm}
+\usepackage{amsmath, amsthm, amssymb, amsfonts}
 \usetikzlibrary{shapes,arrows.meta}
-\usepackage{mathptmx}
+\usepackage{newtxtext,newtxmath,courier}
 \DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
-% \DeclareMathAlphabet{\boldsymbol}{OMS}{cmsy}{m}{n}
 
 % Talon's custom commands
+\usepackage{xcolor}
+\newcommand{\gray}[1]{\colorbox{black!10!white}{$\displaystyle #1\hspace{-0.2em}$}\,}
 \newcommand{\argmin}{\arg\!\min}
@@
     \node [block, below of=den, node distance=2.5cm] (ds) {$F(\bs{\nu})$\\ Monopole\\ spectrum};
-    \node [block,  right of=den, node distance=7cm] (irr) {$g(\rd)$\\ Irradiance};
-    \node [block,  right of=ds, node distance=7cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
+    \node [block,  right of=den, node distance=7cm] (irr) {$g(\rd)$\\ Scaled\\ irradiance};
+    \node [block,  right of=ds, node distance=7cm] (is) {$G(\bs{\nu})$\\ Scaled\\ irradiance\\ spectrum};
     \draw [->] (den) -- node[] {$\mathcal{F}_{\mathbb{R}^2}$} (ds);
     \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);
-
-    \draw [->] (den) -- node[text width=4cm, align=center] (cap1) {Point spread\\ function\\ $\int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro)$} (irr);
-    \draw [->] (ds) -- node[text width=4cm, align=center] (cap1) {Optical transfer\\ function\\ $H(\bs{\nu})F(\bs{\nu})$} (is);
+    \draw [->] (den) -- node[text width=4cm, align=center] (cap1) {Monopole point\\ spread function\\ $\int_{\mbb{R}^2}d\ro\, \gray{h(\rd - \ro)} f(\ro)$} (irr);
+    \draw [->] (ds) -- node[text width=4cm, align=center] (cap1) {Monopole transfer\\ function\\ $\gray{H(\bs{\nu})}F(\bs{\nu})$} (is);
 
     % Dashed box
-    \draw [dashed] (den.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6cm) -- ++(-3.4cm,0) -- ++(0, 6cm);
-    \draw [dashed] (irr.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6cm) -- ++(-3.4cm,0) -- ++(0, 6cm);
+    \draw [dashed] (den.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6.5cm) -- ++(-3.4cm,0) -- ++(0, 6.5cm);
+    \draw [dashed] (irr.north west) ++(-0.5cm,1.6cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-6.5cm) -- ++(-3.4cm,0) -- ++(0, 6.5cm);
       \end{tikzpicture}

### 2018-11-07 papers/basic-theory/figures/transfer-functions/transfer-functions.tex
Add latest figs and bib.

--- 2018-10-20 papers/basic-theory/figures/dipole-block/dipole-block.tex
@@
 
-\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=7em, align=center]
-
+\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=10em, align=center]
 \begin{document}
-  \begin{tikzpicture}[auto, node distance=2cm,>={Latex[length=2mm]}]
+  \begin{tikzpicture}[auto, node distance=2.5cm,>={Latex[length=2mm]}]
     \tikzset{font={\fontsize{9pt}{12}\selectfont}}
-    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Spatio-angular\\ density};
-    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular density\\ spectrum};
-    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Irradiance};
-    \node [block, below of=ads, node distance=2.5cm] (sas) {$F_\ell^m(\bs{\nu})$\\ Spatio-angular\\ spectrum};
-    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Irradiance\\ spectrum};
-    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial density\\ spectrum};
-    \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
-    \draw [->] (ads) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
-    \draw [->] (sds) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
+    \node [block, align=center] (sad) {$h(\rd - \ro, \so)$\\ Dipole point\\ spread function};
+    \node [block,  right of=sad, node distance=5.5cm] (ads) {$H_\ell^m(\rd - \ro)$\\ Angular dipole\\ transfer function};
+    \node [block,  left of=sad, node distance=5.5cm] (e) {$\mb{c}(\rd - \ro, \so)$\\ Coherent dipole \\ spread function};
+      \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{H}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole transfer function};
+      \node [block, below of=sad, node distance=2.5cm] (sds) {$H(\bs{\nu}, \so)$\\ Dipole\\ transfer function};
+        \node [block,  left of=sds, node distance=5.5cm] (e2) {$\mb{C}(\bvp,\so)$\\ Coherent dipole \\transfer function};
+      \draw [->] (sad) -- node[shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);
+      \draw [->] (e) -- node[shift={(0,.75)}] {$|\mb{c}(\rd - \ro, \so)|^2$} (sad);
+      % \draw [->] (e2) -- node[] {$\int_{\mbb{R}^2}d\rb \mb{E}_{\text{bfp}}(\rb, \so)\mb{E}_{\text{bfp}}^\dagger(\rb - \bs{\nu}, \so)$} (sds);
+            \draw [->] (e2) -- node[below, shift={(0,-0.75)}] {$\int_{\mbb{R}^2}d\bvp\, \mb{C}(\bvp, \so)\mb{C}^\dagger(\bvp - \bs{\nu}, \so)$} (sds);        
+      \draw [->] (ads) -- node[left, shift={(0,0)}] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
+          \draw [->] (e) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (e2);
+    \draw [->] (sds) -- node[below, shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
     \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
-    \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);
-
-    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\rd - \ro)F_\ell^m(\ro)$} (irr);
-    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Orientation-dependent\\ point spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, h(\rd - \ro, \so)f(\ro, \so)$} ++(13cm,0) --  (irr.north);
-    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Orientation-dependent\\ optical transfer function\\ $\int_{\mbb{S}^2}d\so\, H(\bs{\nu}, \so)F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
-    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular\\ transfer function\\ $\sum_{\ell m}H_\ell^m(\bs{\nu})F_\ell^m(\bs{\nu})$} (is);
-
-    % Dashed box
-    \draw [dashed] (sad.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Object space\\ $\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$} ++(7.5cm,0) -- ++(0,-9cm) -- ++(-7.5cm,0) -- ++(0, 9cm);
-    \draw [dashed] (irr.north west) ++(-0.5cm,3cm) -- node[below, align=center] {Data space\\ $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$} ++(3.4cm,0) -- ++(0,-9cm) -- ++(-3.4cm,0) -- ++(0, 9cm);
       \end{tikzpicture}

### 2018-11-07 papers/basic-theory/figures/excitation/excitation.py

@@ -46,7 +46,7 @@ for col in range(cols):
     ax.set_xticklabels(['0','$\pi/8$','$\pi/4$','$3\pi/8$','$\pi/2$'])
 
     ax.text(0.5, -0.25, 'Inclination angle $\\vartheta$', ha='center', va='center', transform=ax.transAxes)
-    ax.text(-0.3, 0.5, 'Excitation kernel $h_{\\textrm{exc}}(\\vartheta)$', ha='center', va='center', rotation=90, transform=ax.transAxes)
+    ax.text(-0.3, 0.5, 'Excitation response $h_{\\textrm{exc}}(\\vartheta)$', ha='center', va='center', rotation=90, transform=ax.transAxes)
     
 
 f.savefig('excitation.pdf', dpi=500, bbox_inches='tight')

### 2018-11-07 papers/basic-theory/paper/paper.tex
Corrected a few typos.

@@
   analyzing a single-view fluorescence microscope without using the monopole or
-  scalar approximations. We show that this microscope has an angular band limit,
-  and we demonstrate the value of the transfer function approach by efficiently
-  simulating the imaging process with simple phantoms. Notably, we show that
-  information about the out-of-plane orientation of ensembles of in-focus
-  fluorophores is recorded by fluorescence microscopes, and we show that these
-  effects persist in the paraxial limit. We discuss the implications of our
-  analysis for all quantitative fluorescence microscopy studies and lay out a
-  path towards a complete theory.
+  scalar approximations. We show that this imaging system has an angular band
+  limit, and we demonstrate the value of the transfer function approach by
+  efficiently simulating the imaging process with simple phantoms. Notably, we
+  show that information about the out-of-plane orientation of ensembles of
+  in-focus fluorophores is recorded by fluorescence microscopes, and we show
+  that these effects persist in the paraxial limit. We discuss the implications
+  of our analysis for all quantitative fluorescence microscopy studies and lay
+  out a path towards a complete theory.
 \end{abstract*}
@@
 We start by defining \textit{pupil functions} for both monopole and dipole
-imaging systems, and we explicitly relate the pupil function to the previously
-defined coherent transfer function. Next, we calculate the transfer functions
+imaging systems, and we explicitly relate the pupil functions to the previously
+defined coherent transfer functions. Next, we calculate the transfer functions
 for monopole and dipole imaging systems with high-NA objectives. We resort to
@@
 \begin{align}
-  C(\bvp) \propto p\left(\frac{\lambda f_o}{n_o}\bvp\right). \label{eq:monopupil}
-\end{align}
-Equation \ref{eq:monopupil} is the key result of this section---the monopole
+  C(\bvp) \propto p\left(\frac{\lambda f_o}{n_o}\bvp\right). \label{eq:monopupil0}
+\end{align}
+Equation \ref{eq:monopupil0} is the key result of this section---the monopole
 coherent transfer function is a scaled monopole pupil function.
@@
 system as the electric field immediately following the aperture plane created by
-a dipole oriented along $\so$. Since dipoles emit vector-valued electric fields,
-the dipole pupil function is a vector-valued function. Almost all of the
-arguments in the previous section carry over to the dipole case. Briefly, we can
-write the electric field created at a point in the aperture $\rp$ by a dipole at
-$\ro$ oriented along $\so$ as
+an on-axis dipole oriented along $\so$. Since dipoles emit vector-valued
+electric fields, the dipole pupil function is a vector-valued function. Almost
+all of the arguments in the previous section carry over to the dipole case.
+Briefly, we can write the electric field created at a point in the aperture
+$\rp$ by a dipole at $\ro$ oriented along $\so$ as
  \begin{align}

### 2018-11-21 papers/basic-theory/paper/paper.tex
New special functions, added simulation figures.

@@
 \providecommand{\bv}{\bs{\nu}}
-\providecommand{\bvp}{\bs{\nu}_p}
+\providecommand{\taup}{\bs{\tau}}
 \providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
@@
 
-\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
+\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}Hari Shroff\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
 
@@
   expressed in a basis of spatial and spherical harmonics---a form we call the
-  spatio-angular dipole transfer function. We demonstrate our formalism by
+  dipole spatio-angular transfer function. We demonstrate our formalism by
   analyzing a single-view fluorescence microscope without using the monopole or
@@
   show that information about the out-of-plane orientation of ensembles of
-  in-focus fluorophores is recorded by fluorescence microscopes, and we show
-  that these effects persist in the paraxial limit. We discuss the implications
-  of our analysis for all quantitative fluorescence microscopy studies and lay
-  out a path towards a complete theory.
+  in-focus fluorophores is recorded by fluorescence microscopes. We discuss the
+  implications of our analysis for all quantitative fluorescence microscopy
+  studies and lay out a path towards a complete theory.
 \end{abstract*}
@@
 distribution of fluorophores throughout a sample, all microscopes are
-diffraction limited [cite], so the image is a blurred version of the true
+diffraction limited, so the image is a blurred version of the true
 fluorophore distribution.
@@
 emit light isotropically. Despite their use in models, monopole
-absorber/emitters do not exist in nature. All real fluorophores absorb and emit
+absorbers/emitters do not exist in nature. All real fluorophores absorb and emit
 light anisotropically, and in this work we investigate the more realistic dipole
@@
 The above discussion is quite abstract, but it is a powerful point of view that
-will enable us to draw new conclusions about all fluorescence microscopes. In
-Section \ref{sec:monopole} we will demonstrate the formalism by examining a
+will enable us to unify the analysis of spatio-angular fluorescence microscopes.
+In Section \ref{sec:monopole} we will demonstrate the formalism by examining a
 familiar monopole imaging model, and we will demonstrate the mapping between
@@
 two-dimensional plane. Similarly, we have a two-dimensional detector that
-measures a real number at every point on a plane, so data space is the same set
+measures a real number at each point on a plane, so data space is the same set
 $\mbb{V} = \mbb{L}_2(\mbb{R}^2)$.
@@
 \end{align}
-where $m$ is a magnification factor. Note that we have modeled the object and
-data as continuous two-dimensional functions that extend to infinity. All real
-objects must be restricted to a finite field-of-view and the data must be
-discretely sampled, but we continue with continuous function with infinite
-extent for convenience.
+where $m$ is a magnification factor.
 
@@
 \end{align}
-The monopole point spread function corresponds to a
-measurable irradiance, so it is always real-valued and positive.
+The monopole point spread function corresponds to a measurable irradiance, so it
+is always real and positive.
 
@@
     fluorescence microscope can be computed in two different bases---a delta
-    function basis and a spatial harmonic basis. The change of basis is given by
-    the two-dimensional Fourier transform denoted $\mathcal{F}_{\mbb{R}^2}$.}
+    function basis and a spatial harmonic basis. The change of basis can be
+    computed with a two-dimensional Fourier transform denoted
+    $\mathcal{F}_{\mbb{R}^2}$.}
      \label{fig:monopole-block}      
@@
 
-The mapping between the object and the data in linear shift-invariant
-microscopes takes a particularly simple form in a spatial harmonic basis. If we
-apply the Fourier convolution theorem to Eq. \ref{eq:lsi} we find that
+The mapping between the object and the data in a linear shift-invariant imaging
+system takes a particularly simple form in a spatial harmonic basis. If we apply
+the Fourier convolution theorem to Eq. \ref{eq:lsi} we find that
 \begin{align}
@@
 \end{align}
-The monopole point spread function is normalized and real-valued, so we know
+The monopole point spread function is normalized and real, so we know
 that the monopole transfer function is normalized $H(0) = 1$ and
-conjugate-symmetric $H(-\bv) = H^*(\bv)$ where $z^*$ denotes the complex
+conjugate symmetric $H(-\bv) = H^*(\bv)$ where $z^*$ denotes the complex
 conjugate of $z$.
@@
 
-Note that we have used the term \textit{monopole transfer function} instead of
-the commonly-used term \textit{optical transfer function}. We reserve the term
-\textit{optical transfer function} for optical systems---the optical transfer
-function maps between an input irradiance spectrum and an output irradiance
-spectrum in an optical system. We can use optical transfer functions to model
-the optical fields in a microscope, but ultimately we are always interested in
-measuring an object. Although the monopole transfer function can be identical to
-the optical transfer function, we will find the distinction to be valuable when
-we consider dipole transfer functions.
+We have been careful to use the term \textit{monopole transfer function} instead
+of the commonly-used term \textit{optical transfer function}. We reserve the
+term \textit{optical transfer function} for optical systems---the optical
+transfer function maps between an input irradiance spectrum and an output
+irradiance spectrum in an optical system. We can use optical transfer functions
+to model the propagation of light through a microscope, but ultimately we are
+always interested in the object, not the light emitted by the object. We will
+find the distinction between the optical transfer function and the object
+transfer function to be especially valuable when we consider dipoles later in
+this section.
 
@@
 \begin{align}
-  H(\bv) = \int_{\mbb{R}^2}d\bvp\, C(\bvp)C^*(\bvp - \bv), 
+  H(\bv) = \int_{\mbb{R}^2}d\taup\, C(\taup)C^*(\taup - \bv), 
 \end{align}
@@
 \begin{align}
-  C(\bvp) = \int_{\mbb{R}^2}d\mb{r}\, c(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bvp].
+  C(\taup) = \int_{\mbb{R}^2}d\mb{r}\, c(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\taup].
 \end{align}
@@
 scalar-valued field in a Fourier plane of the detector with appropriate scaling.
-We have chosen the symbol $\bvp$ as the coordinate for the coherent
-transfer function because the Fourier plane of the detector is often called the
-\textit{pupil plane}.
+% We have chosen the symbol $\taup$ as the coordinate for the coherent
+% transfer function because the Fourier plane of the detector is often called the
+% \textit{pupil plane}.
 
 The coherent transfer function provides a valuable shortcut for analyzing
-microscopes since it is usually straightforward to calculate the field in the
-pupil plane. A typical approach for calculating the transfer functions is to (1)
-calculate the field in the pupil plane, (2) scale the field to find the
-coherent monopole transfer function, then (3) use the relationships in Figure
-\ref{fig:monopole-transfer-functions} to calculate the other transfer functions.
+microscopes since it is often straightforward to calculate the field in a
+Fourier plane of the detector. A typical approach for calculating the transfer
+functions is to (1) calculate the field in a Fourier plane of the detector, (2)
+scale the field to find the monopole coherent transfer function, then (3) use
+the relationships in Figure \ref{fig:monopole-transfer-functions} to calculate
+the other transfer functions.
 
@@
 \end{align}
+Eq. \ref{eq:odpsf} is a key result because it represents the mapping between
+object space and data space in a delta function basis. The integrals in
+\ref{eq:odpsf} would be extremely expensive to compute for an arbitrary object,
+but the integrals simplify to an efficient sum if the object consists of
+spatially fixed dipoles in a fixed orientation. In other words, Eq.
+\ref{eq:odpsf} is ideal for simulating and analyzing objects that are spatially
+and angularly sparse; e.g. single fluorophores that are rigidly attached to a
+structure .
 
@@
 \end{align}
-The dipole point spread function is a measurable quantity, so it is real-valued
+The dipole point spread function is a measurable quantity, so it is real
 and positive.
@@
   the spatial dipole transfer function is normalized
-  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \so) = 1$ and conjugate-symmetric
+  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \so) = 1$ and conjugate symmetric
   $H(-\bv, \so) = H^*(\bv, \so)$.
 
-  This choice of basis is well suited for simulating and analyzing objects that
-  are angularly sparse and spatially dense.
+  This basis is ideal for simulating and analyzing objects that are angularly
+  sparse and spatially dense; e.g. rod structures that contain fluorophores in a
+  fixed orientation.
 
@@
   \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
-  \caption{The mapping between the object and data space of a dipole
-    fluorescence microscope can be computed in four different bases---a delta
-    function basis, a spatial-harmonic/angular-delta basis, a
-    spatial-delta/spherical-harmonic basis, and a spatio-angular harmonic basis.
-    The changes of basis are given by the two-dimensional Fourier transform
-    denoted $\mathcal{F}_{\mbb{R}^2}$ and the spherical Fourier transform
-    denoted $\mathcal{F}_{\mbb{S}^2}$.}
+  \caption{The mapping between the object and data space of a dipole imaging
+    system can be computed in four different bases---a delta function basis, a
+    spatial-harmonic/angular-delta basis, a spatial-delta/spherical-harmonic
+    basis, and a spatio-angular harmonic basis. The changes of basis can be
+    computed with the two-dimensional Fourier transform denoted
+    $\mathcal{F}_{\mbb{R}^2}$, and the spherical Fourier transform denoted
+    $\mathcal{F}_{\mbb{S}^2}$.}
    \label{fig:dipole-block}      
@@
 
-\subsubsection{Angular dipole transfer function}
-The spherical harmonics are another set of convenient basis functions. We can
+\subsubsection{Dipole angular transfer function}
+The spherical harmonics are another set of convenient basis functions that are
+play the same role as complex exponentials in spatial transfer functions---see
+Appendix \ref{sec:sph} for an introduction to the spherical harmonics. We can
 change basis from spherical delta functions to spherical harmonics by applying
@@
 \begin{align}
-  \ints{2}d\mh{s}\, p(\mh{s})q(\mh{s}) = \lmsum P_\ell^m Q_\ell^m, \label{eq:plan}
-\end{align}
-where $p(\mh{s})$ and $q(\mh{s})$ are arbitrary functions on the sphere, $P_\ell^m$ and $Q_\ell^m$ are their spherical Fourier transforms defined by
+  \ints{2}d\mh{s}\, p(\mh{s})q^*(\mh{s}) = \lmsum P_\ell^m Q_\ell^{m*}, \label{eq:plan}
+\end{align}
+where $p(\mh{s})$ and $q(\mh{s})$ are arbitrary functions on the sphere,
+$P_\ell^m$ and $Q_\ell^m$ are their spherical Fourier transforms defined by
 \begin{align}
@@
 \end{align}
-where we have defined the \textit{angular dipole transfer function} as
+where we have defined the \textit{dipole angular transfer function} as
 \begin{align}
@@
 \end{align}
-and the \textit{angular dipole spectrum} as
+and the \textit{dipole angular spectrum} as
 \begin{align}
@@
 \end{align}
-Since the dipole point spread function is normalized and real-valued, we know
-that the angular dipole transfer function is normalized
+Since the dipole point spread function is normalized and real, we know
+that the dipole angular transfer function is normalized
 $\int_{\mbb{R}^2}d\mb{r}\, H_0^0(\mb{r}) = 1$ and conjugate symmetric
@@
 This basis is well suited for simulating and analyzing objects that are
-spatially sparse and angularly dense.
+spatially sparse and angularly dense; e.g. rotating single fluorophores that are
+spatially fixed, or many fluorophores that are close together with varying
+orientations.
 
@@
 \end{align}
-where we have defined the \textit{spatio-angular dipole transfer function} as
+where we have defined the \textit{dipole spatio-angular transfer function} as
   \begin{align}
@@
   \end{align}
-  and the \textit{spatio-angular dipole spectrum} as
+  and the \textit{dipole spatio-angular spectrum} as
   \begin{align}
@@
   \end{align}
-  Since the dipole point spread function is normalized and real-valued, we know
-  that the spatio-angular dipole transfer function is normalized
+  Since the dipole point spread function is normalized and real, we know
+  that the dipole spatio-angular transfer function is normalized
   $\msf{H}_0^0(0) = 1$ and conjugate symmetric
@@
   This basis is well suited for simulating and analyzing arbitrary samples
-  because it exploits the sparsity of the imaging system. We will see this
-  advantage explicitly in Section XXX when we calculate a specific
-  spatio-angular dipole transfer function and see that it has an angular band
-  limit.
+  because it exploits the band limit of the imaging system. We will see this
+  advantage explicitly in Section \ref{sec:results} when we calculate a specific
+  dipole spatio-angular transfer function and see that it has spatial and
+  angular band limits.
 
@@
   bases that we can use to compute the image of a field of dipoles. We reiterate
-  that all four bases may be useful depending on the sparsity of the sample.
+  that all four bases may be useful depending on the sample.
 
@@
 
-Since the spatial dipole transfer function is given by the two-dimensional
+Since the dipole spatial transfer function is the two-dimensional
 Fourier transform of the dipole point spread function
@@
 \begin{align}
-  H(\bv) = \int_{\mbb{R}^2}d\bvp\,\mb{C}(\bvp, \so)\mb{C}^\dagger(\bvp - \bv, \so), 
+  H(\bv) = \int_{\mbb{R}^2}d\taup\,\mb{C}(\taup, \so)\mb{C}^\dagger(\taup - \bv, \so), 
 \end{align}
 where we have introduced the \textit{dipole coherent transfer function}
-$\mb{C}(\bvp, \so)$ as the two-dimensional Fourier transform of the dipole
+$\mb{C}(\taup, \so)$ as the two-dimensional Fourier transform of the dipole
 coherent spread function
 \begin{align}
-  \mb{C}(\bvp, \so) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\bvp].
+  \mb{C}(\taup, \so) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\taup].
 \end{align}
@@
 Fourier plane of the detector with appropriate scaling. Similar to the monopole
-case, we can calculate the orientation-dependent fields in the aperture plane,
-scale appropriately to find the dipole coherent transfer function, then use the
-relationships in Figure \ref{fig:transfer-functions} to calculate the other
-transfer functions. Note that we could define coherent equivalents for all four
-incoherent transfer functions, but we restrict ourselves to these two since they
-are the most useful for our calculations.
+case, we can calculate the orientation-dependent fields in a Fourier plane of
+the detector, scale appropriately to find the dipole coherent transfer function,
+then use the relationships in Figure \ref{fig:transfer-functions} to calculate
+the other transfer functions.
 
@@
 In this section we begin to apply the tools we developed in the previous section
-to analyze more specific fluorescence microscopes. During our initial discussion
-we only required the optical system to be aplanatic so that we could model it as
-a shift-invariant magnifier. Now we will be more specific and consider an
-aplanatic optical system in a \textit{$4f$ configuration} with an arbitrary
-first lens (the objective) and a \textit{paraxial second lens} (the tube lens).
-A lens can be considered paraxial if the angle $\alpha$ between the optical axis
-of the lens and the marginal ray is small enough that
-$\sin\alpha \approx \alpha$. As a rule of thumb, paraxial effects become
-significant when the numerical aperture of a lens exceeds 0.7 \cite{gu2000}, but
-this is only a rough guideline.
+to analyze a specific fluorescence microscope. During our initial discussion we
+only required the optical system to be aplanatic so that we could model it as a
+shift-invariant magnifier. Now we will be more specific and consider an
+aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an arbitrary
+first lens (the objective lens) and a \textit{paraxial second lens} (the tube
+lens) as shown in Figure \ref{fig:schematic}. A lens can be considered paraxial
+if the angle $\alpha$ between the optical axis of the lens and the marginal ray
+is small enough that $\sin\alpha \approx \alpha$. As a rule of thumb,
+non-paraxial effects only become significant when the numerical aperture of a
+lens exceeds 0.7 \cite{gu2000}, but this is only a rough guideline.
 
@@
 imaging systems, and we explicitly relate the pupil functions to the previously
-defined coherent transfer functions. Next, we calculate the transfer functions
-for monopole and dipole imaging systems with high-NA objectives. We resort to
-numerics as necessary, but we can calculate several transfer function in closed
-form. We compare these results with paraxial results which are completely in
-closed form.
-
-\subsection{Monpole pupil functions}
+defined coherent transfer functions. After establishing the link between
+physical calculations and the transfer functions, we calculate the monopole and
+dipole transfer functions for imaging systems with a paraxial objective, and we
+demonstrate our approach by simulating simple phantoms.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[width = 0.9\textwidth]{../figures/abstract-micro/abstract-micro.pdf}
+   \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
+     paraxial tube lens. Since we have an aplanatic optical system we only need
+     to consider the image created by on-axis objects.}
+   \label{fig:schematic}
+ \end{figure}
+
+\subsection{Monopole pupil functions}
 We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
-the field immediately following the aperture plane created by an on-axis
+the field immediately following the pupil plane created by an on-axis
 monopole where $\rp$ is an unscaled two-dimensional coordinate in the pupil
@@
 transfer function we defined in Section \ref{sec:theory} by following a near
-variant of the path in Barrett and Myers Section 9.7 \cite{barrett2004}.
+variant of the derivation in Barrett and Myers Section 9.7 \cite{barrett2004}.
 
@@
 
-Since the second lens is paraxial, we can model with relationship between the
+Since the second lens is paraxial, we can model the relationship between the
 field in the aperture plane and the field on the detector with a scaled Fourier
@@
 \end{align}
-If we define $P(\bvp)$ as the two-dimensional Fourier transform of the pupil function
+If we define $P(\taup)$ as the two-dimensional Fourier transform of the pupil function
 then we can rewrite Eq. \ref{eq:detectorfourier} as
@@
 \end{align}
-which we can simplify further in terms of $m = -\frac{f_1n_0}{f_0n_1}$
-\begin{align}
-  U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right),
-\end{align}
-The irradiance on the detector is given by the absolute square of the field so
+which we can simplify further by writing in terms of
+$m = -\frac{f_1n_0}{f_0n_1}$:
+\begin{align}
+  U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right).
+\end{align}
+The irradiance on the detector is the absolute square of the field so
 \begin{align}
@@
 \end{align}
-If we demagnify the coordinates $\rd = \rd'/m$ and the irradiance
-$h(\rd - \ro) \propto h'(m[\rd - \ro])$ we find that the monopole point spread function
-is related to the Fourier transform of the monopole pupil function by
+If we demagnify the coordinates with $\rd = \rd'/m$ and demagnify the irradiance
+with $h(\rd - \ro) \propto h'(m[\rd - \ro])$ we find that the monopole point spread
+function is related to the Fourier transform of the monopole pupil function by
 \begin{align}
@@
 \end{align}
-The monopole coherent transfer function is the Fourier transform of the monopole coherent spread function so
-\begin{align}
-  C(\bvp) \propto p\left(\frac{\lambda f_o}{n_o}\bvp\right). \label{eq:monopupil0}
+Finally, the monopole coherent transfer function is the Fourier transform of the
+monopole coherent spread function so
+\begin{align}
+  C(\taup) \propto p\left(\frac{\lambda f_o}{n_o}\taup\right). \label{eq:monopupil0}
 \end{align}
@@
 We define the \textit{dipole pupil function} $\mb{p}(\rp, \so)$ of the imaging
-system as the electric field immediately following the aperture plane created by
+system as the electric field immediately following the pupil plane created by
 an on-axis dipole oriented along $\so$. Since dipoles emit vector-valued
@@
 all of the arguments in the previous section carry over to the dipole case.
-Briefly, we can write the electric field created at a point in the aperture
+Briefly, we can write the electric field created at a point in the pupil
 $\rp$ by a dipole at $\ro$ oriented along $\so$ as
@@
 \begin{align}
-  \mb{C}(\bvp, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\bvp, \so\right). \label{eq:monopupil}
-\end{align}
-
-\subsection{Monopole transfer functions}
-Several works \cite{petrov2017, backlund2018} have modeled an aplanatic
-fluorescence microscope imaging isotropic emitters with the scalar pupil
-function
-\begin{align}
-  p(\rp) \propto (1 - r_p^2)^{-1/4}\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
-\end{align}
-where $\Pi(\cdot)$ is a rectangle function defined by
+  \mb{C}(\taup, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\taup, \so\right). \label{eq:monopupildip}
+\end{align}
+
+\subsection{Special functions}
+We adopt and generalize Bracewell's notation \cite{bracewell2004} for several
+special functions which will simplify our calculations. First, we define a
+\textit{rectangle function} as
 \begin{align}
@@
     1\quad \text{if}\quad |x| < \frac{1}{2},\\
-    0\quad \text{else},
+    0\quad \text{else}.
   \end{cases}
 \end{align}
-which models the aperture stop of the objective, and $(1 - r_p^2)^{-1/4}$
-conserves power before and after the objective. Applying Eq. XXX we see that the
-coherent transfer function for this system is given by
-\begin{align}
-  C(\bvp)
-\end{align}
-
-In this section we calculate the form of the monopole point spread function
-$h(\rd - \ro)$ when both lenses of the optical system are paraxial. First, we
-place a monopole emitter at the focal point of the objective lens. We can model
-a paraxial thin lens as a quadratic phase element, so it converts an incident
-spherical wave to a plane wave in the back focal plane with a sharp cutoff at
-the exit pupil of the lens
-\begin{align}
-  U_{\text{bfp}}(\mb{r}_b) \propto \Pi\left(\frac{|\mb{r}_b|}{2\alpha}\right) \equiv
-  \begin{cases}
-    1\quad \text{if}\quad |\mb{r}_b| < \alpha,\\
-    0\quad \text{else},
-  \end{cases}
-\end{align}
-where $\rp$ is the two-dimensional coordinate in the back focal plane and
-$\alpha$ is the collection half angle---see Figure XXX.
-
-A central result of Fourier optics is that the fields one focal distance from
-either side of a paraxial lens are related by a scaled two-dimensional Fourier
-transform. If we place a detector in the focal plane of the tube lens, then the
-field on the detector $U_{\text{det}}(\mb{r}_d)$ is given by
-\begin{align}
-  U_{\text{det}}(\mb{r}_d) \propto \frac{J_1(k\alpha|\mb{r}_d|)}{|\mb{r}_d|}.
-\end{align}
-where $J_n(x)$ denotes the Bessel function of the first kind of order $n$, and
-$k = 2\pi/\lambda$ is the wave number.
-
-Finally, the detector measures the irradiance instead of the field, so we take
-the modulus squared of the field to find that the measurable irradiance created
-by a single monopole radiator at the origin is the familiar Airy disk
-\begin{align}
-  h(\mb{r}_d, \ro = 0) \propto |U_{\text{det}}(\mb{r}_d)|^2 = \left[\frac{J_1(k\alpha|\mb{r}_d|)}{|\mb{r}_d|}\right]^2.
-\end{align}
-Shifting the monopole in the transverse plane will introduce a linear phase
-factor in the back focal plane which will manifest as a shift on the detector
-due to the Fourier shift theorem. Therefore, the monopole imaging system is
-shift invariant and we can rewrite the irradiance on the detector due to a
-monopole at $\ro$ as
-\begin{align}
-  h(\rd, \ro) = h(\rd - \ro). \label{eq:shift}
-\end{align}
-We have modeled a microscope with unit magnification, but a similar point spread
-function can be found for magnifying microscopes by making a change of
-variables (see \cite{barrett2004}, section 7.2.7).
-
-Rotating a monopole will leave its image unchanged. Therefore, our imaging
-system is rotation invariant and we can simplify the orientation-dependent point spread function further with
-\begin{align}
-  h(\rd - \ro) = h(|\rd - \ro|). \label{eq:rotational}
-\end{align}
-
-\subsection{Orientation-dependent point spread function of a paraxial epi-fluorescence microscope}
-In this section we will calculate the orientation-dependent point spread
-function $h(\rd - \ro, \mh{s})$ of a paraxial epi-fluorescence microscope. We can
-make our first simplifying step by realizing the excitation and detection
-processes are incoherent, which means that the orientation-dependent PSF is
-separable:
-\begin{align}
-  h(\rd, \ro, \so) = h_{\text{exc}}(\ro, \so)\,h_{\text{det}}(\rd, \ro, \so). \label{eq:kernelsep}
-\end{align}
-We can calculate the excitation and detection terms separately then take their
-product to find the complete orientation-dependent point spread function.
-
-\subsubsection{Orientation-dependent excitation model}
-When we developed the monopole imaging model we ignored the excitation process
-because we excited the fluorophores with a spatially uniform excitation beam and
-monopoles have no orientation dependence. For the dipole imaging model we must
-model the excitation process because the excitation process is rarely angularly
-uniform (carefully calibrated TIRF systems are an exception).
-
-In this section we will calculate the excitation kernel
-$h_{\text{exc}}(\ro, \so)$ for the paraxial epi-illumination microscope under
-unpolarized (TODO: Define/cite) K\"{o}ehler illumination shown in Figure
-\ref{fig:exccoords}. We will only consider spatially uniform excitation, so the
-excitation kernel will not depend on $\ro$
-\begin{align}
-  h_{\text{exc}}(\ro, \so) = h_{\text{exc}}(\so).
-\end{align}
-We can interpret $h_{\text{exc}}(\so)$ as the relative probability of exciting a
-molecule with dipole orientation $\so$. Our approach is similar to previous work
-\cite{fourkas2001, chandler2017}, but here we consider paraxial, incoherent, and
-unpolarized illumination (TODO improve).
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=.9]{../figures/excitation-coords/excitation-coords.pdf}
-   \caption{Illumination geometry and coordinates for a paraxial epifluorescence
-     microscope. An unpolarized and incoherent light source (or its image) is in
-     the back focal plane of the condenser lens.}
-   \label{fig:exccoords}
- \end{figure}
-
-We start by expressing the dipole moment $\so{}$ in Cartesian coordinates
-\begin{align}
-  \so{} &= s_x\mh{x} + s_y\mh{y} + s_z\mh{z}. \label{eq:spherical}
-\end{align}
-We place the dipole in the focal plane of an aplanatic and
-polarization-preserving objective lens with its optical axis aligned with the
-$\mh{z}$ axis. Next, we place a spatially incoherent, spatially uniform,
-unpolarized light source (or its image) in the back aperture of the objective
-lens to illuminate the focal plane. In this geometry each point in the back
-focal plane generates a plane wave that illuminates the sample.
-
-To model the unpolarized light source we will use polarized ray tracing
-\cite{foreman2011} to find the response for a single polarized ray, then
-integrate over the rays and all polarizations to find the complete response.
-First, we model the electric field at every point on the back focal plane as
-\begin{align}
-   \mb{E}_{\text{bfp}}(\phi_{\text{pol}}) &\propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y}, \label{eq:bfp0}
-\end{align}
-where $\phi_{\text{pol}}$ is the polarization orientation and \{$\mh{x}$,
-$\mh{y}$\} are transverse Cartesian basis vectors. Note that Eq. \ref{eq:bfp0}
-describes the incoherent electric fields at every point in the back focal
-plane--- it does not describe a coherent plane wave. To find the electric field
-immediately after the paraxial lens we apply a position-dependent rotation
-matrix (see the rotation matrices in \cite{foreman2011, backer2014} under the
-paraxial approximation):
-
-\begin{align}
-  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) & \propto 
+We also define the \textit{$n^{th}$-order jinc function} as
+\begin{align}
+  \text{jinc}_n(r) = \frac{J_{n+1}(\pi r)}{2r},
+\end{align}
+where $J_{n+1}(r)$ is the $(n+1)^{th}$-order Bessel function of the first kind.
+
+In Appendix \ref{sec:special} we derive the following two-dimensional Fourier
+transform relationships between the jinc functions and the weighted rectangle
+functions
+\begin{align}
+  i^{n}\left\{\substack{
+  \text{exp}(in\phi_r)\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\text{jinc}_n(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} (2\nu)^{n}\left\{\substack{
+    \text{exp}(in\phi_{\nu})\\
+    \cos(n\phi_{\nu})\\
+    \sin(n\phi_{\nu})
+  }\right\}\Pi(\nu), \label{eq:jincrect2}
+  \end{align}
+where the entries inside the curly braces are to be taken one at a time.
+
+Finally, we define the \textit{$n^{th}$-order chat function} as the
+two-dimensional Fourier transform of the squared $n^{th}$-order jinc function
+\begin{align}
+  \text{jinc}_n^2(r) \stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} \text{chat}_n(\nu).
+\end{align}
+
+In Appendix \ref{sec:special} we show that the zero and first order chat
+functions can be written in closed form as
+\begin{align}
+  \text{chat}_0(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right),\\
+  \text{chat}_1(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|(3-2x^2)\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right).  
+\end{align}
+
+\subsection{Monopole transfer functions}
+Our first step towards the monopole transfer functions is to calculate the
+monopole pupil function and coherent transfer function. Several works
+\cite{petrov2017, backlund2018} have modeled an aplanatic fluorescence
+microscope imaging monopole emitters with the scalar pupil function
+\begin{align}
+  p(\rp) \propto \tilde{C}\left(\frac{r_p}{f_o}\right)\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
+\end{align}
+where
+\begin{align}
+  \tilde{C}(x) = (1 - x^2)^{-1/4} = 1 + \frac{x^2}{4} + \frac{5x^4}{32} + \cdots. 
+\end{align}
+The $\tilde{C}(x)$ function models the radial dependence of the field and
+ensures that power is conserved on either side of an aplanatic objective, and
+the rectangle function models the aperture stop of the objective. Applying Eq.
+\ref{eq:monopupil0} and collecting constants we find that the coherent monopole
+transfer function is
+\begin{align}
+  C(\taup) \propto \tilde{C}\left(\frac{2\text{NA}}{n_o}\frac{\tau}{\nu_c}\right)\Pi\left(\frac{\tau}{\nu_c}\right), \label{eq:coherentmonopole}
+\end{align}
+where $\text{NA} = n_o\sin\alpha$ and $\nu_c = 2\text{NA}/\lambda$. This
+coherent transfer function models objectives with an arbitrary numerical
+aperture, but for our initial analysis we restrict ourselves to the paraxial
+regime. We retain only zero and first order radial terms to find that  
+\begin{align}
+  C(\taup) \stackrel{(p)}{\propto} \Pi\left(\frac{\tau}{\nu_c}\right), 
+\end{align}
+where $(p)$ indicates that we have used the paraxial approximation for the
+objective lens.
+
+We can find the monopole coherent spread function by taking the inverse Fourier
+transform of the monopole coherent transfer function
+\begin{align}
+  c(\mb{r}) \stackrel{(p)}{\propto} \text{jinc}_0(\nu_c r).
+\end{align}
+
+The monopole point spread function is the (normalized) absolute square of the
+monopole coherent spread function so,
+\begin{align}
+  h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r)
+\end{align}
+which is the well-known \textit{Airy disk}.
+
+Finally, we can calculate the monopole transfer function as the two-dimensional Fourier transform of the monopole point spread function (or the autocorrelation
+of the coherent transfer function) and find that 
+\begin{align}
+  H(\bs{\nu}) \stackrel{(p)}{=} \frac{4}{\pi}\text{chat}_0\left(\frac{\nu}{\nu_c}\right).
+\end{align}
+
+ \subsection{Dipole transfer functions}
+ To calculate the dipole transfer function we proceed similarly to the monopole
+ case---we find the pupil function, scale to find the coherent dipole transfer
+ function, then calculate the remaining transfer functions.
+
+ Backer and Moerner \cite{backer2014} have calculated the dipole pupil function
+ for a high-NA objective as
+ \begin{align}
+   \mb{p}(\rp, \so) \propto
    \begin{bmatrix}
-    1 & 0 &\theta \cos\phi\\
-    0 & 1 &\theta \sin\phi\\
-    -\theta\cos\phi&-\theta \sin(\phi)&1
+     \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\cos\phi_p\\
+     \tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\sin\phi_p\\
+     0&0&0\\     
    \end{bmatrix}
    \begin{bmatrix}
-    \cos\phi_{\text{pol}}\\
-    \sin\phi_{\text{pol}}\\
-    0
-  \end{bmatrix},\\
-  \intertext{so that}
-  \mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) &\propto \cos\phi_{\text{pol}}\mh{x} + \sin\phi_{\text{pol}}\mh{y} - \theta\cos(\phi - \phi_{\text{pol}})\mh{z}.\label{eq:eff}
-\end{align}
-The probability that a dipole oriented along $\so{}$ is excited by a ray with
-electric field $\mb{E}$ is given by 
-\begin{align}
-  |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2 \propto s_x^2\cos^2\phi_{\text{pol}} + s_y^2\sin^2\phi_{\text{pol}} + s_z^2\theta^2\cos^2(\phi - \phi_{\text{pol}}).
-\label{eq:integrand}
-\end{align}
-To find the complete excitation kernel we need to integrate Eq.
-\ref{eq:integrand} over all polarization orientations and rays:
-\begin{align}
-  h_{\text{exc}}(\so{}) \propto \int_0^{\alpha}\theta d\theta\int_0^{2\pi}d\phi\int_0^{2\pi}d\phi_{\text{pol}}\, |\mb{E}_{\text{ff}}(\theta, \phi, \phi_{\text{pol}}) \cdot \so{}|^2.
-\label{eq:integral}
-\end{align}
-Plugging Eq. \ref{eq:integrand} into Eq. \ref{eq:integral}, evaluating the
-integrals, and dropping constants gives
-\begin{align}
-  h_{\text{exc}}(\vartheta) &\propto s_x^2 + s_y^2 + \frac{1}{2}\alpha^2s_z^2.
-\end{align}
-We can rewrite the excitation kernel in terms of a single variable with the
-substitutions $s_x^2 + s_y^2 = \sin^2\vartheta$ and $s_z^2 = \cos^2\vartheta$:
-\begin{align}
-  h_{\text{exc}}(\vartheta) &\propto \sin^2\vartheta + \frac{1}{2}\alpha^2\cos^2\vartheta \label{eq:hexctheta}.
-\end{align}
-
-Figure \ref{fig:excitation} shows the excitation response as a function of
-inclination angle $\vartheta$ and excitation half angle $\alpha$. The largest
-variation of the excitation kernel occurs when the maximum excitation angle is
-zero---plane-wave illumination. As $\alpha$ grows, dipoles parallel to the optic
-axis are more likely to be excited and the variation of the excitation kernel
-decreases.
+     s_x\\
+     s_y\\
+     s_z
+   \end{bmatrix}
+   \Pi\left(\frac{r_p}{2f_o\sin\alpha}\right). 
+ \end{align}
+ where
+ \begin{alignat}{4}
+   \tilde{C}_0(x) &= \frac{1}{2}(\sqrt{1 - x^2} + 1)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
+   \tilde{C}_1(x) &= x(1 - x^2)^{-1/4} &&= x + \frac{x^3}{4} + \frac{5x^5}{32} + \cdots,\\
+   \tilde{C}_2(x) &= \frac{1}{2}(\sqrt{1 - x^2} - 1)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
+ \end{alignat}
+ Similar to the monopole case, the dipole pupil function conserves power and has
+ a cutoff at the objective aperture, but the dipole pupil function is
+ vector-valued to model the complete electric field in the pupil plane. The
+ fields in the aperture plane have a negligible $\mh{z}$ component which is a
+ consequence of our assumption that the tube lens is paraxial.
+
+ Scaling the dipole pupil function using Eq. \ref{eq:monopupildip} yields the
+ dipole coherent transfer function
+ \begin{align}
+   \mb{C}(\taup, \so) \propto
+   \begin{bmatrix}
+     \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos\phi_{\tau}\\
+     \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin\phi_{\tau}\\
+     0&0&0\\     
+   \end{bmatrix}
+   \begin{bmatrix}
+     s_x\\
+     s_y\\
+     s_z
+   \end{bmatrix}
+   \Pi\left(\frac{\tau}{\nu_c}\right). 
+ \end{align}
+ We restrict our analysis to the paraxial regime by dropping all but the zero
+ and first order radial terms to find that
+ \begin{align}
+   \mb{C}(\taup, \so) \stackrel{(p)}{\propto}
+   \begin{bmatrix}
+     1&0&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\cos\phi_{\tau}\\
+     0&1&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\sin\phi_{\tau}\\
+     0&0&0\\     
+   \end{bmatrix}
+   \begin{bmatrix}
+     s_x\\
+     s_y\\
+     s_z
+   \end{bmatrix}
+   \Pi\left(\frac{\tau}{\nu_c}\right). \label{eq:coherentdip}
+ \end{align}
+ Under the paraxial approximation the transverse component of the dipoles
+ ($s_x, s_y$) creates purely transverse fields in the pupil plane and the axial
+ component of the dipole ($s_z$) creates purely radial fields in the pupil
+ plane. The paraxial approximation may seem crude compared to Backer and
+ Moerner's numerical results, but the approximation will allow us to calculate
+ the transfer functions in closed form so that we can gain an intuition for the
+ limits of the microscope. We also note that many existing works in ensemble
+ polarized fluorescence microscopy make stronger approximations than ours. For
+ example, Fourkas only considers the total irradiance in the back focal plane
+ while ignoring the propagation of fields to the detector \cite{fourkas2001}.
+
+ The dipole coherent spread function is the inverse Fourier transform of the
+ dipole coherent transfer function. Applying Eq. \ref{eq:jincrect2} in reverse
+ yields
+  \begin{align}
+   \mb{c}(\mb{r}, \so) \stackrel{(p)}{\propto}
+   \begin{bmatrix}
+     \text{jinc}_0(\nu_c r)&0&\frac{\text{NA}}{n_o}i\cos\phi\,\text{jinc}_1(\nu_c r)\\
+     0&\text{jinc}_0(\nu_c r)&\frac{\text{NA}}{n_o}i\sin\phi\,\text{jinc}_1(\nu_c r)\\
+     0&0&0\\     
+   \end{bmatrix}
+   \begin{bmatrix}
+     s_x\\
+     s_y\\
+     s_z
+   \end{bmatrix}.
+  \end{align}
+  Notice that the radial component of the dipole coherent spread function has a
+  $\pi/2$ phase shift relative to the transverse component. This phase factor
+  arises because the Fourier transform of a real and odd function is purely
+  imaginary.
+
+  \subsubsection{Paraxial dipole point spread function}
+  The dipole point spread function is the (normalized) absolute square of
+coherent dipole spread function
+\begin{align}
+  h(\mb{r}, \so) \propto \mb{c}(\mb{r}, \so)\mb{c}^\dagger(\mb{r}, \so). 
+\end{align}
+Plugging in the paraxial dipole coherent spread function and normalizing yields
+\begin{align}
+  h(\mb{r}, \so) \stackrel{(p)}{=} N\left[\text{jinc}_0^2(\nu_c r)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\cos^2\vartheta\right],\label{eq:paradpsf}
+\end{align}
+where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization factor is
+\begin{align}
+  N = 6\nu_c^2\pi^{-3/2}\left[2 + \left(\frac{\text{NA}}{n_o}\right)^2\right]^{-1}.
+\end{align}
+
+ Notice that the transverse and radial fields are out of phase on the detector,
+ so the total irradiance is the sum of the contributions from the transverse and
+ radial components. In Figure \ref{fig:hdet} we plot the dipole point spread
+ function for several dipole orientations dipole orientations and numerical
+ apertures, and in Figure \ref{fig:microscopefig} we compare the monopole point
+ spread function to the dipole point spread function. The paraxial monopole and
+ dipole models are equivalent when the sample consists of only transverse
+ dipoles which is clear if we notice that Eq. \ref{eq:paradpsf} reduces to an
+ Airy disk when $\vartheta = \pi/2$.
+
 \begin{figure}[h]
@@
    \centering
-   \includegraphics[scale=0.95]{../figures/excitation/excitation.pdf}
-   \caption{Dipole excitation kernel $h_{\text{exc}}(\vartheta)$ as a function of
-     inclination angle $\vartheta$ and excitation half angle $\alpha$.}
-   \label{fig:excitation}
- \end{figure}
-
- \subsubsection{Orientation-dependent dipole detection model}
- In this section we will calculate the detection kernel of an epi-detection
- microscope---the irradiance on the detector due to a single dipole with fixed
- position and orientation. [TODO Improve] Our approach mimics existing work
- \cite{backer2014, nov2006, agrawal2012}, but we restrict ourselves to the
- paraxial approximation.
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=.9]{../figures/detection-coords/detection-coords.pdf}
-   \caption{Detection geometry and coordinates. We calculate the detection
-     kernel $h_{\text{det}}(\rd, \ro, \so)$ for a paraxial 4$f$ imaging
-     system.}
-   \label{fig:detection}
- \end{figure}
-
-We consider a single dipole emitter at the origin with a fixed dipole emission
-moment oriented along $\so{}$. The electric field at a position $\mb{r}$ far
-from the dipole is given by
-\begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \frac{\text{exp}[ik|\mh{r}|]}{|\mh{r}|}\mh{r} \times \so{} \times \mh{r}. \label{eq:ff}
-\end{align}
-We place the dipole in the focal plane of the same 4$f$ imaging system we
-considered in the monopole case---see Figure \ref{fig:detection}. The dipole emits
-spherical wavefronts so we can reuse our argument for shift invariance and drop
-the phase dependence of the electric field
-\begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto \mh{r} \times \so{} \times \mh{r} \label{eq:ff2}
-\end{align}
-We also note that we can rewrite a shift-invariant kernel as
-\begin{align}
-h_{\text{det}}(\rd, \ro, \so) = h_{\text{det}}(\rd - \ro, \so), 
-\end{align}
-which will simplify our derivation---we only need to calculate the response for
-a dipole positioned along the optic axis. We can rewrite the cross products in terms
-of a matrix multiplication
-\begin{align}
-  \mb{E}_{\text{ff}}(\mb{r}, \so{}) \propto [\tensor{I} - \mh{r}\mh{r}^{\dagger}]\so,
-\end{align}
-where $\tensor{I}$ is a $3\times 3$ identity matrix. If we place the molecule in
-the focal plane of an aplanatic and polarization-preserving objective lens with
-the lens' optical axis aligned with the $\mh{z}$ axis, then we can find the
-electric field in the back focal plane by multiplying the electric field with a
-position-dependent rotation matrix and truncating waves outside the detection
-collection half angle $\alpha$
-\begin{align}
-  \mb{E}_{\text{bfp}}(\mb{r}, \so{}) \propto \mb{R}_{\text{obj}}(\mh{r})[\tensor{I} - \mh{r}\mh{r}^{\dagger}]\so\Pi\left(\frac{\theta}{2\alpha}\right).
-\end{align}
-After plugging in paraxial positions
-\begin{align}
-  \mh{r}(\theta,\phi) \approx \theta\cos\phi\mh{x} + \theta\sin\phi\mh{y} + \mh{z},
-\end{align}
-and the paraxial rotation matrix
-\begin{align}
-  \mb{R}_{\text{obj}}(\theta, \phi) &=
-  \begin{bmatrix}
-    1 & 0 &-\theta \cos\phi\\
-    0 & 1 &-\theta \sin\phi\\
-    -\theta\cos\phi&-\theta \sin(\phi)&1
-  \end{bmatrix},
-\end{align}
-then dropping the $\theta^2$ $\mh{z}$ components and changing from spherical
-coordinates to cylindrical coordinates by substituting $(r_b, \phi_b)$ for
-$(\theta, \phi)$ we find that
-\begin{align}
-  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{\left[s_x - s_zr_b\cos\phi_b\right]\mh{x} + \left[s_y - s_z r_b\sin\phi_b\right]\mh{y}\right\}\Pi\left(\frac{r_b}{2\alpha}\right).
-\label{eq:bfp2}
-\end{align}
-Equation \ref{eq:bfp2} is easier to work with if we introduce the radial vector
-field $\mh{\bs{\rho}} = \cos\phi_b\mh{x} + \sin\phi_b\mh{y}$ and rewrite as
-\begin{align}
-  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{2\alpha}\right). \label{eq:bfp3}
-\end{align}
-Equation \ref{eq:bfp3} shows that the transverse components of the dipole
-($s_x, s_y$) create linear vector fields in the back focal plane
-($\mh{x}, \mh{y}$) while the axial component of the dipole $s_z$ creates a radial
-vector field in the back focal plane $\mh{z}$.
-
-We complete the 4$f$ system by placing a tube lens one focal length from the
-back focal plane and a planar detector---see Figure \ref{fig:detection}. Under
-the paraxial approximation we can find the electric field in the detector plane
-by taking the Fourier transform of the field in the back focal plane
-\cite{goodman1996}
-\begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rp{} \mb{E}_{\text{bfp}}(\rp{})\, \text{exp}\left[ik\,\rp{}\cdot\rd{}\right].\label{eq:det1}
-\end{align}
-We evaluate the integral in Appendix \ref{sec:ftvec} and show that 
-\begin{align}
-  \mb{E}_{\text{det}}(r_d, \so{}) \propto \frac{J_1(k\alpha r_d)}{r_d}s_x\mh{x} + \frac{J_1(k\alpha r_d)}{r_d}s_y\mh{y} - i\alpha\frac{J_2(k\alpha r_d)}{r_d}s_z\mh{\bs{\rho}}.
-\end{align}
-Once again we find that the transverse component of the dipole creates a linear
-field and the axial component of the dipole creates a radial field, but on the
-detector the linear and radial fields are out of phase by $\pi/2$. This crucial
-phase factor is a direct consequence of the fact that the linear fields are real
-and even---the Fourier transform of a real and even function is real and
-even---and the radial fields are real and odd---the Fourier transform of a real
-and odd function is imaginary and odd.
-
-Our final step is to calculate the irradiance on the detector
-\begin{align}
-  h_{\text{det}}(r_d, \so{}) &\propto |\mb{E}_{\text{det}}(r_d, \so{})|^2.
-\end{align}
-The irradiance is the sum of the contributions from the linear and radial fields
-since their fields are out of phase, so
-\begin{align}
-  h_{\text{det}}(r_d, \vartheta) &\propto a_1(r_d)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r_d)\cos^2\vartheta, 
-\end{align}
-where we have defined
-\begin{align}
-  a_n(r_d) \equiv \frac{n}{\pi}\left[\frac{J_n(k\alpha r_d)}{r_d}\right]^2. 
-\end{align}
-Notice that we retain the $\alpha^2$ irradiance term even though we dropped
-$\theta^2$ electric field terms since these terms would become $\theta^4$
-irradiance terms.
-
-Figures \ref{fig:hdet} and \ref{fig:microscope} summarize the most important
-features of the dipole detection model. When $\alpha$ is very small the
-detection kernel is the usual Airy pattern weighted by $\sin^2\vartheta$. Note
-that the monopole detection model ignores the $\sin^2\vartheta$ dependence---see
-Figure \ref{fig:microscope} a) and b). As $\alpha$ grows, the relative
-contribution of the higher-order Airy pattern increases. The most important
-result is that the dipole detection model is not separable into the product of a
-spatial and angular kernel---even under the paraxial approximation. The
-detection model is only separable when $\alpha$ approaches zero, which is almost
-never the case in real microscopes. We refer to the non-separability of the
-detection kernel as \textit{spatio-angular coupling} because the orientation of
-the dipole is coupled to the spatial pattern of irradiance on the detector.
-
-The paraxial detection kernel is rotationally symmetric---it depends on $r_d$ instead of
-$\rd$. This symmetry is a result of the $\pi/2$ phase shift between the linear
-and radial fields on the detector. If the phase shift between the linear and
-radial fields was not exactly $\pi/2$ then the fields would interfere on the
-detector, and we would lose rotational symmetry. Tracing back further, the
-rotational symmetry is due to the fact that the field in the back focal plane
-could be written as a sum of a linear and radial field which is only true under
-the paraxial approximation---the rotational symmetry of the detection kernel is
-only true to first order. Despite the approximation, we still feel that the
-rotational symmetry of the detection kernel is a valuable result since it helps
-build an intuition about the dominant effects outside the paraxial
-approximation.
-
-Note that we have restricted our analysis to an imaging system with unit
-magnification. We will continue with this simplification and mention that an
-imaging system with an arbitrary magnification can be modeled using the model
-for a system with unit magnification and a change of variable (see
-\cite{barrett2004} section 7.2.7).
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/detection/detection.pdf}
-   \caption{Normalized detection kernel as a function of the scaled radial
-     detection coordinate $k\alpha r_d$, the dipole inclination angle
-     $\vartheta$, and the collection angle $\alpha$. For small
-     collection angles (left) the detection kernel of axial dipoles
-     (\textcolor{red}{\textbf{red}}) is small compared to transverse dipoles
-     (\textbf{black}), but the relative contribution of axial dipoles increases
-     with the collection angle (see \textcolor{red}{\textbf{red}} lines from
-     left to right).}
+   \includegraphics[scale=0.8]{../figures/paratfs/dpsf.pdf}
+   \caption{Renormalized paraxial dipole point spread function as a function of
+     the scaled radial coordinate $\nu_c r$, the dipole inclination angle
+     $\vartheta$, and $\text{NA}/n_o$. For small numerical apertures (left) the
+     irradiance pattern created by axial dipoles (\textcolor{red}{\textbf{red}})
+     is small compared to transverse dipoles (\textbf{black}), but the relative
+     contribution of axial dipoles increases with the numerical aperture (see
+     \textcolor{red}{\textbf{red}} lines from left to right).}
    \label{fig:hdet}
@@
    \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
-   \caption{Comparison of paraxial detection models for monopole radiators a)
-     and dipole radiators b)--d). a) Monopole radiators fill the back focal
-     plane with a uniform scalar field which gives rise to the familiar Airy
-     disk on the detector. b) A transverse dipole radiator also creates an Airy
-     disk, but the back focal plane is filled with a uniform vector field. c) An
-     axial dipole radiator creates a radial electric field pattern in the back
-     focal plane which creates a higher-order Airy disk on the detector. d)
+   \caption{Comparison of paraxial models for monopole radiators a) and dipole
+     radiators b)--d). a) Monopole radiators fill the pupil plane with a uniform
+     scalar field which gives rise to an Airy disk on the detector. b) A
+     transverse dipole radiator also creates an Airy disk, but the pupil plane
+     is filled with a uniform vector field. c) An axial dipole radiator creates
+     a radial electric field pattern in the back focal plane which creates a
+     $\text{jinc}_1^2(r)$ (or higher-order Airy disk) on the detector. d)
      Dipoles that are not transverse or axial still create radially symmetric
@@
      symmetric irradiance patterns.}
-   \label{fig:microscope}
+   \label{fig:microscopefig}
  \end{figure}
 
-\subsubsection{Complete orientation-dependent point spread function}
- Combining the results of the previous two sections yields a simplified dipole
- imaging model 
- \begin{align}
-g(\rd{}) = \int_{\mbb{S}^2}d\so{}\int_{\mbb{R}^2}d\ro{}\, h(|\rd - \ro|, |\so\cdot \mh{z}|)f(\ro, \so).\label{eq:simplified}
- \end{align}
- where we have written the kernel in terms of $|\so\cdot\mh{z}| = \cos\vartheta$
- to explicitly show the dependence on $\so$. In previous sections we showed that the
- kernel is given by 
- \begin{align}
-   h(r, \vartheta) &\propto h_{\text{exc}}(\vartheta)h_{\text{det}}(r,\vartheta).
- \end{align}
- Plugging in our results we find:
- \begin{align}
-   h(r, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[a_1(r)\sin^2\vartheta + \frac{1}{2}\alpha^2 a_2(r)\cos^2\vartheta\right]. \label{eq:sa-psf}
- \end{align}
-
- Comment on inversion/antipodal symmetry.
-
- To demonstrate the orientation-dependent point spread function, we calculate
- the irradiance pattern created by a set of equally spaced dipoles with varying
- orientation given by
- \begin{align}
-   f_{\text{(ph1)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \delta\left(x_o - \frac{i}{3}\right)\, \delta\left(y_o - \frac{j}{3}\right)\, \delta\left(\cos\vartheta - \cos\left(\frac{\pi i}{6}\right)\right)\, \delta\left(\varphi - \frac{2\pi j}{3}\right),\label{eq:phantom1}
- \end{align}
- where the subscript (ph1) indicates that this is the first phantom. To find the
- irradiance pattern we plug Eq. \ref{eq:phantom1} into Eq. \ref{eq:simplified}
- and use the sifting property
- \begin{align}
-   g_{\text{(ph1)}}(x_d, y_d) = \sum_{i=0}^3 \sum_{j=0}^3 h\left(\sqrt{\left(x_d - \frac{i}{3}\right)^2 + \left(y_d - \frac{j}{3}\right)^2}, \frac{\pi i}{6}\right).\label{eq:phantom1irr}
- \end{align}
-
-\subsection{Orientation-dependent optical transfer function of a paraxial epi-fluorescence microscope}\label{sec:trans}
-  In Appendix \ref{sec:airy} we evaluate the 2D spatial Fourier transforms of
-  $a_1(r)$ and $a_2(r)$ to find that
-  \begin{align}
-    H(\nu, \vartheta) &\propto \left[\sin^2\vartheta + \frac{1}{2}\alpha^2 \cos^2\vartheta\right]\left[A_1(\nu)\sin^2\vartheta + \frac{1}{2}\alpha^2 A_2(\nu)\cos^2\vartheta\right].
-  \end{align}
-  where 
-\begin{align}
-  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{4\nu_o}\right), \\
-  A_2(\nu) &= \frac{2}{\pi}\Bigg\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{4\nu_o}\right).
-\end{align}
-The orientation-dependent optical transfer function is shown in Figure
-\ref{fig:odotf}. The orientation-dependent transfer function has the usual
-spatial-frequency cutoff at $\nu_c = 2\nu_o$ for all dipole orientations.
+ To demonstrate the paraxial dipole point spread function we simulate a set of
+ equally spaced dipoles with varying orientation
+ \begin{align}
+   f_{(ph1)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, \delta\left(\cos\vartheta - \cos\vartheta_j\right)\, \delta\left(\varphi - \varphi_k\right),\label{eq:phantom1}
+ \end{align}
+ where $\vartheta_j = j\frac{\pi}{6}$, $\varphi_k = k\frac{\pi}{4}$, the
+ subscript $(ph1)$ indicates that this is the first phantom, and the spatial
+ coordinates are expressed in $\mu$m. To find the irradiance pattern created by
+ the phantom Eq. \ref{eq:phantom1} we plug it into Eq. \ref{eq:odpsf} and use
+ the sifting property to find that
+ \begin{align}
+   g_{(ph1)}(r_x, r_y) = \sum_{j=0}^3 \sum_{k=0}^3 h\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}, \vartheta_j\right).\label{eq:phantom1irr}
+ \end{align}
+ In Figure \ref{fig:ph1} we plot the phantom and scaled irradiance for an
+ imaging system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and
+ $n_o = 1.33$. We sample and plot the scaled irradiance at $20\times$ the
+ Nyquist rate $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free
+ of aliasing. The output demonstrates that the irradiance pattern depends on the
+ dipole inclination, but not its azimuth.
 
@@
    \centering
-   \includegraphics[scale=0.8]{../figures/stf/stf.pdf}
-   \caption{Orientation-dependent transfer function as a function of the scaled
-     spatial frequency, the dipole inclination angle $\vartheta$, and the
-     collection angle $\alpha$. For small collection angles (left) the STF for
-     axial dipoles (\textcolor{red}{\textbf{red}}) is small compared to
-     transverse dipoles (\textbf{black}), but the relative contribution of axial
-     dipoles increases with the collection angle (see
-     \textcolor{red}{\textbf{red}} lines from left to right). The STF of axial
-     dipoles is negative at high spatial frequencies because the central minimum
-     of the axial kernel corresponds to the position of the dipole.
-     Equivalently, a high-spatial-frequency pattern of axial dipoles will
-     generate an irradiance pattern where the minimum irradiance corresponds to
-     the peak of the axial dipole density.}
+   \includegraphics[scale=0.8]{../figures/paratfs/ph1.pdf}
+   \caption{\textbf{Left:} A spatially and angularly sparse phantom---uniformly
+     spaced single dipoles with varying orientations (increasing $\vartheta$
+     from left to right and increasing $\varphi$ from bottom to top). White
+     crosses mark the positions of the dipoles. \textbf{Center:} Scaled
+     irradiance for an imaging system with $\text{NA} = 0.75$,
+     $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at $20\times$ the
+     Nyquist rate. \textbf{Right:} $x$ profiles through the scaled irradiance.
+     The response is independent of the azimuth angle and strongly dependent on
+     the inclination angle.}
+   \label{fig:ph1}
+ \end{figure}
+
+\subsection{Paraxial dipole spatial transfer function}\label{sec:trans}
+The dipole spatial transfer function is the spatial Fourier transform of
+the dipole point spread function (or the complex autocorrelation of the dipole
+coherent transfer function). Applying the Fourier transform to Eq.
+\ref{eq:paradpsf} we find that
+  \begin{align}
+    H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
+  \end{align}
+  In Figure \ref{fig:odotf} we plot the dipole spatial transfer function for
+  several dipole orientations dipole orientations and numerical apertures. We
+  find that the dipole spatial transfer function is negative for axial dipoles
+  at high spatial frequencies, especially for larger numerical apertures. The
+  negative spatial transfer corresponds to a contrast inversion for
+  high-frequency patterns of axial dipoles because the irradiance minimum
+  corresponds to the position of the dipole.
+
+\begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/sdtf.pdf}
+   \caption{Dipole spatial transfer function as a function of the scaled spatial
+     frequency $\nu/\nu_c$, the dipole inclination angle $\vartheta$, and
+     $\text{NA}/n_o$. For small numerical apertures (left) the dipole spatial
+     transfer function for axial dipoles (\textcolor{red}{\textbf{red}}) is
+     small compared to transverse dipoles (\textbf{black}), but the relative
+     contribution of axial dipoles increases with the numerical aperture (see
+     \textcolor{red}{\textbf{red}} lines from left to right). The spatial dipole
+     transfer function of axial dipoles is negative at high spatial frequencies
+     because the central minimum of the axial dipole point spread function
+     corresponds to the position of the dipole. Equivalently, a
+     high-spatial-frequency pattern of axial dipoles will generate an irradiance
+     pattern where the minimum irradiance corresponds to the peak of the axial
+     dipole density.}
    \label{fig:odotf}
@@
 
- To demonstrate the spatial transfer spread function, we calculate the
- irradiance pattern created by a set of equally spaced disks with varying radius
- containing fluorophores with varying orientation given by
- \begin{align}
-   f_{\text{(ph2)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \Pi\left(\frac{10}{j}\sqrt{\left(x_o - \frac{i}{3}\right)^2 + \left(y_o - \frac{j}{3}\right)^2}\right) \delta\left(\cos\vartheta - \cos\left(\frac{\pi i}{6}\right)\right)\, \delta\left(\varphi - \frac{2\pi j}{3}\right).\label{eq:phantom2}
- \end{align}
- \begin{align}
-   G_{\text{(ph2)}}(\nu_x, \nu_y) = \sum_{i=0}^3 \sum_{j=0}^3 H\left(\nu_x, \nu_y, \frac{\pi i}{6}, \frac{2\pi j}{3}\right)\left[\frac{j}{10\nu}J_1\left(\frac{2\pi j\nu}{10}\right)\right]\text{exp}\left(-2\pi i\left[\frac{i}{3}\nu_x + \frac{j}{3}\nu_y\right]\right).\label{eq:phantom2g}
- \end{align}
- Finally, we calculate the inverse Fourier transform of the irradiance spectrum
- to find the irradiance.
-
- \subsection{Angular transfer function (ATF) of a paraxial epi-fluorescence microscope}
-To calculate the angular transfer function we plug the spatio-angular point
-spread function Eq. \ref{eq:sa-psf} into Eq. \ref{eq:atf-prep} and evaluate the
-integrals using a computer algebra package \cite{meurer2017} to find
-\begin{alignat}{6}
-  H_l^m(r) \propto \quad 7&\{\hphantom{-}32&&a_1(r)&& + 4\alpha^2[a_1(r) + a_2(r)]&&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
-  4\sqrt{5}&\{-16&&a_1(r)&& + \hphantom{1}\alpha^2[a_1(r) + a_2(r)] &&+ 3\alpha^4a_2(r)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
-  8&\{\hphantom{-1}4&&a_1(r)&& - 2\alpha^2[a_1(r) + a_2(r)] &&+ \hphantom{1}\alpha^4a_2(r)\}&&\delta_{\ell 4}\delta_{m0}.
-\end{alignat}
-The degree $\ell$ and order $m$ of the non-zero terms in the ATF follow directly
-from specific features of the kernel. First, the spatio-angular point spread
-function is symmetric under inversion of the dipole moment. This symmetry is
-maintained in the angular transfer function since all of the non-zero terms have
-an even degree $\ell=0, 2, 4$, and the corresponding spherical harmonics
-$Y_0^0(\so)$, $Y_2^0(\so)$, $Y_4^0(\so)$ are symmetric under inversion. Second,
-we showed that under the paraxial approximation our kernel is rotationally
-symmetric which allows us to write the kernel as a function of $r$ instead of
-$\mb{r}$. This symmetry is maintained in the ATF since all of the non-zero terms
-have order $m=0$. Finally, both the excitation and detection kernels are
-degree-2 trigonometric polynomials, which implies that the maximum degree of the
-spatio-angular point spread function is 4. This feature of the kernel appears in
-the angular transfer function since only $\ell=0, 2$, and $4$ terms are
-non-zero.
+ To demonstrate the spatial dipole transfer function we simulate a set of
+ equally spaced disks with varying diameter containing fluorophores with varying
+ orientation
+ \begin{align}
+   f_{\text{(ph2)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
+ \end{align}
+ where $D_k = 0.15(1+k)\, \mu$m and $\vartheta_j = j\frac{\pi }{6}$. Notice that
+ we have scaled the disks so that the total number of fluorophores in each disk
+ is constant.
+
+ We can calculate the irradiance pattern by taking the spatial Fourier transform
+ for each orientation in the phantom, filtering the result with the dipole
+ spatial transfer function, integrating over the orientations, then taking the
+ inverse spatial Fourier transform. Since our phantom is angularly sparse, the
+ integral becomes a sum and we find that
+ \begin{align}
+   g_{\text{(ph2)}}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{\text{(ph2)}}(r_x, r_y, \vartheta_j)\right\}\right\}.
+ \end{align}
+
+ In Figure \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
+ imaging parameters as the previous section. The small disks create irradiance
+ patterns that are similar to the point sources in the previous section, while
+ larger disks create increasingly uniform irradiance patterns that hide the
+ orientation of the fluorophores.
 
   \begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/atf/atf.pdf}
-   \caption{ATF as a function of the scaled radial detection coordinate
-     $k\alpha r$, the spherical harmonic degree $\ell$, and the collection angle
-     $\alpha$. 
-   }
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/ph2.pdf}
+   \caption{\textbf{Left:} A spatially dense and angularly sparse
+     phantom---uniformly spaced disks with varying size (increasing $D$ from
+     bottom to top) and dipole orientation (increasing $\vartheta$ from left to
+     right) \textbf{Center:} Scaled irradiance for an imaging system with
+     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+     scaled irradiance. Larger disks generate increasingly uniform irradiance
+     patterns with fewer details that may indicate the orientation of
+     fluorophores.}
+   \label{fig:ph2}
+ \end{figure}
+
+ \subsubsection{Paraxial dipole angular transfer function}
+ To calculate the angular dipole transfer function we take the spherical Fourier
+ transform of the dipole point spread function
+ \begin{align}
+H_l^m(\mb{r}) \stackrel{}{=} \int_{\mbb{S}^2}d\so\, h(\mb{r}, \so)Y_l^{m*}(\so).
+ \end{align}
+ After evaluating the integrals and normalizing, the angular dipole transfer
+ function is
+ \begin{align}
+   H_l^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3}\left[2\text{jinc}_0^2(\nu_cr) + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_0\delta_{\ell0}\delta_{m0} + \nonumber\\& \frac{N}{3}\left[-2\text{jinc}_0^2(\nu_c r) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_2\delta_{\ell2}\delta_{m0},
+ \end{align}
+where $\Lambda_{\ell} = \sqrt{4\pi/(2\ell + 1)}$.
+
+In Figure \ref{fig:atf} we plot the dipole angular transfer function for both
+spherical harmonic terms and several numerical apertures. Note that the dipole
+angular transfer function can be negative because the spherical harmonics
+contain negative values. The $\ell=0$ term shows that angularly uniform
+distributions of dipole create spatial irradiance patterns that are nearly
+identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
+because of the large contribution of the transverse negative dipoles in the
+$Y_2^0$ spherical harmonic.
+
+ % The degree $\ell$ and order $m$ of the non-zero terms in the angular dipole
+ % transfer function . First, the spatio-angular point spread function is symmetric
+ % under inversion of the dipole moment. This symmetry is maintained in the
+ % angular transfer function since all of the non-zero terms have an even degree
+ % $\ell=0, 2$, and the corresponding spherical harmonics $Y_0^0(\so)$,
+ % $Y_2^0(\so)$ are symmetric under inversion. Second, we showed that under the
+ % paraxial approximation our kernel is rotationally symmetric which allows us to
+ % write the kernel as a function of $r$ instead of $\mb{r}$. This symmetry is
+ % maintained in the angular dipole transfer function since all of the non-zero
+ % terms have order $m=0$. Finally, the dipole point spread function consists of
+ % degree-2 trigonometric polynomials which implies that the dipole angular
+ % transfer function will only contain $\ell=0, 2$ terms.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/adtf.pdf}
+   \caption{Paraxial dipole angular transfer function in terms of a scaled
+     radial detection coordinate $\nu_c r$, the spherical harmonic degree
+     $\ell$, and $\text{NA}/n_o$. Angularly uniform distributions of dipoles
+     $\ell=0$ generate a spatial pattern that is nearly identical to an Airy
+     disk. $\ell=2$ distributions have a negative response because
+     $Y_2^0(\mh{s})$ is negative for transverse directions. As the numerical
+     aperture increases, the relative contribution of positive axial dipoles in
+     the $\ell=2$ distribution increases.}
    \label{fig:atf}
@@
 
- To demonstrate the angular transfer function, we calculate the irradiance
- pattern created by a set of equally spaced fluorophore distributions with
- varying orientation and angular distribution given by
- \begin{align}
-   f_{\text{(ph3)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \delta\left(x_o - \frac{i}{3}\right)\, \delta\left(y_o - \frac{j}{3}\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right),\label{eq:phantom3}
+ To demonstrate the dipole angular transfer function we simulate a set of
+ equally spaced fluorophore distributions with varying orientation and angular
+ distributions
+ \begin{align}
+   f_{\text{(ph3)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
  \end{align}
@@
  \begin{align}
-   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right).
- \end{align}
- To calculate the irradiance pattern we calculate the angular density spectrum
- of the phantom (we calculate the spherical Fourier transform of the cone in
- Appendix \ref{sec:cone}), plug the result into Eq. XXX, then use the sifting
- property to find that
- \begin{align}
-   g_{\text{(ph3)}}(x_d, y_d) = \sum_{\ell m}\sum_{i=0}^3 \sum_{j=0}^3 H_\ell^m\left(\sqrt{\left(x_d - \frac{i}{3}\right)^2 + \left(y_d - \frac{j}{3}\right)^2}\right) F_{\ell\text{(cone)}}^m\left(\frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right),\label{eq:phantom3}
- \end{align}
-
-\subsection{Spatio-angular transfer function (SATF)  of a paraxial epi-fluorescence microscope}
-  \begin{alignat}{6}
-  H_l^m(\nu) \propto \quad 7&\{\hphantom{-}32&&A_1(\nu)&& + 4\alpha^2[A_1(\nu) + A_2(\nu)]&&+ 3\alpha^4A_2(\nu)\}&&\delta_{\ell 0}\delta_{m0}+\nonumber\\
-  4\sqrt{5}&\{-16&&A_1(\nu)&& + \hphantom{1}\alpha^2[A_1(\nu) + A_2(\nu)] &&+ 3\alpha^4A_2(\nu)\}&&\delta_{\ell 2}\delta_{m0} + \nonumber\\
-  8&\{\hphantom{-1}4&&A_1(\nu)&& - 2\alpha^2[A_1(\nu) + A_2(\nu)] &&+ \hphantom{1}\alpha^4A_2(\nu)\}&&\delta_{\ell 4}\delta_{m0}.
-\end{alignat}
+   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{2\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right),
+ \end{align}
+ is an angular double cone distribution with central direction $\mh{s}'$ and
+ cone half-angle $\Delta$; $\vartheta_j = j\frac{\pi}{6}$; and
+ $\Delta_k = k\frac{\pi}{6}$. Notice that when $\Delta = 0$ the angular double
+ cone reduces to a single direction, and when $\Delta = \pi/2$ the angular
+ double cone reduces to an angularly uniform distribution.
+
+ Our first step towards the irradiance pattern is to calculate the dipole
+ angular spectrum of the phantom. In Appendix \ref{sec:cone} we calculate the
+ spherical Fourier transform of the double cone distribution
+ $F^m_{\ell,\text{(cone)}}(\vartheta', \varphi'; \Delta)$ which we can use to
+ express the dipole angular spectrum as
+ \begin{align}
+   F^{m}_{\ell,\text{(ph3)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
+ \end{align}
+
+ To find the irradiance we plug the dipole angular spectrum into Eq.
+ \ref{eq:atf-form} and use the sifting property we find that
+ \begin{align}
+   g_{\text{(ph3)}}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
+ \end{align}
+
+ In Figure \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
+ imaging parameters as the previous sections. For small cone angles the
+ irradiance patterns are similar to the point sources in the previous sections,
+ while larger cone angles create increasingly uniform irradiance patterns that
+ hide the angular information about the distributions.
 
   \begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/satf/satf.pdf}
-   \caption{SATF as a function of the scaled spatial frequency, the spherical
-     harmonic degree $\ell$, and the collection angle $\alpha$. }
-   \label{fig:atf}
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/ph3.pdf}
+   \caption{\textbf{Left:} A spatially sparse and angularly dense
+     phantom---uniformly spaced double cone distributions of fluorophores with
+     varying central direction (increasing $\vartheta'$ from left to right) and
+     varying cone half-angle (increasing $\Delta$ from bottom to top).
+     \textbf{Center:} Scaled irradiance for an imaging system with
+     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+     scaled irradiance. Small cone angles have irradiance patterns that vary
+     with the central direction, while larger cones angles have increasingly
+     uniform irradiance patterns that hide angular information.}
+   \label{fig:ph3}
  \end{figure}
 
- To demonstrate the spatio-angular transfer function, we calculate the
- irradiance pattern created by a set of equally spaced disks of fluorophores
- with varying radius and angular distribution given by
- \begin{align}
-   f_{\text{(ph4)}}(x_o, y_o, \vartheta, \varphi) = \sum_{i=0}^3 \sum_{j=0}^3 \Pi\left(\frac{10}{j}\sqrt{\left(x_o - \frac{i}{3}\right)^2 + \left(y_o - \frac{j}{3}\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \frac{\pi i}{6}\right),\label{eq:phantom4}
- \end{align}
- To calculate the irradiance pattern created by the phantom we calculate the
- spatio-angular spectrum, plug the result into Eq. XXX, then take the inverse
- Fourier transform to find the irradiance.
-  \begin{align}
-    G_{\text{(ph2)}}(\nu_x, \nu_y) = \sum_{\ell m}\sum_{i=0}^3 \sum_{j=0}^3 H_\ell^m(\nu_x, \nu_y)\left[\frac{j}{10\nu}J_1\left(\frac{2\pi j\nu}{10}\right)\right]\text{exp}\left(-2\pi i\left[\frac{i}{3}\nu_x + \frac{j}{3}\nu_y\right]\right)F_{\ell\text{(cone)}}^m\left(\frac{\pi i}{6}, \frac{2\pi j}{3}, \frac{\pi i}{6}\right).\label{eq:phantom4g}
- \end{align}
+ \subsubsection{Paraxial dipole spatio-angular transfer function}
+ We can calculate the dipole spatio-angular transfer function by taking the
+ spatial Fourier transform of the dipole angular transfer function (or the
+ spherical Fourier transform of the dipole spatial transfer function) to find
+ that
+ \begin{align}
+H_{\ell}^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
+ \end{align}
+
+ In Figure \ref{fig:dsatf} we plot the dipole spatio-angular transfer function
+ for both spherical harmonic terms and several numerical apertures. The $\ell=0$
+ term shows that angularly uniform distributions of dipole create spatial
+ irradiance patterns that are nearly identical to the Airy disk, with high
+ frequencies increasingly suppressed as the numerical aperture increases. The
+ $\ell=2$ term shows a negative pattern because of the large contribution of the
+ transverse negative dipoles in the $Y_2^0$ spherical harmonic, and as the
+ numerical aperture increases the relative contribution of the positive axial
+ dipoles increases and the $\ell=2$ term becomes less negative.
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/satf.pdf}
+   \caption{Spatio-angular dipole transfer function as a function of the scaled
+     spatial frequency $\nu/\nu_c$, the spherical harmonic degree $\ell$, and
+     $\text{NA}/n_o$. When the numerical aperture is small the transverse
+     dipoles contribute the most to the signal which gives rise to a positive
+     $\ell=0$ component and a negative $\ell=2$ component. As the numerical
+     aperture increases, the relative contribution of axial dipoles increases
+     and the $\ell=2$ component becomes less negative.}
+   \label{fig:dsatf}
+ \end{figure}
+
+ To demonstrate the spatio-angular transfer function, we simulate a set of
+ equally spaced disks of fluorophores with varying radius and angular
+ distributions
+ \begin{align}
+   f_{\text{(ph4)}}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
+ \end{align}
+ where $D_k = 0.15(1+k)\, \mu$m, and $\Delta_j = j\frac{\pi}{6}$.
+
+ Our first step towards calculating the irradiance pattern is to calculate the
+ dipole spatio-angular spectrum given by the spatial Fourier transform of the dipole angular spectrum  
+  \begin{align}
+   \mathsf{F}_{\ell,\text{(ph4)}}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
+  \end{align}
+  We can plug the dipole spatio-angular spectrum into Eq. \ref{eq:saft} to find
+  the scaled irradiance as 
+  \begin{align}
+   g_{\text{(ph4)}}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,\text{(ph4)}}^m(\nu_x, \nu_y)\right\}.
+  \end{align}
+
+  In Figure \ref{fig:ph4} we plot the phantom and scaled irradiance with the
+  same imaging parameters as the previous sections. Small cone angles and small
+  disks create relatively unique irradiance patterns, while increasing the cone
+  angle or disk size creates increasingly irradiance patterns.
+
+  \begin{figure}[h]
+ % \captionsetup{width=1.0\linewidth}
+ \centering
+   \centering
+   \includegraphics[scale=0.8]{../figures/paratfs/ph4.pdf}
+   \caption{\textbf{Left:} A spatially and angularly dense phantom---uniformly
+     spaced disks with varying size (increasing $D$ from bottom to top) and
+     double cone half angle (increasing $\Delta$ from left to right)
+     \textbf{Center:} Scaled irradiance for an imaging system with
+     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+     scaled irradiance.}
+   \label{fig:ph4}
+ \end{figure}
 
@@
 \subsection{Reconstructions}
-Since the ATF effectively contains three OTFs it is tempting to conclude that
-fluorescence microscopes pass three times as much information about the dipoles
-as monopoles. This is not true. The microscope still only measures a single
-member of $\mbb{L}_2(\mbb{R}^2)$, so at best we can recover the same amount of
-information about the object. In other words, we know immediately that the
-microscope is a rank-1 operator since it only measures one continuous function.
-
-TODO Expand. Make clear that a later paper will include a full discussion of SVD
-to find the object space singular functions that span the measurement space of
-the instrument.
+% Since the dipole spatio-angular transfer function effectively contains it is
+% tempting to conclude that fluorescence microscopes pass three times as much
+% information about the dipoles as monopoles. This is not true. The microscope
+% still only measures a single member of $\mbb{L}_2(\mbb{R}^2)$, so at best we can
+% recover the same amount of information about the object. In other words, we know
+% immediately that the microscope is a rank-1 operator since it only measures one
+% continuous function.
+\begin{itemize}
+\item Very ill-posed reconstruction problem by dimensionality.
+\item Better-posed reconstruction problem by adding polarized illumination/detection
+  formulated as $\mc{H}: \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)$ and/or multiple views $\mc{H}: \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^2\times\mbb{S}^1)^V$.
+\item Mention SVD for future papers
+\end{itemize}
+
+% TODO Make clear that a later paper will include a full discussion of SVD
+% to find the object space singular functions that span the measurement space of
+% the instrument.
 
@@
 for functions on the sphere, but there are other basis functions that can be
-advantageous in some cases. Backer and others [CITE TODO] have used the second
-moments as basis functions for the sphere because they arise naturally when
-computing the spatio-angular point spread function. Mathematically, Backer and
-[XXX] use an alternative to the angular transfer function that uses the second
-moments as basis functions so their forward model is given by
+advantageous in some cases. Backer and [TODO Brasselet, others] have used
+the second moments as basis functions for the sphere because they arise
+naturally when computing the dipole point spread function. Mathematically,
+Backer and Moerner \cite{backer2014} use an alternative to the dipole angular
+transfer function that uses the second moments as basis functions so their
+forward model becomes
 \begin{align}
@@
 approach because it exploits the spatial sparsity of sample, but it does not
-require a cumbersome expansion of the spatio-angular point spread function onto
+require a cumbersome expansion of the dipole point spread function onto
 spherical harmonics.
@@
 usual approach to extending the span of the second moments is to use the fourth
-(or higher) moments, but these are completely new basis functions. Indeed, the
-microscope we considered in this work cannot be represented using the second
-moments since it contains fourth-order terms. Second, the spherical harmonics
-are orthonormal which allows us to easily deploy tools from linear algebra. For
-example, the spatio-angular transfer function for the microscope we considered
-in this work required three angular terms so we can think of the angular
-response as a vector in a three-dimensional vector space. If we had used the
-second moments we would have required six terms, and we would not have been able
-to say anything about the dimension of the space since the second moments are
-not orthonormal. Finally, using the spherical harmonics provides access to a set
-of fast algorithms. The naive expansion of an arbitrary discretized $N$ point
-spherical function onto spherical harmonics (or second moments) requires a
-$\mc{O}(N^2)$ matrix multiplication, while pioneering work by Driscoll and Healy
-[cite] showed that the forward discrete fast spherical harmonic transform can be
-computed with a $\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed
-with a $\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast
-algorithms exist for expansion onto the higher-order moments.
-
-TODO: Cite Tournier/Descoteux change of basis from SH to SM basis.
-
-\subsection{What determines the angular frequency cutoff?}
-The spatial-frequency cutoff of a fluorescence microscope is well known to be
-2NA$/\lambda$---we can increase spatial resolution by increasing the NA of the
+(or higher) moments, but these are completely new basis functions. Second, the
+spherical harmonics are orthonormal which will allow us to easily deploy
+invaluable tools from linear algebra---linear subspaces, rank, decompositions,
+etc.--- to analyze and compare microscope designs. Finally, using the spherical
+harmonics provides access to a set of fast algorithms. The naive expansion of an
+arbitrary discretized $N$ point spherical function onto spherical harmonics (or
+second moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering
+work by Driscoll and Healy [cite] showed that the forward discrete fast
+spherical harmonic transform can be computed with a $\mc{O}(N(\log N)^2)$
+algorithm and its inverse can be computed with a $\mc{O}(N^{3/2})$ algorithm. To
+our knowledge no similarly fast algorithms exist for expansion onto the
+higher-order moments.
+
+TODO: Cite Tournier/Descoteux for an easy change of basis between spherical
+harmonics and second moments
+
+\subsection{What determines the angular bandwidth?}
+Spatial imaging systems have a spatial bandwidth which characterizes is the
+highest spatial frequency that the system can image. Similarly, angular imaging
+systems have an angular bandwidth that characterizes the highest angular
+frequency, but in the angular case there are two different types of angular
+bandwidths that we call $ell$ and $m$ bandwidths. The $\ell$-bandwidth can be
+interpreted in a similar way to the spatial bandwidth---it characterizes the
+smallest angular features that the imaging system can measure. The $m$-bandwidth
+does not have a direct analog in the spatial domain---it characterizes the
+angular uniformity of the imaging system. If the $\ell$ and $m$ bandwidths are
+equal then the imaging system can be said to be $\textit{rotation invariant}$.
+
+The spatial bandwidth of a fluorescence microscope is well known to be
+$\nu_c = \frac{2\text{NA}}{\lambda}$. In other words, we can increase the
+spatial resolution of a fluorescence microscope by increasing the NA of the
 instrument or by choosing a fluorophore with a shorter emission wavelength.
-Analogously, the angular-frequency spectrum of a fluorescence microscope depends
-on both the instrument and the sample.
-
-The simple paraxial microscope considered in this work always has three terms in
-its angular-frequency spectrum, but we can increase the number of terms by
-modifying the instrument. We will postpone the complete treatment of these
-effects until future work, but we briefly mention that the number of terms in
-the angular-frequency spectrum increases for non-paraxial microscopes,
-microscopes with polarizers on the illumination or detection paths, and
-multiview microscopes. We also mention that there are two ways to extend the
-angular-frequency spectrum of a microscope---by increasing the degree $\ell$ and
-by increasing the order $m$. Extending the angular degree cutoff $\ell_c$ gives
-the microscope the ability to measure finer angular features, while extending
-the angular order cutoff $m_c$ give the microscope the ability to measure
-features of the object that are increasingly invariant to rotation. If the
-angular order cutoff matches the angular degree cutoff $\ell_c = m_c$ then the
-microscope can be said to have $\textit{isotropic angular resolution}$. This
-condition is not met by a single-view paraxial microscope since $\ell_0 = 4$ and
-$m_0 = 0$, but we will model microscopes with this property in future work.
-
-The number of terms in the angular frequency spectrum is also sample dependent.
-Monopoles emit light isotropically so they have a single term, dipoles have a
-three-term ATF, and higher-order excitation and detection moments will have even
-more terms---these objects have different angular band limits. We emphasize the
-similarity between the spatial and angular frequency cutoffs---both the sample
-and the instrument affect the maximum achievable resolution of the imaging
-system.
+Similarly, the angular bandwidth of a fluorescence microscope depends on both
+the instrument and the sample.
+
+The microscope we considered in this work has an $ell$ bandwidth of $\ell = 2$
+and an $m$ bandwidth of $m_c = 0$, so it is not a rotation invariant imaging
+system. In future work we will consider several approaches to improving the
+angular bandwidths in detail, but we briefly mention that non-paraxial
+microscopes, microscopes with polarizers on the illumination or detection paths,
+and multiview microscopes all have higher angular bandwidths that the microscope
+considered here.
+
+The angular bandwidth is also sample dependent. Even though they are just a
+model, monopoles emit light isotropically so they have an $\ell$ bandwidth of 1,
+while dipoles have an $\ell$ bandwidth of 2, and higher-order excitation and
+detection moments will have even higher bandwidths. Multi-photon excitation and
+other non-linear methods can also increase the $\ell$ bandwidth.
 
 \subsection{Towards more realistic models}
-The theoretical model we present in this work is an extreme simplification of a
+The theoretical model we presented in this work is an extreme simplification of a
 real microscope. We have ignored the effects of thick samples, refractive-index
@@
 
-TODO: Discuss/plan future papers. SVD?
-Defocus/3D imaging:
+TODO: Discuss/plan future papers. SVD? Defocus/3D imaging:
 $\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3)$.
-Polarized illumination/detection imaging:
-$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)$.
-Multiview polarized illumination imaging:
-$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)^V$.
 
@@
 phase aberration (like the Gibson-Lanni model), polarization aberrations,
-amplitude masks, phase masks, etc. Also cite Piestun Green's tensor engineering.
-
-% Typical fluorescence microscopy experiments start with the monopole
-% approximation and attempt to characterize the microscope by imaging
-% sub-diffraction beads. These images are assumed to be good approximations of the
-% monopole point spread function and this data can be used to restore (deconvolve)
-% the data taken in arbitrary experiments.
-
-% Imaging sub-diffraction beads is not enough to completely characterize the
-% response of a microscope to an oriented sample. We need at least three samples
-% with a known orientations to characterize the SATF, so isotropic beads are not
-% enough. Small beads may not be isotropic [cite Lew].
+amplitude masks, phase masks, etc.
+
+TODO: Cite Piestun Green's tensor engineering.
 
@@
 Most models of fluorescence microscopes use a monopole model to describe the
-object and the imaging system. A more complete description of any fluorescence
-microscope requires a dipole model of the object and a model of the
-spatio-angular point spread function. We developed several transfer functions
-that simplify the mapping between the spatio-angular density and the irradiance
-pattern on the detector, and we demonstrated these transfer functions by
-efficiently simulating a paraxial widefield fluorescence microscope.
+object and the scalar approximation to model the imaging system. A more complete
+description of any fluorescence microscope requires a dipole model of the object
+and vector optics to model the propagation of light through the microscope. We
+developed several transfer functions that simplify the mapping between the
+dipole density and the irradiance pattern on the detector, and we demonstrated
+these transfer functions by efficiently simulating a paraxial fluorescence
+microscope.
 
@@
 \appendix
-\section{Fourier transform of linear and radial vector fields}\label{sec:ftvec}
-In this appendix we evaluate the two-dimensional Fourier transform of the
-electric field in the back focal plane of paraxial epi-fluorescence microscope
-given by
-  \begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{\mbb{R}^2}d\rp{} \mb{E}_{\text{bfp}}(\rp{})\, \text{exp}\left[ik\,\rp{}\cdot\rd{}\right],\label{eq:det2}
-  \end{align}
-where
-\begin{align}
-  \mb{E}_{\text{bfp}}(r_b, \phi_b, \so{}) \propto \left\{s_x\mh{x} + s_y\mh{y} - s_z r_b \mh{\bs{\rho}}\right\}\Pi\left(\frac{r_b}{\alpha}\right). \label{eq:bfp4}
-\end{align}
-To evaluate the Fourier transform we rewrite it in polar coordinates
-\begin{align}
-\mb{E}_{\text{det}}(\rd{}, \so{}) &= \int_{0}^{\infty}r_bdr_b\int_0^{2\pi} d\phi_b\, \mb{E}_{\text{bfp}}(r_b, \phi_b)\, \text{exp}\left[ikr_b r_d\cos(\phi_b - \phi_d)\right],
-\end{align}
-plug in Eq. \ref{eq:bfp4}, and apply the following pair of identities
-\begin{align}
-  \int_0^{2\pi}d\phi_b
-  \left\{\substack{
-    \sin(n\phi_b)\\
-    \cos(n\phi_b)
-  }\right\}
-  \text{exp}\left[ikr_br_d\cos(\phi_b - \phi_d)\right] &= 2\pi i^n
-  \left\{\substack{
-    \sin(n\phi_d)\\
-    \cos(n\phi_d)
-  }\right\}J_n(k r_br_d),
-\end{align}
-and 
-  \begin{align}
-  \int_0^{\alpha} dr_b (r_b)^{n+1}J_{n}(kr_br_d) &= \alpha^{n+1}\left[\frac{J_{n+1}(k\alpha r_d)}{k r_d}\right],
-  \end{align}
-to find that
-\begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) \propto &\left[s_x\frac{J_1(k\alpha r_d)}{k\alpha r_d} - is_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\cos\phi_d\right]\mh{x}\, + \nonumber \\& \left[s_y\frac{J_1(k\alpha r_d)}{k\alpha r_d} - i s_z\alpha \frac{J_2(k\alpha r_d)}{k\alpha r_d}\sin\phi_d\right]\mh{y}.
-\label{eq:det6}
-\end{align}
-Similar to the expression for the electric field in the back focal plane, we
-rewrite Eq. \ref{eq:det6} in terms of linear and radial vector fields
-\begin{align}
-  \mb{E}_{\text{det}}(\rd{}, \so{}) \propto \frac{J_1(k\alpha r_d)}{k\alpha r_d}[s_x\mh{x} + s_y\mh{y}] - i\alpha\frac{J_2(k\alpha r_d)}{k\alpha r_d}s_z\mh{\bs{\rho}}.
-\end{align}
-
 \section{Spherical harmonics}\label{sec:sph}
@@
 We can find the spherical harmonic coefficients $F_\ell^m$ for a given function
-using Fourier's trick---multiply both sides by $\bar{Y}_\ell^m(\mh{s})$,
+using Fourier's trick---multiply both sides by $Y_\ell^{m*}(\mh{s})$,
 integrate over the sphere, and exploit orthogonality to find that
 \begin{align}
-  F_\ell^m = \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_\ell^m(\mh{s}).
+  F_\ell^m = \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_\ell^{m*}(\mh{s}).
 \end{align}
@@
 \begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)\bar{Y}_\ell^m(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
+  \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)Y_\ell^{m*}(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
 \end{align}
@@
 \begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})\bar{Y}_{2n+1}^m(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})\bar{Y}_{2n+1}^m(-\mh{s}),\\
-&=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})\bar{Y}_{2n+1}^m(\mh{s}) = 0.                                                                
-\end{align}
-\section{Fourier transform of higher-order Airy patterns} \label{sec:airy}
-In this appendix we will evaluate the two-dimensional Fourier transform of the
-higher-order Airy patterns given by
-\begin{align}
-  A_n(\bv) = \int_{\mbb{R}^2}d\mb{r}\, a_n(\mb{r})\, \text{exp}\left[-2\pi i\mb{r}\cdot\bv\right],  \label{eq:ftA}
-\end{align}
-where 
-\begin{align}
-    a_n(\mb{r}) =  \frac{n}{\pi}\left[\frac{J_n(k\alpha r)}{r}\right]^2.
-\end{align}
-
-The crucial step is to rewrite the function $a_n(\mb{r})$ in terms of the absolute
-square of a simpler function with a known Fourier transform. In this case we
-rewrite as
-\begin{align}
-  A_n(\bv) = \frac{n}{\pi}\int_{\mbb{R}^2}d\mb{r}\, |t(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\cdot\bv\right],  \label{eq:ftA}
-\end{align}
-where 
-\begin{align}
-t_n(\mb{r}) = \frac{J_n(2\pi\nu_o r)}{r}\text{exp}[i(n-1)\phi].
-\end{align}
-where $2\pi\nu_o = k\alpha$. Note that we have made a non-obvious choice for
-$t_n(\mb{r})$ because we know that we can find its Fourier transform.
-
-% $A_1(\nu)$ is a well-known result \cite{goodman1996, mertz2009}, but we will
-% review the calculation to establish the tools we'll need to evaluate $A_2(\nu)$.
+  \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})Y_{2n+1}^{m*}(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})Y_{2n+1}^{m*}(-\mh{s}),\\
+&=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) = 0.                                                                
+\end{align}
+\section{Relationships between special functions} \label{sec:special}
+Our first task is to show that 
+\begin{align}
+  i^{n}\left\{\substack{
+  \text{exp}(in\phi_r)\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\text{jinc}_{n}(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow}   (2\nu)^{n}\left\{\substack{
+    \text{exp}(in\phi_{\nu})\\
+    \cos(n\phi_{\nu})\\
+    \sin(n\phi_{\nu})
+  }\right\}\Pi(\nu). \label{eq:jincrect3}
+  \end{align}
+  Writing the inverse Fourier transform in polar coordinates yields
+  \begin{align}
+    =2^n\int_0^{1/2}d\nu\, \nu^{n+1}\int_0^{2\pi}d\phi_\nu\left\{\substack{
+    \text{exp}(in\phi_{\nu})\\
+    \cos(n\phi_{\nu})\\
+    \sin(n\phi_{\nu})
+  }\right\}\text{exp}[2\pi i\nu r\cos(\phi_\nu - \phi_r)].
+  \end{align}
+  The azimuthal integral can be evaluated in terms of an $n^{th}$ order Bessel
+  function (see Barrett and Myers 4.111 for the complex case \cite{barrett2004})
+  \begin{align}
+    =2^n 2\pi i^n \left\{\substack{
+    \text{exp}(in\phi_{r})\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\int_0^{1/2}d\nu\, \nu^{n+1}J_n(2\pi\nu r).
+  \end{align}
+  We can use the following identity (see GR 6.561-5 \cite{gradshteyn2007})
+  \begin{align}
+    \int_0^1 du\, u^{n + 1}J_{n}(au) = a^{-1}J_{n + 1}(a)
+  \end{align}
+  with a change of variable $u = 2\nu$ to find the final result
+  \begin{align}
+    &=2^n 2\pi i^n \left\{\substack{
+    \text{exp}(in\phi_{r})\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\int_0^{1}\frac{du}{2}\, \left(\frac{u}{2}\right)^{n+1}J_n(\pi u r)
+    =i^n \left\{\substack{
+    \text{exp}(in\phi_{r})\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\frac{J_{n+1}(\pi r)}{2r}
+    =i^n \left\{\substack{
+    \text{exp}(in\phi_{r})\\
+    \cos(n\phi_r)\\
+    \sin(n\phi_r)
+  }\right\}\text{jinc}_{n}(r).
+  \end{align}
+
+\begin{figure}[h]
+ \centering
+   \centering
+   \includegraphics[width = 0.45\textwidth]{../figures/special/special.pdf}
+   \caption{The relationships between special functions. The chat functions are
+     defined as the two-dimensional Fourier transform of the squared jinc
+     functions, and they can be calculated with the two-dimensional complex
+     autocorrelations (denoted by $\star_2$) of the complex-weighted rectangle
+     functions.}
+   \label{fig:special}
+ \end{figure}
+
+We can use the relationship in Eq. \ref{eq:jincrect3} to express the chat
+functions in terms of a complex autocorrelation---see the diagram in Figure \ref{fig:special}. Starting with the definition of
+the $n^{th}$-order chat function
+\begin{align}
+  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, \text{jinc}_{n}^2(|\mb{r}|)\, \text{exp}\left[-2\pi i\mb{r}\nu\right],  \label{eq:ftA}
+\end{align}
+we can rewrite the integrand in terms of the absolute square of a simpler
+function with a known Fourier transform
+\begin{align}
+  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, |t_n(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\nu\right].  \label{eq:ftB}
+\end{align}
+\begin{align}
+  t_n(\mb{r}) = i^n\text{exp}[in\phi_r]\text{jinc}_{n}(r).
+\end{align}
 Now we can apply the autocorrelation theorem to rewrite the Fourier transform as
 \begin{align}
-  A_n(\bv) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \bv), \label{eq:autocorr}
-\end{align}
-where
-\begin{align}
-  T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right]. \label{eq:tau}
-\end{align}
-We can evaluate $T_n(\bs{\tau})$ by rewriting in polar coordinates
-\begin{align}
-  T_n(\bs{\tau}) &= \int_0^{2\pi} d\phi \int_{0}^{\infty}dr\, J_n(2\pi\nu_o r)\text{exp}[i(n-1)\phi]\, \text{exp}\left[2\pi ir\tau\cos(\phi - \phi_{\tau})\right].
-\end{align}
-then evaluating the integrals with the identities (Barrett 4.111)
-\begin{align}
-  \int_0^{2\pi} d\phi\, \text{exp}[i(n-1)\phi]\text{exp}[2\pi i \tau r\cos(\phi - \phi_\tau)] = 2\pi i^{n-1}\text{exp}[i(n-1)\phi_\tau]J_{n-1}(2\pi \tau r).
-\end{align}
-and (GR 6.162)
-\begin{align}
-  \int_0^\infty dr J_n(2\pi\nu_o r)J_{n-1}(2\pi\tau r) = \frac{1}{2\pi}\frac{\tau^{n-1}}{\nu_o^n}\Pi\left(\frac{\tau}{2\nu_o}\right),
-\end{align}
-which results in 
-\begin{align}
-  T_n(\bs{\tau}) &= \frac{(i\tau\text{exp}[i\phi_\tau])^{n-1}}{\nu_o^n}\Pi\left(\frac{\tau}{2\nu_o}\right).
+  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})T^*_n(\bs{\tau} - \nu), \label{eq:autocorr}
+\end{align}
+where the function to be autocorrelated can be found with the help of Eq. \ref{eq:jincrect3}
+\begin{align}
+  T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right] = (2\tau)^n\text{exp}[in\phi_\tau]\Pi\left(\tau\right). \label{eq:tau}
 \end{align}
@@
 \begin{align}
-  T_n(\bs{\tau}) &= \frac{(i\tau_x - \tau_y)^{n-1}}{\nu_o^n}\Pi\left(\frac{\sqrt{\tau_x^2 + \tau_y^2}}{2\nu_o}\right). \label{eq:tn}
-\end{align}
-Now we can use Eq. \ref{eq:tn} to evaluate Eq. \ref{eq:autocorr}. Since the
-autocorrelation is rotationally symmetric we can restrict ourselves to shifts
-along the $\mh{x}$ axis so
-\begin{align}
-  A_n(\nu) = \frac{n}{\pi}\int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})\bar{T}_n(\bs{\tau} - \nu\mh{x}).
-\end{align}
-Plugging in Eq. \ref{eq:tn} gives
-\begin{align}
-  A_n(\nu) = \frac{n}{\pi \nu_0^{2n}}\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n-1}\Pi\left(\frac{\sqrt{\tau_x^2 + \tau_y^2}}{\nu_o}\right)\Pi\left(\frac{\sqrt{(\tau_x - \nu)^2 + \tau_y^2}}{2\nu_o}\right).
+  T_n(\bs{\tau}) &= 2^n(\tau_x + i\tau_y)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right). \label{eq:tn}
+\end{align}
+Plugging Eq. \ref{eq:tn} into Eq. \ref{eq:autocorr} gives
+\begin{align}
+  \text{chat}_{n}(\nu) = 4^n\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right)\Pi\left(\sqrt{(\tau_x - \nu)^2 + \tau_y^2}\right).
 \end{align}
@@
 \begin{align}
-  A_n(\nu) = \frac{4n}{\pi\nu_o^{2n}}\Bigg[&\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n-1} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n-1}\Bigg]\Pi\left(\frac{\nu}{4\nu_o}\right).
+  \text{chat}_{n}(\nu) = 4^{n+1}\Bigg[&\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Bigg]\Pi\left(\frac{\nu}{2}\right).
 \end{align}
 \begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
  \centering
@@
    \caption{Geometric construction for evaluating the autocorrelation. We need
-     to integrate over the overlapping region of two circles with radius $\nu_o$
-     and distance $\nu$ between their centers. The region is given by four times
-     the difference in area between a sector of angle
-     $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and a triangle with base $\nu/2$
-     and hypotenuse $\nu_o$.}
+     to integrate over the overlapping region of two circles with radius $1/2$
+     and distance $\nu$ between their centers. The region is four times the
+     difference in area between a sector of angle $\arccos(\nu)$ and radius
+     $1/2$ and a right triangle with base $\nu/2$ and hypotenuse $1/2$.}
    \label{fig:geometry}
@@
 
- We will only evaluate these integrals for $n=1$ and $n=2$, but the result for
- arbitrary $n$ is likely possible as a recurrence relation. For $n=1$:
-
-\begin{align}
-  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\right]\Pi\left(\frac{\nu}{4\nu_o}\right),\\
-%  A_1(\nu) &= \frac{4}{\pi\nu_o^{2}}\left[\int_0^{\nu_o}\tau d\tau\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \int_{0}^{\nu/2}d\tau_x\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  A_1(\nu) &= \frac{2}{\pi}\left\{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right\}\Pi\left(\frac{\nu}{2\nu_o}\right).
-\end{align}
-which is a well-known result \cite{goodman1996, mertz2009}. For $n=2$:
-\begin{align}
-  A_2(\nu) = \frac{8}{\pi\nu_o^{4}}\Bigg[&\int_0^{\nu_o}\tau d\tau\int_0^{\cos^{-1}\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\tau_x\frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
-  A_2(\nu) = \frac{2}{\pi}\Bigg\{&\cos^{-1}\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg\}\Pi\left(\frac{\nu}{4\nu_o}\right).
+For $n=0$:
+\begin{align}
+  \text{chat}_0(\nu) &= 4\left[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2}\right),\\
+  \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}\nu - \nu\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
+\intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
+  \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
+  \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}\nu - \nu (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
 \end{align}
@@
 \end{align}
-The spherical Fourier transform is given by
-\begin{align}
-  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)\bar{Y}_\ell^m(\mh{s}).
+The spherical Fourier transform is
+\begin{align}
+  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)Y_\ell^{m*}(\mh{s}).
 \end{align}
@@
 \end{align}
-The integral evaluates to \cite{gradshteyn2007} 7.111 
+The integral evaluates to (see GR 7.111 \cite{gradshteyn2007})
 \begin{align}
@@
   \begin{cases}
-    1, & \ell = 0,\\
+    \sqrt{1/(4\pi)}, & \ell = 0,\\
     0, & \ell\, \text{odd},\\

### 2018-11-24 papers/basic-theory/paper/paper.tex
First few edits from Patrick.

@@
 
-\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}Hari Shroff\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
+\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
 
@@
   microscopy. We start by modeling an aplanatic microscope imaging an ensemble
-  of in-focus fluorescent dipoles as a linear Hilbert-space operator with domain
-  $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$, and we
-  express the operator in terms of four different sets of object-space basis
-  functions. We show that the operator takes a particularly convenient form when
-  expressed in a basis of spatial and spherical harmonics---a form we call the
-  dipole spatio-angular transfer function. We demonstrate our formalism by
-  analyzing a single-view fluorescence microscope without using the monopole or
-  scalar approximations. We show that this imaging system has an angular band
+  of in-focus fluorescent dipoles as a linear Hilbert-space
+  operator, % with domain
+  % $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$
+  and we express the operator in terms of four different sets of object-space
+  basis functions. We show that the operator takes a particularly convenient
+  form when expressed in a basis of spatial and spherical harmonics---a form we
+  call the dipole spatio-angular transfer function. We demonstrate our formalism
+  by analyzing a single-view fluorescence microscope without using the monopole
+  or scalar approximations. We show that this imaging system has an angular band
   limit, and we demonstrate the value of the transfer function approach by

### 2018-12-01 papers/basic-theory/paper/paper.tex
Patrick's edits. Many formatting changes. Improved intro + discuss

@@
 % Talon's custom commands
+\setlength\arraycolsep{2.25pt}
+\let\originalleft\left
+\let\originalright\right
+\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
+\renewcommand{\right}{\aftergroup\egroup\originalright}
 \DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
@@
 
-\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}
+\author{Talon Chandler,\authormark{1,*}, Rudolf Oldenbourg,\authormark{2} and\\ Patrick La Rivi\`ere\authormark{1,2}}
 
 \address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
-\authormark{2}Publications Department, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
-\authormark{3}Currently with the Department of Electronic Journals, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}
+  \authormark{2}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
+}
 
@@
   microscopy. We start by modeling an aplanatic microscope imaging an ensemble
-  of in-focus fluorescent dipoles as a linear Hilbert-space
-  operator, % with domain
-  % $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$
-  and we express the operator in terms of four different sets of object-space
-  basis functions. We show that the operator takes a particularly convenient
-  form when expressed in a basis of spatial and spherical harmonics---a form we
-  call the dipole spatio-angular transfer function. We demonstrate our formalism
-  by analyzing a single-view fluorescence microscope without using the monopole
-  or scalar approximations. We show that this imaging system has an angular band
-  limit, and we demonstrate the value of the transfer function approach by
-  efficiently simulating the imaging process with simple phantoms. Notably, we
-  show that information about the out-of-plane orientation of ensembles of
-  in-focus fluorophores is recorded by fluorescence microscopes. We discuss the
-  implications of our analysis for all quantitative fluorescence microscopy
-  studies and lay out a path towards a complete theory.
+  of in-focus fluorescent dipoles as a linear Hilbert-space operator, and we
+  show that the operator takes a particularly convenient form when expressed in
+  a basis of spatial and spherical harmonics---a form we call the dipole
+  spatio-angular transfer function. We demonstrate our formalism by analyzing a
+  single-view fluorescence microscope without using the monopole or scalar
+  approximations. We show that this imaging system has a spatio-angular band
+  limit, and we exploit the band limit to perform efficient simulations.
+  Notably, we show that information about the out-of-plane orientation of
+  ensembles of in-focus fluorophores is recorded by paraxial fluorescence
+  microscopes.
 \end{abstract*}
@@
 \section{Introduction}
-
 Fluorescence microscopes are widely used in the biological sciences for
-measuring the spatial distribution of fluorophores throughout a sample [cite].
-While an unprocessed fluorescence micrograph reports the approximate
-distribution of fluorophores throughout a sample, all microscopes are
-diffraction limited, so the image is a blurred version of the true
-fluorophore distribution.
-
-Restoration techniques attempt to recover the true distribution of fluorophores
-using the measured data and a model of the imaging process. A model of the
-imaging process can be obtained theoretically (by mathematically modeling the
-instrument under idealized conditions), experimentally (by measuring the
-instrument's response to a known input), or by a combination of theory and
-experiment (by measuring parameters of an instrument model). In all cases the
-accuracy of the restored fluorophore distribution is limited by the accuracy of
-the imaging model. All theoretical imaging models make simplifying
-approximations that limit the accuracy of restorations, so it is important to
-verify that the approximations introduce an acceptable level of error. This work
-investigates the errors introduced by two common approximations in models of
-fluorescence microscopes---the \textit{monopole approximation} and the
-\textit{scalar approximation}.
-
-The widely-used monopole model treats fluorophores as molecules that absorb and
-emit light isotropically. Despite their use in models, monopole
-absorbers/emitters do not exist in nature. All real fluorophores absorb and emit
-light anisotropically, and in this work we investigate the more realistic dipole
-model of fluorophores. Since the absorption and emission patterns of many widely
-used fluorophores including green fluroescent protein (GFP) are known to be well
-described by the dipole model [cite Inoue], we start by considering the dipole
-model before higher-order multipole models.
-
-The scalar approximation is another widely-used approximation in fluorescence
-microscopy. The scalar approximation models the propagation of light using a
-scalar-valued field $U$ instead of the more realistic vector-valued electric
-field $\mb{E}$. Although the scalar model yields realistic results in many
-cases, the scalar field ignores polarization-dependent effects. The absorption
-and emission response of dipoles strongly depends on the polarization of the
-fields, so we need to use an electromagnetic model of light propagation to
-accurately model a microscope imaging dipoles.
-
-This work lies at the intersection of three classes of fluorescence microscopy:
-(1) ensemble imaging techniques where many fluorophores are imaged in parallel
-and the goal is to find their concentration throughout the sample, (2) single
-molecule localization microscopy (SMLM) techniques where fluorophores are sparse
-in the sample and the goal is to find the position of each fluorophore, and (3)
-polarized fluorescence techniques where many fluorophores are imaged in parallel
-and the goal is to find their concentration and orientation. We briefly review
-these three classes and focus on their use of the monopole and scalar
-approximations.
+measuring the spatial and angular distribution of ensembles of fluorophores.
+While most fluorescence microscopy experiments are designed to measure only the
+spatial distribution of fluorophores, a growing number of experiments use
+polarizers to measure both the spatial and angular distributions of fluorophores
+\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}.
+
+Meanwhile, single-molecule localization microscopy (SMLM) experiments use
+spatially sparse fluorescent samples to localize single molecules with precision
+that surpasses the diffraction limit. Real SMLM experiments are limited by noise
+\cite{foreman2011, chao2016} and model mismatch, and several studies have shown
+that model mismatch (e.g. ignoring the effects of vector optics, dipole
+orientation \cite{backlund2014}, and dipole rotation \cite{lew2013}) can
+introduce localization bias into SMLM experiments. Therefore, the most precise
+SMLM experiments must use an appropriate model and jointly estimate both the
+position and orientation of each fluorophore. Several studies have successfully
+used vector optics and dipole models to estimate the position and orientation of
+single molecules \cite{bohmer2003, lieb2004, toprak2006, aguet2009}, and there
+is growing interest in designing optical systems for measuring the position,
+orientation, and rotational dynamics of single molecules \cite{agrawal2012,
+  backer2014, zhang2018, zhang2018-2}.
+
+While many studies have focused on improving imaging models for spatially sparse
+fluorescent samples, we consider the more general case and aim to improve
+imaging models for arbitrary samples. In particular, we examine the effects of
+two widely used approximations in fluorescence microscopy---the \textit{monopole
+  approximation} and the \textit{scalar approximation}.
+
+We use the term \textit{monopole} to refer to a model of a fluorophore that
+treats it as an isotropic absorber/emitter. Although the term \textit{monopole
+  approximation} is not in widespread use, we think that it is an accurate label
+for the way many models of fluorescence microscopes treat fluorophores, and we
+use the term to distinguish the monopole model from more realistic dipole and
+higher-order models. Despite their use in models, monopole absorber/emitters do
+not exist in nature, and the monopole approximation must be justified. Although
+many works implicitly apply the monopole approximation, we have encountered two
+explicit justifications: (1) the sample contains many randomly oriented
+fluorophores within a resolvable volume or (2) the sample contains unconstrained
+rotating fluorophores. While both of these situations yield monopole-like
+samples, neither yields a sample that is perfectly described by the monopole
+model. In this work we investigate the dipole model of fluorophores in detail
+and find the conditions under which the monopole approximation is justified.
+
+All fluorescence microscopy techniques that use an \textit{optical point spread
+  function} or an \textit{optical transfer function} to model the mapping
+between the fluorophores and the irradiance on the detector implicitly make the
+monopole approximation. The optical point spread function is the irradiance
+response of an optical system to an isotropic point source, so it cannot model
+the response due to an anisotropic dipole radiator. In this work we define
+\textit{monopole and dipole transfer functions} that describe the mapping
+between fluorophores and the measured irradiance. Although optical systems are
+an essential part of microscopes, fluorescence microscopists are interested in
+measuring fluorophores (not optics), so the monopole and dipole transfer
+functions are more valuable than the optical transfer function.
+
+While the monopole approximation applies to the fluorescent object, the
+\textit{scalar approximation} applies to the fields that propagate through the
+microscope. Modeling the electric fields in a region requires a
+three-dimensional vector field, but if the electric fields are random or
+parallel a scalar field is sufficient. Replacing the vector-valued electric
+field, $\mb{E}$, with a scalar-valued field, $U$, is the scalar approximation,
+and this approximation is only justified if the fields are randomly or uniformly
+polarized.
+
+The scalar approximation is often made together with the monopole approximation.
+For example, the Born-Wolf model \cite{born1980} and the Gibson-Lanni model
+\cite{gibson89} make both the monopole and scalar approximations when applied to
+fluorescence microscopes. However, some models make the monopole approximation
+but not the scalar approximation. For example, the Richards-Wolf model
+\cite{richards} considers the role of vector-valued fields in the optical
+system, but it is an optical model so when it is applied to fluorescence
+microscopes the monopole approximation is required. As previously mentioned,
+several works in the SMLM community have modeled and applied dipole point spread
+functions that do not make the monopole or scalar approximations, but to our
+knowledge no works have considered dipole transfer functions.
+
+This work lies at the intersection of three fluorescence microscopy communities:
+(1) the spatial ensemble imaging community where many fluorophores are imaged in
+parallel and the goal is to find their concentration throughout the sample, (2)
+the spatio-angular ensemble community where many fluorophores are imaged in
+parallel and the goal is to find their concentration and orientation, and (3)
+the single molecule localization microscopy (SMLM) community where fluorophores
+are sparse in the sample and the goal is to find the position of each
+fluorophore. We briefly review how these three communities use the monopole and
+scalar approximations.
 
 The large majority of fluorescence microscopes are used to image ensembles of
-fluorophores, and many widely used restoration techniques make either or both of
-the monopole and scalar approximations. The Gibson-Lanni model \cite{gibson89}
-and the Born and Wolf model \cite{born1980} are two examples of scalar models
-that are widely used to restore data collected by fluorescence microscopes, and
-the Richards and Wolf model \cite{richards} is another widely-used model that
-accounts for vectorial diffraction. All three of these models describe how
-optical fields propagate through an optical system, but they are agnostic to the
-object that is being imaged. In other words, these models are \textit{optical}
-models, and when they are used to model fluorescent objects they implicitly make
-the monopole approximation.
-
-The SMLM community has pioneered the use of rigorous electromagnetic models for
-dipole imaging systems that do not adopt the scalar or monopole approximations
-\cite{backer2014, lieb2004, nov2006}. When a single molecule fluoresces, its
-irradiance pattern on the detector is strongly dependent on the orientation of
-the emitting molecule. Backlund et al. \cite{backlund2014} have shown have shown
-that ignoring the orientation of fluorophores can bias position estimates, so
-the most accurate SMLM experiments must jointly estimate the position and
-orientation of each molecule. Some SMLM experiments use polarizers to estimate
-the orientation of single molecules more accurately [Backer DNA paper, other
-Moerner papers], and these works do not adopt the scalar or monopole
-approximations.
-
-A smaller community of microscopists is interested in measuring the orientation
-and position of ensembles of fluorophores \cite{mehta2016} [Forkey, Goldman,
-Moerner, Oldenbourg]. These techniques typically use polarized illumination or
-polarized detection to make multiple measurements of the same object. Current
-angular restoration techniques use a model of the dipole excitation and emission
-processes [Fourkas] to recover the orientation of fluorophores using pixel-wise
-arithmetic, but these techniques do not perform any spatial restoration so they
-do not use all of the available information.
+fluorophores, and all existing restoration techniques make either or both of the
+monopole and scalar approximations. As discussed above, the Gibson-Lanni model,
+the Born-Wolf model, and the Richards-Wolf model are approximate when applied to
+fluorescence microscopes because they only model monopole emitters.
+Deconvolution algorithms that use these models may make biased estimates of
+fluorophore concentrations since they ignore the dipole excitation and emission
+of fluorophores, but we will see that these effects are small when the sample
+contains many randomly oriented fluorophores within a resolvable volume or
+unconstrained rotating fluorophores.
+
+A small but growing group of microscopists is interested in measuring the
+orientation and position of ensembles of fluorophores \cite{vrabioiu2006,
+  mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}. These techniques
+typically use polarizers to make multiple measurements of the same object, then
+they use a model of the dipole excitation and emission processes
+\cite{fourkas2001} to recover the orientation of fluorophores using pixel-wise
+arithmetic. Although these studies do not adopt the scalar or monopole
+approximations for the angular part of the problem, they adopt both
+approximations when they consider the spatial part of the problem. Existing
+works either ignore the spatial reconstruction problem \cite{vrabioiu2006,
+  mattheyses2010, mehta2016, mcquilken2017} or assume that the spatial and
+angular reconstruction problems can be performed sequentially
+\cite{zhanghao2017}.
+
+The most precise experiments in the SMLM community do not adopt the scalar or
+monopole approximations. Although many works have applied dipole models with
+vector optics, fewer have considered the effects of rotational or spatial
+diffusion, and to our knowledge no works have considered both rotational and
+spatial diffusion together. We will see that the dipole transfer functions are
+useful tools for incorporating angular and spatial diffusion into SMLM
+simulations and reconstructions.
 
 In this work we place these three communities on a common theoretical footing.
-We begin in Section \ref{sec:theory} by formulating the imaging problem
+We begin in section \ref{sec:theory} by formulating the imaging problem
 mathematically. We start with an abstract description of fluorescence imaging
@@
 introduce transfer functions that will allow us to efficiently analyze
-spatio-angular microscopes. In Section \ref{sec:results} we use the mathematical
-tools we developed in Section \ref{sec:theory} to analyze and simulate a
-single-view epi-fluorescence microscope, and we demonstrate our model with four
-simple phantoms. Finally, in Section \ref{sec:discussion} we discuss the results
+spatio-angular microscopes. In section \ref{sec:results} we use the mathematical
+tools we developed in section \ref{sec:theory} to analyze and simulate a
+single-view fluorescence microscope, and we demonstrate our techniques with four
+simple phantoms. Finally, in section \ref{sec:discussion} we discuss the results
 and their broader implications.
@@
 We begin our analysis with the abstract Hilbert space formalism of Barrett and
-Myers \cite{barrett2004}. Our first task is to formulate the imaging process as
-a mapping between two Hilbert spaces $\mc{H}: \mbb{U} \rightarrow \mbb{V}$, where
-$\mbb{U}$ is a set than contains all possible objects, $\mbb{V}$ is a set that
-contains all possible datasets, and $\mc{H}$ is a model of the instrument that
-maps between these two spaces. We denote (possibly infinite-dimensional)
+Myers \cite[ch.~1.3]{barrett2004}. Our first task is to formulate
+the imaging process as a mapping between two Hilbert spaces
+$\mc{H}: \mbb{U} \rightarrow \mbb{V}$, where $\mbb{U}$ is a set that contains
+all possible objects, $\mbb{V}$ is a set that contains all (possibly
+noise-corrupted) datasets, and $\mc{H}$ is a model of the instrument that maps
+between these two spaces. We denote (possibly infinite-dimensional)
 Hilbert-space vectors in $\mbb{U}$ with $\mb{f}$, Hilbert-space vectors in
@@
 \end{align}
+Throughout this work we will use the letters $g$, $h$, and $f$ with varying
+fonts, capitalizations, and arguments to represent the data, the instrument, and
+the object, respectively.
 
@@
 will enable us to unify the analysis of spatio-angular fluorescence microscopes.
-In Section \ref{sec:monopole} we will demonstrate the formalism by examining a
+In section \ref{sec:monopole} we will demonstrate the formalism by examining a
 familiar monopole imaging model, and we will demonstrate the mapping between
-object and data space in two different bases. In Section \ref{sec:dipole} we
+object and data space in two different bases. In section \ref{sec:dipole} we
 will extend the monopole imaging model to dipoles and examine the mapping in
@@
 \textit{irradiance}---the power received by a surface per unit area at position
-$\rd'$. It may seem pedantic to emphasize that these representations are in a
-delta function basis, but we highlight this point to make it clear that the
-delta function basis is not special---we can choose a different basis at will.
+$\rd'$. Note that we have adopted a slightly unusual convention of using primes
+to denote unscaled coordinates. Later in this section we will introduce unprimed
+scaled coordinates that we will use throughout the rest of the
+paper.
 
 A reasonable starting point is to assume that the relationship between the
-object and the data is \textit{linear}---this is usually true in fluorescence
-microscopes since fluorophores emit incoherently, so a scaled sum of
+object and the data is \textit{linear}---this is true in many fluorescence
+microscopes because fluorophores emit incoherently, so a scaled sum of
 fluorophores will result in a scaled sum of the irradiance patterns created by
-the individual fluorophores. If the mapping is linear, we can write the
-irradiance as a weighted integral over a field of monopoles
+the individual fluorophores. Note that our assumption of linearity excludes
+cases where fluorophores interact (e.g. homoFRET) or saturate (e.g. non-linear
+fluorescence microscopy).
+
+If the mapping is linear, we can write the irradiance as a weighted integral
+over a field of monopoles
 \begin{align}
@@
 \end{align}
-where $h'(\rd{}', \ro{})$ is the irradiance at position $\rd'$ created by a
+where $h'(\rd', \ro{})$ is the irradiance at position $\rd'$ created by a
 point source at $\ro$.
@@
 sine condition guarantees that off-axis points are imaged without spherical
-aberration or coma \cite{mansuripur2009}, so the imaging system can be modeled
-within the field-of-view of the optical system as a magnifier with
+aberration or coma \cite[ch.~1]{mansuripur2009}, so the imaging system can
+be modeled within the field of view of the optical system as a magnifier with
 shift-invariant blur
@@
 We can simplify our analysis by changing coordinates and writing Eq.
-\ref{eq:nonconv} as a convolution \cite{barrett2004}. We define a demagnified
-detector coordinate $\rd = \rd'/m$ and a normalization factor that corresponds
-to the total power incident on the detector plane due to a point source
-$P_{\text{mono}} = \int_{\mbb{R}^2}d\mb{r}\,h'(m\mb{r})$ where
+\eqref{eq:nonconv} as a convolution \cite[ch.~7.2.7]{barrett2004}. We
+define a demagnified detector coordinate $\rd = \rd'/m$ and a normalization
+factor that corresponds to the total power incident on the detector plane due to
+a point source $P_{\text{mono}} = \int_{\mbb{R}^2}d\mb{r}\,h'(m\mb{r})$ where
 $\mb{r} = \rd - \ro$. We use these scaling factors to define the
@@
 \end{align}
-We will mostly be using scaled coordinates, so we have adopted a slightly
-unusual convention of using primes to denote unscaled coordinates.
 
@@
 The mapping between the object and the data in a linear shift-invariant imaging
-system takes a particularly simple form in a spatial harmonic basis. If we apply
-the Fourier convolution theorem to Eq. \ref{eq:lsi} we find that
+system takes a particularly simple form in a spatial harmonic (i.e. Fourier) basis. If we apply
+the Fourier convolution theorem to Eq. \eqref{eq:lsi} we find that
 \begin{align}
@@
 \end{align}
-The monopole point spread function is normalized and real, so we know
-that the monopole transfer function is normalized $H(0) = 1$ and
-conjugate symmetric $H(-\bv) = H^*(\bv)$ where $z^*$ denotes the complex
-conjugate of $z$.
-
-Notice that Eqs. \ref{eq:lsi} and \ref{eq:freq} are expressions of the same
+The monopole point spread function is normalized and real, so we know that the
+monopole transfer function is normalized, $H(0) = 1$, and conjugate symmetric,
+$H(-\bv) = H^*(\bv)$, where $z^*$ denotes the complex conjugate of $z$.
+
+Notice that Eqs. \eqref{eq:lsi} and \eqref{eq:freq} are expressions of the same
 mapping between object and data space in different bases. Figure
@@
 
-Since the monopole transfer function is given by the two-dimensional Fourier
-transform of the monopole point spread function
-\begin{align}
-  H(\bv) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r})\,\text{exp}[-2\pi i\mb{r}\cdot\bv],
-\end{align}
-we can plug in Eq. \ref{eq:absquarescalar} and use the autocorrelation theorem to
-rewrite the monopole transfer function as
+We can plug Eq. \eqref{eq:absquarescalar} into Eq. \eqref{eq:otf} and use the
+autocorrelation theorem to rewrite the monopole transfer function as
 \begin{align}
@@
 scale the field to find the monopole coherent transfer function, then (3) use
-the relationships in Figure \ref{fig:monopole-transfer-functions} to calculate
+the relationships in Fig. \ref{fig:monopole-transfer-functions} to calculate
 the other transfer functions.
@@
 because the dipoles can have different orientations. To represent the object we
-need to extend object space to $\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$
-where $\mbb{S}^2$ is the two-dimensional sphere (the usual sphere embedded in
-$\mbb{R}^3$).
+need to extend object space to
+$\mbb{U} = \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$---the set of square-integrable
+functions on the product space of a plane and a two-dimensional sphere (the
+usual sphere embedded in $\mbb{R}^3$). To visualize functions in object space we
+imagine a sphere at every point on a plane with a scalar value assigned to every
+point on each sphere.
 
 In a delta function basis the object can be represented by a function
-$f(\ro, \so)$ called the \textit{dipole density}---the number of dipoles at
-position $\ro{}$ per unit area oriented along $\so{}$ per unit solid angle.
-Similar to the monopole case, we model the mapping between the object and the
-irradiance in a delta function basis as an integral transform
-\begin{align}
-  g'(\rd') = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\, h'(\rd', \ro, \so)f(\ro, \so). 
+$f(\ro, \so)$ called the \textit{dipole density}---the number of dipoles per
+unit area and per unit solid angle at position $\ro{}$ and oriented along
+$\so{}$. Similar to the monopole case, we model the mapping between the object
+and the irradiance in a delta function basis as an integral transform
+\begin{align}
+  g'(\rd') = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\, h'(\rd', \ro, \so)f(\ro, \so),
 \end{align}
 where $h'(\rd', \ro, \so)$ is the irradiance at position $\rd'$ created by a
-point source at $\ro$ with orientation $\so$. If the optical system is aplanatic
-we can write the integral transform as
+point source at $\ro$ with orientation $\so$. If the optical system is
+aplanatic, we can write the integral transform as
 \begin{align}
@@
 \end{align}
-Eq. \ref{eq:odpsf} is a key result because it represents the mapping between
-object space and data space in a delta function basis. The integrals in
-\ref{eq:odpsf} would be extremely expensive to compute for an arbitrary object,
-but the integrals simplify to an efficient sum if the object consists of
-spatially fixed dipoles in a fixed orientation. In other words, Eq.
-\ref{eq:odpsf} is ideal for simulating and analyzing objects that are spatially
-and angularly sparse; e.g. single fluorophores that are rigidly attached to a
-structure .
+Equation \eqref{eq:odpsf} is a key result because it represents the mapping
+between object space and data space in a delta function basis. The integrals in
+Eq. \eqref{eq:odpsf} would be extremely expensive to compute for an arbitrary
+object, but the integrals simplify to an efficient sum if the object is
+spatially and angularly sparse. In other words, Eq. \eqref{eq:odpsf} is ideal for
+simulating and analyzing single fluorophores that are rigidly attached to an
+oriented structure.
 
@@
 
-\subsubsection{Spatial dipole transfer function}
+\subsubsection{Dipole spatial transfer function}
 We can make our first change of basis by applying the Fourier-convolution
-theorem to Eq. \ref{eq:odpsf} which yields
+theorem to Eq. \eqref{eq:odpsf}, which yields
 \begin{align}
@@
 \end{align}
-where we define the \textit{spatial dipole transfer function} as
-  \begin{align}
-  H(\bv, \so) &= \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \so)\, \text{exp}(-2\pi i\mb{r}\cdot\bv),
-  \end{align}
-  and the \textit{spatial dipole spectrum} as
+where we define the \textit{dipole spatial transfer function} as
+  \begin{align}
+  H(\bv, \so) &= \int_{\mbb{R}^2}d\mb{r}\, h(\mb{r}, \so)\, \text{exp}(-2\pi i\mb{r}\cdot\bv),\label{eq:dstf}
+  \end{align}
+  and the \textit{dipole spatial spectrum} as
   \begin{align}
@@
   Since the dipole point spread function is normalized and real, we know that
-  the spatial dipole transfer function is normalized
-  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \so) = 1$ and conjugate symmetric
+  the dipole spatial transfer function is normalized,
+  $\int_{\mbb{S}^2}d\mh{s}\, H(0, \so) = 1$, and conjugate symmetric,
   $H(-\bv, \so) = H^*(\bv, \so)$.
@@
   This basis is ideal for simulating and analyzing objects that are angularly
-  sparse and spatially dense; e.g. rod structures that contain fluorophores in a
-  fixed orientation.
+  sparse and spatially dense; e.g. rod-like structures that contain fluorophores
+  in a fixed orientation, or rotationally fixed fluorophores that are undergoing
+  spatial diffusion.
 
@@
 \subsubsection{Dipole angular transfer function}
-The spherical harmonics are another set of convenient basis functions that are
-play the same role as complex exponentials in spatial transfer functions---see
+The spherical harmonics are another set of convenient basis functions that play
+the same role as complex exponentials in spatial transfer functions---see
 Appendix \ref{sec:sph} for an introduction to the spherical harmonics. We can
 change basis from spherical delta functions to spherical harmonics by applying
-the generalized Plancharel theorem for spherical functions
+the generalized Plancherel theorem for spherical functions
 \begin{align}
@@
 and $Y_{\ell}^m(\mh{s})$ are the spherical harmonic functions defined in
-Appendix \ref{sec:sph}. Eq. \ref{eq:plan} expresses the fact that scalar
-products are invariant under a change of basis (see Eq. 3.78 of
-\cite{barrett2004}). The left-hand side of Eq. \ref{eq:plan} is the scalar
-product of $\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the
-right-hand side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a
-spherical harmonic function basis. Applying Eq. \ref{eq:plan} to Eq.
-\ref{eq:odpsf} yields
-\begin{align}
-  g(\rd) = \lmsum H_\ell^m(\rd - \ro)F_\ell^m(\ro), \label{eq:atf-form}
+Appendix \ref{sec:sph}. Equation \eqref{eq:plan} expresses the fact that scalar
+products are invariant under a change of basis \cite[Eq.~3.78]{barrett2004}.
+The left-hand side of Eq. \eqref{eq:plan} is the scalar product of
+$\mbb{L}_2(\mbb{S}^2)$ functions in a delta function basis and the right-hand
+side is the scalar product of $\mbb{L}_2(\mbb{S}^2)$ functions in a spherical
+harmonic function basis. Applying Eq. \eqref{eq:plan} to Eq. \eqref{eq:odpsf} yields
+\begin{align}
+  g(\rd) = \lmsum \int_{\mbb{R}^2}d\ro\, H_\ell^m(\rd - \ro)F_\ell^m(\ro), \label{eq:atf-form}
 \end{align}
@@
 Since the dipole point spread function is normalized and real, we know
-that the dipole angular transfer function is normalized
-$\int_{\mbb{R}^2}d\mb{r}\, H_0^0(\mb{r}) = 1$ and conjugate symmetric
+that the dipole angular transfer function is normalized,
+$\int_{\mbb{R}^2}d\mb{r}\, H_0^0(\mb{r}) = 1$, and conjugate symmetric,
 $H_\ell^{-m}(\mb{r}) = (-1)^mH_\ell^{m*}(\mb{r})$.
@@
 This basis is well suited for simulating and analyzing objects that are
-spatially sparse and angularly dense; e.g. rotating single fluorophores that are
-spatially fixed, or many fluorophores that are close together with varying
-orientations.
+spatially sparse and angularly dense; e.g. single fluorophores that are
+undergoing angular diffusion, or many fluorophores that are within a resolvable
+volume with varying orientations.
 
@@
 We can arrive at our final basis in two ways: by applying the generalized
-Plancharel theorem for spherical functions to Eq. \ref{eq:odotf} or by applying
-the Fourier convolution theorem to Eq. \ref{eq:atf-form}. We follow the
-second path and find that
+Plancherel theorem for spherical functions to Eq. \eqref{eq:odotf} or by applying
+the Fourier convolution theorem to Eq. \eqref{eq:atf-form}. We follow the
+first path and find that
 \begin{align}
@@
   Since the dipole point spread function is normalized and real, we know
-  that the dipole spatio-angular transfer function is normalized
-  $\msf{H}_0^0(0) = 1$ and conjugate symmetric
+  that the dipole spatio-angular transfer function is normalized,
+  $\msf{H}_0^0(0) = 1$, and conjugate symmetric,
   $\msf{H}_\ell^{-m}(-\bv) = (-1)^m\msf{H}_\ell^{m*}(\bv)$.
@@
   This basis is well suited for simulating and analyzing arbitrary samples
-  because it exploits the band limit of the imaging system. We will see this
+  because it exploits the band limit of the imaging system. We will see the
   advantage explicitly in Section \ref{sec:results} when we calculate a specific
   dipole spatio-angular transfer function and see that it has spatial and
-  angular band limits.
-
-  Figure \ref{fig:dipole-block} summarizes the relationship between the four
+  angular band limits. We note that most single molecules imaging experiments
+  are best described in this basis because of the effects of spatial and
+  rotational diffusion.
+
+  Figure \ref{fig:dipole-block} summarizes the relationships between the four
   bases that we can use to compute the image of a field of dipoles. We reiterate
@@
 coherent transfer function since the polarization of the field plays a
-significant role in dipole imaging, so the point spread function cannot be
-written as an absolute square of a scalar-valued function.
-
-Since the dipole spatial transfer function is the two-dimensional
-Fourier transform of the dipole point spread function
-\begin{align}
-  H(\bv) = \int_{\mbb{R}^2}d\mb{r}\,h(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\bv],
-\end{align}
-we can plug in Eq. \ref{eq:absquare2} and use the autocorrelation theorem to
-rewrite the spatial dipole transfer function as 
-\begin{align}
-  H(\bv) = \int_{\mbb{R}^2}d\taup\,\mb{C}(\taup, \so)\mb{C}^\dagger(\taup - \bv, \so), 
-\end{align}
-where we have introduced the \textit{dipole coherent transfer function}
-$\mb{C}(\taup, \so)$ as the two-dimensional Fourier transform of the dipole
-coherent spread function
-\begin{align}
-  \mb{C}(\taup, \so) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\taup].
-\end{align}
-Physically, the dipole coherent transfer function corresponds to the
-vector-valued electric field created by a dipole oriented along $\so$ in a
-Fourier plane of the detector with appropriate scaling. Similar to the monopole
-case, we can calculate the orientation-dependent fields in a Fourier plane of
-the detector, scale appropriately to find the dipole coherent transfer function,
-then use the relationships in Figure \ref{fig:transfer-functions} to calculate
-the other transfer functions.
+significant role in dipole imaging, so the dipole point spread function cannot
+be written as an absolute square of a scalar-valued function.
 
@@
     two-dimensional and spherical Fourier transforms---see center and right
-    columns. There are an additional pair of coherent transfer functions that
+    columns. There is an additional pair of coherent transfer functions that
     are useful for calculating the incoherent transfer functions---see left column.}
@@
  \end{figure}
+
+We can plug Eq. \eqref{eq:absquare2} into Eq. \eqref{eq:dstf} and use the
+autocorrelation theorem to rewrite the dipole spatial transfer function as
+\begin{align}
+  H(\bv, \so) = \int_{\mbb{R}^2}d\taup\,\mb{C}(\taup, \so)\mb{C}^\dagger(\taup - \bv, \so), 
+\end{align}
+where we have introduced the \textit{dipole coherent transfer function}
+$\mb{C}(\taup, \so)$ as the two-dimensional Fourier transform of the dipole
+coherent spread function
+\begin{align}
+  \mb{C}(\taup, \so) = \int_{\mbb{R}^2}d\mb{r}\, \mb{c}(\mb{r}, \so)\,\text{exp}[-2\pi i\mb{r}\cdot\taup].
+\end{align}
+Physically, the dipole coherent transfer function corresponds to the
+vector-valued electric field created by a dipole oriented along $\so$ in a
+Fourier plane of the detector with appropriate scaling. Similar to the monopole
+case, we can calculate the dipole-orientation-dependent fields in a Fourier plane of
+the detector, scale appropriately to find the dipole coherent transfer function,
+then use the relationships in Fig. \ref{fig:transfer-functions} to calculate
+the other transfer functions.
 
@@
 shift-invariant magnifier. Now we will be more specific and consider an
-aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an arbitrary
-first lens (the objective lens) and a \textit{paraxial second lens} (the tube
-lens) as shown in Figure \ref{fig:schematic}. A lens can be considered paraxial
-if the angle $\alpha$ between the optical axis of the lens and the marginal ray
-is small enough that $\sin\alpha \approx \alpha$. As a rule of thumb,
-non-paraxial effects only become significant when the numerical aperture of a
-lens exceeds 0.7 \cite{gu2000}, but this is only a rough guideline.
+aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an
+arbitrary first lens (the objective lens) and a \textit{paraxial second lens}
+(the tube lens) as shown in Fig. \ref{fig:schematic}. A lens can be considered
+paraxial if the angle $\alpha$ between the optical axis of the lens and the
+marginal ray is small enough that $\sin\alpha \approx \alpha$. As a rule of
+thumb, non-paraxial effects only become significant when the numerical aperture
+of a lens exceeds 0.7 \cite[ch.~6]{gu2000}, but this is only a rough
+guideline. Commercial microscopes with infinity-corrected objectives can almost
+always can be modeled by considering the tube lens as paraxial.
 
@@
    \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
-     paraxial tube lens. Since we have an aplanatic optical system we only need
-     to consider the image created by on-axis objects.}
+     paraxial tube lens. We are considering an aplanatic optical system, so we
+     only need to consider the image created by on-axis objects.}
    \label{fig:schematic}
@@
 We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
-the field immediately following the pupil plane created by an on-axis
-monopole where $\rp$ is an unscaled two-dimensional coordinate in the pupil
-plane. In this section we will relate the monopole pupil function to the
-transfer function we defined in Section \ref{sec:theory} by following a near
-variant of the derivation in Barrett and Myers Section 9.7 \cite{barrett2004}.
-
-Since monopoles emit scalar fields, the monpole pupil function is a
+the field immediately following the pupil plane created by an on-axis monopole,
+where $\rp$ is an unscaled two-dimensional coordinate in the pupil plane. In
+this section we will relate the monopole pupil function to the transfer function
+we defined in section \ref{sec:theory} by adapting the treatment in Barrett and
+Myers \cite[ch.~9.7]{barrett2004}.
+
+Since monopoles emit scalar fields, the monopole pupil function is a
 scalar-valued function. The optical system is aplanatic, so we can write the
-field created at a point in the aperture $\rp$ by a monopole at position $\ro$
-as
+field created at a point in the pupil plane $\rp$ by a monopole at position
+$\ro$ as
 \begin{align}
@@
 \end{align}
-Eq. \ref{eq:pupil} is a restatement of the aplanatic condition for a $4f$
-optical system---the field in the aperture plane can be written as the pupil
+Equation \eqref{eq:pupil} is a restatement of the aplanatic condition for a $4f$
+optical system---the fields in the pupil plane can be written as the pupil
 function multiplied by a linear phase factor that encodes the position of the
@@
 Since the second lens is paraxial, we can model the relationship between the
-field in the aperture plane and the field on the detector with a scaled Fourier
-transform \cite{goodman1996}
+field in the pupil plane and the field on the detector with a scaled Fourier
+transform \cite{goodman1996, axelrod2012, backer2014}:
 \begin{align}
@@
 \end{align}
+
 If we define $P(\taup)$ as the two-dimensional Fourier transform of the pupil function
-then we can rewrite Eq. \ref{eq:detectorfourier} as
+then we can rewrite Eq. \eqref{eq:detectorfourier} as
 \begin{align}
@@
 If we demagnify the coordinates with $\rd = \rd'/m$ and demagnify the irradiance
-with $h(\rd - \ro) \propto h'(m[\rd - \ro])$ we find that the monopole point spread
-function is related to the Fourier transform of the monopole pupil function by
+with $h(\rd - \ro) \propto h'(m[\rd - \ro])$, we find that the monopole point
+spread function is related to the Fourier transform of the monopole pupil
+function by
 \begin{align}
@@
 \end{align}
-The monopole coherent spread function is the absolute square of the monopole point spread function so
+The monopole point spread function is the absolute square of the monopole
+coherent spread function so
 \begin{align}
@@
 \end{align}
-Equation \ref{eq:monopupil0} is the key result of this section---the monopole
+Equation \eqref{eq:monopupil0} is the key result of this section---the monopole
 coherent transfer function is a scaled monopole pupil function.
@@
 Note that the Fourier transform of a vector field is the Fourier transform of
-its scalar-valued orthogonal components, so Eq. \ref{eq:detectorfourier2}
-specifies two two-dimensional Fourier transforms. We follow the same
+its scalar-valued orthogonal components, so Eq. \eqref{eq:detectorfourier2}
+specifies three two-dimensional Fourier transforms. We follow the same
 manipulations as the previous section and find that the dipole coherent transfer
@@
 \end{align}
+
+We have restricted our analysis to paraxial tube lenses, but non-paraxial tube
+lenses (or a non-infinity-corrected objective) can be modeled with vector-valued
+three-dimensional pupil functions \cite{sheppard1994, gu2000, arnison2002,
+  foreman2011-2}.
 
@@
 
-In Appendix \ref{sec:special} we derive the following two-dimensional Fourier
-transform relationships between the jinc functions and the weighted rectangle
-functions
+Although the rectangle and jinc functions are defined in one dimension, we will
+usually apply them in two dimensions. In Appendix \ref{sec:special} we derive
+the following two-dimensional Fourier transform relationships between the jinc
+functions and the weighted rectangle functions
 \begin{align}
@@
   \end{align}
-where the entries inside the curly braces are to be taken one at a time.
+  where the entries inside the curly braces are to be taken one at a time and
+  $\{r, \phi_r\}/\{\nu, \phi_\nu\}$ are conjugate sets of polar coordinates.
 
@@
 
-In Appendix \ref{sec:special} we show that the zero and first order chat
+In Appendix \ref{sec:special} we show that the zeroth- and first-order chat
 functions can be written in closed form as
@@
 the rectangle function models the aperture stop of the objective. Applying Eq.
-\ref{eq:monopupil0} and collecting constants we find that the coherent monopole
+\eqref{eq:monopupil0} and collecting constants we find that the coherent monopole
 transfer function is
@@
 aperture, but for our initial analysis we restrict ourselves to the paraxial
-regime. We retain only zero and first order radial terms to find that  
+regime. We drop second- and higher-order radial terms to find that
 \begin{align}
@@
 The monopole point spread function is the (normalized) absolute square of the
-monopole coherent spread function so,
-\begin{align}
-  h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r)
+monopole coherent spread function so
+\begin{align}
+  h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r),
 \end{align}
@@
    \mb{p}(\rp, \so) \propto
+   % \begin{bmatrix}
+   %   \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\cos\phi_p\\
+   %   \tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\sin\phi_p\\
+   %   0&0&0\\     
+   % \end{bmatrix}
    \begin{bmatrix}
-     \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\cos\phi_p\\
-     \tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\sin\phi_p\\
+     \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)c(\phi_p)\\
+     \tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)s(\phi_p)\\
      0&0&0\\     
@@
    \end{bmatrix}
-   \Pi\left(\frac{r_p}{2f_o\sin\alpha}\right). 
- \end{align}
- where
+   \Pi\left(\frac{r_p}{2f_os(\alpha)}\right),
+ \end{align}
+ where $c(x)$ and $s(x)$ are shorthand for $\cos(x)$ and $\sin(x)$,
+ $\{s_x, s_y, s_z\}$ are the Cartesian components of $\so$ when $\mh{z}$ is
+ aligned with the optical axis, and
  \begin{alignat}{4}
@@
  vector-valued to model the complete electric field in the pupil plane. The
- fields in the aperture plane have a negligible $\mh{z}$ component which is a
- consequence of our assumption that the tube lens is paraxial.
-
- Scaling the dipole pupil function using Eq. \ref{eq:monopupildip} yields the
+ fields in the pupil plane have a negligible $\mh{z}$ component which is a
+ consequence of our assumption that the tube lens is paraxial---modeling a
+ non-paraxial tube lens would require a three-dimensional vector-valued pupil
+ function \cite{sheppard1994, gu2000, arnison2002, foreman2011-2}.
+
+ Scaling the dipole pupil function using Eq. \eqref{eq:monopupildip} yields the
  dipole coherent transfer function
@@
    \begin{bmatrix}
-     \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos\phi_{\tau}\\
-     \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin\phi_{\tau}\\
+     \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(\phi_{\tau})\\
+     \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(\phi_{\tau})\\
      0&0&0\\     
    \end{bmatrix}
+   % \begin{bmatrix}
+   %   \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos\phi_{\tau}\\
+   %   \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin\phi_{\tau}\\
+   %   0&0&0\\     
+   % \end{bmatrix}
    \begin{bmatrix}
@@
  \end{align}
- We restrict our analysis to the paraxial regime by dropping all but the zero
- and first order radial terms to find that
+ We restrict our analysis to the paraxial regime by dropping second- and
+ higher-order radial terms to find that
  \begin{align}
@@
  \end{align}
- Under the paraxial approximation the transverse component of the dipoles
- ($s_x, s_y$) creates purely transverse fields in the pupil plane and the axial
- component of the dipole ($s_z$) creates purely radial fields in the pupil
+ Under the paraxial approximation the transverse components of the dipole
+ \{$s_x, s_y$\} create purely transverse fields in the pupil plane and the axial
+ component of the dipole \{$s_z$\} creates purely radial fields in the pupil
  plane. The paraxial approximation may seem crude compared to Backer and
@@
  polarized fluorescence microscopy make stronger approximations than ours. For
- example, Fourkas only considers the total irradiance in the back focal plane
- while ignoring the propagation of fields to the detector \cite{fourkas2001}.
+ example, Fourkas only considers the total irradiance in the pupil plane while
+ ignoring the propagation of fields to the detector \cite{fourkas2001}.
 
  The dipole coherent spread function is the inverse Fourier transform of the
- dipole coherent transfer function. Applying Eq. \ref{eq:jincrect2} in reverse
+ dipole coherent transfer function. Applying Eq. \eqref{eq:jincrect2} in reverse
  yields
@@
   \subsubsection{Paraxial dipole point spread function}
-  The dipole point spread function is the (normalized) absolute square of
+  The dipole point spread function is the (normalized) absolute square of the
 coherent dipole spread function
@@
 
- Notice that the transverse and radial fields are out of phase on the detector,
- so the total irradiance is the sum of the contributions from the transverse and
- radial components. In Figure \ref{fig:hdet} we plot the dipole point spread
- function for several dipole orientations dipole orientations and numerical
- apertures, and in Figure \ref{fig:microscopefig} we compare the monopole point
- spread function to the dipole point spread function. The paraxial monopole and
- dipole models are equivalent when the sample consists of only transverse
- dipoles which is clear if we notice that Eq. \ref{eq:paradpsf} reduces to an
- Airy disk when $\vartheta = \pi/2$.
+As discussed above, the transverse and radial fields are out of phase on the
+detector, so the total irradiance is the sum of the contributions from the
+transverse and radial components. In Fig. \ref{fig:hdet} we plot the dipole
+point spread function for several dipole orientations and numerical apertures,
+and in Fig. \ref{fig:microscopefig} we compare the monopole point spread
+function to the dipole point spread function. The paraxial monopole and dipole
+models are only equivalent when the sample consists of transverse dipoles which
+is clear if we notice that Eq. \eqref{eq:paradpsf} reduces to an Airy disk when
+$\vartheta = \pi/2$---see Novotny and Hecht for a similar observation
+\cite[ch.~4]{nov2006}.
 
@@
      contribution of axial dipoles increases with the numerical aperture (see
-     \textcolor{red}{\textbf{red}} lines from left to right).}
+     \textcolor{red}{\textbf{red}} lines from left to right). Additionally, we
+     plot the monopole point spread function (\textcolor{green}{\textbf{green}})
+     and observe that the paraxial monopole and dipole models are identical for
+     transverse dipoles.}
    \label{fig:hdet}
@@
      is filled with a uniform vector field. c) An axial dipole radiator creates
-     a radial electric field pattern in the back focal plane which creates a
-     $\text{jinc}_1^2(r)$ (or higher-order Airy disk) on the detector. d)
-     Dipoles that are not transverse or axial still create radially symmetric
-     irradiance patterns under the paraxial approximation. Fields from
-     transverse dipoles are real and even while fields from axial dipoles are
-     real and odd which causes a relative $\pi/2$ phase shift for the fields on
-     the detector. This phase shift means that the fields from transverse and
-     axial components of the dipole do not interfere, which causes radially
-     symmetric irradiance patterns.}
+     a radial electric field pattern in the back focal plane that creates a
+     $\text{jinc}_1^2(r)$ pattern on the detector. d) Dipoles that are not
+     transverse or axial still create radially symmetric irradiance patterns
+     under the paraxial approximation. Fields from transverse dipoles are real
+     and even while fields from axial dipoles are real and odd, which causes a
+     relative $\pi/2$ phase shift for the fields on the detector. This phase
+     shift means that the fields from transverse and axial components of the
+     dipole do not interfere, which causes radially symmetric irradiance
+     patterns.}
    \label{fig:microscopefig}
@@
  To demonstrate the paraxial dipole point spread function we simulate a set of
- equally spaced dipoles with varying orientation
+ equally spaced dipoles with varying orientation:
  \begin{align}
@@
  coordinates are expressed in $\mu$m. To find the irradiance pattern created by
- the phantom Eq. \ref{eq:phantom1} we plug it into Eq. \ref{eq:odpsf} and use
+ the phantom we plug Eq. \eqref{eq:phantom1} into Eq. \eqref{eq:odpsf} and use
  the sifting property to find that
@@
  \end{align}
- In Figure \ref{fig:ph1} we plot the phantom and scaled irradiance for an
- imaging system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and
- $n_o = 1.33$. We sample and plot the scaled irradiance at $20\times$ the
- Nyquist rate $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free
- of aliasing. The output demonstrates that the irradiance pattern depends on the
- dipole inclination, but not its azimuth.
+ In Fig. \ref{fig:ph1} we plot the phantom and scaled irradiance for an imaging
+ system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$.
+ We sample and plot the scaled irradiance at $20\times$ the Nyquist rate,
+ $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free of aliasing.
+ The output demonstrates that the irradiance pattern depends on the dipole
+ inclination, but not its azimuth.
 
@@
 coherent transfer function). Applying the Fourier transform to Eq.
-\ref{eq:paradpsf} we find that
+\eqref{eq:paradpsf} we find that
   \begin{align}
@@
   \end{align}
-  In Figure \ref{fig:odotf} we plot the dipole spatial transfer function for
-  several dipole orientations dipole orientations and numerical apertures. We
-  find that the dipole spatial transfer function is negative for axial dipoles
-  at high spatial frequencies, especially for larger numerical apertures. The
-  negative spatial transfer corresponds to a contrast inversion for
-  high-frequency patterns of axial dipoles because the irradiance minimum
-  corresponds to the position of the dipole.
+In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
+several dipole orientations and numerical apertures. We find that the dipole
+spatial transfer function is negative for axial dipoles at high spatial
+frequencies, especially for larger numerical apertures. The negative dipole
+spatial transfer corresponds to a contrast inversion for high-frequency
+patterns of axial dipoles because the irradiance minimum corresponds to the
+position of the dipole.
 
@@
      pattern where the minimum irradiance corresponds to the peak of the axial
-     dipole density.}
+     dipole density. Additionally, we plot the monopole transfer function
+     (\textcolor{green}{\textbf{green}}) and observe that the paraxial monopole
+     and dipole models are identical for transverse dipoles.}
    \label{fig:odotf}
@@
 
- To demonstrate the spatial dipole transfer function we simulate a set of
+ To demonstrate the dipole spatial transfer function we simulate a set of
  equally spaced disks with varying diameter containing fluorophores with varying
@@
  \begin{align}
-   f_{\text{(ph2)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
+   f_{(ph2)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
  \end{align}
@@
  we have scaled the disks so that the total number of fluorophores in each disk
- is constant.
+ is constant. Also notice that the disk can model a spatial distribution of many
+ fluorophores or a single molecule undergoing spatial diffusion within a well.
 
@@
  \begin{align}
-   g_{\text{(ph2)}}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{\text{(ph2)}}(r_x, r_y, \vartheta_j)\right\}\right\}.
- \end{align}
-
- In Figure \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
+   g_{(ph2)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{(ph2)}(r_x, r_y, \vartheta_j)\right\}\right\}.
+ \end{align}
+
+ In Fig. \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
  imaging parameters as the previous section. The small disks create irradiance
@@
 
-In Figure \ref{fig:atf} we plot the dipole angular transfer function for both
+In Fig. \ref{fig:atf} we plot the dipole angular transfer function for both
 spherical harmonic terms and several numerical apertures. Note that the dipole
-angular transfer function can be negative because the spherical harmonics
-contain negative values. The $\ell=0$ term shows that angularly uniform
-distributions of dipole create spatial irradiance patterns that are nearly
-identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
-because of the large contribution of the transverse negative dipoles in the
+angular transfer function can be negative because the spherical harmonics can
+take negative values. The $\ell=0$ term shows that angularly uniform
+distributions of dipoles create spatial irradiance patterns that are similar but
+not identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
+because of the large contribution of the transverse negative values in the
 $Y_2^0$ spherical harmonic.
-
- % The degree $\ell$ and order $m$ of the non-zero terms in the angular dipole
- % transfer function . First, the spatio-angular point spread function is symmetric
- % under inversion of the dipole moment. This symmetry is maintained in the
- % angular transfer function since all of the non-zero terms have an even degree
- % $\ell=0, 2$, and the corresponding spherical harmonics $Y_0^0(\so)$,
- % $Y_2^0(\so)$ are symmetric under inversion. Second, we showed that under the
- % paraxial approximation our kernel is rotationally symmetric which allows us to
- % write the kernel as a function of $r$ instead of $\mb{r}$. This symmetry is
- % maintained in the angular dipole transfer function since all of the non-zero
- % terms have order $m=0$. Finally, the dipole point spread function consists of
- % degree-2 trigonometric polynomials which implies that the dipole angular
- % transfer function will only contain $\ell=0, 2$ terms.
 
@@
      $\ell$, and $\text{NA}/n_o$. Angularly uniform distributions of dipoles
-     $\ell=0$ generate a spatial pattern that is nearly identical to an Airy
-     disk. $\ell=2$ distributions have a negative response because
-     $Y_2^0(\mh{s})$ is negative for transverse directions. As the numerical
-     aperture increases, the relative contribution of positive axial dipoles in
-     the $\ell=2$ distribution increases.}
+     $\ell=0$ generate a spatial pattern that is similar but not identical to
+     the Airy disk created by a monopole (\textcolor{green}{\textbf{green}}),
+     and this discrepancy increases with the numerical aperture. $\ell=2$
+     distributions have a negative response because $Y_2^0(\mh{s})$ is negative
+     for transverse directions. As the numerical aperture increases, the
+     relative contribution of positive axial dipoles in the $\ell=2$
+     distribution increases.}
    \label{fig:atf}
@@
  \begin{align}
-   f_{\text{(ph3)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
+   f_{(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
  \end{align}
@@
  \begin{align}
-   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{2\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right),
+   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right)
  \end{align}
@@
  cone reduces to a single direction, and when $\Delta = \pi/2$ the angular
- double cone reduces to an angularly uniform distribution.
+ double cone reduces to an angularly uniform distribution. Also notice that the
+ double cone can model angular diffusion or the angular distribution of many
+ fluorophores within a resolvable volume.
 
@@
  \begin{align}
-   F^{m}_{\ell,\text{(ph3)}}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
+   F^{m}_{\ell,(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
  \end{align}
@@
  To find the irradiance we plug the dipole angular spectrum into Eq.
- \ref{eq:atf-form} and use the sifting property we find that
- \begin{align}
-   g_{\text{(ph3)}}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
- \end{align}
-
- In Figure \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
+ \eqref{eq:atf-form} and use the sifting property to find that
+ \begin{align}
+   g_{(ph3)}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
+ \end{align}
+
+ In Fig. \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
  imaging parameters as the previous sections. For small cone angles the
@@
 
- In Figure \ref{fig:dsatf} we plot the dipole spatio-angular transfer function
- for both spherical harmonic terms and several numerical apertures. The $\ell=0$
- term shows that angularly uniform distributions of dipole create spatial
- irradiance patterns that are nearly identical to the Airy disk, with high
- frequencies increasingly suppressed as the numerical aperture increases. The
- $\ell=2$ term shows a negative pattern because of the large contribution of the
- transverse negative dipoles in the $Y_2^0$ spherical harmonic, and as the
- numerical aperture increases the relative contribution of the positive axial
- dipoles increases and the $\ell=2$ term becomes less negative.
+ In Fig. \ref{fig:dsatf} we plot the dipole spatio-angular transfer function for
+ both spherical harmonic terms and several numerical apertures. The $\ell=0$
+ term shows that an angularly uniform distribution of dipoles has a transfer
+ function that is similar but not identical to the monopole transfer function
+ with high frequencies increasingly suppressed as the numerical aperture
+ increases. The $\ell=2$ term shows a negative pattern because of the large
+ contribution of the transverse negative values in the $Y_2^0$ spherical
+ harmonic. As the numerical aperture increases the relative contribution of the
+ positive axial values increases and the $\ell=2$ term becomes less negative.
 
@@
      aperture increases, the relative contribution of axial dipoles increases
-     and the $\ell=2$ component becomes less negative.}
+     and the $\ell=2$ component becomes less negative. Additionally, we plot the
+     monopole transfer function (\textcolor{green}{\textbf{green}}) and observe
+     that the $\ell=0$ term is similar but not identical to the monopole
+     transfer function, and this discrepancy increases with the numerical aperture.}
    \label{fig:dsatf}
@@
  \begin{align}
-   f_{\text{(ph4)}}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
+   f_{(ph4)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
  \end{align}
@@
   \begin{align}
-   \mathsf{F}_{\ell,\text{(ph4)}}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
-  \end{align}
-  We can plug the dipole spatio-angular spectrum into Eq. \ref{eq:saft} to find
+   \mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
+  \end{align}
+  We can plug the dipole spatio-angular spectrum into Eq. \eqref{eq:saft} to find
   the scaled irradiance as 
   \begin{align}
-   g_{\text{(ph4)}}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,\text{(ph4)}}^m(\nu_x, \nu_y)\right\}.
-  \end{align}
-
-  In Figure \ref{fig:ph4} we plot the phantom and scaled irradiance with the
+   g_{(ph4)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y)\right\}.
+  \end{align}
+
+  In Fig. \ref{fig:ph4} we plot the phantom and scaled irradiance with the
   same imaging parameters as the previous sections. Small cone angles and small
@@
 \section{Discussion}\label{sec:discussion}
-\subsection{Reconstructions}
-% Since the dipole spatio-angular transfer function effectively contains it is
-% tempting to conclude that fluorescence microscopes pass three times as much
-% information about the dipoles as monopoles. This is not true. The microscope
-% still only measures a single member of $\mbb{L}_2(\mbb{R}^2)$, so at best we can
-% recover the same amount of information about the object. In other words, we know
-% immediately that the microscope is a rank-1 operator since it only measures one
-% continuous function.
-\begin{itemize}
-\item Very ill-posed reconstruction problem by dimensionality.
-\item Better-posed reconstruction problem by adding polarized illumination/detection
-  formulated as $\mc{H}: \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3\times\mbb{S}^1)$ and/or multiple views $\mc{H}: \mbb{L}_2(\mbb{R}^2\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^2\times\mbb{S}^1)^V$.
-\item Mention SVD for future papers
-\end{itemize}
-
-% TODO Make clear that a later paper will include a full discussion of SVD
-% to find the object space singular functions that span the measurement space of
-% the instrument.
+\subsection{When are dipole transfer functions necessary?}
+Model mismatch can lead to biased estimates of the position and orientation of
+fluorophores, so the most precise fluorescence microscopy experiments will
+always use dipole transfer functions over monopole transfer functions. The only
+case when the dipole and monopole transfer functions match exactly is when the
+dipoles are completely constrained to the transverse plane of a paraxial imaging
+system.
+
+However, in many practical situations noise will mask the effects of vector
+optics and dipoles. If the fluorophores are rotationally unconstrained or there
+are many randomly oriented fluorophores in a resolvable volume---common
+situations in biological applications---then the effects of vector optics and
+dipoles will be masked by noise in all but the highest SNR regimes.
+
+The dipole transfer functions are most broadly useful when the sample contains
+fluorophores that are rotationally constrained. As rotational constraints
+increase, the effects of vector optics and dipoles will become apparent in lower
+SNR regimes.
 
@@
 for functions on the sphere, but there are other basis functions that can be
-advantageous in some cases. Backer and [TODO Brasselet, others] have used
-the second moments as basis functions for the sphere because they arise
-naturally when computing the dipole point spread function. Mathematically,
-Backer and Moerner \cite{backer2014} use an alternative to the dipole angular
-transfer function that uses the second moments as basis functions so their
-forward model becomes
-\begin{align}
-  g(\rd) = \sum_{j=1}^6 H_j(\rd - \ro)F_j(\ro),
+advantageous in some cases. Several works \cite{aguet2009, backer2014,
+  brasselet2011, zhang2018, zhang2018-2} have used the second moments as basis
+functions for the sphere because they arise naturally when computing the dipole
+point spread function. These works use an alternative to the dipole angular
+transfer function that uses the second moments as basis functions so the forward
+model can be written as
+\begin{align}
+  g(\rd) = \sum_{j=1}^6 \int_{\mbb{R}^2}d\ro\, H_j(\rd - \ro)F_j(\ro),
 \end{align}
@@
 and $Z_j(\mh{s}) = \{s_x^2, s_y^2, s_z^2, s_xs_y, s_ys_z, s_xs_z\}$ are the
-second moments. This formulation is similar to the angular transfer function
-approach because it exploits the spatial sparsity of sample, but it does not
-require a cumbersome expansion of the dipole point spread function onto
-spherical harmonics.
+second moments. This formulation is similar to the dipole angular transfer
+function approach because it can exploit the spatial sparsity of the sample, but
+it does not require a cumbersome expansion of the dipole point spread function
+onto spherical harmonics.
 
@@
 (or higher) moments, but these are completely new basis functions. Second, the
-spherical harmonics are orthonormal which will allow us to easily deploy
-invaluable tools from linear algebra---linear subspaces, rank, decompositions,
-etc.--- to analyze and compare microscope designs. Finally, using the spherical
-harmonics provides access to a set of fast algorithms. The naive expansion of an
-arbitrary discretized $N$ point spherical function onto spherical harmonics (or
-second moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering
-work by Driscoll and Healy [cite] showed that the forward discrete fast
+spherical harmonics are orthonormal which will allow us to deploy invaluable
+tools from linear algebra---linear subspaces, rank, decompositions, etc.--- to
+analyze and compare microscope designs. Finally, using the spherical harmonics
+provides access to a set of fast algorithms. The naive expansion of an arbitrary
+discretized $N$ point spherical function onto spherical harmonics (or second
+moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering work
+by Driscoll and Healy \cite{driscoll1994} showed that the forward discrete fast
 spherical harmonic transform can be computed with a $\mc{O}(N(\log N)^2)$
@@
 
-TODO: Cite Tournier/Descoteux for an easy change of basis between spherical
-harmonics and second moments
+Zhenghao et. al. \cite{zhanghao2017} have used the circular harmonics to model
+the orientation of dipoles. The circular harmonics are complete and orthogonal,
+but they artificially restrict the angular reconstruction to the transverse
+plane of the microscope---a rare situation in real experiments.
+
+The diffusion magnetic resonance imaging community uses both the second moments
+(or second-order tensor) basis functions \cite{basser1994} and the spherical
+harmonic basis functions \cite{tournier2004}. Descoteaux et. al. have provided
+an explicit transformation matrix to convert between these basis functions
+\cite{descoteaux2006}.
 
 \subsection{What determines the angular bandwidth?}
-Spatial imaging systems have a spatial bandwidth which characterizes is the
-highest spatial frequency that the system can image. Similarly, angular imaging
-systems have an angular bandwidth that characterizes the highest angular
-frequency, but in the angular case there are two different types of angular
-bandwidths that we call $ell$ and $m$ bandwidths. The $\ell$-bandwidth can be
-interpreted in a similar way to the spatial bandwidth---it characterizes the
-smallest angular features that the imaging system can measure. The $m$-bandwidth
-does not have a direct analog in the spatial domain---it characterizes the
-angular uniformity of the imaging system. If the $\ell$ and $m$ bandwidths are
-equal then the imaging system can be said to be $\textit{rotation invariant}$.
+Spatial imaging systems have a spatial bandwidth that characterizes the highest
+spatial frequency that the system can image. Similarly, angular imaging systems
+have an angular bandwidth that characterizes the highest angular frequency that
+the system can image, but in the angular case there are two different types of
+angular bandwidths that we call the $\ell$- and $m$-bandwidth. The $\ell$-bandwidth
+can be interpreted in a similar way to the spatial bandwidth---it characterizes
+the smallest angular features that the imaging system can measure. The
+$m$-bandwidth does not have a direct analog in the spatial domain---it
+characterizes the angular uniformity of the imaging system. If the $\ell$- and
+$m$-bandwidths are equal then the imaging system can be said to have an 
+$\textit{isotropic angular bandwidth}$.
 
@@
 
-The microscope we considered in this work has an $ell$ bandwidth of $\ell = 2$
-and an $m$ bandwidth of $m_c = 0$, so it is not a rotation invariant imaging
-system. In future work we will consider several approaches to improving the
+The microscope we considered in this work has an $\ell$-bandwidth of $\ell_c = 2$
+and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic angular
+bandwidth. In future work we will consider several approaches to improving the
 angular bandwidths in detail, but we briefly mention that non-paraxial
 microscopes, microscopes with polarizers on the illumination or detection paths,
-and multiview microscopes all have higher angular bandwidths that the microscope
+and multiview microscopes all have higher angular bandwidths than the microscope
 considered here.
 
-The angular bandwidth is also sample dependent. Even though they are just a
-model, monopoles emit light isotropically so they have an $\ell$ bandwidth of 1,
-while dipoles have an $\ell$ bandwidth of 2, and higher-order excitation and
+The angular bandwidth is also sample dependent. Monopoles emit light
+isotropically so they have an $\ell$-bandwidth of $\ell_c = 0$, while dipoles
+have an $\ell$-bandwidth of $\ell_c = 2$, and higher-order excitation and
 detection moments will have even higher bandwidths. Multi-photon excitation and
-other non-linear methods can also increase the $\ell$ bandwidth.
+other non-linear methods can also increase the $\ell$-bandwidth
+\cite{brasselet2011}.
 
 \subsection{Towards more realistic models}
-The theoretical model we presented in this work is an extreme simplification of a
-real microscope. We have ignored the effects of thick samples, refractive-index
-mismatch, aberration, scattering, rotation of fluorophores, finite fluorescence
+The theoretical model we presented in this work is an extreme simplification of
+a real microscope. We have ignored the effects of thick samples,
+refractive-index mismatch, aberration, scattering, finite fluorescence
 lifetimes, and interactions between fluorophores among others. Because of this
@@
 
-TODO: Discuss/plan future papers. SVD? Defocus/3D imaging:
-$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2) \rightarrow \mbb{L}_2(\mbb{R}^3)$.
-
-TODO: Mention and cite rotating dipoles like Lew (model start point, rotation, end point):
-$\mc{H}: \mbb{L}_2(\mbb{R}^3\times\mbb{S}^2\times\mbb{SO}^3\times\mbb{S}^2) \rightarrow \mbb{V}$.
-
-TODO: Cite connection between dipole pupil and Jones pupil. We can use the
-Jones/dipole pupil as a way to extend our model in a straightforward way. Add
-phase aberration (like the Gibson-Lanni model), polarization aberrations,
-amplitude masks, phase masks, etc.
-
-TODO: Cite Piestun Green's tensor engineering.
+The dipole pupil function provides the simplest way to create more realistic
+models from the simple model in this paper. Phase aberrations can be added to
+the dipole pupil function with Zernike polynomials, and refractive index
+boundaries can be modeled by applying the work of Gibson and Lanni to the dipole
+pupil function \cite{gibson89}. These additions will model phase aberrations,
+but modeling polarization aberrations will also be necessary, and we anticipate
+that vector Zernike polynomials and the Jones pupil \cite{zhao2007, xu2015,
+  chipman1989} will be essential tools for modeling dipole imaging systems. We
+plan to use the dipole pupil function to include the effects of non-paraxial
+objectives, polarizers, and defocus in future papers of this series.
+
+The dipole pupil function also provides an enormous set of design opportunities.
+The dipole imaging problem may benefit from spatially varying diattenuating and
+birefrigent masks---a much larger set of possibilities than the well-explored
+design space of amplitude and phase masks. The dipole pupil function is a step
+towards Green's tensor engineering \cite{agrawal2012}, and the dipole transfer
+functions provide a strong framework for evaluating dipole imaging designs.
+
+In the simple case considered here we focused on the emission path of the
+microscope, but the excitation path is equally important. Complete models will
+need to consider the spatio-angular dependence of excitation. Zhenghao et. al.
+\cite{zhanghao2017} have taken steps in this direction by considering polarized
+structured illumination microscopy. Rotational dynamics and the fluorescence
+lifetime are also important to consider when incorporating models of the
+excitation process \cite{lew2013, zhang2018, zhang2018-2}.
+
+\subsection{Towards spatio-angular reconstructions}
+We have focused on modeling the mapping between the object and the data in this
+paper, but ultimately we are interested in reconstructing the object from the
+data. Applying the monopole approximation simplifies the reconstruction problem
+because both object and data space are $\mbb{L}_2(\mbb{R}^2)$, so we can
+directly apply regularized inverse filters and maximum likelihood methods. The
+dipole model expands object space to $\mbb{L}_2(\mbb{R}^2\times \mbb{S}^2)$, so
+the inverse problem becomes much more challenging. In future work we will use
+the singular value decomposition to find inverse filters, and we will consider
+using polarizers and multiple views to increase the size of data space.
 
 \section{Conclusion}
-Most models of fluorescence microscopes use a monopole model to describe the
-object and the scalar approximation to model the imaging system. A more complete
-description of any fluorescence microscope requires a dipole model of the object
-and vector optics to model the propagation of light through the microscope. We
-developed several transfer functions that simplify the mapping between the
-dipole density and the irradiance pattern on the detector, and we demonstrated
-these transfer functions by efficiently simulating a paraxial fluorescence
-microscope.
+Many models of fluorescence microscopes use the monopole and scalar
+approximations, and complete models need to consider dipole and vector optics
+effects. We have introduced several transfer functions that simplify the mapping
+between the dipole density and the irradiance pattern on the detector, and we
+demonstrated these transfer functions by efficiently simulating a paraxial
+fluorescence microscope. We found that the monopole and scalar approximations
+are good approximations when the sample consists of unconstrained rotating
+fluorophores or many randomly oriented fluorophores within a resolvable volume.
+We also found that dipole and vector optics effects become larger as rotational
+order increases, and in these cases the dipole transfer functions become valuable
+tools.
+
+\section*{Funding}
+National Institute of Health (NIH) (R01GM114274, R01EB017293).
+
+\section*{Acknowledgments}
+We thank Kyle Myers, Harrison Barrett, Scott Carney, Luke Pfister, Jerome Mertz,
+Mikael Backlund, Matthew Lew, Hari Shroff, Min Guo, Yicong Wu, Shalin Mehta,
+Abhishek Kumar, Peter Basser, Gordon Wetzstein, Hayato Ikoma, Laura Waller, Ren
+Ng, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas, Dimple Modgil,
+Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for valuable discussions
+during the development of this work. TC was supported by a University of Chicago
+Biological Sciences Division Graduate Fellowship, and PL was supported by a
+Marine Biological Laboratory Whitman Center Fellowship.
+
+\section*{Disclosures}
+The authors declare that there are no conflicts of interest related to this article.
 
@@
 \appendix
-\section{Spherical harmonics}\label{sec:sph}
+\section{Spherical harmonics and the spherical Fourier transform}\label{sec:sph}
 The spherical harmonic function of degree $\ell$ and order $-\ell \leq m \leq \ell$
@@
 where $\delta_{\ell\ell'}$ denotes the Kronecker delta. The spherical harmonics form a
-complete basis so an arbitrary function on the sphere $f(\mh{s})$ can be
+complete basis, so an arbitrary function on the sphere $f(\mh{s})$ can be
 expanded into a sum of weighted spherical harmonic functions
@@
 
-We briefly show how two properties of spherical functions propagate to the
-spherical Fourier transform. First, the spherical harmonic coefficients of
-spherical functions that can be written entirely as a function of the
-inclination angle $\vartheta$ are zero when $m\neq0$ because
-\begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)Y_\ell^{m*}(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
-\end{align}
-Second, the spherical harmonic coefficients of spherical functions that are
-symmetric under inversion $f(\mh{s}) = f(-\mh{s})$ are zero when $\ell$ is odd
-because $Y_\ell^m(-\so) = (-1)^\ell Y_\ell^m(\mh{s})$, so if $\ell$ is odd then
-\begin{align}
-  \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})Y_{2n+1}^{m*}(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})Y_{2n+1}^{m*}(-\mh{s}),\\
-&=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) = 0.                                                                
-\end{align}
+% We briefly show how two properties of spherical functions propagate to the
+% spherical Fourier transform. First, the spherical harmonic coefficients of
+% spherical functions that can be written entirely as a function of the
+% inclination angle $\vartheta$ are zero when $m\neq0$ because
+% \begin{align}
+%   \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)Y_\ell^{m*}(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
+% \end{align}
+% Second, the spherical harmonic coefficients of spherical functions that are
+% symmetric under inversion $f(\mh{s}) = f(-\mh{s})$ are zero when $\ell$ is odd
+% because $Y_\ell^m(-\so) = (-1)^\ell Y_\ell^m(\mh{s})$, so if $\ell$ is odd then
+% \begin{align}
+%   \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})Y_{2n+1}^{m*}(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})Y_{2n+1}^{m*}(-\mh{s}),\\
+% &=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) = 0.                                                                
+% \end{align}
 \section{Relationships between special functions} \label{sec:special}
@@
   The azimuthal integral can be evaluated in terms of an $n^{th}$ order Bessel
-  function (see Barrett and Myers 4.111 for the complex case \cite{barrett2004})
+  function (for the complex case see \cite[ch. 4.111]{barrett2004}).
   \begin{align}
@@
   \end{align}
-  We can use the following identity (see GR 6.561-5 \cite{gradshteyn2007})
+  We can use the following identity \cite[ch.~6.561-5]{gradshteyn2007}
   \begin{align}
@@
 
-We can use the relationship in Eq. \ref{eq:jincrect3} to express the chat
-functions in terms of a complex autocorrelation---see the diagram in Figure \ref{fig:special}. Starting with the definition of
+We can use the relationship in Eq. \eqref{eq:jincrect3} to express the chat
+functions in terms of a complex autocorrelation---see the diagram in Fig. \ref{fig:special}. Starting with the definition of
 the $n^{th}$-order chat function
@@
 \end{align}
-where the function to be autocorrelated can be found with the help of Eq. \ref{eq:jincrect3}
+where the function to be autocorrelated can be found with the help of Eq. \eqref{eq:jincrect3}
 \begin{align}
@@
 \end{align}
-Plugging Eq. \ref{eq:tn} into Eq. \ref{eq:autocorr} gives
+Plugging Eq. \eqref{eq:tn} into Eq. \eqref{eq:autocorr} gives
 \begin{align}
@@
 between a circle centered at the origin and a circle shifted to the right by
-$\nu$ (a geometric lens). Using the construction in Figure \ref{fig:geometry} we
+$\nu$ (a geometric lens). Using the construction in Fig. \ref{fig:geometry} we
 can express this region as
@@
      and distance $\nu$ between their centers. The region is four times the
-     difference in area between a sector of angle $\arccos(\nu)$ and radius
+     difference in area between a sector of angle $\cos^{-1}(\nu)$ and radius
      $1/2$ and a right triangle with base $\nu/2$ and hypotenuse $1/2$.}
@@
   \text{chat}_0(\nu) &= 4\left[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2}\right),\\
-  \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}\nu - \nu\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
+  \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu|\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
 \intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
   \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
-  \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}\nu - \nu (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
+  \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu| (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
 \end{align}
@@
 \section{Spherical Fourier transform of a double cone}\label{sec:cone}
-In this appendix we will evaluate the spherical Fourier transform of a
+In this appendix we evaluate the spherical Fourier transform of a
 normalized double-cone angular distribution with central direction $\mh{s}'$ and
@@
 \begin{align}
-  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{2\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right). 
+  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right). 
 \end{align}
@@
 rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
-symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')$ to account for the rotation
+symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
 \begin{align}
@@
 \end{align}
-The integral evaluates to (see GR 7.111 \cite{gradshteyn2007})
+The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
 \begin{align}

### 2018-12-04 papers/basic-theory/paper/paper.tex
Misc edits.

@@
 
-\author{Talon Chandler,\authormark{1,*}, Rudolf Oldenbourg,\authormark{2} and\\ Patrick La Rivi\`ere\authormark{1,2}}
+\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{2} and Patrick La Rivi\`ere\authormark{1,2}}
 
 \address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
-  \authormark{2}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
+  \authormark{2}Section on High Resolution Optical Imaging, National Institute
+  of Biomedical Imaging and Bioengineering, National Institutes of Health,
+  Bethesda, Maryland 20892, USA\\
+  \authormark{3}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
 }
@@
 
-\subsection{Paraxial dipole spatial transfer function}\label{sec:trans}
+\subsubsection{Paraxial dipole spatial transfer function}\label{sec:trans}
 The dipole spatial transfer function is the spatial Fourier transform of
@@
  \begin{align}
-H_{\ell}^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
+H_{\ell}^m(\bv) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
  \end{align}
@@
 We thank Kyle Myers, Harrison Barrett, Scott Carney, Luke Pfister, Jerome Mertz,
-Mikael Backlund, Matthew Lew, Hari Shroff, Min Guo, Yicong Wu, Shalin Mehta,
-Abhishek Kumar, Peter Basser, Gordon Wetzstein, Hayato Ikoma, Laura Waller, Ren
-Ng, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas, Dimple Modgil,
-Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for valuable discussions
-during the development of this work. TC was supported by a University of Chicago
-Biological Sciences Division Graduate Fellowship, and PL was supported by a
-Marine Biological Laboratory Whitman Center Fellowship.
+Sjoerd Stallinga, Mikael Backlund, Matthew Lew, Min Guo, Yicong Wu, Shalin
+Mehta, Abhishek Kumar, Peter Basser, Marc Levoy, Michael Broxton, Gordon
+Wetzstein, Hayato Ikoma, Laura Waller, Ren Ng, Tomomi Tani, Michael Shribak, Mai
+Tran, Amitabh Verma, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas,
+Dimple Modgil, Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for
+valuable discussions during the development of this work. TC was supported by a
+University of Chicago Biological Sciences Division Graduate Fellowship, and PL
+was supported by a Marine Biological Laboratory Whitman Center Fellowship.
 

### 2018-12-11 papers/basic-theory/figures/dipole-block/dipole-block.tex
Hari and Patrick's edits.

@@
     \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Dipole\\ density};
-    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular\\ dipole\\ spectrum};
+    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Dipole\\ angular\\ spectrum};
     \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Scaled\\ irradiance};
-    \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{F}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole\\ spectrum};
+    \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{F}_\ell^m(\bs{\nu})$\\ Dipole\\ spatio-angular\\ spectrum};
     \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Scaled\\ irradiance\\ spectrum};
-    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial\\ dipole\\ spectrum};
+    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Dipole\\ spatial\\ spectrum};
     \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
@@
 
-    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{H_\ell^m(\rd - \ro)}F_\ell^m(\ro)$} (irr);
+    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Dipole angular\\ transfer function\\ $\sum_{\ell m}\int_{\mbb{R}^2}d\ro \gray{H_\ell^m(\rd - \ro)}F_\ell^m(\ro)$} (irr);
     \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Dipole point\\ spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, \gray{h(\rd - \ro, \so)}f(\ro, \so)$} ++(13cm,0) --  (irr.north);
-    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Spatial dipole\\ transfer function\\ $\int_{\mbb{S}^2}d\so\, \gray{H(\bs{\nu}, \so)}F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
-    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{\mathsf{H}_\ell^m(\bs{\nu})}\mathsf{F}_\ell^m(\bs{\nu})$} (is);
+    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Dipole spatial\\ transfer function\\ $\int_{\mbb{S}^2}d\so\, \gray{H(\bs{\nu}, \so)}F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
+    \draw [->] (sas) -- node[text width=4cm, align=center] {Dipole spatio-angular\\ transfer function\\ $\sum_{\ell m}\gray{\mathsf{H}_\ell^m(\bs{\nu})}\mathsf{F}_\ell^m(\bs{\nu})$} (is);
 

### 2018-12-11 papers/basic-theory/figures/transfer-functions/transfer-functions.tex
Hari and Patrick's edits.

@@
 \providecommand{\bv}{\bs{\nu}}
-\providecommand{\bvp}{\bs{\nu}_p}
+\providecommand{\bvp}{\bs{\tau}}
 \providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
@@
     \node [block, align=center] (sad) {$h(\rd - \ro, \so)$\\ Dipole point\\ spread function};
-    \node [block,  right of=sad, node distance=5.5cm] (ads) {$H_\ell^m(\rd - \ro)$\\ Angular dipole\\ transfer function};
-    \node [block,  left of=sad, node distance=5.5cm] (e) {$\mb{c}(\rd - \ro, \so)$\\ Coherent dipole \\ spread function};
-      \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{H}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole transfer function};
-      \node [block, below of=sad, node distance=2.5cm] (sds) {$H(\bs{\nu}, \so)$\\ Dipole\\ transfer function};
-        \node [block,  left of=sds, node distance=5.5cm] (e2) {$\mb{C}(\bvp,\so)$\\ Coherent dipole \\transfer function};
+    \node [block,  right of=sad, node distance=5.5cm] (ads) {$H_\ell^m(\rd - \ro)$\\ Dipole angular\\ transfer function};
+    \node [block,  left of=sad, node distance=5.5cm] (e) {$\mb{c}(\rd - \ro, \so)$\\ Dipole coherent \\ spread function};
+      \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{H}_\ell^m(\bs{\nu})$\\ Dipole spatio-angular\\ transfer function};
+      \node [block, below of=sad, node distance=2.5cm] (sds) {$H(\bs{\nu}, \so)$\\ Dipole spatial\\ transfer function};
+        \node [block,  left of=sds, node distance=5.5cm] (e2) {$\mb{C}(\bvp,\so)$\\ Dipole coherent \\transfer function};
       \draw [->] (sad) -- node[shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);

### 2018-12-11 papers/basic-theory/paper/paper.tex
Hari and Patrick's edits.

@@
 % Talon's custom commands
-\setlength\arraycolsep{2.25pt}
+\setlength\arraycolsep{1.5pt}
 \let\originalleft\left
@@
 
-\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{2} and Patrick La Rivi\`ere\authormark{1,2}}
+\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{3} and Patrick La Rivi\`ere\authormark{1,3}}
 
@@
   show that the operator takes a particularly convenient form when expressed in
-  a basis of spatial and spherical harmonics---a form we call the dipole
-  spatio-angular transfer function. We demonstrate our formalism by analyzing a
-  single-view fluorescence microscope without using the monopole or scalar
-  approximations. We show that this imaging system has a spatio-angular band
-  limit, and we exploit the band limit to perform efficient simulations.
+  a basis of complex exponentials and spherical harmonics---a form we call the
+  dipole spatio-angular transfer function. We demonstrate our formalism by
+  analyzing a single-view fluorescence microscope without using the monopole or
+  scalar approximations. We show that this imaging system has a spatio-angular
+  band limit, and we exploit the band limit to perform efficient simulations.
   Notably, we show that information about the out-of-plane orientation of
@@
 Fluorescence microscopes are widely used in the biological sciences for
-measuring the spatial and angular distribution of ensembles of fluorophores.
-While most fluorescence microscopy experiments are designed to measure only the
-spatial distribution of fluorophores, a growing number of experiments use
-polarizers to measure both the spatial and angular distributions of fluorophores
-\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}.
+measuring ensembles of fluorescent molecules. While most fluorescence microscopy
+experiments are designed to measure only the spatial distribution of
+fluorophores, a growing number of experiments seek to measure both the spatial
+and angular distributions of fluorophores by the use of polarizers
+\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017} or
+point spread function engineering \cite{agrawal2012, zhang2018}.
 
@@
 spatially sparse fluorescent samples to localize single molecules with precision
-that surpasses the diffraction limit. Real SMLM experiments are limited by noise
-\cite{foreman2011, chao2016} and model mismatch, and several studies have shown
-that model mismatch (e.g. ignoring the effects of vector optics, dipole
-orientation \cite{backlund2014}, and dipole rotation \cite{lew2013}) can
-introduce localization bias into SMLM experiments. Therefore, the most precise
-SMLM experiments must use an appropriate model and jointly estimate both the
-position and orientation of each fluorophore. Several studies have successfully
-used vector optics and dipole models to estimate the position and orientation of
+that surpasses the diffraction limit. Noise limits the precision of this
+localization \cite{foreman2011, chao2016}, and several studies have shown that
+model mismatch (e.g. ignoring the effects of vector optics, dipole orientation
+\cite{backlund2014}, and dipole rotation \cite{lew2013}) can introduce
+localization bias as well. Therefore, the most precise and accurate SMLM
+experiments must use an appropriate model and jointly estimate both the position
+and orientation of each fluorophore. Several studies have successfully used
+vector optics and dipole models to estimate the position and orientation of
 single molecules \cite{bohmer2003, lieb2004, toprak2006, aguet2009}, and there
@@
 orientation, and rotational dynamics of single molecules \cite{agrawal2012,
-  backer2014, zhang2018, zhang2018-2}.
+  backer2014, stallinga2015, zhang2018, zhang2018-2}.
 
@@
 fluorescent samples, we consider the more general case and aim to improve
-imaging models for arbitrary samples. In particular, we examine the effects of
-two widely used approximations in fluorescence microscopy---the \textit{monopole
-  approximation} and the \textit{scalar approximation}.
+imaging models for arbitrary samples including those containing ensembles of
+fluorophores within a resolvable volume. In particular, we examine the effects
+of two widely used approximations in fluorescence microscopy---the
+\textit{monopole approximation} and the \textit{scalar approximation}.
 
@@
 treats it as an isotropic absorber/emitter. Although the term \textit{monopole
-  approximation} is not in widespread use, we think that it is an accurate label
-for the way many models of fluorescence microscopes treat fluorophores, and we
-use the term to distinguish the monopole model from more realistic dipole and
+  approximation} is not in widespread use, we think it accurately describes the
+way many models of fluorescence microscopes treat fluorophores, and we use the
+term to distinguish the monopole model from more realistic dipole and
 higher-order models. Despite their use in models, monopole absorber/emitters do
-not exist in nature, and the monopole approximation must be justified. Although
-many works implicitly apply the monopole approximation, we have encountered two
-explicit justifications: (1) the sample contains many randomly oriented
-fluorophores within a resolvable volume or (2) the sample contains unconstrained
-rotating fluorophores. While both of these situations yield monopole-like
-samples, neither yields a sample that is perfectly described by the monopole
-model. In this work we investigate the dipole model of fluorophores in detail
-and find the conditions under which the monopole approximation is justified.
+not exist in nature. All physical fluorophores absorb and emit radiation with
+dipole or higher-order transitions, and these transitions are always oriented in
+space. For a classical mental model of fluorophores we imagine each dipole as a
+small oriented antenna (with incoherent absorption and emission moments) where
+electrons are constrained to move along a single direction. With this model we
+can argue classically that monopole radiators do not exist because they would
+violate the conservation of charge.
+
+Although many works implicitly apply the monopole approximation, we have
+encountered two explicit justifications: (1) the sample contains many randomly
+oriented fluorophores within a resolvable volume or (2) the sample contains
+unconstrained rotating fluorophores. While both of these situations yield
+monopole-like samples, neither yields a sample that is perfectly described by
+the monopole model. In this work we investigate the dipole model of fluorophores
+in detail and find the conditions under which the monopole approximation is
+justified.
 
@@
 an essential part of microscopes, fluorescence microscopists are interested in
-measuring fluorophores (not optics), so the monopole and dipole transfer
-functions are more valuable than the optical transfer function.
+measuring the properties of fluorophores (not optics), so the monopole and
+dipole transfer functions are more directly useful than the optical transfer
+function for the problems that fluorescence microscopists are interested in
+solving.
 
@@
 three-dimensional vector field, but if the electric fields are random or
-parallel a scalar field is sufficient. Replacing the vector-valued electric
-field, $\mb{E}$, with a scalar-valued field, $U$, is the scalar approximation,
-and this approximation is only justified if the fields are randomly or uniformly
-polarized.
+parallel a scalar field is sufficient, and we can replace the vector-valued electric
+field, $\mb{E}$, with a scalar-valued field, $U$.%  is the scalar approximation,
+% and this approximation is only justified if the fields are randomly or uniformly
+% polarized.
 
@@
 system, but it is an optical model so when it is applied to fluorescence
-microscopes the monopole approximation is required. As previously mentioned,
-several works in the SMLM community have modeled and applied dipole point spread
-functions that do not make the monopole or scalar approximations, but to our
-knowledge no works have considered dipole transfer functions.
+microscopes the monopole approximation is assumed. % As previously mentioned,
+% several works in the SMLM community have modeled and applied dipole point spread
+% functions that do not make the monopole or scalar approximations, but to our
+% knowledge no works have considered dipole transfer functions.
 
@@
 parallel and the goal is to find their concentration and orientation, and (3)
-the single molecule localization microscopy (SMLM) community where fluorophores
-are sparse in the sample and the goal is to find the position of each
-fluorophore. We briefly review how these three communities use the monopole and
-scalar approximations.
+the SMLM community where fluorophores are sparse in the sample and the goal is
+to find the position of each fluorophore. We briefly review how these three
+communities use the monopole and scalar approximations.
 
@@
   mattheyses2010, mehta2016, mcquilken2017} or assume that the spatial and
-angular reconstruction problems can be performed sequentially
+angular reconstruction problems can be solved sequentially
 \cite{zhanghao2017}.
@@
     fluorescence microscope can be computed in two different bases---a delta
-    function basis and a spatial harmonic basis. The change of basis can be
+    function basis and a complex exponential basis. The change of basis can be
     computed with a two-dimensional Fourier transform denoted
@@
 The mapping between the object and the data in a linear shift-invariant imaging
-system takes a particularly simple form in a spatial harmonic (i.e. Fourier) basis. If we apply
-the Fourier convolution theorem to Eq. \eqref{eq:lsi} we find that
+system takes a particularly simple form in a complex exponential (i.e. Fourier)
+basis. If we apply the Fourier convolution theorem to Eq. \eqref{eq:lsi} we find
+that
 \begin{align}
@@
 monopole point spread function can always be written as the absolute square of a
-scalar-valued \textit{monopole coherent spread function} defined as
+scalar-valued \textit{monopole coherent spread function}, $c(\rd - \ro)$,
+defined by
 \begin{align}
@@
 \textit{monopole coherent transfer function} as the two-dimensional Fourier
-transform of the monopole coherent spread function
+transform of the monopole coherent spread function:
 \begin{align}
@@
 where $h'(\rd', \ro, \so)$ is the irradiance at position $\rd'$ created by a
-point source at $\ro$ with orientation $\so$. If the optical system is
-aplanatic, we can write the integral transform as
+point source at $\ro$ with orientation $\so$. Notice that we have considered all
+possible orientations $\so$ and integrated over the sphere $\mbb{S}^2$. The
+dipole density is always symmetric under angular inversion,
+$f(\ro, \so) = f(\ro,-\so)$, so we could have chosen to integrate over a
+hemisphere and adjusted the definition the dipole density by a factor of two.
+For convenience we will continue to integrate over the complete sphere. We note
+that all functions in this work with $\so$ as an independent variable are
+symmetric under angular inversion, $\so \rightarrow -\so$.
+
+If the optical system is aplanatic, we can write the
+integral transform as
 \begin{align}
@@
 dipoles
-$P_\text{dip} = \int_{\mbb{S}^2}d\mh{s}\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
+$P_\text{dip} = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\mb{r}\, h'(m\mb{r},
 \so)$. We use these scaling factors to define the
@@
   \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
-  \caption{The mapping between the object and data space of a dipole imaging
-    system can be computed in four different bases---a delta function basis, a
-    spatial-harmonic/angular-delta basis, a spatial-delta/spherical-harmonic
-    basis, and a spatio-angular harmonic basis. The changes of basis can be
+  \caption{The mapping between the object space and data space of a dipole
+    imaging system can be computed in four different bases---a delta function
+    basis, a complex-exponential/angular-delta basis, a
+    spatial-delta/spherical-harmonic basis, and a
+    complex-exponential/spherical-harmonic basis. The changes of basis can be
     computed with the two-dimensional Fourier transform denoted
@@
   dipole spatio-angular transfer function and see that it has spatial and
-  angular band limits. We note that most single molecules imaging experiments
+  angular band limits. We note that most single molecule imaging experiments
   are best described in this basis because of the effects of spatial and
@@
 \subsubsection{Dipole coherent transfer functions}
-Similar to the monopole case, there is efficient way to calculate the transfer
-functions using coherent transfer functions. The dipole point spread function
-can always be written as the absolute square of a vector-valued function called
-the \textit{dipole coherent spread function}
+Similar to the monopole case, there is an efficient way to calculate the
+transfer functions using coherent transfer functions. The dipole point spread
+function can always be written as the absolute square of a vector-valued
+function, $\mb{c}(\rd - \ro, \so)$, called the \textit{dipole coherent spread
+  function}:
 \begin{align}
@@
 $\mb{C}(\taup, \so)$ as the two-dimensional Fourier transform of the dipole
-coherent spread function
+coherent spread function:
 \begin{align}
@@
 Fourier plane of the detector with appropriate scaling. Similar to the monopole
-case, we can calculate the dipole-orientation-dependent fields in a Fourier plane of
-the detector, scale appropriately to find the dipole coherent transfer function,
-then use the relationships in Fig. \ref{fig:transfer-functions} to calculate
-the other transfer functions.
+case, we can calculate the dipole-orientation-dependent fields in a Fourier
+plane of the detector, scale appropriately to find the dipole coherent transfer
+function, then use the relationships in Fig. \ref{fig:transfer-functions} to
+calculate the other transfer functions. Finally, we note that the dipole
+coherent transfer function is identical to what Agrawal et. al. call the
+\textit{Green's tensor} \cite{agrawal2012} and Novotny and Hecht's
+\textit{dyadic point spread function} multiplied by the dipole moment vector
+\cite{nov2006}.
 
@@
    \centering
-   \includegraphics[width = 0.9\textwidth]{../figures/abstract-micro/abstract-micro.pdf}
+   \includegraphics[width = 1.0\textwidth]{../figures/coordinates/detection-coords.pdf}
    \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
      paraxial tube lens. We are considering an aplanatic optical system, so we
-     only need to consider the image created by on-axis objects.}
+     only need to consider the image created by on-axis objects. The fluorescent
+     object consists of ensembles of dipoles embedded in a medium with index of
+     refraction $n_0$. An objective with focal length $f_0$ and numerical
+     aperture $\text{NA} = n_o\sin\alpha$ is trained on the object. A paraxial
+     tube lens with focal length $f_1$ and a detector complete the $4f$
+     geometry, and all components except the object are embedded in a medium
+     with index of refraction $n_1$. The object, pupil, and detector planes are
+     parameterized by vectors $\ro$, $\rp$, and $\rd$ with polar coordinates
+     ($r_o, \phi_o$), ($r_b, \phi_b$), and ($r_d, \phi_d$), respectively. At
+     each position $\ro$ in the object there is a sphere parameterized by a unit
+     vector $\so$ with spherical coordinates ($\vartheta, \varphi$). }
    \label{fig:schematic}
@@
 scalar-valued function. The optical system is aplanatic, so we can write the
-field created at a point in the pupil plane $\rp$ by a monopole at position
-$\ro$ as
+field, $U_p(\rp, \ro)$, created at a point in the pupil plane $\rp$ by a
+monopole at position $\ro$ as
 \begin{align}
@@
  \begin{align}
-   \mb{E}(\rp, \ro, \so) = \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
+   \mb{E}(\rp, \ro, \so) \propto \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
  \end{align}
@@
  \begin{alignat}{4}
-   \tilde{C}_0(x) &= \frac{1}{2}(\sqrt{1 - x^2} + 1)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
+   \tilde{C}_0(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} + 1\right)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
    \tilde{C}_1(x) &= x(1 - x^2)^{-1/4} &&= x + \frac{x^3}{4} + \frac{5x^5}{32} + \cdots,\\
-   \tilde{C}_2(x) &= \frac{1}{2}(\sqrt{1 - x^2} - 1)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
+   \tilde{C}_2(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} - 1\right)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
  \end{alignat}
@@
  dipole coherent transfer function
- \begin{align}
-   \mb{C}(\taup, \so) \propto
+ \begin{equation}
+   \mb{C}(\taup, \so)\hspace{-0.2em}\propto\hspace{-0.2em}
    \begin{bmatrix}
-     \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(\phi_{\tau})\\
-     \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)s(\phi_{\tau})\\
+     \tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!+\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)c(\phi_{\tau})\\
+     \tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!-\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)s(\phi_{\tau})\\
      0&0&0\\     
    \end{bmatrix}
-   % \begin{bmatrix}
-   %   \tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) + \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos\phi_{\tau}\\
-   %   \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin(2\phi_{\tau})&\tilde{C}_0\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right) - \tilde{C}_2\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\cos(2\phi_{\tau})&\tilde{C}_1\left(\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\right)\sin\phi_{\tau}\\
-   %   0&0&0\\     
-   % \end{bmatrix}
    \begin{bmatrix}
@@
    \Pi\left(\frac{\tau}{\nu_c}\right). 
- \end{align}
+ \end{equation}
  We restrict our analysis to the paraxial regime by dropping second- and
@@
  Moerner's numerical results, but the approximation will allow us to calculate
- the transfer functions in closed form so that we can gain an intuition for the
+ the transfer functions in closed form so that we can build an intuition for the
  limits of the microscope. We also note that many existing works in ensemble
@@
 \end{align}
-where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization factor is
+where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization
+factor is
 \begin{align}
@@
 function to the dipole point spread function. The paraxial monopole and dipole
-models are only equivalent when the sample consists of transverse dipoles which
+models are only equivalent when the sample consists of transverse dipoles, which
 is clear if we notice that Eq. \eqref{eq:paradpsf} reduces to an Airy disk when
@@
      and observe that the paraxial monopole and dipole models are identical for
-     transverse dipoles.}
+     transverse dipoles (the \textcolor{green}{\textbf{green}} and
+     \textbf{black} lines are coincident).}
    \label{fig:hdet}
@@
      (\textcolor{green}{\textbf{green}}) and observe that the paraxial monopole
-     and dipole models are identical for transverse dipoles.}
+     and dipole models are identical for transverse dipoles (the
+     \textcolor{green}{\textbf{green}} and \textbf{black} lines are
+     coincident).}
    \label{fig:odotf}
@@
  \begin{align}
-   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right)
+   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right)
  \end{align}
@@
   disks create relatively unique irradiance patterns, while increasing the cone
-  angle or disk size creates increasingly irradiance patterns.
+  angle or disk size creates increasingly similar irradiance patterns.
 
@@
 Model mismatch can lead to biased estimates of the position and orientation of
-fluorophores, so the most precise fluorescence microscopy experiments will
+fluorophores, so the most accurate fluorescence microscopy experiments will
 always use dipole transfer functions over monopole transfer functions. The only
@@
 situations in biological applications---then the effects of vector optics and
-dipoles will be masked by noise in all but the highest SNR regimes.
+dipoles will be masked by noise in all but the highest-SNR regimes.
 
@@
 usual approach to extending the span of the second moments is to use the fourth
-(or higher) moments, but these are completely new basis functions. Second, the
-spherical harmonics are orthonormal which will allow us to deploy invaluable
-tools from linear algebra---linear subspaces, rank, decompositions, etc.--- to
-analyze and compare microscope designs. Finally, using the spherical harmonics
-provides access to a set of fast algorithms. The naive expansion of an arbitrary
-discretized $N$ point spherical function onto spherical harmonics (or second
-moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering work
-by Driscoll and Healy \cite{driscoll1994} showed that the forward discrete fast
-spherical harmonic transform can be computed with a $\mc{O}(N(\log N)^2)$
-algorithm and its inverse can be computed with a $\mc{O}(N^{3/2})$ algorithm. To
-our knowledge no similarly fast algorithms exist for expansion onto the
-higher-order moments.
+(or higher) moments, but this extension requires a completely new set of basis
+functions while the spherical harmonics can be extended by simply adding higher order
+terms. Second, the spherical harmonics are orthonormal, which will allow us to
+deploy invaluable tools from linear algebra---linear subspaces, rank,
+decompositions, etc.--- to analyze and compare microscope designs. Finally,
+using the spherical harmonics provides access to a set of fast algorithms. The
+naive expansion of an arbitrary discretized $N$ point spherical function onto
+spherical harmonics (or second moments) requires a $\mc{O}(N^2)$ matrix
+multiplication, while pioneering work by Driscoll and Healy \cite{driscoll1994}
+showed that the forward discrete fast spherical harmonic transform can be
+computed with a $\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed
+with a $\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast
+algorithms exist for expansion onto the higher-order moments.
 
@@
 the orientation of dipoles. The circular harmonics are complete and orthogonal,
-but they artificially restrict the angular reconstruction to the transverse
+but they artificially restrict the reconstructed dipoles to the transverse
 plane of the microscope---a rare situation in real experiments.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 Many models of fluorescence microscopes use the monopole and scalar
-approximations, and complete models need to consider dipole and vector optics
+approximations, but complete models need to consider dipole and vector optics
 effects. We have introduced several transfer functions that simplify the mapping
 between the dipole density and the irradiance pattern on the detector, and we
-demonstrated these transfer functions by efficiently simulating a paraxial
+have demonstrated these transfer functions by efficiently simulating a paraxial
 fluorescence microscope. We found that the monopole and scalar approximations
@@
 We also found that dipole and vector optics effects become larger as rotational
-order increases, and in these cases the dipole transfer functions become valuable
-tools.
+order increases, and in these cases the dipole transfer functions become
+valuable tools.
 
@@
 was supported by a Marine Biological Laboratory Whitman Center Fellowship.
+Support for this work was provided by the Intramural Research Programs of the
+National Institute of Biomedical Imaging and Bioengineering.
 
@@
 \begin{align}
-  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{\cos\Delta}\right). 
+  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right). \label{eq:doublecone}
 \end{align}
@@
 \end{align}
+% This integral will be difficult to evaluate unless we change coordinates to
+% exploit the axis of symmetry $\mh{s}'$. The key idea is that
+% $f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)$ is a function of
+% $\mh{s}\cdot\mh{s}'$ so it is a one dimensional function on the domain [-1,1]
+% that can be expanded in terms of Legendre polynomials (a Fourier-Legendre
+% series)
+% \begin{align}
+%   f_{\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta) = \sum_{\ell = 0}^{\infty}F_{\ell\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta)P_{\ell}(\mh{s}\cdot\mh{s}').
+% \end{align}
+% We can find the coefficients $F_{\ell\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta)$
+% using Fourier's trick---multiply both sides by $P_{\ell}(\mh{s}\cdot\mh{s}')$,
+% integrate over [-1,1], and exploit orthogonality
+% $\int_{-1}^{1}dx\,P_{\ell}(x)P_{\ell'}(x) = \frac{2}{2\ell +
+%   1}\delta_{\ell\ell'}$ to find that
+% \begin{align}
+%   F_{\ell\text{(cone)}}(x, \Delta) = \frac{2\ell + 1}{2}\int_{-1}^{1}dx\, f_{\text{(cone)}}(x, \Delta)P_\ell(x). \label{eq:legendre}
+% \end{align}
+% Plugging Eq. \eqref{eq:doublecone} into Eq. \eqref{eq:legendre} yields
+% \begin{align}
+%   F_{\ell\text{(cone)}}(x, \Delta) = \frac{2\ell + 1}{4\pi(1-\cos\Delta)}\int^{1}_{\cos\Delta}dx\, P_\ell(x). 
+% \end{align}
+% The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
+% \begin{align}
+%   \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
+% \begin{cases}
+%   1 - \cos\Delta\,, &\ell = 0\,,\\
+%   \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
+% \end{cases}
+% \end{align}
+% where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
+% $m=-1$, not an inverse Legendre polynomial.
+
 The limits of integration will be difficult to find unless we change coordinates
@@
 rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
-symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^m(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
+symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
 \end{align}
@@
 so we can evaluate the azimuthal integral and express the function in terms of an
-integral over
-$\vartheta$
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^m(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
+integral over $\vartheta$:
+\begin{align}
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^{m*}(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
 \end{align}
@@
 \begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right].
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right].
 \end{align}
@@
 \begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right]. 
+    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right]. 
 \end{align}
@@
 $\ell$ is even (odd), so the pair of integrals will be identical when $\ell$ is
-even and cancel when $\ell$ is odd. For even $\ell$
-\begin{align}
-  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^m(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
+even and cancel when $\ell$ is odd. For even $\ell$,
+\begin{align}
+  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
 \end{align}
@@
 $m=-1$, not an inverse Legendre polynomial. Bringing everything together
-
 \begin{align}
@@
     0, & \ell\, \text{odd},\\
-    Y_\ell^m(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
+    Y_\ell^{m*}(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
   \end{cases}

### 2018-12-11 papers/basic-theory/figures/excitation-coords/excitation-coords.py

@@ -1,208 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.lines as lines
-import matplotlib.text as text
-import matplotlib.gridspec as gridspec
-from scipy import special
-outer_gridspec = gridspec.GridSpec
-inner_gridspec = gridspec.GridSpecFromSubplotSpec
-plt.rcParams["font.family"] = "serif"
-plt.rcParams["font.serif"] = "Times"
-import matplotlib
-matplotlib.rc('text', usetex=True)
-matplotlib.rcParams['text.latex.preamble']=[r"\usepackage{bm}"]
-
-# Physical parameters
-lamb = 0.3
-k = 2*np.pi/lamb
-alpha = 0.5
-
-inches = 2
-outer_rows = 1
-outer_cols = 1
-inner_rows = 2
-inner_cols = 3
-widths = [3/2]*outer_cols
-heights = [1]*outer_rows
-wspace = 0
-wspace_inner = 0
-hspace = 0
-hspace_inner = 0.2
-f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(outer_cols - 1) + 0.5*widths[0]*wspace_inner*outer_cols),
-                        inches*(np.sum(heights) + heights[0]*(hspace)*(outer_rows - 1) + 0.5*heights[0]*hspace_inner*outer_rows)))
-
-                                
-outer_grid = outer_gridspec(ncols=outer_cols, nrows=outer_rows,
-                            width_ratios=widths, height_ratios=heights,
-                            hspace=hspace, wspace=wspace)
-for outer_row in range(outer_rows):
-    for outer_col in range(outer_cols):
-        inner_grid = inner_gridspec(inner_rows, inner_cols,
-                                    subplot_spec=outer_grid[outer_row, outer_col],
-                                    width_ratios=[1]*inner_cols, height_ratios=[1]*inner_rows,
-                                    hspace=hspace_inner, wspace=wspace_inner)
-        for inner_row in range(inner_rows):
-            for inner_col in range(inner_cols):
-                ax = f.add_subplot(inner_grid[inner_row, inner_col])
-                ax.get_xaxis().set_visible(False)
-                ax.get_yaxis().set_visible(False)
-                ax.axis('off')
-
-                # Draw lenses
-                if inner_row == 0 and (inner_col == 1 or inner_col == 3):
-                    # Kludge to smooth sharp edges
[…]

### 2018-12-11 papers/basic-theory/figures/microscope/microscope.py

@@ -8,6 +8,8 @@ outer_gridspec = gridspec.GridSpec
 inner_gridspec = gridspec.GridSpecFromSubplotSpec
 plt.rcParams["font.family"] = "serif"
 plt.rcParams["font.serif"] = "Times"
+plt.rc('path',simplify_threshold=.0001)
+
 
 # Physical parameters
 lamb = 0.3
@@ -25,7 +27,7 @@ wspace = 0.1
 wspace_inner = 0.2
 hspace = 0
 f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(outer_cols - 1) + 0.5*widths[0]*wspace_inner*outer_cols),
-                        inches*(np.sum(heights)) + heights[0]*hspace*(outer_rows - 1)))
+                        inches*(np.sum(heights)) + heights[0]*hspace*(outer_rows - 1)), dpi=500)
                                 
 outer_grid = outer_gridspec(ncols=outer_cols, nrows=outer_rows,
                             width_ratios=widths, height_ratios=heights,
@@ -70,7 +72,7 @@ for outer_row in range(outer_rows):
                 if outer_col == 0 and inner_col == 0:
                     row_labels = ['Detector\n irradiance',
                                   'Tube\n lens',
-                                  'Back focal\n plane\n electric field',
+                                  'Pupil plane\n field',
                                   'Objective\n lens',
                                   'Far-field\n radiation\n pattern']
                     ax.text(-0.3,0.5,row_labels[inner_row], ha='right', va='center', transform=ax.transAxes)
@@ -124,7 +126,11 @@ for outer_row in range(outer_rows):
                     if outer_col == 2:
                         z = (special.jn(2,a*r)/(a*r))**2
                     if inner_col == 0:
+                        # ax.plot(x, z[:,N//2]/np.max(z), 'k-', lw=0.5, zorder=10)
+                        # ax.set_xlim((-1,1))
+                        # ax.set_xlim((-1,1))                        
                         l1 = lines.Line2D(x, z[:,N//2]/np.max(z), c='k', lw=1, transform=ax.transData, zorder=0)
+                        # l1.set_marker('.')
                         f.lines.extend([l1])
                     if inner_col == 1:
                         ax.imshow(z/np.max(z), vmin=0, vmax=1, cmap='gray', interpolation='bicubic', origin='lower', extent=[-1,1,-1,1])
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/adtf.py

@@ -1,0 +1,67 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.gridspec as gridspec
+import scipy.misc
+from scipy import special
+import paratf
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+
+inches = 2
+rows = 1
+cols = 3
+widths = [1,1,1]
+heights = [1]
+hspace = 0.05
+wspace = 0.15
+
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
+                        inches*(np.sum(heights))))
+
+outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
+                               width_ratios=widths, height_ratios=heights,
+                               hspace=hspace, wspace=wspace)
+
+alphas = [0.25, 0.5, 0.75]
+alpha_strs = ['0.25', '0.5', '0.75']
+for col in range(cols):
+    alpha = alphas[col]
+    ax = f.add_subplot(outer_grid[0, col])
+    ax.set_xlim([0,2])
+    ax.set_ylim([0,1])
+
+    nucr = np.linspace(1e-3, 2, 100)
+    ax.plot(nucr, paratf.adtf(nucr, 0, NA=alpha)/paratf.adtf(1e-3, 0, NA=alpha), '-', c=[1, 0, 0], lw=0.5)
+    ax.plot(nucr, paratf.adtf(nucr, 2, NA=alpha)/paratf.adtf(1e-3, 0, NA=alpha), '-', c=[0, 0, 1], lw=0.5)
+    ax.plot([0,2],[0,0], 'k--', lw=0.25, zorder=1)
+
+    # Monopole
+    ax.plot(nucr, (paratf.jinc(0, nucr)/paratf.jinc(0, 0))**2, '-', c=[0, 1, 0], lw=1.5, zorder=0, alpha=1)        
+
+    ax.tick_params(direction='out', left=True, right=False, width=0.75)
+    ax.yaxis.set_ticks([-0.5, -0.25, 0, 0.25, 0.5, 0.75, 1.0])
+    if col == 0:
+        ax.set_yticklabels(['-0.5', '-0.25', '0','0.25','0.5','0.75','1'])
+    else:
+        ax.set_yticklabels([])
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/dpsf.py

@@ -5,10 +5,10 @@ import matplotlib.lines as lines
 import matplotlib.gridspec as gridspec
 import scipy.misc
 from scipy import special
+import paratf
 
 plt.rcParams["font.family"] = "serif"
 plt.rcParams["font.serif"] = "Times"
-
 
 inches = 2
 rows = 1
@@ -31,19 +31,22 @@ def an(krda, n):
 def hdet(krd, theta, alpha):
     return an(krd*alpha, 1)*np.sin(theta)**2 + 0.5*an(krd*alpha, 2)*(alpha**2)*(np.cos(theta)**2)
 
-alphas = [np.pi/8, np.pi/4, 3*np.pi/8]
-alpha_strs = ['\\pi/8', '\\pi/4', '3\\pi/8']
+alphas = [0.25, 0.5, 0.75]
+alpha_strs = ['0.25', '0.5', '0.75']
 for col in range(cols):
     alpha = alphas[col]
     ax = f.add_subplot(outer_grid[0, col])
-    ax.set_xlim([0,7])
+    ax.set_xlim([0,2])
     ax.set_ylim([0,1])
 
     thetas = [0, np.pi/8, np.pi/4, 3*np.pi/8, np.pi/2]
     theta_strs = ['0', '$\pi/8$', '$\pi/4$', '$3\pi/8$', '$\pi/2$']
     for theta in thetas:
-        krda = np.linspace(1e-3, 7, 100)
-        ax.plot(krda, hdet(krda/alpha, theta, alpha)/hdet(1e-3,np.pi/2,alpha), '-', c=[1 - theta/(np.pi/2), 0, 0], lw=0.5)
+        nucr = np.linspace(1e-3, 2, 100)
+        ax.plot(nucr, paratf.dpsf(nucr, theta, NA=alpha)/paratf.dpsf(1e-3, np.pi/2, NA=alpha), '-', c=[1 - theta/(np.pi/2), 0, 0], lw=0.5)
+
+    # Monopole
+    ax.plot(nucr, (paratf.jinc(0, nucr)/paratf.jinc(0, 0))**2, '-', c=[0, 1, 0], lw=1.5, zorder=0, alpha=1)        
 
     ax.tick_params(direction='out', left=True, right=False, width=0.75)
     ax.yaxis.set_ticks([0, 0.25, 0.5, 0.75, 1.0])
@@ -51,20 +54,24 @@ for col in range(cols):
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/paratf.py

@@ -1,0 +1,53 @@
+import numpy as np
+np.seterr(all='ignore')
+from scipy import special
+
+def rect(r):
+    return np.abs(r) < 0.5
+
+def jinc(n, r):
+    if n == 0:
+        zero_val = np.pi/4
+    else:
+        zero_val = 0
+    return np.where(r < 1e-5, zero_val, special.jn(n+1, np.pi*r)/(2*r))
+        
+def chat(n, nu):
+    if n == 0:
+        return np.where(nu < 1.0, 0.5*(np.arccos(nu) - nu*np.sqrt(1 - nu**2)), 0)
+    elif n == 1:
+        return np.where(nu < 1.0, 0.5*(np.arccos(nu) - nu*(3 - 2*(nu**2))*np.sqrt(1 - nu**2)), 0)
+    else:
+        return None
+
+def Lambda(l):
+    return np.sqrt(4*np.pi/(2*l + 1))
+
+def norm(NA, n, nuc):
+    return (12*nuc**2)/((np.pi*Lambda(0))*(2 + (NA/n)**2))
+    
+def dpsf(r, theta, NA=1.0, n=1.0, nuc=1.0):
+    A = norm(NA, n, nuc)
+    return A*(jinc(0, nuc*r)**2*np.sin(theta)**2 + (NA/n)**2*jinc(1, nuc*r)**2*np.cos(theta)**2)
+
+def sdtf(nu, theta, NA=1.0, n=1.0, nuc=1.0):
+    A = (norm(NA, n, nuc)/(nuc**2))
+    return A*(chat(0, nu/nuc)*np.sin(theta)**2 + (NA/n)**2*chat(1, nu/nuc)*np.cos(theta)**2)
+
+def adtf(r, l, NA=1.0, n=1.0, nuc=1.0):
+    A = Lambda(l)*norm(NA, n, nuc)/3    
+    if l == 0:
+        return A*(2*jinc(0, nuc*r)**2 + (NA/n)**2*jinc(1, nuc*r)**2)
+    elif l == 2:
+        return A*(-2*jinc(0, nuc*r)**2 + 2*(NA/n)**2*jinc(1, nuc*r)**2)
+    else:
+        return 0
+
+def satf(nu, l, NA=1.0, n=1.0, nuc=1.0):
+    A = Lambda(l)*norm(NA, n, nuc)/3    
+    if l == 0:
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/phantoms.py

@@ -1,0 +1,73 @@
+from paratf import *
+import numpy as np
+
+from scipy.special import *
+
+def ads_cone(l, theta_p, phi_p, delta):
+    if l == 0:
+        return Lambda(l)**(-1)
+    elif l % 2 == 0:
+        Ylm = np.real(sph_harm(0, l, phi_p, theta_p))
+        Pl = lpmv(-1, l, np.cos(delta))
+        total = np.real(Ylm*Pl/np.tan((delta)/2))
+        return total
+
+def phantom_rect(rx, ry, j, k):
+    D = 0.15*k+0.15
+    return rect((1/D)*np.sqrt((rx - j)**2 + (ry - k)**2))/(D**2)
+    
+def phantom1g(rx, ry, NA=0.5, n=1.0, nuc=10, dx=0.1):
+    out = np.zeros_like(rx)
+    for j in range(4):
+        for k in range(4):
+            out += dpsf(np.sqrt((rx - j)**2 + (ry - k)**2), j*np.pi/6,
+                        NA=NA, n=n, nuc=nuc)
+    return out
+
+def phantom2g(rx, ry, NA=0.5, n=1.0, nuc=10, dx=0.1):
+    freqs = np.fft.fftfreq(rx.shape[-1], d=dx)
+    nux, nuy = np.meshgrid(freqs, freqs)
+    nu = np.sqrt(nux**2 + nuy**2)
+
+    out = np.zeros_like(rx)
+    for j in range(4):
+        for k in range(4):
+            dd = phantom_rect(rx, ry, j, k)
+            sds = np.fft.fft2(dd)
+            filt = sdtf(nu, j*np.pi/6, NA=NA, n=n, nuc=nuc)
+            out += np.real(np.fft.ifft2(filt*sds))
+    return out
+
+def phantom2f(rx, ry):
+    out = np.zeros_like(rx)
+    for j in range(4):
+        for k in range(4):
+            out += phantom_rect(rx, ry, j, k)
+    return out
+    
+def phantom3g(rx, ry, NA=0.5, n=1.0, nuc=10, dx=0.1):
+    out = np.zeros_like(rx)
+    for l in [0, 2]:
+        for j in range(4):
+            for k in range(4):
+                Hlm = adtf(np.sqrt((rx - j)**2 + (ry - k)**2), l,
+                           NA=NA, n=n, nuc=nuc)
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/plot_phantoms.py

@@ -1,0 +1,156 @@
+from paratf import *
+from phantoms import *
+import matplotlib.pyplot as plt
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.gridspec as gridspec
+outer_gridspec = gridspec.GridSpec
+inner_gridspec = gridspec.GridSpecFromSubplotSpec
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+plt.rc('path',simplify_threshold=.0001)
+
+def plot_phantom(ph_i, phantom_func, x_head, x_labels, y_head, y_labels, y_tail=True):
+    # Simulation settings
+    lamb = 0.5 # um
+    NA = 0.75
+    n = 1.0
+    nuc = 2*NA/lamb
+    oversamp = 20
+    dx = 1/(oversamp*2*nuc)#0.05#0.005 # um
+    FOVmin = -1
+    FOVmax = 4
+
+    line = np.linspace(FOVmin, FOVmax, (FOVmax - FOVmin)/dx)
+    rx, ry = np.meshgrid(line, line)
+
+    # Plot settings
+    def xbraces(ax):
+        ax.text(-0.5, 4.65, x_head, ha='right', va='center', transform=ax.transData)
+        for x in range(4):
+            w = 0.4
+            h = 0.05
+            l1 = lines.Line2D([-w+x,w+x], [4.25, 4.25], c='k', lw=0.5, transform=ax.transData)
+            l2 = lines.Line2D([w+x,w+x], [4.25, 4.25-h], c='k', lw=0.5, transform=ax.transData)
+            l3 = lines.Line2D([-w+x,-w+x], [4.25-h, 4.25], c='k', lw=0.5, transform=ax.transData)
+            l4 = lines.Line2D([x,x], [4.25+h, 4.25], c='k', lw=0.5, transform=ax.transData)
+            f.lines.extend([l1, l2, l3, l4])
+            ax.text(x, 4.65, x_labels[x], ha='center', va='center', transform=ax.transData)
+
+    def ybraces(ax):
+        ax.text(4.75, 4.25, y_head, ha='center', va='center', transform=ax.transData, rotation=-90)
+        if y_tail:
+            ax.text(4.75, -1.5, '($\mu$m)', ha='center', va='center', transform=ax.transData, rotation=-90)
[…]

### 2018-12-11 papers/basic-theory/figures/paratfs/sdtf.py

@@ -1,0 +1,81 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines as lines
+import matplotlib.gridspec as gridspec
+import scipy.misc
+from scipy import special
+import paratf
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.serif"] = "Times"
+
+inches = 2
+rows = 1
+cols = 3
+widths = [1,1,1]
+heights = [1]
+hspace = 0.05
+wspace = 0.15
+
+f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
+                        inches*(np.sum(heights))))
+
+outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
+                               width_ratios=widths, height_ratios=heights,
+                               hspace=hspace, wspace=wspace)
+
+alphas = [0.25, 0.5, 0.75]
+alpha_strs = ['0.25', '0.5', '0.75']
+for col in range(cols):
+    alpha = alphas[col]
+    ax = f.add_subplot(outer_grid[0, col])
+    ax.set_xlim([0,1])
+    ax.set_ylim([-0.125,1])
+
+    thetas = [0, np.pi/8, np.pi/4, 3*np.pi/8, np.pi/2]
+    theta_strs = ['0', '$\pi/8$', '$\pi/4$', '$3\pi/8$', '$\pi/2$']
+    for theta in thetas:
+        nucr = np.linspace(1e-3, 1, 100)
+        ax.plot(nucr, paratf.sdtf(nucr, theta, NA=alpha)/paratf.sdtf(1e-3, np.pi/2, NA=alpha), '-', c=[1 - theta/(np.pi/2), 0, 0], lw=0.5)
+
+    ax.plot([0,2],[0,0], 'k--', lw=0.25, zorder=1)
+
+    # Monopole
+    ax.plot(nucr, paratf.chat(0, nucr)/paratf.chat(0, 0), '-', c=[0, 1, 0], lw=1.5, zorder=0, alpha=1)        
+
+    ax.tick_params(direction='out', left=True, right=False, width=0.75)
+    ax.yaxis.set_ticks([0, 0.25, 0.5, 0.75, 1.0])
+    if col == 0:
+        ax.set_yticklabels(['0','0.25','0.5','0.75','1'])
+    else:
+        ax.set_yticklabels([])
[…]

### 2018-12-11 papers/basic-theory/figures/satf/satf.py

@@ -1,79 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-import matplotlib.lines as lines
-import matplotlib.gridspec as gridspec
-import scipy.misc
-from scipy import special
-
-plt.rcParams["font.family"] = "serif"
-plt.rcParams["font.serif"] = "Times"
-
-
-inches = 2
-rows = 1
-cols = 3
-widths = [1,1,1]
-heights = [1]
-hspace = 0.05
-wspace = 0.15
-
-f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
-                        inches*(np.sum(heights))))
-
-outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
-                               width_ratios=widths, height_ratios=heights,
-                               hspace=hspace, wspace=wspace)
-
-def An(nu, n):
-    if n == 1:
-        return (2/np.pi)*(np.arccos(nu/2) - (nu/2)*np.sqrt(1 - (nu/2)**2))
-    elif n == 2:
-        return (2/np.pi)*(np.arccos(nu/2) - (3 - 2*((nu/2)**2))*(nu/2)*np.sqrt(1 - (nu/2)**2))
-
-def SATF(l, nu, alpha):
-    if l == 0:
-        return 7*(32*An(nu, 1) + 4*(alpha**2)*(An(nu, 1) + An(nu, 2)) + 3*(alpha**4)*An(nu, 2))
-    if l == 2:
-        return 4*np.sqrt(5)*(-16*An(nu, 1) + (alpha**2)*(An(nu, 1) + An(nu, 2)) + 3*(alpha**4)*An(nu, 2))
-    if l == 4:
-        return 8*(4*An(nu, 1) - 2*(alpha**2)*(An(nu, 1) + An(nu, 2)) + (alpha**4)*An(nu, 2))
-
-alphas = [np.pi/8, np.pi/4, 3*np.pi/8]
-alpha_strs = ['\\pi/8', '\\pi/4', '3\\pi/8']
-for col in range(cols):
-    alpha = alphas[col]
-    ax = f.add_subplot(outer_grid[0, col])
-    ax.set_xlim([0,2])
-    ax.set_ylim([-0.75,1])
-
-    lm_strs = ['$\ell=0$', '$\ell=2$', '$\ell=4$']
[…]

### 2018-12-11 papers/basic-theory/figures/stf/stf.py

@@ -1,81 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-import matplotlib.lines as lines
-import matplotlib.gridspec as gridspec
-import scipy.misc
-from scipy import special
-
-plt.rcParams["font.family"] = "serif"
-plt.rcParams["font.serif"] = "Times"
-
-
-inches = 2
-rows = 1
-cols = 3
-widths = [1,1,1]
-heights = [1]
-hspace = 0.05
-wspace = 0.15
-
-f = plt.figure(figsize=(inches*(np.sum(widths) + widths[0]*(wspace)*(cols - 1)),
-                        inches*(np.sum(heights))))
-
-outer_grid = gridspec.GridSpec(ncols=cols, nrows=rows,
-                               width_ratios=widths, height_ratios=heights,
-                               hspace=hspace, wspace=wspace)
-
-def A1(nu):
-    return (2/np.pi)*(np.arccos(nu/2) - (nu/2)*np.sqrt(1 - (nu/2)**2))
-
-def A2(nu):
-    return (2/np.pi)*(np.arccos(nu/2) - (3 - 2*((nu/2)**2))*(nu/2)*np.sqrt(1 - (nu/2)**2))
-
-def Hdet(nu, theta, alpha):
-    return A1(nu)*np.sin(theta)**2 + 0.5*A2(nu)*(alpha**2)*(np.cos(theta)**2)
-
-def hexc(theta, alpha):
-    return np.sin(theta)**2 + 0.5*(alpha**2)*(np.cos(theta)**2)
-
-def OTF(nu, theta, alpha):
-    return hexc(theta, alpha)*Hdet(nu, theta, alpha)
-
-alphas = [np.pi/8, np.pi/4, 3*np.pi/8]
-alpha_strs = ['\\pi/8', '\\pi/4', '3\\pi/8']
-for col in range(cols):
-    alpha = alphas[col]
-    ax = f.add_subplot(outer_grid[0, col])
-    ax.set_xlim([0,2])
-    ax.set_ylim([-0.25,1])
-
-    thetas = [0, np.pi/8, np.pi/4, 3*np.pi/8, np.pi/2]
-    theta_strs = ['0', '$\pi/8$', '$\pi/4$', '$3\pi/8$', '$\pi/2$']
-    for theta in thetas:
-        nu = np.linspace(1e-3, 2, 100)
[…]

### 2018-12-14 papers/basic-theory/paper/paper.tex
Rudolf's edits.

@@
 Fluorescence microscopes are widely used in the biological sciences for
-measuring ensembles of fluorescent molecules. While most fluorescence microscopy
-experiments are designed to measure only the spatial distribution of
-fluorophores, a growing number of experiments seek to measure both the spatial
-and angular distributions of fluorophores by the use of polarizers
-\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017} or
-point spread function engineering \cite{agrawal2012, zhang2018}.
+measuring ensembles of fluorescent molecules that label specific proteins and
+biologically important molecules. While most fluorescence microscopy experiments
+are designed to measure only the spatial distribution of fluorophores, a growing
+number of experiments seek to measure both the spatial and angular distributions
+of fluorophores by the use of polarizers \cite{vrabioiu2006, mattheyses2010,
+  mehta2016, mcquilken2017, zhanghao2017} or point spread function engineering
+\cite{agrawal2012, zhang2018}.
 
@@
 term to distinguish the monopole model from more realistic dipole and
-higher-order models. Despite their use in models, monopole absorber/emitters do
-not exist in nature. All physical fluorophores absorb and emit radiation with
-dipole or higher-order transitions, and these transitions are always oriented in
-space. For a classical mental model of fluorophores we imagine each dipole as a
-small oriented antenna (with incoherent absorption and emission moments) where
-electrons are constrained to move along a single direction. With this model we
-can argue classically that monopole radiators do not exist because they would
-violate the conservation of charge.
+higher-order models. Despite their use in models, electromagnetic monopole
+absorber/emitters do not exist in nature. All physical fluorophores absorb and
+emit radiation with dipole or higher-order moments, and these moments are always
+oriented in space. For a classical mental model of fluorophores we imagine each
+dipole as a small oriented antenna (with incoherent absorption and emission
+moments) where electrons are constrained to move along a single direction. With
+this model we can argue classically that monopole radiators do not exist because
+they would violate the conservation of charge.
 
@@
 
-All fluorescence microscopy techniques that use an \textit{optical point spread
-  function} or an \textit{optical transfer function} to model the mapping
+All fluorescence microscopy models that use an \textit{optical point spread
+  function} or an \textit{optical transfer function} to describe the mapping
 between the fluorophores and the irradiance on the detector implicitly make the
@@
 
-This work lies at the intersection of three fluorescence microscopy communities:
-(1) the spatial ensemble imaging community where many fluorophores are imaged in
-parallel and the goal is to find their concentration throughout the sample, (2)
-the spatio-angular ensemble community where many fluorophores are imaged in
-parallel and the goal is to find their concentration and orientation, and (3)
-the SMLM community where fluorophores are sparse in the sample and the goal is
-to find the position of each fluorophore. We briefly review how these three
-communities use the monopole and scalar approximations.
+This work lies at the intersection of three subfields of fluorescence
+microscopy: (1) spatial ensemble imaging where fluorophores are imaged as
+ensembles and the goal is to find their concentration as a function of position
+in the sample, (2) the spatio-angular ensemble imaging where fluorophores are
+imaged as ensembles and the goal is to find their concentration and orientation
+as a function of position in the sample, and (3) SMLM imaging where fluorophores
+are sparse in the sample and the goal is to find the position and orientation of
+each fluorophore. We briefly review how these three subfields use the monopole
+and scalar approximations.
 
@@
 the Born-Wolf model, and the Richards-Wolf model are approximate when applied to
-fluorescence microscopes because they only model monopole emitters.
+fluorescence microscopy data because they only model monopole emitters.
 Deconvolution algorithms that use these models may make biased estimates of
@@
 
-The most precise experiments in the SMLM community do not adopt the scalar or
-monopole approximations. Although many works have applied dipole models with
-vector optics, fewer have considered the effects of rotational or spatial
-diffusion, and to our knowledge no works have considered both rotational and
-spatial diffusion together. We will see that the dipole transfer functions are
-useful tools for incorporating angular and spatial diffusion into SMLM
-simulations and reconstructions.
-
-In this work we place these three communities on a common theoretical footing.
-We begin in section \ref{sec:theory} by formulating the imaging problem
+The most precise experiments in SMLM imaging do not adopt the scalar or monopole
+approximations. Although many works have applied dipole models with vector
+optics, fewer have considered the effects of rotational or spatial diffusion,
+and to our knowledge no works have considered both rotational and spatial
+diffusion together. We will see that the dipole transfer functions are useful
+tools for incorporating angular and spatial diffusion into SMLM simulations and
+reconstructions.
+
+In this work we place these three subfields on a common theoretical footing. We
+begin in section \ref{sec:theory} by formulating the imaging problem
 mathematically. We start with an abstract description of fluorescence imaging
@@
 The above discussion is quite abstract, but it is a powerful point of view that
-will enable us to unify the analysis of spatio-angular fluorescence microscopes.
+will enable us to unify the analysis of spatio-angular fluorescence imaging.
 In section \ref{sec:monopole} we will demonstrate the formalism by examining a
@@
   \includegraphics[scale=1.0]{../figures/monopole-transfer-functions/monopole-transfer-functions.pdf}
-  \caption{The incoherent monopole transfer functions are related by a
+  \caption{The monopole transfer functions are related by a
     two-dimensional Fourier transform (right column). The coherent monopole
@@
   \includegraphics[scale=1.0]{../figures/transfer-functions/transfer-functions.pdf}
-  \caption{There is one incoherent transfer function for each set of
-    object-space basis functions, and these transfer functions are related by
-    two-dimensional and spherical Fourier transforms---see center and right
-    columns. There is an additional pair of coherent transfer functions that
-    are useful for calculating the incoherent transfer functions---see left column.}
+  \caption{There is one transfer function for each set of object-space basis
+    functions, and these transfer functions are related by two-dimensional and
+    spherical Fourier transforms---see center and right columns. There is an
+    additional pair of coherent transfer functions that are useful for
+    calculating the transfer functions---see left column.}
    \label{fig:transfer-functions}
@@
 \end{align}
-where $P_\ell^m(\cos\theta)$ are the associated Legendre polynomials with the
+where $P_\ell^m(\cos\vartheta)$ are the associated Legendre polynomials with the
 Condon-Shortley phase
@@
 \intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
-  \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
+  \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \nonumber\\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
   \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu| (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 

### 2018-12-16 papers/basic-theory/paper/paper.tex
Rudolf's second round with discussion comments.

@@
 
-\title{Spatio-angular fluorescence microscopy I. Basic theory (Draft: \today)}
+\title{Spatio-angular fluorescence microscopy\\ I. Basic theory (Draft: \today)}
 
@@
 \section{Introduction}
-Fluorescence microscopes are widely used in the biological sciences for
-measuring ensembles of fluorescent molecules that label specific proteins and
-biologically important molecules. While most fluorescence microscopy experiments
-are designed to measure only the spatial distribution of fluorophores, a growing
-number of experiments seek to measure both the spatial and angular distributions
-of fluorophores by the use of polarizers \cite{vrabioiu2006, mattheyses2010,
+Fluorescence microscopes are widely used in the biological sciences for imaging
+fluorescent molecules that label specific proteins and biologically important
+molecules. While most fluorescence microscopy experiments are designed to
+measure only the spatial distribution of fluorophores, a growing number of
+experiments seek to measure both the spatial and angular distributions of
+fluorophores by the use of polarizers \cite{vrabioiu2006, mattheyses2010,
   mehta2016, mcquilken2017, zhanghao2017} or point spread function engineering
@@
   approximation} is not in widespread use, we think it accurately describes the
-way many models of fluorescence microscopes treat fluorophores, and we use the
+way many models of fluorescence microscopy treat fluorophores, and we use the
 term to distinguish the monopole model from more realistic dipole and
@@
 dipole as a small oriented antenna (with incoherent absorption and emission
-moments) where electrons are constrained to move along a single direction. With
-this model we can argue classically that monopole radiators do not exist because
-they would violate the conservation of charge.
+moments) where electrons are constrained to move along a single direction. % With
+% this model we can argue classically that monopole radiators do not exist because
+% they would violate the conservation of charge.
 
@@
 unconstrained rotating fluorophores. While both of these situations yield
-monopole-like samples, neither yields a sample that is perfectly described by
+monopole-like emitters, neither yields emitters that are perfectly described by
 the monopole model. In this work we investigate the dipole model of fluorophores
@@
 three-dimensional vector field, but if the electric fields are random or
-parallel a scalar field is sufficient, and we can replace the vector-valued electric
-field, $\mb{E}$, with a scalar-valued field, $U$.%  is the scalar approximation,
-% and this approximation is only justified if the fields are randomly or uniformly
-% polarized.
+completely parallel, a scalar field is sufficient, and we can replace the
+vector-valued electric field, $\mb{E}$, with a scalar-valued field, $U$.
 
@@
 system, but it is an optical model so when it is applied to fluorescence
-microscopes the monopole approximation is assumed. % As previously mentioned,
-% several works in the SMLM community have modeled and applied dipole point spread
-% functions that do not make the monopole or scalar approximations, but to our
-% knowledge no works have considered dipole transfer functions.
+microscopes the monopole approximation is assumed.
 
 This work lies at the intersection of three subfields of fluorescence
-microscopy: (1) spatial ensemble imaging where fluorophores are imaged as
-ensembles and the goal is to find their concentration as a function of position
-in the sample, (2) the spatio-angular ensemble imaging where fluorophores are
-imaged as ensembles and the goal is to find their concentration and orientation
-as a function of position in the sample, and (3) SMLM imaging where fluorophores
-are sparse in the sample and the goal is to find the position and orientation of
-each fluorophore. We briefly review how these three subfields use the monopole
-and scalar approximations.
+microscopy: (1) spatial ensemble imaging where each resolvable volume contains
+many fluorophores and the goal is to find the concentration of fluorophores as a
+function of position in the sample, (2) spatio-angular ensemble imaging where
+each resolvable volume contains many fluorophores and the goal is to find the
+concentration and orientation of fluorophores as a function of position in the
+sample, and (3) SMLM imaging where fluorophores are sparse in the sample and the
+goal is to find the position and orientation of each fluorophore. We briefly
+review how these three subfields use the monopole and scalar approximations.
 
 The large majority of fluorescence microscopes are used to image ensembles of
-fluorophores, and all existing restoration techniques make either or both of the
-monopole and scalar approximations. As discussed above, the Gibson-Lanni model,
-the Born-Wolf model, and the Richards-Wolf model are approximate when applied to
-fluorescence microscopy data because they only model monopole emitters.
-Deconvolution algorithms that use these models may make biased estimates of
-fluorophore concentrations since they ignore the dipole excitation and emission
-of fluorophores, but we will see that these effects are small when the sample
-contains many randomly oriented fluorophores within a resolvable volume or
-unconstrained rotating fluorophores.
+fluorophores, and most existing modeling techniques make use of the monopole
+approximation, the scalar approximation, or both. As discussed above, the
+Gibson-Lanni model, the Born-Wolf model, and the Richards-Wolf model are
+approximate when applied to fluorescence microscopy data because they only model
+monopole emitters. Deconvolution algorithms that use these models may make
+biased estimates of fluorophore concentrations since they ignore the dipole
+excitation and emission of fluorophores, but we will see that these effects are
+small when the sample contains many randomly oriented fluorophores within a
+resolvable volume or unconstrained rotating fluorophores.
 
 A small but growing group of microscopists is interested in measuring the
-orientation and position of ensembles of fluorophores \cite{vrabioiu2006,
-  mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}. These techniques
-typically use polarizers to make multiple measurements of the same object, then
-they use a model of the dipole excitation and emission processes
-\cite{fourkas2001} to recover the orientation of fluorophores using pixel-wise
-arithmetic. Although these studies do not adopt the scalar or monopole
-approximations for the angular part of the problem, they adopt both
-approximations when they consider the spatial part of the problem. Existing
-works either ignore the spatial reconstruction problem \cite{vrabioiu2006,
-  mattheyses2010, mehta2016, mcquilken2017} or assume that the spatial and
-angular reconstruction problems can be solved sequentially
+prevailing orientation and position of ensembles of fluorophores
+\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}.
+These techniques typically use polarizers to make multiple measurements of the
+same object with different polarizer orientations, then they use a model of the
+dipole excitation and emission processes \cite{fourkas2001} to recover the
+orientation of fluorophores using pixel-wise arithmetic. Although these studies
+do not adopt the scalar or monopole approximations for the angular part of the
+problem, they adopt both approximations when they consider the spatial part of
+the problem. Existing works either ignore the spatial reconstruction problem
+\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017} or assume that the
+spatial and angular reconstruction problems can be solved sequentially
 \cite{zhanghao2017}.
@@
 
-In this work we place these three subfields on a common theoretical footing. We
-begin in section \ref{sec:theory} by formulating the imaging problem
-mathematically. We start with an abstract description of fluorescence imaging
-systems and extend the usual monopole imaging model to dipoles. Along the way we
-introduce transfer functions that will allow us to efficiently analyze
-spatio-angular microscopes. In section \ref{sec:results} we use the mathematical
-tools we developed in section \ref{sec:theory} to analyze and simulate a
-single-view fluorescence microscope, and we demonstrate our techniques with four
-simple phantoms. Finally, in section \ref{sec:discussion} we discuss the results
-and their broader implications.
+In the present work we begin to place these three subfields on a common
+theoretical footing. First, in section \ref{sec:theory}, we assemble the
+mathematical tools for formulating the imaging problem. We start with an
+abstract description of fluorescence imaging systems and extend the usual
+monopole imaging model to dipoles. Along the way we introduce transfer functions
+that will allow us to efficiently analyze spatio-angular microscopes. In section
+\ref{sec:results} we analyze and simulate a single-view fluorescence microscope,
+and we demonstrate our techniques with four simple phantoms. Finally, in section
+\ref{sec:discussion} we discuss the results and their broader implications.
+
+In this paper we focus on modeling an extremely simple optical system---a
+single-view fluorescence microscope without polarizers. In future papers of this
+series we will extend our models to include polarizers and multi-view
+microscopes. Additionally, we have restricted this paper to the forward
+problem---the mapping between a known object and the data. In future papers we
+will consider the inverse problem, and the singular value decomposition (SVD)
+will play a central role.
 
@@
 scalar-valued field in a Fourier plane of the detector with appropriate scaling.
-% We have chosen the symbol $\taup$ as the coordinate for the coherent
-% transfer function because the Fourier plane of the detector is often called the
-% \textit{pupil plane}.
 
@@
    \mb{p}(\rp, \so) \propto
-   % \begin{bmatrix}
-   %   \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\cos\phi_p\\
-   %   \tilde{C}_2\left(\frac{r_p}{f_o}\right)\sin(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)\cos(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)\sin\phi_p\\
-   %   0&0&0\\     
-   % \end{bmatrix}
    \begin{bmatrix}
@@
 \begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
  \centering
@@
  \begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
  \centering
@@
   \begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
  \centering
@@
 (or higher) moments, but this extension requires a completely new set of basis
-functions while the spherical harmonics can be extended by simply adding higher order
-terms. Second, the spherical harmonics are orthonormal, which will allow us to
-deploy invaluable tools from linear algebra---linear subspaces, rank,
-decompositions, etc.--- to analyze and compare microscope designs. Finally,
-using the spherical harmonics provides access to a set of fast algorithms. The
-naive expansion of an arbitrary discretized $N$ point spherical function onto
-spherical harmonics (or second moments) requires a $\mc{O}(N^2)$ matrix
-multiplication, while pioneering work by Driscoll and Healy \cite{driscoll1994}
-showed that the forward discrete fast spherical harmonic transform can be
-computed with a $\mc{O}(N(\log N)^2)$ algorithm and its inverse can be computed
-with a $\mc{O}(N^{3/2})$ algorithm. To our knowledge no similarly fast
-algorithms exist for expansion onto the higher-order moments.
+functions while the spherical harmonics can be extended by simply adding higher
+order terms. Second, the spherical harmonics are orthonormal, which will allow
+us to deploy invaluable tools from linear algebra---linear subspaces, rank, SVD,
+etc.--- to analyze and compare microscope designs. Finally, using the spherical
+harmonics provides access to a set of fast algorithms. The naive expansion of an
+arbitrary discretized $N$ point spherical function onto spherical harmonics (or
+second moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering
+work by Driscoll and Healy \cite{driscoll1994} showed that the forward discrete
+fast spherical harmonic transform can be computed with a $\mc{O}(N(\log N)^2)$
+algorithm and its inverse can be computed with a $\mc{O}(N^{3/2})$ algorithm. To
+our knowledge no similarly fast algorithms exist for expansion onto the
+higher-order moments.
 
@@
 Spatial imaging systems have a spatial bandwidth that characterizes the highest
-spatial frequency that the system can image. Similarly, angular imaging systems
-have an angular bandwidth that characterizes the highest angular frequency that
-the system can image, but in the angular case there are two different types of
-angular bandwidths that we call the $\ell$- and $m$-bandwidth. The $\ell$-bandwidth
-can be interpreted in a similar way to the spatial bandwidth---it characterizes
-the smallest angular features that the imaging system can measure. The
-$m$-bandwidth does not have a direct analog in the spatial domain---it
-characterizes the angular uniformity of the imaging system. If the $\ell$- and
-$m$-bandwidths are equal then the imaging system can be said to have an 
-$\textit{isotropic angular bandwidth}$.
+spatial frequency that the system can transfer between object and data space.
+Similarly, angular imaging systems have an angular bandwidth that characterizes
+the highest angular frequency that the system can transfer, but in the angular case
+there are two different types of angular bandwidths that we call the $\ell$- and
+$m$-bandwidth. The $\ell$-bandwidth can be interpreted in a similar way to the
+spatial bandwidth---it characterizes the smallest angular features that the
+imaging system can measure. The $m$-bandwidth does not have a direct analog in
+the spatial domain---it characterizes the angular uniformity of the imaging
+system. If the $\ell$- and $m$-bandwidths are equal then the imaging system can
+be said to have an $\textit{isotropic angular bandwidth}$.
 
@@
 
-The microscope we considered in this work has an $\ell$-bandwidth of $\ell_c = 2$
-and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic angular
-bandwidth. In future work we will consider several approaches to improving the
-angular bandwidths in detail, but we briefly mention that non-paraxial
-microscopes, microscopes with polarizers on the illumination or detection paths,
-and multiview microscopes all have higher angular bandwidths than the microscope
-considered here.
+The microscope we considered in this work has an $\ell$-bandwidth of
+$\ell_c = 2$ and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic
+angular bandwidth. In future work we will consider several approaches to
+improving the angular bandwidths in detail, but we briefly mention that
+non-paraxial microscopes, microscopes with polarizers in the illumination or
+detection paths, and multiview microscopes all have higher angular bandwidths
+than the microscope considered here.
 
@@
 lifetimes, and interactions between fluorophores among others. Because of this
-long list of unknown effects, real experiments will likely require extensions of
-the models developed here.
+long list of unconsidered effects, real experiments will likely require
+extensions of the models developed here.
 
@@
 
-% We briefly show how two properties of spherical functions propagate to the
-% spherical Fourier transform. First, the spherical harmonic coefficients of
-% spherical functions that can be written entirely as a function of the
-% inclination angle $\vartheta$ are zero when $m\neq0$ because
-% \begin{align}
-%   \int_{\mbb{S}^2}d\mh{s}\, f(\vartheta)Y_\ell^{m*}(\mh{s}) &= \int_0^{2\pi}d\phi\, \text{exp}[-im\varphi]\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta),\\ &= \delta_{m0}\int_0^{\pi}d\vartheta\, \sin\vartheta f(\vartheta)P_\ell^m(\cos\vartheta).
-% \end{align}
-% Second, the spherical harmonic coefficients of spherical functions that are
-% symmetric under inversion $f(\mh{s}) = f(-\mh{s})$ are zero when $\ell$ is odd
-% because $Y_\ell^m(-\so) = (-1)^\ell Y_\ell^m(\mh{s})$, so if $\ell$ is odd then
-% \begin{align}
-%   \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) &= \int_{\mbb{S}^2/2}d\mh{s}\, f(+\mh{s})Y_{2n+1}^{m*}(+\mh{s}) + \int_{\mbb{S}^2/2}d\mh{s}\, f(-\mh{s})Y_{2n+1}^{m*}(-\mh{s}),\\
-% &=\int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(+\mh{s}) - \int_{\mbb{S}^2/2}d\mh{s}\, f(\mh{s})Y_{2n+1}^{m*}(\mh{s}) = 0.                                                                
-% \end{align}
 \section{Relationships between special functions} \label{sec:special}
@@
 \end{align}
-% This integral will be difficult to evaluate unless we change coordinates to
-% exploit the axis of symmetry $\mh{s}'$. The key idea is that
-% $f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)$ is a function of
-% $\mh{s}\cdot\mh{s}'$ so it is a one dimensional function on the domain [-1,1]
-% that can be expanded in terms of Legendre polynomials (a Fourier-Legendre
-% series)
-% \begin{align}
-%   f_{\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta) = \sum_{\ell = 0}^{\infty}F_{\ell\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta)P_{\ell}(\mh{s}\cdot\mh{s}').
-% \end{align}
-% We can find the coefficients $F_{\ell\text{(cone)}}(\mh{s}\cdot\mh{s}', \Delta)$
-% using Fourier's trick---multiply both sides by $P_{\ell}(\mh{s}\cdot\mh{s}')$,
-% integrate over [-1,1], and exploit orthogonality
-% $\int_{-1}^{1}dx\,P_{\ell}(x)P_{\ell'}(x) = \frac{2}{2\ell +
-%   1}\delta_{\ell\ell'}$ to find that
-% \begin{align}
-%   F_{\ell\text{(cone)}}(x, \Delta) = \frac{2\ell + 1}{2}\int_{-1}^{1}dx\, f_{\text{(cone)}}(x, \Delta)P_\ell(x). \label{eq:legendre}
-% \end{align}
-% Plugging Eq. \eqref{eq:doublecone} into Eq. \eqref{eq:legendre} yields
-% \begin{align}
-%   F_{\ell\text{(cone)}}(x, \Delta) = \frac{2\ell + 1}{4\pi(1-\cos\Delta)}\int^{1}_{\cos\Delta}dx\, P_\ell(x). 
-% \end{align}
-% The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
-% \begin{align}
-%   \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
-% \begin{cases}
-%   1 - \cos\Delta\,, &\ell = 0\,,\\
-%   \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
-% \end{cases}
-% \end{align}
-% where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
-% $m=-1$, not an inverse Legendre polynomial.
 

### 2018-12-17 notes/2018-12-10-angular-svd/report/report.tex
Angular svd notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\usepackage[linesnumbered,ruled]{algorithm2e}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{bold-extra}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\newcommand{\argmax}{\arg\!\max}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathfrak{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\sd}{\mathbf{\hat{s}}_d}
\providecommand{\pp}{\mathbf{\hat{p}}}
\providecommand{\rb}{\mathbf{r}_b}
\providecommand{\rbm}{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{\mathfrak{r}}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\ms}[1]{\mathsf{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\tv}{\texttt{v}}
\providecommand{\tx}[1]{\text{#1}}
\providecommand{\tb}[1]{\textbf{#1}}
\providecommand{\ttt}[1]{\texttt{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bp}{\bs{\rho}}
\providecommand{\p}{\mh{p}}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[H]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Measuring the angular dipole spectrum with arbitrary\\
  polarized illumination microscopes\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
  % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-3em}\today\vspace{-1em}}
\maketitle
\section{Forward model in a delta function basis}
We develop and analyze a simplified model of polarized excitation fluorescence
microscopes with arbitrary angular designs. We simplify the complete problem by
considering large objects and ignoring the irradiance pattern on the detector
(we effectively integrate over a few pixels). These simplifications are
equivalent to the implicit assumptions made by the majority of polarized
fluorescence microscopists. Our main goal is to improve our intuition for the
angular band limit of arbitrary microscopes and to incorporate light-sheet
tilting into our model.

With these simplifications we can model a continuous-to-continuous polarized
excitation fluorescence microscope system as
\begin{align}
  g(\sd, \pp) = \ints{2}d\so\, h(\sd,\pp;\so)f(\so),\label{eq:fwd}
\end{align}
where $\so$ is an orientation in the object, $f(\so)$ is the angular dipole
density (with units of sr${}^{-1}$), $\pp$ is the orientation of an excitation
polarizer, $\sd$ is the orientation of the detection optical axis, $g(\sd, \pp)$
is the measured irradiance with detection optical axis $\sd$ and excitation
polarization $\pp$. Equation \eqref{eq:fwd} assumes that object space is
$\mbb{U} = \mbb{L}_2(\mbb{S}^2)$---functions on the sphere---and data space is
$\mbb{V} = \mbb{L}_2(\mbb{S}^2 \times \mbb{S}^1)$---functions on the product
space of a sphere and a circle (a doughnut made of Timbits!).

Our next task is to find the form of the kernel $h(\sd,\pp;\so)$. We know that
the kernel is separable into excitation and detection parts so
\begin{align}
  h(\sd, \pp;\so) = h^{\text{exc}}(\pp;\so)h^{\text{det}}(\sd;\so). \label{eq:kern}
\end{align}
We restrict ourselves to low-NA excitation (like light-sheet excitation), which
gives the following excitation kernel
\begin{align}
  h^{\text{exc}}(\pp\cdot\so) \propto (\pp\cdot\so)^2. \label{eq:exckern}
\end{align}
In other words, the probability of exciting a fluorophore oriented along $\so$
with light polarized along $\pp$ is proportional to $(\pp\cdot\so)^2$---a
familiar $\cos^2\theta$ dependence where $\theta$ is the angle between $\pp$ and
$\so$. Notice that the excitation kernel is rotationally symmetric, so we can
write it as a function of $\pp\cdot\so$.

The detection kernel is given by
\begin{align}
  h^{\text{det}}(\sd,\so) = \ints{2}d\mh{s}\,\Pi\left(\frac{\mh{s}\cdot\sd}{\cos\alpha}\right)(\mh{s}\cdot\sd)^{-1/2}[1 - (\mh{s}\cdot\so)^2], \label{eq:detkern}
\end{align}
where the $[1 - (\mh{s}\cdot\so)^2]$ term models the familiar $\sin^2\vartheta$
dependence of dipole radiation where $\vartheta$ is the angle between $\sd$ and
$\so$, the $(\mh{s}\cdot\sd)^{-1/2}$ term models the apodization of an aplanatic
objective, and the integral over
$\Pi\left(\frac{\mh{s}\cdot\sd}{\cos\alpha}\right)$ models the finite aperture
of the objective with $\text{NA} = n_o\sin\alpha$. In Appendix
\ref{sec:spherical} we evaluate this integral in closed form to find that
\begin{align}
  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so).
\end{align}
The detection kernel is rotationally symmetric, so it can be written as a
function of $\sd\cdot\so$. For very low NA the detection kernel reduces to
$[1 - (\mh{s}\cdot\so)^2]$ as we would expect.

\section{Forward model in a spherical harmonic basis} \label{sec:shsec}We can rewrite the right-hand side of Eq. \eqref{eq:fwd} in a spherical harmonic
basis by applying the generalized Plancherel theorem for spherical functions
\begin{align}
  g(\sd, \pp) = \sum_{\ell m}H_\ell^m(\sd, \pp)F_\ell^m,\label{eq:fwdsh}
\end{align}
where we have defined the \textit{dipole angular transfer function} as
\begin{align}
  H_\ell^m(\sd, \pp) = \ints{2}d\so\, h(\sd,\pp;\so)Y_\ell^{m*}(\so),
\end{align}
and the \textit{dipole angular spectrum} as
\begin{align}
  F_\ell^m = \ints{2}d\so\, f(\so)Y_\ell^{m*}(\so).
\end{align}

Our remaining task is to calculate the dipole angular transfer function. We can
start by expanding the kernel into excitation and detection parts
\begin{align}
  H_\ell^m(\sd, \pp) = \ints{2}d\so\, h^{\text{exc}}(\pp\cdot\so)h^{\text{det}}(\sd\cdot\so)Y_\ell^{m*}(\so). 
\end{align}
We can expand both the excitation and detection kernels into a sum of spherical harmonics (a Laplace series)
\begin{align}
    H_\ell^m(\sd, \pp) = \ints{2}d\so\, \left[\sum_{\ell' m'}H_{\ell'}^{m',\text{exc}}(\pp\cdot\so)Y_{\ell'}^{m'}(\so)\right]\left[\sum_{\ell'' m''}H_{\ell''}^{m'',\text{det}}(\sd\cdot\so)Y_{\ell''}^{m''}(\so)\right]Y_\ell^{m*}(\so),\label{eq:triple}
\end{align}
where $H_{\ell'}^{m',\text{exc}}(\pp\cdot\so)$ and $H_{\ell''}^{m'',\text{det}}(\sd\cdot\so)$ are the spherical harmonic transforms of the excitation and detection kernels
\begin{align}
  H_{\ell'}^{m',\text{exc}}(\pp) &= \ints{2}d\so\, h^{\text{exc}}(\pp\cdot\so)Y_{\ell'}^{m'*}(\so),\label{eq:sh1}\\
  H_{\ell''}^{m'',\text{det}}(\sd) &= \ints{2}d\so\, h^{\text{det}}(\sd\cdot\so)Y_{\ell''}^{m''*}(\so)\label{eq:sh2}.
\end{align}
In Appendix B we evaluate these spherical Fourier transforms as
\begin{align}
    H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
\end{align}

We continue simplifying Eq. \eqref{eq:triple} by rewriting it as
\begin{align}
    H_\ell^m(\sd, \pp) = \sum_{\ell' m'}\sum_{\ell'' m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd)\ints{2}d\so\, Y_\ell^{m*}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).\label{eq:triple2}
\end{align}
We can simplify this equation further as
\begin{align}
    H_\ell^m(\sd, \pp) = \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd),\label{eq:triple3}
\end{align}
where $G_{\ell,\ell',\ell''}^{m,m',m''}$ are the Gaunt coefficients (sometimes
called the tripling coefficients or triple integrals of the spherical harmonics)
defined by
\begin{align}
  G_{\ell,\ell',\ell''}^{m,m',m''} = \ints{2}d\so\, Y_\ell^{m}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).
\end{align}
Equation \eqref{eq:triple3} is a key result because it allows us to calculate
the dipole angular transfer function from the excitation and detection angular
transfer functions.

We can draw some general conclusions about the band limits of this type of
imaging system by examining the properties of the Gaunt coefficients. First, the
Gaunt coefficient can only be non-zero when the coefficients $\ell$, $\ell'$,
and $\ell''$ satisfy the \textit{triangle condition}---each of the three
coefficients is between the sum and difference of the other two. The most
relevant condition for us is 
\begin{align}
  |\ell' - \ell''| \leq \ell \leq \ell' + \ell'', \label{eq:cond1}
\end{align}
which means that we can only have non-zero coefficients for $0\leq \ell \leq 4$
since $0\leq \ell' \leq 2$ and $0\leq \ell'' \leq 2$. Also, the Gaunt
coefficients can only be non-zero when the $\ell, \ell'$, and $\ell''$ form an
even sum
\begin{align}
  \ell + \ell' + \ell'' = 2n, \quad \text{for}\, n \in \mbb{N}, \label{eq:cond2}
\end{align}
which ensures inversion symmetry. Finally, the Gaunt coefficients can only be
non-zero when each $\ell$ is less than the absolute value of the corresponding
$m$
\begin{align}
  \ell \leq |m|,\quad\ell' \leq |m'|,\quad\ell'' \leq |m''|.\label{eq:cond3}
\end{align}
These conditions are obvious if you consider that the spherical harmonics are
zero (or undefined) when these conditions are not satisfied.

Given that $0\leq \ell' \leq 2$ and $0 \leq \ell'' \leq 2$ for our measurements, the
conditions in Eqs. \eqref{eq:cond1}--\eqref{eq:cond3} imply that the dipole
angular transfer function has at most 15 terms---1 for the $\ell=0$ band, 5 for
the $\ell=2$ band, and 9 for the $\ell=4$ band.

Note that a single choice for a measurement $\sd$ and $\pp$ can have 15 non-zero
terms in the dipole angular transfer function if both $\sd$ and $\pp$ do not lie
on a node (zero) of any of the $\ell = 2$ spherical harmonics. I mention this to
emphasize that the number of terms in the dipole angular transfer function has
little to no bearing on how much we can measure about the object---the choice of
coordinate system changes the nodes of the spherical harmonics and our results
should never depend on a choice of coordinates. The object space singular
vectors are the functions that we care about when we ask: what can this instrument 
measure about the object?

Notice that all of our results so far are completely coordinate-free---we have
used unit vectors everywhere instead of Cartesian or spherical coordinates.

\section{Continuous-to-discrete model}
So far we have modeled the continuous data space
$\mbb{V} = \mbb{L}_2(\mbb{S}^2 \times \mbb{S}^1)$. Now we consider discrete
samples of this data space with the following forward model
\begin{align}
  g_i = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_i(\sd, \pp)\ints{2}d\so\,h(\sd,\pp;\so)f(\so),\label{eq:discrete}
\end{align}
where $g_i$ is a discrete set of $M$ measurements and $w_i(\sd, \pp)$ is the
``sampling aperture'' that indicates which part of data space $(\sd, \pp)$ we
sample during the $i$th measurement. For example, if we have a detector along
the $\mh{z}$ axis and we illuminate with $\mh{x}$ polarized light for the first
measurement and $\mh{y}$ polarized light for the second measurement, then the
sampling aperture is
\begin{align}
  w_i^{(0)}(\sd,\pp) = \delta(\sd - \mh{z})[\delta(\pp - \mh{x})\delta_{i,0} + \delta(\pp - \mh{y})\delta_{i,1}].
\end{align}
It is more convenient to rewrite Eq. \eqref{eq:discrete} as
\begin{align}
  g_i = \ints{2}d\so\,h_i(\so)f(\so),
\end{align}
where
\begin{align}
h_i(\so) = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_i(\sd, \pp) h(\sd,\pp;\so).
\end{align}
In our example, the continuous-to-discrete kernel is given by 
\begin{align}
  h_i^{(0)}(\so) = h(\mh{z},\mh{x};\so)\delta_{i,0} + h(\mh{z},\mh{y};\so)\delta_{i,1}.
\end{align}
\section{Singular value decomposition}
Our continuous-to-discrete forward model can be written in any of the following
equivalent forms
\begin{align}
  \mb{g} &= \mc{H}\mb{f},\label{eq:f1}\\
  g_i &= \ints{2}d\so\,h_i(\so)f(\so),\label{eq:f2}\\
  g_i &= \sum_{\ell,m}H_{i,\ell}^m F_{\ell}^m,\label{eq:f3}\\
  g_i &= \sum_{j}H_{i,j}F_j.\label{eq:f4}
\end{align}
where Eq. \eqref{eq:f1} is the Hilbert-space form, Eq. \eqref{eq:f2} is the
delta-function basis form, Eq. \eqref{eq:f3} is the spherical harmonic basis
form, and Eq. \eqref{eq:f3} is the spherical harmonic basis form with a
collapsed index $j(\ell,m) = [\ell(\ell+1)]/2 + m$ (don't confuse the spherical
Fourier transform with collapsed coefficients, $F_j$, with the Fourier-Legendre
transform, $F_\ell$---I'll consider alternative notations but it should be clear
from the context). Notice that the last two forms blur the line between a CD
operator and a DD operator---we are still considering a continuous object space
and discrete data space, but we have found a basis that allows us to express
this mapping in a completely discrete way.

Similarly, we can write the discrete-to-continuous adjoint operator as
\begin{align}
  \mb{f} &= \mc{H}^{\dagger}\mb{g},\label{eq:a1}\\
  f(\so) &= \sum_i h_i(\so)g_i,\label{eq:a2}\\
  F_{\ell}^m &= \sum_{i} H_{i,\ell}^m g_i,\label{eq:a3}\\
  F_j &= \sum_i H_{i,j}g_i,\label{eq:a4}
\end{align}
where the forms of Eqs. \eqref{eq:a1}--\eqref{eq:a4} match with the forms of Eqs. \eqref{eq:f1}--\eqref{eq:f4}.

To find the object space singular functions we need to solve the eigenvalue
problem in one of its forms
\begin{align}
  \mc{H}^\dagger\mc{H}\mb{u}_n &= \mu_n\mb{u}_n,\label{eq:s1}\\
  \sum_i h_i(\so)\ints{2} d\so'\, h_i(\so')u_n(\so') &= \mu_n u_n(\so),\label{eq:s2}\\
  \sum_i H_{i,\ell}^m \sum_{\ell' m'}, H_{i,\ell'}^{m'} U_{n,\ell'}^{m'} &= \mu_n U_{n,\ell}^m,\label{eq:s3}\\
  \sum_i H_{i,j} \sum_{j'}, H_{i,j'} U_{n,j'} &= \mu_n U_{n,j},\label{eq:s4}
\intertext{where $n$ indexes the singular values and singular functions, and the letter
``u'' is used with varying type and arguments to denote the object space
singular functions. We can tighten up the notation by introducing kernels of the
operators and denoting them with the letter ``k'' with varying type and
arguments:}
  \mc{K}\mb{u}_n &= \mu_n\mb{u}_n,\label{eq:k1}\\
  \ints{2} d\so'\, k(\so, \so')u_n(\so') &= \mu_n u_n(\so),\label{eq:k2}\\
  \sum_{\ell' m'} K_{\ell,\ell'}^{m,m'} U_{n,\ell'}^{m'} &= \mu_n U_{n,\ell}^m,\label{eq:k3}\\
  \sum_{j'} K_{j,j'} U_{n,j'} &= \mu_n U_{n,j},\label{eq:k4}
\intertext{where}
  \mc{K} &= \mc{H}\mc{H}^\dagger,\\
  k(\so,\so') &= \sum_i h_i(\so)h_i(\so'),\\
  K_{\ell,\ell'}^{m,m'} &= \sum_i H_{i,\ell}^m H_{i,\ell'}^{m'},\\
  K_{j,j'} &= \sum_i H_{i,j}H_{i,j'}. \label{eq:kk4}
\end{align}

Now we are in position to solve for the object space singular functions and the
singular values. The first step is to calculate the matrix $K_{j,j'}$ using Eq.
\eqref{eq:kk4} and the closed form expressions for the dipole angular transfer
function, $H_{i,j}$, that we calculated in Sec. \ref{sec:shsec}. As we discussed
previously, $H_{i,j}$ is a $M\times15$ matrix so $K_{j,j'}$ is $15\times15$ and
it is computationally trivial (though impossible analytically) to calculate its
eigenvalues $\mu_n$ and eigenvectors $U_{n,j}$. With $U_{n,j}$ in hand we can
calculate the object-space singular vectors in a delta function basis using an
inverse spherical harmonics transform
\begin{align}
  u_n(\so) = \sum_{j}U_{n,j}Y_j(\so).
\end{align}

Before examining specific designs, we briefly examine and interpret the object
space singular vectors and singular values. The object space singular vectors
span the space of measurable objects---they are orthogonal (and can be chosen to
be orthonormal) because the operator $\mc{H}^\dagger\mc{H}$ is Hermitian. The
singular values tell us ``how efficiently'' each object space singular vector is
transferred through the system---the singular values (the eigenvalues of
$\mc{H}^\dagger\mc{H}$) are real (because $\mc{H}^\dagger\mc{H}$ is Hermitian)
and positive (because of the form of $\mc{H}^\dagger\mc{H}$ see Barrett 1.4.4).
In other words, $\mc{H}^\dagger\mc{H}$ is positive-semidefinite because the
eigenvalues are greater than or equal to zero.

One desirable condition for the operator $\mc{H}^\dagger\mc{H}$ is that it has
the maximum possible rank---$R=15$ in our case which is limited by the
excitation and detection physics. Achieving $R=15$ will always require at least
15 distinct measurements which is far more than we would like, so we search for
designs with fewer measurements.

Another desirable condition is that the object space singular vectors span
subspaces of $\mbb{L}_2(\mbb{S}^2)$ that are invariant under rotation. The
spherical harmonic bands are exactly the subspaces we're looking for: the
$\ell$th band spans a $(2\ell + 1)$-dimension space that is invariant under
rotation---equivalently, the $\ell$th band forms a ($2\ell +1$)-dimensional
representation for the rotation group. Furthermore, we know that the $\ell$th
band is an \textit{irreducible} representation of the rotation group, which
means that we cannot decompose the $\ell$th band of spherical harmonics to find
smaller representations of the rotation group. Therefore, if we would like our
object space singular vectors to span a rotationally-invariant subspace then we
need to take at least 1, 6, or 15 measurements.

% We would like to find the minimum number of measurements required for the object
% space singular vectors to span the $\ell=0$ and $\ell=2$ rotationally invariant
% subspaces. We always measure a linear combination of spherical harmonic
% coefficients from the $\ell=0,2,4$ bands, so we need to make more than 6
% measurements because we are always measuring at least one dimension from the
% $\ell=4$ band. A minimal measurement scheme will only have singular vectors that
% span a single dimension in the 9-dimensional $\ell=4$ subspace, so the minimum
% number of measurements for $\ell=0$ and $\ell=2$ rotationally invariant singular
% vectors is 7.

% How do we choose measurements with singular vectors that span a single dimension
% of the $\ell=4$ band? Surprisingly, the only requirement is that we fix $\pp$ or
% $\sd$. To demonstrate this we'll fix $\sd$ and choose a coordinate system so
% that $\mh{z} = \sd$. In this case the dipole excitation and dipole detection transfer
% functions (see Eqs. \eqref{eq:dipexc} and \eqref{eq:dipdet}) are
%   \begin{align}
%     H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc2}\\
%     H_{\ell''}^{m'',\text{det}}(\mh{z}) &\propto \delta_{m'',0}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet2}
% \end{align}
% Notice that the detection transfer function is only non-zero for $m'' = 0$
% because of our choice of coordinate system. To find the complete dipole angular transfer function we can use the equation
% \begin{align}
%     H_\ell^m(\mh{z}, \pp) = \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\mh{z}).
% \end{align}
% We care about the Gaunt coefficients that put terms in the $\ell=4$ band
% $G_{4,2,2}^{m,m',m''}$. We've chosen a coordinate system so that $m''=0$ and
% from a quick computation of the Gaunt coefficients we know that 
% \begin{align}
%   G_{4,2,2}^{m,m',0} = \frac{3}{7\sqrt{pi}}\delta_{m,0}\delta{m',0}
% \end{align}

\section{Specific designs (in progress)}
one-view epi,
one-view lightsheet,
two-view lightsheet,
two-view lightsheet two-tilt one-side,
two-view lightsheet two-tilt two-side,
two-view lightsheet three-tilt one-side two-tilt one-side.

\appendix
\section{Spherical integral of the product of two rotationally symmetric
  functions} \label{sec:spherical}

Consider two rotationally symmetric functions on the sphere
$f(\mh{s}\cdot\mh{s}')$ and $g(\mh{s}\cdot\mh{s}'')$. In this appendix we will
reduce integrals of the form
\begin{align}
  g(\mh{s}', \mh{s}'') = \ints{2}d\mh{s}\,h(\mh{s}\cdot\mh{s}')f(\mh{s}\cdot\mh{s}'')\label{eq:integral}
\end{align}
to two one-dimensional integrals. The key step is to expand both $f$ and $g$
into a Fourier-Legendre series
\begin{align}
  f(x) = \sum_{\ell=0}^{\infty}F_{\ell}P_{\ell}(x), \label{eq:flseries}
\end{align}
where $P_{\ell}(x)$ are the Legendre polynomials. We can find
the coefficients $F_{\ell}$ using Fourier's trick---multiply both sides of Eq.
\eqref{eq:flseries} by $P_{\ell}(x)$ (the Legendre polynomials
are real so we can ignore complex conjugates) then integrate over the interval
$[-1,1]$ and apply the orthogonality relation
\begin{align}
  \int_{-1}^1dx\,P_\ell(x)P_{\ell'}(x) = \frac{2}{2\ell+1}\delta_{\ell\ell'},
\end{align}
which implies that the Legendre polynomials are orthogonal but not orthonormal.
After applying these steps to Eq. \eqref{eq:flseries} we find that
\begin{align}
  F_{\ell} = \frac{2\ell+1}{2}\int_{-1}^1dx\,f(x)P_{\ell}(x).
\end{align}
The coefficients $F_{\ell}$ are often referred to as the
\textit{Fourier-Legendre transform} of $f(x)$. Now we can expand $f$ and $g$ in
Eq. \eqref{eq:integral} into two Fourier-Legendre series
\begin{align}
  g(\mh{s}', \mh{s}'') &= \ints{2}d\mh{s}\,\left[\sum_{\ell} H_\ell P_\ell (\mh{s}\cdot\mh{s}')\right]\left[\sum_{\ell'}F_{\ell'}P_{\ell'}(\mh{s}\cdot\mh{s}'')\right],\\
  &=\sum_{\ell}\sum_{\ell'} \ints{2}d\mh{s}\,H_\ell F_{\ell'} P_\ell (\mh{s}\cdot\mh{s}')P_{\ell'}(\mh{s}\cdot\mh{s}'').\label{eq:double}
\end{align}
The next step is to expand the Legendre polynomials in terms of spherical harmonics using the \textit{spherical harmonic addition theorem}
\begin{align}
  P_\ell(\mh{s}\cdot\mh{s}') = \frac{4\pi}{2\ell + 1}\sum_{m=-\ell}^{\ell}Y_\ell^m(\mh{s})Y_\ell^{m*}(\mh{s}'). \label{eq:shaddition}
\end{align}
Applying Eq. \eqref{eq:shaddition} to Eq. \eqref{eq:double} yields
\begin{align}
  g(\mh{s}',\mh{s}'') &= \sum_{\ell}\sum_{\ell'} \ints{2}d\mh{s}\,H_\ell F_{\ell'} \left[\frac{4\pi}{2\ell + 1}\sum_{m=-\ell}^{\ell}Y_\ell^m(\mh{s})Y_\ell^{m*}(\mh{s}')\right]\left[\frac{4\pi}{2\ell' + 1}\sum_{m=-\ell'}^{\ell'}Y_{\ell'}^{m'}(\mh{s}'')Y_{\ell'}^{m'*}(\mh{s})\right],\label{eq:one}\\ 
                      &= \sum_{\ell m}\sum_{\ell' m'} H_\ell F_{\ell'} \left[\frac{4\pi}{2\ell + 1}Y_\ell^{m*}(\mh{s}')\right]\left[\frac{4\pi}{2\ell' + 1}Y_{\ell'}^{m'}(\mh{s}'')\right]\ints{2}d\mh{s}Y_\ell^m(\mh{s})Y_{\ell'}^{m'*}(\mh{s}),\label{eq:two}\\
                      &= \sum_{\ell m}\sum_{\ell' m'} H_\ell F_{\ell'} \left[\frac{4\pi}{2\ell + 1}Y_\ell^{m*}(\mh{s}')\right]\left[\frac{4\pi}{2\ell' + 1}Y_{\ell'}^m(\mh{s}'')\right]\delta_{\ell\ell'}\delta_{m m'},\label{eq:three}\\
                      &= \sum_{\ell m}H_\ell F_{\ell} \left(\frac{4\pi}{2\ell + 1}\right)^2 Y_\ell^{m*}(\mh{s}')Y_{\ell'}^m(\mh{s}''),\label{eq:four}\\
  g(\mh{s}'\cdot\mh{s}'') &= \sum_{\ell}\frac{4\pi}{2\ell + 1}H_\ell F_{\ell} P_\ell(\mh{s}'\cdot\mh{s}'').\label{eq:five}
\end{align}
where we have (\ref{eq:one}-\ref{eq:two}) rearranged the equation,
(\ref{eq:two}-\ref{eq:three}) used the orthogonality of spherical harmonics,
(\ref{eq:three}-\ref{eq:four}) used the discrete sifting theorem then,
(\ref{eq:four}-\ref{eq:five}) applied the spherical harmonic addition theorem.

Eq. \eqref{eq:five} is a key result. In words, we can compute the spherical
integral of the product of two rotationally symmetric functions by taking their
Fourier-Legendre transforms then summing over $\ell$ with appropriate weights.
Perhaps surprisingly, the result only depends on $\mh{s}'\cdot\mh{s}''$ so it is
a rotationally symmetric function, too.

We can use this result to evaluate the detection kernel
\begin{align}
  h^{\text{det}}(\sd,\so) = \ints{2}d\mh{s}\,\Pi\left(\frac{\mh{s}\cdot\sd}{\cos\alpha}\right)(\mh{s}\cdot\sd)^{-1/2}[1 - (\mh{s}\cdot\so)^2]. \label{eq:kern}
\end{align}
Comparing Eq. \eqref{eq:kern} to Eq. \eqref{eq:integral} means that
\begin{align}
  f(\mh{s}\cdot\sd) &= 1 - (\mh{s}\cdot\so)^2,  \\
  h(\mh{s}\cdot\sd) &= \Pi\left(\frac{\mh{s}\cdot\sd}{\cos\alpha}\right)(\mh{s}\cdot\sd)^{-1/2}.
\end{align}
Evaluating the Fourier-Legendre transform of these functions gives
\begin{align}
  F_\ell &= \frac{2\ell + 1}{2}\int_{-1}^1dx\,(1 - x^{2})P_\ell(x) = \frac{2}{3}(\delta_{\ell,0} + \delta_{\ell,2}),\label{eq:fl}\\
  H_\ell &= \frac{2\ell + 1}{2}\int_{\cos\alpha}^1dx\,x^{-1/2}P_\ell(x) = (1 - \sqrt{\cos\alpha})\delta_{\ell,0} + \left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]\delta_{\ell,2}+ \cdots,\label{eq:hl}
\end{align}
Notice that we only need to evaluate the first two terms of $H_\ell$ since
only two terms of $F_\ell$ are non-zero. As we've noted before, the physical
dipole emission process is the band limiting step here---not the detection
process.

Plugging Eqs. \eqref{eq:fl} and \eqref{eq:hl} into Eq. \eqref{eq:five} gives the
closed form result for the detection kernel
\begin{align}
  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so).
\end{align}

\section{Spherical Fourier transform of a rotationally symmetric function}
Consider a rotationally symmetric function on the sphere
$f(\mh{s}\cdot\mh{s}')$. In this appendix we will reduce the spherical Fourier
transform
\begin{align}
  F_\ell^m = \ints{2}d\mh{s}f(\mh{s}\cdot\mh{s}')Y_\ell^{m*}(\mh{s})
\end{align}
to a single one-dimensional integral. Similar to Appendix A, we expand $f$ in a Fourier-Legendre series and proceed step by step
\begin{align}
  F_\ell^m &= \ints{2}d\mh{s}\left[\sum_{\ell'}F_{\ell'} P_{\ell'}(\mh{s}\cdot\mh{s}')\right]Y_\ell^{m*}(\mh{s}),\label{eq:one1}\\
  F_\ell^m &= \sum_{\ell'}F_{\ell'}\ints{2}d\mh{s}\,P_{\ell'}(\mh{s}\cdot\mh{s}')Y_\ell^{m*}(\mh{s}),\label{eq:two1}\\
  F_\ell^m &= \sum_{\ell'm'}\frac{4\pi}{2\ell' + 1}F_{\ell'}Y_{\ell'}^{m'*}(\mh{s}')\ints{2}d\mh{s}\,Y_{\ell'}^{m'}(\mh{s})Y_\ell^{m*}(\mh{s}),\label{eq:three1}\\
  F_\ell^m &= \sum_{\ell'm'}\frac{4\pi}{2\ell' + 1}F_{\ell'}Y_{\ell'}^{m'*}(\mh{s}')\delta_{\ell\ell'}\delta_{mm'},\label{eq:four1}\\
  F_\ell^m &= \frac{4\pi}{2\ell + 1}Y_{\ell}^{m*}(\mh{s}')F_{\ell}\label{eq:five1},
\end{align}
where we have (\ref{eq:one1}-\ref{eq:two1}) rearranged the equation,
(\ref{eq:two1}-\ref{eq:three1}) applied the spherical harmonic addition theorem,
(\ref{eq:three1}-\ref{eq:four1}) used the orthogonality of spherical harmonics
then, (\ref{eq:four1}-\ref{eq:five1}) used the discrete sifting theorem. Eq.
\eqref{eq:five1} is the result we were seeking---we can find the spherical
Fourier transform of a rotationally symmetric function by finding the
Fourier-Bessel transform $F_\ell$ then multiplying by
$\frac{4\pi}{2\ell + 1}Y_{\ell}^{m*}(\mh{s}')$.

We can use this result to evaluate the excitation and detection angular transfer
functions
\begin{align}
  H_{\ell'}^{m',\text{exc}}(\pp\cdot\so) &= \ints{2}d\so\, h^{\text{exc}}(\pp\cdot\so)Y_{\ell'}^{m'*}(\so),\\
  H_{\ell''}^{m'',\text{det}}(\sd\cdot\so) &= \ints{2}d\so\, h^{\text{det}}(\sd\cdot\so)Y_{\ell''}^{m''*}(\so).
\end{align}
where
\begin{align}
  h^{\text{exc}}(\pp\cdot\so) &\propto (\pp\cdot\so)^2, \\
  h^{\text{det}}(\sd\cdot\so) &\propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so).
\end{align}
Starting with the excitation kernel
\begin{align}
  H_{\ell'}^{m',\text{exc}}(\pp) &= \frac{4\pi}{2\ell + 1}Y_{\ell'}^{m'*}(\pp)\left[\frac{2\ell' + 1}{2}\int_{-1}^1dx\, x^2P_{\ell'}(x)\right],\\
  H_{\ell'}^{m',\text{exc}}(\pp) &=\frac{4\pi}{2\ell + 1}Y_{\ell'}^{m'*}(\pp)\left[\frac{1}{3}\delta_{0\ell'} + \frac{2}{3}\delta_{2,\ell'}\right],\\
  H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right].
\end{align}
Notice that the polarizer orientation $\pp$ only affects the $m$ components of
the angular transfer function while the relative contribution to the two $\ell$ bands is fixed.

Finally, the detection kernel is
\begin{align}
  H_{\ell''}^{m'',\text{det}}(\sd) &= \frac{4\pi}{2\ell'' + 1}Y_{\ell''}^{m''*}(\sd)\left[\frac{2\ell'' + 1}{2}\int_{-1}^1dx\, h^{\text{det}}(x)P_{\ell''}(x)\right],\\
  H_{\ell''}^{m'',\text{det}}(\sd) &= \frac{4\pi}{2\ell'' + 1}Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \frac{1}{5}\left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right],\\
  H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].
\end{align}
Notice that the detection axis $\sd$ only affects the $m$ components of the
detection axis and the detection NA affects the relative contribution to the two $\ell$ bands.

\end{document}

### 2018-12-17 papers/basic-theory/paper/paper.tex
Minor edits from Rudolf, Patrick, Hari. Remove draft tag.

@@
 
-\title{Spatio-angular fluorescence microscopy\\ I. Basic theory (Draft: \today)}
+\title{Spatio-angular fluorescence microscopy\\ I. Basic theory}
 
@@
 A small but growing group of microscopists is interested in measuring the
-prevailing orientation and position of ensembles of fluorophores
-\cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}.
-These techniques typically use polarizers to make multiple measurements of the
-same object with different polarizer orientations, then they use a model of the
-dipole excitation and emission processes \cite{fourkas2001} to recover the
-orientation of fluorophores using pixel-wise arithmetic. Although these studies
-do not adopt the scalar or monopole approximations for the angular part of the
-problem, they adopt both approximations when they consider the spatial part of
-the problem. Existing works either ignore the spatial reconstruction problem
+orientation and position of ensembles of fluorophores \cite{vrabioiu2006,
+  mattheyses2010, mehta2016, mcquilken2017, zhanghao2017}. These techniques
+typically use polarizers to make multiple measurements of the same object with
+different polarizer orientations, then they use a model of the dipole excitation
+and emission processes \cite{fourkas2001} to recover the orientation of
+fluorophores using pixel-wise arithmetic. Although these studies do not adopt
+the scalar or monopole approximations for the angular part of the problem, they
+adopt both approximations when they consider the spatial part of the problem.
+Existing works either ignore the spatial reconstruction problem
 \cite{vrabioiu2006, mattheyses2010, mehta2016, mcquilken2017} or assume that the
@@
 
-In this paper we focus on modeling an extremely simple optical system---a
-single-view fluorescence microscope without polarizers. In future papers of this
-series we will extend our models to include polarizers and multi-view
-microscopes. Additionally, we have restricted this paper to the forward
-problem---the mapping between a known object and the data. In future papers we
-will consider the inverse problem, and the singular value decomposition (SVD)
-will play a central role.
+In this paper we focus on modeling a single-view fluorescence microscope without
+polarizers. In future papers of this series we will extend our models to include
+polarizers and multi-view microscopes. Additionally, we have restricted this
+paper to the forward problem---the mapping between a known object and the data.
+In future papers we will consider the inverse problem, and the singular value
+decomposition (SVD) will play a central role.
 
@@
 Similarly, the angular bandwidth of a fluorescence microscope depends on both
-the instrument and the sample.
+the instrument and the choice of fluorophore.
 
@@
 
-The angular bandwidth is also sample dependent. Monopoles emit light
+The angular bandwidth is also fluorophore dependent. Monopoles emit light
 isotropically so they have an $\ell$-bandwidth of $\ell_c = 0$, while dipoles

### 2018-12-19 papers/basic-theory/paper/paper.tex
Split paper into two.

@@
 \usepackage{bm}
+\usepackage[normalem]{ulem}
 
@@
 \providecommand{\tb}[1]{\textcolor{blue}{#1}}
+\providecommand{\add}[1]{\textcolor{blue}{\uwave{#1}}}
+\providecommand{\rem}[1]{\textcolor{red}{\sout{#1}}}
 % \DeclareFontFamily{OT1}{pzc}{}
@@
   We introduce the basic elements of a spatio-angular theory of fluorescence
-  microscopy. We start by modeling an aplanatic microscope imaging an ensemble
-  of in-focus fluorescent dipoles as a linear Hilbert-space operator, and we
-  show that the operator takes a particularly convenient form when expressed in
-  a basis of complex exponentials and spherical harmonics---a form we call the
-  dipole spatio-angular transfer function. We demonstrate our formalism by
-  analyzing a single-view fluorescence microscope without using the monopole or
-  scalar approximations. We show that this imaging system has a spatio-angular
-  band limit, and we exploit the band limit to perform efficient simulations.
-  Notably, we show that information about the out-of-plane orientation of
-  ensembles of in-focus fluorophores is recorded by paraxial fluorescence
-  microscopes.
+  microscopy. We model an aplanatic microscope imaging an ensemble of in-focus
+  fluorescent dipoles as a linear Hilbert-space operator, and we show that the
+  operator takes a particularly convenient form when expressed in a basis of
+  complex exponentials and spherical harmonics---a form we call the dipole
+  spatio-angular transfer function. We discuss the implications of our analysis
+  for all quantitative fluorescence microscopy studies and lay out a path
+  towards a complete theory. % We demonstrate our formalism by
+  % analyzing a single-view fluorescence microscope without using the monopole or
+  % scalar approximations. We show that this imaging system has a spatio-angular
+  % band limit, and we exploit the band limit to perform efficient simulations.
+  % Notably, we show that information about the out-of-plane orientation of
+  % ensembles of in-focus fluorophores is recorded by paraxial fluorescence
+  % microscopes.
 \end{abstract*}
@@
 vector optics and dipole models to estimate the position and orientation of
-single molecules \cite{bohmer2003, lieb2004, toprak2006, aguet2009}, and there
-is growing interest in designing optical systems for measuring the position,
-orientation, and rotational dynamics of single molecules \cite{agrawal2012,
-  backer2014, stallinga2015, zhang2018, zhang2018-2}.
+single molecules \cite{bohmer2003, lieb2004, toprak2006, aguet2009,
+  mortensen2010}, and there is growing interest in designing optical systems for
+measuring the position, orientation, and rotational dynamics of single molecules
+\cite{agrawal2012, backer2014, stallinga2015, zhang2018, zhang2018-2}.
 
@@
 dipole as a small oriented antenna (with incoherent absorption and emission
-moments) where electrons are constrained to move along a single direction. % With
-% this model we can argue classically that monopole radiators do not exist because
-% they would violate the conservation of charge.
-
-Although many works implicitly apply the monopole approximation, we have
-encountered two explicit justifications: (1) the sample contains many randomly
-oriented fluorophores within a resolvable volume or (2) the sample contains
-unconstrained rotating fluorophores. While both of these situations yield
-monopole-like emitters, neither yields emitters that are perfectly described by
-the monopole model. In this work we investigate the dipole model of fluorophores
-in detail and find the conditions under which the monopole approximation is
-justified.
+moments) where electrons are constrained to move along a single direction.
+
+% Although many works implicitly apply the monopole approximation, we have
+% encountered two explicit justifications: (1) the sample contains many randomly
+% oriented fluorophores within a resolvable volume or (2) the sample contains
+% unconstrained rotating fluorophores. While both of these situations yield
+% monopole-like emitters, neither yields emitters that are perfectly described by
+% the monopole model. In this work we investigate the dipole model of fluorophores
+% in detail and find the conditions under which the monopole approximation is
+% justified.
 
@@
 biased estimates of fluorophore concentrations since they ignore the dipole
-excitation and emission of fluorophores, but we will see that these effects are
-small when the sample contains many randomly oriented fluorophores within a
-resolvable volume or unconstrained rotating fluorophores.
+excitation and emission of fluorophores.
 
@@
 In the present work we begin to place these three subfields on a common
-theoretical footing. First, in section \ref{sec:theory}, we assemble the
-mathematical tools for formulating the imaging problem. We start with an
-abstract description of fluorescence imaging systems and extend the usual
-monopole imaging model to dipoles. Along the way we introduce transfer functions
-that will allow us to efficiently analyze spatio-angular microscopes. In section
-\ref{sec:results} we analyze and simulate a single-view fluorescence microscope,
-and we demonstrate our techniques with four simple phantoms. Finally, in section
-\ref{sec:discussion} we discuss the results and their broader implications.
+theoretical footing. First, in section \ref{sec:theory}, we consider arbitrary
+fluorescence imaging models and lay out a plan for developing a model for
+spatio-angular
+imaging. % assemble the mathematical tools for formulating the imaging problem.
+In section \ref{sec:monopole} we review the familiar monopole imaging model, and
+in section \ref{sec:dipole} we extend the model to
+dipoles. % Along the way we introduce transfer functions
+% that will allow us to efficiently analyze spatio-angular microscopes. In section
+% \ref{sec:results} we analyze and simulate a single-view fluorescence microscope,
+% and we demonstrate our techniques with four simple phantoms.
+Finally, in section \ref{sec:discussion} we discuss the results and their
+broader implications.
 
@@
 polarizers and multi-view microscopes. Additionally, we have restricted this
-paper to the forward problem---the mapping between a known object and the data.
-In future papers we will consider the inverse problem, and the singular value
+paper to the forward problem---the mapping between a known object and the data. In
+future papers we will consider the inverse problem, and the singular value
 decomposition (SVD) will play a central role.
@@
 
-\subsection{Monopole imaging in different bases}\label{sec:monopole}
+\section{Monopole imaging}\label{sec:monopole}
 We start by considering a microscope that images a field of in-focus monopoles
@@
 find the distinction between the optical transfer function and the object
-transfer function to be especially valuable when we consider dipoles later in
-this section.
-
-\subsubsection{Monopole coherent transfer functions}
+transfer function to be especially valuable when we consider dipoles in section \ref{sec:dipole}.
+
+\subsection{Monopole coherent transfer functions}
 Although the Fourier transform can be used to calculate the monopole transfer
@@
 
-\subsection{Dipole imaging in different bases}\label{sec:dipole}
+\section{Dipole imaging}\label{sec:dipole}
 Now we consider a microscope imaging a field of in-focus dipoles by recording
@@
 $f(\ro, \so) = f(\ro,-\so)$, so we could have chosen to integrate over a
-hemisphere and adjusted the definition the dipole density by a factor of two.
+hemisphere and adjusted the definition of the dipole density by a factor of two.
 For convenience we will continue to integrate over the complete sphere. We note
@@
 
-\subsubsection{Dipole spatial transfer function}
+\subsection{Dipole spatial transfer function}
 We can make our first change of basis by applying the Fourier-convolution
@@
 
-\subsubsection{Dipole angular transfer function}
+\subsection{Dipole angular transfer function}
 The spherical harmonics are another set of convenient basis functions that play
@@
 
-\subsubsection{Spatio-angular dipole transfer function}
+\subsection{Spatio-angular dipole transfer function}
 We can arrive at our final basis in two ways: by applying the generalized
@@
   This basis is well suited for simulating and analyzing arbitrary samples
-  because it exploits the band limit of the imaging system. We will see the
-  advantage explicitly in Section \ref{sec:results} when we calculate a specific
-  dipole spatio-angular transfer function and see that it has spatial and
-  angular band limits. We note that most single molecule imaging experiments
+  because it exploits the band limit of the imaging system. % We will see the
+  % advantage explicitly in Section \ref{sec:results} when we calculate a specific
+  % dipole spatio-angular transfer function and see that it has spatial and
+  % angular band limits. 
+  We note that most single molecule imaging experiments
   are best described in this basis because of the effects of spatial and
@@
 
-\subsubsection{Dipole coherent transfer functions}
+\subsection{Dipole coherent transfer functions}
 Similar to the monopole case, there is an efficient way to calculate the
@@
 calculate the other transfer functions. Finally, we note that the dipole
-coherent transfer function is identical to what Agrawal et. al. call the
-\textit{Green's tensor} \cite{agrawal2012} and Novotny and Hecht's
-\textit{dyadic point spread function} multiplied by the dipole moment vector
-\cite{nov2006}.
-
-\section{Results}\label{sec:results}
-In this section we begin to apply the tools we developed in the previous section
-to analyze a specific fluorescence microscope. During our initial discussion we
-only required the optical system to be aplanatic so that we could model it as a
-shift-invariant magnifier. Now we will be more specific and consider an
-aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an
-arbitrary first lens (the objective lens) and a \textit{paraxial second lens}
-(the tube lens) as shown in Fig. \ref{fig:schematic}. A lens can be considered
-paraxial if the angle $\alpha$ between the optical axis of the lens and the
-marginal ray is small enough that $\sin\alpha \approx \alpha$. As a rule of
-thumb, non-paraxial effects only become significant when the numerical aperture
-of a lens exceeds 0.7 \cite[ch.~6]{gu2000}, but this is only a rough
-guideline. Commercial microscopes with infinity-corrected objectives can almost
-always can be modeled by considering the tube lens as paraxial.
-
-We start by defining \textit{pupil functions} for both monopole and dipole
-imaging systems, and we explicitly relate the pupil functions to the previously
-defined coherent transfer functions. After establishing the link between
-physical calculations and the transfer functions, we calculate the monopole and
-dipole transfer functions for imaging systems with a paraxial objective, and we
-demonstrate our approach by simulating simple phantoms.
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[width = 1.0\textwidth]{../figures/coordinates/detection-coords.pdf}
-   \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
-     paraxial tube lens. We are considering an aplanatic optical system, so we
-     only need to consider the image created by on-axis objects. The fluorescent
-     object consists of ensembles of dipoles embedded in a medium with index of
-     refraction $n_0$. An objective with focal length $f_0$ and numerical
-     aperture $\text{NA} = n_o\sin\alpha$ is trained on the object. A paraxial
-     tube lens with focal length $f_1$ and a detector complete the $4f$
-     geometry, and all components except the object are embedded in a medium
-     with index of refraction $n_1$. The object, pupil, and detector planes are
-     parameterized by vectors $\ro$, $\rp$, and $\rd$ with polar coordinates
-     ($r_o, \phi_o$), ($r_b, \phi_b$), and ($r_d, \phi_d$), respectively. At
-     each position $\ro$ in the object there is a sphere parameterized by a unit
-     vector $\so$ with spherical coordinates ($\vartheta, \varphi$). }
-   \label{fig:schematic}
- \end{figure}
-
-\subsection{Monopole pupil functions}
-We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
-the field immediately following the pupil plane created by an on-axis monopole,
-where $\rp$ is an unscaled two-dimensional coordinate in the pupil plane. In
-this section we will relate the monopole pupil function to the transfer function
-we defined in section \ref{sec:theory} by adapting the treatment in Barrett and
-Myers \cite[ch.~9.7]{barrett2004}.
-
-Since monopoles emit scalar fields, the monopole pupil function is a
-scalar-valued function. The optical system is aplanatic, so we can write the
-field, $U_p(\rp, \ro)$, created at a point in the pupil plane $\rp$ by a
-monopole at position $\ro$ as
-\begin{align}
-   U_p(\rp, \ro) \propto p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil}
-\end{align}
-Equation \eqref{eq:pupil} is a restatement of the aplanatic condition for a $4f$
-optical system---the fields in the pupil plane can be written as the pupil
-function multiplied by a linear phase factor that encodes the position of the
-object.
-
-Since the second lens is paraxial, we can model the relationship between the
-field in the pupil plane and the field on the detector with a scaled Fourier
-transform \cite{goodman1996, axelrod2012, backer2014}:
-\begin{align}
-   U_d(\rd', \ro) \propto \int_{\mbb{R}^2}d\rp\, p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
+coherent transfer function is identical (up to scaling factors) to what
+Agrawal et. al. call the \textit{Green's tensor} \cite{agrawal2012} and Novotny
+and Hecht's \textit{dyadic point spread function} multiplied by the dipole
+moment vector \cite{nov2006}.
+
+% \section{Results}\label{sec:results}
+% In this section we begin to apply the tools we developed in the previous section
+% to analyze a specific fluorescence microscope. During our initial discussion we
+% only required the optical system to be aplanatic so that we could model it as a
+% shift-invariant magnifier. Now we will be more specific and consider an
+% aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an
+% arbitrary first lens (the objective lens) and a \textit{paraxial second lens}
+% (the tube lens) as shown in Fig. \ref{fig:schematic}. A lens can be considered
+% paraxial if the angle $\alpha$ between the optical axis of the lens and the
+% marginal ray is small enough that $\sin\alpha \approx \alpha$. As a rule of
+% thumb, non-paraxial effects only become significant when the numerical aperture
+% of a lens exceeds 0.7 \cite[ch.~6]{gu2000}, but this is only a rough
+% guideline. Commercial microscopes with infinity-corrected objectives can almost
+% always can be modeled by considering the tube lens as paraxial.
+
+% We start by defining \textit{pupil functions} for both monopole and dipole
+% imaging systems, and we explicitly relate the pupil functions to the previously
+% defined coherent transfer functions. After establishing the link between
+% physical calculations and the transfer functions, we calculate the monopole and
+% dipole transfer functions for imaging systems with a paraxial objective, and we
+% demonstrate our approach by simulating simple phantoms.
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[width = 1.0\textwidth]{../figures/coordinates/detection-coords.pdf}
+%    \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
+%      paraxial tube lens. We are considering an aplanatic optical system, so we
+%      only need to consider the image created by on-axis objects. The fluorescent
+%      object consists of ensembles of dipoles embedded in a medium with index of
+%      refraction $n_0$. An objective with focal length $f_0$ and numerical
+%      aperture $\text{NA} = n_o\sin\alpha$ is trained on the object. A paraxial
+%      tube lens with focal length $f_1$ and a detector complete the $4f$
+%      geometry, and all components except the object are embedded in a medium
+%      with index of refraction $n_1$. The object, pupil, and detector planes are
+%      parameterized by vectors $\ro$, $\rp$, and $\rd$ with polar coordinates
+%      ($r_o, \phi_o$), ($r_b, \phi_b$), and ($r_d, \phi_d$), respectively. At
+%      each position $\ro$ in the object there is a sphere parameterized by a unit
+%      vector $\so$ with spherical coordinates ($\vartheta, \varphi$). }
+%    \label{fig:schematic}
+%  \end{figure}
+
+% \subsection{Monopole pupil functions}
+% We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
+% the field immediately following the pupil plane created by an on-axis monopole,
+% where $\rp$ is an unscaled two-dimensional coordinate in the pupil plane. In
+% this section we will relate the monopole pupil function to the transfer function
+% we defined in section \ref{sec:theory} by adapting the treatment in Barrett and
+% Myers \cite[ch.~9.7]{barrett2004}.
+
+% Since monopoles emit scalar fields, the monopole pupil function is a
+% scalar-valued function. The optical system is aplanatic, so we can write the
+% field, $U_p(\rp, \ro)$, created at a point in the pupil plane $\rp$ by a
+% monopole at position $\ro$ as
+% \begin{align}
+%    U_p(\rp, \ro) \propto p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil}
+% \end{align}
+% Equation \eqref{eq:pupil} is a restatement of the aplanatic condition for a $4f$
+% optical system---the fields in the pupil plane can be written as the pupil
+% function multiplied by a linear phase factor that encodes the position of the
+% object.
+
+% Since the second lens is paraxial, we can model the relationship between the
+% field in the pupil plane and the field on the detector with a scaled Fourier
+% transform \cite{goodman1996, axelrod2012, backer2014}:
+% \begin{align}
+%    U_d(\rd', \ro) \propto \int_{\mbb{R}^2}d\rp\, p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
 \label{eq:detectorfourier}
-\end{align}
-
-If we define $P(\taup)$ as the two-dimensional Fourier transform of the pupil function
-then we can rewrite Eq. \eqref{eq:detectorfourier} as
-\begin{align}
-  U_d(\rd', \ro) \propto P\left(\frac{n_0}{\lambda f_0}\ro + \frac{n_1}{\lambda f_1}\rd'\right),
-\end{align}
-which we can simplify further by writing in terms of
-$m = -\frac{f_1n_0}{f_0n_1}$:
-\begin{align}
-  U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right).
-\end{align}
-The irradiance on the detector is the absolute square of the field so
-\begin{align}
-  h'(\rd' - m\ro) \propto \left|P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right)\right|^2.
-\end{align}
-If we demagnify the coordinates with $\rd = \rd'/m$ and demagnify the irradiance
-with $h(\rd - \ro) \propto h'(m[\rd - \ro])$, we find that the monopole point
-spread function is related to the Fourier transform of the monopole pupil
-function by
-\begin{align}
-  h(\rd - \ro) \propto \left|P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right)\right|^2.
-\end{align}
-The monopole point spread function is the absolute square of the monopole
-coherent spread function so
-\begin{align}
-  c(\rd - \ro) \propto P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right).
-\end{align}
-Finally, the monopole coherent transfer function is the Fourier transform of the
-monopole coherent spread function so
-\begin{align}
-  C(\taup) \propto p\left(\frac{\lambda f_o}{n_o}\taup\right). \label{eq:monopupil0}
-\end{align}
-Equation \eqref{eq:monopupil0} is the key result of this section---the monopole
-coherent transfer function is a scaled monopole pupil function.
-
-\subsection{Dipole pupil function}
-We define the \textit{dipole pupil function} $\mb{p}(\rp, \so)$ of the imaging
-system as the electric field immediately following the pupil plane created by
-an on-axis dipole oriented along $\so$. Since dipoles emit vector-valued
-electric fields, the dipole pupil function is a vector-valued function. Almost
-all of the arguments in the previous section carry over to the dipole case.
-Briefly, we can write the electric field created at a point in the pupil
-$\rp$ by a dipole at $\ro$ oriented along $\so$ as
- \begin{align}
-   \mb{E}(\rp, \ro, \so) \propto \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
- \end{align}
- The second lens is paraxial, so we can find the field on the detector with a
- Fourier transform
- \begin{align}
-   \mb{E}_d(\rd', \ro, \so) \propto \int_{\mbb{R}^2}d\rp\, \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
+% \end{align}
+
+% If we define $P(\taup)$ as the two-dimensional Fourier transform of the pupil function
+% then we can rewrite Eq. \eqref{eq:detectorfourier} as
+% \begin{align}
+%   U_d(\rd', \ro) \propto P\left(\frac{n_0}{\lambda f_0}\ro + \frac{n_1}{\lambda f_1}\rd'\right),
+% \end{align}
+% which we can simplify further by writing in terms of
+% $m = -\frac{f_1n_0}{f_0n_1}$:
+% \begin{align}
+%   U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right).
+% \end{align}
+% The irradiance on the detector is the absolute square of the field so
+% \begin{align}
+%   h'(\rd' - m\ro) \propto \left|P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right)\right|^2.
+% \end{align}
+% If we demagnify the coordinates with $\rd = \rd'/m$ and demagnify the irradiance
+% with $h(\rd - \ro) \propto h'(m[\rd - \ro])$, we find that the monopole point
+% spread function is related to the Fourier transform of the monopole pupil
+% function by
+% \begin{align}
+%   h(\rd - \ro) \propto \left|P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right)\right|^2.
+% \end{align}
+% The monopole point spread function is the absolute square of the monopole
+% coherent spread function so
+% \begin{align}
+%   c(\rd - \ro) \propto P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right).
+% \end{align}
+% Finally, the monopole coherent transfer function is the Fourier transform of the
+% monopole coherent spread function so
+% \begin{align}
+%   C(\taup) \propto p\left(\frac{\lambda f_o}{n_o}\taup\right). \label{eq:monopupil0}
+% \end{align}
+% Equation \eqref{eq:monopupil0} is the key result of this section---the monopole
+% coherent transfer function is a scaled monopole pupil function.
+
+% \subsection{Dipole pupil function}
+% We define the \textit{dipole pupil function} $\mb{p}(\rp, \so)$ of the imaging
+% system as the electric field immediately following the pupil plane created by
+% an on-axis dipole oriented along $\so$. Since dipoles emit vector-valued
+% electric fields, the dipole pupil function is a vector-valued function. Almost
+% all of the arguments in the previous section carry over to the dipole case.
+% Briefly, we can write the electric field created at a point in the pupil
+% $\rp$ by a dipole at $\ro$ oriented along $\so$ as
+%  \begin{align}
+%    \mb{E}(\rp, \ro, \so) \propto \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
+%  \end{align}
+%  The second lens is paraxial, so we can find the field on the detector with a
+%  Fourier transform
+%  \begin{align}
+%    \mb{E}_d(\rd', \ro, \so) \propto \int_{\mbb{R}^2}d\rp\, \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right].
 \label{eq:detectorfourier2}
-\end{align}
-Note that the Fourier transform of a vector field is the Fourier transform of
-its scalar-valued orthogonal components, so Eq. \eqref{eq:detectorfourier2}
-specifies three two-dimensional Fourier transforms. We follow the same
-manipulations as the previous section and find that the dipole coherent transfer
-function is a scaled dipole pupil function
-\begin{align}
-  \mb{C}(\taup, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\taup, \so\right). \label{eq:monopupildip}
-\end{align}
-
-We have restricted our analysis to paraxial tube lenses, but non-paraxial tube
-lenses (or a non-infinity-corrected objective) can be modeled with vector-valued
-three-dimensional pupil functions \cite{sheppard1994, gu2000, arnison2002,
-  foreman2011-2}.
-
-\subsection{Special functions}
-We adopt and generalize Bracewell's notation \cite{bracewell2004} for several
-special functions which will simplify our calculations. First, we define a
-\textit{rectangle function} as
-\begin{align}
-  \Pi(x) = 
-  \begin{cases}
-    1\quad \text{if}\quad |x| < \frac{1}{2},\\
-    0\quad \text{else}.
-  \end{cases}
-\end{align}
-We also define the \textit{$n^{th}$-order jinc function} as
-\begin{align}
-  \text{jinc}_n(r) = \frac{J_{n+1}(\pi r)}{2r},
-\end{align}
-where $J_{n+1}(r)$ is the $(n+1)^{th}$-order Bessel function of the first kind.
-
-Although the rectangle and jinc functions are defined in one dimension, we will
-usually apply them in two dimensions. In Appendix \ref{sec:special} we derive
-the following two-dimensional Fourier transform relationships between the jinc
-functions and the weighted rectangle functions
-\begin{align}
-  i^{n}\left\{\substack{
-  \text{exp}(in\phi_r)\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\text{jinc}_n(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} (2\nu)^{n}\left\{\substack{
-    \text{exp}(in\phi_{\nu})\\
-    \cos(n\phi_{\nu})\\
-    \sin(n\phi_{\nu})
-  }\right\}\Pi(\nu), \label{eq:jincrect2}
-  \end{align}
-  where the entries inside the curly braces are to be taken one at a time and
-  $\{r, \phi_r\}/\{\nu, \phi_\nu\}$ are conjugate sets of polar coordinates.
-
-Finally, we define the \textit{$n^{th}$-order chat function} as the
-two-dimensional Fourier transform of the squared $n^{th}$-order jinc function
-\begin{align}
-  \text{jinc}_n^2(r) \stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} \text{chat}_n(\nu).
-\end{align}
-
-In Appendix \ref{sec:special} we show that the zeroth- and first-order chat
-functions can be written in closed form as
-\begin{align}
-  \text{chat}_0(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right),\\
-  \text{chat}_1(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|(3-2x^2)\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right).  
-\end{align}
-
-\subsection{Monopole transfer functions}
-Our first step towards the monopole transfer functions is to calculate the
-monopole pupil function and coherent transfer function. Several works
-\cite{petrov2017, backlund2018} have modeled an aplanatic fluorescence
-microscope imaging monopole emitters with the scalar pupil function
-\begin{align}
-  p(\rp) \propto \tilde{C}\left(\frac{r_p}{f_o}\right)\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
-\end{align}
-where
-\begin{align}
-  \tilde{C}(x) = (1 - x^2)^{-1/4} = 1 + \frac{x^2}{4} + \frac{5x^4}{32} + \cdots. 
-\end{align}
-The $\tilde{C}(x)$ function models the radial dependence of the field and
-ensures that power is conserved on either side of an aplanatic objective, and
-the rectangle function models the aperture stop of the objective. Applying Eq.
-\eqref{eq:monopupil0} and collecting constants we find that the coherent monopole
-transfer function is
-\begin{align}
-  C(\taup) \propto \tilde{C}\left(\frac{2\text{NA}}{n_o}\frac{\tau}{\nu_c}\right)\Pi\left(\frac{\tau}{\nu_c}\right), \label{eq:coherentmonopole}
-\end{align}
-where $\text{NA} = n_o\sin\alpha$ and $\nu_c = 2\text{NA}/\lambda$. This
-coherent transfer function models objectives with an arbitrary numerical
-aperture, but for our initial analysis we restrict ourselves to the paraxial
-regime. We drop second- and higher-order radial terms to find that
-\begin{align}
-  C(\taup) \stackrel{(p)}{\propto} \Pi\left(\frac{\tau}{\nu_c}\right), 
-\end{align}
-where $(p)$ indicates that we have used the paraxial approximation for the
-objective lens.
-
-We can find the monopole coherent spread function by taking the inverse Fourier
-transform of the monopole coherent transfer function
-\begin{align}
-  c(\mb{r}) \stackrel{(p)}{\propto} \text{jinc}_0(\nu_c r).
-\end{align}
-
-The monopole point spread function is the (normalized) absolute square of the
-monopole coherent spread function so
-\begin{align}
-  h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r),
-\end{align}
-which is the well-known \textit{Airy disk}.
-
-Finally, we can calculate the monopole transfer function as the two-dimensional Fourier transform of the monopole point spread function (or the autocorrelation
-of the coherent transfer function) and find that 
-\begin{align}
-  H(\bs{\nu}) \stackrel{(p)}{=} \frac{4}{\pi}\text{chat}_0\left(\frac{\nu}{\nu_c}\right).
-\end{align}
-
- \subsection{Dipole transfer functions}
- To calculate the dipole transfer function we proceed similarly to the monopole
- case---we find the pupil function, scale to find the coherent dipole transfer
- function, then calculate the remaining transfer functions.
-
- Backer and Moerner \cite{backer2014} have calculated the dipole pupil function
- for a high-NA objective as
- \begin{align}
-   \mb{p}(\rp, \so) \propto
-   \begin{bmatrix}
-     \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)c(\phi_p)\\
-     \tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)s(\phi_p)\\
-     0&0&0\\     
-   \end{bmatrix}
-   \begin{bmatrix}
-     s_x\\
-     s_y\\
-     s_z
-   \end{bmatrix}
-   \Pi\left(\frac{r_p}{2f_os(\alpha)}\right),
- \end{align}
- where $c(x)$ and $s(x)$ are shorthand for $\cos(x)$ and $\sin(x)$,
- $\{s_x, s_y, s_z\}$ are the Cartesian components of $\so$ when $\mh{z}$ is
- aligned with the optical axis, and
- \begin{alignat}{4}
-   \tilde{C}_0(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} + 1\right)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
-   \tilde{C}_1(x) &= x(1 - x^2)^{-1/4} &&= x + \frac{x^3}{4} + \frac{5x^5}{32} + \cdots,\\
-   \tilde{C}_2(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} - 1\right)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
- \end{alignat}
- Similar to the monopole case, the dipole pupil function conserves power and has
- a cutoff at the objective aperture, but the dipole pupil function is
- vector-valued to model the complete electric field in the pupil plane. The
- fields in the pupil plane have a negligible $\mh{z}$ component which is a
- consequence of our assumption that the tube lens is paraxial---modeling a
- non-paraxial tube lens would require a three-dimensional vector-valued pupil
- function \cite{sheppard1994, gu2000, arnison2002, foreman2011-2}.
-
- Scaling the dipole pupil function using Eq. \eqref{eq:monopupildip} yields the
- dipole coherent transfer function
- \begin{equation}
-   \mb{C}(\taup, \so)\hspace{-0.2em}\propto\hspace{-0.2em}
-   \begin{bmatrix}
-     \tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!+\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)c(\phi_{\tau})\\
-     \tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!-\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)s(\phi_{\tau})\\
-     0&0&0\\     
-   \end{bmatrix}
-   \begin{bmatrix}
-     s_x\\
-     s_y\\
-     s_z
-   \end{bmatrix}
-   \Pi\left(\frac{\tau}{\nu_c}\right). 
- \end{equation}
- We restrict our analysis to the paraxial regime by dropping second- and
- higher-order radial terms to find that
- \begin{align}
-   \mb{C}(\taup, \so) \stackrel{(p)}{\propto}
-   \begin{bmatrix}
-     1&0&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\cos\phi_{\tau}\\
-     0&1&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\sin\phi_{\tau}\\
-     0&0&0\\     
-   \end{bmatrix}
-   \begin{bmatrix}
-     s_x\\
-     s_y\\
-     s_z
-   \end{bmatrix}
-   \Pi\left(\frac{\tau}{\nu_c}\right). \label{eq:coherentdip}
- \end{align}
- Under the paraxial approximation the transverse components of the dipole
- \{$s_x, s_y$\} create purely transverse fields in the pupil plane and the axial
- component of the dipole \{$s_z$\} creates purely radial fields in the pupil
- plane. The paraxial approximation may seem crude compared to Backer and
- Moerner's numerical results, but the approximation will allow us to calculate
- the transfer functions in closed form so that we can build an intuition for the
- limits of the microscope. We also note that many existing works in ensemble
- polarized fluorescence microscopy make stronger approximations than ours. For
- example, Fourkas only considers the total irradiance in the pupil plane while
- ignoring the propagation of fields to the detector \cite{fourkas2001}.
-
- The dipole coherent spread function is the inverse Fourier transform of the
- dipole coherent transfer function. Applying Eq. \eqref{eq:jincrect2} in reverse
- yields
-  \begin{align}
-   \mb{c}(\mb{r}, \so) \stackrel{(p)}{\propto}
-   \begin{bmatrix}
-     \text{jinc}_0(\nu_c r)&0&\frac{\text{NA}}{n_o}i\cos\phi\,\text{jinc}_1(\nu_c r)\\
-     0&\text{jinc}_0(\nu_c r)&\frac{\text{NA}}{n_o}i\sin\phi\,\text{jinc}_1(\nu_c r)\\
-     0&0&0\\     
-   \end{bmatrix}
-   \begin{bmatrix}
-     s_x\\
-     s_y\\
-     s_z
-   \end{bmatrix}.
-  \end{align}
-  Notice that the radial component of the dipole coherent spread function has a
-  $\pi/2$ phase shift relative to the transverse component. This phase factor
-  arises because the Fourier transform of a real and odd function is purely
-  imaginary.
-
-  \subsubsection{Paraxial dipole point spread function}
-  The dipole point spread function is the (normalized) absolute square of the
-coherent dipole spread function
-\begin{align}
-  h(\mb{r}, \so) \propto \mb{c}(\mb{r}, \so)\mb{c}^\dagger(\mb{r}, \so). 
-\end{align}
-Plugging in the paraxial dipole coherent spread function and normalizing yields
-\begin{align}
-  h(\mb{r}, \so) \stackrel{(p)}{=} N\left[\text{jinc}_0^2(\nu_c r)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\cos^2\vartheta\right],\label{eq:paradpsf}
-\end{align}
-where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization
-factor is
-\begin{align}
-  N = 6\nu_c^2\pi^{-3/2}\left[2 + \left(\frac{\text{NA}}{n_o}\right)^2\right]^{-1}.
-\end{align}
-
-As discussed above, the transverse and radial fields are out of phase on the
-detector, so the total irradiance is the sum of the contributions from the
-transverse and radial components. In Fig. \ref{fig:hdet} we plot the dipole
-point spread function for several dipole orientations and numerical apertures,
-and in Fig. \ref{fig:microscopefig} we compare the monopole point spread
-function to the dipole point spread function. The paraxial monopole and dipole
-models are only equivalent when the sample consists of transverse dipoles, which
-is clear if we notice that Eq. \eqref{eq:paradpsf} reduces to an Airy disk when
-$\vartheta = \pi/2$---see Novotny and Hecht for a similar observation
-\cite[ch.~4]{nov2006}.
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/dpsf.pdf}
-   \caption{Renormalized paraxial dipole point spread function as a function of
-     the scaled radial coordinate $\nu_c r$, the dipole inclination angle
-     $\vartheta$, and $\text{NA}/n_o$. For small numerical apertures (left) the
-     irradiance pattern created by axial dipoles (\textcolor{red}{\textbf{red}})
-     is small compared to transverse dipoles (\textbf{black}), but the relative
-     contribution of axial dipoles increases with the numerical aperture (see
-     \textcolor{red}{\textbf{red}} lines from left to right). Additionally, we
-     plot the monopole point spread function (\textcolor{green}{\textbf{green}})
-     and observe that the paraxial monopole and dipole models are identical for
-     transverse dipoles (the \textcolor{green}{\textbf{green}} and
-     \textbf{black} lines are coincident).}
-   \label{fig:hdet}
- \end{figure}
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
-   \caption{Comparison of paraxial models for monopole radiators a) and dipole
-     radiators b)--d). a) Monopole radiators fill the pupil plane with a uniform
-     scalar field which gives rise to an Airy disk on the detector. b) A
-     transverse dipole radiator also creates an Airy disk, but the pupil plane
-     is filled with a uniform vector field. c) An axial dipole radiator creates
-     a radial electric field pattern in the back focal plane that creates a
-     $\text{jinc}_1^2(r)$ pattern on the detector. d) Dipoles that are not
-     transverse or axial still create radially symmetric irradiance patterns
-     under the paraxial approximation. Fields from transverse dipoles are real
-     and even while fields from axial dipoles are real and odd, which causes a
-     relative $\pi/2$ phase shift for the fields on the detector. This phase
-     shift means that the fields from transverse and axial components of the
-     dipole do not interfere, which causes radially symmetric irradiance
-     patterns.}
-   \label{fig:microscopefig}
- \end{figure}
-
- To demonstrate the paraxial dipole point spread function we simulate a set of
- equally spaced dipoles with varying orientation:
- \begin{align}
-   f_{(ph1)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, \delta\left(\cos\vartheta - \cos\vartheta_j\right)\, \delta\left(\varphi - \varphi_k\right),\label{eq:phantom1}
- \end{align}
- where $\vartheta_j = j\frac{\pi}{6}$, $\varphi_k = k\frac{\pi}{4}$, the
- subscript $(ph1)$ indicates that this is the first phantom, and the spatial
- coordinates are expressed in $\mu$m. To find the irradiance pattern created by
- the phantom we plug Eq. \eqref{eq:phantom1} into Eq. \eqref{eq:odpsf} and use
- the sifting property to find that
- \begin{align}
-   g_{(ph1)}(r_x, r_y) = \sum_{j=0}^3 \sum_{k=0}^3 h\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}, \vartheta_j\right).\label{eq:phantom1irr}
- \end{align}
- In Fig. \ref{fig:ph1} we plot the phantom and scaled irradiance for an imaging
- system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$.
- We sample and plot the scaled irradiance at $20\times$ the Nyquist rate,
- $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free of aliasing.
- The output demonstrates that the irradiance pattern depends on the dipole
- inclination, but not its azimuth.
-
- \begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/ph1.pdf}
-   \caption{\textbf{Left:} A spatially and angularly sparse phantom---uniformly
-     spaced single dipoles with varying orientations (increasing $\vartheta$
-     from left to right and increasing $\varphi$ from bottom to top). White
-     crosses mark the positions of the dipoles. \textbf{Center:} Scaled
-     irradiance for an imaging system with $\text{NA} = 0.75$,
-     $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at $20\times$ the
-     Nyquist rate. \textbf{Right:} $x$ profiles through the scaled irradiance.
-     The response is independent of the azimuth angle and strongly dependent on
-     the inclination angle.}
-   \label{fig:ph1}
- \end{figure}
-
-\subsubsection{Paraxial dipole spatial transfer function}\label{sec:trans}
-The dipole spatial transfer function is the spatial Fourier transform of
-the dipole point spread function (or the complex autocorrelation of the dipole
-coherent transfer function). Applying the Fourier transform to Eq.
-\eqref{eq:paradpsf} we find that
-  \begin{align}
-    H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
-  \end{align}
-In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
-several dipole orientations and numerical apertures. We find that the dipole
-spatial transfer function is negative for axial dipoles at high spatial
-frequencies, especially for larger numerical apertures. The negative dipole
-spatial transfer corresponds to a contrast inversion for high-frequency
-patterns of axial dipoles because the irradiance minimum corresponds to the
-position of the dipole.
-
-\begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/sdtf.pdf}
-   \caption{Dipole spatial transfer function as a function of the scaled spatial
-     frequency $\nu/\nu_c$, the dipole inclination angle $\vartheta$, and
-     $\text{NA}/n_o$. For small numerical apertures (left) the dipole spatial
-     transfer function for axial dipoles (\textcolor{red}{\textbf{red}}) is
-     small compared to transverse dipoles (\textbf{black}), but the relative
-     contribution of axial dipoles increases with the numerical aperture (see
-     \textcolor{red}{\textbf{red}} lines from left to right). The spatial dipole
-     transfer function of axial dipoles is negative at high spatial frequencies
-     because the central minimum of the axial dipole point spread function
-     corresponds to the position of the dipole. Equivalently, a
-     high-spatial-frequency pattern of axial dipoles will generate an irradiance
-     pattern where the minimum irradiance corresponds to the peak of the axial
-     dipole density. Additionally, we plot the monopole transfer function
-     (\textcolor{green}{\textbf{green}}) and observe that the paraxial monopole
-     and dipole models are identical for transverse dipoles (the
-     \textcolor{green}{\textbf{green}} and \textbf{black} lines are
-     coincident).}
-   \label{fig:odotf}
- \end{figure}
-
- To demonstrate the dipole spatial transfer function we simulate a set of
- equally spaced disks with varying diameter containing fluorophores with varying
- orientation
- \begin{align}
-   f_{(ph2)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
- \end{align}
- where $D_k = 0.15(1+k)\, \mu$m and $\vartheta_j = j\frac{\pi }{6}$. Notice that
- we have scaled the disks so that the total number of fluorophores in each disk
- is constant. Also notice that the disk can model a spatial distribution of many
- fluorophores or a single molecule undergoing spatial diffusion within a well.
-
- We can calculate the irradiance pattern by taking the spatial Fourier transform
- for each orientation in the phantom, filtering the result with the dipole
- spatial transfer function, integrating over the orientations, then taking the
- inverse spatial Fourier transform. Since our phantom is angularly sparse, the
- integral becomes a sum and we find that
- \begin{align}
-   g_{(ph2)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{(ph2)}(r_x, r_y, \vartheta_j)\right\}\right\}.
- \end{align}
-
- In Fig. \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
- imaging parameters as the previous section. The small disks create irradiance
- patterns that are similar to the point sources in the previous section, while
- larger disks create increasingly uniform irradiance patterns that hide the
- orientation of the fluorophores.
-
-  \begin{figure}[h]
- % \captionsetup{width=1.0\linewidth}
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/ph2.pdf}
-   \caption{\textbf{Left:} A spatially dense and angularly sparse
-     phantom---uniformly spaced disks with varying size (increasing $D$ from
-     bottom to top) and dipole orientation (increasing $\vartheta$ from left to
-     right) \textbf{Center:} Scaled irradiance for an imaging system with
-     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
-     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
-     scaled irradiance. Larger disks generate increasingly uniform irradiance
-     patterns with fewer details that may indicate the orientation of
-     fluorophores.}
-   \label{fig:ph2}
- \end{figure}
-
- \subsubsection{Paraxial dipole angular transfer function}
- To calculate the angular dipole transfer function we take the spherical Fourier
- transform of the dipole point spread function
- \begin{align}
-H_l^m(\mb{r}) \stackrel{}{=} \int_{\mbb{S}^2}d\so\, h(\mb{r}, \so)Y_l^{m*}(\so).
- \end{align}
- After evaluating the integrals and normalizing, the angular dipole transfer
- function is
- \begin{align}
-   H_l^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3}\left[2\text{jinc}_0^2(\nu_cr) + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_0\delta_{\ell0}\delta_{m0} + \nonumber\\& \frac{N}{3}\left[-2\text{jinc}_0^2(\nu_c r) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_2\delta_{\ell2}\delta_{m0},
- \end{align}
-where $\Lambda_{\ell} = \sqrt{4\pi/(2\ell + 1)}$.
-
-In Fig. \ref{fig:atf} we plot the dipole angular transfer function for both
-spherical harmonic terms and several numerical apertures. Note that the dipole
-angular transfer function can be negative because the spherical harmonics can
-take negative values. The $\ell=0$ term shows that angularly uniform
-distributions of dipoles create spatial irradiance patterns that are similar but
-not identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
-because of the large contribution of the transverse negative values in the
-$Y_2^0$ spherical harmonic.
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/adtf.pdf}
-   \caption{Paraxial dipole angular transfer function in terms of a scaled
-     radial detection coordinate $\nu_c r$, the spherical harmonic degree
-     $\ell$, and $\text{NA}/n_o$. Angularly uniform distributions of dipoles
-     $\ell=0$ generate a spatial pattern that is similar but not identical to
-     the Airy disk created by a monopole (\textcolor{green}{\textbf{green}}),
-     and this discrepancy increases with the numerical aperture. $\ell=2$
-     distributions have a negative response because $Y_2^0(\mh{s})$ is negative
-     for transverse directions. As the numerical aperture increases, the
-     relative contribution of positive axial dipoles in the $\ell=2$
-     distribution increases.}
-   \label{fig:atf}
- \end{figure}
-
- To demonstrate the dipole angular transfer function we simulate a set of
- equally spaced fluorophore distributions with varying orientation and angular
- distributions
- \begin{align}
-   f_{(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
- \end{align}
- where
- \begin{align}
-   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right)
- \end{align}
- is an angular double cone distribution with central direction $\mh{s}'$ and
- cone half-angle $\Delta$; $\vartheta_j = j\frac{\pi}{6}$; and
- $\Delta_k = k\frac{\pi}{6}$. Notice that when $\Delta = 0$ the angular double
- cone reduces to a single direction, and when $\Delta = \pi/2$ the angular
- double cone reduces to an angularly uniform distribution. Also notice that the
- double cone can model angular diffusion or the angular distribution of many
- fluorophores within a resolvable volume.
-
- Our first step towards the irradiance pattern is to calculate the dipole
- angular spectrum of the phantom. In Appendix \ref{sec:cone} we calculate the
- spherical Fourier transform of the double cone distribution
- $F^m_{\ell,\text{(cone)}}(\vartheta', \varphi'; \Delta)$ which we can use to
- express the dipole angular spectrum as
- \begin{align}
-   F^{m}_{\ell,(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
- \end{align}
-
- To find the irradiance we plug the dipole angular spectrum into Eq.
- \eqref{eq:atf-form} and use the sifting property to find that
- \begin{align}
-   g_{(ph3)}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
- \end{align}
-
- In Fig. \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
- imaging parameters as the previous sections. For small cone angles the
- irradiance patterns are similar to the point sources in the previous sections,
- while larger cone angles create increasingly uniform irradiance patterns that
- hide the angular information about the distributions.
-
-  \begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/ph3.pdf}
-   \caption{\textbf{Left:} A spatially sparse and angularly dense
-     phantom---uniformly spaced double cone distributions of fluorophores with
-     varying central direction (increasing $\vartheta'$ from left to right) and
-     varying cone half-angle (increasing $\Delta$ from bottom to top).
-     \textbf{Center:} Scaled irradiance for an imaging system with
-     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
-     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
-     scaled irradiance. Small cone angles have irradiance patterns that vary
-     with the central direction, while larger cones angles have increasingly
-     uniform irradiance patterns that hide angular information.}
-   \label{fig:ph3}
- \end{figure}
-
- \subsubsection{Paraxial dipole spatio-angular transfer function}
- We can calculate the dipole spatio-angular transfer function by taking the
- spatial Fourier transform of the dipole angular transfer function (or the
- spherical Fourier transform of the dipole spatial transfer function) to find
- that
- \begin{align}
-H_{\ell}^m(\bv) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
- \end{align}
-
- In Fig. \ref{fig:dsatf} we plot the dipole spatio-angular transfer function for
- both spherical harmonic terms and several numerical apertures. The $\ell=0$
- term shows that an angularly uniform distribution of dipoles has a transfer
- function that is similar but not identical to the monopole transfer function
- with high frequencies increasingly suppressed as the numerical aperture
- increases. The $\ell=2$ term shows a negative pattern because of the large
- contribution of the transverse negative values in the $Y_2^0$ spherical
- harmonic. As the numerical aperture increases the relative contribution of the
- positive axial values increases and the $\ell=2$ term becomes less negative.
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/satf.pdf}
-   \caption{Spatio-angular dipole transfer function as a function of the scaled
-     spatial frequency $\nu/\nu_c$, the spherical harmonic degree $\ell$, and
-     $\text{NA}/n_o$. When the numerical aperture is small the transverse
-     dipoles contribute the most to the signal which gives rise to a positive
-     $\ell=0$ component and a negative $\ell=2$ component. As the numerical
-     aperture increases, the relative contribution of axial dipoles increases
-     and the $\ell=2$ component becomes less negative. Additionally, we plot the
-     monopole transfer function (\textcolor{green}{\textbf{green}}) and observe
-     that the $\ell=0$ term is similar but not identical to the monopole
-     transfer function, and this discrepancy increases with the numerical aperture.}
-   \label{fig:dsatf}
- \end{figure}
-
- To demonstrate the spatio-angular transfer function, we simulate a set of
- equally spaced disks of fluorophores with varying radius and angular
- distributions
- \begin{align}
-   f_{(ph4)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
- \end{align}
- where $D_k = 0.15(1+k)\, \mu$m, and $\Delta_j = j\frac{\pi}{6}$.
-
- Our first step towards calculating the irradiance pattern is to calculate the
- dipole spatio-angular spectrum given by the spatial Fourier transform of the dipole angular spectrum  
-  \begin{align}
-   \mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
-  \end{align}
-  We can plug the dipole spatio-angular spectrum into Eq. \eqref{eq:saft} to find
-  the scaled irradiance as 
-  \begin{align}
-   g_{(ph4)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y)\right\}.
-  \end{align}
-
-  In Fig. \ref{fig:ph4} we plot the phantom and scaled irradiance with the
-  same imaging parameters as the previous sections. Small cone angles and small
-  disks create relatively unique irradiance patterns, while increasing the cone
-  angle or disk size creates increasingly similar irradiance patterns.
-
-  \begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[scale=0.8]{../figures/paratfs/ph4.pdf}
-   \caption{\textbf{Left:} A spatially and angularly dense phantom---uniformly
-     spaced disks with varying size (increasing $D$ from bottom to top) and
-     double cone half angle (increasing $\Delta$ from left to right)
-     \textbf{Center:} Scaled irradiance for an imaging system with
-     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
-     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
-     scaled irradiance.}
-   \label{fig:ph4}
- \end{figure}
+% \end{align}
+% Note that the Fourier transform of a vector field is the Fourier transform of
+% its scalar-valued orthogonal components, so Eq. \eqref{eq:detectorfourier2}
+% specifies three two-dimensional Fourier transforms. We follow the same
+% manipulations as the previous section and find that the dipole coherent transfer
+% function is a scaled dipole pupil function
+% \begin{align}
+%   \mb{C}(\taup, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\taup, \so\right). \label{eq:monopupildip}
+% \end{align}
+
+% We have restricted our analysis to paraxial tube lenses, but non-paraxial tube
+% lenses (or a non-infinity-corrected objective) can be modeled with vector-valued
+% three-dimensional pupil functions \cite{sheppard1994, gu2000, arnison2002,
+%   foreman2011-2}.
+
+% \subsection{Special functions}
+% We adopt and generalize Bracewell's notation \cite{bracewell2004} for several
+% special functions which will simplify our calculations. First, we define a
+% \textit{rectangle function} as
+% \begin{align}
+%   \Pi(x) = 
+%   \begin{cases}
+%     1\quad \text{if}\quad |x| < \frac{1}{2},\\
+%     0\quad \text{else}.
+%   \end{cases}
+% \end{align}
+% We also define the \textit{$n^{th}$-order jinc function} as
+% \begin{align}
+%   \text{jinc}_n(r) = \frac{J_{n+1}(\pi r)}{2r},
+% \end{align}
+% where $J_{n+1}(r)$ is the $(n+1)^{th}$-order Bessel function of the first kind.
+
+% Although the rectangle and jinc functions are defined in one dimension, we will
+% usually apply them in two dimensions. In Appendix \ref{sec:special} we derive
+% the following two-dimensional Fourier transform relationships between the jinc
+% functions and the weighted rectangle functions
+% \begin{align}
+%   i^{n}\left\{\substack{
+%   \text{exp}(in\phi_r)\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\text{jinc}_n(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} (2\nu)^{n}\left\{\substack{
+%     \text{exp}(in\phi_{\nu})\\
+%     \cos(n\phi_{\nu})\\
+%     \sin(n\phi_{\nu})
+%   }\right\}\Pi(\nu), \label{eq:jincrect2}
+%   \end{align}
+%   where the entries inside the curly braces are to be taken one at a time and
+%   $\{r, \phi_r\}/\{\nu, \phi_\nu\}$ are conjugate sets of polar coordinates.
+
+% Finally, we define the \textit{$n^{th}$-order chat function} as the
+% two-dimensional Fourier transform of the squared $n^{th}$-order jinc function
+% \begin{align}
+%   \text{jinc}_n^2(r) \stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} \text{chat}_n(\nu).
+% \end{align}
+
+% In Appendix \ref{sec:special} we show that the zeroth- and first-order chat
+% functions can be written in closed form as
+% \begin{align}
+%   \text{chat}_0(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right),\\
+%   \text{chat}_1(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|(3-2x^2)\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right).  
+% \end{align}
+
+% \subsection{Monopole transfer functions}
+% Our first step towards the monopole transfer functions is to calculate the
+% monopole pupil function and coherent transfer function. Several works
+% \cite{petrov2017, backlund2018} have modeled an aplanatic fluorescence
+% microscope imaging monopole emitters with the scalar pupil function
+% \begin{align}
+%   p(\rp) \propto \tilde{C}\left(\frac{r_p}{f_o}\right)\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
+% \end{align}
+% where
+% \begin{align}
+%   \tilde{C}(x) = (1 - x^2)^{-1/4} = 1 + \frac{x^2}{4} + \frac{5x^4}{32} + \cdots. 
+% \end{align}
+% The $\tilde{C}(x)$ function models the radial dependence of the field and
+% ensures that power is conserved on either side of an aplanatic objective, and
+% the rectangle function models the aperture stop of the objective. Applying Eq.
+% \eqref{eq:monopupil0} and collecting constants we find that the coherent monopole
+% transfer function is
+% \begin{align}
+%   C(\taup) \propto \tilde{C}\left(\frac{2\text{NA}}{n_o}\frac{\tau}{\nu_c}\right)\Pi\left(\frac{\tau}{\nu_c}\right), \label{eq:coherentmonopole}
+% \end{align}
+% where $\text{NA} = n_o\sin\alpha$ and $\nu_c = 2\text{NA}/\lambda$. This
+% coherent transfer function models objectives with an arbitrary numerical
+% aperture, but for our initial analysis we restrict ourselves to the paraxial
+% regime. We drop second- and higher-order radial terms to find that
+% \begin{align}
+%   C(\taup) \stackrel{(p)}{\propto} \Pi\left(\frac{\tau}{\nu_c}\right), 
+% \end{align}
+% where $(p)$ indicates that we have used the paraxial approximation for the
+% objective lens.
+
+% We can find the monopole coherent spread function by taking the inverse Fourier
+% transform of the monopole coherent transfer function
+% \begin{align}
+%   c(\mb{r}) \stackrel{(p)}{\propto} \text{jinc}_0(\nu_c r).
+% \end{align}
+
+% The monopole point spread function is the (normalized) absolute square of the
+% monopole coherent spread function so
+% \begin{align}
+%   h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r),
+% \end{align}
+% which is the well-known \textit{Airy disk}.
+
+% Finally, we can calculate the monopole transfer function as the two-dimensional Fourier transform of the monopole point spread function (or the autocorrelation
+% of the coherent transfer function) and find that 
+% \begin{align}
+%   H(\bs{\nu}) \stackrel{(p)}{=} \frac{4}{\pi}\text{chat}_0\left(\frac{\nu}{\nu_c}\right).
+% \end{align}
+
+%  \subsection{Dipole transfer functions}
+%  To calculate the dipole transfer function we proceed similarly to the monopole
+%  case---we find the pupil function, scale to find the coherent dipole transfer
+%  function, then calculate the remaining transfer functions.
+
+%  Backer and Moerner \cite{backer2014} have calculated the dipole pupil function
+%  for a high-NA objective as
+%  \begin{align}
+%    \mb{p}(\rp, \so) \propto
+%    \begin{bmatrix}
+%      \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)c(\phi_p)\\
+%      \tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)s(\phi_p)\\
+%      0&0&0\\     
+%    \end{bmatrix}
+%    \begin{bmatrix}
+%      s_x\\
+%      s_y\\
+%      s_z
+%    \end{bmatrix}
+%    \Pi\left(\frac{r_p}{2f_os(\alpha)}\right),
+%  \end{align}
+%  where $c(x)$ and $s(x)$ are shorthand for $\cos(x)$ and $\sin(x)$,
+%  $\{s_x, s_y, s_z\}$ are the Cartesian components of $\so$ when $\mh{z}$ is
+%  aligned with the optical axis, and
+%  \begin{alignat}{4}
+%    \tilde{C}_0(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} + 1\right)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
+%    \tilde{C}_1(x) &= x(1 - x^2)^{-1/4} &&= x + \frac{x^3}{4} + \frac{5x^5}{32} + \cdots,\\
+%    \tilde{C}_2(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} - 1\right)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
+%  \end{alignat}
+%  Similar to the monopole case, the dipole pupil function conserves power and has
+%  a cutoff at the objective aperture, but the dipole pupil function is
+%  vector-valued to model the complete electric field in the pupil plane. The
+%  fields in the pupil plane have a negligible $\mh{z}$ component which is a
+%  consequence of our assumption that the tube lens is paraxial---modeling a
+%  non-paraxial tube lens would require a three-dimensional vector-valued pupil
+%  function \cite{sheppard1994, gu2000, arnison2002, foreman2011-2}.
+
+%  Scaling the dipole pupil function using Eq. \eqref{eq:monopupildip} yields the
+%  dipole coherent transfer function
+%  \begin{equation}
+%    \mb{C}(\taup, \so)\hspace{-0.2em}\propto\hspace{-0.2em}
+%    \begin{bmatrix}
+%      \tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!+\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)c(\phi_{\tau})\\
+%      \tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!-\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)s(\phi_{\tau})\\
+%      0&0&0\\     
+%    \end{bmatrix}
+%    \begin{bmatrix}
+%      s_x\\
+%      s_y\\
+%      s_z
+%    \end{bmatrix}
+%    \Pi\left(\frac{\tau}{\nu_c}\right). 
+%  \end{equation}
+%  We restrict our analysis to the paraxial regime by dropping second- and
+%  higher-order radial terms to find that
+%  \begin{align}
+%    \mb{C}(\taup, \so) \stackrel{(p)}{\propto}
+%    \begin{bmatrix}
+%      1&0&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\cos\phi_{\tau}\\
+%      0&1&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\sin\phi_{\tau}\\
+%      0&0&0\\     
+%    \end{bmatrix}
+%    \begin{bmatrix}
+%      s_x\\
+%      s_y\\
+%      s_z
+%    \end{bmatrix}
+%    \Pi\left(\frac{\tau}{\nu_c}\right). \label{eq:coherentdip}
+%  \end{align}
+%  Under the paraxial approximation the transverse components of the dipole
+%  \{$s_x, s_y$\} create purely transverse fields in the pupil plane and the axial
+%  component of the dipole \{$s_z$\} creates purely radial fields in the pupil
+%  plane. The paraxial approximation may seem crude compared to Backer and
+%  Moerner's numerical results, but the approximation will allow us to calculate
+%  the transfer functions in closed form so that we can build an intuition for the
+%  limits of the microscope. We also note that many existing works in ensemble
+%  polarized fluorescence microscopy make stronger approximations than ours. For
+%  example, Fourkas only considers the total irradiance in the pupil plane while
+%  ignoring the propagation of fields to the detector \cite{fourkas2001}.
+
+%  The dipole coherent spread function is the inverse Fourier transform of the
+%  dipole coherent transfer function. Applying Eq. \eqref{eq:jincrect2} in reverse
+%  yields
+%   \begin{align}
+%    \mb{c}(\mb{r}, \so) \stackrel{(p)}{\propto}
+%    \begin{bmatrix}
+%      \text{jinc}_0(\nu_c r)&0&\frac{\text{NA}}{n_o}i\cos\phi\,\text{jinc}_1(\nu_c r)\\
+%      0&\text{jinc}_0(\nu_c r)&\frac{\text{NA}}{n_o}i\sin\phi\,\text{jinc}_1(\nu_c r)\\
+%      0&0&0\\     
+%    \end{bmatrix}
+%    \begin{bmatrix}
+%      s_x\\
+%      s_y\\
+%      s_z
+%    \end{bmatrix}.
+%   \end{align}
+%   Notice that the radial component of the dipole coherent spread function has a
+%   $\pi/2$ phase shift relative to the transverse component. This phase factor
+%   arises because the Fourier transform of a real and odd function is purely
+%   imaginary.
+
+%   \subsubsection{Paraxial dipole point spread function}
+%   The dipole point spread function is the (normalized) absolute square of the
+% coherent dipole spread function
+% \begin{align}
+%   h(\mb{r}, \so) \propto \mb{c}(\mb{r}, \so)\mb{c}^\dagger(\mb{r}, \so). 
+% \end{align}
+% Plugging in the paraxial dipole coherent spread function and normalizing yields
+% \begin{align}
+%   h(\mb{r}, \so) \stackrel{(p)}{=} N\left[\text{jinc}_0^2(\nu_c r)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\cos^2\vartheta\right],\label{eq:paradpsf}
+% \end{align}
+% where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization
+% factor is
+% \begin{align}
+%   N = 6\nu_c^2\pi^{-3/2}\left[2 + \left(\frac{\text{NA}}{n_o}\right)^2\right]^{-1}.
+% \end{align}
+
+% As discussed above, the transverse and radial fields are out of phase on the
+% detector, so the total irradiance is the sum of the contributions from the
+% transverse and radial components. In Fig. \ref{fig:hdet} we plot the dipole
+% point spread function for several dipole orientations and numerical apertures,
+% and in Fig. \ref{fig:microscopefig} we compare the monopole point spread
+% function to the dipole point spread function. The paraxial monopole and dipole
+% models are only equivalent when the sample consists of transverse dipoles, which
+% is clear if we notice that Eq. \eqref{eq:paradpsf} reduces to an Airy disk when
+% $\vartheta = \pi/2$---see Novotny and Hecht for a similar observation
+% \cite[ch.~4]{nov2006}.
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/dpsf.pdf}
+%    \caption{Renormalized paraxial dipole point spread function as a function of
+%      the scaled radial coordinate $\nu_c r$, the dipole inclination angle
+%      $\vartheta$, and $\text{NA}/n_o$. For small numerical apertures (left) the
+%      irradiance pattern created by axial dipoles (\textcolor{red}{\textbf{red}})
+%      is small compared to transverse dipoles (\textbf{black}), but the relative
+%      contribution of axial dipoles increases with the numerical aperture (see
+%      \textcolor{red}{\textbf{red}} lines from left to right). Additionally, we
+%      plot the monopole point spread function (\textcolor{green}{\textbf{green}})
+%      and observe that the paraxial monopole and dipole models are identical for
+%      transverse dipoles (the \textcolor{green}{\textbf{green}} and
+%      \textbf{black} lines are coincident).}
+%    \label{fig:hdet}
+%  \end{figure}
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
+%    \caption{Comparison of paraxial models for monopole radiators a) and dipole
+%      radiators b)--d). a) Monopole radiators fill the pupil plane with a uniform
+%      scalar field which gives rise to an Airy disk on the detector. b) A
+%      transverse dipole radiator also creates an Airy disk, but the pupil plane
+%      is filled with a uniform vector field. c) An axial dipole radiator creates
+%      a radial electric field pattern in the back focal plane that creates a
+%      $\text{jinc}_1^2(r)$ pattern on the detector. d) Dipoles that are not
+%      transverse or axial still create radially symmetric irradiance patterns
+%      under the paraxial approximation. Fields from transverse dipoles are real
+%      and even while fields from axial dipoles are real and odd, which causes a
+%      relative $\pi/2$ phase shift for the fields on the detector. This phase
+%      shift means that the fields from transverse and axial components of the
+%      dipole do not interfere, which causes radially symmetric irradiance
+%      patterns.}
+%    \label{fig:microscopefig}
+%  \end{figure}
+
+%  To demonstrate the paraxial dipole point spread function we simulate a set of
+%  equally spaced dipoles with varying orientation:
+%  \begin{align}
+%    f_{(ph1)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, \delta\left(\cos\vartheta - \cos\vartheta_j\right)\, \delta\left(\varphi - \varphi_k\right),\label{eq:phantom1}
+%  \end{align}
+%  where $\vartheta_j = j\frac{\pi}{6}$, $\varphi_k = k\frac{\pi}{4}$, the
+%  subscript $(ph1)$ indicates that this is the first phantom, and the spatial
+%  coordinates are expressed in $\mu$m. To find the irradiance pattern created by
+%  the phantom we plug Eq. \eqref{eq:phantom1} into Eq. \eqref{eq:odpsf} and use
+%  the sifting property to find that
+%  \begin{align}
+%    g_{(ph1)}(r_x, r_y) = \sum_{j=0}^3 \sum_{k=0}^3 h\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}, \vartheta_j\right).\label{eq:phantom1irr}
+%  \end{align}
+%  In Fig. \ref{fig:ph1} we plot the phantom and scaled irradiance for an imaging
+%  system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$.
+%  We sample and plot the scaled irradiance at $20\times$ the Nyquist rate,
+%  $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free of aliasing.
+%  The output demonstrates that the irradiance pattern depends on the dipole
+%  inclination, but not its azimuth.
+
+%  \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/ph1.pdf}
+%    \caption{\textbf{Left:} A spatially and angularly sparse phantom---uniformly
+%      spaced single dipoles with varying orientations (increasing $\vartheta$
+%      from left to right and increasing $\varphi$ from bottom to top). White
+%      crosses mark the positions of the dipoles. \textbf{Center:} Scaled
+%      irradiance for an imaging system with $\text{NA} = 0.75$,
+%      $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at $20\times$ the
+%      Nyquist rate. \textbf{Right:} $x$ profiles through the scaled irradiance.
+%      The response is independent of the azimuth angle and strongly dependent on
+%      the inclination angle.}
+%    \label{fig:ph1}
+%  \end{figure}
+
+% \subsubsection{Paraxial dipole spatial transfer function}\label{sec:trans}
+% The dipole spatial transfer function is the spatial Fourier transform of
+% the dipole point spread function (or the complex autocorrelation of the dipole
+% coherent transfer function). Applying the Fourier transform to Eq.
+% \eqref{eq:paradpsf} we find that
+%   \begin{align}
+%     H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
+%   \end{align}
+% In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
+% several dipole orientations and numerical apertures. We find that the dipole
+% spatial transfer function is negative for axial dipoles at high spatial
+% frequencies, especially for larger numerical apertures. The negative dipole
+% spatial transfer corresponds to a contrast inversion for high-frequency
+% patterns of axial dipoles because the irradiance minimum corresponds to the
+% position of the dipole.
+
+% \begin{figure}[h]
+%  % \captionsetup{width=1.0\linewidth}
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/sdtf.pdf}
+%    \caption{Dipole spatial transfer function as a function of the scaled spatial
+%      frequency $\nu/\nu_c$, the dipole inclination angle $\vartheta$, and
+%      $\text{NA}/n_o$. For small numerical apertures (left) the dipole spatial
+%      transfer function for axial dipoles (\textcolor{red}{\textbf{red}}) is
+%      small compared to transverse dipoles (\textbf{black}), but the relative
+%      contribution of axial dipoles increases with the numerical aperture (see
+%      \textcolor{red}{\textbf{red}} lines from left to right). The spatial dipole
+%      transfer function of axial dipoles is negative at high spatial frequencies
+%      because the central minimum of the axial dipole point spread function
+%      corresponds to the position of the dipole. Equivalently, a
+%      high-spatial-frequency pattern of axial dipoles will generate an irradiance
+%      pattern where the minimum irradiance corresponds to the peak of the axial
+%      dipole density. Additionally, we plot the monopole transfer function
+%      (\textcolor{green}{\textbf{green}}) and observe that the paraxial monopole
+%      and dipole models are identical for transverse dipoles (the
+%      \textcolor{green}{\textbf{green}} and \textbf{black} lines are
+%      coincident).}
+%    \label{fig:odotf}
+%  \end{figure}
+
+%  To demonstrate the dipole spatial transfer function we simulate a set of
+%  equally spaced disks with varying diameter containing fluorophores with varying
+%  orientation
+%  \begin{align}
+%    f_{(ph2)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
+%  \end{align}
+%  where $D_k = 0.15(1+k)\, \mu$m and $\vartheta_j = j\frac{\pi }{6}$. Notice that
+%  we have scaled the disks so that the total number of fluorophores in each disk
+%  is constant. Also notice that the disk can model a spatial distribution of many
+%  fluorophores or a single molecule undergoing spatial diffusion within a well.
+
+%  We can calculate the irradiance pattern by taking the spatial Fourier transform
+%  for each orientation in the phantom, filtering the result with the dipole
+%  spatial transfer function, integrating over the orientations, then taking the
+%  inverse spatial Fourier transform. Since our phantom is angularly sparse, the
+%  integral becomes a sum and we find that
+%  \begin{align}
+%    g_{(ph2)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{(ph2)}(r_x, r_y, \vartheta_j)\right\}\right\}.
+%  \end{align}
+
+%  In Fig. \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
+%  imaging parameters as the previous section. The small disks create irradiance
+%  patterns that are similar to the point sources in the previous section, while
+%  larger disks create increasingly uniform irradiance patterns that hide the
+%  orientation of the fluorophores.
+
+%   \begin{figure}[h]
+%  % \captionsetup{width=1.0\linewidth}
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/ph2.pdf}
+%    \caption{\textbf{Left:} A spatially dense and angularly sparse
+%      phantom---uniformly spaced disks with varying size (increasing $D$ from
+%      bottom to top) and dipole orientation (increasing $\vartheta$ from left to
+%      right) \textbf{Center:} Scaled irradiance for an imaging system with
+%      $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+%      $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+%      scaled irradiance. Larger disks generate increasingly uniform irradiance
+%      patterns with fewer details that may indicate the orientation of
+%      fluorophores.}
+%    \label{fig:ph2}
+%  \end{figure}
+
+%  \subsubsection{Paraxial dipole angular transfer function}
+%  To calculate the angular dipole transfer function we take the spherical Fourier
+%  transform of the dipole point spread function
+%  \begin{align}
+% H_l^m(\mb{r}) \stackrel{}{=} \int_{\mbb{S}^2}d\so\, h(\mb{r}, \so)Y_l^{m*}(\so).
+%  \end{align}
+%  After evaluating the integrals and normalizing, the angular dipole transfer
+%  function is
+%  \begin{align}
+%    H_l^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3}\left[2\text{jinc}_0^2(\nu_cr) + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_0\delta_{\ell0}\delta_{m0} + \nonumber\\& \frac{N}{3}\left[-2\text{jinc}_0^2(\nu_c r) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_2\delta_{\ell2}\delta_{m0},
+%  \end{align}
+% where $\Lambda_{\ell} = \sqrt{4\pi/(2\ell + 1)}$.
+
+% In Fig. \ref{fig:atf} we plot the dipole angular transfer function for both
+% spherical harmonic terms and several numerical apertures. Note that the dipole
+% angular transfer function can be negative because the spherical harmonics can
+% take negative values. The $\ell=0$ term shows that angularly uniform
+% distributions of dipoles create spatial irradiance patterns that are similar but
+% not identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
+% because of the large contribution of the transverse negative values in the
+% $Y_2^0$ spherical harmonic.
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/adtf.pdf}
+%    \caption{Paraxial dipole angular transfer function in terms of a scaled
+%      radial detection coordinate $\nu_c r$, the spherical harmonic degree
+%      $\ell$, and $\text{NA}/n_o$. Angularly uniform distributions of dipoles
+%      $\ell=0$ generate a spatial pattern that is similar but not identical to
+%      the Airy disk created by a monopole (\textcolor{green}{\textbf{green}}),
+%      and this discrepancy increases with the numerical aperture. $\ell=2$
+%      distributions have a negative response because $Y_2^0(\mh{s})$ is negative
+%      for transverse directions. As the numerical aperture increases, the
+%      relative contribution of positive axial dipoles in the $\ell=2$
+%      distribution increases.}
+%    \label{fig:atf}
+%  \end{figure}
+
+%  To demonstrate the dipole angular transfer function we simulate a set of
+%  equally spaced fluorophore distributions with varying orientation and angular
+%  distributions
+%  \begin{align}
+%    f_{(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
+%  \end{align}
+%  where
+%  \begin{align}
+%    f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right)
+%  \end{align}
+%  is an angular double cone distribution with central direction $\mh{s}'$ and
+%  cone half-angle $\Delta$; $\vartheta_j = j\frac{\pi}{6}$; and
+%  $\Delta_k = k\frac{\pi}{6}$. Notice that when $\Delta = 0$ the angular double
+%  cone reduces to a single direction, and when $\Delta = \pi/2$ the angular
+%  double cone reduces to an angularly uniform distribution. Also notice that the
+%  double cone can model angular diffusion or the angular distribution of many
+%  fluorophores within a resolvable volume.
+
+%  Our first step towards the irradiance pattern is to calculate the dipole
+%  angular spectrum of the phantom. In Appendix \ref{sec:cone} we calculate the
+%  spherical Fourier transform of the double cone distribution
+%  $F^m_{\ell,\text{(cone)}}(\vartheta', \varphi'; \Delta)$ which we can use to
+%  express the dipole angular spectrum as
+%  \begin{align}
+%    F^{m}_{\ell,(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
+%  \end{align}
+
+%  To find the irradiance we plug the dipole angular spectrum into Eq.
+%  \eqref{eq:atf-form} and use the sifting property to find that
+%  \begin{align}
+%    g_{(ph3)}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
+%  \end{align}
+
+%  In Fig. \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
+%  imaging parameters as the previous sections. For small cone angles the
+%  irradiance patterns are similar to the point sources in the previous sections,
+%  while larger cone angles create increasingly uniform irradiance patterns that
+%  hide the angular information about the distributions.
+
+%   \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/ph3.pdf}
+%    \caption{\textbf{Left:} A spatially sparse and angularly dense
+%      phantom---uniformly spaced double cone distributions of fluorophores with
+%      varying central direction (increasing $\vartheta'$ from left to right) and
+%      varying cone half-angle (increasing $\Delta$ from bottom to top).
+%      \textbf{Center:} Scaled irradiance for an imaging system with
+%      $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+%      $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+%      scaled irradiance. Small cone angles have irradiance patterns that vary
+%      with the central direction, while larger cones angles have increasingly
+%      uniform irradiance patterns that hide angular information.}
+%    \label{fig:ph3}
+%  \end{figure}
+
+%  \subsubsection{Paraxial dipole spatio-angular transfer function}
+%  We can calculate the dipole spatio-angular transfer function by taking the
+%  spatial Fourier transform of the dipole angular transfer function (or the
+%  spherical Fourier transform of the dipole spatial transfer function) to find
+%  that
+%  \begin{align}
+% H_{\ell}^m(\bv) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
+%  \end{align}
+
+%  In Fig. \ref{fig:dsatf} we plot the dipole spatio-angular transfer function for
+%  both spherical harmonic terms and several numerical apertures. The $\ell=0$
+%  term shows that an angularly uniform distribution of dipoles has a transfer
+%  function that is similar but not identical to the monopole transfer function
+%  with high frequencies increasingly suppressed as the numerical aperture
+%  increases. The $\ell=2$ term shows a negative pattern because of the large
+%  contribution of the transverse negative values in the $Y_2^0$ spherical
+%  harmonic. As the numerical aperture increases the relative contribution of the
+%  positive axial values increases and the $\ell=2$ term becomes less negative.
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/satf.pdf}
+%    \caption{Spatio-angular dipole transfer function as a function of the scaled
+%      spatial frequency $\nu/\nu_c$, the spherical harmonic degree $\ell$, and
+%      $\text{NA}/n_o$. When the numerical aperture is small the transverse
+%      dipoles contribute the most to the signal which gives rise to a positive
+%      $\ell=0$ component and a negative $\ell=2$ component. As the numerical
+%      aperture increases, the relative contribution of axial dipoles increases
+%      and the $\ell=2$ component becomes less negative. Additionally, we plot the
+%      monopole transfer function (\textcolor{green}{\textbf{green}}) and observe
+%      that the $\ell=0$ term is similar but not identical to the monopole
+%      transfer function, and this discrepancy increases with the numerical aperture.}
+%    \label{fig:dsatf}
+%  \end{figure}
+
+%  To demonstrate the spatio-angular transfer function, we simulate a set of
+%  equally spaced disks of fluorophores with varying radius and angular
+%  distributions
+%  \begin{align}
+%    f_{(ph4)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
+%  \end{align}
+%  where $D_k = 0.15(1+k)\, \mu$m, and $\Delta_j = j\frac{\pi}{6}$.
+
+%  Our first step towards calculating the irradiance pattern is to calculate the
+%  dipole spatio-angular spectrum given by the spatial Fourier transform of the dipole angular spectrum  
+%   \begin{align}
+%    \mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
+%   \end{align}
+%   We can plug the dipole spatio-angular spectrum into Eq. \eqref{eq:saft} to find
+%   the scaled irradiance as 
+%   \begin{align}
+%    g_{(ph4)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y)\right\}.
+%   \end{align}
+
+%   In Fig. \ref{fig:ph4} we plot the phantom and scaled irradiance with the
+%   same imaging parameters as the previous sections. Small cone angles and small
+%   disks create relatively unique irradiance patterns, while increasing the cone
+%   angle or disk size creates increasingly similar irradiance patterns.
+
+%   \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[scale=0.8]{../figures/paratfs/ph4.pdf}
+%    \caption{\textbf{Left:} A spatially and angularly dense phantom---uniformly
+%      spaced disks with varying size (increasing $D$ from bottom to top) and
+%      double cone half angle (increasing $\Delta$ from left to right)
+%      \textbf{Center:} Scaled irradiance for an imaging system with
+%      $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
+%      $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
+%      scaled irradiance.}
+%    \label{fig:ph4}
+%  \end{figure}
 
@@
 fluorophores, so the most accurate fluorescence microscopy experiments will
-always use dipole transfer functions over monopole transfer functions. The only
-case when the dipole and monopole transfer functions match exactly is when the
-dipoles are completely constrained to the transverse plane of a paraxial imaging
-system.
-
-However, in many practical situations noise will mask the effects of vector
-optics and dipoles. If the fluorophores are rotationally unconstrained or there
-are many randomly oriented fluorophores in a resolvable volume---common
-situations in biological applications---then the effects of vector optics and
-dipoles will be masked by noise in all but the highest-SNR regimes.
-
-The dipole transfer functions are most broadly useful when the sample contains
-fluorophores that are rotationally constrained. As rotational constraints
-increase, the effects of vector optics and dipoles will become apparent in lower
-SNR regimes.
+always use dipole transfer functions over monopole transfer functions. However,
+in many practical situations noise will mask the effects of vector optics and
+dipoles. If the fluorophores are rotationally unconstrained or there are many
+randomly oriented fluorophores in a resolvable volume---common situations in
+biological applications---then the effects of vector optics and dipoles will be
+masked by noise in all but the highest-SNR regimes. Therefore, the dipole
+transfer functions are most broadly useful when the sample contains fluorophores
+that are rotationally constrained. As rotational constraints increase, the
+effects of vector optics and dipoles will become apparent in lower SNR regimes.
+In the next paper of this series we will calculate the dipole transfer functions
+for a 4-$f$ imaging system and investigate the conditions under which the
+monopole and dipole models are identical.
 
@@
 
-\subsection{What determines the angular bandwidth?}
-Spatial imaging systems have a spatial bandwidth that characterizes the highest
-spatial frequency that the system can transfer between object and data space.
-Similarly, angular imaging systems have an angular bandwidth that characterizes
-the highest angular frequency that the system can transfer, but in the angular case
-there are two different types of angular bandwidths that we call the $\ell$- and
-$m$-bandwidth. The $\ell$-bandwidth can be interpreted in a similar way to the
-spatial bandwidth---it characterizes the smallest angular features that the
-imaging system can measure. The $m$-bandwidth does not have a direct analog in
-the spatial domain---it characterizes the angular uniformity of the imaging
-system. If the $\ell$- and $m$-bandwidths are equal then the imaging system can
-be said to have an $\textit{isotropic angular bandwidth}$.
-
-The spatial bandwidth of a fluorescence microscope is well known to be
-$\nu_c = \frac{2\text{NA}}{\lambda}$. In other words, we can increase the
-spatial resolution of a fluorescence microscope by increasing the NA of the
-instrument or by choosing a fluorophore with a shorter emission wavelength.
-Similarly, the angular bandwidth of a fluorescence microscope depends on both
-the instrument and the choice of fluorophore.
-
-The microscope we considered in this work has an $\ell$-bandwidth of
-$\ell_c = 2$ and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic
-angular bandwidth. In future work we will consider several approaches to
-improving the angular bandwidths in detail, but we briefly mention that
-non-paraxial microscopes, microscopes with polarizers in the illumination or
-detection paths, and multiview microscopes all have higher angular bandwidths
-than the microscope considered here.
-
-The angular bandwidth is also fluorophore dependent. Monopoles emit light
-isotropically so they have an $\ell$-bandwidth of $\ell_c = 0$, while dipoles
-have an $\ell$-bandwidth of $\ell_c = 2$, and higher-order excitation and
-detection moments will have even higher bandwidths. Multi-photon excitation and
-other non-linear methods can also increase the $\ell$-bandwidth
-\cite{brasselet2011}.
-
-\subsection{Towards more realistic models}
-The theoretical model we presented in this work is an extreme simplification of
-a real microscope. We have ignored the effects of thick samples,
-refractive-index mismatch, aberration, scattering, finite fluorescence
-lifetimes, and interactions between fluorophores among others. Because of this
-long list of unconsidered effects, real experiments will likely require
-extensions of the models developed here.
-
-The dipole pupil function provides the simplest way to create more realistic
-models from the simple model in this paper. Phase aberrations can be added to
-the dipole pupil function with Zernike polynomials, and refractive index
-boundaries can be modeled by applying the work of Gibson and Lanni to the dipole
-pupil function \cite{gibson89}. These additions will model phase aberrations,
-but modeling polarization aberrations will also be necessary, and we anticipate
-that vector Zernike polynomials and the Jones pupil \cite{zhao2007, xu2015,
-  chipman1989} will be essential tools for modeling dipole imaging systems. We
-plan to use the dipole pupil function to include the effects of non-paraxial
-objectives, polarizers, and defocus in future papers of this series.
-
-The dipole pupil function also provides an enormous set of design opportunities.
-The dipole imaging problem may benefit from spatially varying diattenuating and
-birefrigent masks---a much larger set of possibilities than the well-explored
-design space of amplitude and phase masks. The dipole pupil function is a step
-towards Green's tensor engineering \cite{agrawal2012}, and the dipole transfer
-functions provide a strong framework for evaluating dipole imaging designs.
-
-In the simple case considered here we focused on the emission path of the
-microscope, but the excitation path is equally important. Complete models will
-need to consider the spatio-angular dependence of excitation. Zhenghao et. al.
-\cite{zhanghao2017} have taken steps in this direction by considering polarized
-structured illumination microscopy. Rotational dynamics and the fluorescence
-lifetime are also important to consider when incorporating models of the
-excitation process \cite{lew2013, zhang2018, zhang2018-2}.
+% \subsection{What determines the angular bandwidth?}
+% Spatial imaging systems have a spatial bandwidth that characterizes the highest
+% spatial frequency that the system can transfer between object and data space.
+% Similarly, angular imaging systems have an angular bandwidth that characterizes
+% the highest angular frequency that the system can transfer, but in the angular case
+% there are two different types of angular bandwidths that we call the $\ell$- and
+% $m$-bandwidth. The $\ell$-bandwidth can be interpreted in a similar way to the
+% spatial bandwidth---it characterizes the smallest angular features that the
+% imaging system can measure. The $m$-bandwidth does not have a direct analog in
+% the spatial domain---it characterizes the angular uniformity of the imaging
+% system. If the $\ell$- and $m$-bandwidths are equal then the imaging system can
+% be said to have an $\textit{isotropic angular bandwidth}$.
+
+% The spatial bandwidth of a fluorescence microscope is well known to be
+% $\nu_c = \frac{2\text{NA}}{\lambda}$. In other words, we can increase the
+% spatial resolution of a fluorescence microscope by increasing the NA of the
+% instrument or by choosing a fluorophore with a shorter emission wavelength.
+% Similarly, the angular bandwidth of a fluorescence microscope depends on both
+% the instrument and the choice of fluorophore.
+
+% The microscope we considered in this work has an $\ell$-bandwidth of
+% $\ell_c = 2$ and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic
+% angular bandwidth. In future work we will consider several approaches to
+% improving the angular bandwidths in detail, but we briefly mention that
+% non-paraxial microscopes, microscopes with polarizers in the illumination or
+% detection paths, and multiview microscopes all have higher angular bandwidths
+% than the microscope considered here.
+
+% The angular bandwidth is also fluorophore dependent. Monopoles emit light
+% isotropically so they have an $\ell$-bandwidth of $\ell_c = 0$, while dipoles
+% have an $\ell$-bandwidth of $\ell_c = 2$, and higher-order excitation and
+% detection moments will have even higher bandwidths. Multi-photon excitation and
+% other non-linear methods can also increase the $\ell$-bandwidth
+% \cite{brasselet2011}.
+
+% \subsection{Towards more realistic models}
+% The theoretical model we presented in this work is an extreme simplification of
+% a real microscope. We have ignored the effects of thick samples,
+% refractive-index mismatch, aberration, scattering, finite fluorescence
+% lifetimes, and interactions between fluorophores among others. Because of this
+% long list of unconsidered effects, real experiments will likely require
+% extensions of the models developed here.
+
+% The dipole pupil function provides the simplest way to create more realistic
+% models from the simple model in this paper. Phase aberrations can be added to
+% the dipole pupil function with Zernike polynomials, and refractive index
+% boundaries can be modeled by applying the work of Gibson and Lanni to the dipole
+% pupil function \cite{gibson89}. These additions will model phase aberrations,
+% but modeling polarization aberrations will also be necessary, and we anticipate
+% that vector Zernike polynomials and the Jones pupil \cite{zhao2007, xu2015,
+%   chipman1989} will be essential tools for modeling dipole imaging systems. We
+% plan to use the dipole pupil function to include the effects of non-paraxial
+% objectives, polarizers, and defocus in future papers of this series.
+
+% The dipole pupil function also provides an enormous set of design opportunities.
+% The dipole imaging problem may benefit from spatially varying diattenuating and
+% birefrigent masks---a much larger set of possibilities than the well-explored
+% design space of amplitude and phase masks. The dipole pupil function is a step
+% towards Green's tensor engineering \cite{agrawal2012}, and the dipole transfer
+% functions provide a strong framework for evaluating dipole imaging designs.
+
+% In the simple case considered here we focused on the emission path of the
+% microscope, but the excitation path is equally important. Complete models will
+% need to consider the spatio-angular dependence of excitation. Zhenghao et. al.
+% \cite{zhanghao2017} have taken steps in this direction by considering polarized
+% structured illumination microscopy. Rotational dynamics and the fluorescence
+% lifetime are also important to consider when incorporating models of the
+% excitation process \cite{lew2013, zhang2018, zhang2018-2}.
 
@@
   approximations, but complete models need to consider dipole and vector optics
-effects. We have introduced several transfer functions that simplify the mapping
-between the dipole density and the irradiance pattern on the detector, and we
-have demonstrated these transfer functions by efficiently simulating a paraxial
-fluorescence microscope. We found that the monopole and scalar approximations
-are good approximations when the sample consists of unconstrained rotating
-fluorophores or many randomly oriented fluorophores within a resolvable volume.
-We also found that dipole and vector optics effects become larger as rotational
-order increases, and in these cases the dipole transfer functions become
-valuable tools.
+  effects. In this work we have introduced several transfer functions that
+  simplify the mapping between the dipole density and the irradiance pattern on
+  the detector. In future papers of this series we will calculate these transfer
+  functions for specific instruments and use the results to simulate and analyze
+  data collected by these instruments.% , and we
+% have demonstrated these transfer functions by efficiently simulating a paraxial
+% fluorescence microscope. We found that the monopole and scalar approximations
+% are good approximations when the sample consists of unconstrained rotating
+% fluorophores or many randomly oriented fluorophores within a resolvable volume.
+% We also found that dipole and vector optics effects become larger as rotational
+% order increases, and in these cases the dipole transfer functions become
+% valuable tools.
 
@@
 
-\section{Relationships between special functions} \label{sec:special}
-Our first task is to show that 
-\begin{align}
-  i^{n}\left\{\substack{
-  \text{exp}(in\phi_r)\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\text{jinc}_{n}(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow}   (2\nu)^{n}\left\{\substack{
-    \text{exp}(in\phi_{\nu})\\
-    \cos(n\phi_{\nu})\\
-    \sin(n\phi_{\nu})
-  }\right\}\Pi(\nu). \label{eq:jincrect3}
-  \end{align}
-  Writing the inverse Fourier transform in polar coordinates yields
-  \begin{align}
-    =2^n\int_0^{1/2}d\nu\, \nu^{n+1}\int_0^{2\pi}d\phi_\nu\left\{\substack{
-    \text{exp}(in\phi_{\nu})\\
-    \cos(n\phi_{\nu})\\
-    \sin(n\phi_{\nu})
-  }\right\}\text{exp}[2\pi i\nu r\cos(\phi_\nu - \phi_r)].
-  \end{align}
-  The azimuthal integral can be evaluated in terms of an $n^{th}$ order Bessel
-  function (for the complex case see \cite[ch. 4.111]{barrett2004}).
-  \begin{align}
-    =2^n 2\pi i^n \left\{\substack{
-    \text{exp}(in\phi_{r})\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\int_0^{1/2}d\nu\, \nu^{n+1}J_n(2\pi\nu r).
-  \end{align}
-  We can use the following identity \cite[ch.~6.561-5]{gradshteyn2007}
-  \begin{align}
-    \int_0^1 du\, u^{n + 1}J_{n}(au) = a^{-1}J_{n + 1}(a)
-  \end{align}
-  with a change of variable $u = 2\nu$ to find the final result
-  \begin{align}
-    &=2^n 2\pi i^n \left\{\substack{
-    \text{exp}(in\phi_{r})\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\int_0^{1}\frac{du}{2}\, \left(\frac{u}{2}\right)^{n+1}J_n(\pi u r)
-    =i^n \left\{\substack{
-    \text{exp}(in\phi_{r})\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\frac{J_{n+1}(\pi r)}{2r}
-    =i^n \left\{\substack{
-    \text{exp}(in\phi_{r})\\
-    \cos(n\phi_r)\\
-    \sin(n\phi_r)
-  }\right\}\text{jinc}_{n}(r).
-  \end{align}
-
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[width = 0.45\textwidth]{../figures/special/special.pdf}
-   \caption{The relationships between special functions. The chat functions are
-     defined as the two-dimensional Fourier transform of the squared jinc
-     functions, and they can be calculated with the two-dimensional complex
-     autocorrelations (denoted by $\star_2$) of the complex-weighted rectangle
-     functions.}
-   \label{fig:special}
- \end{figure}
-
-We can use the relationship in Eq. \eqref{eq:jincrect3} to express the chat
-functions in terms of a complex autocorrelation---see the diagram in Fig. \ref{fig:special}. Starting with the definition of
-the $n^{th}$-order chat function
-\begin{align}
-  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, \text{jinc}_{n}^2(|\mb{r}|)\, \text{exp}\left[-2\pi i\mb{r}\nu\right],  \label{eq:ftA}
-\end{align}
-we can rewrite the integrand in terms of the absolute square of a simpler
-function with a known Fourier transform
-\begin{align}
-  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, |t_n(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\nu\right].  \label{eq:ftB}
-\end{align}
-\begin{align}
-  t_n(\mb{r}) = i^n\text{exp}[in\phi_r]\text{jinc}_{n}(r).
-\end{align}
-Now we can apply the autocorrelation theorem to rewrite the Fourier transform as
-\begin{align}
-  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})T^*_n(\bs{\tau} - \nu), \label{eq:autocorr}
-\end{align}
-where the function to be autocorrelated can be found with the help of Eq. \eqref{eq:jincrect3}
-\begin{align}
-  T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right] = (2\tau)^n\text{exp}[in\phi_\tau]\Pi\left(\tau\right). \label{eq:tau}
-\end{align}
-It will be more convenient to set up the autocorrelation in Cartesian coordinates 
-\begin{align}
-  T_n(\bs{\tau}) &= 2^n(\tau_x + i\tau_y)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right). \label{eq:tn}
-\end{align}
-Plugging Eq. \eqref{eq:tn} into Eq. \eqref{eq:autocorr} gives
-\begin{align}
-  \text{chat}_{n}(\nu) = 4^n\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right)\Pi\left(\sqrt{(\tau_x - \nu)^2 + \tau_y^2}\right).
-\end{align}
-We can interpret the autocorrelation as an integral over a region of overlap
-between a circle centered at the origin and a circle shifted to the right by
-$\nu$ (a geometric lens). Using the construction in Fig. \ref{fig:geometry} we
-can express this region as
-\begin{align}
-  \text{chat}_{n}(\nu) = 4^{n+1}\Bigg[&\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Bigg]\Pi\left(\frac{\nu}{2}\right).
-\end{align}
-\begin{figure}[h]
- \centering
-   \centering
-   \includegraphics[width = 1.0\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
-   \caption{Geometric construction for evaluating the autocorrelation. We need
-     to integrate over the overlapping region of two circles with radius $1/2$
-     and distance $\nu$ between their centers. The region is four times the
-     difference in area between a sector of angle $\cos^{-1}(\nu)$ and radius
-     $1/2$ and a right triangle with base $\nu/2$ and hypotenuse $1/2$.}
-   \label{fig:geometry}
- \end{figure}
-
-For $n=0$:
-\begin{align}
-  \text{chat}_0(\nu) &= 4\left[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2}\right),\\
-  \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu|\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
-\intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
-  \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \nonumber\\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
-  \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu| (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
-\end{align}
-
-\section{Spherical Fourier transform of a double cone}\label{sec:cone}
-In this appendix we evaluate the spherical Fourier transform of a
-normalized double-cone angular distribution with central direction $\mh{s}'$ and
-cone half-angle $\Delta$
-\begin{align}
-  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right). \label{eq:doublecone}
-\end{align}
-The spherical Fourier transform is
-\begin{align}
-  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)Y_\ell^{m*}(\mh{s}).
-\end{align}
-
-The limits of integration will be difficult to find unless we change coordinates
-to exploit the axis of symmetry $\mh{s}'$. Since the spherical function is
-rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
-symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
-\end{align}
-In this coordinate system the double cone is independent of the azimuthal angle,
-so we can evaluate the azimuthal integral and express the function in terms of an
-integral over $\vartheta$:
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^{m*}(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
-\end{align}
-The function $f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)$ is only non-zero on
-the intervals $\vartheta \in [0, \Delta]$ and
-$\vartheta \in [\pi - \Delta, \pi]$ so
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right].
-\end{align}
-Applying a change of coordinates with $u = \cos\vartheta$ yields
-\begin{align}
-    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right]. 
-\end{align}
-The Legendre polynomials $P_\ell(u)$ are even (odd) on the interval [-1, 1] when
-$\ell$ is even (odd), so the pair of integrals will be identical when $\ell$ is
-even and cancel when $\ell$ is odd. For even $\ell$,
-\begin{align}
-  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
-\end{align}
-The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
-\begin{align}
-  \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
-\begin{cases}
-  1 - \cos\Delta\,, &\ell = 0\,,\\
-  \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
-\end{cases}
-\end{align}
-where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
-$m=-1$, not an inverse Legendre polynomial. Bringing everything together
-\begin{align}
-  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) =
-  \begin{cases}
-    \sqrt{1/(4\pi)}, & \ell = 0,\\
-    0, & \ell\, \text{odd},\\
-    Y_\ell^{m*}(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
-  \end{cases}
-\end{align}
+% \section{Relationships between special functions} \label{sec:special}
+% Our first task is to show that 
+% \begin{align}
+%   i^{n}\left\{\substack{
+%   \text{exp}(in\phi_r)\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\text{jinc}_{n}(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow}   (2\nu)^{n}\left\{\substack{
+%     \text{exp}(in\phi_{\nu})\\
+%     \cos(n\phi_{\nu})\\
+%     \sin(n\phi_{\nu})
+%   }\right\}\Pi(\nu). \label{eq:jincrect3}
+%   \end{align}
+%   Writing the inverse Fourier transform in polar coordinates yields
+%   \begin{align}
+%     =2^n\int_0^{1/2}d\nu\, \nu^{n+1}\int_0^{2\pi}d\phi_\nu\left\{\substack{
+%     \text{exp}(in\phi_{\nu})\\
+%     \cos(n\phi_{\nu})\\
+%     \sin(n\phi_{\nu})
+%   }\right\}\text{exp}[2\pi i\nu r\cos(\phi_\nu - \phi_r)].
+%   \end{align}
+%   The azimuthal integral can be evaluated in terms of an $n^{th}$ order Bessel
+%   function (for the complex case see \cite[ch. 4.111]{barrett2004}).
+%   \begin{align}
+%     =2^n 2\pi i^n \left\{\substack{
+%     \text{exp}(in\phi_{r})\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\int_0^{1/2}d\nu\, \nu^{n+1}J_n(2\pi\nu r).
+%   \end{align}
+%   We can use the following identity \cite[ch.~6.561-5]{gradshteyn2007}
+%   \begin{align}
+%     \int_0^1 du\, u^{n + 1}J_{n}(au) = a^{-1}J_{n + 1}(a)
+%   \end{align}
+%   with a change of variable $u = 2\nu$ to find the final result
+%   \begin{align}
+%     &=2^n 2\pi i^n \left\{\substack{
+%     \text{exp}(in\phi_{r})\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\int_0^{1}\frac{du}{2}\, \left(\frac{u}{2}\right)^{n+1}J_n(\pi u r)
+%     =i^n \left\{\substack{
+%     \text{exp}(in\phi_{r})\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\frac{J_{n+1}(\pi r)}{2r}
+%     =i^n \left\{\substack{
+%     \text{exp}(in\phi_{r})\\
+%     \cos(n\phi_r)\\
+%     \sin(n\phi_r)
+%   }\right\}\text{jinc}_{n}(r).
+%   \end{align}
+
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[width = 0.45\textwidth]{../figures/special/special.pdf}
+%    \caption{The relationships between special functions. The chat functions are
+%      defined as the two-dimensional Fourier transform of the squared jinc
+%      functions, and they can be calculated with the two-dimensional complex
+%      autocorrelations (denoted by $\star_2$) of the complex-weighted rectangle
+%      functions.}
+%    \label{fig:special}
+%  \end{figure}
+
+% We can use the relationship in Eq. \eqref{eq:jincrect3} to express the chat
+% functions in terms of a complex autocorrelation---see the diagram in Fig. \ref{fig:special}. Starting with the definition of
+% the $n^{th}$-order chat function
+% \begin{align}
+%   \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, \text{jinc}_{n}^2(|\mb{r}|)\, \text{exp}\left[-2\pi i\mb{r}\nu\right],  \label{eq:ftA}
+% \end{align}
+% we can rewrite the integrand in terms of the absolute square of a simpler
+% function with a known Fourier transform
+% \begin{align}
+%   \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, |t_n(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\nu\right].  \label{eq:ftB}
+% \end{align}
+% \begin{align}
+%   t_n(\mb{r}) = i^n\text{exp}[in\phi_r]\text{jinc}_{n}(r).
+% \end{align}
+% Now we can apply the autocorrelation theorem to rewrite the Fourier transform as
+% \begin{align}
+%   \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})T^*_n(\bs{\tau} - \nu), \label{eq:autocorr}
+% \end{align}
+% where the function to be autocorrelated can be found with the help of Eq. \eqref{eq:jincrect3}
+% \begin{align}
+%   T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right] = (2\tau)^n\text{exp}[in\phi_\tau]\Pi\left(\tau\right). \label{eq:tau}
+% \end{align}
+% It will be more convenient to set up the autocorrelation in Cartesian coordinates 
+% \begin{align}
+%   T_n(\bs{\tau}) &= 2^n(\tau_x + i\tau_y)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right). \label{eq:tn}
+% \end{align}
+% Plugging Eq. \eqref{eq:tn} into Eq. \eqref{eq:autocorr} gives
+% \begin{align}
+%   \text{chat}_{n}(\nu) = 4^n\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right)\Pi\left(\sqrt{(\tau_x - \nu)^2 + \tau_y^2}\right).
+% \end{align}
+% We can interpret the autocorrelation as an integral over a region of overlap
+% between a circle centered at the origin and a circle shifted to the right by
+% $\nu$ (a geometric lens). Using the construction in Fig. \ref{fig:geometry} we
+% can express this region as
+% \begin{align}
+%   \text{chat}_{n}(\nu) = 4^{n+1}\Bigg[&\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Bigg]\Pi\left(\frac{\nu}{2}\right).
+% \end{align}
+% \begin{figure}[h]
+%  \centering
+%    \centering
+%    \includegraphics[width = 1.0\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
+%    \caption{Geometric construction for evaluating the autocorrelation. We need
+%      to integrate over the overlapping region of two circles with radius $1/2$
+%      and distance $\nu$ between their centers. The region is four times the
+%      difference in area between a sector of angle $\cos^{-1}(\nu)$ and radius
+%      $1/2$ and a right triangle with base $\nu/2$ and hypotenuse $1/2$.}
+%    \label{fig:geometry}
+%  \end{figure}
+
+% For $n=0$:
+% \begin{align}
+%   \text{chat}_0(\nu) &= 4\left[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2}\right),\\
+%   \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu|\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
+% \intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
+%   \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \nonumber\\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
+%   \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu| (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
+% \end{align}
+
+% \section{Spherical Fourier transform of a double cone}\label{sec:cone}
+% In this appendix we evaluate the spherical Fourier transform of a
+% normalized double-cone angular distribution with central direction $\mh{s}'$ and
+% cone half-angle $\Delta$
+% \begin{align}
+%   f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right). \label{eq:doublecone}
+% \end{align}
+% The spherical Fourier transform is
+% \begin{align}
+%   F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)Y_\ell^{m*}(\mh{s}).
+% \end{align}
+
+% The limits of integration will be difficult to find unless we change coordinates
+% to exploit the axis of symmetry $\mh{s}'$. Since the spherical function is
+% rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
+% symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
+% \begin{align}
+%     F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
+% \end{align}
+% In this coordinate system the double cone is independent of the azimuthal angle,
+% so we can evaluate the azimuthal integral and express the function in terms of an
+% integral over $\vartheta$:
+% \begin{align}
+%     F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^{m*}(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
+% \end{align}
+% The function $f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)$ is only non-zero on
+% the intervals $\vartheta \in [0, \Delta]$ and
+% $\vartheta \in [\pi - \Delta, \pi]$ so
+% \begin{align}
+%     F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right].
+% \end{align}
+% Applying a change of coordinates with $u = \cos\vartheta$ yields
+% \begin{align}
+%     F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right].
+% \end{align}
+% The Legendre polynomials $P_\ell(u)$ are even (odd) on the interval [-1, 1] when
+% $\ell$ is even (odd), so the pair of integrals will be identical when $\ell$ is
+% even and cancel when $\ell$ is odd. For even $\ell$,
+% \begin{align}
+%   F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
+% \end{align}
+% The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
+% \begin{align}
+%   \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
+% \begin{cases}
+%   1 - \cos\Delta\,, &\ell = 0\,,\\
+%   \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
+% \end{cases}
+% \end{align}
+% where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
+% $m=-1$, not an inverse Legendre polynomial. Bringing everything together
+% \begin{align}
+%   F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) =
+%   \begin{cases}
+%     \sqrt{1/(4\pi)}, & \ell = 0,\\
+%     0, & \ell\, \text{odd},\\
+%     Y_\ell^{m*}(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
+%   \end{cases}
+% \end{align}
 

### 2018-12-20 papers/para-4f/paper/paper.tex
Part two split.

\documentclass[]{osa-article}

%% Select the journal you're submitting to
%% oe, boe, ome, osac, osajournal
\journal{osajournal}
% Key:
% Express journals must have the correct journal selected:
% {oe} Optics Express
% {boe} Biomedical Optics Express
% {ome} Optical Material Express
% {osac} OSAC Continuum
% Other OSA journals may use:
% {osajournal} Applied Optics, Advances in Optics and Photonics, Journal of the Optical Society of America A/B, Optics Letters, Optica, Photonics Research

% Uncomment if submitting to Photonics Research.
% ONLY APPLICABLE FOR \journal{osajournal}
% \setprjcopyright

% Set the article type
\articletype{Research Article}
% Note that article type is not required for Express journals (OE, BOE, OME and OSAC)

% Talon's custom libraries
\usepackage{empheq}
\usepackage{bm}
\usepackage[normalem]{ulem}

% Talon's custom commands
\setlength\arraycolsep{1.5pt}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\msf}[1]{\mathsf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathbf{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rp}{\mathbf{r}_p}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\taup}{\bs{\tau}}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\providecommand{\lmsum}{\sum_{\ell=0}^\infty\sum_{m=-\ell}^{\ell}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\tb}[1]{\textcolor{blue}{#1}}
\providecommand{\add}[1]{\textcolor{blue}{\uwave{#1}}}
\providecommand{\rem}[1]{\textcolor{red}{\sout{#1}}}

% \DeclareFontFamily{OT1}{pzc}{}
% \DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
% \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\eqname}[1]{\tag*{#1}}
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

\begin{document}

\title{Spatio-angular fluorescence microscopy\\ II. Paraxial 4f imaging}

\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{3} and Patrick La Rivi\`ere\authormark{1,3}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
  \authormark{2}Section on High Resolution Optical Imaging, National Institute
  of Biomedical Imaging and Bioengineering, National Institutes of Health,
  Bethesda, Maryland 20892, USA\\
  \authormark{3}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
}

\email{\authormark{*}talonchandler@talonchandler.com} %% email address is required

%\homepage{talonchandler@talonchandler.com} %% author's URL, if desired

%%%%%%%%%%%%%%%%%%% abstract %%%%%%%%%%%%%%%%
%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]

\begin{abstract*}
  We analyze a single-view fluorescence microscope in a $4f$ geometry
    without using the monopole or scalar approximations. We show that this
    imaging system has a spatio-angular band limit, and we exploit the band
    limit to perform efficient simulations. Notably, we show that information
    about the out-of-plane orientation of ensembles of in-focus fluorophores is
    recorded by paraxial fluorescence microscopes. Additionally, we show that
    deconvolution algorithms that use the monopole approximation may make biased
    estimates of fluorophore concentrations, but these biases are small when the
    sample contains either many randomly oriented fluorophores in each
    resolvable volume or unconstrained rotating fluorophores.
\end{abstract*}

\section{Introduction}
In the first paper of this series we developed a new set of transfer
  functions that can be used to analyze spatio-angular fluorescence microscopes
\cite{chandler2018}. In this work we will demonstrate these transfer
  functions by analyzing a single-view fluorescence microscope in a $4f$
  geometry.

A central goal of this work is to examine the validity of the monopole
  approximation in fluorescence microscopy. Although many works implicitly
apply the monopole approximation, we have encountered two explicit
justifications: (1) the sample contains many randomly oriented fluorophores
within a resolvable volume or (2) the sample contains unconstrained rotating
fluorophores. While both of these situations yield monopole-like emitters,
neither yields emitters that are perfectly described by the monopole model. We
investigate the dipole model of fluorophores in detail and find the conditions
under which the monopole approximation is justified.

We begin in section \ref{sec:theory} by specifying the imaging geometry and
  defining \textit{pupil functions} for both monopole and dipole imaging
  systems. We explicitly relate the pupil functions to the coherent transfer
  functions to establish a connection between physical calculations and the
  transfer functions. Next, in section \ref{sec:results} we calculate the
  monopole and dipole transfer functions in closed form, and we use these
  transfer functions to perform efficient simulations with four numerical
  phantoms. Finally, in section \ref{sec:discussion} we discuss the results and
  expand on how the pupil functions can be used to develop improved models for
  spatio-angular microscopes.

\section{Theory}\label{sec:theory}
During our initial modeling \cite{chandler2018} we considered an
  aplanatic optical system imaging a sample of in-focus fluorophores---either a
  monopole density, $f(\ro)$, or a dipole density, $f(\ro, \so)$---by recording
  the scaled irradiance on a two-dimensional detector, $g(\rd)$. A central
  result was that we could express the relationship between the object and the
  data as a linear Hilbert-space operator, and we showed that these operators
  took the form of an integral transform in a delta function basis. For
  monopoles the integral transform takes the form
\begin{align}
  g(\rd) = \int_{\mbb{R}^2}d\ro\,h(\rd - \ro)f(\ro), \label{eq:mono}
\end{align}
where $h(\rd - \ro)$ is the monopole point spread function. For dipoles the
  integral transform takes the form
\begin{align}
  g(\rd) = \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\,h(\rd - \ro,\so)f(\ro,\so),\label{eq:dip}
\end{align}
where $h(\rd - \ro, \so)$ is the dipole point spread function. Note that we
  have written Eqs. \eqref{eq:mono} and \eqref{eq:dip} in their
  demagnified forms. We will use primes to denote the unscaled detector
  coordinate, $\rd'$, and unscaled point spread functions, $h'$.

% \add{Once we have found the mapping in a delta function basis, we can change basis to
% simplify the integral transform. For example, in a basis of complex exponentials
% and spherical harmonics Eq. \eqref{eq:dip} takes the form}
%   \begin{align}
%     G(\bv) = \sum_{\ell=0}^{\infty}\sum_{m=-\ell}^{\ell} \msf{H}_{\ell}^m(\bv)\msf{F}_{\ell}^m(\bv), \label{eq:dipharm}
%   \end{align}
%   where
%   \begin{align}
%     G(\bv) &= \int_{\mbb{R}^2}d\mb{r}\,g(\mb{r})\,\text{exp}\left(-2\pi i\mb{r}\cdot\bv\right),\\
%     \msf{H}_{\ell}^m(\bv) &= \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\mb{r}\,h(\mb{r})\,\text{exp}\left(-2\pi i\mb{r}\cdot\bv\right)Y_{\ell}^{m*}(\so),\\
%     \msf{F}_{\ell}^m(\bv) &= \int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\mb{r}\,f(\mb{r})\,\text{exp}\left(-2\pi i\mb{r}\cdot\bv\right)Y_{\ell}^{m*}(\so).
%   \end{align}

Our task is to calculate the form of the monopole and dipole transfer
  functions for a specific imaging geometry. In this work we will consider an
aplanatic optical system in a \textit{$\mathit{4}f$ configuration} with an
arbitrary first lens (the objective lens) and a \textit{paraxial second lens}
(the tube lens) as shown in Fig. \ref{fig:schematic}. A lens can be considered
paraxial if the angle $\alpha$ between the optical axis of the lens and the
marginal ray is small enough that $\sin\alpha \approx \alpha$. As a rule of
thumb, non-paraxial effects only become significant when the numerical aperture
of a lens exceeds 0.7 \cite[ch.~6]{gu2000}, but this is only a rough guideline.
Commercial microscopes with infinity-corrected objectives can almost always can
be modeled by considering the tube lens as paraxial.

% \rem{We start by defining \textit{pupil functions} for both monopole and dipole
% imaging systems, and we explicitly relate the pupil functions to the coherent
% transfer functions. After establishing the link between physical calculations
% and the transfer functions, we calculate the monopole and dipole transfer
% functions for imaging systems with a paraxial objective, and we demonstrate our
% approach by simulating simple phantoms.}

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[width = 1.0\textwidth]{../figures/coordinates/detection-coords.pdf}
   \caption{Schematic of an aplanatic imaging system in a $4f$ geometry with a
     paraxial tube lens. We are considering an aplanatic optical system, so we
     only need to consider the image created by on-axis objects. The fluorescent
     object consists of ensembles of monopoles or dipoles embedded in a
     medium with index of refraction $n_0$. An objective with focal length $f_0$
     and numerical aperture $\text{NA} = n_o\sin\alpha$ is trained on the
     object. A paraxial tube lens with focal length $f_1$ and a detector
     complete the $4f$ geometry, and all components except the object are
     embedded in a medium with index of refraction $n_1$. The object, pupil, and
     detector planes are parameterized by vectors $\ro$, $\rp$, and $\rd$ with
     polar coordinates ($r_o, \phi_o$), ($r_b, \phi_b$), and ($r_d, \phi_d$),
     respectively. At each position $\ro$ in the object there is a sphere
     parameterized by a unit vector $\so$ with spherical coordinates
     ($\vartheta, \varphi$). }
   \label{fig:schematic}
 \end{figure}

\subsection{Monopole pupil functions}
We define the \textit{monopole pupil function} $p(\rp)$ of the imaging system as
the field immediately following the pupil plane created by an on-axis monopole,
where $\rp$ is an unscaled two-dimensional coordinate in the pupil plane. In
this section we will relate the monopole pupil function to the monopole transfer
functions by adapting the treatment in Barrett and Myers
\cite[ch.~9.7]{barrett2004}.

Since monopoles emit scalar fields, the monopole pupil function is a
scalar-valued function. The optical system is aplanatic, so we can write the
field, $U_p(\rp, \ro)$, created at a point in the pupil plane $\rp$ by a
monopole at position $\ro$ as
\begin{align}
   U_p(\rp, \ro) \propto p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right], \label{eq:pupil}
\end{align}
where $\lambda$ is the emission wavelength. Equation \eqref{eq:pupil} is a
restatement of the aplanatic condition for a $4f$ optical system---the fields in
the pupil plane can be written as the pupil function multiplied by a linear
phase factor that encodes the position of the object.

Since the second lens is paraxial, we can model the relationship between the
field in the pupil plane and the field on the detector with a scaled Fourier
transform \cite{goodman1996, axelrod2012, backer2014}:
\begin{align}
   U_d(\rd', \ro) \propto \int_{\mbb{R}^2}d\rp\, p(\rp)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right], \label{eq:detectorfourier}
\end{align}
where $\rd'$ is an unscaled detector coordinate.

If we define $P(\taup)$ as the two-dimensional Fourier transform of the pupil function
then we can rewrite Eq. \eqref{eq:detectorfourier} as
\begin{align}
  U_d(\rd', \ro) \propto P\left(\frac{n_0}{\lambda f_0}\ro + \frac{n_1}{\lambda f_1}\rd'\right),
\end{align}
which we can simplify further by writing in terms of the magnification
$m = -\frac{f_1n_0}{f_0n_1}$:
\begin{align}
  U_d(\rd' - m\ro) \propto P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right).
\end{align}
The irradiance on the detector is the absolute square of the field so
\begin{align}
  h'(\rd' - m\ro) \propto \left|P\left(\frac{n_1}{\lambda f_1}[\rd' - m\ro]\right)\right|^2.
\end{align}
If we demagnify the coordinates with $\rd = \rd'/m$ and demagnify the irradiance
with $h(\rd - \ro) \propto h'(m[\rd - \ro])$, we find that the monopole point
spread function is related to the Fourier transform of the monopole pupil
function by
\begin{align}
  h(\rd - \ro) \propto \left|P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right)\right|^2.
\end{align}
The monopole point spread function is the absolute square of the monopole
coherent spread function so
\begin{align}
  c(\rd - \ro) \propto P\left(-\frac{n_o}{\lambda f_o}[\rd - \ro]\right).
\end{align}
Finally, the monopole coherent transfer function is the Fourier transform of the
monopole coherent spread function so
\begin{align}
  C(\taup) \propto p\left(\frac{\lambda f_o}{n_o}\taup\right). \label{eq:monopupil0}
\end{align}
Equation \eqref{eq:monopupil0} is the key result of this section---the monopole
coherent transfer function is a scaled monopole pupil function.

\subsection{Dipole pupil function}
We define the \textit{dipole pupil function} $\mb{p}(\rp, \so)$ of the imaging
system as the electric field immediately following the pupil plane created by
an on-axis dipole oriented along $\so$. Since dipoles emit vector-valued
electric fields, the dipole pupil function is a vector-valued function. Almost
all of the arguments in the previous section carry over to the dipole case.
Briefly, we can write the electric field created at a point in the pupil
$\rp$ by a dipole at $\ro$ oriented along $\so$ as
 \begin{align}
   \mb{E}_p(\rp, \ro, \so) \propto \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]. \label{eq:pupil2}
 \end{align}
 The second lens is paraxial, so we can find the field on the detector with a
 Fourier transform
 \begin{align}
   \mb{E}_d(\rd', \ro, \so) \propto \int_{\mbb{R}^2}d\rp\, \mb{p}(\rp, \so)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0} \rp\cdot\ro \right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1} \rp\cdot\rd' \right]. \label{eq:detectorfourier2}
\end{align}
Note that the Fourier transform of a vector field is the Fourier transform of
its scalar-valued orthogonal components, so Eq. \eqref{eq:detectorfourier2}
specifies three two-dimensional Fourier transforms. We follow the same
manipulations as the previous section and find that the dipole coherent transfer
function is a scaled dipole pupil function
\begin{align}
  \mb{C}(\taup, \so) \propto \mb{p}\left(\frac{\lambda f_o}{n_o}\taup, \so\right). \label{eq:monopupildip}
\end{align}

We have restricted our analysis to paraxial tube lenses, but non-paraxial tube
lenses (or a non-infinity-corrected objective) can be modeled with vector-valued
three-dimensional pupil functions \cite{sheppard1994, gu2000, arnison2002,
  foreman2011-2}.

\subsection{Special functions}
We adopt and generalize Bracewell's notation \cite{bracewell2004} for several
special functions which will simplify our calculations. First, we define a
\textit{rectangle function} as
\begin{align}
  \Pi(x) = 
  \begin{cases}
    1\quad \text{if}\quad |x| < \frac{1}{2},\\
    0\quad \text{else}.
  \end{cases}
\end{align}
We also define the \textit{$n^{th}$-order jinc function} as
\begin{align}
  \text{jinc}_n(r) = \frac{J_{n+1}(\pi r)}{2r},
\end{align}
where $J_{n+1}(r)$ is the $(n+1)^{th}$-order Bessel function of the first kind.

Although the rectangle and jinc functions are defined in one dimension, we will
usually apply them in two dimensions. In Appendix \ref{sec:special} we derive
the following two-dimensional Fourier transform relationships between the jinc
functions and the weighted rectangle functions
\begin{align}
  i^{n}\left\{\substack{
  \text{exp}(in\phi_r)\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\text{jinc}_n(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} (2\nu)^{n}\left\{\substack{
    \text{exp}(in\phi_{\nu})\\
    \cos(n\phi_{\nu})\\
    \sin(n\phi_{\nu})
  }\right\}\Pi(\nu), \label{eq:jincrect2}
  \end{align}
  where the entries inside the curly braces are to be taken one at a time and
  $\{r, \phi_r\}/\{\nu, \phi_\nu\}$ are conjugate sets of polar coordinates.

Finally, we define the \textit{$n^{th}$-order chat function} as the
two-dimensional Fourier transform of the squared $n^{th}$-order jinc function
\begin{align}
  \text{jinc}_n^2(r) \stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow} \text{chat}_n(\nu).
\end{align}

In Appendix \ref{sec:special} we show that the zeroth- and first-order chat
functions can be written in closed form as
\begin{align}
  \text{chat}_0(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right),\\
  \text{chat}_1(x) &=  \frac{1}{2}\left[\cos^{-1}|x| - |x|(3-2x^2)\sqrt{1 - x^2}\right]\Pi\left(\frac{x}{2}\right).  
\end{align}

\section{Results}\label{sec:results}
\subsection{Monopole transfer functions}
Our first step towards the monopole transfer functions is to calculate the
monopole pupil function and coherent transfer function. Several works
\cite{petrov2017, backlund2018} have modeled an aplanatic fluorescence
microscope imaging monopole emitters with the scalar pupil function
\begin{align}
  p(\rp) \propto \tilde{C}\left(\frac{r_p}{f_o}\right)\Pi\left(\frac{r_p}{2f_o\sin\alpha}\right), 
\end{align}
where
\begin{align}
  \tilde{C}(x) = (1 - x^2)^{-1/4} = 1 + \frac{x^2}{4} + \frac{5x^4}{32} + \cdots. 
\end{align}
The $\tilde{C}(x)$ function models the radial dependence of the field and
ensures that power is conserved on either side of an aplanatic objective, and
the rectangle function models the aperture stop of the objective. Applying Eq.
\eqref{eq:monopupil0} and collecting constants we find that the coherent monopole
transfer function is
\begin{align}
  C(\taup) \propto \tilde{C}\left(\frac{2\text{NA}}{n_o}\frac{\tau}{\nu_c}\right)\Pi\left(\frac{\tau}{\nu_c}\right), \label{eq:coherentmonopole}
\end{align}
where $\text{NA} = n_o\sin\alpha$ and $\nu_c = 2\text{NA}/\lambda$. This
coherent transfer function models objectives with an arbitrary numerical
aperture, but for our initial analysis we restrict ourselves to the paraxial
regime. We drop second- and higher-order radial terms to find that
\begin{align}
  C(\taup) \stackrel{(p)}{\propto} \Pi\left(\frac{\tau}{\nu_c}\right), 
\end{align}
where $(p)$ indicates that we have used the paraxial approximation for the
objective lens.

We can find the monopole coherent spread function by taking the inverse Fourier
transform of the monopole coherent transfer function
\begin{align}
  c(\mb{r}) \stackrel{(p)}{\propto} \text{jinc}_0(\nu_c r).
\end{align}

The monopole point spread function is the (normalized) absolute square of the
monopole coherent spread function so
\begin{align}
  h(\mb{r}) \stackrel{(p)}{=} \frac{4}{\pi}\text{jinc}_0^2(\nu_c r),
\end{align}
which is the well-known \textit{Airy disk}.

Finally, we can calculate the monopole transfer function as the two-dimensional Fourier transform of the monopole point spread function (or the autocorrelation
of the coherent transfer function) and find that 
\begin{align}
  H(\bs{\nu}) \stackrel{(p)}{=} \frac{4}{\pi}\text{chat}_0\left(\frac{\nu}{\nu_c}\right).
\end{align}

 \subsection{Dipole transfer functions}
 To calculate the dipole transfer function we proceed similarly to the monopole
 case---we find the pupil function, scale to find the coherent dipole transfer
 function, then calculate the remaining transfer functions.

 Backer and Moerner \cite{backer2014} have calculated the dipole pupil function
 for a high-NA objective as
 \begin{align}
   \mb{p}(\rp, \so) \propto
   \begin{bmatrix}
     \tilde{C}_0\left(\frac{r_p}{f_o}\right) + \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)c(\phi_p)\\
     \tilde{C}_2\left(\frac{r_p}{f_o}\right)s(2\phi_p)&\tilde{C}_0\left(\frac{r_p}{f_o}\right) - \tilde{C}_2\left(\frac{r_p}{f_o}\right)c(2\phi_p)&\tilde{C}_1\left(\frac{r_p}{f_0}\right)s(\phi_p)\\     
     0&0&0\\     
   \end{bmatrix}
   \begin{bmatrix}
     s_x\\
     s_y\\
     s_z
   \end{bmatrix}
   \Pi\left(\frac{r_p}{2f_os(\alpha)}\right),
 \end{align}
 where $c(x)$ and $s(x)$ are shorthand for $\cos(x)$ and $\sin(x)$,
 $\{s_x, s_y, s_z\}$ are the Cartesian components of $\so$ when $\mh{z}$ is
 aligned with the optical axis, and
 \begin{alignat}{4}
   \tilde{C}_0(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} + 1\right)(1 - x^2)^{-1/4} &&= 1 + \frac{x^4}{32} + \frac{x^6}{32} + \cdots,\\
   \tilde{C}_1(x) &= x(1 - x^2)^{-1/4} &&= x + \frac{x^3}{4} + \frac{5x^5}{32} + \cdots,\\
   \tilde{C}_2(x) &= \frac{1}{2}\left(\sqrt{1 - x^2} - 1\right)(1 - x^2)^{-1/4} &&= -\frac{x^2}{4} - \frac{x^4}{8} - \frac{11x^6}{128} - \cdots.
 \end{alignat}
 Similar to the monopole case, the dipole pupil function conserves power and has
 a cutoff at the objective aperture, but the dipole pupil function is
 vector-valued to model the complete electric field in the pupil plane. The
 fields in the pupil plane have a negligible $\mh{z}$ component which is a
 consequence of our assumption that the tube lens is paraxial---modeling a
 non-paraxial tube lens would require a three-dimensional vector-valued pupil
 function \cite{sheppard1994, gu2000, arnison2002, foreman2011-2}.

 Scaling the dipole pupil function using Eq. \eqref{eq:monopupildip} yields the
 dipole coherent transfer function
 \begin{equation}
   \mb{C}(\taup, \so)\hspace{-0.2em}\propto\hspace{-0.2em}
   \begin{bmatrix}
     \tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!+\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)c(\phi_{\tau})\\
     \tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)s(2\phi_{\tau})&\tilde{C}_0\left(\frac{\lambda r_p\tau}{n_0}\right)\!-\!\tilde{C}_2\left(\frac{\lambda r_p\tau}{n_0}\right)c(2\phi_{\tau})&\tilde{C}_1\left(\frac{\lambda r_p\tau}{n_0}\right)s(\phi_{\tau})\\     
     0&0&0\\     
   \end{bmatrix}
   \begin{bmatrix}
     s_x\\
     s_y\\
     s_z
   \end{bmatrix}
   \Pi\left(\frac{\tau}{\nu_c}\right). 
 \end{equation}
 We restrict our analysis to the paraxial regime by dropping second- and
 higher-order radial terms to find that
 \begin{align}
   \mb{C}(\taup, \so) \stackrel{(p)}{\propto}
   \begin{bmatrix}
     1&0&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\cos\phi_{\tau}\\
     0&1&\frac{\text{2NA}}{n_o}\frac{\tau}{\nu_c}\sin\phi_{\tau}\\
     0&0&0\\     
   \end{bmatrix}
   \begin{bmatrix}
     s_x\\
     s_y\\
     s_z
   \end{bmatrix}
   \Pi\left(\frac{\tau}{\nu_c}\right). \label{eq:coherentdip}
 \end{align}
 Under the paraxial approximation the transverse components of the dipole
 \{$s_x, s_y$\} create purely transverse fields in the pupil plane and the axial
 component of the dipole \{$s_z$\} creates purely radial fields in the pupil
 plane. The paraxial approximation may seem crude compared to Backer and
 Moerner's numerical results, but the approximation will allow us to calculate
 the transfer functions in closed form so that we can build an intuition for the
 limits of the microscope. We also note that many existing works in ensemble
 polarized fluorescence microscopy make stronger approximations than ours. For
 example, Fourkas only considers the total irradiance in the pupil plane while
 ignoring the propagation of fields to the detector \cite{fourkas2001}.

 The dipole coherent spread function is the inverse Fourier transform of the
 dipole coherent transfer function. Applying Eq. \eqref{eq:jincrect2} in reverse
 yields
  \begin{align}
   \mb{c}(\mb{r}, \so) \stackrel{(p)}{\propto}
   \begin{bmatrix}
     \text{jinc}_0(\nu_c r)&0&\frac{\text{NA}}{n_o}i\cos\phi\,\text{jinc}_1(\nu_c r)\\
     0&\text{jinc}_0(\nu_c r)&\frac{\text{NA}}{n_o}i\sin\phi\,\text{jinc}_1(\nu_c r)\\
     0&0&0\\     
   \end{bmatrix}
   \begin{bmatrix}
     s_x\\
     s_y\\
     s_z
   \end{bmatrix}.
  \end{align}
  Notice that the radial component of the dipole coherent spread function has a
  $\pi/2$ phase shift relative to the transverse component. This phase factor
  arises because the Fourier transform of a real and odd function is purely
  imaginary.

  \subsubsection{Paraxial dipole point spread function}
  The dipole point spread function is the (normalized) absolute square of the
coherent dipole spread function
\begin{align}
  h(\mb{r}, \so) \propto \mb{c}(\mb{r}, \so)\mb{c}^\dagger(\mb{r}, \so). 
\end{align}
Plugging in the paraxial dipole coherent spread function and normalizing yields
\begin{align}
  h(\mb{r}, \so) \stackrel{(p)}{=} N\left[\text{jinc}_0^2(\nu_c r)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\cos^2\vartheta\right],\label{eq:paradpsf}
\end{align}
where $\sin^2\vartheta = s_x^2 + s_y^2$, $\cos^2\vartheta = s_z^2$, and the normalization
factor is
\begin{align}
  N = 6\nu_c^2\pi^{-3/2}\left[2 + \left(\frac{\text{NA}}{n_o}\right)^2\right]^{-1}.
\end{align}

As discussed above, the transverse and radial fields are out of phase on the
detector, so the total irradiance is the sum of the contributions from the
transverse and radial components. In Fig. \ref{fig:hdet} we plot the dipole
point spread function for several dipole orientations and numerical apertures,
and in Fig. \ref{fig:microscopefig} we compare the monopole point spread
function to the dipole point spread function. The paraxial monopole and dipole
models are only equivalent when the sample consists of transverse dipoles, which
is clear if we notice that Eq. \eqref{eq:paradpsf} reduces to an Airy disk when
$\vartheta = \pi/2$---see Novotny and Hecht for a similar observation
\cite[ch.~4]{nov2006}.

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/dpsf.pdf}
   \caption{Renormalized paraxial dipole point spread function as a function of
     the scaled radial coordinate $\nu_c r$, the dipole inclination angle
     $\vartheta$, and $\text{NA}/n_o$. For small numerical apertures (left) the
     irradiance pattern created by axial dipoles (\textcolor{red}{\textbf{red}})
     is small compared to transverse dipoles (\textbf{black}), but the relative
     contribution of axial dipoles increases with the numerical aperture (see
     \textcolor{red}{\textbf{red}} lines from left to right). Additionally, we
     plot the monopole point spread function (\textcolor{green}{\textbf{green}})
     and observe that the paraxial monopole and dipole models are identical for
     transverse dipoles (the \textcolor{green}{\textbf{green}} and
     \textbf{black} lines are coincident).}
   \label{fig:hdet}
 \end{figure}

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/microscope/microscope.pdf}
   \caption{Comparison of paraxial models for monopole radiators a) and dipole
     radiators b)--d). a) Monopole radiators fill the pupil plane with a uniform
     scalar field which gives rise to an Airy disk on the detector. b) A
     transverse dipole radiator also creates an Airy disk, but the pupil plane
     is filled with a uniform vector field. c) An axial dipole radiator creates
     a radial electric field pattern in the back focal plane that creates a
     $\text{jinc}_1^2(r)$ pattern on the detector. d) Dipoles that are not
     transverse or axial still create radially symmetric irradiance patterns
     under the paraxial approximation. Fields from transverse dipoles are real
     and even while fields from axial dipoles are real and odd, which causes a
     relative $\pi/2$ phase shift for the fields on the detector. This phase
     shift means that the fields from transverse and axial components of the
     dipole do not interfere, which causes radially symmetric irradiance
     patterns.}
   \label{fig:microscopefig}
 \end{figure}

 To demonstrate the paraxial dipole point spread function we simulate a set of
 equally spaced dipoles with varying orientation:
 \begin{align}
   f_{(ph1)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, \delta\left(\cos\vartheta - \cos\vartheta_j\right)\, \delta\left(\varphi - \varphi_k\right),\label{eq:phantom1}
 \end{align}
 where $\vartheta_j = j\frac{\pi}{6}$, $\varphi_k = k\frac{\pi}{4}$, the
 subscript $(ph1)$ indicates that this is the first phantom, and the spatial
 coordinates are expressed in $\mu$m. To find the irradiance pattern created by
 the phantom we plug Eq. \eqref{eq:phantom1} into Eq. \eqref{eq:dip} and use
 the sifting property to find that
 \begin{align}
   g_{(ph1)}(r_x, r_y) = \sum_{j=0}^3 \sum_{k=0}^3 h\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}, \vartheta_j\right).\label{eq:phantom1irr}
 \end{align}
 In Fig. \ref{fig:ph1} we plot the phantom and scaled irradiance for an imaging
 system with $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$.
 We sample and plot the scaled irradiance at $20\times$ the Nyquist rate,
 $\Delta x = 1/[20(2\nu_c)]$, so the irradiance patterns are free of aliasing.
 The output demonstrates that the irradiance pattern depends on the dipole
 inclination, but not its azimuth.

 \begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/ph1.pdf}
   \caption{\textbf{Left:} A spatially and angularly sparse phantom---uniformly
     spaced single dipoles with varying orientations (increasing $\vartheta$
     from left to right and increasing $\varphi$ from bottom to top). White
     crosses mark the positions of the dipoles. \textbf{Center:} Scaled
     irradiance for an imaging system with $\text{NA} = 0.75$,
     $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at $20\times$ the
     Nyquist rate. \textbf{Right:} $x$ profiles through the scaled irradiance.
     The response is independent of the azimuth angle and strongly dependent on
     the inclination angle.}
   \label{fig:ph1}
 \end{figure}

\subsubsection{Paraxial dipole spatial transfer function}\label{sec:trans}
The dipole spatial transfer function is the spatial Fourier transform of
the dipole point spread function (or the complex autocorrelation of the dipole
coherent transfer function). Applying the Fourier transform to Eq.
\eqref{eq:paradpsf} we find that
  \begin{align}
    H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
  \end{align}
In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
several dipole orientations and numerical apertures. We find that the dipole
spatial transfer function is negative for axial dipoles at high spatial
frequencies, especially for larger numerical apertures. The negative dipole
spatial transfer function corresponds to a contrast inversion for high-frequency
patterns of axial dipoles because the irradiance minimum corresponds to the
position of the dipole.

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/sdtf.pdf}
   \caption{Dipole spatial transfer function as a function of the scaled spatial
     frequency $\nu/\nu_c$, the dipole inclination angle $\vartheta$, and
     $\text{NA}/n_o$. For small numerical apertures (left) the dipole spatial
     transfer function for axial dipoles (\textcolor{red}{\textbf{red}}) is
     small compared to transverse dipoles (\textbf{black}), but the relative
     contribution of axial dipoles increases with the numerical aperture (see
     \textcolor{red}{\textbf{red}} lines from left to right). The spatial dipole
     transfer function of axial dipoles is negative at high spatial frequencies
     because the central minimum of the axial dipole point spread function
     corresponds to the position of the dipole. Equivalently, a
     high-spatial-frequency pattern of axial dipoles will generate an irradiance
     pattern where the minimum irradiance corresponds to the peak of the axial
     dipole density. Additionally, we plot the monopole transfer function
     (\textcolor{green}{\textbf{green}}) and observe that the paraxial monopole
     and dipole models are identical for transverse dipoles (the
     \textcolor{green}{\textbf{green}} and \textbf{black} lines are
     coincident).}
   \label{fig:odotf}
 \end{figure}

 To demonstrate the dipole spatial transfer function we simulate a set of
 equally spaced disks with varying diameter containing fluorophores with varying
 orientation
 \begin{align}
   f_{(ph2)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) \delta\left(\cos\vartheta - \cos\vartheta_j\right)\,\label{eq:phantom2}
 \end{align}
 where $D_k = 0.15(1+k)\, \mu$m and $\vartheta_j = j\frac{\pi }{6}$. Notice that
 we have scaled the disks so that the total number of fluorophores in each disk
 is constant. Also notice that the disk can model a spatial distribution of many
 fluorophores or a single molecule undergoing spatial diffusion within a well.

 We can calculate the scaled irradiance by taking the spatial Fourier
   transform of each orientation in the phantom, multiplying the result with the
   dipole spatial transfer function, summing over the orientations, then taking
   the inverse spatial Fourier transform
 \begin{align}
   g_{(ph2)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{j}H(\nu, \vartheta_j)\mc{F}_{\mbb{R}^2}\left\{f_{(ph2)}(r_x, r_y, \vartheta_j)\right\}\right\}.
 \end{align}

 In Fig. \ref{fig:ph2} we plot the phantom and scaled irradiance with the same
 imaging parameters as the previous section. The small disks create irradiance
 patterns that are similar to the point sources in the previous section, while
 larger disks create increasingly uniform irradiance patterns that hide the
 orientation of the fluorophores.

  \begin{figure}[ht]
 % \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/ph2.pdf}
   \caption{\textbf{Left:} A spatially dense and angularly sparse
     phantom---uniformly spaced disks with varying size (increasing $D$ from
     bottom to top) and dipole orientation (increasing $\vartheta$ from left to
     right) \textbf{Center:} Scaled irradiance for an imaging system with
     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
     scaled irradiance. Larger disks generate increasingly uniform irradiance
     patterns with fewer details that may indicate the orientation of
     fluorophores.}
   \label{fig:ph2}
 \end{figure}

 \subsubsection{Paraxial dipole angular transfer function}
 To calculate the angular dipole transfer function we take the spherical Fourier
 transform of the dipole point spread function
 \begin{align}
H_l^m(\mb{r}) \stackrel{}{=} \int_{\mbb{S}^2}d\so\, h(\mb{r}, \so)Y_l^{m*}(\so).
 \end{align}
 After evaluating the integrals and normalizing, the angular dipole transfer
 function is
 \begin{align}
   H_l^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3}\left[2\text{jinc}_0^2(\nu_cr) + \left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_0\delta_{\ell0}\delta_{m0} + \nonumber\\& \frac{N}{3}\left[-2\text{jinc}_0^2(\nu_c r) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{jinc}_1^2(\nu_c r)\right]\Lambda_2\delta_{\ell2}\delta_{m0},
 \end{align}
where $\Lambda_{\ell} = \sqrt{4\pi/(2\ell + 1)}$.

In Fig. \ref{fig:atf} we plot the dipole angular transfer function for both
spherical harmonic terms and several numerical apertures. Note that the dipole
angular transfer function can be negative because the spherical harmonics can
take negative values. The $\ell=0$ term shows that angularly uniform
distributions of dipoles create spatial irradiance patterns that are similar but
not identical to the Airy disk, while the $\ell=2$ term shows a negative pattern
because of the large contribution of the transverse negative values in the
$Y_2^0$ spherical harmonic.

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/adtf.pdf}
   \caption{Paraxial dipole angular transfer function in terms of a scaled
     radial detection coordinate $\nu_c r$, the spherical harmonic degree
     $\ell$, and $\text{NA}/n_o$. Angularly uniform distributions of dipoles
     $\ell=0$ generate a spatial pattern that is similar but not identical to
     the Airy disk created by a monopole (\textcolor{green}{\textbf{green}}),
     and this discrepancy increases with the numerical aperture. $\ell=2$
     distributions have a negative response because $Y_2^0(\mh{s})$ is negative
     for transverse directions. As the numerical aperture increases, the
     relative contribution of positive axial dipoles in the $\ell=2$
     distribution increases.}
   \label{fig:atf}
 \end{figure}

 To demonstrate the dipole angular transfer function we simulate a set of
 equally spaced fluorophore distributions with varying orientation and angular
 distributions
 \begin{align}
   f_{(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, f_{\text{(cone)}}\left(\vartheta, \varphi; \vartheta_j, 0, \Delta_k\right),\label{eq:phantom3}
 \end{align}
 where
 \begin{align}
   f_{\text{(cone)}}(\so; \so', \Delta) = f_{\text{(cone)}}(\vartheta, \varphi; \vartheta', \varphi', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right)
 \end{align}
 is an angular double cone distribution with central direction $\mh{s}'$ and
 cone half-angle $\Delta$; $\vartheta_j = j\frac{\pi}{6}$; and
 $\Delta_k = k\frac{\pi}{6}$. Notice that when $\Delta = 0$ the angular double
 cone reduces to a single direction, and when $\Delta = \pi/2$ the angular
 double cone reduces to an angularly uniform distribution. Also notice that the
 double cone can model angular diffusion or the angular distribution of many
 fluorophores within a resolvable volume.

 Our first step towards the irradiance pattern is to calculate the dipole
 angular spectrum of the phantom. In Appendix \ref{sec:cone} we calculate the
 spherical Fourier transform of the double cone distribution
 $F^m_{\ell,\text{(cone)}}(\vartheta', \varphi'; \Delta)$ which we can use to
 express the dipole angular spectrum as
 \begin{align}
   F^{m}_{\ell,(ph3)}(r_x, r_y, \vartheta) = \sum_{j=0}^3 \sum_{k=0}^3 \delta\left(r_x - j\right)\, \delta\left(r_y - k\right)\, F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3spect}
 \end{align}

 To calculate the scaled irradiance we multiply the dipole angular spectrum
   by the dipole angular transfer function and sum over the dipoles and
   spherical harmonics
 \begin{align}
   g_{(ph3)}(r_x, r_y) = \sum_{\ell m}\sum_{j=0}^3 \sum_{k=0}^3 H_\ell^m\left(\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right) F^m_{\ell,\text{(cone)}}\left(\vartheta_j, 0, \Delta_k\right).\label{eq:phantom3irr}
 \end{align}

 In Fig. \ref{fig:ph3} we plot the phantom and scaled irradiance with the same
 imaging parameters as the previous sections. For small cone angles the
 irradiance patterns are similar to the point sources in the previous sections,
 while larger cone angles create increasingly uniform irradiance patterns that
 hide the angular information about the distributions.

  \begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/ph3.pdf}
   \caption{\textbf{Left:} A spatially sparse and angularly dense
     phantom---uniformly spaced double cone distributions of fluorophores with
     varying central direction (increasing $\vartheta'$ from left to right) and
     varying cone half-angle (increasing $\Delta$ from bottom to top).
     \textbf{Center:} Scaled irradiance for an imaging system with
     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
     scaled irradiance. Small cone angles have irradiance patterns that vary
     with the central direction, while larger cones angles have increasingly
     uniform irradiance patterns that hide angular information.}
   \label{fig:ph3}
 \end{figure}

 \subsubsection{Paraxial dipole spatio-angular transfer function}
 We can calculate the dipole spatio-angular transfer function by taking the
 spatial Fourier transform of the dipole angular transfer function (or the
 spherical Fourier transform of the dipole spatial transfer function) to find
 that
 \begin{align}
\msf{H}_{\ell}^m(\bv) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
 \end{align}

 In Fig. \ref{fig:dsatf} we plot the dipole spatio-angular transfer function for
 both spherical harmonic terms and several numerical apertures. The $\ell=0$
 term shows that an angularly uniform distribution of dipoles has a transfer
 function that is similar but not identical to the monopole transfer function
 with high frequencies increasingly suppressed as the numerical aperture
 increases. The $\ell=2$ term shows a negative pattern because of the large
 contribution of the transverse negative values in the $Y_2^0$ spherical
 harmonic. As the numerical aperture increases the relative contribution of the
 positive axial values increases and the $\ell=2$ term becomes less negative.

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/satf.pdf}
   \caption{Spatio-angular dipole transfer function as a function of the scaled
     spatial frequency $\nu/\nu_c$, the spherical harmonic degree $\ell$, and
     $\text{NA}/n_o$. When the numerical aperture is small the transverse
     dipoles contribute the most to the signal which gives rise to a positive
     $\ell=0$ component and a negative $\ell=2$ component. As the numerical
     aperture increases, the relative contribution of axial dipoles increases
     and the $\ell=2$ component becomes less negative. Additionally, we plot the
     monopole transfer function (\textcolor{green}{\textbf{green}}) and observe
     that the $\ell=0$ term is similar but not identical to the monopole
     transfer function, and this discrepancy increases with the numerical aperture.}
   \label{fig:dsatf}
 \end{figure}

 To demonstrate the spatio-angular transfer function, we simulate a set of
 equally spaced disks of fluorophores with varying radius and angular
 distributions
 \begin{align}
   f_{(ph4)}(r_x, r_y, \vartheta, \varphi) = \sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)f_{\text{(cone)}}\left(\vartheta, \varphi; \frac{\pi}{2}, 0, \Delta_j\right),\label{eq:phantom4}
 \end{align}
 where $D_k = 0.15(1+k)\, \mu$m, and $\Delta_j = j\frac{\pi}{6}$.

 Our first step towards calculating the irradiance pattern is to calculate the
 dipole spatio-angular spectrum given by the spatial Fourier transform of the dipole angular spectrum  
  \begin{align}
   \mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y) = \mc{F}_{\mbb{R}^2}\left\{\sum_{j=0}^3 \sum_{k=0}^3 \frac{1}{D_k^2}\Pi\left(\frac{1}{D_k}\sqrt{\left(r_x - j\right)^2 + \left(r_y - k\right)^2}\right)F_{\ell,\text{cone}}^m\left(\frac{\pi}{2}, 0, \Delta_j\right)\right\}.
  \end{align}

  To calculate the scaled irradiance we multiply the dipole spatio-angular spectrum by the dipole spatio-angular transfer function, sum over the spherical harmonics, then take an inverse Fourier transform
  \begin{align}
   g_{(ph4)}(r_x, r_y) = \mc{F}^{-1}_{\mbb{R}^2}\left\{\sum_{\ell m}\mathsf{H}_{\ell}^m(\nu_x, \nu_y)\mathsf{F}_{\ell,(ph4)}^m(\nu_x, \nu_y)\right\}.
  \end{align}

  In Fig. \ref{fig:ph4} we plot the phantom and scaled irradiance with the
  same imaging parameters as the previous sections. Small cone angles and small
  disks create relatively unique irradiance patterns, while increasing the cone
  angle or disk size creates increasingly similar irradiance patterns.

  \begin{figure}[ht]
 \centering
   \centering
   \includegraphics[scale=0.8]{../figures/paratfs/ph4.pdf}
   \caption{\textbf{Left:} A spatially and angularly dense phantom---uniformly
     spaced disks with varying size (increasing $D$ from bottom to top) and
     double cone half angle (increasing $\Delta$ from left to right)
     \textbf{Center:} Scaled irradiance for an imaging system with
     $\text{NA} = 0.75$, $\lambda = 500\,\text{nm}$, and $n_o = 1.33$ sampled at
     $20\times$ the Nyquist rate. \textbf{Right:} $x$ profiles through the
     scaled irradiance.}
   \label{fig:ph4}
 \end{figure}

 \section{Discussion}\label{sec:discussion}
 \subsection{Comparing monopole and dipole models}
 The only case when the dipole and monopole transfer functions match
   exactly is when the sample consists of dipoles that are completely
   constrained to the transverse plane of a paraxial imaging system. Applying
   the monopole approximation in any other situation can lead to biased
   estimates of the fluorophore concentrations.

 However, the common justifications for the monopole approximation---the
   fluorophores are rotationally unconstrained or there are many randomly
   oriented fluorophores in a resolvable volume---are good justifications in all
   but the highest SNR regimes. The effects of the dipole model become apparent
   in lower SNR regimes as the rotational constraints on the dipoles increase
   (assuming there are out-of-plane dipole components).

% \subsection{When are dipole transfer functions necessary?}
% Model mismatch can lead to biased estimates of the position and orientation of
% fluorophores, so the most accurate fluorescence microscopy experiments will
% always use dipole transfer functions over monopole transfer functions. The only
% case when the dipole and monopole transfer functions match exactly is when the
% dipoles are completely constrained to the transverse plane of a paraxial imaging
% system.

% However, in many practical situations noise will mask the effects of vector
% optics and dipoles. If the fluorophores are rotationally unconstrained or there
% are many randomly oriented fluorophores in a resolvable volume---common
% situations in biological applications---then the effects of vector optics and
% dipoles will be masked by noise in all but the highest-SNR regimes.

% The dipole transfer functions are most broadly useful when the sample contains
% fluorophores that are rotationally constrained. As rotational constraints
% increase, the effects of vector optics and dipoles will become apparent in lower
% SNR regimes.

% \subsection{Alternative transfer functions}
% Throughout this work we have used the spherical harmonic functions as a basis
% for functions on the sphere, but there are other basis functions that can be
% advantageous in some cases. Several works \cite{aguet2009, backer2014,
%   brasselet2011, zhang2018, zhang2018-2} have used the second moments as basis
% functions for the sphere because they arise naturally when computing the dipole
% point spread function. These works use an alternative to the dipole angular
% transfer function that uses the second moments as basis functions so the forward
% model can be written as
% \begin{align}
%   g(\rd) = \sum_{j=1}^6 \int_{\mbb{R}^2}d\ro\, H_j(\rd - \ro)F_j(\ro),
% \end{align}
% where
% \begin{align}
%   H_j(\rd - \ro) &= \int_{\mbb{S}^2}d\so\, h(\rd - \ro, \so)Z_j(\so),\\
%   F_j(\ro) &= \int_{\mbb{S}^2}d\so\, f(\ro, \so)Z_j(\so),
% \end{align}
% and $Z_j(\mh{s}) = \{s_x^2, s_y^2, s_z^2, s_xs_y, s_ys_z, s_xs_z\}$ are the
% second moments. This formulation is similar to the dipole angular transfer
% function approach because it can exploit the spatial sparsity of the sample, but
% it does not require a cumbersome expansion of the dipole point spread function
% onto spherical harmonics.

% However, the spherical harmonics provide several advantages over the second
% moments. First, the spherical harmonics form a complete basis for functions on
% the sphere, while the second moments span a much smaller function space. The
% usual approach to extending the span of the second moments is to use the fourth
% (or higher) moments, but this extension requires a completely new set of basis
% functions while the spherical harmonics can be extended by simply adding higher
% order terms. Second, the spherical harmonics are orthonormal, which will allow
% us to deploy invaluable tools from linear algebra---linear subspaces, rank, SVD,
% etc.--- to analyze and compare microscope designs. Finally, using the spherical
% harmonics provides access to a set of fast algorithms. The naive expansion of an
% arbitrary discretized $N$ point spherical function onto spherical harmonics (or
% second moments) requires a $\mc{O}(N^2)$ matrix multiplication, while pioneering
% work by Driscoll and Healy \cite{driscoll1994} showed that the forward discrete
% fast spherical harmonic transform can be computed with a $\mc{O}(N(\log N)^2)$
% algorithm and its inverse can be computed with a $\mc{O}(N^{3/2})$ algorithm. To
% our knowledge no similarly fast algorithms exist for expansion onto the
% higher-order moments.

% Zhenghao et. al. \cite{zhanghao2017} have used the circular harmonics to model
% the orientation of dipoles. The circular harmonics are complete and orthogonal,
% but they artificially restrict the reconstructed dipoles to the transverse
% plane of the microscope---a rare situation in real experiments.

% The diffusion magnetic resonance imaging community uses both the second moments
% (or second-order tensor) basis functions \cite{basser1994} and the spherical
% harmonic basis functions \cite{tournier2004}. Descoteaux et. al. have provided
% an explicit transformation matrix to convert between these basis functions
% \cite{descoteaux2006}.

\subsection{What determines the angular bandwidth?}
Spatial imaging systems have a spatial bandwidth that characterizes the highest
spatial frequency that the system can transfer between object and data space.
Similarly, angular imaging systems have an angular bandwidth that characterizes
the highest angular frequency that the system can transfer, but in the angular case
there are two different types of angular bandwidths that we call the $\ell$- and
$m$-bandwidth. The $\ell$-bandwidth can be interpreted in a similar way to the
spatial bandwidth---it characterizes the smallest angular features that the
imaging system can measure. The $m$-bandwidth does not have a direct analog in
the spatial domain---it characterizes the angular uniformity of the imaging
system. If the $\ell$- and $m$-bandwidths are equal then the imaging system can
be said to have an $\textit{isotropic angular bandwidth}$.

The spatial bandwidth of a fluorescence microscope is well known to be
$\nu_c = \frac{2\text{NA}}{\lambda}$. In other words, we can increase the
spatial resolution of a fluorescence microscope by increasing the NA of the
instrument or by choosing a fluorophore with a shorter emission wavelength.
Similarly, the angular bandwidth of a fluorescence microscope depends on both
the instrument and the choice of fluorophore.

The microscope we considered in this work has an $\ell$-bandwidth of
$\ell_c = 2$ and an $m$-bandwidth of $m_c = 0$, so it does not have an isotropic
angular bandwidth. In future work we will consider several approaches to
improving the angular bandwidths in detail, but we briefly mention that
non-paraxial microscopes, microscopes with polarizers in the illumination or
detection paths, and multiview microscopes all have higher angular bandwidths
than the microscope considered here.

The angular bandwidth is also fluorophore dependent. Monopoles emit light
isotropically so they have an $\ell$-bandwidth of $\ell_c = 0$, while dipoles
have an $\ell$-bandwidth of $\ell_c = 2$, and higher-order excitation and
detection moments will have even higher bandwidths. Multi-photon excitation and
other non-linear methods can also increase the $\ell$-bandwidth
\cite{brasselet2011}.

\subsection{Towards more realistic models}
The theoretical model we presented in this work is an extreme simplification of
a real microscope. We have ignored the effects of thick samples,
refractive-index mismatch, aberration, scattering, finite fluorescence
lifetimes, and interactions between fluorophores among others. Because of this
long list of unconsidered effects, real experiments will likely require
extensions of the models developed here.

The dipole pupil function provides the simplest way to create more realistic
models from the simple model in this paper. Phase aberrations can be added to
the dipole pupil function with Zernike polynomials, and refractive index
boundaries can be modeled by applying the work of Gibson and Lanni to the dipole
pupil function \cite{gibson89}. These additions will model phase aberrations,
but modeling polarization aberrations will also be necessary, and we anticipate
that vector Zernike polynomials and the Jones pupil \cite{zhao2007, xu2015,
  chipman1989} will be essential tools for modeling dipole imaging systems. We
plan to use the dipole pupil function to include the effects of non-paraxial
objectives, polarizers, and defocus in future papers of this series.

The dipole pupil function also provides an enormous set of design opportunities.
The dipole imaging problem may benefit from spatially varying diattenuating and
birefrigent masks---a much larger set of possibilities than the well-explored
design space of amplitude and phase masks. The dipole pupil function is a step
towards Green's tensor engineering \cite{agrawal2012}, and the dipole transfer
functions provide a strong framework for evaluating dipole imaging designs.

In the simple case considered here we focused on the emission path of the
microscope, but the excitation path is equally important. Complete models will
need to consider the spatio-angular dependence of excitation. Zhenghao et. al.
\cite{zhanghao2017} have taken steps in this direction by considering polarized
structured illumination microscopy. Rotational dynamics and the fluorescence
lifetime are also important to consider when incorporating models of the
excitation process \cite{lew2013, zhang2018, zhang2018-2}.

% \subsection{Towards spatio-angular reconstructions}
% We have focused on modeling the mapping between the object and the data in this
% paper, but ultimately we are interested in reconstructing the object from the
% data. Applying the monopole approximation simplifies the reconstruction problem
% because both object and data space are $\mbb{L}_2(\mbb{R}^2)$, so we can
% directly apply regularized inverse filters and maximum likelihood methods. The
% dipole model expands object space to $\mbb{L}_2(\mbb{R}^2\times \mbb{S}^2)$, so
% the inverse problem becomes much more challenging. In future work we will use
% the singular value decomposition to find inverse filters, and we will consider
% using polarizers and multiple views to increase the size of data space.

\section{Conclusions}
% Many models of fluorescence microscopes use the monopole and scalar
% approximations, but complete models need to consider dipole and vector optics
% effects. We have introduced several transfer functions that simplify the mapping
% between the dipole density and the irradiance pattern on the detector,

We have calculated the monopole and dipole transfer functions for paraxial
  $4f$ imaging systems and demonstrated these transfer functions with efficient
  simulations. We found that the monopole and scalar approximations are good
  approximations when the sample consists of unconstrained rotating fluorophores
  or many randomly oriented fluorophores within a resolvable volume. We also
  found that dipole and vector optics effects become larger as rotational order
  increases, and in these cases the dipole transfer functions become valuable
  tools.

\section*{Funding}
National Institute of Health (NIH) (R01GM114274, R01EB017293).

\section*{Acknowledgments}
% We thank Kyle Myers, Harrison Barrett, Scott Carney, Luke Pfister, Jerome Mertz,
% Sjoerd Stallinga, Mikael Backlund, Matthew Lew, Min Guo, Yicong Wu, Shalin
% Mehta, Abhishek Kumar, Peter Basser, Marc Levoy, Michael Broxton, Gordon
% Wetzstein, Hayato Ikoma, Laura Waller, Ren Ng, Tomomi Tani, Michael Shribak, Mai
% Tran, Amitabh Verma, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas,
% Dimple Modgil, Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for
% valuable discussions during the development of this work. 
TC was supported by a
University of Chicago Biological Sciences Division Graduate Fellowship, and PL
was supported by a Marine Biological Laboratory Whitman Center Fellowship.
Support for this work was provided by the Intramural Research Programs of the
National Institute of Biomedical Imaging and Bioengineering.

\section*{Disclosures}
The authors declare that there are no conflicts of interest related to this article.

\bibliography{paper}
\appendix
% \section{Spherical harmonics and the spherical Fourier transform}\label{sec:sph}
% The spherical harmonic function of degree $\ell$ and order $-\ell \leq m \leq \ell$
% is defined as \cite{schaeffer2013}
% \begin{align}
% Y_\ell^m(\vartheta, \varphi) = \sqrt{\frac{2\ell+1}{4\pi}}\sqrt{\frac{(\ell-|m|)!}{(\ell+|m|)!}}P_\ell^m\left(\cos\vartheta\right)\exp(i m \varphi),
% \end{align}
% where $P_\ell^m(\cos\vartheta)$ are the associated Legendre polynomials with the
% Condon-Shortley phase
% \begin{align}
%   P_\ell^m(x) = (-1)^m(1-x^2)^{|m|/2}\frac{d^{|m|}}{dx^{|m|}}P_\ell(x),
% \end{align}
% and $P_\ell(x)$ are the Legendre polynomials defined by the recurrence
% \begin{align}
%   P_0(x) &= 1,\\
%   P_1(x) &= x,\\
%   \ell P_\ell(x) &= (2\ell-1)xP_{\ell-1}(x) - (\ell-1)P_{\ell-2}(x). 
% \end{align}
% The spherical harmonics are orthonormal, which means that
% \begin{align}
%   \int_{\mbb{S}^2}d\mh{s}\, Y_\ell^m(\mh{s}){Y}_{\ell'}^{m'*}(\mh{s}) = \delta_{\ell\ell'}\delta_{mm'},
% \end{align}
% where $\delta_{\ell\ell'}$ denotes the Kronecker delta. The spherical harmonics form a
% complete basis, so an arbitrary function on the sphere $f(\mh{s})$ can be
% expanded into a sum of weighted spherical harmonic functions
% \begin{align}
%   f(\mh{s}) = \sum_{\ell=0}^{\infty}\sum_{m=-\ell}^{l}F_\ell^mY_\ell^m(\mh{s}).
% \end{align}
% We can find the spherical harmonic coefficients $F_\ell^m$ for a given function
% using Fourier's trick---multiply both sides by $Y_\ell^{m*}(\mh{s})$,
% integrate over the sphere, and exploit orthogonality to find that
% \begin{align}
%   F_\ell^m = \int_{\mbb{S}^2}d\mh{s}\, f(\mh{s})Y_\ell^{m*}(\mh{s}).
% \end{align}
% The coefficients $F_\ell^m$ are called the \textit{spherical Fourier transform}
% of a spherical function.

\section{Relationships between special functions} \label{sec:special}
Our first task is to show that 
\begin{align}
  i^{n}\left\{\substack{
  \text{exp}(in\phi_r)\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\text{jinc}_{n}(r) &\stackrel{\mathcal{F}_{\mbb{R}^2}}{\longrightarrow}   (2\nu)^{n}\left\{\substack{
    \text{exp}(in\phi_{\nu})\\
    \cos(n\phi_{\nu})\\
    \sin(n\phi_{\nu})
  }\right\}\Pi(\nu). \label{eq:jincrect3}
  \end{align}
  Writing the inverse Fourier transform in polar coordinates yields
  \begin{align}
    =2^n\int_0^{1/2}d\nu\, \nu^{n+1}\int_0^{2\pi}d\phi_\nu\left\{\substack{
    \text{exp}(in\phi_{\nu})\\
    \cos(n\phi_{\nu})\\
    \sin(n\phi_{\nu})
  }\right\}\text{exp}[2\pi i\nu r\cos(\phi_\nu - \phi_r)].
  \end{align}
  The azimuthal integral can be evaluated in terms of an $n^{th}$ order Bessel
  function (for the complex case see \cite[ch. 4.111]{barrett2004}).
  \begin{align}
    =2^n 2\pi i^n \left\{\substack{
    \text{exp}(in\phi_{r})\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\int_0^{1/2}d\nu\, \nu^{n+1}J_n(2\pi\nu r).
  \end{align}
  We can use the following identity \cite[ch.~6.561-5]{gradshteyn2007}
  \begin{align}
    \int_0^1 du\, u^{n + 1}J_{n}(au) = a^{-1}J_{n + 1}(a)
  \end{align}
  with a change of variable $u = 2\nu$ to find the final result
  \begin{align}
    &=2^n 2\pi i^n \left\{\substack{
    \text{exp}(in\phi_{r})\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\int_0^{1}\frac{du}{2}\, \left(\frac{u}{2}\right)^{n+1}J_n(\pi u r)
    =i^n \left\{\substack{
    \text{exp}(in\phi_{r})\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\frac{J_{n+1}(\pi r)}{2r}
    =i^n \left\{\substack{
    \text{exp}(in\phi_{r})\\
    \cos(n\phi_r)\\
    \sin(n\phi_r)
  }\right\}\text{jinc}_{n}(r).
  \end{align}

\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[width = 0.45\textwidth]{../figures/special/special.pdf}
   \caption{The relationships between special functions. The chat functions are
     defined as the two-dimensional Fourier transform of the squared jinc
     functions, and they can be calculated with the two-dimensional complex
     autocorrelations (denoted by $\star_2$) of the complex-weighted rectangle
     functions.}
   \label{fig:special}
 \end{figure}

We can use the relationship in Eq. \eqref{eq:jincrect3} to express the chat
functions in terms of a complex autocorrelation---see the diagram in Fig. \ref{fig:special}. Starting with the definition of
the $n^{th}$-order chat function
\begin{align}
  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, \text{jinc}_{n}^2(|\mb{r}|)\, \text{exp}\left[-2\pi i\mb{r}\nu\right],  \label{eq:ftA}
\end{align}
we can rewrite the integrand in terms of the absolute square of a simpler
function with a known Fourier transform
\begin{align}
  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\mb{r}\, |t_n(\mb{r})|^2\, \text{exp}\left[-2\pi i\mb{r}\nu\right].  \label{eq:ftB}
\end{align}
\begin{align}
  t_n(\mb{r}) = i^n\text{exp}[in\phi_r]\text{jinc}_{n}(r).
\end{align}
Now we can apply the autocorrelation theorem to rewrite the Fourier transform as
\begin{align}
  \text{chat}_{n}(\nu) = \int_{\mbb{R}^2}d\bs{\tau}\, T_n(\bs{\tau})T^*_n(\bs{\tau} - \nu), \label{eq:autocorr}
\end{align}
where the function to be autocorrelated can be found with the help of Eq. \eqref{eq:jincrect3}
\begin{align}
  T_n(\bs{\tau}) = \int_{\mbb{R}^2}d\mb{r}\, t_n(\mb{r})\text{exp}\left[-2\pi i\mb{r}\cdot\bs{\tau}\right] = (2\tau)^n\text{exp}[in\phi_\tau]\Pi\left(\tau\right). \label{eq:tau}
\end{align}
It will be more convenient to set up the autocorrelation in Cartesian coordinates 
\begin{align}
  T_n(\bs{\tau}) &= 2^n(\tau_x + i\tau_y)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right). \label{eq:tn}
\end{align}
Plugging Eq. \eqref{eq:tn} into Eq. \eqref{eq:autocorr} gives
\begin{align}
  \text{chat}_{n}(\nu) = 4^n\int_{\mbb{R}^2}d\bs{\tau}\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Pi\left(\sqrt{\tau_x^2 + \tau_y^2}\right)\Pi\left(\sqrt{(\tau_x - \nu)^2 + \tau_y^2}\right).
\end{align}
We can interpret the autocorrelation as an integral over a region of overlap
between a circle centered at the origin and a circle shifted to the right by
$\nu$ (a geometric lens). Using the construction in Fig. \ref{fig:geometry} we
can express this region as
\begin{align}
  \text{chat}_{n}(\nu) = 4^{n+1}\Bigg[&\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau})^{n} -\nonumber \\ &\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y(\tau_x^2 + \tau_y^2 - \nu\tau_x)^{n}\Bigg]\Pi\left(\frac{\nu}{2}\right).
\end{align}
\begin{figure}[ht]
 \centering
   \centering
   \includegraphics[width = 1.0\textwidth]{../figures/autocorrelation/autocorrelation.pdf}
   \caption{Geometric construction for evaluating the autocorrelation. We need
     to integrate over the overlapping region of two circles with radius $1/2$
     and distance $\nu$ between their centers. The region is four times the
     difference in area between a sector of angle $\cos^{-1}(\nu)$ and radius
     $1/2$ and a right triangle with base $\nu/2$ and hypotenuse $1/2$.}
   \label{fig:geometry}
 \end{figure}

For $n=0$:
\begin{align}
  \text{chat}_0(\nu) &= 4\left[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau} - \int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\right]\Pi\left(\frac{\nu}{2}\right),\\
  \text{chat}_0(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu|\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right),
\intertext{which is a well-known result \cite{goodman1996, mertz2009, bracewell2004}. For $n=1$:}
  \text{chat}_1(\nu) &= 16\Bigg[\int_0^{1/2}\tau d\tau\int_0^{\cos^{-1}\nu}d\phi_{\tau}(\tau^2 - \nu\tau\cos\phi_{\tau}) - \nonumber\\ &\qquad\quad\int_{0}^{\nu/2}d\tau_x\int_0^{\frac{\tau_x}{\nu}\sqrt{1 - \nu^2}}d\tau_y\, (\tau_x^2 + \tau_y^2 - \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2}\right),\\
  \text{chat}_1(\nu) &= \frac{1}{2}\left[\cos^{-1}|\nu| - |\nu| (3 - 2\nu^2)\sqrt{1 - \nu^2}\right]\Pi\left(\frac{\nu}{2}\right). 
\end{align}

\section{Spherical Fourier transform of a double cone}\label{sec:cone}
In this appendix we evaluate the spherical Fourier transform of a
normalized double-cone angular distribution with central direction $\mh{s}'$ and
cone half-angle $\Delta$
\begin{align}
  f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta) = \frac{1}{4\pi(1 - \cos\Delta)}\Pi\left(\frac{\mh{s}\cdot\mh{s}'}{2\cos\Delta}\right). \label{eq:doublecone}
\end{align}
The spherical Fourier transform is
\begin{align}
  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\mh{s}; \mh{s}', \Delta)Y_\ell^{m*}(\mh{s}).
\end{align}

The limits of integration will be difficult to find unless we change coordinates
to exploit the axis of symmetry $\mh{s}'$. Since the spherical function is
rotationally symmetric about $\mh{s}'$ we can rotate the function so that the axis of
symmetry is aligned with $\mh{z}$ and multiply by $\sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')$ to account for the rotation \cite{ramamoorthi2005}
\begin{align}
    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \sqrt{\frac{4\pi}{2l+1}}Y_\ell^{m*}(\mh{s}')\int_{\mbb{S}^2}d\mh{s}\, f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)Y_\ell^0(\mh{s}). 
\end{align}
In this coordinate system the double cone is independent of the azimuthal angle,
so we can evaluate the azimuthal integral and express the function in terms of an
integral over $\vartheta$:
\begin{align}
    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = 2\pi Y_\ell^{m*}(\mh{s}')\int_{0}^\pi d\vartheta\, \sin\vartheta f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)P_\ell(\cos\vartheta). 
\end{align}
The function $f_{\text{(cone)}}(\vartheta; \mh{z}, \Delta)$ is only non-zero on
the intervals $\vartheta \in [0, \Delta]$ and
$\vartheta \in [\pi - \Delta, \pi]$ so
\begin{align}
    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{0}^\Delta d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta) + \int_{\pi - \Delta}^\pi d\vartheta\, \sin\vartheta P_\ell(\cos\vartheta)\right]. 
\end{align}
Applying a change of coordinates with $u = \cos\vartheta$ yields
\begin{align}
    F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{2(1 - \cos\Delta)}\left[\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) + \int_{-1}^{-\cos\Delta} d\vartheta\, P_\ell(u)\right]. 
\end{align}
The Legendre polynomials $P_\ell(u)$ are even (odd) on the interval [-1, 1] when
$\ell$ is even (odd), so the pair of integrals will be identical when $\ell$ is
even and cancel when $\ell$ is odd. For even $\ell$,
\begin{align}
  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) = \frac{Y_\ell^{m*}(\mh{s}')}{1 - \cos\Delta}\int_{\cos\Delta}^1 d\vartheta\, P_\ell(u).
\end{align}
The integral evaluates to \cite[ch.~7.111]{gradshteyn2007}
\begin{align}
  \int_{\cos\Delta}^1 d\vartheta\, P_\ell(u) =
\begin{cases}
  1 - \cos\Delta\,, &\ell = 0\,,\\
  \sin\Delta\, P_l^{-1}(\cos\Delta)\,, &\text{else},
\end{cases}
\end{align}
where $P_l^{-1}(\cos\Delta)$ is the associated Legendre polynomial with order
$m=-1$, not an inverse Legendre polynomial. Bringing everything together
\begin{align}
  F_{\ell\text{(cone)}}^m(\mh{s}', \Delta) =
  \begin{cases}
    \sqrt{1/(4\pi)}, & \ell = 0,\\
    0, & \ell\, \text{odd},\\
    Y_\ell^{m*}(\mh{s}')\cot\left(\frac{\Delta}{2}\right)P_l^{-1}(\cos\Delta), & \ell > 0\,\, \text{even}.
  \end{cases}
\end{align}

\end{document}

### 2018-12-22 papers/basic-theory/paper/paper.tex
Patrick's split edits.

@@
   We introduce the basic elements of a spatio-angular theory of fluorescence
-  microscopy. We model an aplanatic microscope imaging an ensemble of in-focus
-  fluorescent dipoles as a linear Hilbert-space operator, and we show that the
-  operator takes a particularly convenient form when expressed in a basis of
-  complex exponentials and spherical harmonics---a form we call the dipole
+  microscopy, providing a unified framework for analyzing systems that image
+  single molecules or ensembles of molecules labeled with fluorescent dipoles.
+  We model an aplanatic microscope imaging an ensemble of in-focus fluorescent
+  dipoles as a linear Hilbert-space operator, and we show that the operator
+  takes a particularly convenient form when expressed in a basis of complex
+  exponentials and spherical harmonics---a form we call the dipole
   spatio-angular transfer function. We discuss the implications of our analysis

### 2018-12-22 papers/para-4f/paper/paper.tex
Patrick's split edits.

@@
 \usepackage[normalem]{ulem}
+\usepackage{booktabs}
 
@@
 \begin{abstract*}
-  We analyze a single-view fluorescence microscope in a $4f$ geometry
-    without using the monopole or scalar approximations. We show that this
-    imaging system has a spatio-angular band limit, and we exploit the band
-    limit to perform efficient simulations. Notably, we show that information
-    about the out-of-plane orientation of ensembles of in-focus fluorophores is
-    recorded by paraxial fluorescence microscopes. Additionally, we show that
-    deconvolution algorithms that use the monopole approximation may make biased
-    estimates of fluorophore concentrations, but these biases are small when the
-    sample contains either many randomly oriented fluorophores in each
-    resolvable volume or unconstrained rotating fluorophores.
+  We investigate the properties of a single-view fluorescence microscope
+  in a $4f$ geometry when imaging fluorescent dipoles without using the
+  monopole or scalar approximations. We show that this imaging system has a
+  spatio-angular band limit, and we exploit the band limit to perform efficient
+  simulations. Notably, we show that information about the out-of-plane
+  orientation of ensembles of in-focus fluorophores is recorded by paraxial
+  fluorescence microscopes. Additionally, we show that the monopole
+    approximation may cause biased estimates of fluorophore concentrations, but
+  these biases are small when the sample contains either many randomly oriented
+  fluorophores in each resolvable volume or unconstrained rotating fluorophores.
 \end{abstract*}
@@
 We begin in section \ref{sec:theory} by specifying the imaging geometry and
-  defining \textit{pupil functions} for both monopole and dipole imaging
-  systems. We explicitly relate the pupil functions to the coherent transfer
-  functions to establish a connection between physical calculations and the
-  transfer functions. Next, in section \ref{sec:results} we calculate the
-  monopole and dipole transfer functions in closed form, and we use these
-  transfer functions to perform efficient simulations with four numerical
-  phantoms. Finally, in section \ref{sec:discussion} we discuss the results and
-  expand on how the pupil functions can be used to develop improved models for
+defining \textit{pupil functions} for imaging systems with and without the
+monopole approximation. We explicitly relate the pupil functions to the coherent
+transfer functions to establish a connection between physical calculations and
+the transfer functions. Next, in section \ref{sec:results} we calculate the
+monopole and dipole transfer functions in closed form, and we use these transfer
+functions to perform efficient simulations with four numerical phantoms.
+Finally, in section \ref{sec:discussion} we discuss the results and expand on
+how the pupil functions can be used to develop improved models for
 spatio-angular microscopes.
@@
 \end{align}
-where $h(\rd - \ro, \so)$ is the dipole point spread function. Note that we
-  have written Eqs. \eqref{eq:mono} and \eqref{eq:dip} in their
-  demagnified forms. We will use primes to denote the unscaled detector
-  coordinate, $\rd'$, and unscaled point spread functions, $h'$.
+where $h(\rd - \ro, \so)$ is the dipole point spread function. Note that we have
+written Eqs. \eqref{eq:mono} and \eqref{eq:dip} in their demagnified forms. We
+will use primes to denote the unscaled detector coordinate, $\rd'$, and unscaled
+point spread functions, $h'$.
+
+After expressing the operators in a delta function basis we explored the
+  form of the operators with several other choices of basis functions. Tables 1
+  and 2 summarize our results.
+
+  \begin{table}[t]
+    \centering
+  \begin{tabular}{lll}
+    \toprule
+    Quantity&Symbol&Relationships\\
+    \midrule
+    Monopole density&$f(\ro)$&---\\
+    Monopole spectrum&$F(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{f(\ro)\right\}$\\
+    \midrule
+    Monopole coherent spread function&$c(\rd - \ro)$&---\\
+    Monopole coherent transfer function&$C(\taup)$&$=\mc{F}_{\mbb{R}^2}\left\{c(\rd - \ro)\right\}$\\
+    Monopole point spread function&$h(\rd - \ro)$&$=|c(\rd - \ro)|^2$\\
+    Monopole transfer function&$H(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{h(\rd-\ro)\right\}$\\
+    &&$= \int_{\mbb{R}^2}d\taup\,C(\taup)C^{*}(\taup - \bv)$\\
+    \midrule
+    Scaled irradiance&$g(\rd)$&$=\int_{\mbb{R}^2}d\ro\, h(\rd - \ro)f(\ro)$\\
+    Scaled irradiance spectrum&$G(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{g(\rd)\right\}=H(\bv)F(\bv)$\\
+    \bottomrule
+\end{tabular}
+\caption{Summary of relevant quantities in fluorescence microscopy under the
+  monopole approximation---see \cite{chandler2018} for derivations.
+  $\mc{F}_{\mbb{R}^2}$ denotes a two-dimensional Fourier transform.}
+\end{table}
+
+  \begin{table}[t]
+    \hspace{-1.5em}
+  \begin{tabular}{lll}
+    \toprule
+    Quantity&Symbol&Relationships\\
+    \midrule
+    Dipole density&$f(\ro,\so)$&---\\
+    Dipole spatial spectrum&$F(\bv,\so)$&$=\mc{F}_{\mbb{R}^2}\left\{f(\ro,\so)\right\}$\\
+    Dipole angular spectrum&$F_{\ell}^m(\ro)$&$=\mc{F}_{\mbb{S}^2}\left\{f(\ro,\so)\right\}$\\
+    Dipole spatio-angular spectrum&$\msf{F}_{\ell}^m(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{F_{\ell}^m(\ro)\right\} = \mc{F}_{\mbb{S}^2}\left\{F(\bv, \so)\right\}$\\
+    \midrule
+    Dipole coherent spread function&$\mb{c}(\rd - \ro, \so)$&---\\
+    Dipole coherent transfer function&$\mb{C}(\taup,\so)$&$=\mc{F}_{\mbb{R}^2}\left\{\mb{c}(\rd - \ro, \so)\right\}$\\
+    Dipole point spread function&$h(\rd - \ro,\so)$&$=|\mb{c}(\rd - \ro, \so)|^2$\\
+    Dipole spatial transfer function&$H(\bv,\so)$&$=\mc{F}_{\mbb{R}^2}\left\{h(\rd-\ro,\so)\right\}$\\
+    &&$= \int_{\mbb{R}^2}d\taup\,\mb{C}(\taup,\so)\mb{C}^{\dagger}(\taup - \bv,\so)$\\
+    Dipole angular transfer function&$H_{\ell}^m(\rd - \ro)$&$=\mc{F}_{\mbb{S}^2}\left\{h(\rd-\ro,\so)\right\}$\\
+    Dipole spatio-angular transfer function&$\msf{H}_{\ell}^m(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{H_{\ell}^m(\rd - \ro)\right\} = \mc{F}_{\mbb{S}^2}\left\{H(\bv, \so)\right\}$\\
+    \midrule
+    Scaled irradiance&$g(\rd)$&$=\int_{\mbb{S}^2}d\so\int_{\mbb{R}^2}d\ro\, h(\rd - \ro, \so)f(\ro,\so)$\\
+    &&$= \sum_{\ell m}\int_{\mbb{R}^2}d\ro\,H_{\ell}^m(\rd - \ro)F_{\ell}^m(\ro)$\\
+    Scaled irradiance spectrum&$G(\bv)$&$=\mc{F}_{\mbb{R}^2}\left\{g(\rd)\right\}$\\
+            &&$=\int_{\mbb{S}^2}d\so\, H(\bv,\so)F(\bv, \so)$\\
+            &&$=\sum_{\ell m} \msf{H}_{\ell}^m(\bv) \msf{F}_{\ell}^m(\bv)$\\
+    \bottomrule
+\end{tabular}
+  \caption{Summary of relevant quantities in spatio-angular dipole imaging---see \cite{chandler2018} for derivations.
+$\mc{F}_{\mbb{R}^2}$ denotes a two-dimensional Fourier transform, and $\mc{F}_{\mbb{S}^2}$ denotes a spherical Fourier transform.}
+\end{table}
 
@@
  \subsection{Comparing monopole and dipole models}
- The only case when the dipole and monopole transfer functions match
-   exactly is when the sample consists of dipoles that are completely
-   constrained to the transverse plane of a paraxial imaging system. Applying
-   the monopole approximation in any other situation can lead to biased
-   estimates of the fluorophore concentrations.
-
- However, the common justifications for the monopole approximation---the
-   fluorophores are rotationally unconstrained or there are many randomly
+ The only case when the dipole and monopole transfer functions match exactly is
+ when the sample consists of dipoles that are completely constrained to the
+ transverse plane of a paraxial imaging system. Applying the monopole
+ approximation in any other situation can lead to biased estimates of the
+ fluorophore concentrations. To see how these biases manifest, consider the
+   irradiance pattern created by an ensemble of dipoles oriented along the optic
+   axis---see Figs. \ref{fig:ph1}, \ref{fig:ph2}, \ref{fig:ph3}, or \ref{fig:ph4}.
+   Any reconstruction scheme that uses the monopole approximation would
+   attribute the irradiance doughnut to a doughnut of monopoles instead of
+   axially oriented dipoles, which is a clear example of a biased estimate caused
+   by model mismatch.
+
+   However, the common justifications for the monopole approximation---that the
+   fluorophores are rotationally unconstrained or that
+   there are many randomly
    oriented fluorophores in a resolvable volume---are good justifications in all

### 2019-02-06 notes/2019-01-28-angular-optimize/report/report.tex
Angular optimization notes.

\documentclass[11pt]{article}

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\usepackage{tocloft}
\usepackage[linesnumbered,ruled]{algorithm2e}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
$\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
$\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}
\usepackage{bold-extra}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{upgreek}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{amssymb,latexsym,amsmath,gensymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{$\displaystyle} c <{$}}
\usepackage{tikz, calc}
\usetikzlibrary{shapes.geometric, arrows, calc}
\tikzstyle{norm} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\newcommand{\argmin}{\arg\!\min}
\providecommand{\argmax}[1]{\underset{#1}{\mathrm{argmax}}\,}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathfrak{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\sd}{\mathbf{\hat{s}}_d}
\providecommand{\pp}{\mathbf{\hat{p}}}
\providecommand{\rb}{\mathbf{r}_b}
\providecommand{\rbm}{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{\mathfrak{r}}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\ms}[1]{\mathsf{#1}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\tv}{\texttt{v}}
\providecommand{\tx}[1]{\text{#1}}
\providecommand{\tb}[1]{\textbf{#1}}
\providecommand{\ttt}[1]{\texttt{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bp}{\bs{\rho}}
\providecommand{\p}{\mh{p}}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\intinf}{\int_{-\infty}^{\infty}}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

\providecommand{\fig}[4]{
  % filename, width, caption, label
\begin{figure}[H]
 \captionsetup{width=1.0\linewidth}
 \centering
 \includegraphics[width = #2\textwidth]{#1}
 \caption{#3}
 \label{fig:#4}
\end{figure}
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\tunderbrace}[2]{\underbrace{#1}_{\textstyle#2}}
\providecommand{\figs}[7]{
  % filename1, filename2, caption1, caption2, label1, label2, shift
\begin{figure}[H]
\centering
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#1}
  \captionsetup{justification=justified, singlelinecheck=true}
  \caption{#3}
  \label{fig:#5}
\end{minipage}
\hspace{2em}
\begin{minipage}[b]{.45\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{#2}
  \vspace{#7em}
  \captionsetup{justification=justified}
  \caption{#4}
  \label{fig:#6}
\end{minipage}
\end{figure}
}
\makeatletter

\providecommand{\code}[1]{
\begin{center}
\lstinputlisting{#1}
\end{center}
}

\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%
% Spacing %
%%%%%%%%%%%
% Margins
\usepackage[
top    = 1.5cm,
bottom = 1.5cm,
left   = 1.5cm,
right  = 1.5cm]{geometry}

% Indents, paragraph space
%\usepackage{parskip}
\setlength{\parskip}{1.5ex}

% Section spacing
\usepackage{titlesec}
\titlespacing*{\title}
{0pt}{0ex}{0ex}
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% Line spacing
\linespread{1.1}

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Optimizing angular diSPIM measurements\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
  % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
\date{\vspace{-3em}\today\vspace{-1em}}
\maketitle

\section{Introduction}
Our goal in these notes is to find optimal angular sampling schemes for the
diSPIM with light-sheet tilting. We review the continuous angular forward model,
find the sampling schemes available to us, choose an objective function to
optimize, then search through the sampling schemes.

\section{Continuous forward model}
We briefly review the continuous angular forward model---see the
\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-12-10-angular-svd/report/report.pdf}{previous
  notes} for a more detailed discussion. We can write the
continuous-to-continuous forward model in the form
\begin{align}
  \mb{g}_c = \mc{H}_{cc}\mb{f}_c,\label{eq:cc}
\end{align}
where $\mb{f}_c \in \mbb{L}_2(\mbb{S}^2)$ is the angular dipole density,
$\mb{g}_c \in \mbb{L}_2(\mbb{S}^2\times \mbb{S}^1)$ is the continuous irradiance
data taken by varying the detection optical axis (the $\mbb{S}^2$ dimension) and
the illumination polarizer (the $\mbb{S}^1$ dimension), and $\mc{H}_{cc}$ is a
linear continuous-to-continuous Hilbert-space operator between these spaces.

If we choose a delta-function basis for both object and data space then we can
rewrite Eq. \eqref{eq:cc} as 
\begin{align}
  g(\sd, \pp) = \ints{2}d\so\, h(\sd,\pp;\so)f(\so),\label{eq:fwd}
\end{align}
where $\so \in \mbb{S}^2$ is the object angular coordinate, $\sd \in \mbb{S}^2$
is the detection optical axis coordinate, $\pp \in \mbb{S}^1$ is the polarizer
coordinate, and $h(\sd,\pp;\so)$ is the kernel of the integral transform. We can
separate the kernel into an excitation and detection part since these processes
are incoherent
\begin{align}
  h(\sd, \pp;\so) = h^{\text{exc}}(\pp;\so)h^{\text{det}}(\sd;\so). \label{eq:kern}
\end{align}
The excitation kernel is straightforward---the squared dot product of the
polarizer orientation $\pp$ with the object angular coordinate $\so$
\begin{align}
  h^{\text{exc}}(\pp\cdot\so) \propto (\pp\cdot\so)^2. \label{eq:exckern}
\end{align}
The detection kernel requires more care since we are collecting light over the
NA of the objective. In the previous notes we started with the power along a
single ray then integrated over the aperture to find that the detection kernel is
\begin{align}
  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so),
\end{align}
where $\text{NA} = n_o\sin\alpha$, and $P_{\ell}(x)$ are the Legendre
polynomials.

We can rewrite the mapping in Eq. \eqref{eq:cc} in an object-space spherical
harmonic basis as
\begin{align}
  g(\sd, \pp) = \sum_{\ell m}H_\ell^m(\sd, \pp)F_\ell^m,\label{eq:fwdsh}
\end{align}
where $F_\ell^m$ is the angular dipole spectrum given by 
\begin{align}
  F_\ell^m = \int_{\mbb{S}^2}d\so\, f(\so)Y_\ell^{m*}(\so),
\end{align}
and $H_\ell^m(\sd, \pp)$ is the kernel in this basis given by
\begin{align}
  H_\ell^m(\sd, \pp) &= \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd),\label{eq:triple4}\\
    H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
\end{align}
with the Gaunt coefficients given by 
\begin{align}
  G_{\ell,\ell',\ell''}^{m,m',m''} = \ints{2}d\so\, Y_\ell^{m}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).
\end{align}

It's useful to compare Eq. \eqref{eq:fwd} to Eq. \eqref{eq:fwdsh}---in a delta
function basis we need to compute an angular integral, while in the object-space
spherical harmonics basis the kernel has a finite number of terms so we can
compute it exactly.

It's also useful to compare Eq. \eqref{eq:kern} to Eq. \eqref{eq:triple4}---in a
delta function basis the kernel is the product of the excitation and detection
kernels, while in the object-space spherical harmonic basis the kernel is a
generalized convolution of the excitation and detection kernels.

\section{Sampling schemes}
We can write the sampling operation as a continuous-to-discrete Hilbert space
operator $\mc{D}_w$
\begin{align}
  \mb{g}_d = \mc{D}_w\mb{g}_c = \mc{D}_w\mc{H}_{cc}\mb{f}_c. 
\end{align}
We can write the sampling operation in a delta function basis as
\begin{align}
  g_m = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_m(\sd,\pp)g(\sd,\pp).
\end{align}
where $g_m$ is the $m$th discrete measurement and $w_m(\sd,\pp)$ is the $m$th
sampling aperture. For now we will restrict ourselves to delta-function sampling
apertures
\begin{align}
  w_m(\sd,\pp) = \delta(\mh{s}_{d,m} - \sd)\delta(\mh{p}_{m} - \pp),
\end{align}
where $\mh{s}_{d,m}$ and $\mh{p}_{m}$ are the $m$th sampling points. This
restriction means that we will leave the polarizer setting and tilt angle fixed
during each volume acquisition. We could consider scanning the polarizer
setting and tilt angle in the future for faster acquisitions, but I think these
sampling schemes will always decrease ``angular SNR''.

So far we've formulated everything quite generally and haven't made any
reference to the diSPIM geometry. Now we find the constraints that the diSPIM
geometry places on the values of $\mh{s}_{d,m}$ and $\mh{p}_{m}$. If we define
the $\mh{x}$ and $\mh{z}$ axes as the optical axes of the two objective then we
have the following sampling constraint
\begin{align}
\mh{s}_{d,m} \in \{\mh{x}, \mh{z}\}.  \label{eq:first}
\end{align}
In words, this constraint says that we can only detect along one of two discrete
and orthogonal axes.

Next, we constrain the polarizer sampling points $\mh{p}_m$. We introduce a
variable $\mh{s}_{e,m}$ to denote the excitation optical axis for the $m$th
measurement. This variable does not affect the forward model (we've formulated
in terms of $\pp$ only on the excitation side), but it will allow us to
conveniently constrain $\pp$. First, we constrain the excitation optical axis to
be perpendicular to the detection optical axis
\begin{align}
  \mh{s}_{e,m} \cdot \mh{s}_{d,m} = 0.
\end{align}
This is a fairly loose constraint, but it ensures that the light sheet is in
focus across the field of view.

Next, we constrain the excitation optical axis to within the available tilt
angles of the instrument. If we use $\mc{R}$ to denote an ``axis swapping
operator'' ($\mc{R}(\mh{z}) = \mh{x}$ and $\mc{R}(\mh{x}) = \mh{z}$), then the tilting
constraint can be written as
\begin{align}
  \mh{s}_{e,m} \cdot \mc{R}(\mh{s}_{d,m}) \leq \Delta,
\end{align}
where $\Delta$ is the maximum tilt angle. For the current instrument $\Delta = 15^{\circ} = \pi/12$.

Finally, we constrain the excitation polarization $\pp_m$ to be perpendicular to
the excitation optical axis
\begin{align}
  \mh{s}_{e,m} \cdot \pp_m = 0.  \label{eq:final}
\end{align}
For convenience we will denote individual sampling points with $\mf{s}_m$ =
($\pp_m$, $\mh{s}_{d,m}$), and we will denote the set of all sampling points
$\mf{s}_m$ that satisfy Eqs. \eqref{eq:first}--\eqref{eq:final} by $\mc{S}$.
With this notation we can denote a complete sampling scheme with $M$ samples
by $\mf{s} \in \mc{S}^M$ ($M$ copies of the set $\mc{S}^M$).

\section{Objective functions}
Our goal is to choose an $M$-sample sampling scheme $\mf{s} \in \mc{S}^M$ that
is optimal in some sense. We propose that we optimize the Schatten 2-norm of the
continuous-discrete imaging operator
\begin{align}
  \mf{s}^* = \argmax{\mf{s} \in \mc{S}^M}||\mc{D}_{\mf{s}}\mc{H}_{cc}||_2. \label{eq:notime}
\end{align}
The Schatten $p$-norm is defined as the $\mbb{L}_p$ norm of the singular values
of the operator, so the Schatten $2$-norm is a reasonable measure of the amount
of information that the imaging system can pass. It favors sampling schemes that
have many large singular values, so it will prefer sampling schemes that measure
many orthogonal parameters of the object that are insensitive to noise.

It's useful to interpret the Schatten $2$-norm by analyzing a spatial imaging
system. The ``effective OTF'' that appears in many fluorescence microscopy
papers (including Hari and Yicong's 2018 SIM review) is a specific example of a
continuous singular value spectrum. We can calculate the Schatten $2$-norm by
taking the effective OTF, squaring its value at each spatial frequency,
integrating over the spatial frequencies, then taking the square root. The
Schatten $2$-norm will be largest for imaging systems that have many singular
values (a high spatial frequency bandwidth) that are large (we prefer effective
OTFs that are large and constant over the bandwidth).

Eq. \eqref{eq:notime} will optimize the number and size of the singular values
without considering how interpretable the corresponding parameters are. One of
our motivations for adding light-sheet tilting was to measure rotationally
invariant parameters of the object which will be much more interpretable than
rotationally variant parameters. To achieve this objective we need to measure at
least the $\ell=0$ and $\ell = 2$ rotationally invariant subspaces---a
6-dimensional subspace of $\mbb{L}_2(\mbb{S}^2)$. This will require at least 6
measurements. To ensure that a sampling scheme has measured this rotationally
invariant subspace, we require that
\begin{align}
  \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}) \geq 6 \label{eq:constraint}
\end{align}
where $\mc{P}_{\ell_c=2}$ is a projection operator onto the $\ell=0$ and
$\ell=2$ subspace. For convenience we will denote the set of sampling schemes
that satisfy the constraint in Eq. \eqref{eq:constraint} by
$\mc{Z} = \{\mf{s}\, |\, \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2})
\geq 6\}$.

The solutions of Eq. \eqref{eq:notime} will not necessarily satisfy Eq.
\eqref{eq:constraint}, and simply adding an extra constraint to Eq.
\eqref{eq:constraint} will not ensure that we are optimally measuring the
parameters in the subspace that we want to measure. Instead, we propose an
alternative optimization problem
\begin{align}
    \mf{s}_{\ell_c =2}^* = \argmax{\mf{s} \in \mc{S}^M\cap\mc{Z}}||\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}||_2,
\end{align}
which ensures that the objective function is independent of singular values that
measure parameters outside of the objective subspace. Note that the set
$\mc{S}^M\cap\mc{Z}$ will definitely be empty for $M \leq 6$, and we are not sure
what value of $M$ will yield solutions.

\section{Practical implementation details}
The two optimization problems above are sufficient to propose optimal sampling
schemes, but they lack many of the details required for an implementation. In
this section I'll go through some of the practical work of converting the
abstract forms into finite-dimensional optimization problems.

First, we need to choose a basis and find matrix representations for the
operators $\mc{D}_{\mf{s}}$ and $\mc{H}_{cc}$. At first glance this seems
difficult---$\mc{D}_{\mf{s}}$ is a CD operator and $\mc{H}_{cc}$ is a CC
operator so they do not have finite-dimensional matrix representations
individually. Luckily, the combination $\mc{D}_{\mf{s}} \mc{H}_{cc}$ is a
band-limited compact operator, so it has a finite-dimensional representation as
a $15\times M$ matrix that we will call $\ms{H}$. The entries of this matrix are
given by
\begin{align}
  \ms{H}_{jm} = H_j(\mh{s}_{d,m}, \mh{p}_m),
\end{align}
where $j$ is a single index over the spherical harmonics, and Eq.
\ref{eq:triple4} shows us how to calculate the entries in terms
of the excitation and detection kernels.

Next, we need a matrix representation of $\mc{P}_{\ell_c=2}$. This is simple in
a spherical harmonics basis---we create a 15$\times$15 matrix called
$\ms{P}$, fill the first six diagonal elements with ones, and place zeroes
elsewhere
\begin{align}
  \ms{P}_{ij} = \delta_{ij}, \qquad i,j = 0,1,2,3,4,5.
\end{align}

Next, we need a way to calculate the Schatten 2-norm efficiently. We could
calculate the singular values of each $15\times 15$ matrix, but this would be
slow. We can take a shortcut and replace the Schatten 2-norm with the Frobenius
norm---the $\mbb{L}_2$ norm of the matrix entries. Note that this replacement is
only valid for finite-dimensional representations of the operators.

Finally, we need an efficient set of scalar parameters to search through the set
of sampling schemes $\mc{S}^M$. We will parameterize each sample with a discrete
view index $v \in \{0, 1\}$ to indicate the detection axis, a tilt angle defined
from the nominal excitation axis $\delta \in [-\Delta, \Delta]$, and a polarizer
angle defined from the detection axis $\phi \in [0, 2\pi)$.

This parameter space is challenging to search because it is continuous in some
parameters and discrete in others. It's not clear if it's possible to take
derivatives with respect to the continuous parameters, so as a first pass we
will discretize the continuous parameters and use a search heuristic.
Discretization has the advantage of providing solutions that will be easier to
implement experimentally since we can constrain our solutions to sampling
schemes that are easy to align, but of course we can't guarantee that our
sampling scheme solutions will be globally optimal.

We will discretize the tilt angle into 5 angles
$\delta \in \{-\Delta, -\Delta/2, 0,\Delta/2, \Delta\}$, and we will discretize
the polarizer angle into 8 angles $\phi \in \{0,\pi/8,\dots,7\pi/8\}$. This means
that a brute-force approach will need to search
$(2\,\text{views}\times 5\,\text{tilts}\times 8\,\text{polarizer settings})^M$
possible measurement schemes which becomes computationally infeasible for $M$
larger than about 5 or 6.

To avoid a brute-force search we will use a simple hill-climbing algorithm. In
words, we (1) start with an initial guess for each of the $3M$ parameters and
evaluate the objective function, (2) increment and decrement the first parameter
and move in the direction that improves the objective function, (3) repeat (2)
for each parameter one by one, (4) repeat (3) and keep cycling parameters until
no movement improves the objective function or a fixed number of objective
function evaluations is reached. Although the algorithm is extremely coarse and
provides no guarantees, it is simple to implement and it can be stopped at any
time and will always return its best guess.

\section{Results}

\end{document}

### 2019-02-21 notes/2018-12-10-angular-svd/report/report.tex
Latest angular notes with summary.

@@
 \begin{align}
-  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so).
+  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right]P_2(\sd\cdot\so).
 \end{align}
@@
     H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
-    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
+    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
 \end{align}
@@
 
-\section{Specific designs (in progress)}
-one-view epi,
-one-view lightsheet,
-two-view lightsheet,
-two-view lightsheet two-tilt one-side,
-two-view lightsheet two-tilt two-side,
-two-view lightsheet three-tilt one-side two-tilt one-side.
+% \section{Specific designs (in progress)}
+% one-view epi,
+% one-view lightsheet,
+% two-view lightsheet,
+% two-view lightsheet two-tilt one-side,
+% two-view lightsheet two-tilt two-side,
+% two-view lightsheet three-tilt one-side two-tilt one-side.
 
@@
   F_\ell &= \frac{2\ell + 1}{2}\int_{-1}^1dx\,(1 - x^{2})P_\ell(x) = \frac{2}{3}(\delta_{\ell,0} + \delta_{\ell,2}),\label{eq:fl}\\
-  H_\ell &= \frac{2\ell + 1}{2}\int_{\cos\alpha}^1dx\,x^{-1/2}P_\ell(x) = (1 - \sqrt{\cos\alpha})\delta_{\ell,0} + \left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]\delta_{\ell,2}+ \cdots,\label{eq:hl}
+  H_\ell &= \frac{2\ell + 1}{2}\int_{\cos\alpha}^1dx\,x^{-1/2}P_\ell(x) = (1 - \sqrt{\cos\alpha})\delta_{\ell,0} + \left[\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right]\delta_{\ell,2}+ \cdots,\label{eq:hl}
 \end{align}
@@
   h^{\text{exc}}(\pp\cdot\so) &\propto (\pp\cdot\so)^2, \\
-  h^{\text{det}}(\sd\cdot\so) &\propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so).
+  h^{\text{det}}(\sd\cdot\so) &\propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right]P_2(\sd\cdot\so).
 \end{align}
@@
   H_{\ell''}^{m'',\text{det}}(\sd) &= \frac{4\pi}{2\ell'' + 1}Y_{\ell''}^{m''*}(\sd)\left[\frac{2\ell'' + 1}{2}\int_{-1}^1dx\, h^{\text{det}}(x)P_{\ell''}(x)\right],\\
-  H_{\ell''}^{m'',\text{det}}(\sd) &= \frac{4\pi}{2\ell'' + 1}Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \frac{1}{5}\left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right],\\
-  H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].
+  H_{\ell''}^{m'',\text{det}}(\sd) &= \frac{4\pi}{2\ell'' + 1}Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \frac{1}{5}\left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right],\\
+  H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right].
 \end{align}

### 2019-02-21 notes/2019-01-28-angular-optimize/report/report.tex
Latest angular notes with summary.

@@
 
-\newcommand{\argmin}{\arg\!\min}
 \providecommand{\argmax}[1]{\underset{#1}{\mathrm{argmax}}\,}
+\providecommand{\argmin}[1]{\underset{#1}{\mathrm{argmin}}\,}
 \newcommand{\me}{\mathrm{e}}
@@
 \begin{align}
-  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so),
+  h^{\text{det}}(\sd\cdot\so) \propto 2(1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right]P_2(\sd\cdot\so),
 \end{align}
@@
     H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
-    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
+    H_{\ell''}^{m'',\text{det}}(\sd) &\propto \frac{Y_{\ell''}^{m''*}(\sd)}{1 - \cos\alpha}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
 \end{align}
@@
 Our goal is to choose an $M$-sample sampling scheme $\mf{s} \in \mc{S}^M$ that
-is optimal in some sense. We propose that we optimize the Schatten 2-norm of the
-continuous-discrete imaging operator
+is optimal in some sense. We propose that we minimize the $\mbb{L}_2$ condition
+number of the continuous-to-discrete imaging operator---the ratio of the largest
+and smallest singular values of the matrix. We can interpret the condition
+number as the ``invertibility'' of the matrix.
+
+Optimizing the condition number will generate designs that are easily inverted,
+but the designs may estimate a small number of uninteresting parameters. For
+this reason we impose a rank constraint on the matrix. We require that
 \begin{align}
-  \mf{s}^* = \argmax{\mf{s} \in \mc{S}^M}||\mc{D}_{\mf{s}}\mc{H}_{cc}||_2. \label{eq:notime}
-\end{align}
-The Schatten $p$-norm is defined as the $\mbb{L}_p$ norm of the singular values
-of the operator, so the Schatten $2$-norm is a reasonable measure of the amount
-of information that the imaging system can pass. It favors sampling schemes that
-have many large singular values, so it will prefer sampling schemes that measure
-many orthogonal parameters of the object that are insensitive to noise.
-
-It's useful to interpret the Schatten $2$-norm by analyzing a spatial imaging
-system. The ``effective OTF'' that appears in many fluorescence microscopy
-papers (including Hari and Yicong's 2018 SIM review) is a specific example of a
-continuous singular value spectrum. We can calculate the Schatten $2$-norm by
-taking the effective OTF, squaring its value at each spatial frequency,
-integrating over the spatial frequencies, then taking the square root. The
-Schatten $2$-norm will be largest for imaging systems that have many singular
-values (a high spatial frequency bandwidth) that are large (we prefer effective
-OTFs that are large and constant over the bandwidth).
-
-Eq. \eqref{eq:notime} will optimize the number and size of the singular values
-without considering how interpretable the corresponding parameters are. One of
-our motivations for adding light-sheet tilting was to measure rotationally
-invariant parameters of the object which will be much more interpretable than
-rotationally variant parameters. To achieve this objective we need to measure at
-least the $\ell=0$ and $\ell = 2$ rotationally invariant subspaces---a
-6-dimensional subspace of $\mbb{L}_2(\mbb{S}^2)$. This will require at least 6
-measurements. To ensure that a sampling scheme has measured this rotationally
-invariant subspace, we require that
-\begin{align}
-  \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}) \geq 6 \label{eq:constraint}
+  \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}) \geq 6, \label{eq:constraint}
 \end{align}
@@
 that satisfy the constraint in Eq. \eqref{eq:constraint} by
-$\mc{Z} = \{\mf{s}\, |\, \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2})
-\geq 6\}$.
+$\mc{Z} = \{\mf{s}\, |\, \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c =
+  2}) \geq 6\}$. An optimal $M$-sample sampling scheme will be the solution of the optimization problem 
+\begin{align}
+  \mf{s}^* = \argmin{\mf{s} \in \mc{S}^M \cap \mc{Z}}\kappa(\mc{D}_{\mf{s}}\mc{H}_{cc}), \label{eq:notimekappa}
+\end{align}
+where $\kappa(A)$ denotes the $\mbb{L}_2$ condition number of $A$.
 
-The solutions of Eq. \eqref{eq:notime} will not necessarily satisfy Eq.
-\eqref{eq:constraint}, and simply adding an extra constraint to Eq.
-\eqref{eq:constraint} will not ensure that we are optimally measuring the
-parameters in the subspace that we want to measure. Instead, we propose an
-alternative optimization problem
-\begin{align}
-    \mf{s}_{\ell_c =2}^* = \argmax{\mf{s} \in \mc{S}^M\cap\mc{Z}}||\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}||_2,
-\end{align}
-which ensures that the objective function is independent of singular values that
-measure parameters outside of the objective subspace. Note that the set
-$\mc{S}^M\cap\mc{Z}$ will definitely be empty for $M \leq 6$, and we are not sure
-what value of $M$ will yield solutions.
+Earlier we mainly used the Schatten 2-norm of the continuous-discrete imaging
+operator---the root sum of squares of the singular values---as the objective
+function. This objective function resulted in useful designs, but the last
+singular value was usually small which led us to optimizing the condition
+number. We can interpret the Schatten 2-norm designs as the ``learn as much as
+we can about all parameters'' designs and the condition number designs as the
+``no parameter left behind'' designs.
+
+% Schatten 2-norm of the
+% continuous-discrete imaging operator
+% \begin{align}
+%   \mf{s}^* = \argmax{\mf{s} \in \mc{S}^M}||\mc{D}_{\mf{s}}\mc{H}_{cc}||_2. \label{eq:notime}
+% \end{align}
+% The Schatten $p$-norm is defined as the $\mbb{L}_p$ norm of the singular values
+% of the operator, so the Schatten $2$-norm is a reasonable measure of the amount
+% of information that the imaging system can pass. It favors sampling schemes that
+% have many large singular values, so it will prefer sampling schemes that measure
+% many orthogonal parameters of the object that are insensitive to noise.
+
+% It's useful to interpret the Schatten $2$-norm by analyzing a spatial imaging
+% system. The ``effective OTF'' that appears in many fluorescence microscopy
+% papers (including Hari and Yicong's 2018 SIM review) is a specific example of a
+% continuous singular value spectrum. We can calculate the Schatten $2$-norm by
+% taking the effective OTF, squaring its value at each spatial frequency,
+% integrating over the spatial frequencies, then taking the square root. The
+% Schatten $2$-norm will be largest for imaging systems that have many singular
+% values (a high spatial frequency bandwidth) that are large (we prefer effective
+% OTFs that are large and constant over the bandwidth).
+
+% Eq. \eqref{eq:notime} will optimize the number and size of the singular values
+% without considering how interpretable the corresponding parameters are. One of
+% our motivations for adding light-sheet tilting was to measure rotationally
+% invariant parameters of the object which will be much more interpretable than
+% rotationally variant parameters. To achieve this objective we need to measure at
+% least the $\ell=0$ and $\ell = 2$ rotationally invariant subspaces---a
+% 6-dimensional subspace of $\mbb{L}_2(\mbb{S}^2)$. This will require at least 6
+% measurements. To ensure that a sampling scheme has measured this rotationally
+% invariant subspace, we require that
+% \begin{align}
+%   \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}) \geq 6, \label{eq:constraint}
+% \end{align}
+% where $\mc{P}_{\ell_c=2}$ is a projection operator onto the $\ell=0$ and
+% $\ell=2$ subspace. For convenience we will denote the set of sampling schemes
+% that satisfy the constraint in Eq. \eqref{eq:constraint} by
+% $\mc{Z} = \{\mf{s}\, |\, \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2})
+% \geq 6\}$.
+
+% The solutions of Eq. \eqref{eq:notime} will not necessarily satisfy Eq.
+% \eqref{eq:constraint}, and simply adding an extra constraint to Eq.
+% \eqref{eq:constraint} will not ensure that we are optimally measuring the
+% parameters in the subspace that we want to measure. Instead, we propose an
+% alternative optimization problem
+% \begin{align}
+%     \mf{s}_{\ell_c =2}^* = \argmax{\mf{s} \in \mc{S}^M\cap\mc{Z}}||\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}||_2,
+% \end{align}
+% which ensures that the objective function is independent of singular values that
+% measure parameters outside of the objective subspace. Note that the set
+% $\mc{S}^M\cap\mc{Z}$ will definitely be empty for $M \leq 6$, and we are not sure
+% what value of $M$ will yield solutions.
 
 \section{Practical implementation details}
-The two optimization problems above are sufficient to propose optimal sampling
-schemes, but they lack many of the details required for an implementation. In
-this section I'll go through some of the practical work of converting the
-abstract forms into finite-dimensional optimization problems.
+The optimization problem above lacks many of the details required for an
+implementation. In this section I'll go through some of the practical work of
+converting the abstract form into a finite-dimensional optimization problem.
 
@@
 
-Next, we need a way to calculate the Schatten 2-norm efficiently. We could
-calculate the singular values of each $15\times 15$ matrix, but this would be
-slow. We can take a shortcut and replace the Schatten 2-norm with the Frobenius
-norm---the $\mbb{L}_2$ norm of the matrix entries. Note that this replacement is
-only valid for finite-dimensional representations of the operators.
+% Next, we need a way to calculate the Schatten 2-norm efficiently. We could
+% calculate the singular values of each $15\times 15$ matrix, but this would be
+% slow. We can take a shortcut and replace the Schatten 2-norm with the Frobenius
+% norm---the $\mbb{L}_2$ norm of the matrix entries. Note that this replacement is
+% only valid for finite-dimensional representations of the operators.
 
@@
 
-We will discretize the tilt angle into 5 angles
-$\delta \in \{-\Delta, -\Delta/2, 0,\Delta/2, \Delta\}$, and we will discretize
-the polarizer angle into 8 angles $\phi \in \{0,\pi/8,\dots,7\pi/8\}$. This means
-that a brute-force approach will need to search
-$(2\,\text{views}\times 5\,\text{tilts}\times 8\,\text{polarizer settings})^M$
-possible measurement schemes which becomes computationally infeasible for $M$
-larger than about 5 or 6.
+We will discretize the tilt angle into 3 angles
+$\delta \in \{-\Delta, 0, \Delta\}$, and we will discretize the polarizer angle
+into $P$ angles $\phi \in \{0,\pi/P,\dots,(P-1)\pi/P\}$. This means that a
+brute-force approach will need to search the number of ways to choose $M$
+elements from $2\,\,\text{views}\times 3\,\,\text{tilts}\times P\,\,\text{polarizer}$
+options = $\binom{6P}{M}$.
 
-To avoid a brute-force search we will use a simple hill-climbing algorithm. In
-words, we (1) start with an initial guess for each of the $3M$ parameters and
-evaluate the objective function, (2) increment and decrement the first parameter
-and move in the direction that improves the objective function, (3) repeat (2)
-for each parameter one by one, (4) repeat (3) and keep cycling parameters until
-no movement improves the objective function or a fixed number of objective
-function evaluations is reached. Although the algorithm is extremely coarse and
-provides no guarantees, it is simple to implement and it can be stopped at any
-time and will always return its best guess.
+My current implementation requires about 2 milliseconds per objective function
+evaluation, so a brute force search is feasible for $P=6$ and $M=6$ since
+$\binom{36}{6} \approx 2\e{6}$ evaluations will take about 2 hours.
 
-\section{Results}
+\section{Results}\label{sec:results}
+Figure 1--3 include several subfigures that we can use to compare the designs.
+
+In the \textbf{top left} subfigure we show a schematic of the angular design.
+Each arrow indicates a single polarized excitation direction and tilt angle. In
+the current diSPIM design we do not use any excitation arm tilting, so all 6
+arrows are centered on the optic axes (indicated by large black dots). The
+colors of the arrows match the small colored squares in the \textbf{top center}
+subfigure which indicate the point response functions for each measurement. The
+radius of each point response function indicates the size of the signal measured
+from a fluorophore oriented along that direction.
+
+In the \textbf{top right} subfigure we show an set of single direction
+reconstructions with the given design. We start by creating a uniformly oriented
+phantom for each of the 250 directions in the positive octant of the sphere
+indicated by \textcolor{green}{green} dots. Next, we simulate the imaging
+process, simulate Poisson noise with SNR = 20, reconstruct the phantom, then
+find maximum of the reconstructed ODF. We mark each reconstructed maximum with a
+\textcolor{red}{red} dot and connect each phantom/reconstruction pair with a
+black line.
+
+In the \textbf{center} subfigure we show the singular value spectrum of the
+imaging system with the singular vectors plotted on the $x$ axis. The singular
+vectors are orthogonal functions, so they necessarily have positive
+(\textcolor{red}{red}) and negative (\textcolor{blue}{blue}) components. In the
+top-right of the figure we show the Schatten 2-norm of the design, the condition
+number, and the rank.
+
+In the \textbf{bottom} subfigure we show the singular value spectrum of the
+imaging system after projecting onto the $\ell = 0, 2$ subspace with the associated
+Schatten 2-norm, condition number, and rank.
+
+\fig{../figures/custom-designs/3dispim.pdf}{1.0}{3-polarization diSPIM design.
+  See the top of Section \ref{sec:results} for the general caption. The current design
+  does not use any light sheet tilting, so the arrows in the schematic are
+  centered on the black dots. Although the 3-polarization diSPIM design measures
+  a 6-dimensional space (its rank is 6), the last singular value is very small
+  (1/22 of the maximum singular value) so it is effectively lost in the noise.
+  The 3-polarization diSPIM design only measures a 5-dimensional subspace of the
+  $\ell = 0, 2$ subspace, so the reconstructions suffer from significant blind
+  spots. The single direction reconstructions show that many directions are
+  reconstructed with errors larger than 30 degrees.}{3dispim}
+
+\fig{../figures/custom-designs/optimal-6pol.pdf}{1.0}{Optimal $M=6$, $P=3$
+  tilting diSPIM design. See the top of Section \ref{sec:results} for the general
+  caption. This design is the optimal $6$-measurement design when $3$ equally
+  spaced polarizer settings and light-sheet tilting are available. First,
+  collect the \textcolor{blue}{blue} samples by tilting the light sheet and
+  cycling through the three polarizer settings. Next, collect the
+  \textcolor{red}{red} samples from the other view by choosing the polarizer
+  setting that points towards \textcolor{blue}{blue} excitation axis and tilting
+  the excitation sheet both directions. Finally, collect the
+  \textcolor{green}{green} sample by changing the polarizer setting and exciting
+  along the optic axis. This design shows several advantages over our current
+  design: the smallest singular value is 1/9 the size of the largest singular
+  value, so we have a much better chance of recovering it from the noise; we
+  measure components from all 6 dimensions of the $\ell=0, 2$ subspace; and the
+  single direction reconstruction shows that we can reconstruct with errors less
+  than 15 degrees.}{33dispim}
+
+\fig{../figures/custom-designs/optimal-6pol-6choice.pdf}{1.0}{Optimal $P=6$
+  tilting diSPIM design. See the top of Section \ref{sec:results} for the general
+  caption. This design is the optimal $6$-measurement design when $6$ equally
+  spaced polarizer settings and light-sheet tilting are available. Compared to
+  the optimal $P=3$ design in Figure 2, the optimal $P=6$ design has a smallest
+  singular value that is 1/7 the size of the largest singular value, so it is
+  even less susceptible to corruption by noise. Interestingly, the singular
+  direction reconstruction looks worse for the $P=6$ design than the $P=3$
+  design. This isn't too troubling since we have optimized on the condition
+  number, not the single direction reconstruction. Although this design has a
+  slightly better condition number, it requires finer polarization alignment
+  than the $P=3$ design, it requires tilting on both arms, and it does not
+  provide a very large improvement. With these comments and the ``Min constraint''
+  in mind, I'm happy to recommend the $P=3$ design.}{36dispim}
 

### 2019-02-21 notes/2019-01-28-angular-optimize/summary/summary.tex
Latest angular notes with summary.

--- 2019-02-06 notes/2019-01-28-angular-optimize/report/report.tex
@@
 \begin{document}
-\title{\vspace{-2.5em} Optimizing angular diSPIM measurements\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
+\title{\vspace{-2.5em} Polarized tilting diSPIM design recommendation\vspace{-1em}} % \author{Talon Chandler, Min Guo, Hari
   % Shroff, Rudolf Oldenbourg, Patrick La Rivi\`ere}
@@
 
-\section{Introduction}
-Our goal in these notes is to find optimal angular sampling schemes for the
-diSPIM with light-sheet tilting. We review the continuous angular forward model,
-find the sampling schemes available to us, choose an objective function to
-optimize, then search through the sampling schemes.
+Here we recommend a polarized tilting diSPIM design and compare the design to
+earlier non-tilting designs. These notes summarize two note sets
+\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-12-10-angular-svd/report/report.pdf}{here}
+and
+\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2019-01-28-angular-optimize/report/report.pdf}{here}.
 
-\section{Continuous forward model}
-We briefly review the continuous angular forward model---see the
-\href{https://github.com/talonchandler/polharmonic/blob/master/notes/2018-12-10-angular-svd/report/report.pdf}{previous
-  notes} for a more detailed discussion. We can write the
-continuous-to-continuous forward model in the form
-\begin{align}
-  \mb{g}_c = \mc{H}_{cc}\mb{f}_c,\label{eq:cc}
-\end{align}
-where $\mb{f}_c \in \mbb{L}_2(\mbb{S}^2)$ is the angular dipole density,
-$\mb{g}_c \in \mbb{L}_2(\mbb{S}^2\times \mbb{S}^1)$ is the continuous irradiance
-data taken by varying the detection optical axis (the $\mbb{S}^2$ dimension) and
-the illumination polarizer (the $\mbb{S}^1$ dimension), and $\mc{H}_{cc}$ is a
-linear continuous-to-continuous Hilbert-space operator between these spaces.
+Our goal was to find a design that can optimally measure angular distributions
+of fluorophores given the following requirements: (1) the design must meet
+practical experimental constraints---we can only recommend diSPIM tilting angles
+up to 15${}^{\circ}$ and the polarizer settings must be easy to align, (2) the
+design must measure all fluorophore orientations in 3D without major blind spots, and
+(3) the design should minimize the number of measurements. In the previous notes
+we formulated this design problem as an optimization problem. We chose to
+optimize the condition number of the system matrix---the ``invertibility'' of
+the reconstruction problem---subject to the constraints above.
 
-If we choose a delta-function basis for both object and data space then we can
-rewrite Eq. \eqref{eq:cc} as 
-\begin{align}
-  g(\sd, \pp) = \ints{2}d\so\, h(\sd,\pp;\so)f(\so),\label{eq:fwd}
-\end{align}
-where $\so \in \mbb{S}^2$ is the object angular coordinate, $\sd \in \mbb{S}^2$
-is the detection optical axis coordinate, $\pp \in \mbb{S}^1$ is the polarizer
-coordinate, and $h(\sd,\pp;\so)$ is the kernel of the integral transform. We can
-separate the kernel into an excitation and detection part since these processes
-are incoherent
-\begin{align}
-  h(\sd, \pp;\so) = h^{\text{exc}}(\pp;\so)h^{\text{det}}(\sd;\so). \label{eq:kern}
-\end{align}
-The excitation kernel is straightforward---the squared dot product of the
-polarizer orientation $\pp$ with the object angular coordinate $\so$
-\begin{align}
-  h^{\text{exc}}(\pp\cdot\so) \propto (\pp\cdot\so)^2. \label{eq:exckern}
-\end{align}
-The detection kernel requires more care since we are collecting light over the
-NA of the objective. In the previous notes we started with the power along a
-single ray then integrated over the aperture to find that the detection kernel is
-\begin{align}
-  h^{\text{det}}(\sd\cdot\so) \propto (1 - \sqrt{\cos\alpha})P_0(\sd\cdot\so) + \frac{1}{5}\left[\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right]P_2(\sd\cdot\so),
-\end{align}
-where $\text{NA} = n_o\sin\alpha$, and $P_{\ell}(x)$ are the Legendre
-polynomials.
+Figures 1--3 summarize three angular designs: our recommended design, the
+current 3-polarization diSPIM without tilting, and a single-view design. In each
+\textbf{top left} subfigure we show a schematic of the angular design. Each
+arrow indicates a polarizer orientation and the center of each arrow indicates
+the excitation optical axis (the tilt angle).
 
-We can rewrite the mapping in Eq. \eqref{eq:cc} in an object-space spherical
-harmonic basis as
-\begin{align}
-  g(\sd, \pp) = \sum_{\ell m}H_\ell^m(\sd, \pp)F_\ell^m,\label{eq:fwdsh}
-\end{align}
-where $F_\ell^m$ is the angular dipole spectrum given by 
-\begin{align}
-  F_\ell^m = \int_{\mbb{S}^2}d\so\, f(\so)Y_\ell^{m*}(\so),
-\end{align}
-and $H_\ell^m(\sd, \pp)$ is the kernel in this basis given by
-\begin{align}
-  H_\ell^m(\sd, \pp) &= \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd),\label{eq:triple4}\\
-    H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
-    H_{\ell''}^{m'',\text{det}}(\sd) &\propto Y_{\ell''}^{m''*}(\sd)\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{1}{4}\sqrt{\cos\alpha}(7-3\cos(2\alpha)) - 1\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
-\end{align}
-with the Gaunt coefficients given by 
-\begin{align}
-  G_{\ell,\ell',\ell''}^{m,m',m''} = \ints{2}d\so\, Y_\ell^{m}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).
-\end{align}
+In each \textbf{top right} subfigure we show a set of single direction
+reconstructions with the design. We start by creating a uniformly oriented
+phantom for each of the 250 directions in the positive octant of the sphere
+indicated by \textcolor{green}{green dots}. Next, we simulate the imaging
+process, simulate Poisson noise with SNR = 20, reconstruct the phantom, then
+find the maximum of the reconstructed ODF. We mark each reconstructed maximum with a
+\textcolor{red}{red dot} and connect each phantom/reconstruction pair with a
+black line. These figures show the ``blind spots'' of the design---long lines
+indicate a large angular error.
 
-It's useful to compare Eq. \eqref{eq:fwd} to Eq. \eqref{eq:fwdsh}---in a delta
-function basis we need to compute an angular integral, while in the object-space
-spherical harmonics basis the kernel has a finite number of terms so we can
-compute it exactly.
+In each \textbf{bottom} subfigure we show the singular value spectrum of the
+imaging system with the singular functions plotted along the $x$ axis. The
+singular function are mutually orthogonal functions, so they necessarily have
+\textcolor{red}{positive (red)} and \textcolor{blue}{negative (blue)}
+components. The singular value spectrum is a generalized version of the familiar
+OTF. In an OTF the $x$ axis is always implicitly labeled with complex
+exponentials, while here the $x$ axis is explicitly labeled with angular
+functions.
 
-It's also useful to compare Eq. \eqref{eq:kern} to Eq. \eqref{eq:triple4}---in a
-delta function basis the kernel is the product of the excitation and detection
-kernels, while in the object-space spherical harmonic basis the kernel is a
-generalized convolution of the excitation and detection kernels.
+\begin{figure}[p]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+ \includegraphics[width = 0.7\textwidth]{../figures/summary/optimal-6pol.pdf}
+ \vspace{-1.5em}
+ \caption{Our recommendation for a 6-measurement polarized tilting diSPIM
+   design. First, collect the \textcolor{blue}{blue} samples by tilting the
+   light sheet and cycling through the three polarizer settings (0${}^{\circ}$,
+   60${}^{\circ}$, 120${}^{\circ}$). Next, collect the \textcolor{red}{red}
+   samples from the other view by choosing the polarizer setting that points
+   towards the \textcolor{blue}{blue} excitation axis (60${}^{\circ}$) then
+   tilting the excitation sheet both directions. Finally, collect the
+   \textcolor{green}{green} sample by changing the polarizer setting to
+   120${}^{\circ}$ and exciting along the optic axis. This design requires 3 equally spaced polarizer settings and 3 equally spaced tilt settings on one arm.\\ \\
+   The single direction reconstruction shows that the angular error introduced
+   by this design is $\approx 15^{\circ}$. Also, the singular value spectrum
+   shows that the last singular value is $\approx 0.15$, so it will not be lost
+   in the
+   noise at SNR = 20.\\ \\
+   Note that the order of collection (\textcolor{blue}{blue},
+   \textcolor{red}{red}, \textcolor{green}{green}) is not important---any order
+   will work. Also, the design shows 15${}^{\circ}$ tilt angles, but any tilt
+   angle will work. Larger tilt angles are better conditioned, so we recommend
+   using all of the available tilt.\\ \\
+   This design has the largest condition number for an instrument with 6
+   measurements and 3 equally spaced polarization settings. We originally tried
+   optimizing the root sum of squares of the singular values (the Schatten
+   2-norm) and these optimizations resulted in intuitive symmetric
+   designs---equally spaced polarizers with equally spaced tilts for both views.
+   However, these designs performed poorly because the last singular value was
+   very small and lost in the noise. Optimizing the condition number leads to
+   less intuitive designs with better performance in noisy conditions.}
+ \label{6pol}
+\end{figure}
 
-\section{Sampling schemes}
-We can write the sampling operation as a continuous-to-discrete Hilbert space
-operator $\mc{D}_w$
-\begin{align}
-  \mb{g}_d = \mc{D}_w\mb{g}_c = \mc{D}_w\mc{H}_{cc}\mb{f}_c. 
-\end{align}
-We can write the sampling operation in a delta function basis as
-\begin{align}
-  g_m = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_m(\sd,\pp)g(\sd,\pp).
-\end{align}
-where $g_m$ is the $m$th discrete measurement and $w_m(\sd,\pp)$ is the $m$th
-sampling aperture. For now we will restrict ourselves to delta-function sampling
-apertures
-\begin{align}
-  w_m(\sd,\pp) = \delta(\mh{s}_{d,m} - \sd)\delta(\mh{p}_{m} - \pp),
-\end{align}
-where $\mh{s}_{d,m}$ and $\mh{p}_{m}$ are the $m$th sampling points. This
-restriction means that we will leave the polarizer setting and tilt angle fixed
-during each volume acquisition. We could consider scanning the polarizer
-setting and tilt angle in the future for faster acquisitions, but I think these
-sampling schemes will always decrease ``angular SNR''.
+\begin{figure}[H]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+ \includegraphics[width = 0.55\textwidth]{../figures/summary/3dispim.pdf}
+ \vspace{-1.55em}
+ \caption{Current 3-polarization diSPIM design without tilting. The current
+   design introduces errors as large as 30${}^{\circ}$ for single-direction
+   reconstructions, and the last singular value is very small so we effectively
+   measure a 5-dimensional space. Furthermore, this design has a blind spot in
+   the $\ell=2$ band---see previous notes for more details. }
+ \label{6pol}
+\end{figure}
 
-So far we've formulated everything quite generally and haven't made any
-reference to the diSPIM geometry. Now we find the constraints that the diSPIM
-geometry places on the values of $\mh{s}_{d,m}$ and $\mh{p}_{m}$. If we define
-the $\mh{x}$ and $\mh{z}$ axes as the optical axes of the two objective then we
-have the following sampling constraint
-\begin{align}
-\mh{s}_{d,m} \in \{\mh{x}, \mh{z}\}.  \label{eq:first}
-\end{align}
-In words, this constraint says that we can only detect along one of two discrete
-and orthogonal axes.
-
-Next, we constrain the polarizer sampling points $\mh{p}_m$. We introduce a
-variable $\mh{s}_{e,m}$ to denote the excitation optical axis for the $m$th
-measurement. This variable does not affect the forward model (we've formulated
-in terms of $\pp$ only on the excitation side), but it will allow us to
-conveniently constrain $\pp$. First, we constrain the excitation optical axis to
-be perpendicular to the detection optical axis
-\begin{align}
-  \mh{s}_{e,m} \cdot \mh{s}_{d,m} = 0.
-\end{align}
-This is a fairly loose constraint, but it ensures that the light sheet is in
-focus across the field of view.
-
-Next, we constrain the excitation optical axis to within the available tilt
-angles of the instrument. If we use $\mc{R}$ to denote an ``axis swapping
-operator'' ($\mc{R}(\mh{z}) = \mh{x}$ and $\mc{R}(\mh{x}) = \mh{z}$), then the tilting
-constraint can be written as
-\begin{align}
-  \mh{s}_{e,m} \cdot \mc{R}(\mh{s}_{d,m}) \leq \Delta,
-\end{align}
-where $\Delta$ is the maximum tilt angle. For the current instrument $\Delta = 15^{\circ} = \pi/12$.
-
-Finally, we constrain the excitation polarization $\pp_m$ to be perpendicular to
-the excitation optical axis
-\begin{align}
-  \mh{s}_{e,m} \cdot \pp_m = 0.  \label{eq:final}
-\end{align}
-For convenience we will denote individual sampling points with $\mf{s}_m$ =
-($\pp_m$, $\mh{s}_{d,m}$), and we will denote the set of all sampling points
-$\mf{s}_m$ that satisfy Eqs. \eqref{eq:first}--\eqref{eq:final} by $\mc{S}$.
-With this notation we can denote a complete sampling scheme with $M$ samples
-by $\mf{s} \in \mc{S}^M$ ($M$ copies of the set $\mc{S}^M$).
-
-\section{Objective functions}
-Our goal is to choose an $M$-sample sampling scheme $\mf{s} \in \mc{S}^M$ that
-is optimal in some sense. We propose that we optimize the Schatten 2-norm of the
-continuous-discrete imaging operator
-\begin{align}
-  \mf{s}^* = \argmax{\mf{s} \in \mc{S}^M}||\mc{D}_{\mf{s}}\mc{H}_{cc}||_2. \label{eq:notime}
-\end{align}
-The Schatten $p$-norm is defined as the $\mbb{L}_p$ norm of the singular values
-of the operator, so the Schatten $2$-norm is a reasonable measure of the amount
-of information that the imaging system can pass. It favors sampling schemes that
-have many large singular values, so it will prefer sampling schemes that measure
-many orthogonal parameters of the object that are insensitive to noise.
-
-It's useful to interpret the Schatten $2$-norm by analyzing a spatial imaging
-system. The ``effective OTF'' that appears in many fluorescence microscopy
-papers (including Hari and Yicong's 2018 SIM review) is a specific example of a
-continuous singular value spectrum. We can calculate the Schatten $2$-norm by
-taking the effective OTF, squaring its value at each spatial frequency,
-integrating over the spatial frequencies, then taking the square root. The
-Schatten $2$-norm will be largest for imaging systems that have many singular
-values (a high spatial frequency bandwidth) that are large (we prefer effective
-OTFs that are large and constant over the bandwidth).
-
-Eq. \eqref{eq:notime} will optimize the number and size of the singular values
-without considering how interpretable the corresponding parameters are. One of
-our motivations for adding light-sheet tilting was to measure rotationally
-invariant parameters of the object which will be much more interpretable than
-rotationally variant parameters. To achieve this objective we need to measure at
-least the $\ell=0$ and $\ell = 2$ rotationally invariant subspaces---a
-6-dimensional subspace of $\mbb{L}_2(\mbb{S}^2)$. This will require at least 6
-measurements. To ensure that a sampling scheme has measured this rotationally
-invariant subspace, we require that
-\begin{align}
-  \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}) \geq 6 \label{eq:constraint}
-\end{align}
-where $\mc{P}_{\ell_c=2}$ is a projection operator onto the $\ell=0$ and
-$\ell=2$ subspace. For convenience we will denote the set of sampling schemes
-that satisfy the constraint in Eq. \eqref{eq:constraint} by
-$\mc{Z} = \{\mf{s}\, |\, \text{rank}(\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2})
-\geq 6\}$.
-
-The solutions of Eq. \eqref{eq:notime} will not necessarily satisfy Eq.
-\eqref{eq:constraint}, and simply adding an extra constraint to Eq.
-\eqref{eq:constraint} will not ensure that we are optimally measuring the
-parameters in the subspace that we want to measure. Instead, we propose an
-alternative optimization problem
-\begin{align}
-    \mf{s}_{\ell_c =2}^* = \argmax{\mf{s} \in \mc{S}^M\cap\mc{Z}}||\mc{D}_{\mf{s}}\mc{H}_{cc}\mc{P}_{\ell_c = 2}||_2,
-\end{align}
-which ensures that the objective function is independent of singular values that
-measure parameters outside of the objective subspace. Note that the set
-$\mc{S}^M\cap\mc{Z}$ will definitely be empty for $M \leq 6$, and we are not sure
-what value of $M$ will yield solutions.
-
-\section{Practical implementation details}
-The two optimization problems above are sufficient to propose optimal sampling
-schemes, but they lack many of the details required for an implementation. In
-this section I'll go through some of the practical work of converting the
-abstract forms into finite-dimensional optimization problems.
-
-First, we need to choose a basis and find matrix representations for the
-operators $\mc{D}_{\mf{s}}$ and $\mc{H}_{cc}$. At first glance this seems
-difficult---$\mc{D}_{\mf{s}}$ is a CD operator and $\mc{H}_{cc}$ is a CC
-operator so they do not have finite-dimensional matrix representations
-individually. Luckily, the combination $\mc{D}_{\mf{s}} \mc{H}_{cc}$ is a
-band-limited compact operator, so it has a finite-dimensional representation as
-a $15\times M$ matrix that we will call $\ms{H}$. The entries of this matrix are
-given by
-\begin{align}
-  \ms{H}_{jm} = H_j(\mh{s}_{d,m}, \mh{p}_m),
-\end{align}
-where $j$ is a single index over the spherical harmonics, and Eq.
-\ref{eq:triple4} shows us how to calculate the entries in terms
-of the excitation and detection kernels.
-
-Next, we need a matrix representation of $\mc{P}_{\ell_c=2}$. This is simple in
-a spherical harmonics basis---we create a 15$\times$15 matrix called
-$\ms{P}$, fill the first six diagonal elements with ones, and place zeroes
-elsewhere
-\begin{align}
-  \ms{P}_{ij} = \delta_{ij}, \qquad i,j = 0,1,2,3,4,5.
-\end{align}
-
-Next, we need a way to calculate the Schatten 2-norm efficiently. We could
-calculate the singular values of each $15\times 15$ matrix, but this would be
-slow. We can take a shortcut and replace the Schatten 2-norm with the Frobenius
-norm---the $\mbb{L}_2$ norm of the matrix entries. Note that this replacement is
-only valid for finite-dimensional representations of the operators.
-
-Finally, we need an efficient set of scalar parameters to search through the set
-of sampling schemes $\mc{S}^M$. We will parameterize each sample with a discrete
-view index $v \in \{0, 1\}$ to indicate the detection axis, a tilt angle defined
-from the nominal excitation axis $\delta \in [-\Delta, \Delta]$, and a polarizer
-angle defined from the detection axis $\phi \in [0, 2\pi)$.
-
-This parameter space is challenging to search because it is continuous in some
-parameters and discrete in others. It's not clear if it's possible to take
-derivatives with respect to the continuous parameters, so as a first pass we
-will discretize the continuous parameters and use a search heuristic.
-Discretization has the advantage of providing solutions that will be easier to
-implement experimentally since we can constrain our solutions to sampling
-schemes that are easy to align, but of course we can't guarantee that our
-sampling scheme solutions will be globally optimal.
-
-We will discretize the tilt angle into 5 angles
-$\delta \in \{-\Delta, -\Delta/2, 0,\Delta/2, \Delta\}$, and we will discretize
-the polarizer angle into 8 angles $\phi \in \{0,\pi/8,\dots,7\pi/8\}$. This means
-that a brute-force approach will need to search
-$(2\,\text{views}\times 5\,\text{tilts}\times 8\,\text{polarizer settings})^M$
-possible measurement schemes which becomes computationally infeasible for $M$
-larger than about 5 or 6.
-
-To avoid a brute-force search we will use a simple hill-climbing algorithm. In
-words, we (1) start with an initial guess for each of the $3M$ parameters and
-evaluate the objective function, (2) increment and decrement the first parameter
-and move in the direction that improves the objective function, (3) repeat (2)
-for each parameter one by one, (4) repeat (3) and keep cycling parameters until
-no movement improves the objective function or a fixed number of objective
-function evaluations is reached. Although the algorithm is extremely coarse and
-provides no guarantees, it is simple to implement and it can be stopped at any
-time and will always return its best guess.
-
-\section{Results}
+\begin{figure}[H]
+ \captionsetup{width=1.0\linewidth}
+ \centering
+ \includegraphics[width = 0.55\textwidth]{../figures/summary/single.pdf}
+ \vspace{-3em}
+ \caption{Single-view PolScope design. This design ``projects'' single-direction
+   reconstructions into the transverse plane of the microscope and measures a
+   3-dimensional angular space.}
+ \label{6pol}
+\end{figure}
 

### 2019-02-28 notes/2019-01-28-angular-optimize/report/report.tex
Patrick's angular diSPIM optimization edits.

@@
     H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
-    H_{\ell''}^{m'',\text{det}}(\sd) &\propto \frac{Y_{\ell''}^{m''*}(\sd)}{1 - \cos\alpha}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
+    H_{\ell''}^{m'',\text{det}}(\sd) &\propto \frac{Y_{\ell''}^{m''*}(\sd)}{1 - \cos\alpha}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right],\label{eq:dipdet}
 \end{align}
@@
 It's useful to compare Eq. \eqref{eq:fwd} to Eq. \eqref{eq:fwdsh}---in a delta
-function basis we need to compute an angular integral, while in the object-space
-spherical harmonics basis the kernel has a finite number of terms so we can
-compute it exactly.
+function basis we need to compute a continuous angular integral (in general this
+requires an approximate Riemann sum), while in the object-space spherical
+harmonics basis the kernel has a finite number of terms so we can compute it
+exactly.
 
@@
 restriction means that we will leave the polarizer setting and tilt angle fixed
-during each volume acquisition. We could consider scanning the polarizer
-setting and tilt angle in the future for faster acquisitions, but I think these
-sampling schemes will always decrease ``angular SNR''.
+during each volume acquisition. We could consider scanning the polarizer setting
+and tilt angle while acquiring data in the future for faster imaging, but I
+think these sampling schemes will always decrease ``angular SNR''.
 
@@
 \end{align}
-This is a fairly loose constraint, but it ensures that the light sheet is in
-focus across the field of view.
+This constraint ensures that the light sheet is in focus across the field of
+view.
 
@@
 function. This objective function resulted in useful designs, but the last
-singular value was usually small which led us to optimizing the condition
-number. We can interpret the Schatten 2-norm designs as the ``learn as much as
+singular value was usually small which led us to optimizing the condition number
+instead. We can interpret the Schatten 2-norm designs as the ``learn as much as
 we can about all parameters'' designs and the condition number designs as the
@@
 
-In the \textbf{top right} subfigure we show an set of single direction
+In the \textbf{top right} subfigure we show a set of single direction
 reconstructions with the given design. We start by creating a uniformly oriented

### 2019-07-19 papers/three-dimensions/paper/paper.tex
Early version of three-dimensional high-aperture paper

\documentclass[]{osa-article}

%% Select the journal you're submitting to
%% oe, boe, ome, osac, osajournal
\journal{osajournal}
% Key:
% Express journals must have the correct journal selected:
% {oe} Optics Express
% {boe} Biomedical Optics Express
% {ome} Optical Material Express
% {osac} OSAC Continuum
% Other OSA journals may use:
% {osajournal} Applied Optics, Advances in Optics and Photonics, Journal of the Optical Society of America A/B, Optics Letters, Optica, Photonics Research

% Uncomment if submitting to Photonics Research.
% ONLY APPLICABLE FOR \journal{osajournal}
% \setprjcopyright

% Set the article type
\articletype{Research Article}
% Note that article type is not required for Express journals (OE, BOE, OME and OSAC)

% Talon's custom libraries
\usepackage{empheq}
\usepackage{bm}
\usepackage[normalem]{ulem}
\usepackage{booktabs}
\usepackage{upgreek}

% Talon's custom commands
\setlength\arraycolsep{1.5pt}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\newcommand{\tensor}[1]{\overset{\text{\tiny$\leftrightarrow$}}{\mb{#1}}}
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\msf}[1]{\mathsf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\boldsymbol{\mathfrak{r}}_o}
\providecommand{\rs}{\boldsymbol{\mathfrak{r}}_s}
\newcommand{\mypar}{\parallel}
\providecommand{\ropar}{r_o^{\mypar}}
\providecommand{\roperp}{\mathbf{r}_o^{\bot}}
\providecommand{\rspar}{r_s^{\mypar}}
\providecommand{\rsperp}{\mathbf{r}_s^{\bot}}
\providecommand{\rppar}{r_p^{\mypar}}
\providecommand{\rpperp}{\mathbf{r}_p^{\bot}}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rp}{\mathbf{r}_p}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bv}{\boldsymbol{\mathfrak{v}}}
\providecommand{\bvperp}{\bs{\nu}^{\bot}}
\providecommand{\bvpar}{\nu^{\parallel}}
\providecommand{\bt}{\bs{\uptau}}
\providecommand{\btperp}{\bs{\tau}^{\bot}}
\providecommand{\btpar}{\tau^{\mypar}}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\providecommand{\lmsum}{\sum_{\ell=0}^\infty\sum_{m=-\ell}^{\ell}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\providecommand{\tb}[1]{\textcolor{blue}{#1}}
\providecommand{\eqp}{\stackrel{(p)}{=}}
\providecommand{\propp}{\stackrel{(p)}{\propto}}

\providecommand{\add}[1]{{\color{blue}#1}}
% \DeclareFontFamily{OT1}{pzc}{}
% \DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
% \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\eqname}[1]{\tag*{#1}}
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

\begin{document}

\title{Spatio-angular fluorescence microscopy\\ III. Three-dimensional high-aperture 4f imaging}

\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{3} and Patrick La Rivi\`ere\authormark{1,3}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
  \authormark{2}Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering, National Institutes of Health, Bethesda, Maryland 20892, USA\\
  \authormark{3}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA}

\email{\authormark{*}talonchandler@talonchandler.com} %% email address is required

\begin{abstract*}
  TODO
\end{abstract*}

\section{Introduction}
\add{Patrick: Key references for comparison are sheppard1994} \cite{sheppard1994} \add{and arnison2002} \cite{arnison2002}.\\

\noindent Skeleton literature review ahead. \\

\noindent First and second papers transfer functions for dipoles \cite{chandler2019a, chandler2019b}\\

\noindent First 3D pupil function: \cite{mccutchen1964}\\
First paraxial 3D transfer function: \cite{frieden1967}\\
First defocused transfer functions: \cite{stokseth1969}\\
Interpretation of 3D transfer function: \cite{sheppard1989}\\
First high-aperture monopole transfer function: \cite{sheppard1994}\\
Vectorial 3D transfer function: \cite{sheppard1997a, philip1999, arnison2002, schonle2002}\\
Brief mention of dipoles and vectorial 3d transfer functions \cite{sheppard1997b, schonle2002}\\

\noindent PSF of single fixed dipole radiator \cite{sheppard1997b, nov2006, sick2000, bohmer2003, patra2004, toprak2006, backer2014, khadir2019}\\
Images/PSFs of rotating dipoles: \cite{lew2013, backlund2014, backer2015, stallinga2015, backer2019}\\
Orientation induced localization biases: \cite{engelhardt2011, stallinga2012, backlund2014}\\
3D angular transfer function approaches that use the second moments instead of the spherical harmonics \cite{aguet2009a, backer2014, brasselet2011, zhang2018a, zhang2018b}\\

\section{Theory}
\subsection{Comments on units}
Variants of $\nu$ and $\tau$ denote spatial frequencies with units
$\text{m}^{-1}$.

\noindent Variants of $r$, $f$, and $\lambda$ denote distances with units $\text{m}^{+1}$.

\noindent Variants of $\theta$, $\phi$, and $\beta$ denote unitless angles.

\noindent Boldface gothic symbols denote 3D vectors $[\ro] = \text{m}^{+3}$, and boldface roman symbols denote 2D vectors $[\btperp] = \text{m}^{-2}$.

\noindent Delta functions have inverse units of the argument $[\delta(\ro)] = \text{m}^{-3}$.

\noindent \add{I'm having some difficulty getting units to agree in section 2.2.3, but section 3 and the appendix are fairly consistent.}

\subsection{Three-dimensional monopole transfer functions}
\subsubsection{Monopole transfer functions}
Monopole point spread function
\begin{align}
  g(\rd) = \int_{\mbb{R}}d\ropar\int_{\mbb{R}^2}d\roperp\, h(\rd - \roperp, \ropar)f(\ro),
\end{align}
We can rewrite as 
\begin{align}
  G(\bvperp) = \int_{\mbb{R}}d\bvpar\, H(\bv)F(\bv),
\end{align}
where
\begin{align}
  G(\bvperp) = \int_{\mbb{R}^2}d\mb{r}^{\perp}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bvperp),
\end{align}
\begin{align}
  H(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, h(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv),
\end{align}
and
\begin{align}
  F(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, f(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv).
\end{align}

\begin{figure}
  \centering
  \includegraphics[scale=1.0]{../figures/monopole-block/monopole-block.pdf}
  \caption{
    The mapping between the object and data space of a monopole fluorescence microscope can be computed in two different bases---a delta function basis and a complex exponential basis. The change of basis can be computed with $n$-dimensional Fourier transforms denoted $\mathcal{F}_{\mbb{R}^n}$. Gray highlighting indicates which part of each expression is being named.
  }
  \label{fig:monopole-block}
\end{figure}

\subsubsection{Monopole coherent transfer functions}
\begin{align}
  |c(\rd - \roperp, \ropar)|^2 = h(\rd - \roperp, \ropar)
\end{align}
\begin{align}
  H(\bv) = \int_{\mbb{R}^3}d\bt\,C(\bt)C^*(\bt - \bv)
\end{align}
\begin{align}
  C(\bt) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, c(\bs{\mf{r}})\,\text{exp}(-2\pi i\bs{\mf{r}}\cdot\bt).\label{eq:monoctf}
\end{align}
This implies that the three-dimensional coherent transfer function is a scaled pupil function on a spherical shell.

\begin{figure}
  \centering
\includegraphics[scale=1.0]{../figures/monopole-transfer-functions/monopole-transfer-functions.pdf}
  \caption{
    The monopole transfer functions are related by a two-dimensional Fourier transform (right column). The coherent monopole transfer functions (left column) can be used to simplify the calculation of the remaining transfer functions.
  }
  \label{fig:monopole-transfer-functions}
\end{figure}

\subsubsection{Monopole pupil functions}
% First, consider the field created at $\rs$ by a monopole at $\ro$ 
% \begin{align}
%   U_s(\rs, \ro) \propto \frac{\text{exp}[2\pi i\nu_m|\rs - \ro|]}{|\rs - \ro|},
% \end{align}
% where $\nu_m = n_o/\lambda$. For monopoles near the origin we can find the fields on the Gaussian reference sphere of an objectives lens with focal length $f_0 \gg |\ro|$ by applying the approximation $|\rs - \ro| \approx |\rs| - \rs\cdot\ro/|\rs|$ and dropping second-order amplitude and constant phase terms
% \begin{align}
%   U_s(\rs, \ro) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rs\cdot\ro)/f_0].
% \end{align}
% Next, we expand the coordinates into transverse and axial components
% \begin{align}
%   U_s(\rs, \ro) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rsperp\cdot\roperp + \rspar\ropar)/f_0],
% \end{align}
% then rewrite in pupil coordinates using the relationships $\rsperp = \rpperp$ and $\rspar = \sqrt{f_0^2 - |\rppar|^2}$
% \begin{align}
%   U_p(\rpperp, \roperp, \ropar) \propto \frac{1}{f_0}\text{exp}\left[-2\pi i\nu_m\left(\rpperp\cdot\roperp + \rspar\sqrt{f_0^2 - |\roperp|^2}\right)/f_0\right].
% \end{align}
\add{Patrick: This section follows section 2A in the second paper \cite{chandler2019b} fairly closely with modifications for 3D.}

We can write the field in the pupil plane at point $\rpperp$ due to a monopole at $\ro = (\roperp, \ropar)$ as
\begin{align}
  U_p(\rpperp, \roperp, \ropar) \propto p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right],
\end{align}
where $p_d(\rpperp, \ropar)$ is the \textit{defocused monopole pupil function}  
\begin{align}
  p_d(\rpperp, \ropar) = p(\rpperp)\, \text{exp}\left[-2\pi i\ropar\nu_m\sqrt{1 - (|\rpperp|/f_0)^2}\right],
\end{align}
and $p(\rpperp)$ is the usual pupil function which can be used to model angular cutoff, apodization, or aberrations.

Since the second lens is paraxial, we can model the relationship between the field in the pupil plane and the field on the detector with a scaled Fourier transform
\begin{align}
  U_d(\rd', \roperp, \ropar) \propto \int_{\mbb{R}^2}d\rpperp\,p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1}\rpperp\cdot\rd'\right].
\end{align}

If we define $P(\btperp, \ropar)$ as the two-dimensional transverse Fourier transform of the defocused pupil function
\begin{align}
  P_d(\btperp, \ropar) = \int_{\mbb{R}^2}d\rpperp\, p_d(\rpperp, \ropar)\,\text{exp}(-2\pi i \rpperp\cdot\btperp),\label{eq:pupilF}
\end{align}
then we can rewrite the field on the detector as
\begin{align}
  U_d(\rd', \roperp, \ropar) \propto P\left(\frac{n_0}{\lambda f_0}\roperp + \frac{n_1}{\lambda f_1}\rd', \ropar\right).
\end{align}
After rewriting in terms of the magnification $m = -\frac{f_1 n_0}{f_0 n_1}$, demagnifying the coordinates with $\rd = \rd'/m$, and demagnifying the irradiance with $h(\rd - \roperp, \ropar) \propto h'(m[\rd - \roperp], \ropar) $, we find the defocused monopole point spread function is related to the Fourier transform of the defocused monopole pupil function by 
\begin{align}
  h(\rd-\roperp, \ropar) \propto \left|P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right)\right|^2.
\end{align}
The monopole point spread function is the absolute square of the monopole coherent spread function so
\begin{align}
  c(\rd - \roperp, \ropar) \propto P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right). \label{eq:monocsf}
\end{align}
Our final task is to calculate the monopole coherent transfer function by plugging Eq. \eqref{eq:monocsf} into Eq. \eqref{eq:monoctf} which yields
\begin{align}
  C(\bt) = \int_{\mbb{R}}dr^{\mypar}\int_{\mbb{R}^2}d\mb{r}^{\bot}\, P\left(-\frac{n_0}{\lambda f_0}\mb{r}^{\bot}, r^{\mypar}\right)\,\text{exp}(-2\pi i[\mb{r}^{\bot}\cdot\btperp + r^{\mypar}\btpar]).
\end{align}
Using Eq. \eqref{eq:pupilF} to simplify the transverse integral yields
\begin{align}
  C(\bt) \propto p\left(\frac{\lambda f_0}{n_0}\btperp\right) \int_{\mbb{R}}d r^{\mypar} \,\text{exp}\left(-2\pi i r^{\mypar}\sqrt{\nu_m - |\btperp|^2}\right)\,\text{exp}(-2\pi i r^{\mypar}\btpar)
\end{align}
Finally, we use the Fourier shift theorem to evaluate the axial integral to find that 
\begin{align}
  C(\bt) \propto p\left(\frac{\lambda f_0}{n_0}\btperp\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right).\label{eq:monoctf}
\end{align}

% \subsection{Three-dimensional dipole transfer functions}
% \subsubsection{Dipole transfer functions}
% \begin{figure}
%   \hspace{-6em}
%   \includegraphics[scale=1.0]{../figures/dipole-block/dipole-block.pdf}
%   \caption{
%     % The mapping between the object space and data space of a dipole imaging system can be computed in four different bases---a delta function basis, a complex-exponential/angular-delta basis, a spatial-delta/spherical-harmonic basis, and a complex-exponential/spherical-harmonic basis. The changes of basis can be computed with the two-dimensional Fourier transform denoted $\mathcal{F}_{\mbb{R}^2}$, and the spherical Fourier transform denoted $\mathcal{F}_{\mbb{S}^2}$. Gray highlighting indicates which part of each expression is being named.
%   }
%   \label{fig:dipole-block}      
% \end{figure}

% \subsubsection{Dipole coherent transfer functions}

% \begin{figure}
%   \hspace{-2em}
% \includegraphics[scale=1.0]{../figures/dipole-transfer-functions/dipole-transfer-functions.pdf}
% \caption{
%   % There is one transfer function for each set of object-space basis functions, and these transfer functions are related by two-dimensional and spherical Fourier transforms---see center and right columns. There is an additional pair of coherent transfer functions that are useful for calculating the transfer functions---see left column.
% }
%   \label{fig:transfer-functions}
% \end{figure}

% \subsubsection{Dipole pupil functions}

\section{Results}
\subsection{Monopole transfer functions}
We can model an aplanatic microscope imaging monopole emitters with the scalar pupil function
\begin{align}
  p(\rpperp) \propto  \tilde{C}\left(\frac{|\rpperp|}{f_0}\right)\Pi\left(\frac{|\rpperp|}{2f_0\sin\alpha}\right). \label{eq:monopupil}
\end{align}

Plugging Eq. \eqref{eq:monopupil} in Eq. \eqref{eq:monoctf} yields
\begin{align}
  C(\bt) \propto \tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right)
\end{align}
where $\nu_c = 2\text{NA}/\lambda$, $\text{NA} = n_0\sin\alpha$, and 
\begin{align}
  \tilde{C}(x) = (1 - x^2)^{-1/4}.
\end{align}

\add{To make the units check we need to add a normalization factor of $\frac{1}{\nu_c}$ to the coherent transfer function. Arguably this factor should have been included in the Eqs. 22 and 23 of the second paper \cite{chandler2019b}, but we played a bit loose with the proportionality symbol. I'm not sure if there's a more elegant way to motivate this factor of $\frac{1}{\nu_c}$.}
\begin{align}
  C(\bt) \propto \frac{1}{\nu_c}\tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right)
\end{align}

In Appendix \ref{sec:monoauto} we calculate the autocorrelation of the coherent transfer function and show that the monopole transfer function is given by
\begin{align}
  H(\bv) = \delta(\bv) + \frac{4\tau_{\circ}^2\bvpar}{\pi\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right),
\end{align}
where $E(\beta_m, k)  = \int_0^{\beta_m} d\phi\sqrt{1 - k^2\sin^2\phi}$ is an incomplete elliptic integral of the second kind and
\begin{align}
  p = \frac{|\bvperp|\nu_\circ}{\bvpar|\bv|},\qquad
  \nu_\circ = \sqrt{\nu_m^2 - (|\bv|/2)^2},\qquad
  \beta_m = \cos^{-1}\left(\frac{1}{p}\left[\frac{2\nu_m}{|\bvpar|}\cos\alpha + 1\right]\right).
\end{align}

We can also investigate the three-dimensional monopole transfer functions under the paraxial approximation by expanding the coherent transfer about $|\btperp| = 0$ and dropping second-order terms
\begin{align}
  C(\bt) \propp \frac{1}{\nu_c}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right).
\end{align}
In Appendix B we calculate the autocorrelation of the paraxial coherent transfer and show that the paraxial monopole transfer function is given by
\begin{align}
  H(\bv) \eqp \delta(\bv) + \frac{8\nu_m}{\pi\nu_c^2}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
\end{align}
where
\begin{align}
 \text{nez}(x, z) = \frac{1}{2|x|}\text{Re}\left[\sqrt{1 - \left(\frac{|z|}{|x|} + |x|\right)^2}\right].
\end{align}

% \subsection{Dipole transfer functions}
% \subsubsection{Dipole point spread function}

% \subsubsection{Dipole spatial transfer function}

% \subsubsection{Dipole angular transfer function}

% \subsubsection{Dipole spatio-angular transfer function}

\section{Discussion}
% Dipole phase masking:
% Azimuthal polarization filtering: \cite{lew2014}
% Metasurface polarization filtering: \cite{backlund2016}

\section{Conclusions}

\section*{Funding}
National Institute of Health (NIH) (R01GM114274, R01EB017293).

\section*{Acknowledgments}
TC was supported by a University of Chicago Biological Sciences Division Graduate Fellowship, and PL was supported by a Marine Biological Laboratory Whitman Center Fellowship. Support for this work was provided by the Intramural Research Programs of the National Institute of Biomedical Imaging and Bioengineering.

\section*{Disclosures}
The authors declare that there are no conflicts of interest related to this article.

\bibliography{/Users/Talon/Library/texmf/talon}
\appendix

\section{Multidimensional curvilinear delta functions}

\add{TODO: Summarize operational rules for tricky curvilinear delta functions. TBH I haven't mastered these rules yet.}
% In this appendix we review operational rules for manipulating multidimensional curvilinear delta functions. For a gentle introduction see Bracewell \cite{bracewell2004} and for details see Gelfand and Shilov \cite{gelfand2016}. Here we attempt to be brief and accessible.

% $\delta(f(x))$

% $\delta(f(\mb{r}))$

% $\delta(\mb{f}(\mb{r}))$

\section{Three-dimensional monopole transfer functions}\label{sec:monoauto}
\add{I have recently reworked this section with units in mind, and as far as I can tell all of the units are consistent. The paraxial results agree with the literature and when they project to 2D we get a result that is consistent with the previous paper.}

\add{I'm still having problems with the high-NA result, though. When I integrate over the axial coordinate the result is not normalized (see Fig. \ref{fig:compare}), and the result does not agree with Sheppard/Barakat \cite{barakat1963, sheppard1994} who predict a suppressed low-frequency response and an enhanced high-frequency response for high-NA objectives compared to the paraxial approximation. I'm hot on the trail of a few issues, but I'd appreciate any flags.}

In this appendix we will calculate the three-dimensional monopole transfer function
by evaluating the integral
\begin{align}
  H(\bv) = \int_{\mbb{R}^3}d\bt\, C(\bt + \bv/2)\,C^*(\bt - \bv/2). \label{eq:3dauto}
\end{align}
We will start by calculating the transfer function for the most general high-aperture case by setting the coherent transfer function to
\begin{align}
  C(\bt) \propto \frac{1}{\nu_c}\tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right).
\end{align}
Equivalently, we can express the high-aperture coherent transfer function in spherical coordinates as
\begin{align}
  C(\bt) \propto \,\frac{1}{\nu_c}\sqrt{\cos\theta_{\tau}}\,\delta\left(|\bt| - \nu_m\right)\,\Pi\left(\frac{\theta_{\tau}}{2\alpha}\right).
\end{align}
Therefore, we can interpret the integral in Eq. \eqref{eq:3dauto} as the autocorrelation of a $\sqrt{\cos\tau_\theta}$-weighted spherical cap with radius $\nu_m$ and half angle $\alpha$.

For $|\bv| = 0$ we can integrate over the spherical cap to find that 
\begin{align}
  H(\bv) \propto \frac{1}{\nu_c^2}\int_{0}^{\infty}|\bt|^2d|\bt|\int_0^{2\pi}d\phi_\tau\int_{0}^{\alpha}d\theta_\tau \sin\theta_\tau\cos\theta_\tau\delta(|\bt| - \nu_m)\delta(|\bt| - \nu_m) = \frac{\pi}{4}\delta(|\bv|).
\end{align}

When $|\bv| > 0$ we need to integrate over the intersection of the two spherical
caps which only intersect when
\begin{align}
  |\bvpar| < \sqrt{\nu_m^2 - (|\bvperp| - \nu_m\sin\alpha)^2} - \nu_m\cos\alpha. 
\end{align}
Therefore, the transfer function is zero when this condition is not satisfied.

\begin{figure}
  \centering
  \includegraphics[scale=0.3]{../figures/caps/general.pdf}
  \includegraphics[scale=0.25]{../figures/caps/spherical.pdf}\hspace{0.5em}
  \includegraphics[scale=0.28]{../figures/caps/cylindrical.pdf}
  \caption{Geometric constructions and coordinate systems for performing the three-dimensional autocorrelation. (Top) Two spherical caps with spherical radius $\nu_m = n_o/\lambda$ and base diameter $\nu_c = 2\text{NA}/\lambda$ are shifted by $\bv$ and intersect along a circular arc in the plane perpendicular to $\bv$. (Bottom left) We define a spherical coordinate system for each cap. These coordinate systems  are most convenient for expressing the individual coherent transfer functions. (Bottom right) We define a cylindrical coordinate system with the long axis of the cylinder parallel to the shift direction $\bv$ and the azimuthal angle $\beta_\tau$ defined with respect to the lowest point of each cylindrical slice. This coordinate system is most convenient for integrating over the circular arc of intersection.}
  \label{fig:caps}
\end{figure}

By inspection of Fig. \ref{fig:caps}, the intersection of the two shifted spherical caps is a circular arc centered on the origin in the plane perpendicular to the shift direction $\bv$. To integrate along this arc it will be convenient to define three new coordinate systems: (1, 2) two spherical coordinate systems defined with respect to the centers of the shifted spheres, and (3) a cylindrical coordinate system with long axis parallel to the shift direction $\bv$. The shifted spherical coordinate systems are straightforward to derive as
\begin{align}
  \begin{bmatrix}
    \tau_x\\
    \tau_y\\
    \btpar
  \end{bmatrix}
  =
  \begin{bmatrix}
    |\bt|_{1,2}\sin\theta_{\tau_{1,2}}\cos\phi_{\tau_{1,2}} \pm \nu_x/2\\
    |\bt|_{1,2}\sin\theta_{\tau_{1,2}}\sin\phi_{\tau_{1,2}} \pm \nu_y/2\\
    |\bt|_{1,2}\cos\theta_{\tau_{1,2}} \pm \bvpar/2
  \end{bmatrix},\label{eq:spherical}
\end{align}
where the subscripts and $\pm$ indicate which of the pair of shifted coordinate systems we are using.

Deriving the cylindrical coordinate system is more involved. We follow Arnison and Sheppard \cite{arnison2002} and define a cylindrical coordinate system for shifts along the $x$ axis $\bv = (1,0,0)$ then generalize to arbitrary shifts by multiplying with rotation matrices
\begin{align}
  \begin{bmatrix}
    \tau_x\\
    \tau_y\\
    \btpar
  \end{bmatrix}
  &= \mb{R}_{\mb{z}}(-\tan^{-1}(\nu_y/\nu_x)\mb{R}_{\mb{y}}(\sin^{-1}(\bvpar/|\bv|))
  \begin{bmatrix}
    \tau_\xi\\
    \tau_R\sin\beta_\tau\\
    -\tau_R\cos\beta_\tau
  \end{bmatrix}\nonumber\\
  &=
  \begin{bmatrix}
    \displaystyle\frac{\nu_x}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_x\cos\beta_\tau - |\bv|\nu_y\sin\beta_\tau)\\[1em]
    \displaystyle\frac{\nu_y}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_y\cos\beta_\tau + |\bv|\nu_x\sin\beta_\tau)\\[1em]
    \displaystyle\frac{\bvpar}{|\bv|}\tau_\xi - \frac{|\bvperp|\tau_R}{|\bv|}\cos\beta_\tau
  \end{bmatrix},\label{eq:cylindrical}
\end{align}
where
\begin{align}
  \mb{R}_\mb{z}(\theta) =
  \begin{bmatrix}
    \cos\theta & 0 & -\sin\theta\\
    0 & 1 & 0\\
    \sin\theta & 0 &\cos\theta
  \end{bmatrix}\, ,\quad 
  \mb{R}_\mb{y}(\theta) =
  \begin{bmatrix}
    \cos\theta & \sin\theta & 0\\
    -\sin\theta & \cos\theta & 0\\
    0 & 0 & 1
  \end{bmatrix}.
\end{align}

To evaluate the integral we need to express it in our new cylindrical coordinate system. We start by considering the pair of delta functions in the integrand $\delta(|\bt - \bv/2| - \nu_m)\,\delta(|\bt + \bv/2| - \nu_m)$. The spherical shells intersect in a circle of radius $\nu_\circ = \sqrt{\nu_m^2 - (|\bv|/2)^2}$ centered on the origin so we expect the delta functions to become $\delta(\tau_\xi)\,\delta(\tau_R - \nu_\circ)$ in the cylindrical coordinate system. However, we need to preserve the ``strength'' of the delta functions in the new coordinate system (see Bracewell \cite{bracewell2004} for operational rules and see Gelfand and Shilov \cite{gelfand2016} for a detailed discussion), so we normalize by the Jacobian determinant in each coordinate system. After accounting for the changing strength of the delta functions we find that
\begin{align}
  \delta(|\bt - \bv/2| - \nu_m)\,\delta(|\bt + \bv/2| - \nu_m) = \frac{\nu_\circ}{|\bv|}\delta(\tau_\xi)\,\delta(\tau_R - \nu_\circ).
\end{align}
\add{This step is a prime candidate for an error. I derived this factor
  $\frac{\nu_\circ}{|\bv|}$ by matching the Jacobian on both sides, but this
  disagrees with the factor Arnison \cite{arnison2002} uses which is $\propto \frac{1}{|\bv|\nu_\circ}$. Arnison's factor doesn't seem to have the correct units...although all of the Sheppard papers seem pretty free-form when it comes to normalizing/units.}

The integrating measure in the cylindrical coordinate system is
\begin{align}
  d\bt = \tau_R d\tau_R d\tau_\xi d\beta_\tau,
\end{align}
so we can write the integral as 
\begin{align}
  H(\bv) \propto \frac{1}{\nu_c^2}\frac{\nu_\circ}{|\bv|}\int_{\mbb{R}}d\tau_\xi\int_{0}^{\infty}\tau_Rd\tau_R\int_{-\pi}^{\pi}d\beta_\tau\, \sqrt{\cos\tau_{\theta_1}\cos\tau_{\theta_2}}\,\delta(\tau_\xi)\delta(\tau_R - \nu_\circ)\,\Pi\left(\frac{\tau_{\theta_1}}{2\alpha}\right)\Pi\left(\frac{\tau_{\theta_2}}{2\alpha}\right).
\end{align}

Next, we express the integrand in cylindrical coordinates. Equating the $\btpar$ components in Eqs. \eqref{eq:spherical} and \eqref{eq:cylindrical} and evaluating on the circle of intersection ($|\bt|\rightarrow \nu_m$, $\tau_\xi\rightarrow 0$, $\tau_R\rightarrow \nu_\circ$) yields the relationship
\begin{align}
  \nu_m\cos\theta_{\tau_{1,2}} \pm \frac{\bvpar}{2} = -\frac{|\bvperp|\nu_\circ}{|\bv|}\cos\beta_\tau\label{eq:angles}.
\end{align}
The integrand is written in terms of $\cos\tau_{\theta_{1,2}}$, so we rewrite Eq. \eqref{eq:angles} to find the relationship
\begin{align}
  \cos\theta_{\tau_{1,2}} = \frac{1}{\nu_m}\left(-\frac{|\bvperp|\nu_\circ}{|\bv|}\cos\beta_\tau\mp \frac{\bvpar}{2}\right) = \frac{\bvpar}{2\nu_m}\left(-p\cos\beta_\tau \mp 1\right)
\end{align}
where
\begin{align}
  p = \frac{2|\bvperp|\nu_\circ}{\bvpar|\bv|}.
\end{align}

We can also use Eq. \eqref{eq:angles} to find the limits of integration for $\tau_\beta$ by setting $\tau_{\theta_2} \rightarrow \alpha$ then solving for $\tau_\beta$ to find the maximum azimuthal angle $\beta_m$
\begin{align}
  \beta_m = \cos^{-1}\left[\frac{1}{p}\left(\frac{2\nu_m}{|\bvpar|}\cos\alpha + 1\right)\right].
\end{align}

Bringing everything together yields the one-dimensional integral
\begin{align}
  H(\bv) \propto \frac{\nu_\circ^2\bvpar}{2\nu_c^2|\bv|\nu_m}\int_{-\beta_m}^{\beta_m}d\tau_\beta\, \sqrt{p^2\cos^2\beta_\tau - 1}, 
\end{align}
which can be written as 
\begin{align}
  H(\bv) \propto \frac{\tau_{\circ}^2\bvpar}{\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right),
\end{align}
where $E(\beta_m, k)  = \int_0^{\beta_m} d\phi\sqrt{1 - k^2\sin^2\phi}$ is an incomplete elliptic integral of the second kind.

After normalization, the complete transfer function is given by
\begin{align}
  H(\bv) = \delta(|\bv|) + \frac{4\tau_{\circ}^2\bvpar}{\pi\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right).
\end{align}

Next, we calculate the monopole transfer function under the paraxial approximation. We approximate the $\sqrt{\cos\theta_\tau}$-weighted spherical cap with a truncated paraboloid
\begin{align}
  C(\bt) \propp \frac{1}{\nu_c}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right). \label{eq:ctf}
\end{align}

For the high-aperture case we evaluated the three-dimensional autocorrelation
directly, but for the paraxial case it is easier to evaluate the two-dimensional
autocorrelation of the defocused coherent transfer functions. We rewrite the
three-dimensional transfer function as
\begin{align}
  H(\bv) = \int_{\mbb{R}}dr^{\mypar}\,H^{(d)}(\bvperp,r^{\mypar})\,\text{exp}(-2\pi i r^{\mypar}\bvpar),\label{eq:def3dtf}
\end{align}
where $H^{(d)}(\bvperp,r^{\mypar})$ is the defocused transfer function given by
\begin{align}
  H^{(d)}(\bvperp,r^{\mypar}) = \int_{\mbb{R}^2}d\btperp\,C^{(d)}(\btperp + \bvperp/2, r^{\mypar})C^{(d)*}(\btperp - \bvperp/2, r^{\mypar}), \label{eq:defautocorr}
\end{align}
and $C^{(d)}(\btperp, r^{\mypar})$ is the defocused coherent transfer function given by
\begin{align}
  C^{(d)}(\btperp, r^{\mypar}) = \int_{\mbb{R}}d\btpar\, C(\bt)\,\text{exp}(2\pi i r^{\mypar}\btpar).\label{eq:deftf}
\end{align}
We plug Eq. \eqref{eq:ctf} into Eq. \eqref{eq:deftf} and evaluate the Fourier transform to find that the defocused coherent transfer function is
\begin{align}
  C^{(d)}(\btperp, r^{\mypar}) \propp \frac{1}{\nu_c}\text{exp}(2\pi i r^{\mypar}[-\nu_m + |\btperp|^2/2\nu_m])\Pi\left(\frac{|\btperp|}{\nu_c}\right), \label{eq:defctf}
\end{align}
which we can interpret as a disk with uniform magnitude and quadratic phase factor that depends on the defocus $r^{\mypar}$.

To evaluate the three-dimensional transfer function at $|\bv| = 0$ we start by evaluating the defocused transfer function at $|\bvperp| = 0$
\begin{align}
  H^{(d)}(\bv, r^{\mypar}) = \frac{\pi}{4}. \label{eq:result}
\end{align}
After plugging \eqref{eq:result} into Eq. \eqref{eq:def3dtf} and evaluating the Fourier transform we find that 
\begin{align}
  H(\bv) = \frac{\pi}{4}\delta(|\bv|). 
\end{align}

When $|\bv| > 0$ we need to integrate over the intersection of the two truncated paraboloids which only intersect when
\begin{align}
  |\bvpar| < -\frac{1}{2\nu_m}|\bvperp|(|\bvperp| - \nu_c). 
\end{align}
Therefore, the paraxial transfer function is zero when this condition is not satisfied.

First we evaluate the defocused transfer function by plugging Eq. \eqref{eq:defctf} into Eq. \eqref{eq:defautocorr}
\begin{align}
  H^{(d)}(\bvperp,r^{\mypar}) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \text{exp}(2\pi i r^{\mypar}[|\btperp + \bvperp/2|^2/2\nu_m])\, \text{exp}(-2\pi i r^{\mypar}[|\btperp - \bvperp/2|^2/2\nu_m])\nonumber\\\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right),
\end{align}
then simplifying the complex exponentials
\begin{align}
  H^{(d)}(\bvperp,r^{\mypar}) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \text{exp}(2\pi i r^{\mypar}[\btperp\cdot\bvperp/\nu_m])\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).\label{eq:defocusresult}
\end{align}
Next, we plug Eq. \eqref{eq:defocusresult} into Eq. \eqref{eq:def3dtf} and evaluate the
Fourier transform to find that 
\begin{align}
  H(\bv) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \delta(\bvpar - \btperp\cdot\bvperp/\nu_m)\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).
\end{align}
\begin{figure}
  \centering
  \includegraphics[scale=0.2]{../figures/para-geometry/para-geometry.pdf}
  \caption{Geometric construction for evaluating the three-dimensional autocorrelation under the paraxial approximation. We need to integrate over a line perpendicular to the transverse shift direction $\bvperp$ that is displaced from the origin by $\nu_m|\bvpar|/|\bvperp|$ and truncated by the shifted circles with diameter $\nu_c$.}
  \label{fig:geometry}
\end{figure}

We can evaluate this integral with the help of the geometric construction in Fig. \ref{fig:geometry}. The delta function corresponds to a line perpendicular to the transverse shift direction $\bvperp$ displaced from the origin by $\nu_m|\bvpar|/|\bvperp|$. Within the intersection of the shifted circles this line has length $2\sqrt{(\nu_c/2)^2 - ([\nu_m|\bvpar|/|\bvperp|] + [|\bvperp|/2])^2}$. Finally, the ``strength'' of the delta function is $\nu_m/|\bvperp|$, so the integral evaluates to 
\begin{align}
  H(\bv) \propp \frac{2\nu_m}{\nu_c^2|\bvperp|}\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}. 
\end{align}

After normalization, the complete paraxial transfer function is 
\begin{align}
  H(\bv) \eqp \delta(|\bv|) + \frac{8\nu_m}{\pi\nu_c^2|\bvperp|}\text{Re}\left\{\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}\right\}.
\end{align}

We can rewrite the paraxial transfer function in a scaled form 
\begin{align}
  H(\bv) \eqp \delta(|\bv|) + \frac{8\nu_m}{\pi\nu_c^2}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
\end{align}
where we have defined the function
\begin{align}
 \text{nez}(x, z) = \frac{1}{2|x|}\text{Re}\left[\sqrt{1 - \left(\frac{|z|}{|x|} + |x|\right)^2}\right]
\end{align}
and named it for its resemblance to pince-nez (nose-pinching glasses)---see Fig. \ref{fig:nez}.
\begin{figure}
  \centering
  \includegraphics[scale=0.9]{../figures/nez/nez.pdf}
  \caption{Plot of $\text{nez}(x,z)$ with contours on integer values between 0 and 5. $\text{nez}(x,z)$ has a singularity at the origin, so we have truncated values above 10.}
  \label{fig:nez}
\end{figure}

We can recover the two-dimensional paraxial transfer function by integrating over the axial coordinate
\begin{align}
  H(\bvperp) \eqp \int_{\mbb{R}}d\bvpar\, H(\bv) = \frac{4}{\pi}\text{chat}_0\left(\frac{|\bvperp|}{\nu_c}\right), 
\end{align}
where we have used
\begin{align}
  \int_{\mbb{R}}dz\,\text{nez}(x,z) = \text{chat}_0(x) = \frac{1}{2}\left[\cos^{-1}|x| - |x|\sqrt{1-x^2}\right]\Pi\left(\frac{x}{2}\right).
\end{align}

\begin{figure}
  \centering
  \includegraphics[scale=0.85]{../figures/monopole-psf/dpsf.pdf}
  \caption{Comparison of high-aperture and paraxial three-dimensional transfer functions for $\text{NA} = (1.00, 1.25, 1.50)$, $n_o = 1.5$, and $\lambda = 500\,\text{nm}$. \add{Notice the units: input spatial frequencies are in  m${}^{-1}$ and the output is in m${}^{+1}$. I have overlaid each plot with two lines: a blue line which is the paraxial transverse transfer function ($\text{chat}(\nu/\nu_c)$) and a green line which is the numerical integral of the 3D transfer function over $\bvpar$. The blue and green lines should have their own $y$ axis, but I'm reusing the left $y$ axis without units. In the paraxial case these lines agree which is a good check that my results are correct. In the high-aperture case the green line is not normalized, and I expect the green line to be lower than the blue line at low frequencies and higher than the blue line at high frequencies (see Barakat \cite{barakat1963}). Therefore, I'm searching for an error that makes the high-aperture transfer function too large everywhere (normalization) and too small at high-frequencies.}}
  \label{fig:compare}
\end{figure}

\end{document}

### 2019-07-29 papers/three-dimensions/paper/paper.tex
Properly normalized monopole tfs and Patrick's comments.

@@
 \providecommand{\rbm}[1]{r_b^{\text{m}}}
-\providecommand{\rd}{\mathbf{r}_d}
+\providecommand{\rd}{\mathbf{r}^{\bot}_d}
+\providecommand{\rdp}{\mathbf{r}^{'\bot}_d}
 \providecommand{\rdf}{\mathpzc{r}_d}
@@
 \section{Introduction}
-\add{Patrick: Key references for comparison are sheppard1994} \cite{sheppard1994} \add{and arnison2002} \cite{arnison2002}.\\
-
 \noindent Skeleton literature review ahead. \\
@@
 
-\noindent \add{I'm having some difficulty getting units to agree in section 2.2.3, but section 3 and the appendix are fairly consistent.}
-
 \subsection{Three-dimensional monopole transfer functions}
 \subsubsection{Monopole transfer functions}
-Monopole point spread function
+We begin by modeling a microscope that is imaging a three-dimensional sample of monopole emitters with a two-dimensional detector using an integral transform
 \begin{align}
-  g(\rd) = \int_{\mbb{R}}d\ropar\int_{\mbb{R}^2}d\roperp\, h(\rd - \roperp, \ropar)f(\ro),
+  g(\rd) = \int_{\mbb{R}}d\ropar\int_{\mbb{R}^2}d\roperp\, h(\rd - \roperp, \ropar)f(\ro),\label{eq:opener}
 \end{align}
-We can rewrite as 
+where $\rd$ is a two-dimensional detector position, $\ro = (\roperp, \ropar)$ is a three-dimensional detector coordinate with its transverse/axial decomposition, $g(\rd)$ is the measured irradiance on the detector, $f(\ro)$ is the monopole density, and $h(\rd - \roperp, \ropar)$ is a three-to-two-dimensional point spread function.
+
+We can use the Fourier-convolution theorem to rewrite Eq. \eqref{eq:opener} as
 \begin{align}
@@
 \end{align}
-where
+where $\bv = (\bvperp, \bvpar)$ is a three-dimensional spatial frequency coordinate with its transverse/axial decomposition, 
 \begin{align}
-  G(\bvperp) = \int_{\mbb{R}^2}d\mb{r}^{\perp}\, g(\mb{r})\, \text{exp}(-2\pi i\mb{r}\cdot\bvperp),
+  G(\bvperp) = \int_{\mbb{R}^2}d\rd\, g(\rd)\, \text{exp}(-2\pi i\rd\cdot\bvperp)
 \end{align}
+is the scaled irradiance spectrum,
 \begin{align}
-  H(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, h(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv),
+  H(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, h(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv)
 \end{align}
-and
+is the monopole transfer function, and
 \begin{align}
-  F(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, f(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv).
+  F(\bv) = \int_{\mbb{R}^3}d\bs{\mf{r}}\, f(\bs{\mf{r}})\, \text{exp}(-2\pi i\bs{\mf{r}}\cdot\bv)
 \end{align}
+is the monopole spectrum. Figure \ref{fig:monopole-block} summarizes the relationships between the object and data representations.
 
@@
 \subsubsection{Monopole coherent transfer functions}
+The monopole point spread function can always be written as the absolute square of a monopole coherent spread function
 \begin{align}
-  |c(\rd - \roperp, \ropar)|^2 = h(\rd - \roperp, \ropar)
+  |c(\rd - \roperp, \ropar)|^2 = h(\rd - \roperp, \ropar).
 \end{align}
+By applying the autocorrelation theorem we can use the monopole coherent transfer function as a shortcut for calculating the monopole transfer function
 \begin{align}
-  H(\bv) = \int_{\mbb{R}^3}d\bt\,C(\bt)C^*(\bt - \bv)
+  H(\bv) = \int_{\mbb{R}^3}d\bt\,C(\bt)C^*(\bt - \bv),
 \end{align}
+where $\bt = (\btperp, \btpar)$ is a three-dimensional transverse spatial frequency coordinate with its transverse/axial decomposition, and $C(\bt)$ is a coherent transfer function defined by
 \begin{align}
@@
 \end{align}
-This implies that the three-dimensional coherent transfer function is a scaled pupil function on a spherical shell.
+Figure \ref{fig:monopole-transfer-functions} summarizes the relationships between the transfer functions.
 
@@
 \subsubsection{Monopole pupil functions}
-% First, consider the field created at $\rs$ by a monopole at $\ro$ 
-% \begin{align}
-%   U_s(\rs, \ro) \propto \frac{\text{exp}[2\pi i\nu_m|\rs - \ro|]}{|\rs - \ro|},
-% \end{align}
-% where $\nu_m = n_o/\lambda$.
+In this section we will relate the monopole transfer functions to physical
+parameters. First, consider the field created at $\rs$ by a monopole at $\ro$
+\begin{align}
+  U_s(\rs, \ro) \propto \frac{\text{exp}[2\pi i\nu_m|\rs - \ro|]}{|\rs - \ro|},
+\end{align}
+where $\nu_m = n_o/\lambda$ is the radius of the Ewald sphere.
 For monopoles near the origin we can find the fields on the Gaussian reference sphere of an objectives lens with focal length $f_0 \gg |\ro|$ by applying the approximation $|\rs - \ro| \approx |\rs| - \rs\cdot\ro/|\rs|$ and dropping second-order amplitude and constant phase terms
-% \begin{align}
-%   U_s(\rs, \ro) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rs\cdot\ro)/f_0].
-% \end{align}
-% Next, we expand the coordinates into transverse and axial components
-% \begin{align}
-%   U_s(\rs, \ro) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rsperp\cdot\roperp + \rspar\ropar)/f_0],
-% \end{align}
-% then rewrite in pupil coordinates using the relationships $\rsperp = \rpperp$ and $\rspar = \sqrt{f_0^2 - |\rppar|^2}$
-% \begin{align}
-%   U_p(\rpperp, \roperp, \ropar) \propto \frac{1}{f_0}\text{exp}\left[-2\pi i\nu_m\left(\rpperp\cdot\roperp + \rspar\sqrt{f_0^2 - |\roperp|^2}\right)/f_0\right].
-% \end{align}
-\add{Patrick: This section follows section 2A in the second paper \cite{chandler2019b} fairly closely with modifications for 3D.}
-
-We can write the field in the pupil plane at point $\rpperp$ due to a monopole at $\ro = (\roperp, \ropar)$ as
 \begin{align}
-  U_p(\rpperp, \roperp, \ropar) \propto p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right],
+  U_s(\rs, \ro) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rs\cdot\ro)/f_0].
+\end{align}
+Next, we expand the coordinates into transverse and axial components
+\begin{align}
+  U_s(\rs, \roperp, \ropar) \propto \frac{1}{f_0}\text{exp}[-2\pi i\nu_m(\rsperp\cdot\roperp + \rspar\ropar)/f_0],
+\end{align}
+then rewrite in pupil coordinates using the relationships $\rsperp = \rpperp$ and $\rspar = \sqrt{f_0^2 - |\rppar|^2}$
+\begin{align}
+  U_p(\rpperp, \roperp, \ropar) \propto \frac{1}{f_0}\text{exp}\left[-2\pi i\nu_m\left(\rpperp\cdot\roperp + \ropar\sqrt{f_0^2 - |\roperp|^2}\right)/f_0\right].
+\end{align}
+We can rewrite the field in the pupil plane as
+\begin{align}
+  U_p(\rpperp, \roperp, \ropar) \propto \frac{1}{f_0}p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right],
 \end{align}
@@
 \begin{align}
-  p_d(\rpperp, \ropar) = p(\rpperp)\, \text{exp}\left[-2\pi i\ropar\nu_m\sqrt{1 - (|\rpperp|/f_0)^2}\right],
+  p_d(\rpperp, \ropar) = p(\rpperp)\, \text{exp}\left[-2\pi i\nu_m\ropar\sqrt{1 - (|\rpperp|/f_0)^2}\right],
 \end{align}
-and $p(\rpperp)$ is the usual pupil function which can be used to model angular cutoff, apodization, or aberrations.
+and $p(\rpperp)$ is the usual pupil function that can be used to model the angular cutoff, apodization, aberration, or phase masks.
 
@@
 \begin{align}
-  U_d(\rd', \roperp, \ropar) \propto \int_{\mbb{R}^2}d\rpperp\,p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1}\rpperp\cdot\rd'\right].
+  U_d(\rdp, \roperp, \ropar) \propto \frac{n_1}{\lambda f_0f_1}\int_{\mbb{R}^2}d\rpperp\,p_d(\rpperp, \ropar)\,\text{exp}\left[-2\pi i \frac{n_0}{\lambda f_0}\rpperp\cdot\roperp\right]\text{exp}\left[-2\pi i \frac{n_1}{\lambda f_1}\rpperp\cdot\rdp\right].
 \end{align}
@@
 \begin{align}
-  P_d(\btperp, \ropar) = \int_{\mbb{R}^2}d\rpperp\, p_d(\rpperp, \ropar)\,\text{exp}(-2\pi i \rpperp\cdot\btperp),\label{eq:pupilF}
+  P(\btperp, \ropar) = \int_{\mbb{R}^2}d\rpperp\, p_d(\rpperp, \ropar)\,\text{exp}(-2\pi i \rpperp\cdot\btperp),\label{eq:pupilF}
 \end{align}
@@
 \begin{align}
-  U_d(\rd', \roperp, \ropar) \propto P\left(\frac{n_0}{\lambda f_0}\roperp + \frac{n_1}{\lambda f_1}\rd', \ropar\right).
+  U_d(\rdp, \roperp, \ropar) \propto \frac{n_1}{\lambda f_0f_1}P\left(\frac{n_0}{\lambda f_0}\roperp + \frac{n_1}{\lambda f_1}\rdp, \ropar\right).
 \end{align}
-After rewriting in terms of the magnification $m = -\frac{f_1 n_0}{f_0 n_1}$, demagnifying the coordinates with $\rd = \rd'/m$, and demagnifying the irradiance with $h(\rd - \roperp, \ropar) \propto h'(m[\rd - \roperp], \ropar) $, we find the defocused monopole point spread function is related to the Fourier transform of the defocused monopole pupil function by
+After rewriting in terms of the magnification $m = -\frac{f_1 n_0}{f_0 n_1}$, demagnifying the coordinates with $\rd = \rdp/m$, and demagnifying the irradiance with $h(\rd - \roperp, \ropar) \propto h'(m[\rd - \roperp], \ropar) $, we find the defocused monopole point spread function is related to the Fourier transform of the defocused monopole pupil function by
 \begin{align}
-  h(\rd-\roperp, \ropar) \propto \left|P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right)\right|^2.
+  h(\rd-\roperp, \ropar) \propto \left|\frac{n_1}{\lambda f_0f_1}P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right)\right|^2.
 \end{align}
@@
 \begin{align}
-  c(\rd - \roperp, \ropar) \propto P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right). \label{eq:monocsf}
+  c(\rd - \roperp, \ropar) \propto \frac{n_1}{\lambda f_0f_1}P\left(-\frac{n_0}{\lambda f_0}[\rd - \roperp], \ropar\right). \label{eq:monocsf}
 \end{align}
@@
 \begin{align}
-  C(\bt) = \int_{\mbb{R}}dr^{\mypar}\int_{\mbb{R}^2}d\mb{r}^{\bot}\, P\left(-\frac{n_0}{\lambda f_0}\mb{r}^{\bot}, r^{\mypar}\right)\,\text{exp}(-2\pi i[\mb{r}^{\bot}\cdot\btperp + r^{\mypar}\btpar]).
+  C(\bt) \propto \frac{n_1}{\lambda f_0f_1}\int_{\mbb{R}}dr^{\mypar}\int_{\mbb{R}^2}d\mb{r}^{\bot}\, P\left(-\frac{n_0}{\lambda f_0}\mb{r}^{\bot}, r^{\mypar}\right)\,\text{exp}(-2\pi i[\mb{r}^{\bot}\cdot\btperp + r^{\mypar}\btpar]).
 \end{align}
@@
 \begin{align}
-  C(\bt) \propto p\left(\frac{\lambda f_0}{n_0}\btperp\right) \int_{\mbb{R}}d r^{\mypar} \,\text{exp}\left(-2\pi i r^{\mypar}\sqrt{\nu_m - |\btperp|^2}\right)\,\text{exp}(-2\pi i r^{\mypar}\btpar)
+  C(\bt) \propto \frac{1}{\nu_m}\, p\left(\frac{\lambda f_0}{n_0}\btperp\right) \int_{\mbb{R}}d r^{\mypar} \,\text{exp}\left(-2\pi i r^{\mypar}\sqrt{\nu_m - |\btperp|^2}\right)\,\text{exp}(-2\pi i r^{\mypar}\btpar).
 \end{align}
@@
 \begin{align}
-  C(\bt) \propto p\left(\frac{\lambda f_0}{n_0}\btperp\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right).\label{eq:monoctf}
+  C(\bt) \propto \frac{1}{\nu_m}p\left(\frac{\lambda f_0}{n_0}\btperp\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right).
 \end{align}
+This shows that the three-dimensional coherent transfer function is a scaled pupil function on a spherical cap.
 
@@
 \begin{align}
-  p(\rpperp) \propto  \tilde{C}\left(\frac{|\rpperp|}{f_0}\right)\Pi\left(\frac{|\rpperp|}{2f_0\sin\alpha}\right). \label{eq:monopupil}
+  p(\rpperp) \propto  \tilde{C}\left(\frac{|\rpperp|}{f_0}\right)\Pi\left(\frac{|\rpperp|}{2f_0\sin\alpha}\right), \label{eq:monopupil}
 \end{align}
-
-Plugging Eq. \eqref{eq:monopupil} in Eq. \eqref{eq:monoctf} yields
-\begin{align}
-  C(\bt) \propto \tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right)
-\end{align}
-where $\nu_c = 2\text{NA}/\lambda$, $\text{NA} = n_0\sin\alpha$, and 
+where
 \begin{align}
@@
 \end{align}
-
-\add{To make the units check we need to add a normalization factor of $\frac{1}{\nu_c}$ to the coherent transfer function.
-Arguably this factor should have been included in the Eqs.
-22 and 23 of the second paper \cite{chandler2019b}, but we played a bit loose with the proportionality symbol.
-I'm not sure if there's a more elegant way to motivate this factor of $\frac{1}{\nu_c}$.}
+Plugging Eq. \eqref{eq:monopupil} in Eq. \eqref{eq:monoctf} yields
 \begin{align}
-  C(\bt) \propto \frac{1}{\nu_c}\tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right)
+  C(\bt) \propto \frac{1}{\nu_m}\tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right),\label{eq:toexpand}
+\end{align}
+where $\nu_c = 2\text{NA}/\lambda$ and $\text{NA} = n_0\sin\alpha$.
+Applying an identity from Appendix \ref{sec:delta} (Eq.
+\eqref{eq:sphereidentity}) allows us to write the coherent transfer function in spherical coordinates as
+\begin{align}
+  C(\bt) \propto \frac{1}{\nu_m}\sqrt{\cos\theta_\tau}\,\delta\left(|\bt| - \nu_m\right)\,\Pi\left(\frac{\theta_\tau}{2\alpha}\right).
 \end{align}
@@
 \begin{align}
-  H(\bv) = \delta(\bv) + \frac{4\tau_{\circ}^2\bvpar}{\pi\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right),
+  H(\bv) = 4\pi\sin^2(\alpha/2)\,\delta(|\bv|) + \frac{|\bvpar|}{\nu_m|\bv|}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right)\infty\left(\frac{|\bvperp|}{\nu_m}, \frac{|\bvpar|}{\nu_m}, \alpha\right),
 \end{align}
@@
 \begin{align}
-  p = \frac{|\bvperp|\nu_\circ}{\bvpar|\bv|},\qquad
-  \nu_\circ = \sqrt{\nu_m^2 - (|\bv|/2)^2},\qquad
-  \beta_m = \cos^{-1}\left(\frac{1}{p}\left[\frac{2\nu_m}{|\bvpar|}\cos\alpha + 1\right]\right).
+  p = \frac{2|\bvperp|}{\bvpar|\bv|}\sqrt{\nu_m^2 - (|\bv|/2)^2},\qquad
+  \beta_m = \cos^{-1}\left(\frac{1}{p}\left[\frac{2\nu_m}{|\bvpar|}\cos\alpha + 1\right]\right),\nonumber\\ \infty(x, z, \alpha) = \Pi\left(\frac{|z|}{2(\sqrt{1 - (|x| - \sin\alpha)^2} - \cos\alpha)}\right).
 \end{align}
 
-We can also investigate the three-dimensional monopole transfer functions under the paraxial approximation by expanding the coherent transfer about $|\btperp| = 0$ and dropping second-order terms
-\begin{align}
-  C(\bt) \propp \frac{1}{\nu_c}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right).
+We can also investigate the three-dimensional monopole transfer functions under the paraxial approximation by expanding the argument of the delta function in Eq.
+\eqref{eq:toexpand} about $|\btperp| = 0$ and dropping fourth- and higher-order terms \begin{align}
+  C(\bt) \propp \frac{1}{\nu_m}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right).
 \end{align}
@@
 \begin{align}
-  H(\bv) \eqp \delta(\bv) + \frac{8\nu_m}{\pi\nu_c^2}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
+  H(\bv) \eqp \frac{\pi\nu_c^2}{4\nu_m^2}\delta(|\bv|) + \frac{4}{\nu_m}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
 \end{align}
@@
 \end{align}
+
+Figure 3 compares the high-aperture transfer function to the paraxial transfer function in their normalized forms.
+For extremely high numerical apertures $\alpha = \pi/2$ the high-aperture transfer function predicts an axial spatial frequency cutoff that is double the prediction of the paraxial model.
+Additionally, the high-aperture transfer function predicts a spatial frequency support that is a horn torus at $\alpha = \pi/2$ and a lemon-profiled torus for $\alpha < \pi/2$, while the paraxial transfer function predicts a scaled parabolic-lemon-profiled torus for all $\alpha$.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.85]{../figures/monopole-psf/dpsf.pdf}
+  \caption{Comparison of high-aperture and paraxial three-dimensional transfer functions for $\text{NA} = (1.00, 1.25, 1.50)$, $n_o = 1.5$, and $\lambda = 500\,\text{nm}$.
+Input spatial frequencies are in  m${}^{-1}$ and the output is in m${}^{+1}$.
+All transfer functions are normalized so that $\lim_{|{\bvperp}|\rightarrow 0} \int_\mbb{R}d\bvpar H(\bvperp, \bvpar) = 1$.}
+  \label{fig:compare}
+\end{figure}
 
@@
 
-\section{Multidimensional curvilinear delta functions}
+\section{Multidimensional curvilinear delta functions}\label{sec:delta}
+In this appendix we summarize operational rules for manipulating multidimensional curvilinear delta functions.
+See Bracewell \cite{bracewell2004} for an intuitive approach to two-dimensional delta functions, and see Gelfand and Shilov \cite{gelfand2016} for a more mathematical discussion of multidimensional delta functions.
 
-\add{TODO: Summarize operational rules for tricky curvilinear delta functions. TBH I haven't mastered these rules yet.}
-% In this appendix we review operational rules for manipulating multidimensional curvilinear delta functions.
-For a gentle introduction see Bracewell \cite{bracewell2004} and for details see Gelfand and Shilov \cite{gelfand2016}.
-Here we attempt to be brief and accessible.
+Our goal is to interpret delta functions of the form $\delta(\mb{g}(\mb{r}))$ where $\mb{g}: \mbb{R}^N \rightarrow \mbb{R}^M$.
+Starting with a simple case $N = M = 1$ and $g(r) = r$ we can use the sifting property to interpret the delta function
+\begin{align}
+  \int_{\mbb{R}}dr\,\delta(r)f(r) = f(0).
+\end{align}
+When $g(r) = ar$ then we can use a change of variables to show that 
+\begin{align}
+  \int_{\mbb{R}}dr\,\delta(ar)f(r) = \frac{f(0)}{|a|}.
+\end{align}
+Intuitively, the function $ar$ crosses its zero with an absolute slope $|a|$ so it sifts less of the function $f(r)$ by a factor of $|a|^{-1}$.
 
-% $\delta(f(x))$
-
-% $\delta(f(\mb{r}))$
-
-% $\delta(\mb{f}(\mb{r}))$
-
-\section{Three-dimensional monopole transfer functions}\label{sec:monoauto}
-\add{I have recently reworked this section with units in mind, and as far as I can tell all of the units are consistent.
-The paraxial results agree with the literature and when they project to 2D we get a result that is consistent with the previous paper.}
-
-\add{I'm still having problems with the high-NA result, though.
-When I integrate over the axial coordinate the result is not normalized (see Fig.
-\ref{fig:compare}), and the result does not agree with Sheppard/Barakat \cite{barakat1963, sheppard1994} who predict a suppressed low-frequency response and an enhanced high-frequency response for high-NA objectives compared to the paraxial approximation.
-I'm hot on the trail of a few issues, but I'd appreciate any flags.}
-
-In this appendix we will calculate the three-dimensional monopole transfer function
-by evaluating the integral
+When $g(r)$ is a function with multiple zeros then the delta functions sifts (with appropriate weighting) at all of the function's zeros 
 \begin{align}
-  H(\bv) = \int_{\mbb{R}^3}d\bt\, C(\bt + \bv/2)\,C^*(\bt - \bv/2). \label{eq:3dauto}
-\end{align}
-We will start by calculating the transfer function for the most general high-aperture case by setting the coherent transfer function to
-\begin{align}
-  C(\bt) \propto \frac{1}{\nu_c}\tilde{C}\left(\frac{|\btperp|}{\nu_m}\right)\,\delta\left(\btpar - \sqrt{\nu_m^2 - |\btperp|^2}\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right).
-\end{align}
-Equivalently, we can express the high-aperture coherent transfer function in spherical coordinates as
-\begin{align}
-  C(\bt) \propto \,\frac{1}{\nu_c}\sqrt{\cos\theta_{\tau}}\,\delta\left(|\bt| - \nu_m\right)\,\Pi\left(\frac{\theta_{\tau}}{2\alpha}\right).
-\end{align}
-Therefore, we can interpret the integral in Eq. \eqref{eq:3dauto} as the autocorrelation of a $\sqrt{\cos\tau_\theta}$-weighted spherical cap with radius $\nu_m$ and half angle $\alpha$.
-
-For $|\bv| = 0$ we can integrate over the spherical cap to find that 
-\begin{align}
-  H(\bv) \propto \frac{1}{\nu_c^2}\int_{0}^{\infty}|\bt|^2d|\bt|\int_0^{2\pi}d\phi_\tau\int_{0}^{\alpha}d\theta_\tau \sin\theta_\tau\cos\theta_\tau\delta(|\bt| - \nu_m)\delta(|\bt| - \nu_m) = \frac{\pi}{4}\delta(|\bv|).
+  \int_{\mbb{R}}dr\,\delta(g(r))f(r) = \sum_{g(r_i) = 0}f(r_i)\left|\frac{dg(r_i)}{dr}\right|^{-1}.\label{eq:zero1}
 \end{align}
 
-When $|\bv| > 0$ we need to integrate over the intersection of the two spherical
-caps which only intersect when
+When $N > 1$ and $M = 1$ we can interpret the delta function as sifting over the (potentially infinite) set of zeros of $g(\mb{r})$
 \begin{align}
-  |\bvpar| < \sqrt{\nu_m^2 - (|\bvperp| - \nu_m\sin\alpha)^2} - \nu_m\cos\alpha. 
+  \int_{\mbb{R}^N}d\mb{r}\,\delta(g(\mb{r}))f(\mb{r}) = \int_{g^{-1}(0)}d\sigma(\mb{r})f(\mb{r})|\nabla g(\mb{r})|^{-1},\label{eq:zero2}
 \end{align}
-Therefore, the transfer function is zero when this condition is not satisfied.
+where $d\sigma(\mb{r})$ is an appropriate measure for the solution set, and $|\nabla g(\mb{r})|$ denotes the gradient magnitude evaluated at $\mb{r}$.
 
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.3]{../figures/caps/general.pdf}
-  \includegraphics[scale=0.25]{../figures/caps/spherical.pdf}\hspace{0.5em}
-  \includegraphics[scale=0.28]{../figures/caps/cylindrical.pdf}
-  \caption{Geometric constructions and coordinate systems for performing the three-dimensional autocorrelation.
-(Top) Two spherical caps with spherical radius $\nu_m = n_o/\lambda$ and base diameter $\nu_c = 2\text{NA}/\lambda$ are shifted by $\bv$ and intersect along a circular arc in the plane perpendicular to $\bv$.
-(Bottom left) We define a spherical coordinate system for each cap.
-These coordinate systems  are most convenient for expressing the individual coherent transfer functions.
-(Bottom right) We define a cylindrical coordinate system with the long axis of the cylinder parallel to the shift direction $\bv$ and the azimuthal angle $\beta_\tau$ defined with respect to the lowest point of each cylindrical slice.
-This coordinate system is most convenient for integrating over the circular arc of intersection.}
-  \label{fig:caps}
-\end{figure}
+When $M > 1$ then $\mb{g}$ is a vector-valued function, and $\delta(\mb{g}(\mb{r})$ can be used to manipulate the product of multiple delta functions.
+For example, we can rewrite $\delta(g_1(\mb{r}))\delta(g_2(\mb{r}))$ as $\delta(\mb{g}(\mb{r}))$.
+When $N = M > 1$
+we interpret the delta function in a familiar way
+\begin{align}
+  \int_{\mbb{R}^N}d\mb{r}\,\delta(\mb{g}(\mb{r}))f(\mb{r}) = \int_{\mb{g}^{-1}(0)}d\sigma(\mb{r})f(\mb{r})\left|\frac{\partial(g_1,\dots,g_M)}{\partial(r_1,\dots,r_N)}(\mb{r})\right|^{-1},
+\end{align}
+where $\left|\frac{\partial(g_1,\dots,g_M)}{\partial(r_1,\dots,r_N)}(\mb{r})\right|$ denotes the Jacobian determinant evaluated at $\mb{r}$.
 
+The final case we will consider is when $N > M > 1$ which we can interpret with
+\begin{align}
+  \int_{\mbb{R}^N}d\mb{r}\,\delta(\mb{g}(\mb{r}))f(\mb{r}) = \int_{\mb{g}^{-1}(0)}d\sigma(\mb{r})f(\mb{r})\left|\frac{\partial(g_1,\dots,g_M)}{\partial(r^*_1,\dots,r^*_M)}(\mb{r})\right|^{-1},\label{eq:transversedelta}
+\end{align}
+where $r_1^*,\dots,r_M^*$ form an orthogonal basis for the tangent space of the solution set $\mb{g}^{-1}(0)$, and $\left|\frac{\partial(g_1,\dots,g_M)}{\partial(r^*_1,\dots,r^*_M)}(\mb{r})\right|$ denotes the Jacobian determinant in the tangent space evaluated at $\mb{r}$.
+For example, if $N = 3$, $M = 2$ and $\mb{g}(\mb{r}) = [2x, 3z]$, then the solution set is the $y$ axis.
+We can use the $x$ and $z$ unit vectors as a basis for the tangent space of the solution set, so we can write
+\begin{align}
+  \int_{\mbb{R}^3}dxdydz\,\delta\left(\begin{bmatrix}2x\\3z\end{bmatrix}\right)f(x,y,z) = \frac{1}{6}\int_{\mbb{R}}dy f(0,y,0).
+\end{align}
+
+In these examples we have been interpreting delta functions by sifting functions with a one-dimensional output $f:\mbb{R}^N\rightarrow \mbb{R}$, but these interpretations work equally well for functions with multidimensional outputs $\mb{f}:\mbb{R}^N\rightarrow \mbb{R}^P$.
+
+The rules in this section can be used to manipulate delta functions that appear outside integrals. For example, we can use Eq. \eqref{eq:zero1} to verify the identity
+\begin{align}
+  \delta(x^2 - 1) = \frac{1}{2}[\delta(x - 1) + \delta(x + 1)]. 
+\end{align}
+Similar identities can be established for any multidimensional delta function by taking care that both the solution set and the appropriate Jacobian determinant are preserved.
+For example, we can use Eq.
+\eqref{eq:zero2} to verify that
+\begin{align}
+   \delta\left(\btpar \pm \sqrt{\nu_m^2 - |\btperp|^2}\right) = \frac{\btpar}{\nu_m}\delta\left(|\bt| - \nu_m\right) = \cos\theta_\tau\delta\left(|\bt| - \nu_m\right).\label{eq:sphereidentity}
+\end{align}
+
+\section{Coordinate systems for evaluating the autocorrelation of a spherical cap}\label{sec:coord}
+In this appendix specify three coordinate systems which will be useful for evaluating the autocorrelation of spherical caps.
 By inspection of Fig.
 \ref{fig:caps}, the intersection of the two shifted spherical caps is a circular arc centered on the origin in the plane perpendicular to the shift direction $\bv$.
-To integrate along this arc it will be convenient to define three new coordinate systems: (1, 2) two spherical coordinate systems defined with respect to the centers of the shifted spheres, and (3) a cylindrical coordinate system with long axis parallel to the shift direction $\bv$.
+To integrate along this arc it will be convenient to define two spherical coordinate systems defined with respect to the centers of the shifted spheres and a cylindrical coordinate system with its long axis parallel to the shift direction $\bv$.
 The shifted spherical coordinate systems are straightforward to derive as
@@
   \end{bmatrix}
-  &= \mb{R}_{\mb{z}}(-\tan^{-1}(\nu_y/\nu_x)\mb{R}_{\mb{y}}(\sin^{-1}(\bvpar/|\bv|))
-  \begin{bmatrix}
+&= \mb{R}_{\mb{z}}(-\tan^{-1}(\nu_y/\nu_x)\mb{R}_{\mb{y}}(\sin^{-1}(\bvpar/|\bv|))\begin{bmatrix}
     \tau_\xi\\
@@
     -\tau_R\cos\beta_\tau
-  \end{bmatrix}\nonumber\\
-  &=
-  \begin{bmatrix}
-    \displaystyle\frac{\nu_x}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_x\cos\beta_\tau - |\bv|\nu_y\sin\beta_\tau)\\[1em]
-    \displaystyle\frac{\nu_y}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_y\cos\beta_\tau + |\bv|\nu_x\sin\beta_\tau)\\[1em]
-    \displaystyle\frac{\bvpar}{|\bv|}\tau_\xi - \frac{|\bvperp|\tau_R}{|\bv|}\cos\beta_\tau
-  \end{bmatrix},\label{eq:cylindrical}
+  \end{bmatrix},
 \end{align}
@@
     0 & 0 & 1
-  \end{bmatrix}.
+  \end{bmatrix}  .
+\end{align}
+Multiplying the matrices and simplifying yields
+\begin{align}
+    \begin{bmatrix}
+    \tau_x\\
+    \tau_y\\
+    \btpar
+  \end{bmatrix}
+  &=
+  \begin{bmatrix}
+    \displaystyle\frac{\nu_x}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_x\cos\beta_\tau - |\bv|\nu_y\sin\beta_\tau)\\[1em]
+    \displaystyle\frac{\nu_y}{|\bv|}\tau_\xi + \frac{\tau_R}{|\bvperp||\bv|}(\bvpar\nu_y\cos\beta_\tau + |\bv|\nu_x\sin\beta_\tau)\\[1em]
+    \displaystyle\frac{\bvpar}{|\bv|}\tau_\xi - \frac{|\bvperp|\tau_R}{|\bv|}\cos\beta_\tau
+  \end{bmatrix}.\label{eq:cylindrical}
 \end{align}
 
-To evaluate the integral we need to express it in our new cylindrical coordinate system.
-We start by considering the pair of delta functions in the integrand $\delta(|\bt - \bv/2| - \nu_m)\,\delta(|\bt + \bv/2| - \nu_m)$.
-The spherical shells intersect in a circle of radius $\nu_\circ = \sqrt{\nu_m^2 - (|\bv|/2)^2}$ centered on the origin so we expect the delta functions to become $\delta(\tau_\xi)\,\delta(\tau_R - \nu_\circ)$ in the cylindrical coordinate system.
-However, we need to preserve the ``strength'' of the delta functions in the new coordinate system (see Bracewell \cite{bracewell2004} for operational rules and see Gelfand and Shilov \cite{gelfand2016} for a detailed discussion), so we normalize by the Jacobian determinant in each coordinate system.
-After accounting for the changing strength of the delta functions we find that
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.3]{../figures/caps/general.pdf}
+  \includegraphics[scale=0.25]{../figures/caps/spherical.pdf}\hspace{0.5em}
+  \includegraphics[scale=0.28]{../figures/caps/cylindrical.pdf}
+  \caption{Geometric constructions and coordinate systems for performing the three-dimensional autocorrelation.
+(Top) Two spherical caps with spherical radius $\nu_m = n_o/\lambda$ and base diameter $\nu_c = 2\text{NA}/\lambda$ are shifted by $\bv$ and intersect along a circular arc in the plane perpendicular to $\bv$.
+(Bottom left) We define a spherical coordinate system for each cap.
+These coordinate systems  are most convenient for expressing the individual coherent transfer functions.
+(Bottom right) We define a cylindrical coordinate system with the long axis of the cylinder parallel to the shift direction $\bv$ and the azimuthal angle $\beta_\tau$ defined with respect to the lowest point of each cylindrical slice.
+This coordinate system is most convenient for integrating over the circular arc of intersection.}
+  \label{fig:caps}
+\end{figure}
+
+\section{Three-dimensional monopole transfer functions}\label{sec:monoauto}
+In this appendix we calculate the three-dimensional monopole transfer function
+by evaluating the integral
 \begin{align}
-  \delta(|\bt - \bv/2| - \nu_m)\,\delta(|\bt + \bv/2| - \nu_m) = \frac{\nu_\circ}{|\bv|}\delta(\tau_\xi)\,\delta(\tau_R - \nu_\circ).
+  H(\bv) \propto \int_{\mbb{R}^3}d\bt\, C(\bt + \bv/2)\,C^*(\bt - \bv/2). \label{eq:3dauto}
 \end{align}
-\add{This step is a prime candidate for an error. I derived this factor
-  $\frac{\nu_\circ}{|\bv|}$ by matching the Jacobian on both sides, but this
-  disagrees with the factor Arnison \cite{arnison2002} uses which is $\propto \frac{1}{|\bv|\nu_\circ}$.
-Arnison's factor doesn't seem to have the correct units...although all of the Sheppard papers seem pretty free-form when it comes to normalizing/units.}
+where the coherent transfer function is
+\begin{align}
+  C(\bt) \propto \,\frac{1}{\nu_m}\sqrt{\cos\theta_{\tau}}\,\delta\left(|\bt| - \nu_m\right)\,\Pi\left(\frac{\theta_{\tau}}{2\alpha}\right).\label{eq:3dctf2}
+\end{align}
+We can interpret the integral in Eq. \eqref{eq:3dauto} as the autocorrelation of a $\sqrt{\cos\theta_\tau}$-weighted spherical cap with radius $\nu_m$ and half angle $\alpha$.
 
-The integrating measure in the cylindrical coordinate system is
+First, we plug Eq. \eqref{eq:3dctf2} into Eq. \eqref{eq:3dauto}, rewrite the delta functions in vector notation, and use the shifted spherical coordinates from Appendix \ref{sec:coord}
 \begin{align}
-  d\bt = \tau_R d\tau_R d\tau_\xi d\beta_\tau,
+  H(\bv) \propto \frac{1}{\nu_m^2}\int_{\mbb{R}^3}d\bt\,\delta\left(\begin{bmatrix}|\bt + \bv/2| - \nu_m\\ |\bt - \bv/2| - \nu_m \end{bmatrix}\right)\sqrt{\cos\theta_{\tau_1}\cos\theta_{\tau_2}}\,\Pi\left(\frac{\theta_{\tau_1}}{2\alpha}\right)\Pi\left(\frac{\theta_{\tau_2}}{2\alpha}\right).
 \end{align}
-so we can write the integral as 
+Next, we calculate all of the pieces we need to apply Eq.
+\eqref{eq:transversedelta} from Appendix \ref{sec:delta}.
+First, the argument of the delta function is zero on a circle with radius $\nu_\circ = \sqrt{\nu_m^2 - (|\bv|/2)}$.
+We will integrate over the circle in cylindrical coordinates (see Appendix \ref{sec:coord}) using the measure $\nu_\circ d\beta_\tau$.
+Next, we calculate the transverse Jacobian determinant on the circle of intersection.
+The transverse Jacobian determinant will be the same for all points around the circle of intersection and for all shift directions (by the symmetry of the spheres), so we only calculate the transverse Jacobian for shifts along the $\mb{x}$ axis at the point of intersection $\bs{\tau}^* = [0, 0, \nu_\circ]$.
+We will use the $x$ and $z$ directions as a basis for the tangent space and calculate the transverse Jacobean determinant as
 \begin{align}
-  H(\bv) \propto \frac{1}{\nu_c^2}\frac{\nu_\circ}{|\bv|}\int_{\mbb{R}}d\tau_\xi\int_{0}^{\infty}\tau_Rd\tau_R\int_{-\pi}^{\pi}d\beta_\tau\, \sqrt{\cos\tau_{\theta_1}\cos\tau_{\theta_2}}\,\delta(\tau_\xi)\delta(\tau_R - \nu_\circ)\,\Pi\left(\frac{\tau_{\theta_1}}{2\alpha}\right)\Pi\left(\frac{\tau_{\theta_2}}{2\alpha}\right).
+  \left|\begin{bmatrix}\frac{\partial g_1}{\partial x}(\bs{\tau}^*)&\frac{\partial g_1}{\partial z}(\bs{\tau}^*)\\\frac{\partial g_2}{\partial x}(\bs{\tau}^*)&\frac{\partial g_2}{\partial z}(\bs{\tau}^*)\end{bmatrix}\right| = \left|\begin{bmatrix}\frac{-|\bv|}{2\nu_m}&\frac{\nu_\circ}{\nu_m}\\\frac{|\bv|}{2\nu_m}&\frac{\nu_\circ}{\nu_m}\end{bmatrix}\right| = \frac{|\bv|\nu_\circ}{\nu_m^2}.
+\end{align}
+Bringing the solution set, the measure, and the inverse transverse Jacobian together yields
+\begin{align}
+  H(\bv) = \frac{1}{|\bv|}\int_0^{2\pi} d\beta_\tau\,\sqrt{\cos\theta_{\tau_1}\cos\theta_{\tau_2}}\,\Pi\left(\frac{\theta_{\tau_1}}{2\alpha}\right)\Pi\left(\frac{\theta_{\tau_2}}{2\alpha}\right).\label{eq:lastform}
 \end{align}
 
-Next, we express the integrand in cylindrical coordinates.
+Next, we express the integrand in terms of $\beta_\tau$.
 Equating the $\btpar$ components in Eqs.
@@
 We can also use Eq.
-\eqref{eq:angles} to find the limits of integration for $\tau_\beta$ by setting $\tau_{\theta_2} \rightarrow \alpha$ then solving for $\tau_\beta$ to find the maximum azimuthal angle $\beta_m$
+\eqref{eq:angles} to find the limits of integration for $\beta_\tau$ by setting $\tau_{\theta_2} \rightarrow \alpha$ then solving for $\beta_\tau$ to find the maximum azimuthal angle $\beta_m$
 \begin{align}
@@
 
-Bringing everything together yields the one-dimensional integral
+Now that we have written the integrand in terms of $\beta_tau$, we can write Eq. \eqref{eq:lastform} as
 \begin{align}
-  H(\bv) \propto \frac{\nu_\circ^2\bvpar}{2\nu_c^2|\bv|\nu_m}\int_{-\beta_m}^{\beta_m}d\tau_\beta\, \sqrt{p^2\cos^2\beta_\tau - 1}, 
+  H(\bv) \propto \frac{\bvpar}{|\bv|\nu_m}\int_{0}^{\beta_m}d\beta_\tau\, \sqrt{p^2\cos^2\beta_\tau - 1}, 
 \end{align}
@@
 \begin{align}
-  H(\bv) \propto \frac{\tau_{\circ}^2\bvpar}{\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right),
+  H(\bv) \propto \frac{\bvpar}{|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right), \label{eq:intresult}
 \end{align}
@@
 
-After normalization, the complete transfer function is given by
+The spherical shells only intersect when 
 \begin{align}
-  H(\bv) = \delta(|\bv|) + \frac{4\tau_{\circ}^2\bvpar}{\pi\nu_c^2|\bv|\nu_m}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right).
+|\bvpar| < \sqrt{\nu_m^2 - (|\bvperp| - \nu_m\sin\alpha)^2} - \nu_m\cos\alpha, 
+\end{align}
+so the transfer function will be zero when this condition is not satisfied.
+We can rewrite this condition conveniently by defining a function
+\begin{align}
+  \infty(x, z, \alpha) = \Pi\left(\frac{|z|}{2(\sqrt{1 - (|x| - \sin\alpha)^2} - \cos\alpha)}\right).
+\end{align}
+
+The result in Eq.
+\eqref{eq:intresult} diverges as $|\bv| \rightarrow 0$ so the transfer function is still undefined at that point.
+Instead, we calculate the value of the transfer function at $\bv = 0$ by applying the central-ordinate theorem.
+The solid angle of the sphere collected by the optical system is the value of the transfer functions $\bv = 0$ so $H(0) = 4\pi\sin^2(\alpha/2)$.
+
+Stitching together the two solutions and accounting for the region of validity yields the complete transfer function
+\begin{align}
+  H(\bv) \propto 4\pi\sin^2(\alpha/2)\,\delta(|\bv|) + \frac{|\bvpar|}{\nu_m|\bv|}\sqrt{p^2 - 1}\,E\left(\beta_m, \frac{p}{\sqrt{p^2 - 1}}\right)\infty\left(\frac{|\bvperp|}{\nu_m}, \frac{\bvpar}{\nu_m}, \alpha \right).
 \end{align}
@@
 \begin{align}
-  C(\bt) \propp \frac{1}{\nu_c}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right). \label{eq:ctf}
+  C(\bt) \propp \frac{1}{\nu_m}\delta\left(\btpar - \nu_m + |\btperp|^2/2\nu_m\right)\,\Pi\left(\frac{|\btperp|}{\nu_c}\right). \label{eq:ctf}
 \end{align}
@@
 \begin{align}
-  C^{(d)}(\btperp, r^{\mypar}) \propp \frac{1}{\nu_c}\text{exp}(2\pi i r^{\mypar}[-\nu_m + |\btperp|^2/2\nu_m])\Pi\left(\frac{|\btperp|}{\nu_c}\right), \label{eq:defctf}
+  C^{(d)}(\btperp, r^{\mypar}) \propp \frac{1}{\nu_m}\text{exp}(2\pi i r^{\mypar}[-\nu_m + |\btperp|^2/2\nu_m])\Pi\left(\frac{|\btperp|}{\nu_c}\right), \label{eq:defctf}
 \end{align}
-which we can interpret as a disk with uniform magnitude and quadratic phase factor that depends on the defocus $r^{\mypar}$.
+which we can interpret as a disk with uniform magnitude and a quadratic phase factor that depends on the defocus $r^{\mypar}$.
 
-To evaluate the three-dimensional transfer function at $|\bv| = 0$ we start by evaluating the defocused transfer function at $|\bvperp| = 0$
+Next, we evaluate the defocused transfer function by plugging Eq. \eqref{eq:defctf} into Eq. \eqref{eq:defautocorr} and simplifying the complex exponentials
 \begin{align}
-  H^{(d)}(\bv, r^{\mypar}) = \frac{\pi}{4}. \label{eq:result}
+  H^{(d)}(\bvperp,r^{\mypar}) \propp \frac{1}{\nu_m^2}\int_{\mbb{R}^2}d\btperp\, \text{exp}(2\pi i r^{\mypar}[\btperp\cdot\bvperp/\nu_m])\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).\label{eq:defocusresult}
 \end{align}
-After plugging \eqref{eq:result} into Eq. \eqref{eq:def3dtf} and evaluating the Fourier transform we find that 
+Plugging Eq. \eqref{eq:defocusresult} into Eq. \eqref{eq:def3dtf} and evaluating the
+Fourier transform yields 
 \begin{align}
-  H(\bv) = \frac{\pi}{4}\delta(|\bv|). 
-\end{align}
-
-When $|\bv| > 0$ we need to integrate over the intersection of the two truncated paraboloids which only intersect when
-\begin{align}
-  |\bvpar| < -\frac{1}{2\nu_m}|\bvperp|(|\bvperp| - \nu_c). 
-\end{align}
-Therefore, the paraxial transfer function is zero when this condition is not satisfied.
-
-First we evaluate the defocused transfer function by plugging Eq. \eqref{eq:defctf} into Eq. \eqref{eq:defautocorr}
-\begin{align}
-  H^{(d)}(\bvperp,r^{\mypar}) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \text{exp}(2\pi i r^{\mypar}[|\btperp + \bvperp/2|^2/2\nu_m])\, \text{exp}(-2\pi i r^{\mypar}[|\btperp - \bvperp/2|^2/2\nu_m])\nonumber\\\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right),
-\end{align}
-then simplifying the complex exponentials
-\begin{align}
-  H^{(d)}(\bvperp,r^{\mypar}) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \text{exp}(2\pi i r^{\mypar}[\btperp\cdot\bvperp/\nu_m])\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).\label{eq:defocusresult}
-\end{align}
-Next, we plug Eq. \eqref{eq:defocusresult} into Eq. \eqref{eq:def3dtf} and evaluate the
-Fourier transform to find that 
-\begin{align}
-  H(\bv) \propp \frac{1}{\nu_c^2}\int_{\mbb{R}^2}d\btperp\, \delta(\bvpar - \btperp\cdot\bvperp/\nu_m)\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).
+  H(\bv) \propp \frac{1}{\nu_m^2}\int_{\mbb{R}^2}d\btperp\, \delta(\bvpar - \btperp\cdot\bvperp/\nu_m)\Pi\left(\frac{|\btperp + \bvperp/2|}{\nu_c}\right) \Pi\left(\frac{|\btperp - \bvperp/2|}{\nu_c}\right).
 \end{align}
@@
 Within the intersection of the shifted circles this line has length $2\sqrt{(\nu_c/2)^2 - ([\nu_m|\bvpar|/|\bvperp|] + [|\bvperp|/2])^2}$.
-Finally, the ``strength'' of the delta function is $\nu_m/|\bvperp|$, so the integral evaluates to
+Finally, the transverse Jacobian (the transverse derivative in this case) of the function is $|\bvperp|/\nu_m$, so the integral evaluates to
 \begin{align}
-  H(\bv) \propp \frac{2\nu_m}{\nu_c^2|\bvperp|}\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}. 
+  H(\bv) \propp \frac{2}{\nu_m|\bvperp|}\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}. \label{eq:intresult3}
 \end{align}
 
-After normalization, the complete paraxial transfer function is 
+The truncated paraboloids only intersect when
 \begin{align}
-  H(\bv) \eqp \delta(|\bv|) + \frac{8\nu_m}{\pi\nu_c^2|\bvperp|}\text{Re}\left\{\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}\right\}.
+  |\bvpar| < -\frac{1}{2\nu_m}|\bvperp|(|\bvperp| - \nu_c),
 \end{align}
+so the paraxial transfer function is zero when this condition is not satisfied.
+We can incorporate this condition conveniently by only considering the real part of the expression in Eq.
+\eqref{eq:intresult3}.
 
+Once again, the result in Eq. \eqref{eq:intresult3} diverges as $|\bv| \rightarrow 0$, but we can use the central-ordinate theorem to find that $H(0) = \frac{\pi\nu_c^2}{4\nu_m^2}$.
+
+The complete paraxial transfer function is 
+\begin{align}
+  H(\bv) \propp \frac{\pi\nu_c^2}{4\nu_m^2}\delta(|\bv|) + \frac{2}{\nu_m|\bvperp|}\text{Re}\left\{\sqrt{\left(\frac{\nu_c}{2}\right)^2 - \left(\frac{\nu_m|\bvpar|}{|\bvperp|} + \frac{|\bvperp|}{2}\right)^2}\right\}.
+\end{align}
 We can rewrite the paraxial transfer function in a scaled form 
 \begin{align}
-  H(\bv) \eqp \delta(|\bv|) + \frac{8\nu_m}{\pi\nu_c^2}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
+  H(\bv) \eqp \frac{\pi\nu_c^2}{4\nu_m^2}\delta(|\bv|) + \frac{4}{\nu_m}\text{nez}\left(\frac{|\bvperp|}{\nu_c}, \frac{2\nu_m|\bvpar|}{\nu_c^2}\right),
 \end{align}
@@
 \begin{align}
-  H(\bvperp) \eqp \int_{\mbb{R}}d\bvpar\, H(\bv) = \frac{4}{\pi}\text{chat}_0\left(\frac{|\bvperp|}{\nu_c}\right), 
+  H(\bvperp) \eqp \int_{\mbb{R}}d\bvpar\, H(\bv) = \frac{4\nu_c^2}{\pi\nu_m^2}\text{chat}_0\left(\frac{|\bvperp|}{\nu_c}\right), 
 \end{align}
@@
 \end{align}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.85]{../figures/monopole-psf/dpsf.pdf}
-  \caption{Comparison of high-aperture and paraxial three-dimensional transfer functions for $\text{NA} = (1.00, 1.25, 1.50)$, $n_o = 1.5$, and $\lambda = 500\,\text{nm}$.
-\add{Notice the units: input spatial frequencies are in  m${}^{-1}$ and the output is in m${}^{+1}$.
-I have overlaid each plot with two lines: a blue line which is the paraxial transverse transfer function ($\text{chat}(\nu/\nu_c)$) and a green line which is the numerical integral of the 3D transfer function over $\bvpar$.
-The blue and green lines should have their own $y$ axis, but I'm reusing the left $y$ axis without units.
-In the paraxial case these lines agree which is a good check that my results are correct.
-In the high-aperture case the green line is not normalized, and I expect the green line to be lower than the blue line at low frequencies and higher than the blue line at high frequencies (see Barakat \cite{barakat1963}).
-Therefore, I'm searching for an error that makes the high-aperture transfer function too large everywhere (normalization) and too small at high-frequencies.}}
-  \label{fig:compare}
-\end{figure}
-
 \end{document}
